---
title: "Figure 1: CRP-Guided Strategy Survival Curves"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05", "06"),
  funs = c("prediction_functions"),
  packages = c("here", "ggplot2", "dplyr", "scales", "cowplot",
               "flexsurv", "survival"),
  set_theme = FALSE
)

theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    legend.position = "bottom",
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 9)
  )
)
```

```{r load-data, include=FALSE}
# Get treatment level references
exp_rx <- levels(data_complete$Rx)[2]
ctrl_rx <- levels(data_complete$Rx)[1]
crp_prev <- strategies_df$prevalence[strategies_df$id == "crp"]

cat("CRP prevalence:", crp_prev, "\n")
cat("Treatment levels:", ctrl_rx, "(control),", exp_rx, "(experimental)\n")

# Plotted subsets (issue #157). The parametric curves and their intervals are
# predicted for exactly these patients (own covariates, the arm they were
# actually in), so each overlay is a fit check on matched patients. The
# economic model's curves are standardised to all complete-case patients with
# Rx set by strategy (the `predictions` object) and are not shown.
data_control <- data_complete[data_complete$Rx == ctrl_rx, ]

# CRP-guided strategy: CRP+ patients from the experimental arm + CRP- patients
# from the control arm, the observed analogue of biomarker-guided assignment.
# The CRP+ share of this cohort is its own mixing weight.
data_crp_guided <- rbind(
  data_complete[as.numeric(as.character(data_complete$crp)) == 1 &
                data_complete$Rx == exp_rx, ],
  data_complete[as.numeric(as.character(data_complete$crp)) == 0 &
                data_complete$Rx == ctrl_rx, ]
)
n_crp_guided_pos <- sum(as.numeric(as.character(data_crp_guided$crp)) == 1)
```

```{r fit-models, include=FALSE}
# ===============================================================================
# Base-case curves from the selected joint economic model (models$best_fit,
# the ordering-constrained pair chosen in script 04; no refit, no hard-coded
# distribution), predicted for the plotted subsets
# ===============================================================================

# Helper for population-averaged predictions
predict_population_avg <- function(model, newdata, time_points) {
  tryCatch({
    pred <- predict(model, newdata = newdata, type = "survival", times = time_points)
    if (".pred" %in% names(pred)) {
      surv_probs <- lapply(pred$.pred, function(x) x$.pred_survival)
      surv_matrix <- do.call(cbind, surv_probs)
      return(rowMeans(surv_matrix, na.rm = TRUE))
    } else if (is.list(pred) && length(pred) > 0 && is.data.frame(pred[[1]])) {
      surv_probs <- sapply(pred, function(x) x$est)
      if (is.matrix(surv_probs)) {
        return(rowMeans(surv_probs, na.rm = TRUE))
      } else {
        return(surv_probs)
      }
    } else {
      return(NULL)
    }
  }, error = function(e) {
    return(NULL)
  })
}

# Fit models and generate base-case predictions
fitted_models <- list()
base_predictions <- list()

for (model_name in "joint") {
  fitted_models[[model_name]] <- list(os = models$best_fit$os, pfs = models$best_fit$pfs)
  base_predictions[[model_name]] <- list()

  if (is.null(fitted_models[[model_name]]$os) || is.null(fitted_models[[model_name]]$pfs)) next

  for (outcome in c("os", "pfs")) {
    # Control: the control-arm patients with their own covariates
    base_predictions[[model_name]][[paste0("control_", outcome)]] <-
      predict_population_avg(fitted_models[[model_name]][[outcome]], data_control, time_points)
    # CRP-guided: the observed guided cohort, each patient on the arm they were in
    base_predictions[[model_name]][[paste0("crp_", outcome)]] <-
      predict_population_avg(fitted_models[[model_name]][[outcome]], data_crp_guided, time_points)
  }
}

cat("Base-case predictions generated for models:",
    paste(names(base_predictions), collapse = ", "), "\n")
```

```{r bootstrap-ci, include=FALSE}
# ===============================================================================
# Load sampling caches and compute 95% bootstrap CIs
# ===============================================================================

n_boot_subset <- 500  # Subset of 5000 for speed

ci_data <- list()

for (model_name in "joint") {
  # Already validated without regeneration by setup_report().
  sampling_models_cache <- sampling_models

  joint_cache <- get_joint_sampling_models(sampling_models_cache)
  n_available <- min(n_boot_subset, joint_cache$n_samples)
  set.seed(analysis_seed)
  boot_indices <- sample(seq_len(joint_cache$n_samples), n_available)

  ci_data[[model_name]] <- list()

  for (outcome in c("os", "pfs")) {
    # Storage for bootstrap predictions
    control_boot <- matrix(NA, nrow = length(time_points), ncol = n_available)
    crp_boot <- matrix(NA, nrow = length(time_points), ncol = n_available)

    for (j in seq_along(boot_indices)) {
      idx <- boot_indices[j]

      # Both curves come from the SAME sampled joint model (issue #151), each
      # predicted for the same subset as its base-case line (issue #157).
      sampled_idx <- tryCatch(sampled_survival_models(joint_cache, idx),
                              error = function(e) NULL)
      boot_model <- sampled_idx[[outcome]]$model
      if (!is.null(boot_model)) {
        ctrl_pred <- tryCatch(
          predict_population_avg(boot_model, data_control, time_points),
          error = function(e) NULL
        )
        if (!is.null(ctrl_pred)) control_boot[, j] <- ctrl_pred

        crp_pred <- tryCatch(
          predict_population_avg(boot_model, data_crp_guided, time_points),
          error = function(e) NULL
        )
        if (!is.null(crp_pred)) crp_boot[, j] <- crp_pred
      }

      if (j %% 100 == 0) cat("  ", model_name, outcome, ":", j, "/", n_available, "\n")
    }

    # Compute percentile CIs
    ci_data[[model_name]][[paste0("control_", outcome, "_lower")]] <-
      apply(control_boot, 1, quantile, probs = 0.025, na.rm = TRUE)
    ci_data[[model_name]][[paste0("control_", outcome, "_upper")]] <-
      apply(control_boot, 1, quantile, probs = 0.975, na.rm = TRUE)
    ci_data[[model_name]][[paste0("crp_", outcome, "_lower")]] <-
      apply(crp_boot, 1, quantile, probs = 0.025, na.rm = TRUE)
    ci_data[[model_name]][[paste0("crp_", outcome, "_upper")]] <-
      apply(crp_boot, 1, quantile, probs = 0.975, na.rm = TRUE)
  }

  # Free memory
  rm(sampling_models_cache, joint_cache)
  gc()

  cat("Bootstrap CIs computed for", model_name, "\n")
}

has_ci <- length(ci_data) > 0
cat("Bootstrap CI available:", has_ci, "\n")
```

```{r km-data, include=FALSE}
# ===============================================================================
# Compute Kaplan-Meier curves from observed data
# ===============================================================================

# Same subsets as the parametric curves (defined in the load-data chunk)
km_control_os <- survfit(Surv(OSwk, Death) ~ 1, data = data_control)
km_control_pfs <- survfit(Surv(PFSwk, Progression) ~ 1, data = data_control)

km_crp_os <- survfit(Surv(OSwk, Death) ~ 1, data = data_crp_guided)
km_crp_pfs <- survfit(Surv(PFSwk, Progression) ~ 1, data = data_crp_guided)

km_data_list <- list(
  control_os = extract_km_data(km_control_os),
  control_pfs = extract_km_data(km_control_pfs),
  crp_os = extract_km_data(km_crp_os),
  crp_pfs = extract_km_data(km_crp_pfs)
)

cat("KM curves computed. Control arm:", nrow(data_control), "patients.",
    "CRP-guided:", nrow(data_crp_guided), "patients.\n")
```

```{r create-panels, include=FALSE}
# ===============================================================================
# Build individual panels: 3 models x 2 outcomes
# ===============================================================================

model_display <- c(joint = "Joint model")
strategy_colors <- c("Control" = "gray50", "CRP Strategy" = "#E69F00")

create_survival_panel <- function(model_name, outcome, show_legend = FALSE) {
  outcome_label <- if (outcome == "os") "Overall Survival" else "Progression-Free Survival"
  km_ctrl_key <- paste0("control_", outcome)
  km_crp_key <- paste0("crp_", outcome)
  pred_ctrl_key <- paste0("control_", outcome)
  pred_crp_key <- paste0("crp_", outcome)

  # Build plot data: parametric base-case curves
  plot_df <- data.frame()

  ctrl_pred <- base_predictions[[model_name]][[pred_ctrl_key]]
  crp_pred <- base_predictions[[model_name]][[pred_crp_key]]

  if (!is.null(ctrl_pred)) {
    plot_df <- rbind(plot_df, data.frame(
      time = time_points, surv = ctrl_pred, group = "Control"))
  }
  if (!is.null(crp_pred)) {
    plot_df <- rbind(plot_df, data.frame(
      time = time_points, surv = crp_pred, group = "CRP Strategy"))
  }

  if (nrow(plot_df) == 0) return(NULL)

  p <- ggplot()

  # Layer 1: Bootstrap CI ribbon (if available)
  if (model_name %in% names(ci_data)) {
    ci <- ci_data[[model_name]]

    ctrl_lower <- ci[[paste0("control_", outcome, "_lower")]]
    ctrl_upper <- ci[[paste0("control_", outcome, "_upper")]]
    crp_lower <- ci[[paste0("crp_", outcome, "_lower")]]
    crp_upper <- ci[[paste0("crp_", outcome, "_upper")]]

    if (!is.null(ctrl_lower) && !all(is.na(ctrl_lower))) {
      ci_ctrl_df <- data.frame(time = time_points, lower = ctrl_lower, upper = ctrl_upper)
      p <- p + geom_ribbon(data = ci_ctrl_df, aes(x = time, ymin = lower, ymax = upper),
                           fill = "gray50", alpha = 0.15)
    }
    if (!is.null(crp_lower) && !all(is.na(crp_lower))) {
      ci_crp_df <- data.frame(time = time_points, lower = crp_lower, upper = crp_upper)
      p <- p + geom_ribbon(data = ci_crp_df, aes(x = time, ymin = lower, ymax = upper),
                           fill = "#E69F00", alpha = 0.15)
    }
  }

  # Layer 2: Parametric base-case curves (solid lines)
  p <- p +
    geom_line(data = plot_df, aes(x = time, y = surv, color = group), linewidth = 0.8)

  # Layer 3: KM overlay (step functions)
  km_ctrl <- km_data_list[[km_ctrl_key]]
  km_crp <- km_data_list[[km_crp_key]]

  if (!is.null(km_ctrl) && nrow(km_ctrl) > 0) {
    km_ctrl$group <- "Control"
    p <- p + geom_step(data = km_ctrl, aes(x = time, y = surv, color = group),
                       linetype = "dashed", linewidth = 0.4, alpha = 0.7)
  }
  if (!is.null(km_crp) && nrow(km_crp) > 0) {
    km_crp$group <- "CRP Strategy"
    p <- p + geom_step(data = km_crp, aes(x = time, y = surv, color = group),
                       linetype = "dashed", linewidth = 0.4, alpha = 0.7)
  }

  # Formatting
  p <- p +
    scale_color_manual(values = strategy_colors, name = NULL) +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    scale_x_continuous(
      breaks = seq(0, max(time_points), by = 104),
      labels = function(x) x / 52
    ) +
    labs(x = "Time (years)", y = outcome_label,
         title = outcome_label) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 11, face = "bold", hjust = 0.5),
      panel.grid.minor = element_blank()
    )

  if (show_legend) {
    p <- p + theme(legend.position = "bottom",
                   legend.text = element_text(size = 8))
  } else {
    p <- p + theme(legend.position = "none")
  }

  return(p)
}

# Generate panels for the single joint model (OS, PFS)
panels <- list()
for (model_name in "joint") {
  for (outcome in c("os", "pfs")) {
    key <- paste0(model_name, "_", outcome)
    panels[[key]] <- create_survival_panel(model_name, outcome, show_legend = FALSE)
  }
}
```

```{r combined-figure, fig.width=10, fig.height=5}
# Extract a shared legend from one panel
legend_panel <- create_survival_panel("joint", "os", show_legend = TRUE)
# cowplot::get_legend() returns an empty grob under ggplot2 >= 3.5 (the legend
# grob is now named "guide-box-<position>"), which left the committed figure
# without its legend. Pick the first non-empty guide-box grob instead.
extract_legend <- function(p) {
  g <- ggplot2::ggplotGrob(p)
  idx <- which(grepl("guide-box", g$layout$name))
  for (i in idx) {
    if (!inherits(g$grobs[[i]], "zeroGrob")) return(g$grobs[[i]])
  }
  stop("No legend found in the panel used for the shared legend")
}
shared_legend <- extract_legend(legend_panel)

# Assemble 2 columns x 1 row grid (OS, PFS) for the single joint model
plot_grid_main <- plot_grid(
  panels$joint_os, panels$joint_pfs,
  ncol = 2, nrow = 1,
  labels = c("A", "B"),
  label_size = 14
)

# Add shared legend at bottom
combined_plot <- plot_grid(
  plot_grid_main, shared_legend,
  ncol = 1, rel_heights = c(1, 0.08)
)

print(combined_plot)
```

```{r save-figure, include=FALSE}
figs_dir <- here("outputs", "figs")
if (!dir.exists(figs_dir)) {
  dir.create(figs_dir, recursive = TRUE)
}

ggsave(
  filename = here("outputs", "figs", "figure1.png"),
  plot = combined_plot,
  width = 10,
  height = 5,
  dpi = 300,
  bg = "white"
)

cat("Figure saved to:", here("outputs", "figs", "figure1.png"), "\n")
```

Figure 1 has been saved to `outputs/figs/figure1.png`.

**Notes.** Solid lines are the selected joint parametric models
(`r models$best_fit$os_distribution` OS, `r models$best_fit$pfs_distribution`
PFS) predicted for each patient in the plotted subset with that patient's own
covariates and actual arm, then averaged; ribbons are 95% percentile intervals
from `r n_boot_subset` of the `r n_samples` multivariate-normal coefficient
draws of the sampling cache, predicted for the same subsets. Dashed step lines
are the Kaplan-Meier curves of the same patients: the `r nrow(data_control)`
control-arm patients (Control) and the `r nrow(data_crp_guided)` patients of
the observed CRP-guided cohort (`r n_crp_guided_pos` CRP-positive patients from
the experimental arm and `r nrow(data_crp_guided) - n_crp_guided_pos`
CRP-negative patients from the control arm). The economic model uses the same
fitted models standardised to all `r nrow(data_complete)` complete-case
patients with treatment set by strategy and the canonical CRP prevalence
(`r sprintf("%.1f%%", 100 * crp_prev)`); those standardised curves are not
shown because their covariate mix differs from the subsets (issue #157).
