---
title: "Poster: Modeling Multiple Biomarkers — Correlation, Prognostic vs Predictive Value"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
    toc: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
# ==============================================================================
# Vignette supporting the SMDM poster:
#   "Modeling Multiple Biomarkers in Precision Oncology:
#    How Ignoring Biomarker Correlations Can Reverse Clinical Conclusions"
#
# STANDALONE — re-introduces TLR (a post-randomization mediator that the main
# economic pipeline deliberately EXCLUDES) only to illustrate the poster's
# methodological point. Does not modify the main pipeline.
#
# Outputs: outputs/figs/poster_forest.png, figs/poster_ceac.png, tables/poster_cea.csv,
#          outputs/tables/poster_forest_data.csv, tables/poster_ceac_data.csv
#
# Script 06 is sourced for the sampling cache (joint-model coefficient draws)
# and sample_survival_coefficients(), which the CEAC section reuses for the
# single-biomarker models (issue #157).
# ==============================================================================
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05", "06"),
  funs = c("model_fun", "calculate_outcomes", "prediction_functions",
           "report_format", "cea_helpers", "psa_functions"),
  packages = c("here", "survival", "flexsurv", "coxphf", "dplyr", "ggplot2",
               "scales", "dampack", "knitr", "kableExtra"),
  set_theme = FALSE
)

pipeline_psa <- load_current_psa_cache()
pipeline_psa_params <- load_psa_params_cache(required = TRUE, seed = analysis_seed,
                                              n_sim = pipeline_psa$n_sim)

# model_fun() and the prediction helpers resolve these accessors in their source
# environment. Temporarily extend that environment for the poster-only TLR
# analysis, then restore the exact canonical function objects even if it errors.
with_poster_model_config <- function(strategies, biomarkers, code) {
  model_env <- environment(model_fun)
  original_get_strategies <- get("get_strategies", envir = model_env)
  original_get_biomarkers <- get("get_biomarkers", envir = model_env)
  original_biomarker_cost_key <- get("biomarker_cost_key", envir = model_env)
  original_strategy_display_name <- get("strategy_display_name", envir = model_env)
  force(strategies)
  force(biomarkers)

  assign("get_strategies", function() strategies, envir = model_env)
  assign("get_biomarkers", function() biomarkers, envir = model_env)
  assign("biomarker_cost_key", function(selected = biomarkers) {
    key_map <- c(
      original_biomarker_cost_key(canonical_biomarkers),
      tlr = "c_test_TLR"
    )
    unknown <- setdiff(selected, names(key_map))
    if (length(unknown) > 0L) stop("Unknown poster biomarkers: ", paste(unknown, collapse = ", "))
    key_map[selected]
  }, envir = model_env)
  assign("strategy_display_name", function(selected = strategies) {
    label_map <- c(
      original_strategy_display_name(canonical_strategies),
      tlr = "TLR"
    )
    label_map[selected]
  }, envir = model_env)
  on.exit({
    assign("get_strategies", original_get_strategies, envir = model_env)
    assign("get_biomarkers", original_get_biomarkers, envir = model_env)
    assign("biomarker_cost_key", original_biomarker_cost_key, envir = model_env)
    assign("strategy_display_name", original_strategy_display_name, envir = model_env)
  }, add = TRUE)

  force(code)
}
```

```{r cohort, include=FALSE}
# Common complete-case cohort for all three biomarkers, so single vs joint
# models are compared on the SAME patients (isolates adjustment, not sample size).
req <- c("Age","sex","Rx","crp","tlr","tmb_braf","OSwk","Death","PFSwk","Progression")
d3  <- data[stats::complete.cases(data[, req]), ]
n3  <- nrow(d3)

bms      <- c("crp","tlr","tmb_braf")
bm_label <- c(crp = "CRP", tlr = "TLR (mediator)", tmb_braf = "TMB/BRAF")
# Use the ordering-constrained pair selected by script 04 (currently gamma / gamma);
# the former hard-coded Weibull / log-normal pair lets PFS exceed OS under the
# progression-or-death PFS endpoint (issue #149).
dist_for <- list(OS = models$best_fit$os_distribution, PFS = models$best_fit$pfs_distribution)
surv_lhs <- list(OS = "Surv(OSwk, Death)", PFS = "Surv(PFSwk, Progression)")
```

```{r forest-data, include=FALSE}
# Biomarker MAIN effects (prognostic) and treatment x biomarker INTERACTIONS
# (predictive), estimated with Firth-corrected Cox PH (penalised likelihood;
# corrects small-sample bias / monotone-likelihood separation) in the SAME n=65
# cohort, two ways: single-biomarker (one biomarker at a time) and joint (all
# biomarkers and all biomarker x treatment terms in one model).
# HR < 1 = lower hazard. Interaction: alternating immunotherapy more beneficial
# in biomarker-positive. Main effect: better prognosis in the control arm.
flhs <- list(PFS = "Surv(PFSwk, Progression)", OS = "Surv(OSwk, Death)")

row_mi <- function(fit, ep, bm, estimator) {
  cf <- fit$coefficients
  mn <- paste0(bm, "1"); it <- names(cf)[grepl(":", names(cf)) & grepl(bm, names(cf))]
  rbind(
    data.frame(endpoint=ep, biomarker=bm, effect="Main effect (prognostic)", estimator=estimator,
               HR=exp(cf[mn]), lo=fit$ci.lower[mn], hi=fit$ci.upper[mn], row.names=NULL),
    data.frame(endpoint=ep, biomarker=bm, effect="Interaction (predictive)", estimator=estimator,
               HR=exp(cf[it]), lo=fit$ci.lower[it], hi=fit$ci.upper[it], row.names=NULL))
}
firth_single <- function(ep, bm)
  row_mi(suppressWarnings(coxphf(as.formula(paste0(flhs[[ep]], " ~ Age + sex + Rx*", bm)),
         data = d3, firth = TRUE, pl = TRUE, maxit = 400, maxstep = 0.1)),
         ep, bm, "Single-biomarker (Firth Cox)")
firth_joint <- function(ep) {
  fit <- suppressWarnings(coxphf(as.formula(paste0(flhs[[ep]],
            " ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx")),
            data = d3, firth = TRUE, pl = TRUE, maxit = 400, maxstep = 0.1))
  do.call(rbind, lapply(bms, function(bm) row_mi(fit, ep, bm, "Joint (Firth Cox)")))
}

forest_df <- rbind(
  do.call(rbind, lapply(c("PFS","OS"), function(ep) do.call(rbind, lapply(bms, firth_single, ep = ep)))),
  do.call(rbind, lapply(c("PFS","OS"), firth_joint)))
for (cl in c("HR","lo","hi")) forest_df[[cl]] <- as.numeric(forest_df[[cl]])
lab <- c(crp = "CRP", tmb_braf = "TMB/BRAF", tlr = "TLR")
forest_df$biomarker <- factor(lab[forest_df$biomarker], levels = c("TMB/BRAF","CRP","TLR"))  # CRP in middle
forest_df$endpoint  <- factor(forest_df$endpoint, levels = c("PFS","OS"))
forest_df$effect    <- factor(forest_df$effect,
                              levels = c("Main effect (prognostic)","Interaction (predictive)"))  # prognostic on top
forest_df$estimator <- factor(forest_df$estimator,
                              levels = c("Single-biomarker (Firth Cox)","Joint (Firth Cox)"))
```

> **Why TLR is excluded from the economic model.** Target lesion reduction (TLR) is shown below as an illustrative third candidate, but it is *not* used as an economic treatment-selection biomarker for two reasons. (1) It lies **on the causal pathway** between treatment and survival — a post-randomization mediator — so building a selection strategy on it (or conditioning on it) would bias the estimated treatment effect. (2) It is a **dynamic biomarker** measured on follow-up imaging after nivolumab has started, so it cannot inform the treatment-selection decision. Only the two biomarkers available before that decision enter the economic model: TMB/BRAF (baseline NGS) and CRP (week-4 value, measured after two FLOX cycles common to both arms and before the first nivolumab dose).

# Forest plot: prognostic main effects and predictive interactions

```{r forest-plot, fig.width=8, fig.height=6}
#| fig-cap: "Biomarker main effects (prognostic, upper panels) and treatment x biomarker interactions (predictive, lower panels) on the log hazard-ratio scale, estimated by Firth-corrected Cox PH one biomarker at a time (single-biomarker) versus all biomarkers and interactions jointly, in the same n = 65 cohort. HR < 1 favours alternating immunotherapy in biomarker-positive (interaction) or indicates better prognosis in the control arm (main effect). TLR shows a strong prognostic main effect but a null predictive interaction; as a dynamic, post-baseline mediator it is excluded from the economic model. No interaction reaches significance at this sample size."
p_forest <- ggplot(forest_df, aes(x = HR, y = biomarker, colour = estimator, shape = estimator)) +
  geom_vline(xintercept = 1, linetype = "dashed", colour = "grey45") +
  geom_pointrange(aes(xmin = lo, xmax = hi),
                  position = position_dodge(width = 0.6), linewidth = 0.7, fatten = 2.6) +
  facet_grid(effect ~ endpoint) +
  scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4)) +
  scale_colour_manual(values = c("Single-biomarker (Firth Cox)" = "#C0392B",
                                 "Joint (Firth Cox)" = "#1F4E79")) +
  labs(
    x = "Hazard ratio (HR < 1 favours alternating immunotherapy)",
    y = NULL, colour = NULL, shape = NULL,
    subtitle = sprintf("Firth-corrected Cox PH: single-biomarker vs joint, METIMMOX (n = %d)", n3)
  ) +
  theme_minimal(base_size = 12) +
  theme(legend.position = "bottom",
        plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank(),
        panel.spacing.x = grid::unit(0.3, "lines"),
        strip.text = element_text(face = "bold"))
print(p_forest)
```

```{r save-forest, include=FALSE}
figs_dir <- here("outputs", "figs"); if (!dir.exists(figs_dir)) dir.create(figs_dir, recursive = TRUE)
tables_dir <- here("outputs", "tables"); if (!dir.exists(tables_dir)) dir.create(tables_dir, recursive = TRUE)

ggsave(here("outputs", "figs", "poster_forest.png"), p_forest, width = 8, height = 6, dpi = 300, bg = "white")
write.csv(forest_df, here("outputs", "tables", "poster_forest_data.csv"), row.names = FALSE)
```

# Three-strategy cost-effectiveness analysis

```{r cea, include=FALSE}
# Override strategy/biomarker sets so model_fun + predictions include TLR.
canonical_strategies <- get_strategies()
canonical_biomarkers <- get_biomarkers()
poster_strategies <- append(canonical_strategies, "tlr",
                            after = match("crp", canonical_strategies))
poster_biomarkers <- append(canonical_biomarkers, "tlr",
                            after = match("crp", canonical_biomarkers))

with_poster_model_config(poster_strategies, poster_biomarkers, {

m_os3  <- flexsurvreg(Surv(OSwk, Death) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx, data = d3, dist = dist_for$OS)
m_pfs3 <- flexsurvreg(Surv(PFSwk, Progression) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx, data = d3, dist = dist_for$PFS)

prev <- sapply(bms, function(b) mean(as.numeric(as.character(d3[[b]]))))
# TLR is read on treatment at the first CT (about week 8-9) and its prevalence
# differs by arm. The share relevant to a TLR-guided strategy is the share of
# experimental-arm patients who respond, so the pooled value is replaced by
# the experimental-arm value (issue #157). CRP and TMB/BRAF keep the pooled
# value, as in the economic model.
exp_rx3 <- levels(d3$Rx)[2]
tlr_num3 <- as.numeric(as.character(d3$tlr))
n_exp3 <- sum(d3$Rx == exp_rx3);  tlr_pos_exp3 <- sum(tlr_num3[d3$Rx == exp_rx3])
n_ctrl3 <- sum(d3$Rx != exp_rx3); tlr_pos_ctrl3 <- sum(tlr_num3[d3$Rx != exp_rx3])
prev[["tlr"]] <- tlr_pos_exp3 / n_exp3
strategies_df3 <- data.frame(id = c("control", bms),
                             prevalence = c(1, prev[bms]), stringsAsFactors = FALSE)

preds3 <- generate_population_averaged_predictions(
  models = list(os = m_os3, pfs = m_pfs3),
  strategies_df = strategies_df3, data_complete = d3,
  time_points = seq(0, time_horizon, by = 1),
  prevalences = prev)

mk <- function(side, ep)
  setNames(lapply(bms, function(b) preds3[[b]][[paste0("biomarker_", side)]][[ep]]),
           paste0(bms, if (side == "positive") "_pos_" else "_neg_", toupper(ep)))
p_os3 <- c(list(control_OS = preds3$control$os), mk("positive","os"), mk("negative","os"),
           setNames(lapply(bms, function(b) preds3[[b]]$os), paste0(bms, "_weighted_OS")))
p_pfs3 <- c(list(control_PFS = preds3$control$pfs), mk("positive","pfs"), mk("negative","pfs"),
            setNames(lapply(bms, function(b) preds3[[b]]$pfs), paste0(bms, "_weighted_PFS")))

l_params_base3 <- set_population_predictions(l_params_base, preds3)
l_params_base3$p_os  <- p_os3
l_params_base3$p_pfs <- p_pfs3
l_params_base3$p_crp      <- prev[["crp"]]
l_params_base3$p_tlr      <- prev[["tlr"]]
l_params_base3$p_tmb_braf <- prev[["tmb_braf"]]
# Simplification (stated in the table notes): TLR is treated as if it were
# known at treatment selection, at no separate test cost, because it is read
# from the first on-treatment CT that is already in the monitoring schedule.
l_params_base3$c_test_TLR <- 0
l_params_base3 <- sync_biomarker_test_costs(l_params_base3)

res3  <- suppressWarnings(model_fun(l_params_base3, determpsa = "det"))
icer3 <- dampack::calculate_icers(cost = res3$Cost, effect = res3$Effect, strategies = res3$Strategy)

label_strategy <- c(strategy_labels, tlr = "TLR-guided")
cea_tbl <- as.data.frame(icer3) %>%
  mutate(Strategy = label_strategy[as.character(Strategy)],
         NMB = Effect * WTP - Cost)
write.csv(cea_tbl, here("outputs", "tables", "poster_cea.csv"), row.names = FALSE)

# Conclusion computed from the dampack frontier status, not typed (issue #157)
ctrl_label3 <- label_strategy[[get_control_strategy()]]
guided_status3 <- cea_tbl$Status[cea_tbl$Strategy != ctrl_label3]
frontier3 <- cea_tbl$Strategy[cea_tbl$Status == "ND"]
cea_conclusion <- if (all(guided_status3 %in% c("D", "ED"))) {
  "All guided strategies are dominated or extendedly dominated by standard care."
} else {
  sprintf("Strategies on the cost-effectiveness frontier: %s.",
          paste(frontier3, collapse = ", "))
}
})
```

```{r cea-display}
cea_display <- cea_tbl %>%
  transmute(
    Strategy,
    Cost = fmt_eur(Cost),
    QALYs = sprintf("%.3f", Effect),
    NMB = fmt_eur(NMB),
    Status = recode(Status, ND = "On frontier / optimal", D = "Dominated", ED = "Ext. dominated",
                    .default = Status)
  )

kable(cea_display,
      caption = sprintf("Three-strategy cost-effectiveness (joint model, n = %d, WTP = EUR %s/QALY)",
                        n3, format(WTP, big.mark = ",")),
      format = "html", align = c("l","r","r","r","l")) %>%
  kable_styling(bootstrap_options = c("striped","hover","condensed"),
                full_width = TRUE, font_size = 13) %>%
  footnote(general = c(
    "Comprehensive joint model: OS/PFS ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx.",
    "TLR is a post-randomization mediator, included here only to illustrate the poster point.",
    sprintf("Prevalence in the poster's %d-patient TLR-complete cohort: CRP %.1f%% (arms pooled), TLR %.1f%% (experimental arm, %d/%d; control arm %d/%d), TMB/BRAF %.1f%% (arms pooled). The economic model uses the full complete-case cohort (TMB/BRAF %.1f%%).",
            n3, 100*prev[["crp"]], 100*prev[["tlr"]], tlr_pos_exp3, n_exp3,
            tlr_pos_ctrl3, n_ctrl3, 100*prev[["tmb_braf"]],
            100*strategies_df$prevalence[strategies_df$id == "tmb_braf"]),
    "Simplification: TLR is modelled as if it were known at treatment selection, at no separate test cost (it is read from the first on-treatment CT, which is in the monitoring schedule). In the trial it is observed only after two nivolumab doses; a faithful TLR strategy would be a run-in design that the partitioned survival model cannot represent, which is one reason TLR is excluded from the economic model.",
    sprintf("Utilities: %s (UTILITY_SOURCE = %d). %s",
            if (resolve_util_label() == "correct") "CORRECT trial" else "METIMMOX IPD",
            UTILITY_SOURCE, cea_conclusion)),
    general_title = "Notes: ")
```

# Cost-effectiveness acceptability curves: single-biomarker vs joint modelling

```{r ceac-build, include=FALSE}
# Two CEAC panels for the two PRE-IMMUNOTHERAPY economic biomarkers (CRP, TMB/BRAF):
#   Panel A  "one biomarker"  - each guided strategy from its OWN single-biomarker model
#   Panel B  "two biomarkers" - both guided strategies from the joint model
# The SAME cached economic-parameter draws are used in both panels, so the only
# thing that differs is single vs joint survival modelling.
#
# Survival uncertainty follows the pipeline (issue #156, reused here per issue
# #157): multivariate-normal coefficient draws around each fitted model, OS and
# PFS drawn independently. The joint-model draws ARE the repository sampling
# cache, aligned to the cached economic-parameter draws through model_idx, so
# panel B is the repository PSA at biosimilar pricing. The single-biomarker
# models are drawn with the same sampler (sample_survival_coefficients() from
# 06_sampling.R). The control curve is the joint model with Rx = control in
# BOTH panels (issue #151), so the panels differ only in the guided-strategy
# curves. Patient curves are predicted and averaged with shared weights on the
# materialised sampled models and each draw goes through model_fun() in PSA
# mode, which caps a PFS > OS crossing instead of aborting (the deterministic
# path stops on any crossing; with independent OS and PFS draws about half of
# the draws cross somewhere on the grid, as in the repository PSA).
#
# Shown at biosimilar nivolumab pricing, where the decision is a close call and
# the modelling choice is economically visible. The poster-only TLR override
# above has already restored the canonical economic configuration.

dc <- data_complete
times_c <- seq(0, time_horizon)
ctrl_rx <- levels(dc$Rx)[1]; exp_rx <- levels(dc$Rx)[2]
set_rx <- function(nd, rx) { nd$Rx <- factor(rx, levels = levels(dc$Rx)); nd }
bm_sub <- function(bm, val) dc[as.numeric(as.character(dc[[bm]])) == val, ]
newdata <- list(
  ctrl  = set_rx(dc, ctrl_rx),
  crp_p = set_rx(bm_sub("crp", 1), exp_rx),      crp_n = set_rx(bm_sub("crp", 0), ctrl_rx),
  tmb_p = set_rx(bm_sub("tmb_braf", 1), exp_rx), tmb_n = set_rx(bm_sub("tmb_braf", 0), ctrl_rx))

N <- 1000
psa_params <- pipeline_psa_params
if (is.null(psa_params$model_idx)) stop("psa_params has no model_idx column; regenerate the PSA cache (10_PSA.R, issue #156)")
set.seed(2026); idx <- sample(nrow(psa_params), N)

# Joint model: the repository sampling cache (06_sampling.R)
joint_cache <- get_joint_sampling_models(sampling_models)
stopifnot(identical(joint_cache$dist_os, dist_for$OS), identical(joint_cache$dist_pfs, dist_for$PFS))
# Single-biomarker models: same sampler, same distributions, N draws each
single_draws <- list(
  crp = sample_survival_coefficients(
    Surv(OSwk, Death) ~ Age + sex + Rx * crp,
    Surv(PFSwk, Progression) ~ Age + sex + Rx * crp,
    data = dc, dist_os = dist_for$OS, dist_pfs = dist_for$PFS,
    n_samples = N, seed = 2027L),
  tmb_braf = sample_survival_coefficients(
    Surv(OSwk, Death) ~ Age + sex + Rx * tmb_braf,
    Surv(PFSwk, Progression) ~ Age + sex + Rx * tmb_braf,
    data = dc, dist_os = dist_for$OS, dist_pfs = dist_for$PFS,
    n_samples = N, seed = 2028L))

NIVO_FACTOR <- 4641 / 13923            # biosimilar nivolumab price (repo biosimilar scenario)

curve <- function(sm, outcome, nd) {
  prediction <- predict(sm[[outcome]]$model, newdata = nd, type = "survival", times = times_c)
  s <- weighted_survival_average(extract_all_survival_probabilities(prediction),
    population_weights[match(nd$ID, dc$ID)])
  if (is.null(s)) stop("Prediction failed in the poster CEAC draw")
  s[1] <- 1
  s
}
guided_curves <- function(sm_crp, sm_tmb) list(
  os = list(crp_pos_OS = curve(sm_crp, "os", newdata$crp_p),
            crp_neg_OS = curve(sm_crp, "os", newdata$crp_n),
            tmb_braf_pos_OS = curve(sm_tmb, "os", newdata$tmb_p),
            tmb_braf_neg_OS = curve(sm_tmb, "os", newdata$tmb_n)),
  pfs = list(crp_pos_PFS = curve(sm_crp, "pfs", newdata$crp_p),
             crp_neg_PFS = curve(sm_crp, "pfs", newdata$crp_n),
             tmb_braf_pos_PFS = curve(sm_tmb, "pfs", newdata$tmb_p),
             tmb_braf_neg_PFS = curve(sm_tmb, "pfs", newdata$tmb_n)))

run_panel <- function(d_row, ctrl, guided) {
  p <- l_params_base
  # Take whatever the PSA cache actually sampled. Unit prices are fixed in the
  # PSA since issue #154 and keep their base-case values; a hardcoded name list
  # would silently drop them from the parameter set.
  for (nm in intersect(names(d_row), names(l_params_base))) p[[nm]] <- d_row[[nm]]
  p <- sync_biomarker_test_costs(p)
  p$c_drug_nivo <- p$c_drug_nivo * NIVO_FACTOR
  p$p_os  <- c(list(control_OS = ctrl$os), guided$os)
  p$p_pfs <- c(list(control_PFS = ctrl$pfs), guided$pfs)
  # These supplied curves already use this draw's common population weights.
  p$population_weights <- population_weights
  p$population_curves <- NULL
  # PSA mode without sim_idx uses the supplied curves and caps a PFS > OS
  # crossing instead of aborting.
  suppressWarnings(model_fun(p, determpsa = "psa"))
}

cj <- ej <- cs <- es <- matrix(NA, N, 3, dimnames = list(NULL, c("control","crp","tmb_braf")))
t_start <- Sys.time()
for (i in seq_len(N)) {
  r <- idx[i]
  population_params <- l_params_base
  for (nm in intersect(names(psa_params), names(population_params)))
    population_params[[nm]] <- psa_params[[nm]][r]
  population_weights <- model_population_weights(population_params, dc)
  sm_joint <- sampled_survival_models(joint_cache, psa_params$model_idx[r])
  sm_crp   <- sampled_survival_models(single_draws$crp, i)
  sm_tmb   <- sampled_survival_models(single_draws$tmb_braf, i)
  ctrl <- list(os = curve(sm_joint, "os", newdata$ctrl), pfs = curve(sm_joint, "pfs", newdata$ctrl))
  a <- run_panel(psa_params[r, ], ctrl, guided_curves(sm_joint, sm_joint)); cj[i,] <- a$Cost; ej[i,] <- a$Effect
  b <- run_panel(psa_params[r, ], ctrl, guided_curves(sm_crp, sm_tmb));     cs[i,] <- b$Cost; es[i,] <- b$Effect
  if (i %% 100 == 0) cat(sprintf("  CEAC draw %d/%d (%.1f min)\n", i, N,
                                 as.numeric(difftime(Sys.time(), t_start, units = "mins"))))
}
mk_psa <- function(co, ef) dampack::make_psa_obj(as.data.frame(co), as.data.frame(ef),
            parameters = NULL, strategies = c("control","crp","tmb_braf"))
panel_single <- "One biomarker (modelled in isolation)"
panel_joint  <- "Two biomarkers (joint, correlation-adjusted)"
wtp_range <- sort(unique(c(seq(0, 150000, by = 2000), WTP)))   # base-case WTP is a grid point
c1 <- dampack::ceac(wtp_range, mk_psa(cs, es)); c1$Panel <- panel_single
c2 <- dampack::ceac(wtp_range, mk_psa(cj, ej)); c2$Panel <- panel_joint
ceac_df <- rbind(as.data.frame(c1), as.data.frame(c2))
names(ceac_df)[names(ceac_df) == "Proportion"] <- "Probability"
ceac_df$Strategy <- strategy_label(as.character(ceac_df$Strategy))
write.csv(ceac_df, here("outputs", "tables", "poster_ceac_data.csv"), row.names = FALSE)

# Caption computed from the curves at the base-case WTP (issue #157)
soc_lab <- strategy_label("control"); crp_lab <- strategy_label("crp"); tmb_lab <- strategy_label("tmb_braf")
at_wtp <- ceac_df[ceac_df$WTP == WTP, ]
pct <- function(panel, strat) sprintf("%.0f%%", 100 * at_wtp$Probability[at_wtp$Panel == panel & at_wtp$Strategy == strat])
ceac_caption <- sprintf(paste(
  "Cost-effectiveness acceptability curves at biosimilar nivolumab pricing (EUR 4,641 per administration).",
  "Left: each biomarker-guided strategy from its own single-biomarker survival model.",
  "Right: both from the joint, correlation-adjusted economic model.",
  "The standard-of-care curve is the joint model with treatment set to control in both panels, so the panels differ only in the guided-strategy curves.",
  "At EUR %s per QALY (dotted line) the probability of being optimal is: standard of care %s (single) vs %s (joint); CRP-guided %s vs %s; TMB/BRAF-guided %s vs %s.",
  "Survival uncertainty: multivariate-normal coefficient draws (n = %d; joint model from the repository sampling cache, single-biomarker models with the same sampler), OS and PFS drawn independently as in the repository PSA; PFS > OS crossings are capped in PSA mode."),
  format(WTP, big.mark = ","), pct(panel_single, soc_lab), pct(panel_joint, soc_lab),
  pct(panel_single, crp_lab), pct(panel_joint, crp_lab), pct(panel_single, tmb_lab), pct(panel_joint, tmb_lab), N)
```

```{r ceac-plot, fig.width=11, fig.height=5}
#| fig-cap: !expr ceac_caption
p_ceac <- ggplot(ceac_df, aes(WTP, Probability, colour = Strategy)) +
  geom_vline(xintercept = WTP, linetype = "dotted", colour = "grey40") +
  geom_line(linewidth = 0.9) +
  facet_wrap(~ Panel) +
  scale_x_continuous(labels = scales::dollar_format(prefix = "EUR ", scale = 0.001, suffix = "K")) +
  scale_y_continuous(labels = scales::percent_format(), limits = c(0, 1)) +
  scale_colour_manual(values = c("Standard of Care" = "#2E7D32",
                                 "CRP-guided" = "#C0392B", "TMB/BRAF-guided" = "#1F4E79")) +
  labs(x = "Willingness-to-pay (EUR/QALY)", y = "Probability cost-effective", colour = NULL) +
  theme_minimal(base_size = 13) +
  theme(legend.position = "bottom", plot.title = element_text(face = "bold"),
        panel.grid.minor = element_blank(), strip.text = element_text(face = "bold"))
print(p_ceac)
ggsave(here("outputs", "figs", "poster_ceac.png"), p_ceac, width = 11, height = 5, dpi = 300, bg = "white")
```

---

Figure saved to `outputs/figs/poster_forest.png` and `outputs/figs/poster_ceac.png`.
Tables saved to `outputs/tables/poster_cea.csv`, `outputs/tables/poster_forest_data.csv`, and `outputs/tables/poster_ceac_data.csv`.
