---
title: "Biomarker Effect Decomposition"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 8, fig.height = 6,
                      dpi = 300, out.width = "100%")
knitr::opts_knit$set(root.dir = here::here())

if (!require("pacman")) install.packages("pacman")
pacman::p_load(here, knitr, kableExtra, ggplot2, dplyr, tidyr, scales)

suppressMessages(suppressWarnings({
  source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
  source(here::here("scripts/R/analysis/03_biomarker_strategies.R"))
  source(here::here("scripts/R/analysis/06_parametric_survival_analysis.R"))
  source(here::here("scripts/R/analysis/07_basecase_input_parameters.R"))
}))

biomarker_label <- function(x) {
  dplyr::recode(x, crp = "CRP", tmb_braf = "TMB/BRAF", .default = x)
}

curve_df <- function(biomarker, endpoint = c("os", "pfs")) {
  endpoint <- match.arg(endpoint)
  source_list <- if (endpoint == "os") l_params_base$p_os else l_params_base$p_pfs
  suffix <- if (endpoint == "os") "OS" else "PFS"

  data.frame(
    Week = time_points,
    Positive = source_list[[paste0(biomarker, "_pos_", suffix)]],
    Negative = source_list[[paste0(biomarker, "_neg_", suffix)]],
    Weighted = source_list[[paste0(biomarker, "_weighted_", suffix)]],
    Control = source_list[[paste0("control_", suffix)]],
    Biomarker = biomarker_label(biomarker),
    Endpoint = ifelse(endpoint == "os", "Overall survival", "Progression-free survival"),
    stringsAsFactors = FALSE
  ) %>%
    pivot_longer(cols = c(Positive, Negative, Weighted, Control),
                 names_to = "Curve", values_to = "Survival")
}

restricted_mean <- function(y) sum(y) * cl
```

# Overview

This report decomposes the survival contribution of the two economic biomarker strategies in the single joint model. Each strategy is shown as biomarker-positive, biomarker-negative, prevalence-weighted, and standard-of-care survival curves.

# Biomarker Prevalence

```{r prevalence}
prev_df <- strategies_df %>%
  filter(id %in% get_biomarkers()) %>%
  transmute(
    Biomarker = biomarker_label(id),
    Prevalence = scales::percent(prevalence, accuracy = 0.1)
  )

knitr::kable(prev_df, booktabs = TRUE, align = c("l", "r"),
             caption = "Economic biomarker prevalences") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Restricted Mean Survival

```{r rmst-table}
rmst_rows <- lapply(get_biomarkers(), function(bm) {
  os <- l_params_base$p_os
  pfs <- l_params_base$p_pfs
  data.frame(
    Biomarker = biomarker_label(bm),
    Endpoint = rep(c("Overall survival", "Progression-free survival"), each = 4),
    Curve = rep(c("Positive", "Negative", "Weighted", "Control"), times = 2),
    Years = c(
      restricted_mean(os[[paste0(bm, "_pos_OS")]]),
      restricted_mean(os[[paste0(bm, "_neg_OS")]]),
      restricted_mean(os[[paste0(bm, "_weighted_OS")]]),
      restricted_mean(os$control_OS),
      restricted_mean(pfs[[paste0(bm, "_pos_PFS")]]),
      restricted_mean(pfs[[paste0(bm, "_neg_PFS")]]),
      restricted_mean(pfs[[paste0(bm, "_weighted_PFS")]]),
      restricted_mean(pfs$control_PFS)
    ),
    stringsAsFactors = FALSE
  )
})

rmst_df <- bind_rows(rmst_rows) %>%
  mutate(Years = sprintf("%.2f", Years))

knitr::kable(
  rmst_df,
  booktabs = TRUE,
  align = c("l", "l", "l", "r"),
  caption = "Restricted mean survival by biomarker subgroup and strategy curve"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Survival Decomposition

```{r decomposition-plot, fig.cap="Survival decomposition by economic biomarker", fig.height=8, fig.width=10}
plot_data <- bind_rows(
  lapply(get_biomarkers(), curve_df, endpoint = "os"),
  lapply(get_biomarkers(), curve_df, endpoint = "pfs")
)

ggplot(plot_data, aes(x = Week, y = Survival, color = Curve, linetype = Curve)) +
  geom_line(linewidth = 0.8) +
  facet_grid(Biomarker ~ Endpoint) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = "Weeks", y = "Survival probability", color = NULL, linetype = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Interpretation

The prevalence-weighted strategy curve combines biomarker-positive patients assigned to experimental treatment and biomarker-negative patients assigned to standard care. The distance between the weighted strategy curve and the control curve is the survival component of the economic strategy effect.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
