---
title: "Biomarker Effect Decomposition"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%",
  fig.keep = "last"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10)
  )
)
```

```{r load-analysis-scripts, include=FALSE}
# Load analysis results if not already in environment
if (!exists("data_complete")) {
  cat("Loading analysis scripts...\n")

  # Load required scripts in order
  if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
  }

  if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
  }

  if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
  }
}

# Load prediction functions
source(here("scripts/R/functions/prediction_functions.R"))
```

```{r model-setup, include=FALSE}
# ===============================================================================
# MODEL STRUCTURE SETUP - Gamma distribution only
# ===============================================================================

# Define model formulas for all 7 model types
model_formulas <- list(
  # Model A: Joint (All-in-One) - all biomarkers + all interactions
  A = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx
  ),

  # Model B: Focused - all biomarkers as covariates + ONE interaction
  B_crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx
  ),
  B_tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx
  ),
  B_tmb = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx
  ),

  # Model C: Single-biomarker (Separate) - ONE biomarker only + its interaction
  C_crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp:Rx
  ),
  C_tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + tlr:Rx
  ),
  C_tmb = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + tmb_braf:Rx
  )
)

# Model labels
model_labels_short <- c(
  "A" = "Model A",
  "B_crp" = "Model B",
  "B_tlr" = "Model B",
  "B_tmb" = "Model B",
  "C_crp" = "Model C",
  "C_tlr" = "Model C",
  "C_tmb" = "Model C"
)

# Color scheme for subgroups
subgroup_colors <- c(
  "Biomarker+" = "#E31A1C",   # Red
  "Biomarker-" = "#1F78B4",   # Blue
  "Strategy" = "#33A02C",      # Green
  "Control" = "gray50"
)

# Model linetypes for combined plots
model_linetypes <- c(
  "A" = "solid",
  "B" = "dashed",
  "C" = "dotted"
)

# Vector of model types to fit
model_types <- c("A", "B_crp", "B_tlr", "B_tmb", "C_crp", "C_tlr", "C_tmb")

# Biomarker-model mapping
model_biomarker_map <- list(
  A = c("crp", "tlr", "tmb_braf"),
  B_crp = c("crp"),
  B_tlr = c("tlr"),
  B_tmb = c("tmb_braf"),
  C_crp = c("crp"),
  C_tlr = c("tlr"),
  C_tmb = c("tmb_braf")
)
```

```{r fit-models, include=FALSE}
# ===============================================================================
# FIT GAMMA MODELS
# ===============================================================================

# Check for cache file from para_models.qmd
cache_file <- here("data", "output", "multi_models_cache.rds")

if (file.exists(cache_file)) {
  cat("Loading cached models from para_models.qmd...\n")
  cache_data <- readRDS(cache_file)
  multi_models <- cache_data$multi_models
  cat("Cache loaded successfully.\n")
} else {
  cat("No cache found. Fitting gamma models...\n")

  multi_models <- list(gamma = list())

  for (model_type in model_types) {
    cat("Fitting model:", model_type, "\n")

    # Fit OS model
    os_fit <- tryCatch({
      flexsurvreg(
        formula = model_formulas[[model_type]]$os,
        data = data_complete,
        dist = "gamma"
      )
    }, error = function(e) {
      warning(paste("Failed to fit", model_type, "OS:", e$message))
      return(NULL)
    })

    # Fit PFS model
    pfs_fit <- tryCatch({
      flexsurvreg(
        formula = model_formulas[[model_type]]$pfs,
        data = data_complete,
        dist = "gamma"
      )
    }, error = function(e) {
      warning(paste("Failed to fit", model_type, "PFS:", e$message))
      return(NULL)
    })

    # Store models
    multi_models$gamma[[model_type]] <- list(
      os = os_fit,
      pfs = pfs_fit
    )
  }
}

# Clean up memory
gc(verbose = FALSE)
```

```{r generate-predictions, include=FALSE}
# ===============================================================================
# GENERATE PREDICTIONS FOR ALL MODEL TYPES (Gamma only)
# ===============================================================================

cat("Generating predictions...\n")

# Helper function for population-averaged predictions
predict_population_avg <- function(model, newdata, time_points) {
  tryCatch({
    pred <- predict(model, newdata = newdata, type = "survival", times = time_points)
    if (".pred" %in% names(pred)) {
      surv_probs <- lapply(pred$.pred, function(x) x$.pred_survival)
      surv_matrix <- do.call(cbind, surv_probs)
      return(rowMeans(surv_matrix, na.rm = TRUE))
    } else if (is.list(pred) && length(pred) > 0 && is.data.frame(pred[[1]])) {
      surv_probs <- sapply(pred, function(x) x$est)
      if (is.matrix(surv_probs)) {
        return(rowMeans(surv_probs, na.rm = TRUE))
      } else {
        return(surv_probs)
      }
    } else {
      return(NULL)
    }
  }, error = function(e) {
    return(NULL)
  })
}

# Get treatment level references
exp_rx <- levels(data_complete$Rx)[2]
ctrl_rx <- levels(data_complete$Rx)[1]

# Initialize predictions storage
multi_predictions <- list(gamma = list())

# Loop through model types
for (model_type in model_types) {
  os_model <- multi_models$gamma[[model_type]]$os
  pfs_model <- multi_models$gamma[[model_type]]$pfs

  if (is.null(os_model) || is.null(pfs_model)) next

  multi_predictions$gamma[[model_type]] <- list()

  # Control predictions
  control_data <- data_complete
  control_data$Rx <- factor(ctrl_rx, levels = levels(data_complete$Rx))

  control_os <- predict_population_avg(os_model, control_data, time_points)
  control_pfs <- predict_population_avg(pfs_model, control_data, time_points)

  if (!is.null(control_os) && !is.null(control_pfs)) {
    multi_predictions$gamma[[model_type]]$control <- list(os = control_os, pfs = control_pfs)
  }

  # Biomarker-specific predictions
  biomarkers_to_predict <- model_biomarker_map[[model_type]]

  for (biomarker in biomarkers_to_predict) {
    # Biomarker-positive: experimental treatment
    pos_data <- data_complete[as.numeric(as.character(data_complete[[biomarker]])) == 1, ]
    if (nrow(pos_data) > 0) {
      pos_data$Rx <- factor(exp_rx, levels = levels(data_complete$Rx))
      pos_os <- predict_population_avg(os_model, pos_data, time_points)
      pos_pfs <- predict_population_avg(pfs_model, pos_data, time_points)

      if (!is.null(pos_os) && !is.null(pos_pfs)) {
        multi_predictions$gamma[[model_type]][[paste0(biomarker, "_pos")]] <- list(os = pos_os, pfs = pos_pfs)
      }
    }

    # Biomarker-negative: control treatment
    neg_data <- data_complete[as.numeric(as.character(data_complete[[biomarker]])) == 0, ]
    if (nrow(neg_data) > 0) {
      neg_data$Rx <- factor(ctrl_rx, levels = levels(data_complete$Rx))
      neg_os <- predict_population_avg(os_model, neg_data, time_points)
      neg_pfs <- predict_population_avg(pfs_model, neg_data, time_points)

      if (!is.null(neg_os) && !is.null(neg_pfs)) {
        multi_predictions$gamma[[model_type]][[paste0(biomarker, "_neg")]] <- list(os = neg_os, pfs = neg_pfs)
      }
    }

    # Population-weighted prediction
    biomarker_prev <- strategies_df$prevalence[strategies_df$id == biomarker]
    pos_pred <- multi_predictions$gamma[[model_type]][[paste0(biomarker, "_pos")]]
    neg_pred <- multi_predictions$gamma[[model_type]][[paste0(biomarker, "_neg")]]

    if (length(biomarker_prev) > 0 && !is.null(pos_pred) && !is.null(neg_pred)) {
      multi_predictions$gamma[[model_type]][[paste0(biomarker, "_weighted")]] <- list(
        os = biomarker_prev * pos_pred$os + (1 - biomarker_prev) * neg_pred$os,
        pfs = biomarker_prev * pos_pred$pfs + (1 - biomarker_prev) * neg_pred$pfs
      )
    }
  }
}

cat("Predictions generated successfully.\n")
```

```{r helper-functions, include=FALSE}
# ===============================================================================
# HELPER FUNCTIONS
# ===============================================================================

# Calculate life-years from survival curve
calculate_ly <- function(survival_curve, cl = 1/52) {
  sum(survival_curve * cl, na.rm = TRUE)
}

# Create decomposition plot for a biomarker
create_decomposition_plot <- function(biomarker, outcome = "os",
                                       show_models = c("A", "B", "C"),
                                       faceted = TRUE) {

  # Map biomarker to model types
  model_map <- list(
    crp = c("A", "B_crp", "C_crp"),
    tlr = c("A", "B_tlr", "C_tlr"),
    tmb_braf = c("A", "B_tmb", "C_tmb")
  )

  relevant_models <- model_map[[biomarker]]

  # Biomarker labels
  biomarker_labels <- c(
    crp = "CRP",
    tlr = "TLR",
    tmb_braf = "TMB/BRAF"
  )

  # Build plot data
  plot_data <- data.frame()

  for (model_type in relevant_models) {
    pred <- multi_predictions$gamma[[model_type]]
    if (is.null(pred)) next

    # Get model letter (A, B, or C)
    model_letter <- substr(model_type, 1, 1)
    model_label <- paste0("Model ", model_letter)

    # Control
    if (!is.null(pred$control[[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred$control[[outcome]],
        subgroup = "Control",
        model = model_label,
        model_type = model_type
      ))
    }

    # Biomarker positive
    pos_key <- paste0(biomarker, "_pos")
    if (!is.null(pred[[pos_key]][[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred[[pos_key]][[outcome]],
        subgroup = "Biomarker+",
        model = model_label,
        model_type = model_type
      ))
    }

    # Biomarker negative
    neg_key <- paste0(biomarker, "_neg")
    if (!is.null(pred[[neg_key]][[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred[[neg_key]][[outcome]],
        subgroup = "Biomarker-",
        model = model_label,
        model_type = model_type
      ))
    }

    # Weighted strategy
    weighted_key <- paste0(biomarker, "_weighted")
    if (!is.null(pred[[weighted_key]][[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred[[weighted_key]][[outcome]],
        subgroup = "Strategy",
        model = model_label,
        model_type = model_type
      ))
    }
  }

  if (nrow(plot_data) == 0) return(NULL)

  # Set factor levels
  plot_data$subgroup <- factor(plot_data$subgroup,
                                levels = c("Biomarker+", "Biomarker-", "Strategy", "Control"))
  plot_data$model <- factor(plot_data$model, levels = c("Model A", "Model B", "Model C"))

  # Create plot
  outcome_label <- ifelse(outcome == "os", "Overall Survival", "Progression-Free Survival")
  bio_label <- biomarker_labels[biomarker]

  if (faceted) {
    p <- ggplot(plot_data, aes(x = time, y = survival, color = subgroup)) +
      geom_line(linewidth = 1) +
      facet_wrap(~ model, nrow = 1) +
      scale_color_manual(values = subgroup_colors, name = "Group") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Survival Probability",
           title = paste0(bio_label, " Strategy: ", outcome_label),
           subtitle = "Decomposition by biomarker subgroup across model structures") +
      theme(legend.position = "bottom",
            strip.text = element_text(size = 10, face = "bold"))
  } else {
    p <- ggplot(plot_data, aes(x = time, y = survival, color = subgroup, linetype = model)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = subgroup_colors, name = "Group") +
      scale_linetype_manual(values = c("Model A" = "solid", "Model B" = "dashed", "Model C" = "dotted"),
                            name = "Model") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Survival Probability",
           title = paste0(bio_label, " Strategy: ", outcome_label)) +
      theme(legend.position = "bottom")
  }

  return(p)
}

# Create individual model plot
create_individual_model_plot <- function(biomarker, model_type, outcome = "os") {
  pred <- multi_predictions$gamma[[model_type]]
  if (is.null(pred)) return(NULL)

  # Biomarker labels
  biomarker_labels <- c(
    crp = "CRP",
    tlr = "TLR",
    tmb_braf = "TMB/BRAF"
  )

  # Build plot data
  plot_data <- data.frame()

  # Control
  if (!is.null(pred$control[[outcome]])) {
    plot_data <- rbind(plot_data, data.frame(
      time = time_points,
      survival = pred$control[[outcome]],
      subgroup = "Control"
    ))
  }

  # Biomarker positive
  pos_key <- paste0(biomarker, "_pos")
  if (!is.null(pred[[pos_key]][[outcome]])) {
    plot_data <- rbind(plot_data, data.frame(
      time = time_points,
      survival = pred[[pos_key]][[outcome]],
      subgroup = "Biomarker+"
    ))
  }

  # Biomarker negative
  neg_key <- paste0(biomarker, "_neg")
  if (!is.null(pred[[neg_key]][[outcome]])) {
    plot_data <- rbind(plot_data, data.frame(
      time = time_points,
      survival = pred[[neg_key]][[outcome]],
      subgroup = "Biomarker-"
    ))
  }

  # Weighted strategy
  weighted_key <- paste0(biomarker, "_weighted")
  if (!is.null(pred[[weighted_key]][[outcome]])) {
    plot_data <- rbind(plot_data, data.frame(
      time = time_points,
      survival = pred[[weighted_key]][[outcome]],
      subgroup = "Strategy"
    ))
  }

  if (nrow(plot_data) == 0) return(NULL)

  plot_data$subgroup <- factor(plot_data$subgroup,
                                levels = c("Biomarker+", "Biomarker-", "Strategy", "Control"))

  # Model label
  model_letter <- substr(model_type, 1, 1)
  model_label <- paste0("Model ", model_letter)
  outcome_label <- ifelse(outcome == "os", "Overall Survival", "Progression-Free Survival")
  bio_label <- biomarker_labels[biomarker]

  p <- ggplot(plot_data, aes(x = time, y = survival, color = subgroup)) +
    geom_line(linewidth = 1.2) +
    scale_color_manual(values = subgroup_colors, name = "Group") +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
    labs(x = "Time (weeks)", y = "Survival Probability",
         title = paste0(bio_label, " Strategy - ", model_label, ": ", outcome_label)) +
    theme(legend.position = "bottom")

  return(p)
}

# Create life-years table for a biomarker
create_ly_table <- function(biomarker, outcome = "os") {
  # Map biomarker to model types
  model_map <- list(
    crp = c("A", "B_crp", "C_crp"),
    tlr = c("A", "B_tlr", "C_tlr"),
    tmb_braf = c("A", "B_tmb", "C_tmb")
  )

  relevant_models <- model_map[[biomarker]]

  # Build table data
  table_data <- data.frame()

  for (model_type in relevant_models) {
    pred <- multi_predictions$gamma[[model_type]]
    if (is.null(pred)) next

    model_letter <- substr(model_type, 1, 1)
    model_label <- paste0("Model ", model_letter)

    # Calculate LY for each group
    control_ly <- if (!is.null(pred$control[[outcome]])) calculate_ly(pred$control[[outcome]]) else NA
    pos_ly <- if (!is.null(pred[[paste0(biomarker, "_pos")]][[outcome]]))
                calculate_ly(pred[[paste0(biomarker, "_pos")]][[outcome]]) else NA
    neg_ly <- if (!is.null(pred[[paste0(biomarker, "_neg")]][[outcome]]))
                calculate_ly(pred[[paste0(biomarker, "_neg")]][[outcome]]) else NA
    strategy_ly <- if (!is.null(pred[[paste0(biomarker, "_weighted")]][[outcome]]))
                     calculate_ly(pred[[paste0(biomarker, "_weighted")]][[outcome]]) else NA

    # Calculate deltas relative to control
    pos_delta <- pos_ly - control_ly
    neg_delta <- neg_ly - control_ly
    strategy_delta <- strategy_ly - control_ly

    table_data <- rbind(table_data, data.frame(
      Model = model_label,
      Control = control_ly,
      `Biomarker+` = pos_ly,
      `Delta+` = pos_delta,
      `Biomarker-` = neg_ly,
      `Delta-` = neg_delta,
      Strategy = strategy_ly,
      `Delta Strategy` = strategy_delta,
      check.names = FALSE
    ))
  }

  return(table_data)
}

# Create combined OS and PFS life-years table for a biomarker
create_combined_ly_table <- function(biomarker) {
  # Map biomarker to model types
  model_map <- list(
    crp = c("A", "B_crp", "C_crp"),
    tlr = c("A", "B_tlr", "C_tlr"),
    tmb_braf = c("A", "B_tmb", "C_tmb")
  )

  relevant_models <- model_map[[biomarker]]

  # Build table data
  table_data <- data.frame()

  for (model_type in relevant_models) {
    pred <- multi_predictions$gamma[[model_type]]
    if (is.null(pred)) next

    model_letter <- substr(model_type, 1, 1)
    model_label <- paste0("Model ", model_letter)

    # OS life-years
    control_os <- if (!is.null(pred$control$os)) calculate_ly(pred$control$os) else NA
    pos_os <- if (!is.null(pred[[paste0(biomarker, "_pos")]]$os))
                calculate_ly(pred[[paste0(biomarker, "_pos")]]$os) else NA
    neg_os <- if (!is.null(pred[[paste0(biomarker, "_neg")]]$os))
                calculate_ly(pred[[paste0(biomarker, "_neg")]]$os) else NA
    strategy_os <- if (!is.null(pred[[paste0(biomarker, "_weighted")]]$os))
                     calculate_ly(pred[[paste0(biomarker, "_weighted")]]$os) else NA

    # PFS life-years
    control_pfs <- if (!is.null(pred$control$pfs)) calculate_ly(pred$control$pfs) else NA
    pos_pfs <- if (!is.null(pred[[paste0(biomarker, "_pos")]]$pfs))
                 calculate_ly(pred[[paste0(biomarker, "_pos")]]$pfs) else NA
    neg_pfs <- if (!is.null(pred[[paste0(biomarker, "_neg")]]$pfs))
                 calculate_ly(pred[[paste0(biomarker, "_neg")]]$pfs) else NA
    strategy_pfs <- if (!is.null(pred[[paste0(biomarker, "_weighted")]]$pfs))
                      calculate_ly(pred[[paste0(biomarker, "_weighted")]]$pfs) else NA

    table_data <- rbind(table_data, data.frame(
      Model = model_label,
      `OS Control` = control_os,
      `OS Biomarker+` = pos_os,
      `OS Biomarker-` = neg_os,
      `OS Strategy` = strategy_os,
      `OS LY Gain` = strategy_os - control_os,
      `PFS Control` = control_pfs,
      `PFS Biomarker+` = pos_pfs,
      `PFS Biomarker-` = neg_pfs,
      `PFS Strategy` = strategy_pfs,
      `PFS LY Gain` = strategy_pfs - control_pfs,
      check.names = FALSE
    ))
  }

  return(table_data)
}

# Create single-panel plot with all models overlaid
create_single_panel_plot <- function(biomarker, outcome = "os") {
  # Map biomarker to model types
  model_map <- list(
    crp = c("A", "B_crp", "C_crp"),
    tlr = c("A", "B_tlr", "C_tlr"),
    tmb_braf = c("A", "B_tmb", "C_tmb")
  )

  relevant_models <- model_map[[biomarker]]

  # Biomarker labels
  biomarker_labels <- c(
    crp = "CRP",
    tlr = "TLR",
    tmb_braf = "TMB/BRAF"
  )

  # Build plot data
  plot_data <- data.frame()

  for (model_type in relevant_models) {
    pred <- multi_predictions$gamma[[model_type]]
    if (is.null(pred)) next

    model_letter <- substr(model_type, 1, 1)
    model_label <- paste0("Model ", model_letter)

    # Control
    if (!is.null(pred$control[[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred$control[[outcome]],
        subgroup = "Control",
        model = model_label
      ))
    }

    # Biomarker positive
    pos_key <- paste0(biomarker, "_pos")
    if (!is.null(pred[[pos_key]][[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred[[pos_key]][[outcome]],
        subgroup = "Biomarker+",
        model = model_label
      ))
    }

    # Biomarker negative
    neg_key <- paste0(biomarker, "_neg")
    if (!is.null(pred[[neg_key]][[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred[[neg_key]][[outcome]],
        subgroup = "Biomarker-",
        model = model_label
      ))
    }

    # Weighted strategy
    weighted_key <- paste0(biomarker, "_weighted")
    if (!is.null(pred[[weighted_key]][[outcome]])) {
      plot_data <- rbind(plot_data, data.frame(
        time = time_points,
        survival = pred[[weighted_key]][[outcome]],
        subgroup = "Strategy",
        model = model_label
      ))
    }
  }

  if (nrow(plot_data) == 0) return(NULL)

  # Set factor levels
  plot_data$subgroup <- factor(plot_data$subgroup,
                                levels = c("Biomarker+", "Biomarker-", "Strategy", "Control"))
  plot_data$model <- factor(plot_data$model, levels = c("Model A", "Model B", "Model C"))

  outcome_label <- ifelse(outcome == "os", "Overall Survival", "Progression-Free Survival")
  bio_label <- biomarker_labels[biomarker]

  p <- ggplot(plot_data, aes(x = time, y = survival, color = subgroup, linetype = model)) +
    geom_line(linewidth = 1) +
    scale_color_manual(values = subgroup_colors, name = "Group") +
    scale_linetype_manual(values = c("Model A" = "solid", "Model B" = "dashed", "Model C" = "dotted"),
                          name = "Model") +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
    labs(x = "Time (weeks)", y = "Survival Probability",
         title = paste0(bio_label, " Strategy: ", outcome_label),
         subtitle = "All model structures combined") +
    theme(legend.position = "bottom") +
    guides(color = guide_legend(nrow = 1), linetype = guide_legend(nrow = 1))

  return(p)
}
```

# Overview

This report examines how biomarker-positive and biomarker-negative patient subgroups contribute to the overall survival benefit of biomarker-guided treatment strategies. For each biomarker strategy (CRP, TLR, TMB/BRAF), we show:

1. **Survival curves** decomposed into:
   - Biomarker-positive patients (receiving experimental treatment)
   - Biomarker-negative patients (receiving control treatment)
   - Overall strategy (population-weighted average)
   - Control (all patients receiving standard treatment)

2. **Life-years** for each subgroup across different model structures

3. **Model comparisons** showing how results vary by model specification (A, B, C)

## Model Structures and Biomarker Populations

This report uses only the Gamma distribution for all survival models. For detailed model selection and comparison (including Weibull PH models and AIC/BIC statistics), see the Parametric Survival Modeling report (`para_models.qmd`).

Three model structures are compared for each biomarker strategy:

- **Model A (Joint)**: All biomarker-treatment interactions in a single model
- **Model B (Focused)**: All biomarkers as main effects plus one interaction term
- **Model C (Separate)**: Single biomarker with its interaction term only

Table 1 summarizes the patient populations for each biomarker strategy, showing the number of biomarker-positive and biomarker-negative patients and the overall prevalence rate.

```{r biomarker-prevalence-table}
# Calculate patient counts by biomarker status
biomarker_stats <- data.frame(
  Biomarker = c("CRP (<5 g/L)", "TLR (>=10%)", "TMB (>=9 mut/MB) or BRAF"),
  `N Positive` = c(
    sum(data_complete$crp == 1, na.rm = TRUE),
    sum(data_complete$tlr == 1, na.rm = TRUE),
    sum(data_complete$tmb_braf == 1, na.rm = TRUE)
  ),
  `N Negative` = c(
    sum(data_complete$crp == 0, na.rm = TRUE),
    sum(data_complete$tlr == 0, na.rm = TRUE),
    sum(data_complete$tmb_braf == 0, na.rm = TRUE)
  ),
  `Prevalence (%)` = c(
    round(100 * p_crp, 1),
    round(100 * p_tlr, 1),
    round(100 * p_tmb_braf, 1)
  ),
  check.names = FALSE
)

biomarker_stats$`N Total` <- biomarker_stats$`N Positive` + biomarker_stats$`N Negative`

kable(biomarker_stats[, c("Biomarker", "N Positive", "N Negative", "N Total", "Prevalence (%)")],
      caption = "Biomarker patient populations and prevalence rates.",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE)
```

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# CRP Biomarker Strategy

C-reactive protein (CRP) with a cutoff of <5 for biomarker-positive status. **Biomarker prevalence: `r round(100 * p_crp, 1)`%**. Biomarker-positive patients receive alternating FLOX and nivolumab; biomarker-negative patients receive FLOX only.

```{r crp-os-ly-table}
ly_table <- create_ly_table("crp", "os")
kable(ly_table,
      caption = "CRP strategy: Overall survival life-years by model structure. Delta columns show difference vs. control.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

```{r crp-pfs-ly-table}
ly_table <- create_ly_table("crp", "pfs")
kable(ly_table,
      caption = "CRP strategy: Progression-free survival life-years by model structure. Delta columns show difference vs. control.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

## Overall Survival

```{r crp-os-combined, fig.height=5, fig.width=10}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%) decomposition for overall survival across model structures. Red: biomarker-positive (experimental treatment), Blue: biomarker-negative (control treatment), Green: population-weighted strategy, Gray: control (all patients on standard treatment).")'

p <- create_decomposition_plot("crp", "os", faceted = TRUE)
if (!is.null(p)) print(p)
```

```{r crp-os-single-panel, fig.height=6, fig.width=10}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%): All model structures overlaid in a single panel for overall survival. Solid line = Model A, dashed = Model B, dotted = Model C.")'

p <- create_single_panel_plot("crp", "os")
if (!is.null(p)) print(p)
```

```{r crp-os-individual, fig.height=12, fig.width=8}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%): Individual model plots for overall survival showing detailed subgroup curves.")'

p_a <- create_individual_model_plot("crp", "A", "os")
p_b <- create_individual_model_plot("crp", "B_crp", "os")
p_c <- create_individual_model_plot("crp", "C_crp", "os")

if (!is.null(p_a) && !is.null(p_b) && !is.null(p_c)) {
  gridExtra::grid.arrange(p_a, p_b, p_c, ncol = 1)
}
```

## Progression-Free Survival

```{r crp-pfs-combined, fig.height=5, fig.width=10}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%) decomposition for progression-free survival across model structures.")'

p <- create_decomposition_plot("crp", "pfs", faceted = TRUE)
if (!is.null(p)) print(p)
```

```{r crp-pfs-single-panel, fig.height=6, fig.width=10}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%): All model structures overlaid in a single panel for progression-free survival. Solid line = Model A, dashed = Model B, dotted = Model C.")'

p <- create_single_panel_plot("crp", "pfs")
if (!is.null(p)) print(p)
```

```{r crp-pfs-individual, fig.height=12, fig.width=8}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%): Individual model plots for progression-free survival showing detailed subgroup curves.")'

p_a <- create_individual_model_plot("crp", "A", "pfs")
p_b <- create_individual_model_plot("crp", "B_crp", "pfs")
p_c <- create_individual_model_plot("crp", "C_crp", "pfs")

if (!is.null(p_a) && !is.null(p_b) && !is.null(p_c)) {
  gridExtra::grid.arrange(p_a, p_b, p_c, ncol = 1)
}
```

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# TLR Biomarker Strategy

Tumor lesion reduction (TLR) with a cutoff of >=10% for biomarker-positive status. **Biomarker prevalence: `r round(100 * p_tlr, 1)`%**. This is an early response biomarker measured after initial treatment cycles. Biomarker-positive patients receive alternating FLOX and nivolumab; biomarker-negative patients receive FLOX only.

```{r tlr-os-ly-table}
ly_table <- create_ly_table("tlr", "os")
kable(ly_table,
      caption = "TLR strategy: Overall survival life-years by model structure. Delta columns show difference vs. control.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

```{r tlr-pfs-ly-table}
ly_table <- create_ly_table("tlr", "pfs")
kable(ly_table,
      caption = "TLR strategy: Progression-free survival life-years by model structure. Delta columns show difference vs. control.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

## Overall Survival

```{r tlr-os-combined, fig.height=5, fig.width=10}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%) decomposition for overall survival across model structures. Red: biomarker-positive (experimental treatment), Blue: biomarker-negative (control treatment), Green: population-weighted strategy, Gray: control (all patients on standard treatment).")'

p <- create_decomposition_plot("tlr", "os", faceted = TRUE)
if (!is.null(p)) print(p)
```

```{r tlr-os-single-panel, fig.height=6, fig.width=10}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%): All model structures overlaid in a single panel for overall survival. Solid line = Model A, dashed = Model B, dotted = Model C.")'

p <- create_single_panel_plot("tlr", "os")
if (!is.null(p)) print(p)
```

```{r tlr-os-individual, fig.height=12, fig.width=8}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%): Individual model plots for overall survival showing detailed subgroup curves.")'

p_a <- create_individual_model_plot("tlr", "A", "os")
p_b <- create_individual_model_plot("tlr", "B_tlr", "os")
p_c <- create_individual_model_plot("tlr", "C_tlr", "os")

if (!is.null(p_a) && !is.null(p_b) && !is.null(p_c)) {
  gridExtra::grid.arrange(p_a, p_b, p_c, ncol = 1)
}
```

## Progression-Free Survival

```{r tlr-pfs-combined, fig.height=5, fig.width=10}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%) decomposition for progression-free survival across model structures.")'

p <- create_decomposition_plot("tlr", "pfs", faceted = TRUE)
if (!is.null(p)) print(p)
```

```{r tlr-pfs-single-panel, fig.height=6, fig.width=10}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%): All model structures overlaid in a single panel for progression-free survival. Solid line = Model A, dashed = Model B, dotted = Model C.")'

p <- create_single_panel_plot("tlr", "pfs")
if (!is.null(p)) print(p)
```

```{r tlr-pfs-individual, fig.height=12, fig.width=8}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%): Individual model plots for progression-free survival showing detailed subgroup curves.")'

p_a <- create_individual_model_plot("tlr", "A", "pfs")
p_b <- create_individual_model_plot("tlr", "B_tlr", "pfs")
p_c <- create_individual_model_plot("tlr", "C_tlr", "pfs")

if (!is.null(p_a) && !is.null(p_b) && !is.null(p_c)) {
  gridExtra::grid.arrange(p_a, p_b, p_c, ncol = 1)
}
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# TMB/BRAF Biomarker Strategy

Combined genomic biomarker: either tumor mutational burden (TMB) >= 9 mutations/MB or BRAF V600 mutation positive (both determined by next-generation sequencing). **Biomarker prevalence: `r round(100 * p_tmb_braf, 1)`%**. Biomarker-positive patients receive alternating FLOX and nivolumab; biomarker-negative patients receive FLOX only.

```{r tmb-os-ly-table}
ly_table <- create_ly_table("tmb_braf", "os")
kable(ly_table,
      caption = "TMB/BRAF strategy: Overall survival life-years by model structure. Delta columns show difference vs. control.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

```{r tmb-pfs-ly-table}
ly_table <- create_ly_table("tmb_braf", "pfs")
kable(ly_table,
      caption = "TMB/BRAF strategy: Progression-free survival life-years by model structure. Delta columns show difference vs. control.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 7))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

## Overall Survival

```{r tmb-os-combined, fig.height=5, fig.width=10}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%) decomposition for overall survival across model structures. Red: biomarker-positive (experimental treatment), Blue: biomarker-negative (control treatment), Green: population-weighted strategy, Gray: control (all patients on standard treatment).")'

p <- create_decomposition_plot("tmb_braf", "os", faceted = TRUE)
if (!is.null(p)) print(p)
```

```{r tmb-os-single-panel, fig.height=6, fig.width=10}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%): All model structures overlaid in a single panel for overall survival. Solid line = Model A, dashed = Model B, dotted = Model C.")'

p <- create_single_panel_plot("tmb_braf", "os")
if (!is.null(p)) print(p)
```

```{r tmb-os-individual, fig.height=12, fig.width=8}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%): Individual model plots for overall survival showing detailed subgroup curves.")'

p_a <- create_individual_model_plot("tmb_braf", "A", "os")
p_b <- create_individual_model_plot("tmb_braf", "B_tmb", "os")
p_c <- create_individual_model_plot("tmb_braf", "C_tmb", "os")

if (!is.null(p_a) && !is.null(p_b) && !is.null(p_c)) {
  gridExtra::grid.arrange(p_a, p_b, p_c, ncol = 1)
}
```

## Progression-Free Survival

```{r tmb-pfs-combined, fig.height=5, fig.width=10}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%) decomposition for progression-free survival across model structures.")'

p <- create_decomposition_plot("tmb_braf", "pfs", faceted = TRUE)
if (!is.null(p)) print(p)
```

```{r tmb-pfs-single-panel, fig.height=6, fig.width=10}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%): All model structures overlaid in a single panel for progression-free survival. Solid line = Model A, dashed = Model B, dotted = Model C.")'

p <- create_single_panel_plot("tmb_braf", "pfs")
if (!is.null(p)) print(p)
```

```{r tmb-pfs-individual, fig.height=12, fig.width=8}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%): Individual model plots for progression-free survival showing detailed subgroup curves.")'

p_a <- create_individual_model_plot("tmb_braf", "A", "pfs")
p_b <- create_individual_model_plot("tmb_braf", "B_tmb", "pfs")
p_c <- create_individual_model_plot("tmb_braf", "C_tmb", "pfs")

if (!is.null(p_a) && !is.null(p_b) && !is.null(p_c)) {
  gridExtra::grid.arrange(p_a, p_b, p_c, ncol = 1)
}
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Summary

All life-year (LY) gains reported in these tables are relative to the control strategy (standard of care with FLOX chemotherapy only). The tables show the decomposition of overall strategy effects into contributions from biomarker-positive and biomarker-negative patient subgroups.

```{r summary-os-table}
# Create OS summary table across all biomarkers with subgroup breakdown
summary_os <- data.frame()

for (biomarker in c("crp", "tlr", "tmb_braf")) {
  biomarker_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

  for (model_type in c("A", paste0(c("B_", "C_"), biomarker))) {
    if (model_type == paste0("B_", biomarker)) model_type <- switch(biomarker,
      crp = "B_crp", tlr = "B_tlr", tmb_braf = "B_tmb")
    if (model_type == paste0("C_", biomarker)) model_type <- switch(biomarker,
      crp = "C_crp", tlr = "C_tlr", tmb_braf = "C_tmb")

    pred <- multi_predictions$gamma[[model_type]]
    if (is.null(pred)) next

    model_letter <- substr(model_type, 1, 1)

    # Control life-years (baseline)
    control_os_ly <- if (!is.null(pred$control$os)) calculate_ly(pred$control$os) else NA

    # Biomarker+ life-years
    pos_os_ly <- if (!is.null(pred[[paste0(biomarker, "_pos")]]$os))
                   calculate_ly(pred[[paste0(biomarker, "_pos")]]$os) else NA

    # Biomarker- life-years
    neg_os_ly <- if (!is.null(pred[[paste0(biomarker, "_neg")]]$os))
                   calculate_ly(pred[[paste0(biomarker, "_neg")]]$os) else NA

    # Strategy (weighted) life-years
    strategy_os_ly <- if (!is.null(pred[[paste0(biomarker, "_weighted")]]$os))
                        calculate_ly(pred[[paste0(biomarker, "_weighted")]]$os) else NA

    summary_os <- rbind(summary_os, data.frame(
      Biomarker = biomarker_labels[biomarker],
      Model = paste0("Model ", model_letter),
      Strategy = strategy_os_ly - control_os_ly,
      `Biomarker+` = pos_os_ly - control_os_ly,
      `Biomarker-` = neg_os_ly - control_os_ly,
      check.names = FALSE
    ))
  }
}

kable(summary_os,
      caption = "Summary of overall survival life-year gains relative to control, decomposed by subgroup.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", "l", rep("r", 3))) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE) %>%
  collapse_rows(columns = 1, valign = "middle")
```

```{r summary-pfs-table}
# Create PFS summary table across all biomarkers with subgroup breakdown
summary_pfs <- data.frame()

for (biomarker in c("crp", "tlr", "tmb_braf")) {
  biomarker_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

  for (model_type in c("A", paste0(c("B_", "C_"), biomarker))) {
    if (model_type == paste0("B_", biomarker)) model_type <- switch(biomarker,
      crp = "B_crp", tlr = "B_tlr", tmb_braf = "B_tmb")
    if (model_type == paste0("C_", biomarker)) model_type <- switch(biomarker,
      crp = "C_crp", tlr = "C_tlr", tmb_braf = "C_tmb")

    pred <- multi_predictions$gamma[[model_type]]
    if (is.null(pred)) next

    model_letter <- substr(model_type, 1, 1)

    # Control life-years (baseline)
    control_pfs_ly <- if (!is.null(pred$control$pfs)) calculate_ly(pred$control$pfs) else NA

    # Biomarker+ life-years
    pos_pfs_ly <- if (!is.null(pred[[paste0(biomarker, "_pos")]]$pfs))
                    calculate_ly(pred[[paste0(biomarker, "_pos")]]$pfs) else NA

    # Biomarker- life-years
    neg_pfs_ly <- if (!is.null(pred[[paste0(biomarker, "_neg")]]$pfs))
                    calculate_ly(pred[[paste0(biomarker, "_neg")]]$pfs) else NA

    # Strategy (weighted) life-years
    strategy_pfs_ly <- if (!is.null(pred[[paste0(biomarker, "_weighted")]]$pfs))
                         calculate_ly(pred[[paste0(biomarker, "_weighted")]]$pfs) else NA

    summary_pfs <- rbind(summary_pfs, data.frame(
      Biomarker = biomarker_labels[biomarker],
      Model = paste0("Model ", model_letter),
      Strategy = strategy_pfs_ly - control_pfs_ly,
      `Biomarker+` = pos_pfs_ly - control_pfs_ly,
      `Biomarker-` = neg_pfs_ly - control_pfs_ly,
      check.names = FALSE
    ))
  }
}

kable(summary_pfs,
      caption = "Summary of progression-free survival life-year gains relative to control, decomposed by subgroup.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", "l", rep("r", 3))) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE) %>%
  collapse_rows(columns = 1, valign = "middle")
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
