---
title: "Biomarker Distributions"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup}
#| include: false

# Load required packages
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(here, knitr, kableExtra, dplyr, tableone, vcd)

# Set knitr options for PDF
options(knitr.table.format = "latex")

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())
```

```{r load-data}
#| include: false

# Load the full dataset directly to preserve continuous biomarker variables
data_full <- readRDS(here("data/tidy/METIMMOX.rds"))

# Create binary biomarker variables (same as 03_biomarker_strategies.R)
data_full$crp <- as.numeric(data_full$CRP1cat == 1)
data_full$tlr <- as.numeric(data_full$TLRcat == 1)
data_full$tmb_braf <- as.numeric((data_full$TMBcat == 1) | (data_full$Mutation == "BRAF"))

# Rename sex variable for consistency
data_full$sex <- data_full$Female

# Rename Progression exit to Progression (as in 02_setup_and_global_variables.R)
names(data_full)[names(data_full) == "Progression exit"] <- "Progression"
```

# Introduction

This report presents the distribution of patient characteristics stratified by treatment arm and biomarker status. Three biomarker strategies are evaluated:

- **CRP**: C-reactive protein (positive: CRP < 5)
- **TLR**: Tumor lesion reduction (positive: TLR $\geq$ 10%)
- **TMB/BRAF**: Combined biomarker (positive: TMB $\geq$ 9 mut/MB OR BRAF mutation)

Each table shows the distribution of age, sex, and the other two biomarkers (both categorical and continuous) within subgroups defined by treatment arm and biomarker status.

```{r prepare-data}
#| include: false

# Create complete cases dataset for analysis
data_complete <- data_full[complete.cases(data_full[, c("Age", "sex", "Rx", "crp", "tlr",
                                                         "tmb_braf", "OSwk", "Death",
                                                         "PFSwk", "Progression")]), ]

# Sample characteristics
n_total <- nrow(data_complete)
n_control <- sum(data_complete$Rx == "Control arm")
n_experimental <- sum(data_complete$Rx == "Experimental arm")

# Event counts
n_deaths <- sum(data_complete$Death)
n_progressions <- sum(data_complete$Progression)

# Biomarker prevalence
prev_crp <- mean(data_complete$crp)
prev_tlr <- mean(data_complete$tlr)
prev_tmb_braf <- mean(data_complete$tmb_braf)

# Create factor versions of biomarkers for better table display
data_complete <- data_complete %>%
  mutate(
    # Strata labels use just + and -
    crp_strata = factor(ifelse(crp == 1, "+", "-"), levels = c("-", "+")),
    tlr_strata = factor(ifelse(tlr == 1, "+", "-"), levels = c("-", "+")),
    tmb_braf_strata = factor(ifelse(tmb_braf == 1, "+", "-"), levels = c("-", "+")),
    # Row variable labels include biomarker name
    crp_status = factor(ifelse(crp == 1, "CRP+", "CRP-"), levels = c("CRP-", "CRP+")),
    tlr_status = factor(ifelse(tlr == 1, "TLR+", "TLR-"), levels = c("TLR-", "TLR+")),
    tmb_braf_status = factor(ifelse(tmb_braf == 1, "TMB/BRAF+", "TMB/BRAF-"),
                              levels = c("TMB/BRAF-", "TMB/BRAF+")),
    # Continuous variables with better names
    CRP_continuous = CRP1,
    TLR_continuous = TLR,
    TMB_continuous = TMB,
    # Events as factors for tableone
    Death_event = factor(Death, levels = c(0, 1), labels = c("No", "Yes")),
    Progression_event = factor(Progression, levels = c(0, 1), labels = c("No", "Yes"))
  )

# Create strata variables for each biomarker with clean labels
data_complete$strata_crp <- interaction(data_complete$Rx, data_complete$crp_strata, sep = " / ")
levels(data_complete$strata_crp) <- c("Control / -", "Control / +", "Exp / -", "Exp / +")

data_complete$strata_tlr <- interaction(data_complete$Rx, data_complete$tlr_strata, sep = " / ")
levels(data_complete$strata_tlr) <- c("Control / -", "Control / +", "Exp / -", "Exp / +")

data_complete$strata_tmb_braf <- interaction(data_complete$Rx, data_complete$tmb_braf_strata, sep = " / ")
levels(data_complete$strata_tmb_braf) <- c("Control / -", "Control / +", "Exp / -", "Exp / +")

# Calculate complete cases per stratum for each biomarker
complete_cases_crp <- table(data_complete$strata_crp)
complete_cases_tlr <- table(data_complete$strata_tlr)
complete_cases_tmb_braf <- table(data_complete$strata_tmb_braf)
```

# Sample Characteristics

```{r table-sample}
sample_df <- data.frame(
  Characteristic = c("Total patients (complete cases)",
                     "Control arm (FLOX alone)",
                     "Experimental arm (alternating FLOX/nivolumab)",
                     "",
                     "Deaths (OS events)",
                     "Progressions (PFS events)",
                     "",
                     "CRP-positive (low CRP)",
                     "TLR-positive (early response)",
                     "TMB/BRAF-positive"),
  Value = c(n_total,
            paste0(n_control, " (", round(100*n_control/n_total, 1), "%)"),
            paste0(n_experimental, " (", round(100*n_experimental/n_total, 1), "%)"),
            "",
            paste0(n_deaths, " (", round(100*n_deaths/n_total, 1), "%)"),
            paste0(n_progressions, " (", round(100*n_progressions/n_total, 1), "%)"),
            "",
            paste0(sum(data_complete$crp), " (", round(100*prev_crp, 1), "%)"),
            paste0(sum(data_complete$tlr), " (", round(100*prev_tlr, 1), "%)"),
            paste0(sum(data_complete$tmb_braf), " (", round(100*prev_tmb_braf, 1), "%)"))
)

sample_df %>%
  kable(col.names = c("Characteristic", "N (%)"),
        caption = "Sample Characteristics",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("HOLD_position"), font_size = 10) %>%
  row_spec(c(4, 7), bold = FALSE, extra_css = "border-bottom: none;")
```

# CRP Stratification

Distribution of patient characteristics by treatment arm and CRP status.

```{r table-crp}
# Variables for CRP table (exclude CRP, include TLR and TMB/BRAF both ways, plus events)
vars_crp <- c("Age", "sex", "TLR_continuous", "tlr_status", "TMB_continuous", "tmb_braf_status",
              "Death_event", "Progression_event")
factor_vars_crp <- c("sex", "tlr_status", "tmb_braf_status", "Death_event", "Progression_event")

# Create TableOne
tab_crp <- CreateTableOne(
  vars = vars_crp,
  strata = "strata_crp",
  data = data_complete,
  factorVars = factor_vars_crp,
  test = FALSE,
  addOverall = FALSE
)

# Print and convert to matrix
tab_crp_mat <- print(tab_crp,
                      printToggle = FALSE,
                      noSpaces = TRUE,
                      showAllLevels = TRUE)

# Convert to kable
kable(tab_crp_mat,
      caption = "Patient Characteristics by Treatment Arm and CRP Status",
      booktabs = TRUE,
      linesep = "") %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"),
                font_size = 10)
```

{{< pagebreak >}}
# TLR Stratification

Distribution of patient characteristics by treatment arm and TLR status.

```{r table-tlr}
# Variables for TLR table (exclude TLR, include CRP and TMB/BRAF both ways, plus events)
vars_tlr <- c("Age", "sex", "CRP_continuous", "crp_status", "TMB_continuous", "tmb_braf_status",
              "Death_event", "Progression_event")
factor_vars_tlr <- c("sex", "crp_status", "tmb_braf_status", "Death_event", "Progression_event")

# Create TableOne
tab_tlr <- CreateTableOne(
  vars = vars_tlr,
  strata = "strata_tlr",
  data = data_complete,
  factorVars = factor_vars_tlr,
  test = FALSE,
  addOverall = FALSE
)

# Print and convert to matrix
tab_tlr_mat <- print(tab_tlr,
                      printToggle = FALSE,
                      noSpaces = TRUE,
                      showAllLevels = TRUE)

# Convert to kable
kable(tab_tlr_mat,
      caption = "Patient Characteristics by Treatment Arm and TLR Status",
      booktabs = TRUE,
      linesep = "") %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"),
                font_size = 10)
```

# TMB/BRAF Stratification

Distribution of patient characteristics by treatment arm and TMB/BRAF status.

```{r table-tmb-braf}
# Variables for TMB/BRAF table (exclude TMB/BRAF, include CRP and TLR both ways, plus events)
vars_tmb <- c("Age", "sex", "CRP_continuous", "crp_status", "TLR_continuous", "tlr_status",
              "Death_event", "Progression_event")
factor_vars_tmb <- c("sex", "crp_status", "tlr_status", "Death_event", "Progression_event")

# Create TableOne
tab_tmb <- CreateTableOne(
  vars = vars_tmb,
  strata = "strata_tmb_braf",
  data = data_complete,
  factorVars = factor_vars_tmb,
  test = FALSE,
  addOverall = FALSE
)

# Print and convert to matrix
tab_tmb_mat <- print(tab_tmb,
                      printToggle = FALSE,
                      noSpaces = TRUE,
                      showAllLevels = TRUE)

# Convert to kable
kable(tab_tmb_mat,
      caption = "Patient Characteristics by Treatment Arm and TMB/BRAF Status",
      booktabs = TRUE,
      linesep = "") %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"),
                font_size = 10)
```

{{< pagebreak >}}
# Biomarker Correlations

```{r biomarker-correlation}
#| include: false

# CRP vs TLR
crp_tlr_table <- table(data_complete$crp, data_complete$tlr)
crp_tlr_assoc <- assocstats(crp_tlr_table)
cramers_v_crp_tlr <- crp_tlr_assoc$cramer

# CRP vs TMB/BRAF
crp_tmb_table <- table(data_complete$crp, data_complete$tmb_braf)
crp_tmb_assoc <- assocstats(crp_tmb_table)
cramers_v_crp_tmb <- crp_tmb_assoc$cramer

# TLR vs TMB/BRAF
tlr_tmb_table <- table(data_complete$tlr, data_complete$tmb_braf)
tlr_tmb_assoc <- assocstats(tlr_tmb_table)
cramers_v_tlr_tmb <- tlr_tmb_assoc$cramer

# Build correlation summary
correlation_df <- data.frame(
  Comparison = c("CRP vs TLR", "CRP vs TMB/BRAF", "TLR vs TMB/BRAF"),
  Cramers_V = round(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), 3),
  Interpretation = sapply(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), function(v) {
    if (v > 0.3) "Moderate/Strong"
    else if (v > 0.1) "Weak"
    else "Negligible"
  })
)
```

```{r table-correlation}
correlation_df %>%
  kable(col.names = c("Biomarker Pair", "Cramer's V", "Interpretation"),
        caption = "Biomarker Correlations (Cramer's V)",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("HOLD_position"), font_size = 10)
```

**Note:** Cramer's V interpretation: <0.1 = Negligible, 0.1-0.3 = Weak, >0.3 = Moderate/Strong. The observed correlations are weak to negligible.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0