---
title: "Biosimilar Nivolumab Pricing Scenario"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r biosim-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")

# Load rlang explicitly first
library(rlang)

# Then load other packages
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/psa_functions.R",
  "scripts/R/functions/evppi_functions.R",
  "scripts/R/functions/scenario_analysis.R",
  "scripts/R/functions/multi_model_cea.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Source analysis setup script to define global variables (e.g. utility_source_label)
suppressMessages(suppressWarnings(
  source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
))
```

```{r biosim-load-cache, include=FALSE}
# Load scenario analysis results (try full cache first, then preview, then legacy names)
cache_file         <- here("data/tidy", paste0("scenario_evppi_results_", utility_source_label, ".rds"))
preview_cache_file <- here("data/tidy", paste0("scenario_evppi_results_", utility_source_label, "_PREVIEW.rds"))
legacy_cache_file  <- here("data/tidy", "scenario_evppi_results.rds")
legacy_preview_file <- here("data/tidy", "scenario_evppi_results_PREVIEW.rds")

if (file.exists(cache_file)) {
  cat("Loading full scenario analysis results from cache...\n")
  evppi_cache <- readRDS(cache_file)
} else if (file.exists(preview_cache_file)) {
  cat("Full cache not found. Loading PREVIEW results (reduced iterations)...\n")
  evppi_cache <- readRDS(preview_cache_file)
} else if (file.exists(legacy_cache_file)) {
  cat("Loading legacy full cache (no utility label)...\n")
  evppi_cache <- readRDS(legacy_cache_file)
} else if (file.exists(legacy_preview_file)) {
  cat("Loading legacy PREVIEW cache (no utility label)...\n")
  evppi_cache <- readRDS(legacy_preview_file)
} else {
  stop("No scenario analysis cache found. Please run script 14 (14_scenario_EVPPIs.R) or 14b_scenario_preview.R first.")
}

# Extract components
all_model_scenario_results <- evppi_cache$all_model_scenario_results
scenarios <- evppi_cache$scenarios

cat("Cache loaded successfully.\n")
cat("Available model structures:", names(all_model_scenario_results), "\n")
cat("Available scenarios:", scenarios$scenario_id, "\n")
```

```{r biosim-extract-results, include=FALSE}
# Determine which model structures are available in cache
all_model_labels <- c("joint", "focused", "separate")
all_model_names <- c("Model A: Joint", "Model B: Focused", "Model C: Separate")
all_short_labels <- c("A", "B", "C")

available_mask <- all_model_labels %in% names(all_model_scenario_results)
model_labels <- all_model_labels[available_mask]
model_names <- all_model_names[available_mask]
short_labels <- all_short_labels[available_mask]

cat("Available model structures:", paste(model_labels, collapse = ", "), "\n")

# Storage for comparison
base_case_results <- list()
biosim_results <- list()

for (i in seq_along(model_labels)) {
  model_label <- model_labels[i]

  # Base case
  base_case_results[[model_label]] <- all_model_scenario_results[[model_label]][["base"]]

  # Biosimilar scenario
  biosim_results[[model_label]] <- all_model_scenario_results[[model_label]][["s1_decreased_nivo"]]
}

cat("Results extracted for base case and biosimilar scenario.\n")
```

# Overview

This report presents cost-effectiveness results under a biosimilar nivolumab pricing scenario. The analysis examines whether reduced drug costs make biomarker-guided immunotherapy strategies cost-effective at the EUR 51,000 willingness-to-pay threshold.

## Pricing Scenarios

We compare two pricing scenarios:

```{r biosim-pricing-table}
pricing_table <- data.frame(
  Scenario = c("Base Case", "Biosimilar"),
  Nivolumab_Cost = c("EUR 13,923", "EUR 4,641"),
  Price_Change = c("--", "-67%"),
  Description = c(
    "List price for branded nivolumab per administration",
    "Biosimilar price (80% discount from list price)"
  )
)

knitr::kable(pricing_table,
             col.names = c("Scenario", "Nivolumab Cost", "Price Change", "Description"),
             align = c("l", "r", "r", "l"),
             booktabs = TRUE,
             caption = "Nivolumab Pricing Scenarios") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

The biosimilar price of EUR 4,641 per administration represents a 67% reduction from the base case price of EUR 13,923, equivalent to an 80% discount from the list price.

## Model Structures

Each pricing scenario is analyzed using three alternative model structures for survival analysis:

```{r biosim-model-table}
model_structure_df <- data.frame(
  Model = c("Model A", "Model B", "Model C"),
  Name = c("Joint", "Focused", "Separate"),
  Formula = c(
    "Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx",
    "Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx",
    "Age + sex + Rx + [biomarker]:Rx"
  ),
  Description = c(
    "All biomarkers and all treatment interactions",
    "Per-strategy formulas: CRP/TMB_BRAF with both interactions",
    "One biomarker and its interaction per model"
  )
)

knitr::kable(model_structure_df,
             col.names = c("Model", "Name", "Formula Pattern", "Description"),
             align = c("l", "l", "l", "l"),
             booktabs = TRUE,
             caption = "Model Structures for Survival Analysis") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::column_spec(3, width = "5cm") %>%
  kableExtra::column_spec(4, width = "4cm")
```

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Deterministic Cost-Effectiveness Results

## Multi-Model Comparison: Base Case vs. Biosimilar

```{r biosim-det-comparison, include=FALSE}
# Get strategy names from PSA object
strategies_list <- base_case_results[[model_labels[1]]]$psa_obj$strategies

# Strategy display names
strategy_display <- c("control" = "Standard of Care", "crp" = "CRP-guided",
                      "tlr" = "TLR-guided", "tmb_braf" = "TMB/BRAF-guided")

# Initialize comparison data frame
comparison_df <- data.frame(
  Strategy = strategy_display[strategies_list]
)

# Build columns for each available model
for (i in seq_along(model_labels)) {
  model_label <- model_labels[i]
  short_label <- short_labels[i]

  # Base case
  base_psa <- base_case_results[[model_label]]$psa_obj
  base_summary <- summary(base_psa, calc_sds = FALSE)

  comparison_df[[paste0("Cost_Base_", short_label)]] <- base_summary$meanCost
  comparison_df[[paste0("QALY_Base_", short_label)]] <- base_summary$meanEffect

  # Calculate ICERs
  base_icer <- dampack::calculate_icers(
    cost = base_summary$meanCost,
    effect = base_summary$meanEffect,
    strategies = strategies_list
  )
  comparison_df[[paste0("ICER_Base_", short_label)]] <- base_icer$ICER

  # Biosimilar scenario
  biosim_psa <- biosim_results[[model_label]]$psa_obj
  biosim_summary <- summary(biosim_psa, calc_sds = FALSE)

  comparison_df[[paste0("Cost_Biosim_", short_label)]] <- biosim_summary$meanCost
  comparison_df[[paste0("QALY_Biosim_", short_label)]] <- biosim_summary$meanEffect

  # Calculate ICERs
  biosim_icer <- dampack::calculate_icers(
    cost = biosim_summary$meanCost,
    effect = biosim_summary$meanEffect,
    strategies = strategies_list
  )
  comparison_df[[paste0("ICER_Biosim_", short_label)]] <- biosim_icer$ICER
}
```

```{r biosim-tables, results='asis'}
# Generate ICER table for each available model structure
for (i in seq_along(model_labels)) {
  short_label <- short_labels[i]
  model_name <- model_names[i]

  cat("###", model_name, "\n\n")

  model_df <- data.frame(
    Strategy = comparison_df$Strategy,
    Cost_Base = comparison_df[[paste0("Cost_Base_", short_label)]],
    QALY_Base = comparison_df[[paste0("QALY_Base_", short_label)]],
    ICER_Base = comparison_df[[paste0("ICER_Base_", short_label)]],
    Cost_Biosim = comparison_df[[paste0("Cost_Biosim_", short_label)]],
    QALY_Biosim = comparison_df[[paste0("QALY_Biosim_", short_label)]],
    ICER_Biosim = comparison_df[[paste0("ICER_Biosim_", short_label)]]
  )

  # Format for display
  display_df <- model_df
  display_df$Cost_Base <- scales::dollar(display_df$Cost_Base, prefix = "EUR ", accuracy = 1, big.mark = ",")
  display_df$QALY_Base <- sprintf("%.3f", display_df$QALY_Base)
  display_df$ICER_Base <- ifelse(is.na(display_df$ICER_Base) | is.infinite(display_df$ICER_Base),
                                  "--",
                                  scales::dollar(display_df$ICER_Base, prefix = "EUR ", accuracy = 1, big.mark = ","))
  display_df$Cost_Biosim <- scales::dollar(display_df$Cost_Biosim, prefix = "EUR ", accuracy = 1, big.mark = ",")
  display_df$QALY_Biosim <- sprintf("%.3f", display_df$QALY_Biosim)
  display_df$ICER_Biosim <- ifelse(is.na(display_df$ICER_Biosim) | is.infinite(display_df$ICER_Biosim),
                                    "--",
                                    scales::dollar(display_df$ICER_Biosim, prefix = "EUR ", accuracy = 1, big.mark = ","))

  tbl <- knitr::kable(display_df,
               col.names = c("Strategy",
                            "Cost", "QALY", "ICER",
                            "Cost", "QALY", "ICER"),
               align = c("l", "r", "r", "r", "r", "r", "r"),
               booktabs = TRUE,
               caption = paste0(model_name, " - Base Case vs. Biosimilar Scenario")) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
    kableExtra::add_header_above(c(" " = 1, "Base Case" = 3, "Biosimilar Scenario" = 3))

  print(tbl)
  cat("\n\n")
}
```

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Probabilistic Sensitivity Analysis

## Cost-Effectiveness Planes: Biosimilar Scenario

```{r biosim-ce-planes, results='asis', fig.width=8, fig.height=6}
for (i in seq_along(model_labels)) {
  model_label <- model_labels[i]
  model_name <- model_names[i]

  cat("###", model_name, "\n\n")

  psa_plot <- plot(biosim_results[[model_label]]$psa_obj,
                   frontier = TRUE,
                   points = TRUE,
                   alpha = 0.4,
                   txtsize = 11,
                   currency = "EUR",
                   effect_units = "QALYs")
  print(psa_plot)
  cat("\n\n")
}
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

## Cost-Effectiveness Acceptability Curves (CEAC)

```{r biosim-ceac-setup, include=FALSE}
# Define WTP range
c_wtp <- seq(from = 0, to = 2e5, by = 5e3)

# Create CEAC objects for base case and biosimilar (for each available model)
ceac_base <- list()
ceac_biosim <- list()

for (model_label in model_labels) {
  ceac_base[[model_label]] <- ceac(c_wtp, base_case_results[[model_label]]$psa_obj)
  ceac_biosim[[model_label]] <- ceac(c_wtp, biosim_results[[model_label]]$psa_obj)
}
```

```{r biosim-ceac-plots, results='asis', fig.width=8, fig.height=6}
for (i in seq_along(model_labels)) {
  model_label <- model_labels[i]
  model_name <- model_names[i]

  cat("###", model_name, "\n\n")

  cat("**Base Case:**\n\n")
  ceac_plot_base <- plot(ceac_base[[model_label]], frontier = TRUE, currency = "EUR", txtsize = 11)
  print(ceac_plot_base)
  cat("\n\n")

  cat("**Biosimilar Scenario:**\n\n")
  ceac_plot_biosim <- plot(ceac_biosim[[model_label]], frontier = TRUE, currency = "EUR", txtsize = 11)
  print(ceac_plot_biosim)
  cat("\n\n")
}
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Summary of Key Findings

## Cost-Effectiveness at EUR 51,000 WTP Threshold

```{r biosim-summary-stats, include=FALSE}
# Calculate probability cost-effective at EUR 51,000 for each model and scenario
wtp_threshold <- 51000

# dampack::ceac() returns long-format data frame: WTP, Strategy, Proportion, On_Frontier
# Extract per-strategy probabilities at a specific WTP
get_prob_at_wtp <- function(ceac_obj, wtp) {
  # Find closest WTP value
  closest_wtp <- ceac_obj$WTP[which.min(abs(unique(ceac_obj$WTP) - wtp))]
  ceac_at_wtp <- ceac_obj[ceac_obj$WTP == closest_wtp, ]
  probs <- setNames(ceac_at_wtp$Proportion, ceac_at_wtp$Strategy)
  return(probs)
}

# Extract probabilities for each available model
prob_base <- list()
prob_biosim <- list()

for (model_label in model_labels) {
  prob_base[[model_label]] <- get_prob_at_wtp(ceac_base[[model_label]], wtp_threshold)
  prob_biosim[[model_label]] <- get_prob_at_wtp(ceac_biosim[[model_label]], wtp_threshold)
}

# Create summary table
summary_rows <- list()
for (i in seq_along(model_labels)) {
  model_label <- model_labels[i]
  model_name <- model_names[i]
  strats <- names(prob_base[[model_label]])

  for (s in strats) {
    summary_rows[[length(summary_rows) + 1]] <- data.frame(
      Model = model_name,
      Strategy = strategy_display[s],
      Prob_Base = prob_base[[model_label]][s],
      Prob_Biosim = prob_biosim[[model_label]][s],
      stringsAsFactors = FALSE
    )
  }
}

summary_table <- do.call(rbind, summary_rows)
rownames(summary_table) <- NULL

# Format as percentages
summary_table$Prob_Base_pct <- sprintf("%.1f%%", summary_table$Prob_Base * 100)
summary_table$Prob_Biosim_pct <- sprintf("%.1f%%", summary_table$Prob_Biosim * 100)
summary_table$Change <- sprintf("%+.1f pp", (summary_table$Prob_Biosim - summary_table$Prob_Base) * 100)
```

```{r biosim-summary-table}
display_summary <- summary_table[, c("Model", "Strategy", "Prob_Base_pct", "Prob_Biosim_pct", "Change")]

knitr::kable(display_summary,
             col.names = c("Model", "Strategy", "Base Case", "Biosimilar", "Change"),
             align = c("l", "l", "r", "r", "r"),
             booktabs = TRUE,
             caption = "Probability of Cost-Effectiveness at EUR 51,000 WTP Threshold") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::add_header_above(c(" " = 2, "Probability Cost-Effective" = 2, " " = 1)) %>%
  kableExtra::collapse_rows(columns = 1, latex_hline = "major")
```

## Key Observations

```{r biosim-text-summary, results='asis'}
for (i in seq_along(model_labels)) {
  model_label <- model_labels[i]
  model_name <- model_names[i]

  pb <- prob_base[[model_label]]
  pbio <- prob_biosim[[model_label]]

  optimal_base <- names(pb)[which.max(pb)]
  optimal_biosim <- names(pbio)[which.max(pbio)]

  cat("**", model_name, ":**\n\n", sep = "")
  cat("- Base case optimal strategy:", strategy_display[optimal_base],
      "(", sprintf("%.1f%%", max(pb) * 100), "probability)\n")
  cat("- Biosimilar optimal strategy:", strategy_display[optimal_biosim],
      "(", sprintf("%.1f%%", max(pbio) * 100), "probability)\n\n")
}
```

## Impact of Biosimilar Pricing

The 67% reduction in nivolumab cost (from EUR 13,923 to EUR 4,641 per administration) represents a substantial price decrease. However, the impact on cost-effectiveness depends on several factors:

1. **Direct cost savings**: Only biomarker-positive patients receive nivolumab, so cost savings are proportional to biomarker prevalence
2. **Testing costs**: Biomarker strategies incur additional testing costs (EUR 2,000 for TMB/BRAF NGS testing)
3. **Clinical effectiveness**: The biosimilar pricing scenario does not change clinical outcomes (QALYs), so any improvement in cost-effectiveness is purely through cost reduction

The results demonstrate whether the biosimilar price reduction is sufficient to make biomarker-guided strategies cost-effective at the EUR 51,000 willingness-to-pay threshold.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
