---
title: "Biosimilar Nivolumab Pricing Scenario"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05"),
  funs = c("model_fun", "calculate_outcomes", "cea_helpers", "report_format"),
  set_theme = FALSE
)

# Pairwise ICERs versus standard of care plus the dampack frontier status
# (issue #153): the two conventions are reported side by side, never mixed.
run_pairwise <- function(params) {
  calculate_pairwise_icers(model_fun(params, determpsa = "det"))
}

base_params <- l_params_base
biosimilar_params <- l_params_base
biosimilar_params$c_drug_nivo <- 4641

base_results <- run_pairwise(base_params)
biosimilar_results <- run_pairwise(biosimilar_params)
```

# Overview

This scenario examines whether a lower nivolumab acquisition cost changes the cost-effectiveness of the single joint economic model. The strategies are standard of care, CRP-guided immunotherapy, and TMB/BRAF-guided immunotherapy.

# Pricing Scenarios

```{r pricing-table}
pricing_table <- data.frame(
  Scenario = c("Base case", "Biosimilar"),
  Nivolumab_Cost = c(l_params_base$c_drug_nivo, biosimilar_params$c_drug_nivo),
  Price_Change = c("--", scales::percent(biosimilar_params$c_drug_nivo / l_params_base$c_drug_nivo - 1,
                                          accuracy = 0.1)),
  stringsAsFactors = FALSE
)

pricing_table$Nivolumab_Cost <- format_eur(pricing_table$Nivolumab_Cost)

knitr::kable(
  pricing_table,
  booktabs = TRUE,
  align = c("l", "r", "r"),
  col.names = c("Scenario", "Nivolumab Cost per Administration", "Change"),
  caption = "Nivolumab pricing scenarios"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Deterministic Results

```{r scenario-results}
scenario_all <- bind_rows(
  base_results %>% mutate(Scenario = "Base case"),
  biosimilar_results %>% mutate(Scenario = "Biosimilar")
) %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Cost = format_eur(Cost),
    Effect = sprintf("%.3f", Effect),
    Inc_Cost = ifelse(Status == "Reference", "--", format_eur(Inc_Cost)),
    Inc_Effect = ifelse(Status == "Reference", "--", sprintf("%.3f", Inc_Effect)),
    ICER = mapply(format_icer, ICER, Status),
    Frontier = frontier_label(Frontier_Status)
  )

knitr::kable(
  scenario_all %>% select(Scenario, Strategy, Cost, Effect),
  booktabs = TRUE,
  align = c("l", "l", "r", "r"),
  col.names = c("Scenario", "Strategy", "Cost", "QALYs"),
  caption = "Base case and biosimilar deterministic results: discounted cost and QALYs per patient"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario-incremental}
knitr::kable(
  scenario_all %>% select(Scenario, Strategy, Inc_Cost, Inc_Effect, ICER, Status, Frontier),
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r", "l", "l"),
  col.names = c("Scenario", "Strategy", "Incr. cost", "Incr. QALYs", "ICER",
                "Pairwise status", "Frontier"),
  caption = "Incremental results versus standard of care (pairwise convention) with the efficiency-frontier status"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"), font_size = 9) %>%
  kableExtra::footnote(
    general = paste(
      "Incremental cost, incremental QALYs and ICER compare each guided strategy",
      "with standard of care (pairwise convention). 'Frontier' is the dampack",
      "efficiency-frontier status across all three strategies; a strategy can be",
      "dominated on the frontier (more costly and less effective than another",
      "guided strategy) while still having a finite pairwise ICER versus standard",
      "of care. Percentage changes between pairwise ICERs of frontier-dominated",
      "strategies are not reported."
    ),
    threeparttable = TRUE
  )
```

```{r nmb-plot, fig.cap="Net monetary benefit by pricing scenario"}
nmb_plot <- bind_rows(
  base_results %>% mutate(Scenario = "Base case"),
  biosimilar_results %>% mutate(Scenario = "Biosimilar")
) %>%
  mutate(
    Strategy = strategy_label(Strategy),
    NMB = Effect * WTP - Cost
  )

ggplot(nmb_plot, aes(x = Strategy, y = NMB, fill = Scenario)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  scale_y_continuous(labels = scales::dollar_format(prefix = "EUR ", scale = 0.001,
                                                    suffix = "K")) +
  labs(x = NULL, y = "Net Monetary Benefit", fill = NULL) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 20, hjust = 1),
        legend.position = "bottom")
```

# Summary

The biosimilar scenario is evaluated with the same single joint economic survival model as the base case. Only the nivolumab administration cost is changed; strategy definitions, biomarker prevalences, utilities, and survival curves are unchanged.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.1
