---
title: "Cost-Effectiveness Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

knitr::opts_knit$set(root.dir = here::here())

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, scales,
  survival, flexsurv, dampack
)

theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom"
  ))

suppressMessages(suppressWarnings({
  source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
  source(here::here("scripts/R/analysis/03_biomarker_strategies.R"))
  source(here::here("scripts/R/analysis/06_parametric_survival_analysis.R"))
  source(here::here("scripts/R/analysis/07_basecase_input_parameters.R"))
  source(here::here("scripts/R/functions/model_fun.R"))
  source(here::here("scripts/R/functions/calculate_outcomes.R"))
  source(here::here("scripts/R/functions/multi_model_cea.R"))
}))

strategy_label <- function(x) {
  dplyr::recode(
    x,
    control = "Standard of Care",
    crp = "CRP-guided",
    tmb_braf = "TMB/BRAF-guided",
    .default = x
  )
}

format_eur <- function(x) {
  ifelse(is.na(x) | !is.finite(x), "--",
         scales::dollar(x, prefix = "EUR ", accuracy = 1))
}

format_icer <- function(x, status = NULL) {
  if (!is.null(status) && status %in% c("D", "ED", "Dominated")) return("Dominated")
  if (!is.null(status) && status %in% c("Reference", "ref")) return("--")
  if (is.na(x) || !is.finite(x)) return("--")
  scales::dollar(x, prefix = "EUR ", accuracy = 1)
}

basecase <- run_basecase(verbose = FALSE)
base_results <- basecase$base_results
icer_obj <- basecase$icer_obj
model_config <- basecase$model_config
psa_obj <- load_psa_cache(verbose = FALSE)
```

# Overview

This cost-effectiveness analysis evaluates standard of care against two pre-treatment biomarker-guided immunotherapy strategies for metastatic MSS/pMMR colorectal cancer:

- CRP-guided treatment selection
- TMB/BRAF-guided treatment selection

The economic survival model is a single joint model with CRP and TMB/BRAF treatment interactions. Economic strategies are restricted to pre-treatment biomarkers.

# Economic Survival Model

```{r model-table}
model_df <- data.frame(
  Component = c("OS", "PFS", "Control"),
  Formula = c(
    "Surv(OSwk, Death) ~ Age + sex + Rx + crp*Rx + tmb_braf*Rx",
    "Surv(PFSwk, Progression) ~ Age + sex + Rx + crp*Rx + tmb_braf*Rx",
    "Surv(time, event) ~ Age + sex"
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  model_df,
  booktabs = TRUE,
  align = c("l", "l"),
  caption = "Single economic survival model"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "10cm")
```

```{r strategy-table}
strategy_df <- data.frame(
  Strategy = strategy_label(get_strategies()),
  Definition = c(
    "All patients receive standard FLOX chemotherapy",
    "CRP-positive patients receive FLOX + nivolumab; CRP-negative patients receive FLOX",
    "TMB/BRAF-positive patients receive FLOX + nivolumab; TMB/BRAF-negative patients receive FLOX"
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  strategy_df,
  booktabs = TRUE,
  align = c("l", "l"),
  caption = "Economic strategies"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "10cm")
```

# Base Case Results

```{r basecase-table}
base_display <- base_results %>%
  mutate(
    NMB = Effect * WTP - Cost,
    Strategy = strategy_label(Strategy),
    Cost = format_eur(Cost),
    Effect = sprintf("%.3f", Effect),
    NMB = format_eur(NMB)
  )

knitr::kable(
  base_display,
  booktabs = TRUE,
  align = c("l", "r", "r", "r"),
  col.names = c("Strategy", "Cost", "QALYs", "NMB"),
  caption = paste0("Base case results at WTP = EUR ", format(WTP, big.mark = ","))
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r icer-table}
icer_display <- as.data.frame(icer_obj) %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Cost = format_eur(Cost),
    Effect = sprintf("%.3f", Effect),
    Inc_Cost = format_eur(Inc_Cost),
    Inc_Effect = ifelse(is.na(Inc_Effect), "--", sprintf("%.3f", Inc_Effect)),
    ICER = mapply(format_icer, ICER, Status)
  )

knitr::kable(
  icer_display,
  booktabs = TRUE,
  align = c("l", "r", "r", "r", "r", "r", "l"),
  col.names = c("Strategy", "Cost", "QALYs", "Incremental Cost",
                "Incremental QALYs", "ICER", "Status"),
  caption = "Incremental cost-effectiveness results"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r ce-plane, fig.cap="Cost-effectiveness plane for the single joint economic model"}
plot(
  icer_obj,
  txtsize = 11,
  currency = "EUR",
  effect_units = "QALYs",
  label = "all",
  alpha = 0.8
)
```

# Probabilistic Sensitivity Analysis

```{r psa-summary}
if (is.null(psa_obj)) {
  cat("PSA cache not found. Run scripts/R/analysis/12_PSA.R after regenerating the single-model sampling cache.")
} else {
  psa_summary <- create_psa_summary_table(psa_obj, wtp = WTP) %>%
    mutate(
      Strategy = strategy_label(Strategy),
      Mean_Cost = format_eur(Mean_Cost),
      Mean_QALY = sprintf("%.3f", Mean_QALY),
      Prob_CE = scales::percent(Prob_CE, accuracy = 0.1)
    )

  knitr::kable(
    psa_summary,
    booktabs = TRUE,
    align = c("l", "r", "r", "r"),
    col.names = c("Strategy", "Mean Cost", "Mean QALYs", "Probability Cost-Effective"),
    caption = paste0("PSA summary at WTP = EUR ", format(WTP, big.mark = ","))
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
}
```

```{r ceac, fig.cap="Cost-effectiveness acceptability curves"}
if (is.null(psa_obj)) {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = "PSA cache not available", size = 5) +
    theme_void()
} else {
  create_ceac_plot(psa_obj, wtp_line = WTP)
}
```

# Summary

The economic evaluation now uses one joint survival model and three economic strategies: standard of care, CRP-guided immunotherapy, and TMB/BRAF-guided immunotherapy.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
