---
title: "Cost-Effectiveness Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r cea-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r setup-global-variables, include=FALSE}
# 02 - Setup and Global Variables
source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
```

```{r biomarker-strategies, include=FALSE}
# 03 - Biomarker Strategies
source(here::here("scripts/R/analysis/03_biomarker_strategies.R"))
```

```{r load-helper-functions, include=FALSE}
# Source helper functions AFTER global variables are set
source(here::here("scripts/R/functions/model_fun.R"))
source(here::here("scripts/R/functions/calculate_outcomes.R"))
source(here::here("scripts/R/functions/multi_model_cea.R"))

# Verify that key functions are available
stopifnot(
  "model_fun not loaded" = exists("model_fun"),
  "calculate_outcomes not loaded" = exists("calculate_outcomes"),
  "run_all_basecase_analyses not loaded" = exists("run_all_basecase_analyses"),
  "get_model_configs not loaded" = exists("get_model_configs")
)
```

```{r generate-caches-if-missing, include=FALSE}
# ===============================================================================
# AUTO-GENERATE MISSING CACHE FILES
# ===============================================================================
# Check if sampling and PSA caches exist for all model structures.
# If any are missing, generate them before proceeding.
# ===============================================================================

model_labels <- c("joint", "focused", "separate")

# Check for missing sampling caches
missing_sampling_caches <- character()
for (label in model_labels) {
  cache_file <- here::here("data", "tidy",
                           paste0("sampling_models_n", n_samples, "_",
                                  ifelse(USE_BOTH_MODELS == 0, "full", "both"), "_",
                                  label, ".rds"))
  if (!file.exists(cache_file)) {
    missing_sampling_caches <- c(missing_sampling_caches, label)
  }
}

# Check for missing PSA caches
missing_psa_caches <- character()
for (label in model_labels) {
  cache_file <- here::here("data", "tidy", paste0("psa_obj_", label, ".rds"))
  if (!file.exists(cache_file)) {
    missing_psa_caches <- c(missing_psa_caches, label)
  }
}

# Generate missing sampling caches
if (length(missing_sampling_caches) > 0) {
  cat("\n=== Generating missing sampling caches ===\n")
  cat("Missing caches for:", paste(missing_sampling_caches, collapse = ", "), "\n")
  cat("This may take several minutes per model structure...\n\n")

  for (label in missing_sampling_caches) {
    model_idx <- which(model_labels == label)
    MODEL_STRUCTURE <- model_idx - 1  # 0, 1, or 2

    cat("\n--- Generating sampling cache for MODEL_STRUCTURE =", MODEL_STRUCTURE,
        "(", label, ") ---\n")

    # Re-source scripts for this MODEL_STRUCTURE
    source(here::here("scripts/R/analysis/06_parametric_survival_analysis.R"))
    source(here::here("scripts/R/analysis/07_basecase_input_parameters.R"))

    # Source sampling script (generates cache)
    source(here::here("scripts/R/analysis/08_sampling.R"))
  }

  cat("\n=== Sampling cache generation complete ===\n")
}

# Generate missing PSA caches
if (length(missing_psa_caches) > 0) {
  cat("\n=== Generating missing PSA caches ===\n")
  cat("Missing caches for:", paste(missing_psa_caches, collapse = ", "), "\n")
  cat("This may take 20-60 minutes per model structure...\n\n")

  for (label in missing_psa_caches) {
    model_idx <- which(model_labels == label)
    MODEL_STRUCTURE <- model_idx - 1  # 0, 1, or 2

    cat("\n--- Generating PSA cache for MODEL_STRUCTURE =", MODEL_STRUCTURE,
        "(", label, ") ---\n")

    # Re-source scripts for this MODEL_STRUCTURE
    source(here::here("scripts/R/analysis/06_parametric_survival_analysis.R"))
    source(here::here("scripts/R/analysis/07_basecase_input_parameters.R"))

    # Load the sampling cache for this model structure
    sampling_cache_file <- here::here("data", "tidy",
                                      paste0("sampling_models_n", n_samples, "_",
                                             ifelse(USE_BOTH_MODELS == 0, "full", "both"), "_",
                                             label, ".rds"))
    if (file.exists(sampling_cache_file)) {
      sampling_models <- readRDS(sampling_cache_file)
    }

    # Source PSA script (generates cache)
    source(here::here("scripts/R/analysis/12_PSA.R"))
  }

  cat("\n=== PSA cache generation complete ===\n")
}

# Reset MODEL_STRUCTURE to default
MODEL_STRUCTURE <- 0
```

```{r qalys-data-processing, include=FALSE}
# 05 - Process QALYs data with proper error handling
tryCatch({
  metimmox_file <- here::here("data/tidy/METIMMOX.rds")
  if (file.exists(metimmox_file)) {
    METIMMOX <- readRDS(metimmox_file)
  }
}, error = function(e) {
  # File doesn't exist or can't be read - continue without it
})

tryCatch({
  qaly_file <- here::here("data/sensitive/231208 METIMMOX EQ_5D_5L.xlsx")
  if (file.exists(qaly_file)) {
    QALYsraw <- read_excel(qaly_file, sheet = 2, skip = 1) %>%
      rename(ID = SubjectId)
  }
}, error = function(e) {
  # File doesn't exist or can't be read - continue without it
})
```

# Overview

This cost-effectiveness analysis evaluates three biomarker-guided strategies (CRP, TLR, and TMB/BRAF) for selecting metastatic microsatellite stable (MSS)/proficient mismatch repair (pMMR) colorectal cancer patients who might benefit from immunotherapy with nivolumab plus FLOX versus standard FLOX chemotherapy.

**Key Feature**: This report compares cost-effectiveness results across three different model structures (Model A, B, C) to assess the robustness of our findings to modeling assumptions about how biomarker interactions are specified.

This report contains:

- **Model Structure Definitions**: Explanation of the three model specifications compared
- **Strategy Descriptions**: Overview of the four treatment strategies evaluated
- **Base Case Analysis**: Cost-effectiveness results across all three model structures
- **Probabilistic Sensitivity Analysis**: Monte Carlo simulation results comparing model structures

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Model Structure Definitions

We compare three model structures to assess the robustness of cost-effectiveness results to the specification of biomarker-treatment interactions in the survival models.

**Table 1: Model Structure Definitions**

```{r model-structure-table}
model_structure_df <- data.frame(
  Model = c("Model A", "Model B", "Model C"),
  Name = c("Joint", "Focused", "Separate"),
  Formula = c(
    "Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx",
    "Age + sex + Rx + crp + tlr + tmb_braf + [biomarker]:Rx",
    "Age + sex + Rx + [biomarker]:Rx"
  ),
  Description = c(
    "All biomarkers and all treatment interactions in one unified model",
    "All biomarkers as main effects, with only one interaction per biomarker-specific model",
    "Only one biomarker and its treatment interaction per model (simplest specification)"
  )
)

knitr::kable(model_structure_df,
             col.names = c("Model", "Name", "Formula Pattern", "Description"),
             booktabs = TRUE,
             align = c("l", "l", "l", "l")) %>%
  kableExtra::column_spec(1, width = "1.5cm") %>%
  kableExtra::column_spec(2, width = "1.5cm") %>%
  kableExtra::column_spec(3, width = "5cm") %>%
  kableExtra::column_spec(4, width = "6cm") %>%
  kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position"))
```

**Rationale**: Model A (Joint) is the most comprehensive specification but may suffer from overfitting with limited sample size. Model C (Separate) is the simplest but ignores potential confounding from other biomarkers. Model B (Focused) represents a middle ground. Comparing results across all three structures provides insight into the structural uncertainty of our findings.

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Strategies Evaluated

**Table 2: Treatment Strategies Evaluated in the Cost-Effectiveness Analysis**

```{r strategies-table}
if (exists("strategies_df") && nrow(strategies_df) > 0) {
  strategies_display <- strategies_df %>%
    mutate(
      name = case_when(
        id == "control" ~ "Standard of Care",
        id == "crp" ~ "CRP-guided Strategy",
        id == "tlr" ~ "TLR-guided Strategy",
        id == "tmb_braf" ~ "TMB/BRAF-guided Strategy",
        TRUE ~ name
      ),
      prevalence = scales::percent(prevalence, accuracy = 0.1),
      n_patients = as.character(n_patients)
    ) %>%
    select(
      Strategy = name,
      Description = description,
      `Biomarker Prevalence` = prevalence,
      `Patients (n)` = n_patients
    )

  knitr::kable(strategies_display,
               booktabs = TRUE,
               align = c("l", "l", "c", "c")) %>%
    kableExtra::column_spec(1, width = "2.5cm") %>%
    kableExtra::column_spec(2, width = "8cm") %>%
    kableExtra::column_spec(c(3,4), width = "1.5cm") %>%
    kableExtra::kable_styling(font_size = 9, latex_options = c("scale_down", "HOLD_position"))

} else {
  cat("**Strategy information not available. Check biomarker strategies script.**\n")
}
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# Base Case Analysis

```{r run-all-basecase, include=FALSE}
# Run base case analysis for all three model structures
# This re-sources scripts 06 and 07 for each MODEL_STRUCTURE value

cat("Running base case analyses for all model structures...\n")

all_model_results <- run_all_basecase_analyses(verbose = TRUE)

cat("\nAll base case analyses complete.\n")
```

## Summary Comparison

**Table 3: Base Case Cost-Effectiveness Results Across Model Structures**

```{r basecase-comparison-table}
# Create and format comparison table
comparison_df <- format_multimodel_comparison_table(all_model_results)
display_df <- format_comparison_for_display(comparison_df)

# Rename columns for display
names(display_df) <- c("Strategy",
                       "Cost (A)", "QALY (A)", "ICER (A)",
                       "Cost (B)", "QALY (B)", "ICER (B)",
                       "Cost (C)", "QALY (C)", "ICER (C)")

knitr::kable(display_df,
             booktabs = TRUE,
             align = c("l", rep("r", 9))) %>%
  kableExtra::add_header_above(c(" " = 1,
                                  "Model A: Joint" = 3,
                                  "Model B: Focused" = 3,
                                  "Model C: Separate" = 3)) %>%
  kableExtra::kable_styling(font_size = 8,
                            latex_options = c("scale_down", "HOLD_position")) %>%
  kableExtra::footnote(general = "ICER = Incremental Cost-Effectiveness Ratio (EUR/QALY). Reference = lowest-cost strategy.",
                       footnote_as_chunk = TRUE)
```

## Optimal Strategy by Model Structure

**Table 4: Optimal Strategy at WTP Threshold of EUR `r format(WTP, big.mark=",")`/QALY**

```{r optimal-strategy-table}
optimal_df <- create_optimal_strategy_table(all_model_results, wtp = WTP)

optimal_df$NMB <- scales::dollar(optimal_df$NMB, accuracy = 1)

knitr::kable(optimal_df,
             col.names = c("Model Structure", "Optimal Strategy", "Net Monetary Benefit"),
             booktabs = TRUE,
             align = c("l", "l", "r")) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

## Model A: Joint Model

```{r model-a-results}
result_A <- all_model_results$Model_A

# Display ICER table
icer_table_A <- as.data.frame(result_A$icer_obj)
icer_table_A$Cost <- scales::dollar(icer_table_A$Cost, accuracy = 1)
icer_table_A$Effect <- sprintf("%.3f", icer_table_A$Effect)
icer_table_A$ICER[!is.na(icer_table_A$ICER)] <-
  scales::dollar(icer_table_A$ICER[!is.na(icer_table_A$ICER)], accuracy = 1)

knitr::kable(icer_table_A,
             caption = "Model A (Joint): Cost-Effectiveness Results",
             align = c("l", "r", "r", "r", "l"),
             booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r ce-plane-A, fig.cap="Cost-Effectiveness Plane - Model A (Joint)"}
ce_plot_A <- plot(result_A$icer_obj,
                  txtsize = 10,
                  currency = "EUR",
                  effect_units = "QALYs",
                  label = "all")
print(ce_plot_A)
```

```{r pagebreak-5, results='asis'}
cat("\\newpage\n")
```

## Model B: Focused Model

```{r model-b-results}
result_B <- all_model_results$Model_B

icer_table_B <- as.data.frame(result_B$icer_obj)
icer_table_B$Cost <- scales::dollar(icer_table_B$Cost, accuracy = 1)
icer_table_B$Effect <- sprintf("%.3f", icer_table_B$Effect)
icer_table_B$ICER[!is.na(icer_table_B$ICER)] <-
  scales::dollar(icer_table_B$ICER[!is.na(icer_table_B$ICER)], accuracy = 1)

knitr::kable(icer_table_B,
             caption = "Model B (Focused): Cost-Effectiveness Results",
             align = c("l", "r", "r", "r", "l"),
             booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r ce-plane-B, fig.cap="Cost-Effectiveness Plane - Model B (Focused)"}
ce_plot_B <- plot(result_B$icer_obj,
                  txtsize = 10,
                  currency = "EUR",
                  effect_units = "QALYs",
                  label = "all")
print(ce_plot_B)
```

```{r pagebreak-6, results='asis'}
cat("\\newpage\n")
```

## Model C: Separate Model

```{r model-c-results}
result_C <- all_model_results$Model_C

icer_table_C <- as.data.frame(result_C$icer_obj)
icer_table_C$Cost <- scales::dollar(icer_table_C$Cost, accuracy = 1)
icer_table_C$Effect <- sprintf("%.3f", icer_table_C$Effect)
icer_table_C$ICER[!is.na(icer_table_C$ICER)] <-
  scales::dollar(icer_table_C$ICER[!is.na(icer_table_C$ICER)], accuracy = 1)

knitr::kable(icer_table_C,
             caption = "Model C (Separate): Cost-Effectiveness Results",
             align = c("l", "r", "r", "r", "l"),
             booktabs = TRUE) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r ce-plane-C, fig.cap="Cost-Effectiveness Plane - Model C (Separate)"}
ce_plot_C <- plot(result_C$icer_obj,
                  txtsize = 10,
                  currency = "EUR",
                  effect_units = "QALYs",
                  label = "all")
print(ce_plot_C)
```

```{r pagebreak-7, results='asis'}
cat("\\newpage\n")
```

# Probabilistic Sensitivity Analysis

```{r load-psa-caches, include=FALSE}
# Load PSA caches for all model structures
all_psa_results <- load_all_psa_caches(n_samples = n_samples,
                                        use_both_models = USE_BOTH_MODELS)

psa_available <- length(all_psa_results) > 0

if (psa_available) {
  cat("Loaded PSA results for", length(all_psa_results), "model structures.\n")
} else {
  cat("No PSA caches found. Please run 12_PSA.R with RUN_ALL_MODELS = TRUE.\n")
}
```

```{r psa-check, results='asis'}
if (!psa_available) {
  cat("**PSA results not available.** Please generate PSA caches by running:\n\n")
  cat("```r\n")
  cat("RUN_ALL_MODELS <- TRUE\n")
  cat("source('scripts/R/analysis/08_sampling.R')\n")
  cat("source('scripts/R/analysis/12_PSA.R')\n")
  cat("```\n")
}
```

```{r psa-summary-table, eval=psa_available}
# Create PSA summary table
psa_summary <- create_psa_summary_table(all_psa_results, wtp = WTP)

# Format for display
psa_summary$Mean_Cost <- scales::dollar(psa_summary$Mean_Cost, accuracy = 1)
psa_summary$Mean_QALY <- sprintf("%.3f", psa_summary$Mean_QALY)
psa_summary$Prob_CE <- scales::percent(psa_summary$Prob_CE, accuracy = 0.1)

knitr::kable(psa_summary,
             caption = paste0("PSA Summary: Mean Outcomes and Probability of Cost-Effectiveness at WTP = EUR ",
                             format(WTP, big.mark = ",")),
             col.names = c("Model", "Strategy", "Mean Cost", "Mean QALY", "P(CE)"),
             booktabs = TRUE,
             align = c("l", "l", "r", "r", "r")) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r psa-scatterplots, eval=psa_available, fig.height=10, fig.width=10, fig.cap="PSA Scatterplots by Model Structure"}
# Create faceted PSA scatterplot
psa_scatter_data <- data.frame()

model_configs <- get_model_configs()

for (model_name in names(all_psa_results)) {
  psa_obj <- all_psa_results[[model_name]]
  config <- model_configs[[model_name]]

  if (is.null(psa_obj)) next

  # Extract cost and effect matrices
  cost_df <- as.data.frame(psa_obj$cost)
  effect_df <- as.data.frame(psa_obj$effect)

  for (strategy in psa_obj$strategies) {
    scatter_df <- data.frame(
      Cost = cost_df[[strategy]],
      Effect = effect_df[[strategy]],
      Strategy = strategy,
      Model = config$label,
      stringsAsFactors = FALSE
    )
    psa_scatter_data <- rbind(psa_scatter_data, scatter_df)
  }
}

if (nrow(psa_scatter_data) > 0) {
  p_scatter <- ggplot(psa_scatter_data, aes(x = Effect, y = Cost, color = Strategy)) +
    geom_point(alpha = 0.3, size = 0.5) +
    facet_wrap(~Model, ncol = 2) +
    scale_y_continuous(labels = scales::dollar_format()) +
    scale_color_viridis_d(name = "Strategy") +
    labs(
      x = "Effectiveness (QALYs)",
      y = "Total Cost (EUR)"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      strip.text = element_text(size = 11, face = "bold")
    ) +
    guides(color = guide_legend(override.aes = list(alpha = 1, size = 3)))

  print(p_scatter)
}
```

```{r pagebreak-8, results='asis', eval=psa_available}
cat("\\newpage\n")
```

```{r ceac-comparison, eval=psa_available, fig.height=8, fig.width=10, fig.cap="Cost-Effectiveness Acceptability Curves by Model Structure"}
# Create CEAC comparison plot
ceac_plot <- create_multimodel_ceac_plot(
  all_psa_results,
  wtp_range = seq(0, 100000, by = 2000)
)

print(ceac_plot)
```

```{r pagebreak-9, results='asis'}
cat("\\newpage\n")
```

# Other Reports

This report focuses on comparing cost-effectiveness results across model structures. Additional analyses are available in companion reports:

- **One-Way Sensitivity Analysis (OWSA)**: Deterministic sensitivity analysis with tornado diagrams showing the impact of individual parameters on model outcomes. See `OWSA.qmd`.

- **Scenario Analysis**: Alternative scenarios including reduced nivolumab prices and higher willingness-to-pay thresholds. See `scenario_effect.qmd`.

- **Value of Information Analysis**: Expected Value of Perfect Partial Information (EVPPI) analysis identifying parameters with highest value for additional research. See `EVPPIs.qmd`.

- **Clinical Effectiveness**: Detailed clinical effectiveness results including survival analysis and treatment effect heterogeneity. See `clinical_effectiveness.qmd`.

- **Input Parameters**: Comprehensive documentation of all model input parameters. See `input_parameters.qmd`.

# Summary

This analysis compared cost-effectiveness results across three model structures to assess structural uncertainty:

1. **Model Structure Comparison**: Results were [generally consistent / showed variation] across Model A (Joint), Model B (Focused), and Model C (Separate) specifications.

2. **Base Case Results**: The optimal strategy at the WTP threshold of EUR `r format(WTP, big.mark=",")` per QALY was [strategy] across [all / most] model structures.

3. **Probabilistic Sensitivity Analysis**: PSA results confirmed the robustness of base case findings, with [consistent / varying] probability of cost-effectiveness across model structures.

4. **Implications**: The [consistency / variation] in results across model structures suggests that our conclusions are [robust to / sensitive to] the specification of biomarker-treatment interactions.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.0
