---
title: "METIMMOX-1 Cost-Effectiveness Analysis Report"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: true
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r cea-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions if they exist (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/create_tornado_plot.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r setup-global-variables, include=FALSE}
# 02 - Setup and Global Variables
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}
```

```{r biomarker-strategies, include=FALSE}
# 03 - Biomarker Strategies
if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}
```

```{r qalys-data-processing, include=FALSE}
# 05 - Process QALYs data with proper error handling
tryCatch({
  # Check for METIMMOX data file and load if exists
  metimmox_file <- here("data/tidy/METIMMOX.rds")
  if (file.exists(metimmox_file)) {
    METIMMOX <- readRDS(metimmox_file)
  }
}, error = function(e) {
  # File doesn't exist or can't be read - continue without it
})

tryCatch({
  # Check for QALY data file and load if exists
  qaly_file <- here("data/sensitive/231208 METIMMOX EQ_5D_5L.xlsx")
  if (file.exists(qaly_file)) {
    QALYsraw <- read_excel(qaly_file, sheet = 2, skip = 1) %>%
      rename(ID = SubjectId)
  }
}, error = function(e) {
  # File doesn't exist or can't be read - continue without it
})
```

```{r survival-analysis, include=FALSE}
# 06 - Parametric Survival Analysis
# First ensure all required variables exist before running survival analysis

# Check if biomarker variables exist, if not, recreate them
if (!all(c("crp", "tlr", "tmb_braf") %in% names(data))) {
  # Recreate biomarker variables (from script 03 logic)
  if (all(c("CRP1cat", "TLRcat", "TMBcat") %in% names(data))) {
    data$crp <- as.numeric(data$CRP1cat == 1)
    data$tlr <- as.numeric(data$TLRcat == 1)
    
    # Handle TMB/BRAF combination (check if Mutation column exists)
    if ("Mutation" %in% names(data)) {
      data$tmb_braf <- as.numeric((data$TMBcat == 1) | (data$Mutation == "BRAF"))
    } else {
      data$tmb_braf <- as.numeric(data$TMBcat == 1)
    }
    
    message("Biomarker variables recreated successfully")
  } else {
    message("Warning: Original biomarker variables not found. Survival analysis may fail.")
  }
}

# Now run the survival analysis script
if (file.exists(here("scripts/R/analysis/06_parametric_survival analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival analysis.R"))))
} else {
  message("Survival analysis script not found")
}
```

```{r input-parameters, include=FALSE}
# 07 - Base Case Input Parameters
if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
}
```

```{r sampling-setup, include=FALSE}
# 08 - Sampling Setup with path safety
if (file.exists(here("scripts/R/analysis/08_sampling.R"))) {
  # Check if required function file exists before sourcing
  bootstrap_func_path <- here("scripts/R/functions/bootstrap_survival_model.R")
  if (file.exists(bootstrap_func_path)) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/08_sampling.R"))))
  } else {
    message("Bootstrap function file not found at: ", bootstrap_func_path)
    message("Skipping sampling setup - this will affect PSA analysis")
  }
} else {
  message("Sampling script not found")
}
```

# Overview

This cost-effectiveness analysis evaluates three biomarker-guided strategies (CRP, TLR, and TMB/BRAF) for selecting metastatic microsatellite stable (MSS)/proficient mismatch repair (pMMR) colorectal cancer patients for immunotherapy versus the standard of care strategy of chemotherapy alone.

This report contains:

- **Strategy Descriptions**: Overview of the four treatment strategies evaluated
- **Base Case Analysis**: Cost-effectiveness results with incremental cost-effectiveness ratios (ICERs) and cost-effectiveness plane
- **Deterministic Sensitivity Analysis**: Tornado diagrams showing parameter impact on each strategy
- **Probabilistic Sensitivity Analysis**: Monte Carlo simulation results including scatterplot and cost-effectiveness acceptability curves

# Strategies Evaluated

```{r strategies-table}
#| tbl-cap: "Treatment Strategies Evaluated in the Cost-Effectiveness Analysis"

if (exists("strategies_df") && nrow(strategies_df) > 0) {
  # Format the strategies dataframe for display
  strategies_display <- strategies_df %>%
    mutate(
      name = case_when(
        id == "control" ~ "Standard of Care",
        id == "crp" ~ "CRP-guided Strategy", 
        id == "tlr" ~ "TLR-guided Strategy",
        id == "tmb_braf" ~ "TMB/BRAF-guided Strategy",
        TRUE ~ name
      ),
      prevalence = scales::percent(prevalence, accuracy = 0.1),
      n_patients = as.character(n_patients)
    ) %>%
    select(
      Strategy = name,
      Description = description,
      `Biomarker Prevalence` = prevalence,
      `Patients (n)` = n_patients
    )
  
  knitr::kable(strategies_display,
               booktabs = TRUE,
               align = c("l", "l", "c", "c")) %>%
    kableExtra::column_spec(1, width = "2.5cm") %>%
    kableExtra::column_spec(2, width = "8cm") %>%
    kableExtra::column_spec(c(3,4), width = "1.5cm") %>%
    kableExtra::kable_styling(font_size = 9, latex_options = c("scale_down", "HOLD_position"))
  
} else {
  cat("**Strategy information not available. Check biomarker strategies script.**\n")
}
```

```{r base-case-pagebreak, results='asis'}
cat("\\newpage\n")
```

# Base Case Analysis

```{r base-case-analysis, include=FALSE}
# 10 - Base Case Analysis
if (file.exists(here("scripts/R/analysis/10_basecase_analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/10_basecase_analysis.R"))))
}
```

```{r base-case-results-table}
#| tbl-cap: "Base Case Cost-Effectiveness Results with ICERs"

if (exists("icer_obj") && "icers" %in% class(icer_obj)) {
  # Use the properly calculated ICER object from dampack
  icer_table <- as.data.frame(icer_obj)
  
  # Format for display
  icer_table$Cost <- scales::dollar(icer_table$Cost, accuracy = 1)
  icer_table$Effect <- sprintf("%.3f", icer_table$Effect)
  icer_table$ICER[!is.na(icer_table$ICER)] <- 
    scales::dollar(icer_table$ICER[!is.na(icer_table$ICER)], accuracy = 1)
  
  knitr::kable(icer_table, 
               align = c("l", "r", "r", "r", "l"),
               booktabs = TRUE)
} else if (exists("base_results")) {
  # Fallback to base results if ICER object doesn't exist
  formatted_df <- base_results %>%
    mutate(
      Cost = scales::dollar(Cost, accuracy = 1),
      Effect = sprintf("%.3f", Effect)
    )
  
  knitr::kable(formatted_df, 
               col.names = c("Strategy", "Total Cost (€)", "QALYs"),
               align = c("l", "r", "r"),
               booktabs = TRUE)
  cat("\n*Note: ICERs not calculated - check base case analysis completion*\n")
} else {
  cat("**Base case results pending - check analysis completion**\n")
}
```

```{r cost-effectiveness-plane}
#| fig-cap: "Cost-Effectiveness Plane with Efficiency Frontier"

if (exists("ce_plot") && "ggplot" %in% class(ce_plot)) {
  # Display the pre-generated CE plot from base case analysis
  print(ce_plot)
} else if (exists("icer_obj") && "icers" %in% class(icer_obj)) {
  # Generate the plot if it doesn't exist
  ce_plot <- plot(icer_obj, 
                  txtsize = 12,
                  currency = "€",
                  effect_units = "QALYs",
                  label = "all")
  print(ce_plot)
} else if (exists("base_results") && is.data.frame(base_results)) {
  # Create basic scatter plot if dampack objects don't exist
  if (all(c("Effect", "Cost", "Strategy") %in% names(base_results))) {
    p <- ggplot(base_results, aes(x = Effect, y = Cost, color = Strategy, shape = Strategy)) +
      geom_point(size = 4) +
      scale_y_continuous(labels = scales::dollar_format()) +
      scale_color_viridis_d(name = "Strategy") +
      labs(
        title = "Cost-Effectiveness Plane",
        subtitle = "Base Case Analysis",
        x = "Effectiveness (QALYs)",
        y = "Total Cost (€)"
      ) +
      theme_minimal() +
      theme(legend.position = "bottom")
    
    print(p)
  }
} else {
  ggplot() + 
    annotate("text", x = 0.5, y = 0.5, 
             label = "Cost-effectiveness plane will appear\nonce ICER calculation completes", 
             size = 5, hjust = 0.5) +
    xlim(0, 1) + ylim(0, 1) +
    theme_void() +
    labs(title = "Cost-Effectiveness Plane", subtitle = "Analysis in Progress")
}
```

# Deterministic Sensitivity Analysis

```{r deterministic-sa, include=FALSE}
# 11 - Deterministic Sensitivity Analysis
if (file.exists(here("scripts/R/analysis/11_DSA.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/11_DSA.R"))))
}
```

```{r tornado-control}
#| fig-cap: "Tornado Diagram - Standard of Care One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  library(ggplot2)
  
  # Function to create tornado data for a specific strategy
  create_tornado_data <- function(strategy_name, dsa_results) {
    strat_results <- dsa_results[dsa_results$Strategy == strategy_name & 
                                 dsa_results$Parameter != "base_case", ]
    
    tornado_data <- data.frame()
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "max", ]
      
      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        tornado_data <- rbind(tornado_data, data.frame(
          Parameter = param,
          Min_diff = min_row$NMB_diff,
          Max_diff = max_row$NMB_diff,
          Range = abs(max_row$NMB_diff - min_row$NMB_diff)
        ))
      }
    }
    
    if (nrow(tornado_data) > 0) {
      tornado_data <- tornado_data[order(tornado_data$Range), ]
      tornado_data$Parameter <- factor(tornado_data$Parameter, levels = tornado_data$Parameter)
      return(tornado_data)
    }
    return(NULL)
  }
  
  # Create tornado plot for control strategy
  tornado_data <- create_tornado_data("control", dsa_results)
  
  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff), 
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff), 
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (€)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 11),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )
    
    print(p)
  }
}
```

```{r tornado-crp}
#| fig-cap: "Tornado Diagram - CRP-guided Strategy One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  library(ggplot2)
  
  # Function to create tornado data for a specific strategy
  create_tornado_data <- function(strategy_name, dsa_results) {
    strat_results <- dsa_results[dsa_results$Strategy == strategy_name & 
                                 dsa_results$Parameter != "base_case", ]
    
    tornado_data <- data.frame()
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "max", ]
      
      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        tornado_data <- rbind(tornado_data, data.frame(
          Parameter = param,
          Min_diff = min_row$NMB_diff,
          Max_diff = max_row$NMB_diff,
          Range = abs(max_row$NMB_diff - min_row$NMB_diff)
        ))
      }
    }
    
    if (nrow(tornado_data) > 0) {
      tornado_data <- tornado_data[order(tornado_data$Range), ]
      tornado_data$Parameter <- factor(tornado_data$Parameter, levels = tornado_data$Parameter)
      return(tornado_data)
    }
    return(NULL)
  }
  
  # Create tornado plot for CRP strategy
  tornado_data <- create_tornado_data("crp", dsa_results)
  
  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff), 
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff), 
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (€)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 11),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )
    
    print(p)
  }
}
```

```{r tornado-tlr}
#| fig-cap: "Tornado Diagram - TLR-guided Strategy One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  library(ggplot2)
  
  # Function to create tornado data for a specific strategy
  create_tornado_data <- function(strategy_name, dsa_results) {
    strat_results <- dsa_results[dsa_results$Strategy == strategy_name & 
                                 dsa_results$Parameter != "base_case", ]
    
    tornado_data <- data.frame()
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "max", ]
      
      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        tornado_data <- rbind(tornado_data, data.frame(
          Parameter = param,
          Min_diff = min_row$NMB_diff,
          Max_diff = max_row$NMB_diff,
          Range = abs(max_row$NMB_diff - min_row$NMB_diff)
        ))
      }
    }
    
    if (nrow(tornado_data) > 0) {
      tornado_data <- tornado_data[order(tornado_data$Range), ]
      tornado_data$Parameter <- factor(tornado_data$Parameter, levels = tornado_data$Parameter)
      return(tornado_data)
    }
    return(NULL)
  }
  
  # Create tornado plot for TLR strategy
  tornado_data <- create_tornado_data("tlr", dsa_results)
  
  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff), 
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff), 
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (€)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 11),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )
    
    print(p)
  }
}
```

```{r tornado-tmb-braf}
#| fig-cap: "Tornado Diagram - TMB/BRAF-guided Strategy One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  library(ggplot2)
  
  # Function to create tornado data for a specific strategy
  create_tornado_data <- function(strategy_name, dsa_results) {
    strat_results <- dsa_results[dsa_results$Strategy == strategy_name & 
                                 dsa_results$Parameter != "base_case", ]
    
    tornado_data <- data.frame()
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "max", ]
      
      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        tornado_data <- rbind(tornado_data, data.frame(
          Parameter = param,
          Min_diff = min_row$NMB_diff,
          Max_diff = max_row$NMB_diff,
          Range = abs(max_row$NMB_diff - min_row$NMB_diff)
        ))
      }
    }
    
    if (nrow(tornado_data) > 0) {
      tornado_data <- tornado_data[order(tornado_data$Range), ]
      tornado_data$Parameter <- factor(tornado_data$Parameter, levels = tornado_data$Parameter)
      return(tornado_data)
    }
    return(NULL)
  }
  
  # Create tornado plot for TMB/BRAF strategy
  tornado_data <- create_tornado_data("tmb_braf", dsa_results)
  
  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff), 
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff), 
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black", size = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (€)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 11),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )
    
    print(p)
  }
}
```

```{r impact-table-pagebreak, results='asis'}
cat("\\newpage\n")
```

```{r parameter-impact-summary}
#| tbl-cap: "Parameter Impact Summary - Most Influential Parameters by Strategy"

if (exists("impact_summary") && nrow(impact_summary) > 0) {
  # Improve the formatting of the impact summary table
  impact_formatted <- impact_summary %>%
    mutate(
      Strategy = case_when(
        Strategy == "control" ~ "Standard Care",
        Strategy == "crp" ~ "CRP-guided",
        Strategy == "tlr" ~ "TLR-guided", 
        Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
        TRUE ~ Strategy
      ),
      Parameter = case_when(
        Parameter == "u_np" ~ "Utility (No Progression)",
        Parameter == "u_p" ~ "Utility (Progression)",
        Parameter == "c_drug_nivo" ~ "Nivolumab Cost",
        Parameter == "c_drug_FLOX" ~ "FLOX Cost",
        Parameter == "c_test_NGS" ~ "NGS Testing Cost",
        Parameter == "c_test_CT" ~ "CT Scan Cost",
        Parameter == "c_test_blood" ~ "Blood Test Cost",
        Parameter == "c_other_last" ~ "End-of-Life Care Cost",
        Parameter == "c_other_visit" ~ "Visit Cost",
        Parameter == "c_other_baseline" ~ "Baseline Care Cost",
        Parameter == "c_other_follow" ~ "Follow-up Care Cost",
        TRUE ~ Parameter
      ),
      `Impact (€)` = scales::dollar(Impact, accuracy = 1)
    ) %>%
    # Remove the Strategy column for display
    select(Rank, Parameter, `Impact (€)`)
  
  # Create table without strategy column - use only pack_rows for grouping
  knitr::kable(impact_formatted,
               align = c("c", "l", "r"),
               booktabs = TRUE,
               col.names = c("Rank", "Parameter", "Impact on NMB (€)")) %>%
    kableExtra::column_spec(1, width = "1.5cm") %>%
    kableExtra::column_spec(2, width = "5cm") %>%
    kableExtra::column_spec(3, width = "2.5cm") %>%
    kableExtra::pack_rows("Standard Care", 1, 3, bold = TRUE, color = "white", background = "#4472C4") %>%
    kableExtra::pack_rows("CRP-guided", 4, 6, bold = TRUE, color = "white", background = "#70AD47") %>%
    kableExtra::pack_rows("TLR-guided", 7, 9, bold = TRUE, color = "white", background = "#FFC000") %>%
    kableExtra::pack_rows("TMB/BRAF-guided", 10, 12, bold = TRUE, color = "white", background = "#C55A11") %>%
    kableExtra::kable_styling(font_size = 10, latex_options = c("HOLD_position"))
  
} else if (exists("dsa_results") && nrow(dsa_results) > 0) {
  # Generate impact summary if it doesn't exist but DSA results do
  cat("**Generating parameter impact summary from DSA results...**\n\n")
  
  impact_summary_new <- data.frame()
  
  for (strat in unique(dsa_results$Strategy)) {
    if (strat == "base_case") next
    
    strat_results <- dsa_results[dsa_results$Strategy == strat & 
                                 dsa_results$Parameter != "base_case", ]
    
    param_impact <- data.frame()
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param & 
                               strat_results$Value == "max", ]
      
      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        range <- abs(max_row$NMB_diff - min_row$NMB_diff)
        param_impact <- rbind(param_impact, data.frame(
          Parameter = param,
          Range = range
        ))
      }
    }
    
    if (nrow(param_impact) > 0) {
      param_impact <- param_impact[order(-param_impact$Range), ]
      top_n <- min(3, nrow(param_impact))
      
      for (i in 1:top_n) {
        impact_summary_new <- rbind(impact_summary_new, data.frame(
          Strategy = strat,
          Rank = i,
          Parameter = param_impact$Parameter[i],
          Impact = param_impact$Range[i]
        ))
      }
    }
  }
  
  if (nrow(impact_summary_new) > 0) {
    # Apply the same formatting as above
    impact_formatted <- impact_summary_new %>%
      mutate(
        Strategy = case_when(
          Strategy == "control" ~ "Standard Care",
          Strategy == "crp" ~ "CRP-guided",
          Strategy == "tlr" ~ "TLR-guided", 
          Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
          TRUE ~ Strategy
        ),
        Parameter = case_when(
          Parameter == "u_np" ~ "Utility (No Progression)",
          Parameter == "u_p" ~ "Utility (Progression)", 
          Parameter == "c_drug_nivo" ~ "Nivolumab Cost",
          Parameter == "c_drug_FLOX" ~ "FLOX Cost",
          Parameter == "c_test_NGS" ~ "NGS Testing Cost",
          Parameter == "c_test_CT" ~ "CT Scan Cost",
          Parameter == "c_test_blood" ~ "Blood Test Cost",
          Parameter == "c_other_last" ~ "End-of-Life Care Cost",
          Parameter == "c_other_visit" ~ "Visit Cost",
          Parameter == "c_other_baseline" ~ "Baseline Care Cost",
          Parameter == "c_other_follow" ~ "Follow-up Care Cost",
          TRUE ~ Parameter
        ),
        `Impact (€)` = scales::dollar(Impact, accuracy = 1)
      ) %>%
      # Remove Strategy column
      select(Rank, Parameter, `Impact (€)`)
    
    # Create table with pack_rows grouping only
    knitr::kable(impact_formatted,
                 align = c("c", "l", "r"),
                 booktabs = TRUE,
                 col.names = c("Rank", "Parameter", "Impact on NMB (€)")) %>%
      kableExtra::column_spec(1, width = "1.5cm") %>%
      kableExtra::column_spec(2, width = "5cm") %>%
      kableExtra::column_spec(3, width = "2.5cm") %>%
      kableExtra::pack_rows("Standard Care", 1, 3, bold = TRUE, color = "white", background = "#4472C4") %>%
      kableExtra::pack_rows("CRP-guided", 4, 6, bold = TRUE, color = "white", background = "#70AD47") %>%
      kableExtra::pack_rows("TLR-guided", 7, 9, bold = TRUE, color = "white", background = "#FFC000") %>%
      kableExtra::pack_rows("TMB/BRAF-guided", 10, 12, bold = TRUE, color = "white", background = "#C55A11") %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("HOLD_position"))
  }
  
} else {
  cat("**Parameter impact summary requires completed DSA analysis.**\n")
}
```

```{r psa-pagebreak, results='asis'}
cat("\\newpage\n")
```

# Probabilistic Sensitivity Analysis

```{r probabilistic-sa, include=FALSE}
# 12 - Probabilistic Sensitivity Analysis
if (file.exists(here("scripts/R/analysis/12_PSA.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/12_PSA.R"))))
}
```

```{r psa-scatterplot}
#| fig-cap: "Cost-effectiveness Scatterplot"

if (exists("psa_obj") && "psa" %in% class(psa_obj)) {
  # Use dampack's built-in plot function for PSA
  psa_plot <- plot(psa_obj, 
                   frontier = TRUE, 
                   points = TRUE,
                   alpha = 0.3,
                   txtsize = 12) +
    labs(x = "Effectiveness (QALYs)",
         y = "Total Cost (€)") +
    theme_minimal()
  
  print(psa_plot)
  
} else if (exists("psa_results") && "cost" %in% names(psa_results) && "effect" %in% names(psa_results)) {
  # Alternative: use the raw PSA results
  cost_matrix <- psa_results$cost
  effect_matrix <- psa_results$effect
  
  psa_data <- data.frame(
    Cost = as.vector(cost_matrix),
    Effect = as.vector(effect_matrix),
    Strategy = rep(colnames(cost_matrix), each = nrow(cost_matrix))
  ) %>%
    filter(!is.na(Cost) & !is.na(Effect))
  
  if (nrow(psa_data) > 0) {
    p <- ggplot(psa_data, aes(x = Effect, y = Cost, color = Strategy)) +
      geom_point(alpha = 0.3, size = 0.8) +
      scale_y_continuous(labels = scales::dollar_format()) +
      scale_color_viridis_d(name = "Strategy") +
      labs(
        x = "Effectiveness (QALYs)",
        y = "Total Cost (€)"
      ) +
      theme_minimal() +
      theme(legend.position = "bottom")
    
    print(p)
  }
  
} else {
  cat("**PSA data not found. Check if PSA script completed successfully.**\n")
  cat("Available objects:", paste(ls()[grepl("psa", ls(), ignore.case = TRUE)], collapse = ", "), "\n")
}
```

```{r ceac-curve}
#| fig-cap: "Cost-Effectiveness Acceptability Curve"

if (exists("ceac_obj") && "ceac" %in% class(ceac_obj)) {
  # Use the CEAC object created in the PSA script
  ceac_plot <- plot(ceac_obj, 
                    frontier = TRUE, 
                    points = TRUE, 
                    currency = "€",
                    txtsize = 12)
  
  print(ceac_plot)
  
} else if (exists("psa_obj") && "psa" %in% class(psa_obj)) {
  # Generate CEAC from PSA object
  wtp_range <- seq(0, 100000, by = 2000)
  
  tryCatch({
    ceac_obj <- dampack::ceac(wtp = wtp_range, psa = psa_obj)
    ceac_plot <- plot(ceac_obj, 
                      frontier = TRUE, 
                      currency = "€",
                      txtsize = 12)
    
    print(ceac_plot)
  }, error = function(e) {
    cat("**CEAC generation failed:**", e$message, "\n")
  })
  
} else {
  cat("**CEAC requires PSA object or completed PSA analysis.**\n")
  cat("Available PSA objects:", paste(ls()[grepl("psa|ceac", ls(), ignore.case = TRUE)], collapse = ", "), "\n")
}
```

# Other Reports

I am working on the following other reports:

- **Input Parameters Report**: Comprehensive documentation of all model input parameters including clinical effectiveness data, cost parameters, and utility values with their respective sources and uncertainty distributions.

- **Parametric Survival Analysis Report**: Detailed documentation of the parametric survival modeling process, including goodness-of-fit statistics for all tested distributions, model selection criteria, and validation of the chosen survival models for both overall survival and progression-free survival endpoints.

- **One-Way Sensitivity Analysis (OWSA) Report**: Extended sensitivity analysis providing detailed examination of each individual parameter's impact on model outcomes, including threshold analyses and parameter sensitivity rankings across all strategies.

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.0