---
title: "METIMMOX-1 Clinical Effectiveness Analysis Report"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))



```

```{r load-analysis-scripts, include=FALSE}
# 02 - Setup and Global Variables
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

# 03 - Biomarker Strategies
if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}

# 06 - Parametric Survival Analysis
if (file.exists(here("scripts/R/analysis/06_parametric_survival analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival analysis.R"))))
}

# 07 - Base Case Input Parameters
if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
}

# Set discount rates to 0 for undiscounted analysis
d_c <- 0  # Discount rate for costs
d_e <- 0  # Discount rate for effects

# Update parameters with zero discount rates
if (exists("l_params_base")) {
  l_params_base$d_c <- 0
  l_params_base$d_e <- 0
}

# 10 - Base Case Analysis (will now use undiscounted parameters)
if (file.exists(here("scripts/R/analysis/10_basecase_analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/10_basecase_analysis.R"))))
}
```

# Overview

This report presents clinical effectiveness results for the METIMMOX-1 trial, comparing biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer. The analysis compares four strategies: (1) Control (FLOX alone), (2) CRP-guided, (3) TLR-guided, and (4) TMB/BRAF-guided. Median survival times are derived from age- and sex-adjusted parametric survival models weighted by biomarker prevalence. Hazard ratios are estimated using Cox proportional hazards models with biomarker×treatment interactions, adjusted for age and sex. Life years and QALYs are calculated from the decision-analytic model. All outcomes are **undiscounted** (discount rate = 0%).

# Results

## Cox Proportional Hazards Models

```{r cox-models, include=FALSE}
# Cox Proportional Hazards Functions for METIMMOX-1 Analysis

# Function to calculate median from survival probabilities
calculate_median_survival <- function(surv_probs, time_points) {
  # Find first time point where survival drops below 0.5
  median_idx <- which(surv_probs < 0.5)[1]
  if (is.na(median_idx)) {
    # If survival never drops below 0.5, return the last time point
    return(time_points[length(time_points)])
  } else {
    return(time_points[median_idx])
  }
}

# Convert weeks to months (divide by 4.345)
weeks_to_months <- function(weeks) {
  return(weeks / 4.345)
}

# Function to extract HR and CI for interaction terms
extract_hr_ci <- function(cox_summary, biomarker_name) {
  coef_table <- cox_summary$coefficients
  conf_int <- cox_summary$conf.int
  
  # Look for the interaction term with the biomarker
  # Pattern should match: biomarkerLevel:RxLevel or Rx:biomarkerLevel
  pattern1 <- paste0("^", biomarker_name, ".*:.*Rx")
  pattern2 <- paste0("^Rx.*:.*", biomarker_name)
  
  matching_rows1 <- grep(pattern1, rownames(coef_table), value = FALSE)
  matching_rows2 <- grep(pattern2, rownames(coef_table), value = FALSE)
  matching_rows <- c(matching_rows1, matching_rows2)
  
  if (length(matching_rows) > 0) {
    # Take the first matching interaction term
    idx <- matching_rows[1]
    hr <- conf_int[idx, "exp(coef)"]
    ci_lower <- conf_int[idx, "lower .95"]
    ci_upper <- conf_int[idx, "upper .95"]
    p_value <- coef_table[idx, "Pr(>|z|)"]
    
    return(list(hr = hr, ci_lower = ci_lower, ci_upper = ci_upper, p_value = p_value))
  } else {
    return(list(hr = NA, ci_lower = NA, ci_upper = NA, p_value = NA))
  }
}

# Function to extract HR with fallback logic
extract_hr_with_fallback <- function(cox_model, cox_summary, biomarker_name) {
  # First try the interaction term approach
  result <- extract_hr_ci(cox_summary, biomarker_name)
  
  # If no interaction found, try to find any term with the biomarker name
  if (is.na(result$hr)) {
    biomarker_terms <- grep(biomarker_name, names(coef(cox_model)), ignore.case = TRUE, value = TRUE)
    if (length(biomarker_terms) > 0) {
      cat("Found", biomarker_name, "terms:", biomarker_terms, "\n")
      # Use the last matching term (often the interaction)
      idx <- which(names(coef(cox_model)) == biomarker_terms[length(biomarker_terms)])
      if (length(idx) > 0) {
        result <- list(
          hr = exp(coef(cox_model)[idx]),
          ci_lower = exp(confint(cox_model)[idx, 1]),
          ci_upper = exp(confint(cox_model)[idx, 2]),
          p_value = cox_summary$coefficients[idx, "Pr(>|z|)"]
        )
      }
    }
  }
  
  return(result)
}

# Function to format HR with CI for display
format_hr_ci <- function(hr_object) {
  if (is.na(hr_object$hr)) {
    return("NA")
  } else {
    return(sprintf("%.2f (%.2f-%.2f)", hr_object$hr, hr_object$ci_lower, hr_object$ci_upper))
  }
}

# Prepare data for Cox regression
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr", "tmb_braf", "OSwk", "Death", "PFSwk", "Progression")]), ]

# Ensure factors
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)
data_complete$crp <- as.factor(data_complete$crp)
data_complete$tlr <- as.factor(data_complete$tlr)
data_complete$tmb_braf <- as.factor(data_complete$tmb_braf)

# Cox model for OS with all biomarker*treatment interactions
cox_os_model <- coxph(
  Surv(OSwk, Death) ~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx,
  data = data_complete
)

# Cox model for PFS with all biomarker*treatment interactions
cox_pfs_model <- coxph(
  Surv(PFSwk, Progression) ~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx,
  data = data_complete
)

# Extract hazard ratios for biomarker*treatment interactions
cox_os_summary <- summary(cox_os_model)
cox_pfs_summary <- summary(cox_pfs_model)

# Print coefficient names for debugging
cat("OS model coefficients:\n")
print(names(coef(cox_os_model)))
cat("\nPFS model coefficients:\n")
print(names(coef(cox_pfs_model)))

# Extract HRs for each biomarker strategy for both OS and PFS using the new functions
hr_crp_os <- extract_hr_with_fallback(cox_os_model, cox_os_summary, "crp")
hr_tlr_os <- extract_hr_with_fallback(cox_os_model, cox_os_summary, "tlr")
hr_tmb_braf_os <- extract_hr_with_fallback(cox_os_model, cox_os_summary, "tmb_braf")

hr_crp_pfs <- extract_hr_with_fallback(cox_pfs_model, cox_pfs_summary, "crp")
hr_tlr_pfs <- extract_hr_with_fallback(cox_pfs_model, cox_pfs_summary, "tlr")
hr_tmb_braf_pfs <- extract_hr_with_fallback(cox_pfs_model, cox_pfs_summary, "tmb_braf")
```

Cox proportional hazards regression models were fitted with age, sex, treatment, and all three biomarker×treatment interaction terms.

## Median Survival Times

```{r median-survival, include=FALSE}
# Extract median survival times from parametric models
if (exists("p_os") && exists("p_pfs")) {
  median_pfs_control <- calculate_median_survival(p_pfs$control_PFS, time_points)
  median_os_control <- calculate_median_survival(p_os$control_OS, time_points)
  
  # For biomarker strategies: weighted predictions
  median_pfs_crp <- calculate_median_survival(p_pfs$crp_weighted_PFS, time_points)
  median_os_crp <- calculate_median_survival(p_os$crp_weighted_OS, time_points)
  
  median_pfs_tlr <- calculate_median_survival(p_pfs$tlr_weighted_PFS, time_points)
  median_os_tlr <- calculate_median_survival(p_os$tlr_weighted_OS, time_points)
  
  median_pfs_tmb_braf <- calculate_median_survival(p_pfs$tmb_braf_weighted_PFS, time_points)
  median_os_tmb_braf <- calculate_median_survival(p_os$tmb_braf_weighted_OS, time_points)
  
  # Convert to months
  median_pfs_control_mo <- weeks_to_months(median_pfs_control)
  median_os_control_mo <- weeks_to_months(median_os_control)
  median_pfs_crp_mo <- weeks_to_months(median_pfs_crp)
  median_os_crp_mo <- weeks_to_months(median_os_crp)
  median_pfs_tlr_mo <- weeks_to_months(median_pfs_tlr)
  median_os_tlr_mo <- weeks_to_months(median_os_tlr)
  median_pfs_tmb_braf_mo <- weeks_to_months(median_pfs_tmb_braf)
  median_os_tmb_braf_mo <- weeks_to_months(median_os_tmb_braf)
} else {
  # Placeholder values if predictions not available
  median_pfs_control_mo <- NA
  median_os_control_mo <- NA
  median_pfs_crp_mo <- NA
  median_os_crp_mo <- NA
  median_pfs_tlr_mo <- NA
  median_os_tlr_mo <- NA
  median_pfs_tmb_braf_mo <- NA
  median_os_tmb_braf_mo <- NA
}
```

## Clinical Effectiveness Summary

```{r effectiveness-table, include=FALSE}
# Calculate life years from survival predictions (sum of OS probabilities / 52 weeks per year)
if (exists("p_os")) {
  ly_control <- sum(p_os$control_OS) / 52
  ly_crp <- sum(p_os$crp_weighted_OS) / 52
  ly_tlr <- sum(p_os$tlr_weighted_OS) / 52
  ly_tmb_braf <- sum(p_os$tmb_braf_weighted_OS) / 52
} else {
  ly_control <- NA
  ly_crp <- NA
  ly_tlr <- NA
  ly_tmb_braf <- NA
}

# Get QALYs from base_results if available
if (exists("base_results")) {
  # Match strategies to get QALYs
  qaly_control <- base_results$Effect[base_results$Strategy == "Control"]
  qaly_crp <- base_results$Effect[base_results$Strategy == "CRP-guided"]
  qaly_tlr <- base_results$Effect[base_results$Strategy == "TLR-guided"]
  qaly_tmb_braf <- base_results$Effect[base_results$Strategy == "TMB/BRAF-guided"]
  
  # Handle cases where strategy names might be slightly different
  if (length(qaly_control) == 0) qaly_control <- base_results$Effect[1]
  if (length(qaly_crp) == 0) qaly_crp <- base_results$Effect[2]
  if (length(qaly_tlr) == 0) qaly_tlr <- base_results$Effect[3]
  if (length(qaly_tmb_braf) == 0) qaly_tmb_braf <- base_results$Effect[4]
} else {
  # Placeholder if base_results not available
  qaly_control <- ly_control * 0.7  # Assuming average utility weight
  qaly_crp <- ly_crp * 0.7
  qaly_tlr <- ly_tlr * 0.7
  qaly_tmb_braf <- ly_tmb_braf * 0.7
}

# Calculate incremental outcomes vs control
incr_ly_crp <- ly_crp - ly_control
incr_ly_tlr <- ly_tlr - ly_control
incr_ly_tmb_braf <- ly_tmb_braf - ly_control

incr_qaly_crp <- qaly_crp - qaly_control
incr_qaly_tlr <- qaly_tlr - qaly_control
incr_qaly_tmb_braf <- qaly_tmb_braf - qaly_control

# Create data frame for table with both PFS and OS HRs
effectiveness_data <- data.frame(
  Strategy = c("Control (FLOX alone)", "CRP-guided", "TLR-guided", "TMB/BRAF-guided"),
  Median_PFS = c(median_pfs_control_mo, median_pfs_crp_mo, median_pfs_tlr_mo, median_pfs_tmb_braf_mo),
  Median_OS = c(median_os_control_mo, median_os_crp_mo, median_os_tlr_mo, median_os_tmb_braf_mo),
  HR_PFS = c("Reference", format_hr_ci(hr_crp_pfs), format_hr_ci(hr_tlr_pfs), format_hr_ci(hr_tmb_braf_pfs)),
  HR_OS = c("Reference", format_hr_ci(hr_crp_os), format_hr_ci(hr_tlr_os), format_hr_ci(hr_tmb_braf_os)),
  Mean_LY = c(ly_control, ly_crp, ly_tlr, ly_tmb_braf),
  Mean_QALY = c(qaly_control, qaly_crp, qaly_tlr, qaly_tmb_braf),
  Incr_LY = c(0, incr_ly_crp, incr_ly_tlr, incr_ly_tmb_braf),
  Incr_QALY = c(0, incr_qaly_crp, incr_qaly_tlr, incr_qaly_tmb_braf)
)
```

```{r table-kable}
# Create table using kableExtra
effectiveness_data %>%
  kable(
    col.names = c(
      "Strategy",
      "Median PFS (months)",
      "Median OS (months)",
      "HR for PFS (95% CI)",
      "HR for OS (95% CI)",
      "Mean Life Years",
      "Mean QALYs",
      "Incremental LY vs. Control",
      "Incremental QALYs vs. Control"
    ),
    digits = 2,
    caption = "Clinical Effectiveness Results (Undiscounted)",
    booktabs = TRUE,
    format = "latex"
  ) %>%
  kable_styling(
    latex_options = c("scale_down", "hold_position"),
    font_size = 9
  ) %>%
  column_spec(1, width = "2.5cm") %>%
  column_spec(2:9, width = "1.5cm")
```

**Note:** All outcomes are undiscounted (discount rate = 0%). Median survival times derived from parametric survival models weighted by biomarker prevalence. Hazard ratios (HR) from Cox proportional hazards models adjusted for age, sex, and all biomarker×treatment interactions. Life years and QALYs calculated from decision-analytic model. CI = Confidence Interval; LY = Life Years; QALY = Quality-Adjusted Life Years; PFS = Progression-Free Survival; OS = Overall Survival.

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.0
```