---
title: "METIMMOX-1 Clinical Effectiveness Analysis Report"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))



```

```{r load-analysis-scripts, include=FALSE}
# 02 - Setup and Global Variables
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

# 03 - Biomarker Strategies
if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}

# 06 - Parametric Survival Analysis
if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
}

# 07 - Base Case Input Parameters
if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
}

# Set discount rates to 0 for undiscounted analysis
d_c <- 0  # Discount rate for costs
d_e <- 0  # Discount rate for effects

# Update parameters with zero discount rates
if (exists("l_params_base")) {
  l_params_base$d_c <- 0
  l_params_base$d_e <- 0
}

# Load model function
if (file.exists(here("scripts/R/functions/model_fun.R"))) {
  source(here("scripts/R/functions/model_fun.R"))
}

# Load calculate_outcomes function
if (file.exists(here("scripts/R/functions/calculate_outcomes.R"))) {
  source(here("scripts/R/functions/calculate_outcomes.R"))
}

# 10 - Base Case Analysis with traces to get subgroup QALYs
if (file.exists(here("scripts/R/analysis/10_basecase_analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/10_basecase_analysis.R"))))
}

# Run model with traces to extract subgroup outcomes
model_with_traces <- model_fun(l_params_base, return_traces = TRUE)
base_results <- model_with_traces$results
traces <- model_with_traces$traces
```

# Overview

This report presents clinical effectiveness results for the METIMMOX-1 trial, comparing biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer.

# Results

## Cox Proportional Hazards Models

```{r cox-models, include=FALSE}
# Cox Proportional Hazards Functions for METIMMOX-1 Analysis

# Function to calculate median from survival probabilities
calculate_median_survival <- function(surv_probs, time_points) {
  # Find first time point where survival drops below 0.5
  median_idx <- which(surv_probs < 0.5)[1]
  if (is.na(median_idx)) {
    # If survival never drops below 0.5, return the last time point
    return(time_points[length(time_points)])
  } else {
    return(time_points[median_idx])
  }
}

# Convert weeks to months (divide by 4.345)
weeks_to_months <- function(weeks) {
  return(weeks / 4.345)
}

# Function to calculate RMST (area under curve) using trapezoidal rule
calculate_auc <- function(surv_probs, time_points) {
  # Ensure surv_probs is a vector
  if (is.matrix(surv_probs) || is.data.frame(surv_probs)) {
    surv_probs <- as.vector(surv_probs)
  }
  
  # Ensure time_points is a vector
  if (is.matrix(time_points) || is.data.frame(time_points)) {
    time_points <- as.vector(time_points)
  }
  
  # Remove any NA values
  valid_idx <- !is.na(surv_probs) & !is.na(time_points)
  surv_probs <- surv_probs[valid_idx]
  time_points <- time_points[valid_idx]
  
  # If empty, return NA
  if (length(surv_probs) == 0 || length(time_points) == 0) {
    return(NA)
  }
  
  # Add initial point if not present
  if (time_points[1] != 0) {
    time_points <- c(0, time_points)
    surv_probs <- c(1, surv_probs)
  }
  
  # Calculate AUC using trapezoidal rule
  auc <- 0
  for (i in 1:(length(time_points)-1)) {
    auc <- auc + (time_points[i+1] - time_points[i]) * (surv_probs[i] + surv_probs[i+1]) / 2
  }
  
  return(auc)
}

# Function to format HR with CI for display
format_hr_ci <- function(hr_object) {
  if (is.na(hr_object$hr)) {
    return("NA")
  } else {
    return(sprintf("%.2f (%.2f-%.2f)", hr_object$hr, hr_object$ci_lower, hr_object$ci_upper))
  }
}

# Prepare data for Cox regression
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr", "tmb_braf", "OSwk", "Death", "PFSwk", "Progression")]), ]

# Ensure proper coding
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)

# Convert biomarkers to numeric (0/1)
data_complete$crp <- as.numeric(as.character(data_complete$crp))
data_complete$tlr <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf <- as.numeric(as.character(data_complete$tmb_braf))

# Create combined treatment/biomarker groups for each biomarker
# Reference group = all patients on Rx=0 (standard of care), regardless of biomarker

# For CRP strategy
data_complete$crp_group <- factor(
  case_when(
    data_complete$Rx == levels(data_complete$Rx)[1] ~ "SoC (all)",  # All Rx=0 pooled
    data_complete$Rx == levels(data_complete$Rx)[2] & data_complete$crp == 1 ~ "CRP+ on Rx",
    data_complete$Rx == levels(data_complete$Rx)[2] & data_complete$crp == 0 ~ "CRP- on Rx"
  ),
  levels = c("SoC (all)", "CRP+ on Rx", "CRP- on Rx")
)

# For TLR strategy
data_complete$tlr_group <- factor(
  case_when(
    data_complete$Rx == levels(data_complete$Rx)[1] ~ "SoC (all)",
    data_complete$Rx == levels(data_complete$Rx)[2] & data_complete$tlr == 1 ~ "TLR+ on Rx",
    data_complete$Rx == levels(data_complete$Rx)[2] & data_complete$tlr == 0 ~ "TLR- on Rx"
  ),
  levels = c("SoC (all)", "TLR+ on Rx", "TLR- on Rx")
)

# For TMB/BRAF strategy
data_complete$tmb_group <- factor(
  case_when(
    data_complete$Rx == levels(data_complete$Rx)[1] ~ "SoC (all)",
    data_complete$Rx == levels(data_complete$Rx)[2] & data_complete$tmb_braf == 1 ~ "TMB/BRAF+ on Rx",
    data_complete$Rx == levels(data_complete$Rx)[2] & data_complete$tmb_braf == 0 ~ "TMB/BRAF- on Rx"
  ),
  levels = c("SoC (all)", "TMB/BRAF+ on Rx", "TMB/BRAF- on Rx")
)

# Fit Cox models comparing each subgroup to pooled SoC
# CRP models
cox_os_crp <- coxph(Surv(OSwk, Death) ~ Age + sex + crp_group, data = data_complete)
cox_pfs_crp <- coxph(Surv(PFSwk, Progression) ~ Age + sex + crp_group, data = data_complete)

# TLR models
cox_os_tlr <- coxph(Surv(OSwk, Death) ~ Age + sex + tlr_group, data = data_complete)
cox_pfs_tlr <- coxph(Surv(PFSwk, Progression) ~ Age + sex + tlr_group, data = data_complete)

# TMB/BRAF models
cox_os_tmb <- coxph(Surv(OSwk, Death) ~ Age + sex + tmb_group, data = data_complete)
cox_pfs_tmb <- coxph(Surv(PFSwk, Progression) ~ Age + sex + tmb_group, data = data_complete)

# Extract HRs with confidence intervals
# Function to extract HR from grouped Cox model
extract_grouped_hr <- function(cox_model, positive_level, negative_level) {
  summ <- summary(cox_model)
  coef_table <- summ$coefficients
  conf_int <- summ$conf.int
  
  # Find rows for positive and negative groups
  pos_idx <- grep(positive_level, rownames(coef_table), fixed = TRUE)
  neg_idx <- grep(negative_level, rownames(coef_table), fixed = TRUE)
  
  if (length(pos_idx) > 0) {
    hr_pos <- conf_int[pos_idx, "exp(coef)"]
    ci_pos_lower <- conf_int[pos_idx, "lower .95"]
    ci_pos_upper <- conf_int[pos_idx, "upper .95"]
  } else {
    hr_pos <- ci_pos_lower <- ci_pos_upper <- NA
  }
  
  if (length(neg_idx) > 0) {
    hr_neg <- conf_int[neg_idx, "exp(coef)"]
    ci_neg_lower <- conf_int[neg_idx, "lower .95"]
    ci_neg_upper <- conf_int[neg_idx, "upper .95"]
  } else {
    hr_neg <- ci_neg_lower <- ci_neg_upper <- NA
  }
  
  return(list(
    positive = list(hr = hr_pos, ci_lower = ci_pos_lower, ci_upper = ci_pos_upper),
    negative = list(hr = hr_neg, ci_lower = ci_neg_lower, ci_upper = ci_neg_upper)
  ))
}

# Extract HRs for each biomarker strategy
hr_os_crp <- extract_grouped_hr(cox_os_crp, "CRP+ on Rx", "CRP- on Rx")
hr_pfs_crp <- extract_grouped_hr(cox_pfs_crp, "CRP+ on Rx", "CRP- on Rx")

hr_os_tlr <- extract_grouped_hr(cox_os_tlr, "TLR+ on Rx", "TLR- on Rx")
hr_pfs_tlr <- extract_grouped_hr(cox_pfs_tlr, "TLR+ on Rx", "TLR- on Rx")

hr_os_tmb <- extract_grouped_hr(cox_os_tmb, "TMB/BRAF+ on Rx", "TMB/BRAF- on Rx")
hr_pfs_tmb <- extract_grouped_hr(cox_pfs_tmb, "TMB/BRAF+ on Rx", "TMB/BRAF- on Rx")
```

Cox proportional hazards regression models were fitted comparing each biomarker-defined treatment subgroup to a common reference of all patients receiving standard of care (Rx=0), adjusting for age and sex. This approach pools all control patients regardless of biomarker status as the reference group.

## Median Survival Times and Overall Outcomes

```{r median-survival, include=FALSE}
# Extract median survival times from parametric models
if (exists("predictions") && length(predictions) > 0) {
  # Overall strategies
  median_pfs_control <- calculate_median_survival(predictions$control$pfs, time_points)
  median_os_control <- calculate_median_survival(predictions$control$os, time_points)
  
  median_pfs_crp <- calculate_median_survival(predictions$crp$pfs, time_points)
  median_os_crp <- calculate_median_survival(predictions$crp$os, time_points)
  
  median_pfs_tlr <- calculate_median_survival(predictions$tlr$pfs, time_points)
  median_os_tlr <- calculate_median_survival(predictions$tlr$os, time_points)
  
  median_pfs_tmb_braf <- calculate_median_survival(predictions$tmb_braf$pfs, time_points)
  median_os_tmb_braf <- calculate_median_survival(predictions$tmb_braf$os, time_points)
  
  # Subgroups - CRP
  median_pfs_crp_pos <- calculate_median_survival(predictions$crp$biomarker_positive$pfs, time_points)
  median_os_crp_pos <- calculate_median_survival(predictions$crp$biomarker_positive$os, time_points)
  median_pfs_crp_neg <- calculate_median_survival(predictions$crp$biomarker_negative$pfs, time_points)
  median_os_crp_neg <- calculate_median_survival(predictions$crp$biomarker_negative$os, time_points)
  
  # Subgroups - TLR
  median_pfs_tlr_pos <- calculate_median_survival(predictions$tlr$biomarker_positive$pfs, time_points)
  median_os_tlr_pos <- calculate_median_survival(predictions$tlr$biomarker_positive$os, time_points)
  median_pfs_tlr_neg <- calculate_median_survival(predictions$tlr$biomarker_negative$pfs, time_points)
  median_os_tlr_neg <- calculate_median_survival(predictions$tlr$biomarker_negative$os, time_points)
  
  # Subgroups - TMB/BRAF
  median_pfs_tmb_pos <- calculate_median_survival(predictions$tmb_braf$biomarker_positive$pfs, time_points)
  median_os_tmb_pos <- calculate_median_survival(predictions$tmb_braf$biomarker_positive$os, time_points)
  median_pfs_tmb_neg <- calculate_median_survival(predictions$tmb_braf$biomarker_negative$pfs, time_points)
  median_os_tmb_neg <- calculate_median_survival(predictions$tmb_braf$biomarker_negative$os, time_points)
  
  # Convert all to months
  median_pfs_control_mo <- weeks_to_months(median_pfs_control)
  median_os_control_mo <- weeks_to_months(median_os_control)
  median_pfs_crp_mo <- weeks_to_months(median_pfs_crp)
  median_os_crp_mo <- weeks_to_months(median_os_crp)
  median_pfs_tlr_mo <- weeks_to_months(median_pfs_tlr)
  median_os_tlr_mo <- weeks_to_months(median_os_tlr)
  median_pfs_tmb_braf_mo <- weeks_to_months(median_pfs_tmb_braf)
  median_os_tmb_braf_mo <- weeks_to_months(median_os_tmb_braf)
  
  median_pfs_crp_pos_mo <- weeks_to_months(median_pfs_crp_pos)
  median_os_crp_pos_mo <- weeks_to_months(median_os_crp_pos)
  median_pfs_crp_neg_mo <- weeks_to_months(median_pfs_crp_neg)
  median_os_crp_neg_mo <- weeks_to_months(median_os_crp_neg)
  
  median_pfs_tlr_pos_mo <- weeks_to_months(median_pfs_tlr_pos)
  median_os_tlr_pos_mo <- weeks_to_months(median_os_tlr_pos)
  median_pfs_tlr_neg_mo <- weeks_to_months(median_pfs_tlr_neg)
  median_os_tlr_neg_mo <- weeks_to_months(median_os_tlr_neg)
  
  median_pfs_tmb_pos_mo <- weeks_to_months(median_pfs_tmb_pos)
  median_os_tmb_pos_mo <- weeks_to_months(median_os_tmb_pos)
  median_pfs_tmb_neg_mo <- weeks_to_months(median_pfs_tmb_neg)
  median_os_tmb_neg_mo <- weeks_to_months(median_os_tmb_neg)
  
} else {
  median_pfs_control_mo <- median_os_control_mo <- NA
  median_pfs_crp_mo <- median_os_crp_mo <- NA
  median_pfs_tlr_mo <- median_os_tlr_mo <- NA
  median_pfs_tmb_braf_mo <- median_os_tmb_braf_mo <- NA
  median_pfs_crp_pos_mo <- median_os_crp_pos_mo <- NA
  median_pfs_crp_neg_mo <- median_os_crp_neg_mo <- NA
  median_pfs_tlr_pos_mo <- median_os_tlr_pos_mo <- NA
  median_pfs_tlr_neg_mo <- median_os_tlr_neg_mo <- NA
  median_pfs_tmb_pos_mo <- median_os_tmb_pos_mo <- NA
  median_pfs_tmb_neg_mo <- median_os_tmb_neg_mo <- NA
}

# Calculate life years from survival predictions
if (exists("predictions") && length(predictions) > 0) {
  # Overall strategies
  ly_control <- calculate_auc(predictions$control$os, time_points) / 52
  ly_crp <- calculate_auc(predictions$crp$os, time_points) / 52
  ly_tlr <- calculate_auc(predictions$tlr$os, time_points) / 52
  ly_tmb_braf <- calculate_auc(predictions$tmb_braf$os, time_points) / 52
  
  # Subgroups
  ly_crp_pos <- calculate_auc(predictions$crp$biomarker_positive$os, time_points) / 52
  ly_crp_neg <- calculate_auc(predictions$crp$biomarker_negative$os, time_points) / 52
  ly_tlr_pos <- calculate_auc(predictions$tlr$biomarker_positive$os, time_points) / 52
  ly_tlr_neg <- calculate_auc(predictions$tlr$biomarker_negative$os, time_points) / 52
  ly_tmb_pos <- calculate_auc(predictions$tmb_braf$biomarker_positive$os, time_points) / 52
  ly_tmb_neg <- calculate_auc(predictions$tmb_braf$biomarker_negative$os, time_points) / 52
  
} else {
  ly_control <- ly_crp <- ly_tlr <- ly_tmb_braf <- NA
  ly_crp_pos <- ly_crp_neg <- ly_tlr_pos <- ly_tlr_neg <- ly_tmb_pos <- ly_tmb_neg <- NA
}

# Get QALYs from base_results and traces
if (exists("base_results") && exists("traces")) {
  # Overall strategies
  qaly_control <- base_results$Effect[base_results$Strategy == "control"]
  qaly_crp <- base_results$Effect[base_results$Strategy == "crp"]
  qaly_tlr <- base_results$Effect[base_results$Strategy == "tlr"]
  qaly_tmb_braf <- base_results$Effect[base_results$Strategy == "tmb_braf"]
  
  # Subgroup QALYs from traces
  qaly_crp_pos <- traces$crp$positive$qalys_total
  qaly_crp_neg <- traces$crp$negative$qalys_total
  qaly_tlr_pos <- traces$tlr$positive$qalys_total
  qaly_tlr_neg <- traces$tlr$negative$qalys_total
  qaly_tmb_pos <- traces$tmb_braf$positive$qalys_total
  qaly_tmb_neg <- traces$tmb_braf$negative$qalys_total
  
} else {
  qaly_control <- qaly_crp <- qaly_tlr <- qaly_tmb_braf <- NA
  qaly_crp_pos <- qaly_crp_neg <- qaly_tlr_pos <- qaly_tlr_neg <- qaly_tmb_pos <- qaly_tmb_neg <- NA
}
```

```{r create-tables, include=FALSE}
# Create data frame for Table 1: Overall outcomes with subgroups
overall_outcomes <- data.frame(
  Strategy = c(
    "Control (FLOX alone)", 
    "CRP-guided (overall)", 
    "  CRP-positive (Rx=1)",
    "  CRP-negative (Rx=0)",
    "TLR-guided (overall)",
    "  TLR-positive (Rx=1)",
    "  TLR-negative (Rx=0)",
    "TMB/BRAF-guided (overall)",
    "  TMB/BRAF-positive (Rx=1)",
    "  TMB/BRAF-negative (Rx=0)"
  ),
  Median_PFS = c(
    median_pfs_control_mo, 
    median_pfs_crp_mo, 
    median_pfs_crp_pos_mo,
    median_pfs_crp_neg_mo,
    median_pfs_tlr_mo,
    median_pfs_tlr_pos_mo,
    median_pfs_tlr_neg_mo,
    median_pfs_tmb_braf_mo,
    median_pfs_tmb_pos_mo,
    median_pfs_tmb_neg_mo
  ),
  Median_OS = c(
    median_os_control_mo, 
    median_os_crp_mo, 
    median_os_crp_pos_mo,
    median_os_crp_neg_mo,
    median_os_tlr_mo,
    median_os_tlr_pos_mo,
    median_os_tlr_neg_mo,
    median_os_tmb_braf_mo,
    median_os_tmb_pos_mo,
    median_os_tmb_neg_mo
  ),
  Mean_LY = c(
    ly_control, 
    ly_crp, 
    ly_crp_pos,
    ly_crp_neg,
    ly_tlr,
    ly_tlr_pos,
    ly_tlr_neg,
    ly_tmb_braf,
    ly_tmb_pos,
    ly_tmb_neg
  ),
  Mean_QALY = c(
    qaly_control, 
    qaly_crp, 
    qaly_crp_pos,
    qaly_crp_neg,
    qaly_tlr,
    qaly_tlr_pos,
    qaly_tlr_neg,
    qaly_tmb_braf,
    qaly_tmb_pos,
    qaly_tmb_neg
  )
)

# Create data frame for Table 2: PFS hazard ratios
pfs_hr_table <- data.frame(
  Strategy = c("Control (FLOX alone)", 
               "CRP-guided: Biomarker-positive (Rx=1)", 
               "CRP-guided: Biomarker-negative (Rx=0)",
               "TLR-guided: Biomarker-positive (Rx=1)",
               "TLR-guided: Biomarker-negative (Rx=0)",
               "TMB/BRAF-guided: Biomarker-positive (Rx=1)",
               "TMB/BRAF-guided: Biomarker-negative (Rx=0)"),
  HR_PFS = c("Reference",
             format_hr_ci(hr_pfs_crp$positive),
             format_hr_ci(hr_pfs_crp$negative),
             format_hr_ci(hr_pfs_tlr$positive),
             format_hr_ci(hr_pfs_tlr$negative),
             format_hr_ci(hr_pfs_tmb$positive),
             format_hr_ci(hr_pfs_tmb$negative))
)

# Create data frame for Table 3: OS hazard ratios
os_hr_table <- data.frame(
  Strategy = c("Control (FLOX alone)", 
               "CRP-guided: Biomarker-positive (Rx=1)", 
               "CRP-guided: Biomarker-negative (Rx=0)",
               "TLR-guided: Biomarker-positive (Rx=1)",
               "TLR-guided: Biomarker-negative (Rx=0)",
               "TMB/BRAF-guided: Biomarker-positive (Rx=1)",
               "TMB/BRAF-guided: Biomarker-negative (Rx=0)"),
  HR_OS = c("Reference",
            format_hr_ci(hr_os_crp$positive),
            format_hr_ci(hr_os_crp$negative),
            format_hr_ci(hr_os_tlr$positive),
            format_hr_ci(hr_os_tlr$negative),
            format_hr_ci(hr_os_tmb$positive),
            format_hr_ci(hr_os_tmb$negative))
)
```

## Clinical Effectiveness Summary

### Table 1: Overall Survival and Quality-Adjusted Outcomes by Strategy and Biomarker Subgroup

```{r table1-overall}
overall_outcomes %>%
  kable(
    col.names = c(
      "Strategy and Subgroup",
      "Median PFS (months)",
      "Median OS (months)",
      "Mean Life Years",
      "Mean QALYs"
    ),
    digits = 2,
    caption = "Clinical Effectiveness Results (Undiscounted)",
    booktabs = TRUE,
    format = "latex"
  ) %>%
  kable_styling(
    latex_options = c("hold_position", "scale_down"),
    font_size = 9
  ) %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2:5, width = "2.2cm") %>%
  pack_rows("Standard of Care", 1, 1, bold = TRUE) %>%
  pack_rows("CRP-guided Strategy", 2, 4, bold = TRUE) %>%
  pack_rows("TLR-guided Strategy", 5, 7, bold = TRUE) %>%
  pack_rows("TMB/BRAF-guided Strategy", 8, 10, bold = TRUE)
```

**Note:** All outcomes are undiscounted (discount rate = 0%). All results are derived from parametric survival models. Overall strategy outcomes are weighted by biomarker prevalence. Subgroup QALYs are calculated from the health economic model accounting for time in progression-free and progressed health states with different utility weights. Rx=1 indicates treatment with alternating FLOX/nivolumab; Rx=0 indicates FLOX alone (standard of care).

\newpage

### Table 2: Hazard Ratios for Progression-Free Survival by Biomarker Status

```{r table2-pfs-hr}
pfs_hr_table %>%
  kable(
    col.names = c(
      "Strategy and Biomarker Subgroup",
      "HR for PFS (95% CI)"
    ),
    caption = "Hazard Ratios for Progression-Free Survival by Biomarker Status",
    booktabs = TRUE,
    format = "latex"
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    font_size = 10
  ) %>%
  column_spec(1, width = "8cm") %>%
  column_spec(2, width = "4cm") %>%
  pack_rows("Standard of Care", 1, 1) %>%
  pack_rows("CRP-guided Strategy", 2, 3) %>%
  pack_rows("TLR-guided Strategy", 4, 5) %>%
  pack_rows("TMB/BRAF-guided Strategy", 6, 7)
```

**Note:** Hazard ratios compare each biomarker-defined treatment subgroup to all patients receiving standard of care (Rx=0), pooled regardless of biomarker status, adjusted for age and sex. HR < 1 indicates better survival than pooled control group.

\newpage

### Table 3: Hazard Ratios for Overall Survival by Biomarker Status

```{r table3-os-hr}
os_hr_table %>%
  kable(
    col.names = c(
      "Strategy and Biomarker Subgroup",
      "HR for OS (95% CI)"
    ),
    caption = "Hazard Ratios for Overall Survival by Biomarker Status",
    booktabs = TRUE,
    format = "latex"
  ) %>%
  kable_styling(
    latex_options = c("hold_position"),
    font_size = 10
  ) %>%
  column_spec(1, width = "8cm") %>%
  column_spec(2, width = "4cm") %>%
  pack_rows("Standard of Care", 1, 1) %>%
  pack_rows("CRP-guided Strategy", 2, 3) %>%
  pack_rows("TLR-guided Strategy", 4, 5) %>%
  pack_rows("TMB/BRAF-guided Strategy", 6, 7)
```

**Note:** Hazard ratios compare each biomarker-defined treatment subgroup to all patients receiving standard of care (Rx=0), pooled regardless of biomarker status, adjusted for age and sex. HR < 1 indicates better survival than pooled control group.

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.1