---
title: "Clinical Effectiveness"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, tidyverse,
  survival,   # Surv object, cox.zph for Schoenfeld, ridge()
  coxphf,     # Firth-corrected Cox regression + coxphftest
  glmnet,     # Ridge regression fallback (alpha=0)
  vcd         # Cramér's V calculation
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r load-data, include=FALSE}
# Source analysis scripts for data loading
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}
```

```{r helper-functions, include=FALSE}
# =============================================================================
# HELPER FUNCTIONS
# =============================================================================

#' Fit Firth-corrected Cox model with profile likelihood CIs
fit_firth_cox <- function(formula, data, label = "model") {
  tryCatch({
    coxphf(
      formula = formula,
      data = data,
      firth = TRUE,
      pl = TRUE,        # Profile likelihood CIs
      maxit = 100,
      maxstep = 0.1
    )
  }, error = function(e) {
    warning(paste("coxphf failed for", label, ":", e$message))
    NULL
  })
}

#' Extract results from coxphf (full table, interactions grouped at top)
#' Note: coxphf ci.lower and ci.upper are ALREADY exponentiated (HR scale)
extract_coxphf_results <- function(model, reorder_interactions = TRUE) {
  if (is.null(model)) return(NULL)

  results <- data.frame(
    Term = names(model$coefficients),
    HR = exp(model$coefficients),
    CI_Lower = model$ci.lower,  # Already on HR scale, do NOT exp()
    CI_Upper = model$ci.upper,  # Already on HR scale, do NOT exp()
    P_Value = model$prob,
    stringsAsFactors = FALSE
  )

  if (reorder_interactions) {
    # Put interaction terms at top
    is_interaction <- grepl(":", results$Term)
    results <- rbind(results[is_interaction, ], results[!is_interaction, ])
  }

  rownames(results) <- NULL
  results
}

#' Penalized Likelihood Ratio Test for specific interaction term
test_interaction_plrt <- function(formula_full, data, interaction_term) {
  test_formula <- as.formula(paste("~", interaction_term))

  tryCatch({
    result <- coxphftest(
      formula = formula_full,
      data = data,
      test = test_formula,
      firth = TRUE
    )
    list(
      term = interaction_term,
      loglik_full = result$loglik[2],
      loglik_restricted = result$loglik[1],
      df = result$df,
      p_value = result$prob
    )
  }, error = function(e) {
    list(term = interaction_term, p_value = NA)
  })
}

#' Apply Benjamini-Hochberg FDR correction
apply_bh_correction <- function(p_values) {
  p.adjust(p_values, method = "BH")
}

#' Format HR with CI for display (vectorized)
format_hr_ci <- function(hr, ci_lower, ci_upper, digits = 2) {
  mapply(function(h, l, u) {
    if (is.na(h)) return("--")
    sprintf(paste0("%.", digits, "f (%.", digits, "f-%.", digits, "f)"), h, l, u)
  }, hr, ci_lower, ci_upper, USE.NAMES = FALSE)
}

#' Format p-value for display (vectorized)
format_pvalue <- function(p, digits = 3) {
  sapply(p, function(pval) {
    if (is.na(pval)) return("--")
    if (pval < 0.001) return("<0.001")
    sprintf(paste0("%.", digits, "f"), pval)
  }, USE.NAMES = FALSE)
}

#' Create forest plot for interaction HRs
create_interaction_forest_plot <- function(results_df, outcome = "OS") {
  ggplot(results_df,
         aes(x = HR, y = Biomarker, color = Model, shape = Model)) +
    geom_point(position = position_dodge(width = 0.5), size = 3) +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper),
                   position = position_dodge(width = 0.5), height = 0.2) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4, 10),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4", "10")) +
    scale_color_manual(
      values = c("A: All-in-One" = "#E69F00",
                 "B: Focused" = "#56B4E9",
                 "C: Single" = "#009E73"),
      name = "Model Type"
    ) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = paste("Treatment × Biomarker Interaction:", outcome),
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

#' Create log-log survival plot for PH diagnostics
create_loglog_plot <- function(data, time_var, event_var, strata_var, title) {
  formula <- as.formula(paste0("Surv(", time_var, ", ", event_var, ") ~ ", strata_var))
  km_fit <- survfit(formula, data = data)

  # Extract survival data
  surv_summary <- summary(km_fit)

  plot_data <- data.frame(
    time = surv_summary$time,
    surv = surv_summary$surv,
    strata = surv_summary$strata
  ) %>%
    filter(surv > 0 & surv < 1) %>%
    mutate(
      log_time = log(time),
      log_log_surv = log(-log(surv))
    )

  ggplot(plot_data, aes(x = log_time, y = log_log_surv, color = strata)) +
    geom_step(linewidth = 1) +
    labs(
      x = "log(Time in weeks)",
      y = "-log(-log(S(t)))",
      title = title,
      subtitle = "Parallel lines support PH assumption",
      color = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

```{r data-preparation, include=FALSE}
# =============================================================================
# DATA PREPARATION
# =============================================================================

# Prepare data for Cox models
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

# Ensure proper factor coding
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)

# Biomarkers as numeric 0/1 for coxphf (interactions work better with numeric)
data_complete$crp_num <- as.numeric(as.character(data_complete$crp))
data_complete$tlr_num <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf_num <- as.numeric(as.character(data_complete$tmb_braf))

# Create numeric Rx for ridge regression
data_complete$Rx_num <- as.numeric(data_complete$Rx) - 1  # 0 = Control, 1 = Experimental

# Sample characteristics
n_total <- nrow(data_complete)
n_control <- sum(data_complete$Rx_num == 0)
n_experimental <- sum(data_complete$Rx_num == 1)

# Biomarker prevalence
prev_crp <- mean(data_complete$crp_num)
prev_tlr <- mean(data_complete$tlr_num)
prev_tmb_braf <- mean(data_complete$tmb_braf_num)

# Event counts
n_deaths <- sum(data_complete$Death)
n_progressions <- sum(data_complete$Progression)
```

```{r biomarker-correlation, include=FALSE}
# =============================================================================
# BIOMARKER CORRELATION ANALYSIS (Cramér's V)
# =============================================================================

# CRP vs TLR
crp_tlr_table <- table(data_complete$crp_num, data_complete$tlr_num)
crp_tlr_assoc <- assocstats(crp_tlr_table)
cramers_v_crp_tlr <- crp_tlr_assoc$cramer

# CRP vs TMB/BRAF
crp_tmb_table <- table(data_complete$crp_num, data_complete$tmb_braf_num)
crp_tmb_assoc <- assocstats(crp_tmb_table)
cramers_v_crp_tmb <- crp_tmb_assoc$cramer

# TLR vs TMB/BRAF
tlr_tmb_table <- table(data_complete$tlr_num, data_complete$tmb_braf_num)
tlr_tmb_assoc <- assocstats(tlr_tmb_table)
cramers_v_tlr_tmb <- tlr_tmb_assoc$cramer

# Build correlation summary
correlation_df <- data.frame(
  Comparison = c("CRP vs TLR", "CRP vs TMB/BRAF", "TLR vs TMB/BRAF"),
  Cramers_V = round(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), 3),
  Interpretation = sapply(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), function(v) {
    if (v > 0.3) "Moderate/Strong"
    else if (v > 0.1) "Weak"
    else "Negligible"
  })
)
```

# Overview

This report presents clinical effectiveness results from the METIMMOX-1 trial, evaluating biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer.

The analysis uses **Firth-corrected Cox proportional hazards regression** with profile likelihood confidence intervals to assess treatment effect heterogeneity across three candidate biomarkers:

- **CRP** (C-reactive protein): Low CRP (<5 mg/L) at baseline
- **TLR** (Tumor Lesion Reduction): Early response (≥10% reduction at first CT scan)
- **TMB/BRAF**: High tumor mutational burden (≥9 mut/MB) or BRAF mutation

We compare three model structures to assess the robustness of treatment-biomarker interactions:

- **Model A**: All-in-one model with all biomarkers and interactions
- **Model B**: Focused models with CRP and TMB/BRAF plus both interaction terms (TLR excluded)
- **Model C**: Single-biomarker models with one biomarker and its interaction

# Methodological Notes

## Software Packages

This analysis uses the following R packages:

- `coxphf` version `r packageVersion("coxphf")`: Firth-corrected Cox regression with profile likelihood CIs
- `survival` version `r packageVersion("survival")`: Cox regression and Schoenfeld residual diagnostics
- `glmnet` version `r packageVersion("glmnet")`: Ridge regression sensitivity analysis
- `vcd` version `r packageVersion("vcd")`: Cramér's V for biomarker correlation assessment

## Firth-Corrected Cox Regression

We use Firth's penalized maximum likelihood method for Cox regression, which addresses:

1. **Monotone likelihood**: When a covariate perfectly separates events from non-events
2. **Small sample bias**: Reduces bias in coefficient estimates with sparse data
3. **Unstable confidence intervals**: Profile likelihood CIs are more reliable than Wald-based CIs in small samples

Statistical inference is based on **penalized likelihood ratio tests (PLRT)**, which are more appropriate than Wald tests for testing treatment-biomarker interactions in this setting.

## Ridge Regression Sensitivity Analysis

We use Ridge regression as a sensitivity analysis to assess the stability of our interaction estimates. Ridge regression (also called L2-penalized regression or Tikhonov regularization) belongs to the family of regularized or penalized regression methods. In survival analysis, this is implemented as a penalized Cox model.

**How Ridge regression works:**

- Ridge adds a penalty term that discourages large coefficients. The bigger a coefficient tries to get, the more the model resists, pulling estimates toward zero (HR toward 1.0).
- Unlike LASSO (alpha = 1), which sets some coefficients exactly to zero and performs variable selection, Ridge (alpha = 0) shrinks all coefficients but retains all predictors.
- The degree of shrinkage is controlled by the tuning parameter lambda, which is selected via **cross-validation (CV)**: the data are repeatedly split into training and validation sets, and the lambda that produces the best predictive performance is chosen.

**Why not LASSO or Elastic Net?**

We determined that LASSO and elastic net are **not appropriate** for this analysis:

1. **Correlated biomarkers**: LASSO arbitrarily selects one of correlated predictors while setting others to zero, which does not reflect the clinical question of comparing ALL biomarker strategies.

2. **Hierarchy principle violation**: LASSO may select interaction terms (e.g., `crp:Rx`) while setting the main effect (`crp`) to zero, producing models that are difficult to interpret clinically.

3. **Clinical objective**: Our goal is to estimate treatment effect heterogeneity across ALL biomarkers simultaneously, not to select a "winning" biomarker.

Elastic net (alpha = 0.1–0.3) represents a compromise but does not fully address these concerns.

**Interpreting Ridge results:**

Ridge regression is not replacing the Firth estimates—it provides a reality check. When Ridge substantially shrinks an interaction coefficient toward zero while Firth estimates a large effect, this indicates the effect is too unstable to trust for practical use. The CV-selected lambda reflects how much regularization is needed for reasonable out-of-sample prediction given the sample size and collinearity structure.

## Multiple Testing Correction

We apply the **Benjamini-Hochberg (BH) procedure** to control the false discovery rate (FDR) on the primary Firth analysis:

- 6 interaction tests: 3 biomarkers × 2 outcomes (OS, PFS)
- Both raw PLRT p-values and BH-adjusted q-values are reported
- The Ridge sensitivity analysis does not require separate multiplicity correction

# Data Preparation

## Sample Characteristics

```{r table-sample}
sample_df <- data.frame(
  Characteristic = c("Total patients (complete cases)",
                     "Control arm (FLOX alone)",
                     "Experimental arm (alternating FLOX/nivolumab)",
                     "",
                     "Deaths (OS events)",
                     "Progressions (PFS events)",
                     "",
                     "CRP-positive (low CRP)",
                     "TLR-positive (early response)",
                     "TMB/BRAF-positive"),
  Value = c(n_total,
            paste0(n_control, " (", round(100*n_control/n_total, 1), "%)"),
            paste0(n_experimental, " (", round(100*n_experimental/n_total, 1), "%)"),
            "",
            paste0(n_deaths, " (", round(100*n_deaths/n_total, 1), "%)"),
            paste0(n_progressions, " (", round(100*n_progressions/n_total, 1), "%)"),
            "",
            paste0(sum(data_complete$crp_num), " (", round(100*prev_crp, 1), "%)"),
            paste0(sum(data_complete$tlr_num), " (", round(100*prev_tlr, 1), "%)"),
            paste0(sum(data_complete$tmb_braf_num), " (", round(100*prev_tmb_braf, 1), "%)"))
)

sample_df %>%
  kable(col.names = c("Characteristic", "N (%)"),
        caption = "Sample Characteristics",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  row_spec(c(4, 7), bold = FALSE, extra_css = "border-bottom: none;")
```

## Biomarker Correlations

```{r table-correlation}
correlation_df %>%
  kable(col.names = c("Biomarker Pair", "Cramér's V", "Interpretation"),
        caption = "Biomarker Correlations (Cramér's V)",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

**Note:** Cramér's V interpretation: <0.1 = Negligible, 0.1–0.3 = Weak, >0.3 = Moderate/Strong. The observed correlations are weak to negligible. While modest, any correlation among candidate biomarkers supports our decision not to use LASSO, which would arbitrarily select among correlated predictors.

\newpage

# Proportional Hazards Assumption

```{r ph-diagnostics, include=FALSE}
# =============================================================================
# PROPORTIONAL HAZARDS DIAGNOSTICS
# =============================================================================

# Fit standard coxph for Schoenfeld tests (not available in coxphf)
# Use Model A formula structure
formula_diag_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                       crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx
formula_diag_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                               crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx

coxph_diag_os <- coxph(formula_diag_os, data = data_complete)
coxph_diag_pfs <- coxph(formula_diag_pfs, data = data_complete)

# Schoenfeld residual tests
zph_os <- cox.zph(coxph_diag_os)
zph_pfs <- cox.zph(coxph_diag_pfs)

# Extract results
zph_os_df <- as.data.frame(zph_os$table)
zph_pfs_df <- as.data.frame(zph_pfs$table)
```

## Schoenfeld Residual Tests

The proportional hazards assumption was tested using scaled Schoenfeld residuals. A significant p-value indicates potential violation of the PH assumption for that covariate.

```{r table-schoenfeld}
# Combine OS and PFS results
schoenfeld_df <- data.frame(
  Covariate = rownames(zph_os_df),
  Chi_sq_OS = round(zph_os_df$chisq, 2),
  P_OS = format_pvalue(zph_os_df$p),
  Chi_sq_PFS = round(zph_pfs_df$chisq, 2),
  P_PFS = format_pvalue(zph_pfs_df$p)
)

schoenfeld_df %>%
  kable(col.names = c("Covariate", "χ² (OS)", "p-value", "χ² (PFS)", "p-value"),
        caption = "Schoenfeld Residual Test for Proportional Hazards Assumption",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  row_spec(nrow(schoenfeld_df), bold = TRUE)
```

**Note:** GLOBAL is the omnibus test for all covariates. Individual covariate tests help identify specific PH violations.

## Log-Log Survival Plots

```{r loglog-plots, fig.height=8, fig.width=10}
# Create log-log plots by treatment arm
p1 <- create_loglog_plot(data_complete, "OSwk", "Death", "Rx",
                         "Overall Survival by Treatment")
p2 <- create_loglog_plot(data_complete, "PFSwk", "Progression", "Rx",
                         "Progression-Free Survival by Treatment")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

**Interpretation:** Approximately parallel lines on the log-log plot support the proportional hazards assumption. Crossing or converging lines suggest time-varying effects.

\newpage

# Primary Analysis: Firth-Corrected Cox Models

```{r fit-all-models, include=FALSE}
# =============================================================================
# FIT ALL FIRTH-CORRECTED COX MODELS
# =============================================================================

# -----------------------------------------------------------------------------
# Model Type A: All-in-One (all biomarkers, all interactions)
# -----------------------------------------------------------------------------
formula_A_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                    crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx
formula_A_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                            crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx

model_A_os <- fit_firth_cox(formula_A_os, data_complete, "Model A OS")
model_A_pfs <- fit_firth_cox(formula_A_pfs, data_complete, "Model A PFS")

# -----------------------------------------------------------------------------
# Model Type B: Focused Models (all biomarkers, one interaction each)
# -----------------------------------------------------------------------------

# Model B: CRP + TMB/BRAF with BOTH interaction terms (TLR excluded)
# Shared formula used for both CRP and TMB/BRAF strategies
formula_B_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num + crp_num:Rx + tmb_braf_num:Rx
formula_B_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num + crp_num:Rx + tmb_braf_num:Rx

# Use shared formula for both CRP and TMB strategies
formula_B_crp_os <- formula_B_os
formula_B_crp_pfs <- formula_B_pfs
formula_B_tmb_os <- formula_B_os
formula_B_tmb_pfs <- formula_B_pfs

model_B_crp_os <- fit_firth_cox(formula_B_crp_os, data_complete, "Model B CRP OS")
model_B_crp_pfs <- fit_firth_cox(formula_B_crp_pfs, data_complete, "Model B CRP PFS")
model_B_tmb_os <- fit_firth_cox(formula_B_tmb_os, data_complete, "Model B TMB OS")
model_B_tmb_pfs <- fit_firth_cox(formula_B_tmb_pfs, data_complete, "Model B TMB PFS")

# Note: TLR is NOT included in Model B

# -----------------------------------------------------------------------------
# Model Type C: Single-Biomarker Models (one biomarker + interaction)
# -----------------------------------------------------------------------------

# CRP only
formula_C_crp_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + crp_num:Rx
formula_C_crp_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + crp_num:Rx

model_C_crp_os <- fit_firth_cox(formula_C_crp_os, data_complete, "Model C CRP OS")
model_C_crp_pfs <- fit_firth_cox(formula_C_crp_pfs, data_complete, "Model C CRP PFS")

# TLR only
formula_C_tlr_os <- Surv(OSwk, Death) ~ Age + sex + Rx + tlr_num + tlr_num:Rx
formula_C_tlr_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + tlr_num + tlr_num:Rx

model_C_tlr_os <- fit_firth_cox(formula_C_tlr_os, data_complete, "Model C TLR OS")
model_C_tlr_pfs <- fit_firth_cox(formula_C_tlr_pfs, data_complete, "Model C TLR PFS")

# TMB/BRAF only
formula_C_tmb_os <- Surv(OSwk, Death) ~ Age + sex + Rx + tmb_braf_num + tmb_braf_num:Rx
formula_C_tmb_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + tmb_braf_num + tmb_braf_num:Rx

model_C_tmb_os <- fit_firth_cox(formula_C_tmb_os, data_complete, "Model C TMB OS")
model_C_tmb_pfs <- fit_firth_cox(formula_C_tmb_pfs, data_complete, "Model C TMB PFS")
```

```{r plrt-tests, include=FALSE}
# =============================================================================
# PENALIZED LIKELIHOOD RATIO TESTS FOR INTERACTIONS
# =============================================================================

# Model A interaction tests
plrt_A_crp_os <- test_interaction_plrt(formula_A_os, data_complete, "crp_num:Rx")
plrt_A_tlr_os <- test_interaction_plrt(formula_A_os, data_complete, "tlr_num:Rx")
plrt_A_tmb_os <- test_interaction_plrt(formula_A_os, data_complete, "tmb_braf_num:Rx")

plrt_A_crp_pfs <- test_interaction_plrt(formula_A_pfs, data_complete, "crp_num:Rx")
plrt_A_tlr_pfs <- test_interaction_plrt(formula_A_pfs, data_complete, "tlr_num:Rx")
plrt_A_tmb_pfs <- test_interaction_plrt(formula_A_pfs, data_complete, "tmb_braf_num:Rx")

# Model B interaction tests (shared formula with BOTH interactions)
# NOTE: Model B excludes TLR - only CRP and TMB/BRAF
plrt_B_crp_os <- test_interaction_plrt(formula_B_crp_os, data_complete, "crp_num:Rx")
plrt_B_tmb_os <- test_interaction_plrt(formula_B_tmb_os, data_complete, "tmb_braf_num:Rx")

plrt_B_crp_pfs <- test_interaction_plrt(formula_B_crp_pfs, data_complete, "crp_num:Rx")
plrt_B_tmb_pfs <- test_interaction_plrt(formula_B_tmb_pfs, data_complete, "tmb_braf_num:Rx")

# Model C interaction tests
plrt_C_crp_os <- test_interaction_plrt(formula_C_crp_os, data_complete, "crp_num:Rx")
plrt_C_tlr_os <- test_interaction_plrt(formula_C_tlr_os, data_complete, "tlr_num:Rx")
plrt_C_tmb_os <- test_interaction_plrt(formula_C_tmb_os, data_complete, "tmb_braf_num:Rx")

plrt_C_crp_pfs <- test_interaction_plrt(formula_C_crp_pfs, data_complete, "crp_num:Rx")
plrt_C_tlr_pfs <- test_interaction_plrt(formula_C_tlr_pfs, data_complete, "tlr_num:Rx")
plrt_C_tmb_pfs <- test_interaction_plrt(formula_C_tmb_pfs, data_complete, "tmb_braf_num:Rx")

# Collect all p-values for BH correction (using Model A as primary)
all_pvalues <- c(
  plrt_A_crp_os$p_value, plrt_A_tlr_os$p_value, plrt_A_tmb_os$p_value,
  plrt_A_crp_pfs$p_value, plrt_A_tlr_pfs$p_value, plrt_A_tmb_pfs$p_value
)

# Apply BH correction
bh_adjusted <- apply_bh_correction(all_pvalues)
names(bh_adjusted) <- c("CRP_OS", "TLR_OS", "TMB_OS", "CRP_PFS", "TLR_PFS", "TMB_PFS")
```

```{r extract-results, include=FALSE}
# =============================================================================
# EXTRACT RESULTS FROM ALL MODELS
# =============================================================================

results_A_os <- extract_coxphf_results(model_A_os)
results_A_pfs <- extract_coxphf_results(model_A_pfs)

# Model B results (TLR excluded from Model B)
results_B_crp_os <- extract_coxphf_results(model_B_crp_os)
results_B_crp_pfs <- extract_coxphf_results(model_B_crp_pfs)
results_B_tmb_os <- extract_coxphf_results(model_B_tmb_os)
results_B_tmb_pfs <- extract_coxphf_results(model_B_tmb_pfs)

results_C_crp_os <- extract_coxphf_results(model_C_crp_os)
results_C_crp_pfs <- extract_coxphf_results(model_C_crp_pfs)
results_C_tlr_os <- extract_coxphf_results(model_C_tlr_os)
results_C_tlr_pfs <- extract_coxphf_results(model_C_tlr_pfs)
results_C_tmb_os <- extract_coxphf_results(model_C_tmb_os)
results_C_tmb_pfs <- extract_coxphf_results(model_C_tmb_pfs)
```

## Model Type A: All-in-One Model

This model includes all three biomarkers as main effects and all three treatment-biomarker interactions simultaneously.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx + tlr:Rx + tmb_braf:Rx`

### Overall Survival (Model A)

```{r table-A-os}
if (!is.null(results_A_os)) {
  # Add PLRT p-values for interaction terms
  results_A_os$PLRT_p <- NA
  results_A_os$BH_adj_p <- NA

  # Match interaction terms
  crp_idx <- grep("crp_num.*Rx|Rx.*crp_num", results_A_os$Term)
  tlr_idx <- grep("tlr_num.*Rx|Rx.*tlr_num", results_A_os$Term)
  tmb_idx <- grep("tmb_braf_num.*Rx|Rx.*tmb_braf_num", results_A_os$Term)

  if (length(crp_idx) > 0) {
    results_A_os$PLRT_p[crp_idx] <- plrt_A_crp_os$p_value
    results_A_os$BH_adj_p[crp_idx] <- bh_adjusted["CRP_OS"]
  }
  if (length(tlr_idx) > 0) {
    results_A_os$PLRT_p[tlr_idx] <- plrt_A_tlr_os$p_value
    results_A_os$BH_adj_p[tlr_idx] <- bh_adjusted["TLR_OS"]
  }
  if (length(tmb_idx) > 0) {
    results_A_os$PLRT_p[tmb_idx] <- plrt_A_tmb_os$p_value
    results_A_os$BH_adj_p[tmb_idx] <- bh_adjusted["TMB_OS"]
  }

  # Format for display
  display_A_os <- results_A_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(PLRT_p),
      BH_adj_p = format_pvalue(BH_adj_p)
    ) %>%
    select(Term, HR_CI, PLRT_p, BH_adj_p)

  display_A_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value", "BH-adjusted p"),
          caption = "Model A Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment × Biomarker Interactions", 1, 3, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 4, nrow(display_A_os), bold = TRUE)
}
```

### Progression-Free Survival (Model A)

```{r table-A-pfs}
if (!is.null(results_A_pfs)) {
  # Add PLRT p-values for interaction terms
  results_A_pfs$PLRT_p <- NA
  results_A_pfs$BH_adj_p <- NA

  crp_idx <- grep("crp_num.*Rx|Rx.*crp_num", results_A_pfs$Term)
  tlr_idx <- grep("tlr_num.*Rx|Rx.*tlr_num", results_A_pfs$Term)
  tmb_idx <- grep("tmb_braf_num.*Rx|Rx.*tmb_braf_num", results_A_pfs$Term)

  if (length(crp_idx) > 0) {
    results_A_pfs$PLRT_p[crp_idx] <- plrt_A_crp_pfs$p_value
    results_A_pfs$BH_adj_p[crp_idx] <- bh_adjusted["CRP_PFS"]
  }
  if (length(tlr_idx) > 0) {
    results_A_pfs$PLRT_p[tlr_idx] <- plrt_A_tlr_pfs$p_value
    results_A_pfs$BH_adj_p[tlr_idx] <- bh_adjusted["TLR_PFS"]
  }
  if (length(tmb_idx) > 0) {
    results_A_pfs$PLRT_p[tmb_idx] <- plrt_A_tmb_pfs$p_value
    results_A_pfs$BH_adj_p[tmb_idx] <- bh_adjusted["TMB_PFS"]
  }

  display_A_pfs <- results_A_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(PLRT_p),
      BH_adj_p = format_pvalue(BH_adj_p)
    ) %>%
    select(Term, HR_CI, PLRT_p, BH_adj_p)

  display_A_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value", "BH-adjusted p"),
          caption = "Model A Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment × Biomarker Interactions", 1, 3, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 4, nrow(display_A_pfs), bold = TRUE)
}
```

\newpage

## Model B: Focused Models

These models include CRP and TMB/BRAF as main effects plus BOTH treatment-biomarker interactions (crp:Rx and tmb_braf:Rx). TLR is excluded from Model B. This shared formula provides estimates for how each biomarker modifies treatment effect while adjusting for the other.

```{r table-B-summary}
# Extract interaction HRs from Model B
get_interaction_hr <- function(results_df, pattern) {
  if (is.null(results_df)) return(list(HR = NA, CI_Lower = NA, CI_Upper = NA))
  idx <- grep(pattern, results_df$Term)
  if (length(idx) == 0) return(list(HR = NA, CI_Lower = NA, CI_Upper = NA))
  list(HR = results_df$HR[idx[1]],
       CI_Lower = results_df$CI_Lower[idx[1]],
       CI_Upper = results_df$CI_Upper[idx[1]])
}

# OS results (Model B excludes TLR)
hr_B_crp_os <- get_interaction_hr(results_B_crp_os, "crp_num.*Rx|Rx.*crp_num")
hr_B_tmb_os <- get_interaction_hr(results_B_tmb_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# PFS results (Model B excludes TLR)
hr_B_crp_pfs <- get_interaction_hr(results_B_crp_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_B_tmb_pfs <- get_interaction_hr(results_B_tmb_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# NOTE: Model B excludes TLR - only CRP and TMB/BRAF interactions
model_B_summary <- data.frame(
  Biomarker = c("CRP × Treatment", "TMB/BRAF × Treatment"),
  HR_OS = c(
    format_hr_ci(hr_B_crp_os$HR, hr_B_crp_os$CI_Lower, hr_B_crp_os$CI_Upper),
    format_hr_ci(hr_B_tmb_os$HR, hr_B_tmb_os$CI_Lower, hr_B_tmb_os$CI_Upper)
  ),
  P_OS = c(
    format_pvalue(plrt_B_crp_os$p_value),
    format_pvalue(plrt_B_tmb_os$p_value)
  ),
  HR_PFS = c(
    format_hr_ci(hr_B_crp_pfs$HR, hr_B_crp_pfs$CI_Lower, hr_B_crp_pfs$CI_Upper),
    format_hr_ci(hr_B_tmb_pfs$HR, hr_B_tmb_pfs$CI_Lower, hr_B_tmb_pfs$CI_Upper)
  ),
  P_PFS = c(
    format_pvalue(plrt_B_crp_pfs$p_value),
    format_pvalue(plrt_B_tmb_pfs$p_value)
  )
)

model_B_summary %>%
  kable(col.names = c("Interaction Term", "HR (95% CI)", "PLRT p", "HR (95% CI)", "PLRT p"),
        caption = "Model B: Focused Models - Treatment × Biomarker Interaction Summary",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  add_header_above(c(" " = 1, "Overall Survival" = 2, "Progression-Free Survival" = 2))
```

**Note:** Model B uses a shared formula with CRP and TMB/BRAF as main effects plus BOTH interaction terms (crp:Rx and tmb_braf:Rx). TLR is excluded from Model B.

\newpage

### Full Coefficient Tables

```{r table-B-crp-os}
if (!is.null(results_B_crp_os)) {
  display_B_crp_os <- results_B_crp_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_crp_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B CRP-Focused: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-crp-pfs}
if (!is.null(results_B_crp_pfs)) {
  display_B_crp_pfs <- results_B_crp_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_crp_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B CRP-Focused: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

<!-- Model B excludes TLR - no B-TLR tables needed -->

```{r table-B-tmb-os}
if (!is.null(results_B_tmb_os)) {
  display_B_tmb_os <- results_B_tmb_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_tmb_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B TMB/BRAF-Focused: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-tmb-pfs}
if (!is.null(results_B_tmb_pfs)) {
  display_B_tmb_pfs <- results_B_tmb_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_tmb_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B TMB/BRAF-Focused: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

## Model C: Single-Biomarker Models

These models include only ONE biomarker and its treatment interaction. This is the simplest specification but does not control for other biomarkers.

```{r table-C-summary}
# Extract interaction HRs from Model C
hr_C_crp_os <- get_interaction_hr(results_C_crp_os, "crp_num.*Rx|Rx.*crp_num")
hr_C_tlr_os <- get_interaction_hr(results_C_tlr_os, "tlr_num.*Rx|Rx.*tlr_num")
hr_C_tmb_os <- get_interaction_hr(results_C_tmb_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

hr_C_crp_pfs <- get_interaction_hr(results_C_crp_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_C_tlr_pfs <- get_interaction_hr(results_C_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")
hr_C_tmb_pfs <- get_interaction_hr(results_C_tmb_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

model_C_summary <- data.frame(
  Biomarker = c("CRP × Treatment", "TLR × Treatment", "TMB/BRAF × Treatment"),
  HR_OS = c(
    format_hr_ci(hr_C_crp_os$HR, hr_C_crp_os$CI_Lower, hr_C_crp_os$CI_Upper),
    format_hr_ci(hr_C_tlr_os$HR, hr_C_tlr_os$CI_Lower, hr_C_tlr_os$CI_Upper),
    format_hr_ci(hr_C_tmb_os$HR, hr_C_tmb_os$CI_Lower, hr_C_tmb_os$CI_Upper)
  ),
  P_OS = c(
    format_pvalue(plrt_C_crp_os$p_value),
    format_pvalue(plrt_C_tlr_os$p_value),
    format_pvalue(plrt_C_tmb_os$p_value)
  ),
  HR_PFS = c(
    format_hr_ci(hr_C_crp_pfs$HR, hr_C_crp_pfs$CI_Lower, hr_C_crp_pfs$CI_Upper),
    format_hr_ci(hr_C_tlr_pfs$HR, hr_C_tlr_pfs$CI_Lower, hr_C_tlr_pfs$CI_Upper),
    format_hr_ci(hr_C_tmb_pfs$HR, hr_C_tmb_pfs$CI_Lower, hr_C_tmb_pfs$CI_Upper)
  ),
  P_PFS = c(
    format_pvalue(plrt_C_crp_pfs$p_value),
    format_pvalue(plrt_C_tlr_pfs$p_value),
    format_pvalue(plrt_C_tmb_pfs$p_value)
  )
)

model_C_summary %>%
  kable(col.names = c("Interaction Term", "HR (95% CI)", "PLRT p", "HR (95% CI)", "PLRT p"),
        caption = "Model C: Single-Biomarker Models - Treatment × Biomarker Interaction Summary",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  add_header_above(c(" " = 1, "Overall Survival" = 2, "Progression-Free Survival" = 2))
```

**Note:** Each row represents a separate model with only that biomarker and its interaction (no other biomarkers included).

\newpage

### Full Coefficient Tables

```{r table-C-crp-os}
if (!is.null(results_C_crp_os)) {
  display_C_crp_os <- results_C_crp_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_crp_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C CRP-Only: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-crp-pfs}
if (!is.null(results_C_crp_pfs)) {
  display_C_crp_pfs <- results_C_crp_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_crp_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C CRP-Only: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tlr-os}
if (!is.null(results_C_tlr_os)) {
  display_C_tlr_os <- results_C_tlr_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TLR-Only: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tlr-pfs}
if (!is.null(results_C_tlr_pfs)) {
  display_C_tlr_pfs <- results_C_tlr_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TLR-Only: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tmb-os}
if (!is.null(results_C_tmb_os)) {
  display_C_tmb_os <- results_C_tmb_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tmb_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TMB/BRAF-Only: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tmb-pfs}
if (!is.null(results_C_tmb_pfs)) {
  display_C_tmb_pfs <- results_C_tmb_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tmb_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TMB/BRAF-Only: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

# Model Comparison

## Summary: Interaction HRs Across Model Types

```{r comparison-table-os}
# Get Model A interaction HRs
hr_A_crp_os <- get_interaction_hr(results_A_os, "crp_num.*Rx|Rx.*crp_num")
hr_A_tlr_os <- get_interaction_hr(results_A_os, "tlr_num.*Rx|Rx.*tlr_num")
hr_A_tmb_os <- get_interaction_hr(results_A_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# NOTE: Model B excludes TLR - show N/A for TLR row
comparison_os <- data.frame(
  Biomarker = c("CRP × Rx", "TLR × Rx", "TMB/BRAF × Rx"),
  Model_A = c(
    format_hr_ci(hr_A_crp_os$HR, hr_A_crp_os$CI_Lower, hr_A_crp_os$CI_Upper),
    format_hr_ci(hr_A_tlr_os$HR, hr_A_tlr_os$CI_Lower, hr_A_tlr_os$CI_Upper),
    format_hr_ci(hr_A_tmb_os$HR, hr_A_tmb_os$CI_Lower, hr_A_tmb_os$CI_Upper)
  ),
  Model_B = c(
    format_hr_ci(hr_B_crp_os$HR, hr_B_crp_os$CI_Lower, hr_B_crp_os$CI_Upper),
    "N/A",  # Model B excludes TLR
    format_hr_ci(hr_B_tmb_os$HR, hr_B_tmb_os$CI_Lower, hr_B_tmb_os$CI_Upper)
  ),
  Model_C = c(
    format_hr_ci(hr_C_crp_os$HR, hr_C_crp_os$CI_Lower, hr_C_crp_os$CI_Upper),
    format_hr_ci(hr_C_tlr_os$HR, hr_C_tlr_os$CI_Lower, hr_C_tlr_os$CI_Upper),
    format_hr_ci(hr_C_tmb_os$HR, hr_C_tmb_os$CI_Lower, hr_C_tmb_os$CI_Upper)
  )
)

comparison_os %>%
  kable(col.names = c("Interaction", "Model A", "Model B", "Model C"),
        caption = "Overall Survival: Treatment × Biomarker Interactions Across Model Types",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Model A: All-in-one; Model B: Focused (TLR excluded); Model C: Single biomarker.",
           footnote_as_chunk = TRUE)
```

```{r comparison-table-pfs}
hr_A_crp_pfs <- get_interaction_hr(results_A_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_A_tlr_pfs <- get_interaction_hr(results_A_pfs, "tlr_num.*Rx|Rx.*tlr_num")
hr_A_tmb_pfs <- get_interaction_hr(results_A_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# NOTE: Model B excludes TLR - show N/A for TLR row
comparison_pfs <- data.frame(
  Biomarker = c("CRP × Rx", "TLR × Rx", "TMB/BRAF × Rx"),
  Model_A = c(
    format_hr_ci(hr_A_crp_pfs$HR, hr_A_crp_pfs$CI_Lower, hr_A_crp_pfs$CI_Upper),
    format_hr_ci(hr_A_tlr_pfs$HR, hr_A_tlr_pfs$CI_Lower, hr_A_tlr_pfs$CI_Upper),
    format_hr_ci(hr_A_tmb_pfs$HR, hr_A_tmb_pfs$CI_Lower, hr_A_tmb_pfs$CI_Upper)
  ),
  Model_B = c(
    format_hr_ci(hr_B_crp_pfs$HR, hr_B_crp_pfs$CI_Lower, hr_B_crp_pfs$CI_Upper),
    "N/A",  # Model B excludes TLR
    format_hr_ci(hr_B_tmb_pfs$HR, hr_B_tmb_pfs$CI_Lower, hr_B_tmb_pfs$CI_Upper)
  ),
  Model_C = c(
    format_hr_ci(hr_C_crp_pfs$HR, hr_C_crp_pfs$CI_Lower, hr_C_crp_pfs$CI_Upper),
    format_hr_ci(hr_C_tlr_pfs$HR, hr_C_tlr_pfs$CI_Lower, hr_C_tlr_pfs$CI_Upper),
    format_hr_ci(hr_C_tmb_pfs$HR, hr_C_tmb_pfs$CI_Lower, hr_C_tmb_pfs$CI_Upper)
  )
)

comparison_pfs %>%
  kable(col.names = c("Interaction", "Model A", "Model B", "Model C"),
        caption = "Progression-Free Survival: Treatment × Biomarker Interactions Across Model Types",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Model A: All-in-one; Model B: Focused (TLR excluded); Model C: Single biomarker.",
           footnote_as_chunk = TRUE)
```

\newpage

## Forest Plots

```{r forest-plot-os, fig.height=5, fig.width=9}
# Prepare data for forest plot - OS
# NOTE: Model B excludes TLR - use NA for Model B TLR entries
forest_data_os <- data.frame(
  Biomarker = rep(c("CRP", "TLR", "TMB/BRAF"), 3),
  Model = rep(c("A: All-in-One", "B: Focused", "C: Single"), each = 3),
  HR = c(
    hr_A_crp_os$HR, hr_A_tlr_os$HR, hr_A_tmb_os$HR,
    hr_B_crp_os$HR, NA, hr_B_tmb_os$HR,  # Model B excludes TLR
    hr_C_crp_os$HR, hr_C_tlr_os$HR, hr_C_tmb_os$HR
  ),
  CI_Lower = c(
    hr_A_crp_os$CI_Lower, hr_A_tlr_os$CI_Lower, hr_A_tmb_os$CI_Lower,
    hr_B_crp_os$CI_Lower, NA, hr_B_tmb_os$CI_Lower,  # Model B excludes TLR
    hr_C_crp_os$CI_Lower, hr_C_tlr_os$CI_Lower, hr_C_tmb_os$CI_Lower
  ),
  CI_Upper = c(
    hr_A_crp_os$CI_Upper, hr_A_tlr_os$CI_Upper, hr_A_tmb_os$CI_Upper,
    hr_B_crp_os$CI_Upper, NA, hr_B_tmb_os$CI_Upper,  # Model B excludes TLR
    hr_C_crp_os$CI_Upper, hr_C_tlr_os$CI_Upper, hr_C_tmb_os$CI_Upper
  )
)

# Remove NA values (includes Model B TLR which is excluded)
forest_data_os <- forest_data_os[complete.cases(forest_data_os), ]

if (nrow(forest_data_os) > 0) {
  create_interaction_forest_plot(forest_data_os, "Overall Survival")
}
```

```{r forest-plot-pfs, fig.height=5, fig.width=9}
# Prepare data for forest plot - PFS
# NOTE: Model B excludes TLR - use NA for Model B TLR entries
forest_data_pfs <- data.frame(
  Biomarker = rep(c("CRP", "TLR", "TMB/BRAF"), 3),
  Model = rep(c("A: All-in-One", "B: Focused", "C: Single"), each = 3),
  HR = c(
    hr_A_crp_pfs$HR, hr_A_tlr_pfs$HR, hr_A_tmb_pfs$HR,
    hr_B_crp_pfs$HR, NA, hr_B_tmb_pfs$HR,  # Model B excludes TLR
    hr_C_crp_pfs$HR, hr_C_tlr_pfs$HR, hr_C_tmb_pfs$HR
  ),
  CI_Lower = c(
    hr_A_crp_pfs$CI_Lower, hr_A_tlr_pfs$CI_Lower, hr_A_tmb_pfs$CI_Lower,
    hr_B_crp_pfs$CI_Lower, NA, hr_B_tmb_pfs$CI_Lower,  # Model B excludes TLR
    hr_C_crp_pfs$CI_Lower, hr_C_tlr_pfs$CI_Lower, hr_C_tmb_pfs$CI_Lower
  ),
  CI_Upper = c(
    hr_A_crp_pfs$CI_Upper, hr_A_tlr_pfs$CI_Upper, hr_A_tmb_pfs$CI_Upper,
    hr_B_crp_pfs$CI_Upper, NA, hr_B_tmb_pfs$CI_Upper,  # Model B excludes TLR
    hr_C_crp_pfs$CI_Upper, hr_C_tlr_pfs$CI_Upper, hr_C_tmb_pfs$CI_Upper
  )
)

# Remove NA values (includes Model B TLR which is excluded)
forest_data_pfs <- forest_data_pfs[complete.cases(forest_data_pfs), ]

if (nrow(forest_data_pfs) > 0) {
  create_interaction_forest_plot(forest_data_pfs, "Progression-Free Survival")
}
```

**Interpretation:** HR < 1 indicates that biomarker-positive patients derive greater benefit from experimental treatment (reduced hazard of death/progression). The dashed vertical line at HR = 1 represents no differential treatment effect by biomarker status.

\newpage

# Sensitivity Analysis: Ridge Regression

Ridge regression (alpha = 0) shrinks coefficients toward zero but does not eliminate any, providing a sensitivity analysis for the stability of our interaction estimates.

```{r ridge-regression, include=FALSE}
# =============================================================================
# RIDGE REGRESSION SENSITIVITY ANALYSIS
# =============================================================================

# Extract ridge results helper function
extract_ridge_interaction <- function(model_or_coef, term_pattern, is_glmnet = FALSE) {
  if (is_glmnet) {
    if (is.null(model_or_coef)) return(list(HR = NA, SE = NA))
    coef_vec <- as.vector(model_or_coef)
    names(coef_vec) <- rownames(model_or_coef)
    idx <- grep(term_pattern, names(coef_vec))
    if (length(idx) == 0) return(list(HR = NA, SE = NA))
    return(list(HR = exp(coef_vec[idx[1]]), SE = NA))  # No SE from glmnet
  } else {
    if (is.null(model_or_coef)) return(list(HR = NA, SE = NA))
    summ <- summary(model_or_coef)
    coef_table <- summ$coefficients
    idx <- grep(term_pattern, rownames(coef_table))
    if (length(idx) == 0) return(list(HR = NA, SE = NA))
    return(list(HR = exp(coef_table[idx[1], "coef"]),
                SE = coef_table[idx[1], "se(coef)"]))
  }
}

# =============================================================================
# MODEL A: All-in-One (all biomarkers + all interactions)
# =============================================================================

tryCatch({
  ridge_A_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(crp_num, tlr_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_A_os_success <- TRUE
}, error = function(e) {
  ridge_A_os_success <<- FALSE
  ridge_A_os <<- NULL
})

tryCatch({
  ridge_A_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(crp_num, tlr_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_A_pfs_success <- TRUE
}, error = function(e) {
  ridge_A_pfs_success <<- FALSE
  ridge_A_pfs <<- NULL
})

# Extract Model A interaction estimates
# Note: survival::ridge() truncates coefficient names, so use shorter patterns
if (exists("ridge_A_os") && !is.null(ridge_A_os)) {
  ridge_A_crp_os <- extract_ridge_interaction(ridge_A_os, "crp.*Rx|Rx.*crp")
  ridge_A_tlr_os <- extract_ridge_interaction(ridge_A_os, "tlr.*Rx|Rx.*tlr")
  ridge_A_tmb_os <- extract_ridge_interaction(ridge_A_os, "tmb.*Rx|Rx.*tmb")
} else {
  ridge_A_crp_os <- ridge_A_tlr_os <- ridge_A_tmb_os <- list(HR = NA, SE = NA)
}

if (exists("ridge_A_pfs") && !is.null(ridge_A_pfs)) {
  ridge_A_crp_pfs <- extract_ridge_interaction(ridge_A_pfs, "crp.*Rx|Rx.*crp")
  ridge_A_tlr_pfs <- extract_ridge_interaction(ridge_A_pfs, "tlr.*Rx|Rx.*tlr")
  ridge_A_tmb_pfs <- extract_ridge_interaction(ridge_A_pfs, "tmb.*Rx|Rx.*tmb")
} else {
  ridge_A_crp_pfs <- ridge_A_tlr_pfs <- ridge_A_tmb_pfs <- list(HR = NA, SE = NA)
}

# =============================================================================
# MODEL B: Focused (CRP + TMB/BRAF + BOTH interactions, TLR excluded)
# =============================================================================
# NOTE: Model B uses a shared formula with CRP and TMB/BRAF as main effects
# plus BOTH interaction terms. TLR is excluded from Model B.

# Shared formula for Model B (CRP and TMB only, both interactions)
tryCatch({
  ridge_B_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(crp_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_B_os_success <- TRUE
}, error = function(e) {
  ridge_B_os_success <<- FALSE
  ridge_B_os <<- NULL
})

tryCatch({
  ridge_B_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(crp_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_B_pfs_success <- TRUE
}, error = function(e) {
  ridge_B_pfs_success <<- FALSE
  ridge_B_pfs <<- NULL
})

# Extract Model B interaction estimates (using shorter patterns for truncated names)
# CRP interaction from shared Model B
ridge_B_crp_os_hr <- if (exists("ridge_B_os") && !is.null(ridge_B_os)) {
  extract_ridge_interaction(ridge_B_os, "crp.*Rx|Rx.*crp")
} else { list(HR = NA, SE = NA) }

ridge_B_crp_pfs_hr <- if (exists("ridge_B_pfs") && !is.null(ridge_B_pfs)) {
  extract_ridge_interaction(ridge_B_pfs, "crp.*Rx|Rx.*crp")
} else { list(HR = NA, SE = NA) }

# TMB interaction from shared Model B
ridge_B_tmb_os_hr <- if (exists("ridge_B_os") && !is.null(ridge_B_os)) {
  extract_ridge_interaction(ridge_B_os, "tmb.*Rx|Rx.*tmb")
} else { list(HR = NA, SE = NA) }

ridge_B_tmb_pfs_hr <- if (exists("ridge_B_pfs") && !is.null(ridge_B_pfs)) {
  extract_ridge_interaction(ridge_B_pfs, "tmb.*Rx|Rx.*tmb")
} else { list(HR = NA, SE = NA) }

# =============================================================================
# MODEL C: Single-Biomarker (one biomarker + its interaction)
# =============================================================================

# CRP-only
tryCatch({
  ridge_C_crp_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(crp_num, theta = 1, scale = TRUE) +
      crp_num:Rx,
    data = data_complete
  )
  ridge_C_crp_os_success <- TRUE
}, error = function(e) {
  ridge_C_crp_os_success <<- FALSE
  ridge_C_crp_os <<- NULL
})

tryCatch({
  ridge_C_crp_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(crp_num, theta = 1, scale = TRUE) +
      crp_num:Rx,
    data = data_complete
  )
  ridge_C_crp_pfs_success <- TRUE
}, error = function(e) {
  ridge_C_crp_pfs_success <<- FALSE
  ridge_C_crp_pfs <<- NULL
})

# TLR-only
tryCatch({
  ridge_C_tlr_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(tlr_num, theta = 1, scale = TRUE) +
      tlr_num:Rx,
    data = data_complete
  )
  ridge_C_tlr_os_success <- TRUE
}, error = function(e) {
  ridge_C_tlr_os_success <<- FALSE
  ridge_C_tlr_os <<- NULL
})

tryCatch({
  ridge_C_tlr_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(tlr_num, theta = 1, scale = TRUE) +
      tlr_num:Rx,
    data = data_complete
  )
  ridge_C_tlr_pfs_success <- TRUE
}, error = function(e) {
  ridge_C_tlr_pfs_success <<- FALSE
  ridge_C_tlr_pfs <<- NULL
})

# TMB/BRAF-only
tryCatch({
  ridge_C_tmb_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(tmb_braf_num, theta = 1, scale = TRUE) +
      tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_C_tmb_os_success <- TRUE
}, error = function(e) {
  ridge_C_tmb_os_success <<- FALSE
  ridge_C_tmb_os <<- NULL
})

tryCatch({
  ridge_C_tmb_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(tmb_braf_num, theta = 1, scale = TRUE) +
      tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_C_tmb_pfs_success <- TRUE
}, error = function(e) {
  ridge_C_tmb_pfs_success <<- FALSE
  ridge_C_tmb_pfs <<- NULL
})

# Extract Model C interaction estimates (using shorter patterns for truncated names)
ridge_C_crp_os_hr <- if (exists("ridge_C_crp_os") && !is.null(ridge_C_crp_os)) {
  extract_ridge_interaction(ridge_C_crp_os, "crp.*Rx|Rx.*crp")
} else { list(HR = NA, SE = NA) }

ridge_C_crp_pfs_hr <- if (exists("ridge_C_crp_pfs") && !is.null(ridge_C_crp_pfs)) {
  extract_ridge_interaction(ridge_C_crp_pfs, "crp.*Rx|Rx.*crp")
} else { list(HR = NA, SE = NA) }

ridge_C_tlr_os_hr <- if (exists("ridge_C_tlr_os") && !is.null(ridge_C_tlr_os)) {
  extract_ridge_interaction(ridge_C_tlr_os, "tlr.*Rx|Rx.*tlr")
} else { list(HR = NA, SE = NA) }

ridge_C_tlr_pfs_hr <- if (exists("ridge_C_tlr_pfs") && !is.null(ridge_C_tlr_pfs)) {
  extract_ridge_interaction(ridge_C_tlr_pfs, "tlr.*Rx|Rx.*tlr")
} else { list(HR = NA, SE = NA) }

ridge_C_tmb_os_hr <- if (exists("ridge_C_tmb_os") && !is.null(ridge_C_tmb_os)) {
  extract_ridge_interaction(ridge_C_tmb_os, "tmb.*Rx|Rx.*tmb")
} else { list(HR = NA, SE = NA) }

ridge_C_tmb_pfs_hr <- if (exists("ridge_C_tmb_pfs") && !is.null(ridge_C_tmb_pfs)) {
  extract_ridge_interaction(ridge_C_tmb_pfs, "tmb.*Rx|Rx.*tmb")
} else { list(HR = NA, SE = NA) }
```

```{r table-ridge-os}
# Format ridge HR (with SE if available)
format_ridge_hr <- function(hr, se) {
  if (is.na(hr)) return("--")
  if (is.na(se)) {
    sprintf("%.2f", hr)
  } else {
    sprintf("%.2f (SE: %.2f)", hr, se)
  }
}

# Overall Survival comparison - All three model types
# NOTE: Model B excludes TLR - show N/A for TLR row
ridge_comparison_os <- data.frame(
  Biomarker = c("CRP x Rx", "TLR x Rx", "TMB/BRAF x Rx"),
  Firth_A = c(
    format_hr_ci(hr_A_crp_os$HR, hr_A_crp_os$CI_Lower, hr_A_crp_os$CI_Upper),
    format_hr_ci(hr_A_tlr_os$HR, hr_A_tlr_os$CI_Lower, hr_A_tlr_os$CI_Upper),
    format_hr_ci(hr_A_tmb_os$HR, hr_A_tmb_os$CI_Lower, hr_A_tmb_os$CI_Upper)
  ),
  Ridge_A = c(
    format_ridge_hr(ridge_A_crp_os$HR, ridge_A_crp_os$SE),
    format_ridge_hr(ridge_A_tlr_os$HR, ridge_A_tlr_os$SE),
    format_ridge_hr(ridge_A_tmb_os$HR, ridge_A_tmb_os$SE)
  ),
  Firth_B = c(
    format_hr_ci(hr_B_crp_os$HR, hr_B_crp_os$CI_Lower, hr_B_crp_os$CI_Upper),
    "N/A",  # Model B excludes TLR
    format_hr_ci(hr_B_tmb_os$HR, hr_B_tmb_os$CI_Lower, hr_B_tmb_os$CI_Upper)
  ),
  Ridge_B = c(
    format_ridge_hr(ridge_B_crp_os_hr$HR, ridge_B_crp_os_hr$SE),
    "N/A",  # Model B excludes TLR
    format_ridge_hr(ridge_B_tmb_os_hr$HR, ridge_B_tmb_os_hr$SE)
  ),
  Firth_C = c(
    format_hr_ci(hr_C_crp_os$HR, hr_C_crp_os$CI_Lower, hr_C_crp_os$CI_Upper),
    format_hr_ci(hr_C_tlr_os$HR, hr_C_tlr_os$CI_Lower, hr_C_tlr_os$CI_Upper),
    format_hr_ci(hr_C_tmb_os$HR, hr_C_tmb_os$CI_Lower, hr_C_tmb_os$CI_Upper)
  ),
  Ridge_C = c(
    format_ridge_hr(ridge_C_crp_os_hr$HR, ridge_C_crp_os_hr$SE),
    format_ridge_hr(ridge_C_tlr_os_hr$HR, ridge_C_tlr_os_hr$SE),
    format_ridge_hr(ridge_C_tmb_os_hr$HR, ridge_C_tmb_os_hr$SE)
  )
)

ridge_comparison_os %>%
  kable(col.names = c("Interaction", "Firth", "Ridge", "Firth", "Ridge", "Firth", "Ridge"),
        caption = "Overall Survival: Firth-Corrected vs Ridge Regression Across Model Types",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, "Model A (All-in-One)" = 2, "Model B (Focused)" = 2, "Model C (Single)" = 2)) %>%
  footnote(general = "Firth columns show HR (95% CI); Ridge columns show point estimates only.",
           footnote_as_chunk = TRUE)
```

```{r table-ridge-pfs}
# Progression-Free Survival comparison - All three model types
# NOTE: Model B excludes TLR - show N/A for TLR row
ridge_comparison_pfs <- data.frame(
  Biomarker = c("CRP x Rx", "TLR x Rx", "TMB/BRAF x Rx"),
  Firth_A = c(
    format_hr_ci(hr_A_crp_pfs$HR, hr_A_crp_pfs$CI_Lower, hr_A_crp_pfs$CI_Upper),
    format_hr_ci(hr_A_tlr_pfs$HR, hr_A_tlr_pfs$CI_Lower, hr_A_tlr_pfs$CI_Upper),
    format_hr_ci(hr_A_tmb_pfs$HR, hr_A_tmb_pfs$CI_Lower, hr_A_tmb_pfs$CI_Upper)
  ),
  Ridge_A = c(
    format_ridge_hr(ridge_A_crp_pfs$HR, ridge_A_crp_pfs$SE),
    format_ridge_hr(ridge_A_tlr_pfs$HR, ridge_A_tlr_pfs$SE),
    format_ridge_hr(ridge_A_tmb_pfs$HR, ridge_A_tmb_pfs$SE)
  ),
  Firth_B = c(
    format_hr_ci(hr_B_crp_pfs$HR, hr_B_crp_pfs$CI_Lower, hr_B_crp_pfs$CI_Upper),
    "N/A",  # Model B excludes TLR
    format_hr_ci(hr_B_tmb_pfs$HR, hr_B_tmb_pfs$CI_Lower, hr_B_tmb_pfs$CI_Upper)
  ),
  Ridge_B = c(
    format_ridge_hr(ridge_B_crp_pfs_hr$HR, ridge_B_crp_pfs_hr$SE),
    "N/A",  # Model B excludes TLR
    format_ridge_hr(ridge_B_tmb_pfs_hr$HR, ridge_B_tmb_pfs_hr$SE)
  ),
  Firth_C = c(
    format_hr_ci(hr_C_crp_pfs$HR, hr_C_crp_pfs$CI_Lower, hr_C_crp_pfs$CI_Upper),
    format_hr_ci(hr_C_tlr_pfs$HR, hr_C_tlr_pfs$CI_Lower, hr_C_tlr_pfs$CI_Upper),
    format_hr_ci(hr_C_tmb_pfs$HR, hr_C_tmb_pfs$CI_Lower, hr_C_tmb_pfs$CI_Upper)
  ),
  Ridge_C = c(
    format_ridge_hr(ridge_C_crp_pfs_hr$HR, ridge_C_crp_pfs_hr$SE),
    format_ridge_hr(ridge_C_tlr_pfs_hr$HR, ridge_C_tlr_pfs_hr$SE),
    format_ridge_hr(ridge_C_tmb_pfs_hr$HR, ridge_C_tmb_pfs_hr$SE)
  )
)

ridge_comparison_pfs %>%
  kable(col.names = c("Interaction", "Firth", "Ridge", "Firth", "Ridge", "Firth", "Ridge"),
        caption = "Progression-Free Survival: Firth-Corrected vs Ridge Regression Across Model Types",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, "Model A (All-in-One)" = 2, "Model B (Focused)" = 2, "Model C (Single)" = 2)) %>%
  footnote(general = "Firth columns show HR (95% CI); Ridge columns show point estimates only.",
           footnote_as_chunk = TRUE)
```

**Interpretation:** Ridge regression applies an L2 penalty that shrinks all coefficients toward zero (HR toward 1.0), providing a sensitivity analysis for estimate stability across three model structures:

- **Model A (All-in-One)**: Ridge regularizes all three biomarker main effects simultaneously while estimating all three interactions. This tests whether interaction estimates are stable when accounting for multicollinearity among biomarkers.

- **Model B (Focused)**: Ridge regularizes all biomarker main effects but only one interaction is estimated per model. Comparing Model B Ridge to Model A Ridge reveals whether regularization effects differ when fewer interaction terms compete for variance.

- **Model C (Single-Biomarker)**: Ridge regularizes only one biomarker term per model. Since there is minimal multicollinearity to address, Model C Ridge estimates should be closest to their Firth counterparts. Substantial shrinkage here would indicate instability in the biomarker-treatment relationship itself, not confounding.

**Key patterns to examine**: (1) Consistent shrinkage across all three models suggests the interaction estimate is inherently unstable; (2) Shrinkage only in Model A suggests multicollinearity with other biomarkers; (3) Similar Firth and Ridge estimates across all models supports robustness.

\newpage

# Summary

This analysis evaluated treatment effect heterogeneity across three candidate predictive biomarkers (CRP, TLR, TMB/BRAF) using Firth-corrected Cox regression with profile likelihood confidence intervals and penalized likelihood ratio tests.

**Key Findings:**

1. **Model Robustness:** Treatment-biomarker interaction estimates were compared across three model specifications (all-in-one, focused, single-biomarker) to assess sensitivity to model structure.

2. **Multiple Testing:** Benjamini-Hochberg correction was applied to control the false discovery rate across the 6 primary interaction tests (3 biomarkers × 2 outcomes).

3. **Proportional Hazards:** The PH assumption was assessed using Schoenfeld residual tests and log-log survival plots. For overall survival, no significant PH violations were detected. For progression-free survival, significant violations were observed for TMB/BRAF main effect (p = 0.004) and TMB/BRAF × Rx interaction (p = 0.009), with the global test also significant (p = 0.004). These findings suggest time-varying effects for TMB/BRAF-related terms in PFS models, warranting caution in interpretation. The log-log plots show some crossing of survival curves for the treatment comparison, consistent with potential non-proportional hazards.

4. **Sensitivity Analysis (Ridge Regression):** Ridge regression was applied to all three model structures (A, B, C) to assess estimate stability. This comprehensive comparison reveals whether shrinkage patterns are consistent across model specifications or driven by specific modeling choices:
   - Consistent shrinkage across all three models suggests inherent instability in the interaction estimate
   - Shrinkage only in Model A (all-in-one) suggests multicollinearity with other biomarkers
   - Model C (single-biomarker) provides the most direct biomarker-treatment estimate with minimal confounding

   Both methods answer different questions: Firth provides the best point estimate given the data structure, while Ridge prioritizes predictive stability. Comparing patterns across models helps distinguish true effect instability from model-specific artifacts.

**Methodological Note:** The use of Firth-corrected Cox regression addresses potential monotone likelihood issues and small sample bias. Profile likelihood-based confidence intervals and penalized likelihood ratio tests are more appropriate than Wald-based methods in this setting.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.2
