---
title: "Clinical Effectiveness"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Load required libraries and shared Cox extraction helpers.
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("cox_extract"),
  packages = c("here", "knitr", "kableExtra", "ggplot2", "dplyr", "tidyverse",
               "survival", "survminer", "coxphf", "glmnet", "vcd"),
  set_theme = FALSE
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r helper-functions, include=FALSE}
# =============================================================================
# HELPER FUNCTIONS
# =============================================================================

#' Extract results from standard Cox model (full table, interactions grouped at top)
extract_coxph_results <- function(model, reorder_interactions = TRUE) {
  if (is.null(model)) return(NULL)

  model_summary <- summary(model)
  coef_table <- model_summary$coefficients
  conf_table <- model_summary$conf.int

  results <- data.frame(
    Term = rownames(coef_table),
    HR = exp(coef(model)),
    CI_Lower = conf_table[, "lower .95"],
    CI_Upper = conf_table[, "upper .95"],
    P_Value = coef_table[, "Pr(>|z|)"],
    stringsAsFactors = FALSE
  )

  if (reorder_interactions) {
    # Put interaction terms at top
    is_interaction <- grepl(":", results$Term)
    results <- rbind(results[is_interaction, ], results[!is_interaction, ])
  }

  rownames(results) <- NULL
  results
}

#' Apply Benjamini-Hochberg FDR correction
apply_bh_correction <- function(p_values) {
  p.adjust(p_values, method = "BH")
}

#' Format HR with CI for display (vectorized)
format_hr_ci <- function(hr, ci_lower, ci_upper, digits = 2) {
  mapply(function(h, l, u) {
    if (is.na(h)) return("--")
    sprintf(paste0("%.", digits, "f (%.", digits, "f-%.", digits, "f)"), h, l, u)
  }, hr, ci_lower, ci_upper, USE.NAMES = FALSE)
}

#' Build a side-by-side standard Cox vs Firth comparison table
build_std_firth_comparison <- function(std_results, firth_results, row_specs) {
  format_result_cell <- function(results_df, pattern) {
    if (is.null(results_df) || is.null(pattern)) return("--")
    idx <- grep(pattern, results_df$Term)
    if (length(idx) == 0) return("--")
    format_hr_ci(
      results_df$HR[idx[1]],
      results_df$CI_Lower[idx[1]],
      results_df$CI_Upper[idx[1]]
    )
  }

  do.call(rbind, lapply(row_specs, function(rs) {
    data.frame(
      Term = rs$label,
      Standard_Cox = format_result_cell(std_results, rs$std_pat),
      Firth = format_result_cell(firth_results, rs$firth_pat),
      stringsAsFactors = FALSE
    )
  }))
}

#' Render standard Cox vs Firth tables for both PDF and GFM outputs
render_std_firth_comparison_table <- function(comparison_df, caption,
                                             first_group_label, first_group_end,
                                             second_group_label) {
  table_format <- if (knitr::is_latex_output()) "latex" else "pipe"

  comparison_table <- comparison_df %>%
    kable(col.names = c("Term", "Standard Cox HR (95% CI)", "Firth HR (95% CI)"),
          caption = caption, booktabs = TRUE, format = table_format)

  if (knitr::is_latex_output()) {
    comparison_table %>%
      kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
      pack_rows(first_group_label, 1, first_group_end, bold = TRUE) %>%
      pack_rows(second_group_label, first_group_end + 1, nrow(comparison_df), bold = TRUE)
  } else {
    comparison_table
  }
}

#' Format p-value for display (vectorized)
format_pvalue <- function(p, digits = 3) {
  sapply(p, function(pval) {
    if (is.na(pval)) return("--")
    if (pval < 0.001) return("<0.001")
    sprintf(paste0("%.", digits, "f"), pval)
  }, USE.NAMES = FALSE)
}

#' Create forest plot for interaction HRs
create_interaction_forest_plot <- function(results_df, outcome = "OS") {
  ggplot(results_df,
         aes(x = HR, y = Biomarker, color = Model, shape = Model)) +
    geom_point(position = position_dodge(width = 0.5), size = 3) +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper),
                   position = position_dodge(width = 0.5), height = 0.2) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4, 10),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4", "10")) +
    scale_color_manual(
      values = c("A: All-in-One" = "#E69F00",
                 "B: Focused" = "#56B4E9",
                 "C: Single" = "#009E73"),
      name = "Model Type"
    ) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = paste("Treatment × Biomarker Interaction:", outcome),
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

#' Create log-log survival plot for PH diagnostics
create_loglog_plot <- function(data, time_var, event_var, strata_var, title) {
  formula <- as.formula(paste0("Surv(", time_var, ", ", event_var, ") ~ ", strata_var))
  km_fit <- survfit(formula, data = data)

  # Extract survival data
  surv_summary <- summary(km_fit)

  plot_data <- data.frame(
    time = surv_summary$time,
    surv = surv_summary$surv,
    strata = surv_summary$strata
  ) %>%
    filter(surv > 0 & surv < 1) %>%
    mutate(
      log_time = log(time),
      log_log_surv = log(-log(surv))
    )

  ggplot(plot_data, aes(x = log_time, y = log_log_surv, color = strata)) +
    geom_step(linewidth = 1) +
    labs(
      x = "log(Time in weeks)",
      y = "-log(-log(S(t)))",
      title = title,
      subtitle = "Parallel lines support PH assumption",
      color = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

```{r data-preparation, include=FALSE}
# =============================================================================
# DATA PREPARATION
# =============================================================================

# Prepare data for Cox models
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

# Ensure proper factor coding
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)

# Biomarkers as numeric 0/1 for coxphf (interactions work better with numeric)
data_complete$crp_num <- as.numeric(as.character(data_complete$crp))
data_complete$tlr_num <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf_num <- as.numeric(as.character(data_complete$tmb_braf))

# Create numeric Rx for ridge regression
data_complete$Rx_num <- as.numeric(data_complete$Rx) - 1  # 0 = Control, 1 = Experimental

# Sample characteristics
n_total <- nrow(data_complete)
n_control <- sum(data_complete$Rx_num == 0)
n_experimental <- sum(data_complete$Rx_num == 1)

# Biomarker prevalence
prev_crp <- mean(data_complete$crp_num)
prev_tlr <- mean(data_complete$tlr_num)
prev_tmb_braf <- mean(data_complete$tmb_braf_num)

# Event counts
n_deaths <- sum(data_complete$Death)
n_progressions <- sum(data_complete$Progression)
```

```{r biomarker-correlation, include=FALSE}
# =============================================================================
# BIOMARKER CORRELATION ANALYSIS (Cramér's V)
# =============================================================================

# CRP vs TLR
crp_tlr_table <- table(data_complete$crp_num, data_complete$tlr_num)
crp_tlr_assoc <- assocstats(crp_tlr_table)
cramers_v_crp_tlr <- crp_tlr_assoc$cramer

# CRP vs TMB/BRAF
crp_tmb_table <- table(data_complete$crp_num, data_complete$tmb_braf_num)
crp_tmb_assoc <- assocstats(crp_tmb_table)
cramers_v_crp_tmb <- crp_tmb_assoc$cramer

# TLR vs TMB/BRAF
tlr_tmb_table <- table(data_complete$tlr_num, data_complete$tmb_braf_num)
tlr_tmb_assoc <- assocstats(tlr_tmb_table)
cramers_v_tlr_tmb <- tlr_tmb_assoc$cramer

# Build correlation summary
correlation_df <- data.frame(
  Comparison = c("CRP vs TLR", "CRP vs TMB/BRAF", "TLR vs TMB/BRAF"),
  Cramers_V = round(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), 3),
  Interpretation = sapply(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), function(v) {
    if (v > 0.3) "Moderate/Strong"
    else if (v > 0.1) "Weak"
    else "Negligible"
  })
)
```

# Overview

This report presents clinical effectiveness results from the METIMMOX-1 trial, evaluating biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer.

The analysis uses **Firth-corrected Cox proportional hazards regression** with profile likelihood confidence intervals to assess treatment effect heterogeneity across two pre-treatment biomarkers identified by the causal DAG analysis:

- **CRP** (C-reactive protein): Low CRP (<5 mg/L) at baseline — a pre-treatment prognostic and potentially predictive marker
- **TMB/BRAF**: High tumor mutational burden (≥9 mut/MB) or BRAF mutation — a pre-treatment genomic marker

**Model specification is motivated by the causal DAG** (see `dag.qmd` and `dag_associations.qmd`). The DAG encodes treatment (T) as randomized with no parents, so no confounding adjustment is needed for causal identification; Age and Sex are included as precision covariates. TLR (Tumor Lesion Reduction) is encoded as a post-randomization intermediate variable (T → TLR → PFS): it is not a pre-treatment baseline characteristic and conditioning on it as a covariate would block part of the treatment effect pathway. TLR is therefore excluded from the primary survival models and examined separately as a descriptive endpoint.

The **unified DAG-informed model** is:

$$\text{Surv}(\text{time}, \text{event}) \sim \text{Age} + \text{sex} + \text{Rx} + \text{CRP} + \text{TMB/BRAF} + \text{CRP} \times \text{Rx} + \text{TMB/BRAF} \times \text{Rx}$$

Ridge regression (L2-penalized Cox) is applied as a sensitivity analysis to assess the stability of the interaction estimates under shrinkage. TLR is reported in a separate exploratory section.

# Methodological Notes

## Software Packages

This analysis uses the following R packages:

- `coxphf` version `r packageVersion("coxphf")`: Firth-corrected Cox regression with profile likelihood CIs
- `survival` version `r packageVersion("survival")`: Cox regression and Schoenfeld residual diagnostics
- `glmnet` version `r packageVersion("glmnet")`: Ridge regression sensitivity analysis
- `vcd` version `r packageVersion("vcd")`: Cramér's V for biomarker correlation assessment

## Firth-Corrected Cox Regression

We use Firth's penalized maximum likelihood method for Cox regression, which addresses:

1. **Monotone likelihood**: When a covariate perfectly separates events from non-events
2. **Small sample bias**: Reduces bias in coefficient estimates with sparse data
3. **Unstable confidence intervals**: Profile likelihood CIs are more reliable than Wald-based CIs in small samples

Statistical inference is based on **penalized likelihood ratio tests (PLRT)**, which are more appropriate than Wald tests for testing treatment-biomarker interactions in this setting.

## Ridge Regression Sensitivity Analysis

We use Ridge regression as a sensitivity analysis to assess the stability of our interaction estimates. Ridge regression (also called L2-penalized regression or Tikhonov regularization) belongs to the family of regularized or penalized regression methods. In survival analysis, this is implemented as a penalized Cox model.

**How Ridge regression works:**

- Ridge adds a penalty term that discourages large coefficients. The bigger a coefficient tries to get, the more the model resists, pulling estimates toward zero (HR toward 1.0).
- Unlike LASSO (alpha = 1), which sets some coefficients exactly to zero and performs variable selection, Ridge (alpha = 0) shrinks all coefficients but retains all predictors.
- The degree of shrinkage is controlled by the tuning parameter lambda, which is selected via **cross-validation (CV)**: the data are repeatedly split into training and validation sets, and the lambda that produces the best predictive performance is chosen.

**Why not LASSO or Elastic Net?**

We determined that LASSO and elastic net are **not appropriate** for this analysis:

1. **Correlated biomarkers**: LASSO arbitrarily selects one of correlated predictors while setting others to zero, which does not reflect the clinical question of comparing ALL biomarker strategies.

2. **Hierarchy principle violation**: LASSO may select interaction terms (e.g., `crp:Rx`) while setting the main effect (`crp`) to zero, producing models that are difficult to interpret clinically.

3. **Clinical objective**: Our goal is to estimate treatment effect heterogeneity across ALL biomarkers simultaneously, not to select a "winning" biomarker.

Elastic net (alpha = 0.1–0.3) represents a compromise but does not fully address these concerns.

**Interpreting Ridge results:**

Ridge regression is not replacing the Firth estimates—it provides a reality check. When Ridge substantially shrinks an interaction coefficient toward zero while Firth estimates a large effect, this indicates the effect is too unstable to trust for practical use. The CV-selected lambda reflects how much regularization is needed for reasonable out-of-sample prediction given the sample size and collinearity structure.

# Data Preparation

## Sample Characteristics

```{r table-sample}
# Helper: format n (%) with subgroup denominator
fmt_n_pct <- function(n, total, digits = 1) {
  if (is.na(n) || total == 0) return("--")
  sprintf(paste0("%d (%.", digits, "f%%)"), n, 100 * n / total)
}

# Helper: format mean (SD)
fmt_mean_sd <- function(x, digits = 1) {
  if (length(x) == 0 || all(is.na(x))) return("--")
  sprintf(paste0("%.", digits, "f (%.", digits, "f)"),
          mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))
}

# Compute the column of statistics for a given subgroup
build_col <- function(df) {
  n <- nrow(df)
  sex_levels   <- levels(data_complete$sex)
  rx_levels    <- levels(data_complete$Rx)
  n_female     <- sum(df$sex == sex_levels[length(sex_levels)])  # last level (typically Female)
  n_male       <- sum(df$sex == sex_levels[1])
  n_ctrl       <- sum(df$Rx == rx_levels[1])
  n_exp        <- sum(df$Rx == rx_levels[2])
  c(
    as.character(n),
    fmt_mean_sd(df$Age),
    fmt_n_pct(n_male,   n),
    fmt_n_pct(n_female, n),
    fmt_n_pct(n_ctrl,   n),
    fmt_n_pct(n_exp,    n),
    fmt_n_pct(sum(df$Death),       n),
    fmt_n_pct(sum(df$Progression), n),
    fmt_n_pct(sum(df$crp_num),      n),
    fmt_n_pct(sum(df$tlr_num),      n),
    fmt_n_pct(sum(df$tmb_braf_num), n)
  )
}

# Build subgroup data frames
sub_overall <- data_complete
sub_crp_pos <- data_complete[data_complete$crp_num      == 1, ]
sub_crp_neg <- data_complete[data_complete$crp_num      == 0, ]
sub_tlr_pos <- data_complete[data_complete$tlr_num      == 1, ]
sub_tlr_neg <- data_complete[data_complete$tlr_num      == 0, ]
sub_tmb_pos <- data_complete[data_complete$tmb_braf_num == 1, ]
sub_tmb_neg <- data_complete[data_complete$tmb_braf_num == 0, ]

table1_df <- data.frame(
  Characteristic = c(
    "Patients, n",
    "Age, mean (SD)",
    "Male",
    "Female",
    "Control (FLOX alone)",
    "Experimental (FLOX/nivolumab)",
    "Deaths (OS events)",
    "PFS events (progression or death)",
    "CRP-positive (low CRP)",
    "TLR-positive (early response)",
    "TMB/BRAF-positive"
  ),
  Overall = build_col(sub_overall),
  CRP_pos = build_col(sub_crp_pos),
  CRP_neg = build_col(sub_crp_neg),
  TLR_pos = build_col(sub_tlr_pos),
  TLR_neg = build_col(sub_tlr_neg),
  TMB_pos = build_col(sub_tmb_pos),
  TMB_neg = build_col(sub_tmb_neg),
  stringsAsFactors = FALSE
)

table1_df %>%
  kable(col.names = c("Characteristic", "Overall",
                      "Positive", "Negative",
                      "Positive", "Negative",
                      "Positive", "Negative"),
        caption = "Sample Characteristics by Biomarker Status",
        booktabs = TRUE, format = "latex", align = c("l", rep("c", 7))) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 2, "CRP" = 2, "TLR" = 2, "TMB/BRAF" = 2),
                   bold = TRUE) %>%
  pack_rows("Demographics",          2, 4,  bold = TRUE, italic = FALSE) %>%
  pack_rows("Treatment arm",         5, 6,  bold = TRUE, italic = FALSE) %>%
  pack_rows("Outcome events",        7, 8,  bold = TRUE, italic = FALSE) %>%
  pack_rows("Biomarker prevalence",  9, 11, bold = TRUE, italic = FALSE) %>%
  footnote(general = "Percentages within each column use the column subgroup as denominator. CRP/TLR/TMB-BRAF rows in the corresponding subgroup column equal 100% by definition.",
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Biomarker Correlations

```{r table-correlation}
correlation_df %>%
  kable(col.names = c("Biomarker Pair", "Cramér's V", "Interpretation"),
        caption = "Biomarker Correlations (Cramér's V)",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

**Note:** Cramér's V interpretation: <0.1 = Negligible, 0.1–0.3 = Weak, >0.3 = Moderate/Strong. The observed correlations are weak to negligible. While modest, any correlation among candidate biomarkers supports our decision not to use LASSO, which would arbitrarily select among correlated predictors.

\newpage

# Proportional Hazards Assumption

```{r ph-diagnostics, include=FALSE}
# =============================================================================
# PROPORTIONAL HAZARDS DIAGNOSTICS
# =============================================================================

# Fit standard coxph for Schoenfeld tests (not available in coxphf)
# Use the unified DAG-informed formula (CRP and TMB/BRAF only; TLR is a post-treatment mediator)
formula_diag_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                       crp_num:Rx + tmb_braf_num:Rx
formula_diag_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                               crp_num:Rx + tmb_braf_num:Rx

coxph_diag_os <- coxph(formula_diag_os, data = data_complete)
coxph_diag_pfs <- coxph(formula_diag_pfs, data = data_complete)

# Schoenfeld residual tests
zph_os <- cox.zph(coxph_diag_os)
zph_pfs <- cox.zph(coxph_diag_pfs)

# Extract results
zph_os_df <- as.data.frame(zph_os$table)
zph_pfs_df <- as.data.frame(zph_pfs$table)
```

## Schoenfeld Residual Tests

The proportional hazards assumption was tested using scaled Schoenfeld residuals. A significant p-value indicates potential violation of the PH assumption for that covariate.

```{r table-schoenfeld}
# Combine OS and PFS results
schoenfeld_df <- data.frame(
  Covariate = rownames(zph_os_df),
  Chi_sq_OS = round(zph_os_df$chisq, 2),
  P_OS = format_pvalue(zph_os_df$p),
  Chi_sq_PFS = round(zph_pfs_df$chisq, 2),
  P_PFS = format_pvalue(zph_pfs_df$p)
)

schoenfeld_df %>%
  kable(col.names = c("Covariate", "χ² (OS)", "p-value", "χ² (PFS)", "p-value"),
        caption = "Schoenfeld Residual Test for Proportional Hazards Assumption",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  row_spec(nrow(schoenfeld_df), bold = TRUE)
```

**Note:** GLOBAL is the omnibus test for all covariates. Individual covariate tests help identify specific PH violations.

## Log-Log Survival Plots

```{r loglog-plots, fig.height=8, fig.width=10}
# Create log-log plots by treatment arm
p1 <- create_loglog_plot(data_complete, "OSwk", "Death", "Rx",
                         "Overall Survival by Treatment")
p2 <- create_loglog_plot(data_complete, "PFSwk", "Progression", "Rx",
                         "Progression-Free Survival by Treatment")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

**Interpretation:** Approximately parallel lines on the log-log plot support the proportional hazards assumption. Crossing or converging lines suggest time-varying effects.

\newpage

# Primary Analysis: Firth-Corrected Cox Models

```{r fit-unified-model, include=FALSE}
# =============================================================================
# FIT UNIFIED DAG-INFORMED FIRTH-CORRECTED COX MODELS
# Formula: Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx
# TLR excluded: post-randomization mediator (T -> TLR -> PFS in DAG)
# =============================================================================

formula_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                   crp_num:Rx + tmb_braf_num:Rx
formula_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                          crp_num:Rx + tmb_braf_num:Rx

std_os  <- coxph(formula_os,  data = data_complete)
std_pfs <- coxph(formula_pfs, data = data_complete)

model_os  <- fit_firth_cox(formula_os,  data_complete, "Unified OS")
model_pfs <- fit_firth_cox(formula_pfs, data_complete, "Unified PFS")
```

```{r extract-results, include=FALSE}
# =============================================================================
# EXTRACT RESULTS FROM UNIFIED MODEL
# =============================================================================

results_os  <- extract_coxphf_results(model_os)
results_pfs <- extract_coxphf_results(model_pfs)

std_results_os  <- extract_coxph_results(std_os)
std_results_pfs <- extract_coxph_results(std_pfs)

primary_std_firth_row_specs <- list(
  list(label = "CRP x Rx",
       std_pat = "crp_num.*Rx|Rx.*crp_num",
       firth_pat = "crp_num.*Rx|Rx.*crp_num"),
  list(label = "TMB/BRAF x Rx",
       std_pat = "tmb_braf_num.*Rx|Rx.*tmb_braf_num",
       firth_pat = "tmb_braf_num.*Rx|Rx.*tmb_braf_num"),
  list(label = "Rx (Experimental)",
       std_pat = "^Rx[^:]+$",
       firth_pat = "^Rx[^:]+$"),
  list(label = "CRP",
       std_pat = "^crp_num$",
       firth_pat = "^crp_num$"),
  list(label = "TMB/BRAF",
       std_pat = "^tmb_braf_num$",
       firth_pat = "^tmb_braf_num$"),
  list(label = "Age",
       std_pat = "^Age$",
       firth_pat = "^Age$"),
  list(label = "Sex",
       std_pat = "^sex[^:]*$",
       firth_pat = "^sex[^:]*$")
)

std_firth_comparison_os <- build_std_firth_comparison(
  std_results_os, results_os, primary_std_firth_row_specs
)
std_firth_comparison_pfs <- build_std_firth_comparison(
  std_results_pfs, results_pfs, primary_std_firth_row_specs
)

# Convenience scalars for inline references in narrative.
# coxphf$prob (carried as P_Value) is the per-coefficient PLRT p-value.
get_pvalue_by_term <- function(results_df, pattern) {
  if (is.null(results_df)) return(NA_real_)
  idx <- grep(pattern, results_df$Term)
  if (length(idx) == 0) return(NA_real_)
  results_df$P_Value[idx[1]]
}

p_crp_os  <- get_pvalue_by_term(results_os,  "crp_num.*Rx|Rx.*crp_num")
p_tmb_os  <- get_pvalue_by_term(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
p_crp_pfs <- get_pvalue_by_term(results_pfs, "crp_num.*Rx|Rx.*crp_num")
p_tmb_pfs <- get_pvalue_by_term(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
```

## Standard Cox vs Firth

The standard Cox model is the unpenalized maximum-likelihood reference. Divergence between standard Cox and Firth estimates flags small-sample or near-separation instability that Firth corrects.

```{r table-std-firth-os}
render_std_firth_comparison_table(
  std_firth_comparison_os,
  caption = "Unified Model - Overall Survival: Standard Cox vs Firth",
  first_group_label = "Treatment x Biomarker Interactions",
  first_group_end = 2,
  second_group_label = "Main Effects and Covariates"
)
```

```{r table-std-firth-pfs}
render_std_firth_comparison_table(
  std_firth_comparison_pfs,
  caption = "Unified Model - Progression-Free Survival: Standard Cox vs Firth",
  first_group_label = "Treatment x Biomarker Interactions",
  first_group_end = 2,
  second_group_label = "Main Effects and Covariates"
)
```

## Unified Model Results

The unified DAG-informed model includes CRP and TMB/BRAF as pre-treatment biomarkers with their treatment interactions, adjusted for Age and Sex.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx`

### Overall Survival

```{r table-os}
if (!is.null(results_os)) {
  display_os <- results_os %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Unified Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment x Biomarker Interactions", 1, 2, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 3, nrow(display_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-pfs}
if (!is.null(results_pfs)) {
  display_pfs <- results_pfs %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Unified Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment x Biomarker Interactions", 1, 2, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 3, nrow(display_pfs), bold = TRUE)
}
```

\newpage

## Forest Plot

```{r forest-plot, fig.height=4, fig.width=8}
hr_crp_os  <- get_interaction_hr(results_os,  "crp_num.*Rx|Rx.*crp_num")
hr_tmb_os  <- get_interaction_hr(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
hr_crp_pfs <- get_interaction_hr(results_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_tmb_pfs <- get_interaction_hr(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

forest_data <- data.frame(
  Biomarker = rep(c("CRP", "TMB/BRAF"), 2),
  Outcome   = rep(c("Overall Survival", "Progression-Free Survival"), each = 2),
  HR        = c(hr_crp_os$HR,  hr_tmb_os$HR,  hr_crp_pfs$HR,  hr_tmb_pfs$HR),
  CI_Lower  = c(hr_crp_os$CI_Lower,  hr_tmb_os$CI_Lower,  hr_crp_pfs$CI_Lower,  hr_tmb_pfs$CI_Lower),
  CI_Upper  = c(hr_crp_os$CI_Upper,  hr_tmb_os$CI_Upper,  hr_crp_pfs$CI_Upper,  hr_tmb_pfs$CI_Upper)
)
forest_data <- forest_data[complete.cases(forest_data), ]

if (nrow(forest_data) > 0) {
  ggplot(forest_data, aes(x = HR, y = Biomarker)) +
    geom_point(size = 3, color = "#0072B2") +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.15, color = "#0072B2") +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4")) +
    facet_wrap(~ Outcome) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = "Treatment x Biomarker Interaction (Unified Model)",
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(panel.grid.minor = element_blank())
}
```

**Interpretation:** HR < 1 indicates that biomarker-positive patients derive greater benefit from experimental treatment (reduced hazard of death/progression). The dashed line at HR = 1 represents no differential treatment effect.

\newpage

# Sensitivity Analysis: Ridge Regression

Ridge regression (L2-penalized Cox, alpha = 0) shrinks all coefficients toward zero but does not eliminate any, providing a sensitivity check for the stability of the interaction estimates. The same unified model formula is used; only the main effects (CRP and TMB/BRAF) are penalized.

```{r ridge-regression, include=FALSE}
# =============================================================================
# RIDGE REGRESSION SENSITIVITY ANALYSIS (unified model)
# Penalize main effects (CRP, TMB/BRAF); interaction terms are unpenalized
# =============================================================================

tryCatch({
  ridge_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(crp_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_os_ok <- TRUE
}, error = function(e) { ridge_os_ok <<- FALSE; ridge_os <<- NULL })

tryCatch({
  ridge_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(crp_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_pfs_ok <- TRUE
}, error = function(e) { ridge_pfs_ok <<- FALSE; ridge_pfs <<- NULL })

# Use "Experimental" in pattern to avoid matching RxControl arm coefficients
# (survival::ridge() with a factor Rx creates both arms; we want the experimental arm)
ridge_crp_os  <- if (exists("ridge_os")  && !is.null(ridge_os))  extract_ridge_interaction(ridge_os,  "Experimental.*crp|crp.*Experimental")  else list(HR = NA, SE = NA)
ridge_tmb_os  <- if (exists("ridge_os")  && !is.null(ridge_os))  extract_ridge_interaction(ridge_os,  "Experimental.*tmb|tmb.*Experimental")  else list(HR = NA, SE = NA)
ridge_crp_pfs <- if (exists("ridge_pfs") && !is.null(ridge_pfs)) extract_ridge_interaction(ridge_pfs, "Experimental.*crp|crp.*Experimental")  else list(HR = NA, SE = NA)
ridge_tmb_pfs <- if (exists("ridge_pfs") && !is.null(ridge_pfs)) extract_ridge_interaction(ridge_pfs, "Experimental.*tmb|tmb.*Experimental")  else list(HR = NA, SE = NA)
```

```{r table-ridge-os}
format_ridge_hr <- function(hr, se) {
  if (is.na(hr)) return("--")
  if (is.na(se)) sprintf("%.2f", hr) else sprintf("%.2f (SE: %.2f)", hr, se)
}

data.frame(
  Interaction = c("CRP x Rx", "TMB/BRAF x Rx"),
  Firth = c(
    format_hr_ci(hr_crp_os$HR, hr_crp_os$CI_Lower, hr_crp_os$CI_Upper),
    format_hr_ci(hr_tmb_os$HR, hr_tmb_os$CI_Lower, hr_tmb_os$CI_Upper)
  ),
  Ridge = c(
    format_ridge_hr(ridge_crp_os$HR, ridge_crp_os$SE),
    format_ridge_hr(ridge_tmb_os$HR, ridge_tmb_os$SE)
  )
) %>%
  kable(col.names = c("Interaction", "Firth (95% CI)", "Ridge (point est.)"),
        caption = "Overall Survival: Firth vs Ridge Regression",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Ridge: L2 shrinkage on main effects. Substantial shrinkage vs Firth = estimate sensitive to regularization.",
           footnote_as_chunk = TRUE)
```

```{r table-ridge-pfs}
data.frame(
  Interaction = c("CRP x Rx", "TMB/BRAF x Rx"),
  Firth = c(
    format_hr_ci(hr_crp_pfs$HR, hr_crp_pfs$CI_Lower, hr_crp_pfs$CI_Upper),
    format_hr_ci(hr_tmb_pfs$HR, hr_tmb_pfs$CI_Lower, hr_tmb_pfs$CI_Upper)
  ),
  Ridge = c(
    format_ridge_hr(ridge_crp_pfs$HR, ridge_crp_pfs$SE),
    format_ridge_hr(ridge_tmb_pfs$HR, ridge_tmb_pfs$SE)
  )
) %>%
  kable(col.names = c("Interaction", "Firth (95% CI)", "Ridge (point est.)"),
        caption = "Progression-Free Survival: Firth vs Ridge Regression",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Ridge applies L2 shrinkage to main effects only.",
           footnote_as_chunk = TRUE)
```

**Interpretation:** Firth provides the best unbiased point estimate given the sample size and data structure. Ridge applies L2 shrinkage toward zero (HR toward 1.0). Comparing the two methods reveals estimate stability: if Firth and Ridge agree closely, the estimate is robust; if Ridge substantially shrinks the interaction toward null, the effect is sensitive to regularization in this sample.

\newpage

# Exploratory: TLR as a Predictive Biomarker (Responder Analysis)

This section presents an **exploratory responder analysis** that includes TLR (Tumor Lesion Reduction) as an effect modifier in a Cox model with the same structural form as the primary analysis. Because TLR is measured post-randomization (at the first on-treatment CT scan), this is not a pre-treatment patient-selection analysis: TLR status is itself influenced by treatment, and the resulting TLR x Rx interaction is informative only as a hypothesis-generating, responder-stratified contrast. It cannot be used to guide treatment decisions at baseline. The primary causal-DAG-informed analysis remains the inferential anchor for predictive biomarker claims.

The model adjusts for the pre-treatment biomarkers **CRP** and **TMB/BRAF** as prognostic main effects (their treatment interactions belong to the primary analysis and are not re-estimated here). In the ridge sensitivity model, CRP and TMB/BRAF remain **unpenalized** (well-established prognostic adjustment covariates), while the **TLR main effect and TLR x Rx interaction are penalized**. These are the post-randomization terms whose stability we want to stress-test against the small effective sample size and the partially tautological TLR-PFS association.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx`

```{r tlr-descriptive, include=FALSE}
# Descriptive TLR statistics by treatment arm
tlr_by_arm <- data_complete %>%
  group_by(Rx) %>%
  summarise(
    n = n(),
    n_tlr_pos = sum(tlr_num),
    pct_tlr_pos = round(100 * mean(tlr_num), 1)
  ) %>%
  mutate(Arm = ifelse(Rx == levels(Rx)[1], "Control (FLOX)", "Experimental (FLOX/nivo)"))
```

## Descriptive Context

### TLR Prevalence by Treatment Arm

```{r table-tlr-arm}
tlr_by_arm %>%
  select(Arm, n, n_tlr_pos, pct_tlr_pos) %>%
  kable(col.names = c("Treatment Arm", "N", "TLR-positive", "%"),
        caption = "TLR Prevalence by Treatment Arm (Descriptive)",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "TLR = Tumour Lesion Reduction >= 10% at first CT scan (post-treatment).",
           footnote_as_chunk = TRUE)
```

### Kaplan-Meier Curves Stratified by TLR

```{r km-tlr, fig.height=5, fig.width=10}
km_os_tlr  <- survfit(Surv(OSwk, Death)       ~ tlr_num, data = data_complete)
km_pfs_tlr <- survfit(Surv(PFSwk, Progression) ~ tlr_num, data = data_complete)

p_os <- ggsurvplot(
  km_os_tlr, data = data_complete,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Overall Survival by TLR status",
  xlab = "Time (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

p_pfs <- ggsurvplot(
  km_pfs_tlr, data = data_complete,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Progression-Free Survival by TLR status",
  xlab = "Time (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

gridExtra::grid.arrange(p_os, p_pfs, ncol = 2)
```

**Note:** These curves are purely descriptive and stratify by a post-treatment response variable. The observed difference in survival by TLR status reflects treatment response, not a pre-treatment patient characteristic.

\newpage

```{r fit-tlr-firth, include=FALSE}
# =============================================================================
# TLR RESPONDER-ANALYSIS FIRTH-COX MODELS
# Formula: Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx
# CRP and TMB/BRAF enter as main-effect prognostic adjustments only.
# =============================================================================

formula_tlr_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                       tlr_num + tlr_num:Rx
formula_tlr_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                              tlr_num + tlr_num:Rx

std_tlr_os  <- coxph(formula_tlr_os,  data = data_complete)
std_tlr_pfs <- coxph(formula_tlr_pfs, data = data_complete)

model_tlr_os  <- fit_firth_cox(formula_tlr_os,  data_complete, "TLR OS")
model_tlr_pfs <- fit_firth_cox(formula_tlr_pfs, data_complete, "TLR PFS")

results_tlr_os  <- extract_coxphf_results(model_tlr_os)
results_tlr_pfs <- extract_coxphf_results(model_tlr_pfs)

std_results_tlr_os  <- extract_coxph_results(std_tlr_os)
std_results_tlr_pfs <- extract_coxph_results(std_tlr_pfs)

tlr_std_firth_row_specs <- list(
  list(label = "TLR x Rx",
       std_pat = "tlr_num.*Rx|Rx.*tlr_num",
       firth_pat = "tlr_num.*Rx|Rx.*tlr_num"),
  list(label = "TLR (main effect)",
       std_pat = "^tlr_num$",
       firth_pat = "^tlr_num$"),
  list(label = "Rx (Experimental)",
       std_pat = "^Rx[^:]+$",
       firth_pat = "^Rx[^:]+$"),
  list(label = "CRP",
       std_pat = "^crp_num$",
       firth_pat = "^crp_num$"),
  list(label = "TMB/BRAF",
       std_pat = "^tmb_braf_num$",
       firth_pat = "^tmb_braf_num$"),
  list(label = "Age",
       std_pat = "^Age$",
       firth_pat = "^Age$"),
  list(label = "Sex",
       std_pat = "^sex[^:]*$",
       firth_pat = "^sex[^:]*$")
)

std_firth_comparison_tlr_os <- build_std_firth_comparison(
  std_results_tlr_os, results_tlr_os, tlr_std_firth_row_specs
)
std_firth_comparison_tlr_pfs <- build_std_firth_comparison(
  std_results_tlr_pfs, results_tlr_pfs, tlr_std_firth_row_specs
)

# PLRT p-values for the TLR x Rx interaction (for narrative)
p_tlr_os  <- get_pvalue_by_term(results_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
p_tlr_pfs <- get_pvalue_by_term(results_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")
```

## Standard Cox vs Firth

The standard Cox model is the unpenalized maximum-likelihood reference. Divergence between standard Cox and Firth estimates flags small-sample or near-separation instability that Firth corrects.

```{r table-tlr-std-firth-os}
render_std_firth_comparison_table(
  std_firth_comparison_tlr_os,
  caption = "TLR Responder Model - Overall Survival: Standard Cox vs Firth",
  first_group_label = "TLR Terms",
  first_group_end = 2,
  second_group_label = "Adjustment Covariates"
)
```

```{r table-tlr-std-firth-pfs}
render_std_firth_comparison_table(
  std_firth_comparison_tlr_pfs,
  caption = "TLR Responder Model - Progression-Free Survival: Standard Cox vs Firth",
  first_group_label = "TLR Terms",
  first_group_end = 2,
  second_group_label = "Adjustment Covariates"
)
```

## Firth-Corrected Cox Model

### Overall Survival

```{r table-tlr-firth-os}
if (!is.null(results_tlr_os)) {
  display_tlr_os <- results_tlr_os %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "TLR Responder Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 2, nrow(display_tlr_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-tlr-firth-pfs}
if (!is.null(results_tlr_pfs)) {
  display_tlr_pfs <- results_tlr_pfs %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "TLR Responder Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 2, nrow(display_tlr_pfs), bold = TRUE)
}
```

\newpage

## Ridge Sensitivity Analysis (TLR Terms Penalized)

Ridge regression is applied here with a targeted penalty: only the TLR main effect and the TLR x Rx interaction are L2-shrunk. CRP, TMB/BRAF, Age, sex, and Rx are estimated without penalty, since they enter the model as adjustment covariates whose effects are not the inferential target.

```{r tlr-ridge, include=FALSE}
# =============================================================================
# RIDGE SENSITIVITY: penalize TLR main effect + TLR x Rx interaction
# CRP and TMB/BRAF main effects remain unpenalized (prognostic adjustment)
# Rx_num is defined earlier (0 = Control, 1 = Experimental).
# survival::ridge() takes raw variables, so pre-construct the interaction.
# =============================================================================

data_complete$tlr_x_rx <- data_complete$tlr_num * data_complete$Rx_num

ridge_tlr_os_ok <- TRUE
tryCatch({
  ridge_tlr_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
      ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
    data = data_complete
  )
}, error = function(e) { ridge_tlr_os_ok <<- FALSE; ridge_tlr_os <<- NULL })

ridge_tlr_pfs_ok <- TRUE
tryCatch({
  ridge_tlr_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
      ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
    data = data_complete
  )
}, error = function(e) { ridge_tlr_pfs_ok <<- FALSE; ridge_tlr_pfs <<- NULL })

ridge_tlr_os_int  <- if (!is.null(ridge_tlr_os))  extract_ridge_interaction(ridge_tlr_os,  "tlr_x_rx\\)")  else list(HR = NA, SE = NA)
ridge_tlr_pfs_int <- if (!is.null(ridge_tlr_pfs)) extract_ridge_interaction(ridge_tlr_pfs, "tlr_x_rx\\)") else list(HR = NA, SE = NA)

# Firth TLR x Rx HRs for the in-text inline summary
tlr_firth_os  <- get_interaction_hr(results_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
tlr_firth_pfs <- get_interaction_hr(results_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")

# Extract all ridge coefficients into a tidy data frame
extract_all_ridge_coefs <- function(model) {
  if (is.null(model)) return(NULL)
  ct <- summary(model)$coefficients
  data.frame(
    Term = rownames(ct),
    HR = exp(ct[, "coef"]),
    SE = ct[, "se(coef)"],
    stringsAsFactors = FALSE
  )
}

ridge_tlr_os_coefs  <- extract_all_ridge_coefs(ridge_tlr_os)
ridge_tlr_pfs_coefs <- extract_all_ridge_coefs(ridge_tlr_pfs)

# Build the full-coefficient Firth vs Ridge comparison.
# Firth coefficient names: Age, sex<level>, Rx<level>, crp_num, tmb_braf_num,
#   tlr_num, Rx<level>:tlr_num
# Ridge coefficient names: Age, sex<level>, Rx<level>, crp_num, tmb_braf_num,
#   ridge(tlr_num), ridge(tlr_x_rx)
# Ridge patterns use the closing ")" to disambiguate the TLR main effect
# from the TLR x Rx interaction.
build_tlr_comparison <- function(firth_results, ridge_coefs) {
  row_specs <- list(
    list(label = "TLR x Rx",
         firth_pat = "tlr_num.*Rx|Rx.*tlr_num",
         ridge_pat = "tlr_x_rx\\)"),
    list(label = "TLR (main effect)",
         firth_pat = "^tlr_num$",
         ridge_pat = "tlr_num\\)"),
    list(label = "Age",
         firth_pat = "^Age$",
         ridge_pat = "^Age$"),
    list(label = "Sex",
         firth_pat = "^sex",
         ridge_pat = "^sex"),
    list(label = "Rx (Experimental)",
         firth_pat = "^Rx[A-Za-z]",
         ridge_pat = "^Rx[A-Za-z]"),
    list(label = "CRP",
         firth_pat = "^crp_num$",
         ridge_pat = "^crp_num$"),
    list(label = "TMB/BRAF",
         firth_pat = "^tmb_braf_num$",
         ridge_pat = "^tmb_braf_num$")
  )

  do.call(rbind, lapply(row_specs, function(rs) {
    firth_cell <- "--"
    ridge_cell <- "--"

    if (!is.null(firth_results)) {
      f_idx <- grep(rs$firth_pat, firth_results$Term)
      if (length(f_idx) > 0) {
        firth_cell <- format_hr_ci(
          firth_results$HR[f_idx[1]],
          firth_results$CI_Lower[f_idx[1]],
          firth_results$CI_Upper[f_idx[1]]
        )
      }
    }

    if (!is.null(ridge_coefs)) {
      r_idx <- grep(rs$ridge_pat, ridge_coefs$Term)
      if (length(r_idx) > 0) {
        ridge_cell <- format_ridge_hr(
          ridge_coefs$HR[r_idx[1]],
          ridge_coefs$SE[r_idx[1]]
        )
      }
    }

    data.frame(Term = rs$label, Firth = firth_cell, Ridge = ridge_cell,
               stringsAsFactors = FALSE)
  }))
}

tlr_comparison_os  <- build_tlr_comparison(results_tlr_os,  ridge_tlr_os_coefs)
tlr_comparison_pfs <- build_tlr_comparison(results_tlr_pfs, ridge_tlr_pfs_coefs)
```

```{r table-tlr-ridge-os}
tlr_comparison_os %>%
  kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
        caption = "TLR Responder Model - Overall Survival: Firth vs Ridge, all coefficients",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
  pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
  pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(tlr_comparison_os), bold = TRUE) %>%
  footnote(general = "Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized. survival::ridge() does not produce confidence intervals; standard errors are shown for reference.",
           footnote_as_chunk = TRUE)
```

```{r table-tlr-ridge-pfs}
tlr_comparison_pfs %>%
  kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
        caption = "TLR Responder Model - Progression-Free Survival: Firth vs Ridge, all coefficients",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
  pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
  pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(tlr_comparison_pfs), bold = TRUE) %>%
  footnote(general = "Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized. survival::ridge() does not produce confidence intervals; standard errors are shown for reference.",
           footnote_as_chunk = TRUE)
```

**Interpretation:** The Firth HR is the best unbiased point estimate of the TLR x Rx interaction under penalized maximum likelihood. The ridge HR applies L2 shrinkage targeted at the TLR terms; if the ridge estimate is substantially closer to HR = 1.0 than the Firth estimate, the responder-stratified interaction is sensitive to regularization, consistent with a small-sample, partly tautological signal. Findings here are exploratory and should not be used for pre-treatment patient selection, since TLR is not measurable at baseline. They may motivate landmark or formal causal-mediation analyses in future work.

\newpage

# Landmark Analysis: TLR at Week 9

The responder analysis above treats TLR status as if it were known at baseline. It is not: TLR is measured at the first on-treatment CT scan, so a patient can only be classified TLR-positive or TLR-negative *after* surviving (and remaining progression-free) long enough to reach that scan. Conditioning survival on a post-baseline response therefore induces **guarantee-time (immortal-time) bias** — TLR-classified patients are, by construction, a more favourable risk set than the full randomized population.

A **landmark analysis** removes this bias by (i) fixing a landmark time, (ii) restricting to patients still at risk at the landmark, and (iii) measuring survival **from the landmark onward**. Here the landmark is set to **week 9**, the time of the second CT (the first on-treatment response assessment): TLR compares this scan to the baseline CT, so a patient's TLR status does not exist until week 9. Placing the landmark at the measurement time ensures every patient in the cohort has actually reached the scan and has a defined TLR. Every retained patient is guaranteed to have reached the assessment, so the TLR x Rx contrast is no longer inflated by the survival required to be classifiable. This section **complements** the responder analysis above (which is retained for comparison); it does not replace it.

If the true response-assessment week differs from 9, only the single `LANDMARK_WK` value below needs changing. Because the small trial loses patients with events or censoring before the landmark, the cohort sizes and event counts are reported explicitly, and all model fits are wrapped so a too-small cohort degrades gracefully rather than aborting the render.

```{r tlr-landmark-cohort, include=FALSE}
# =============================================================================
# LANDMARK COHORT CONSTRUCTION (week 9)
# Endpoint-specific at-risk sets; clock reset to start at the landmark.
#   OS  cohort: OSwk  >= LANDMARK_WK; analysis time OSwk_lm  = OSwk  - LANDMARK_WK
#   PFS cohort: PFSwk >= LANDMARK_WK; analysis time PFSwk_lm = PFSwk - LANDMARK_WK
# =============================================================================
LANDMARK_WK <- 9

data_lm_os <- data_complete[data_complete$OSwk >= LANDMARK_WK, ]
data_lm_os$OSwk_lm <- data_lm_os$OSwk - LANDMARK_WK

data_lm_pfs <- data_complete[data_complete$PFSwk >= LANDMARK_WK, ]
data_lm_pfs$PFSwk_lm <- data_lm_pfs$PFSwk - LANDMARK_WK

# Pre-build the ridge interaction term on each landmark cohort
data_lm_os$tlr_x_rx  <- data_lm_os$tlr_num  * data_lm_os$Rx_num
data_lm_pfs$tlr_x_rx <- data_lm_pfs$tlr_num * data_lm_pfs$Rx_num

# Attrition / sample-size accounting
lm_attrition <- data.frame(
  Endpoint = c("Overall survival", "Progression-free survival"),
  N_total = c(nrow(data_complete), nrow(data_complete)),
  N_landmark = c(nrow(data_lm_os), nrow(data_lm_pfs)),
  N_excluded = c(nrow(data_complete) - nrow(data_lm_os),
                 nrow(data_complete) - nrow(data_lm_pfs)),
  Events_landmark = c(sum(data_lm_os$Death), sum(data_lm_pfs$Progression)),
  stringsAsFactors = FALSE
)

# Characterize the PFS exclusions. Because progression and TLR are read from the
# SAME first on-treatment scan, patients who progress at that scan are excluded
# from the landmark cohort and are, by construction, TLR-negative. Quantify this
# so the prose can report the entanglement honestly.
pfs_excl <- data_complete[data_complete$PFSwk < LANDMARK_WK, ]
os_excl  <- data_complete[data_complete$OSwk  < LANDMARK_WK, ]
n_pfs_excl          <- nrow(pfs_excl)
n_pfs_excl_prog     <- sum(pfs_excl$Progression == 1)
n_pfs_excl_prog_tn  <- sum(pfs_excl$Progression == 1 & pfs_excl$tlr_num == 0)
n_os_excl_death     <- sum(os_excl$Death == 1)
```

## Landmark Cohort and Attrition

```{r table-lm-attrition}
lm_attrition %>%
  kable(col.names = c("Endpoint", "N randomized (complete cases)",
                      "N at risk at week 9", "N excluded (event/censor < week 9)",
                      "Events from week 9"),
        caption = "Week-9 landmark cohort: attrition and remaining events",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  footnote(general = "Patients with death, progression, or censoring before week 9 are excluded from the corresponding endpoint. Survival is measured from week 9 onward.",
           footnote_as_chunk = TRUE)
```

## Descriptive Context (Landmark Cohort)

### Characteristics of the Week-9 Landmark Cohorts by TLR Status

The two tables below describe the patients who enter the landmark analysis, overall and split by the TLR status that becomes defined at the week-9 scan. The at-risk set is endpoint-specific: the **overall-survival** cohort keeps everyone alive at week 9, whereas the **progression-free-survival** cohort additionally drops patients who had already progressed by week 9. The PFS cohort is therefore smaller. Reporting both fixes the denominators for the OS and PFS models that follow and makes the composition of the two TLR groups directly comparable.

```{r lm-characteristics, include=FALSE}
# =============================================================================
# LANDMARK COHORT CHARACTERISTICS, split by TLR status.
# Two endpoint-specific at-risk sets:
#   OS  cohort (data_lm_os):  OSwk  >= 9  (alive at week 9)
#   PFS cohort (data_lm_pfs): PFSwk >= 9  (alive AND progression-free at week 9)
# Note on sex: the source column is "Sex 0female", so sex == 0 is female.
# =============================================================================
format_n_pct <- function(count, n) {
  if (n == 0) return("--")
  sprintf("%d (%.1f%%)", count, 100 * count / n)
}

summarise_lm_cohort <- function(df) {
  n <- nrow(df)
  sex_num <- as.numeric(as.character(df$sex))
  c(
    sprintf("%d", n),
    sprintf("%.1f (%.1f)", mean(df$Age), sd(df$Age)),
    format_n_pct(sum(sex_num == 0), n),
    format_n_pct(sum(df$Rx == levels(df$Rx)[1]), n),
    format_n_pct(sum(df$Rx == levels(df$Rx)[2]), n),
    format_n_pct(sum(df$Death), n),
    format_n_pct(sum(df$Progression), n),
    format_n_pct(sum(df$crp_num), n),
    format_n_pct(sum(df$tmb_braf_num), n)
  )
}

build_lm_characteristics <- function(df) {
  data.frame(
    Characteristic = c("n", "Age, years, mean (SD)", "Female sex",
                       "Control arm (FLOX)", "Experimental arm (FLOX/nivolumab)",
                       "Deaths (OS events)", "PFS events (progression or death)",
                       "CRP-positive", "TMB/BRAF-positive"),
    All     = summarise_lm_cohort(df),
    TLR_pos = summarise_lm_cohort(df[df$tlr_num == 1, ]),
    TLR_neg = summarise_lm_cohort(df[df$tlr_num == 0, ]),
    stringsAsFactors = FALSE
  )
}

lm_characteristics_os  <- build_lm_characteristics(data_lm_os)
lm_characteristics_pfs <- build_lm_characteristics(data_lm_pfs)

render_lm_char_table <- function(char_df, caption) {
  tbl <- char_df %>%
    kable(col.names = c("Characteristic", "At-risk cohort", "TLR-positive", "TLR-negative"),
          caption = caption, booktabs = TRUE, align = c("l", "r", "r", "r"),
          format = if (knitr::is_latex_output()) "latex" else "pipe")
  if (knitr::is_latex_output()) {
    tbl %>% kable_styling(latex_options = c("hold_position"), font_size = 9)
  } else {
    tbl
  }
}
```

#### Overall-survival at-risk set (OSwk >= 9)

```{r table-lm-characteristics-os}
render_lm_char_table(
  lm_characteristics_os,
  "Characteristics of the week-9 OS landmark cohort (alive at week 9), by TLR status"
)
```

Because no patient dies or is censored before week 9, the OS at-risk set coincides with the full complete-case cohort (n = `r nrow(data_lm_os)`).

#### Progression-free-survival at-risk set (PFSwk >= 9)

```{r table-lm-characteristics-pfs}
render_lm_char_table(
  lm_characteristics_pfs,
  "Characteristics of the week-9 PFS landmark cohort (alive and progression-free at week 9), by TLR status"
)
```

The PFS at-risk set drops the `r nrow(data_lm_os) - nrow(data_lm_pfs)` patient(s) who had already progressed, died, or were censored by week 9, leaving n = `r nrow(data_lm_pfs)`.

*Definitions:* percentages are column percentages; the "Deaths" and "PFS events" rows count events over the whole follow-up, not only after the landmark. CRP-positive = CRP < 5 mg/L; TMB/BRAF-positive = TMB >= 9 mut/Mb or BRAF mutation; TLR-positive = tumour lesion reduction >= 10% at the first on-treatment CT.

**Note:** In both cohorts the two TLR groups are well matched on age, sex, and TMB/BRAF status, but differ sharply on treatment arm and CRP: the TLR-positive group is enriched for control-arm patients and for CRP-positivity, while every TLR-negative patient died during follow-up. These imbalances are the descriptive counterpart of the interaction estimates below and reinforce that TLR status is realised after randomization rather than being a baseline characteristic.

### TLR Prevalence by Treatment Arm at Week 9

```{r table-lm-tlr-arm}
tlr_by_arm_lm <- data_lm_os %>%
  group_by(Rx) %>%
  summarise(
    n = n(),
    n_tlr_pos = sum(tlr_num),
    pct_tlr_pos = round(100 * mean(tlr_num), 1),
    .groups = "drop"
  ) %>%
  mutate(Arm = ifelse(Rx == levels(Rx)[1], "Control (FLOX)", "Experimental (FLOX/nivo)"))

tlr_by_arm_lm %>%
  select(Arm, n, n_tlr_pos, pct_tlr_pos) %>%
  kable(col.names = c("Treatment Arm", "N", "TLR-positive", "%"),
        caption = "TLR Prevalence by Treatment Arm, Week-9 Landmark Cohort (OS at-risk set)",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Restricted to patients alive at week 9. TLR = Tumour Lesion Reduction >= 10% at first CT scan.",
           footnote_as_chunk = TRUE)
```

### Landmark Kaplan-Meier Curves Stratified by TLR

```{r km-lm-tlr, fig.height=5, fig.width=10}
km_os_tlr_lm  <- survfit(Surv(OSwk_lm, Death)        ~ tlr_num, data = data_lm_os)
km_pfs_tlr_lm <- survfit(Surv(PFSwk_lm, Progression) ~ tlr_num, data = data_lm_pfs)

p_os_lm <- ggsurvplot(
  km_os_tlr_lm, data = data_lm_os,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Overall Survival by TLR status (from week 9)",
  xlab = "Time since landmark (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

p_pfs_lm <- ggsurvplot(
  km_pfs_tlr_lm, data = data_lm_pfs,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Progression-Free Survival by TLR status (from week 9)",
  xlab = "Time since landmark (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

gridExtra::grid.arrange(p_os_lm, p_pfs_lm, ncol = 2)
```

**Note:** Follow-up time is measured from the week-9 landmark. All patients shown were alive (OS) or alive and progression-free (PFS) at the landmark, so the curves are free of the guarantee-time bias affecting the responder-analysis curves above.

\newpage

```{r fit-lm-tlr-firth, include=FALSE}
# =============================================================================
# LANDMARK FIRTH-COX MODELS (TLR responder form, conditioned on week-9 survival)
# Formula: Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx, time reset to landmark
# Reuses tlr_std_firth_row_specs defined in the responder section above.
# =============================================================================
formula_lm_tlr_os  <- Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                             tlr_num + tlr_num:Rx
formula_lm_tlr_pfs <- Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                                    tlr_num + tlr_num:Rx

std_lm_tlr_os  <- tryCatch(coxph(formula_lm_tlr_os,  data = data_lm_os),  error = function(e) NULL)
std_lm_tlr_pfs <- tryCatch(coxph(formula_lm_tlr_pfs, data = data_lm_pfs), error = function(e) NULL)

model_lm_tlr_os  <- tryCatch(fit_firth_cox(formula_lm_tlr_os,  data_lm_os,  "Landmark TLR OS"),  error = function(e) NULL)
model_lm_tlr_pfs <- tryCatch(fit_firth_cox(formula_lm_tlr_pfs, data_lm_pfs, "Landmark TLR PFS"), error = function(e) NULL)

results_lm_tlr_os  <- if (!is.null(model_lm_tlr_os))  extract_coxphf_results(model_lm_tlr_os)  else NULL
results_lm_tlr_pfs <- if (!is.null(model_lm_tlr_pfs)) extract_coxphf_results(model_lm_tlr_pfs) else NULL

std_results_lm_tlr_os  <- if (!is.null(std_lm_tlr_os))  extract_coxph_results(std_lm_tlr_os)  else NULL
std_results_lm_tlr_pfs <- if (!is.null(std_lm_tlr_pfs)) extract_coxph_results(std_lm_tlr_pfs) else NULL

std_firth_comparison_lm_tlr_os <- if (!is.null(std_results_lm_tlr_os) && !is.null(results_lm_tlr_os))
  build_std_firth_comparison(std_results_lm_tlr_os, results_lm_tlr_os, tlr_std_firth_row_specs) else NULL
std_firth_comparison_lm_tlr_pfs <- if (!is.null(std_results_lm_tlr_pfs) && !is.null(results_lm_tlr_pfs))
  build_std_firth_comparison(std_results_lm_tlr_pfs, results_lm_tlr_pfs, tlr_std_firth_row_specs) else NULL

# PLRT p-values for the landmark TLR x Rx interaction (for narrative)
p_lm_tlr_os  <- if (!is.null(results_lm_tlr_os))  get_pvalue_by_term(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num") else NA
p_lm_tlr_pfs <- if (!is.null(results_lm_tlr_pfs)) get_pvalue_by_term(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num") else NA
```

## Standard Cox vs Firth (Landmark)

```{r table-lm-tlr-std-firth-os}
if (!is.null(std_firth_comparison_lm_tlr_os)) {
  render_std_firth_comparison_table(
    std_firth_comparison_lm_tlr_os,
    caption = "Landmark (Week 9) TLR Model - Overall Survival: Standard Cox vs Firth",
    first_group_label = "TLR Terms",
    first_group_end = 2,
    second_group_label = "Adjustment Covariates"
  )
}
```

```{r table-lm-tlr-std-firth-pfs}
if (!is.null(std_firth_comparison_lm_tlr_pfs)) {
  render_std_firth_comparison_table(
    std_firth_comparison_lm_tlr_pfs,
    caption = "Landmark (Week 9) TLR Model - Progression-Free Survival: Standard Cox vs Firth",
    first_group_label = "TLR Terms",
    first_group_end = 2,
    second_group_label = "Adjustment Covariates"
  )
}
```

## Firth-Corrected Cox Model (Landmark)

### Overall Survival

```{r table-lm-tlr-firth-os}
if (!is.null(results_lm_tlr_os)) {
  display_lm_tlr_os <- results_lm_tlr_os %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_lm_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Landmark TLR Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 2, nrow(display_lm_tlr_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-lm-tlr-firth-pfs}
if (!is.null(results_lm_tlr_pfs)) {
  display_lm_tlr_pfs <- results_lm_tlr_pfs %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_lm_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Landmark TLR Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 2, nrow(display_lm_tlr_pfs), bold = TRUE)
}
```

\newpage

## Ridge Sensitivity Analysis (Landmark, TLR Terms Penalized)

Ridge regression is applied to the landmark cohorts with the same targeted penalty as the responder analysis: only the TLR main effect and the TLR x Rx interaction are L2-shrunk, while Age, sex, Rx, CRP, and TMB/BRAF remain unpenalized.

```{r lm-tlr-ridge, include=FALSE}
# Reuses build_tlr_comparison() and extract_all_ridge_coefs() defined in the
# responder ridge chunk above. Models fitted on the week-9 landmark cohorts.
ridge_lm_tlr_os <- tryCatch(
  coxph(Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
        data = data_lm_os),
  error = function(e) NULL)

ridge_lm_tlr_pfs <- tryCatch(
  coxph(Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
        data = data_lm_pfs),
  error = function(e) NULL)

ridge_lm_tlr_os_int  <- if (!is.null(ridge_lm_tlr_os))  extract_ridge_interaction(ridge_lm_tlr_os,  "tlr_x_rx\\)")  else list(HR = NA, SE = NA)
ridge_lm_tlr_pfs_int <- if (!is.null(ridge_lm_tlr_pfs)) extract_ridge_interaction(ridge_lm_tlr_pfs, "tlr_x_rx\\)") else list(HR = NA, SE = NA)

# Firth landmark TLR x Rx HRs for the in-text inline summary
lm_tlr_firth_os  <- if (!is.null(results_lm_tlr_os))  get_interaction_hr(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num") else list(HR = NA, CI_Lower = NA, CI_Upper = NA)
lm_tlr_firth_pfs <- if (!is.null(results_lm_tlr_pfs)) get_interaction_hr(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num") else list(HR = NA, CI_Lower = NA, CI_Upper = NA)

ridge_lm_tlr_os_coefs  <- extract_all_ridge_coefs(ridge_lm_tlr_os)
ridge_lm_tlr_pfs_coefs <- extract_all_ridge_coefs(ridge_lm_tlr_pfs)

lm_tlr_comparison_os  <- if (!is.null(results_lm_tlr_os))  build_tlr_comparison(results_lm_tlr_os,  ridge_lm_tlr_os_coefs)  else NULL
lm_tlr_comparison_pfs <- if (!is.null(results_lm_tlr_pfs)) build_tlr_comparison(results_lm_tlr_pfs, ridge_lm_tlr_pfs_coefs) else NULL
```

```{r table-lm-tlr-ridge-os}
if (!is.null(lm_tlr_comparison_os)) {
  lm_tlr_comparison_os %>%
    kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
          caption = "Landmark TLR Model - Overall Survival: Firth vs Ridge, all coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
    pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(lm_tlr_comparison_os), bold = TRUE) %>%
    footnote(general = "Week-9 landmark cohort. Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized.",
             footnote_as_chunk = TRUE)
}
```

```{r table-lm-tlr-ridge-pfs}
if (!is.null(lm_tlr_comparison_pfs)) {
  lm_tlr_comparison_pfs %>%
    kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
          caption = "Landmark TLR Model - Progression-Free Survival: Firth vs Ridge, all coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
    pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(lm_tlr_comparison_pfs), bold = TRUE) %>%
    footnote(general = "Week-9 landmark cohort. Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized.",
             footnote_as_chunk = TRUE)
}
```

**Interpretation:** The two endpoints behave very differently under the landmark, and the contrast is itself informative.

*Overall survival* is clean: `r lm_attrition$N_excluded[1]` patient(s) are excluded (no deaths occur before week 9), so the landmark OS cohort is the full randomized population and the landmark Firth TLR x Rx HR (`r format_hr_ci(lm_tlr_firth_os$HR, lm_tlr_firth_os$CI_Lower, lm_tlr_firth_os$CI_Upper)`) is **identical** to the responder estimate (`r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)`) — a Cox model is invariant to a common shift of the time origin when no one leaves the risk set. The OS responder signal is therefore not an early-death guarantee-time artefact.

*Progression-free survival* exposes a deeper problem. `r lm_attrition$N_excluded[2]` patients are excluded, of whom `r n_pfs_excl_prog` progressed, `r n_pfs_excl_prog_tn` of them **TLR-negative**. This is not a coincidence: progression and TLR are read from the *same* first on-treatment scan, so a patient whose tumour grows at that scan is simultaneously classified as a progression and as TLR-negative. The week-9 landmark removes exactly these TLR-negative scan-time progressors, shifting the Firth TLR x Rx HR from `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` (responder) to `r format_hr_ci(lm_tlr_firth_pfs$HR, lm_tlr_firth_pfs$CI_Lower, lm_tlr_firth_pfs$CI_Upper)` (landmark). The responder PFS association is thus **partly tautological** — TLR-negativity and early progression are the same measurement — which the landmark makes explicit by excluding the coupled events.

Neither analysis resolves the most fundamental issue: TLR lies on the causal path of treatment (Rx -> TLR -> outcome), so the TLR x Rx contrast is not a baseline patient-selection estimate under any time origin; disentangling it would require formal causal mediation, not a landmark. All estimates remain exploratory and imprecise (PLRT p `r format_pvalue(p_lm_tlr_os)` OS, `r format_pvalue(p_lm_tlr_pfs)` PFS) and must not guide treatment selection. The landmark is fixed at week 9 (the second, first-on-treatment CT); if the assessment week differs, change `LANDMARK_WK`.

\newpage

```{r discussion-values, include=FALSE}
# Values quoted in the Discussion and Summary are pulled from the objects
# computed above so the prose cannot drift from the tables.
get_zph_p <- function(zph_df, pattern) {
  idx <- grep(pattern, rownames(zph_df))
  if (length(idx) == 0) NA_real_ else zph_df$p[idx[1]]
}
p_zph_os_global  <- get_zph_p(zph_os_df,  "^GLOBAL$")
p_zph_pfs_global <- get_zph_p(zph_pfs_df, "^GLOBAL$")
p_zph_pfs_crp    <- get_zph_p(zph_pfs_df, "^crp_num$")
p_zph_pfs_tmb    <- get_zph_p(zph_pfs_df, "^tmb_braf_num$")
p_zph_pfs_crp_rx <- get_zph_p(zph_pfs_df, "crp_num.*Rx|Rx.*crp_num")
p_zph_pfs_tmb_rx <- get_zph_p(zph_pfs_df, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# Firth HR (95% CI) and point-estimate shorthands
hr_txt <- function(x) format_hr_ci(x$HR, x$CI_Lower, x$CI_Upper)
hr_pt  <- function(x) if (is.na(x$HR)) "--" else sprintf("%.2f", x$HR)
```

# Discussion

## Primary interaction results

Neither biomarker-treatment interaction reached conventional significance in the unified model (Firth HR with 95% CI in parentheses). For **overall survival**, CRP × Rx yielded HR `r hr_txt(hr_crp_os)` (PLRT p = `r format_pvalue(p_crp_os)`) and TMB/BRAF × Rx HR `r hr_txt(hr_tmb_os)` (p = `r format_pvalue(p_tmb_os)`) — point estimates close to null with very wide confidence intervals. For **progression-free survival**, the CRP × Rx interaction was directionally favourable but imprecise (HR `r hr_txt(hr_crp_pfs)`, p = `r format_pvalue(p_crp_pfs)`): CRP-positive patients in the experimental arm had a lower estimated hazard of progression or death than CRP-positive controls, though the CI spans more than an order of magnitude and includes 1. The TMB/BRAF × Rx PFS interaction was HR `r hr_txt(hr_tmb_pfs)` (p = `r format_pvalue(p_tmb_pfs)`). These results are consistent with the trial being underpowered to detect treatment-effect heterogeneity (n = `r n_total`, `r sum(data_complete$Progression)` PFS events (progression or death), `r sum(data_complete$Death)` deaths): even a moderate subgroup effect (HR ~0.5) would require far larger samples for reliable estimation.

The PFS pattern is worth noting as a hypothesis-generating finding. The CRP direction (HR `r hr_pt(hr_crp_pfs)`) is consistent with the DAG association test showing CRP → PFS (HR 0.41, p = 0.001; see the DAG associations report) and the biological hypothesis that low CRP (reflecting lower systemic inflammation) identifies patients more likely to respond to immunotherapy. However, the OS CRP interaction estimate (HR `r hr_pt(hr_crp_os)`) is closer to null, suggesting that any PFS benefit does not clearly translate to an OS benefit in this dataset.

## Proportional hazards

The PH assumption was well supported in overall survival (Schoenfeld global p = `r format_pvalue(p_zph_os_global)`). In progression-free survival the global test indicated some departure from proportionality (p = `r format_pvalue(p_zph_pfs_global)`), and this is carried by the biomarker main effects rather than the interaction terms: CRP main effect p = `r format_pvalue(p_zph_pfs_crp)`, TMB/BRAF main effect p = `r format_pvalue(p_zph_pfs_tmb)`, versus CRP × Rx p = `r format_pvalue(p_zph_pfs_crp_rx)` and TMB/BRAF × Rx p = `r format_pvalue(p_zph_pfs_tmb_rx)`. This suggests that the prognostic hazard ratios for CRP and TMB/BRAF are not constant over time in PFS, which may reflect different kinetics of early vs late events (now including deaths) across biomarker-defined subgroups. The PFS main-effect estimates for CRP and TMB/BRAF should therefore be read as time-averaged effects; a time-varying Cox model or landmark analysis would be more appropriate for characterizing them. The interaction estimates themselves are not flagged by this diagnostic.

## Ridge regression sensitivity

For OS, the CRP × Rx estimate changes substantially when the biomarker main effects are penalized (Firth HR `r hr_pt(hr_crp_os)` → Ridge HR `r hr_pt(ridge_crp_os)`), indicating that the OS estimate is sensitive to model specification and should be treated as imprecise. The TMB/BRAF × Rx OS estimate changes little (`r hr_pt(hr_tmb_os)` → `r hr_pt(ridge_tmb_os)`), consistent with a near-null interaction. For PFS, both interaction estimates also move under Ridge (CRP × Rx `r hr_pt(hr_crp_pfs)` → `r hr_pt(ridge_crp_pfs)`; TMB/BRAF × Rx `r hr_pt(hr_tmb_pfs)` → `r hr_pt(ridge_tmb_pfs)`). Because only the main effects are penalized, a shift in the interaction terms reflects redistribution of the shrunken main-effect signal rather than independent support for a particular effect size; the PFS interaction estimates are therefore not stable under regularization and should not be over-interpreted.

## TLR responder analysis (exploratory)

The exploratory responder model — `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx` — estimates the differential treatment effect between TLR-positive and TLR-negative subgroups while adjusting for the pre-treatment biomarkers as prognostic main effects. The Firth-estimated TLR × Rx HR was `r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)` for overall survival and `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` for progression-free survival. The OS estimate sits **above 1.0**, which directionally implies the (TLR-positive vs TLR-negative) hazard contrast is *worse* on the experimental arm than on the control arm — the opposite of a "TLR-positive predicts immunotherapy benefit" pattern. PFS is closer to null. Ridge shrinkage of the TLR terms gives `r format_ridge_hr(ridge_tlr_os_int$HR, ridge_tlr_os_int$SE)` (OS) and `r format_ridge_hr(ridge_tlr_pfs_int$HR, ridge_tlr_pfs_int$SE)` (PFS): ridge moves the OS estimate modestly toward null but preserves the directional pattern, and barely changes the PFS estimate. PLRT p-values (`r format_pvalue(p_tlr_os)` OS, `r format_pvalue(p_tlr_pfs)` PFS) do not reach conventional significance, consistent with the wide profile-likelihood CIs in this small sample.

The directional pattern is consistent with the descriptive imbalance: TLR-positive prevalence is `r tlr_by_arm$pct_tlr_pos[1]`% in the control arm and `r tlr_by_arm$pct_tlr_pos[2]`% in the experimental arm. If TLR cleanly captured immunotherapy response one would expect higher TLR-positivity in the experimental arm, not lower. The observed prevalence pattern, together with the OS direction (HR > 1) of the TLR × Rx interaction, is more consistent with TLR acting as a **prognostic** marker (identifying chemotherapy-responsive disease, which is more prevalent in the control arm by chance or by timing) than as a predictive marker for immunotherapy benefit. Possible explanations for the imbalance include small-sample randomization imbalance, a timing artefact (TLR measured at a fixed CT that may occur during different treatment phases across arms), or genuine heterogeneity in the patient mix. Because TLR is itself influenced by treatment, the TLR × Rx interaction is a responder-stratified contrast — useful for hypothesis generation, but not a causal predictive-biomarker estimate.

## TLR landmark analysis (exploratory)

A **week-9 landmark analysis** conditions on survival to the second (first on-treatment) CT — the scan at which TLR is defined — and measures survival from that point, to test whether the responder signal is a guarantee-time artefact. The two endpoints diverge instructively. For **OS**, `r lm_attrition$N_excluded[1]` patients are excluded (no early deaths), so the landmark estimate is identical to the responder estimate (`r format_hr_ci(lm_tlr_firth_os$HR, lm_tlr_firth_os$CI_Lower, lm_tlr_firth_os$CI_Upper)`): the OS signal is not driven by early-death immortal time. For **PFS**, `r lm_attrition$N_excluded[2]` patients are excluded, with `r n_pfs_excl_prog_tn` of the `r n_pfs_excl_prog` excluded progressors being TLR-negative, because progression and TLR are ascertained at the same scan; removing these coupled events moves the Firth TLR × Rx HR from `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` to `r format_hr_ci(lm_tlr_firth_pfs$HR, lm_tlr_firth_pfs$CI_Lower, lm_tlr_firth_pfs$CI_Upper)`. The PFS responder association is therefore partly tautological. Under any time origin TLR remains on the causal path of treatment, so a definitive predictive-biomarker estimate would require causal mediation rather than a landmark. Both analyses remain underpowered and exploratory, and neither supports baseline treatment selection on TLR.

\newpage

# Summary

**Study:** METIMMOX-1 biomarker subgroup analysis. N = `r n_total` complete cases, `r sum(data_complete$Death)` OS events, `r sum(data_complete$Progression)` PFS events (progression or death).

**Methods:** Two Firth-corrected Cox analyses are presented. **Primary (DAG-informed):** `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx` — pre-treatment biomarkers as effect modifiers; TLR omitted because it is post-randomization. **Exploratory responder analysis:** `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx` — adds TLR and its treatment interaction, with CRP and TMB/BRAF retained as prognostic main-effect adjustments. Profile likelihood CIs, PLRT for interaction testing. Ridge sensitivity analysis penalizes the CRP/TMB main effects in the primary model and the TLR terms (main effect + TLR:Rx) in the exploratory model.

**Proportional hazards:** No violations in OS (global p = `r format_pvalue(p_zph_os_global)`). In PFS the global test gives p = `r format_pvalue(p_zph_pfs_global)`, carried by the biomarker main effects (CRP p = `r format_pvalue(p_zph_pfs_crp)`; TMB/BRAF p = `r format_pvalue(p_zph_pfs_tmb)`) rather than the interaction terms (CRP × Rx p = `r format_pvalue(p_zph_pfs_crp_rx)`; TMB/BRAF × Rx p = `r format_pvalue(p_zph_pfs_tmb_rx)`); PFS biomarker main-effect estimates should be read as time-averaged.

**Interaction estimates:**

| Interaction | OS HR (95% CI) | PLRT p | PFS HR (95% CI) | PLRT p |
|-------------|----------------|--------|-----------------|--------|
| CRP × Rx    | `r hr_txt(hr_crp_os)` | `r format_pvalue(p_crp_os)` | `r hr_txt(hr_crp_pfs)` | `r format_pvalue(p_crp_pfs)` |
| TMB/BRAF × Rx | `r hr_txt(hr_tmb_os)` | `r format_pvalue(p_tmb_os)` | `r hr_txt(hr_tmb_pfs)` | `r format_pvalue(p_tmb_pfs)` |

No interaction is statistically significant. CRP × Rx PFS (HR `r hr_pt(hr_crp_pfs)`) is the strongest directional signal but is not stable under Ridge regularization (Ridge HR `r hr_pt(ridge_crp_pfs)`). TMB/BRAF OS shows a near-null interaction (Ridge HR `r hr_pt(ridge_tmb_os)` ≈ Firth `r hr_pt(hr_tmb_os)`). The PFS PH departure concerns the biomarker main effects, not the interaction terms.

**TLR responder analysis (exploratory):** Firth TLR × Rx HR `r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)` for OS and `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` for PFS. Ridge-penalized TLR terms: `r format_ridge_hr(ridge_tlr_os_int$HR, ridge_tlr_os_int$SE)` (OS), `r format_ridge_hr(ridge_tlr_pfs_int$HR, ridge_tlr_pfs_int$SE)` (PFS). PLRT p-values (`r format_pvalue(p_tlr_os)` OS, `r format_pvalue(p_tlr_pfs)` PFS) do not reach conventional significance in this small sample. TLR-positive prevalence: control `r tlr_by_arm$pct_tlr_pos[1]`%, experimental `r tlr_by_arm$pct_tlr_pos[2]`% — markedly higher TLR-positivity in the control arm. The OS direction (HR > 1) of TLR × Rx, combined with the prevalence pattern, is more consistent with TLR acting as a prognostic marker for chemo-responsive disease than as a predictive marker for immunotherapy benefit. Because TLR is post-randomization, this is a responder-stratified, hypothesis-generating contrast rather than a causal predictive-biomarker estimate.

**TLR week-9 landmark analysis (exploratory):** A landmark analysis conditioning on survival to the second (first on-treatment) CT in week 9 — the scan at which TLR is defined — was added. For OS, `r lm_attrition$N_excluded[1]` patients are excluded (no early deaths), so the landmark HR `r format_hr_ci(lm_tlr_firth_os$HR, lm_tlr_firth_os$CI_Lower, lm_tlr_firth_os$CI_Upper)` is identical to the responder value: the OS signal is not an early-death immortal-time artefact. For PFS, `r lm_attrition$N_excluded[2]` patients are excluded, `r n_pfs_excl_prog_tn` of the `r n_pfs_excl_prog` excluded progressors being TLR-negative because progression and TLR are read from the same scan; this shifts the HR from `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` (responder) to `r format_hr_ci(lm_tlr_firth_pfs$HR, lm_tlr_firth_pfs$CI_Lower, lm_tlr_firth_pfs$CI_Upper)` (landmark), exposing the PFS association as partly tautological (PLRT p `r format_pvalue(p_lm_tlr_os)` OS, `r format_pvalue(p_lm_tlr_pfs)` PFS). Both analyses are retained for comparison; both are underpowered and exploratory, and the residual confounding from TLR being treatment-influenced needs causal mediation, not a landmark. Neither supports baseline treatment selection on TLR.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 3.4
