---
title: "METIMMOX-1 Clinical Effectiveness Analysis Report"
subtitle: "Biomarker-Guided Strategies - Firth-Corrected Cox Regression"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
    include-in-header:
      text: |
        \usepackage{fancyhdr}
        \pagestyle{fancy}
        \fancyhead{}
        \renewcommand{\headrulewidth}{0pt}
        \fancyfoot[L]{\rule{\textwidth}{0.4pt}\\ Report Version 2.0 | Completed: \today | METIMMOX-1}
        \fancyfoot[C]{}
        \fancyfoot[R]{\thepage}
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, tidyverse,
  survival,   # Surv object, cox.zph for Schoenfeld, ridge()
  coxphf,     # Firth-corrected Cox regression + coxphftest
  glmnet,     # Ridge regression fallback (alpha=0)
  vcd         # Cramér's V calculation
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r load-data, include=FALSE}
# Source analysis scripts for data loading
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}
```

```{r helper-functions, include=FALSE}
# =============================================================================
# HELPER FUNCTIONS
# =============================================================================

#' Fit Firth-corrected Cox model with profile likelihood CIs
fit_firth_cox <- function(formula, data, label = "model") {
  tryCatch({
    coxphf(
      formula = formula,
      data = data,
      firth = TRUE,
      pl = TRUE,        # Profile likelihood CIs
      maxit = 100,
      maxstep = 0.1
    )
  }, error = function(e) {
    warning(paste("coxphf failed for", label, ":", e$message))
    NULL
  })
}

#' Extract results from coxphf (full table, interactions grouped at top)
#' Note: coxphf ci.lower and ci.upper are ALREADY exponentiated (HR scale)
extract_coxphf_results <- function(model, reorder_interactions = TRUE) {
  if (is.null(model)) return(NULL)

  results <- data.frame(
    Term = names(model$coefficients),
    HR = exp(model$coefficients),
    CI_Lower = model$ci.lower,  # Already on HR scale, do NOT exp()
    CI_Upper = model$ci.upper,  # Already on HR scale, do NOT exp()
    P_Value = model$prob,
    stringsAsFactors = FALSE
  )

  if (reorder_interactions) {
    # Put interaction terms at top
    is_interaction <- grepl(":", results$Term)
    results <- rbind(results[is_interaction, ], results[!is_interaction, ])
  }

  rownames(results) <- NULL
  results
}

#' Penalized Likelihood Ratio Test for specific interaction term
test_interaction_plrt <- function(formula_full, data, interaction_term) {
  test_formula <- as.formula(paste("~", interaction_term))

  tryCatch({
    result <- coxphftest(
      formula = formula_full,
      data = data,
      test = test_formula,
      firth = TRUE
    )
    list(
      term = interaction_term,
      loglik_full = result$loglik[2],
      loglik_restricted = result$loglik[1],
      df = result$df,
      p_value = result$prob
    )
  }, error = function(e) {
    list(term = interaction_term, p_value = NA)
  })
}

#' Apply Benjamini-Hochberg FDR correction
apply_bh_correction <- function(p_values) {
  p.adjust(p_values, method = "BH")
}

#' Format HR with CI for display (vectorized)
format_hr_ci <- function(hr, ci_lower, ci_upper, digits = 2) {
  mapply(function(h, l, u) {
    if (is.na(h)) return("--")
    sprintf(paste0("%.", digits, "f (%.", digits, "f-%.", digits, "f)"), h, l, u)
  }, hr, ci_lower, ci_upper, USE.NAMES = FALSE)
}

#' Format p-value for display (vectorized)
format_pvalue <- function(p, digits = 3) {
  sapply(p, function(pval) {
    if (is.na(pval)) return("--")
    if (pval < 0.001) return("<0.001")
    sprintf(paste0("%.", digits, "f"), pval)
  }, USE.NAMES = FALSE)
}

#' Create forest plot for interaction HRs
create_interaction_forest_plot <- function(results_df, outcome = "OS") {
  ggplot(results_df,
         aes(x = HR, y = Biomarker, color = Model, shape = Model)) +
    geom_point(position = position_dodge(width = 0.5), size = 3) +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper),
                   position = position_dodge(width = 0.5), height = 0.2) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4, 10),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4", "10")) +
    scale_color_manual(
      values = c("A: All-in-One" = "#E69F00",
                 "B: Focused" = "#56B4E9",
                 "C: Single" = "#009E73"),
      name = "Model Type"
    ) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = paste("Treatment × Biomarker Interaction:", outcome),
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

#' Create log-log survival plot for PH diagnostics
create_loglog_plot <- function(data, time_var, event_var, strata_var, title) {
  formula <- as.formula(paste0("Surv(", time_var, ", ", event_var, ") ~ ", strata_var))
  km_fit <- survfit(formula, data = data)

  # Extract survival data
  surv_summary <- summary(km_fit)

  plot_data <- data.frame(
    time = surv_summary$time,
    surv = surv_summary$surv,
    strata = surv_summary$strata
  ) %>%
    filter(surv > 0 & surv < 1) %>%
    mutate(
      log_time = log(time),
      log_log_surv = log(-log(surv))
    )

  ggplot(plot_data, aes(x = log_time, y = log_log_surv, color = strata)) +
    geom_step(linewidth = 1) +
    labs(
      x = "log(Time in weeks)",
      y = "-log(-log(S(t)))",
      title = title,
      subtitle = "Parallel lines support PH assumption",
      color = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

```{r data-preparation, include=FALSE}
# =============================================================================
# DATA PREPARATION
# =============================================================================

# Prepare data for Cox models
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

# Ensure proper factor coding
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)

# Biomarkers as numeric 0/1 for coxphf (interactions work better with numeric)
data_complete$crp_num <- as.numeric(as.character(data_complete$crp))
data_complete$tlr_num <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf_num <- as.numeric(as.character(data_complete$tmb_braf))

# Create numeric Rx for ridge regression
data_complete$Rx_num <- as.numeric(data_complete$Rx) - 1  # 0 = Control, 1 = Experimental

# Sample characteristics
n_total <- nrow(data_complete)
n_control <- sum(data_complete$Rx_num == 0)
n_experimental <- sum(data_complete$Rx_num == 1)

# Biomarker prevalence
prev_crp <- mean(data_complete$crp_num)
prev_tlr <- mean(data_complete$tlr_num)
prev_tmb_braf <- mean(data_complete$tmb_braf_num)

# Event counts
n_deaths <- sum(data_complete$Death)
n_progressions <- sum(data_complete$Progression)
```

```{r biomarker-correlation, include=FALSE}
# =============================================================================
# BIOMARKER CORRELATION ANALYSIS (Cramér's V)
# =============================================================================

# CRP vs TLR
crp_tlr_table <- table(data_complete$crp_num, data_complete$tlr_num)
crp_tlr_assoc <- assocstats(crp_tlr_table)
cramers_v_crp_tlr <- crp_tlr_assoc$cramer

# CRP vs TMB/BRAF
crp_tmb_table <- table(data_complete$crp_num, data_complete$tmb_braf_num)
crp_tmb_assoc <- assocstats(crp_tmb_table)
cramers_v_crp_tmb <- crp_tmb_assoc$cramer

# TLR vs TMB/BRAF
tlr_tmb_table <- table(data_complete$tlr_num, data_complete$tmb_braf_num)
tlr_tmb_assoc <- assocstats(tlr_tmb_table)
cramers_v_tlr_tmb <- tlr_tmb_assoc$cramer

# Build correlation summary
correlation_df <- data.frame(
  Comparison = c("CRP vs TLR", "CRP vs TMB/BRAF", "TLR vs TMB/BRAF"),
  Cramers_V = round(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), 3),
  Interpretation = sapply(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), function(v) {
    if (v > 0.3) "Moderate/Strong"
    else if (v > 0.1) "Weak"
    else "Negligible"
  })
)
```

# Overview

This report presents clinical effectiveness results from the METIMMOX-1 trial, evaluating biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer.

The analysis uses **Firth-corrected Cox proportional hazards regression** with profile likelihood confidence intervals to assess treatment effect heterogeneity across three candidate biomarkers:

- **CRP** (C-reactive protein): Low CRP (<5 mg/L) at baseline
- **TLR** (Tumor Lesion Reduction): Early response (≥10% reduction at first CT scan)
- **TMB/BRAF**: High tumor mutational burden (≥9 mut/MB) or BRAF mutation

We compare three model structures to assess the robustness of treatment-biomarker interactions:

- **Model A**: All-in-one model with all biomarkers and interactions
- **Model B**: Focused models with all biomarkers but only one interaction per model
- **Model C**: Single-biomarker models with one biomarker and its interaction

# Methodological Notes

## Firth-Corrected Cox Regression

We use Firth's penalized maximum likelihood method for Cox regression, which addresses:

1. **Monotone likelihood**: When a covariate perfectly separates events from non-events
2. **Small sample bias**: Reduces bias in coefficient estimates with sparse data
3. **Unstable confidence intervals**: Profile likelihood CIs are more reliable than Wald-based CIs in small samples

Statistical inference is based on **penalized likelihood ratio tests** (PLRT), which are more appropriate than Wald tests for testing treatment-biomarker interactions in this setting.

## Why Not LASSO or Elastic Net

We considered LASSO and elastic net penalized regression but determined they are **not appropriate** for this analysis:

1. **Correlated biomarkers**: Our biomarkers show significant correlation (Cramér's V reported below). LASSO arbitrarily selects one of correlated predictors while setting others to zero, which does not reflect the clinical question of comparing ALL biomarker strategies.

2. **Hierarchy principle violation**: LASSO may select interaction terms (e.g., `crp:Rx`) while setting the main effect (`crp`) to zero, producing models that are difficult to interpret clinically.

3. **Clinical objective**: Our goal is to estimate treatment effect heterogeneity across ALL biomarkers simultaneously, not to select a "winning" biomarker.

**Elastic net** (α = 0.1-0.3) represents a compromise but does not fully address these concerns. Instead, we use **Ridge regression** (α = 0) as a sensitivity analysis, which shrinks but does not eliminate coefficients.

## Multiple Testing Correction

We apply the **Benjamini-Hochberg procedure** to control the false discovery rate (FDR) on the primary Firth analysis:

- 6 interaction tests: 3 biomarkers × 2 outcomes (OS, PFS)
- Both raw PLRT p-values and BH-adjusted q-values are reported
- The Ridge sensitivity analysis does not require separate multiplicity correction

# Data Preparation

## Sample Characteristics

```{r table-sample}
sample_df <- data.frame(
  Characteristic = c("Total patients (complete cases)",
                     "Control arm (FLOX alone)",
                     "Experimental arm (alternating FLOX/nivolumab)",
                     "",
                     "Deaths (OS events)",
                     "Progressions (PFS events)",
                     "",
                     "CRP-positive (low CRP)",
                     "TLR-positive (early response)",
                     "TMB/BRAF-positive"),
  Value = c(n_total,
            paste0(n_control, " (", round(100*n_control/n_total, 1), "%)"),
            paste0(n_experimental, " (", round(100*n_experimental/n_total, 1), "%)"),
            "",
            paste0(n_deaths, " (", round(100*n_deaths/n_total, 1), "%)"),
            paste0(n_progressions, " (", round(100*n_progressions/n_total, 1), "%)"),
            "",
            paste0(sum(data_complete$crp_num), " (", round(100*prev_crp, 1), "%)"),
            paste0(sum(data_complete$tlr_num), " (", round(100*prev_tlr, 1), "%)"),
            paste0(sum(data_complete$tmb_braf_num), " (", round(100*prev_tmb_braf, 1), "%)"))
)

sample_df %>%
  kable(col.names = c("Characteristic", "N (%)"),
        caption = "Sample Characteristics",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  row_spec(c(4, 7), bold = FALSE, extra_css = "border-bottom: none;")
```

## Biomarker Correlations

```{r table-correlation}
correlation_df %>%
  kable(col.names = c("Biomarker Pair", "Cramér's V", "Interpretation"),
        caption = "Biomarker Correlations (Cramér's V)",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

**Note:** Cramér's V interpretation: <0.1 = Negligible, 0.1-0.3 = Weak, >0.3 = Moderate/Strong. These correlations support our decision not to use LASSO, which would arbitrarily select among correlated biomarkers.

\newpage

# Proportional Hazards Assumption

```{r ph-diagnostics, include=FALSE}
# =============================================================================
# PROPORTIONAL HAZARDS DIAGNOSTICS
# =============================================================================

# Fit standard coxph for Schoenfeld tests (not available in coxphf)
# Use Model A formula structure
formula_diag_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                       crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx
formula_diag_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                               crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx

coxph_diag_os <- coxph(formula_diag_os, data = data_complete)
coxph_diag_pfs <- coxph(formula_diag_pfs, data = data_complete)

# Schoenfeld residual tests
zph_os <- cox.zph(coxph_diag_os)
zph_pfs <- cox.zph(coxph_diag_pfs)

# Extract results
zph_os_df <- as.data.frame(zph_os$table)
zph_pfs_df <- as.data.frame(zph_pfs$table)
```

## Schoenfeld Residual Tests

The proportional hazards assumption was tested using scaled Schoenfeld residuals. A significant p-value indicates potential violation of the PH assumption for that covariate.

```{r table-schoenfeld}
# Combine OS and PFS results
schoenfeld_df <- data.frame(
  Covariate = rownames(zph_os_df),
  Chi_sq_OS = round(zph_os_df$chisq, 2),
  P_OS = format_pvalue(zph_os_df$p),
  Chi_sq_PFS = round(zph_pfs_df$chisq, 2),
  P_PFS = format_pvalue(zph_pfs_df$p)
)

schoenfeld_df %>%
  kable(col.names = c("Covariate", "χ² (OS)", "p-value", "χ² (PFS)", "p-value"),
        caption = "Schoenfeld Residual Test for Proportional Hazards Assumption",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  row_spec(nrow(schoenfeld_df), bold = TRUE)
```

**Note:** GLOBAL is the omnibus test for all covariates. Individual covariate tests help identify specific PH violations.

## Log-Log Survival Plots

```{r loglog-plots, fig.height=8, fig.width=10}
# Create log-log plots by treatment arm
p1 <- create_loglog_plot(data_complete, "OSwk", "Death", "Rx",
                         "Overall Survival by Treatment")
p2 <- create_loglog_plot(data_complete, "PFSwk", "Progression", "Rx",
                         "Progression-Free Survival by Treatment")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

**Interpretation:** Approximately parallel lines on the log-log plot support the proportional hazards assumption. Crossing or converging lines suggest time-varying effects.

\newpage

# Primary Analysis: Firth-Corrected Cox Models

```{r fit-all-models, include=FALSE}
# =============================================================================
# FIT ALL FIRTH-CORRECTED COX MODELS
# =============================================================================

# -----------------------------------------------------------------------------
# Model Type A: All-in-One (all biomarkers, all interactions)
# -----------------------------------------------------------------------------
formula_A_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                    crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx
formula_A_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num +
                                            crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx

model_A_os <- fit_firth_cox(formula_A_os, data_complete, "Model A OS")
model_A_pfs <- fit_firth_cox(formula_A_pfs, data_complete, "Model A PFS")

# -----------------------------------------------------------------------------
# Model Type B: Focused Models (all biomarkers, one interaction each)
# -----------------------------------------------------------------------------

# CRP focus
formula_B_crp_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num + crp_num:Rx
formula_B_crp_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num + crp_num:Rx

model_B_crp_os <- fit_firth_cox(formula_B_crp_os, data_complete, "Model B CRP OS")
model_B_crp_pfs <- fit_firth_cox(formula_B_crp_pfs, data_complete, "Model B CRP PFS")

# TLR focus
formula_B_tlr_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num + tlr_num:Rx
formula_B_tlr_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num + tlr_num:Rx

model_B_tlr_os <- fit_firth_cox(formula_B_tlr_os, data_complete, "Model B TLR OS")
model_B_tlr_pfs <- fit_firth_cox(formula_B_tlr_pfs, data_complete, "Model B TLR PFS")

# TMB/BRAF focus
formula_B_tmb_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num + tmb_braf_num:Rx
formula_B_tmb_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tlr_num + tmb_braf_num + tmb_braf_num:Rx

model_B_tmb_os <- fit_firth_cox(formula_B_tmb_os, data_complete, "Model B TMB OS")
model_B_tmb_pfs <- fit_firth_cox(formula_B_tmb_pfs, data_complete, "Model B TMB PFS")

# -----------------------------------------------------------------------------
# Model Type C: Single-Biomarker Models (one biomarker + interaction)
# -----------------------------------------------------------------------------

# CRP only
formula_C_crp_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + crp_num:Rx
formula_C_crp_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + crp_num:Rx

model_C_crp_os <- fit_firth_cox(formula_C_crp_os, data_complete, "Model C CRP OS")
model_C_crp_pfs <- fit_firth_cox(formula_C_crp_pfs, data_complete, "Model C CRP PFS")

# TLR only
formula_C_tlr_os <- Surv(OSwk, Death) ~ Age + sex + Rx + tlr_num + tlr_num:Rx
formula_C_tlr_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + tlr_num + tlr_num:Rx

model_C_tlr_os <- fit_firth_cox(formula_C_tlr_os, data_complete, "Model C TLR OS")
model_C_tlr_pfs <- fit_firth_cox(formula_C_tlr_pfs, data_complete, "Model C TLR PFS")

# TMB/BRAF only
formula_C_tmb_os <- Surv(OSwk, Death) ~ Age + sex + Rx + tmb_braf_num + tmb_braf_num:Rx
formula_C_tmb_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + tmb_braf_num + tmb_braf_num:Rx

model_C_tmb_os <- fit_firth_cox(formula_C_tmb_os, data_complete, "Model C TMB OS")
model_C_tmb_pfs <- fit_firth_cox(formula_C_tmb_pfs, data_complete, "Model C TMB PFS")
```

```{r plrt-tests, include=FALSE}
# =============================================================================
# PENALIZED LIKELIHOOD RATIO TESTS FOR INTERACTIONS
# =============================================================================

# Model A interaction tests
plrt_A_crp_os <- test_interaction_plrt(formula_A_os, data_complete, "crp_num:Rx")
plrt_A_tlr_os <- test_interaction_plrt(formula_A_os, data_complete, "tlr_num:Rx")
plrt_A_tmb_os <- test_interaction_plrt(formula_A_os, data_complete, "tmb_braf_num:Rx")

plrt_A_crp_pfs <- test_interaction_plrt(formula_A_pfs, data_complete, "crp_num:Rx")
plrt_A_tlr_pfs <- test_interaction_plrt(formula_A_pfs, data_complete, "tlr_num:Rx")
plrt_A_tmb_pfs <- test_interaction_plrt(formula_A_pfs, data_complete, "tmb_braf_num:Rx")

# Model B interaction tests (one per model)
plrt_B_crp_os <- test_interaction_plrt(formula_B_crp_os, data_complete, "crp_num:Rx")
plrt_B_tlr_os <- test_interaction_plrt(formula_B_tlr_os, data_complete, "tlr_num:Rx")
plrt_B_tmb_os <- test_interaction_plrt(formula_B_tmb_os, data_complete, "tmb_braf_num:Rx")

plrt_B_crp_pfs <- test_interaction_plrt(formula_B_crp_pfs, data_complete, "crp_num:Rx")
plrt_B_tlr_pfs <- test_interaction_plrt(formula_B_tlr_pfs, data_complete, "tlr_num:Rx")
plrt_B_tmb_pfs <- test_interaction_plrt(formula_B_tmb_pfs, data_complete, "tmb_braf_num:Rx")

# Model C interaction tests
plrt_C_crp_os <- test_interaction_plrt(formula_C_crp_os, data_complete, "crp_num:Rx")
plrt_C_tlr_os <- test_interaction_plrt(formula_C_tlr_os, data_complete, "tlr_num:Rx")
plrt_C_tmb_os <- test_interaction_plrt(formula_C_tmb_os, data_complete, "tmb_braf_num:Rx")

plrt_C_crp_pfs <- test_interaction_plrt(formula_C_crp_pfs, data_complete, "crp_num:Rx")
plrt_C_tlr_pfs <- test_interaction_plrt(formula_C_tlr_pfs, data_complete, "tlr_num:Rx")
plrt_C_tmb_pfs <- test_interaction_plrt(formula_C_tmb_pfs, data_complete, "tmb_braf_num:Rx")

# Collect all p-values for BH correction (using Model A as primary)
all_pvalues <- c(
  plrt_A_crp_os$p_value, plrt_A_tlr_os$p_value, plrt_A_tmb_os$p_value,
  plrt_A_crp_pfs$p_value, plrt_A_tlr_pfs$p_value, plrt_A_tmb_pfs$p_value
)

# Apply BH correction
bh_adjusted <- apply_bh_correction(all_pvalues)
names(bh_adjusted) <- c("CRP_OS", "TLR_OS", "TMB_OS", "CRP_PFS", "TLR_PFS", "TMB_PFS")
```

```{r extract-results, include=FALSE}
# =============================================================================
# EXTRACT RESULTS FROM ALL MODELS
# =============================================================================

results_A_os <- extract_coxphf_results(model_A_os)
results_A_pfs <- extract_coxphf_results(model_A_pfs)

results_B_crp_os <- extract_coxphf_results(model_B_crp_os)
results_B_crp_pfs <- extract_coxphf_results(model_B_crp_pfs)
results_B_tlr_os <- extract_coxphf_results(model_B_tlr_os)
results_B_tlr_pfs <- extract_coxphf_results(model_B_tlr_pfs)
results_B_tmb_os <- extract_coxphf_results(model_B_tmb_os)
results_B_tmb_pfs <- extract_coxphf_results(model_B_tmb_pfs)

results_C_crp_os <- extract_coxphf_results(model_C_crp_os)
results_C_crp_pfs <- extract_coxphf_results(model_C_crp_pfs)
results_C_tlr_os <- extract_coxphf_results(model_C_tlr_os)
results_C_tlr_pfs <- extract_coxphf_results(model_C_tlr_pfs)
results_C_tmb_os <- extract_coxphf_results(model_C_tmb_os)
results_C_tmb_pfs <- extract_coxphf_results(model_C_tmb_pfs)
```

## Model Type A: All-in-One Model

This model includes all three biomarkers as main effects and all three treatment-biomarker interactions simultaneously.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx + tlr:Rx + tmb_braf:Rx`

### Overall Survival (Model A)

```{r table-A-os}
if (!is.null(results_A_os)) {
  # Add PLRT p-values for interaction terms
  results_A_os$PLRT_p <- NA
  results_A_os$BH_adj_p <- NA

  # Match interaction terms
  crp_idx <- grep("crp_num.*Rx|Rx.*crp_num", results_A_os$Term)
  tlr_idx <- grep("tlr_num.*Rx|Rx.*tlr_num", results_A_os$Term)
  tmb_idx <- grep("tmb_braf_num.*Rx|Rx.*tmb_braf_num", results_A_os$Term)

  if (length(crp_idx) > 0) {
    results_A_os$PLRT_p[crp_idx] <- plrt_A_crp_os$p_value
    results_A_os$BH_adj_p[crp_idx] <- bh_adjusted["CRP_OS"]
  }
  if (length(tlr_idx) > 0) {
    results_A_os$PLRT_p[tlr_idx] <- plrt_A_tlr_os$p_value
    results_A_os$BH_adj_p[tlr_idx] <- bh_adjusted["TLR_OS"]
  }
  if (length(tmb_idx) > 0) {
    results_A_os$PLRT_p[tmb_idx] <- plrt_A_tmb_os$p_value
    results_A_os$BH_adj_p[tmb_idx] <- bh_adjusted["TMB_OS"]
  }

  # Format for display
  display_A_os <- results_A_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(PLRT_p),
      BH_adj_p = format_pvalue(BH_adj_p)
    ) %>%
    select(Term, HR_CI, PLRT_p, BH_adj_p)

  display_A_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value", "BH-adjusted p"),
          caption = "Model A Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment × Biomarker Interactions", 1, 3, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 4, nrow(display_A_os), bold = TRUE)
}
```

### Progression-Free Survival (Model A)

```{r table-A-pfs}
if (!is.null(results_A_pfs)) {
  # Add PLRT p-values for interaction terms
  results_A_pfs$PLRT_p <- NA
  results_A_pfs$BH_adj_p <- NA

  crp_idx <- grep("crp_num.*Rx|Rx.*crp_num", results_A_pfs$Term)
  tlr_idx <- grep("tlr_num.*Rx|Rx.*tlr_num", results_A_pfs$Term)
  tmb_idx <- grep("tmb_braf_num.*Rx|Rx.*tmb_braf_num", results_A_pfs$Term)

  if (length(crp_idx) > 0) {
    results_A_pfs$PLRT_p[crp_idx] <- plrt_A_crp_pfs$p_value
    results_A_pfs$BH_adj_p[crp_idx] <- bh_adjusted["CRP_PFS"]
  }
  if (length(tlr_idx) > 0) {
    results_A_pfs$PLRT_p[tlr_idx] <- plrt_A_tlr_pfs$p_value
    results_A_pfs$BH_adj_p[tlr_idx] <- bh_adjusted["TLR_PFS"]
  }
  if (length(tmb_idx) > 0) {
    results_A_pfs$PLRT_p[tmb_idx] <- plrt_A_tmb_pfs$p_value
    results_A_pfs$BH_adj_p[tmb_idx] <- bh_adjusted["TMB_PFS"]
  }

  display_A_pfs <- results_A_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(PLRT_p),
      BH_adj_p = format_pvalue(BH_adj_p)
    ) %>%
    select(Term, HR_CI, PLRT_p, BH_adj_p)

  display_A_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value", "BH-adjusted p"),
          caption = "Model A Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
    pack_rows("Treatment × Biomarker Interactions", 1, 3, bold = TRUE) %>%
    pack_rows("Main Effects and Covariates", 4, nrow(display_A_pfs), bold = TRUE)
}
```

\newpage

## Model B: Focused Models

These models include all three biomarkers as main effects but only ONE treatment-biomarker interaction per model. This approach tests each interaction while controlling for all biomarkers.

```{r table-B-summary}
# Extract interaction HRs from Model B
get_interaction_hr <- function(results_df, pattern) {
  if (is.null(results_df)) return(list(HR = NA, CI_Lower = NA, CI_Upper = NA))
  idx <- grep(pattern, results_df$Term)
  if (length(idx) == 0) return(list(HR = NA, CI_Lower = NA, CI_Upper = NA))
  list(HR = results_df$HR[idx[1]],
       CI_Lower = results_df$CI_Lower[idx[1]],
       CI_Upper = results_df$CI_Upper[idx[1]])
}

# OS results
hr_B_crp_os <- get_interaction_hr(results_B_crp_os, "crp_num.*Rx|Rx.*crp_num")
hr_B_tlr_os <- get_interaction_hr(results_B_tlr_os, "tlr_num.*Rx|Rx.*tlr_num")
hr_B_tmb_os <- get_interaction_hr(results_B_tmb_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# PFS results
hr_B_crp_pfs <- get_interaction_hr(results_B_crp_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_B_tlr_pfs <- get_interaction_hr(results_B_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")
hr_B_tmb_pfs <- get_interaction_hr(results_B_tmb_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

model_B_summary <- data.frame(
  Biomarker = c("CRP × Treatment", "TLR × Treatment", "TMB/BRAF × Treatment"),
  HR_OS = c(
    format_hr_ci(hr_B_crp_os$HR, hr_B_crp_os$CI_Lower, hr_B_crp_os$CI_Upper),
    format_hr_ci(hr_B_tlr_os$HR, hr_B_tlr_os$CI_Lower, hr_B_tlr_os$CI_Upper),
    format_hr_ci(hr_B_tmb_os$HR, hr_B_tmb_os$CI_Lower, hr_B_tmb_os$CI_Upper)
  ),
  P_OS = c(
    format_pvalue(plrt_B_crp_os$p_value),
    format_pvalue(plrt_B_tlr_os$p_value),
    format_pvalue(plrt_B_tmb_os$p_value)
  ),
  HR_PFS = c(
    format_hr_ci(hr_B_crp_pfs$HR, hr_B_crp_pfs$CI_Lower, hr_B_crp_pfs$CI_Upper),
    format_hr_ci(hr_B_tlr_pfs$HR, hr_B_tlr_pfs$CI_Lower, hr_B_tlr_pfs$CI_Upper),
    format_hr_ci(hr_B_tmb_pfs$HR, hr_B_tmb_pfs$CI_Lower, hr_B_tmb_pfs$CI_Upper)
  ),
  P_PFS = c(
    format_pvalue(plrt_B_crp_pfs$p_value),
    format_pvalue(plrt_B_tlr_pfs$p_value),
    format_pvalue(plrt_B_tmb_pfs$p_value)
  )
)

model_B_summary %>%
  kable(col.names = c("Interaction Term", "HR (95% CI)", "PLRT p", "HR (95% CI)", "PLRT p"),
        caption = "Model B: Focused Models - Treatment × Biomarker Interaction Summary",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  add_header_above(c(" " = 1, "Overall Survival" = 2, "Progression-Free Survival" = 2))
```

**Note:** Each row represents a separate model with all biomarkers as main effects but only the specified interaction.

### Full Coefficient Tables

```{r table-B-crp-os}
if (!is.null(results_B_crp_os)) {
  display_B_crp_os <- results_B_crp_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_crp_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B CRP-Focused: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-crp-pfs}
if (!is.null(results_B_crp_pfs)) {
  display_B_crp_pfs <- results_B_crp_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_crp_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B CRP-Focused: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-tlr-os}
if (!is.null(results_B_tlr_os)) {
  display_B_tlr_os <- results_B_tlr_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B TLR-Focused: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-tlr-pfs}
if (!is.null(results_B_tlr_pfs)) {
  display_B_tlr_pfs <- results_B_tlr_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B TLR-Focused: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-tmb-os}
if (!is.null(results_B_tmb_os)) {
  display_B_tmb_os <- results_B_tmb_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_tmb_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B TMB/BRAF-Focused: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-B-tmb-pfs}
if (!is.null(results_B_tmb_pfs)) {
  display_B_tmb_pfs <- results_B_tmb_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_B_tmb_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model B TMB/BRAF-Focused: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

## Model C: Single-Biomarker Models

These models include only ONE biomarker and its treatment interaction. This is the simplest specification but does not control for other biomarkers.

```{r table-C-summary}
# Extract interaction HRs from Model C
hr_C_crp_os <- get_interaction_hr(results_C_crp_os, "crp_num.*Rx|Rx.*crp_num")
hr_C_tlr_os <- get_interaction_hr(results_C_tlr_os, "tlr_num.*Rx|Rx.*tlr_num")
hr_C_tmb_os <- get_interaction_hr(results_C_tmb_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

hr_C_crp_pfs <- get_interaction_hr(results_C_crp_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_C_tlr_pfs <- get_interaction_hr(results_C_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")
hr_C_tmb_pfs <- get_interaction_hr(results_C_tmb_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

model_C_summary <- data.frame(
  Biomarker = c("CRP × Treatment", "TLR × Treatment", "TMB/BRAF × Treatment"),
  HR_OS = c(
    format_hr_ci(hr_C_crp_os$HR, hr_C_crp_os$CI_Lower, hr_C_crp_os$CI_Upper),
    format_hr_ci(hr_C_tlr_os$HR, hr_C_tlr_os$CI_Lower, hr_C_tlr_os$CI_Upper),
    format_hr_ci(hr_C_tmb_os$HR, hr_C_tmb_os$CI_Lower, hr_C_tmb_os$CI_Upper)
  ),
  P_OS = c(
    format_pvalue(plrt_C_crp_os$p_value),
    format_pvalue(plrt_C_tlr_os$p_value),
    format_pvalue(plrt_C_tmb_os$p_value)
  ),
  HR_PFS = c(
    format_hr_ci(hr_C_crp_pfs$HR, hr_C_crp_pfs$CI_Lower, hr_C_crp_pfs$CI_Upper),
    format_hr_ci(hr_C_tlr_pfs$HR, hr_C_tlr_pfs$CI_Lower, hr_C_tlr_pfs$CI_Upper),
    format_hr_ci(hr_C_tmb_pfs$HR, hr_C_tmb_pfs$CI_Lower, hr_C_tmb_pfs$CI_Upper)
  ),
  P_PFS = c(
    format_pvalue(plrt_C_crp_pfs$p_value),
    format_pvalue(plrt_C_tlr_pfs$p_value),
    format_pvalue(plrt_C_tmb_pfs$p_value)
  )
)

model_C_summary %>%
  kable(col.names = c("Interaction Term", "HR (95% CI)", "PLRT p", "HR (95% CI)", "PLRT p"),
        caption = "Model C: Single-Biomarker Models - Treatment × Biomarker Interaction Summary",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  add_header_above(c(" " = 1, "Overall Survival" = 2, "Progression-Free Survival" = 2))
```

**Note:** Each row represents a separate model with only that biomarker and its interaction (no other biomarkers included).

### Full Coefficient Tables

```{r table-C-crp-os}
if (!is.null(results_C_crp_os)) {
  display_C_crp_os <- results_C_crp_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_crp_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C CRP-Only: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-crp-pfs}
if (!is.null(results_C_crp_pfs)) {
  display_C_crp_pfs <- results_C_crp_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_crp_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C CRP-Only: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tlr-os}
if (!is.null(results_C_tlr_os)) {
  display_C_tlr_os <- results_C_tlr_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TLR-Only: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tlr-pfs}
if (!is.null(results_C_tlr_pfs)) {
  display_C_tlr_pfs <- results_C_tlr_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TLR-Only: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tmb-os}
if (!is.null(results_C_tmb_os)) {
  display_C_tmb_os <- results_C_tmb_os %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tmb_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TMB/BRAF-Only: Overall Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

```{r table-C-tmb-pfs}
if (!is.null(results_C_tmb_pfs)) {
  display_C_tmb_pfs <- results_C_tmb_pfs %>%
    mutate(
      HR_CI = format_hr_ci(HR, CI_Lower, CI_Upper),
      P = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, P)

  display_C_tmb_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "p-value"),
          caption = "Model C TMB/BRAF-Only: Progression-Free Survival - Full Coefficients",
          booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

# Model Comparison

## Summary: Interaction HRs Across Model Types

```{r comparison-table-os}
# Get Model A interaction HRs
hr_A_crp_os <- get_interaction_hr(results_A_os, "crp_num.*Rx|Rx.*crp_num")
hr_A_tlr_os <- get_interaction_hr(results_A_os, "tlr_num.*Rx|Rx.*tlr_num")
hr_A_tmb_os <- get_interaction_hr(results_A_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

comparison_os <- data.frame(
  Biomarker = c("CRP × Rx", "TLR × Rx", "TMB/BRAF × Rx"),
  Model_A = c(
    format_hr_ci(hr_A_crp_os$HR, hr_A_crp_os$CI_Lower, hr_A_crp_os$CI_Upper),
    format_hr_ci(hr_A_tlr_os$HR, hr_A_tlr_os$CI_Lower, hr_A_tlr_os$CI_Upper),
    format_hr_ci(hr_A_tmb_os$HR, hr_A_tmb_os$CI_Lower, hr_A_tmb_os$CI_Upper)
  ),
  Model_B = c(
    format_hr_ci(hr_B_crp_os$HR, hr_B_crp_os$CI_Lower, hr_B_crp_os$CI_Upper),
    format_hr_ci(hr_B_tlr_os$HR, hr_B_tlr_os$CI_Lower, hr_B_tlr_os$CI_Upper),
    format_hr_ci(hr_B_tmb_os$HR, hr_B_tmb_os$CI_Lower, hr_B_tmb_os$CI_Upper)
  ),
  Model_C = c(
    format_hr_ci(hr_C_crp_os$HR, hr_C_crp_os$CI_Lower, hr_C_crp_os$CI_Upper),
    format_hr_ci(hr_C_tlr_os$HR, hr_C_tlr_os$CI_Lower, hr_C_tlr_os$CI_Upper),
    format_hr_ci(hr_C_tmb_os$HR, hr_C_tmb_os$CI_Lower, hr_C_tmb_os$CI_Upper)
  )
)

comparison_os %>%
  kable(col.names = c("Interaction", "Model A", "Model B", "Model C"),
        caption = "Overall Survival: Treatment × Biomarker Interactions Across Model Types",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Model A: All-in-one; Model B: Focused; Model C: Single biomarker.",
           footnote_as_chunk = TRUE)
```

```{r comparison-table-pfs}
hr_A_crp_pfs <- get_interaction_hr(results_A_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_A_tlr_pfs <- get_interaction_hr(results_A_pfs, "tlr_num.*Rx|Rx.*tlr_num")
hr_A_tmb_pfs <- get_interaction_hr(results_A_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

comparison_pfs <- data.frame(
  Biomarker = c("CRP × Rx", "TLR × Rx", "TMB/BRAF × Rx"),
  Model_A = c(
    format_hr_ci(hr_A_crp_pfs$HR, hr_A_crp_pfs$CI_Lower, hr_A_crp_pfs$CI_Upper),
    format_hr_ci(hr_A_tlr_pfs$HR, hr_A_tlr_pfs$CI_Lower, hr_A_tlr_pfs$CI_Upper),
    format_hr_ci(hr_A_tmb_pfs$HR, hr_A_tmb_pfs$CI_Lower, hr_A_tmb_pfs$CI_Upper)
  ),
  Model_B = c(
    format_hr_ci(hr_B_crp_pfs$HR, hr_B_crp_pfs$CI_Lower, hr_B_crp_pfs$CI_Upper),
    format_hr_ci(hr_B_tlr_pfs$HR, hr_B_tlr_pfs$CI_Lower, hr_B_tlr_pfs$CI_Upper),
    format_hr_ci(hr_B_tmb_pfs$HR, hr_B_tmb_pfs$CI_Lower, hr_B_tmb_pfs$CI_Upper)
  ),
  Model_C = c(
    format_hr_ci(hr_C_crp_pfs$HR, hr_C_crp_pfs$CI_Lower, hr_C_crp_pfs$CI_Upper),
    format_hr_ci(hr_C_tlr_pfs$HR, hr_C_tlr_pfs$CI_Lower, hr_C_tlr_pfs$CI_Upper),
    format_hr_ci(hr_C_tmb_pfs$HR, hr_C_tmb_pfs$CI_Lower, hr_C_tmb_pfs$CI_Upper)
  )
)

comparison_pfs %>%
  kable(col.names = c("Interaction", "Model A", "Model B", "Model C"),
        caption = "Progression-Free Survival: Treatment × Biomarker Interactions Across Model Types",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "Model A: All-in-one; Model B: Focused; Model C: Single biomarker.",
           footnote_as_chunk = TRUE)
```

\newpage

## Forest Plots

```{r forest-plot-os, fig.height=5, fig.width=9}
# Prepare data for forest plot - OS
forest_data_os <- data.frame(
  Biomarker = rep(c("CRP", "TLR", "TMB/BRAF"), 3),
  Model = rep(c("A: All-in-One", "B: Focused", "C: Single"), each = 3),
  HR = c(
    hr_A_crp_os$HR, hr_A_tlr_os$HR, hr_A_tmb_os$HR,
    hr_B_crp_os$HR, hr_B_tlr_os$HR, hr_B_tmb_os$HR,
    hr_C_crp_os$HR, hr_C_tlr_os$HR, hr_C_tmb_os$HR
  ),
  CI_Lower = c(
    hr_A_crp_os$CI_Lower, hr_A_tlr_os$CI_Lower, hr_A_tmb_os$CI_Lower,
    hr_B_crp_os$CI_Lower, hr_B_tlr_os$CI_Lower, hr_B_tmb_os$CI_Lower,
    hr_C_crp_os$CI_Lower, hr_C_tlr_os$CI_Lower, hr_C_tmb_os$CI_Lower
  ),
  CI_Upper = c(
    hr_A_crp_os$CI_Upper, hr_A_tlr_os$CI_Upper, hr_A_tmb_os$CI_Upper,
    hr_B_crp_os$CI_Upper, hr_B_tlr_os$CI_Upper, hr_B_tmb_os$CI_Upper,
    hr_C_crp_os$CI_Upper, hr_C_tlr_os$CI_Upper, hr_C_tmb_os$CI_Upper
  )
)

# Remove NA values
forest_data_os <- forest_data_os[complete.cases(forest_data_os), ]

if (nrow(forest_data_os) > 0) {
  create_interaction_forest_plot(forest_data_os, "Overall Survival")
}
```

```{r forest-plot-pfs, fig.height=5, fig.width=9}
# Prepare data for forest plot - PFS
forest_data_pfs <- data.frame(
  Biomarker = rep(c("CRP", "TLR", "TMB/BRAF"), 3),
  Model = rep(c("A: All-in-One", "B: Focused", "C: Single"), each = 3),
  HR = c(
    hr_A_crp_pfs$HR, hr_A_tlr_pfs$HR, hr_A_tmb_pfs$HR,
    hr_B_crp_pfs$HR, hr_B_tlr_pfs$HR, hr_B_tmb_pfs$HR,
    hr_C_crp_pfs$HR, hr_C_tlr_pfs$HR, hr_C_tmb_pfs$HR
  ),
  CI_Lower = c(
    hr_A_crp_pfs$CI_Lower, hr_A_tlr_pfs$CI_Lower, hr_A_tmb_pfs$CI_Lower,
    hr_B_crp_pfs$CI_Lower, hr_B_tlr_pfs$CI_Lower, hr_B_tmb_pfs$CI_Lower,
    hr_C_crp_pfs$CI_Lower, hr_C_tlr_pfs$CI_Lower, hr_C_tmb_pfs$CI_Lower
  ),
  CI_Upper = c(
    hr_A_crp_pfs$CI_Upper, hr_A_tlr_pfs$CI_Upper, hr_A_tmb_pfs$CI_Upper,
    hr_B_crp_pfs$CI_Upper, hr_B_tlr_pfs$CI_Upper, hr_B_tmb_pfs$CI_Upper,
    hr_C_crp_pfs$CI_Upper, hr_C_tlr_pfs$CI_Upper, hr_C_tmb_pfs$CI_Upper
  )
)

forest_data_pfs <- forest_data_pfs[complete.cases(forest_data_pfs), ]

if (nrow(forest_data_pfs) > 0) {
  create_interaction_forest_plot(forest_data_pfs, "Progression-Free Survival")
}
```

**Interpretation:** HR < 1 indicates that biomarker-positive patients derive greater benefit from experimental treatment (reduced hazard of death/progression). The dashed vertical line at HR = 1 represents no differential treatment effect by biomarker status.

\newpage

# Sensitivity Analysis: Ridge Regression

Ridge regression (α = 0) shrinks coefficients toward zero but does not eliminate any, providing a sensitivity analysis for the stability of our interaction estimates.

```{r ridge-regression, include=FALSE}
# =============================================================================
# RIDGE REGRESSION SENSITIVITY ANALYSIS
# =============================================================================

# Try survival::ridge() first, then fall back to glmnet

# Approach 1: survival::ridge() within coxph
# Note: ridge() in survival package applies ridge penalty to specified terms

tryCatch({
  # OS with ridge penalty on biomarker terms and interactions
  ridge_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx +
      ridge(crp_num, tlr_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_os_success <- TRUE
}, error = function(e) {
  ridge_os_success <<- FALSE
  ridge_os <<- NULL
})

tryCatch({
  ridge_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx +
      ridge(crp_num, tlr_num, tmb_braf_num, theta = 1, scale = TRUE) +
      crp_num:Rx + tlr_num:Rx + tmb_braf_num:Rx,
    data = data_complete
  )
  ridge_pfs_success <- TRUE
}, error = function(e) {
  ridge_pfs_success <<- FALSE
  ridge_pfs <<- NULL
})

# If ridge() fails, use glmnet
if (!exists("ridge_os_success") || !ridge_os_success) {
  # Fallback to glmnet
  tryCatch({
    # Create design matrix
    X_os <- model.matrix(~ Age + sex + Rx_num + crp_num + tlr_num + tmb_braf_num +
                           crp_num:Rx_num + tlr_num:Rx_num + tmb_braf_num:Rx_num - 1,
                         data = data_complete)
    y_os <- Surv(data_complete$OSwk, data_complete$Death)

    cv_ridge_os <- cv.glmnet(X_os, y_os, family = "cox", alpha = 0, nfolds = 10)
    ridge_coef_os <- coef(cv_ridge_os, s = "lambda.min")
    ridge_os_glmnet <- TRUE
  }, error = function(e) {
    ridge_os_glmnet <<- FALSE
  })
} else {
  ridge_os_glmnet <- FALSE
}

if (!exists("ridge_pfs_success") || !ridge_pfs_success) {
  tryCatch({
    X_pfs <- model.matrix(~ Age + sex + Rx_num + crp_num + tlr_num + tmb_braf_num +
                            crp_num:Rx_num + tlr_num:Rx_num + tmb_braf_num:Rx_num - 1,
                          data = data_complete)
    y_pfs <- Surv(data_complete$PFSwk, data_complete$Progression)

    cv_ridge_pfs <- cv.glmnet(X_pfs, y_pfs, family = "cox", alpha = 0, nfolds = 10)
    ridge_coef_pfs <- coef(cv_ridge_pfs, s = "lambda.min")
    ridge_pfs_glmnet <- TRUE
  }, error = function(e) {
    ridge_pfs_glmnet <<- FALSE
  })
} else {
  ridge_pfs_glmnet <- FALSE
}

# Extract ridge results
extract_ridge_interaction <- function(model_or_coef, term_pattern, is_glmnet = FALSE) {
  if (is_glmnet) {
    if (is.null(model_or_coef)) return(list(HR = NA, SE = NA))
    coef_vec <- as.vector(model_or_coef)
    names(coef_vec) <- rownames(model_or_coef)
    idx <- grep(term_pattern, names(coef_vec))
    if (length(idx) == 0) return(list(HR = NA, SE = NA))
    return(list(HR = exp(coef_vec[idx[1]]), SE = NA))  # No SE from glmnet
  } else {
    if (is.null(model_or_coef)) return(list(HR = NA, SE = NA))
    summ <- summary(model_or_coef)
    coef_table <- summ$coefficients
    idx <- grep(term_pattern, rownames(coef_table))
    if (length(idx) == 0) return(list(HR = NA, SE = NA))
    return(list(HR = exp(coef_table[idx[1], "coef"]),
                SE = coef_table[idx[1], "se(coef)"]))
  }
}

# Get ridge interaction estimates
if (exists("ridge_os") && !is.null(ridge_os)) {
  ridge_crp_os <- extract_ridge_interaction(ridge_os, "crp_num.*Rx|Rx.*crp_num")
  ridge_tlr_os <- extract_ridge_interaction(ridge_os, "tlr_num.*Rx|Rx.*tlr_num")
  ridge_tmb_os <- extract_ridge_interaction(ridge_os, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
} else if (exists("ridge_coef_os")) {
  ridge_crp_os <- extract_ridge_interaction(ridge_coef_os, "crp_num.*Rx_num|Rx_num.*crp_num", TRUE)
  ridge_tlr_os <- extract_ridge_interaction(ridge_coef_os, "tlr_num.*Rx_num|Rx_num.*tlr_num", TRUE)
  ridge_tmb_os <- extract_ridge_interaction(ridge_coef_os, "tmb_braf_num.*Rx_num|Rx_num.*tmb_braf_num", TRUE)
} else {
  ridge_crp_os <- ridge_tlr_os <- ridge_tmb_os <- list(HR = NA, SE = NA)
}

if (exists("ridge_pfs") && !is.null(ridge_pfs)) {
  ridge_crp_pfs <- extract_ridge_interaction(ridge_pfs, "crp_num.*Rx|Rx.*crp_num")
  ridge_tlr_pfs <- extract_ridge_interaction(ridge_pfs, "tlr_num.*Rx|Rx.*tlr_num")
  ridge_tmb_pfs <- extract_ridge_interaction(ridge_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
} else if (exists("ridge_coef_pfs")) {
  ridge_crp_pfs <- extract_ridge_interaction(ridge_coef_pfs, "crp_num.*Rx_num|Rx_num.*crp_num", TRUE)
  ridge_tlr_pfs <- extract_ridge_interaction(ridge_coef_pfs, "tlr_num.*Rx_num|Rx_num.*tlr_num", TRUE)
  ridge_tmb_pfs <- extract_ridge_interaction(ridge_coef_pfs, "tmb_braf_num.*Rx_num|Rx_num.*tmb_braf_num", TRUE)
} else {
  ridge_crp_pfs <- ridge_tlr_pfs <- ridge_tmb_pfs <- list(HR = NA, SE = NA)
}
```

```{r table-ridge-os}
# Format ridge HR (with SE if available)
format_ridge_hr <- function(hr, se) {
  if (is.na(hr)) return("--")
  if (is.na(se)) {
    sprintf("%.2f*", hr)  # Asterisk indicates no SE available
  } else {
    sprintf("%.2f (SE: %.2f)", hr, se)
  }
}

# Overall Survival comparison
ridge_comparison_os <- data.frame(
  Biomarker = c("CRP × Rx", "TLR × Rx", "TMB/BRAF × Rx"),
  Firth_HR = c(
    format_hr_ci(hr_A_crp_os$HR, hr_A_crp_os$CI_Lower, hr_A_crp_os$CI_Upper),
    format_hr_ci(hr_A_tlr_os$HR, hr_A_tlr_os$CI_Lower, hr_A_tlr_os$CI_Upper),
    format_hr_ci(hr_A_tmb_os$HR, hr_A_tmb_os$CI_Lower, hr_A_tmb_os$CI_Upper)
  ),
  Ridge_HR = c(
    format_ridge_hr(ridge_crp_os$HR, ridge_crp_os$SE),
    format_ridge_hr(ridge_tlr_os$HR, ridge_tlr_os$SE),
    format_ridge_hr(ridge_tmb_os$HR, ridge_tmb_os$SE)
  )
)

ridge_comparison_os %>%
  kable(col.names = c("Interaction", "Firth HR (95% CI)", "Ridge HR"),
        caption = "Overall Survival: Firth-Corrected vs Ridge Regression",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "* Point estimate only (SE not available from glmnet).",
           footnote_as_chunk = TRUE)
```

```{r table-ridge-pfs}
# Progression-Free Survival comparison
ridge_comparison_pfs <- data.frame(
  Biomarker = c("CRP × Rx", "TLR × Rx", "TMB/BRAF × Rx"),
  Firth_HR = c(
    format_hr_ci(hr_A_crp_pfs$HR, hr_A_crp_pfs$CI_Lower, hr_A_crp_pfs$CI_Upper),
    format_hr_ci(hr_A_tlr_pfs$HR, hr_A_tlr_pfs$CI_Lower, hr_A_tlr_pfs$CI_Upper),
    format_hr_ci(hr_A_tmb_pfs$HR, hr_A_tmb_pfs$CI_Lower, hr_A_tmb_pfs$CI_Upper)
  ),
  Ridge_HR = c(
    format_ridge_hr(ridge_crp_pfs$HR, ridge_crp_pfs$SE),
    format_ridge_hr(ridge_tlr_pfs$HR, ridge_tlr_pfs$SE),
    format_ridge_hr(ridge_tmb_pfs$HR, ridge_tmb_pfs$SE)
  )
)

ridge_comparison_pfs %>%
  kable(col.names = c("Interaction", "Firth HR (95% CI)", "Ridge HR"),
        caption = "Progression-Free Survival: Firth-Corrected vs Ridge Regression",
        booktabs = TRUE, format = "latex") %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10) %>%
  footnote(general = "* Point estimate only (SE not available from glmnet).",
           footnote_as_chunk = TRUE)
```

**Interpretation:** Ridge regression applies an L2 penalty that shrinks all coefficients toward zero (HR toward 1.0). Large differences between Firth and Ridge estimates (as may be observed for TLR × Rx) indicate that the interaction effect is sensitive to regularization, potentially reflecting limited data or collinearity with other predictors. When Firth estimates suggest strong effects (HR >> 1 or HR << 1) but Ridge shrinks toward 1.0, this indicates the estimate may be unstable. Similar estimates across methods would support robustness, but substantial shrinkage warrants caution in interpreting the magnitude of interaction effects.

\newpage

# Summary

This analysis evaluated treatment effect heterogeneity across three candidate predictive biomarkers (CRP, TLR, TMB/BRAF) using Firth-corrected Cox regression with profile likelihood confidence intervals and penalized likelihood ratio tests.

**Key findings:**

1. **Model Robustness:** Treatment-biomarker interaction estimates were compared across three model specifications (all-in-one, focused, single-biomarker) to assess sensitivity to model structure.

2. **Multiple Testing:** Benjamini-Hochberg correction was applied to control the false discovery rate across the 6 primary interaction tests (3 biomarkers × 2 outcomes).

3. **Proportional Hazards:** The PH assumption was assessed using Schoenfeld residual tests and log-log survival plots.

4. **Sensitivity Analysis:** Ridge regression provided an alternative estimate of interaction effects with coefficient shrinkage.

**Methodological Note:** The use of Firth-corrected Cox regression addresses potential monotone likelihood issues and small sample bias. Profile likelihood-based confidence intervals and penalized likelihood ratio tests are more appropriate than Wald-based methods in this setting.

---

**Report completed on:** `r Sys.Date()`
**Repository:** ben-geisler/METIMMOX-1
**Report version:** 2.0

**Analysis packages:**

- `coxphf` version `r packageVersion("coxphf")` (Firth-corrected Cox regression)
- `survival` version `r packageVersion("survival")` (Cox regression, PH diagnostics)
- `glmnet` version `r packageVersion("glmnet")` (Ridge regression fallback)
- `vcd` version `r packageVersion("vcd")` (Biomarker correlation analysis)
