---
title: "Causal DAG"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  gfm:
    toc: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 9
    fig-height: 7
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup}
#| include: false
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(here, knitr, kableExtra, dagitty, ggdag, ggplot2, dplyr)

knitr::opts_knit$set(root.dir = here::here())
```

# Introduction

This report presents the directed acyclic graph (DAG) for the METIMMOX-1 cost-effectiveness analysis. The DAG encodes the assumed causal structure between patient characteristics, biomarkers, treatment, intermediate outcomes, and survival endpoints. It was specified in DAGitty format and visualised using the **ggdag** package in R.

Three node types are distinguished:

- **Exposure** (T): the randomised treatment (alternating FLOX + nivolumab vs FLOX alone)
- **Outcomes** (PFS, OS): the clinical endpoints of interest
- **Latent** (U): unmeasured patient characteristics that act as common causes of biomarkers and/or survival

# Node Definitions

```{r node-table}
node_defs <- data.frame(
  Node = c("Age", "Sex", "U", "TMB_BRAF", "CRP", "T",
           "TxTMB", "ETS", "PFS", "OS"),
  Label = c("Age", "Sex", "U", "TMB/BRAF", "CRP", "T",
            "T x TMB", "ETS", "PFS", "OS"),
  Type = c("Covariate", "Covariate", "Latent",
           "Biomarker", "Biomarker", "Exposure",
           "Effect modifier", "Mediator", "Outcome", "Outcome"),
  Description = c(
    "Patient age at baseline",
    "Patient sex",
    "Unmeasured prognostic factors (latent)",
    "Combined biomarker: TMB >= 9 mut/MB or BRAF mutation",
    "C-reactive protein (positive: CRP < 5 mg/L)",
    "Treatment: alternating FLOX + nivolumab vs FLOX alone",
    "Interaction between treatment and TMB/BRAF status",
    "Early tumour shrinkage (radiological response)",
    "Progression-free survival",
    "Overall survival"
  )
)

tbl <- kable(node_defs,
             col.names = c("Node", "Display", "Type", "Description"),
             caption = "DAG node definitions",
             booktabs = TRUE)
if (knitr::is_latex_output()) {
  tbl |> kable_styling(latex_options = c("HOLD_position"), font_size = 10)
} else {
  tbl
}
```

# Causal Structure

```{r dag-define}
#| include: false

dag <- dagitty('dag {
bb="0,0,1,1"
Age [pos="0.100,0.100"]
Sex [pos="0.280,0.100"]
U [latent,pos="0.750,0.080"]
TMB_BRAF [pos="0.200,0.380"]
CRP [pos="0.720,0.320"]
T [exposure,pos="0.050,0.680"]
TxTMB [pos="0.350,0.560"]
ETS [pos="0.560,0.560"]
PFS [outcome,pos="0.720,0.760"]
OS [outcome,pos="0.900,0.920"]

Age -> TMB_BRAF
Age -> OS
Sex -> TMB_BRAF
U -> TMB_BRAF
U -> CRP
U -> PFS
U -> OS
TMB_BRAF -> PFS
TMB_BRAF -> OS
TMB_BRAF -> ETS
TMB_BRAF -> TxTMB
CRP -> PFS
CRP -> OS
CRP -> ETS
T -> PFS
T -> OS
T -> ETS
T -> TxTMB
TxTMB -> PFS
TxTMB -> OS
ETS -> PFS
PFS -> OS
}')
```

```{r dag-plot}
#| fig-cap: "Causal DAG for the METIMMOX-1 analysis. Node colour indicates role: blue = exposure (T), red = outcomes (PFS, OS), green = latent variable (U), grey = covariates and intermediate variables. Arrows denote assumed causal effects. Node abbreviations: T = Treatment; TxTMB = Treatment x TMB/BRAF interaction; ETS = Early Tumour Shrinkage; U = Unmeasured confounders."
#| fig-width: 9
#| fig-height: 7

tidy_dag <- tidy_dagitty(dag)

# DAGitty uses y-down coordinates; flip to ggplot2 y-up convention
tidy_dag$data <- tidy_dag$data |>
  mutate(
    y    = 1 - y,
    yend = if_else(is.na(yend), NA_real_, 1 - yend)
  )

# Colour palette
pal <- c(
  "exposure" = "#2166ac",
  "outcome"  = "#b2182b",
  "latent"   = "#1b7837"
)

ggdag_status(tidy_dag, node_size = 24, text_size = 3.0, text_col = "white") +
  theme_dag() +
  scale_color_manual(
    name     = "Node type",
    values   = pal,
    na.value = "grey55",
    breaks   = c("exposure", "latent", "outcome"),
    labels   = c("exposure" = "Exposure (T)",
                 "latent"   = "Latent (U)",
                 "outcome"  = "Outcome (PFS, OS)")
  ) +
  scale_fill_manual(
    name     = "Node type",
    values   = pal,
    na.value = "grey55",
    breaks   = c("exposure", "latent", "outcome"),
    labels   = c("exposure" = "Exposure (T)",
                 "latent"   = "Latent (U)",
                 "outcome"  = "Outcome (PFS, OS)")
  ) +
  theme(
    legend.position   = "bottom",
    legend.text       = element_text(size = 10),
    legend.title      = element_text(size = 10, face = "bold"),
    plot.margin       = margin(10, 10, 10, 10)
  )
```

# Causal Analysis

Because T is a randomised exposure with no parents in the DAG, there are no backdoor paths from T to PFS or OS. The sections below confirm this using dagitty's formal algorithms and list the implied conditional independencies encoded by the DAG.

## Adjustment Sets

```{r adjustment-sets}
#| results: asis

report_adj <- function(exposure, outcome) {
  adj <- adjustmentSets(dag, exposure = exposure, outcome = outcome,
                        type = "minimal")
  if (length(adj) == 0) {
    cat(sprintf(
      "**%s -> %s:** No adjustment required (randomised exposure; no open backdoor paths).\n\n",
      exposure, outcome
    ))
  } else {
    sets <- sapply(adj, function(s) {
      if (length(s) == 0) "{}" else paste0("{", paste(s, collapse = ", "), "}")
    })
    cat(sprintf("**%s -> %s:** Minimal adjustment sets: %s\n\n",
                exposure, outcome, paste(sets, collapse = "; ")))
  }
}

report_adj("T", "PFS")
report_adj("T", "OS")
```

## Implied Conditional Independencies

```{r independencies}
indep <- impliedConditionalIndependencies(dag)

if (length(indep) == 0) {
  cat("The DAG implies no testable conditional independencies (saturated structure).\n")
} else {
  fmt_ci <- function(s) {
    z <- s$Z
    if (length(z) == 0) {
      sprintf("%s _||_ %s", s$X, s$Y)
    } else {
      sprintf("%s _||_ %s  |  {%s}", s$X, s$Y, paste(sort(z), collapse = ", "))
    }
  }
  indep_df <- data.frame(Statement = sapply(indep, fmt_ci))
  tbl2 <- kable(indep_df,
               col.names = "Implied conditional independence  (X _||_ Y | {Z})",
               caption   = "Conditional independencies implied by the causal DAG",
               booktabs  = TRUE)
  if (knitr::is_latex_output()) {
    tbl2 |> kable_styling(latex_options = c("HOLD_position"), font_size = 10)
  } else {
    tbl2
  }
}
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
