---
title: "Causal DAG"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  gfm:
    toc: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 9
    fig-height: 7
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup}
#| include: false
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  funs = c("dag_helpers"),
  packages = c("here", "knitr", "kableExtra", "dagitty", "ggdag", "ggplot2",
               "dplyr", "ggtext"),
  set_theme = FALSE
)
```

# Introduction

This report presents the directed acyclic graph (DAG) for the METIMMOX-1 cost-effectiveness analysis. The DAG encodes the assumed causal structure between patient characteristics, biomarkers, treatment, intermediate outcomes, and survival endpoints. It was specified in DAGitty format and visualised using the **ggdag** package in R.

Three node types are distinguished:

- **Exposure** (T): the randomised treatment (alternating FLOX + nivolumab vs FLOX alone)
- **Outcomes** (PFS, OS): the clinical endpoints of interest
- **Latent** (U): unmeasured patient characteristics that act as common causes of biomarkers and/or survival

# Node Definitions

```{r node-table}
node_defs <- data.frame(
  Node = c("Age", "Sex", "U", "TMB_BRAF", "CRP", "T",
           "TxTMB", "TxCRP", "TLR", "PFS", "OS"),
  Label = c("Age", "Sex", "U", "TMB/BRAF", "CRP", "T",
            "T x TMB", "T x CRP", "TLR", "PFS", "OS"),
  Type = c("Covariate", "Covariate", "Latent",
           "Biomarker", "Biomarker", "Exposure",
           "Effect modifier", "Effect modifier", "Mediator", "Outcome", "Outcome"),
  Description = c(
    "Patient age at baseline",
    "Patient sex",
    "Unmeasured prognostic factors (latent)",
    "Combined biomarker: TMB >= 9 mut/MB or BRAF mutation",
    "C-reactive protein at week 4, before the first nivolumab dose (positive: CRP < 5 mg/L)",
    "Treatment: alternating FLOX + nivolumab vs FLOX alone",
    "Interaction between treatment and TMB/BRAF status",
    "Interaction between treatment and CRP status",
    "Tumour lesion reduction (radiological response)",
    "Progression-free survival",
    "Overall survival"
  )
)

tbl <- kable(node_defs,
             col.names = c("Node", "Display", "Type", "Description"),
             caption = "DAG node definitions",
             booktabs = TRUE)
if (knitr::is_latex_output()) {
  tbl |> kable_styling(latex_options = c("HOLD_position"), font_size = 10)
} else {
  tbl
}
```

**CRP timing.** The CRP node is the week-4 value (cycle 3 day 1), measured after the two FLOX cycles that both arms receive and before the first nivolumab dose, not the baseline (pre-randomization) value. It is nevertheless drawn without a `T -> CRP` edge: at week 4 no nivolumab has been given and the two arms have received identical treatment, so treatment assignment cannot yet have affected CRP. CRP is therefore a pre-immunotherapy covariate in the DAG, unlike TLR, which is read from the first on-treatment CT after nivolumab has started and is modelled as a mediator (`T -> TLR`).

# Causal Structure

```{r dag-define}
#| include: false

# `dag` is provided by dag_helpers.R.
```

```{r dag-plot}
#| fig-cap: "Causal DAG for the METIMMOX-1 analysis. Node colour indicates role: blue = exposure (T), red = outcomes (PFS, OS), green = latent variable (U), grey = covariates and intermediate variables. Solid arrows denote assumed causal effects; dashed arrows indicate the hypothesised interaction effects of T x TMB/BRAF and T x CRP on PFS and OS. Node abbreviations: T = Treatment; TxTMB = Treatment x TMB/BRAF interaction; TxCRP = Treatment x CRP interaction; TLR = Tumour Lesion Reduction; U = Unmeasured confounders."
#| fig-width: 9
#| fig-height: 7

tidy_dag <- tidy_dagitty(dag)

# DAGitty uses y-down coordinates; flip to ggplot2 y-up convention
tidy_dag$data <- tidy_dag$data |>
  mutate(
    y    = 1 - y,
    yend = if_else(is.na(yend), NA_real_, 1 - yend),
    hyp  = !is.na(to) & name %in% c("TxTMB", "TxCRP") & to %in% c("PFS", "OS")
  )

# Colour palette
plot_dag(tidy_dag, dag_palette)
```

# Causal Analysis

Because T is a randomised exposure with no parents in the DAG, there are no backdoor paths from T to PFS or OS. The sections below confirm this using dagitty's formal algorithms and list the implied conditional independencies encoded by the DAG.

## Adjustment Sets

```{r adjustment-sets}
#| results: asis

report_adj <- function(dag_obj, exposure, outcome) {
  adj <- adjustmentSets(dag_obj, exposure = exposure, outcome = outcome,
                        type = "minimal")
  if (length(adj) == 0) {
    cat(sprintf(
      "**%s -> %s:** No adjustment required (randomised exposure; no open backdoor paths).\n\n",
      exposure, outcome
    ))
  } else {
    sets <- sapply(adj, function(s) {
      if (length(s) == 0) "{}" else paste0("{", paste(s, collapse = ", "), "}")
    })
    cat(sprintf("**%s -> %s:** Minimal adjustment sets: %s\n\n",
                exposure, outcome, paste(sets, collapse = "; ")))
  }
}

report_adj(dag, "T", "PFS")
report_adj(dag, "T", "OS")
```

## Implied Conditional Independencies

```{r independencies}
indep <- impliedConditionalIndependencies(dag)

if (length(indep) == 0) {
  cat("The DAG implies no testable conditional independencies (saturated structure).\n")
} else {
  indep_df <- data.frame(Statement = sapply(indep, format_ci_statement))
  tbl2 <- kable(indep_df,
               col.names = "Implied conditional independence  (X _||_ Y | {Z})",
               caption   = "Conditional independencies implied by the causal DAG",
               booktabs  = TRUE)
  if (knitr::is_latex_output()) {
    tbl2 |> kable_styling(latex_options = c("HOLD_position"), font_size = 10)
  } else {
    tbl2
  }
}
```

# Sensitivity Analysis: Excluding Age/Sex → TMB/BRAF

This sensitivity DAG removes the `Age -> TMB_BRAF` and `Sex -> TMB_BRAF` edges while keeping the remainder of the structure identical to the primary specification. The primary DAG retains these arrows on biological grounds; this sensitivity analysis shows the downstream implications of omitting them.

```{r dag-sens-define}
#| include: false

# `dag_sens` is provided by dag_helpers.R.
```

## Sensitivity DAG

```{r dag-sens-plot}
#| fig-cap: "Sensitivity DAG for the METIMMOX-1 analysis, excluding the Age -> TMB_BRAF and Sex -> TMB_BRAF edges while retaining all other assumed causal relationships. Solid arrows denote assumed causal effects; dashed arrows indicate the hypothesised interaction effects of T x TMB/BRAF and T x CRP on PFS and OS."
#| fig-width: 9
#| fig-height: 7

tidy_dag_sens <- tidy_dagitty(dag_sens)

# DAGitty uses y-down coordinates; flip to ggplot2 y-up convention
tidy_dag_sens$data <- tidy_dag_sens$data |>
  mutate(
    y    = 1 - y,
    yend = if_else(is.na(yend), NA_real_, 1 - yend),
    hyp  = !is.na(to) & name %in% c("TxTMB", "TxCRP") & to %in% c("PFS", "OS")
  )

plot_dag(tidy_dag_sens, dag_palette)
```

## Sensitivity Causal Analysis

The treatment node remains randomised in the sensitivity DAG, so the formal adjustment recommendations for `T -> PFS` and `T -> OS` are unchanged. The main difference is in the implied conditional independencies, which now reflect the omission of direct Age/Sex effects on TMB/BRAF status.

### Adjustment Sets

```{r adjustment-sets-sens}
#| results: asis

report_adj(dag_sens, "T", "PFS")
report_adj(dag_sens, "T", "OS")
```

### Implied Conditional Independencies

```{r independencies-sens}
indep_sens <- impliedConditionalIndependencies(dag_sens)

if (length(indep_sens) == 0) {
  cat("The sensitivity DAG implies no testable conditional independencies (saturated structure).\n")
} else {
  indep_sens_df <- data.frame(Statement = sapply(indep_sens, format_ci_statement))
  tbl3 <- kable(
    indep_sens_df,
    col.names = "Implied conditional independence  (X _||_ Y | {Z})",
    caption   = "Conditional independencies implied by the sensitivity DAG",
    booktabs  = TRUE
  )
  if (knitr::is_latex_output()) {
    tbl3 |> kable_styling(latex_options = c("HOLD_position"), font_size = 10)
  } else {
    tbl3
  }
}
```

# Simplified DAG

The following DAG presents the same causal assumptions in a condensed form intended for a clinical audience. The interaction terms (T × TMB/BRAF and T × CRP) and the latent common-cause node (U) have been omitted; their roles are described in the text. Dashed arrows from T to PFS and OS indicate that the magnitude of the treatment effect on survival outcomes is hypothesised to be modified by TMB/BRAF and CRP status — the central question addressed by the biomarker analysis.

```{r dag-simple-define}
#| include: false

# `dag_simple` is provided by dag_helpers.R.
```

```{r dag-simple-plot}
#| fig-cap: "Figure 3. Simplified causal DAG for METIMMOX-1. Solid arrows denote assumed causal effects. The dashed arrow indicates that the treatment effect on survival is hypothesised to be modified by TMB/BRAF and CRP status. Interaction and latent-variable nodes are shown in the full DAG. Abbreviations: CRP = C-reactive protein, OS = overall survival, PFS = progression-free survival, T = treatment, TMB = tumour mutational burden."
#| fig-width: 9
#| fig-height: 6

tidy_dag_simple <- tidy_dagitty(dag_simple)
tidy_dag_simple$data <- tidy_dag_simple$data |>
  mutate(
    y    = 1 - y,
    yend = if_else(is.na(yend), NA_real_, 1 - yend),
    hyp  = !is.na(to) & name == "T" & to == "Survival"
  )

pal_simple <- c("exposure" = "#2166ac", "outcome" = "#b2182b", "covariate" = "grey55")

node_data_s <- node_status(tidy_dag_simple)$data |>
  distinct(name, x, y, status) |>
  mutate(
    status = if_else(is.na(status), "covariate", status),
    label  = case_when(
      name == "Demo"     ~ "Age/<br>Sex",
      name == "Survival" ~ "PFS/<br>OS",
      name == "TMB_BRAF" ~ "TMB/<br><i>BRAF</i>",
      TRUE               ~ name
    )
  )
x_range_s <- range(node_data_s$x, na.rm = TRUE)
y_range_s <- range(node_data_s$y, na.rm = TRUE)

ggplot(tidy_dag_simple$data, aes(x = x, y = y, xend = xend, yend = yend)) +
  geom_dag_edges_link(
    data = function(d) dplyr::filter(d, !is.na(to), !hyp)
  ) +
  geom_dag_edges_link(
    data = function(d) dplyr::filter(d, !is.na(to), hyp),
    edge_linetype = "dashed"
  ) +
  geom_dag_node(
    data = node_data_s,
    mapping = aes(x = x, y = y, colour = status, fill = status),
    size = 24, inherit.aes = FALSE
  ) +
  ggtext::geom_richtext(
    data = node_data_s,
    mapping = aes(x = x, y = y, label = label),
    colour = "white", size = 3.5,
    fill = NA, label.color = NA,
    label.padding = grid::unit(c(0, 0, 0, 0), "pt"),
    inherit.aes = FALSE
  ) +
  coord_equal(
    xlim = c(x_range_s[1] - diff(x_range_s) * 0.10, x_range_s[2] + diff(x_range_s) * 0.10),
    ylim = c(y_range_s[1] - diff(y_range_s) * 0.10, y_range_s[2] + diff(y_range_s) * 0.10),
    clip = "off"
  ) +
  theme_dag() +
  scale_color_manual(
    name   = NULL,
    values = pal_simple,
    breaks = c("exposure", "outcome", "covariate"),
    labels = c("exposure"  = "Treatment",
               "outcome"   = "Outcome",
               "covariate" = "Covariates and biomarkers")
  ) +
  scale_fill_manual(
    name   = NULL,
    values = pal_simple,
    breaks = c("exposure", "outcome", "covariate"),
    labels = c("exposure"  = "Treatment",
               "outcome"   = "Outcome",
               "covariate" = "Covariates and biomarkers")
  ) +
  theme(
    legend.position = "bottom",
    legend.text     = element_text(size = 10),
    plot.margin     = margin(10, 10, 10, 10)
  )
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.2
