---
title: "Enriched Population Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r enriched-setup, include=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

knitr::opts_knit$set(root.dir = here::here())

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r setup-global-variables, include=FALSE}
source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
```

```{r biomarker-strategies, include=FALSE}
source(here::here("scripts/R/analysis/03_biomarker_strategies.R"))
```

```{r source-enriched-functions, include=FALSE}
# Source the enriched population analysis functions (suppresses console output)
invisible(capture.output({
  source(here::here("scripts/R/analysis/10b_enriched_population_analysis.R"))
}, type = "message"))
invisible(capture.output({
  source(here::here("scripts/R/analysis/10b_enriched_population_analysis.R"))
}, type = "output"))
```

```{r run-enriched-analysis, include=FALSE}
# Run the enriched analysis across all model structures
# This calls run_basecase_for_structure() for each model, which re-sources 06+07
all_enriched_results <- run_all_enriched_analyses(verbose = FALSE)

# Restore original MODEL_STRUCTURE
MODEL_STRUCTURE <<- original_model_structure

# Format comparison table
enriched_comparison <- format_enriched_comparison_table(all_enriched_results)
```

# Overview

This report presents an enriched population cost-effectiveness analysis (ceiling scenario) for the METIMMOX-1 biomarker-guided immunotherapy strategies. In the base case analysis, each biomarker strategy's costs and effects are calculated as a prevalence-weighted average of the biomarker-positive subgroup (receiving experimental treatment) and the biomarker-negative subgroup (receiving standard treatment). This dilutes the incremental benefit with patients who do not receive immunotherapy.

The enriched population analysis models a **biomarker-enriched trial design** where only biomarker-positive patients are enrolled. For each biomarker:

- **Enriched experimental arm:** biomarker-positive patients receive FLOX + nivolumab
- **Enriched control arm:** biomarker-positive patients receive FLOX only (counterfactual)

The enriched control curves are generated by predicting from the fitted survival models for biomarker-positive patients assigned to control treatment. Both arms incur the biomarker test cost. This provides an apples-to-apples comparison within the enriched cohort.

## Biomarker Prevalences

```{r prevalence-table}
prev_df <- data.frame(
  Biomarker = c("CRP (C-reactive protein)", "TLR (Tumor lesion reduction)", "TMB/BRAF (TMB or BRAF mutation)"),
  Prevalence = c(
    strategies_df$prevalence[strategies_df$id == "crp"],
    strategies_df$prevalence[strategies_df$id == "tlr"],
    strategies_df$prevalence[strategies_df$id == "tmb_braf"]
  )
)
prev_df$Prevalence_Display <- sprintf("%.1f%%", prev_df$Prevalence * 100)
prev_df$N_Positive <- c(
  sum(data$crp == 1, na.rm = TRUE),
  sum(data$tlr == 1, na.rm = TRUE),
  sum(data$tmb_braf == 1, na.rm = TRUE)
)

knitr::kable(prev_df[, c("Biomarker", "Prevalence_Display", "N_Positive")],
             col.names = c("Biomarker", "Prevalence", "N Positive"),
             align = c("l", "r", "r"),
             booktabs = TRUE,
             caption = "Biomarker-Positive Prevalences in the METIMMOX Trial") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

## Model Structures

Each enriched analysis is run under three alternative survival model specifications:

```{r model-structure-table}
model_configs <- get_model_configs()
model_structure_df <- data.frame(
  Model = sapply(model_configs, function(x) x$label),
  Description = sapply(model_configs, function(x) x$description)
)

knitr::kable(model_structure_df,
             col.names = c("Model", "Description"),
             align = c("l", "l"),
             booktabs = TRUE,
             caption = "Survival Model Specifications") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "10cm")
```

\newpage

# Base Case vs Enriched Population ICERs

The following tables compare the base case (population-weighted, vs overall control) and enriched (biomarker-positive only, vs biomarker-positive control) cost-effectiveness results. Base case ICERs compare each biomarker strategy to the overall control. Enriched ICERs compare biomarker-positive patients on experimental treatment to biomarker-positive patients on FLOX only.

```{r enriched-summary-table}
# Create a focused summary table across all models
biomarkers <- c("crp", "tlr", "tmb_braf")
biomarker_labels <- c("CRP", "TLR", "TMB/BRAF")

summary_rows <- list()
for (i in seq_along(biomarkers)) {
  bm <- biomarkers[i]
  prev <- strategies_df$prevalence[strategies_df$id == bm]

  for (model_name in names(all_enriched_results)) {
    result <- all_enriched_results[[model_name]]
    config <- model_configs[[model_name]]

    base_row <- result$base_pairwise[result$base_pairwise$Strategy == bm, ]
    enr_row <- result$enriched_pairwise[result$enriched_pairwise$Strategy == bm, ]

    # Format base ICER
    if (base_row$Status == "Dominated") {
      base_icer_fmt <- "Dominated"
    } else if (is.na(base_row$ICER) || !is.finite(base_row$ICER)) {
      base_icer_fmt <- "--"
    } else {
      base_icer_fmt <- scales::dollar(base_row$ICER, prefix = "EUR ", accuracy = 1)
    }

    # Format enriched ICER
    if (enr_row$Status == "Dominated") {
      enr_icer_fmt <- "Dominated"
    } else if (is.na(enr_row$ICER) || !is.finite(enr_row$ICER)) {
      enr_icer_fmt <- "--"
    } else {
      enr_icer_fmt <- scales::dollar(enr_row$ICER, prefix = "EUR ", accuracy = 1)
    }

    # Format % change
    if (base_row$Status == "Non-dominated" && enr_row$Status == "Non-dominated" &&
        !is.na(base_row$ICER) && !is.na(enr_row$ICER) &&
        is.finite(base_row$ICER) && is.finite(enr_row$ICER) && base_row$ICER != 0) {
      pct <- (enr_row$ICER - base_row$ICER) / abs(base_row$ICER) * 100
      pct_fmt <- sprintf("%+.1f%%", pct)
    } else {
      pct_fmt <- "--"
    }

    summary_rows[[length(summary_rows) + 1]] <- data.frame(
      Biomarker = biomarker_labels[i],
      Prevalence = sprintf("%.1f%%", prev * 100),
      Model = config$short_label,
      Base_ICER = base_icer_fmt,
      Enriched_ICER = enr_icer_fmt,
      Change = pct_fmt,
      stringsAsFactors = FALSE
    )
  }
}

summary_df <- do.call(rbind, summary_rows)

knitr::kable(summary_df,
             col.names = c("Biomarker", "Prevalence", "Model", "Base Case ICER", "Enriched ICER", "Change"),
             align = c("l", "r", "c", "r", "r", "r"),
             booktabs = TRUE,
             caption = "Pairwise ICERs vs Control: Base Case vs Enriched Population") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::collapse_rows(columns = 1:2, valign = "top")
```

**Interpretation:** A negative percentage change indicates the enriched population is more cost-effective than the base case. Strategies that are "Dominated" in the base case (higher cost and lower effect than control) may become non-dominated in the enriched population if the biomarker-positive subgroup has better treatment outcomes.

\newpage

# Detailed Cost and QALY Breakdown

```{r detailed-tables, results='asis'}
for (model_name in names(all_enriched_results)) {
  result <- all_enriched_results[[model_name]]
  config <- model_configs[[model_name]]

  # Build detailed table with enriched control info
  detail_rows <- list()
  for (i in seq_along(biomarkers)) {
    bm <- biomarkers[i]
    base_row <- result$base_pairwise[result$base_pairwise$Strategy == bm, ]
    enr_row <- result$enriched_pairwise[result$enriched_pairwise$Strategy == bm, ]

    detail_rows[[i]] <- data.frame(
      Biomarker = biomarker_labels[i],
      Enr_Exp_Cost = scales::dollar(enr_row$Cost, prefix = "EUR ", accuracy = 1),
      Enr_Exp_QALY = sprintf("%.3f", enr_row$Effect),
      Enr_Ctrl_Cost = scales::dollar(enr_row$Ctrl_Cost, prefix = "EUR ", accuracy = 1),
      Enr_Ctrl_QALY = sprintf("%.3f", enr_row$Ctrl_Effect),
      Enr_Inc_Cost = scales::dollar(enr_row$Inc_Cost, prefix = "EUR ", accuracy = 1),
      Enr_Inc_QALY = sprintf("%.3f", enr_row$Inc_Effect),
      stringsAsFactors = FALSE
    )
  }

  detail_df <- do.call(rbind, detail_rows)

  # Overall control reference
  ctrl_base <- result$base_pairwise[result$base_pairwise$Strategy == "control", ]
  cat(paste0("\n\n## ", config$label, "\n\n"))
  cat(paste0("**Overall control (base case):** Cost = ",
             scales::dollar(ctrl_base$Cost, prefix = "EUR ", accuracy = 1),
             ", QALYs = ", sprintf("%.3f", ctrl_base$Effect), "\n\n"))

  print(knitr::kable(detail_df,
               col.names = c("Biomarker",
                              "Exp. Cost", "Exp. QALYs",
                              "Ctrl Cost", "Ctrl QALYs",
                              "Inc. Cost", "Inc. QALYs"),
               align = c("l", rep("r", 6)),
               booktabs = TRUE,
               caption = paste0("Enriched Cohort Results: ", config$label,
                                " (Biomarker+ Experimental vs Biomarker+ Control)")) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
    kableExtra::add_header_above(c(" " = 1,
                                    "Biomarker+ Experimental" = 2,
                                    "Biomarker+ Control" = 2,
                                    "Incremental" = 2)))
}
```

\newpage

# Cost-Effectiveness Planes

```{r ce-planes, fig.height=12, fig.width=10}
#| fig-cap: "Incremental Cost-Effectiveness: Base Case vs Enriched Population"

# Build data for plotting
plot_data <- data.frame()

for (model_name in names(all_enriched_results)) {
  result <- all_enriched_results[[model_name]]
  config <- model_configs[[model_name]]

  for (bm in biomarkers) {
    bm_label <- biomarker_labels[match(bm, biomarkers)]

    base_row <- result$base_pairwise[result$base_pairwise$Strategy == bm, ]
    enr_row <- result$enriched_pairwise[result$enriched_pairwise$Strategy == bm, ]

    plot_data <- rbind(plot_data, data.frame(
      Model = config$label,
      Biomarker = bm_label,
      Analysis = "Base Case",
      Inc_Effect = base_row$Inc_Effect,
      Inc_Cost = base_row$Inc_Cost,
      stringsAsFactors = FALSE
    ))
    plot_data <- rbind(plot_data, data.frame(
      Model = config$label,
      Biomarker = bm_label,
      Analysis = "Enriched",
      Inc_Effect = enr_row$Inc_Effect,
      Inc_Cost = enr_row$Inc_Cost,
      stringsAsFactors = FALSE
    ))
  }
}

p_ce <- ggplot(plot_data, aes(x = Inc_Effect, y = Inc_Cost,
                               color = Biomarker, shape = Analysis)) +
  geom_point(size = 3.5) +
  geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
  geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
  geom_abline(intercept = 0, slope = WTP, linetype = "dotted", color = "gray40") +
  facet_wrap(~Model, ncol = 1, scales = "free") +
  scale_color_brewer(palette = "Set1") +
  scale_shape_manual(values = c("Base Case" = 16, "Enriched" = 17)) +
  scale_y_continuous(labels = scales::dollar_format(prefix = "EUR ")) +
  labs(
    x = "Incremental QALYs (vs Control)",
    y = "Incremental Cost (vs Control)",
    color = "Biomarker",
    shape = "Analysis"
  ) +
  theme(legend.position = "bottom") +
  guides(color = guide_legend(nrow = 1), shape = guide_legend(nrow = 1))

print(p_ce)
```

The dotted line represents the willingness-to-pay threshold (EUR `r format(WTP, big.mark = ",")`/QALY). Points below this line are cost-effective. Base case points (circles) show incremental cost/effect vs the overall control population. Enriched points (triangles) show incremental cost/effect vs the biomarker-positive control population. The enriched comparison uses a matched control arm (same biomarker-positive patients on FLOX only), providing an apples-to-apples comparison.

\newpage

# Interpretation

## Mechanism of ICER Improvement

In the base case, biomarker strategy costs and effects are prevalence-weighted averages:

$$\text{Strategy Cost} = p \times \text{Cost}_{pos} + (1-p) \times \text{Cost}_{neg}$$

where $p$ is the biomarker prevalence. The biomarker-negative subgroup receives standard treatment (same as control), so their incremental cost and effect are near zero. This dilutes the incremental benefit from the biomarker-positive subgroup.

In the enriched analysis, only biomarker-positive patients are considered in **both** the experimental and control arms. The enriched control arm uses survival curves predicted from the fitted models for biomarker-positive patients assigned to FLOX only. This removes dilution from biomarker-negative patients and provides a direct comparison of treatment effect within the target population.

## Clinical Implications

```{r interpretation-table}
interp_rows <- list()
for (i in seq_along(biomarkers)) {
  bm <- biomarkers[i]
  prev <- strategies_df$prevalence[strategies_df$id == bm]

  # Use Model A results as primary
  result_a <- all_enriched_results$Model_A
  base_row <- result_a$base_pairwise[result_a$base_pairwise$Strategy == bm, ]
  enr_row <- result_a$enriched_pairwise[result_a$enriched_pairwise$Strategy == bm, ]

  base_status <- base_row$Status
  enr_status <- enr_row$Status

  if (base_status == "Dominated" && enr_status == "Non-dominated") {
    interpretation <- paste0("Strategy is dominated at population level but has a finite ICER (",
                              scales::dollar(enr_row$ICER, prefix = "EUR ", accuracy = 1),
                              "/QALY) in the enriched population")
  } else if (base_status == "Non-dominated" && enr_status == "Non-dominated") {
    pct <- (enr_row$ICER - base_row$ICER) / abs(base_row$ICER) * 100
    interpretation <- paste0("ICER improves by ", sprintf("%.0f%%", abs(pct)),
                              " from ", scales::dollar(base_row$ICER, prefix = "EUR ", accuracy = 1),
                              " to ", scales::dollar(enr_row$ICER, prefix = "EUR ", accuracy = 1))
  } else {
    interpretation <- paste0("Base: ", base_status, "; Enriched: ", enr_status)
  }

  interp_rows[[i]] <- data.frame(
    Biomarker = biomarker_labels[i],
    Prevalence = sprintf("%.1f%%", prev * 100),
    Interpretation = interpretation,
    stringsAsFactors = FALSE
  )
}

interp_df <- do.call(rbind, interp_rows)

knitr::kable(interp_df,
             col.names = c("Biomarker", "Prevalence", "Enrichment Effect (Model A)"),
             align = c("l", "r", "l"),
             booktabs = TRUE,
             caption = "Summary of Enrichment Effects on Cost-Effectiveness") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(3, width = "9cm")
```

## Limitations

- This is a deterministic analysis only; probabilistic sensitivity analysis of the enriched scenario is not included.
- The enriched control arm survival curves are counterfactual predictions from the fitted model (biomarker-positive patients assigned to control treatment), not observed data from a separate enriched trial.
- The analysis assumes perfect biomarker test sensitivity and specificity.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
