---
title: "Enriched Population Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("report_format"),
  set_theme = FALSE
)

invisible(capture.output(
  source(here::here("scripts/R/analysis/08b_enriched_population_analysis.R"))
))

```

# Overview

This report presents a ceiling scenario for the economic biomarkers included in the single joint model. The analysis compares biomarker-positive patients receiving FLOX + nivolumab with biomarker-positive patients receiving FLOX only.

Economic biomarkers are CRP and TMB/BRAF.

# Biomarker Prevalence

```{r prevalence-table}
prev_df <- strategies_df %>%
  filter(id %in% get_biomarkers()) %>%
  transmute(
    Biomarker = biomarker_label(id),
    Prevalence = sprintf("%.1f%%", prevalence * 100),
    `N Positive` = sapply(id, function(bm) sum(data[[bm]] == 1, na.rm = TRUE))
  )

knitr::kable(
  prev_df,
  booktabs = TRUE,
  align = c("l", "r", "r"),
  caption = "Economic biomarker-positive prevalences"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Base Case vs Enriched Population

```{r enriched-summary}
summary_cols <- c("Biomarker", "Prevalence", "Base_ICER",
                  "Enr_ICER", "Pct_Change")

knitr::kable(
  enriched_display[, summary_cols],
  booktabs = TRUE,
  align = c("l", "r", "r", "r", "r"),
  col.names = c("Biomarker", "Prevalence", "Base Case ICER",
                "Enriched ICER", "Change"),
  caption = "Base case and enriched-population ICERs"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r enriched-detail}
detail_cols <- c("Biomarker", "Enr_Cost", "Enr_Effect",
                 "Enr_Ctrl_Cost", "Enr_Ctrl_Effect", "Enr_ICER")

knitr::kable(
  enriched_display[, detail_cols],
  booktabs = TRUE,
  align = c("l", "r", "r", "r", "r", "r"),
  col.names = c("Biomarker", "Experimental Cost", "Experimental QALYs",
                "Control Cost", "Control QALYs", "Enriched ICER"),
  caption = "Detailed enriched-population results"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r enriched-plot, fig.cap="Base case and enriched-population ICERs"}
plot_df <- enriched_comparison %>%
  select(Biomarker, Base_ICER, Enr_ICER, Base_Status, Enr_Status) %>%
  tidyr::pivot_longer(
    cols = c(Base_ICER, Enr_ICER),
    names_to = "Analysis",
    values_to = "ICER"
  ) %>%
  mutate(
    Analysis = recode(Analysis,
                      Base_ICER = "Base case",
                      Enr_ICER = "Enriched population"),
    Biomarker = biomarker_label(tolower(gsub("/", "_", Biomarker)))
  )

ggplot(plot_df, aes(x = Biomarker, y = ICER, fill = Analysis)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  geom_hline(yintercept = WTP, linetype = "dashed", color = "gray40") +
  scale_y_continuous(labels = scales::dollar_format(prefix = "EUR ", scale = 0.001,
                                                    suffix = "K")) +
  labs(x = NULL, y = "ICER", fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Interpretation

The enriched analysis isolates expected value among biomarker-positive patients and removes dilution from biomarker-negative patients who would receive standard care under a guided strategy. The enriched control arm is counterfactual and is generated from the fitted single joint survival model.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
