---
title: "METIMMOX-1 Value of Information Analysis"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r evppi-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r load-dependencies, include=FALSE}
# Load dependencies
if (!exists("USE_BOTH_MODELS")) {
  USE_BOTH_MODELS <- 0
}

if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}

if (file.exists(here("scripts/R/analysis/06_parametric_survival analysis.R"))) {
  suppressMessages(suppressWarnings(tryCatch({
    source(here("scripts/R/analysis/06_parametric_survival analysis.R"))
  }, error = function(e) NULL)))
}

if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(tryCatch({
    source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
  }, error = function(e) NULL)))
}

if (!exists("time_points") && exists("time_horizon")) {
  time_points <- seq(0, time_horizon, by = 1)
  time_points_length <- length(time_points)
}

if (file.exists(here("scripts/R/analysis/08_sampling.R"))) {
  suppressMessages(suppressWarnings(tryCatch({
    source(here("scripts/R/analysis/08_sampling.R"))
  }, error = function(e) NULL)))
}

if (file.exists(here("scripts/R/analysis/12_PSA.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/12_PSA.R"))))
}

# Ensure fallback values
if (!exists("time_horizon")) time_horizon <- 520
if (!exists("WTP")) WTP <- 51000
if (!exists("strategies")) strategies <- c("control", "crp", "tlr", "tmb_braf")
```

```{r analyze-decision-uncertainty, include=FALSE}
# Comprehensive analysis of decision uncertainty
if (exists("psa_obj") && exists("WTP")) {
  
  # Calculate NMB matrix
  cost_matrix <- as.matrix(psa_obj$cost)
  effect_matrix <- as.matrix(psa_obj$effect)
  nmb_matrix <- effect_matrix * WTP - cost_matrix
  
  # Strategy performance analysis
  expected_costs <- colMeans(cost_matrix, na.rm = TRUE)
  expected_effects <- colMeans(effect_matrix, na.rm = TRUE)
  expected_nmb <- colMeans(nmb_matrix, na.rm = TRUE)
  
  # Calculate standard errors
  se_costs <- apply(cost_matrix, 2, function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x))))
  se_effects <- apply(effect_matrix, 2, function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x))))
  se_nmb <- apply(nmb_matrix, 2, function(x) sd(x, na.rm = TRUE) / sqrt(sum(!is.na(x))))
  
  # EVPI calculation
  max_nmb_per_sim <- apply(nmb_matrix, 1, max, na.rm = TRUE)
  expected_max_nmb <- mean(max_nmb_per_sim, na.rm = TRUE)
  max_expected_nmb <- max(expected_nmb, na.rm = TRUE)
  evpi_calculated <- expected_max_nmb - max_expected_nmb
  
  # Optimal strategy analysis
  optimal_strategies <- apply(nmb_matrix, 1, function(x) colnames(nmb_matrix)[which.max(x)])
  strategy_distribution <- table(optimal_strategies)
  proportion_control <- ifelse("control" %in% names(strategy_distribution), 
                               strategy_distribution["control"] / sum(strategy_distribution), 0)
  
  # Cost-effectiveness analysis
  incremental_costs <- expected_costs - expected_costs["control"]
  incremental_effects <- expected_effects - expected_effects["control"]
  icers <- ifelse(incremental_effects > 0, incremental_costs / incremental_effects, NA)
  
  # Create probabilistic data for ICE scatter plot
  # Convert matrices to long format with incremental values
  psa_long <- data.frame()
  for (i in 1:nrow(cost_matrix)) {
    sim_data <- data.frame(
      Simulation = i,
      Strategy = colnames(cost_matrix),
      Cost = cost_matrix[i, ],
      Effect = effect_matrix[i, ],
      NMB = nmb_matrix[i, ]
    )
    # Calculate incremental values vs control
    control_cost <- sim_data$Cost[sim_data$Strategy == "control"]
    control_effect <- sim_data$Effect[sim_data$Strategy == "control"]
    
    sim_data$Incremental_Cost <- sim_data$Cost - control_cost
    sim_data$Incremental_Effect <- sim_data$Effect - control_effect
    
    psa_long <- rbind(psa_long, sim_data)
  }
  
  # NMB distributions for plotting
  nmb_long <- data.frame(
    Strategy = rep(colnames(nmb_matrix), each = nrow(nmb_matrix)),
    NMB = as.vector(nmb_matrix),
    Simulation = rep(1:nrow(nmb_matrix), ncol(nmb_matrix))
  )
  
  # Store comprehensive results
  analysis_results <- list(
    evpi = evpi_calculated,
    expected_costs = expected_costs,
    expected_effects = expected_effects,
    expected_nmb = expected_nmb,
    se_costs = se_costs,
    se_effects = se_effects,
    se_nmb = se_nmb,
    strategy_distribution = strategy_distribution,
    proportion_control = proportion_control,
    incremental_costs = incremental_costs,
    incremental_effects = incremental_effects,
    icers = icers,
    nmb_long = nmb_long,
    psa_long = psa_long,
    optimal_strategy = names(expected_nmb)[which.max(expected_nmb)]
  )
} else {
  # Create fallback empty results
  analysis_results <- list(
    evpi = 0,
    expected_costs = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    expected_effects = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    expected_nmb = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    se_costs = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    se_effects = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    se_nmb = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    strategy_distribution = table(c("control")),
    proportion_control = 1,
    incremental_costs = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    incremental_effects = c(control = 0, crp = 0, tlr = 0, tmb_braf = 0),
    icers = c(control = NA, crp = NA, tlr = NA, tmb_braf = NA),
    nmb_long = data.frame(Strategy = "control", NMB = 0, Simulation = 1),
    psa_long = data.frame(Strategy = "control", Incremental_Cost = 0, Incremental_Effect = 0),
    optimal_strategy = "control"
  )
}
```

# Summary

This report presents an Expected Values of Partially Perfect Information (EVPPI) analysis for the METIMMOX-1 economic model. I aim to use EVPPIs as probabilistic sensitivity analyses to identify parameters that contribute most to decision uncertainty and prioritize future research efforts. The report includes:

- Expected Value of Perfect Information (EVPI) calculation and decision uncertainty assessment
- Strategy performance comparison across treatment alternatives
- Incremental cost-effectiveness scatter plot analysis
- Interpretation of findings for clinical and research decision-making

\newpage

# Results

## Strategy Performance Comparison

```{r ice-scatter-plot, fig.cap="Incremental Cost-Effectiveness Scatter Plot", fig.height=7}
if (exists("analysis_results") && !is.null(analysis_results$psa_long)) {
  
  # Filter out control strategy (reference) and prepare data
  ice_data <- analysis_results$psa_long %>%
    filter(Strategy != "control") %>%
    mutate(
      Strategy_Label = case_when(
        Strategy == "crp" ~ "CRP-guided",
        Strategy == "tlr" ~ "TLR-guided", 
        Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
        TRUE ~ Strategy
      )
    )
  
  if (nrow(ice_data) > 0) {
    # Create ICE scatter plot
    p2 <- ggplot(ice_data, aes(x = Incremental_Effect, y = Incremental_Cost, color = Strategy_Label)) +
      geom_point(alpha = 0.3, size = 0.8) +
      geom_hline(yintercept = 0, linetype = "solid", alpha = 0.5) +
      geom_vline(xintercept = 0, linetype = "solid", alpha = 0.5) +
      geom_abline(slope = WTP, intercept = 0, linetype = "dashed", 
                  color = "blue", alpha = 0.8, size = 1.2) +
      stat_ellipse(aes(color = Strategy_Label), alpha = 0.7, size = 1) +
      scale_color_brewer(type = "qual", palette = "Set1") +
      scale_x_continuous(labels = scales::number_format(accuracy = 0.01)) +
      scale_y_continuous(labels = scales::comma_format(prefix = "€")) +
      labs(
        title = "Incremental Cost-Effectiveness Scatter Plot",
        subtitle = paste0("WTP threshold: €", format(WTP, big.mark = ","), "/QALY (dashed line) | ", 
                         nrow(ice_data)/3, " simulations per strategy"),
        x = "Incremental QALYs vs. Control",
        y = "Incremental Cost vs. Control (€)",
        color = "Strategy"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 11),
        legend.position = "bottom",
        legend.title = element_text(size = 11),
        panel.grid.minor = element_blank()
      ) +
      guides(color = guide_legend(override.aes = list(alpha = 1, size = 3)))
    
    print(p2)
  }
}
```

```{r strategy-performance-table}
if (exists("analysis_results") && !is.null(analysis_results$expected_costs)) {
  # Create more compact strategy comparison table with standard errors
  strategy_table <- data.frame(
    Strategy = c("Control", "CRP-guided", "TLR-guided", "TMB/BRAF-guided"),
    `Cost (€)` = paste0(round(analysis_results$expected_costs, 0), " (", round(analysis_results$se_costs, 0), ")"),
    `QALYs` = paste0(round(analysis_results$expected_effects, 3), " (", round(analysis_results$se_effects, 3), ")"),
    `NMB (€)` = paste0(round(analysis_results$expected_nmb, 0), " (", round(analysis_results$se_nmb, 0), ")"),
    `Inc. Cost (€)` = round(analysis_results$incremental_costs, 0),
    `Inc. QALYs` = round(analysis_results$incremental_effects, 3),
    `ICER (€/QALY)` = ifelse(is.na(analysis_results$icers), "Dominated", 
                             paste0("€", format(round(analysis_results$icers, 0), big.mark = ",")))
  )
  
  kable(strategy_table, 
        caption = "Strategy Performance Summary: Mean (Standard Error)",
        booktabs = TRUE,
        col.names = c("Strategy", "Cost (€)", "QALYs", "NMB (€)", "Inc. Cost (€)", "Inc. QALYs", "ICER (€/QALY)")) %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"), 
                  font_size = 8,
                  full_width = FALSE) %>%
    add_header_above(c(" " = 1, "Absolute Values" = 3, "Incremental vs. Control" = 3)) %>%
    column_spec(1, width = "2.5cm") %>%
    column_spec(2:4, width = "2cm") %>%
    column_spec(5:7, width = "1.8cm")
}
```

```{r nmb-comparison-plot, fig.cap="Net Monetary Benefit Distribution by Strategy", fig.height=6}
if (exists("analysis_results") && !is.null(analysis_results$nmb_long) && nrow(analysis_results$nmb_long) > 0) {
  # Create comprehensive NMB comparison plot
  p1 <- ggplot(analysis_results$nmb_long, aes(x = Strategy, y = NMB, fill = Strategy)) +
    geom_boxplot(alpha = 0.7, outlier.size = 0.5) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red", alpha = 0.7) +
    scale_fill_brewer(type = "qual", palette = "Set2") +
    scale_y_continuous(labels = scales::comma_format(prefix = "€")) +
    labs(
      title = "Net Monetary Benefit Distribution by Strategy",
      subtitle = paste0("At WTP threshold of €", format(WTP, big.mark = ","), " per QALY"),
      x = "Treatment Strategy",
      y = "Net Monetary Benefit (€)"
    ) +
    theme_minimal() +
    theme(
      legend.position = "none",
      axis.text.x = element_text(angle = 45, hjust = 1),
      plot.title = element_text(size = 14, face = "bold")
    )
  
  print(p1)
}
```

## Expected Value of Perfect Information

```{r evpi-summary, results='asis'}
if (exists("analysis_results") && !is.null(analysis_results)) {
  
  # Safely handle potentially missing values
  evpi_val <- ifelse(is.numeric(analysis_results$evpi) && !is.na(analysis_results$evpi), 
                     analysis_results$evpi, 0)
  expected_max_val <- ifelse(is.numeric(analysis_results$expected_max_nmb) && !is.na(analysis_results$expected_max_nmb), 
                             analysis_results$expected_max_nmb, 0)
  max_expected_val <- ifelse(is.numeric(analysis_results$expected_nmb) && length(analysis_results$expected_nmb) > 0, 
                             max(analysis_results$expected_nmb, na.rm = TRUE), 0)
  proportion_val <- ifelse(is.numeric(analysis_results$proportion_control) && !is.na(analysis_results$proportion_control), 
                           analysis_results$proportion_control, 1)
  
  cat("Total EVPI: €", round(evpi_val, 2), "\n\n")
  cat("Expected value with perfect information: €", round(expected_max_val, 2), "\n\n")
  cat("Expected value with current information: €", round(max_expected_val, 2), "\n\n")
  cat("Optimal strategy: ", analysis_results$optimal_strategy, " (standard care)\n\n")
  cat("Decision certainty: Control strategy optimal in ", 
      round(proportion_val * 100, 1), "% of simulations\n\n")
  
  cat("The EVPI of €", round(evpi_val, 2), 
      " indicates that there is no decision uncertainty in the current model. The standard care strategy (FLOX chemotherapy alone) dominates all biomarker-guided strategies across the entire range of parameter uncertainty considered in the probabilistic sensitivity analysis.")
} else {
  cat("Analysis results not available. Please check that the PSA analysis completed successfully.")
}
```

\newpage

# Interpretation

```{r clinical-implications, results='asis'}
if (exists("analysis_results") && !is.null(analysis_results$expected_nmb)) {
  cat("The analysis demonstrates that standard FLOX chemotherapy alone provides superior cost-effectiveness compared to biomarker-guided immunotherapy strategies at the €51,000/QALY threshold. The control strategy dominates across all parameter uncertainty ranges considered, indicating that biomarker strategies add substantial costs without sufficient QALY gains to justify the expense.\n\n")
  
  incremental_costs_noncontrol <- analysis_results$incremental_costs[names(analysis_results$incremental_costs) != "control"]
  incremental_costs_noncontrol <- incremental_costs_noncontrol[!is.na(incremental_costs_noncontrol)]
  
  if (length(incremental_costs_noncontrol) > 0) {
    cat("The biomarker-guided strategies show incremental costs ranging from €", 
        format(round(min(incremental_costs_noncontrol), 0), big.mark = ","), 
        " to €", format(round(max(incremental_costs_noncontrol), 0), big.mark = ","), 
        " compared to standard care, while providing mixed effectiveness outcomes. ")
  }
  
  # Identify strategies with negative NMB
  neg_nmb_strategies <- names(analysis_results$expected_nmb)[analysis_results$expected_nmb < 0]
  if (length(neg_nmb_strategies) > 0) {
    strategy_labels <- case_when(
      neg_nmb_strategies == "tlr" ~ "TLR-guided",
      neg_nmb_strategies == "crp" ~ "CRP-guided", 
      neg_nmb_strategies == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ neg_nmb_strategies
    )
    cat("Notably, the ", paste(strategy_labels, collapse = " and "), 
        " strategy shows negative expected net monetary benefit, indicating it is not cost-effective even compared to no intervention.")
  }
  cat("\n\n")
  
  cat("Given the absence of decision uncertainty (EVPI = €0), traditional EVPPI analysis cannot identify parameters for prioritized research, as no additional parameter precision would change the optimal treatment decision. This finding suggests that research efforts should focus on implementation of standard care rather than parameter refinement studies. The current evidence base appears sufficient for robust decision-making regarding these specific biomarker strategies.\n\n")
  
  cat("Future research might better target fundamental redesign of biomarker approaches, investigation of alternative cost structures, or development of entirely different treatment strategies that could achieve cost-effectiveness thresholds. The robust dominance of standard care across parameter uncertainty ranges indicates that substantial changes to model assumptions or intervention design would be required to alter the cost-effectiveness conclusion.\n\n")
  
  cat("The zero EVPI finding depends on current model assumptions and parameter uncertainty ranges. Results may differ under alternative model structures, wider parameter distributions, different willingness-to-pay thresholds, or longer time horizons that capture extended immunotherapy benefits. The healthcare system perspective may not reflect broader societal value, and real-world implementation factors are not captured in the current analysis.")
} else {
  cat("Analysis not available due to missing data.")
}
```

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.0