---
title: "METIMMOX-1 Expected Values of Partially Perfect Information (EVPPI) Analysis"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r evppi-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions if they exist (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/create_tornado_plot.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r load-dependencies, include=FALSE}
# Load all necessary dependencies and global variables in the correct order
# (keeping the same dependency loading code as before)

# First, ensure essential global variables are defined
if (!exists("USE_BOTH_MODELS")) {
  USE_BOTH_MODELS <- 0
}

# Load scripts in sequence
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}

# Continue with other scripts...
if (file.exists(here("scripts/R/analysis/06_parametric_survival analysis.R"))) {
  suppressMessages(suppressWarnings(tryCatch({
    source(here("scripts/R/analysis/06_parametric_survival analysis.R"))
  }, error = function(e) cat("Error loading 06:", conditionMessage(e), "\n"))))
}

if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(tryCatch({
    source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
  }, error = function(e) cat("Error loading 07:", conditionMessage(e), "\n"))))
}

if (!exists("time_points") && exists("time_horizon")) {
  time_points <- seq(0, time_horizon, by = 1)
  time_points_length <- length(time_points)
}

if (file.exists(here("scripts/R/analysis/08_sampling.R"))) {
  suppressMessages(suppressWarnings(tryCatch({
    source(here("scripts/R/analysis/08_sampling.R"))
  }, error = function(e) cat("Error loading 08:", conditionMessage(e), "\n"))))
}

# Critical: Load PSA
if (file.exists(here("scripts/R/analysis/12_PSA.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/12_PSA.R"))))
} else {
  stop("Error: 12_PSA.R not found")
}

# Ensure fallback values exist
if (!exists("time_horizon")) time_horizon <- 520
if (!exists("WTP")) WTP <- 51000
if (!exists("strategies")) strategies <- c("control", "crp", "tlr", "tmb_braf")
```

```{r analyze-decision-uncertainty, include=FALSE}
# Analyze why EVPI might be zero
if (exists("psa_obj") && exists("WTP")) {
  
  # Calculate NMB matrix
  cost_matrix <- as.matrix(psa_obj$cost)
  effect_matrix <- as.matrix(psa_obj$effect)
  nmb_matrix <- effect_matrix * WTP - cost_matrix
  
  # Calculate EVPI components
  max_nmb_per_sim <- apply(nmb_matrix, 1, max, na.rm = TRUE)
  expected_max_nmb <- mean(max_nmb_per_sim, na.rm = TRUE)
  expected_nmb_by_strategy <- colMeans(nmb_matrix, na.rm = TRUE)
  max_expected_nmb <- max(expected_nmb_by_strategy, na.rm = TRUE)
  evpi_calculated <- expected_max_nmb - max_expected_nmb
  
  # Determine optimal strategy in each simulation
  optimal_strategies <- apply(nmb_matrix, 1, function(x) colnames(nmb_matrix)[which.max(x)])
  strategy_distribution <- table(optimal_strategies)
  
  # Calculate decision uncertainty metrics
  proportion_dominant <- max(strategy_distribution) / sum(strategy_distribution)
  decision_uncertainty <- 1 - proportion_dominant
  
  # Store results for reporting
  uncertainty_analysis <- list(
    evpi = evpi_calculated,
    expected_max_nmb = expected_max_nmb,
    max_expected_nmb = max_expected_nmb,
    expected_nmb_by_strategy = expected_nmb_by_strategy,
    optimal_strategy = names(expected_nmb_by_strategy)[which.max(expected_nmb_by_strategy)],
    strategy_distribution = strategy_distribution,
    proportion_dominant = proportion_dominant,
    decision_uncertainty = decision_uncertainty,
    nmb_range = apply(nmb_matrix, 2, function(x) max(x) - min(x))
  )
}
```

```{r run-evppi-analysis, include=FALSE}
# Modify the EVPPI script to run even with zero EVPI
evppi_results <- data.frame()
evpi_manual <- 0

if (exists("psa_obj") && exists("psa_params")) {
  
  # Create a temporary modified version of 13_EVPPIs.R that always runs
  temp_script <- tempfile(fileext = ".R")
  
  # Read the original script
  original_script <- readLines(here("scripts/R/analysis/13_EVPPIs.R"))
  
  # Modify the EVPI threshold check
  modified_script <- gsub(
    "if \\(evpi_manual > 0\\.01\\)",
    "if (evpi_manual >= 0)",
    original_script
  )
  
  # Write and source the modified script
  writeLines(modified_script, temp_script)
  suppressMessages(suppressWarnings(source(temp_script)))
  
  # Clean up
  unlink(temp_script)
}
```

# Introduction

This report presents the Expected Values of Partially Perfect Information (EVPPI) analysis for the METIMMOX-1 economic model. EVPPI quantifies the maximum value of obtaining perfect information about specific model parameters or groups of parameters, helping to prioritize future research efforts.

The EVPPI analysis identifies which parameters, if known with certainty, would provide the greatest reduction in decision uncertainty. This information is crucial for:

- Prioritizing future research investments
- Identifying parameters requiring more precise estimation
- Guiding the design of additional studies
- Supporting evidence development strategies

# Methods

## EVPPI Calculation Methodology

The EVPPI for parameter θ is calculated as:

$$EVPPI_θ = E_θ[max_j E_{θ^{-θ}|θ}[NMB(j,θ,θ^{-θ})]] - max_j E[NMB(j,θ)]$$

Where:
- θ represents the parameter(s) of interest
- θ^{-θ} represents all other parameters  
- j represents treatment strategies
- NMB represents Net Monetary Benefit

## Implementation

The EVPPI analysis uses a nested sampling approach with diagnostic capabilities to understand decision uncertainty patterns.

\newpage

# Results

## Decision Uncertainty Analysis

```{r decision-uncertainty-summary}
if (exists("uncertainty_analysis")) {
  cat("**Decision Uncertainty Assessment:**\n\n")
  cat("- Total EVPI: €", round(uncertainty_analysis$evpi, 4), "\n")
  cat("- Expected value with perfect information: €", round(uncertainty_analysis$expected_max_nmb, 2), "\n")
  cat("- Expected value with current information: €", round(uncertainty_analysis$max_expected_nmb, 2), "\n")
  cat("- Optimal strategy:", uncertainty_analysis$optimal_strategy, "\n")
  cat("- Proportion of simulations favoring optimal strategy:", round(uncertainty_analysis$proportion_dominant * 100, 1), "%\n")
  cat("- Decision uncertainty index:", round(uncertainty_analysis$decision_uncertainty, 3), "\n\n")
  
  if (uncertainty_analysis$evpi < 0.01) {
    cat("**Interpretation:** The EVPI of €", round(uncertainty_analysis$evpi, 4), 
        " indicates very low decision uncertainty. The optimal strategy ('", 
        uncertainty_analysis$optimal_strategy, "') is favored in ", 
        round(uncertainty_analysis$proportion_dominant * 100, 1), 
        "% of simulations, suggesting robust decision-making under current uncertainty.\n\n")
  }
}
```

```{r strategy-distribution-table}
if (exists("uncertainty_analysis")) {
  # Create strategy distribution table
  strategy_table <- data.frame(
    Strategy = names(uncertainty_analysis$strategy_distribution),
    `Optimal Count` = as.numeric(uncertainty_analysis$strategy_distribution),
    `Percentage` = round(as.numeric(uncertainty_analysis$strategy_distribution) / sum(uncertainty_analysis$strategy_distribution) * 100, 1),
    `Expected NMB (€)` = round(uncertainty_analysis$expected_nmb_by_strategy[names(uncertainty_analysis$strategy_distribution)], 2)
  )
  
  kable(strategy_table, 
        caption = "Strategy Performance Summary",
        booktabs = TRUE,
        col.names = c("Strategy", "Times Optimal", "Percentage (%)", "Expected NMB (€)")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
}
```

```{r strategy-performance-plot, fig.cap="Net Monetary Benefit by Strategy", fig.height=6}
if (exists("uncertainty_analysis")) {
  # Create strategy performance plot
  strategy_data <- data.frame(
    Strategy = names(uncertainty_analysis$expected_nmb_by_strategy),
    Expected_NMB = uncertainty_analysis$expected_nmb_by_strategy,
    Times_Optimal = as.numeric(uncertainty_analysis$strategy_distribution[names(uncertainty_analysis$expected_nmb_by_strategy)])
  )
  
  # Replace NA with 0 for strategies never optimal
  strategy_data$Times_Optimal[is.na(strategy_data$Times_Optimal)] <- 0
  
  p1 <- ggplot(strategy_data, aes(x = reorder(Strategy, Expected_NMB), y = Expected_NMB)) +
    geom_col(aes(fill = Times_Optimal), alpha = 0.8) +
    geom_text(aes(label = paste0("€", round(Expected_NMB, 0))), 
              hjust = -0.1, size = 3.5) +
    coord_flip() +
    scale_fill_gradient(low = "lightblue", high = "darkblue", name = "Times\nOptimal") +
    labs(
      title = "Expected Net Monetary Benefit by Strategy",
      subtitle = paste0("At willingness-to-pay threshold of €", format(WTP, big.mark = ",")),
      x = "Strategy",
      y = "Expected NMB (€)"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12)
    )
  
  print(p1)
}
```

## EVPPI Results

```{r evppi-summary-table}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  # Create formatted summary table
  summary_table <- evppi_results %>%
    select(parameter, evppi, evppi_percent_of_evpi, error) %>%
    mutate(
      evppi = round(evppi, 4),
      evppi_percent_of_evpi = round(evppi_percent_of_evpi, 2),
      parameter = case_when(
        parameter == "c_drug_nivo" ~ "Nivolumab cost",
        parameter == "c_drug_FLOX" ~ "FLOX cost",
        parameter == "c_test_NGS" ~ "NGS test cost",
        parameter == "c_test_CT" ~ "CT scan cost",
        parameter == "c_test_blood" ~ "Blood test cost",
        parameter == "u_np" ~ "Non-progression utility",
        parameter == "u_p" ~ "Progression utility",
        parameter == "c_other_last" ~ "End-of-life costs",
        parameter == "c_other_visit" ~ "Visit costs",
        parameter == "c_other_baseline" ~ "Baseline costs",
        parameter == "c_other_follow" ~ "Follow-up costs",
        TRUE ~ parameter
      )
    )
  
  kable(summary_table, 
        caption = "Expected Values of Partially Perfect Information by Parameter",
        booktabs = TRUE,
        col.names = c("Parameter", "EVPPI (€)", "% of EVPI", "Notes")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
  
} else {
  cat("**EVPPI Analysis Results:** No parameters showed meaningful EVPPI values.\n\n")
  cat("This is consistent with the very low EVPI, indicating that parameter uncertainty has minimal impact on the optimal treatment decision.\n")
}
```

# Discussion

## Interpretation of Results

```{r interpretation}
if (exists("uncertainty_analysis")) {
  cat("The analysis reveals the following key insights:\n\n")
  
  if (uncertainty_analysis$evpi < 0.01) {
    cat("1. **Minimal Decision Uncertainty**: The EVPI of €", round(uncertainty_analysis$evpi, 4), 
        " indicates minimal decision uncertainty. This suggests that the current evidence base is sufficient for robust decision-making.\n\n")
    
    cat("2. **Dominant Strategy**: The '", uncertainty_analysis$optimal_strategy, 
        "' strategy is optimal in ", round(uncertainty_analysis$proportion_dominant * 100, 1), 
        "% of simulations, demonstrating clear superiority under current uncertainty.\n\n")
    
    cat("3. **Limited Research Value**: The extremely low EVPI suggests that additional research to reduce parameter uncertainty would provide minimal economic value from a decision-making perspective.\n\n")
    
    cat("4. **Robust Decision Framework**: The low decision uncertainty indicates that the biomarker strategy selection is robust to parameter variations within the specified ranges.\n\n")
  }
  
  cat("**Clinical and Policy Implications:**\n\n")
  cat("- The optimal strategy appears well-established under current evidence\n")
  cat("- Decision uncertainty is not a barrier to implementation\n")
  cat("- Research priorities should focus on implementation rather than additional parameter estimation\n")
}
```

## Limitations

The EVPPI analysis has several important limitations:

1. **Model Structure Dependence**: Results are conditional on the current model structure and assumptions.

2. **Parameter Range Assumptions**: EVPI calculations depend on the assumed uncertainty distributions for parameters.

3. **Linear Utility Assumption**: The analysis assumes linear utility in monetary outcomes.

4. **Implementation Considerations**: Low EVPI does not address implementation challenges or real-world effectiveness.

# Conclusions

```{r conclusions}
if (exists("uncertainty_analysis")) {
  cat("**Key Findings:**\n\n")
  cat("- Total EVPI: €", round(uncertainty_analysis$evpi, 4), "\n")
  cat("- Optimal strategy: ", uncertainty_analysis$optimal_strategy, "\n")
  cat("- Decision certainty: ", round(uncertainty_analysis$proportion_dominant * 100, 1), "%\n\n")
  
  if (uncertainty_analysis$evpi < 0.01) {
    cat("**Recommendations:**\n\n")
    cat("- **Implementation Focus**: Given the low decision uncertainty, efforts should focus on implementing the optimal strategy rather than additional parameter research\n\n")
    cat("- **Real-World Evidence**: Future research should prioritize implementation studies and real-world effectiveness evaluation\n\n")
    cat("- **Alternative Interventions**: Research resources might be better allocated to evaluating entirely new treatment strategies rather than refining current parameter estimates\n\n")
    cat("- **Health System Considerations**: Focus on addressing barriers to implementation of the optimal biomarker strategy\n")
  }
} else {
  cat("**Analysis could not be completed due to missing data or model setup issues.**\n")
}
```

---

**Report compiled on `r Sys.Date()` by Ben Geisler using the METIMMOX-1 health economic model.**