---
title: "Value of Information Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 8, fig.height = 6,
                      dpi = 300, out.width = "100%")
knitr::opts_knit$set(root.dir = here::here())

if (!require("pacman")) install.packages("pacman")
pacman::p_load(here, knitr, kableExtra, ggplot2, dplyr, scales, dampack)

suppressMessages(suppressWarnings({
  source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
  source(here::here("scripts/R/analysis/03_biomarker_strategies.R"))
  source(here::here("scripts/R/functions/multi_model_cea.R"))
}))

evppi_results <- NULL
evpi_manual <- NA_real_
evppi_cache_file <- here::here("data", "tidy",
                               paste0("evppi_results_", utility_source_label, ".RData"))
if (file.exists(evppi_cache_file)) {
  load(evppi_cache_file)
}

psa_obj <- load_psa_cache(verbose = FALSE)

format_eur <- function(x) {
  ifelse(is.na(x) | !is.finite(x), "--",
         scales::dollar(x, prefix = "EUR ", accuracy = 1))
}
```

# Overview

This report summarizes expected value of information results for the single joint economic model. The underlying PSA object contains three strategies: standard of care, CRP-guided immunotherapy, and TMB/BRAF-guided immunotherapy.

# PSA Decision Uncertainty

```{r evpi-summary}
if (is.null(psa_obj)) {
  cat("PSA cache not found. Run scripts/R/analysis/12_PSA.R before rendering this report.")
} else {
  psa_summary <- create_psa_summary_table(psa_obj, wtp = WTP) %>%
    mutate(
      Mean_Cost = format_eur(Mean_Cost),
      Mean_QALY = sprintf("%.3f", Mean_QALY),
      Prob_CE = scales::percent(Prob_CE, accuracy = 0.1)
    )

  knitr::kable(
    psa_summary,
    booktabs = TRUE,
    align = c("l", "r", "r", "r"),
    col.names = c("Strategy", "Mean Cost", "Mean QALYs", "Probability Cost-Effective"),
    caption = paste0("PSA summary at WTP = EUR ", format(WTP, big.mark = ","))
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
}
```

```{r evpi-value}
evpi_display <- data.frame(
  Metric = c("Per-patient EVPI", "Population EVPI"),
  Value = c(
    format_eur(evpi_manual),
    if ("evpi_population_millions" %in% names(evppi_results)) {
      paste0("EUR ", sprintf("%.2f", max(evppi_results$evpi_population_millions, na.rm = TRUE)), "M")
    } else {
      "--"
    }
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  evpi_display,
  booktabs = TRUE,
  align = c("l", "r"),
  caption = "Expected value of perfect information"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# EVPPI Results

```{r evppi-table}
if (is.null(evppi_results) || nrow(evppi_results) == 0) {
  cat("EVPPI cache not found. Run scripts/R/analysis/13_EVPPIs.R before rendering this report.")
} else {
  evppi_display <- evppi_results %>%
    arrange(desc(evppi)) %>%
    mutate(
      EVPPI = format_eur(evppi),
      `Percent of EVPI` = sprintf("%.1f%%", evppi_percent_of_evpi),
      `Population EVPPI` = if ("evppi_population_millions" %in% names(.)) {
        paste0("EUR ", sprintf("%.2f", evppi_population_millions), "M")
      } else {
        "--"
      }
    ) %>%
    select(Parameter = parameter, EVPPI, `Percent of EVPI`, `Population EVPPI`)

  knitr::kable(
    evppi_display,
    booktabs = TRUE,
    align = c("l", "r", "r", "r"),
    caption = "Expected value of partial perfect information"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
}
```

```{r evppi-plot, fig.cap="EVPPI by parameter or parameter group"}
if (is.null(evppi_results) || nrow(evppi_results) == 0) {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = "EVPPI cache not available", size = 5) +
    theme_void()
} else {
  plot_df <- evppi_results %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))

  ggplot(plot_df, aes(x = evppi, y = parameter)) +
    geom_col(fill = "#3B6EA8") +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR ")) +
    labs(x = "EVPPI", y = NULL) +
    theme_minimal()
}
```

# Population Scaling

Population-level values assume `r annual_incidence_norway` annual eligible patients in Norway, a `r research_horizon_years`-year research horizon, and a `r scales::percent(discount_rate_research, accuracy = 0.1)` annual discount rate for research benefits.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
