---
title: "METIMMOX-1 Expected Value of Partially Perfect Information Analysis"
subtitle: "Multi-Scenario Analysis for Biomarker-Guided Strategies in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r evppi-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  tidyr, scales, gridExtra, dampack
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Check if results file exists
results_file <- here::here("data/tidy/scenario_evppi_results.RData")

if (!file.exists(results_file)) {
  stop("Results file not found. Please run scripts/R/analysis/14_scenario_EVPPIs.R first to generate the analysis results.")
}

# Load results
load(results_file)
```

# Summary

This report presents the results of an Expected Value of Partially Perfect Information (EVPPI) analysis for the METIMMOX-1 decision-analytic model. The analysis evaluates the value of reducing uncertainty in individual model parameters across multiple scenarios with varying willingness-to-pay (WTP) thresholds and nivolumab drug costs.

The Expected Value of Partially Perfect Information (EVPPI) quantifies the value of eliminating uncertainty in specific model parameters. It represents the maximum amount that should be paid for additional research to perfectly inform a particular parameter. EVPI (Expected Value of Perfect Information) represents the value of eliminating all uncertainty, and EVPPI for any parameter cannot exceed total EVPI.

```{r scenario-table-summary}
scenario_summary <- scenarios %>%
  mutate(
    `WTP Threshold` = paste0("€", format(wtp, big.mark = ",")),
    `Nivolumab Cost` = paste0("€", format(c_drug_nivo, big.mark = ","))
  ) %>%
  select(`Scenario Name` = scenario_name,
         `WTP Threshold`,
         `Nivolumab Cost`)

kable(scenario_summary,
      caption = "Analysis scenario definitions. Higher WTP thresholds (€100,000 and €150,000) are arbitrary exploratory thresholds, though the highest severity adjustment in Norwegian guidelines may fall between these values. The decreased nivolumab cost (€4,641) represents an 80\\% discount compared to the 40\\% discount in the base case scenario.",
      booktabs = TRUE,
      align = c("l", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), 
                font_size = 10,
                full_width = FALSE)
```

\newpage

# Probabilistic Sensitivity Analysis Results

## Incremental Cost-Effectiveness Scatter Plot

```{r ice-scatter, fig.cap="Incremental cost-effectiveness scatter plot from probabilistic sensitivity analysis (base case)", fig.height=6}
base_results <- all_scenario_results[["base"]]

if (!is.null(base_results$psa_obj)) {
  plot(base_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

## Cost-Effectiveness Analysis Summary

```{r cea-summary-table}
base_results <- all_scenario_results[["base"]]

if (!is.null(base_results$psa_obj)) {
  psa_summary <- summary(base_results$psa_obj, calc_sds = TRUE)
  
  # Format the summary table
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `SD Effect` = round(sdEffect, 3)
    ) %>%
    select(Strategy, `Mean Cost (€)`, `Mean Effect (QALYs)`, `SD Cost`, `SD Effect`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary from probabilistic sensitivity analysis",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 9,
                  full_width = FALSE)
}
```

## Cost-Effectiveness Acceptability Curves

```{r ceac-plot, fig.cap="Cost-effectiveness acceptability curves showing probability of cost-effectiveness across willingness-to-pay thresholds", fig.height=6}
base_results <- all_scenario_results[["base"]]

if (!is.null(base_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
  ceac_obj <- ceac(c_wtp, base_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

## Expected Value of Perfect Information

The Expected Value of Perfect Information (EVPI) represents the maximum amount that should be paid to eliminate all parameter uncertainty in the decision model. A positive EVPI indicates decision uncertainty exists at the specified WTP threshold.

```{r evpi-base-case}
base_results <- all_scenario_results[["base"]]

if (!is.null(base_results) && nrow(base_results$evppi_results) > 0) {
  base_evpi <- base_results$evppi_results$evpi[1]
  base_wtp <- scenarios$wtp[scenarios$scenario_id == "base"]
} else {
  base_evpi <- 0
  base_wtp <- 51000
}
```

**Base Case EVPI (WTP = €`r format(base_wtp, big.mark = ",")`): €`r round(base_evpi, 2)`**

```{r evpi-interpretation, results='asis'}
if (base_evpi > 0.01) {
  cat("\n\nThe positive EVPI indicates decision uncertainty at the base case WTP threshold. This suggests that additional research to reduce parameter uncertainty could have value.\n")
} else {
  cat("\n\nThe EVPI is effectively zero, indicating no decision uncertainty at the base case WTP threshold. In this case, one strategy is clearly dominant regardless of parameter uncertainty, making EVPPI calculations less meaningful for the base case scenario.\n")
}
```

\newpage

# Base Case Scenario

**Willingness-to-Pay Threshold:** €`r format(scenarios$wtp[scenarios$scenario_id == "base"], big.mark = ",")`

**Nivolumab Cost:** €`r format(scenarios$c_drug_nivo[scenarios$scenario_id == "base"], big.mark = ",")`

**Total EVPI:** €`r round(base_evpi, 2)`

## EVPPI Results

```{r base-case-evppi-table}
if (!is.null(base_results) && nrow(base_results$evppi_results) > 0 && base_evpi > 0.01) {
  base_evppi <- base_results$evppi_results %>%
    select(Parameter = parameter,
           EVPPI = evppi,
           `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(
      EVPPI = paste0("€", round(EVPPI, 2)),
      `% of EVPI` = paste0(round(`% of EVPI`, 1), "%")
    )
  
  kable(base_evppi,
        caption = "Base case EVPPI results (ranked by importance)",
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
} else {
  cat("\n\nNo meaningful EVPPI results available for base case scenario due to zero EVPI.\n")
}
```

```{r base-case-plot, fig.cap="Base case EVPPI by parameter"}
if (!is.null(base_results) && nrow(base_results$evppi_results) > 0 && base_evpi > 0.01) {
  base_plot_data <- base_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(desc(evppi)) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(base_plot_data) > 0) {
    ggplot(base_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "steelblue", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))),
                hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(
        title = "Base Case: Expected Value of Partially Perfect Information",
        subtitle = paste0("WTP = €", format(scenarios$wtp[1], big.mark = ",")),
        x = "EVPPI (€)",
        y = NULL
      ) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 1: Decreased Nivolumab Cost

**Willingness-to-Pay Threshold:** €51,000

**Nivolumab Cost:** €4,641 (80% discount)

```{r s1-evpi}
s1_results <- all_scenario_results[["s1_decreased_nivo"]]

if (!is.null(s1_results) && nrow(s1_results$evppi_results) > 0) {
  s1_evpi <- s1_results$evppi_results$evpi[1]
} else {
  s1_evpi <- 0
}
```

**Total EVPI:** €`r round(s1_evpi, 2)`

```{r s1-interpretation, results='asis'}
if (s1_evpi > 0.01) {
  cat("\n\nReducing nivolumab costs creates decision uncertainty, making EVPPI analysis meaningful.\n")
} else {
  cat("\n\nEven with decreased nivolumab costs, EVPI remains near zero at this WTP threshold.\n")
}
```

## Incremental Cost-Effectiveness Results

```{r s1-ice-scatter, fig.cap="Incremental cost-effectiveness scatter plot (Scenario 1: Decreased nivolumab cost)", fig.height=6}
if (!is.null(s1_results$psa_obj)) {
  plot(s1_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

## EVPPI Results

```{r s1-evppi-table}
if (!is.null(s1_results) && nrow(s1_results$evppi_results) > 0 && s1_evpi > 0.01) {
  s1_evppi <- s1_results$evppi_results %>%
    select(Parameter = parameter,
           EVPPI = evppi,
           `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(
      EVPPI = paste0("€", round(EVPPI, 2)),
      `% of EVPI` = paste0(round(`% of EVPI`, 1), "%")
    )
  
  kable(s1_evppi,
        caption = "EVPPI results: Decreased nivolumab cost",
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
} else {
  cat("\n\nNo meaningful EVPPI results available for this scenario.\n")
}
```

```{r s1-plot, fig.cap="EVPPI with decreased nivolumab cost"}
if (!is.null(s1_results) && nrow(s1_results$evppi_results) > 0 && s1_evpi > 0.01) {
  s1_plot_data <- s1_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(desc(evppi)) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s1_plot_data) > 0) {
    ggplot(s1_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "darkorange", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))),
                hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(
        title = "EVPPI with Decreased Nivolumab Cost",
        subtitle = "WTP = €51,000 | Nivolumab = €4,641",
        x = "EVPPI (€)",
        y = NULL
      ) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 2: Higher WTP Threshold (€100,000)

**Willingness-to-Pay Threshold:** €100,000

**Nivolumab Cost:** Standard (base case)

```{r s2-evpi}
s2_results <- all_scenario_results[["s2_wtp100k"]]

if (!is.null(s2_results) && nrow(s2_results$evppi_results) > 0) {
  s2_evpi <- s2_results$evppi_results$evpi[1]
} else {
  s2_evpi <- 0
}
```

**Total EVPI:** €`r round(s2_evpi, 2)`

## Incremental Cost-Effectiveness Results

```{r s2-ice-scatter, fig.cap="Incremental cost-effectiveness scatter plot (Scenario 2: WTP €100,000)", fig.height=6}
if (!is.null(s2_results$psa_obj)) {
  plot(s2_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

## EVPPI Results

```{r s2-evppi-table}
if (!is.null(s2_results) && nrow(s2_results$evppi_results) > 0 && s2_evpi > 0.01) {
  s2_evppi <- s2_results$evppi_results %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s2_evppi, 
        caption = "EVPPI results: WTP €100,000", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
} else {
  cat("\n\nNo meaningful EVPPI results available for this scenario.\n")
}
```

```{r s2-plot, fig.cap="EVPPI at WTP €100,000"}
if (!is.null(s2_results) && nrow(s2_results$evppi_results) > 0 && s2_evpi > 0.01) {
  s2_plot_data <- s2_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(desc(evppi)) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s2_plot_data) > 0) {
    ggplot(s2_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "forestgreen", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI at Higher WTP Threshold",
           subtitle = "WTP = €100,000 | Standard Nivolumab Cost",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 3: Higher WTP with Decreased Nivolumab Cost

**Willingness-to-Pay Threshold:** €100,000

**Nivolumab Cost:** €4,641 (80% discount)

```{r s3-evpi}
s3_results <- all_scenario_results[["s3_wtp100k_decreased"]]

if (!is.null(s3_results) && nrow(s3_results$evppi_results) > 0) {
  s3_evpi <- s3_results$evppi_results$evpi[1]
} else {
  s3_evpi <- 0
}
```

**Total EVPI:** €`r round(s3_evpi, 2)`

## Incremental Cost-Effectiveness Results

```{r s3-ice-scatter, fig.cap="Incremental cost-effectiveness scatter plot (Scenario 3: WTP €100,000 with decreased nivolumab)", fig.height=6}
if (!is.null(s3_results$psa_obj)) {
  plot(s3_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

## EVPPI Results

```{r s3-evppi-table}
if (!is.null(s3_results) && nrow(s3_results$evppi_results) > 0 && s3_evpi > 0.01) {
  s3_evppi <- s3_results$evppi_results %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s3_evppi, 
        caption = "EVPPI results: WTP €100,000 + decreased nivolumab", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
} else {
  cat("\n\nNo meaningful EVPPI results available for this scenario.\n")
}
```

```{r s3-plot, fig.cap="EVPPI: WTP €100,000 with decreased nivolumab"}
if (!is.null(s3_results) && nrow(s3_results$evppi_results) > 0 && s3_evpi > 0.01) {
  s3_plot_data <- s3_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(desc(evppi)) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s3_plot_data) > 0) {
    ggplot(s3_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "purple", alpha = 0.7) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI: Combined Scenario",
           subtitle = "WTP = €100,000 | Decreased Nivolumab (€4,641)",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 4: Highest WTP Threshold (€150,000)

**Willingness-to-Pay Threshold:** €150,000

**Nivolumab Cost:** Standard (base case)

```{r s4-evpi}
s4_results <- all_scenario_results[["s4_wtp150k"]]

if (!is.null(s4_results) && nrow(s4_results$evppi_results) > 0) {
  s4_evpi <- s4_results$evppi_results$evpi[1]
} else {
  s4_evpi <- 0
}
```

**Total EVPI:** €`r round(s4_evpi, 2)`

## Incremental Cost-Effectiveness Results

```{r s4-ice-scatter, fig.cap="Incremental cost-effectiveness scatter plot (Scenario 4: WTP €150,000)", fig.height=6}
if (!is.null(s4_results$psa_obj)) {
  plot(s4_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

## EVPPI Results

```{r s4-evppi-table}
if (!is.null(s4_results) && nrow(s4_results$evppi_results) > 0 && s4_evpi > 0.01) {
  s4_evppi <- s4_results$evppi_results %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s4_evppi, 
        caption = "EVPPI results: WTP €150,000", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
} else {
  cat("\n\nNo meaningful EVPPI results available for this scenario.\n")
}
```

```{r s4-plot, fig.cap="EVPPI at WTP €150,000"}
if (!is.null(s4_results) && nrow(s4_results$evppi_results) > 0 && s4_evpi > 0.01) {
  s4_plot_data <- s4_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(desc(evppi)) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s4_plot_data) > 0) {
    ggplot(s4_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "darkred", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI at Highest WTP Threshold",
           subtitle = "WTP = €150,000 | Standard Nivolumab Cost",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 5: Highest WTP with Decreased Nivolumab Cost

**Willingness-to-Pay Threshold:** €150,000

**Nivolumab Cost:** €4,641 (80% discount)

```{r s5-evpi}
s5_results <- all_scenario_results[["s5_wtp150k_decreased"]]

if (!is.null(s5_results) && nrow(s5_results$evppi_results) > 0) {
  s5_evpi <- s5_results$evppi_results$evpi[1]
} else {
  s5_evpi <- 0
}
```

**Total EVPI:** €`r round(s5_evpi, 2)`

## Incremental Cost-Effectiveness Results

```{r s5-ice-scatter, fig.cap="Incremental cost-effectiveness scatter plot (Scenario 5: WTP €150,000 with decreased nivolumab)", fig.height=6}
if (!is.null(s5_results$psa_obj)) {
  plot(s5_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

## EVPPI Results

```{r s5-evppi-table}
if (!is.null(s5_results) && nrow(s5_results$evppi_results) > 0 && s5_evpi > 0.01) {
  s5_evppi <- s5_results$evppi_results %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s5_evppi, 
        caption = "EVPPI results: WTP €150,000 + decreased nivolumab", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
} else {
  cat("\n\nNo meaningful EVPPI results available for this scenario.\n")
}
```

```{r s5-plot, fig.cap="EVPPI: Highest WTP with decreased nivolumab cost"}
if (!is.null(s5_results) && nrow(s5_results$evppi_results) > 0 && s5_evpi > 0.01) {
  s5_plot_data <- s5_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(desc(evppi)) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s5_plot_data) > 0) {
    ggplot(s5_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "navy", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI: Highest WTP + Decreased Cost",
           subtitle = "WTP = €150,000 | Decreased Nivolumab (€4,641)",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Comparative Analysis Across Scenarios

```{r comparative-summary-table}
# Create comparative summary table
if (nrow(evppi_all_scenarios) > 0) {
  comp_summary <- evppi_all_scenarios %>%
    group_by(scenario_name, wtp) %>%
    summarise(
      EVPI = first(evpi),
      `Top Parameter` = parameter[which.max(evppi)],
      `Max EVPPI` = max(evppi),
      `% of EVPI` = round(max(evppi) / first(evpi) * 100, 1),
      .groups = "drop"
    ) %>%
    mutate(
      WTP = paste0("€", format(wtp, big.mark = ",")),
      EVPI = paste0("€", round(EVPI, 2)),
      `Max EVPPI` = paste0("€", round(`Max EVPPI`, 2))
    ) %>%
    select(Scenario = scenario_name, WTP, EVPI, `Top Parameter`, `Max EVPPI`, `% of EVPI`)
  
  kable(comp_summary, 
        caption = "Summary of EVPI and top EVPPI by scenario",
        booktabs = TRUE,
        align = c("l", "r", "r", "l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 9,
                  full_width = FALSE)
}
```

## EVPI Comparison

```{r evpi-comparison, fig.cap="Expected Value of Perfect Information across scenarios", fig.height=5}
if (nrow(evppi_all_scenarios) > 0) {
  evpi_comparison <- evppi_all_scenarios %>%
    select(scenario_name, wtp, evpi) %>%
    distinct() %>%
    mutate(
      cost_type = ifelse(grepl("Decreased", scenario_name), "Decreased Nivo", "Standard Nivo"),
      wtp_label = paste0("€", format(wtp/1000, big.mark = ","), "k")
    )
  
  ggplot(evpi_comparison, aes(x = wtp_label, y = evpi, fill = cost_type)) +
    geom_col(position = "dodge", alpha = 0.8) +
    geom_text(aes(label = paste0("€", round(evpi, 2))),
              position = position_dodge(width = 0.9),
              vjust = -0.5, size = 3) +
    scale_fill_manual(values = c("Decreased Nivo" = "coral", "Standard Nivo" = "steelblue")) +
    labs(
      title = "Expected Value of Perfect Information Across Scenarios",
      subtitle = "Comparison by WTP Threshold and Nivolumab Cost",
      x = "Willingness-to-Pay Threshold",
      y = "EVPI (€)",
      fill = "Cost Scenario"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

## Parameter Importance Heatmap

```{r parameter-heatmap, fig.cap="Parameter importance across scenarios (top 10 parameters)", fig.height=7}
if (nrow(evppi_all_scenarios) > 0) {
  # Get top 10 parameters overall
  top_params <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(total_evppi = sum(evppi), .groups = "drop") %>%
    arrange(desc(total_evppi)) %>%
    slice(1:10) %>%
    pull(parameter)
  
  heatmap_data <- evppi_all_scenarios %>%
    filter(parameter %in% top_params) %>%
    mutate(
      scenario_short = factor(case_when(
        scenario_id == "base" ~ "Base\n(€51k)",
        scenario_id == "s1_decreased_nivo" ~ "S1: €51k\nDecreased",
        scenario_id == "s2_wtp100k" ~ "S2: €100k\nStandard",
        scenario_id == "s3_wtp100k_decreased" ~ "S3: €100k\nDecreased",
        scenario_id == "s4_wtp150k" ~ "S4: €150k\nStandard",
        scenario_id == "s5_wtp150k_decreased" ~ "S5: €150k\nDecreased"
      ), levels = c("Base\n(€51k)", "S1: €51k\nDecreased", "S2: €100k\nStandard", 
                    "S3: €100k\nDecreased", "S4: €150k\nStandard", "S5: €150k\nDecreased"))
    )
  
  ggplot(heatmap_data, aes(x = scenario_short, y = parameter, fill = evppi)) +
    geom_tile(color = "white", linewidth = 1) +
    geom_text(aes(label = paste0("€", round(evppi, 1))), 
              color = "white", fontface = "bold", size = 2.5) +
    scale_fill_gradient(low = "navy", high = "red", 
                       name = "EVPPI (€)",
                       labels = scales::dollar_format(prefix = "€")) +
    labs(
      title = "Parameter Importance Across Scenarios",
      subtitle = "EVPPI values for top 10 parameters",
      x = "Scenario",
      y = "Parameter"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 12),
      axis.text.x = element_text(angle = 0, hjust = 0.5, size = 9),
      axis.text.y = element_text(size = 9),
      legend.position = "right"
    )
}
```

\newpage

# Conclusions and Recommendations

## Summary of Findings

```{r conclusions, results='asis'}
if (nrow(evppi_all_scenarios) > 0) {
  # Find scenario with highest EVPI
  max_evpi_scenario <- evppi_all_scenarios %>%
    select(scenario_name, evpi) %>%
    distinct() %>%
    arrange(desc(evpi)) %>%
    slice(1)
  
  # Find most important parameter overall
  top_param_overall <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(total = sum(evppi), .groups = "drop") %>%
    arrange(desc(total)) %>%
    slice(1)
  
  cat("**Scenario with Greatest Decision Uncertainty:** ", max_evpi_scenario$scenario_name, " (EVPI = €", 
      round(max_evpi_scenario$evpi, 2), ")\n\n", sep = "")
  
  cat("**Most Important Parameter Across All Scenarios:** ", top_param_overall$parameter, " (Total EVPPI = €", 
      round(top_param_overall$total, 2), ")\n\n", sep = "")
  
  cat("**Impact of WTP Threshold:** Higher WTP thresholds generally increase decision uncertainty (EVPI), creating greater value for additional research to reduce parameter uncertainty.\n\n")
  
  cat("**Impact of Nivolumab Cost:** Decreased nivolumab costs shift the cost-effectiveness landscape and may change which parameters drive decision uncertainty.\n\n")
}
```

## Research Priorities

Based on the EVPPI analysis, future research should prioritize:

```{r research-priorities}
if (nrow(evppi_all_scenarios) > 0) {
  priorities <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(
      max_evppi = max(evppi),
      avg_evppi = mean(evppi),
      n_scenarios = sum(evppi > 0),
      .groups = "drop"
    ) %>%
    arrange(desc(max_evppi)) %>%
    slice(1:5) %>%
    mutate(
      Priority = 1:n(),
      Parameter = parameter,
      `Max EVPPI` = paste0("€", round(max_evppi, 2)),
      `Avg EVPPI` = paste0("€", round(avg_evppi, 2)),
      `Relevant Scenarios` = n_scenarios
    ) %>%
    select(Priority, Parameter, `Max EVPPI`, `Avg EVPPI`, `Relevant Scenarios`)
  
  kable(priorities,
        caption = "Top 5 research priorities based on EVPPI",
        booktabs = TRUE,
        align = c("c", "l", "r", "r", "c")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

\newpage

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.1