---
title: "METIMMOX-1 Expected Values of Partially Perfect Information (EVPPI) Analysis"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r evppi-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions if they exist (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/create_tornado_plot.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r load-dependencies, include=FALSE}
# Load all necessary dependencies and global variables in the correct order
cat("Loading analysis scripts in sequence...\n")

# First, ensure essential global variables are defined
if (!exists("USE_BOTH_MODELS")) {
  USE_BOTH_MODELS <- 0  # Default value as seen in the repository
}

# 02 - Setup and global variables
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  cat("Loading 02_setup_and_global_variables.R...\n")
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
} else {
  cat("Warning: 02_setup_and_global_variables.R not found\n")
  # Define essential variables if script not found
  time_horizon <- 520  # 10 years in weeks
  WTP <- 51000        # CE threshold in Euros
  DSA_mult <- 0.2     # +/- 20% variations
  dr <- 0.04          # discount rate
  cl <- 1/52          # 1 week cycle
  n_samples <- 5000   # number of bootstrap samples
  n_sim <- n_samples  # number of PSA simulations
  USE_BOTH_MODELS <- 0
}

# Ensure USE_BOTH_MODELS is properly set for subsequent scripts
if (!exists("USE_BOTH_MODELS")) {
  USE_BOTH_MODELS <- 0
  cat("Set USE_BOTH_MODELS to default value 0\n")
}

# 03 - Biomarker strategies
if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  cat("Loading 03_biomarker_strategies.R...\n")
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
} else {
  cat("Warning: 03_biomarker_strategies.R not found\n")
  strategies <- c("control", "crp", "tlr", "tmb_braf")
  biomarkers <- c("crp", "tlr", "tmb_braf")
}

# 05 - (Check for existence)
possible_05_names <- c("05_survival_analysis.R", "05_data_analysis.R", "05_preprocessing.R")
found_05 <- FALSE
for (name in possible_05_names) {
  if (file.exists(here("scripts/R/analysis", name))) {
    cat("Loading", name, "...\n")
    tryCatch({
      suppressMessages(suppressWarnings(source(here("scripts/R/analysis", name))))
      found_05 <- TRUE
      break
    }, error = function(e) {
      cat("Error loading", name, ":", conditionMessage(e), "\n")
    })
  }
}
if (!found_05) {
  cat("05 script not found - skipping\n")
}

# 06 - Parametric survival analysis
if (file.exists(here("scripts/R/analysis/06_parametric_survival analysis.R"))) {
  cat("Loading 06_parametric_survival analysis.R...\n")
  tryCatch({
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival analysis.R"))))
  }, error = function(e) {
    cat("Error loading 06_parametric_survival analysis.R:", conditionMessage(e), "\n")
  })
} else {
  cat("Warning: 06_parametric_survival analysis.R not found\n")
}

# 07 - Base case input parameters
if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  cat("Loading 07_basecase_input_parameters.R...\n")
  tryCatch({
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
  }, error = function(e) {
    cat("Error loading 07_basecase_input_parameters.R:", conditionMessage(e), "\n")
  })
} else {
  cat("Warning: 07_basecase_input_parameters.R not found\n")
}

# Ensure time_points is defined before loading 08_sampling.R
if (!exists("time_points") && exists("time_horizon")) {
  time_points <- seq(0, time_horizon, by = 1)
  time_points_length <- length(time_points)
  cat("Defined time_points with length:", time_points_length, "\n")
}

# 08 - Sampling
if (file.exists(here("scripts/R/analysis/08_sampling.R"))) {
  cat("Loading 08_sampling.R...\n")
  tryCatch({
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/08_sampling.R"))))
  }, error = function(e) {
    cat("Error loading 08_sampling.R:", conditionMessage(e), "\n")
  })
} else {
  cat("Warning: 08_sampling.R not found\n")
}

# 10 - (Check for existence)
possible_10_names <- c("10_cost_effectiveness.R", "10_base_case.R", "10_analysis.R")
found_10 <- FALSE
for (name in possible_10_names) {
  if (file.exists(here("scripts/R/analysis", name))) {
    cat("Loading", name, "...\n")
    tryCatch({
      suppressMessages(suppressWarnings(source(here("scripts/R/analysis", name))))
      found_10 <- TRUE
      break
    }, error = function(e) {
      cat("Error loading", name, ":", conditionMessage(e), "\n")
    })
  }
}
if (!found_10) {
  cat("10 script not found - skipping\n")
}

# 12 - PSA (critical for EVPPI)
if (file.exists(here("scripts/R/analysis/12_PSA.R"))) {
  cat("Loading 12_PSA.R...\n")
  tryCatch({
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/12_PSA.R"))))
  }, error = function(e) {
    cat("Error loading 12_PSA.R:", conditionMessage(e), "\n")
    stop("Failed to load 12_PSA.R - this is required for EVPPI analysis")
  })
} else {
  stop("Error: 12_PSA.R not found - this is required for EVPPI analysis")
}

# Verify required objects exist
required_objects <- c("psa_obj", "psa_params", "time_horizon", "WTP")
missing_objects <- required_objects[!sapply(required_objects, exists)]

if (length(missing_objects) > 0) {
  cat("Missing required objects:", paste(missing_objects, collapse = ", "), "\n")
  
  # Try to provide fallback values
  if ("time_horizon" %in% missing_objects) {
    time_horizon <- 520
    cat("Set fallback time_horizon:", time_horizon, "\n")
  }
  if ("WTP" %in% missing_objects) {
    WTP <- 51000
    cat("Set fallback WTP:", WTP, "\n")
  }
  
  # Re-check after fallbacks
  remaining_missing <- required_objects[!sapply(required_objects, exists)]
  if (length(remaining_missing) > 0) {
    stop("Still missing critical objects after fallbacks: ", paste(remaining_missing, collapse = ", "))
  }
}

# Provide fallbacks for other important objects
optional_objects <- c("time_points", "strategies", "l_params_base", "biomarkers")
for (obj in optional_objects) {
  if (!exists(obj)) {
    if (obj == "time_points" && exists("time_horizon")) {
      time_points <- seq(0, time_horizon, by = 1)
      time_points_length <- length(time_points)
    }
    if (obj == "strategies") {
      strategies <- c("control", "crp", "tlr", "tmb_braf")
    }
    if (obj == "biomarkers") {
      biomarkers <- c("crp", "tlr", "tmb_braf")
    }
  }
}

cat("Successfully loaded dependencies\n")
```

```{r run-evppi-analysis, include=FALSE}
# Run the EVPPI analysis
cat("Running EVPPI analysis...\n")
suppressMessages(suppressWarnings(source(here("scripts/R/analysis/13_EVPPIs.R"))))
```

# Introduction

This report presents the Expected Values of Partially Perfect Information (EVPPI) analysis for the METIMMOX-1 economic model. EVPPI quantifies the maximum value of obtaining perfect information about specific model parameters or groups of parameters, helping to prioritize future research efforts.

The EVPPI analysis identifies which parameters, if known with certainty, would provide the greatest reduction in decision uncertainty. This information is crucial for:

- Prioritizing future research investments
- Identifying parameters requiring more precise estimation
- Guiding the design of additional studies
- Supporting evidence development strategies

# Methods

## EVPPI Calculation Methodology

The EVPPI for parameter θ is calculated as:

$$EVPPI_θ = E_θ[max_j E_{θ^{-θ}|θ}[NMB(j,θ,θ^{-θ})]] - max_j E[NMB(j,θ)]$$

Where:

- θ represents the parameter(s) of interest
- θ^{-θ} represents all other parameters  
- j represents treatment strategies
- NMB represents Net Monetary Benefit

## Implementation

The EVPPI analysis uses a nested sampling approach:

1. **Outer loop**: Integrates over the distribution of the parameter(s) of interest
2. **Inner loop**: For each parameter value, estimates expected NMB using simulations with similar parameter values
3. **Calculation**: Computes the difference between expected value with partial perfect information and current expected value

\newpage

# Results

## Overall EVPPI Summary

```{r evppi-summary-table}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  # Create a formatted summary table
  summary_table <- evppi_results %>%
    select(parameter, evppi, evppi_percent_of_evpi, error) %>%
    mutate(
      evppi = round(evppi, 2),
      evppi_percent_of_evpi = round(evppi_percent_of_evpi, 1),
      parameter = case_when(
        parameter == "c_drug_nivo" ~ "Nivolumab cost",
        parameter == "c_drug_FLOX" ~ "FLOX cost",
        parameter == "c_test_NGS" ~ "NGS test cost",
        parameter == "c_test_CT" ~ "CT scan cost",
        parameter == "c_test_blood" ~ "Blood test cost",
        parameter == "u_np" ~ "Non-progression utility",
        parameter == "u_p" ~ "Progression utility",
        parameter == "c_other_last" ~ "End-of-life costs",
        parameter == "c_other_visit" ~ "Visit costs",
        parameter == "c_other_baseline" ~ "Baseline costs",
        parameter == "c_other_follow" ~ "Follow-up costs",
        TRUE ~ parameter
      )
    ) %>%
    rename(
      "Parameter" = parameter,
      "EVPPI (€)" = evppi,
      "% of EVPI" = evppi_percent_of_evpi,
      "Notes" = error
    )
  
  # Create table for PDF output
  kable(summary_table, 
        caption = "Expected Values of Partially Perfect Information by Parameter",
        booktabs = TRUE) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10) %>%
    column_spec(1, width = "4cm") %>%
    column_spec(2, width = "2.5cm") %>%
    column_spec(3, width = "2.5cm") %>%
    column_spec(4, width = "4cm")
} else {
  cat("No EVPPI results available for display.\n")
}
```

```{r key-statistics}
if (exists("evpi_manual") && exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  cat("**Key Statistics:**\n\n")
  cat("- Total EVPI: €", round(evpi_manual, 2), "\n")
  cat("- Number of parameters analyzed:", nrow(evppi_results), "\n")
  cat("- Highest EVPPI: €", round(max(evppi_results$evppi), 2), 
      " (", evppi_results$parameter[which.max(evppi_results$evppi)], ")\n")
  cat("- Parameters with EVPPI > 1% of EVPI:", 
      sum(evppi_results$evppi_percent_of_evpi > 1), "\n")
} else {
  cat("Key statistics not available - missing required objects or empty results.\n")
}
```

## EVPPI Visualization

```{r evppi-plot, fig.cap="Expected Value of Partially Perfect Information (EVPPI) by Parameter", fig.height=8}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  # Filter to meaningful results (EVPPI > 0)
  plot_data <- evppi_results %>%
    filter(evppi > 0) %>%
    mutate(
      parameter_label = case_when(
        parameter == "c_drug_nivo" ~ "Nivolumab cost",
        parameter == "c_drug_FLOX" ~ "FLOX cost",
        parameter == "c_test_NGS" ~ "NGS test cost",
        parameter == "c_test_CT" ~ "CT scan cost",
        parameter == "c_test_blood" ~ "Blood test cost",
        parameter == "u_np" ~ "Non-progression utility",
        parameter == "u_p" ~ "Progression utility",
        parameter == "c_other_last" ~ "End-of-life costs",
        parameter == "c_other_visit" ~ "Visit costs",
        parameter == "c_other_baseline" ~ "Baseline costs",
        parameter == "c_other_follow" ~ "Follow-up costs",
        TRUE ~ parameter
      )
    ) %>%
    arrange(desc(evppi))
  
  if (nrow(plot_data) > 0) {
    # Create EVPPI bar plot
    p1 <- ggplot(plot_data, aes(x = reorder(parameter_label, evppi), y = evppi)) +
      geom_col(fill = "steelblue", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), 
                hjust = -0.1, size = 3.5) +
      coord_flip() +
      labs(
        title = "Expected Value of Partially Perfect Information (EVPPI)",
        subtitle = paste0("At willingness-to-pay threshold of €", format(WTP, big.mark = ",")),
        x = "Parameter",
        y = "EVPPI (€)"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 11)
      )
    
    print(p1)
  } else {
    cat("No parameters with meaningful EVPPI values to plot.\n")
  }
} else {
  cat("No EVPPI results available for plotting.\n")
}
```

```{r evppi-percentage-plot, fig.cap="EVPPI as Percentage of Total EVPI", fig.height=6}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  plot_data <- evppi_results %>%
    filter(evppi > 0) %>%
    mutate(
      parameter_label = case_when(
        parameter == "c_drug_nivo" ~ "Nivolumab cost",
        parameter == "c_drug_FLOX" ~ "FLOX cost",
        parameter == "c_test_NGS" ~ "NGS test cost",
        parameter == "c_test_CT" ~ "CT scan cost",
        parameter == "c_test_blood" ~ "Blood test cost",
        parameter == "u_np" ~ "Non-progression utility",
        parameter == "u_p" ~ "Progression utility",
        parameter == "c_other_last" ~ "End-of-life costs",
        parameter == "c_other_visit" ~ "Visit costs",
        parameter == "c_other_baseline" ~ "Baseline costs",
        parameter == "c_other_follow" ~ "Follow-up costs",
        TRUE ~ parameter
      )
    ) %>%
    arrange(desc(evppi_percent_of_evpi))
  
  if (nrow(plot_data) > 0) {
    # Create percentage plot
    p2 <- ggplot(plot_data, aes(x = reorder(parameter_label, evppi_percent_of_evpi), 
                                y = evppi_percent_of_evpi)) +
      geom_col(fill = "darkgreen", alpha = 0.8) +
      geom_text(aes(label = paste0(round(evppi_percent_of_evpi, 1), "%")), 
                hjust = -0.1, size = 3.5) +
      coord_flip() +
      labs(
        title = "EVPPI as Percentage of Total EVPI",
        x = "Parameter",
        y = "EVPPI as % of EVPI"
      ) +
      theme_minimal() +
      theme(
        plot.title = element_text(size = 14, face = "bold"),
        axis.text = element_text(size = 10),
        axis.title = element_text(size = 11)
      )
    
    print(p2)
  }
}
```

\newpage

## Research Prioritization

```{r research-priorities}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  # Define priority thresholds
  high_priority <- evppi_results %>% 
    filter(evppi_percent_of_evpi > 5) %>%
    arrange(desc(evppi))
  
  medium_priority <- evppi_results %>% 
    filter(evppi_percent_of_evpi > 1 & evppi_percent_of_evpi <= 5) %>%
    arrange(desc(evppi))
  
  low_priority <- evppi_results %>% 
    filter(evppi_percent_of_evpi > 0 & evppi_percent_of_evpi <= 1) %>%
    arrange(desc(evppi))
  
  cat("### Research Priority Classification\n\n")
  
  if (nrow(high_priority) > 0) {
    cat("**High Priority (>5% of EVPI):**\n\n")
    for (i in 1:nrow(high_priority)) {
      cat("- ", high_priority$parameter[i], ": €", round(high_priority$evppi[i], 2), 
          " (", round(high_priority$evppi_percent_of_evpi[i], 1), "% of EVPI)\n")
    }
    cat("\n")
  }
  
  if (nrow(medium_priority) > 0) {
    cat("**Medium Priority (1-5% of EVPI):**\n\n")
    for (i in 1:nrow(medium_priority)) {
      cat("- ", medium_priority$parameter[i], ": €", round(medium_priority$evppi[i], 2), 
          " (", round(medium_priority$evppi_percent_of_evpi[i], 1), "% of EVPI)\n")
    }
    cat("\n")
  }
  
  if (nrow(low_priority) > 0) {
    cat("**Low Priority (<1% of EVPI):**\n\n")
    for (i in 1:nrow(low_priority)) {
      cat("- ", low_priority$parameter[i], ": €", round(low_priority$evppi[i], 2), 
          " (", round(low_priority$evppi_percent_of_evpi[i], 1), "% of EVPI)\n")
    }
  }
  
  if (nrow(high_priority) == 0 && nrow(medium_priority) == 0 && nrow(low_priority) == 0) {
    cat("No parameters show meaningful EVPPI values.\n")
  }
} else {
  cat("No EVPPI results available for research prioritization.\n")
}
```

## Parameter Group Analysis

```{r parameter-groups}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  # Group parameters by type
  cost_params <- evppi_results %>% filter(grepl("^c_", parameter))
  utility_params <- evppi_results %>% filter(grepl("^u_", parameter))
  
  cat("### Parameter Group Summary\n\n")
  
  if (nrow(cost_params) > 0) {
    cat("**Cost Parameters:**\n\n")
    cat("- Total EVPPI: €", round(sum(cost_params$evppi), 2), "\n")
    cat("- Percentage of total EVPI:", round(sum(cost_params$evppi_percent_of_evpi), 1), "%\n")
    cat("- Number of parameters:", nrow(cost_params), "\n")
    cat("- Top parameter:", cost_params$parameter[which.max(cost_params$evppi)], 
        " (€", round(max(cost_params$evppi), 2), ")\n\n")
  }
  
  if (nrow(utility_params) > 0) {
    cat("**Utility Parameters:**\n\n")
    cat("- Total EVPPI: €", round(sum(utility_params$evppi), 2), "\n")
    cat("- Percentage of total EVPI:", round(sum(utility_params$evppi_percent_of_evpi), 1), "%\n")
    cat("- Number of parameters:", nrow(utility_params), "\n")
    cat("- Top parameter:", utility_params$parameter[which.max(utility_params$evppi)], 
        " (€", round(max(utility_params$evppi), 2), ")\n\n")
  }
  
  if (nrow(cost_params) == 0 && nrow(utility_params) == 0) {
    cat("No parameter groups identified.\n")
  }
} else {
  cat("No EVPPI results available for parameter group analysis.\n")
}
```

\newpage

# Discussion

## Interpretation of Results

```{r interpretation}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0 && exists("evpi_manual")) {
  total_meaningful_evppi <- sum(evppi_results$evppi[evppi_results$evppi > 0])
  
  cat("The EVPPI analysis reveals the following key insights:\n\n")
  
  if (evpi_manual > 1) {
    cat("1. **Decision Uncertainty**: The total EVPI of €", round(evpi_manual, 2), 
        " indicates", ifelse(evpi_manual > 1000, " substantial", " moderate"), 
        " decision uncertainty in the model.\n\n")
  } else {
    cat("1. **Limited Uncertainty**: The low EVPI of €", round(evpi_manual, 2), 
        " suggests limited decision uncertainty.\n\n")
  }
  
  if (total_meaningful_evppi > 0) {
    cat("2. **Parameter Importance**: Parameters with non-zero EVPPI values represent opportunities for targeted research to reduce uncertainty.\n\n")
    
    top_param <- evppi_results$parameter[which.max(evppi_results$evppi)]
    top_evppi <- max(evppi_results$evppi)
    
    if (top_evppi > evpi_manual * 0.1) {
      cat("3. **Research Focus**: The parameter '", top_param, "' shows the highest EVPPI (€", 
          round(top_evppi, 2), "), suggesting it should be prioritized for future research.\n\n")
    }
  } else {
    cat("2. **Limited Research Value**: All parameters show zero or negligible EVPPI, suggesting limited value from additional parameter research.\n\n")
  }
} else {
  cat("Unable to provide interpretation - missing required results or EVPI data.\n")
}
```

## Limitations

The EVPPI analysis has several important limitations:

1. **Computational Approximation**: The nested sampling approach provides an approximation of the true EVPPI, which may underestimate values for highly nonlinear models.

2. **Parameter Independence**: The analysis assumes parameters can be learned independently, which may not reflect real-world research scenarios.

3. **Linear Utility**: The analysis assumes linear utility in money, which may not hold for all decision-makers.

4. **Model Structure**: EVPPI values are conditional on the current model structure and may change with model modifications.

# Conclusions

```{r conclusions}
if (exists("evppi_results") && is.data.frame(evppi_results) && nrow(evppi_results) > 0) {
  meaningful_params <- sum(evppi_results$evppi > 0)
  high_value_params <- sum(evppi_results$evppi_percent_of_evpi > 5)
  
  cat("**Key Findings:**\n\n")
  if (exists("evpi_manual")) {
    cat("- Total EVPI: €", round(evpi_manual, 2), "\n")
  }
  cat("- Parameters analyzed:", nrow(evppi_results), "\n")
  cat("- Parameters with meaningful EVPPI:", meaningful_params, "\n")
  cat("- High-priority parameters (>5% EVPI):", high_value_params, "\n\n")
  
  if (high_value_params > 0) {
    cat("**Recommendations:**\n\n")
    cat("- Focus future research on high-priority parameters\n")
    cat("- Consider design of studies to improve precision of key estimates\n")
    cat("- Evaluate cost-effectiveness of additional data collection\n")
  } else if (meaningful_params > 0) {
    cat("**Recommendations:**\n\n")
    cat("- Consider moderate investment in improving parameter estimates\n")
    cat("- Focus on parameters with highest relative EVPPI values\n")
  } else {
    cat("**Recommendations:**\n\n")
    cat("- Current parameter uncertainty has limited impact on decisions\n")
    cat("- Focus research efforts on model structure or alternative interventions\n")
  }
} else {
  cat("**No conclusive EVPPI results available.**\n\n")
  cat("This may indicate:\n\n")
  cat("- Very low decision uncertainty in the model\n")
  cat("- Insufficient parameter variation in the PSA\n")
  cat("- Technical issues with the EVPPI calculation\n")
}
```

---

**Report compiled on `r Sys.Date()` by Ben Geisler using the METIMMOX-1 health economic model.**