---
title: "METIMMOX-1 Value of Information Analysis"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r evppi-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  tidyr, scales, gridExtra, dampack
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Check if results file exists
results_file <- here::here("data/tidy/scenario_evppi_results.RData")

if (!file.exists(results_file)) {
  stop("Results file not found. Please run scripts/R/analysis/14_scenario_EVPPIs.R first to generate the analysis results.")
}

# Load results
load(results_file)

# Function to create incremental CE plot relative to control with WTP threshold
create_incremental_ce_plot <- function(psa_obj, wtp_threshold, scenario_name = "") {
  # Extract cost and effect matrices
  cost_mat <- as.matrix(psa_obj$cost)
  effect_mat <- as.matrix(psa_obj$effect)
  strategies <- colnames(cost_mat)
  
  # Find control strategy
  control_idx <- which(strategies == "control")
  
  if (length(control_idx) == 0) {
    return(NULL)
  }
  
  # Calculate incremental costs and effects relative to control
  incr_costs <- cost_mat - cost_mat[, control_idx]
  incr_effects <- effect_mat - effect_mat[, control_idx]
  
  # Create data frame for plotting (exclude control)
  plot_data <- data.frame()
  for (i in seq_along(strategies)) {
    if (i != control_idx) {
      plot_data <- rbind(plot_data, data.frame(
        Strategy = strategies[i],
        Incremental_Cost = incr_costs[, i],
        Incremental_Effect = incr_effects[, i]
      ))
    }
  }
  
  # Create the plot
  p <- ggplot(plot_data, aes(x = Incremental_Effect, y = Incremental_Cost, color = Strategy)) +
    geom_point(alpha = 0.3, size = 1) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_abline(slope = wtp_threshold, intercept = 0, 
                linetype = "dotted", color = "black", linewidth = 0.8,
                alpha = 0.7) +
    scale_y_continuous(labels = scales::dollar_format(prefix = "€")) +
    scale_color_brewer(palette = "Set1") +
    labs(
      title = "Incremental Cost-Effectiveness Scatter Plot",
      subtitle = paste0(scenario_name, " (relative to control)"),
      x = "Incremental QALYs",
      y = "Incremental Cost (€)",
      color = "Strategy"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
  
  return(p)
}

# Function to create NMB boxplot
create_nmb_boxplot <- function(psa_obj, wtp_threshold, scenario_name = "") {
  # Extract cost and effect matrices
  cost_mat <- as.matrix(psa_obj$cost)
  effect_mat <- as.matrix(psa_obj$effect)
  strategies <- colnames(cost_mat)
  
  # Calculate NMB
  nmb_mat <- effect_mat * wtp_threshold - cost_mat
  
  # Create data frame for plotting
  plot_data <- data.frame()
  for (i in seq_along(strategies)) {
    plot_data <- rbind(plot_data, data.frame(
      Strategy = strategies[i],
      NMB = nmb_mat[, i]
    ))
  }
  
  # Create the plot
  p <- ggplot(plot_data, aes(x = Strategy, y = NMB, fill = Strategy)) +
    geom_boxplot(alpha = 0.7) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red", alpha = 0.5) +
    scale_y_continuous(labels = scales::dollar_format(prefix = "€")) +
    scale_fill_brewer(palette = "Set1") +
    labs(
      title = "Net Monetary Benefit Distribution",
      subtitle = scenario_name,
      x = "Strategy",
      y = "Net Monetary Benefit (€)"
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))
  
  return(p)
}
```

# Overview

This report presents the results of an Expected Value of Partially Perfect Information (EVPPI) analysis for the METIMMOX-1 decision-analytic model. The analysis evaluates the value of reducing uncertainty in individual model parameters across multiple scenarios with varying willingness-to-pay (WTP) thresholds and nivolumab drug costs.

The Expected Value of Partially Perfect Information (EVPPI) quantifies the value of eliminating uncertainty in specific model parameters. It represents the maximum amount that should be paid for additional research to perfectly inform a particular parameter. EVPI (Expected Value of Perfect Information) represents the value of eliminating all uncertainty, and EVPPI for any parameter cannot exceed total EVPI.

```{r scenario-table-summary}
scenario_summary <- scenarios %>%
  mutate(
    `WTP Threshold` = paste0("€", format(wtp, big.mark = ",")),
    `Nivolumab Cost` = paste0("€", format(c_drug_nivo, big.mark = ","))
  ) %>%
  select(`Scenario Name` = scenario_name,
         `WTP Threshold`,
         `Nivolumab Cost`)

kable(scenario_summary,
      caption = "Analysis scenario definitions. Higher WTP thresholds (€100,000 and €150,000) are arbitrary exploratory thresholds, though the highest severity adjustment in Norwegian guidelines may fall between these values. The decreased nivolumab cost (€4,641) represents an 80\\% discount compared to the 40\\% discount in the base case scenario.",
      booktabs = TRUE,
      align = c("l", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), 
                font_size = 10,
                full_width = FALSE)
```

\newpage

# Base Case Scenario

```{r base-params}
base_results <- all_scenario_results[["base"]]

if (!is.null(base_results) && nrow(base_results$evppi_results) > 0) {
  base_evpi <- base_results$evppi_results$evpi[1]
  base_wtp <- scenarios$wtp[scenarios$scenario_id == "base"]
  base_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
} else {
  base_evpi <- 0
  base_wtp <- 51000
  base_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
}
```

**Willingness-to-Pay Threshold:** €`r format(base_wtp, big.mark = ",")`

**Nivolumab Cost:** €`r format(base_nivo_cost, big.mark = ",")`

```{r base-ice-scatter, fig.cap="Cost-effectiveness scatter plot (base case)", fig.height=6}
if (!is.null(base_results$psa_obj)) {
  plot(base_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

```{r base-ice-incremental, fig.cap="Incremental cost-effectiveness scatter plot relative to control (base case)", fig.height=6}
if (!is.null(base_results$psa_obj)) {
  incr_plot <- create_incremental_ce_plot(base_results$psa_obj, base_wtp, "Base Case")
  if (!is.null(incr_plot)) {
    print(incr_plot)
  }
}
```

```{r base-cea-summary}
if (!is.null(base_results$psa_obj)) {
  psa_summary <- summary(base_results$psa_obj, calc_sds = TRUE)
  
  # Calculate NMB
  cost_mat <- as.matrix(base_results$psa_obj$cost)
  effect_mat <- as.matrix(base_results$psa_obj$effect)
  nmb_mat <- effect_mat * base_wtp - cost_mat
  
  # Format the summary table with NMB
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Effect` = round(sdEffect, 3),
      `Mean NMB (€)` = paste0("€", format(round(colMeans(nmb_mat)[Strategy], 2), big.mark = ",")),
      `SD NMB` = paste0("€", format(round(apply(nmb_mat, 2, sd)[Strategy], 2), big.mark = ","))
    ) %>%
    select(Strategy, `Mean Cost (€)`, `SD Cost`, `Mean Effect (QALYs)`, `SD Effect`, `Mean NMB (€)`, `SD NMB`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary from probabilistic sensitivity analysis (base case)",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 8,
                  full_width = FALSE)
}
```

```{r base-nmb-boxplot, fig.cap="Net Monetary Benefit distribution (base case)", fig.height=6}
if (!is.null(base_results$psa_obj)) {
  nmb_plot <- create_nmb_boxplot(base_results$psa_obj, base_wtp, "Base Case")
  if (!is.null(nmb_plot)) {
    print(nmb_plot)
  }
}
```

```{r base-ceac, fig.cap="Cost-effectiveness acceptability curves (base case)", fig.height=6}
if (!is.null(base_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 1e6, by = 5e3)
  ceac_obj <- ceac(c_wtp, base_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

**Total EVPI:** €`r round(base_evpi, 2)`

```{r base-interpretation, results='asis'}
if (base_evpi > 0.01) {
  cat("\n\nThe positive EVPI indicates decision uncertainty at the base case WTP threshold. This suggests that additional research to reduce parameter uncertainty could have value.\n")
} else {
  cat("\n\nThe EVPI is effectively zero, indicating no decision uncertainty at the base case WTP threshold. In this case, one strategy is clearly dominant regardless of parameter uncertainty, making EVPPI calculations less meaningful for the base case scenario.\n")
}
```

```{r base-case-evppi-table}
if (!is.null(base_results) && nrow(base_results$evppi_results) > 0 && base_evpi > 0.01) {
  base_evppi <- base_results$evppi_results %>%
    arrange(desc(evppi)) %>%
    select(Parameter = parameter,
           EVPPI = evppi,
           `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(
      EVPPI = paste0("€", round(EVPPI, 2)),
      `% of EVPI` = paste0(round(`% of EVPI`, 1), "%")
    )
  
  kable(base_evppi,
        caption = "Base case EVPPI results (ranked by importance)",
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

```{r base-case-plot, fig.cap="Base case EVPPI by parameter", eval=!is.null(base_results) && nrow(base_results$evppi_results) > 0 && base_evpi > 0.01}
if (!is.null(base_results) && nrow(base_results$evppi_results) > 0 && base_evpi > 0.01) {
  base_plot_data <- base_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(base_plot_data) > 0) {
    ggplot(base_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "steelblue", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))),
                hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(
        title = "Base Case: Expected Value of Partially Perfect Information",
        subtitle = paste0("WTP = €", format(base_wtp, big.mark = ",")),
        x = "EVPPI (€)",
        y = NULL
      ) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 1: Decreased Nivolumab Cost

```{r s1-params}
s1_results <- all_scenario_results[["s1_decreased_nivo"]]

if (!is.null(s1_results) && nrow(s1_results$evppi_results) > 0) {
  s1_evpi <- s1_results$evppi_results$evpi[1]
  s1_wtp <- 51000
  s1_nivo_cost <- 4641
} else {
  s1_evpi <- 0
  s1_wtp <- 51000
  s1_nivo_cost <- 4641
}
```

**Willingness-to-Pay Threshold:** €`r format(s1_wtp, big.mark = ",")`

**Nivolumab Cost:** €`r format(s1_nivo_cost, big.mark = ",")` (80% discount)

```{r s1-ice-scatter, fig.cap="Cost-effectiveness scatter plot (Scenario 1)", fig.height=6}
if (!is.null(s1_results$psa_obj)) {
  plot(s1_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

```{r s1-ice-incremental, fig.cap="Incremental cost-effectiveness scatter plot relative to control (Scenario 1)", fig.height=6}
if (!is.null(s1_results$psa_obj)) {
  incr_plot <- create_incremental_ce_plot(s1_results$psa_obj, s1_wtp, "Scenario 1: Decreased Nivolumab")
  if (!is.null(incr_plot)) {
    print(incr_plot)
  }
}
```

```{r s1-cea-summary}
if (!is.null(s1_results$psa_obj)) {
  psa_summary <- summary(s1_results$psa_obj, calc_sds = TRUE)
  
  cost_mat <- as.matrix(s1_results$psa_obj$cost)
  effect_mat <- as.matrix(s1_results$psa_obj$effect)
  nmb_mat <- effect_mat * s1_wtp - cost_mat
  
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Effect` = round(sdEffect, 3),
      `Mean NMB (€)` = paste0("€", format(round(colMeans(nmb_mat)[Strategy], 2), big.mark = ",")),
      `SD NMB` = paste0("€", format(round(apply(nmb_mat, 2, sd)[Strategy], 2), big.mark = ","))
    ) %>%
    select(Strategy, `Mean Cost (€)`, `SD Cost`, `Mean Effect (QALYs)`, `SD Effect`, `Mean NMB (€)`, `SD NMB`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary (Scenario 1)",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 8,
                  full_width = FALSE)
}
```

```{r s1-nmb-boxplot, fig.cap="Net Monetary Benefit distribution (Scenario 1)", fig.height=6}
if (!is.null(s1_results$psa_obj)) {
  nmb_plot <- create_nmb_boxplot(s1_results$psa_obj, s1_wtp, "Scenario 1: Decreased Nivolumab")
  if (!is.null(nmb_plot)) {
    print(nmb_plot)
  }
}
```

```{r s1-ceac, fig.cap="Cost-effectiveness acceptability curves (Scenario 1)", fig.height=6}
if (!is.null(s1_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
  ceac_obj <- ceac(c_wtp, s1_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

**Total EVPI:** €`r round(s1_evpi, 2)`

```{r s1-interpretation, results='asis'}
if (s1_evpi > 0.01) {
  cat("\n\nReducing nivolumab costs creates decision uncertainty, making EVPPI analysis meaningful.\n")
} else {
  cat("\n\nEven with decreased nivolumab costs, EVPI remains near zero at this WTP threshold.\n")
}
```

```{r s1-evppi-table}
if (!is.null(s1_results) && nrow(s1_results$evppi_results) > 0 && s1_evpi > 0.01) {
  s1_evppi <- s1_results$evppi_results %>%
    arrange(desc(evppi)) %>%
    select(Parameter = parameter,
           EVPPI = evppi,
           `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(
      EVPPI = paste0("€", round(EVPPI, 2)),
      `% of EVPI` = paste0(round(`% of EVPI`, 1), "%")
    )
  
  kable(s1_evppi,
        caption = "EVPPI results: Decreased nivolumab cost",
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

```{r s1-plot, fig.cap="EVPPI with decreased nivolumab cost", eval=!is.null(s1_results) && nrow(s1_results$evppi_results) > 0 && s1_evpi > 0.01}
if (!is.null(s1_results) && nrow(s1_results$evppi_results) > 0 && s1_evpi > 0.01) {
  s1_plot_data <- s1_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s1_plot_data) > 0) {
    ggplot(s1_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "darkorange", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))),
                hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(
        title = "EVPPI with Decreased Nivolumab Cost",
        subtitle = "WTP = €51,000 | Nivolumab = €4,641",
        x = "EVPPI (€)",
        y = NULL
      ) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 2: Higher WTP Threshold (€100,000)

```{r s2-params}
s2_results <- all_scenario_results[["s2_wtp100k"]]

if (!is.null(s2_results) && nrow(s2_results$evppi_results) > 0) {
  s2_evpi <- s2_results$evppi_results$evpi[1]
  s2_wtp <- 100000
  s2_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
} else {
  s2_evpi <- 0
  s2_wtp <- 100000
  s2_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
}
```

**Willingness-to-Pay Threshold:** €`r format(s2_wtp, big.mark = ",")`

**Nivolumab Cost:** €`r format(s2_nivo_cost, big.mark = ",")` (standard)

```{r s2-ice-scatter, fig.cap="Cost-effectiveness scatter plot (Scenario 2)", fig.height=6}
if (!is.null(s2_results$psa_obj)) {
  plot(s2_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

```{r s2-ice-incremental, fig.cap="Incremental cost-effectiveness scatter plot relative to control (Scenario 2)", fig.height=6}
if (!is.null(s2_results$psa_obj)) {
  incr_plot <- create_incremental_ce_plot(s2_results$psa_obj, s2_wtp, "Scenario 2: WTP €100,000")
  if (!is.null(incr_plot)) {
    print(incr_plot)
  }
}
```

```{r s2-cea-summary}
if (!is.null(s2_results$psa_obj)) {
  psa_summary <- summary(s2_results$psa_obj, calc_sds = TRUE)
  
  cost_mat <- as.matrix(s2_results$psa_obj$cost)
  effect_mat <- as.matrix(s2_results$psa_obj$effect)
  nmb_mat <- effect_mat * s2_wtp - cost_mat
  
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Effect` = round(sdEffect, 3),
      `Mean NMB (€)` = paste0("€", format(round(colMeans(nmb_mat)[Strategy], 2), big.mark = ",")),
      `SD NMB` = paste0("€", format(round(apply(nmb_mat, 2, sd)[Strategy], 2), big.mark = ","))
    ) %>%
    select(Strategy, `Mean Cost (€)`, `SD Cost`, `Mean Effect (QALYs)`, `SD Effect`, `Mean NMB (€)`, `SD NMB`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary (Scenario 2)",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 8,
                  full_width = FALSE)
}
```

```{r s2-nmb-boxplot, fig.cap="Net Monetary Benefit distribution (Scenario 2)", fig.height=6}
if (!is.null(s2_results$psa_obj)) {
  nmb_plot <- create_nmb_boxplot(s2_results$psa_obj, s2_wtp, "Scenario 2: WTP €100,000")
  if (!is.null(nmb_plot)) {
    print(nmb_plot)
  }
}
```

```{r s2-ceac, fig.cap="Cost-effectiveness acceptability curves (Scenario 2)", fig.height=6}
if (!is.null(s2_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
  ceac_obj <- ceac(c_wtp, s2_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

**Total EVPI:** €`r round(s2_evpi, 2)`

```{r s2-evppi-table}
if (!is.null(s2_results) && nrow(s2_results$evppi_results) > 0 && s2_evpi > 0.01) {
  s2_evppi <- s2_results$evppi_results %>%
    arrange(desc(evppi)) %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s2_evppi, 
        caption = "EVPPI results: WTP €100,000", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

```{r s2-plot, fig.cap="EVPPI at WTP €100,000", eval=!is.null(s2_results) && nrow(s2_results$evppi_results) > 0 && s2_evpi > 0.01}
if (!is.null(s2_results) && nrow(s2_results$evppi_results) > 0 && s2_evpi > 0.01) {
  s2_plot_data <- s2_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s2_plot_data) > 0) {
    ggplot(s2_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "forestgreen", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI at Higher WTP Threshold",
           subtitle = "WTP = €100,000 | Standard Nivolumab Cost",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 3: Higher WTP with Decreased Nivolumab Cost

```{r s3-params}
s3_results <- all_scenario_results[["s3_wtp100k_decreased"]]

if (!is.null(s3_results) && nrow(s3_results$evppi_results) > 0) {
  s3_evpi <- s3_results$evppi_results$evpi[1]
  s3_wtp <- 100000
  s3_nivo_cost <- 4641
} else {
  s3_evpi <- 0
  s3_wtp <- 100000
  s3_nivo_cost <- 4641
}
```

**Willingness-to-Pay Threshold:** €`r format(s3_wtp, big.mark = ",")`

**Nivolumab Cost:** €`r format(s3_nivo_cost, big.mark = ",")` (80% discount)

```{r s3-ice-scatter, fig.cap="Cost-effectiveness scatter plot (Scenario 3)", fig.height=6}
if (!is.null(s3_results$psa_obj)) {
  plot(s3_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

```{r s3-ice-incremental, fig.cap="Incremental cost-effectiveness scatter plot relative to control (Scenario 3)", fig.height=6}
if (!is.null(s3_results$psa_obj)) {
  incr_plot <- create_incremental_ce_plot(s3_results$psa_obj, s3_wtp, "Scenario 3: WTP €100k + Decreased Nivo")
  if (!is.null(incr_plot)) {
    print(incr_plot)
  }
}
```

```{r s3-cea-summary}
if (!is.null(s3_results$psa_obj)) {
  psa_summary <- summary(s3_results$psa_obj, calc_sds = TRUE)
  
  cost_mat <- as.matrix(s3_results$psa_obj$cost)
  effect_mat <- as.matrix(s3_results$psa_obj$effect)
  nmb_mat <- effect_mat * s3_wtp - cost_mat
  
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Effect` = round(sdEffect, 3),
      `Mean NMB (€)` = paste0("€", format(round(colMeans(nmb_mat)[Strategy], 2), big.mark = ",")),
      `SD NMB` = paste0("€", format(round(apply(nmb_mat, 2, sd)[Strategy], 2), big.mark = ","))
    ) %>%
    select(Strategy, `Mean Cost (€)`, `SD Cost`, `Mean Effect (QALYs)`, `SD Effect`, `Mean NMB (€)`, `SD NMB`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary (Scenario 3)",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 8,
                  full_width = FALSE)
}
```

```{r s3-nmb-boxplot, fig.cap="Net Monetary Benefit distribution (Scenario 3)", fig.height=6}
if (!is.null(s3_results$psa_obj)) {
  nmb_plot <- create_nmb_boxplot(s3_results$psa_obj, s3_wtp, "Scenario 3: WTP €100k + Decreased Nivo")
  if (!is.null(nmb_plot)) {
    print(nmb_plot)
  }
}
```

```{r s3-ceac, fig.cap="Cost-effectiveness acceptability curves (Scenario 3)", fig.height=6}
if (!is.null(s3_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
  ceac_obj <- ceac(c_wtp, s3_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

**Total EVPI:** €`r round(s3_evpi, 2)`

```{r s3-evppi-table}
if (!is.null(s3_results) && nrow(s3_results$evppi_results) > 0 && s3_evpi > 0.01) {
  s3_evppi <- s3_results$evppi_results %>%
    arrange(desc(evppi)) %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s3_evppi, 
        caption = "EVPPI results: WTP €100,000 + decreased nivolumab", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

```{r s3-plot, fig.cap="EVPPI: WTP €100,000 with decreased nivolumab", eval=!is.null(s3_results) && nrow(s3_results$evppi_results) > 0 && s3_evpi > 0.01}
if (!is.null(s3_results) && nrow(s3_results$evppi_results) > 0 && s3_evpi > 0.01) {
  s3_plot_data <- s3_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s3_plot_data) > 0) {
    ggplot(s3_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "purple", alpha = 0.7) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI: Combined Scenario",
           subtitle = "WTP = €100,000 | Decreased Nivolumab (€4,641)",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 4: Highest WTP Threshold (€150,000)

```{r s4-params}
s4_results <- all_scenario_results[["s4_wtp150k"]]

if (!is.null(s4_results) && nrow(s4_results$evppi_results) > 0) {
  s4_evpi <- s4_results$evppi_results$evpi[1]
  s4_wtp <- 150000
  s4_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
} else {
  s4_evpi <- 0
  s4_wtp <- 150000
  s4_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
}
```

**Willingness-to-Pay Threshold:** €`r format(s4_wtp, big.mark = ",")`

**Nivolumab Cost:** €`r format(s4_nivo_cost, big.mark = ",")` (standard)

```{r s4-ice-scatter, fig.cap="Cost-effectiveness scatter plot (Scenario 4)", fig.height=6}
if (!is.null(s4_results$psa_obj)) {
  plot(s4_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

```{r s4-ice-incremental, fig.cap="Incremental cost-effectiveness scatter plot relative to control (Scenario 4)", fig.height=6}
if (!is.null(s4_results$psa_obj)) {
  incr_plot <- create_incremental_ce_plot(s4_results$psa_obj, s4_wtp, "Scenario 4: WTP €150,000")
  if (!is.null(incr_plot)) {
    print(incr_plot)
  }
}
```

```{r s4-cea-summary}
if (!is.null(s4_results$psa_obj)) {
  psa_summary <- summary(s4_results$psa_obj, calc_sds = TRUE)
  
  cost_mat <- as.matrix(s4_results$psa_obj$cost)
  effect_mat <- as.matrix(s4_results$psa_obj$effect)
  nmb_mat <- effect_mat * s4_wtp - cost_mat
  
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Effect` = round(sdEffect, 3),
      `Mean NMB (€)` = paste0("€", format(round(colMeans(nmb_mat)[Strategy], 2), big.mark = ",")),
      `SD NMB` = paste0("€", format(round(apply(nmb_mat, 2, sd)[Strategy], 2), big.mark = ","))
    ) %>%
    select(Strategy, `Mean Cost (€)`, `SD Cost`, `Mean Effect (QALYs)`, `SD Effect`, `Mean NMB (€)`, `SD NMB`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary (Scenario 4)",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 8,
                  full_width = FALSE)
}
```

```{r s4-nmb-boxplot, fig.cap="Net Monetary Benefit distribution (Scenario 4)", fig.height=6}
if (!is.null(s4_results$psa_obj)) {
  nmb_plot <- create_nmb_boxplot(s4_results$psa_obj, s4_wtp, "Scenario 4: WTP €150,000")
  if (!is.null(nmb_plot)) {
    print(nmb_plot)
  }
}
```

```{r s4-ceac, fig.cap="Cost-effectiveness acceptability curves (Scenario 4)", fig.height=6}
if (!is.null(s4_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
  ceac_obj <- ceac(c_wtp, s4_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

**Total EVPI:** €`r round(s4_evpi, 2)`

```{r s4-evppi-table}
if (!is.null(s4_results) && nrow(s4_results$evppi_results) > 0 && s4_evpi > 0.01) {
  s4_evppi <- s4_results$evppi_results %>%
    arrange(desc(evppi)) %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s4_evppi, 
        caption = "EVPPI results: WTP €150,000", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

```{r s4-plot, fig.cap="EVPPI at WTP €150,000", eval=!is.null(s4_results) && nrow(s4_results$evppi_results) > 0 && s4_evpi > 0.01}
if (!is.null(s4_results) && nrow(s4_results$evppi_results) > 0 && s4_evpi > 0.01) {
  s4_plot_data <- s4_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s4_plot_data) > 0) {
    ggplot(s4_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "darkred", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI at Highest WTP Threshold",
           subtitle = "WTP = €150,000 | Standard Nivolumab Cost",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Scenario 5: Highest WTP with Decreased Nivolumab Cost

```{r s5-params}
s5_results <- all_scenario_results[["s5_wtp150k_decreased"]]

if (!is.null(s5_results) && nrow(s5_results$evppi_results) > 0) {
  s5_evpi <- s5_results$evppi_results$evpi[1]
  s5_wtp <- 150000
  s5_nivo_cost <- 4641
} else {
  s5_evpi <- 0
  s5_wtp <- 150000
  s5_nivo_cost <- 4641
}
```

**Willingness-to-Pay Threshold:** €`r format(s5_wtp, big.mark = ",")`

**Nivolumab Cost:** €`r format(s5_nivo_cost, big.mark = ",")` (80% discount)

```{r s5-ice-scatter, fig.cap="Cost-effectiveness scatter plot (Scenario 5)", fig.height=6}
if (!is.null(s5_results$psa_obj)) {
  plot(s5_results$psa_obj, frontier = TRUE, points = TRUE)
}
```

```{r s5-ice-incremental, fig.cap="Incremental cost-effectiveness scatter plot relative to control (Scenario 5)", fig.height=6}
if (!is.null(s5_results$psa_obj)) {
  incr_plot <- create_incremental_ce_plot(s5_results$psa_obj, s5_wtp, "Scenario 5: WTP €150k + Decreased Nivo")
  if (!is.null(incr_plot)) {
    print(incr_plot)
  }
}
```

```{r s5-cea-summary}
if (!is.null(s5_results$psa_obj)) {
  psa_summary <- summary(s5_results$psa_obj, calc_sds = TRUE)
  
  cost_mat <- as.matrix(s5_results$psa_obj$cost)
  effect_mat <- as.matrix(s5_results$psa_obj$effect)
  nmb_mat <- effect_mat * s5_wtp - cost_mat
  
  summary_formatted <- psa_summary %>%
    mutate(
      Strategy = Strategy,
      `Mean Cost (€)` = paste0("€", format(round(meanCost, 2), big.mark = ",")),
      `SD Cost` = paste0("€", format(round(sdCost, 2), big.mark = ",")),
      `Mean Effect (QALYs)` = round(meanEffect, 3),
      `SD Effect` = round(sdEffect, 3),
      `Mean NMB (€)` = paste0("€", format(round(colMeans(nmb_mat)[Strategy], 2), big.mark = ",")),
      `SD NMB` = paste0("€", format(round(apply(nmb_mat, 2, sd)[Strategy], 2), big.mark = ","))
    ) %>%
    select(Strategy, `Mean Cost (€)`, `SD Cost`, `Mean Effect (QALYs)`, `SD Effect`, `Mean NMB (€)`, `SD NMB`)
  
  kable(summary_formatted,
        caption = "Cost-effectiveness analysis summary (Scenario 5)",
        booktabs = TRUE,
        align = c("l", "r", "r", "r", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 8,
                  full_width = FALSE)
}
```

```{r s5-nmb-boxplot, fig.cap="Net Monetary Benefit distribution (Scenario 5)", fig.height=6}
if (!is.null(s5_results$psa_obj)) {
  nmb_plot <- create_nmb_boxplot(s5_results$psa_obj, s5_wtp, "Scenario 5: WTP €150k + Decreased Nivo")
  if (!is.null(nmb_plot)) {
    print(nmb_plot)
  }
}
```

```{r s5-ceac, fig.cap="Cost-effectiveness acceptability curves (Scenario 5)", fig.height=6}
if (!is.null(s5_results$psa_obj)) {
  c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
  ceac_obj <- ceac(c_wtp, s5_results$psa_obj)
  plot(ceac_obj, frontier = TRUE, points = TRUE, currency = "€")
}
```

**Total EVPI:** €`r round(s5_evpi, 2)`

```{r s5-evppi-table}
if (!is.null(s5_results) && nrow(s5_results$evppi_results) > 0 && s5_evpi > 0.01) {
  s5_evppi <- s5_results$evppi_results %>%
    arrange(desc(evppi)) %>%
    select(Parameter = parameter, EVPPI = evppi, `% of EVPI` = evppi_percent_of_evpi) %>%
    mutate(EVPPI = paste0("€", round(EVPPI, 2)),
           `% of EVPI` = paste0(round(`% of EVPI`, 1), "%"))
  
  kable(s5_evppi, 
        caption = "EVPPI results: WTP €150,000 + decreased nivolumab", 
        booktabs = TRUE,
        align = c("l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 10,
                  full_width = FALSE)
}
```

```{r s5-plot, fig.cap="EVPPI: Highest WTP with decreased nivolumab cost", eval=!is.null(s5_results) && nrow(s5_results$evppi_results) > 0 && s5_evpi > 0.01}
if (!is.null(s5_results) && nrow(s5_results$evppi_results) > 0 && s5_evpi > 0.01) {
  s5_plot_data <- s5_results$evppi_results %>%
    filter(evppi > 0) %>%
    arrange(evppi) %>%
    mutate(parameter = factor(parameter, levels = parameter))
  
  if (nrow(s5_plot_data) > 0) {
    ggplot(s5_plot_data, aes(x = evppi, y = parameter)) +
      geom_col(fill = "navy", alpha = 0.8) +
      geom_text(aes(label = paste0("€", round(evppi, 2))), hjust = -0.1, size = 3) +
      scale_x_continuous(labels = scales::dollar_format(prefix = "€"),
                        expand = expansion(mult = c(0, 0.15))) +
      labs(title = "EVPPI: Highest WTP + Decreased Cost",
           subtitle = "WTP = €150,000 | Decreased Nivolumab (€4,641)",
           x = "EVPPI (€)", y = NULL) +
      theme_minimal()
  }
}
```

\newpage

# Comparative Analysis Across Scenarios

## EVPI

```{r evpi-comparison, fig.cap="Expected Value of Perfect Information across scenarios", fig.height=5}
if (nrow(evppi_all_scenarios) > 0) {
  evpi_comparison <- evppi_all_scenarios %>%
    select(scenario_name, wtp, evpi) %>%
    distinct() %>%
    mutate(
      cost_type = ifelse(grepl("Decreased", scenario_name), "Decreased Nivo", "Standard Nivo"),
      wtp_label = paste0("€", format(wtp/1000, big.mark = ","), "k")
    )
  
  ggplot(evpi_comparison, aes(x = wtp_label, y = evpi, fill = cost_type)) +
    geom_col(position = "dodge", alpha = 0.8) +
    geom_text(aes(label = paste0("€", round(evpi, 2))),
              position = position_dodge(width = 0.9),
              vjust = -0.5, size = 3) +
    scale_fill_manual(values = c("Decreased Nivo" = "coral", "Standard Nivo" = "steelblue")) +
    labs(
      title = "Expected Value of Perfect Information Across Scenarios",
      subtitle = "Comparison by WTP Threshold and Nivolumab Cost",
      x = "Willingness-to-Pay Threshold",
      y = "EVPI (€)",
      fill = "Cost Scenario"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

## EVPPI

```{r parameter-heatmap, fig.cap="Parameter importance across scenarios (top 10 parameters)", fig.height=7}
if (nrow(evppi_all_scenarios) > 0) {
  # Get top 10 parameters overall
  top_params <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(total_evppi = sum(evppi), .groups = "drop") %>%
    arrange(desc(total_evppi)) %>%
    slice(1:10) %>%
    pull(parameter)
  
  heatmap_data <- evppi_all_scenarios %>%
    filter(parameter %in% top_params) %>%
    mutate(
      scenario_short = factor(case_when(
        scenario_id == "base" ~ "Base\n(€51k)",
        scenario_id == "s1_decreased_nivo" ~ "S1: €51k\nDecreased",
        scenario_id == "s2_wtp100k" ~ "S2: €100k\nStandard",
        scenario_id == "s3_wtp100k_decreased" ~ "S3: €100k\nDecreased",
        scenario_id == "s4_wtp150k" ~ "S4: €150k\nStandard",
        scenario_id == "s5_wtp150k_decreased" ~ "S5: €150k\nDecreased"
      ), levels = c("Base\n(€51k)", "S1: €51k\nDecreased", "S2: €100k\nStandard", 
                    "S3: €100k\nDecreased", "S4: €150k\nStandard", "S5: €150k\nDecreased"))
    )
  
  ggplot(heatmap_data, aes(x = scenario_short, y = parameter, fill = evppi)) +
    geom_tile(color = "white", linewidth = 1) +
    geom_text(aes(label = paste0("€", round(evppi, 1))), 
              color = "white", fontface = "bold", size = 2.5) +
    scale_fill_gradient(low = "navy", high = "red", 
                       name = "EVPPI (€)",
                       labels = scales::dollar_format(prefix = "€")) +
    labs(
      title = "Parameter Importance Across Scenarios",
      subtitle = "EVPPI values for top 10 parameters",
      x = "Scenario",
      y = "Parameter"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 12),
      axis.text.x = element_text(angle = 0, hjust = 0.5, size = 9),
      axis.text.y = element_text(size = 9),
      legend.position = "right"
    )
}
```

## Summary

```{r comparative-summary-table}
# Create comparative summary table
if (nrow(evppi_all_scenarios) > 0) {
  comp_summary <- evppi_all_scenarios %>%
    group_by(scenario_name, wtp) %>%
    summarise(
      EVPI = first(evpi),
      `Top Parameter` = parameter[which.max(evppi)],
      `Max EVPPI` = max(evppi),
      `% of EVPI` = round(max(evppi) / first(evpi) * 100, 1),
      .groups = "drop"
    ) %>%
    mutate(
      WTP = paste0("€", format(wtp, big.mark = ",")),
      EVPI = paste0("€", round(EVPI, 2)),
      `Max EVPPI` = paste0("€", round(`Max EVPPI`, 2))
    ) %>%
    select(Scenario = scenario_name, WTP, EVPI, `Top Parameter`, `Max EVPPI`, `% of EVPI`)
  
  kable(comp_summary, 
        caption = "Summary of EVPI and top EVPPI by scenario",
        booktabs = TRUE,
        align = c("l", "r", "r", "l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position"), 
                  font_size = 9,
                  full_width = FALSE)
}
```


```{r conclusions, results='asis'}
if (nrow(evppi_all_scenarios) > 0) {
  # Find scenario with highest EVPI
  max_evpi_scenario <- evppi_all_scenarios %>%
    select(scenario_name, evpi) %>%
    distinct() %>%
    arrange(desc(evpi)) %>%
    slice(1)
  
  # Find most important parameter overall
  top_param_overall <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(total = sum(evppi), .groups = "drop") %>%
    arrange(desc(total)) %>%
    slice(1)
  
  cat("**Scenario with Greatest Decision Uncertainty:** ", max_evpi_scenario$scenario_name, " (EVPI = €", 
      round(max_evpi_scenario$evpi, 2), ")\n\n", sep = "")
  
  cat("**Most Important Parameter Across All Scenarios:** ", top_param_overall$parameter, " (Total EVPPI = €", 
      round(top_param_overall$total, 2), ")\n\n", sep = "")
  
  cat("**Impact of WTP Threshold:** Higher WTP thresholds generally increase decision uncertainty (EVPI), creating greater value for additional research to reduce parameter uncertainty.\n\n")
  
  cat("**Impact of Nivolumab Cost:** Decreased nivolumab costs shift the cost-effectiveness landscape and may change which parameters drive decision uncertainty.\n\n")
}
```

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.1