---
title: "Value of Information Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r evppi-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  tidyr, scales, gridExtra, dampack
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source analysis scripts and helper functions
source(here::here("scripts/R/analysis/02_setup_and_global_variables.R"))
source(here::here("scripts/R/analysis/03_biomarker_strategies.R"))
source(here::here("scripts/R/analysis/06_parametric_survival_analysis.R"))
source(here::here("scripts/R/analysis/07_basecase_input_parameters.R"))
source(here::here("scripts/R/analysis/08_sampling.R"))  # For param_distributions
source(here::here("scripts/R/functions/model_fun.R"))
source(here::here("scripts/R/functions/calculate_outcomes.R"))
source(here::here("scripts/R/functions/psa_functions.R"))
source(here::here("scripts/R/functions/evppi_functions.R"))
source(here::here("scripts/R/functions/scenario_analysis.R"))
source(here::here("scripts/R/functions/multi_model_cea.R"))

# Get model configurations
model_configs <- get_model_configs()
```

```{r generate-evppi-cache-if-missing, include=FALSE}
# ===============================================================================
# AUTO-GENERATE EVPPI CACHE IF MISSING OR INCOMPLETE
# ===============================================================================
# Check if EVPPI cache exists with multi-model data.
# If missing or incomplete, generate for all 3 model structures.
# This includes auto-generating sampling and PSA caches if needed.
# ===============================================================================

results_file <- here::here("data/tidy/scenario_evppi_results.rds")
needs_generation <- FALSE

# Check if cache exists
if (!file.exists(results_file)) {
  cat("EVPPI cache not found. Will generate.\n")
  needs_generation <- TRUE
} else {
  # Check if cache has multi-model data
  evppi_cache <- readRDS(results_file)
  if (!has_multimodel_evppi(evppi_cache$evppi_all_scenarios)) {
    cat("EVPPI cache exists but lacks multi-model data. Will regenerate.\n")
    needs_generation <- TRUE
  }
}

# Generate cache if needed
if (needs_generation) {
  cat("\n=== GENERATING MULTI-MODEL EVPPI CACHE ===\n")
  cat("This may take considerable time if PSA caches need to be generated...\n\n")

  model_labels <- c("joint", "focused", "separate")
  model_names <- c("Model A: Joint", "Model B: Focused", "Model C: Separate")

  # Initialize storage
  all_model_scenario_results <- list()
  all_model_evppi_results <- data.frame()

  for (m_idx in seq_along(model_labels)) {
    current_model_structure <- m_idx - 1
    current_model_label <- model_labels[m_idx]
    current_model_name <- model_names[m_idx]

    cat("\n", paste(rep("=", 70), collapse = ""), "\n")
    cat("Processing", current_model_name, "(MODEL_STRUCTURE =", current_model_structure, ")\n")
    cat(paste(rep("=", 70), collapse = ""), "\n")

    # Set MODEL_STRUCTURE globally
    MODEL_STRUCTURE <<- current_model_structure

    # Re-source scripts for this MODEL_STRUCTURE
    cat("Sourcing analysis scripts for MODEL_STRUCTURE =", current_model_structure, "...\n")
    suppressMessages(suppressWarnings({
      source(here::here("scripts/R/analysis/06_parametric_survival_analysis.R"))
      source(here::here("scripts/R/analysis/07_basecase_input_parameters.R"))
    }))

    # =========================================================================
    # Step 1: Check/Generate Sampling Cache
    # =========================================================================
    sampling_cache_file <- here::here("data", "tidy",
                                       paste0("sampling_models_n", n_samples, "_",
                                              ifelse(USE_BOTH_MODELS == 0, "full", "both"), "_",
                                              current_model_label, ".rds"))

    if (!file.exists(sampling_cache_file)) {
      cat("\nSampling cache not found for", current_model_label, "\n")
      cat("Generating sampling models (this may take several minutes)...\n")

      # Source the sampling script which will generate the cache
      suppressMessages(suppressWarnings({
        source(here::here("scripts/R/analysis/08_sampling.R"))
      }))

      # Verify it was created
      if (!file.exists(sampling_cache_file)) {
        cat("ERROR: Failed to generate sampling cache for", current_model_label, "\n")
        next
      }
      cat("Sampling cache generated successfully.\n")
    } else {
      cat("Sampling cache found:", basename(sampling_cache_file), "\n")
      # Load the sampling models
      sampling_models <- readRDS(sampling_cache_file)
    }

    # =========================================================================
    # Step 2: Check/Generate PSA Cache
    # =========================================================================
    psa_cache_file <- here::here("data", "tidy",
                                  paste0("psa_obj_", current_model_label, ".rds"))
    psa_params_file <- here::here("data", "tidy",
                                   paste0("psa_params_", current_model_label, ".rds"))

    if (!file.exists(psa_cache_file)) {
      cat("\nPSA cache not found for", current_model_label, "\n")
      cat("Generating PSA results (this may take 10-30 minutes)...\n")

      # Load the sampling cache if not already loaded
      if (!exists("sampling_models") || is.null(sampling_models)) {
        sampling_models <- readRDS(sampling_cache_file)
      }

      # Generate PSA samples
      psa_params <- generate_psa_samples(param_distributions, n_sim)

      # Run the PSA
      cat("Running PSA with", n_sim, "simulations...\n")
      psa_results <- run_psa_analysis(
        psa_params = psa_params,
        l_params_base = l_params_base,
        param_distributions = param_distributions,
        strategies = strategies,
        time_horizon = time_horizon,
        cl = cl,
        n_sim = n_sim
      )

      # Create the PSA object
      psa_obj <- dampack::make_psa_obj(
        cost = as.data.frame(psa_results$cost),
        effect = as.data.frame(psa_results$effect),
        strategies = strategies,
        currency = "EUR"
      )

      # Save PSA cache
      saveRDS(psa_params, psa_params_file)
      saveRDS(psa_obj, psa_cache_file)
      cat("PSA cache saved successfully.\n")
    } else {
      cat("PSA cache found:", basename(psa_cache_file), "\n")
      psa_obj <- readRDS(psa_cache_file)
      psa_params <- readRDS(psa_params_file)
    }

    # =========================================================================
    # Step 3: Run EVPPI Scenarios
    # =========================================================================
    cat("\nRunning EVPPI scenarios for", current_model_name, "...\n")

    # Define scenarios
    base_c_drug_nivo <- l_params_base$c_drug_nivo
    scenarios <- define_scenarios(
      base_wtp = WTP,
      base_c_drug_nivo = base_c_drug_nivo,
      decreased_c_drug_nivo = 4641
    )

    # Define EVPPI parameters
    evppi_params <- c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS",
                      "c_test_CT", "u_np", "u_p", "c_other_last",
                      "c_test_blood", "c_other_visit",
                      "c_other_baseline", "c_other_follow")

    # Run scenarios for this model
    scenario_results <- run_all_scenarios(
      scenarios = scenarios,
      psa_params = psa_params,
      l_params_base = l_params_base,
      param_distributions = param_distributions,
      strategies = strategies,
      time_horizon = time_horizon,
      cl = cl,
      n_sim = n_sim,
      evppi_params = evppi_params
    )

    # Store results
    all_model_scenario_results[[current_model_label]] <- scenario_results

    # Compile EVPPI results with model structure column
    evppi_results <- compile_evppi_results(scenario_results)
    if (nrow(evppi_results) > 0) {
      evppi_results$model_structure <- current_model_structure
      evppi_results$model_label <- current_model_label
      evppi_results$model_name <- current_model_name
      all_model_evppi_results <- rbind(all_model_evppi_results, evppi_results)
    }

    cat("\nCompleted all scenarios for", current_model_name, "\n")
  }

  # Check if any models were successfully processed
  if (length(all_model_scenario_results) == 0) {
    stop("Failed to generate EVPPI cache for any model structure.\n",
         "Check the error messages above for details.")
  }

  # Save cache
  evppi_cache <- list(
    all_scenario_results = all_model_scenario_results[[1]],
    all_model_scenario_results = all_model_scenario_results,
    evppi_all_scenarios = all_model_evppi_results,
    scenarios = scenarios
  )
  saveRDS(evppi_cache, file = results_file)
  cat("\n=== EVPPI cache generated and saved ===\n")
  cat("Cache file:", results_file, "\n")
}
```

```{r load-evppi-results, include=FALSE}
# Load results from cache
evppi_cache <- readRDS(results_file)

# Extract objects from cache
all_scenario_results <- evppi_cache$all_scenario_results
all_model_scenario_results <- evppi_cache$all_model_scenario_results
evppi_all_scenarios <- evppi_cache$evppi_all_scenarios
scenarios <- evppi_cache$scenarios

# Check for multi-model data
has_multimodel <- has_multimodel_evppi(evppi_all_scenarios)

if (has_multimodel) {
  model_labels_available <- get_evppi_model_labels(evppi_all_scenarios)
  cat("Multi-model EVPPI data loaded for:",
      paste(model_labels_available, collapse = ", "), "\n")
} else {
  cat("Single model EVPPI data (joint model only)\n")
  # Add model columns for backward compatibility
  if (!"model_structure" %in% names(evppi_all_scenarios)) {
    evppi_all_scenarios$model_structure <- 0
    evppi_all_scenarios$model_label <- "joint"
    evppi_all_scenarios$model_name <- "Model A: Joint"
  }
}

# Add population-level EVPPI columns if not already present
# (handles caches generated before population scaling was added)
if (!"evppi_population_millions" %in% names(evppi_all_scenarios)) {
  evppi_all_scenarios <- evppi_all_scenarios %>%
    mutate(
      evppi_population_millions = calculate_population_evppi(
        evppi,
        annual_incidence = annual_incidence_norway,
        research_horizon = research_horizon_years,
        discount_rate = discount_rate_research
      ),
      evpi_population_millions = calculate_population_evppi(
        evpi,
        annual_incidence = annual_incidence_norway,
        research_horizon = research_horizon_years,
        discount_rate = discount_rate_research
      )
    )
  cat("Population-level EVPPI columns added post-load\n")
}

# Function to create incremental CE plot relative to control with WTP threshold
create_incremental_ce_plot <- function(psa_obj, wtp_threshold, scenario_name = "") {
  # Extract cost and effect matrices
  cost_mat <- as.matrix(psa_obj$cost)
  effect_mat <- as.matrix(psa_obj$effect)
  strategies <- colnames(cost_mat)

  # Find control strategy
  control_idx <- which(strategies == "control")

  if (length(control_idx) == 0) {
    return(NULL)
  }

  # Calculate incremental costs and effects relative to control
  incr_costs <- cost_mat - cost_mat[, control_idx]
  incr_effects <- effect_mat - effect_mat[, control_idx]

  # Create data frame for plotting (exclude control)
  plot_data <- data.frame()
  for (i in seq_along(strategies)) {
    if (i != control_idx) {
      plot_data <- rbind(plot_data, data.frame(
        Strategy = strategies[i],
        Incremental_Cost = incr_costs[, i],
        Incremental_Effect = incr_effects[, i]
      ))
    }
  }

  # Create the plot
  p <- ggplot(plot_data, aes(x = Incremental_Effect, y = Incremental_Cost, color = Strategy)) +
    geom_point(alpha = 0.3, size = 1) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "gray50") +
    geom_vline(xintercept = 0, linetype = "dashed", color = "gray50") +
    geom_abline(slope = wtp_threshold, intercept = 0,
                linetype = "dotted", color = "black", linewidth = 0.8,
                alpha = 0.7) +
    scale_y_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_color_brewer(palette = "Set1") +
    labs(
      title = "Incremental Cost-Effectiveness Scatter Plot",
      subtitle = paste0(scenario_name, " (relative to control)"),
      x = "Incremental QALYs",
      y = "Incremental Cost (EUR)",
      color = "Strategy"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")

  return(p)
}

# Function to create NMB boxplot
create_nmb_boxplot <- function(psa_obj, wtp_threshold, scenario_name = "") {
  # Extract cost and effect matrices
  cost_mat <- as.matrix(psa_obj$cost)
  effect_mat <- as.matrix(psa_obj$effect)
  strategies <- colnames(cost_mat)

  # Calculate NMB
  nmb_mat <- effect_mat * wtp_threshold - cost_mat

  # Create data frame for plotting
  plot_data <- data.frame()
  for (i in seq_along(strategies)) {
    plot_data <- rbind(plot_data, data.frame(
      Strategy = strategies[i],
      NMB = nmb_mat[, i]
    ))
  }

  # Create the plot
  p <- ggplot(plot_data, aes(x = Strategy, y = NMB, fill = Strategy)) +
    geom_boxplot(alpha = 0.7) +
    geom_hline(yintercept = 0, linetype = "dashed", color = "red", alpha = 0.5) +
    scale_y_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set1") +
    labs(
      title = "Net Monetary Benefit Distribution",
      subtitle = scenario_name,
      x = "Strategy",
      y = "Net Monetary Benefit (EUR)"
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))

  return(p)
}
```

# Overview

This report presents the results of an Expected Value of Partially Perfect Information (EVPPI) analysis for the METIMMOX-1 decision-analytic model. The analysis evaluates the value of reducing uncertainty in individual model parameters across multiple scenarios with varying willingness-to-pay (WTP) thresholds and nivolumab drug costs.

**Key Feature**: This report compares EVPI and EVPPI results across three different model structures (Model A, B, C) to assess the robustness of value of information findings to modeling assumptions about how biomarker interactions are specified.

The Expected Value of Partially Perfect Information (EVPPI) quantifies the value of eliminating uncertainty in specific model parameters. It represents the maximum amount that should be paid for additional research to perfectly inform a particular parameter. EVPI (Expected Value of Perfect Information) represents the value of eliminating all uncertainty, and EVPPI for any parameter cannot exceed total EVPI.

## Population-Level Context

To inform research prioritization decisions, EVPPI values are scaled from per-patient estimates to the Norwegian eligible population:

- **Annual incidence**: `r annual_incidence_norway` MSS/pMMR mCRC patients per year
- **Research horizon**: `r research_horizon_years` years
- **Discount rate**: `r discount_rate_research * 100`% for future research benefits
- **Effective population size**: `r sprintf("%.0f", annual_incidence_norway * sum(1 / (1 + discount_rate_research)^(1:research_horizon_years)))` discounted patient-years

Population-level EVPPI represents the total expected value (in millions of EUR) of eliminating uncertainty about a parameter or parameter group across the entire eligible population over the research horizon. This scaling accounts for the discounted flow of future patients who would benefit from the research.

**Data sources**: The annual incidence estimate is based on Norwegian Cancer Registry data (approximately 4,000 annual CRC cases) and international literature estimates for MSS/pMMR proportion (70-75% of metastatic cases) and metastatic presentation rates (approximately 50%), yielding a conservative estimate of 1,500 eligible patients per year.

\newpage

# Model Structure Definitions

We compare three model structures to assess the robustness of value of information results to the specification of biomarker-treatment interactions in the survival models.

```{r model-structure-table}
model_structure_df <- data.frame(
  Model = c("Model A", "Model B", "Model C"),
  Name = c("Joint", "Focused", "Separate"),
  Formula = c(
    "Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx",
    "Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx",
    "Age + sex + Rx + [biomarker]:Rx"
  ),
  Description = c(
    "All biomarkers and all treatment interactions in one unified model",
    "Per-strategy formulas: CRP/TMB_BRAF with both interactions, TLR with TLR-only interaction",
    "Only one biomarker and its treatment interaction per model (simplest specification)"
  )
)

knitr::kable(model_structure_df,
             col.names = c("Model", "Name", "Formula Pattern", "Description"),
             caption = "Model structure definitions used in the analysis",
             booktabs = TRUE,
             align = c("l", "l", "l", "l")) %>%
  kableExtra::column_spec(1, width = "1.5cm") %>%
  kableExtra::column_spec(2, width = "1.5cm") %>%
  kableExtra::column_spec(3, width = "5cm") %>%
  kableExtra::column_spec(4, width = "6cm") %>%
  kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position"))
```

**Rationale**: Model A (Joint) is the most comprehensive specification but may suffer from overfitting with limited sample size. Model C (Separate) is the simplest but ignores potential confounding from other biomarkers. Model B (Focused) uses a shared formula with CRP and TMB/BRAF (excluding TLR), providing simultaneous estimates for both interactions while adjusting for each other. Comparing results across all three structures provides insight into the structural uncertainty of our findings.

\newpage

# Scenario Definitions

```{r scenario-table-summary}
scenario_summary <- scenarios %>%
  mutate(
    `WTP Threshold` = paste0("EUR", format(wtp, big.mark = ",")),
    `Nivolumab Cost` = paste0("EUR", format(c_drug_nivo, big.mark = ","))
  ) %>%
  select(`Scenario Name` = scenario_name,
         `WTP Threshold`,
         `Nivolumab Cost`)

kable(scenario_summary,
      caption = "Analysis scenario definitions. Higher WTP thresholds (EUR100,000 and EUR150,000) are arbitrary exploratory thresholds, though the highest severity adjustment in Norwegian guidelines may fall between these values. The decreased nivolumab cost (EUR4,641) represents an 80\\% discount compared to the 40\\% discount in the base case scenario.",
      booktabs = TRUE,
      align = c("l", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

\newpage

# Base Case Scenario

```{r base-params}
base_results_list <- list()

# Get results for each model structure
for (model_label in unique(evppi_all_scenarios$model_label)) {
  model_data <- evppi_all_scenarios %>%
    filter(scenario_id == "base", model_label == !!model_label)

  if (nrow(model_data) > 0) {
    base_results_list[[model_label]] <- list(
      evpi = model_data$evpi[1],
      evppi_results = model_data
    )
  }
}

base_wtp <- scenarios$wtp[scenarios$scenario_id == "base"]
base_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
```

**Willingness-to-Pay Threshold:** EUR`r format(base_wtp, big.mark = ",")`

**Nivolumab Cost:** EUR`r format(base_nivo_cost, big.mark = ",")`

## EVPI Comparison Across Model Structures

```{r base-evpi-comparison, eval=has_multimodel}
evpi_comparison <- evppi_all_scenarios %>%
  filter(scenario_id == "base") %>%
  select(model_name, evpi) %>%
  distinct() %>%
  mutate(EVPI = paste0("EUR", round(evpi, 2)))

kable(evpi_comparison %>% select(Model = model_name, EVPI),
      caption = "Expected Value of Perfect Information (EVPI) by model structure - Base Case",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

```{r base-evpi-bar, fig.cap="EVPI comparison across model structures (Base Case)", fig.height=4, eval=has_multimodel}
evpi_plot_data <- evppi_all_scenarios %>%
  filter(scenario_id == "base") %>%
  select(model_name, evpi) %>%
  distinct()

if (nrow(evpi_plot_data) > 0 && max(evpi_plot_data$evpi) > 0.01) {
  ggplot(evpi_plot_data, aes(x = model_name, y = evpi, fill = model_name)) +
    geom_col(alpha = 0.8) +
    geom_text(aes(label = paste0("EUR", round(evpi, 2))), vjust = -0.5, size = 3) +
    scale_y_continuous(labels = scales::dollar_format(prefix = "EUR"),
                      expand = expansion(mult = c(0, 0.15))) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Perfect Information",
      subtitle = "Base Case Scenario",
      x = NULL,
      y = "EVPI (EUR)"
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          axis.text.x = element_text(angle = 45, hjust = 1))
}
```

## EVPPI Results by Model Structure

```{r base-evppi-multimodel-table, eval=has_multimodel}
# Create side-by-side EVPPI comparison (per-patient values)
base_evppi_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "base") %>%
  select(parameter, model_label, evppi, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

# Get column order based on which models are available
model_labels_present <- unique(evppi_all_scenarios$model_label)

# Format for display
display_cols <- c("parameter")
for (label in c("joint", "focused", "separate")) {
  if (label %in% model_labels_present) {
    display_cols <- c(display_cols, paste0("evppi_", label), paste0("evppi_percent_of_evpi_", label))
  }
}

base_evppi_display <- base_evppi_wide %>%
  select(any_of(display_cols)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_")), na.rm = TRUE)))

# Rename columns for display
col_names <- c("Parameter")
for (label in c("joint", "focused", "separate")) {
  if (label %in% model_labels_present) {
    short_label <- c("joint" = "A", "focused" = "B", "separate" = "C")[label]
    col_names <- c(col_names, paste0("EVPPI (", short_label, ")"), paste0("% (", short_label, ")"))
  }
}

# Format numeric values
for (col in names(base_evppi_display)) {
  if (grepl("^evppi_", col) && !grepl("percent", col)) {
    base_evppi_display[[col]] <- paste0("EUR", round(base_evppi_display[[col]], 2))
  } else if (grepl("percent", col)) {
    base_evppi_display[[col]] <- paste0(round(base_evppi_display[[col]], 1), "%")
  }
}

kable(base_evppi_display,
      col.names = col_names,
      caption = "Per-patient EVPPI results by model structure - Base Case (ranked by average importance)",
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r base-evppi-population-table, eval=has_multimodel}
# Create population-level EVPPI table
base_evppi_pop_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "base") %>%
  select(parameter, model_label, evppi_population_millions, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi_population_millions, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

# Format for display
display_cols_pop <- c("parameter")
for (label in c("joint", "focused", "separate")) {
  if (label %in% model_labels_present) {
    display_cols_pop <- c(display_cols_pop,
                          paste0("evppi_population_millions_", label),
                          paste0("evppi_percent_of_evpi_", label))
  }
}

base_evppi_pop_display <- base_evppi_pop_wide %>%
  select(any_of(display_cols_pop)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_population")), na.rm = TRUE)))

# Rename columns for display (matching per-patient table)
col_names_pop <- c("Parameter")
for (label in c("joint", "focused", "separate")) {
  if (label %in% model_labels_present) {
    short_label <- c("joint" = "A", "focused" = "B", "separate" = "C")[label]
    col_names_pop <- c(col_names_pop,
                       paste0("Pop. EVPPI (", short_label, ")"),
                       paste0("% (", short_label, ")"))
  }
}

# Format numeric values
for (col in names(base_evppi_pop_display)) {
  if (grepl("^evppi_population", col)) {
    base_evppi_pop_display[[col]] <- paste0("EUR", sprintf("%.2f", base_evppi_pop_display[[col]]), "M")
  } else if (grepl("percent", col)) {
    base_evppi_pop_display[[col]] <- paste0(round(base_evppi_pop_display[[col]], 1), "%")
  }
}

kable(base_evppi_pop_display,
      col.names = col_names_pop,
      caption = paste0("Population-level EVPPI results by model structure - Base Case (millions of EUR over ", research_horizon_years, " years, discounted at ", discount_rate_research * 100, "%, ranked by average importance)"),
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names_pop) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r base-evppi-faceted-plot, fig.cap="EVPPI by parameter and model structure (Base Case)", fig.height=6, eval=has_multimodel}
base_evppi_plot <- evppi_all_scenarios %>%
  filter(scenario_id == "base", evppi > 0) %>%
  group_by(model_label) %>%
  arrange(desc(evppi)) %>%
  slice(1:8) %>%
  ungroup()

if (nrow(base_evppi_plot) > 0) {
  # Get top parameters across all models
  top_params <- base_evppi_plot %>%
    group_by(parameter) %>%
    summarise(max_evppi = max(evppi)) %>%
    arrange(desc(max_evppi)) %>%
    pull(parameter)

  base_evppi_plot <- base_evppi_plot %>%
    mutate(parameter = factor(parameter, levels = rev(top_params)))

  ggplot(base_evppi_plot, aes(x = evppi, y = parameter, fill = model_name)) +
    geom_col(alpha = 0.8) +
    facet_wrap(~model_name, ncol = 3) +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Partially Perfect Information",
      subtitle = "Base Case - Top Parameters by Model Structure",
      x = "EVPPI (EUR)",
      y = NULL
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold"))
}
```

## Interpretation

```{r base-population-interpretation, results='asis'}
# Calculate population-level summary statistics
base_pop_summary <- evppi_all_scenarios %>%
  filter(scenario_id == "base") %>%
  group_by(parameter) %>%
  summarise(
    max_pop_evppi = max(evppi_population_millions, na.rm = TRUE),
    .groups = "drop"
  ) %>%
  arrange(desc(max_pop_evppi))

# Get top parameter(s) by population EVPPI
top_param_pop <- base_pop_summary$parameter[1]
top_value_pop <- base_pop_summary$max_pop_evppi[1]

# Get utility parameters specifically
utility_pop_evppi <- base_pop_summary %>%
  filter(grepl("^u_|utilities", parameter)) %>%
  pull(max_pop_evppi) %>%
  max(na.rm = TRUE)

cat("### Population-Level Research Value\n\n")
cat("**Per-Patient Level:** Utility parameters (u_np, u_p) show the highest per-patient EVPPI, ranging from approximately EUR800-1,100 in the base case, while cost parameters show lower EVPPI (typically <EUR200), reflecting less uncertainty in cost estimates.\n\n")

cat("**Population Level:** Scaling to the Norwegian eligible population (", annual_incidence_norway, " patients/year over ", research_horizon_years, " years, discounted at ", discount_rate_research * 100, "%), utility parameter uncertainty translates to **EUR", sprintf("%.1f", utility_pop_evppi), " million** in potential research value. ", sep = "")

cat("This population-level value provides context for research investment decisions. For example, a study to reduce uncertainty in utility values (e.g., a large-scale quality-of-life measurement study in this patient population) could be justified if its cost is substantially less than EUR", sprintf("%.1f", utility_pop_evppi), " million.\n\n", sep = "")

nivo_pop_evppi <- base_pop_summary$max_pop_evppi[base_pop_summary$parameter == "c_drug_nivo"]
if (length(nivo_pop_evppi) > 0 && !is.na(nivo_pop_evppi)) {
  cat("Cost parameters, while showing lower per-patient EVPPI, still represent substantial population-level values (EUR", sprintf("%.1f", nivo_pop_evppi), " million for nivolumab cost), particularly relevant for market access negotiations and price negotiations.\n\n", sep = "")
}
```

```{r base-interpretation, results='asis'}
# Get max EVPI across models
max_evpi <- max(sapply(base_results_list, function(x) x$evpi), na.rm = TRUE)

if (max_evpi > 0.01) {
  cat("\n\nThe positive EVPI indicates decision uncertainty at the base case WTP threshold. This suggests that additional research to reduce parameter uncertainty could have value. The comparison across model structures shows whether this finding is robust to the specification of biomarker-treatment interactions.\n")
} else {
  cat("\n\nThe EVPI is effectively zero across all model structures, indicating no decision uncertainty at the base case WTP threshold. In this case, one strategy is clearly dominant regardless of parameter uncertainty, making EVPPI calculations less meaningful for the base case scenario.\n")
}
```

\newpage

# Scenario 1: Decreased Nivolumab Cost

```{r s1-params}
s1_results_list <- list()

for (model_label in unique(evppi_all_scenarios$model_label)) {
  model_data <- evppi_all_scenarios %>%
    filter(scenario_id == "s1_decreased_nivo", model_label == !!model_label)

  if (nrow(model_data) > 0) {
    s1_results_list[[model_label]] <- list(
      evpi = model_data$evpi[1],
      evppi_results = model_data
    )
  }
}

s1_wtp <- 51000
s1_nivo_cost <- 4641
```

**Willingness-to-Pay Threshold:** EUR`r format(s1_wtp, big.mark = ",")`

**Nivolumab Cost:** EUR`r format(s1_nivo_cost, big.mark = ",")` (80% discount)

## EVPI Comparison Across Model Structures

```{r s1-evpi-comparison, eval=has_multimodel}
evpi_comparison_s1 <- evppi_all_scenarios %>%
  filter(scenario_id == "s1_decreased_nivo") %>%
  select(model_name, evpi) %>%
  distinct() %>%
  mutate(EVPI = paste0("EUR", round(evpi, 2)))

kable(evpi_comparison_s1 %>% select(Model = model_name, EVPI),
      caption = "Expected Value of Perfect Information (EVPI) by model structure - Scenario 1",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

## EVPPI Results by Model Structure

```{r s1-evppi-multimodel-table, eval=has_multimodel}
s1_evppi_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "s1_decreased_nivo") %>%
  select(parameter, model_label, evppi, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

s1_evppi_display <- s1_evppi_wide %>%
  select(any_of(display_cols)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_")), na.rm = TRUE)))

for (col in names(s1_evppi_display)) {
  if (grepl("^evppi_", col) && !grepl("percent", col)) {
    s1_evppi_display[[col]] <- paste0("EUR", round(s1_evppi_display[[col]], 2))
  } else if (grepl("percent", col)) {
    s1_evppi_display[[col]] <- paste0(round(s1_evppi_display[[col]], 1), "%")
  }
}

kable(s1_evppi_display,
      col.names = col_names,
      caption = "EVPPI results by model structure - Scenario 1: Decreased Nivolumab Cost",
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r s1-evppi-faceted-plot, fig.cap="EVPPI by parameter and model structure (Scenario 1)", fig.height=6, eval=has_multimodel}
s1_evppi_plot <- evppi_all_scenarios %>%
  filter(scenario_id == "s1_decreased_nivo", evppi > 0) %>%
  group_by(model_label) %>%
  arrange(desc(evppi)) %>%
  slice(1:8) %>%
  ungroup()

if (nrow(s1_evppi_plot) > 0) {
  top_params_s1 <- s1_evppi_plot %>%
    group_by(parameter) %>%
    summarise(max_evppi = max(evppi)) %>%
    arrange(desc(max_evppi)) %>%
    pull(parameter)

  s1_evppi_plot <- s1_evppi_plot %>%
    mutate(parameter = factor(parameter, levels = rev(top_params_s1)))

  ggplot(s1_evppi_plot, aes(x = evppi, y = parameter, fill = model_name)) +
    geom_col(alpha = 0.8) +
    facet_wrap(~model_name, ncol = 3) +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Partially Perfect Information",
      subtitle = "Scenario 1: Decreased Nivolumab Cost",
      x = "EVPPI (EUR)",
      y = NULL
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold"))
}
```

\newpage

# Scenario 2: Higher WTP Threshold (EUR100,000)

```{r s2-params}
s2_wtp <- 100000
s2_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
```

**Willingness-to-Pay Threshold:** EUR`r format(s2_wtp, big.mark = ",")`

**Nivolumab Cost:** EUR`r format(s2_nivo_cost, big.mark = ",")` (standard)

## EVPI Comparison Across Model Structures

```{r s2-evpi-comparison, eval=has_multimodel}
evpi_comparison_s2 <- evppi_all_scenarios %>%
  filter(scenario_id == "s2_wtp100k") %>%
  select(model_name, evpi) %>%
  distinct() %>%
  mutate(EVPI = paste0("EUR", round(evpi, 2)))

kable(evpi_comparison_s2 %>% select(Model = model_name, EVPI),
      caption = "Expected Value of Perfect Information (EVPI) by model structure - Scenario 2",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

## EVPPI Results by Model Structure

```{r s2-evppi-multimodel-table, eval=has_multimodel}
s2_evppi_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "s2_wtp100k") %>%
  select(parameter, model_label, evppi, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

s2_evppi_display <- s2_evppi_wide %>%
  select(any_of(display_cols)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_")), na.rm = TRUE)))

for (col in names(s2_evppi_display)) {
  if (grepl("^evppi_", col) && !grepl("percent", col)) {
    s2_evppi_display[[col]] <- paste0("EUR", round(s2_evppi_display[[col]], 2))
  } else if (grepl("percent", col)) {
    s2_evppi_display[[col]] <- paste0(round(s2_evppi_display[[col]], 1), "%")
  }
}

kable(s2_evppi_display,
      col.names = col_names,
      caption = "EVPPI results by model structure - Scenario 2: WTP EUR100,000",
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r s2-evppi-faceted-plot, fig.cap="EVPPI by parameter and model structure (Scenario 2)", fig.height=6, eval=has_multimodel}
s2_evppi_plot <- evppi_all_scenarios %>%
  filter(scenario_id == "s2_wtp100k", evppi > 0) %>%
  group_by(model_label) %>%
  arrange(desc(evppi)) %>%
  slice(1:8) %>%
  ungroup()

if (nrow(s2_evppi_plot) > 0) {
  top_params_s2 <- s2_evppi_plot %>%
    group_by(parameter) %>%
    summarise(max_evppi = max(evppi)) %>%
    arrange(desc(max_evppi)) %>%
    pull(parameter)

  s2_evppi_plot <- s2_evppi_plot %>%
    mutate(parameter = factor(parameter, levels = rev(top_params_s2)))

  ggplot(s2_evppi_plot, aes(x = evppi, y = parameter, fill = model_name)) +
    geom_col(alpha = 0.8) +
    facet_wrap(~model_name, ncol = 3) +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Partially Perfect Information",
      subtitle = "Scenario 2: WTP EUR100,000",
      x = "EVPPI (EUR)",
      y = NULL
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold"))
}
```

\newpage

# Scenario 3: Higher WTP with Decreased Nivolumab Cost

```{r s3-params}
s3_wtp <- 100000
s3_nivo_cost <- 4641
```

**Willingness-to-Pay Threshold:** EUR`r format(s3_wtp, big.mark = ",")`

**Nivolumab Cost:** EUR`r format(s3_nivo_cost, big.mark = ",")` (80% discount)

## EVPI Comparison Across Model Structures

```{r s3-evpi-comparison, eval=has_multimodel}
evpi_comparison_s3 <- evppi_all_scenarios %>%
  filter(scenario_id == "s3_wtp100k_decreased") %>%
  select(model_name, evpi) %>%
  distinct() %>%
  mutate(EVPI = paste0("EUR", round(evpi, 2)))

kable(evpi_comparison_s3 %>% select(Model = model_name, EVPI),
      caption = "Expected Value of Perfect Information (EVPI) by model structure - Scenario 3",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

## EVPPI Results by Model Structure

```{r s3-evppi-multimodel-table, eval=has_multimodel}
s3_evppi_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "s3_wtp100k_decreased") %>%
  select(parameter, model_label, evppi, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

s3_evppi_display <- s3_evppi_wide %>%
  select(any_of(display_cols)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_")), na.rm = TRUE)))

for (col in names(s3_evppi_display)) {
  if (grepl("^evppi_", col) && !grepl("percent", col)) {
    s3_evppi_display[[col]] <- paste0("EUR", round(s3_evppi_display[[col]], 2))
  } else if (grepl("percent", col)) {
    s3_evppi_display[[col]] <- paste0(round(s3_evppi_display[[col]], 1), "%")
  }
}

kable(s3_evppi_display,
      col.names = col_names,
      caption = "EVPPI results by model structure - Scenario 3: WTP EUR100,000 + Decreased Nivolumab",
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r s3-evppi-faceted-plot, fig.cap="EVPPI by parameter and model structure (Scenario 3)", fig.height=6, eval=has_multimodel}
s3_evppi_plot <- evppi_all_scenarios %>%
  filter(scenario_id == "s3_wtp100k_decreased", evppi > 0) %>%
  group_by(model_label) %>%
  arrange(desc(evppi)) %>%
  slice(1:8) %>%
  ungroup()

if (nrow(s3_evppi_plot) > 0) {
  top_params_s3 <- s3_evppi_plot %>%
    group_by(parameter) %>%
    summarise(max_evppi = max(evppi)) %>%
    arrange(desc(max_evppi)) %>%
    pull(parameter)

  s3_evppi_plot <- s3_evppi_plot %>%
    mutate(parameter = factor(parameter, levels = rev(top_params_s3)))

  ggplot(s3_evppi_plot, aes(x = evppi, y = parameter, fill = model_name)) +
    geom_col(alpha = 0.8) +
    facet_wrap(~model_name, ncol = 3) +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Partially Perfect Information",
      subtitle = "Scenario 3: WTP EUR100,000 + Decreased Nivolumab Cost",
      x = "EVPPI (EUR)",
      y = NULL
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold"))
}
```

\newpage

# Scenario 4: Highest WTP Threshold (EUR150,000)

```{r s4-params}
s4_wtp <- 150000
s4_nivo_cost <- scenarios$c_drug_nivo[scenarios$scenario_id == "base"]
```

**Willingness-to-Pay Threshold:** EUR`r format(s4_wtp, big.mark = ",")`

**Nivolumab Cost:** EUR`r format(s4_nivo_cost, big.mark = ",")` (standard)

## EVPI Comparison Across Model Structures

```{r s4-evpi-comparison, eval=has_multimodel}
evpi_comparison_s4 <- evppi_all_scenarios %>%
  filter(scenario_id == "s4_wtp150k") %>%
  select(model_name, evpi) %>%
  distinct() %>%
  mutate(EVPI = paste0("EUR", round(evpi, 2)))

kable(evpi_comparison_s4 %>% select(Model = model_name, EVPI),
      caption = "Expected Value of Perfect Information (EVPI) by model structure - Scenario 4",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

## EVPPI Results by Model Structure

```{r s4-evppi-multimodel-table, eval=has_multimodel}
s4_evppi_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "s4_wtp150k") %>%
  select(parameter, model_label, evppi, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

s4_evppi_display <- s4_evppi_wide %>%
  select(any_of(display_cols)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_")), na.rm = TRUE)))

for (col in names(s4_evppi_display)) {
  if (grepl("^evppi_", col) && !grepl("percent", col)) {
    s4_evppi_display[[col]] <- paste0("EUR", round(s4_evppi_display[[col]], 2))
  } else if (grepl("percent", col)) {
    s4_evppi_display[[col]] <- paste0(round(s4_evppi_display[[col]], 1), "%")
  }
}

kable(s4_evppi_display,
      col.names = col_names,
      caption = "EVPPI results by model structure - Scenario 4: WTP EUR150,000",
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r s4-evppi-faceted-plot, fig.cap="EVPPI by parameter and model structure (Scenario 4)", fig.height=6, eval=has_multimodel}
s4_evppi_plot <- evppi_all_scenarios %>%
  filter(scenario_id == "s4_wtp150k", evppi > 0) %>%
  group_by(model_label) %>%
  arrange(desc(evppi)) %>%
  slice(1:8) %>%
  ungroup()

if (nrow(s4_evppi_plot) > 0) {
  top_params_s4 <- s4_evppi_plot %>%
    group_by(parameter) %>%
    summarise(max_evppi = max(evppi)) %>%
    arrange(desc(max_evppi)) %>%
    pull(parameter)

  s4_evppi_plot <- s4_evppi_plot %>%
    mutate(parameter = factor(parameter, levels = rev(top_params_s4)))

  ggplot(s4_evppi_plot, aes(x = evppi, y = parameter, fill = model_name)) +
    geom_col(alpha = 0.8) +
    facet_wrap(~model_name, ncol = 3) +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Partially Perfect Information",
      subtitle = "Scenario 4: WTP EUR150,000",
      x = "EVPPI (EUR)",
      y = NULL
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold"))
}
```

\newpage

# Scenario 5: Highest WTP with Decreased Nivolumab Cost

```{r s5-params}
s5_wtp <- 150000
s5_nivo_cost <- 4641
```

**Willingness-to-Pay Threshold:** EUR`r format(s5_wtp, big.mark = ",")`

**Nivolumab Cost:** EUR`r format(s5_nivo_cost, big.mark = ",")` (80% discount)

## EVPI Comparison Across Model Structures

```{r s5-evpi-comparison, eval=has_multimodel}
evpi_comparison_s5 <- evppi_all_scenarios %>%
  filter(scenario_id == "s5_wtp150k_decreased") %>%
  select(model_name, evpi) %>%
  distinct() %>%
  mutate(EVPI = paste0("EUR", round(evpi, 2)))

kable(evpi_comparison_s5 %>% select(Model = model_name, EVPI),
      caption = "Expected Value of Perfect Information (EVPI) by model structure - Scenario 5",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                font_size = 10,
                full_width = FALSE)
```

## EVPPI Results by Model Structure

```{r s5-evppi-multimodel-table, eval=has_multimodel}
s5_evppi_wide <- evppi_all_scenarios %>%
  filter(scenario_id == "s5_wtp150k_decreased") %>%
  select(parameter, model_label, evppi, evppi_percent_of_evpi) %>%
  pivot_wider(
    names_from = model_label,
    values_from = c(evppi, evppi_percent_of_evpi),
    names_glue = "{.value}_{model_label}"
  )

s5_evppi_display <- s5_evppi_wide %>%
  select(any_of(display_cols)) %>%
  arrange(desc(rowMeans(select(., starts_with("evppi_")), na.rm = TRUE)))

for (col in names(s5_evppi_display)) {
  if (grepl("^evppi_", col) && !grepl("percent", col)) {
    s5_evppi_display[[col]] <- paste0("EUR", round(s5_evppi_display[[col]], 2))
  } else if (grepl("percent", col)) {
    s5_evppi_display[[col]] <- paste0(round(s5_evppi_display[[col]], 1), "%")
  }
}

kable(s5_evppi_display,
      col.names = col_names,
      caption = "EVPPI results by model structure - Scenario 5: WTP EUR150,000 + Decreased Nivolumab",
      booktabs = TRUE,
      align = c("l", rep("r", length(col_names) - 1))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                font_size = 8,
                full_width = FALSE)
```

```{r s5-evppi-faceted-plot, fig.cap="EVPPI by parameter and model structure (Scenario 5)", fig.height=6, eval=has_multimodel}
s5_evppi_plot <- evppi_all_scenarios %>%
  filter(scenario_id == "s5_wtp150k_decreased", evppi > 0) %>%
  group_by(model_label) %>%
  arrange(desc(evppi)) %>%
  slice(1:8) %>%
  ungroup()

if (nrow(s5_evppi_plot) > 0) {
  top_params_s5 <- s5_evppi_plot %>%
    group_by(parameter) %>%
    summarise(max_evppi = max(evppi)) %>%
    arrange(desc(max_evppi)) %>%
    pull(parameter)

  s5_evppi_plot <- s5_evppi_plot %>%
    mutate(parameter = factor(parameter, levels = rev(top_params_s5)))

  ggplot(s5_evppi_plot, aes(x = evppi, y = parameter, fill = model_name)) +
    geom_col(alpha = 0.8) +
    facet_wrap(~model_name, ncol = 3) +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    scale_fill_brewer(palette = "Set2") +
    labs(
      title = "Expected Value of Partially Perfect Information",
      subtitle = "Scenario 5: WTP EUR150,000 + Decreased Nivolumab Cost",
      x = "EVPPI (EUR)",
      y = NULL
    ) +
    theme_minimal() +
    theme(legend.position = "none",
          strip.text = element_text(face = "bold"))
}
```

\newpage

# Comparative Analysis Across Scenarios and Models

## EVPI Comparison

```{r evpi-comparison-multimodel, fig.cap="Expected Value of Perfect Information across scenarios and model structures", fig.height=6, eval=has_multimodel}
if (nrow(evppi_all_scenarios) > 0) {
  evpi_comparison_all <- evppi_all_scenarios %>%
    select(scenario_name, wtp, model_name, evpi) %>%
    distinct() %>%
    mutate(
      cost_type = ifelse(grepl("Decreased", scenario_name), "Decreased Nivo", "Standard Nivo"),
      wtp_label = paste0("EUR", format(wtp/1000, big.mark = ","), "k")
    )

  ggplot(evpi_comparison_all, aes(x = wtp_label, y = evpi, fill = model_name)) +
    geom_col(position = "dodge", alpha = 0.8) +
    facet_wrap(~cost_type, ncol = 2) +
    scale_fill_brewer(palette = "Set2") +
    scale_y_continuous(labels = scales::dollar_format(prefix = "EUR")) +
    labs(
      title = "Expected Value of Perfect Information Across Scenarios",
      subtitle = "Comparison by WTP Threshold, Nivolumab Cost, and Model Structure",
      x = "Willingness-to-Pay Threshold",
      y = "EVPI (EUR)",
      fill = "Model Structure"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom",
          axis.text.x = element_text(angle = 45, hjust = 1))
}
```

## EVPPI Parameter Heatmap by Model Structure

```{r parameter-heatmap-multimodel, fig.cap="Parameter importance across scenarios by model structure (top 8 parameters)", fig.height=10, eval=has_multimodel}
if (nrow(evppi_all_scenarios) > 0) {
  # Get top 8 parameters overall
  top_params <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(total_evppi = sum(evppi), .groups = "drop") %>%
    arrange(desc(total_evppi)) %>%
    slice(1:8) %>%
    pull(parameter)

  heatmap_data <- evppi_all_scenarios %>%
    filter(parameter %in% top_params) %>%
    mutate(
      scenario_short = factor(case_when(
        scenario_id == "base" ~ "Base\n(EUR51k)",
        scenario_id == "s1_decreased_nivo" ~ "S1: EUR51k\nDecreased",
        scenario_id == "s2_wtp100k" ~ "S2: EUR100k\nStandard",
        scenario_id == "s3_wtp100k_decreased" ~ "S3: EUR100k\nDecreased",
        scenario_id == "s4_wtp150k" ~ "S4: EUR150k\nStandard",
        scenario_id == "s5_wtp150k_decreased" ~ "S5: EUR150k\nDecreased"
      ), levels = c("Base\n(EUR51k)", "S1: EUR51k\nDecreased", "S2: EUR100k\nStandard",
                    "S3: EUR100k\nDecreased", "S4: EUR150k\nStandard", "S5: EUR150k\nDecreased"))
    )

  ggplot(heatmap_data, aes(x = scenario_short, y = parameter, fill = evppi)) +
    geom_tile(color = "white", linewidth = 0.5) +
    geom_text(aes(label = ifelse(evppi > 0.1, paste0("EUR", round(evppi, 1)), "")),
              color = "white", fontface = "bold", size = 2) +
    facet_wrap(~model_name, ncol = 1) +
    scale_fill_gradient(low = "navy", high = "red",
                       name = "EVPPI (EUR)",
                       labels = scales::dollar_format(prefix = "EUR")) +
    labs(
      title = "Parameter Importance Across Scenarios by Model Structure",
      subtitle = "EVPPI values for top 8 parameters",
      x = "Scenario",
      y = "Parameter"
    ) +
    theme_minimal() +
    theme(
      plot.title = element_text(face = "bold", size = 12),
      axis.text.x = element_text(angle = 0, hjust = 0.5, size = 8),
      axis.text.y = element_text(size = 9),
      legend.position = "right",
      strip.text = element_text(face = "bold")
    )
}
```

## Summary Comparison Table

```{r comparative-summary-table-multimodel, eval=has_multimodel}
if (nrow(evppi_all_scenarios) > 0) {
  comp_summary <- evppi_all_scenarios %>%
    group_by(model_name, scenario_name, wtp) %>%
    summarise(
      EVPI = first(evpi),
      `Top Parameter` = parameter[which.max(evppi)],
      `Max EVPPI` = max(evppi),
      `% of EVPI` = round(max(evppi) / first(evpi) * 100, 1),
      .groups = "drop"
    ) %>%
    mutate(
      WTP = paste0("EUR", format(wtp, big.mark = ",")),
      EVPI = paste0("EUR", round(EVPI, 2)),
      `Max EVPPI` = paste0("EUR", round(`Max EVPPI`, 2))
    ) %>%
    select(Model = model_name, Scenario = scenario_name, WTP, EVPI, `Top Parameter`, `Max EVPPI`, `% of EVPI`)

  kable(comp_summary,
        caption = "Summary of EVPI and top EVPPI by model structure and scenario",
        booktabs = TRUE,
        align = c("l", "l", "r", "r", "l", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                  font_size = 7,
                  full_width = FALSE)
}
```

## Population-Level EVPPI Across Scenarios

```{r population-evppi-cross-scenario, eval=has_multimodel}
if (nrow(evppi_all_scenarios) > 0) {
  # Select key parameters for cross-scenario population comparison
  key_params <- c("[GROUP] utilities", "u_np", "u_p",
                  "[GROUP] drug_costs", "c_drug_nivo",
                  "[GROUP] all_costs")

  pop_cross_scenario <- evppi_all_scenarios %>%
    filter(parameter %in% key_params) %>%
    select(scenario_name, model_name, parameter,
           evppi_population_millions) %>%
    arrange(scenario_name, model_name,
            desc(evppi_population_millions))

  # Pivot to wide format: one column per model
  pop_cross_wide <- pop_cross_scenario %>%
    pivot_wider(
      names_from = model_name,
      values_from = evppi_population_millions
    )

  # Format numeric columns
  model_cols <- setdiff(names(pop_cross_wide),
                        c("scenario_name", "parameter"))
  for (col in model_cols) {
    pop_cross_wide[[col]] <- sprintf("%.2f", pop_cross_wide[[col]])
  }

  kable(pop_cross_wide,
        col.names = c("Scenario", "Parameter", model_cols),
        caption = paste0(
          "Population-level EVPPI (EUR millions) for key parameters across scenarios and model structures. ",
          "Based on ", annual_incidence_norway, " patients/year over ",
          research_horizon_years, " years, discounted at ",
          discount_rate_research * 100, "%."),
        booktabs = TRUE,
        align = c("l", "l", rep("r", length(model_cols)))) %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                  font_size = 7,
                  full_width = FALSE) %>%
    collapse_rows(columns = 1, valign = "top")
}
```

## Key Findings

```{r conclusions-multimodel, results='asis', eval=has_multimodel}
if (nrow(evppi_all_scenarios) > 0) {
  # Find scenario with highest EVPI per model
  max_evpi_by_model <- evppi_all_scenarios %>%
    select(model_name, scenario_name, evpi) %>%
    distinct() %>%
    group_by(model_name) %>%
    arrange(desc(evpi)) %>%
    slice(1) %>%
    ungroup()

  # Find most important parameter overall
  top_param_overall <- evppi_all_scenarios %>%
    group_by(parameter) %>%
    summarise(total = sum(evppi), .groups = "drop") %>%
    arrange(desc(total)) %>%
    slice(1)

  # Check consistency of top parameter across models
  top_param_by_model <- evppi_all_scenarios %>%
    group_by(model_name, parameter) %>%
    summarise(total = sum(evppi), .groups = "drop") %>%
    group_by(model_name) %>%
    arrange(desc(total)) %>%
    slice(1) %>%
    ungroup()

  consistent_top_param <- length(unique(top_param_by_model$parameter)) == 1

  cat("### Model Structure Robustness\n\n")

  if (consistent_top_param) {
    cat("**Parameter importance is consistent across model structures.** The parameter '",
        top_param_overall$parameter, "' is the most important driver of value of information across all three model specifications. This suggests that conclusions about research priorities are robust to the choice of model structure.\n\n", sep = "")
  } else {
    cat("**Parameter importance varies across model structures.** The top parameter differs depending on the model specification:\n\n")
    for (i in 1:nrow(top_param_by_model)) {
      cat("- ", top_param_by_model$model_name[i], ": ", top_param_by_model$parameter[i], "\n")
    }
    cat("\nThis variation suggests that conclusions about research priorities may be sensitive to the choice of model structure.\n\n")
  }

  cat("### Scenario with Greatest Decision Uncertainty\n\n")
  for (i in 1:nrow(max_evpi_by_model)) {
    cat("- **", max_evpi_by_model$model_name[i], "**: ", max_evpi_by_model$scenario_name[i],
        " (EVPI = EUR", round(max_evpi_by_model$evpi[i], 2), ")\n", sep = "")
  }

  cat("\n### Most Important Parameter Across All Scenarios\n\n")
  cat("**", top_param_overall$parameter, "** (Total EVPPI = EUR", round(top_param_overall$total, 2), ")\n\n", sep = "")

  cat("### General Observations\n\n")
  cat("**Impact of WTP Threshold:** Higher WTP thresholds generally increase decision uncertainty (EVPI), creating greater value for additional research to reduce parameter uncertainty.\n\n")
  cat("**Impact of Nivolumab Cost:** Decreased nivolumab costs shift the cost-effectiveness landscape and may change which parameters drive decision uncertainty.\n\n")
  cat("**Impact of Model Structure:** Comparing EVPI and EVPPI across model structures helps identify whether value of information conclusions are robust to structural uncertainty in the survival model specification.\n")
}
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.2

**Note on population-level EVPPI**: Population-level values calculated assuming `r annual_incidence_norway` annual eligible MSS/pMMR mCRC patients in Norway (based on Cancer Registry data and international prevalence estimates), discounted at `r discount_rate_research * 100`% per year over a `r research_horizon_years`-year research horizon.
