---
title: "Input Parameters"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup}
#| include: false

# Load required packages
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(here, knitr, kableExtra, DT, dplyr, tidyr, ggplot2)

# Set knitr options for PDF
options(knitr.table.format = "latex")

# Load PSA results - adjust path as needed based on where your PSA results are saved
# This assumes the PSA has been run and results are available
psa_results_path <- here("data/tidy", "psa_results.rds")
psa_params_path <- here("data/tidy", "psa_params.rds")

# Try to load PSA object and parameters
psa_obj <- NULL
psa_params <- NULL

if (file.exists(psa_results_path)) {
  psa_obj <- readRDS(psa_results_path)
}

if (file.exists(psa_params_path)) {
  psa_params <- readRDS(psa_params_path)
}
```

# Summary

This report provides an overview of all input parameters used in the METIMMOX-1 health economic model, organized into global model settings and variable parameters across base case, DSA, and PSA analyses.

# Global Model Parameters

These parameters define the overall model structure and are held constant across all analyses.

```{r global-parameters}
#| echo: false

global_params <- data.frame(
  Parameter = c("Time Horizon", 
               "Cycle Length", 
               "Discount Rate", 
               "WTP Threshold",
               "PSA Sample Size",
               "Sampling Models",
               "DSA Variation Range"),
  Value = c("520 weeks (10 years)",
           "1 week",
           "4% per annum",
           "€51,000 per QALY",
           "5,000 iterations",
           "5,000 models",
           "±20%"),
  Description = c("Model time horizon",
                 "Cycle length for discrete-time model",
                 "Annual discount rate for costs and effects",
                 "Willingness-to-pay threshold",
                 "Number of Monte Carlo iterations for PSA",
                 "Resampled models for survival uncertainty",
                 "Parameter variation range for DSA"),
  Source = c("Clinical follow-up period", 
            "Model assumption", 
            "Model specification", 
            "Norwegian threshold based on severity (14.5 QALYs lost for diagnosis, based on a health 65-year old)",
            "Computational adequacy",
            "Statistical adequacy",
            "Standard practice")
)

kable(global_params, caption = "Global Model Parameters", booktabs = TRUE) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 9) %>%
  column_spec(1, width = "3.5cm") %>%
  column_spec(2, width = "3.5cm") %>%
  column_spec(3, width = "4cm") %>%
  column_spec(4, width = "3.5cm")
```

\newpage

# Model Input Parameters

This table presents all variable model parameters organized by type, showing their base case values, DSA variation ranges, and PSA distribution specifications.

```{r comprehensive-parameters}
#| echo: false

# Create comprehensive parameter table sorted by type
comprehensive_params <- data.frame(
  Parameter_Type = character(),
  Parameter = character(),
  Base_Case = character(),
  DSA_Range = character(),
  PSA_Distribution = character(),
  stringsAsFactors = FALSE
)

# Cost Parameters
cost_data <- data.frame(
  Parameter_Type = rep("Cost", 9),
  Parameter = c("Nivolumab per administration",
               "FLOX per administration", 
               "CT scan",
               "Blood tests",
               "NGS testing",
               "Standard outpatient visit",
               "Baseline visit",
               "Follow-up visit",
               "End-of-life care"),
  Base_Case = c("€13,923",
               "€427",
               "€386",
               "€0",
               "€1,439", 
               "€33",
               "€530",
               "€33",
               "€13,803"),
  DSA_Range = c("€11,138 - €16,708",
                "€342 - €512",
                "€309 - €463",
                "Not varied",
                "€1,151 - €1,727",
                "Not varied", 
                "Not varied",
                "Not varied",
                "€11,042 - €16,564"),
  PSA_Distribution = c("Gamma (shape=25, rate=0.0018)",
                      "Gamma (shape=25, rate=0.0586)",
                      "Gamma (shape=25, rate=0.0648)",
                      "Fixed at 0",
                      "Gamma (shape=25, rate=0.0174)",
                      "Gamma (shape=25, rate=0.7576)",
                      "Gamma (shape=25, rate=0.0472)",
                      "Gamma (shape=25, rate=0.7576)",
                      "Gamma (shape=25, rate=0.0018)"),
  stringsAsFactors = FALSE
)

# Utility Parameters  
utility_data <- data.frame(
  Parameter_Type = rep("Utility", 2),
  Parameter = c("Non-progressed state",
               "Progressed state"),
  Base_Case = c("0.9077",
               "0.9005"),
  DSA_Range = c("0.7262 - 1.0000",
               "0.7204 - 1.0000"),
  PSA_Distribution = c("Beta (α=41.0, β=4.2)",
                      "Beta (α=40.6, β=4.5)"),
  stringsAsFactors = FALSE
)

# Biomarker Prevalence Parameters
biomarker_data <- data.frame(
  Parameter_Type = rep("Prevalence", 3),
  Parameter = c("CRP biomarker positive",
               "TLR biomarker positive", 
               "TMB/BRAF biomarker positive"),
  Base_Case = c("30%",
               "25%",
               "20%"),
  DSA_Range = rep("Not varied", 3),
  PSA_Distribution = rep("Fixed", 3),
  stringsAsFactors = FALSE
)

# Survival Parameters - simplified to one row
survival_data <- data.frame(
  Parameter_Type = "Survival",
  Parameter = "OS and PFS curves by biomarker status",
  Base_Case = "Fitted parametric survival models",
  DSA_Range = "Not varied",
  PSA_Distribution = "Survival resampling (5,000 models)",
  stringsAsFactors = FALSE
)

# Combine all parameter types
comprehensive_params <- rbind(
  cost_data,
  utility_data, 
  biomarker_data,
  survival_data
)

# Create the table
kable(comprehensive_params, 
      caption = "Model Input Parameters by Type", 
      booktabs = TRUE,
      col.names = c("Type", "Parameter", "Base Case", "DSA Range", "PSA Distribution")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 8) %>%
  column_spec(1, width = "2cm") %>%
  column_spec(2, width = "4cm") %>%
  column_spec(3, width = "2.5cm") %>%
  column_spec(4, width = "3cm") %>%
  column_spec(5, width = "3.5cm") %>%
  pack_rows("Cost Parameters", 1, 9, latex_gap_space = "0.5em") %>%
  pack_rows("Utility Parameters", 10, 11, latex_gap_space = "0.5em") %>%
  pack_rows("Prevalence Parameters", 12, 14, latex_gap_space = "0.5em") %>%
  pack_rows("Survival Parameters", 15, 15, latex_gap_space = "0.5em") %>%
  footnote(general = c("DSA ranges calculated as base case ± 20%. Utility upper bounds capped at 1.0.",
                      "PSA: Gamma distributions for costs (CV=20%), Beta for utilities (CV=15%).",
                      "Survival curves use non-parametric resampling with age and sex adjustments."),
           general_title = "Notes:")
```

\newpage

# PSA Parameter Distributions

This section displays histograms of all sampled parameters from the probabilistic sensitivity analysis (PSA), showing the distribution shapes and ranges used in the Monte Carlo simulation.

```{r psa-histograms}
#| echo: false
#| fig-width: 12
#| fig-height: 10
#| fig-cap: "Distribution of PSA Parameters"

# Check if PSA parameters are available
if (!is.null(psa_params) && is.data.frame(psa_params)) {
  
  # Get numeric columns only
  numeric_cols <- sapply(psa_params, is.numeric)
  psa_params_numeric <- psa_params[, numeric_cols, drop = FALSE]
  
  if (ncol(psa_params_numeric) > 0) {
    n_params <- ncol(psa_params_numeric)
    
    # Calculate grid dimensions based on number of parameters
    n_cols <- 5
    n_rows <- ceiling(n_params / n_cols)
    
    par(mfrow = c(n_rows, n_cols), mar = c(4, 4, 2, 1))
    
    for(i in 1:n_params) {
      hist(psa_params_numeric[, i], 
           main = paste("Distribution of\n", colnames(psa_params_numeric)[i]),
           xlab = colnames(psa_params_numeric)[i],
           col = "lightblue",
           breaks = 30,
           cex.main = 0.9,
           cex.lab = 0.8,
           cex.axis = 0.8)
    }
    
    par(mfrow = c(1, 1))  # Reset layout
    
  } else {
    cat("No numeric parameters found in PSA data.\n")
  }
  
} else {
  cat("PSA parameter data not available.\n")
  cat("To generate these histograms:\n")
  cat("1. Run your PSA analysis script (e.g., scripts/R/analysis/13_EVPPIs.R)\n")
  cat("2. Save the psa_params object using: saveRDS(psa_params, here('results', 'psa_params.rds'))\n")
  cat("3. Re-render this report\n")
}
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.1