---
title: "METIMMOX-1 Model Input Parameters"
subtitle: "Base Case, Deterministic Sensitivity Analysis (DSA), and Probabilistic Sensitivity Analysis (PSA) Parameters"
author: "Health Economic Analysis Team"
date: "`r Sys.Date()`"
format:
  html:
    toc: true
    toc-depth: 3
    number-sections: true
    code-fold: true
    theme: cosmo
    html-math-method: katex
editor: visual
execute:
  echo: false
  warning: false
  message: false
---

```{r setup}
#| include: false

# Load required packages
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(here, knitr, kableExtra, DT, dplyr, tidyr, ggplot2)

# Source required files (assuming they've been run)
# Note: This assumes the analysis scripts have been executed
```

# Introduction

This report provides a comprehensive overview of all input parameters used in the METIMMOX-1 health economic model. The parameters are organized into three main categories:

1. **Base Case Parameters**: Point estimates used in the deterministic base case analysis
2. **DSA Parameters**: Parameter ranges and variations used in the deterministic sensitivity analysis
3. **PSA Parameters**: Probability distributions used in the probabilistic sensitivity analysis

# Base Case Parameters

The base case analysis uses fixed point estimates for all model parameters. These values represent the most likely or best available estimates from the literature and clinical data.

## Time and Discount Parameters

```{r base-time-params}
#| echo: true

# Time parameters (assuming these are defined in the environment)
time_params <- data.frame(
  Parameter = c("Time Horizon", "Cycle Length", "Discount Rate (Costs)", "Discount Rate (Effects)"),
  Value = c("time_horizon", "cl", "dr", "dr"),
  Description = c("Model time horizon in weeks", "Cycle length in weeks", 
                 "Annual discount rate for costs", "Annual discount rate for effects"),
  Source = c("Model assumption", "Model assumption", "Standard guideline", "Standard guideline")
)

kable(time_params, caption = "Time and Discount Parameters") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Utility Parameters

```{r base-utility-params}
#| echo: true

utility_params <- data.frame(
  Parameter = c("Non-progressed state utility", "Progressed state utility"),
  Symbol = c("u_np", "u_p"),
  Value = c(0.9077, 0.9005),
  Description = c("Utility weight for non-progressed disease state", 
                 "Utility weight for progressed disease state"),
  Source = c("Literature/clinical data", "Literature/clinical data")
)

kable(utility_params, caption = "Health State Utility Values") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Cost Parameters

### Drug Costs

```{r base-drug-costs}
#| echo: true

drug_costs <- data.frame(
  Parameter = c("Nivolumab per administration", "FLOX per administration"),
  Symbol = c("c_drug_nivo", "c_drug_FLOX"),
  Value = c("€13,923", "€427"),
  Description = c("Cost of nivolumab per treatment cycle", 
                 "Cost of FLOX chemotherapy per treatment cycle"),
  Source = c("Drug pricing data", "Drug pricing data")
)

kable(drug_costs, caption = "Drug Costs per Administration") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Test Costs

```{r base-test-costs}
#| echo: true

test_costs <- data.frame(
  Parameter = c("CT scan", "Blood tests", "Next-generation sequencing (NGS)"),
  Symbol = c("c_test_CT", "c_test_blood", "c_test_NGS"),
  Value = c("€386", "€0", "€1,439"),
  Description = c("Cost of CT imaging", "Cost of routine blood work", 
                 "Cost of NGS testing for TMB/BRAF"),
  Source = c("Healthcare tariffs", "Healthcare tariffs", "Laboratory pricing")
)

kable(test_costs, caption = "Diagnostic Test Costs") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Other Healthcare Costs

```{r base-other-costs}
#| echo: true

other_costs <- data.frame(
  Parameter = c("Standard outpatient visit", "Comprehensive baseline visit", 
               "Follow-up visits", "End-of-life care"),
  Symbol = c("c_other_visit", "c_other_baseline", "c_other_follow", "c_other_last"),
  Value = c("€33", "€530", "€33", "€13,803"),
  Description = c("Cost of routine outpatient consultation", 
                 "Cost of comprehensive baseline assessment",
                 "Cost of quarterly follow-up visits",
                 "Cost of terminal care and end-of-life management"),
  Source = c("Healthcare tariffs", "Healthcare tariffs", "Healthcare tariffs", "Literature")
)

kable(other_costs, caption = "Other Healthcare Resource Costs") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Biomarker Prevalence

```{r base-biomarker-prev}
#| echo: true

# Note: These values would come from strategies_df
biomarker_prev <- data.frame(
  Biomarker = c("CRP", "TLR", "TMB/BRAF"),
  Symbol = c("p_crp", "p_tlr", "p_tmb_braf"),
  Prevalence = c("strategies_df value", "strategies_df value", "strategies_df value"),
  Description = c("Prevalence of positive CRP biomarker", 
                 "Prevalence of positive TLR biomarker",
                 "Prevalence of positive TMB/BRAF biomarker"),
  Source = c("Clinical trial data", "Clinical trial data", "Clinical trial data")
)

kable(biomarker_prev, caption = "Biomarker Prevalence Rates") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Treatment Schedules

The model incorporates detailed treatment schedules that specify when different interventions are administered throughout the treatment period:

```{r treatment-schedules}
#| echo: true

schedule_info <- data.frame(
  Treatment = c("Nivolumab", "FLOX (Experimental)", "FLOX (Control)", "CT Scans", "Blood Tests", "Clinic Visits"),
  Symbol = c("l_nivo", "l_FLOX_exp", "l_FLOX_control", "l_CT", "l_blood", "l_visit"),
  Schedule = c("Weeks 5, 7, 13, 15, 29, 31, 37, 39", 
              "Weeks 1, 3, 9, 11, 25, 27, 33, 35",
              "Weeks 1, 3, 5, 7, 9, 11, 13, 15, 25, 27, 29, 31, 33, 35, 37, 39",
              "Baseline + every 12 weeks",
              "Baseline + every 4 weeks", 
              "All treatment and assessment visits"),
  Description = c("Immunotherapy administration schedule", 
                 "Experimental chemotherapy schedule",
                 "Control chemotherapy schedule",
                 "Imaging assessment schedule",
                 "Laboratory monitoring schedule",
                 "Clinical assessment schedule")
)

kable(schedule_info, caption = "Treatment and Monitoring Schedules") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Deterministic Sensitivity Analysis (DSA) Parameters

The DSA examines the impact of parameter uncertainty by varying individual parameters across plausible ranges while holding all other parameters at their base case values.

## DSA Parameter Selection

```{r dsa-parameters}
#| echo: true

dsa_params_info <- data.frame(
  Parameter = c("Nivolumab cost", "FLOX cost", "NGS test cost", "CT scan cost", 
               "Non-progressed utility", "Progressed utility", "End-of-life care cost"),
  Symbol = c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS", "c_test_CT", 
            "u_np", "u_p", "c_other_last"),
  Base_Value = c("€13,923", "€427", "€1,439", "€386", "0.9077", "0.9005", "€13,803"),
  Rationale = c("High cost driver", "Treatment cost", "Biomarker testing cost", 
               "Monitoring cost", "Quality of life impact", "Quality of life impact", 
               "High cost driver")
)

kable(dsa_params_info, caption = "Parameters Included in Deterministic Sensitivity Analysis") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## DSA Parameter Ranges

```{r dsa-ranges}
#| echo: true

# DSA uses ±20% variation
dsa_variation <- 0.2

# Define base values as numeric vector
base_vals <- c(13923, 427, 1439, 386, 0.9077, 0.9005, 13803)
param_labels <- c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS", "c_test_CT", 
                 "u_np", "u_p", "c_other_last")

# Calculate numeric bounds
lower_vals <- base_vals * (1 - dsa_variation)
upper_vals <- base_vals * (1 + dsa_variation)

# Cap utility values at 1.0
upper_vals[5] <- min(upper_vals[5], 1.0)  # u_np
upper_vals[6] <- min(upper_vals[6], 1.0)  # u_p

# Create data frame with properly formatted values
dsa_table <- data.frame(
  Parameter = param_labels,
  Base_Value = character(7),
  Lower_Bound = character(7),
  Upper_Bound = character(7),
  Variation = rep("±20%", 7),
  stringsAsFactors = FALSE
)

# Format cost parameters (1-4, 7) as currency
cost_idx <- c(1, 2, 3, 4, 7)
utility_idx <- c(5, 6)

for (i in cost_idx) {
  dsa_table$Base_Value[i] <- paste0("€", format(round(base_vals[i]), big.mark = ","))
  dsa_table$Lower_Bound[i] <- paste0("€", format(round(lower_vals[i]), big.mark = ","))
  dsa_table$Upper_Bound[i] <- paste0("€", format(round(upper_vals[i]), big.mark = ","))
}

# Format utility parameters to 4 decimal places
for (i in utility_idx) {
  dsa_table$Base_Value[i] <- sprintf("%.4f", base_vals[i])
  dsa_table$Lower_Bound[i] <- sprintf("%.4f", lower_vals[i])
  dsa_table$Upper_Bound[i] <- sprintf("%.4f", upper_vals[i])
}

kable(dsa_table, caption = "DSA Parameter Ranges") %>%
  kable_styling(bootstrap_options = c("striped", "hover")) %>%
  add_footnote("Utility parameters are capped at 1.0 for the upper bound", notation = "symbol")
```

# Probabilistic Sensitivity Analysis (PSA) Parameters

The PSA accounts for parameter uncertainty by assigning probability distributions to key model parameters and conducting Monte Carlo simulation.

## PSA Distribution Specifications

### Cost Parameter Distributions

All cost parameters follow **Gamma distributions** to ensure non-negative values, with a coefficient of variation (CV) of 20%.

```{r psa-cost-distributions}
#| echo: true

# Function to calculate gamma parameters
get_gamma_params <- function(mean_val, cv) {
  if (mean_val <= 0) return(list(shape = 0, rate = 0))
  shape <- 1/cv^2
  rate <- shape/mean_val
  return(list(shape = shape, rate = rate))
}

cv_costs <- 0.2

cost_means <- c(13923, 427, 386, 0, 1439, 33, 530, 33, 13803)
cost_params <- c("c_drug_nivo", "c_drug_FLOX", "c_test_CT", "c_test_blood", 
                "c_test_NGS", "c_other_visit", "c_other_baseline", 
                "c_other_follow", "c_other_last")

cost_distributions <- data.frame(
  Parameter = cost_params,
  Mean = cost_means,
  Distribution = rep("Gamma", 9),
  CV = rep("20%", 9),
  Shape = numeric(9),
  Rate = numeric(9)
)

for (i in 1:9) {
  params <- get_gamma_params(cost_means[i], cv_costs)
  cost_distributions$Shape[i] <- round(params$shape, 2)
  cost_distributions$Rate[i] <- round(params$rate, 6)
}

kable(cost_distributions, caption = "Cost Parameter Distributions for PSA") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Utility Parameter Distributions

Utility parameters follow **Beta distributions** to ensure values remain between 0 and 1, with a CV of 15%.

```{r psa-utility-distributions}
#| echo: true

# Function to calculate beta parameters
get_beta_params <- function(mean_val, cv) {
  var_val <- (mean_val * cv)^2
  alpha <- mean_val * (mean_val * (1 - mean_val) / var_val - 1)
  beta <- (1 - mean_val) * (mean_val * (1 - mean_val) / var_val - 1)
  return(list(shape1 = alpha, shape2 = beta))
}

cv_utilities <- 0.15

utility_means <- c(0.9077, 0.9005)
utility_params <- c("u_np", "u_p")

utility_distributions <- data.frame(
  Parameter = utility_params,
  Mean = utility_means,
  Distribution = rep("Beta", 2),
  CV = rep("15%", 2),
  Alpha = numeric(2),
  Beta = numeric(2)
)

for (i in 1:2) {
  params <- get_beta_params(utility_means[i], cv_utilities)
  utility_distributions$Alpha[i] <- round(params$shape1, 2)
  utility_distributions$Beta[i] <- round(params$shape2, 2)
}

kable(utility_distributions, caption = "Utility Parameter Distributions for PSA") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

### Survival Parameter Distributions

Survival parameters use **bootstrap sampling** from fitted survival models to capture uncertainty in the survival curves. The bootstrap approach:

1. Resamples the original survival data with replacement
2. Refits survival models to each bootstrap sample
3. Stores coefficient distributions for Monte Carlo sampling

```{r survival-distributions}
#| echo: true

survival_info <- data.frame(
  Model_Type = c("Control OS", "Control PFS", "Biomarker OS", "Biomarker PFS"),
  Formula = c("Surv(OSwk, Death) ~ Age + sex", 
             "Surv(PFSwk, Progression) ~ Age + sex",
             "Surv(OSwk, Death) ~ Age + sex + Rx + biomarker:Rx",
             "Surv(PFSwk, Progression) ~ Age + sex + Rx + biomarker:Rx"),
  Sampling_Method = rep("Bootstrap resampling", 4),
  Adjustments = rep("Age and sex adjusted", 4),
  Biomarkers = c("N/A", "N/A", "CRP, TLR, TMB/BRAF", "CRP, TLR, TMB/BRAF")
)

kable(survival_info, caption = "Survival Model Parameter Sampling for PSA") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

# Model Parameters Summary

## Parameter Categories Overview

```{r parameter-summary}
#| echo: true

param_summary <- data.frame(
  Category = c("Time & Discount", "Utilities", "Drug Costs", "Test Costs", 
              "Other Costs", "Treatment Schedules", "Survival Curves", "Biomarker Prevalence"),
  Base_Case = c("Fixed values", "Point estimates", "Point estimates", "Point estimates",
               "Point estimates", "Fixed schedules", "Fitted curves", "Point estimates"),
  DSA = c("Not varied", "Beta ranges ±20%", "Ranges ±20%", "Ranges ±20%",
         "Ranges ±20%", "Not varied", "Not varied", "Not varied"),
  PSA = c("Fixed", "Beta distributions", "Gamma distributions", "Gamma distributions",
         "Gamma distributions", "Fixed", "Bootstrap sampling", "Fixed"),
  Count = c(4, 2, 2, 3, 4, 6, 10, 3)
)

kable(param_summary, caption = "Summary of Parameter Treatment Across Analyses") %>%
  kable_styling(bootstrap_options = c("striped", "hover"))
```

## Total Parameter Count

- **Base Case**: 34 fixed parameters
- **DSA**: 7 parameters varied across ranges
- **PSA**: 16 parameters with probability distributions (9 cost + 2 utility + 5 survival model sets)

# Technical Notes

## Model Structure Consistency

- All analyses use the same base model structure and time horizon
- Treatment schedules are derived from the clinical trial protocol
- Survival curves are stratified by biomarker status and treatment arm
- Cost and utility parameters reflect the healthcare system perspective

## Uncertainty Handling

- **DSA**: One-way sensitivity analysis with ±20% variation
- **PSA**: Monte Carlo simulation with appropriate distributions
- **Survival uncertainty**: Bootstrap sampling preserves correlation structure
- **Parameter constraints**: Utilities bounded at [0,1], costs non-negative

## Data Sources

- Clinical effectiveness: METIMMOX-1 trial data
- Costs: National healthcare tariffs and drug pricing databases
- Utilities: Published literature and patient-reported outcomes
- Biomarker prevalence: Trial population characteristics

---

*Report generated on `r Sys.Date()` for the METIMMOX-1 health economic model.*