---
title: "Input Parameters"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05"),
  funs = c("report_format"),
  set_theme = FALSE
)

fmt_pct <- function(x) scales::percent(x, accuracy = 0.1)
```

# Model Configuration

```{r model-config}
config <- get_current_model_config()

config_table <- data.frame(
  Item = c("Economic strategies", "Economic biomarkers", "OS formula",
           "PFS formula", "Control formula"),
  Value = c(
    paste(get_strategies(), collapse = ", "),
    paste(get_biomarkers(), collapse = ", "),
    paste(deparse(config$formulas$shared$os), collapse = " "),
    paste(deparse(config$formulas$shared$pfs), collapse = " "),
    "Surv(time, event) ~ Age + sex"
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  config_table,
  booktabs = TRUE,
  align = c("l", "l"),
  caption = "Single economic model configuration"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "11cm")
```

# Biomarker Prevalence

```{r biomarker-prevalence}
prevalence_table <- strategies_df %>%
  filter(id %in% get_biomarkers()) %>%
  transmute(
    Biomarker = recode(id, crp = "CRP-positive", tmb_braf = "TMB/BRAF-positive"),
    Prevalence = fmt_pct(prevalence),
    Source = "METIMMOX-1 trial data"
  )

knitr::kable(
  prevalence_table,
  booktabs = TRUE,
  align = c("l", "r", "l"),
  caption = "Economic biomarker prevalences"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Utilities

The two health-state utilities are not sampled independently in the PSA. Independent beta draws placed the progressed utility above the progression-free utility in a substantial minority of draws (about 16% under the CORRECT utilities and about 49% under the IPD utilities), which widened the PSA with orderings that cannot occur. The PSA instead draws a non-negative decrement `u_decrement` (gamma, CV 0.15, mean equal to the base-case difference `u_np - u_p`) and sets `u_p = u_np - u_decrement`, so `u_p <= u_np` holds in every draw and the marginal mean of `u_p` is unchanged (issue #154). The realised reversal fraction is reported in the cost-effectiveness report.

```{r utility-table}
utility_table <- data.frame(
  Parameter = c("Progression-free utility", "Post-progression utility"),
  Symbol = c("u_np", "u_p"),
  Base_Case = c(l_params_base$u_np, l_params_base$u_p),
  DSA_Low = c(l_params_base$u_np, l_params_base$u_p) * (1 - DSA_mult),
  DSA_High = pmin(c(l_params_base$u_np, l_params_base$u_p) * (1 + DSA_mult), 1),
  stringsAsFactors = FALSE
) %>%
  mutate(across(c(Base_Case, DSA_Low, DSA_High), ~ sprintf("%.3f", .x)))

knitr::kable(
  utility_table,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r"),
  col.names = c("Parameter", "Symbol", "Base Case", "DSA Low", "DSA High"),
  caption = "Health-state utilities"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Costs

Unit drug and test costs are **fixed in the PSA** and varied deterministically only (issue #154). They are published tariffs, laboratory prices, or — for nivolumab — an assumed acquisition price; none of them is a quantity that further research could resolve, so sampling them attributed decision uncertainty — and, under the earlier nearest-neighbour value-of-information estimator, research value — to prices that are known. Fixing them roughly halved total EVPI (from EUR 45.2 to EUR 22.1 per patient) without changing any base-case result. Visit, baseline, follow-up and end-of-life costs remain probabilistic because they bundle genuine resource-use uncertainty, and the deterministic influence of the prices is undiminished: the nivolumab price is still the second-largest one-way driver for both guided strategies.

The nivolumab price of `r sprintf("EUR %s", format(l_params_base$c_drug_nivo, big.mark = ","))` per administration is an **assumption, not a citable tariff**: it represents an assumed Norwegian hospital acquisition price (about 40% below list). Norwegian hospital prices are set by confidential LIS tender and cannot be published; international list prices are higher. Eight administrations give about `r sprintf("EUR %s", format(8 * l_params_base$c_drug_nivo, big.mark = ","))` per treated patient, making this the largest single cost driver in the model. It is varied by +/-20% in the one-way analysis and by a factor of three in the biosimilar scenario.

```{r cost-table}
cost_spec <- parameter_distribution_spec()
cost_psa_status <- function(symbol) {
  row <- cost_spec[cost_spec$parameter == symbol, , drop = FALSE]
  if (nrow(row) != 1) return("Fixed")
  if (row$psa) "Sampled (gamma)" else "Fixed"
}

cost_table <- data.frame(
  Parameter = c(
    "Nivolumab per administration",
    "FLOX per administration",
    "CT scan",
    "Routine blood monitoring",
    "CRP biomarker test",
    "NGS test",
    "Visit",
    "Baseline other cost",
    "Follow-up other cost",
    "Post-progression treatment (per quarter)",
    "End-of-life cost"
  ),
  Symbol = c(
    "c_drug_nivo", "c_drug_FLOX", "c_test_CT", "c_test_blood",
    "c_test_CRP", "c_test_NGS", "c_other_visit", "c_other_baseline",
    "c_other_follow", "c_other_pp", "c_other_last"
  ),
  Base_Case = c(
    l_params_base$c_drug_nivo, l_params_base$c_drug_FLOX,
    l_params_base$c_test_CT, l_params_base$c_test_blood,
    l_params_base$c_test_CRP, l_params_base$c_test_NGS, l_params_base$c_other_visit,
    l_params_base$c_other_baseline, l_params_base$c_other_follow,
    l_params_base$c_other_pp, l_params_base$c_other_last
  ),
  stringsAsFactors = FALSE
) %>%
  mutate(
    PSA = vapply(Symbol, cost_psa_status, character(1)),
    DSA_Low = pmax(Base_Case * (1 - DSA_mult), 0),
    DSA_High = Base_Case * (1 + DSA_mult),
    across(c(Base_Case, DSA_Low, DSA_High), fmt_eur)
  ) %>%
  select(Parameter, Symbol, Base_Case, DSA_Low, DSA_High, PSA)

knitr::kable(
  cost_table,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r", "l"),
  col.names = c("Parameter", "Symbol", "Base Case", "DSA Low", "DSA High", "PSA"),
  caption = "Cost inputs"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::footnote(
    general = c(
      "Fixed parameters are not sampled in the PSA and therefore carry no value-of-information; they are varied in the one-way analysis.",
      "c_other_pp is zero in the base case: post-progression treatment is outside the modeled scope (see below). Its deterministic range is degenerate, so it is tested as a structural scenario rather than in the one-way analysis."
    ),
    general_title = "Notes: "
  )
```

## Post-progression treatment costs

The base case applies **no post-progression treatment cost**. Once a patient has progressed, the model charges only the quarterly follow-up contact (`c_other_follow`) and the one-time end-of-life cost (`c_other_last`); second-line systemic therapy, post-progression imaging and post-progression outpatient visits are not modeled. Because the strategies differ in the time patients spend in the progressed state, this omission is **differential** rather than a common offset, and its direction depends on which strategy accrues more progressed time. The parameter `c_other_pp` makes the omission explicit and is varied in a structural scenario (EUR 5,000 per quarter in the progressed state) reported in the one-way sensitivity analysis.

## Second treatment sequence

The treatment schedules give a second eight-cycle sequence at weeks 24-38 to **every patient still progression-free** at that point, in both arms. In METIMMOX the second sequence was started on progression during the treatment break, so the model charges second-sequence drug and visit costs to progression-free patients who would not have been re-treated. A partitioned survival model has no on-treatment substate, so re-treatment cannot be triggered on progression without restructuring the model; the assumption is instead bounded by a structural scenario that removes the second sequence entirely while holding survival at the trial estimate, giving a cost-side bound.

# Structural Parameters

```{r structural-table}
structural_table <- data.frame(
  Parameter = c("Cycle length", "Time horizon", "Cost discount rate",
                "Effect discount rate", "Willingness-to-pay threshold",
                "PSA sample size"),
  Value = c(
    paste0(cl, " years"),
    paste0(time_horizon, " weeks"),
    fmt_pct(dr),
    fmt_pct(dr),
    fmt_eur(WTP),
    format(n_samples, big.mark = ",")
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  structural_table,
  booktabs = TRUE,
  align = c("l", "r"),
  caption = "Structural model parameters"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.1
