---
title: "One-Way Sensitivity Analysis Report"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r owsa-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions if they exist (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/create_tornado_plot.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r setup-minimal-dependencies, include=FALSE}
# Define minimal dependencies needed for DSA
# These would normally come from scripts 02, 03, 06, 07

# Global variables (from script 02)
cl <- 1/52         # 1 week cycle
time_horizon <- 520 # 10 years in weeks
WTP <- 51000       # CE threshold (in Euros)
DSA_mult <- 0.2    # +/- 20% variations
dr <- 0.04         # discount rate
n_samples <- 5000  # Number of resampled models (for cache file naming)

# =============================================================================
# MODEL STRUCTURE DEFINITIONS (matches clinical_effectiveness.qmd)
# =============================================================================
# This report analyzes all three model structures:
# - Model A (joint): All biomarkers + all treatment interactions in one model
# - Model B (focused): Per-strategy formulas; CRP/TMB_BRAF with both interactions, TLR with TLR-only interaction
# - Model C (separate): Only one biomarker + its interaction per model

model_structures <- list(
  A = list(
    value = 0,
    name = "Joint (All-in-One)",
    label = "joint",
    formula = "~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx",
    desc = "All biomarkers and all treatment interactions in a single model"
  ),
  B = list(
    value = 1,
    name = "Focused",
    label = "focused",
    formula = "Per-strategy: CRP/TMB_BRAF use crp:Rx + tmb_braf:Rx; TLR uses tlr:Rx only",
    desc = "CRP/TMB_BRAF with both interactions; TLR with TLR-only interaction (adjusts for other biomarkers)"
  ),
  C = list(
    value = 2,
    name = "Separate",
    label = "separate",
    formula = "~ Age + sex + Rx + [biomarker]:Rx",
    desc = "Only one biomarker and its treatment interaction per model"
  )
)

# Check which sampling caches exist for each model structure
cache_status <- sapply(c(0, 1, 2), function(ms) {
  label <- c("joint", "focused", "separate")[ms + 1]
  cache_file <- here("data", "tidy",
                     paste0("sampling_models_n", n_samples, "_full_", label, ".rds"))
  file.exists(cache_file)
})
names(cache_status) <- c("A", "B", "C")

# Report cache status
cat("Sampling cache status:\n")
for (model_letter in c("A", "B", "C")) {
  status <- if (cache_status[model_letter]) "FOUND" else "MISSING"
  cat("  Model", model_letter, "(", model_structures[[model_letter]]$name, "):", status, "\n")
}

# Set default MODEL_STRUCTURE for fallback/mock data scenarios
MODEL_STRUCTURE <- 0  # 0 = joint, 1 = focused, 2 = separate

# Source model configurations (single source of truth)
source(here::here("scripts/R/functions/model_configs.R"))

# Time points (from script 07)
time_points <- seq(0, time_horizon, by = 1)
time_points_length <- length(time_points)

# Strategies and biomarkers from central config
strategies <- get_strategies()
biomarkers <- get_biomarkers()

# Parameter groups for sensitivity analysis (from 08_sampling.R)
# Define here for availability in fallback/mock data scenarios
param_groups <- list(
  drug_costs = c("c_drug_nivo", "c_drug_FLOX"),
  test_costs = c("c_test_CT", "c_test_blood", "c_test_NGS"),
  other_costs = c("c_other_visit", "c_other_baseline",
                  "c_other_follow", "c_other_last"),
  all_costs = c("c_drug_nivo", "c_drug_FLOX", "c_test_CT", "c_test_blood",
                "c_test_NGS", "c_other_visit", "c_other_baseline",
                "c_other_follow", "c_other_last"),
  utilities = c("u_np", "u_p"),
  prevalence = c("p_crp", "p_tlr", "p_tmb_braf")
)

# Create placeholder survival curves (exponential decay)
# These would normally come from the survival analysis pipeline
create_survival_curve <- function(median_survival, time_points) {
  # Convert median survival to rate parameter
  rate <- log(2) / median_survival
  survival_probs <- exp(-rate * time_points)
  return(pmax(survival_probs, 0.01))  # Minimum 1% survival
}

# Placeholder survival curves based on typical colorectal cancer data
control_os <- create_survival_curve(60, time_points)  # 60 weeks median OS
control_pfs <- create_survival_curve(25, time_points) # 25 weeks median PFS

# Biomarker positive (better outcomes with treatment)
crp_pos_os <- create_survival_curve(80, time_points)
crp_pos_pfs <- create_survival_curve(35, time_points)
tlr_pos_os <- create_survival_curve(75, time_points)
tlr_pos_pfs <- create_survival_curve(32, time_points)
tmb_braf_pos_os <- create_survival_curve(85, time_points)
tmb_braf_pos_pfs <- create_survival_curve(40, time_points)

# Biomarker negative (similar to control)
crp_neg_os <- control_os
crp_neg_pfs <- control_pfs
tlr_neg_os <- control_os
tlr_neg_pfs <- control_pfs
tmb_braf_neg_os <- control_os
tmb_braf_neg_pfs <- control_pfs

# Create treatment schedules
l_nivo <- rep(0, time_points_length)
l_nivo[c(5, 7, 13, 15, 29, 31, 37, 39)] <- 1  

l_FLOX_exp <- rep(0, time_points_length)
l_FLOX_exp[c(1, 3, 9, 11, 25, 27, 33, 35)] <- 1

l_FLOX_control <- rep(0, time_points_length)
l_FLOX_control[c(1, 3, 5, 7, 9, 11, 13, 15, 25, 27, 29, 31, 33, 35, 37, 39)] <- 1

l_CT <- rep(0, time_points_length)
l_CT[1] <- 1  # baseline
l_CT[seq(13, min(time_points_length, 13*40), by=12)] <- 1  # every 12 weeks

l_blood <- rep(0, time_points_length)
l_blood[1] <- 1  # baseline
l_blood[seq(5, min(time_points_length, 5*100), by=4)] <- 1  # every 4 weeks

l_visit <- rep(0, time_points_length)
l_visit[1] <- 1  # baseline
l_visit[which(l_nivo == 1 | l_FLOX_exp == 1 | l_FLOX_control == 1)] <- 1

# Create survival probability lists
p_os <- list(
  control_OS = control_os,  
  crp_pos_OS = crp_pos_os,
  crp_neg_OS = crp_neg_os,
  tlr_pos_OS = tlr_pos_os,
  tlr_neg_OS = tlr_neg_os,
  tmb_braf_pos_OS = tmb_braf_pos_os,
  tmb_braf_neg_OS = tmb_braf_neg_os,
  crp_weighted_OS = 0.3 * crp_pos_os + 0.7 * crp_neg_os,      # 30% prevalence
  tlr_weighted_OS = 0.25 * tlr_pos_os + 0.75 * tlr_neg_os,    # 25% prevalence
  tmb_braf_weighted_OS = 0.2 * tmb_braf_pos_os + 0.8 * tmb_braf_neg_os  # 20% prevalence
)

p_pfs <- list(
  control_PFS = control_pfs, 
  crp_pos_PFS = crp_pos_pfs,
  crp_neg_PFS = crp_neg_pfs,
  tlr_pos_PFS = tlr_pos_pfs,
  tlr_neg_PFS = tlr_neg_pfs,
  tmb_braf_pos_PFS = tmb_braf_pos_pfs,
  tmb_braf_neg_PFS = tmb_braf_neg_pfs,
  crp_weighted_PFS = 0.3 * crp_pos_pfs + 0.7 * crp_neg_pfs,    # 30% prevalence
  tlr_weighted_PFS = 0.25 * tlr_pos_pfs + 0.75 * tlr_neg_pfs,  # 25% prevalence
  tmb_braf_weighted_PFS = 0.2 * tmb_braf_pos_pfs + 0.8 * tmb_braf_neg_pfs  # 20% prevalence
)

# Comprehensive l_params_base with all necessary components
l_params_base <- list(
  # Time parameters
  cl = cl,
  time_horizon = time_horizon,
  
  # Discount rates
  dr_costs = dr,
  dr_effects = dr,
  
  # Utilities
  u_np = 0.9077, # utility in non-progressed state
  u_p = 0.9005,  # utility in progressed state
  
  # Drug costs
  c_drug_nivo = 13923,   # cost of nivolumab per administration
  c_drug_FLOX = 427,     # cost of FLOX per administration
  
  # Test costs
  c_test_CT = 386,       # cost of CT scan
  c_test_blood = 16,     # cost of blood tests (CRP, CBC, chem-7)
  c_test_NGS = 2518,     # cost of next-generation sequencing (for TMB/BRAF)
  
  # Other costs
  c_other_visit = 33,    # cost of standard outpatient visit
  c_other_baseline = 530, # cost of comprehensive baseline visit
  c_other_follow = 33,   # cost of follow-up visits
  c_other_last = 13803,  # cost of end-of-life care
  
  # Treatment schedules
  l_nivo = l_nivo,
  l_FLOX_exp = l_FLOX_exp,
  l_FLOX_control = l_FLOX_control,
  l_CT = l_CT,
  l_blood = l_blood,
  l_visit = l_visit,
  
  # Survival curves
  p_os = p_os,
  p_pfs = p_pfs,
  
  # Biomarker prevalence
  p_crp = 0.3,
  p_tlr = 0.25,
  p_tmb_braf = 0.2
)
```

```{r fix-calculate-outcomes, include=FALSE}
# Create a safer version of calculate_outcomes that handles edge cases
safe_calculate_outcomes <- function(params, p_pf, p_p, p_d, treatment_type, biomarker, v_dw_c, v_dw_e, cl) {
  # Number of cycles
  n_cycles <- length(p_pf)
  
  # Safety check for n_cycles
  if (n_cycles <= 0) {
    warning("Invalid n_cycles: ", n_cycles, ". Using default.")
    n_cycles <- 521  # Default to time_horizon + 1
    p_pf <- rep(0.5, n_cycles)
    p_p <- rep(0.3, n_cycles)
    p_d <- rep(0.2, n_cycles)
  }
  
  # Extend treatment schedules to match time horizon
  extend_schedule <- function(schedule, length_needed) {
    if (length(schedule) < length_needed) {
      extended <- c(schedule, rep(0, length_needed - length(schedule)))
      return(extended)
    }
    return(schedule[1:length_needed])
  }
  
  # Extend all treatment schedules
  l_nivo <- extend_schedule(params$l_nivo, n_cycles)
  l_FLOX_exp <- extend_schedule(params$l_FLOX_exp, n_cycles)
  l_FLOX_control <- extend_schedule(params$l_FLOX_control, n_cycles)
  l_CT <- extend_schedule(params$l_CT, n_cycles)
  l_blood <- extend_schedule(params$l_blood, n_cycles)
  l_visit <- extend_schedule(params$l_visit, n_cycles)
  
  # Define quarterly cycles for follow-up costs (safe version)
  if (n_cycles > 13) {
    quarterly_cycles <- seq(13, n_cycles, by = 13)
    quarterly_cycles <- quarterly_cycles[quarterly_cycles <= n_cycles]
  } else {
    quarterly_cycles <- c()  # No quarterly cycles if time horizon too short
  }
  
  # Calculate QALYs
  qalys_pf <- p_pf * params$u_np * cl
  qalys_p <- p_p * params$u_p * cl
  qalys_undiscounted <- qalys_pf + qalys_p
  qalys_discounted <- qalys_undiscounted * v_dw_e
  qalys_total <- sum(qalys_discounted, na.rm = TRUE)
  
  # Calculate costs based on treatment type
  if(treatment_type == "experimental") {
    # For biomarker positive: nivolumab + FLOX experimental regimen
    drug_costs <- (l_nivo * params$c_drug_nivo + l_FLOX_exp * params$c_drug_FLOX) * p_pf
  } else {
    # For control and biomarker negative: standard FLOX regimen
    drug_costs <- l_FLOX_control * params$c_drug_FLOX * p_pf
  }
  
  # Test costs (standard for all patients)
  test_costs <- l_CT * params$c_test_CT * p_pf + l_blood * params$c_test_blood * p_pf
  
  # Add biomarker test cost if applicable
  if(!is.null(biomarker)) {
    if(biomarker == "tmb_braf") {
      test_costs[1] <- test_costs[1] + params$c_test_NGS
    } else if(biomarker == "crp") {
      test_costs[1] <- test_costs[1] + params$c_test_blood
    } else if(biomarker == "tlr") {
      test_costs[1] <- test_costs[1] + params$c_test_CT
    }
  }
  
  # Visit costs
  visit_costs <- l_visit * params$c_other_visit * p_pf
  visit_costs[1] <- visit_costs[1] + params$c_other_baseline
  
  # Follow-up costs
  follow_up_costs <- rep(0, n_cycles)
  if(length(quarterly_cycles) > 0) {
    follow_up_costs[quarterly_cycles] <- params$c_other_follow * p_p[quarterly_cycles]
  }
  
  # End-of-life costs
  death_transitions <- c(p_d[1], diff(p_d))
  death_transitions[death_transitions < 0] <- 0  # Ensure non-negative
  end_of_life_costs <- death_transitions * params$c_other_last
  
  # Total costs
  costs_undiscounted <- drug_costs + test_costs + visit_costs + follow_up_costs + end_of_life_costs
  costs_discounted <- costs_undiscounted * v_dw_c
  costs_total <- sum(costs_discounted, na.rm = TRUE)
  
  return(list(
    qalys_total = qalys_total,
    costs_total = costs_total,
    qalys_undiscounted = qalys_undiscounted,
    costs_undiscounted = costs_undiscounted
  ))
}

# Replace the original function if it exists
if (exists("calculate_outcomes")) {
  calculate_outcomes <- safe_calculate_outcomes
}
```

```{r dsa-runner-function, include=FALSE}
# =============================================================================
# PARAMETERIZED DSA RUNNER FUNCTION
# =============================================================================
# This function runs DSA for a specific model structure by:
# 1. Setting MODEL_STRUCTURE to the target value
# 2. Re-sourcing the analysis scripts that depend on MODEL_STRUCTURE
# 3. Capturing and returning the DSA results

run_dsa_for_model <- function(target_structure, verbose = TRUE) {
  # Store original MODEL_STRUCTURE

  original_structure <- if (exists("MODEL_STRUCTURE")) MODEL_STRUCTURE else 0

  if (verbose) {
    label <- c("joint", "focused", "separate")[target_structure + 1]
    cat("Running DSA for MODEL_STRUCTURE =", target_structure, "(", label, ")...\n")
  }

  tryCatch({
    # Set target structure globally
    MODEL_STRUCTURE <<- target_structure

    # Source prerequisite scripts in order
    # These scripts respect the MODEL_STRUCTURE setting
    suppressMessages(suppressWarnings({
      source(here("scripts/R/analysis/02_setup_and_global_variables.R"))
      source(here("scripts/R/analysis/03_biomarker_strategies.R"))
      source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
      source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
      source(here("scripts/R/analysis/08_sampling.R"))
      source(here("scripts/R/analysis/11_DSA.R"))
    }))

    # Capture results
    results <- list(
      dsa_results = if (exists("dsa_results")) dsa_results else NULL,
      dsa_ranges = if (exists("dsa_ranges")) dsa_ranges else NULL,
      base_optimal = if (exists("base_optimal")) base_optimal else NULL,
      impact_summary = if (exists("impact_summary")) impact_summary else NULL,
      l_params_base = if (exists("l_params_base")) l_params_base else NULL,
      model_sensitivity_df = if (exists("model_sensitivity_df")) model_sensitivity_df else NULL,
      model_impact_summary = if (exists("model_impact_summary")) model_impact_summary else NULL
    )

    if (verbose) {
      cat("  DSA completed successfully.\n")
      if (!is.null(results$dsa_results)) {
        cat("  Results:", nrow(results$dsa_results), "rows\n")
      }
    }

    return(results)

  }, error = function(e) {
    if (verbose) {
      cat("  DSA FAILED:", e$message, "\n")
    }
    return(NULL)
  }, finally = {
    # Restore original MODEL_STRUCTURE
    MODEL_STRUCTURE <<- original_structure
  })
}
```

```{r dsa-analysis, include=FALSE}
# =============================================================================
# RUN DSA FOR ALL THREE MODEL STRUCTURES
# =============================================================================
# This chunk runs DSA for each model structure where the sampling cache exists.
# Results are stored in all_dsa_results list for use in subsequent sections.

# IMPORTANT: Sourcing analysis scripts runs rm(list=ls()) which clears the global
# environment. We use a protected environment to store key variables that must
# persist across source() calls.
.owsa_protected_env <- new.env(parent = emptyenv())

# Store the run_dsa_for_model function in protected environment (survives rm(list=ls()))
.owsa_protected_env$run_dsa_for_model <- run_dsa_for_model

# Define model_structures in the protected environment
.owsa_protected_env$model_structures <- list(
  A = list(
    value = 0,
    name = "Joint (All-in-One)",
    label = "joint",
    formula = "~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx",
    desc = "All biomarkers and all treatment interactions in a single model"
  ),
  B = list(
    value = 1,
    name = "Focused",
    label = "focused",
    formula = "Per-strategy: CRP/TMB_BRAF use crp:Rx + tmb_braf:Rx; TLR uses tlr:Rx only",
    desc = "CRP/TMB_BRAF with both interactions; TLR with TLR-only interaction (adjusts for other biomarkers)"
  ),
  C = list(
    value = 2,
    name = "Separate",
    label = "separate",
    formula = "~ Age + sex + Rx + [biomarker]:Rx",
    desc = "Only one biomarker and its treatment interaction per model"
  )
)

# Store n_samples in protected environment
.owsa_protected_env$n_samples <- 5000

# Check cache status and store in protected environment
.owsa_protected_env$cache_status <- sapply(c(0, 1, 2), function(ms) {
  label <- c("joint", "focused", "separate")[ms + 1]
  cache_file <- here("data", "tidy",
                     paste0("sampling_models_n", .owsa_protected_env$n_samples, "_full_", label, ".rds"))
  file.exists(cache_file)
})
names(.owsa_protected_env$cache_status) <- c("A", "B", "C")

# Initialize storage for all model results in protected environment
.owsa_protected_env$all_dsa_results <- list()

# Create convenience aliases (will be restored after each source() call)
model_structures <- .owsa_protected_env$model_structures
cache_status <- .owsa_protected_env$cache_status
n_samples <- .owsa_protected_env$n_samples
all_dsa_results <- .owsa_protected_env$all_dsa_results

# Define DSA parameters
dsa_pars <- c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS", "c_test_CT",
              "c_test_blood", "c_other_visit", "c_other_baseline",
              "c_other_follow", "c_other_last", "u_np", "u_p",
              "p_crp", "p_tlr", "p_tmb_braf")

# =============================================================================
# AUTO-GENERATE MISSING SAMPLING CACHES
# =============================================================================
# If any sampling caches are missing, generate them now before running DSA.
# This ensures the report always uses real data, never mock/fake data.
# NOTE: We use .owsa_protected_env to store variables that must survive rm(list=ls())

if (any(!.owsa_protected_env$cache_status)) {
  missing_models <- names(.owsa_protected_env$cache_status)[!.owsa_protected_env$cache_status]
  cat("\n=== Generating Missing Sampling Caches ===\n")
  cat("Missing caches for:", paste(missing_models, collapse = ", "), "\n\n")

  for (model_letter in missing_models) {
    # Store loop variable in protected environment (survives rm(list=ls()) in sourced scripts)
    .owsa_protected_env$current_model_letter <- model_letter
    target_structure <- .owsa_protected_env$model_structures[[model_letter]]$value
    label <- .owsa_protected_env$model_structures[[model_letter]]$label
    .owsa_protected_env$current_label <- label

    cat("Generating cache for Model", model_letter, "(", label, ")...\n")
    cat("  NOTE: This may take 20-60 minutes on first run.\n")

    tryCatch({
      # Set MODEL_STRUCTURE and source scripts to generate cache
      MODEL_STRUCTURE <<- target_structure
      suppressMessages(suppressWarnings({
        source(here("scripts/R/analysis/02_setup_and_global_variables.R"))
        source(here("scripts/R/analysis/03_biomarker_strategies.R"))
        source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
        source(here("scripts/R/analysis/08_sampling.R"))  # This generates/loads the cache
      }))

      # Verify cache was created (use protected env variables - originals cleared by rm(list=ls()))
      cache_file <- here("data", "tidy",
                         paste0("sampling_models_n", .owsa_protected_env$n_samples, "_full_",
                                .owsa_protected_env$current_label, ".rds"))
      if (file.exists(cache_file)) {
        .owsa_protected_env$cache_status[.owsa_protected_env$current_model_letter] <- TRUE
        cat("  SUCCESS: Cache created at", cache_file, "\n\n")
      } else {
        cat("  WARNING: Cache file not found after generation attempt\n\n")
      }
    }, error = function(e) {
      cat("  ERROR generating cache:", conditionMessage(e), "\n\n")
    })
  }

  # Restore convenience aliases from protected environment
  model_structures <- .owsa_protected_env$model_structures
  cache_status <- .owsa_protected_env$cache_status
  n_samples <- .owsa_protected_env$n_samples

  cat("=== Cache Generation Complete ===\n\n")
}

cat("\n=== Running DSA for All Model Structures ===\n\n")

# Run DSA for each model structure where cache exists (including newly generated)
# NOTE: run_dsa_for_model sources scripts that clear environment via rm(list=ls()),
# so we use .owsa_protected_env which is NOT cleared (objects starting with . are excluded from ls())

for (model_letter in c("A", "B", "C")) {
  # Store loop variable in protected environment (survives rm(list=ls()) in run_dsa_for_model)
  .owsa_protected_env$current_model_letter <- model_letter

  cat("Model", model_letter, "(", .owsa_protected_env$model_structures[[model_letter]]$name, "):\n")

  if (.owsa_protected_env$cache_status[model_letter]) {
    # Cache exists - run DSA for this model structure
    target_structure <- .owsa_protected_env$model_structures[[model_letter]]$value

    result <- .owsa_protected_env$run_dsa_for_model(target_structure, verbose = TRUE)

    # Restore model_letter from protected environment (may have been cleared by rm(list=ls()))
    model_letter <- .owsa_protected_env$current_model_letter

    # Store result in protected environment (survives rm(list=ls()) from next iteration)
    if (!is.null(result) && !is.null(result$dsa_results)) {
      .owsa_protected_env$all_dsa_results[[model_letter]] <- result
      cat("  Stored", nrow(result$dsa_results), "DSA results\n\n")
    } else {
      cat("  WARNING: DSA returned no results\n\n")
      .owsa_protected_env$all_dsa_results[[model_letter]] <- NULL
    }
  } else {
    # Cache still missing after generation attempt
    cat("  SKIPPED - cache unavailable\n\n")
    .owsa_protected_env$all_dsa_results[[model_letter]] <- NULL
  }
}

# Restore convenience aliases from protected environment for use in rest of document
model_structures <- .owsa_protected_env$model_structures
cache_status <- .owsa_protected_env$cache_status
n_samples <- .owsa_protected_env$n_samples
all_dsa_results <- .owsa_protected_env$all_dsa_results

# Count how many models have results
models_with_results <- sum(vapply(all_dsa_results, function(x) !is.null(x), logical(1)))
cat("=== DSA Complete:", models_with_results, "of 3 models have results ===\n")

# NO MOCK DATA - If no results available, the report sections will show appropriate messages
# The auto-generation above should have created any missing caches

# For backward compatibility with existing code that expects dsa_results
# Use Model A results as the default (or first available model)
for (model_letter in c("A", "B", "C")) {
  if (!is.null(all_dsa_results[[model_letter]])) {
    dsa_results <- all_dsa_results[[model_letter]]$dsa_results
    dsa_ranges <- all_dsa_results[[model_letter]]$dsa_ranges
    base_optimal <- all_dsa_results[[model_letter]]$base_optimal
    impact_summary <- all_dsa_results[[model_letter]]$impact_summary
    break
  }
}
```

```{r plot-functions, include=FALSE}
# Color palette for parameter groups
group_colors <- c(
  "drug_costs" = "#E41A1C",
  "test_costs" = "#377EB8",
  "other_costs" = "#4DAF4A",
  "utilities" = "#984EA3",
  "prevalence" = "#FF7F00",
  "survival_model" = "#A65628"  # Brown for survival model structural sensitivity
)

# Function to create tornado data for a specific strategy
create_tornado_data <- function(strategy_name, dsa_results) {
  strat_results <- dsa_results[dsa_results$Strategy == strategy_name &
                               dsa_results$Parameter != "base_case", ]

  tornado_data <- data.frame()
  for (param in unique(strat_results$Parameter)) {
    min_row <- strat_results[strat_results$Parameter == param &
                             strat_results$Value == "min", ]
    max_row <- strat_results[strat_results$Parameter == param &
                             strat_results$Value == "max", ]

    if (nrow(min_row) > 0 && nrow(max_row) > 0) {
      # Get group from dsa_results if available (with fallback)
      param_group <- "other"
      if ("group" %in% names(strat_results)) {
        grp <- unique(strat_results$group[strat_results$Parameter == param])
        if (length(grp) > 0 && !is.na(grp[1])) {
          param_group <- as.character(grp[1])
        }
      }

      # Safely extract NMB_diff values with NA handling
      min_diff <- if (!is.null(min_row$NMB_diff) && length(min_row$NMB_diff) > 0)
                    min_row$NMB_diff[1] else 0
      max_diff <- if (!is.null(max_row$NMB_diff) && length(max_row$NMB_diff) > 0)
                    max_row$NMB_diff[1] else 0

      # Handle NA values
      if (is.na(min_diff)) min_diff <- 0
      if (is.na(max_diff)) max_diff <- 0

      # Calculate Range as the MAXIMUM ABSOLUTE DEVIATION from base case
      # This is the standard tornado ordering metric - which parameter has the
      # largest potential single-sided impact on results
      max_abs_impact <- max(abs(min_diff), abs(max_diff))

      tornado_data <- rbind(tornado_data, data.frame(
        Parameter = param,
        Min_diff = min_diff,
        Max_diff = max_diff,
        Range = max_abs_impact,
        group = param_group,
        stringsAsFactors = FALSE
      ))
    }
  }

  if (nrow(tornado_data) > 0) {
    # Sort by Range in ascending order (smallest at bottom, largest at top after coord_flip)
    # Handle NA in Range by treating as 0
    tornado_data$Range[is.na(tornado_data$Range)] <- 0
    tornado_data <- tornado_data[order(tornado_data$Range, na.last = FALSE), ]
    tornado_data$Parameter <- factor(tornado_data$Parameter,
                                     levels = tornado_data$Parameter)
    return(tornado_data)
  }
  return(NULL)
}

# Function to create line plot data with real x-axis values
create_line_plot_data_real <- function(dsa_results, outcome_var = "NMB") {
  # Check required global variables exist
  if (!exists("dsa_ranges") || !exists("l_params_base")) {
    return(data.frame())
  }

  # Define parameter constraints for validation
  cost_params <- c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS", "c_test_CT",
                   "c_test_blood", "c_other_visit", "c_other_baseline",
                   "c_other_follow", "c_other_last")
  utility_params <- c("u_np", "u_p")
  prevalence_params <- c("p_crp", "p_tlr", "p_tmb_braf")

  # Get all data except base case
  strat_results <- dsa_results[dsa_results$Parameter != "base_case", ]

  # Get base case data
  base_results <- dsa_results[dsa_results$Parameter == "base_case", ]

  line_data <- data.frame()

  for (strategy in strategies) {
    for (param in unique(strat_results$Parameter)) {
      # Get min and max rows for this strategy and parameter
      min_row <- strat_results[strat_results$Strategy == strategy &
                               strat_results$Parameter == param &
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Strategy == strategy &
                               strat_results$Parameter == param &
                               strat_results$Value == "max", ]
      base_row <- base_results[base_results$Strategy == strategy, ]

      if (nrow(min_row) > 0 && nrow(max_row) > 0 && nrow(base_row) > 0) {
        # Get parameter values from dsa_ranges
        param_idx <- which(dsa_ranges$pars == param)
        if (length(param_idx) > 0) {
          min_val <- dsa_ranges$min[param_idx]
          max_val <- dsa_ranges$max[param_idx]

          # Safely get base value with fallback to midpoint
          base_val <- NULL
          if (!is.null(l_params_base) && param %in% names(l_params_base)) {
            base_val <- l_params_base[[param]]
          }
          if (is.null(base_val) || length(base_val) == 0) {
            base_val <- (min_val + max_val) / 2
          }

          # Apply parameter-specific bounds validation
          if (param %in% cost_params) {
            # Costs must be non-negative
            min_val <- max(0, min_val)
            max_val <- max(0, max_val)
            base_val <- max(0, base_val)
          } else if (param %in% utility_params) {
            # Utilities must be between 0 and 1
            min_val <- max(0, min(1, min_val))
            max_val <- max(0, min(1, max_val))
            base_val <- max(0, min(1, base_val))
          } else if (param %in% prevalence_params) {
            # Prevalence must be between 0 and 1
            min_val <- max(0, min(1, min_val))
            max_val <- max(0, min(1, max_val))
            base_val <- max(0, min(1, base_val))
          }

          # Skip parameters with no variation (min == max)
          if (abs(max_val - min_val) < 1e-10) {
            next
          }

          # Safely extract outcome values
          min_outcome <- if (outcome_var %in% names(min_row)) min_row[[outcome_var]][1] else NA
          base_outcome <- if (outcome_var %in% names(base_row)) base_row[[outcome_var]][1] else NA
          max_outcome <- if (outcome_var %in% names(max_row)) max_row[[outcome_var]][1] else NA

          # Only add if we have valid outcome values
          if (!is.na(min_outcome) && !is.na(base_outcome) && !is.na(max_outcome)) {
            param_data <- data.frame(
              Parameter = param,
              Strategy = strategy,
              ParamValue = c(min_val, base_val, max_val),
              Outcome = c(min_outcome, base_outcome, max_outcome)
            )
            line_data <- rbind(line_data, param_data)
          }
        }
      }
    }
  }

  return(line_data)
}

# Function to calculate nice y-axis limits (centered on data range, not starting at 0)
get_nice_ylimits <- function(data_values, expand_pct = 0.1) {
  min_val <- min(data_values, na.rm = TRUE)
  max_val <- max(data_values, na.rm = TRUE)
  range_val <- max_val - min_val

  # If all values are essentially the same, expand around the mean
  if (range_val < 1) {
    mean_val <- mean(data_values, na.rm = TRUE)
    return(c(mean_val * 0.9, mean_val * 1.1))
  }

  # Add padding to show full range
  padding <- range_val * expand_pct
  nice_min <- min_val - padding
  nice_max <- max_val + padding

  return(c(nice_min, nice_max))
}
```

```{r pagebreak-0, results='asis'}
cat("\\newpage\n")
```

# Overview

This one-way sensitivity analysis (OWSA) evaluates the robustness of the cost-effectiveness results for three biomarker-guided strategies (CRP, TLR, and TMB/BRAF) compared to standard of care for selecting metastatic microsatellite stable (MSS)/proficient mismatch repair (pMMR) colorectal cancer patients for immunotherapy treatment.

The analysis examines how variations in individual model parameters affect the net monetary benefit (NMB) and optimal strategy selection, providing insights into which parameters have the greatest impact on decision uncertainty.

**This report presents OWSA results for all three survival model structures:**

- **Model A (Joint)**: All biomarkers and treatment interactions in a single model
- **Model B (Focused)**: Per-strategy formulas; CRP/TMB_BRAF with both interactions, TLR with TLR-only interaction (adjusts for other biomarkers)
- **Model C (Separate)**: Only one biomarker and its treatment interaction per model

This report contains:

- **Technical Details**: Analysis specifications and methodology
- **Parameter Overview**: Description of the key parameters varied in the sensitivity analysis
- **Model A Results**: Tornado diagrams, line plots, and impact rankings for the Joint model
- **Model B Results**: Tornado diagrams, line plots, and impact rankings for the Focused model
- **Model C Results**: Tornado diagrams, line plots, and impact rankings for the Separate model
- **Cross-Model Comparison**: Assessment of robustness across model structures
- **Survival Model Structural Sensitivity**: Impact of parametric distribution choice

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Technical Details

## Analysis Specifications

**Model Structures Analyzed:**

```{r model-structures-table, results='asis'}
# Display model structure availability
model_status_df <- data.frame(
  Model = c("A", "B", "C"),
  Name = c("Joint (All-in-One)", "Focused", "Separate"),
  Formula = c(
    "Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx",
    "Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx",
    "Age + sex + Rx + [biomarker]:Rx"
  ),
  Status = sapply(c("A", "B", "C"), function(m) {
    if (!is.null(all_dsa_results[[m]])) "Results available" else "Cache missing"
  })
)

knitr::kable(model_status_df,
             booktabs = TRUE,
             align = c("c", "l", "l", "c"),
             col.names = c("Model", "Name", "Formula Pattern", "Status")) %>%
  kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position"))
```

**Model Configuration (per model structure):**

- Strategies evaluated: `r if(exists("strategies")) paste(length(strategies), "(", paste(strategies, collapse = ", "), ")") else "N/A"`
- Parameters tested: `r if(exists("dsa_pars")) length(dsa_pars) else "N/A"`
- Time horizon: `r time_horizon` weeks (`r round(time_horizon/52, 1)` years)
- Discount rate: `r paste0(dr * 100, "%")` per annum
- Willingness-to-pay threshold: `r scales::dollar(WTP, prefix = "\u20AC")`
- Parameter variation range: `r paste0("\u00B1", DSA_mult * 100, "%")`

**Parameter Constraints:**

- Utility parameters capped at maximum value of 1.0
- All cost parameters constrained to non-negative values

**Methodology:**

- One-way sensitivity analysis varies each parameter individually
- All other parameters held at base case values during each test
- DSA is run separately for each model structure to capture structural differences
- Net Monetary Benefit calculated as: NMB = Effect x WTP - Cost
- Tornado diagrams ordered by magnitude of parameter impact
- Line plots show outcome response across actual parameter values
- Three outcome measures: Net Monetary Benefit, Total Costs, and Total Effectiveness

## Computational Environment

**Analysis completed on:** `r format(Sys.Date(), "%B %d, %Y")`
**R version:** `r R.version.string`
**Repository:** ben-geisler/METIMMOX-1
**Report version:** 3.1

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Analysis Parameters

**Table 1: Parameters Included in One-Way Sensitivity Analysis**

```{r parameter-table}
if (exists("dsa_ranges") && nrow(dsa_ranges) > 0) {
  # Define all 15 parameters with descriptions and groups
  param_info <- data.frame(
    Parameter = c("c_drug_nivo", "c_drug_FLOX",
                  "c_test_NGS", "c_test_CT", "c_test_blood",
                  "c_other_visit", "c_other_baseline", "c_other_follow", "c_other_last",
                  "u_np", "u_p",
                  "p_crp", "p_tlr", "p_tmb_braf",
                  "Survival_Model"),
    Description = c("Nivolumab cost per administration",
                    "FLOX chemotherapy cost per administration",
                    "Next-generation sequencing (TMB/BRAF testing)",
                    "Computed tomography imaging",
                    "Blood test cost",
                    "Standard outpatient visit",
                    "Comprehensive baseline visit",
                    "Follow-up visit cost",
                    "End-of-life care costs",
                    "Utility - progression-free state",
                    "Utility - progressed disease state",
                    "CRP biomarker positive prevalence",
                    "TLR biomarker positive prevalence",
                    "TMB/BRAF biomarker positive prevalence",
                    "Parametric survival distribution (OS & PFS)"),
    Group = c("Drug costs", "Drug costs",
              "Test costs", "Test costs", "Test costs",
              "Other costs", "Other costs", "Other costs", "Other costs",
              "Utilities", "Utilities",
              "Prevalence", "Prevalence", "Prevalence",
              "Survival model"),
    stringsAsFactors = FALSE
  )

  # Merge with actual values from dsa_ranges
  param_descriptions <- merge(param_info, dsa_ranges, by.x = "Parameter", by.y = "pars", all.x = TRUE)

  # Add base values
  param_descriptions$Base <- sapply(param_descriptions$Parameter, function(x) {
    if (x %in% names(l_params_base)) l_params_base[[x]] else NA
  })

  # Reorder to match original order
  param_descriptions <- param_descriptions[match(param_info$Parameter, param_descriptions$Parameter), ]

  # Format numeric columns - handle different scales and NA values
  param_descriptions$Base_fmt <- sapply(1:nrow(param_descriptions), function(i) {
    if (param_descriptions$Parameter[i] == "Survival_Model") {
      # For survival model, show base distribution name if available
      if (exists("models") && !is.null(models$best_fit$os_distribution)) {
        return(models$best_fit$os_distribution)
      } else {
        return("gamma")
      }
    } else if (is.na(param_descriptions$Base[i])) {
      return("--")
    } else if (param_descriptions$Base[i] >= 100) {
      return(sprintf("%.0f", param_descriptions$Base[i]))
    } else {
      return(sprintf("%.2f", param_descriptions$Base[i]))
    }
  })

  param_descriptions$Min_fmt <- sapply(1:nrow(param_descriptions), function(i) {
    if (param_descriptions$Parameter[i] == "Survival_Model") {
      return("See section 7")
    } else if (is.na(param_descriptions$min[i])) {
      return("--")
    } else if (param_descriptions$min[i] >= 100) {
      return(sprintf("%.0f", param_descriptions$min[i]))
    } else {
      return(sprintf("%.2f", param_descriptions$min[i]))
    }
  })

  param_descriptions$Max_fmt <- sapply(1:nrow(param_descriptions), function(i) {
    if (param_descriptions$Parameter[i] == "Survival_Model") {
      return("See section 7")
    } else if (is.na(param_descriptions$max[i])) {
      return("--")
    } else if (param_descriptions$max[i] >= 100) {
      return(sprintf("%.0f", param_descriptions$max[i]))
    } else {
      return(sprintf("%.2f", param_descriptions$max[i]))
    }
  })

  # Create display table
  display_table <- param_descriptions[, c("Group", "Description", "Base_fmt", "Min_fmt", "Max_fmt")]

  knitr::kable(display_table,
               booktabs = TRUE,
               align = c("l", "l", "r", "r", "r"),
               col.names = c("Group", "Parameter Description", "Base", "Min (-20%)", "Max (+20%)"),
               row.names = FALSE) %>%
    kableExtra::column_spec(1, width = "2.2cm") %>%
    kableExtra::column_spec(2, width = "7cm") %>%
    kableExtra::column_spec(c(3,4,5), width = "1.8cm") %>%
    kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
    kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position"))

} else {
  cat("**Parameter information not available. Check DSA analysis completion.**\n")
}
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

```{r model-visualization-helpers, include=FALSE}
# =============================================================================
# HELPER FUNCTIONS FOR MODEL-SPECIFIC VISUALIZATIONS
# =============================================================================

# Create tornado plot for a specific model and strategy
create_model_tornado <- function(model_letter, strategy_name) {
  if (is.null(all_dsa_results[[model_letter]])) {
    return(NULL)
  }

  model_dsa <- all_dsa_results[[model_letter]]$dsa_results
  tornado_data <- create_tornado_data(strategy_name, model_dsa)

  if (is.null(tornado_data) || nrow(tornado_data) == 0) {
    return(NULL)
  }

  label_colors <- group_colors[as.character(tornado_data$group)]
  label_colors[is.na(label_colors)] <- "black"

  p <- ggplot(tornado_data) +
    geom_col(aes(x = Parameter, y = Min_diff),
             fill = "steelblue", alpha = 0.8, width = 0.7) +
    geom_col(aes(x = Parameter, y = Max_diff),
             fill = "darkred", alpha = 0.8, width = 0.7) +
    coord_flip() +
    geom_hline(yintercept = 0, linetype = "dashed", color = "black",
               linewidth = 0.8) +
    labs(x = "Model Parameters",
         y = "Change in NMB (EUR)") +
    scale_y_continuous(labels = scales::dollar_format(scale = 0.001,
                                                      suffix = "K",
                                                      prefix = "")) +
    theme_minimal() +
    theme(
      axis.text.y = element_text(size = 10, color = label_colors),
      axis.text.x = element_text(size = 10),
      plot.title = element_text(size = 14, face = "bold"),
      plot.subtitle = element_text(size = 12),
      axis.title = element_text(size = 12),
      panel.grid.minor = element_blank()
    )

  return(p)
}

# Create line plot for a specific model
create_model_line_plot <- function(model_letter, outcome_var = "NMB") {
  if (is.null(all_dsa_results[[model_letter]])) {
    return(NULL)
  }

  model_dsa <- all_dsa_results[[model_letter]]$dsa_results
  model_ranges <- all_dsa_results[[model_letter]]$dsa_ranges
  model_params <- all_dsa_results[[model_letter]]$l_params_base

  # Validate required data structures
  if (is.null(model_dsa) || is.null(model_ranges)) {
    return(NULL)
  }

  # Define parameter constraints for validation
  cost_params <- c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS", "c_test_CT",
                   "c_test_blood", "c_other_visit", "c_other_baseline",
                   "c_other_follow", "c_other_last")
  utility_params <- c("u_np", "u_p")
  prevalence_params <- c("p_crp", "p_tlr", "p_tmb_braf")

  # Custom line plot data function for this model
  strat_results <- model_dsa[model_dsa$Parameter != "base_case", ]
  base_results <- model_dsa[model_dsa$Parameter == "base_case", ]

  line_data <- data.frame()

  for (strategy in strategies) {
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Strategy == strategy &
                               strat_results$Parameter == param &
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Strategy == strategy &
                               strat_results$Parameter == param &
                               strat_results$Value == "max", ]
      base_row <- base_results[base_results$Strategy == strategy, ]

      if (nrow(min_row) > 0 && nrow(max_row) > 0 && nrow(base_row) > 0) {
        param_idx <- which(model_ranges$pars == param)
        if (length(param_idx) > 0) {
          min_val <- model_ranges$min[param_idx]
          max_val <- model_ranges$max[param_idx]

          # Safely get base value with fallback to midpoint
          base_val <- NULL
          if (!is.null(model_params) && param %in% names(model_params)) {
            base_val <- model_params[[param]]
          }
          if (is.null(base_val) || length(base_val) == 0) {
            # Fallback: use midpoint between min and max
            base_val <- (min_val + max_val) / 2
          }

          # Apply parameter-specific bounds validation
          if (param %in% cost_params) {
            # Costs must be non-negative
            min_val <- max(0, min_val)
            max_val <- max(0, max_val)
            base_val <- max(0, base_val)
          } else if (param %in% utility_params) {
            # Utilities must be between 0 and 1
            min_val <- max(0, min(1, min_val))
            max_val <- max(0, min(1, max_val))
            base_val <- max(0, min(1, base_val))
          } else if (param %in% prevalence_params) {
            # Prevalence must be between 0 and 1
            min_val <- max(0, min(1, min_val))
            max_val <- max(0, min(1, max_val))
            base_val <- max(0, min(1, base_val))
          }

          # Skip parameters with no variation (min == max)
          if (abs(max_val - min_val) < 1e-10) {
            next
          }

          # Safely extract outcome values
          min_outcome <- if (outcome_var %in% names(min_row)) min_row[[outcome_var]][1] else NA
          base_outcome <- if (outcome_var %in% names(base_row)) base_row[[outcome_var]][1] else NA
          max_outcome <- if (outcome_var %in% names(max_row)) max_row[[outcome_var]][1] else NA

          # Only add if we have valid outcome values
          if (!is.na(min_outcome) && !is.na(base_outcome) && !is.na(max_outcome)) {
            param_data <- data.frame(
              Parameter = param,
              Strategy = strategy,
              ParamValue = c(min_val, base_val, max_val),
              Outcome = c(min_outcome, base_outcome, max_outcome)
            )
            line_data <- rbind(line_data, param_data)
          }
        }
      }
    }
  }

  if (nrow(line_data) == 0) {
    return(NULL)
  }

  y_label <- switch(outcome_var,
    "NMB" = "Net Monetary Benefit (EUR, thousands)",
    "Cost" = "Total Cost (EUR, thousands)",
    "Effect" = "Total Effectiveness (QALYs)"
  )

  p <- ggplot(line_data, aes(x = ParamValue, y = Outcome, color = Strategy)) +
    geom_line(linewidth = 1.0, alpha = 0.8) +
    geom_point(size = 2) +
    facet_wrap(~ Parameter, scales = "free", ncol = 3) +
    scale_color_brewer(palette = "Set1", name = "Strategy") +
    labs(x = "Parameter Value", y = y_label) +
    theme_minimal() +
    theme(
      strip.text = element_text(size = 8, face = "bold"),
      legend.position = "bottom",
      panel.grid.minor = element_blank(),
      axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
      axis.text.y = element_text(size = 7)
    )

  if (outcome_var %in% c("NMB", "Cost")) {
    p <- p + scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K", prefix = ""))
  }

  return(p)
}

# Create impact rankings for a specific model
# IMPORTANT: Calculate rankings directly from DSA results using the same metric
# as tornado diagrams (max absolute deviation) for consistency
create_model_impact_table <- function(model_letter, top_n = 3) {
  if (is.null(all_dsa_results[[model_letter]])) {
    return(NULL)
  }

  model_dsa <- all_dsa_results[[model_letter]]$dsa_results
  if (is.null(model_dsa) || nrow(model_dsa) == 0) {
    return(NULL)
  }

  param_desc <- c(
    "c_drug_nivo" = "Nivolumab cost",
    "c_drug_FLOX" = "FLOX cost",
    "c_test_NGS" = "NGS testing",
    "c_test_CT" = "CT imaging",
    "c_test_blood" = "Blood tests",
    "c_other_visit" = "Visit cost",
    "c_other_baseline" = "Baseline visit",
    "c_other_follow" = "Follow-up",
    "c_other_last" = "End-of-life",
    "u_np" = "Utility (PF)",
    "u_p" = "Utility (P)",
    "p_crp" = "CRP prevalence",
    "p_tlr" = "TLR prevalence",
    "p_tmb_braf" = "TMB/BRAF prevalence"
  )

  # Calculate impact rankings using the same metric as tornado diagrams
  impact_data <- data.frame()

  for (strategy in strategies) {
    strat_results <- model_dsa[model_dsa$Strategy == strategy &
                               model_dsa$Parameter != "base_case", ]

    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param &
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param &
                               strat_results$Value == "max", ]

      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        min_diff <- if (!is.null(min_row$NMB_diff) && length(min_row$NMB_diff) > 0)
                      min_row$NMB_diff[1] else 0
        max_diff <- if (!is.null(max_row$NMB_diff) && length(max_row$NMB_diff) > 0)
                      max_row$NMB_diff[1] else 0

        if (is.na(min_diff)) min_diff <- 0
        if (is.na(max_diff)) max_diff <- 0

        # Use same metric as tornado: maximum absolute deviation
        max_abs_impact <- max(abs(min_diff), abs(max_diff))

        impact_data <- rbind(impact_data, data.frame(
          Strategy = strategy,
          Parameter = param,
          Impact = max_abs_impact,
          stringsAsFactors = FALSE
        ))
      }
    }
  }

  if (nrow(impact_data) == 0) {
    return(NULL)
  }

  # Rank parameters within each strategy and get top N
  impact_table <- impact_data %>%
    group_by(Strategy) %>%
    arrange(desc(Impact)) %>%
    mutate(Rank = row_number()) %>%
    filter(Rank <= top_n) %>%
    ungroup() %>%
    mutate(
      Strategy = case_when(
        Strategy == "control" ~ "Standard of Care",
        Strategy == "crp" ~ "CRP-guided",
        Strategy == "tlr" ~ "TLR-guided",
        Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
        TRUE ~ Strategy
      ),
      Description = param_desc[Parameter],
      Impact_fmt = sprintf("%.1f", Impact / 1000)
    ) %>%
    select(Strategy, Rank, Description, Impact_fmt) %>%
    arrange(Strategy, Rank)

  return(impact_table)
}
```

# Model A: Joint Model Results {#model-a}

Model A uses a **joint survival model** with all three biomarkers and all treatment-biomarker interactions included in a single model.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx`

```{r model-a-check, results='asis'}
if (is.null(all_dsa_results[["A"]])) {
  cat("\n**Results not available for Model A.** Sampling cache is missing.\n\n")
  cat("To generate the cache, run in R console:\n")
  cat("```r\n")
  cat("MODEL_STRUCTURE <- 0\n")
  cat("source('scripts/R/analysis/02_setup_and_global_variables.R')\n")
  cat("source('scripts/R/analysis/08_sampling.R')\n")
  cat("```\n")
}
```

```{r model-a-content, eval=!is.null(all_dsa_results[["A"]]), child=NULL}
```

## Tornado Diagrams - Model A

```{r tornado-a-control, fig.cap="Tornado Diagram - Model A: Standard of Care", fig.height=7, fig.width=9}
p <- create_model_tornado("A", "control")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-a-crp, fig.cap="Tornado Diagram - Model A: CRP-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("A", "crp")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-a-tlr, fig.cap="Tornado Diagram - Model A: TLR-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("A", "tlr")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-a-tmb, fig.cap="Tornado Diagram - Model A: TMB/BRAF-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("A", "tmb_braf")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

## Line Plot Sensitivity - Model A

```{r line-a-nmb, fig.cap="Model A: Parameter Sensitivity - Net Monetary Benefit", fig.height=12, fig.width=10}
p <- create_model_line_plot("A", "NMB")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r line-a-cost, fig.cap="Model A: Parameter Sensitivity - Total Costs", fig.height=12, fig.width=10}
p <- create_model_line_plot("A", "Cost")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r line-a-effect, fig.cap="Model A: Parameter Sensitivity - Total Effectiveness", fig.height=12, fig.width=10}
p <- create_model_line_plot("A", "Effect")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

## Parameter Impact Rankings - Model A

```{r impact-a}
impact_table <- create_model_impact_table("A")
if (!is.null(impact_table)) {
  knitr::kable(impact_table,
               booktabs = TRUE,
               align = c("l", "c", "l", "r"),
               col.names = c("Strategy", "Rank", "Parameter", "NMB Range (EUR K)"),
               caption = "Model A: Top 3 Most Influential Parameters by Strategy") %>%
    kableExtra::column_spec(1, width = "3cm") %>%
    kableExtra::column_spec(2, width = "1cm") %>%
    kableExtra::column_spec(3, width = "4cm") %>%
    kableExtra::column_spec(4, width = "2.5cm") %>%
    kableExtra::collapse_rows(columns = 1, valign = "top") %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
} else {
  cat("**Impact rankings not available for Model A**\n")
}
```

```{r pagebreak-model-a, results='asis'}
cat("\\newpage\n")
```

# Model B: Focused Model Results {#model-b}

Model B uses **focused survival models** with per-strategy formulas. CRP and TMB/BRAF strategies use both interaction terms (crp:Rx + tmb_braf:Rx), while TLR uses only the TLR-treatment interaction (tlr:Rx), adjusting for other biomarkers as main effects.

**Formulas:**

- CRP/TMB_BRAF: `Surv(time, event) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx`
- TLR: `Surv(time, event) ~ Age + sex + Rx + crp + tmb_braf + tlr:Rx`

```{r model-b-check, results='asis'}
if (is.null(all_dsa_results[["B"]])) {
  cat("\n**Results not available for Model B.** Sampling cache is missing.\n\n")
  cat("To generate the cache, run in R console:\n")
  cat("```r\n")
  cat("MODEL_STRUCTURE <- 1\n")
  cat("source('scripts/R/analysis/02_setup_and_global_variables.R')\n")
  cat("source('scripts/R/analysis/08_sampling.R')\n")
  cat("```\n")
}
```

## Tornado Diagrams - Model B

```{r tornado-b-control, fig.cap="Tornado Diagram - Model B: Standard of Care", fig.height=7, fig.width=9}
p <- create_model_tornado("B", "control")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-b-crp, fig.cap="Tornado Diagram - Model B: CRP-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("B", "crp")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-b-tlr, fig.cap="Tornado Diagram - Model B: TLR-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("B", "tlr")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-b-tmb, fig.cap="Tornado Diagram - Model B: TMB/BRAF-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("B", "tmb_braf")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

## Line Plot Sensitivity - Model B

```{r line-b-nmb, fig.cap="Model B: Parameter Sensitivity - Net Monetary Benefit", fig.height=12, fig.width=10}
p <- create_model_line_plot("B", "NMB")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r line-b-cost, fig.cap="Model B: Parameter Sensitivity - Total Costs", fig.height=12, fig.width=10}
p <- create_model_line_plot("B", "Cost")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r line-b-effect, fig.cap="Model B: Parameter Sensitivity - Total Effectiveness", fig.height=12, fig.width=10}
p <- create_model_line_plot("B", "Effect")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

## Parameter Impact Rankings - Model B

```{r impact-b}
impact_table <- create_model_impact_table("B")
if (!is.null(impact_table)) {
  knitr::kable(impact_table,
               booktabs = TRUE,
               align = c("l", "c", "l", "r"),
               col.names = c("Strategy", "Rank", "Parameter", "NMB Range (EUR K)"),
               caption = "Model B: Top 3 Most Influential Parameters by Strategy") %>%
    kableExtra::column_spec(1, width = "3cm") %>%
    kableExtra::column_spec(2, width = "1cm") %>%
    kableExtra::column_spec(3, width = "4cm") %>%
    kableExtra::column_spec(4, width = "2.5cm") %>%
    kableExtra::collapse_rows(columns = 1, valign = "top") %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
} else {
  cat("**Impact rankings not available for Model B**\n")
}
```

```{r pagebreak-model-b, results='asis'}
cat("\\newpage\n")
```

# Model C: Separate Model Results {#model-c}

Model C uses **separate survival models** with only one biomarker and its treatment interaction per model.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + [biomarker]:Rx`

```{r model-c-check, results='asis'}
if (is.null(all_dsa_results[["C"]])) {
  cat("\n**Results not available for Model C.** Sampling cache is missing.\n\n")
  cat("To generate the cache, run in R console:\n")
  cat("```r\n")
  cat("MODEL_STRUCTURE <- 2\n")
  cat("source('scripts/R/analysis/02_setup_and_global_variables.R')\n")
  cat("source('scripts/R/analysis/08_sampling.R')\n")
  cat("```\n")
}
```

## Tornado Diagrams - Model C

```{r tornado-c-control, fig.cap="Tornado Diagram - Model C: Standard of Care", fig.height=7, fig.width=9}
p <- create_model_tornado("C", "control")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-c-crp, fig.cap="Tornado Diagram - Model C: CRP-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("C", "crp")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-c-tlr, fig.cap="Tornado Diagram - Model C: TLR-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("C", "tlr")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r tornado-c-tmb, fig.cap="Tornado Diagram - Model C: TMB/BRAF-guided Strategy", fig.height=7, fig.width=9}
p <- create_model_tornado("C", "tmb_braf")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

## Line Plot Sensitivity - Model C

```{r line-c-nmb, fig.cap="Model C: Parameter Sensitivity - Net Monetary Benefit", fig.height=12, fig.width=10}
p <- create_model_line_plot("C", "NMB")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r line-c-cost, fig.cap="Model C: Parameter Sensitivity - Total Costs", fig.height=12, fig.width=10}
p <- create_model_line_plot("C", "Cost")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

```{r line-c-effect, fig.cap="Model C: Parameter Sensitivity - Total Effectiveness", fig.height=12, fig.width=10}
p <- create_model_line_plot("C", "Effect")
if (!is.null(p)) print(p) else cat("**No data available**\n")
```

## Parameter Impact Rankings - Model C

```{r impact-c}
impact_table <- create_model_impact_table("C")
if (!is.null(impact_table)) {
  knitr::kable(impact_table,
               booktabs = TRUE,
               align = c("l", "c", "l", "r"),
               col.names = c("Strategy", "Rank", "Parameter", "NMB Range (EUR K)"),
               caption = "Model C: Top 3 Most Influential Parameters by Strategy") %>%
    kableExtra::column_spec(1, width = "3cm") %>%
    kableExtra::column_spec(2, width = "1cm") %>%
    kableExtra::column_spec(3, width = "4cm") %>%
    kableExtra::column_spec(4, width = "2.5cm") %>%
    kableExtra::collapse_rows(columns = 1, valign = "top") %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
} else {
  cat("**Impact rankings not available for Model C**\n")
}
```

```{r pagebreak-model-c, results='asis'}
cat("\\newpage\n")
```

# Cross-Model Comparison {#cross-model}

This section compares the sensitivity analysis results across all three model structures to assess the robustness of conclusions.

## Optimal Strategy Comparison

```{r cross-model-optimal}
# Create comparison table of optimal strategies
comparison_df <- data.frame(
  Model = c("A (Joint)", "B (Focused)", "C (Separate)"),
  Structure = c(
    "All interactions in one model",
    "All biomarkers + one interaction",
    "One biomarker per model"
  ),
  Optimal_Strategy = sapply(c("A", "B", "C"), function(m) {
    if (!is.null(all_dsa_results[[m]])) {
      all_dsa_results[[m]]$base_optimal
    } else {
      "N/A"
    }
  }),
  stringsAsFactors = FALSE
)

knitr::kable(comparison_df,
             booktabs = TRUE,
             align = c("l", "l", "l"),
             col.names = c("Model", "Structure", "Optimal Strategy"),
             caption = "Base Case Optimal Strategy by Model Structure") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

## Top Parameter Comparison

```{r cross-model-params}
# Calculate top parameter for each model and strategy directly from DSA results
# Uses same metric as tornado diagrams: max(abs(min_diff), abs(max_diff))
top_params_comparison <- data.frame()

for (m in c("A", "B", "C")) {
  if (!is.null(all_dsa_results[[m]])) {
    model_dsa <- all_dsa_results[[m]]$dsa_results
    if (!is.null(model_dsa) && nrow(model_dsa) > 0) {

      for (strategy in strategies) {
        strat_results <- model_dsa[model_dsa$Strategy == strategy &
                                   model_dsa$Parameter != "base_case", ]

        # Calculate impact for each parameter
        param_impacts <- data.frame()
        for (param in unique(strat_results$Parameter)) {
          min_row <- strat_results[strat_results$Parameter == param &
                                   strat_results$Value == "min", ]
          max_row <- strat_results[strat_results$Parameter == param &
                                   strat_results$Value == "max", ]

          if (nrow(min_row) > 0 && nrow(max_row) > 0) {
            min_diff <- if (!is.null(min_row$NMB_diff)) min_row$NMB_diff[1] else 0
            max_diff <- if (!is.null(max_row$NMB_diff)) max_row$NMB_diff[1] else 0
            if (is.na(min_diff)) min_diff <- 0
            if (is.na(max_diff)) max_diff <- 0

            max_abs_impact <- max(abs(min_diff), abs(max_diff))
            param_impacts <- rbind(param_impacts, data.frame(
              Parameter = param, Impact = max_abs_impact
            ))
          }
        }

        if (nrow(param_impacts) > 0) {
          # Get top parameter for this strategy
          top_param <- param_impacts[which.max(param_impacts$Impact), ]
          top_params_comparison <- rbind(top_params_comparison, data.frame(
            Strategy = strategy,
            Parameter = top_param$Parameter,
            Impact = top_param$Impact,
            Model = m,
            stringsAsFactors = FALSE
          ))
        }
      }
    }
  }
}

if (nrow(top_params_comparison) > 0) {
  # Reshape to wide format
  wide_comparison <- top_params_comparison %>%
    mutate(
      Strategy = case_when(
        Strategy == "control" ~ "Standard of Care",
        Strategy == "crp" ~ "CRP-guided",
        Strategy == "tlr" ~ "TLR-guided",
        Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
        TRUE ~ Strategy
      ),
      Value = paste0(Parameter, " (", sprintf("%.1f", Impact/1000), "K)")
    ) %>%
    select(Strategy, Model, Value) %>%
    tidyr::pivot_wider(names_from = Model, values_from = Value, values_fill = "N/A")

  knitr::kable(wide_comparison,
               booktabs = TRUE,
               align = c("l", "l", "l", "l"),
               col.names = c("Strategy", "Model A", "Model B", "Model C"),
               caption = "Most Influential Parameter by Strategy and Model (with NMB Range in EUR K)") %>%
    kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position", "scale_down"))
} else {
  cat("**Cross-model comparison not available - insufficient data**\n")
}
```

## Robustness Assessment

```{r robustness-assessment, results='asis'}
# Count models with consistent optimal strategy
available_models <- vapply(c("A", "B", "C"), function(m) !is.null(all_dsa_results[[m]]), logical(1))
n_available <- sum(available_models)

if (n_available > 0) {
  optimal_strategies <- sapply(c("A", "B", "C"), function(m) {
    if (!is.null(all_dsa_results[[m]])) all_dsa_results[[m]]$base_optimal else NA
  })
  optimal_strategies <- optimal_strategies[!is.na(optimal_strategies)]

  if (length(unique(optimal_strategies)) == 1) {
    cat("**Robust Conclusion:** The optimal strategy (**", unique(optimal_strategies),
        "**) is consistent across all ", n_available, " model structures analyzed.\n\n", sep = "")
    cat("This indicates that the cost-effectiveness conclusions are robust to the choice of ")
    cat("survival model specification.\n")
  } else {
    cat("**Model Sensitivity Detected:** The optimal strategy varies across model structures.\n\n")
    cat("- This suggests structural uncertainty in the survival model specification affects conclusions.\n")
    cat("- Decision-makers should consider results from multiple model structures.\n")
  }
} else {
  cat("**Robustness assessment requires at least one model with available results.**\n")
}
```

```{r pagebreak-cross-model, results='asis'}
cat("\\newpage\n")
```

# Survival Model Structural Sensitivity

## Overview

This section examines how the choice of parametric survival distribution affects cost-effectiveness results. The base case uses the best-fitting distribution selected by AIC. All 9 fitted distributions are tested with the constraint that OS and PFS use the same distribution to ensure methodological consistency.

**Distributions tested:**

1. Exponential
2. Weibull
3. Weibull PH (proportional hazards)
4. Log-logistic
5. Log-normal
6. Gamma (base case)
7. Gompertz
8. Generalized Gamma
9. Generalized F

## NMB by Parametric Distribution

**Table 3: Net Monetary Benefit by Parametric Distribution and Strategy**

```{r model-sensitivity-table}
if (exists("model_sensitivity_df") && !is.null(model_sensitivity_df) && nrow(model_sensitivity_df) > 0) {

  # Reshape to wide format: rows = distributions, cols = strategies
  model_table <- model_sensitivity_df %>%
    select(Distribution, Strategy, NMB) %>%
    tidyr::pivot_wider(names_from = Strategy, values_from = NMB)

  # Round values
  numeric_cols <- sapply(model_table, is.numeric)
  model_table[numeric_cols] <- round(model_table[numeric_cols], 0)

  # Add ranking column for each strategy
  for (strat in strategies) {
    if (strat %in% names(model_table)) {
      model_table[[paste0(strat, "_rank")]] <- rank(-model_table[[strat]], na.last = "keep")
    }
  }

  # Display table
  knitr::kable(model_table,
               booktabs = TRUE,
               align = c("l", rep("r", ncol(model_table) - 1)),
               col.names = gsub("_rank", " Rank", names(model_table))) %>%
    kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position", "scale_down")) %>%
    kableExtra::row_spec(0, bold = TRUE)

} else {
  cat("**Model sensitivity results not available.** Run the prerequisite analysis scripts first.\n")
}
```

## Impact Summary

**Table 4: Survival Model Impact on NMB by Strategy**

```{r model-impact-table}
if (exists("model_impact_summary") && !is.null(model_impact_summary) && nrow(model_impact_summary) > 0) {

  # Format the impact summary table
  impact_display <- model_impact_summary %>%
    mutate(
      Strategy = case_when(
        Strategy == "control" ~ "Standard of Care",
        Strategy == "crp" ~ "CRP-guided",
        Strategy == "tlr" ~ "TLR-guided",
        Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
        TRUE ~ Strategy
      ),
      `Base NMB` = sprintf("%.0f", Base_NMB),
      `Min NMB` = sprintf("%.0f (%s)", Min_NMB, Min_Dist),
      `Max NMB` = sprintf("%.0f (%s)", Max_NMB, Max_Dist),
      `Range` = sprintf("%.0f", Range)
    ) %>%
    select(Strategy, `Base NMB`, `Min NMB`, `Max NMB`, Range)

  knitr::kable(impact_display,
               booktabs = TRUE,
               align = c("l", "r", "r", "r", "r")) %>%
    kableExtra::kable_styling(font_size = 10, latex_options = c("HOLD_position"))

} else {
  cat("**Model impact summary not available.**\n")
}
```

## Interpretation

The survival model choice represents **structural uncertainty** in the cost-effectiveness analysis. Different parametric distributions make different assumptions about how hazard rates change over time:

- **Exponential**: Constant hazard (no change over time)
- **Weibull/Gompertz**: Monotonically increasing or decreasing hazard
- **Log-logistic/Log-normal**: Non-monotonic hazard (can increase then decrease)
- **Gamma/Generalized Gamma**: Flexible hazard shapes

The range of NMB across distributions indicates sensitivity to these extrapolation assumptions. A large range suggests that long-term survival projections are particularly influential and that the choice of parametric form matters for decision-making.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 3.1