---
title: "One-Way Sensitivity Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03", "06", "07"),
  funs = c("report_format"),
  set_theme = FALSE
)

param_groups <- list(
  drug_costs = c("c_drug_nivo", "c_drug_FLOX"),
  test_costs = c("c_test_CRP", "c_test_NGS", "c_test_CT", "c_test_blood"),
  other_costs = c("c_other_visit", "c_other_baseline",
                  "c_other_follow", "c_other_last"),
  utilities = c("u_np", "u_p"),
  prevalence = c("p_crp", "p_tmb_braf")
)

invisible(capture.output(
  source(here::here("scripts/R/analysis/11_DSA.R"))
))

```

# Overview

This one-way sensitivity analysis varies economic parameters by the deterministic sensitivity-analysis range and summarizes the impact on net monetary benefit (NMB). The analysis uses the single joint economic model and the economic strategies returned by `get_strategies()`.

# Parameter Ranges

```{r parameter-ranges}
ranges_display <- dsa_ranges %>%
  mutate(
    Parameter = pars,
    Low = ifelse(grepl("^c_", pars), format_eur(min), sprintf("%.3f", min)),
    High = ifelse(grepl("^c_", pars), format_eur(max), sprintf("%.3f", max))
  ) %>%
  select(Parameter, Low, High)

knitr::kable(
  ranges_display,
  booktabs = TRUE,
  align = c("l", "r", "r"),
  caption = "One-way sensitivity-analysis parameter ranges"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Base Case and Optimal Strategy

```{r basecase}
base_display <- dsa_results %>%
  filter(Parameter == "base_case") %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Cost = format_eur(Cost),
    Effect = sprintf("%.3f", Effect),
    NMB = format_eur(NMB)
  ) %>%
  select(Strategy, Cost, Effect, NMB)

knitr::kable(
  base_display,
  booktabs = TRUE,
  align = c("l", "r", "r", "r"),
  col.names = c("Strategy", "Cost", "QALYs", "NMB"),
  caption = paste0("Base case at WTP = EUR ", format(WTP, big.mark = ","))
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Tornado Plots

```{r tornado-plots, fig.cap="Tornado plots by economic strategy", fig.height=8, fig.width=10}
par(mfrow = c(length(get_strategies()), 1), mar = c(4, 8, 3, 1))
for (strategy in get_strategies()) {
  create_tornado_plot(strategy, dsa_results)
}
par(mfrow = c(1, 1))
```

# Parameter Impact Ranking

```{r impact-ranking}
impact_display <- impact_summary %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Impact = format_eur(Impact)
  )

knitr::kable(
  impact_display,
  booktabs = TRUE,
  align = c("l", "r", "l", "r"),
  col.names = c("Strategy", "Rank", "Parameter", "NMB Range"),
  caption = "Top one-way sensitivity drivers by strategy"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r model-sensitivity}
if (exists("model_impact_summary") && !is.null(model_impact_summary)) {
  model_sens_display <- model_impact_summary %>%
    mutate(
      Strategy = strategy_label(Strategy),
      Base_NMB = format_eur(Base_NMB),
      Min_NMB = paste0(format_eur(Min_NMB), " (", Min_Dist, ")"),
      Max_NMB = paste0(format_eur(Max_NMB), " (", Max_Dist, ")"),
      Range = format_eur(Range)
    ) %>%
    select(Strategy, Base_NMB, Min_NMB, Max_NMB, Range)

  knitr::kable(
    model_sens_display,
    booktabs = TRUE,
    align = c("l", "r", "r", "r", "r"),
    col.names = c("Strategy", "Base NMB", "Lowest NMB", "Highest NMB", "Range"),
    caption = "Structural sensitivity to parametric survival distribution"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
} else {
  cat("Survival-distribution sensitivity results were not available.")
}
```

# Interpretation

The tornado plots and rankings show which parameters drive uncertainty in NMB for the single economic model. Survival distribution sensitivity is shown separately because it reflects extrapolation uncertainty rather than a scalar model input.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
