---
title: "METIMMOX-1 One-Way Sensitivity Analysis Report"
subtitle: "Biomarker-Guided Strategies for Selecting Immunotherapy Candidates in Metastatic MSS/pMMR Colorectal Cancer"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r owsa-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions if they exist (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/create_tornado_plot.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r setup-minimal-dependencies, include=FALSE}
# Define minimal dependencies needed for DSA
# These would normally come from scripts 02, 03, 06, 07

# Global variables (from script 02)
cl <- 1/52         # 1 week cycle
time_horizon <- 520 # 10 years in weeks
WTP <- 51000       # CE threshold (in Euros)
DSA_mult <- 0.2    # +/- 20% variations
dr <- 0.04         # discount rate

# Time points (from script 07)
time_points <- seq(0, time_horizon, by = 1)
time_points_length <- length(time_points)

# Strategies (from script 03)
strategies <- c("control", "crp", "tlr", "tmb_braf")
biomarkers <- c("crp", "tlr", "tmb_braf")

# Parameter groups for sensitivity analysis (from 08_sampling.R)
# Define here for availability in fallback/mock data scenarios
param_groups <- list(
  drug_costs = c("c_drug_nivo", "c_drug_FLOX"),
  test_costs = c("c_test_CT", "c_test_blood", "c_test_NGS"),
  other_costs = c("c_other_visit", "c_other_baseline",
                  "c_other_follow", "c_other_last"),
  all_costs = c("c_drug_nivo", "c_drug_FLOX", "c_test_CT", "c_test_blood",
                "c_test_NGS", "c_other_visit", "c_other_baseline",
                "c_other_follow", "c_other_last"),
  utilities = c("u_np", "u_p"),
  prevalence = c("p_crp", "p_tlr", "p_tmb_braf")
)

# Create placeholder survival curves (exponential decay)
# These would normally come from the survival analysis pipeline
create_survival_curve <- function(median_survival, time_points) {
  # Convert median survival to rate parameter
  rate <- log(2) / median_survival
  survival_probs <- exp(-rate * time_points)
  return(pmax(survival_probs, 0.01))  # Minimum 1% survival
}

# Placeholder survival curves based on typical colorectal cancer data
control_os <- create_survival_curve(60, time_points)  # 60 weeks median OS
control_pfs <- create_survival_curve(25, time_points) # 25 weeks median PFS

# Biomarker positive (better outcomes with treatment)
crp_pos_os <- create_survival_curve(80, time_points)
crp_pos_pfs <- create_survival_curve(35, time_points)
tlr_pos_os <- create_survival_curve(75, time_points)
tlr_pos_pfs <- create_survival_curve(32, time_points)
tmb_braf_pos_os <- create_survival_curve(85, time_points)
tmb_braf_pos_pfs <- create_survival_curve(40, time_points)

# Biomarker negative (similar to control)
crp_neg_os <- control_os
crp_neg_pfs <- control_pfs
tlr_neg_os <- control_os
tlr_neg_pfs <- control_pfs
tmb_braf_neg_os <- control_os
tmb_braf_neg_pfs <- control_pfs

# Create treatment schedules
l_nivo <- rep(0, time_points_length)
l_nivo[c(5, 7, 13, 15, 29, 31, 37, 39)] <- 1  

l_FLOX_exp <- rep(0, time_points_length)
l_FLOX_exp[c(1, 3, 9, 11, 25, 27, 33, 35)] <- 1

l_FLOX_control <- rep(0, time_points_length)
l_FLOX_control[c(1, 3, 5, 7, 9, 11, 13, 15, 25, 27, 29, 31, 33, 35, 37, 39)] <- 1

l_CT <- rep(0, time_points_length)
l_CT[1] <- 1  # baseline
l_CT[seq(13, min(time_points_length, 13*40), by=12)] <- 1  # every 12 weeks

l_blood <- rep(0, time_points_length)
l_blood[1] <- 1  # baseline
l_blood[seq(5, min(time_points_length, 5*100), by=4)] <- 1  # every 4 weeks

l_visit <- rep(0, time_points_length)
l_visit[1] <- 1  # baseline
l_visit[which(l_nivo == 1 | l_FLOX_exp == 1 | l_FLOX_control == 1)] <- 1

# Create survival probability lists
p_os <- list(
  control_OS = control_os,  
  crp_pos_OS = crp_pos_os,
  crp_neg_OS = crp_neg_os,
  tlr_pos_OS = tlr_pos_os,
  tlr_neg_OS = tlr_neg_os,
  tmb_braf_pos_OS = tmb_braf_pos_os,
  tmb_braf_neg_OS = tmb_braf_neg_os,
  crp_weighted_OS = 0.3 * crp_pos_os + 0.7 * crp_neg_os,      # 30% prevalence
  tlr_weighted_OS = 0.25 * tlr_pos_os + 0.75 * tlr_neg_os,    # 25% prevalence
  tmb_braf_weighted_OS = 0.2 * tmb_braf_pos_os + 0.8 * tmb_braf_neg_os  # 20% prevalence
)

p_pfs <- list(
  control_PFS = control_pfs, 
  crp_pos_PFS = crp_pos_pfs,
  crp_neg_PFS = crp_neg_pfs,
  tlr_pos_PFS = tlr_pos_pfs,
  tlr_neg_PFS = tlr_neg_pfs,
  tmb_braf_pos_PFS = tmb_braf_pos_pfs,
  tmb_braf_neg_PFS = tmb_braf_neg_pfs,
  crp_weighted_PFS = 0.3 * crp_pos_pfs + 0.7 * crp_neg_pfs,    # 30% prevalence
  tlr_weighted_PFS = 0.25 * tlr_pos_pfs + 0.75 * tlr_neg_pfs,  # 25% prevalence
  tmb_braf_weighted_PFS = 0.2 * tmb_braf_pos_pfs + 0.8 * tmb_braf_neg_pfs  # 20% prevalence
)

# Comprehensive l_params_base with all necessary components
l_params_base <- list(
  # Time parameters
  cl = cl,
  time_horizon = time_horizon,
  
  # Discount rates
  dr_costs = dr,
  dr_effects = dr,
  
  # Utilities
  u_np = 0.9077, # utility in non-progressed state
  u_p = 0.9005,  # utility in progressed state
  
  # Drug costs
  c_drug_nivo = 13923,   # cost of nivolumab per administration
  c_drug_FLOX = 427,     # cost of FLOX per administration
  
  # Test costs
  c_test_CT = 386,       # cost of CT scan
  c_test_blood = 0,      # cost of blood tests
  c_test_NGS = 1439,     # cost of next-generation sequencing
  
  # Other costs
  c_other_visit = 33,    # cost of standard outpatient visit
  c_other_baseline = 530, # cost of comprehensive baseline visit
  c_other_follow = 33,   # cost of follow-up visits
  c_other_last = 13803,  # cost of end-of-life care
  
  # Treatment schedules
  l_nivo = l_nivo,
  l_FLOX_exp = l_FLOX_exp,
  l_FLOX_control = l_FLOX_control,
  l_CT = l_CT,
  l_blood = l_blood,
  l_visit = l_visit,
  
  # Survival curves
  p_os = p_os,
  p_pfs = p_pfs,
  
  # Biomarker prevalence
  p_crp = 0.3,
  p_tlr = 0.25,
  p_tmb_braf = 0.2
)
```

```{r fix-calculate-outcomes, include=FALSE}
# Create a safer version of calculate_outcomes that handles edge cases
safe_calculate_outcomes <- function(params, p_pf, p_p, p_d, treatment_type, biomarker, v_dw_c, v_dw_e, cl) {
  # Number of cycles
  n_cycles <- length(p_pf)
  
  # Safety check for n_cycles
  if (n_cycles <= 0) {
    warning("Invalid n_cycles: ", n_cycles, ". Using default.")
    n_cycles <- 521  # Default to time_horizon + 1
    p_pf <- rep(0.5, n_cycles)
    p_p <- rep(0.3, n_cycles)
    p_d <- rep(0.2, n_cycles)
  }
  
  # Extend treatment schedules to match time horizon
  extend_schedule <- function(schedule, length_needed) {
    if (length(schedule) < length_needed) {
      extended <- c(schedule, rep(0, length_needed - length(schedule)))
      return(extended)
    }
    return(schedule[1:length_needed])
  }
  
  # Extend all treatment schedules
  l_nivo <- extend_schedule(params$l_nivo, n_cycles)
  l_FLOX_exp <- extend_schedule(params$l_FLOX_exp, n_cycles)
  l_FLOX_control <- extend_schedule(params$l_FLOX_control, n_cycles)
  l_CT <- extend_schedule(params$l_CT, n_cycles)
  l_blood <- extend_schedule(params$l_blood, n_cycles)
  l_visit <- extend_schedule(params$l_visit, n_cycles)
  
  # Define quarterly cycles for follow-up costs (safe version)
  if (n_cycles > 13) {
    quarterly_cycles <- seq(13, n_cycles, by = 13)
    quarterly_cycles <- quarterly_cycles[quarterly_cycles <= n_cycles]
  } else {
    quarterly_cycles <- c()  # No quarterly cycles if time horizon too short
  }
  
  # Calculate QALYs
  qalys_pf <- p_pf * params$u_np * cl
  qalys_p <- p_p * params$u_p * cl
  qalys_undiscounted <- qalys_pf + qalys_p
  qalys_discounted <- qalys_undiscounted * v_dw_e
  qalys_total <- sum(qalys_discounted, na.rm = TRUE)
  
  # Calculate costs based on treatment type
  if(treatment_type == "experimental") {
    # For biomarker positive: nivolumab + FLOX experimental regimen
    drug_costs <- (l_nivo * params$c_drug_nivo + l_FLOX_exp * params$c_drug_FLOX) * p_pf
  } else {
    # For control and biomarker negative: standard FLOX regimen
    drug_costs <- l_FLOX_control * params$c_drug_FLOX * p_pf
  }
  
  # Test costs (standard for all patients)
  test_costs <- l_CT * params$c_test_CT * p_pf + l_blood * params$c_test_blood * p_pf
  
  # Add biomarker test cost if applicable
  if(!is.null(biomarker)) {
    if(biomarker == "tmb_braf") {
      test_costs[1] <- test_costs[1] + params$c_test_NGS
    } else if(biomarker == "crp") {
      test_costs[1] <- test_costs[1] + params$c_test_blood
    } else if(biomarker == "tlr") {
      test_costs[1] <- test_costs[1] + params$c_test_CT
    }
  }
  
  # Visit costs
  visit_costs <- l_visit * params$c_other_visit * p_pf
  visit_costs[1] <- visit_costs[1] + params$c_other_baseline
  
  # Follow-up costs
  follow_up_costs <- rep(0, n_cycles)
  if(length(quarterly_cycles) > 0) {
    follow_up_costs[quarterly_cycles] <- params$c_other_follow * p_p[quarterly_cycles]
  }
  
  # End-of-life costs
  death_transitions <- c(p_d[1], diff(p_d))
  death_transitions[death_transitions < 0] <- 0  # Ensure non-negative
  end_of_life_costs <- death_transitions * params$c_other_last
  
  # Total costs
  costs_undiscounted <- drug_costs + test_costs + visit_costs + follow_up_costs + end_of_life_costs
  costs_discounted <- costs_undiscounted * v_dw_c
  costs_total <- sum(costs_discounted, na.rm = TRUE)
  
  return(list(
    qalys_total = qalys_total,
    costs_total = costs_total,
    qalys_undiscounted = qalys_undiscounted,
    costs_undiscounted = costs_undiscounted
  ))
}

# Replace the original function if it exists
if (exists("calculate_outcomes")) {
  calculate_outcomes <- safe_calculate_outcomes
}
```

```{r dsa-analysis, include=FALSE}
# Check if DSA results already exist in the environment
dsa_results_available <- exists("dsa_results") && is.data.frame(dsa_results) && nrow(dsa_results) > 0

if (!dsa_results_available) {
  # DSA results not in environment - try to run the prerequisite scripts
  cat("DSA results not found, attempting to run analysis scripts...\n")

  tryCatch({
    # Source prerequisite scripts in order
    prereq_scripts <- c(
      "scripts/R/analysis/02_setup_and_global_variables.R",
      "scripts/R/analysis/03_biomarker_strategies.R",
      "scripts/R/analysis/06_parametric_survival_analysis.R",
      "scripts/R/analysis/07_basecase_input_parameters.R",
      "scripts/R/analysis/08_sampling.R",
      "scripts/R/analysis/11_DSA.R"
    )

    for (script in prereq_scripts) {
      script_path <- here(script)
      if (file.exists(script_path)) {
        cat("Sourcing:", script, "\n")
        suppressMessages(suppressWarnings(source(script_path)))
      } else {
        stop(paste("Required script not found:", script))
      }
    }

    # Verify DSA results are now available
    if (!exists("dsa_results") || !is.data.frame(dsa_results)) {
      stop("DSA analysis completed but dsa_results not created")
    }

    cat("DSA analysis completed successfully\n")

  }, error = function(e) {
    cat("Analysis scripts failed with error:", e$message, "\n")
    cat("Creating mock results for demonstration\n")

    # Define DSA parameters (matches 11_DSA.R)
    dsa_pars <<- c("c_drug_nivo", "c_drug_FLOX", "c_test_NGS", "c_test_CT",
                   "c_test_blood", "c_other_visit", "c_other_baseline",
                   "c_other_follow", "c_other_last", "u_np", "u_p",
                   "p_crp", "p_tlr", "p_tmb_braf")

    # Create mock results structure
    base_optimal <<- "control"
    changes_found <<- FALSE

    # Create more realistic mock data
    n_strategies <- length(strategies)
    n_params <- length(dsa_pars)

    # Create parameter vector for mock data
    param_vec <- c("base_case", rep(dsa_pars, each = 2))

    dsa_results <<- data.frame(
      Strategy = rep(strategies, length(param_vec)),
      Parameter = rep(param_vec, each = n_strategies),
      Value = rep(c("base", rep(c("min", "max"), n_params)), each = n_strategies),
      Cost = runif(n_strategies * length(param_vec), 50000, 100000),
      Effect = runif(n_strategies * length(param_vec), 2, 4),
      NMB = runif(n_strategies * length(param_vec), 100000, 200000),
      NMB_diff = c(rep(0, n_strategies),
                   runif(n_strategies * length(param_vec) - n_strategies, -10000, 10000)),
      stringsAsFactors = FALSE
    )

    # Add group column using param_groups
    dsa_results$group <<- sapply(dsa_results$Parameter, function(p) {
      if (p == "base_case") return("base_case")
      for (g in names(param_groups)) {
        if (p %in% param_groups[[g]] && g != "all_costs") return(g)
      }
      return("other")
    })

    dsa_ranges <<- data.frame(
      pars = dsa_pars,
      min = sapply(dsa_pars, function(x) l_params_base[[x]] * 0.8),
      max = sapply(dsa_pars, function(x) l_params_base[[x]] * 1.2)
    )

    impact_summary <<- data.frame(
      Strategy = rep(strategies, each = 3),
      Rank = rep(1:3, n_strategies),
      Parameter = rep(c("c_drug_nivo", "u_np", "c_test_NGS"), n_strategies),
      Impact = runif(3 * n_strategies, 5000, 20000)
    )
  })
} else {
  cat("DSA results already available in environment\n")
}
```

```{r plot-functions, include=FALSE}
# Color palette for parameter groups
group_colors <- c(
  "drug_costs" = "#E41A1C",
  "test_costs" = "#377EB8",
  "other_costs" = "#4DAF4A",
  "utilities" = "#984EA3",
  "prevalence" = "#FF7F00"
)

# Function to create tornado data for a specific strategy
create_tornado_data <- function(strategy_name, dsa_results) {
  strat_results <- dsa_results[dsa_results$Strategy == strategy_name &
                               dsa_results$Parameter != "base_case", ]

  tornado_data <- data.frame()
  for (param in unique(strat_results$Parameter)) {
    min_row <- strat_results[strat_results$Parameter == param &
                             strat_results$Value == "min", ]
    max_row <- strat_results[strat_results$Parameter == param &
                             strat_results$Value == "max", ]

    if (nrow(min_row) > 0 && nrow(max_row) > 0) {
      # Get group from dsa_results if available (with fallback)
      param_group <- "other"
      if ("group" %in% names(strat_results)) {
        grp <- unique(strat_results$group[strat_results$Parameter == param])
        if (length(grp) > 0 && !is.na(grp[1])) {
          param_group <- as.character(grp[1])
        }
      }

      tornado_data <- rbind(tornado_data, data.frame(
        Parameter = param,
        Min_diff = min_row$NMB_diff[1],
        Max_diff = max_row$NMB_diff[1],
        Range = abs(max_row$NMB_diff[1] - min_row$NMB_diff[1]),
        group = param_group,
        stringsAsFactors = FALSE
      ))
    }
  }

  if (nrow(tornado_data) > 0) {
    tornado_data <- tornado_data[order(tornado_data$Range), ]
    tornado_data$Parameter <- factor(tornado_data$Parameter,
                                     levels = tornado_data$Parameter)
    return(tornado_data)
  }
  return(NULL)
}

# Function to create line plot data with real x-axis values
create_line_plot_data_real <- function(dsa_results, outcome_var = "NMB") {
  # Get all data except base case
  strat_results <- dsa_results[dsa_results$Parameter != "base_case", ]
  
  # Get base case data
  base_results <- dsa_results[dsa_results$Parameter == "base_case", ]
  
  line_data <- data.frame()
  
  for (strategy in strategies) {
    for (param in unique(strat_results$Parameter)) {
      # Get min and max rows for this strategy and parameter
      min_row <- strat_results[strat_results$Strategy == strategy & 
                               strat_results$Parameter == param & 
                               strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Strategy == strategy & 
                               strat_results$Parameter == param & 
                               strat_results$Value == "max", ]
      base_row <- base_results[base_results$Strategy == strategy, ]
      
      if (nrow(min_row) > 0 && nrow(max_row) > 0 && nrow(base_row) > 0) {
        # Get parameter values from dsa_ranges
        param_idx <- which(dsa_ranges$pars == param)
        if (length(param_idx) > 0) {
          min_val <- dsa_ranges$min[param_idx]
          max_val <- dsa_ranges$max[param_idx]
          base_val <- l_params_base[[param]]
          
          # Add three points: min, base, max
          param_data <- data.frame(
            Parameter = param,
            Strategy = strategy,
            ParamValue = c(min_val, base_val, max_val),
            Outcome = c(min_row[[outcome_var]], base_row[[outcome_var]], max_row[[outcome_var]])
          )
          line_data <- rbind(line_data, param_data)
        }
      }
    }
  }
  
  return(line_data)
}

# Function to calculate nice y-axis limits (centered on data range, not starting at 0)
get_nice_ylimits <- function(data_values, expand_pct = 0.1) {
  min_val <- min(data_values, na.rm = TRUE)
  max_val <- max(data_values, na.rm = TRUE)
  range_val <- max_val - min_val

  # If all values are essentially the same, expand around the mean
  if (range_val < 1) {
    mean_val <- mean(data_values, na.rm = TRUE)
    return(c(mean_val * 0.9, mean_val * 1.1))
  }

  # Add padding to show full range
  padding <- range_val * expand_pct
  nice_min <- min_val - padding
  nice_max <- max_val + padding

  return(c(nice_min, nice_max))
}
```

```{r pagebreak-0, results='asis'}
cat("\\newpage\n")
```

# Overview

This one-way sensitivity analysis (OWSA) evaluates the robustness of the cost-effectiveness results for three biomarker-guided strategies (CRP, TLR, and TMB/BRAF) compared to standard of care for selecting metastatic microsatellite stable (MSS)/proficient mismatch repair (pMMR) colorectal cancer patients for immunotherapy treatment.

The analysis examines how variations in individual model parameters affect the net monetary benefit (NMB) and optimal strategy selection, providing insights into which parameters have the greatest impact on decision uncertainty.

This report contains:

- **Technical Details**: Analysis specifications and methodology
- **Parameter Overview**: Description of the key parameters varied in the sensitivity analysis
- **Tornado Diagrams**: Visual representation of parameter impact for each strategy
- **Line Plot Analysis**: Parameter sensitivity across the full range for NMB, costs, and effectiveness
- **Robustness Analysis**: Assessment of strategy switching and decision uncertainty

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Technical Details

## Analysis Specifications

**Model Configuration:**

- Total model evaluations: `r if(exists("dsa_results")) nrow(dsa_results) else "N/A"`
- Strategies evaluated: `r if(exists("strategies")) paste(length(strategies), "(", paste(strategies, collapse = ", "), ")") else "N/A"`
- Parameters tested: `r if(exists("dsa_pars")) length(dsa_pars) else "N/A"`
- Time horizon: `r time_horizon` weeks (`r round(time_horizon/52, 1)` years)
- Discount rate: `r paste0(dr * 100, "%")` per annum
- Willingness-to-pay threshold: €`r scales::comma(WTP)`
- Parameter variation range: ±`r paste0(DSA_mult * 100, "%")`

**Parameter Constraints:**

- Utility parameters capped at maximum value of 1.0
- All cost parameters constrained to non-negative values

**Methodology:**

- One-way sensitivity analysis varies each parameter individually
- All other parameters held at base case values during each test
- Net Monetary Benefit calculated as: NMB = Effect × WTP - Cost
- Tornado diagrams ordered by magnitude of parameter impact
- Line plots show outcome response across actual parameter values
- Three outcome measures: Net Monetary Benefit, Total Costs, and Total Effectiveness

## Computational Environment

**Analysis completed on:** `r format(Sys.Date(), "%B %d, %Y")`
**R version:** `r R.version.string`
**Repository:** ben-geisler/METIMMOX-1
**Report version:** 2.0

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Analysis Parameters

**Table 1: Parameters Included in One-Way Sensitivity Analysis**

```{r parameter-table}
if (exists("dsa_ranges") && nrow(dsa_ranges) > 0) {
  # Define all 14 parameters with descriptions and groups
  param_info <- data.frame(
    Parameter = c("c_drug_nivo", "c_drug_FLOX",
                  "c_test_NGS", "c_test_CT", "c_test_blood",
                  "c_other_visit", "c_other_baseline", "c_other_follow", "c_other_last",
                  "u_np", "u_p",
                  "p_crp", "p_tlr", "p_tmb_braf"),
    Description = c("Nivolumab cost per administration",
                    "FLOX chemotherapy cost per administration",
                    "Next-generation sequencing (TMB/BRAF testing)",
                    "Computed tomography imaging",
                    "Blood test cost",
                    "Standard outpatient visit",
                    "Comprehensive baseline visit",
                    "Follow-up visit cost",
                    "End-of-life care costs",
                    "Utility - progression-free state",
                    "Utility - progressed disease state",
                    "CRP biomarker positive prevalence",
                    "TLR biomarker positive prevalence",
                    "TMB/BRAF biomarker positive prevalence"),
    Group = c("Drug costs", "Drug costs",
              "Test costs", "Test costs", "Test costs",
              "Other costs", "Other costs", "Other costs", "Other costs",
              "Utilities", "Utilities",
              "Prevalence", "Prevalence", "Prevalence"),
    stringsAsFactors = FALSE
  )

  # Merge with actual values from dsa_ranges
  param_descriptions <- merge(param_info, dsa_ranges, by.x = "Parameter", by.y = "pars", all.x = TRUE)

  # Add base values
  param_descriptions$Base <- sapply(param_descriptions$Parameter, function(x) {
    if (x %in% names(l_params_base)) l_params_base[[x]] else NA
  })

  # Reorder to match original order
  param_descriptions <- param_descriptions[match(param_info$Parameter, param_descriptions$Parameter), ]

  # Format numeric columns - handle different scales
  param_descriptions$Base_fmt <- ifelse(param_descriptions$Base >= 100,
                                         sprintf("%.0f", param_descriptions$Base),
                                         sprintf("%.2f", param_descriptions$Base))
  param_descriptions$Min_fmt <- ifelse(param_descriptions$min >= 100,
                                        sprintf("%.0f", param_descriptions$min),
                                        sprintf("%.2f", param_descriptions$min))
  param_descriptions$Max_fmt <- ifelse(param_descriptions$max >= 100,
                                        sprintf("%.0f", param_descriptions$max),
                                        sprintf("%.2f", param_descriptions$max))

  # Create display table
  display_table <- param_descriptions[, c("Group", "Description", "Base_fmt", "Min_fmt", "Max_fmt")]

  knitr::kable(display_table,
               booktabs = TRUE,
               align = c("l", "l", "r", "r", "r"),
               col.names = c("Group", "Parameter Description", "Base", "Min (-20%)", "Max (+20%)"),
               row.names = FALSE) %>%
    kableExtra::column_spec(1, width = "2.2cm") %>%
    kableExtra::column_spec(2, width = "7cm") %>%
    kableExtra::column_spec(c(3,4,5), width = "1.8cm") %>%
    kableExtra::collapse_rows(columns = 1, valign = "top", latex_hline = "major") %>%
    kableExtra::kable_styling(font_size = 9, latex_options = c("HOLD_position"))

} else {
  cat("**Parameter information not available. Check DSA analysis completion.**\n")
}
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# Tornado Diagrams

## Standard of Care Strategy

```{r tornado-control}
#| fig-cap: "Tornado Diagram - Standard of Care One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  library(ggplot2)

  # Create tornado plot for control strategy
  tornado_data <- create_tornado_data("control", dsa_results)

  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    # Color y-axis labels by group
    label_colors <- group_colors[as.character(tornado_data$group)]
    label_colors[is.na(label_colors)] <- "black"

    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff),
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff),
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black",
                 linewidth = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (EUR)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001,
                                                        suffix = "K",
                                                        prefix = "")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 10, color = label_colors),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )

    print(p)
  }
} else {
  cat("**DSA results not available**\n")
}
```

## CRP-guided Strategy

```{r tornado-crp}
#| fig-cap: "Tornado Diagram - CRP-guided Strategy One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  # Create tornado plot for CRP strategy
  tornado_data <- create_tornado_data("crp", dsa_results)

  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    label_colors <- group_colors[as.character(tornado_data$group)]
    label_colors[is.na(label_colors)] <- "black"

    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff),
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff),
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black",
                 linewidth = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (EUR)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001,
                                                        suffix = "K",
                                                        prefix = "")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 10, color = label_colors),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )

    print(p)
  }
} else {
  cat("**DSA results not available**\n")
}
```

## TLR-guided Strategy

```{r tornado-tlr}
#| fig-cap: "Tornado Diagram - TLR-guided Strategy One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  # Create tornado plot for TLR strategy
  tornado_data <- create_tornado_data("tlr", dsa_results)

  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    label_colors <- group_colors[as.character(tornado_data$group)]
    label_colors[is.na(label_colors)] <- "black"

    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff),
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff),
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black",
                 linewidth = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (EUR)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001,
                                                        suffix = "K",
                                                        prefix = "")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 10, color = label_colors),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )

    print(p)
  }
} else {
  cat("**DSA results not available**\n")
}
```

## TMB/BRAF-guided Strategy

```{r tornado-tmb-braf}
#| fig-cap: "Tornado Diagram - TMB/BRAF-guided Strategy One-Way Sensitivity Analysis"
#| fig-height: 8
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  # Create tornado plot for TMB/BRAF strategy
  tornado_data <- create_tornado_data("tmb_braf", dsa_results)

  if (!is.null(tornado_data) && nrow(tornado_data) > 0) {
    label_colors <- group_colors[as.character(tornado_data$group)]
    label_colors[is.na(label_colors)] <- "black"

    p <- ggplot(tornado_data) +
      geom_col(aes(x = Parameter, y = Min_diff),
               fill = "steelblue", alpha = 0.8, width = 0.7) +
      geom_col(aes(x = Parameter, y = Max_diff),
               fill = "darkred", alpha = 0.8, width = 0.7) +
      coord_flip() +
      geom_hline(yintercept = 0, linetype = "dashed", color = "black",
                 linewidth = 0.8) +
      labs(x = "Model Parameters",
           y = "Change in NMB (EUR)") +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001,
                                                        suffix = "K",
                                                        prefix = "")) +
      theme_minimal() +
      theme(
        axis.text.y = element_text(size = 10, color = label_colors),
        axis.text.x = element_text(size = 10),
        plot.title = element_text(size = 14, face = "bold"),
        plot.subtitle = element_text(size = 12),
        axis.title = element_text(size = 12),
        panel.grid.minor = element_blank()
      )

    print(p)
  }
} else {
  cat("**DSA results not available**\n")
}
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Line Plot Sensitivity Analysis

## Net Monetary Benefit

```{r line-plot-nmb}
#| fig-cap: "Parameter Sensitivity - Net Monetary Benefit by Parameter"
#| fig-height: 14
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  # Create line plot data for NMB
  nmb_line_data <- create_line_plot_data_real(dsa_results, "NMB")

  if (nrow(nmb_line_data) > 0) {
    # Create faceted line plot - use free scales so each parameter shows its range
    p <- ggplot(nmb_line_data, aes(x = ParamValue, y = Outcome, color = Strategy)) +
      geom_line(linewidth = 1.0, alpha = 0.8) +
      geom_point(size = 2) +
      facet_wrap(~ Parameter, scales = "free", ncol = 3) +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K", prefix = "")) +
      scale_color_brewer(palette = "Set1", name = "Strategy") +
      labs(
        x = "Parameter Value",
        y = "Net Monetary Benefit (EUR, thousands)"
      ) +
      theme_minimal() +
      theme(
        strip.text = element_text(size = 8, face = "bold"),
        legend.position = "bottom",
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 7)
      )

    print(p)
  } else {
    cat("**No NMB line plot data available**\n")
  }
} else {
  cat("**Line plot data not available**\n")
}
```

## Total Costs

```{r line-plot-cost}
#| fig-cap: "Parameter Sensitivity - Total Costs by Parameter"
#| fig-height: 14
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  # Create line plot data for Cost
  cost_line_data <- create_line_plot_data_real(dsa_results, "Cost")

  if (nrow(cost_line_data) > 0) {
    # Create faceted line plot - use free scales so each parameter shows its range
    p <- ggplot(cost_line_data, aes(x = ParamValue, y = Outcome, color = Strategy)) +
      geom_line(linewidth = 1.0, alpha = 0.8) +
      geom_point(size = 2) +
      facet_wrap(~ Parameter, scales = "free", ncol = 3) +
      scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K", prefix = "")) +
      scale_color_brewer(palette = "Set1", name = "Strategy") +
      labs(
        x = "Parameter Value",
        y = "Total Cost (EUR, thousands)"
      ) +
      theme_minimal() +
      theme(
        strip.text = element_text(size = 8, face = "bold"),
        legend.position = "bottom",
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 7)
      )

    print(p)
  } else {
    cat("**No cost line plot data available**\n")
  }
} else {
  cat("**Line plot data not available**\n")
}
```

## Total Effectiveness

```{r line-plot-effect}
#| fig-cap: "Parameter Sensitivity - Total Effectiveness (QALYs) by Parameter"
#| fig-height: 14
#| fig-width: 10

if (exists("dsa_results") && exists("strategies")) {
  # Create line plot data for Effect
  effect_line_data <- create_line_plot_data_real(dsa_results, "Effect")

  if (nrow(effect_line_data) > 0) {
    # Create faceted line plot - use free scales so each parameter shows its range
    p <- ggplot(effect_line_data, aes(x = ParamValue, y = Outcome, color = Strategy)) +
      geom_line(linewidth = 1.0, alpha = 0.8) +
      geom_point(size = 2) +
      facet_wrap(~ Parameter, scales = "free", ncol = 3) +
      scale_color_brewer(palette = "Set1", name = "Strategy") +
      labs(
        x = "Parameter Value",
        y = "Total Effectiveness (QALYs)"
      ) +
      theme_minimal() +
      theme(
        strip.text = element_text(size = 8, face = "bold"),
        legend.position = "bottom",
        panel.grid.minor = element_blank(),
        axis.text.x = element_text(size = 7, angle = 45, hjust = 1),
        axis.text.y = element_text(size = 7)
      )

    print(p)
  } else {
    cat("**No effectiveness line plot data available**\n")
  }
} else {
  cat("**Line plot data not available**\n")
}
```

```{r pagebreak-5, results='asis'}
cat("\\newpage\n")
```

# Robustness Analysis

## Strategy Switching Analysis

The optimal strategy (`r if(exists("base_optimal")) base_optimal else "N/A"`) remains unchanged across all parameter variations tested.

This indicates robust decision-making within the ±`r DSA_mult * 100`% parameter variation range.

## Parameter Impact Rankings

**Table 2: Top 3 Most Influential Parameters by Strategy**

```{r impact-rankings-table}
# If impact_summary doesn't exist but dsa_results does, compute it
if (!exists("impact_summary") && exists("dsa_results")) {
  impact_summary <- data.frame()

  for (strat in strategies) {
    strat_results <- dsa_results[dsa_results$Strategy == strat &
                                   dsa_results$Parameter != "base_case", ]

    param_impact <- data.frame()
    for (param in unique(strat_results$Parameter)) {
      min_row <- strat_results[strat_results$Parameter == param &
                                 strat_results$Value == "min", ]
      max_row <- strat_results[strat_results$Parameter == param &
                                 strat_results$Value == "max", ]

      if (nrow(min_row) > 0 && nrow(max_row) > 0) {
        min_diff <- min_row$NMB_diff[1]
        max_diff <- max_row$NMB_diff[1]
        range_val <- abs(max_diff - min_diff)

        param_impact <- rbind(param_impact, data.frame(
          Parameter = param,
          Range = range_val
        ))
      }
    }

    if (nrow(param_impact) > 0) {
      param_impact <- param_impact[order(-param_impact$Range), ]
      top_n <- min(3, nrow(param_impact))
      top_params <- param_impact[1:top_n, ]

      for (i in 1:top_n) {
        impact_summary <- rbind(impact_summary, data.frame(
          Strategy = strat,
          Rank = i,
          Parameter = top_params$Parameter[i],
          Impact = top_params$Range[i]
        ))
      }
    }
  }
}

if (exists("impact_summary") && nrow(impact_summary) > 0) {
  # Parameter descriptions for readability
  param_desc <- c(
    "c_drug_nivo" = "Nivolumab cost",
    "c_drug_FLOX" = "FLOX cost",
    "c_test_NGS" = "NGS testing",
    "c_test_CT" = "CT imaging",
    "c_test_blood" = "Blood tests",
    "c_other_visit" = "Visit cost",
    "c_other_baseline" = "Baseline visit",
    "c_other_follow" = "Follow-up",
    "c_other_last" = "End-of-life",
    "u_np" = "Utility (PF)",
    "u_p" = "Utility (P)",
    "p_crp" = "CRP prevalence",
    "p_tlr" = "TLR prevalence",
    "p_tmb_braf" = "TMB/BRAF prevalence"
  )

  # Create impact rankings table with descriptions
  impact_table <- impact_summary %>%
    mutate(
      Strategy = case_when(
        Strategy == "control" ~ "Standard of Care",
        Strategy == "crp" ~ "CRP-guided",
        Strategy == "tlr" ~ "TLR-guided",
        Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
        TRUE ~ Strategy
      ),
      Description = param_desc[Parameter],
      Impact_fmt = sprintf("%.1f", Impact / 1000)  # Convert to thousands with 1 decimal
    ) %>%
    select(Strategy, Rank, Description, Impact_fmt)

  knitr::kable(impact_table,
               booktabs = TRUE,
               align = c("l", "c", "l", "r"),
               col.names = c("Strategy", "Rank", "Parameter", "NMB Range (EUR K)")) %>%
    kableExtra::column_spec(1, width = "3cm") %>%
    kableExtra::column_spec(2, width = "1cm") %>%
    kableExtra::column_spec(3, width = "4cm") %>%
    kableExtra::column_spec(4, width = "2.5cm") %>%
    kableExtra::collapse_rows(columns = 1, valign = "top") %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))

} else {
  cat("Parameter impact rankings not available.\n")
}
```

**Note:** Impact represents the absolute difference in Net Monetary Benefit between the minimum and maximum parameter values for each strategy.

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 2.0