---
title: "Parametric Survival Models"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05"),
  funs = c("report_format"),
  packages = c(REPORT_PACKAGES, "survminer"),
  set_theme = FALSE
)

coef_table <- function(fit, outcome, distribution) {
  if (is.null(fit)) return(NULL)
  tab <- as.data.frame(fit$res)
  tab$Parameter <- rownames(tab)
  rownames(tab) <- NULL
  tab %>%
    transmute(
      Outcome = outcome,
      Distribution = distribution,
      Parameter,
      Estimate = est,
      SE = se,
      L95 = `L95%`,
      U95 = `U95%`
    )
}

surv_curve_df <- function(strategy, endpoint = c("os", "pfs")) {
  endpoint <- match.arg(endpoint)
  source_list <- if (endpoint == "os") l_params_base$p_os else l_params_base$p_pfs
  suffix <- if (endpoint == "os") "OS" else "PFS"

  data.frame(
    Week = time_points,
    Control = source_list[[paste0("control_", suffix)]],
    Positive = source_list[[paste0(strategy, "_pos_", suffix)]],
    Negative = source_list[[paste0(strategy, "_neg_", suffix)]],
    Weighted = source_list[[paste0(strategy, "_weighted_", suffix)]],
    Biomarker = biomarker_label(strategy),
    Endpoint = ifelse(endpoint == "os", "Overall survival", "Progression-free survival"),
    stringsAsFactors = FALSE
  ) %>%
    pivot_longer(cols = c(Control, Positive, Negative, Weighted),
                 names_to = "Curve", values_to = "Survival")
}
```

# Overview

This report documents the parametric survival models used in the economic evaluation. A single joint model is fitted for both endpoints:

```{r formula-table}
formula_df <- data.frame(
  Endpoint = c("Overall survival", "Progression-free survival"),
  Formula = c(
    paste(deparse(get_strategy_formula("crp", "os")), collapse = " "),
    paste(deparse(get_strategy_formula("crp", "pfs")), collapse = " ")
  ),
  stringsAsFactors = FALSE
)

knitr::kable(formula_df, booktabs = TRUE, align = c("l", "l"),
             caption = "Economic survival formulas") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "11cm")
```

# Distribution Selection

```{r os-ic}
os_ic <- models$full$os_ic %>%
  filter(!is.na(AIC)) %>%
  arrange(AIC) %>%
  mutate(
    delta_AIC = AIC - min(AIC),
    delta_BIC = BIC - min(BIC)
  )

knitr::kable(
  os_ic,
  booktabs = TRUE,
  digits = 2,
  align = "r",
  caption = "Overall survival distribution comparison"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r pfs-ic}
pfs_ic <- models$full$pfs_ic %>%
  filter(!is.na(AIC)) %>%
  arrange(AIC) %>%
  mutate(
    delta_AIC = AIC - min(AIC),
    delta_BIC = BIC - min(BIC)
  )

knitr::kable(
  pfs_ic,
  booktabs = TRUE,
  digits = 2,
  align = "r",
  caption = "Progression-free survival distribution comparison"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

# Coefficients

```{r coefficients}
coef_rows <- list(
  coef_table(models$full$os[[models$best_fit$os_distribution]], "OS", models$best_fit$os_distribution),
  coef_table(models$full$pfs[[models$best_fit$pfs_distribution]], "PFS", models$best_fit$pfs_distribution),
  coef_table(models$full$os$weibullph, "OS", "weibullph"),
  coef_table(models$full$pfs$weibullph, "PFS", "weibullph")
)

coef_display <- bind_rows(coef_rows) %>%
  mutate(
    Estimate = sprintf("%.4f", Estimate),
    SE = sprintf("%.4f", SE),
    `95% CI` = sprintf("[%.4f, %.4f]", L95, U95)
  ) %>%
  select(Outcome, Distribution, Parameter, Estimate, SE, `95% CI`)

knitr::kable(
  coef_display,
  booktabs = TRUE,
  align = c("l", "l", "l", "r", "r", "r"),
  caption = "Best-fit and Weibull PH coefficient estimates"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

# Strategy Survival Curves

```{r survival-curves, fig.cap="Predicted survival curves for economic biomarker strategies", fig.height=8, fig.width=10}
plot_data <- bind_rows(
  lapply(get_biomarkers(), surv_curve_df, endpoint = "os"),
  lapply(get_biomarkers(), surv_curve_df, endpoint = "pfs")
)

ggplot(plot_data, aes(x = Week, y = Survival, color = Curve, linetype = Curve)) +
  geom_line(linewidth = 0.8) +
  facet_grid(Biomarker ~ Endpoint) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = "Weeks", y = "Survival probability", color = NULL, linetype = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Summary

The economic model uses one joint formula for both CRP-guided and TMB/BRAF-guided strategies. Parametric distribution choice is selected by AIC for each endpoint, with Weibull PH retained as a familiar reference fit.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
