---
title: "Parametric Survival Modeling"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r para-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%",
  fig.keep = "last"  # Only keep the last plot from each chunk
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10)
  )
)
```

```{r load-analysis-results, include=FALSE}
# Set USE_BOTH_MODELS flag before loading scripts - FORCE to 1 for this report
USE_BOTH_MODELS <- 1

# Load analysis results if not already in environment
if (!exists("models")) {
  cat("Loading parametric survival analysis results...\n")

  # Load required scripts in order
  if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
  }

  if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
  }

  # Set USE_BOTH_MODELS again AFTER loading global variables to override it
  USE_BOTH_MODELS <- 1

  if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
  }
} else {
  # If models already exists, check if we need to refit
  if (is.null(models$no_age_sex)) {
    cat("Models without age/sex not found. Refitting with USE_BOTH_MODELS = 1...\n")
    USE_BOTH_MODELS <- 1
    if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
      suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
    }
  }
}

# Display model structure configuration
model_structure_name <- c("joint", "focused", "separate")[MODEL_STRUCTURE + 1]
cat("Model structure: MODEL_STRUCTURE =", MODEL_STRUCTURE, "(", model_structure_name, ")\n")
```

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Overview

This report presents parametric survival models fitted for the METIMMOX-1 economic evaluation. The models compare different biomarker strategies for overall survival (OS) and progression-free survival (PFS) outcomes. This analysis serves as the foundation for the cost-effectiveness evaluation by quantifying treatment effects across biomarker-defined patient subgroups.

# Population Characteristics including Biomarker Prevalences

```{r population-summary, results='asis'}
if (exists("ref_age") && exists("predictions") && exists("strategies_df")) {

  # Display population characteristics
  cat("Continuous variables:\n\n")
  cat("- Age (mean):", round(ref_age, 2), "years\n\n")

  cat("Categorical variables (most frequent category used):\n\n")
  cat("- Sex:", ref_sex, "(0=female, 1=male)\n")
  cat("- CRP:", ref_crp, "(0=negative, 1=positive)\n")
  cat("- TLR:", ref_tlr, "(0=negative, 1=positive)\n")
  cat("- TMB_BRAF:", ref_tmb_braf, "(0=negative, 1=positive)\n\n")

  cat("Biomarker prevalences in population:\n\n")
  for (strategy in strategies_df$id[strategies_df$id != "control"]) {
    prevalence <- strategies_df$prevalence[strategies_df$id == strategy]
    cat("- ", toupper(strategy), " positive:", round(prevalence * 100, 1), "%\n")
  }

  cat("\nData completeness:\n\n")
  cat("- Complete cases used:", nrow(data_complete), "of", nrow(data), "observations")
  cat(" (", round(nrow(data_complete)/nrow(data) * 100, 1), "%)\n\n")

} else {
  cat("Population characteristics not available. Run main analysis first.\n")
}
```

# Model Selection and Comparison

## Analysis Specifications

- **Distributions tested**:
  1. Exponential
  2. Weibull
  3. Weibull PH
  4. Gompertz
  5. Log-logistic
  6. Log-normal
  7. Generalized Gamma
  8. Gamma
  9. Generalized F Distribution

- **Covariate structure**: Full models with age and sex adjustment, treatment effects, and treatment-biomarker interactions:
  1. Age (continuous, years)
  2. Sex (categorical, 0=female, 1=male)
  3. Treatment assignment (Control arm vs Experimental arm)
  4. CRP biomarker status (0=negative, 1=positive)
  5. TLR biomarker status (0=negative, 1=positive)
  6. TMB_BRAF biomarker status (0=negative, 1=positive)
  7. Treatment × CRP interaction
  8. Treatment × TLR interaction
  9. Treatment × TMB_BRAF interaction

  Note: Models without age and sex adjustment were also considered but are not used in the primary analysis.

## Data Considerations

- **Complete case analysis**: Only patients with complete covariate data included
- **Reference patient**: Modal categories for categorical variables, mean for continuous variables
- **Time horizon**: Models fitted to observed follow-up period with extrapolation capability
- **Biomarker prevalences**: Taken from the METIMMOX-1 trial and may or may not reflect real world settings

## Model Validation and Goodness of Fit

- **Selection criterion**: AIC is more appropriate here because:
  - BIC penalizes model complexity more heavily (uses log(n) vs 2 for AIC)
  - For prediction purposes, we want the model that best balances fit and complexity
  - BIC tends to select overly simple models that might miss important biomarker interactions
  - AIC is better for predictive modeling while BIC is better for identifying the "true" model
- **Validation**: Visual comparison with Kaplan-Meier curves and clinical plausibility assessment

# Model Comparison

```{r model-comparison-os}
#| tbl-cap: "Overall Survival (OS) model comparison using AIC and BIC"

if (exists("models") && !is.null(models$full)) {

  # Overall Survival models - start with full model
  os_comparison <- data.frame(Structure = "Full Model", models$full$os_ic)

  # Add no_age_sex model only if it exists
  if (!is.null(models$no_age_sex) && !is.null(models$no_age_sex$os_ic)) {
    os_comparison <- rbind(
      os_comparison,
      data.frame(Structure = "w/o Age/Sex", models$no_age_sex$os_ic)
    )
  }

  os_comparison <- os_comparison %>%
    arrange(AIC) %>%
    mutate(
      AIC = round(AIC, 2),
      BIC = round(BIC, 2),
      `Delta AIC` = round(AIC - min(AIC, na.rm = TRUE), 2),
      Rank = rank(AIC, na.last = "keep")
    )

  # Mark best model
  if (exists("models") && !is.null(models$best_fit$os_aic)) {
    best_idx <- which.min(abs(os_comparison$AIC - models$best_fit$os_aic))
    if (length(best_idx) > 0) {
      os_comparison$Selected <- ""
      os_comparison$Selected[best_idx] <- "***"
    }
  }

  if (knitr::is_latex_output()) {
    kable(os_comparison, format = "latex", booktabs = TRUE, escape = FALSE) %>%
      kableExtra::kable_styling(font_size = 9, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(os_comparison, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("OS model comparison not available.\n")
}
```

```{r model-comparison-pfs}
#| tbl-cap: "Progression-Free Survival (PFS) model comparison using AIC and BIC"

if (exists("models") && !is.null(models$full)) {

  # Progression-Free Survival models - start with full model
  pfs_comparison <- data.frame(Structure = "Full Model", models$full$pfs_ic)

  # Add no_age_sex model only if it exists
  if (!is.null(models$no_age_sex) && !is.null(models$no_age_sex$pfs_ic)) {
    pfs_comparison <- rbind(
      pfs_comparison,
      data.frame(Structure = "w/o Age/Sex", models$no_age_sex$pfs_ic)
    )
  }

  pfs_comparison <- pfs_comparison %>%
    arrange(AIC) %>%
    mutate(
      AIC = round(AIC, 2),
      BIC = round(BIC, 2),
      `Delta AIC` = round(AIC - min(AIC, na.rm = TRUE), 2),
      Rank = rank(AIC, na.last = "keep")
    )

  # Mark best model
  if (exists("models") && !is.null(models$best_fit$pfs_aic)) {
    best_idx <- which.min(abs(pfs_comparison$AIC - models$best_fit$pfs_aic))
    if (length(best_idx) > 0) {
      pfs_comparison$Selected <- ""
      pfs_comparison$Selected[best_idx] <- "***"
    }
  }

  if (knitr::is_latex_output()) {
    kable(pfs_comparison, format = "latex", booktabs = TRUE, escape = FALSE) %>%
      kableExtra::kable_styling(font_size = 9, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(pfs_comparison, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("PFS model comparison not available.\n")
}
```

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Model Coefficients

## Overall Survival (OS) Model Coefficients

```{r os-coefficients, results='asis'}
#| tbl-cap: "Regression coefficients for gamma and Weibull PH OS parametric survival models"

if (exists("models") && !is.null(models$full)) {

  # Extract both gamma and Weibull PH model objects
  gamma_model <- models$full$os$gamma
  weibullph_model <- models$full$os$weibullph

  if (!is.null(gamma_model) && !is.null(weibullph_model)) {

    # Add model information first
    cat("Model comparison:\n\n")
    cat("- Best-fitting distribution:", models$best_fit$os_distribution, "\n")
    cat("- Covariate adjustment: Age and sex adjusted\n\n")

    # Get coefficient estimates from gamma model
    gamma_coef <- as.data.frame(gamma_model$res.t)
    gamma_table <- data.frame(
      Parameter = rownames(gamma_coef),
      Gamma_Est = round(gamma_coef$est, 4),
      Gamma_SE = round(gamma_coef$se, 4),
      Gamma_Exp = round(exp(gamma_coef$est), 4),
      stringsAsFactors = FALSE
    )

    # Get coefficient estimates from Weibull PH model
    weibullph_coef <- as.data.frame(weibullph_model$res.t)
    weibullph_table <- data.frame(
      Parameter = rownames(weibullph_coef),
      WeibullPH_Est = round(weibullph_coef$est, 4),
      WeibullPH_SE = round(weibullph_coef$se, 4),
      WeibullPH_Exp = round(exp(weibullph_coef$est), 4),
      stringsAsFactors = FALSE
    )

    # Merge tables
    coef_table <- merge(gamma_table, weibullph_table, by = "Parameter", all = TRUE)

    # Add units/notes to parameter names
    coef_table$Parameter <- gsub("^Age$", "Age (per year)", coef_table$Parameter)
    coef_table$Parameter <- gsub("^sex1$", "Sex (male vs female)", coef_table$Parameter)

    # Reorder columns for side-by-side comparison
    coef_table <- coef_table[, c("Parameter",
                                  "Gamma_Est", "Gamma_SE", "Gamma_Exp",
                                  "WeibullPH_Est", "WeibullPH_SE", "WeibullPH_Exp")]

    rownames(coef_table) <- NULL

    # Display coefficient table
    if (knitr::is_latex_output()) {
      kable(coef_table, format = "latex", booktabs = TRUE,
            longtable = FALSE, escape = TRUE,
            col.names = c("Parameter",
                         "Estimate", "SE", "exp(Est)",
                         "Estimate", "SE", "exp(Est)")) %>%
        kableExtra::kable_styling(font_size = 8,
                                 latex_options = c("striped", "HOLD_position", "scale_down"),
                                 full_width = TRUE) %>%
        kableExtra::add_header_above(c(" " = 1, "Gamma" = 3, "Weibull PH" = 3))
    } else {
      kable(coef_table, format = "html",
            col.names = c("Parameter",
                         "Estimate", "SE", "exp(Est)",
                         "Estimate", "SE", "exp(Est)")) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::add_header_above(c(" " = 1, "Gamma" = 3, "Weibull PH" = 3))
    }

  } else {
    cat("Gamma or Weibull PH models not available for OS.\n")
  }

} else {
  cat("OS model coefficients not available.\n")
}
```

## Progression-Free Survival (PFS) Model Coefficients

```{r pfs-coefficients, results='asis'}
#| tbl-cap: "Regression coefficients for gamma and Weibull PH PFS parametric survival models"

if (exists("models") && !is.null(models$full)) {

  # Extract both gamma and Weibull PH model objects
  gamma_model <- models$full$pfs$gamma
  weibullph_model <- models$full$pfs$weibullph

  if (!is.null(gamma_model) && !is.null(weibullph_model)) {

    # Add model information first
    cat("Model comparison:\n\n")
    cat("- Best-fitting distribution:", models$best_fit$pfs_distribution, "\n")
    cat("- Covariate adjustment: Age and sex adjusted\n\n")

    # Get coefficient estimates from gamma model
    gamma_coef <- as.data.frame(gamma_model$res.t)
    gamma_table <- data.frame(
      Parameter = rownames(gamma_coef),
      Gamma_Est = round(gamma_coef$est, 4),
      Gamma_SE = round(gamma_coef$se, 4),
      Gamma_Exp = round(exp(gamma_coef$est), 4),
      stringsAsFactors = FALSE
    )

    # Get coefficient estimates from Weibull PH model
    weibullph_coef <- as.data.frame(weibullph_model$res.t)
    weibullph_table <- data.frame(
      Parameter = rownames(weibullph_coef),
      WeibullPH_Est = round(weibullph_coef$est, 4),
      WeibullPH_SE = round(weibullph_coef$se, 4),
      WeibullPH_Exp = round(exp(weibullph_coef$est), 4),
      stringsAsFactors = FALSE
    )

    # Merge tables
    coef_table <- merge(gamma_table, weibullph_table, by = "Parameter", all = TRUE)

    # Add units/notes to parameter names
    coef_table$Parameter <- gsub("^Age$", "Age (per year)", coef_table$Parameter)
    coef_table$Parameter <- gsub("^sex1$", "Sex (male vs female)", coef_table$Parameter)

    # Reorder columns for side-by-side comparison
    coef_table <- coef_table[, c("Parameter",
                                  "Gamma_Est", "Gamma_SE", "Gamma_Exp",
                                  "WeibullPH_Est", "WeibullPH_SE", "WeibullPH_Exp")]

    rownames(coef_table) <- NULL

    # Display coefficient table
    if (knitr::is_latex_output()) {
      kable(coef_table, format = "latex", booktabs = TRUE,
            longtable = FALSE, escape = TRUE,
            col.names = c("Parameter",
                         "Estimate", "SE", "exp(Est)",
                         "Estimate", "SE", "exp(Est)")) %>%
        kableExtra::kable_styling(font_size = 8,
                                 latex_options = c("striped", "HOLD_position", "scale_down"),
                                 full_width = TRUE) %>%
        kableExtra::add_header_above(c(" " = 1, "Gamma" = 3, "Weibull PH" = 3))
    } else {
      kable(coef_table, format = "html",
            col.names = c("Parameter",
                         "Estimate", "SE", "exp(Est)",
                         "Estimate", "SE", "exp(Est)")) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
        kableExtra::add_header_above(c(" " = 1, "Gamma" = 3, "Weibull PH" = 3))
    }

  } else {
    cat("Gamma or Weibull PH models not available for PFS.\n")
  }

} else {
  cat("PFS model coefficients not available.\n")
}
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# Population Survival Curves

The following figures compare empirical Kaplan-Meier estimates with predicted survival curves from the selected parametric models. "Population" refers to different patient groups: biomarker-positive patients, biomarker-negative patients, or the entire population. For the control strategy, population curves represent all patients. For biomarker-guided strategies, population-level predictions are weighted by the prevalence of biomarker-positive and biomarker-negative patients in the sample.

```{r survival-functions, include=FALSE}
# Function to create population survival plots
create_population_plots <- function(models, data_complete, time_points, outcome_type = "OS") {

  # Get Kaplan-Meier estimates
  if (outcome_type == "OS") {
    km_fit <- survfit(Surv(OSwk, Death) ~ 1, data = data_complete)
  } else {
    km_fit <- survfit(Surv(PFSwk, Progression) ~ 1, data = data_complete)
  }

  # Create plotting data for KM
  km_data <- data.frame(
    time = km_fit$time,
    survival = km_fit$surv,
    model = "Kaplan-Meier",
    structure = "Observed"
  )

  plot_data <- km_data

  # Create representative patient
  ref_patient <- data.frame(
    Age = mean(data_complete$Age, na.rm = TRUE),
    sex = get_modal_category(data_complete$sex),
    Rx = get_modal_category(data_complete$Rx),
    crp = get_modal_category(data_complete$crp),
    tlr = get_modal_category(data_complete$tlr),
    tmb_braf = get_modal_category(data_complete$tmb_braf)
  )

  # Ensure factors have correct levels
  ref_patient$sex <- factor(ref_patient$sex, levels = levels(data_complete$sex))
  ref_patient$Rx <- factor(ref_patient$Rx, levels = levels(data_complete$Rx))
  ref_patient$crp <- factor(ref_patient$crp, levels = levels(data_complete$crp))
  ref_patient$tlr <- factor(ref_patient$tlr, levels = levels(data_complete$tlr))
  ref_patient$tmb_braf <- factor(ref_patient$tmb_braf, levels = levels(data_complete$tmb_braf))

  # Add parametric model predictions
  for (structure in c("full", "no_age_sex")) {
    if (!is.null(models[[structure]])) {
      structure_models <- models[[structure]]
      outcome_models <- if (outcome_type == "OS") structure_models$os else structure_models$pfs

      if (!is.null(outcome_models)) {
        for (dist_name in names(outcome_models)) {
          model_obj <- outcome_models[[dist_name]]

          if (inherits(model_obj, "flexsurvreg")) {
            tryCatch({
              model_obj$data <- data_complete

              pred_summary <- summary(model_obj, t = time_points, newdata = ref_patient, type = "survival")

              if (is.list(pred_summary) && length(pred_summary) > 0) {
                first_result <- pred_summary[[1]]

                if (is.data.frame(first_result) && all(c("time", "est") %in% names(first_result))) {
                  temp_data <- data.frame(
                    time = first_result$time,
                    survival = first_result$est,
                    model = dist_name,
                    structure = structure
                  )

                  plot_data <- rbind(plot_data, temp_data)
                }
              }

              model_obj$data <- NULL

            }, error = function(e) {
              # Handle errors silently
            })
          }
        }
      }
    }
  }

  return(plot_data)
}

# Function to add KM estimates for biomarker subgroups
add_biomarker_km <- function(data_complete, biomarker_col, outcome_type = "OS") {

  # Get treatment levels
  exp_rx <- levels(data_complete$Rx)[2]  # Experimental arm
  ctrl_rx <- levels(data_complete$Rx)[1]  # Control arm

  km_data_list <- list()

  # Biomarker positive + experimental treatment
  pos_exp <- data_complete[data_complete[[biomarker_col]] == 1 & data_complete$Rx == exp_rx, ]
  if (nrow(pos_exp) > 0) {
    if (outcome_type == "OS") {
      km_fit <- survfit(Surv(OSwk, Death) ~ 1, data = pos_exp)
    } else {
      km_fit <- survfit(Surv(PFSwk, Progression) ~ 1, data = pos_exp)
    }
    km_data_list$pos_exp <- data.frame(
      time = km_fit$time,
      survival = km_fit$surv,
      group = "Biomarker+ (Exp)"
    )
  }

  # Biomarker negative + control treatment
  neg_ctrl <- data_complete[data_complete[[biomarker_col]] == 0 & data_complete$Rx == ctrl_rx, ]
  if (nrow(neg_ctrl) > 0) {
    if (outcome_type == "OS") {
      km_fit <- survfit(Surv(OSwk, Death) ~ 1, data = neg_ctrl)
    } else {
      km_fit <- survfit(Surv(PFSwk, Progression) ~ 1, data = neg_ctrl)
    }
    km_data_list$neg_ctrl <- data.frame(
      time = km_fit$time,
      survival = km_fit$surv,
      group = "Biomarker- (Ctrl)"
    )
  }

  # Combine all KM data
  if (length(km_data_list) > 0) {
    km_combined <- do.call(rbind, km_data_list)
    return(km_combined)
  } else {
    return(NULL)
  }
}
```

## Model Validation: Comparison with Kaplan-Meier Estimates

These figures show how well each tested parametric distribution fits the observed data for the entire study population.

```{r os-full-plot}
#| fig-cap: "Overall survival curves for age- and sex-adjusted models compared to Kaplan-Meier estimates. All curves represent the entire study population using a representative patient profile (mean age, modal sex and biomarker values)."
#| fig-height: 6
#| fig-width: 8

if (exists("models") && exists("data_complete")) {

  # OS curves - full models
  os_full_data <- create_population_plots(models, data_complete, time_points, "OS")
  os_full_data <- os_full_data[os_full_data$structure %in% c("Observed", "full"), ]

  if (nrow(os_full_data) > 0) {
    p_os_full <- ggplot(os_full_data, aes(x = time, y = survival, color = model)) +
      geom_line(linewidth = 1.2) +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
      labs(x = "Time (weeks)", y = "Survival Probability",
           color = "Model") +
      theme(legend.position = "bottom")

    print(p_os_full)
  }
}
```

```{r pfs-full-plot}
#| fig-cap: "Progression-free survival curves for age- and sex-adjusted models compared to Kaplan-Meier estimates. All curves represent the entire study population using a representative patient profile (mean age, modal sex and biomarker values)."
#| fig-height: 6
#| fig-width: 8

if (exists("models") && exists("data_complete")) {

  # PFS curves - full models
  pfs_full_data <- create_population_plots(models, data_complete, time_points, "PFS")
  pfs_full_data <- pfs_full_data[pfs_full_data$structure %in% c("Observed", "full"), ]

  if (nrow(pfs_full_data) > 0) {
    p_pfs_full <- ggplot(pfs_full_data, aes(x = time, y = survival, color = model)) +
      geom_line(linewidth = 1.2) +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
      labs(x = "Time (weeks)", y = "Survival Probability",
           color = "Model") +
      theme(legend.position = "bottom")

    print(p_pfs_full)
  }
}
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Biomarker-Specific Results

The following figures compare survival outcomes between biomarker-positive and biomarker-negative patient subgroups for each biomarker strategy. These comparisons inform the potential value of biomarker-guided treatment selection. Kaplan-Meier estimates are shown for biomarker-positive patients receiving experimental treatment and biomarker-negative patients receiving control treatment, alongside parametric model predictions.

## CRP Biomarker Strategy

```{r crp-plots, fig.height=10, fig.width=8}
#| fig-cap: "Overall survival and progression-free survival for CRP biomarker-positive versus biomarker-negative patients. Colored curves show predicted survival from the selected parametric model. Black curves show Kaplan-Meier estimates for the treated (biomarker-positive, experimental arm, solid line) and untreated (biomarker-negative, control arm, dashed line) subgroups. Differences between curves indicate the predictive value of CRP status for treatment benefit."

if (exists("predictions") && exists("strategies_df") && exists("time_points")) {

  tryCatch({
    # Create OS plot
    biomarker_pred <- predictions[["crp"]]

    if (!is.null(biomarker_pred)) {
      # OS data - only biomarker+ and biomarker-
      plot_data_os <- data.frame(
        time = rep(time_points, 2),
        survival = c(
          biomarker_pred$biomarker_positive$os,
          biomarker_pred$biomarker_negative$os
        ),
        group = rep(c("CRP+", "CRP-"), each = length(time_points))
      )

      # Get KM data
      km_data_os <- add_biomarker_km(data_complete, "crp", "OS")

      # Create OS plot
      p_os <- ggplot(plot_data_os, aes(x = time, y = survival, color = group)) +
        geom_line(linewidth = 1.2) +
        scale_color_manual(values = c("CRP+" = "#E31A1C", "CRP-" = "#1F78B4"),
                          name = "Parametric Model") +
        scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
        scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
        labs(x = "Time (weeks)", y = "Overall Survival Probability") +
        theme_minimal() +
        theme(legend.position = "bottom")

      # Add KM estimates if available
      if (!is.null(km_data_os)) {
        p_os <- p_os +
          geom_step(data = km_data_os, aes(x = time, y = survival, linetype = group),
                   color = "black", linewidth = 0.8, inherit.aes = FALSE) +
          scale_linetype_manual(values = c("Biomarker+ (Exp)" = "solid",
                                          "Biomarker- (Ctrl)" = "dashed"),
                               name = "Kaplan-Meier")
      }

      # PFS data - only biomarker+ and biomarker-
      plot_data_pfs <- data.frame(
        time = rep(time_points, 2),
        survival = c(
          biomarker_pred$biomarker_positive$pfs,
          biomarker_pred$biomarker_negative$pfs
        ),
        group = rep(c("CRP+", "CRP-"), each = length(time_points))
      )

      # Get KM data
      km_data_pfs <- add_biomarker_km(data_complete, "crp", "PFS")

      # Create PFS plot
      p_pfs <- ggplot(plot_data_pfs, aes(x = time, y = survival, color = group)) +
        geom_line(linewidth = 1.2) +
        scale_color_manual(values = c("CRP+" = "#E31A1C", "CRP-" = "#1F78B4"),
                          name = "Parametric Model") +
        scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
        scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
        labs(x = "Time (weeks)", y = "Progression-Free Survival Probability") +
        theme_minimal() +
        theme(legend.position = "bottom")

      # Add KM estimates if available
      if (!is.null(km_data_pfs)) {
        p_pfs <- p_pfs +
          geom_step(data = km_data_pfs, aes(x = time, y = survival, linetype = group),
                   color = "black", linewidth = 0.8, inherit.aes = FALSE) +
          scale_linetype_manual(values = c("Biomarker+ (Exp)" = "solid",
                                          "Biomarker- (Ctrl)" = "dashed"),
                               name = "Kaplan-Meier")
      }

      # Combine plots
      gridExtra::grid.arrange(p_os, p_pfs, ncol = 1)
    }
  }, error = function(e) {
    cat("CRP plots not available\n")
    print(e)
  })
}
```

```{r pagebreak-5, results='asis'}
cat("\\newpage\n")
```

## TLR Biomarker Strategy

```{r tlr-plots, fig.height=10, fig.width=8}
#| fig-cap: "Overall survival and progression-free survival for TLR (target lesion reduction) biomarker-positive versus biomarker-negative patients. Colored curves show predicted survival from the selected parametric model. Black curves show Kaplan-Meier estimates for the treated (biomarker-positive, experimental arm, solid line) and untreated (biomarker-negative, control arm, dashed line) subgroups. Differences between curves indicate the predictive value of TLR status for treatment benefit."

if (exists("predictions") && exists("strategies_df") && exists("time_points")) {

  tryCatch({
    # Create OS plot
    biomarker_pred <- predictions[["tlr"]]

    if (!is.null(biomarker_pred)) {
      # OS data - only biomarker+ and biomarker-
      plot_data_os <- data.frame(
        time = rep(time_points, 2),
        survival = c(
          biomarker_pred$biomarker_positive$os,
          biomarker_pred$biomarker_negative$os
        ),
        group = rep(c("TLR+", "TLR-"), each = length(time_points))
      )

      # Get KM data
      km_data_os <- add_biomarker_km(data_complete, "tlr", "OS")

      # Create OS plot
      p_os <- ggplot(plot_data_os, aes(x = time, y = survival, color = group)) +
        geom_line(linewidth = 1.2) +
        scale_color_manual(values = c("TLR+" = "#E31A1C", "TLR-" = "#1F78B4"),
                          name = "Parametric Model") +
        scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
        scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
        labs(x = "Time (weeks)", y = "Overall Survival Probability") +
        theme_minimal() +
        theme(legend.position = "bottom")

      # Add KM estimates if available
      if (!is.null(km_data_os)) {
        p_os <- p_os +
          geom_step(data = km_data_os, aes(x = time, y = survival, linetype = group),
                   color = "black", linewidth = 0.8, inherit.aes = FALSE) +
          scale_linetype_manual(values = c("Biomarker+ (Exp)" = "solid",
                                          "Biomarker- (Ctrl)" = "dashed"),
                               name = "Kaplan-Meier")
      }

      # PFS data - only biomarker+ and biomarker-
      plot_data_pfs <- data.frame(
        time = rep(time_points, 2),
        survival = c(
          biomarker_pred$biomarker_positive$pfs,
          biomarker_pred$biomarker_negative$pfs
        ),
        group = rep(c("TLR+", "TLR-"), each = length(time_points))
      )

      # Get KM data
      km_data_pfs <- add_biomarker_km(data_complete, "tlr", "PFS")

      # Create PFS plot
      p_pfs <- ggplot(plot_data_pfs, aes(x = time, y = survival, color = group)) +
        geom_line(linewidth = 1.2) +
        scale_color_manual(values = c("TLR+" = "#E31A1C", "TLR-" = "#1F78B4"),
                          name = "Parametric Model") +
        scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
        scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
        labs(x = "Time (weeks)", y = "Progression-Free Survival Probability") +
        theme_minimal() +
        theme(legend.position = "bottom")

      # Add KM estimates if available
      if (!is.null(km_data_pfs)) {
        p_pfs <- p_pfs +
          geom_step(data = km_data_pfs, aes(x = time, y = survival, linetype = group),
                   color = "black", linewidth = 0.8, inherit.aes = FALSE) +
          scale_linetype_manual(values = c("Biomarker+ (Exp)" = "solid",
                                          "Biomarker- (Ctrl)" = "dashed"),
                               name = "Kaplan-Meier")
      }

      # Combine plots
      gridExtra::grid.arrange(p_os, p_pfs, ncol = 1)
    }
  }, error = function(e) {
    cat("TLR plots not available\n")
    print(e)
  })
}
```

```{r pagebreak-6, results='asis'}
cat("\\newpage\n")
```

## TMB_BRAF Biomarker Strategy

```{r tmb-braf-plots, fig.height=10, fig.width=8}
#| fig-cap: "Overall survival and progression-free survival for TMB_BRAF biomarker-positive versus biomarker-negative patients. Colored curves show predicted survival from the selected parametric model. Black curves show Kaplan-Meier estimates for the treated (biomarker-positive, experimental arm, solid line) and untreated (biomarker-negative, control arm, dashed line) subgroups. Differences between curves indicate the predictive value of TMB_BRAF status for treatment benefit."

if (exists("predictions") && exists("strategies_df") && exists("time_points")) {

  tryCatch({
    # Create OS plot
    biomarker_pred <- predictions[["tmb_braf"]]

    if (!is.null(biomarker_pred)) {
      # OS data - only biomarker+ and biomarker-
      plot_data_os <- data.frame(
        time = rep(time_points, 2),
        survival = c(
          biomarker_pred$biomarker_positive$os,
          biomarker_pred$biomarker_negative$os
        ),
        group = rep(c("TMB_BRAF+", "TMB_BRAF-"), each = length(time_points))
      )

      # Get KM data
      km_data_os <- add_biomarker_km(data_complete, "tmb_braf", "OS")

      # Create OS plot
      p_os <- ggplot(plot_data_os, aes(x = time, y = survival, color = group)) +
        geom_line(linewidth = 1.2) +
        scale_color_manual(values = c("TMB_BRAF+" = "#E31A1C", "TMB_BRAF-" = "#1F78B4"),
                          name = "Parametric Model") +
        scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
        scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
        labs(x = "Time (weeks)", y = "Overall Survival Probability") +
        theme_minimal() +
        theme(legend.position = "bottom")

      # Add KM estimates if available
      if (!is.null(km_data_os)) {
        p_os <- p_os +
          geom_step(data = km_data_os, aes(x = time, y = survival, linetype = group),
                   color = "black", linewidth = 0.8, inherit.aes = FALSE) +
          scale_linetype_manual(values = c("Biomarker+ (Exp)" = "solid",
                                          "Biomarker- (Ctrl)" = "dashed"),
                               name = "Kaplan-Meier")
      }

      # PFS data - only biomarker+ and biomarker-
      plot_data_pfs <- data.frame(
        time = rep(time_points, 2),
        survival = c(
          biomarker_pred$biomarker_positive$pfs,
          biomarker_pred$biomarker_negative$pfs
        ),
        group = rep(c("TMB_BRAF+", "TMB_BRAF-"), each = length(time_points))
      )

      # Get KM data
      km_data_pfs <- add_biomarker_km(data_complete, "tmb_braf", "PFS")

      # Create PFS plot
      p_pfs <- ggplot(plot_data_pfs, aes(x = time, y = survival, color = group)) +
        geom_line(linewidth = 1.2) +
        scale_color_manual(values = c("TMB_BRAF+" = "#E31A1C", "TMB_BRAF-" = "#1F78B4"),
                          name = "Parametric Model") +
        scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
        scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
        labs(x = "Time (weeks)", y = "Progression-Free Survival Probability") +
        theme_minimal() +
        theme(legend.position = "bottom")

      # Add KM estimates if available
      if (!is.null(km_data_pfs)) {
        p_pfs <- p_pfs +
          geom_step(data = km_data_pfs, aes(x = time, y = survival, linetype = group),
                   color = "black", linewidth = 0.8, inherit.aes = FALSE) +
          scale_linetype_manual(values = c("Biomarker+ (Exp)" = "solid",
                                          "Biomarker- (Ctrl)" = "dashed"),
                               name = "Kaplan-Meier")
      }

      # Combine plots
      gridExtra::grid.arrange(p_os, p_pfs, ncol = 1)
    }
  }, error = function(e) {
    cat("TMB_BRAF plots not available\n")
    print(e)
  })
}
```

```{r pagebreak-7, results='asis'}
cat("\\newpage\n")
```

# Strategy Comparison

The following figures compare all three biomarker-guided treatment strategies against the control (standard of care) strategy. These population-level predictions are weighted by biomarker prevalence to reflect expected outcomes in an unselected population.

```{r strategy-comparison-os}
#| fig-cap: "Overall survival comparison across all treatment strategies. Each curve represents the population-weighted expected OS for each strategy: Control (standard of care for all patients), CRP-guided treatment allocation, TLR-guided treatment allocation, and TMB_BRAF-guided treatment allocation. Differences between strategies reflect both the predictive accuracy of each biomarker and its prevalence in the population."
#| fig-height: 6
#| fig-width: 8

if (exists("predictions") && exists("time_points")) {

  # Prepare data for strategy comparison
  strategy_data_os <- data.frame()

  for (strategy in names(predictions)) {
    if (!is.null(predictions[[strategy]]$os)) {
      temp_df <- data.frame(
        time = time_points,
        survival = predictions[[strategy]]$os,
        strategy = toupper(strategy),
        stringsAsFactors = FALSE
      )
      strategy_data_os <- rbind(strategy_data_os, temp_df)
    }
  }

  if (nrow(strategy_data_os) > 0) {
    # Create plot
    p_strategy_os <- ggplot(strategy_data_os, aes(x = time, y = survival, color = strategy)) +
      geom_line(linewidth = 1.2) +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
      scale_color_manual(values = c("CONTROL" = "black",
                                     "CRP" = "#E69F00",
                                     "TLR" = "#56B4E9",
                                     "TMB_BRAF" = "#009E73")) +
      labs(x = "Time (weeks)",
           y = "Overall Survival Probability",
           color = "Strategy") +
      theme(legend.position = "bottom")

    print(p_strategy_os)
  } else {
    cat("Strategy comparison data not available for OS.\n")
  }
}
```

```{r strategy-comparison-pfs}
#| fig-cap: "Progression-free survival comparison across all treatment strategies. Each curve represents the population-weighted expected PFS for each strategy: Control (standard of care for all patients), CRP-guided treatment allocation, TLR-guided treatment allocation, and TMB_BRAF-guided treatment allocation. Differences between strategies reflect both the predictive accuracy of each biomarker and its prevalence in the population."
#| fig-height: 6
#| fig-width: 8

if (exists("predictions") && exists("time_points")) {

  # Prepare data for strategy comparison
  strategy_data_pfs <- data.frame()

  for (strategy in names(predictions)) {
    if (!is.null(predictions[[strategy]]$pfs)) {
      temp_df <- data.frame(
        time = time_points,
        survival = predictions[[strategy]]$pfs,
        strategy = toupper(strategy),
        stringsAsFactors = FALSE
      )
      strategy_data_pfs <- rbind(strategy_data_pfs, temp_df)
    }
  }

  if (nrow(strategy_data_pfs) > 0) {
    # Create plot
    p_strategy_pfs <- ggplot(strategy_data_pfs, aes(x = time, y = survival, color = strategy)) +
      geom_line(linewidth = 1.2) +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
      scale_color_manual(values = c("CONTROL" = "black",
                                     "CRP" = "#E69F00",
                                     "TLR" = "#56B4E9",
                                     "TMB_BRAF" = "#009E73")) +
      labs(x = "Time (weeks)",
           y = "Progression-Free Survival Probability",
           color = "Strategy") +
      theme(legend.position = "bottom")

    print(p_strategy_pfs)
  } else {
    cat("Strategy comparison data not available for PFS.\n")
  }
}
```

## Unadjusted Life-Years by Strategy

The following table shows unadjusted life-years (area under the survival curve) for each treatment strategy. Population-weighted values reflect the expected outcomes accounting for biomarker prevalence.

```{r strategy-life-years-table}
#| tbl-cap: "Unadjusted Life-Years by Treatment Strategy (Population-Weighted)"

if (exists("predictions") && exists("time_points")) {

  # Function to calculate life-years
  calc_ly <- function(survival_probs, time_points) {
    time_years <- time_points / 52
    n <- length(time_years)
    sum((survival_probs[-n] + survival_probs[-1]) / 2 * diff(time_years))
  }

  # Build strategy life-years table
  strategy_ly <- data.frame(
    Strategy = character(),
    `OS Life-Years` = numeric(),
    `PFS Life-Years` = numeric(),
    stringsAsFactors = FALSE,
    check.names = FALSE
  )

  for (strategy in c("control", "crp", "tlr", "tmb_braf")) {
    if (!is.null(predictions[[strategy]])) {
      os_ly <- calc_ly(predictions[[strategy]]$os, time_points)
      pfs_ly <- calc_ly(predictions[[strategy]]$pfs, time_points)

      strategy_ly <- rbind(strategy_ly, data.frame(
        Strategy = toupper(strategy),
        `OS Life-Years` = round(os_ly, 2),
        `PFS Life-Years` = round(pfs_ly, 2),
        stringsAsFactors = FALSE,
        check.names = FALSE
      ))
    }
  }

  # Add difference from control
  control_os <- strategy_ly$`OS Life-Years`[strategy_ly$Strategy == "CONTROL"]
  control_pfs <- strategy_ly$`PFS Life-Years`[strategy_ly$Strategy == "CONTROL"]

  strategy_ly <- strategy_ly %>%
    mutate(
      `OS Gain vs Control` = round(`OS Life-Years` - control_os, 2),
      `PFS Gain vs Control` = round(`PFS Life-Years` - control_pfs, 2)
    )

  if (knitr::is_latex_output()) {
    kable(strategy_ly, format = "latex", booktabs = TRUE) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(strategy_ly, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("Strategy life-years data not available.\n")
}
```

*Note: Life-years are calculated as the area under the survival curve (restricted mean survival time) over the model time horizon. These are unadjusted values without utility weighting. Population-weighted values account for biomarker prevalence in each strategy.*

```{r pagebreak-8, results='asis'}
cat("\\newpage\n")
```

# Sensitivity Analysis: Separate Biomarker Models

## Rationale

The **all-in-one model** includes all biomarkers and their treatment interaction terms simultaneously:

> Surv(time, event) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx + tlr:Rx + tmb_braf:Rx

When predicting survival for a biomarker-positive patient (e.g., CRP+), the model also activates OTHER biomarker main effects and interaction terms if that patient happens to be positive for those biomarkers. Since biomarkers are correlated (e.g., approximately 65% of patients are TLR-positive), this can attenuate or amplify the estimated treatment effect for a specific biomarker strategy.

This sensitivity analysis fits **separate biomarker-specific models** where each model only includes the biomarker of interest and its treatment interaction:

- CRP model: `~ Age + sex + Rx + crp + crp:Rx`
- TLR model: `~ Age + sex + Rx + tlr + tlr:Rx`
- TMB_BRAF model: `~ Age + sex + Rx + tmb_braf + tmb_braf:Rx`

All models use the **gamma distribution**, selected by AIC in the primary analysis.

```{r load-separate-models, include=FALSE}
# Source the separate biomarker models script
if (!exists("separate_models") || !exists("separate_predictions")) {
  cat("Fitting separate biomarker models...\n")
  suppressMessages(suppressWarnings(
    source(here("scripts/R/tests/fit_independent_biomarker_models.R"))
  ))
}
```

## Hazard Ratio Comparison

The following table compares the treatment × biomarker interaction hazard ratios between the all-in-one model and separate models.

**Interpretation**: HR < 1 indicates reduced hazard (improved survival) with experimental treatment in biomarker-positive patients. HR = 1.0 is the reference (no interaction effect), meaning biomarker-positive patients have the same treatment effect as biomarker-negative patients receiving control treatment.

```{r hr-comparison-table}
#| tbl-cap: "Treatment × Biomarker Interaction Hazard Ratios: All-in-One vs Separate Models"

if (exists("coef_comparison")) {

  # Reshape for better display
  hr_table <- coef_comparison %>%
    mutate(
      HR_CI = sprintf("%.3f (%.3f-%.3f)", HR, HR_Lower, HR_Upper)
    ) %>%
    select(Biomarker, Outcome, Model_Type, HR_CI) %>%
    pivot_wider(
      names_from = Model_Type,
      values_from = HR_CI
    )

  if (knitr::is_latex_output()) {
    kable(hr_table, format = "latex", booktabs = TRUE,
          col.names = c("Biomarker", "Outcome", "All-in-One", "Separate")) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(hr_table, format = "html",
          col.names = c("Biomarker", "Outcome", "All-in-One", "Separate")) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("Coefficient comparison not available.\n")
}
```

```{r pagebreak-9, results='asis'}
cat("\\newpage\n")
```

## Biomarker-Positive vs. Biomarker-Negative Subgroups

The following figures compare survival predictions between biomarker-positive and biomarker-negative subgroups for each biomarker strategy, using both the all-in-one model and separate models. Control strategy and Kaplan-Meier estimates are shown for reference.

```{r survival-comparison-os, fig.height=10, fig.width=10}
#| fig-cap: "Overall survival: Biomarker-positive vs. biomarker-negative vs. control. Solid lines: All-in-One model. Dashed lines: Separate model. Red: Biomarker-positive. Blue: Biomarker-negative. Gray dotted: Control. Black step lines: Kaplan-Meier estimates."

if (exists("predictions") && exists("separate_predictions") && exists("time_points")) {

  # Create a list to store plots for each biomarker
  plot_list <- list()

  for (biomarker in c("crp", "tlr", "tmb_braf")) {

    # Prepare parametric model data
    model_data <- data.frame(
      time = rep(time_points, 4),
      survival = c(
        predictions[[biomarker]]$biomarker_positive$os,
        predictions[[biomarker]]$biomarker_negative$os,
        separate_predictions[[biomarker]]$biomarker_positive$os,
        separate_predictions[[biomarker]]$biomarker_negative$os
      ),
      model = rep(c("All-in-One", "All-in-One", "Separate", "Separate"), each = length(time_points)),
      subgroup = rep(c("Biomarker+", "Biomarker-", "Biomarker+", "Biomarker-"), each = length(time_points))
    )

    # Add control strategy
    control_data <- data.frame(
      time = time_points,
      survival = control_os,
      model = "Control",
      subgroup = "Control (All)"
    )
    model_data <- rbind(model_data, control_data)

    # Get Kaplan-Meier data
    km_data <- add_biomarker_km(data_complete, biomarker, "OS")

    # Create plot
    p <- ggplot() +
      # Parametric curves
      geom_line(data = model_data[model_data$subgroup != "Control (All)", ],
                aes(x = time, y = survival, color = subgroup, linetype = model),
                linewidth = 1.0) +
      # Control strategy (include in legend via aes)
      geom_line(data = model_data[model_data$subgroup == "Control (All)", ],
                aes(x = time, y = survival, color = "Control"),
                linewidth = 1.0, linetype = "dotted") +
      scale_color_manual(values = c("Biomarker+" = "#E31A1C", "Biomarker-" = "#1F78B4", "Control" = "gray50"),
                         name = "Subgroup") +
      scale_linetype_manual(values = c("All-in-One" = "solid", "Separate" = "dashed"),
                            name = "Model") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(title = toupper(biomarker),
           x = "Time (weeks)",
           y = "Overall Survival") +
      theme_minimal() +
      theme(legend.position = "bottom",
            plot.title = element_text(size = 12, face = "bold")) +
      guides(color = guide_legend(order = 1), linetype = guide_legend(order = 2))

    # Add KM estimates if available
    if (!is.null(km_data) && nrow(km_data) > 0) {
      p <- p +
        geom_step(data = km_data, aes(x = time, y = survival, group = group),
                  color = "black", linewidth = 0.6, alpha = 0.7)
    }

    plot_list[[biomarker]] <- p
  }

  # Combine plots
  gridExtra::grid.arrange(grobs = plot_list, ncol = 1)

} else {
  cat("Survival comparison data not available.\n")
}
```

```{r survival-comparison-pfs, fig.height=10, fig.width=10}
#| fig-cap: "Progression-free survival: Biomarker-positive vs. biomarker-negative vs. control. Solid lines: All-in-One model. Dashed lines: Separate model. Red: Biomarker-positive. Blue: Biomarker-negative. Gray dotted: Control. Black step lines: Kaplan-Meier estimates."

if (exists("predictions") && exists("separate_predictions") && exists("time_points")) {

  # Create a list to store plots for each biomarker
  plot_list <- list()

  for (biomarker in c("crp", "tlr", "tmb_braf")) {

    # Prepare parametric model data
    model_data <- data.frame(
      time = rep(time_points, 4),
      survival = c(
        predictions[[biomarker]]$biomarker_positive$pfs,
        predictions[[biomarker]]$biomarker_negative$pfs,
        separate_predictions[[biomarker]]$biomarker_positive$pfs,
        separate_predictions[[biomarker]]$biomarker_negative$pfs
      ),
      model = rep(c("All-in-One", "All-in-One", "Separate", "Separate"), each = length(time_points)),
      subgroup = rep(c("Biomarker+", "Biomarker-", "Biomarker+", "Biomarker-"), each = length(time_points))
    )

    # Add control strategy
    control_data <- data.frame(
      time = time_points,
      survival = control_pfs,
      model = "Control",
      subgroup = "Control (All)"
    )
    model_data <- rbind(model_data, control_data)

    # Get Kaplan-Meier data
    km_data <- add_biomarker_km(data_complete, biomarker, "PFS")

    # Create plot
    p <- ggplot() +
      # Parametric curves
      geom_line(data = model_data[model_data$subgroup != "Control (All)", ],
                aes(x = time, y = survival, color = subgroup, linetype = model),
                linewidth = 1.0) +
      # Control strategy (include in legend via aes)
      geom_line(data = model_data[model_data$subgroup == "Control (All)", ],
                aes(x = time, y = survival, color = "Control"),
                linewidth = 1.0, linetype = "dotted") +
      scale_color_manual(values = c("Biomarker+" = "#E31A1C", "Biomarker-" = "#1F78B4", "Control" = "gray50"),
                         name = "Subgroup") +
      scale_linetype_manual(values = c("All-in-One" = "solid", "Separate" = "dashed"),
                            name = "Model") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(title = toupper(biomarker),
           x = "Time (weeks)",
           y = "Progression-Free Survival") +
      theme_minimal() +
      theme(legend.position = "bottom",
            plot.title = element_text(size = 12, face = "bold")) +
      guides(color = guide_legend(order = 1), linetype = guide_legend(order = 2))

    # Add KM estimates if available
    if (!is.null(km_data) && nrow(km_data) > 0) {
      p <- p +
        geom_step(data = km_data, aes(x = time, y = survival, group = group),
                  color = "black", linewidth = 0.6, alpha = 0.7)
    }

    plot_list[[biomarker]] <- p
  }

  # Combine plots
  gridExtra::grid.arrange(grobs = plot_list, ncol = 1)

} else {
  cat("Survival comparison data not available.\n")
}
```

```{r pagebreak-9a, results='asis'}
cat("\\newpage\n")
```

## Strategy-Level Comparison: All-in-One vs Separate Models

The following figures compare population-weighted survival predictions between the all-in-one model and separate models for each biomarker strategy, with the control strategy as reference.

```{r strategy-model-comparison, fig.height=12, fig.width=10}
#| fig-cap: "Population-weighted overall survival by biomarker strategy comparing All-in-One model, Separate model, and Control strategy. Each panel shows one biomarker strategy with population-weighted predictions that account for biomarker prevalence."

if (exists("predictions") && exists("separate_predictions") && exists("time_points")) {

  plot_list <- list()

  for (biomarker in c("crp", "tlr", "tmb_braf")) {

    # All-in-One model: population-weighted prediction
    allinone_os <- predictions[[biomarker]]$os

    # Separate model: population-weighted prediction
    prevalence <- separate_predictions[[biomarker]]$prevalence
    separate_os <- prevalence * separate_predictions[[biomarker]]$biomarker_positive$os +
                   (1 - prevalence) * separate_predictions[[biomarker]]$biomarker_negative$os

    # Control strategy
    control_os_curve <- predictions$control$os

    # Build plot data
    plot_data <- data.frame(
      time = rep(time_points, 3),
      survival = c(allinone_os, separate_os, control_os_curve),
      model = rep(c("All-in-One", "Separate", "Control"), each = length(time_points))
    )

    # Create plot
    p <- ggplot(plot_data, aes(x = time, y = survival, color = model, linetype = model)) +
      geom_line(linewidth = 1.2) +
      scale_color_manual(values = c("All-in-One" = "#E69F00", "Separate" = "#56B4E9", "Control" = "black"),
                         name = "Model") +
      scale_linetype_manual(values = c("All-in-One" = "solid", "Separate" = "dashed", "Control" = "dotted"),
                            name = "Model") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(title = paste0(toupper(biomarker), " Strategy (Population-Weighted OS)"),
           x = "Time (weeks)",
           y = "Overall Survival") +
      theme_minimal() +
      theme(legend.position = "bottom",
            plot.title = element_text(size = 12, face = "bold"))

    plot_list[[biomarker]] <- p
  }

  # Combine plots
  gridExtra::grid.arrange(grobs = plot_list, ncol = 1)

} else {
  cat("Strategy comparison data not available.\n")
}
```

```{r strategy-model-comparison-pfs, fig.height=12, fig.width=10}
#| fig-cap: "Population-weighted progression-free survival by biomarker strategy comparing All-in-One model, Separate model, and Control strategy. Each panel shows one biomarker strategy with population-weighted predictions that account for biomarker prevalence."

if (exists("predictions") && exists("separate_predictions") && exists("time_points")) {

  plot_list <- list()

  for (biomarker in c("crp", "tlr", "tmb_braf")) {

    # All-in-One model: population-weighted prediction
    allinone_pfs <- predictions[[biomarker]]$pfs

    # Separate model: population-weighted prediction
    prevalence <- separate_predictions[[biomarker]]$prevalence
    separate_pfs <- prevalence * separate_predictions[[biomarker]]$biomarker_positive$pfs +
                   (1 - prevalence) * separate_predictions[[biomarker]]$biomarker_negative$pfs

    # Control strategy
    control_pfs_curve <- predictions$control$pfs

    # Build plot data
    plot_data <- data.frame(
      time = rep(time_points, 3),
      survival = c(allinone_pfs, separate_pfs, control_pfs_curve),
      model = rep(c("All-in-One", "Separate", "Control"), each = length(time_points))
    )

    # Create plot
    p <- ggplot(plot_data, aes(x = time, y = survival, color = model, linetype = model)) +
      geom_line(linewidth = 1.2) +
      scale_color_manual(values = c("All-in-One" = "#E69F00", "Separate" = "#56B4E9", "Control" = "black"),
                         name = "Model") +
      scale_linetype_manual(values = c("All-in-One" = "solid", "Separate" = "dashed", "Control" = "dotted"),
                            name = "Model") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(title = paste0(toupper(biomarker), " Strategy (Population-Weighted PFS)"),
           x = "Time (weeks)",
           y = "Progression-Free Survival") +
      theme_minimal() +
      theme(legend.position = "bottom",
            plot.title = element_text(size = 12, face = "bold"))

    plot_list[[biomarker]] <- p
  }

  # Combine plots
  gridExtra::grid.arrange(grobs = plot_list, ncol = 1)

} else {
  cat("Strategy comparison data not available.\n")
}
```

```{r pagebreak-9b, results='asis'}
cat("\\newpage\n")
```

## Mean Survival Comparison

The following tables show mean survival (restricted mean survival time, i.e., area under the survival curve) comparing the all-in-one model versus separate models for each biomarker strategy. These are unadjusted life-years without utility weighting.

### Biomarker Subgroups: Overall Survival

```{r life-years-table-os}
#| tbl-cap: "Mean Overall Survival (Unadjusted Life-Years) by Subgroup"

if (exists("ly_biomarker_positive") && exists("ly_biomarker_negative") && exists("control_life_years")) {

  # Filter to OS only from both positive and negative datasets
  ly_pos_os <- ly_biomarker_positive %>%
    filter(Outcome == "OS") %>%
    pivot_wider(names_from = Model_Type, values_from = Life_Years) %>%
    mutate(Subgroup = paste0(Biomarker, "+")) %>%
    select(Subgroup, `All-in-One`, Separate)

  ly_neg_os <- ly_biomarker_negative %>%
    filter(Outcome == "OS") %>%
    pivot_wider(names_from = Model_Type, values_from = Life_Years) %>%
    mutate(Subgroup = paste0(Biomarker, "-")) %>%
    select(Subgroup, `All-in-One`, Separate)

  # Create control row (same for both models, no difference)
  control_row <- data.frame(
    Subgroup = "Control",
    `All-in-One` = round(control_life_years$os, 3),
    Separate = round(control_life_years$os, 3),
    check.names = FALSE
  )

  # Combine all rows: Control first, then alternating +/- for each biomarker
  os_table <- rbind(control_row, ly_pos_os[1,], ly_neg_os[1,],
                    ly_pos_os[2,], ly_neg_os[2,],
                    ly_pos_os[3,], ly_neg_os[3,])

  # Add difference and % change
  os_table <- os_table %>%
    mutate(
      Difference = round(Separate - `All-in-One`, 3),
      `% Change` = round((Separate - `All-in-One`) / `All-in-One` * 100, 1)
    )

  # Set Control row to have no difference/change (since it's model-independent)
  os_table$Difference[os_table$Subgroup == "Control"] <- NA
  os_table$`% Change`[os_table$Subgroup == "Control"] <- NA

  if (knitr::is_latex_output()) {
    kable(os_table, format = "latex", booktabs = TRUE, digits = 3,
          col.names = c("Subgroup", "All-in-One", "Separate", "Difference", "% Change")) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(os_table, format = "html", digits = 3,
          col.names = c("Subgroup", "All-in-One", "Separate", "Difference", "% Change")) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("Life-years comparison not available.\n")
}
```

### Biomarker Subgroups: Progression-Free Survival

```{r life-years-table-pfs}
#| tbl-cap: "Mean Progression-Free Survival by Subgroup"

if (exists("ly_biomarker_positive") && exists("ly_biomarker_negative") && exists("control_life_years")) {

  # Filter to PFS only from both positive and negative datasets
  ly_pos_pfs <- ly_biomarker_positive %>%
    filter(Outcome == "PFS") %>%
    pivot_wider(names_from = Model_Type, values_from = Life_Years) %>%
    mutate(Subgroup = paste0(Biomarker, "+")) %>%
    select(Subgroup, `All-in-One`, Separate)

  ly_neg_pfs <- ly_biomarker_negative %>%
    filter(Outcome == "PFS") %>%
    pivot_wider(names_from = Model_Type, values_from = Life_Years) %>%
    mutate(Subgroup = paste0(Biomarker, "-")) %>%
    select(Subgroup, `All-in-One`, Separate)

  # Create control row (same for both models, no difference)
  control_row <- data.frame(
    Subgroup = "Control",
    `All-in-One` = round(control_life_years$pfs, 3),
    Separate = round(control_life_years$pfs, 3),
    check.names = FALSE
  )

  # Combine all rows: Control first, then alternating +/- for each biomarker
  pfs_table <- rbind(control_row, ly_pos_pfs[1,], ly_neg_pfs[1,],
                     ly_pos_pfs[2,], ly_neg_pfs[2,],
                     ly_pos_pfs[3,], ly_neg_pfs[3,])

  # Add difference and % change
  pfs_table <- pfs_table %>%
    mutate(
      Difference = round(Separate - `All-in-One`, 3),
      `% Change` = round((Separate - `All-in-One`) / `All-in-One` * 100, 1)
    )

  # Set Control row to have no difference/change (since it's model-independent)
  pfs_table$Difference[pfs_table$Subgroup == "Control"] <- NA
  pfs_table$`% Change`[pfs_table$Subgroup == "Control"] <- NA

  if (knitr::is_latex_output()) {
    kable(pfs_table, format = "latex", booktabs = TRUE, digits = 3,
          col.names = c("Subgroup", "All-in-One", "Separate", "Difference", "% Change")) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(pfs_table, format = "html", digits = 3,
          col.names = c("Subgroup", "All-in-One", "Separate", "Difference", "% Change")) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("Life-years comparison not available.\n")
}
```

### Overall Strategy Comparison

The following tables compare population-weighted outcomes across all strategies, sorted by incremental gain vs control. Population-weighted values account for biomarker prevalence in each strategy. The control strategy is model-independent (interaction terms do not activate when all patients receive control treatment).

```{r life-years-table-overall-os}
#| tbl-cap: "Overall Survival (Population-Weighted)"

if (exists("ly_overall_strategy") && exists("control_life_years")) {

  # Filter to OS only and reshape
  os_table <- ly_overall_strategy %>%
    filter(Outcome == "OS") %>%
    pivot_wider(names_from = Model_Type, values_from = Life_Years) %>%
    select(-Outcome) %>%
    mutate(
      `Incr. (All-in-One)` = round(`All-in-One` - control_life_years$os, 3),
      `Incr. (Separate)` = round(Separate - control_life_years$os, 3)
    ) %>%
    arrange(`Incr. (All-in-One)`)

  # Add control strategy row at top (reference)
  control_row <- data.frame(
    Biomarker = "Control",
    `All-in-One` = round(control_life_years$os, 3),
    Separate = NA_real_,
    `Incr. (All-in-One)` = 0,
    `Incr. (Separate)` = NA_real_,
    check.names = FALSE
  )
  os_table <- rbind(control_row, os_table)

  if (knitr::is_latex_output()) {
    kable(os_table, format = "latex", booktabs = TRUE, digits = 3,
          col.names = c("Strategy", "Life-Years", "—", "Incr. (A-i-O)", "Incr. (Sep)")) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position")) %>%
      kableExtra::add_header_above(c(" " = 1, "All-in-One" = 1, "Separate" = 1, "vs Control" = 2))
  } else {
    kable(os_table, format = "html", digits = 3,
          col.names = c("Strategy", "Life-Years", "—", "Incr. (A-i-O)", "Incr. (Sep)")) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
      kableExtra::add_header_above(c(" " = 1, "All-in-One" = 1, "Separate" = 1, "vs Control" = 2))
  }

} else {
  cat("Life-years comparison not available.\n")
}
```

```{r life-years-table-overall-pfs}
#| tbl-cap: "Progression-Free Survival (Population-Weighted)"

if (exists("ly_overall_strategy") && exists("control_life_years")) {

  # Filter to PFS only and reshape
  pfs_table <- ly_overall_strategy %>%
    filter(Outcome == "PFS") %>%
    pivot_wider(names_from = Model_Type, values_from = Life_Years) %>%
    select(-Outcome) %>%
    mutate(
      `Incr. (All-in-One)` = round(`All-in-One` - control_life_years$pfs, 3),
      `Incr. (Separate)` = round(Separate - control_life_years$pfs, 3)
    ) %>%
    arrange(`Incr. (All-in-One)`)

  # Add control strategy row at top (reference)
  control_row <- data.frame(
    Biomarker = "Control",
    `All-in-One` = round(control_life_years$pfs, 3),
    Separate = NA_real_,
    `Incr. (All-in-One)` = 0,
    `Incr. (Separate)` = NA_real_,
    check.names = FALSE
  )
  pfs_table <- rbind(control_row, pfs_table)

  if (knitr::is_latex_output()) {
    kable(pfs_table, format = "latex", booktabs = TRUE, digits = 3,
          col.names = c("Strategy", "PFS Years", "—", "Incr. (A-i-O)", "Incr. (Sep)")) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position")) %>%
      kableExtra::add_header_above(c(" " = 1, "All-in-One" = 1, "Separate" = 1, "vs Control" = 2))
  } else {
    kable(pfs_table, format = "html", digits = 3,
          col.names = c("Strategy", "PFS Years", "—", "Incr. (A-i-O)", "Incr. (Sep)")) %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover")) %>%
      kableExtra::add_header_above(c(" " = 1, "All-in-One" = 1, "Separate" = 1, "vs Control" = 2))
  }

} else {
  cat("Life-years comparison not available.\n")
}
```

# Summary

- Parametric survival models were fitted for both overall survival (OS) and progression-free survival (PFS) outcomes
- Model selection was based on Akaike Information Criterion (AIC) to optimize predictive performance
- Age- and sex-adjusted models with treatment-biomarker interactions were used in the primary analysis
- Biomarker-specific survival patterns were characterized for CRP, TLR (target lesion reduction), and TMB_BRAF strategies
- Visual validation against Kaplan-Meier estimates confirms good model fit across all tested distributions
- Population-level predictions account for biomarker prevalence to reflect expected outcomes in clinical practice
- Strategy comparison shows relative performance of biomarker-guided treatment allocation approaches
- Sensitivity analysis comparing all-in-one vs separate biomarker models assesses robustness to biomarker correlation effects

---

**Report completed on:** `r Sys.Date()`
**Repository:** METIMMOX-1
**Report version:** 1.41
