---
title: "Parametric Survival Modeling"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r para-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%",
  fig.keep = "last"  # Only keep the last plot from each chunk
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10)
  )
)
```

```{r load-analysis-results, include=FALSE}
# Set USE_BOTH_MODELS flag before loading scripts - FORCE to 1 for this report
USE_BOTH_MODELS <- 1

# Load analysis results if not already in environment
if (!exists("models")) {
  cat("Loading parametric survival analysis results...\n")

  # Load required scripts in order
  if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
  }

  if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
  }

  # Set USE_BOTH_MODELS again AFTER loading global variables to override it
  USE_BOTH_MODELS <- 1

  if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
  }
} else {
  # If models already exists, check if we need to refit
  if (is.null(models$no_age_sex)) {
    cat("Models without age/sex not found. Refitting with USE_BOTH_MODELS = 1...\n")
    USE_BOTH_MODELS <- 1
    if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
      suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
    }
  }
}

# Display model structure configuration
model_structure_name <- c("joint", "focused", "separate")[MODEL_STRUCTURE + 1]
cat("Model structure: MODEL_STRUCTURE =", MODEL_STRUCTURE, "(", model_structure_name, ")\n")
```

```{r multi-model-setup, include=FALSE}
# ===============================================================================
# PHASE 1: MULTI-MODEL STRUCTURE SETUP
# ===============================================================================
# This report compares three model structure types (A, B, C) across two
# distributions (Gamma, Weibull PH). Total: 28 models (7 types × 2 dist × 2 outcomes)

# Load prediction functions
source(here("scripts/R/functions/prediction_functions.R"))

# -------------------------------------------------------------------------------
# 1. Define model formulas for all 7 model types
# -------------------------------------------------------------------------------

model_formulas <- list(
  # Model A: Joint (All-in-One) - all biomarkers + all interactions
  A = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx
  ),

  # Model B: Focused - Per-strategy formulas
  # CRP and TMB/BRAF share a formula with both interactions
  B_crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
  ),
  B_tmb = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
  ),
  # TLR uses its own formula with TLR-only interaction
  B_tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + tlr:Rx
  ),

  # Model C: Single-biomarker (Separate) - ONE biomarker only + its interaction
  C_crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp:Rx
  ),
  C_tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + tlr:Rx
  ),
  C_tmb = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + tmb_braf:Rx
  )
)

# -------------------------------------------------------------------------------
# 2. Define model labeling conventions
# -------------------------------------------------------------------------------

# Short labels for plots
model_labels_short <- c(
  "A" = "Model A",
  "B_crp" = "Model B-CRP",
  "B_tlr" = "Model B-TLR",
  "B_tmb" = "Model B-TMB",
  "C_crp" = "Model C-CRP",
  "C_tlr" = "Model C-TLR",
  "C_tmb" = "Model C-TMB"
)

# Full labels for tables
model_labels_full <- c(
  "A" = "Model A: Joint (all biomarkers + all interactions)",
  "B_crp" = "Model B-CRP: Focused (CRP + TMB/BRAF + both interactions)",
  "B_tlr" = "Model B-TLR: Focused (CRP + TMB/BRAF main effects, TLR interaction only)",
  "B_tmb" = "Model B-TMB: Focused (CRP + TMB/BRAF + both interactions)",
  "C_crp" = "Model C-CRP: Single-biomarker (CRP only)",
  "C_tlr" = "Model C-TLR: Single-biomarker (TLR only)",
  "C_tmb" = "Model C-TMB: Single-biomarker (TMB only)"
)

# -------------------------------------------------------------------------------
# 3. Define color palettes (colorblind-friendly)
# -------------------------------------------------------------------------------

# Model type colors (colorblind-friendly)
model_colors <- c(
  "A" = "#E69F00",        # Orange
  "B_crp" = "#56B4E9",    # Sky blue
  "B_tlr" = "#009E73",    # Bluish green
  "B_tmb" = "#F0E442",    # Yellow
  "C_crp" = "#0072B2",    # Blue
  "C_tlr" = "#D55E00",    # Vermillion
  "C_tmb" = "#CC79A7"     # Reddish purple
)

# Distribution linetypes
dist_linetypes <- c(
  "gamma" = "solid",
  "weibullph" = "dashed"
)

# Biomarker subgroup colors
subgroup_colors <- c(
  "positive" = "#E31A1C",   # Red
  "negative" = "#1F78B4",   # Blue
  "control" = "gray50"
)

# -------------------------------------------------------------------------------
# 4. Initialize storage structures
# -------------------------------------------------------------------------------

# Storage for fitted models
multi_models <- list(
  gamma = list(),
  weibullph = list()
)

# Storage for predictions
multi_predictions <- list(
  gamma = list(),
  weibullph = list()
)

# Vector of model types to fit
model_types <- c("A", "B_crp", "B_tlr", "B_tmb", "C_crp", "C_tlr", "C_tmb")

# Vector of distributions to test
distributions <- c("gamma", "weibullph")

cat("Phase 1 setup complete: Model formulas, labels, and storage structures initialized\n")
cat("Ready to fit", length(model_types), "model types ×", length(distributions),
    "distributions × 2 outcomes =", length(model_types) * length(distributions) * 2, "models\n")
```

```{r fit-multi-models, include=FALSE}
# ===============================================================================
# PHASE 2: FIT ALL 28 PARAMETRIC SURVIVAL MODELS
# ===============================================================================

cat("\n===============================================\n")
cat("Phase 2: Fitting multi-model structures...\n")
cat("===============================================\n")

# Check for cache file
cache_file <- here("data", "output", "multi_models_cache.rds")

if (file.exists(cache_file)) {
  cat("Loading cached multi-models from:", cache_file, "\n")
  cache_data <- readRDS(cache_file)
  multi_models <- cache_data$multi_models
  cat("Cache loaded successfully. Total models:", sum(sapply(multi_models, length)) * 2, "\n")
} else {
  cat("No cache found. Fitting all models (this will take several minutes)...\n\n")

  # Initialize counters
  total_models <- length(model_types) * length(distributions) * 2
  current_model <- 0

  # Nested loop: distribution → model type → outcome
  for (dist in distributions) {
    cat("\n--- Fitting", toupper(dist), "distribution ---\n")

    for (model_type in model_types) {
      cat("  Model:", model_type, "\n")

      # Fit OS model
      current_model <- current_model + 1
      cat("    [", current_model, "/", total_models, "] Fitting OS...\n")

      os_fit <- tryCatch({
        flexsurvreg(
          formula = model_formulas[[model_type]]$os,
          data = data_complete,
          dist = dist
        )
      }, error = function(e) {
        warning(paste("Failed to fit", model_type, "OS with", dist, ":", e$message))
        return(NULL)
      })

      # Fit PFS model
      current_model <- current_model + 1
      cat("    [", current_model, "/", total_models, "] Fitting PFS...\n")

      pfs_fit <- tryCatch({
        flexsurvreg(
          formula = model_formulas[[model_type]]$pfs,
          data = data_complete,
          dist = dist
        )
      }, error = function(e) {
        warning(paste("Failed to fit", model_type, "PFS with", dist, ":", e$message))
        return(NULL)
      })

      # Store models
      multi_models[[dist]][[model_type]] <- list(
        os = os_fit,
        pfs = pfs_fit
      )

      # Extract and store AIC/BIC if models fitted successfully
      if (!is.null(os_fit) && !is.null(pfs_fit)) {
        multi_models[[dist]][[model_type]]$os_aic <- AIC(os_fit)
        multi_models[[dist]][[model_type]]$os_bic <- BIC(os_fit)
        multi_models[[dist]][[model_type]]$pfs_aic <- AIC(pfs_fit)
        multi_models[[dist]][[model_type]]$pfs_bic <- BIC(pfs_fit)

        cat("    OS AIC:", round(multi_models[[dist]][[model_type]]$os_aic, 2),
            "| PFS AIC:", round(multi_models[[dist]][[model_type]]$pfs_aic, 2), "\n")
      } else {
        cat("    FAILED - skipping AIC/BIC extraction\n")
      }
    }
  }

  # Save cache
  cat("\nSaving models to cache:", cache_file, "\n")
  dir.create(dirname(cache_file), showWarnings = FALSE, recursive = TRUE)
  saveRDS(list(multi_models = multi_models), cache_file)
  cat("Cache saved successfully.\n")
}

cat("\n===============================================\n")
cat("Phase 2 complete: All models fitted.\n")
cat("===============================================\n")

# Clean up memory
gc(verbose = FALSE)
```

```{r generate-multi-predictions, include=FALSE}
# ===============================================================================
# PHASE 3: GENERATE PREDICTIONS FOR ALL MODEL TYPES
# ===============================================================================

cat("\n===============================================\n")
cat("Phase 3: Generating predictions...\n")
cat("===============================================\n")

# Define which biomarkers each model type can predict
model_biomarker_map <- list(
  A = c("crp", "tlr", "tmb_braf"),
  B_crp = c("crp"),
  B_tlr = c("tlr"),
  B_tmb = c("tmb_braf"),
  C_crp = c("crp"),
  C_tlr = c("tlr"),
  C_tmb = c("tmb_braf")
)

# -------------------------------------------------------------------------------
# Helper function for population-averaged predictions (inline version)
# -------------------------------------------------------------------------------
predict_population_avg <- function(model, newdata, time_points) {
  # Generate predictions for each patient, then average across population
  tryCatch({
    pred <- predict(model, newdata = newdata, type = "survival", times = time_points)
    # Extract survival probabilities - handle different flexsurv output formats
    if (".pred" %in% names(pred)) {
      # New format: tibble with .pred column
      surv_probs <- lapply(pred$.pred, function(x) x$.pred_survival)
      surv_matrix <- do.call(cbind, surv_probs)
      return(rowMeans(surv_matrix, na.rm = TRUE))
    } else if (is.list(pred) && length(pred) > 0 && is.data.frame(pred[[1]])) {
      # Old format: list of data frames
      surv_probs <- sapply(pred, function(x) x$est)
      if (is.matrix(surv_probs)) {
        return(rowMeans(surv_probs, na.rm = TRUE))
      } else {
        return(surv_probs)
      }
    } else {
      return(NULL)
    }
  }, error = function(e) {
    cat("    Prediction error:", e$message, "\n")
    return(NULL)
  })
}

# Get treatment level references
exp_rx <- levels(data_complete$Rx)[2]  # Experimental treatment
ctrl_rx <- levels(data_complete$Rx)[1]  # Control treatment

# Loop through distributions and model types
for (dist in distributions) {
  cat("\n--- Generating predictions for", toupper(dist), "---\n")

  for (model_type in model_types) {
    cat("  Model:", model_type, "\n")

    # Check if models exist
    os_model <- multi_models[[dist]][[model_type]]$os
    pfs_model <- multi_models[[dist]][[model_type]]$pfs

    if (is.null(os_model) || is.null(pfs_model)) {
      cat("    Skipping (models not fitted)\n")
      next
    }

    # Initialize prediction storage for this model type
    multi_predictions[[dist]][[model_type]] <- list()

    # -------------------------------------------------------------------------
    # Control predictions: All patients receive control treatment
    # -------------------------------------------------------------------------
    cat("    Generating control predictions...\n")
    control_data <- data_complete
    control_data$Rx <- factor(ctrl_rx, levels = levels(data_complete$Rx))

    control_os <- predict_population_avg(os_model, control_data, time_points)
    control_pfs <- predict_population_avg(pfs_model, control_data, time_points)

    if (!is.null(control_os) && !is.null(control_pfs)) {
      multi_predictions[[dist]][[model_type]]$control <- list(
        os = control_os,
        pfs = control_pfs
      )
      cat("    Control predictions generated successfully\n")
    } else {
      cat("    WARNING: Control predictions failed\n")
    }

    # -------------------------------------------------------------------------
    # Biomarker-specific predictions based on model type
    # -------------------------------------------------------------------------
    biomarkers_to_predict <- model_biomarker_map[[model_type]]

    for (biomarker in biomarkers_to_predict) {
      cat("    Generating", biomarker, "predictions...\n")

      # Biomarker-positive: experimental treatment
      pos_data <- data_complete[as.numeric(as.character(data_complete[[biomarker]])) == 1, ]
      if (nrow(pos_data) > 0) {
        pos_data$Rx <- factor(exp_rx, levels = levels(data_complete$Rx))
        pos_os <- predict_population_avg(os_model, pos_data, time_points)
        pos_pfs <- predict_population_avg(pfs_model, pos_data, time_points)

        if (!is.null(pos_os) && !is.null(pos_pfs)) {
          multi_predictions[[dist]][[model_type]][[paste0(biomarker, "_pos")]] <- list(
            os = pos_os,
            pfs = pos_pfs
          )
        }
      }

      # Biomarker-negative: control treatment
      neg_data <- data_complete[as.numeric(as.character(data_complete[[biomarker]])) == 0, ]
      if (nrow(neg_data) > 0) {
        neg_data$Rx <- factor(ctrl_rx, levels = levels(data_complete$Rx))
        neg_os <- predict_population_avg(os_model, neg_data, time_points)
        neg_pfs <- predict_population_avg(pfs_model, neg_data, time_points)

        if (!is.null(neg_os) && !is.null(neg_pfs)) {
          multi_predictions[[dist]][[model_type]][[paste0(biomarker, "_neg")]] <- list(
            os = neg_os,
            pfs = neg_pfs
          )
        }
      }

      # Population-weighted prediction
      biomarker_prev <- strategies_df$prevalence[strategies_df$id == biomarker]
      pos_pred <- multi_predictions[[dist]][[model_type]][[paste0(biomarker, "_pos")]]
      neg_pred <- multi_predictions[[dist]][[model_type]][[paste0(biomarker, "_neg")]]

      if (length(biomarker_prev) > 0 && !is.null(pos_pred) && !is.null(neg_pred)) {
        multi_predictions[[dist]][[model_type]][[paste0(biomarker, "_weighted")]] <- list(
          os = biomarker_prev * pos_pred$os + (1 - biomarker_prev) * neg_pred$os,
          pfs = biomarker_prev * pos_pred$pfs + (1 - biomarker_prev) * neg_pred$pfs
        )
        cat("    ", biomarker, "predictions generated successfully\n")
      }
    }
  }
}

cat("\n===============================================\n")
cat("Phase 3 complete: Predictions generated.\n")
cat("===============================================\n")

# Diagnostic: Check what was actually generated
cat("\nDiagnostic: Checking multi_predictions structure:\n")
for (dist in distributions) {
  for (model_type in model_types) {
    pred <- multi_predictions[[dist]][[model_type]]
    if (!is.null(pred)) {
      cat("  ", dist, "-", model_type, ": ", paste(names(pred), collapse=", "), "\n")
    }
  }
}

# Clean up memory
gc(verbose = FALSE)
```

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Overview

This report presents parametric survival models fitted for the METIMMOX-1 economic evaluation. The models compare different biomarker strategies for overall survival (OS) and progression-free survival (PFS) outcomes. This analysis serves as the foundation for the cost-effectiveness evaluation by quantifying treatment effects across biomarker-defined patient subgroups.

## Model Structure Types

This report compares three model structure types to assess sensitivity to biomarker correlation and model complexity:

- **Model A (Joint)**: All three biomarkers and their treatment interactions are included in a single model. This specification tests each biomarker interaction while adjusting for the others, providing mutually adjusted effect estimates. Model A is the primary specification used in the cost-effectiveness analysis.

- **Model B (Focused)**: Per-strategy formulas. CRP and TMB/BRAF strategies share a formula with both biomarkers as main effects and both interaction terms (`crp:Rx + tmb_braf:Rx`). TLR uses a separate formula with CRP and TMB/BRAF as main effects but only the TLR interaction (`tlr:Rx`). This creates three models per outcome (B-CRP, B-TLR, B-TMB).

- **Model C (Single-biomarker)**: Each biomarker is modeled separately without adjustment for other biomarkers, creating three independent models per outcome (C-CRP, C-TLR, C-TMB). This is the simplest specification but may overestimate effects if biomarkers are correlated.

For each model structure type, we fit two parametric distributions (Gamma and Weibull proportional hazards) for both OS and PFS, resulting in **28 total models** (7 model variants × 2 distributions × 2 outcomes).

# Population Characteristics including Biomarker Prevalences

```{r population-summary, results='asis'}
if (exists("ref_age") && exists("predictions") && exists("strategies_df")) {

  # Display population characteristics
  cat("Continuous variables:\n\n")
  cat("- Age (mean):", round(ref_age, 2), "years\n\n")

  cat("Categorical variables (most frequent category used):\n\n")
  cat("- Sex:", ref_sex, "(0=female, 1=male)\n")
  cat("- CRP:", ref_crp, "(0=negative, 1=positive)\n")
  cat("- TLR:", ref_tlr, "(0=negative, 1=positive)\n")
  cat("- TMB_BRAF:", ref_tmb_braf, "(0=negative, 1=positive)\n\n")

  cat("Biomarker prevalences in population:\n\n")
  for (strategy in strategies_df$id[strategies_df$id != "control"]) {
    prevalence <- strategies_df$prevalence[strategies_df$id == strategy]
    cat("- ", toupper(strategy), " positive:", round(prevalence * 100, 1), "%\n")
  }

  cat("\nData completeness:\n\n")
  cat("- Complete cases used:", nrow(data_complete), "of", nrow(data), "observations")
  cat(" (", round(nrow(data_complete)/nrow(data) * 100, 1), "%)\n\n")

} else {
  cat("Population characteristics not available. Run main analysis first.\n")
}
```

# Model Selection and Comparison

## Analysis Specifications

### Model Structure Types

We compare seven model variants representing three structural approaches:

```{r model-formulas-table, results='asis'}
# Create model formulas table
formula_table <- data.frame(
  `Model Type` = c(
    "Model A",
    "Model B-CRP/TMB",
    "Model B-TLR",
    "Model C-CRP",
    "Model C-TLR",
    "Model C-TMB"
  ),
  `Structure` = c(
    "Joint",
    "Focused",
    "Focused",
    "Single-biomarker",
    "Single-biomarker",
    "Single-biomarker"
  ),
  `Formula` = c(
    "Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx",
    "Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx",
    "Age + sex + Rx + crp + tmb_braf + tlr:Rx",
    "Age + sex + Rx + crp:Rx",
    "Age + sex + Rx + tlr:Rx",
    "Age + sex + Rx + tmb_braf:Rx"
  ),
  check.names = FALSE
)

if (knitr::is_latex_output()) {
  kable(formula_table, format = "latex", booktabs = TRUE, escape = TRUE) %>%
    kable_styling(font_size = 8, latex_options = c("striped", "HOLD_position", "scale_down")) %>%
    column_spec(3, width = "8cm")
} else {
  kable(formula_table, format = "html") %>%
    kable_styling(bootstrap_options = c("striped", "hover"))
}
```

All models include:

- **Age** (continuous, years) - prognostic covariate
- **Sex** (categorical, 0=female, 1=male) - prognostic covariate
- **Treatment** (Rx) - experimental vs control
- **Biomarker interactions** - as shown in formulas above

### Distributions Tested

For Model A (Joint), we test nine parametric distributions to select the best-fitting family:

1. Exponential
2. Weibull
3. Weibull PH
4. Gompertz
5. Log-logistic
6. Log-normal
7. Generalized Gamma
8. Gamma
9. Generalized F Distribution

The best-fitting distribution (Gamma) and reference distribution (Weibull PH) are then applied to all seven model structure types.

### Data Considerations

- **Complete case analysis**: Only patients with complete covariate data included
- **Time horizon**: Models fitted to observed follow-up period with extrapolation capability
- **Biomarker prevalences**: Taken from the METIMMOX-1 trial and may or may not reflect real world settings

### Model Selection Criterion

**AIC (Akaike Information Criterion)** is used for model selection because:

- BIC penalizes model complexity more heavily (uses log(n) vs 2 for AIC)
- For prediction purposes, we want the model that best balances fit and complexity
- AIC is better for predictive modeling while BIC is better for identifying the "true" model
- Validation via visual comparison with Kaplan-Meier curves and clinical plausibility assessment

## Distribution Selection (Model A)

We first select the best-fitting parametric distribution using Model A (Joint), the most comprehensive specification. This distribution is then applied to all seven model structure types for fair comparison.

```{r model-comparison-os}
#| tbl-cap: "Overall Survival (OS) distribution comparison for Model A using AIC and BIC"

if (exists("models") && !is.null(models$full)) {

  # Overall Survival models - start with full model
  os_comparison <- data.frame(Structure = "Full Model", models$full$os_ic)

  # Add no_age_sex model only if it exists
  if (!is.null(models$no_age_sex) && !is.null(models$no_age_sex$os_ic)) {
    os_comparison <- rbind(
      os_comparison,
      data.frame(Structure = "w/o Age/Sex", models$no_age_sex$os_ic)
    )
  }

  os_comparison <- os_comparison %>%
    arrange(AIC) %>%
    mutate(
      AIC = round(AIC, 2),
      BIC = round(BIC, 2),
      `Delta AIC` = round(AIC - min(AIC, na.rm = TRUE), 2),
      Rank = rank(AIC, na.last = "keep")
    )

  # Mark best model
  if (exists("models") && !is.null(models$best_fit$os_aic)) {
    best_idx <- which.min(abs(os_comparison$AIC - models$best_fit$os_aic))
    if (length(best_idx) > 0) {
      os_comparison$Selected <- ""
      os_comparison$Selected[best_idx] <- "***"
    }
  }

  if (knitr::is_latex_output()) {
    kable(os_comparison, format = "latex", booktabs = TRUE, escape = TRUE) %>%
      kableExtra::kable_styling(font_size = 9, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(os_comparison, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("OS model comparison not available.\n")
}
```

```{r model-comparison-pfs}
#| tbl-cap: "Progression-Free Survival (PFS) distribution comparison for Model A using AIC and BIC"

if (exists("models") && !is.null(models$full)) {

  # Progression-Free Survival models - start with full model
  pfs_comparison <- data.frame(Structure = "Full Model", models$full$pfs_ic)

  # Add no_age_sex model only if it exists
  if (!is.null(models$no_age_sex) && !is.null(models$no_age_sex$pfs_ic)) {
    pfs_comparison <- rbind(
      pfs_comparison,
      data.frame(Structure = "w/o Age/Sex", models$no_age_sex$pfs_ic)
    )
  }

  pfs_comparison <- pfs_comparison %>%
    arrange(AIC) %>%
    mutate(
      AIC = round(AIC, 2),
      BIC = round(BIC, 2),
      `Delta AIC` = round(AIC - min(AIC, na.rm = TRUE), 2),
      Rank = rank(AIC, na.last = "keep")
    )

  # Mark best model
  if (exists("models") && !is.null(models$best_fit$pfs_aic)) {
    best_idx <- which.min(abs(pfs_comparison$AIC - models$best_fit$pfs_aic))
    if (length(best_idx) > 0) {
      pfs_comparison$Selected <- ""
      pfs_comparison$Selected[best_idx] <- "***"
    }
  }

  if (knitr::is_latex_output()) {
    kable(pfs_comparison, format = "latex", booktabs = TRUE, escape = TRUE) %>%
      kableExtra::kable_styling(font_size = 9, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(pfs_comparison, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("PFS model comparison not available.\n")
}
```

Based on AIC, **Gamma** is selected as the best-fitting distribution for both OS and PFS. **Weibull PH** is retained as a reference distribution for robustness assessment.

## Model Structure Comparison

Having selected Gamma as the best-fitting distribution, we now compare all seven model structure types using this distribution. This comparison assesses the impact of biomarker specification on model fit.

```{r model-structure-comparison}
#| tbl-cap: "Model structure comparison using Gamma distribution"

if (exists("multi_models") && !is.null(multi_models$gamma)) {

  # Create comparison table for all 7 model types
  structure_comparison <- data.frame(
    `Model Type` = character(),
    `OS AIC` = numeric(),
    `OS BIC` = numeric(),
    `PFS AIC` = numeric(),
    `PFS BIC` = numeric(),
    check.names = FALSE
  )

  for (model_type in model_types) {
    if (!is.null(multi_models$gamma[[model_type]])) {
      structure_comparison <- rbind(
        structure_comparison,
        data.frame(
          `Model Type` = model_labels_short[model_type],
          `OS AIC` = round(multi_models$gamma[[model_type]]$os_aic, 2),
          `OS BIC` = round(multi_models$gamma[[model_type]]$os_bic, 2),
          `PFS AIC` = round(multi_models$gamma[[model_type]]$pfs_aic, 2),
          `PFS BIC` = round(multi_models$gamma[[model_type]]$pfs_bic, 2),
          check.names = FALSE
        )
      )
    }
  }

  # Add delta AIC columns
  structure_comparison$`OS Delta AIC` <- round(
    structure_comparison$`OS AIC` - min(structure_comparison$`OS AIC`, na.rm = TRUE), 2
  )
  structure_comparison$`PFS Delta AIC` <- round(
    structure_comparison$`PFS AIC` - min(structure_comparison$`PFS AIC`, na.rm = TRUE), 2
  )

  # Reorder columns
  structure_comparison <- structure_comparison[, c(
    "Model Type", "OS AIC", "OS Delta AIC", "OS BIC", "PFS AIC", "PFS Delta AIC", "PFS BIC"
  )]

  if (knitr::is_latex_output()) {
    kable(structure_comparison, format = "latex", booktabs = TRUE, escape = TRUE) %>%
      kable_styling(font_size = 9, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(structure_comparison, format = "html") %>%
      kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("Model structure comparison not available.\n")
}
```

**Interpretation:**

- **Model A (Joint)** has the lowest AIC (most parameters, best fit) but highest BIC (penalized for complexity)
- **Model C variants** (Single-biomarker) have the highest AIC (fewest parameters, worse fit) but lowest BIC
- **Model B variants** (Focused) represent intermediate complexity
- All Delta AIC values are relatively small, indicating reasonable fit across all model structures
- **Model A is used for the primary cost-effectiveness analysis** as it provides the most comprehensive assessment of biomarker interactions while controlling for confounding

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Model Coefficients

The following tables present model coefficients for each model type, organized by outcome and distribution. Coefficients are presented as estimates with 95% confidence intervals. For treatment-biomarker interaction hazard ratios, see the Clinical Effectiveness report.

```{r coef-helper-function, include=FALSE}
# Helper function to extract coefficients from a flexsurvreg model
extract_coef_table <- function(model, dist_label) {
  if (is.null(model)) {
    return(NULL)
  }

  tryCatch({
    coef_table <- as.data.frame(model$res.t)
    if (is.null(coef_table) || nrow(coef_table) == 0) {
      return(NULL)
    }

    coef_df <- data.frame(
      Parameter = rownames(coef_table),
      Estimate = round(coef_table$est, 4),
      SE = round(coef_table$se, 4),
      `L95%` = round(coef_table$`L95%`, 4),
      `U95%` = round(coef_table$`U95%`, 4),
      check.names = FALSE,
      stringsAsFactors = FALSE
    )
    return(coef_df)
  }, error = function(e) {
    return(NULL)
  })
}

# Function to display a single model's coefficients
display_coef_table <- function(coef_df, caption_text) {
  if (is.null(coef_df) || nrow(coef_df) == 0) {
    cat("Coefficients not available.\n")
    return(invisible(NULL))
  }

  if (knitr::is_latex_output()) {
    print(kable(coef_df, format = "latex", booktabs = TRUE, row.names = FALSE,
                caption = caption_text) %>%
      kable_styling(font_size = 8, latex_options = c("striped", "HOLD_position")))
  } else {
    print(kable(coef_df, format = "html", row.names = FALSE, caption = caption_text) %>%
      kable_styling(bootstrap_options = c("striped", "hover"), font_size = 10))
  }
}
```

## Model A (Joint) Coefficients

Model A includes all three biomarker interactions: `Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx`

```{r model-a-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$A)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$A$os, "Gamma")
  display_coef_table(coef_df, "Model A - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$A$os, "Weibull PH")
  display_coef_table(coef_df, "Model A - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$A$pfs, "Gamma")
  display_coef_table(coef_df, "Model A - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$A$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model A - PFS - Weibull PH")
} else {
  cat("Model A coefficients not available.\n")
}
```

```{r pagebreak-coef-a, results='asis'}
cat("\\newpage\n")
```

## Model B-CRP (Focused) Coefficients

Model B-CRP includes CRP and TMB/BRAF with both interaction terms: `Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx`

```{r model-b-crp-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$B_crp)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$B_crp$os, "Gamma")
  display_coef_table(coef_df, "Model B-CRP - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$B_crp$os, "Weibull PH")
  display_coef_table(coef_df, "Model B-CRP - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$B_crp$pfs, "Gamma")
  display_coef_table(coef_df, "Model B-CRP - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$B_crp$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model B-CRP - PFS - Weibull PH")
} else {
  cat("Model B-CRP coefficients not available.\n")
}
```

```{r pagebreak-coef-b-crp, results='asis'}
cat("\\newpage\n")
```

## Model B-TMB (Focused) Coefficients

Model B-TMB includes CRP and TMB/BRAF with both interaction terms: `Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx`

```{r model-b-tmb-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$B_tmb)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$B_tmb$os, "Gamma")
  display_coef_table(coef_df, "Model B-TMB - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$B_tmb$os, "Weibull PH")
  display_coef_table(coef_df, "Model B-TMB - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$B_tmb$pfs, "Gamma")
  display_coef_table(coef_df, "Model B-TMB - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$B_tmb$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model B-TMB - PFS - Weibull PH")
} else {
  cat("Model B-TMB coefficients not available.\n")
}
```

```{r pagebreak-coef-b-tmb, results='asis'}
cat("\\newpage\n")
```

## Model B-TLR (Focused) Coefficients

Model B-TLR includes CRP and TMB/BRAF as main effects with TLR interaction only: `Age + sex + Rx + crp + tmb_braf + tlr:Rx`

```{r model-b-tlr-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$B_tlr)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$B_tlr$os, "Gamma")
  display_coef_table(coef_df, "Model B-TLR - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$B_tlr$os, "Weibull PH")
  display_coef_table(coef_df, "Model B-TLR - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$B_tlr$pfs, "Gamma")
  display_coef_table(coef_df, "Model B-TLR - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$B_tlr$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model B-TLR - PFS - Weibull PH")
} else {
  cat("Model B-TLR coefficients not available.\n")
}
```

```{r pagebreak-coef-b-tlr, results='asis'}
cat("\\newpage\n")
```

## Model C-CRP (Single-biomarker) Coefficients

Model C-CRP includes only CRP with its interaction: `Age + sex + Rx + crp:Rx`

```{r model-c-crp-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$C_crp)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$C_crp$os, "Gamma")
  display_coef_table(coef_df, "Model C-CRP - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$C_crp$os, "Weibull PH")
  display_coef_table(coef_df, "Model C-CRP - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$C_crp$pfs, "Gamma")
  display_coef_table(coef_df, "Model C-CRP - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$C_crp$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model C-CRP - PFS - Weibull PH")
} else {
  cat("Model C-CRP coefficients not available.\n")
}
```

```{r pagebreak-coef-c-crp, results='asis'}
cat("\\newpage\n")
```

## Model C-TLR (Single-biomarker) Coefficients

Model C-TLR includes only TLR with its interaction: `Age + sex + Rx + tlr:Rx`

```{r model-c-tlr-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$C_tlr)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$C_tlr$os, "Gamma")
  display_coef_table(coef_df, "Model C-TLR - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$C_tlr$os, "Weibull PH")
  display_coef_table(coef_df, "Model C-TLR - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$C_tlr$pfs, "Gamma")
  display_coef_table(coef_df, "Model C-TLR - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$C_tlr$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model C-TLR - PFS - Weibull PH")
} else {
  cat("Model C-TLR coefficients not available.\n")
}
```

```{r pagebreak-coef-c-tlr, results='asis'}
cat("\\newpage\n")
```

## Model C-TMB (Single-biomarker) Coefficients

Model C-TMB includes only TMB_BRAF with its interaction: `Age + sex + Rx + tmb_braf:Rx`

```{r model-c-tmb-coefs, results='asis'}
if (exists("multi_models") && !is.null(multi_models$gamma$C_tmb)) {
  cat("### Overall Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$C_tmb$os, "Gamma")
  display_coef_table(coef_df, "Model C-TMB - OS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$C_tmb$os, "Weibull PH")
  display_coef_table(coef_df, "Model C-TMB - OS - Weibull PH")

  cat("\n\n### Progression-Free Survival\n\n")
  cat("**Gamma Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$gamma$C_tmb$pfs, "Gamma")
  display_coef_table(coef_df, "Model C-TMB - PFS - Gamma")

  cat("\n\n**Weibull PH Distribution:**\n\n")
  coef_df <- extract_coef_table(multi_models$weibullph$C_tmb$pfs, "Weibull PH")
  display_coef_table(coef_df, "Model C-TMB - PFS - Weibull PH")
} else {
  cat("Model C-TMB coefficients not available.\n")
}
```

**Note:** Parameters include distribution shape/scale parameters (e.g., `shape`, `rate` for Gamma; `shape`, `scale` for Weibull) as well as covariate effects. Coefficients are on the log scale; exponentiate to obtain hazard ratios for covariate effects.

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# Population Survival Curves

The following figures compare empirical Kaplan-Meier estimates with predicted survival curves from the selected parametric models. "Population" refers to different patient groups: biomarker-positive patients, biomarker-negative patients, or the entire population. For the control strategy, population curves represent all patients. For biomarker-guided strategies, population-level predictions are weighted by the prevalence of biomarker-positive and biomarker-negative patients in the sample.

**Note:** For simplicity, population-level validation plots show Model A (Joint) with Gamma distribution only. All model structure types show similar population-level fit; differences emerge primarily at the biomarker subgroup level (presented in subsequent biomarker-specific sections).

```{r survival-functions, include=FALSE}
# Function to create population survival plots
create_population_plots <- function(models, data_complete, time_points, outcome_type = "OS") {

  # Get Kaplan-Meier estimates
  if (outcome_type == "OS") {
    km_fit <- survfit(Surv(OSwk, Death) ~ 1, data = data_complete)
  } else {
    km_fit <- survfit(Surv(PFSwk, Progression) ~ 1, data = data_complete)
  }

  # Create plotting data for KM
  km_data <- data.frame(
    time = km_fit$time,
    survival = km_fit$surv,
    model = "Kaplan-Meier",
    structure = "Observed"
  )

  plot_data <- km_data

  # Create representative patient
  ref_patient <- data.frame(
    Age = mean(data_complete$Age, na.rm = TRUE),
    sex = get_modal_category(data_complete$sex),
    Rx = get_modal_category(data_complete$Rx),
    crp = get_modal_category(data_complete$crp),
    tlr = get_modal_category(data_complete$tlr),
    tmb_braf = get_modal_category(data_complete$tmb_braf)
  )

  # Ensure factors have correct levels
  ref_patient$sex <- factor(ref_patient$sex, levels = levels(data_complete$sex))
  ref_patient$Rx <- factor(ref_patient$Rx, levels = levels(data_complete$Rx))
  ref_patient$crp <- factor(ref_patient$crp, levels = levels(data_complete$crp))
  ref_patient$tlr <- factor(ref_patient$tlr, levels = levels(data_complete$tlr))
  ref_patient$tmb_braf <- factor(ref_patient$tmb_braf, levels = levels(data_complete$tmb_braf))

  # Add parametric model predictions
  for (structure in c("full", "no_age_sex")) {
    if (!is.null(models[[structure]])) {
      structure_models <- models[[structure]]
      outcome_models <- if (outcome_type == "OS") structure_models$os else structure_models$pfs

      if (!is.null(outcome_models)) {
        for (dist_name in names(outcome_models)) {
          model_obj <- outcome_models[[dist_name]]

          if (inherits(model_obj, "flexsurvreg")) {
            tryCatch({
              model_obj$data <- data_complete

              pred_summary <- summary(model_obj, t = time_points, newdata = ref_patient, type = "survival")

              if (is.list(pred_summary) && length(pred_summary) > 0) {
                first_result <- pred_summary[[1]]

                if (is.data.frame(first_result) && all(c("time", "est") %in% names(first_result))) {
                  temp_data <- data.frame(
                    time = first_result$time,
                    survival = first_result$est,
                    model = dist_name,
                    structure = structure
                  )

                  plot_data <- rbind(plot_data, temp_data)
                }
              }

              model_obj$data <- NULL

            }, error = function(e) {
              # Handle errors silently
            })
          }
        }
      }
    }
  }

  return(plot_data)
}

# Function to add KM estimates for biomarker subgroups
add_biomarker_km <- function(data_complete, biomarker_col, outcome_type = "OS") {

  # Get treatment levels
  exp_rx <- levels(data_complete$Rx)[2]  # Experimental arm
  ctrl_rx <- levels(data_complete$Rx)[1]  # Control arm

  km_data_list <- list()

  # Biomarker positive + experimental treatment
  pos_exp <- data_complete[data_complete[[biomarker_col]] == 1 & data_complete$Rx == exp_rx, ]
  if (nrow(pos_exp) > 0) {
    if (outcome_type == "OS") {
      km_fit <- survfit(Surv(OSwk, Death) ~ 1, data = pos_exp)
    } else {
      km_fit <- survfit(Surv(PFSwk, Progression) ~ 1, data = pos_exp)
    }
    km_data_list$pos_exp <- data.frame(
      time = km_fit$time,
      survival = km_fit$surv,
      group = "Biomarker+ (Exp)"
    )
  }

  # Biomarker negative + control treatment
  neg_ctrl <- data_complete[data_complete[[biomarker_col]] == 0 & data_complete$Rx == ctrl_rx, ]
  if (nrow(neg_ctrl) > 0) {
    if (outcome_type == "OS") {
      km_fit <- survfit(Surv(OSwk, Death) ~ 1, data = neg_ctrl)
    } else {
      km_fit <- survfit(Surv(PFSwk, Progression) ~ 1, data = neg_ctrl)
    }
    km_data_list$neg_ctrl <- data.frame(
      time = km_fit$time,
      survival = km_fit$surv,
      group = "Biomarker- (Ctrl)"
    )
  }

  # Combine all KM data
  if (length(km_data_list) > 0) {
    km_combined <- do.call(rbind, km_data_list)
    return(km_combined)
  } else {
    return(NULL)
  }
}
```

## Model Validation: Comparison with Kaplan-Meier Estimates

These figures show how well each tested parametric distribution fits the observed data for the entire study population.

```{r os-full-plot}
#| fig-cap: "Overall survival curves for age- and sex-adjusted models compared to Kaplan-Meier estimates. All curves represent the entire study population using a representative patient profile (mean age, modal sex and biomarker values)."
#| fig-height: 6
#| fig-width: 8

if (exists("models") && exists("data_complete")) {

  # OS curves - full models
  os_full_data <- create_population_plots(models, data_complete, time_points, "OS")
  os_full_data <- os_full_data[os_full_data$structure %in% c("Observed", "full"), ]

  if (nrow(os_full_data) > 0) {
    p_os_full <- ggplot(os_full_data, aes(x = time, y = survival, color = model)) +
      geom_line(linewidth = 1.2) +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
      labs(x = "Time (weeks)", y = "Survival Probability",
           color = "Model") +
      theme(legend.position = "bottom")

    print(p_os_full)
  }
}
```

```{r pfs-full-plot}
#| fig-cap: "Progression-free survival curves for age- and sex-adjusted models compared to Kaplan-Meier estimates. All curves represent the entire study population using a representative patient profile (mean age, modal sex and biomarker values)."
#| fig-height: 6
#| fig-width: 8

if (exists("models") && exists("data_complete")) {

  # PFS curves - full models
  pfs_full_data <- create_population_plots(models, data_complete, time_points, "PFS")
  pfs_full_data <- pfs_full_data[pfs_full_data$structure %in% c("Observed", "full"), ]

  if (nrow(pfs_full_data) > 0) {
    p_pfs_full <- ggplot(pfs_full_data, aes(x = time, y = survival, color = model)) +
      geom_line(linewidth = 1.2) +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 26)) +
      labs(x = "Time (weeks)", y = "Survival Probability",
           color = "Model") +
      theme(legend.position = "bottom")

    print(p_pfs_full)
  }
}
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Biomarker-Specific Results

The following figures compare survival outcomes between biomarker-positive and biomarker-negative patient subgroups for each biomarker strategy. These comparisons inform the potential value of biomarker-guided treatment selection. Kaplan-Meier estimates are shown for biomarker-positive patients receiving experimental treatment and biomarker-negative patients receiving control treatment, alongside parametric model predictions.

## CRP Biomarker Strategy

```{r crp-plots, fig.height=12, fig.width=10}
#| fig-cap: "CRP biomarker strategy: Model structure comparison across OS and PFS. Rows show Model A (Joint), Model B-CRP (Focused), and Model C-CRP (Single-biomarker). Colored lines: parametric predictions (red=CRP+, blue=CRP-; solid=Gamma, dashed=Weibull PH). Black step lines: Kaplan-Meier estimates (solid=biomarker+, dashed=biomarker-)."

if (exists("multi_predictions") && exists("time_points")) {

  tryCatch({
    # Define relevant model types for CRP
    crp_model_types <- c("A", "B_crp", "C_crp")

    # Build plot data from multi_predictions
    plot_data <- data.frame()

    for (model_type in crp_model_types) {
      for (dist in c("gamma", "weibullph")) {
        crp_pos <- multi_predictions[[dist]][[model_type]][["crp_pos"]]
        crp_neg <- multi_predictions[[dist]][[model_type]][["crp_neg"]]

        if (!is.null(crp_pos) && !is.null(crp_neg)) {
          # OS data
          plot_data <- rbind(plot_data, data.frame(
            time = rep(time_points, 2),
            survival = c(crp_pos$os, crp_neg$os),
            subgroup = rep(c("CRP+", "CRP-"), each = length(time_points)),
            distribution = dist,
            model_type = model_labels_short[model_type],
            outcome = "OS"
          ))
          # PFS data
          plot_data <- rbind(plot_data, data.frame(
            time = rep(time_points, 2),
            survival = c(crp_pos$pfs, crp_neg$pfs),
            subgroup = rep(c("CRP+", "CRP-"), each = length(time_points)),
            distribution = dist,
            model_type = model_labels_short[model_type],
            outcome = "PFS"
          ))
        }
      }
    }

    # Set factor levels for ordering
    plot_data$model_type <- factor(plot_data$model_type,
                                    levels = c("Model A", "Model B-CRP", "Model C-CRP"))
    plot_data$outcome <- factor(plot_data$outcome, levels = c("OS", "PFS"))

    # Get KM data and expand to all model types for faceting
    km_os <- add_biomarker_km(data_complete, "crp", "OS")
    km_pfs <- add_biomarker_km(data_complete, "crp", "PFS")

    km_data <- data.frame()
    for (mt in crp_model_types) {
      if (!is.null(km_os)) {
        km_data <- rbind(km_data, km_os %>%
          mutate(model_type = model_labels_short[mt], outcome = "OS"))
      }
      if (!is.null(km_pfs)) {
        km_data <- rbind(km_data, km_pfs %>%
          mutate(model_type = model_labels_short[mt], outcome = "PFS"))
      }
    }
    km_data$model_type <- factor(km_data$model_type,
                                  levels = c("Model A", "Model B-CRP", "Model C-CRP"))
    km_data$outcome <- factor(km_data$outcome, levels = c("OS", "PFS"))

    # Split KM by group for separate linetypes
    km_pos <- km_data[km_data$group == "Biomarker+ (Exp)", ]
    km_neg <- km_data[km_data$group == "Biomarker- (Ctrl)", ]

    # Create faceted plot
    p <- ggplot(plot_data, aes(x = time, y = survival,
                                color = subgroup, linetype = distribution)) +
      geom_line(linewidth = 1) +
      geom_step(data = km_pos, aes(x = time, y = survival),
                color = "black", linetype = "solid", linewidth = 0.6,
                inherit.aes = FALSE) +
      geom_step(data = km_neg, aes(x = time, y = survival),
                color = "black", linetype = "dashed", linewidth = 0.6,
                inherit.aes = FALSE) +
      facet_grid(model_type ~ outcome) +
      scale_color_manual(values = c("CRP+" = "#E31A1C", "CRP-" = "#1F78B4"),
                         name = "Subgroup") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma", "Weibull PH"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Survival Probability") +
      theme_minimal() +
      theme(legend.position = "bottom",
            strip.text = element_text(size = 10, face = "bold"),
            panel.spacing = unit(1, "lines"))

    print(p)

  }, error = function(e) {
    cat("CRP multi-model comparison not available:", e$message, "\n")
  })
}
```

**Interpretation:** Compare CRP+ (red) and CRP- (blue) survival across model types. Model A shows mutually adjusted effects, Model B-CRP shows effects adjusted for other biomarker main effects, and Model C-CRP shows unadjusted single-biomarker effects. Substantial divergence between Model C and Models A/B would suggest confounding from other biomarkers.

```{r pagebreak-5, results='asis'}
cat("\\newpage\n")
```

## TLR Biomarker Strategy

```{r tlr-plots, fig.height=12, fig.width=10}
#| fig-cap: "TLR biomarker strategy: Model structure comparison across OS and PFS. Rows show Model A (Joint), Model B-TLR (Focused), and Model C-TLR (Single-biomarker). Colored lines: parametric predictions (red=TLR+, blue=TLR-; solid=Gamma, dashed=Weibull PH). Black step lines: Kaplan-Meier estimates (solid=biomarker+, dashed=biomarker-)."

if (exists("multi_predictions") && exists("time_points")) {

  tryCatch({
    # Define relevant model types for TLR
    tlr_model_types <- c("A", "B_tlr", "C_tlr")

    # Build plot data from multi_predictions
    plot_data <- data.frame()

    for (model_type in tlr_model_types) {
      for (dist in c("gamma", "weibullph")) {
        tlr_pos <- multi_predictions[[dist]][[model_type]][["tlr_pos"]]
        tlr_neg <- multi_predictions[[dist]][[model_type]][["tlr_neg"]]

        if (!is.null(tlr_pos) && !is.null(tlr_neg)) {
          # OS data
          plot_data <- rbind(plot_data, data.frame(
            time = rep(time_points, 2),
            survival = c(tlr_pos$os, tlr_neg$os),
            subgroup = rep(c("TLR+", "TLR-"), each = length(time_points)),
            distribution = dist,
            model_type = model_labels_short[model_type],
            outcome = "OS"
          ))
          # PFS data
          plot_data <- rbind(plot_data, data.frame(
            time = rep(time_points, 2),
            survival = c(tlr_pos$pfs, tlr_neg$pfs),
            subgroup = rep(c("TLR+", "TLR-"), each = length(time_points)),
            distribution = dist,
            model_type = model_labels_short[model_type],
            outcome = "PFS"
          ))
        }
      }
    }

    # Set factor levels for ordering
    plot_data$model_type <- factor(plot_data$model_type,
                                    levels = c("Model A", "Model B-TLR", "Model C-TLR"))
    plot_data$outcome <- factor(plot_data$outcome, levels = c("OS", "PFS"))

    # Get KM data and expand to all model types for faceting
    km_os <- add_biomarker_km(data_complete, "tlr", "OS")
    km_pfs <- add_biomarker_km(data_complete, "tlr", "PFS")

    km_data <- data.frame()
    for (mt in tlr_model_types) {
      if (!is.null(km_os)) {
        km_data <- rbind(km_data, km_os %>%
          mutate(model_type = model_labels_short[mt], outcome = "OS"))
      }
      if (!is.null(km_pfs)) {
        km_data <- rbind(km_data, km_pfs %>%
          mutate(model_type = model_labels_short[mt], outcome = "PFS"))
      }
    }
    km_data$model_type <- factor(km_data$model_type,
                                  levels = c("Model A", "Model B-TLR", "Model C-TLR"))
    km_data$outcome <- factor(km_data$outcome, levels = c("OS", "PFS"))

    # Split KM by group for separate linetypes
    km_pos <- km_data[km_data$group == "Biomarker+ (Exp)", ]
    km_neg <- km_data[km_data$group == "Biomarker- (Ctrl)", ]

    # Create faceted plot
    p <- ggplot(plot_data, aes(x = time, y = survival,
                                color = subgroup, linetype = distribution)) +
      geom_line(linewidth = 1) +
      geom_step(data = km_pos, aes(x = time, y = survival),
                color = "black", linetype = "solid", linewidth = 0.6,
                inherit.aes = FALSE) +
      geom_step(data = km_neg, aes(x = time, y = survival),
                color = "black", linetype = "dashed", linewidth = 0.6,
                inherit.aes = FALSE) +
      facet_grid(model_type ~ outcome) +
      scale_color_manual(values = c("TLR+" = "#E31A1C", "TLR-" = "#1F78B4"),
                         name = "Subgroup") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma", "Weibull PH"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Survival Probability") +
      theme_minimal() +
      theme(legend.position = "bottom",
            strip.text = element_text(size = 10, face = "bold"),
            panel.spacing = unit(1, "lines"))

    print(p)

  }, error = function(e) {
    cat("TLR multi-model comparison not available:", e$message, "\n")
  })
}
```

**Interpretation:** Compare TLR+ (red) and TLR- (blue) survival across model types. TLR (target lesion reduction) is an early response biomarker. Model stability across A, B, and C structures indicates robust predictive value.

```{r pagebreak-6, results='asis'}
cat("\\newpage\n")
```

## TMB_BRAF Biomarker Strategy

```{r tmb-braf-plots, fig.height=12, fig.width=10}
#| fig-cap: "TMB_BRAF biomarker strategy: Model structure comparison across OS and PFS. Rows show Model A (Joint), Model B-TMB (Focused), and Model C-TMB (Single-biomarker). Colored lines: parametric predictions (red=TMB_BRAF+, blue=TMB_BRAF-; solid=Gamma, dashed=Weibull PH). Black step lines: Kaplan-Meier estimates (solid=biomarker+, dashed=biomarker-)."

if (exists("multi_predictions") && exists("time_points")) {

  tryCatch({
    # Define relevant model types for TMB_BRAF
    tmb_model_types <- c("A", "B_tmb", "C_tmb")

    # Build plot data from multi_predictions
    plot_data <- data.frame()

    for (model_type in tmb_model_types) {
      for (dist in c("gamma", "weibullph")) {
        tmb_pos <- multi_predictions[[dist]][[model_type]][["tmb_braf_pos"]]
        tmb_neg <- multi_predictions[[dist]][[model_type]][["tmb_braf_neg"]]

        if (!is.null(tmb_pos) && !is.null(tmb_neg)) {
          # OS data
          plot_data <- rbind(plot_data, data.frame(
            time = rep(time_points, 2),
            survival = c(tmb_pos$os, tmb_neg$os),
            subgroup = rep(c("TMB_BRAF+", "TMB_BRAF-"), each = length(time_points)),
            distribution = dist,
            model_type = model_labels_short[model_type],
            outcome = "OS"
          ))
          # PFS data
          plot_data <- rbind(plot_data, data.frame(
            time = rep(time_points, 2),
            survival = c(tmb_pos$pfs, tmb_neg$pfs),
            subgroup = rep(c("TMB_BRAF+", "TMB_BRAF-"), each = length(time_points)),
            distribution = dist,
            model_type = model_labels_short[model_type],
            outcome = "PFS"
          ))
        }
      }
    }

    # Set factor levels for ordering
    plot_data$model_type <- factor(plot_data$model_type,
                                    levels = c("Model A", "Model B-TMB", "Model C-TMB"))
    plot_data$outcome <- factor(plot_data$outcome, levels = c("OS", "PFS"))

    # Get KM data and expand to all model types for faceting
    km_os <- add_biomarker_km(data_complete, "tmb_braf", "OS")
    km_pfs <- add_biomarker_km(data_complete, "tmb_braf", "PFS")

    km_data <- data.frame()
    for (mt in tmb_model_types) {
      if (!is.null(km_os)) {
        km_data <- rbind(km_data, km_os %>%
          mutate(model_type = model_labels_short[mt], outcome = "OS"))
      }
      if (!is.null(km_pfs)) {
        km_data <- rbind(km_data, km_pfs %>%
          mutate(model_type = model_labels_short[mt], outcome = "PFS"))
      }
    }
    km_data$model_type <- factor(km_data$model_type,
                                  levels = c("Model A", "Model B-TMB", "Model C-TMB"))
    km_data$outcome <- factor(km_data$outcome, levels = c("OS", "PFS"))

    # Split KM by group for separate linetypes
    km_pos <- km_data[km_data$group == "Biomarker+ (Exp)", ]
    km_neg <- km_data[km_data$group == "Biomarker- (Ctrl)", ]

    # Create faceted plot
    p <- ggplot(plot_data, aes(x = time, y = survival,
                                color = subgroup, linetype = distribution)) +
      geom_line(linewidth = 1) +
      geom_step(data = km_pos, aes(x = time, y = survival),
                color = "black", linetype = "solid", linewidth = 0.6,
                inherit.aes = FALSE) +
      geom_step(data = km_neg, aes(x = time, y = survival),
                color = "black", linetype = "dashed", linewidth = 0.6,
                inherit.aes = FALSE) +
      facet_grid(model_type ~ outcome) +
      scale_color_manual(values = c("TMB_BRAF+" = "#E31A1C", "TMB_BRAF-" = "#1F78B4"),
                         name = "Subgroup") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma", "Weibull PH"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Survival Probability") +
      theme_minimal() +
      theme(legend.position = "bottom",
            strip.text = element_text(size = 10, face = "bold"),
            panel.spacing = unit(1, "lines"))

    print(p)

  }, error = function(e) {
    cat("TMB_BRAF multi-model comparison not available:", e$message, "\n")
  })
}
```

**Interpretation:** Compare TMB_BRAF+ (red) and TMB_BRAF- (blue) survival across model types. TMB_BRAF is a genomic biomarker combining high tumor mutational burden and BRAF mutation status. Divergence between model structures may indicate correlation with other biomarkers.

```{r pagebreak-7, results='asis'}
cat("\\newpage\n")
```

# Strategy Comparison

The following figures compare biomarker-guided treatment strategies against control, showing how population-weighted survival predictions vary across model structure types. Each biomarker strategy is shown separately to assess sensitivity to model specification.

## CRP Strategy: Model Structure Comparison

```{r crp-strategy-comparison, fig.height=10, fig.width=8}
#| fig-cap: "CRP strategy comparison across model structure types. Each line shows population-weighted survival for CRP-guided treatment allocation using different model specifications. Solid lines = Gamma, dashed lines = Weibull PH."

if (exists("multi_predictions") && exists("time_points")) {

  tryCatch({
    # Build strategy data
    strategy_data <- data.frame()

    # Control (from Model A - same for all)
    for (dist in c("gamma", "weibullph")) {
      ctrl_pred <- multi_predictions[[dist]][["A"]]$control
      if (!is.null(ctrl_pred)) {
        strategy_data <- rbind(strategy_data, data.frame(
          time = time_points,
          os = ctrl_pred$os,
          pfs = ctrl_pred$pfs,
          strategy = "Control",
          distribution = dist
        ))
      }
    }

    # CRP strategy from each model type
    for (model_type in c("A", "B_crp", "C_crp")) {
      for (dist in c("gamma", "weibullph")) {
        crp_pred <- multi_predictions[[dist]][[model_type]][["crp_weighted"]]
        if (!is.null(crp_pred)) {
          strategy_data <- rbind(strategy_data, data.frame(
            time = time_points,
            os = crp_pred$os,
            pfs = crp_pred$pfs,
            strategy = paste("CRP -", model_labels_short[model_type]),
            distribution = dist
          ))
        }
      }
    }

    strategy_data$strategy <- factor(strategy_data$strategy,
      levels = c("Control", "CRP - Model A", "CRP - Model B-CRP", "CRP - Model C-CRP"))

    # OS plot
    p_os <- ggplot(strategy_data, aes(x = time, y = os,
                                       color = strategy, linetype = distribution)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = c(
        "Control" = "gray50",
        "CRP - Model A" = "#E69F00",
        "CRP - Model B-CRP" = "#56B4E9",
        "CRP - Model C-CRP" = "#0072B2"
      ), name = "Strategy") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma (solid)", "Weibull PH (dashed)"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Overall Survival Probability",
           title = "CRP Strategy: Overall Survival") +
      theme(legend.position = "bottom", legend.box = "vertical") +
      guides(color = guide_legend(order = 1, nrow = 1),
             linetype = guide_legend(order = 2, override.aes = list(linewidth = 1.2)))

    # PFS plot
    p_pfs <- ggplot(strategy_data, aes(x = time, y = pfs,
                                        color = strategy, linetype = distribution)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = c(
        "Control" = "gray50",
        "CRP - Model A" = "#E69F00",
        "CRP - Model B-CRP" = "#56B4E9",
        "CRP - Model C-CRP" = "#0072B2"
      ), name = "Strategy") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma (solid)", "Weibull PH (dashed)"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Progression-Free Survival Probability",
           title = "CRP Strategy: Progression-Free Survival") +
      theme(legend.position = "bottom", legend.box = "vertical") +
      guides(color = guide_legend(order = 1, nrow = 1),
             linetype = guide_legend(order = 2, override.aes = list(linewidth = 1.2)))

    gridExtra::grid.arrange(p_os, p_pfs, ncol = 1)

  }, error = function(e) {
    cat("CRP strategy comparison not available:", e$message, "\n")
  })
}
```

## TLR Strategy: Model Structure Comparison

```{r tlr-strategy-comparison, fig.height=10, fig.width=8}
#| fig-cap: "TLR strategy comparison across model structure types. Each line shows population-weighted survival for TLR-guided treatment allocation using different model specifications. Solid lines = Gamma, dashed lines = Weibull PH."

if (exists("multi_predictions") && exists("time_points")) {

  tryCatch({
    # Build strategy data
    strategy_data <- data.frame()

    # Control (from Model A - same for all)
    for (dist in c("gamma", "weibullph")) {
      ctrl_pred <- multi_predictions[[dist]][["A"]]$control
      if (!is.null(ctrl_pred)) {
        strategy_data <- rbind(strategy_data, data.frame(
          time = time_points,
          os = ctrl_pred$os,
          pfs = ctrl_pred$pfs,
          strategy = "Control",
          distribution = dist
        ))
      }
    }

    # TLR strategy from each model type
    for (model_type in c("A", "B_tlr", "C_tlr")) {
      for (dist in c("gamma", "weibullph")) {
        tlr_pred <- multi_predictions[[dist]][[model_type]][["tlr_weighted"]]
        if (!is.null(tlr_pred)) {
          strategy_data <- rbind(strategy_data, data.frame(
            time = time_points,
            os = tlr_pred$os,
            pfs = tlr_pred$pfs,
            strategy = paste("TLR -", model_labels_short[model_type]),
            distribution = dist
          ))
        }
      }
    }

    strategy_data$strategy <- factor(strategy_data$strategy,
      levels = c("Control", "TLR - Model A", "TLR - Model B-TLR", "TLR - Model C-TLR"))

    # OS plot
    p_os <- ggplot(strategy_data, aes(x = time, y = os,
                                       color = strategy, linetype = distribution)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = c(
        "Control" = "gray50",
        "TLR - Model A" = "#E69F00",
        "TLR - Model B-TLR" = "#009E73",
        "TLR - Model C-TLR" = "#D55E00"
      ), name = "Strategy") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma (solid)", "Weibull PH (dashed)"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Overall Survival Probability",
           title = "TLR Strategy: Overall Survival") +
      theme(legend.position = "bottom", legend.box = "vertical") +
      guides(color = guide_legend(order = 1, nrow = 1),
             linetype = guide_legend(order = 2, override.aes = list(linewidth = 1.2)))

    # PFS plot
    p_pfs <- ggplot(strategy_data, aes(x = time, y = pfs,
                                        color = strategy, linetype = distribution)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = c(
        "Control" = "gray50",
        "TLR - Model A" = "#E69F00",
        "TLR - Model B-TLR" = "#009E73",
        "TLR - Model C-TLR" = "#D55E00"
      ), name = "Strategy") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma (solid)", "Weibull PH (dashed)"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Progression-Free Survival Probability",
           title = "TLR Strategy: Progression-Free Survival") +
      theme(legend.position = "bottom", legend.box = "vertical") +
      guides(color = guide_legend(order = 1, nrow = 1),
             linetype = guide_legend(order = 2, override.aes = list(linewidth = 1.2)))

    gridExtra::grid.arrange(p_os, p_pfs, ncol = 1)

  }, error = function(e) {
    cat("TLR strategy comparison not available:", e$message, "\n")
  })
}
```

## TMB_BRAF Strategy: Model Structure Comparison

```{r tmb-strategy-comparison, fig.height=10, fig.width=8}
#| fig-cap: "TMB_BRAF strategy comparison across model structure types. Each line shows population-weighted survival for TMB_BRAF-guided treatment allocation using different model specifications. Solid lines = Gamma, dashed lines = Weibull PH."

if (exists("multi_predictions") && exists("time_points")) {

  tryCatch({
    # Build strategy data
    strategy_data <- data.frame()

    # Control (from Model A - same for all)
    for (dist in c("gamma", "weibullph")) {
      ctrl_pred <- multi_predictions[[dist]][["A"]]$control
      if (!is.null(ctrl_pred)) {
        strategy_data <- rbind(strategy_data, data.frame(
          time = time_points,
          os = ctrl_pred$os,
          pfs = ctrl_pred$pfs,
          strategy = "Control",
          distribution = dist
        ))
      }
    }

    # TMB_BRAF strategy from each model type
    for (model_type in c("A", "B_tmb", "C_tmb")) {
      for (dist in c("gamma", "weibullph")) {
        tmb_pred <- multi_predictions[[dist]][[model_type]][["tmb_braf_weighted"]]
        if (!is.null(tmb_pred)) {
          strategy_data <- rbind(strategy_data, data.frame(
            time = time_points,
            os = tmb_pred$os,
            pfs = tmb_pred$pfs,
            strategy = paste("TMB -", model_labels_short[model_type]),
            distribution = dist
          ))
        }
      }
    }

    strategy_data$strategy <- factor(strategy_data$strategy,
      levels = c("Control", "TMB - Model A", "TMB - Model B-TMB", "TMB - Model C-TMB"))

    # OS plot
    p_os <- ggplot(strategy_data, aes(x = time, y = os,
                                       color = strategy, linetype = distribution)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = c(
        "Control" = "gray50",
        "TMB - Model A" = "#E69F00",
        "TMB - Model B-TMB" = "#F0E442",
        "TMB - Model C-TMB" = "#CC79A7"
      ), name = "Strategy") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma (solid)", "Weibull PH (dashed)"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Overall Survival Probability",
           title = "TMB_BRAF Strategy: Overall Survival") +
      theme(legend.position = "bottom", legend.box = "vertical") +
      guides(color = guide_legend(order = 1, nrow = 1),
             linetype = guide_legend(order = 2, override.aes = list(linewidth = 1.2)))

    # PFS plot
    p_pfs <- ggplot(strategy_data, aes(x = time, y = pfs,
                                        color = strategy, linetype = distribution)) +
      geom_line(linewidth = 1) +
      scale_color_manual(values = c(
        "Control" = "gray50",
        "TMB - Model A" = "#E69F00",
        "TMB - Model B-TMB" = "#F0E442",
        "TMB - Model C-TMB" = "#CC79A7"
      ), name = "Strategy") +
      scale_linetype_manual(values = c("gamma" = "solid", "weibullph" = "dashed"),
                            labels = c("Gamma (solid)", "Weibull PH (dashed)"),
                            name = "Distribution") +
      scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
      scale_x_continuous(breaks = seq(0, max(time_points), by = 52)) +
      labs(x = "Time (weeks)", y = "Progression-Free Survival Probability",
           title = "TMB_BRAF Strategy: Progression-Free Survival") +
      theme(legend.position = "bottom", legend.box = "vertical") +
      guides(color = guide_legend(order = 1, nrow = 1),
             linetype = guide_legend(order = 2, override.aes = list(linewidth = 1.2)))

    gridExtra::grid.arrange(p_os, p_pfs, ncol = 1)

  }, error = function(e) {
    cat("TMB_BRAF strategy comparison not available:", e$message, "\n")
  })
}
```

## Life-Years by Strategy and Model Structure

The following table shows life-years (area under the survival curve) for each treatment strategy across all model structure types. This allows comparison of how model structure choice affects life-year estimates.

```{r strategy-life-years-table}
#| tbl-cap: "Life-Years by Strategy and Model Structure Type (Gamma / Weibull PH)"

if (exists("multi_predictions") && exists("time_points")) {

  # Function to calculate life-years (restricted mean survival time)
  calc_ly <- function(survival_probs, time_points) {
    time_years <- time_points / 52
    n <- length(time_years)
    sum((survival_probs[-n] + survival_probs[-1]) / 2 * diff(time_years))
  }

  tryCatch({
    # Get control baseline from Model A (same for all model types)
    ctrl_gamma <- multi_predictions$gamma$A$control
    ctrl_weibull <- multi_predictions$weibullph$A$control

    ctrl_os_g <- calc_ly(ctrl_gamma$os, time_points)
    ctrl_os_w <- calc_ly(ctrl_weibull$os, time_points)
    ctrl_pfs_g <- calc_ly(ctrl_gamma$pfs, time_points)
    ctrl_pfs_w <- calc_ly(ctrl_weibull$pfs, time_points)

    # Build expanded table
    ly_table <- data.frame(
      Strategy = "Control",
      `Model Type` = "—",
      `OS LY (G/W)` = paste(round(ctrl_os_g, 2), "/", round(ctrl_os_w, 2)),
      `PFS LY (G/W)` = paste(round(ctrl_pfs_g, 2), "/", round(ctrl_pfs_w, 2)),
      `OS Gain` = "—",
      `PFS Gain` = "—",
      check.names = FALSE,
      stringsAsFactors = FALSE
    )

    # Biomarker-model mapping: which models are relevant for each biomarker
    biomarker_model_map <- list(
      crp = c("A", "B_crp", "C_crp"),
      tlr = c("A", "B_tlr", "C_tlr"),
      tmb_braf = c("A", "B_tmb", "C_tmb")
    )

    biomarker_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB_BRAF")

    for (biomarker in names(biomarker_model_map)) {
      for (model_type in biomarker_model_map[[biomarker]]) {

        gamma_pred <- multi_predictions$gamma[[model_type]][[paste0(biomarker, "_weighted")]]
        weibull_pred <- multi_predictions$weibullph[[model_type]][[paste0(biomarker, "_weighted")]]

        if (!is.null(gamma_pred) && !is.null(weibull_pred)) {
          os_g <- calc_ly(gamma_pred$os, time_points)
          os_w <- calc_ly(weibull_pred$os, time_points)
          pfs_g <- calc_ly(gamma_pred$pfs, time_points)
          pfs_w <- calc_ly(weibull_pred$pfs, time_points)

          ly_table <- rbind(ly_table, data.frame(
            Strategy = biomarker_labels[biomarker],
            `Model Type` = model_labels_short[model_type],
            `OS LY (G/W)` = paste(round(os_g, 2), "/", round(os_w, 2)),
            `PFS LY (G/W)` = paste(round(pfs_g, 2), "/", round(pfs_w, 2)),
            `OS Gain` = sprintf("%+.2f / %+.2f", os_g - ctrl_os_g, os_w - ctrl_os_w),
            `PFS Gain` = sprintf("%+.2f / %+.2f", pfs_g - ctrl_pfs_g, pfs_w - ctrl_pfs_w),
            check.names = FALSE,
            stringsAsFactors = FALSE
          ))
        }
      }
    }

    if (knitr::is_latex_output()) {
      kable(ly_table, format = "latex", booktabs = TRUE, row.names = FALSE) %>%
        kableExtra::kable_styling(font_size = 8, latex_options = c("striped", "HOLD_position", "scale_down"))
    } else {
      kable(ly_table, format = "html", row.names = FALSE) %>%
        kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
    }

  }, error = function(e) {
    cat("Strategy life-years data not available:", e$message, "\n")
  })

} else {
  cat("Multi-model predictions not available for life-years calculation.\n")
}
```

*Note: Life-years are calculated as the area under the survival curve (restricted mean survival time) over the model time horizon. G = Gamma distribution, W = Weibull PH distribution. Gains are relative to the Control strategy. Population-weighted values account for biomarker prevalence in each strategy.*

```{r pagebreak-8, results='asis'}
cat("\\newpage\n")
```

# Summary

This report compared three model structure types for parametric survival analysis:

- **Model A (Joint)**: All biomarkers and interactions in one model - provides mutually adjusted estimates and is used for the primary cost-effectiveness analysis
- **Model B (Focused)**: Each biomarker modeled with its treatment interaction while controlling for other biomarker main effects. CRP and TMB/BRAF share a formula with both interaction terms; TLR has a separate formula with only its interaction term. Allows biomarker-specific model selection
- **Model C (Single-biomarker)**: Each biomarker modeled independently - simplest specification but may overestimate effects if biomarkers are correlated

## Key Findings

- **Distribution selection**: Gamma distribution selected by AIC for both OS and PFS; Weibull PH retained as reference
- **Model fit**: All seven model structure types show reasonable fit based on AIC; Model A has lowest AIC (best fit) due to additional parameters
- **Interaction effects**: Treatment-biomarker interaction hazard ratios show [consistency/variation] across model types, indicating [robust/sensitive] effect estimates
- **Model structure impact**: Comparison across Models A, B, and C assesses sensitivity to biomarker correlation and model complexity
- **Validation**: Visual comparison with Kaplan-Meier estimates confirms adequate model fit across all parametric distributions
- **Clinical implications**: Model A (Joint) provides the most comprehensive assessment for cost-effectiveness analysis by accounting for all biomarker interactions simultaneously

## Recommendations

- Use **Model A (Joint)** for primary cost-effectiveness analysis as it provides mutually adjusted biomarker interaction estimates
- Consider **Model B (Focused)** variants if biomarker-specific model selection is desired
- **Model C (Single-biomarker)** results should be interpreted cautiously if biomarkers are correlated, as effect estimates may be biased

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.3
