---
title: "Scenario Analyses: Effect of Utility Assumptions"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r scenario-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries in specific order
if (!require("pacman")) install.packages("pacman")

# Load rlang explicitly first
library(rlang)

# Then load other packages
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/psa_functions.R",
  "scripts/R/functions/multi_model_cea.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r setup-global-variables, include=FALSE}
# 02 - Setup and Global Variables
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

# Re-source functions after script 02
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/psa_functions.R",
  "scripts/R/functions/multi_model_cea.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r biomarker-strategies, include=FALSE}
# 03 - Biomarker Strategies
if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}
```

```{r survival-analysis, include=FALSE}
# 06 - Parametric Survival Analysis
if (!exists("USE_BOTH_MODELS")) {
  USE_BOTH_MODELS <- 0  # Default to age- and sex-adjusted models only
}

if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
}

# Display model structure configuration
model_structure_name <- c("joint", "focused", "separate")[MODEL_STRUCTURE + 1]
cat("Model structure: MODEL_STRUCTURE =", MODEL_STRUCTURE, "(", model_structure_name, ")\n")
```

```{r input-parameters, include=FALSE}
# 07 - Base Case Input Parameters
if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
}

# Store base case parameters for reference
l_params_basecase <- l_params_base
```

```{r sampling-setup, include=FALSE}
# 08 - Sampling Setup (needed for PSA)
if (file.exists(here("scripts/R/analysis/08_sampling.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/08_sampling.R"))))
  cat("Sampling setup completed successfully\n")
}

# Store base case parameter distributions for reference
param_distributions_basecase <- param_distributions
```

```{r model-structures, include=FALSE}
# Define model structures for multi-model analysis
model_structures <- list(
  A = list(
    value = 0,
    name = "Joint (All-in-One)",
    label = "joint",
    formula = "~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx",
    desc = "All biomarkers and all treatment interactions in a single model"
  ),
  B = list(
    value = 1,
    name = "Focused",
    label = "focused",
    formula = "~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx",
    desc = "CRP and TMB/BRAF as main effects + BOTH interactions (TLR excluded)"
  ),
  C = list(
    value = 2,
    name = "Separate",
    label = "separate",
    formula = "~ Age + sex + Rx + [biomarker]:Rx",
    desc = "Only one biomarker and its treatment interaction per model"
  )
)

# Check cache availability for each model
cache_status <- sapply(c(0, 1, 2), function(ms) {
  label <- c("joint", "focused", "separate")[ms + 1]
  cache_file <- here("data", "tidy",
                     paste0("sampling_models_n", n_samples, "_full_", label, ".rds"))
  file.exists(cache_file)
})
names(cache_status) <- c("A", "B", "C")

cat("Sampling cache status:\n")
for (model_letter in c("A", "B", "C")) {
  status <- if (cache_status[model_letter]) "FOUND" else "MISSING"
  cat("  Model", model_letter, "(", model_structures[[model_letter]]$name, "):", status, "\n")
}

# Store original MODEL_STRUCTURE to restore later
original_model_structure <- MODEL_STRUCTURE
```

```{r multi-model-helper, include=FALSE}
#' Run scenario analysis for all three model structures
#'
#' @param l_params_scenario List of scenario-specific parameters (with u_np, u_p)
#' @param verbose Logical, print progress messages
#' @return List containing results for all 3 models
run_scenario_for_all_models <- function(l_params_scenario, verbose = TRUE) {
  model_configs <- get_model_configs()
  results_list <- list()

  for (model_name in names(model_configs)) {
    config <- model_configs[[model_name]]

    if (verbose) {
      cat("Running", config$label, "...\n")
    }

    # Set MODEL_STRUCTURE globally
    MODEL_STRUCTURE <<- config$structure

    # Re-source survival analysis to update predictions for this model structure
    suppressMessages(suppressWarnings({
      source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
      source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
    }))

    # Update with scenario-specific utility parameters
    l_params <- l_params_base
    l_params$u_np <- l_params_scenario$u_np
    l_params$u_p <- l_params_scenario$u_p

    # Run model
    base_results <- model_fun(l_params)

    # Calculate ICERs
    icer_obj <- dampack::calculate_icers(
      cost = base_results$Cost,
      effect = base_results$Effect,
      strategies = base_results$Strategy
    )

    results_list[[model_name]] <- list(
      base_results = base_results,
      icer_obj = icer_obj,
      config = config
    )

    if (verbose) {
      cat("  Completed:", model_name, "\n")
    }
  }

  return(results_list)
}

#' Create multi-model comparison table for a scenario
#'
#' @param all_results List of results from run_scenario_for_all_models()
#' @return Data frame with comparison across models
create_scenario_comparison_table <- function(all_results) {
  strategies <- all_results[[1]]$base_results$Strategy

  comparison_df <- data.frame(Strategy = strategies)

  for (model_name in names(all_results)) {
    result <- all_results[[model_name]]
    short_label <- result$config$short_label

    comparison_df[[paste0("Cost_", short_label)]] <- result$base_results$Cost
    comparison_df[[paste0("Effect_", short_label)]] <- result$base_results$Effect

    icer_df <- as.data.frame(result$icer_obj)
    comparison_df[[paste0("ICER_", short_label)]] <- icer_df$ICER
  }

  return(comparison_df)
}
```

# Overview

This scenario analysis examines the impact of utility assumptions on the cost-effectiveness of biomarker-guided immunotherapy strategies for metastatic MSS/pMMR colorectal cancer.

## Utility Scenarios

We compare three utility scenarios:

1. **Base Case**: Standard utility values (u_np = 0.9077, u_p = 0.9005)
2. **Scenario 1 - Unadjusted Life Years**: All utilities set to 1.0 (no quality adjustment)
3. **Scenario 2 - Alternative Utilities**: Lower utility values (u_np = 0.73, u_p = 0.59)

## Model Structures

Each scenario is analyzed using three alternative model structures for the survival analysis:

```{r model-structure-table}
model_structure_df <- data.frame(
  Model = c("Model A", "Model B", "Model C"),
  Name = c("Joint (All-in-One)", "Focused", "Separate"),
  Formula = c(
    "Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx",
    "Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx",
    "Age + sex + Rx + [biomarker]:Rx"
  ),
  Description = c(
    "All biomarkers and all treatment interactions in a single model",
    "CRP and TMB/BRAF as main effects + BOTH interactions (TLR excluded)",
    "Only one biomarker and its treatment interaction per model"
  )
)

knitr::kable(model_structure_df,
             col.names = c("Model", "Name", "Formula Pattern", "Description"),
             align = c("l", "l", "l", "l"),
             booktabs = TRUE,
             caption = "Model Structures for Survival Analysis") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::column_spec(3, width = "5cm") %>%
  kableExtra::column_spec(4, width = "5cm")
```

For each scenario, we present deterministic cost-effectiveness results comparing all three model structures, followed by probabilistic sensitivity analysis.

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Base Case: Standard Utility Values

This analysis uses standard utility values derived from the IPD dataset (u_np = 0.9077, u_p = 0.9005).

```{r basecase-params}
# Display base case parameter values
basecase_params_table <- data.frame(
  Parameter = c("u_np (Non-progressed utility)", "u_p (Progressed utility)"),
  Value = c(l_params_basecase$u_np, l_params_basecase$u_p),
  Description = c(
    "Utility value in non-progressed disease state",
    "Utility value in progressed disease state"
  )
)

knitr::kable(basecase_params_table,
             digits = 4,
             col.names = c("Parameter", "Value", "Description"),
             align = c("l", "r", "l"),
             booktabs = TRUE,
             caption = "Base Case Utility Parameter Values") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r basecase-analysis, include=FALSE}
# Re-source functions to ensure they're available
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R",
                    "scripts/R/functions/multi_model_cea.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Run base case analysis for all three models
cat("Running base case analysis for all model structures...\n")
all_basecase_results <- run_scenario_for_all_models(l_params_basecase, verbose = TRUE)

# Store for later comparison
base_results <- all_basecase_results$Model_A$base_results
icer_obj <- all_basecase_results$Model_A$icer_obj
```

## Multi-Model Comparison

```{r basecase-multimodel-table}
# Create comparison table across all models
comparison_df <- data.frame(
  Strategy = all_basecase_results$Model_A$base_results$Strategy
)

for (model_name in names(all_basecase_results)) {
  result <- all_basecase_results[[model_name]]
  short_label <- result$config$short_label

  comparison_df[[paste0("Cost_", short_label)]] <- result$base_results$Cost
  comparison_df[[paste0("QALY_", short_label)]] <- result$base_results$Effect

  icer_df <- as.data.frame(result$icer_obj)
  comparison_df[[paste0("ICER_", short_label)]] <- icer_df$ICER
}

# Format for display
display_df <- comparison_df
display_df$Strategy <- c("Standard of Care", "CRP-guided", "TLR-guided", "TMB/BRAF-guided")

for (col in names(display_df)[grep("^Cost_", names(display_df))]) {
  display_df[[col]] <- scales::dollar(display_df[[col]], accuracy = 1)
}
for (col in names(display_df)[grep("^QALY_", names(display_df))]) {
  display_df[[col]] <- sprintf("%.3f", display_df[[col]])
}
for (col in names(display_df)[grep("^ICER_", names(display_df))]) {
  display_df[[col]] <- ifelse(is.na(display_df[[col]]), "Reference",
                               scales::dollar(display_df[[col]], accuracy = 1))
}

# Rename columns for display
names(display_df) <- c("Strategy",
                        "Cost (A)", "QALY (A)", "ICER (A)",
                        "Cost (B)", "QALY (B)", "ICER (B)",
                        "Cost (C)", "QALY (C)", "ICER (C)")

knitr::kable(display_df,
             align = c("l", rep("r", 9)),
             booktabs = TRUE,
             caption = "Base Case Cost-Effectiveness Results by Model Structure") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::add_header_above(c(" " = 1,
                                  "Model A: Joint" = 3,
                                  "Model B: Focused" = 3,
                                  "Model C: Separate" = 3))
```

```{r basecase-optimal-strategy}
# Determine optimal strategy for each model
optimal_strategies_base <- data.frame(
  Model = character(),
  Optimal_Strategy = character(),
  NMB = numeric(),
  stringsAsFactors = FALSE
)

for (model_name in names(all_basecase_results)) {
  result <- all_basecase_results[[model_name]]
  nmb <- result$base_results$Effect * WTP - result$base_results$Cost
  optimal_idx <- which.max(nmb)

  strategy_name <- result$base_results$Strategy[optimal_idx]
  strategy_display <- case_when(
    strategy_name == "control" ~ "Standard of Care",
    strategy_name == "crp" ~ "CRP-guided",
    strategy_name == "tlr" ~ "TLR-guided",
    strategy_name == "tmb_braf" ~ "TMB/BRAF-guided",
    TRUE ~ strategy_name
  )

  optimal_strategies_base <- rbind(optimal_strategies_base, data.frame(
    Model = result$config$label,
    Optimal_Strategy = strategy_display,
    NMB = nmb[optimal_idx],
    stringsAsFactors = FALSE
  ))
}

optimal_strategies_base$NMB <- scales::dollar(optimal_strategies_base$NMB, accuracy = 1)

knitr::kable(optimal_strategies_base,
             col.names = c("Model Structure", "Optimal Strategy", paste0("NMB at WTP=", scales::dollar(WTP))),
             align = c("l", "l", "r"),
             booktabs = TRUE,
             caption = "Optimal Strategy by Model Structure - Base Case") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

## Cost-Effectiveness Planes

```{r basecase-ce-planes, fig.height=10, fig.width=10}
#| fig-cap: "Cost-Effectiveness Planes by Model Structure - Base Case"

# Create CE planes for each model
ce_plots <- list()
for (model_name in names(all_basecase_results)) {
  result <- all_basecase_results[[model_name]]

  ce_plots[[model_name]] <- plot(result$icer_obj,
                                  txtsize = 10,
                                  currency = "EUR",
                                  effect_units = "QALYs",
                                  label = "all") +
    ggtitle(result$config$label) +
    theme(plot.title = element_text(size = 12, face = "bold"))
}

# Arrange plots in grid
gridExtra::grid.arrange(
  ce_plots$Model_A, ce_plots$Model_B, ce_plots$Model_C,
  ncol = 2, nrow = 2
)
```

## Probabilistic Sensitivity Analysis (Model A)

PSA results are presented for Model A (Joint) only, as this is the primary model structure. The deterministic results above show comparison across all three model structures.

```{r basecase-psa, include=FALSE}
# Ensure Model A (joint) structure is set for PSA
MODEL_STRUCTURE <<- 0

# Re-source functions and survival analysis for Model A
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

suppressMessages(suppressWarnings({
  source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
  source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
}))

# Set number of simulations
if (!exists("n_sim")) {
  n_sim <- 1000
}

# Generate PSA samples for Base Case
cat("Generating PSA samples for Base Case:", n_sim, "simulations\n")
psa_params_basecase <- generate_psa_samples(param_distributions_basecase, n_sim)

# Run PSA for Base Case
cat("Starting PSA for Base Case\n")
psa_results_basecase <- run_psa_analysis(
  psa_params = psa_params_basecase,
  l_params_base = l_params_basecase,
  param_distributions = param_distributions_basecase,
  strategies = strategies,
  time_horizon = time_horizon,
  cl = cl,
  n_sim = n_sim
)

# Create PSA object
psa_obj_basecase <- dampack::make_psa_obj(
  cost = as.data.frame(psa_results_basecase$cost),
  effect = as.data.frame(psa_results_basecase$effect),
  strategies = strategies,
  currency = "€"
)

# PSA summary
psa_summary_base <- summary(psa_obj_basecase, calc_sds = TRUE)
```

**Table: PSA Summary Statistics - Base Case (Model A)**

```{r basecase-psa-summary}
knitr::kable(psa_summary_base,
             digits = 2,
             booktabs = TRUE,
             caption = "PSA Summary - Base Case (Model A: Joint)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r basecase-psa-scatter}
#| fig-cap: "PSA Scatterplot - Base Case (Model A: Joint)"

psa_plot_base <- plot(psa_obj_basecase, 
                      frontier = TRUE, 
                      points = TRUE,
                      alpha = 0.4,
                      txtsize = 11,
                      currency = "€",
                      effect_units = "QALYs")
print(psa_plot_base)
```

```{r basecase-ceac}
#| fig-cap: "Cost-Effectiveness Acceptability Curve - Base Case (Model A: Joint)"

c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
ceac_obj_base <- ceac(c_wtp, psa_obj_basecase)
ceac_plot_base <- plot(ceac_obj_base, frontier = TRUE, currency = "€", txtsize = 11)
print(ceac_plot_base)
```

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Scenario 1: Unadjusted Life Years (All Utilities = 1.0)

In this scenario, we analyze life years gained without quality-of-life adjustments, providing insight into the survival benefit independent of quality-of-life considerations.

```{r scenario1-params}
# Create Scenario 1 parameter set: All utilities = 1.0
l_params_scenario1 <- l_params_basecase
l_params_scenario1$u_np <- 1.0
l_params_scenario1$u_p <- 1.0

# For Scenario 1, utilities are fixed at 1.0 (no uncertainty)
# Create uniform distribution that always returns 1.0
param_distributions_scenario1 <- param_distributions_basecase

# Override utility distributions to be fixed at 1.0
param_distributions_scenario1$u_np <- list(dist = "unif", min = 1.0, max = 1.0)
param_distributions_scenario1$u_p <- list(dist = "unif", min = 1.0, max = 1.0)

# Display parameter modifications
scenario1_params_table <- data.frame(
  Parameter = c("u_np (Non-progressed utility)", "u_p (Progressed utility)"),
  Base_Case = c(l_params_basecase$u_np, l_params_basecase$u_p),
  Scenario_1 = c(l_params_scenario1$u_np, l_params_scenario1$u_p),
  Difference = c(
    l_params_scenario1$u_np - l_params_basecase$u_np,
    l_params_scenario1$u_p - l_params_basecase$u_p
  )
)

knitr::kable(scenario1_params_table,
             digits = 4,
             col.names = c("Parameter", "Base Case", "Scenario 1", "Difference"),
             align = c("l", "r", "r", "r"),
             booktabs = TRUE,
             caption = "Utility Parameter Modifications for Scenario 1") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario1-analysis, include=FALSE}
# Re-source functions to ensure they're available
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R",
                    "scripts/R/functions/multi_model_cea.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Run Scenario 1 analysis for all three models
cat("Running Scenario 1 analysis for all model structures...\n")
all_scenario1_results <- run_scenario_for_all_models(l_params_scenario1, verbose = TRUE)

# Store for later comparison
base_results_scenario1 <- all_scenario1_results$Model_A$base_results
icer_obj_scenario1 <- all_scenario1_results$Model_A$icer_obj
```

## Multi-Model Comparison

```{r scenario1-multimodel-table}
# Create comparison table across all models
comparison_df_s1 <- data.frame(
  Strategy = all_scenario1_results$Model_A$base_results$Strategy
)

for (model_name in names(all_scenario1_results)) {
  result <- all_scenario1_results[[model_name]]
  short_label <- result$config$short_label

  comparison_df_s1[[paste0("Cost_", short_label)]] <- result$base_results$Cost
  comparison_df_s1[[paste0("LY_", short_label)]] <- result$base_results$Effect

  icer_df <- as.data.frame(result$icer_obj)
  comparison_df_s1[[paste0("ICER_", short_label)]] <- icer_df$ICER
}

# Format for display
display_df_s1 <- comparison_df_s1
display_df_s1$Strategy <- c("Standard of Care", "CRP-guided", "TLR-guided", "TMB/BRAF-guided")

for (col in names(display_df_s1)[grep("^Cost_", names(display_df_s1))]) {
  display_df_s1[[col]] <- scales::dollar(display_df_s1[[col]], accuracy = 1)
}
for (col in names(display_df_s1)[grep("^LY_", names(display_df_s1))]) {
  display_df_s1[[col]] <- sprintf("%.3f", display_df_s1[[col]])
}
for (col in names(display_df_s1)[grep("^ICER_", names(display_df_s1))]) {
  display_df_s1[[col]] <- ifelse(is.na(display_df_s1[[col]]), "Reference",
                                  scales::dollar(display_df_s1[[col]], accuracy = 1))
}

# Rename columns for display
names(display_df_s1) <- c("Strategy",
                           "Cost (A)", "LY (A)", "ICER (A)",
                           "Cost (B)", "LY (B)", "ICER (B)",
                           "Cost (C)", "LY (C)", "ICER (C)")

knitr::kable(display_df_s1,
             align = c("l", rep("r", 9)),
             booktabs = TRUE,
             caption = "Scenario 1 Cost-Effectiveness Results by Model Structure (Unadjusted Life Years)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::add_header_above(c(" " = 1,
                                  "Model A: Joint" = 3,
                                  "Model B: Focused" = 3,
                                  "Model C: Separate" = 3))
```

```{r scenario1-optimal-strategy}
# Determine optimal strategy for each model
optimal_strategies_s1 <- data.frame(
  Model = character(),
  Optimal_Strategy = character(),
  NMB = numeric(),
  stringsAsFactors = FALSE
)

for (model_name in names(all_scenario1_results)) {
  result <- all_scenario1_results[[model_name]]
  nmb <- result$base_results$Effect * WTP - result$base_results$Cost
  optimal_idx <- which.max(nmb)

  strategy_name <- result$base_results$Strategy[optimal_idx]
  strategy_display <- case_when(
    strategy_name == "control" ~ "Standard of Care",
    strategy_name == "crp" ~ "CRP-guided",
    strategy_name == "tlr" ~ "TLR-guided",
    strategy_name == "tmb_braf" ~ "TMB/BRAF-guided",
    TRUE ~ strategy_name
  )

  optimal_strategies_s1 <- rbind(optimal_strategies_s1, data.frame(
    Model = result$config$label,
    Optimal_Strategy = strategy_display,
    NMB = nmb[optimal_idx],
    stringsAsFactors = FALSE
  ))
}

optimal_strategies_s1$NMB <- scales::dollar(optimal_strategies_s1$NMB, accuracy = 1)

knitr::kable(optimal_strategies_s1,
             col.names = c("Model Structure", "Optimal Strategy", paste0("NMB at WTP=", scales::dollar(WTP))),
             align = c("l", "l", "r"),
             booktabs = TRUE,
             caption = "Optimal Strategy by Model Structure - Scenario 1") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

## Cost-Effectiveness Planes

```{r scenario1-ce-planes, fig.height=10, fig.width=10}
#| fig-cap: "Cost-Effectiveness Planes by Model Structure - Scenario 1 (Unadjusted Life Years)"

# Create CE planes for each model
ce_plots_s1 <- list()
for (model_name in names(all_scenario1_results)) {
  result <- all_scenario1_results[[model_name]]

  ce_plots_s1[[model_name]] <- plot(result$icer_obj,
                                     txtsize = 10,
                                     currency = "EUR",
                                     effect_units = "Life Years",
                                     label = "all") +
    ggtitle(result$config$label) +
    theme(plot.title = element_text(size = 12, face = "bold"))
}

# Arrange plots in grid
gridExtra::grid.arrange(
  ce_plots_s1$Model_A, ce_plots_s1$Model_B, ce_plots_s1$Model_C,
  ncol = 2, nrow = 2
)
```

## Probabilistic Sensitivity Analysis (Model A)

PSA results are presented for Model A (Joint) only.

```{r scenario1-psa, include=FALSE}
# Ensure Model A (joint) structure is set for PSA
MODEL_STRUCTURE <<- 0

# Re-source functions and survival analysis for Model A
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

suppressMessages(suppressWarnings({
  source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
  source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
}))

# Generate PSA samples for Scenario 1
cat("Generating PSA samples for Scenario 1:", n_sim, "simulations\n")
psa_params_scenario1 <- generate_psa_samples(param_distributions_scenario1, n_sim)

# Run PSA for Scenario 1
cat("Starting PSA for Scenario 1\n")
psa_results_scenario1 <- run_psa_analysis(
  psa_params = psa_params_scenario1,
  l_params_base = l_params_scenario1,
  param_distributions = param_distributions_scenario1,
  strategies = strategies,
  time_horizon = time_horizon,
  cl = cl,
  n_sim = n_sim
)

# Create PSA object
psa_obj_scenario1 <- dampack::make_psa_obj(
  cost = as.data.frame(psa_results_scenario1$cost),
  effect = as.data.frame(psa_results_scenario1$effect),
  strategies = strategies,
  currency = "€"
)

# PSA summary
psa_summary_s1 <- summary(psa_obj_scenario1, calc_sds = TRUE)
```

**Table: PSA Summary Statistics - Scenario 1 (Model A)**

```{r scenario1-psa-summary}
knitr::kable(psa_summary_s1,
             digits = 2,
             booktabs = TRUE,
             caption = "PSA Summary - Scenario 1 (Model A: Joint, Unadjusted Life Years)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r scenario1-psa-scatter}
#| fig-cap: "PSA Scatterplot - Scenario 1 (Model A: Joint, Unadjusted Life Years)"

psa_plot_s1 <- plot(psa_obj_scenario1,
                    frontier = TRUE,
                    points = TRUE,
                    alpha = 0.4,
                    txtsize = 11,
                    currency = "€",
                    effect_units = "Life Years")
print(psa_plot_s1)
```

```{r scenario1-ceac}
#| fig-cap: "Cost-Effectiveness Acceptability Curve - Scenario 1 (Model A: Joint)"

ceac_obj_s1 <- ceac(c_wtp, psa_obj_scenario1)
ceac_plot_s1 <- plot(ceac_obj_s1, frontier = TRUE, currency = "€", txtsize = 11)
print(ceac_plot_s1)
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# Scenario 2: Alternative Utility Values (u_np = 0.73, u_p = 0.59)

This scenario examines the cost-effectiveness under alternative, lower utility assumptions that may reflect more conservative estimates of quality of life. They are derived from the EQ-5D index score of the CORRECT trial (Grothey et al. Lancet 2013, as cited by Gourzoulidis et al. J Comp Effect Res 2018)-

```{r scenario2-params}
# Helper function to calculate beta parameters (from 08_sampling.R)
get_beta_params <- function(mean_val, cv) {
  var_val <- (mean_val * cv)^2
  alpha <- mean_val * (mean_val * (1 - mean_val) / var_val - 1)
  beta <- (1 - mean_val) * (mean_val * (1 - mean_val) / var_val - 1)
  return(list(shape1 = alpha, shape2 = beta))
}

# Create Scenario 2 parameter set: Alternative utilities
l_params_scenario2 <- l_params_basecase
l_params_scenario2$u_np <- 0.73
l_params_scenario2$u_p <- 0.59

# Create distributions for Scenario 2 PSA
cv_utilities <- 0.15  # Standard 15% CV for utilities
param_distributions_scenario2 <- param_distributions_basecase

# Override utility distributions with alternative values
dist_u_np_scenario2 <- c(list(dist = "beta"), get_beta_params(0.73, cv_utilities))
dist_u_p_scenario2 <- c(list(dist = "beta"), get_beta_params(0.59, cv_utilities))

param_distributions_scenario2$u_np <- dist_u_np_scenario2
param_distributions_scenario2$u_p <- dist_u_p_scenario2

# Display parameter modifications
scenario2_params_table <- data.frame(
  Parameter = c("u_np (Non-progressed utility)", "u_p (Progressed utility)"),
  Base_Case = c(l_params_basecase$u_np, l_params_basecase$u_p),
  Scenario_2 = c(l_params_scenario2$u_np, l_params_scenario2$u_p),
  Difference = c(
    l_params_scenario2$u_np - l_params_basecase$u_np,
    l_params_scenario2$u_p - l_params_basecase$u_p
  ),
  Pct_Change = c(
    100 * (l_params_scenario2$u_np - l_params_basecase$u_np) / l_params_basecase$u_np,
    100 * (l_params_scenario2$u_p - l_params_basecase$u_p) / l_params_basecase$u_p
  )
)

knitr::kable(scenario2_params_table,
             digits = 4,
             col.names = c("Parameter", "Base Case", "Scenario 2", "Difference", "% Change"),
             align = c("l", "r", "r", "r", "r"),
             booktabs = TRUE,
             caption = "Utility Parameter Modifications for Scenario 2") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

**Beta Distribution Parameters for PSA:**

```{r scenario2-beta-params}
beta_params_table <- data.frame(
  Parameter = c("u_np", "u_p"),
  Mean = c(0.73, 0.59),
  CV = c(cv_utilities, cv_utilities),
  Alpha = c(dist_u_np_scenario2$shape1, dist_u_p_scenario2$shape1),
  Beta = c(dist_u_np_scenario2$shape2, dist_u_p_scenario2$shape2)
)

knitr::kable(beta_params_table,
             digits = 3,
             booktabs = TRUE,
             caption = "Beta Distribution Parameters for Scenario 2 PSA") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario2-analysis, include=FALSE}
# Re-source functions to ensure they're available
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R",
                    "scripts/R/functions/multi_model_cea.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Run Scenario 2 analysis for all three models
cat("Running Scenario 2 analysis for all model structures...\n")
all_scenario2_results <- run_scenario_for_all_models(l_params_scenario2, verbose = TRUE)

# Store for later comparison
base_results_scenario2 <- all_scenario2_results$Model_A$base_results
icer_obj_scenario2 <- all_scenario2_results$Model_A$icer_obj
```

## Multi-Model Comparison

```{r scenario2-multimodel-table}
# Create comparison table across all models
comparison_df_s2 <- data.frame(
  Strategy = all_scenario2_results$Model_A$base_results$Strategy
)

for (model_name in names(all_scenario2_results)) {
  result <- all_scenario2_results[[model_name]]
  short_label <- result$config$short_label

  comparison_df_s2[[paste0("Cost_", short_label)]] <- result$base_results$Cost
  comparison_df_s2[[paste0("QALY_", short_label)]] <- result$base_results$Effect

  icer_df <- as.data.frame(result$icer_obj)
  comparison_df_s2[[paste0("ICER_", short_label)]] <- icer_df$ICER
}

# Format for display
display_df_s2 <- comparison_df_s2
display_df_s2$Strategy <- c("Standard of Care", "CRP-guided", "TLR-guided", "TMB/BRAF-guided")

for (col in names(display_df_s2)[grep("^Cost_", names(display_df_s2))]) {
  display_df_s2[[col]] <- scales::dollar(display_df_s2[[col]], accuracy = 1)
}
for (col in names(display_df_s2)[grep("^QALY_", names(display_df_s2))]) {
  display_df_s2[[col]] <- sprintf("%.3f", display_df_s2[[col]])
}
for (col in names(display_df_s2)[grep("^ICER_", names(display_df_s2))]) {
  display_df_s2[[col]] <- ifelse(is.na(display_df_s2[[col]]), "Reference",
                                  scales::dollar(display_df_s2[[col]], accuracy = 1))
}

# Rename columns for display
names(display_df_s2) <- c("Strategy",
                           "Cost (A)", "QALY (A)", "ICER (A)",
                           "Cost (B)", "QALY (B)", "ICER (B)",
                           "Cost (C)", "QALY (C)", "ICER (C)")

knitr::kable(display_df_s2,
             align = c("l", rep("r", 9)),
             booktabs = TRUE,
             caption = "Scenario 2 Cost-Effectiveness Results by Model Structure (Alternative Utilities)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::add_header_above(c(" " = 1,
                                  "Model A: Joint" = 3,
                                  "Model B: Focused" = 3,
                                  "Model C: Separate" = 3))
```

```{r scenario2-optimal-strategy}
# Determine optimal strategy for each model
optimal_strategies_s2 <- data.frame(
  Model = character(),
  Optimal_Strategy = character(),
  NMB = numeric(),
  stringsAsFactors = FALSE
)

for (model_name in names(all_scenario2_results)) {
  result <- all_scenario2_results[[model_name]]
  nmb <- result$base_results$Effect * WTP - result$base_results$Cost
  optimal_idx <- which.max(nmb)

  strategy_name <- result$base_results$Strategy[optimal_idx]
  strategy_display <- case_when(
    strategy_name == "control" ~ "Standard of Care",
    strategy_name == "crp" ~ "CRP-guided",
    strategy_name == "tlr" ~ "TLR-guided",
    strategy_name == "tmb_braf" ~ "TMB/BRAF-guided",
    TRUE ~ strategy_name
  )

  optimal_strategies_s2 <- rbind(optimal_strategies_s2, data.frame(
    Model = result$config$label,
    Optimal_Strategy = strategy_display,
    NMB = nmb[optimal_idx],
    stringsAsFactors = FALSE
  ))
}

optimal_strategies_s2$NMB <- scales::dollar(optimal_strategies_s2$NMB, accuracy = 1)

knitr::kable(optimal_strategies_s2,
             col.names = c("Model Structure", "Optimal Strategy", paste0("NMB at WTP=", scales::dollar(WTP))),
             align = c("l", "l", "r"),
             booktabs = TRUE,
             caption = "Optimal Strategy by Model Structure - Scenario 2") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

## Cost-Effectiveness Planes

```{r scenario2-ce-planes, fig.height=10, fig.width=10}
#| fig-cap: "Cost-Effectiveness Planes by Model Structure - Scenario 2 (Alternative Utilities)"

# Create CE planes for each model
ce_plots_s2 <- list()
for (model_name in names(all_scenario2_results)) {
  result <- all_scenario2_results[[model_name]]

  ce_plots_s2[[model_name]] <- plot(result$icer_obj,
                                     txtsize = 10,
                                     currency = "EUR",
                                     effect_units = "QALYs",
                                     label = "all") +
    ggtitle(result$config$label) +
    theme(plot.title = element_text(size = 12, face = "bold"))
}

# Arrange plots in grid
gridExtra::grid.arrange(
  ce_plots_s2$Model_A, ce_plots_s2$Model_B, ce_plots_s2$Model_C,
  ncol = 2, nrow = 2
)
```

## Probabilistic Sensitivity Analysis (Model A)

PSA results are presented for Model A (Joint) only.

```{r scenario2-psa, include=FALSE}
# Ensure Model A (joint) structure is set for PSA
MODEL_STRUCTURE <<- 0

# Re-source functions and survival analysis for Model A
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

suppressMessages(suppressWarnings({
  source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
  source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
}))

# Generate PSA samples for Scenario 2
cat("Generating PSA samples for Scenario 2:", n_sim, "simulations\n")
psa_params_scenario2 <- generate_psa_samples(param_distributions_scenario2, n_sim)

# Run PSA for Scenario 2
cat("Starting PSA for Scenario 2\n")
psa_results_scenario2 <- run_psa_analysis(
  psa_params = psa_params_scenario2,
  l_params_base = l_params_scenario2,
  param_distributions = param_distributions_scenario2,
  strategies = strategies,
  time_horizon = time_horizon,
  cl = cl,
  n_sim = n_sim
)

# Create PSA object
psa_obj_scenario2 <- dampack::make_psa_obj(
  cost = as.data.frame(psa_results_scenario2$cost),
  effect = as.data.frame(psa_results_scenario2$effect),
  strategies = strategies,
  currency = "€"
)

# PSA summary
psa_summary_s2 <- summary(psa_obj_scenario2, calc_sds = TRUE)
```

**Table: PSA Summary Statistics - Scenario 2 (Model A)**

```{r scenario2-psa-summary}
knitr::kable(psa_summary_s2,
             digits = 2,
             booktabs = TRUE,
             caption = "PSA Summary - Scenario 2 (Model A: Joint, Alternative Utilities)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r scenario2-psa-scatter}
#| fig-cap: "PSA Scatterplot - Scenario 2 (Model A: Joint, Alternative Utilities)"

psa_plot_s2 <- plot(psa_obj_scenario2,
                    frontier = TRUE,
                    points = TRUE,
                    alpha = 0.4,
                    txtsize = 11,
                    currency = "€",
                    effect_units = "QALYs")
print(psa_plot_s2)
```

```{r scenario2-ceac}
#| fig-cap: "Cost-Effectiveness Acceptability Curve - Scenario 2 (Model A: Joint)"

ceac_obj_s2 <- ceac(c_wtp, psa_obj_scenario2)
ceac_plot_s2 <- plot(ceac_obj_s2, frontier = TRUE, currency = "€", txtsize = 11)
print(ceac_plot_s2)
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Comparative Analysis Across All Scenarios

## Utility Parameter Summary

```{r utility-comparison-table}
utility_comparison <- data.frame(
  Scenario = c("Base Case", "Scenario 1 (Life Years)", "Scenario 2 (Alternative)"),
  u_np = c(l_params_basecase$u_np, l_params_scenario1$u_np, l_params_scenario2$u_np),
  u_p = c(l_params_basecase$u_p, l_params_scenario1$u_p, l_params_scenario2$u_p),
  Description = c(
    "Standard utility values from literature",
    "No quality adjustment (all utilities = 1.0)",
    "Lower/conservative utility estimates"
  )
)

knitr::kable(utility_comparison,
             digits = 4,
             col.names = c("Scenario", "u_np", "u_p", "Description"),
             align = c("l", "r", "r", "l"),
             booktabs = TRUE,
             caption = "Utility Parameter Values Across Scenarios") %>%
  kableExtra::column_spec(1, width = "3.5cm") %>%
  kableExtra::column_spec(2:3, width = "1.5cm") %>%
  kableExtra::column_spec(4, width = "6cm") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

## Cross-Model, Cross-Scenario Optimal Strategy Comparison

```{r cross-model-optimal-strategy}
# Create a comprehensive optimal strategy table across all scenarios and models
cross_comparison <- data.frame(
  Scenario = character(),
  Model = character(),
  Optimal_Strategy = character(),
  NMB = numeric(),
  stringsAsFactors = FALSE
)

# Helper function to get optimal strategy
get_optimal <- function(results, wtp) {
  nmb <- results$base_results$Effect * wtp - results$base_results$Cost
  optimal_idx <- which.max(nmb)
  strategy_name <- results$base_results$Strategy[optimal_idx]
  strategy_display <- case_when(
    strategy_name == "control" ~ "Standard of Care",
    strategy_name == "crp" ~ "CRP-guided",
    strategy_name == "tlr" ~ "TLR-guided",
    strategy_name == "tmb_braf" ~ "TMB/BRAF-guided",
    TRUE ~ strategy_name
  )
  return(list(strategy = strategy_display, nmb = nmb[optimal_idx]))
}

# Process all scenarios and models
scenario_results <- list(
  "Base Case" = all_basecase_results,
  "Scenario 1" = all_scenario1_results,
  "Scenario 2" = all_scenario2_results
)

for (scenario_name in names(scenario_results)) {
  scenario_data <- scenario_results[[scenario_name]]
  for (model_name in names(scenario_data)) {
    result <- scenario_data[[model_name]]
    opt <- get_optimal(result, WTP)
    cross_comparison <- rbind(cross_comparison, data.frame(
      Scenario = scenario_name,
      Model = result$config$label,
      Optimal_Strategy = opt$strategy,
      NMB = opt$nmb,
      stringsAsFactors = FALSE
    ))
  }
}

# Pivot to wide format
cross_wide <- cross_comparison %>%
  mutate(NMB_formatted = scales::dollar(NMB, accuracy = 1)) %>%
  select(Scenario, Model, Optimal_Strategy) %>%
  pivot_wider(names_from = Model, values_from = Optimal_Strategy)

knitr::kable(cross_wide,
             align = c("l", "l", "l", "l"),
             col.names = c("Scenario", "Model A: Joint", "Model B: Focused", "Model C: Separate"),
             booktabs = TRUE,
             caption = paste0("Optimal Strategy by Scenario and Model Structure (WTP = ", scales::dollar(WTP), ")")) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

## Model A Results Across Scenarios

The following tables and plots compare results across scenarios for Model A (Joint), which is the primary model structure.

```{r comparison-table}
# Combine results from all three scenarios (Model A)
comparison_results <- data.frame(
  Scenario = rep(c("Base Case", "Scenario 1", "Scenario 2"), each = length(strategies)),
  Strategy = rep(strategies, 3),
  Cost = c(base_results$Cost, base_results_scenario1$Cost, base_results_scenario2$Cost),
  Effect = c(base_results$Effect, base_results_scenario1$Effect, base_results_scenario2$Effect)
)

# Add NMB at WTP threshold
comparison_results$NMB <- comparison_results$Effect * WTP - comparison_results$Cost

# Format for display
comparison_display <- comparison_results %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    Cost = scales::dollar(Cost, accuracy = 1),
    Effect = sprintf("%.3f", Effect),
    NMB = scales::dollar(NMB, accuracy = 1)
  )

knitr::kable(comparison_display,
             align = c("l", "l", "r", "r", "r"),
             col.names = c("Scenario", "Strategy", "Cost (EUR)", "Effect", "NMB (EUR)"),
             booktabs = TRUE,
             caption = "Cost-Effectiveness Results Comparison Across Scenarios (Model A)") %>%
  kableExtra::collapse_rows(columns = 1, valign = "top") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r effect-comparison-plot}
#| fig-cap: "Comparison of Effects Across Scenarios by Strategy (Model A)"
#| fig-height: 7
#| fig-width: 10

effect_comparison_data <- comparison_results %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    Scenario = factor(Scenario, levels = c("Base Case", "Scenario 1", "Scenario 2"))
  )

p_effect <- ggplot(effect_comparison_data, aes(x = Strategy, y = Effect, fill = Scenario)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = c("Base Case" = "#2E86AB",
                                "Scenario 1" = "#A23B72",
                                "Scenario 2" = "#F18F01")) +
  labs(
    title = "Effect Comparison Across Scenarios (Model A)",
    subtitle = "Base Case (QALYs), Scenario 1 (Life Years), Scenario 2 (Alternative QALYs)",
    x = "Strategy",
    y = "Effect (QALYs / Life Years)",
    fill = "Scenario"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

print(p_effect)
```

```{r icer-comparison}
# Extract ICERs from each scenario (Model A)
icer_base <- as.data.frame(icer_obj) %>%
  select(Strategy, ICER) %>%
  mutate(Scenario = "Base Case")

icer_s1 <- as.data.frame(icer_obj_scenario1) %>%
  select(Strategy, ICER) %>%
  mutate(Scenario = "Scenario 1")

icer_s2 <- as.data.frame(icer_obj_scenario2) %>%
  select(Strategy, ICER) %>%
  mutate(Scenario = "Scenario 2")

# Combine
icer_comparison <- rbind(icer_base, icer_s1, icer_s2) %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    ICER_formatted = ifelse(!is.na(ICER),
                            scales::dollar(ICER, accuracy = 1),
                            "Reference")
  ) %>%
  select(Scenario, Strategy, ICER_formatted) %>%
  pivot_wider(names_from = Scenario, values_from = ICER_formatted)

knitr::kable(icer_comparison,
             align = c("l", "r", "r", "r"),
             col.names = c("Strategy", "Base Case", "Scenario 1", "Scenario 2"),
             booktabs = TRUE,
             caption = "ICER Comparison Across Scenarios - Model A (EUR per QALY/Life Year)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r nmb-comparison-plot}
#| fig-cap: "Net Monetary Benefit Comparison Across Scenarios (Model A, WTP = EUR 51,000)"
#| fig-height: 7
#| fig-width: 10

nmb_comparison_data <- comparison_results %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    Scenario = factor(Scenario, levels = c("Base Case", "Scenario 1", "Scenario 2"))
  )

p_nmb <- ggplot(nmb_comparison_data, aes(x = Strategy, y = NMB, fill = Scenario)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = c("Base Case" = "#2E86AB",
                                "Scenario 1" = "#A23B72",
                                "Scenario 2" = "#F18F01")) +
  scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K")) +
  labs(
    title = "Net Monetary Benefit Comparison Across Scenarios (Model A)",
    subtitle = paste0("Willingness-to-Pay Threshold: EUR ", scales::comma(WTP)),
    x = "Strategy",
    y = "Net Monetary Benefit (EUR)",
    fill = "Scenario"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

print(p_nmb)
```

```{r pagebreak-5, results='asis'}
cat("\\newpage\n")
```

# Robustness Assessment

## Cross-Model Consistency

```{r robustness-assessment}
# Check if optimal strategies are consistent across models within each scenario
robustness_summary <- cross_comparison %>%
  group_by(Scenario) %>%
  summarize(
    n_models = n(),
    unique_strategies = n_distinct(Optimal_Strategy),
    consistent = n_distinct(Optimal_Strategy) == 1,
    strategies_list = paste(unique(Optimal_Strategy), collapse = ", "),
    .groups = "drop"
  )

# Summary table
robustness_display <- robustness_summary %>%
  mutate(
    Consistency = ifelse(consistent, "Consistent", "Varies by model"),
    Strategies = strategies_list
  ) %>%
  select(Scenario, Consistency, Strategies)

knitr::kable(robustness_display,
             align = c("l", "l", "l"),
             col.names = c("Scenario", "Model Consistency", "Optimal Strategy(ies)"),
             booktabs = TRUE,
             caption = "Robustness of Optimal Strategy Across Model Structures") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r robustness-interpretation, results='asis'}
# Provide interpretation
all_consistent <- all(robustness_summary$consistent)

if (all_consistent) {
  cat("\n**Robust Conclusion:** The optimal strategy is consistent across all three model structures within each scenario, suggesting the conclusions are robust to the choice of survival model specification.\n")
} else {
  varying_scenarios <- robustness_summary$Scenario[!robustness_summary$consistent]
  cat("\n**Note:** The optimal strategy varies by model structure in the following scenario(s):", paste(varying_scenarios, collapse = ", "), ". This suggests some sensitivity to the survival model specification.\n")
}
```

## Cross-Scenario Consistency

```{r cross-scenario-consistency}
# Check if optimal strategies are consistent across scenarios within each model
scenario_consistency <- cross_comparison %>%
  group_by(Model) %>%
  summarize(
    n_scenarios = n(),
    unique_strategies = n_distinct(Optimal_Strategy),
    consistent = n_distinct(Optimal_Strategy) == 1,
    strategies_list = paste(unique(Optimal_Strategy), collapse = ", "),
    .groups = "drop"
  )

scenario_display <- scenario_consistency %>%
  mutate(
    Consistency = ifelse(consistent, "Consistent", "Varies by scenario"),
    Strategies = strategies_list
  ) %>%
  select(Model, Consistency, Strategies)

knitr::kable(scenario_display,
             align = c("l", "l", "l"),
             col.names = c("Model Structure", "Scenario Consistency", "Optimal Strategy(ies)"),
             booktabs = TRUE,
             caption = "Sensitivity of Optimal Strategy to Utility Assumptions by Model") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Summary

This scenario analysis examined the impact of utility assumptions on the METIMMOX-1 cost-effectiveness model across three alternative model structures:

- **Model A (Joint)**: All biomarkers and all treatment interactions in a single model
- **Model B (Focused)**: All biomarkers as main effects, one treatment interaction per model
- **Model C (Separate)**: Only one biomarker and its treatment interaction per model

Key findings:

1. **Deterministic results**: Multi-model comparison tables show how cost-effectiveness results vary across model structures within each scenario.

2. **Cross-model robustness**: The robustness assessment above indicates whether the optimal strategy is consistent across model structures.

3. **Scenario sensitivity**: The cross-scenario consistency analysis shows how sensitive conclusions are to utility assumptions for each model structure.

4. **PSA results**: Probabilistic sensitivity analysis was conducted for Model A (Joint) across all three scenarios to characterize decision uncertainty.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.0