---
title: "Scenario Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  # psa_functions supplies psa_failed_draw_policy(), used by the cache check below.
  funs = c("cea_helpers", "report_format", "psa_functions"),
  set_theme = FALSE
)

scenario_cache_file <- scenario_evppi_path()
if (!file.exists(scenario_cache_file)) {
  stop(
    "Full scenario cache not found: ", scenario_cache_file, ". Run ",
    "scripts/R/analysis/12_scenario_EVPPIs.R before rendering this report."
  )
}
scenario_cache <- readRDS(scenario_cache_file)
cache_source <- basename(scenario_cache_file)

# Compare against the accessor rather than a literal. The identifier is bumped
# whenever the failed-draw policy changes (it is currently
# "cyclic_other_models_drop_unreplaced_v2"), and a hard-coded copy here silently
# rejects every freshly generated cache.
if (!is.null(scenario_cache) &&
    !identical(scenario_cache$failed_draw_policy, psa_failed_draw_policy())) {
  cached_policy <- scenario_cache$failed_draw_policy
  if (is.null(cached_policy)) cached_policy <- "none"
  stop(
    "Scenario cache uses failed-draw policy '", cached_policy,
    "' but this build expects '", psa_failed_draw_policy(),
    "'; rerun 12_scenario_EVPPIs.R before rendering this report."
  )
}

```

# Overview

This report summarizes scenario EVPPI and PSA outputs for the single joint economic model. It requires the full `scenario_evppi_results_{utility}.rds` cache generated by `12_scenario_EVPPIs.R`. EVPPI values are regression estimates (`voi::evppi()`, generalized additive models; Strong et al. 2014) reported with Monte Carlo standard errors; the Value of Information report describes the estimator. Rows prefixed `[GROUP]` are joint estimates for a parameter group and are never sums of single-parameter rows.

# Scenario Definitions

```{r scenario-table}
if (is.null(scenario_cache)) {
  cat("Scenario cache not found. Run scripts/R/analysis/12_scenario_EVPPIs.R before rendering this report.")
} else {
  scenarios <- scenario_cache$scenarios
  scenario_display <- scenarios %>%
    mutate(
      wtp = format_eur(wtp),
      c_drug_nivo = format_eur(c_drug_nivo)
    )

  knitr::kable(
    scenario_display,
    booktabs = TRUE,
    align = "l",
    caption = paste0("Scenario definitions loaded from ",
                     gsub("_", "\\\\_", cache_source))
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
}
```

# PSA Summary by Scenario

```{r scenario-psa}
if (!is.null(scenario_cache)) {
  scenario_rows <- lapply(names(scenario_cache$all_scenario_results), function(id) {
    result <- scenario_cache$all_scenario_results[[id]]
    psa_obj <- result$psa_obj
    info <- result$scenario_info

    if (is.null(psa_obj)) return(NULL)

    cost <- as.matrix(psa_obj$cost)
    effect <- if (!is.null(psa_obj$effect)) as.matrix(psa_obj$effect) else as.matrix(psa_obj$effectiveness)
    nmb <- effect * info$wtp - cost

    data.frame(
      Scenario = info$scenario_name,
      WTP = info$wtp,
      Strategy = psa_obj$strategies,
      Mean_Cost = colMeans(cost, na.rm = TRUE),
      Mean_QALY = colMeans(effect, na.rm = TRUE),
      Mean_NMB = colMeans(nmb, na.rm = TRUE),
      stringsAsFactors = FALSE
    )
  })

  scenario_psa <- bind_rows(scenario_rows) %>%
    mutate(
      Strategy = strategy_label(Strategy),
      WTP = format_eur(WTP),
      Mean_Cost = format_eur(Mean_Cost),
      Mean_QALY = sprintf("%.3f", Mean_QALY),
      Mean_NMB = format_eur(Mean_NMB)
    )

  knitr::kable(
    scenario_psa,
    booktabs = TRUE,
    align = c("l", "r", "l", "r", "r", "r"),
    col.names = c("Scenario", "WTP", "Strategy", "Mean Cost", "Mean QALYs", "Mean NMB"),
    caption = "PSA summary by scenario"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
}
```

# Scenario EVPPI

```{r scenario-evppi}
if (!is.null(scenario_cache) &&
    !is.null(scenario_cache$evppi_all_scenarios) &&
    nrow(scenario_cache$evppi_all_scenarios) > 0) {
  evppi_all <- scenario_cache$evppi_all_scenarios
  if (!"evppi_se" %in% names(evppi_all)) evppi_all$evppi_se <- NA_real_
  if (!"evppi_population_millions" %in% names(evppi_all)) {
    evppi_all$evppi_population_millions <- NA_real_
  }

  evppi_display <- evppi_all %>%
    filter(is.finite(evppi)) %>%
    group_by(scenario_name, wtp) %>%
    slice_max(evppi, n = 5, with_ties = FALSE) %>%
    ungroup() %>%
    mutate(
      WTP = format_eur(wtp),
      EVPPI = format_eur(evppi, accuracy = 0.01),
      SE = format_eur(evppi_se, accuracy = 0.01),
      `Percent of EVPI` = ifelse(is.finite(evppi_percent_of_evpi),
                                 sprintf("%.1f%%", evppi_percent_of_evpi), "--"),
      `Population EVPPI` = ifelse(
        is.finite(evppi_population_millions),
        paste0("EUR ", sprintf("%.2f", evppi_population_millions), "M"),
        "--"
      )
    ) %>%
    select(Scenario = scenario_name, WTP, Parameter = parameter,
           EVPPI, SE, `Percent of EVPI`, `Population EVPPI`)

  knitr::kable(
    evppi_display,
    booktabs = TRUE,
    align = c("l", "r", "l", "r", "r", "r", "r"),
    caption = "Top EVPPI parameters and groups by scenario (regression estimates with Monte Carlo SE)"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
} else if (!is.null(scenario_cache)) {
  cat("Scenario cache was found, but no EVPPI rows were available.")
}
```

```{r scenario-evppi-plot, fig.cap="Scenario EVPPI by parameter"}
if (!is.null(scenario_cache) &&
    !is.null(scenario_cache$evppi_all_scenarios) &&
    nrow(scenario_cache$evppi_all_scenarios) > 0) {
  plot_df <- scenario_cache$evppi_all_scenarios %>%
    filter(is.finite(evppi)) %>%
    group_by(scenario_name, parameter) %>%
    summarise(evppi = max(evppi, na.rm = TRUE), .groups = "drop")

  ggplot(plot_df, aes(x = evppi, y = reorder(parameter, evppi), fill = scenario_name)) +
    geom_col(position = "dodge") +
    scale_x_continuous(labels = scales::dollar_format(prefix = "EUR ")) +
    labs(x = "EVPPI", y = NULL, fill = "Scenario") +
    theme_minimal() +
    theme(legend.position = "bottom")
} else {
  ggplot() +
    annotate("text", x = 0.5, y = 0.5,
             label = "Scenario EVPPI cache not available", size = 5) +
    theme_void()
}
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 5.0
