---
title: "Scenario Analyses: Effect of Utility Assumptions"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r scenario-setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries in specific order
if (!require("pacman")) install.packages("pacman")

# Load rlang explicitly first
library(rlang)

# Then load other packages
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr, 
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv, 
  survival, survminer, gems, mstate, 
  tidyverse, xtable, darthtools, dampack, 
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() + 
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))

# Source helper functions (silently)
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/psa_functions.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r setup-global-variables, include=FALSE}
# 02 - Setup and Global Variables
if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
}

# Re-source functions after script 02
helper_functions <- c(
  "scripts/R/functions/model_fun.R",
  "scripts/R/functions/calculate_outcomes.R",
  "scripts/R/functions/psa_functions.R"
)

for (func_file in helper_functions) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}
```

```{r biomarker-strategies, include=FALSE}
# 03 - Biomarker Strategies
if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
}
```

```{r survival-analysis, include=FALSE}
# 06 - Parametric Survival Analysis
if (!exists("USE_BOTH_MODELS")) {
  USE_BOTH_MODELS <- 0  # Default to age- and sex-adjusted models only
}

if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
}
```

```{r input-parameters, include=FALSE}
# 07 - Base Case Input Parameters
if (file.exists(here("scripts/R/analysis/07_basecase_input_parameters.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
}

# Store base case parameters for reference
l_params_basecase <- l_params_base
```

```{r sampling-setup, include=FALSE}
# 08 - Sampling Setup (needed for PSA)
if (file.exists(here("scripts/R/analysis/08_sampling.R"))) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/08_sampling.R"))))
  cat("Sampling setup completed successfully\n")
}

# Store base case parameter distributions for reference
param_distributions_basecase <- param_distributions
```

# Overview

This scenario analysis examines the impact of utility assumptions on the cost-effectiveness of biomarker-guided immunotherapy strategies for metastatic MSS/pMMR colorectal cancer. We compare three scenarios:

1. **Base Case**: Standard utility values (u_np = 0.9077, u_p = 0.9005)
2. **Scenario 1 - Unadjusted Life Years**: All utilities set to 1.0 (no quality adjustment)
3. **Scenario 2 - Alternative Utilities**: Lower utility values (u_np = 0.73, u_p = 0.59)

For each scenario, we present deterministic cost-effectiveness results with ICERs and probabilistic sensitivity analysis results.

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Base Case: Standard Utility Values

This analysis uses standard utility values derived from the IPD dataset (u_np = 0.9077, u_p = 0.9005).

```{r basecase-params}
# Display base case parameter values
basecase_params_table <- data.frame(
  Parameter = c("u_np (Non-progressed utility)", "u_p (Progressed utility)"),
  Value = c(l_params_basecase$u_np, l_params_basecase$u_p),
  Description = c(
    "Utility value in non-progressed disease state",
    "Utility value in progressed disease state"
  )
)

knitr::kable(basecase_params_table,
             digits = 4,
             col.names = c("Parameter", "Value", "Description"),
             align = c("l", "r", "l"),
             booktabs = TRUE,
             caption = "Base Case Utility Parameter Values") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r basecase-analysis}
# Re-source functions to ensure they're available
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Run base case analysis
base_results <- model_fun(l_params_basecase)

# Calculate ICERs
icer_obj <- dampack::calculate_icers(
  cost = base_results$Cost,
  effect = base_results$Effect,
  strategies = base_results$Strategy
)

# Display results
icer_table_base <- as.data.frame(icer_obj)
icer_table_base$Cost <- scales::dollar(icer_table_base$Cost, accuracy = 1)
icer_table_base$Effect <- sprintf("%.3f", icer_table_base$Effect)
icer_table_base$ICER[!is.na(icer_table_base$ICER)] <- 
  scales::dollar(icer_table_base$ICER[!is.na(icer_table_base$ICER)], accuracy = 1)

knitr::kable(icer_table_base, 
             align = c("l", "r", "r", "r", "l"),
             booktabs = TRUE,
             caption = "Base Case Cost-Effectiveness Results") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r basecase-ce-plane}
#| fig-cap: "Cost-Effectiveness Plane - Base Case"

ce_plot_base <- plot(icer_obj, 
                     txtsize = 12,
                     currency = "€",
                     effect_units = "QALYs",
                     label = "all")
print(ce_plot_base)
```

```{r basecase-psa, include=FALSE}
# Re-source functions
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Set number of simulations
if (!exists("n_sim")) {
  n_sim <- 1000
}

# Generate PSA samples for Base Case
cat("Generating PSA samples for Base Case:", n_sim, "simulations\n")
psa_params_basecase <- generate_psa_samples(param_distributions_basecase, n_sim)

# Run PSA for Base Case
cat("Starting PSA for Base Case\n")
psa_results_basecase <- run_psa_analysis(
  psa_params = psa_params_basecase,
  l_params_base = l_params_basecase,
  param_distributions = param_distributions_basecase,
  strategies = strategies,
  time_horizon = time_horizon,
  cl = cl,
  n_sim = n_sim
)

# Create PSA object
psa_obj_basecase <- dampack::make_psa_obj(
  cost = as.data.frame(psa_results_basecase$cost),
  effect = as.data.frame(psa_results_basecase$effect),
  strategies = strategies,
  currency = "€"
)

# PSA summary
psa_summary_base <- summary(psa_obj_basecase, calc_sds = TRUE)
```

**Table: PSA Summary Statistics - Base Case**

```{r basecase-psa-summary}
knitr::kable(psa_summary_base,
             digits = 2,
             booktabs = TRUE,
             caption = "PSA Summary - Base Case") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r basecase-psa-scatter}
#| fig-cap: "PSA Scatterplot - Base Case"

psa_plot_base <- plot(psa_obj_basecase, 
                      frontier = TRUE, 
                      points = TRUE,
                      alpha = 0.4,
                      txtsize = 11,
                      currency = "€",
                      effect_units = "QALYs")
print(psa_plot_base)
```

```{r basecase-ceac}
#| fig-cap: "Cost-Effectiveness Acceptability Curve - Base Case"

c_wtp <- seq(from = 0, to = 2e5, by = 5e3)
ceac_obj_base <- ceac(c_wtp, psa_obj_basecase)
ceac_plot_base <- plot(ceac_obj_base, frontier = TRUE, currency = "€", txtsize = 11)
print(ceac_plot_base)
```

```{r pagebreak-2, results='asis'}
cat("\\newpage\n")
```

# Scenario 1: Unadjusted Life Years (All Utilities = 1.0)

In this scenario, we analyze life years gained without quality-of-life adjustments, providing insight into the survival benefit independent of quality-of-life considerations.

```{r scenario1-params}
# Create Scenario 1 parameter set: All utilities = 1.0
l_params_scenario1 <- l_params_basecase
l_params_scenario1$u_np <- 1.0
l_params_scenario1$u_p <- 1.0

# For Scenario 1, utilities are fixed at 1.0 (no uncertainty)
# Create uniform distribution that always returns 1.0
param_distributions_scenario1 <- param_distributions_basecase

# Override utility distributions to be fixed at 1.0
param_distributions_scenario1$u_np <- list(dist = "unif", min = 1.0, max = 1.0)
param_distributions_scenario1$u_p <- list(dist = "unif", min = 1.0, max = 1.0)

# Display parameter modifications
scenario1_params_table <- data.frame(
  Parameter = c("u_np (Non-progressed utility)", "u_p (Progressed utility)"),
  Base_Case = c(l_params_basecase$u_np, l_params_basecase$u_p),
  Scenario_1 = c(l_params_scenario1$u_np, l_params_scenario1$u_p),
  Difference = c(
    l_params_scenario1$u_np - l_params_basecase$u_np,
    l_params_scenario1$u_p - l_params_basecase$u_p
  )
)

knitr::kable(scenario1_params_table,
             digits = 4,
             col.names = c("Parameter", "Base Case", "Scenario 1", "Difference"),
             align = c("l", "r", "r", "r"),
             booktabs = TRUE,
             caption = "Utility Parameter Modifications for Scenario 1") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario1-basecase}
# Re-source functions to ensure they're available
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Run base case analysis for Scenario 1
base_results_scenario1 <- model_fun(l_params_scenario1)

# Calculate ICERs
icer_obj_scenario1 <- dampack::calculate_icers(
  cost = base_results_scenario1$Cost,
  effect = base_results_scenario1$Effect,
  strategies = base_results_scenario1$Strategy
)

# Display results
icer_table_s1 <- as.data.frame(icer_obj_scenario1)
icer_table_s1$Cost <- scales::dollar(icer_table_s1$Cost, accuracy = 1)
icer_table_s1$Effect <- sprintf("%.3f", icer_table_s1$Effect)
icer_table_s1$ICER[!is.na(icer_table_s1$ICER)] <- 
  scales::dollar(icer_table_s1$ICER[!is.na(icer_table_s1$ICER)], accuracy = 1)

knitr::kable(icer_table_s1, 
             align = c("l", "r", "r", "r", "l"),
             booktabs = TRUE,
             caption = "Scenario 1 Cost-Effectiveness Results (Unadjusted Life Years)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario1-ce-plane}
#| fig-cap: "Cost-Effectiveness Plane - Scenario 1 (Unadjusted Life Years)"

ce_plot_s1 <- plot(icer_obj_scenario1, 
                   txtsize = 12,
                   currency = "€",
                   effect_units = "Life Years",
                   label = "all")
print(ce_plot_s1)
```

```{r scenario1-psa, include=FALSE}
# Re-source functions
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Generate PSA samples for Scenario 1
cat("Generating PSA samples for Scenario 1:", n_sim, "simulations\n")
psa_params_scenario1 <- generate_psa_samples(param_distributions_scenario1, n_sim)

# Run PSA for Scenario 1
cat("Starting PSA for Scenario 1\n")
psa_results_scenario1 <- run_psa_analysis(
  psa_params = psa_params_scenario1,
  l_params_base = l_params_scenario1,
  param_distributions = param_distributions_scenario1,
  strategies = strategies,
  time_horizon = time_horizon,
  cl = cl,
  n_sim = n_sim
)

# Create PSA object
psa_obj_scenario1 <- dampack::make_psa_obj(
  cost = as.data.frame(psa_results_scenario1$cost),
  effect = as.data.frame(psa_results_scenario1$effect),
  strategies = strategies,
  currency = "€"
)

# PSA summary
psa_summary_s1 <- summary(psa_obj_scenario1, calc_sds = TRUE)
```

**Table: PSA Summary Statistics - Scenario 1**

```{r scenario1-psa-summary}
knitr::kable(psa_summary_s1,
             digits = 2,
             booktabs = TRUE,
             caption = "PSA Summary - Scenario 1 (Unadjusted Life Years)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r scenario1-psa-scatter}
#| fig-cap: "PSA Scatterplot - Scenario 1 (Unadjusted Life Years)"

psa_plot_s1 <- plot(psa_obj_scenario1, 
                    frontier = TRUE, 
                    points = TRUE,
                    alpha = 0.4,
                    txtsize = 11,
                    currency = "€",
                    effect_units = "Life Years")
print(psa_plot_s1)
```

```{r scenario1-ceac}
#| fig-cap: "Cost-Effectiveness Acceptability Curve - Scenario 1"

ceac_obj_s1 <- ceac(c_wtp, psa_obj_scenario1)
ceac_plot_s1 <- plot(ceac_obj_s1, frontier = TRUE, currency = "€", txtsize = 11)
print(ceac_plot_s1)
```

```{r pagebreak-3, results='asis'}
cat("\\newpage\n")
```

# Scenario 2: Alternative Utility Values (u_np = 0.73, u_p = 0.59)

This scenario examines the cost-effectiveness under alternative, lower utility assumptions that may reflect more conservative estimates of quality of life. They are derived from the EQ-5D index score of the CORRECT trial (Grothey et al. Lancet 2013, as cited by Gourzoulidis et al. J Comp Effect Res 2018)-

```{r scenario2-params}
# Helper function to calculate beta parameters (from 08_sampling.R)
get_beta_params <- function(mean_val, cv) {
  var_val <- (mean_val * cv)^2
  alpha <- mean_val * (mean_val * (1 - mean_val) / var_val - 1)
  beta <- (1 - mean_val) * (mean_val * (1 - mean_val) / var_val - 1)
  return(list(shape1 = alpha, shape2 = beta))
}

# Create Scenario 2 parameter set: Alternative utilities
l_params_scenario2 <- l_params_basecase
l_params_scenario2$u_np <- 0.73
l_params_scenario2$u_p <- 0.59

# Create distributions for Scenario 2 PSA
cv_utilities <- 0.15  # Standard 15% CV for utilities
param_distributions_scenario2 <- param_distributions_basecase

# Override utility distributions with alternative values
dist_u_np_scenario2 <- c(list(dist = "beta"), get_beta_params(0.73, cv_utilities))
dist_u_p_scenario2 <- c(list(dist = "beta"), get_beta_params(0.59, cv_utilities))

param_distributions_scenario2$u_np <- dist_u_np_scenario2
param_distributions_scenario2$u_p <- dist_u_p_scenario2

# Display parameter modifications
scenario2_params_table <- data.frame(
  Parameter = c("u_np (Non-progressed utility)", "u_p (Progressed utility)"),
  Base_Case = c(l_params_basecase$u_np, l_params_basecase$u_p),
  Scenario_2 = c(l_params_scenario2$u_np, l_params_scenario2$u_p),
  Difference = c(
    l_params_scenario2$u_np - l_params_basecase$u_np,
    l_params_scenario2$u_p - l_params_basecase$u_p
  ),
  Pct_Change = c(
    100 * (l_params_scenario2$u_np - l_params_basecase$u_np) / l_params_basecase$u_np,
    100 * (l_params_scenario2$u_p - l_params_basecase$u_p) / l_params_basecase$u_p
  )
)

knitr::kable(scenario2_params_table,
             digits = 4,
             col.names = c("Parameter", "Base Case", "Scenario 2", "Difference", "% Change"),
             align = c("l", "r", "r", "r", "r"),
             booktabs = TRUE,
             caption = "Utility Parameter Modifications for Scenario 2") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

**Beta Distribution Parameters for PSA:**

```{r scenario2-beta-params}
beta_params_table <- data.frame(
  Parameter = c("u_np", "u_p"),
  Mean = c(0.73, 0.59),
  CV = c(cv_utilities, cv_utilities),
  Alpha = c(dist_u_np_scenario2$shape1, dist_u_p_scenario2$shape1),
  Beta = c(dist_u_np_scenario2$shape2, dist_u_p_scenario2$shape2)
)

knitr::kable(beta_params_table,
             digits = 3,
             booktabs = TRUE,
             caption = "Beta Distribution Parameters for Scenario 2 PSA") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario2-basecase}
# Re-source functions
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Run base case analysis for Scenario 2
base_results_scenario2 <- model_fun(l_params_scenario2)

# Calculate ICERs
icer_obj_scenario2 <- dampack::calculate_icers(
  cost = base_results_scenario2$Cost,
  effect = base_results_scenario2$Effect,
  strategies = base_results_scenario2$Strategy
)

# Display results
icer_table_s2 <- as.data.frame(icer_obj_scenario2)
icer_table_s2$Cost <- scales::dollar(icer_table_s2$Cost, accuracy = 1)
icer_table_s2$Effect <- sprintf("%.3f", icer_table_s2$Effect)
icer_table_s2$ICER[!is.na(icer_table_s2$ICER)] <- 
  scales::dollar(icer_table_s2$ICER[!is.na(icer_table_s2$ICER)], accuracy = 1)

knitr::kable(icer_table_s2, 
             align = c("l", "r", "r", "r", "l"),
             booktabs = TRUE,
             caption = "Scenario 2 Cost-Effectiveness Results (Alternative Utilities)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r scenario2-ce-plane}
#| fig-cap: "Cost-Effectiveness Plane - Scenario 2 (Alternative Utilities)"

ce_plot_s2 <- plot(icer_obj_scenario2, 
                   txtsize = 12,
                   currency = "€",
                   effect_units = "QALYs",
                   label = "all")
print(ce_plot_s2)
```

```{r scenario2-psa, include=FALSE}
# Re-source functions
for (func_file in c("scripts/R/functions/model_fun.R",
                    "scripts/R/functions/calculate_outcomes.R",
                    "scripts/R/functions/psa_functions.R")) {
  if (file.exists(here(func_file))) {
    suppressMessages(suppressWarnings(source(here(func_file))))
  }
}

# Generate PSA samples for Scenario 2
cat("Generating PSA samples for Scenario 2:", n_sim, "simulations\n")
psa_params_scenario2 <- generate_psa_samples(param_distributions_scenario2, n_sim)

# Run PSA for Scenario 2
cat("Starting PSA for Scenario 2\n")
psa_results_scenario2 <- run_psa_analysis(
  psa_params = psa_params_scenario2,
  l_params_base = l_params_scenario2,
  param_distributions = param_distributions_scenario2,
  strategies = strategies,
  time_horizon = time_horizon,
  cl = cl,
  n_sim = n_sim
)

# Create PSA object
psa_obj_scenario2 <- dampack::make_psa_obj(
  cost = as.data.frame(psa_results_scenario2$cost),
  effect = as.data.frame(psa_results_scenario2$effect),
  strategies = strategies,
  currency = "€"
)

# PSA summary
psa_summary_s2 <- summary(psa_obj_scenario2, calc_sds = TRUE)
```

**Table: PSA Summary Statistics - Scenario 2**

```{r scenario2-psa-summary}
knitr::kable(psa_summary_s2,
             digits = 2,
             booktabs = TRUE,
             caption = "PSA Summary - Scenario 2 (Alternative Utilities)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r scenario2-psa-scatter}
#| fig-cap: "PSA Scatterplot - Scenario 2 (Alternative Utilities)"

psa_plot_s2 <- plot(psa_obj_scenario2, 
                    frontier = TRUE, 
                    points = TRUE,
                    alpha = 0.4,
                    txtsize = 11,
                    currency = "€",
                    effect_units = "QALYs")
print(psa_plot_s2)
```

```{r scenario2-ceac}
#| fig-cap: "Cost-Effectiveness Acceptability Curve - Scenario 2"

ceac_obj_s2 <- ceac(c_wtp, psa_obj_scenario2)
ceac_plot_s2 <- plot(ceac_obj_s2, frontier = TRUE, currency = "€", txtsize = 11)
print(ceac_plot_s2)
```

```{r pagebreak-4, results='asis'}
cat("\\newpage\n")
```

# Comparative Analysis Across All Scenarios

```{r utility-comparison-table}
utility_comparison <- data.frame(
  Scenario = c("Base Case", "Scenario 1 (Life Years)", "Scenario 2 (Alternative)"),
  u_np = c(l_params_basecase$u_np, l_params_scenario1$u_np, l_params_scenario2$u_np),
  u_p = c(l_params_basecase$u_p, l_params_scenario1$u_p, l_params_scenario2$u_p),
  Description = c(
    "Standard utility values from literature",
    "No quality adjustment (all utilities = 1.0)",
    "Lower/conservative utility estimates"
  )
)

knitr::kable(utility_comparison,
             digits = 4,
             col.names = c("Scenario", "u_np", "u_p", "Description"),
             align = c("l", "r", "r", "l"),
             booktabs = TRUE,
             caption = "Utility Parameter Values Across Scenarios") %>%
  kableExtra::column_spec(1, width = "3.5cm") %>%
  kableExtra::column_spec(2:3, width = "1.5cm") %>%
  kableExtra::column_spec(4, width = "6cm") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r comparison-table}
# Combine results from all three scenarios
comparison_results <- data.frame(
  Scenario = rep(c("Base Case", "Scenario 1", "Scenario 2"), each = length(strategies)),
  Strategy = rep(strategies, 3),
  Cost = c(base_results$Cost, base_results_scenario1$Cost, base_results_scenario2$Cost),
  Effect = c(base_results$Effect, base_results_scenario1$Effect, base_results_scenario2$Effect)
)

# Add NMB at WTP threshold
comparison_results$NMB <- comparison_results$Effect * WTP - comparison_results$Cost

# Format for display
comparison_display <- comparison_results %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    Cost = scales::dollar(Cost, accuracy = 1),
    Effect = sprintf("%.3f", Effect),
    NMB = scales::dollar(NMB, accuracy = 1)
  )

knitr::kable(comparison_display,
             align = c("l", "l", "r", "r", "r"),
             col.names = c("Scenario", "Strategy", "Cost (€)", "Effect", "NMB (€)"),
             booktabs = TRUE,
             caption = "Cost-Effectiveness Results Comparison Across Scenarios") %>%
  kableExtra::collapse_rows(columns = 1, valign = "top") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

```{r effect-comparison-plot}
#| fig-cap: "Comparison of Effects Across Scenarios by Strategy"
#| fig-height: 7
#| fig-width: 10

effect_comparison_data <- comparison_results %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    Scenario = factor(Scenario, levels = c("Base Case", "Scenario 1", "Scenario 2"))
  )

p_effect <- ggplot(effect_comparison_data, aes(x = Strategy, y = Effect, fill = Scenario)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = c("Base Case" = "#2E86AB", 
                                "Scenario 1" = "#A23B72", 
                                "Scenario 2" = "#F18F01")) +
  labs(
    title = "Effect Comparison Across Scenarios",
    subtitle = "Base Case (QALYs), Scenario 1 (Life Years), Scenario 2 (Alternative QALYs)",
    x = "Strategy",
    y = "Effect (QALYs / Life Years)",
    fill = "Scenario"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

print(p_effect)
```

```{r icer-comparison}
# Extract ICERs from each scenario
icer_base <- as.data.frame(icer_obj) %>%
  select(Strategy, ICER) %>%
  mutate(Scenario = "Base Case")

icer_s1 <- as.data.frame(icer_obj_scenario1) %>%
  select(Strategy, ICER) %>%
  mutate(Scenario = "Scenario 1")

icer_s2 <- as.data.frame(icer_obj_scenario2) %>%
  select(Strategy, ICER) %>%
  mutate(Scenario = "Scenario 2")

# Combine
icer_comparison <- rbind(icer_base, icer_s1, icer_s2) %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    ICER_formatted = ifelse(!is.na(ICER), 
                            scales::dollar(ICER, accuracy = 1), 
                            "Reference")
  ) %>%
  select(Scenario, Strategy, ICER_formatted) %>%
  pivot_wider(names_from = Scenario, values_from = ICER_formatted)

knitr::kable(icer_comparison,
             align = c("l", "r", "r", "r"),
             col.names = c("Strategy", "Base Case", "Scenario 1", "Scenario 2"),
             booktabs = TRUE,
             caption = "ICER Comparison Across Scenarios (€ per QALY/Life Year)") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r nmb-comparison-plot}
#| fig-cap: "Net Monetary Benefit Comparison Across Scenarios (WTP = €51,000)"
#| fig-height: 7
#| fig-width: 10

nmb_comparison_data <- comparison_results %>%
  mutate(
    Strategy = case_when(
      Strategy == "control" ~ "Standard of Care",
      Strategy == "crp" ~ "CRP-guided",
      Strategy == "tlr" ~ "TLR-guided",
      Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
      TRUE ~ Strategy
    ),
    Scenario = factor(Scenario, levels = c("Base Case", "Scenario 1", "Scenario 2"))
  )

p_nmb <- ggplot(nmb_comparison_data, aes(x = Strategy, y = NMB, fill = Scenario)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.8), width = 0.7) +
  scale_fill_manual(values = c("Base Case" = "#2E86AB", 
                                "Scenario 1" = "#A23B72", 
                                "Scenario 2" = "#F18F01")) +
  scale_y_continuous(labels = scales::dollar_format(scale = 0.001, suffix = "K")) +
  labs(
    title = "Net Monetary Benefit Comparison Across Scenarios",
    subtitle = paste0("Willingness-to-Pay Threshold: €", scales::comma(WTP)),
    x = "Strategy",
    y = "Net Monetary Benefit (€)",
    fill = "Scenario"
  ) +
  theme_minimal() +
  theme(
    axis.text.x = element_text(angle = 45, hjust = 1),
    legend.position = "bottom"
  )

print(p_nmb)
```

```{r optimal-strategy-comparison}
# Determine optimal strategy for each scenario
optimal_base <- comparison_results %>%
  filter(Scenario == "Base Case") %>%
  slice_max(NMB, n = 1) %>%
  pull(Strategy)

optimal_s1 <- comparison_results %>%
  filter(Scenario == "Scenario 1") %>%
  slice_max(NMB, n = 1) %>%
  pull(Strategy)

optimal_s2 <- comparison_results %>%
  filter(Scenario == "Scenario 2") %>%
  slice_max(NMB, n = 1) %>%
  pull(Strategy)

optimal_summary <- data.frame(
  Scenario = c("Base Case", "Scenario 1 (Life Years)", "Scenario 2 (Alternative)"),
  Optimal_Strategy = c(optimal_base, optimal_s1, optimal_s2),
  WTP_Threshold = rep(scales::dollar(WTP), 3)
)

optimal_summary$Optimal_Strategy <- case_when(
  optimal_summary$Optimal_Strategy == "control" ~ "Standard of Care",
  optimal_summary$Optimal_Strategy == "crp" ~ "CRP-guided",
  optimal_summary$Optimal_Strategy == "tlr" ~ "TLR-guided",
  optimal_summary$Optimal_Strategy == "tmb_braf" ~ "TMB/BRAF-guided",
  TRUE ~ optimal_summary$Optimal_Strategy
)

knitr::kable(optimal_summary,
             align = c("l", "l", "r"),
             col.names = c("Scenario", "Optimal Strategy", "WTP Threshold"),
             booktabs = TRUE,
             caption = "Optimal Strategy by Scenario at WTP Threshold") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

```{r pagebreak-5, results='asis'}
cat("\\newpage\n")
```

# Summary

This scenario analysis examined the impact of utility assumptions on the METIMMOX+1 model. The cut-off effectiveness from the base case scatter plot disappears when using alternative values.

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.1