---
title: "Bug Fix Impact Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("snapshot_utils", "report_format"),
  packages = c("here", "knitr", "kableExtra", "dplyr", "ggplot2", "scales"),
  set_theme = FALSE
)

snapshots_dir <- snapshot_path()
snapshot_files <- if (dir.exists(snapshots_dir)) {
  list.files(snapshots_dir, pattern = "^snapshot_.*\\.rds$", full.names = FALSE)
} else {
  character()
}

snapshot_info <- if (length(snapshot_files) > 0) {
  do.call(rbind, lapply(snapshot_files, parse_snapshot_filename)) %>%
    mutate(mtime = file.info(file.path(snapshots_dir, filename))$mtime) %>%
    arrange(issue, mtime)
} else {
  data.frame()
}

# ---- Assemble bug-fix impact comparisons ----------------------------------
# Resolve the snapshot file for a given issue + status (newest if duplicated).
snapshot_file_for <- function(issue, status) {
  if (nrow(snapshot_info) == 0) return(NA_character_)
  hit <- snapshot_info$type == "snapshot" &
    snapshot_info$issue == issue &
    !is.na(snapshot_info$status) & snapshot_info$status == status
  if (!any(hit)) return(NA_character_)
  cand <- snapshot_info[hit, ]
  cand$filename[which.max(cand$mtime)]
}

# Build one comparison, loading both snapshots; NULL if either is unavailable.
make_comparison <- function(label, before_issue, before_status,
                            after_issue, after_status) {
  bf <- snapshot_file_for(before_issue, before_status)
  af <- snapshot_file_for(after_issue, after_status)
  if (is.na(bf) || is.na(af)) return(NULL)
  before <- tryCatch(load_snapshot(bf, snapshots_dir), error = function(e) NULL)
  after  <- tryCatch(load_snapshot(af, snapshots_dir), error = function(e) NULL)
  if (is.null(before) || is.null(after)) return(NULL)
  list(label = label, before_file = bf, after_file = af,
       before = before, after = after)
}

# Issues that have BOTH a baseline and a fixed snapshot, in numeric order.
paired_issues <- character()
if (nrow(snapshot_info) > 0) {
  snap_only <- snapshot_info[snapshot_info$type == "snapshot", ]
  issue_status <- split(snap_only$status, snap_only$issue)
  paired_issues <- names(Filter(
    function(s) all(c("baseline", "fixed") %in% s), issue_status))
  paired_issues <- paired_issues[order(as.numeric(paired_issues))]
}

comparisons <- list()
# Per-issue baseline -> fixed, one comparison per bug-fix issue.
for (iss in paired_issues) {
  comparisons[[length(comparisons) + 1]] <- make_comparison(
    paste0("Issue ", iss, ": baseline vs fixed"),
    iss, "baseline", iss, "fixed")
}
# Cumulative: earliest baseline -> latest fixed (only when >1 paired issue).
if (length(paired_issues) > 1) {
  first_iss <- paired_issues[1]
  last_iss  <- paired_issues[length(paired_issues)]
  comparisons[[length(comparisons) + 1]] <- make_comparison(
    paste0("Cumulative: issue ", first_iss, " baseline vs issue ",
           last_iss, " fixed"),
    first_iss, "baseline", last_iss, "fixed")
}
comparisons <- Filter(Negate(is.null), comparisons)

# ---- Impact-table builders (shared by every comparison) -------------------
build_base_impact <- function(before, after) {
  before$base_results %>%
    select(Strategy, Cost_Before = Cost, Effect_Before = Effect) %>%
    inner_join(
      after$base_results %>%
        select(Strategy, Cost_After = Cost, Effect_After = Effect),
      by = "Strategy"
    ) %>%
    mutate(
      Cost_Change = Cost_After - Cost_Before,
      Effect_Change = Effect_After - Effect_Before,
      Strategy = strategy_label(Strategy),
      across(c(Cost_Before, Cost_After, Cost_Change), format_eur),
      across(c(Effect_Before, Effect_After, Effect_Change), ~ sprintf("%.4f", .x))
    )
}

build_nmb_impact <- function(before, after) {
  inner_join(
    before$nmb_at_wtp %>% select(Strategy, NMB_Before = NMB),
    after$nmb_at_wtp %>% select(Strategy, NMB_After = NMB),
    by = "Strategy"
  ) %>%
    mutate(
      NMB_Change = NMB_After - NMB_Before,
      Strategy = strategy_label(Strategy),
      across(c(NMB_Before, NMB_After, NMB_Change), format_eur)
    )
}

# EVPPI comparison (issue #152 onwards). Snapshots carry the EVPPI cache under
# `evppi`; older snapshots lack it and the table is skipped.
build_evppi_impact <- function(before, after) {
  b <- before$evppi$evppi_results
  a <- after$evppi$evppi_results
  if (is.null(b) || is.null(a) || nrow(b) == 0 || nrow(a) == 0) return(NULL)
  pick_se <- function(df) if ("evppi_se" %in% names(df)) df$evppi_se else NA_real_
  full_join(
    data.frame(Parameter = b$parameter, EVPPI_Before = b$evppi,
               Pct_Before = b$evppi_percent_of_evpi, stringsAsFactors = FALSE),
    data.frame(Parameter = a$parameter, EVPPI_After = a$evppi,
               SE_After = pick_se(a), Pct_After = a$evppi_percent_of_evpi,
               stringsAsFactors = FALSE),
    by = "Parameter"
  ) %>%
    arrange(desc(EVPPI_Before), Parameter) %>%
    mutate(
      Parameter = ifelse(grepl("^\\[GROUP\\] ", Parameter),
                         paste0(evppi_group_label(Parameter), " (group)"), Parameter),
      across(c(EVPPI_Before, EVPPI_After, SE_After), ~ format_eur(.x, accuracy = 0.01)),
      across(c(Pct_Before, Pct_After),
             ~ ifelse(is.finite(.x), sprintf("%.1f%%", .x), "--"))
    ) %>%
    select(Parameter, EVPPI_Before, Pct_Before, EVPPI_After, SE_After, Pct_After)
}

evpi_line <- function(before, after) {
  b <- before$evppi$evpi
  a <- after$evppi$evpi
  if (is.null(b) || is.null(a)) return(NULL)
  sprintf("Per-patient EVPI: %s before, %s after.",
          format_eur(b, accuracy = 0.01), format_eur(a, accuracy = 0.01))
}

# Wide table needs a smaller font in PDF (scale_down is dropped by Quarto's
# raw-table handling); tbl_style() is a no-op under gfm.
style_wide   <- function(k) tbl_style(k, latex_options = "HOLD_position", font_size = 8)
style_narrow <- function(k) tbl_style(k, latex_options = "HOLD_position")

```

# Snapshot Inventory

```{r inventory}
if (nrow(snapshot_info) == 0) {
  cat("No snapshot files were found in data/output/snapshots.")
} else {
  inventory <- snapshot_info %>%
    select(filename, issue, status, commit, mtime)

  knitr::kable(
    inventory,
    booktabs = TRUE,
    align = "l",
    caption = "Available single-model snapshots"
  ) %>%
    tbl_style(latex_options = c("HOLD_position", "scale_down"))
}
```

# Impact Comparisons

```{r overview}
if (length(comparisons) == 0) {
  cat("No baseline/fixed snapshot pairs were available for comparison.")
} else {
  overview <- do.call(rbind, lapply(comparisons, function(cmp) data.frame(
    Comparison = cmp$label,
    Before = cmp$before_file,
    After = cmp$after_file,
    stringsAsFactors = FALSE
  )))

  knitr::kable(
    overview,
    booktabs = TRUE,
    align = "l",
    caption = "Impact comparisons included in this report"
  ) %>%
    style_wide()
}
```

Each comparison below reports the change in base case costs and QALYs, and in net monetary benefit at the willingness-to-pay threshold, from the *before* snapshot to the *after* snapshot. Where both snapshots carry the EVPPI cache (snapshots taken from issue #152 onwards), the per-patient EVPI and the EVPPI table are compared as well; the *after* column includes the Monte Carlo standard error of the regression estimator. From issue #156 onwards each snapshot records the md5 and modification time of the PSA cache it copied, and a *fixed* snapshot regenerates the PSA and EVPPI caches when they predate the fix commit; the provenance line under each comparison states whether the two PSA files are the same cache.

```{r comparisons, results='asis'}
for (cmp in comparisons) {
  cat("\n\n## ", cmp$label, "\n\n")

  base_tbl <- knitr::kable(
    build_base_impact(cmp$before, cmp$after),
    booktabs = TRUE,
    align = c("l", "r", "r", "r", "r", "r", "r"),
    col.names = c("Strategy", "Cost Before", "QALYs Before",
                  "Cost After", "QALYs After", "Cost Change", "QALY Change"),
    caption = paste0("Base case impact -- ", cmp$label)
  ) %>%
    style_wide()
  cat(as.character(base_tbl), "\n\n")

  nmb_tbl <- knitr::kable(
    build_nmb_impact(cmp$before, cmp$after),
    booktabs = TRUE,
    align = c("l", "r", "r", "r"),
    col.names = c("Strategy", "NMB Before", "NMB After", "NMB Change"),
    caption = paste0("Net monetary benefit impact -- ", cmp$label)
  ) %>%
    style_narrow()
  cat(as.character(nmb_tbl), "\n\n")

  # PSA provenance (issue #156): identical md5 means the PSA side of the
  # comparison is a copy of the same cache, not evidence of "no change".
  cat(describe_psa_provenance(cmp$before, cmp$after), "\n\n")

  # EVPI is reported whenever both snapshots carry it, even when one EVPPI
  # table is empty (EVPI = 0 stores no rows; issue #156).
  evpi_text <- evpi_line(cmp$before, cmp$after)
  if (!is.null(evpi_text)) cat(evpi_text, "\n\n")
  evppi_df <- build_evppi_impact(cmp$before, cmp$after)
  if (!is.null(evppi_df)) {
    evppi_tbl <- knitr::kable(
      evppi_df,
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r", "r"),
      col.names = c("Parameter / group", "EVPPI Before", "% EVPI Before",
                    "EVPPI After", "SE After", "% EVPI After"),
      caption = paste0("EVPPI impact -- ", cmp$label)
    ) %>%
      style_wide()
    cat(as.character(evppi_tbl), "\n\n")
  }
}
```

# Interpretation

This report compares baseline and fixed single-model snapshots for each bug-fix issue that has both, plus a cumulative comparison from the earliest baseline to the latest fixed snapshot. Snapshots are produced by the `13_save_snapshot.R` analysis script (in `analysis/`). If older snapshots contain obsolete multi-model components, `load_snapshot()` warns during render and the tables use the top-level single-model results.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.2
