---
title: "Week-4 CRP Estimand"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# ===============================================================================
# Week-4 CRP estimand (issue #175)
#
# States the estimand of the CRP-guided strategy and quantifies, deterministically,
#   1. a missingness sensitivity analysis that restores the patients without a
#      week-4 CRP under four assignments of CRP and unknown TMB/BRAF status;
#   2. the costs and QALYs the model accrues before the first nivolumab dose.
# All calculations are in R/crp_week4_estimand.R. No model code or cache is
# changed and no PSA is run.
#
# Version history
#   1.0  2026-09-24  first version
# ===============================================================================
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05"),
  funs = c("model_fun", "calculate_outcomes", "cea_helpers", "report_format",
           "crp_week4_estimand"),
  set_theme = FALSE,
  quiet_sources = TRUE
)

control <- get_control_strategy()
guided <- setdiff(get_strategies(), control)

# Deterministic base case, exactly as 08_basecase_analysis.R and CEA.qmd run it.
base <- run_basecase(l_params_base, verbose = FALSE)
base_pairwise <- calculate_pairwise_icers(base$base_results)

# Missingness sensitivity analysis (four scenarios plus a reproduction run of
# the same code on the unmodified complete-case cohort).
sens <- run_crp_missingness_sensitivity(data, l_params_base, models, time_points)
reproduction_diff <- max(abs(c(
  sens$reproduction$results$Cost - base$base_results$Cost,
  sens$reproduction$results$Effect - base$base_results$Effect)))
if (!identical(sens$reproduction$status, "ok") || reproduction_diff > 1e-8) {
  stop("The scenario code does not reproduce the deterministic base case.")
}

# Pre-decision accrual: the decision week is the first nivolumab dose.
decision_week <- which(l_params_base$l_nivo == 1)[1] - 1
pre <- pre_decision_outcomes(l_params_base, decision_week = decision_week,
                             time_horizon = time_horizon, cl = cl)
pre_inc <- pre_decision_increments(pre)
if (pre$check > 1e-8) stop("Recomputed outcomes do not match model_fun().")
if (pre$schedule$nivo_before != 0 || !pre$schedule$flox_identical) {
  stop("Treatment schedules differ before the decision week.")
}

# Aggregate description of the restored patients (no patient-level output
# beyond the death weeks already published in the issue and AGENTS.md).
restored <- data[sens$restored_rows, , drop = FALSE]
raw <- readRDS(here::here("data", "tidy", "METIMMOX.rds"))
raw_restored <- raw[match(restored$ID, raw$ID), , drop = FALSE]
arm_levels <- levels(data$Rx)
is_control <- restored$Rx == arm_levels[1]
n_restored <- nrow(restored)
n_restored_control <- sum(is_control)
n_restored_exp <- sum(!is_control)
death_weeks <- sort(round(restored$OSwk[restored$Death == 1], 1))
control_death_week <- round(restored$OSwk[is_control & restored$Death == 1], 1)
exp_death_weeks <- sort(round(restored$OSwk[!is_control & restored$Death == 1], 1))
n_dead_before_decision <- sum(restored$Death == 1 & restored$OSwk < decision_week)
n_alive_at_decision <- n_restored - n_dead_before_decision
n_baseline_crp <- sum(!is.na(raw_restored$CRP0cat))
n_braf <- sum(raw_restored$Mutation == "BRAF")
n_tmb_unknown <- sum(is.na(restored$tmb_braf))
n_kras_no_tmb <- sum(raw_restored$Mutation == "KRAS" & is.na(raw_restored$TMBcat))
n_pfs_progression <- sum(restored$PFS_rule == "progression")
n_pfs_death_window <- sum(restored$PFS_rule == "death_within_window")
# Context: complete-case exclusions with a week-4 CRP but no TMB/BRAF result.
other_excluded <- data[!is.na(data$crp) & is.na(data$tmb_braf), , drop = FALSE]
n_other_excluded <- nrow(other_excluded)
n_other_excluded_control <- sum(other_excluded$Rx == arm_levels[1])
n_combinations <- 2^(n_restored + n_tmb_unknown)

# Formatting helpers.
fmt_int <- function(x) ifelse(is.na(x), "--", format(round(x), big.mark = ",", trim = TRUE))
fmt_q <- function(x, digits = 4) ifelse(is.na(x), "--", formatC(x, format = "f", digits = digits))
fmt_small <- function(x) format(signif(x, 3), scientific = FALSE, drop0trailing = TRUE, trim = TRUE)
fmt_pct <- function(x, digits = 1) paste0(formatC(100 * x, format = "f", digits = digits), "%")
fmt_diff <- function(x) if (x == 0) "0, identical" else format(x, scientific = TRUE, digits = 3)
tab <- function(x, caption, align = NULL, font_size = NULL) {
  knitr::kable(x, booktabs = TRUE, align = align, caption = caption,
               row.names = FALSE) %>%
    tbl_style(latex_options = "HOLD_position", font_size = font_size)
}

# One entry per cohort: base case first, then the four scenarios.
cohort_ids <- c("base", sens$scenarios$id)
cohort_labels <- setNames(c("Base case", sens$scenarios$label), cohort_ids)
cohort_runs <- c(list(base = sens$reproduction), sens$runs)
cohort_results <- c(list(base = base$base_results),
                    lapply(sens$runs, `[[`, "results"))
cohort_pairwise <- c(list(base = base_pairwise), lapply(sens$runs, `[[`, "pairwise"))
failed_runs <- names(sens$runs)[vapply(sens$runs, function(r) r$status != "ok", logical(1))]

value_of <- function(results, strategy, column) {
  if (is.null(results)) return(NA_real_)
  results[[column]][results$Strategy == strategy]
}
```

# Purpose

The CRP-guided strategy uses the week-4 C-reactive protein value (CRP, cycle 3
day 1), measured after the two FLOX cycles that both arms receive and before
the first nivolumab dose. Issue #175 asked which estimand the economic model
targets, and how much two consequences of that choice matter:

- the patients without a week-4 CRP are excluded from the complete-case
  cohort, and
- the fitted treatment effects act from randomisation, although the
  treatment schedules of all strategies are identical until the first
  nivolumab dose.

The chosen approach is to keep the current model and quantify both points with
deterministic sensitivity analyses (option (c) of the issue). This report
states the estimand, describes the patients without a week-4 CRP in aggregate,
restores them under four biomarker assignments, and measures the costs and
QALYs the model accrues before the first nivolumab dose. No model code and no
cache is changed; all results are deterministic.

# Estimand

The economic model estimates a **randomisation-time policy**. Each strategy is
assigned at randomisation (t = 0), and costs and QALYs are counted from that
point over the `r time_horizon`-week horizon. Under the CRP-guided strategy,
nivolumab is added from modeled week `r decision_week` for patients whose
week-4 CRP is below 5 mg/L; the other patients continue FLOX alone. The
week-4 value is available when the decision is made, because it is measured
before the first nivolumab dose. The target population is the complete-case
cohort of `r nrow(data_complete)` patients with age, sex, arm, week-4 CRP,
TMB/BRAF and both endpoints recorded. Patients without a week-4 CRP are
excluded from this cohort and are not modeled as a separate decision
population. Under a randomisation-time estimand they belong to the target
population, so all `r n_restored` of them are missing data, including the
patient who died before week `r decision_week`. The missingness sensitivity
analysis therefore restores all of them.

The treatment contrast is estimated from randomisation. The joint OS and PFS
models contain `Rx` and biomarker-by-`Rx` terms that act from t = 0, so the
strategies' survival curves separate before week `r decision_week`, although
every strategy receives the same FLOX, monitoring and visits until then. Two
alternatives were considered and not adopted:

- **(a)** force identical curves up to week `r decision_week` and start the
  treatment contrast at the decision point; or
- **(b)** a landmark estimand among patients alive at week `r decision_week`.
  It would place the patient who died before week `r decision_week` outside
  the decision population and treat only the patients alive at week
  `r decision_week` as missing data.

The missingness sensitivity analysis and the pre-decision accrual below
quantify how much the results depend on the adopted estimand.

# Patients Without a Week-4 CRP

```{r restored-table}
restored_table <- data.frame(
  Characteristic = c(
    "Patients without a week-4 CRP",
    "Control arm / experimental arm",
    sprintf("Died before week %d (week-4 CRP could not be measured)", decision_week),
    sprintf("Alive at week %d without a week-4 CRP", decision_week),
    "Deaths during follow-up",
    "Baseline CRP (cycle 1 day 1) available",
    "TMB/BRAF known positive (BRAF-mutant)",
    "TMB/BRAF unknown (KRAS-mutant, no TMB result)",
    "PFS events: recorded progression / death within window"
  ),
  Value = c(
    n_restored,
    paste(n_restored_control, "/", n_restored_exp),
    n_dead_before_decision,
    n_alive_at_decision,
    sum(restored$Death),
    n_baseline_crp,
    n_braf,
    n_kras_no_tmb,
    paste(n_pfs_progression, "/", n_pfs_death_window)
  ),
  stringsAsFactors = FALSE
)
tab(restored_table, "Patients without a week-4 CRP (aggregate)",
    align = c("l", "r"))
```

`r n_restored` patients have no week-4 CRP: `r n_restored_control` in the
control arm and `r n_restored_exp` in the experimental arm. All
`r sum(restored$Death)` died, at weeks `r paste(death_weeks, collapse = ", ")`:
the control-arm patient at week `r control_death_week`, and the
experimental-arm patients at weeks `r paste(exp_death_weeks, collapse = " and ")`.
Only `r n_dead_before_decision` of them died before week `r decision_week`;
the other `r n_alive_at_decision` were alive at week `r decision_week` but
have no week-4 value. All `r n_baseline_crp` have a baseline CRP. The
control-arm patient is BRAF-mutant and therefore TMB/BRAF-positive. The
`r n_kras_no_tmb` experimental-arm patients are KRAS-mutant with no TMB
result, so their TMB/BRAF status is unknown; they would be excluded from the
complete-case cohort even with a week-4 CRP. Their PFS endpoints follow the
issue #181 rule already applied by script 02 (a
`r pfs_death_window_weeks`-week death window after the last assessment) and
are used as they are.

The complete-case cohort also excludes `r n_other_excluded` patients who
have a week-4 CRP but no TMB/BRAF result
(`r if (n_other_excluded_control == n_other_excluded) "all in the control arm" else paste(n_other_excluded_control, "in the control arm")`). They are not part of this analysis and stay excluded in
every scenario.

# Missingness Sensitivity Analysis

## Methods

The `r n_restored` patients without a week-4 CRP are restored to the
complete-case cohort, giving `r sens$runs[[1]]$summary$n` patients. Four
scenarios cross two assignments:

- the CRP value assigned to all `r n_restored` patients (negative or
  positive), and
- the TMB/BRAF value assigned to the `r n_tmb_unknown` patients with unknown
  TMB/BRAF status (negative or positive).

The control-arm patient keeps the known TMB/BRAF-positive status. For each
scenario:

1. **Refit.** The joint OS and PFS models are refitted with the pipeline
   formulas (`get_model_formulas()`) and the distributions selected for the
   base case (`r sens$os_distribution` for OS, `r sens$pfs_distribution` for
   PFS). The distributions are not re-selected.
2. **Rebuild the population.** The common prediction population, the
   biomarker prevalences and the joint biomarker cells are rebuilt from the
   `r sens$runs[[1]]$summary$n`-patient cohort with the pipeline helpers,
   among them `economic_prediction_population()` and
   `set_population_predictions()`.
3. **Check ordering.** OS >= PFS is checked for the control curve and the four
   biomarker-subgroup curves at every weekly time point. The deterministic
   model stops on a violation, so a scenario that violates the ordering is
   reported, not clamped.
4. **Run the model.** The deterministic model is run with the unchanged
   schedules, prices and utilities, as script 05 builds them.

Pairwise ICERs and statuses versus standard of care come from
`calculate_pairwise_icers()`, and frontier statuses from dampack. Applied to
the unmodified `r nrow(data_complete)`-patient cohort, the same code
reproduces the deterministic base case (largest absolute difference in costs
and QALYs: `r fmt_diff(reproduction_diff)`).
Each scenario changes both the fitted treatment effects and the target
population (its size, prevalences and age/sex mix), so a difference from the
base case combines the two.

## Scenario cohorts and fits

```{r cohort-table}
cohort_table <- do.call(rbind, lapply(cohort_ids, function(id) {
  run <- cohort_runs[[id]]
  s <- run$summary
  data.frame(
    Cohort = cohort_labels[[id]],
    n = s$n,
    `Control/exp.` = paste(s$n_control, "/", s$n_experimental),
    `CRP+` = fmt_pct(s$crp),
    `TMB/BRAF+` = fmt_pct(s$tmb_braf),
    Converged = if (all(run$converged)) "Yes" else "No",
    `PFS > OS points` = if (is.null(run$ordering)) "--" else as.character(run$ordering$n_violations),
    check.names = FALSE, stringsAsFactors = FALSE
  )
}))
fit_status_text <- if (length(failed_runs) == 0) {
  sprintf(paste(
    "All %d scenario fits converged, and no refitted scenario puts PFS above OS",
    "on any of the five curves at any of the %d weekly time points, so every",
    "scenario could be run through the deterministic model."),
    nrow(sens$scenarios), length(time_points))
} else {
  run_status <- vapply(sens$runs[failed_runs], function(r) r$status, character(1))
  sprintf("%d of %d scenarios could not be evaluated: %s.", length(failed_runs),
          nrow(sens$scenarios),
          paste(sprintf("%s (%s)", cohort_labels[failed_runs], run_status), collapse = "; "))
}
tab(cohort_table, "Cohorts, prevalences, convergence and OS >= PFS ordering",
    align = c("l", "r", "r", "r", "r", "l", "r"), font_size = 9) %>%
  tbl_footnote(general = paste(
    "Converged: both refitted models converged with a finite covariance matrix.",
    "PFS > OS points: weekly time points at which PFS exceeds OS, summed over the",
    "control curve and the four biomarker-subgroup curves. The base-case row is",
    "the reproduction run on the complete-case cohort."), threeparttable = TRUE)
```

`r fit_status_text`

```{r coefficient-table}
location <- flexsurv::flexsurv.dists[[sens$os_distribution]]$location
coef_terms <- function(fit) {
  est <- fit$res[, "est"]
  names(est) <- rownames(fit$res)
  interaction <- function(b) {
    hit <- grepl(":", names(est)) & grepl(paste0("(^|:)", b), names(est))
    unname(est[hit])
  }
  rx_main <- grepl("^Rx", names(est)) & !grepl(":", names(est))
  c(Rx = unname(est[rx_main]),
    setNames(vapply(get_biomarkers(), interaction, numeric(1)),
             paste0(get_biomarkers(), "_x_rx")))
}
coef_table <- function(endpoint) {
  do.call(rbind, lapply(cohort_ids, function(id) {
    x <- coef_terms(cohort_runs[[id]]$models[[endpoint]])
    data.frame(
      Cohort = cohort_labels[[id]],
      Rx = fmt_q(x[["Rx"]], 3),
      `CRP x Rx` = fmt_q(x[["crp_x_rx"]], 3),
      `TMB/BRAF x Rx` = fmt_q(x[["tmb_braf_x_rx"]], 3),
      check.names = FALSE, stringsAsFactors = FALSE
    )
  }))
}
coef_note <- paste0(
  "Coefficients on the flexsurvreg ", location, " scale of the ",
  sens$os_distribution, " (OS) and ", sens$pfs_distribution,
  " (PFS) models; Rx is the experimental arm. ",
  if (identical(location, "rate")) "A positive coefficient raises the rate and shortens survival. " else "",
  "Standard errors are not shown.")
tab(coef_table("os"), "OS model: treatment and biomarker-by-treatment coefficients",
    align = c("l", "r", "r", "r"))
```

```{r coefficient-table-pfs}
tab(coef_table("pfs"), "PFS model: treatment and biomarker-by-treatment coefficients",
    align = c("l", "r", "r", "r")) %>%
  tbl_footnote(general = coef_note, threeparttable = TRUE)
```

## Cost-effectiveness results

```{r outcome-tables}
outcome_table <- function(column, formatter, with_optimal = FALSE) {
  do.call(rbind, lapply(cohort_ids, function(id) {
    results <- cohort_results[[id]]
    cells <- vapply(get_strategies(), function(s) formatter(value_of(results, s, column)),
                    character(1))
    out <- data.frame(t(c(cohort_labels[[id]], cells)), stringsAsFactors = FALSE)
    names(out) <- c("Cohort", strategy_label(get_strategies()))
    if (with_optimal) {
      out$`Highest NMB` <- if (is.null(results)) "--" else
        strategy_label(results$Strategy[which.max(results$Effect * WTP - results$Cost)])
    }
    out
  }))
}
tab(outcome_table("Cost", fmt_int, with_optimal = TRUE),
    "Deterministic costs (EUR) by cohort",
    align = c("l", rep("r", length(get_strategies())), "l"), font_size = 9) %>%
  tbl_footnote(general = sprintf(
    "Highest NMB: strategy with the highest net monetary benefit at WTP = %s per QALY.",
    format_eur(WTP)), threeparttable = TRUE)
```

```{r qaly-table}
tab(outcome_table("Effect", fmt_q), "Deterministic QALYs by cohort",
    align = c("l", rep("r", length(get_strategies()))))
```

```{r pairwise-table-crp}
pairwise_table <- function(strategy) {
  do.call(rbind, lapply(cohort_ids, function(id) {
    pw <- cohort_pairwise[[id]]
    row <- if (is.null(pw)) NULL else pw[pw$Strategy == strategy, ]
    if (is.null(row)) {
      return(data.frame(Cohort = cohort_labels[[id]], `Inc. cost` = "--",
        `Inc. QALYs` = "--", ICER = "--", Frontier = "--",
        check.names = FALSE, stringsAsFactors = FALSE))
    }
    data.frame(
      Cohort = cohort_labels[[id]],
      `Inc. cost` = fmt_int(row$Inc_Cost),
      `Inc. QALYs` = fmt_q(row$Inc_Effect),
      ICER = sub("^EUR ", "", format_icer(row$ICER, row$Status)),
      Frontier = frontier_label(row$Frontier_Status),
      check.names = FALSE, stringsAsFactors = FALSE
    )
  }))
}
pairwise_note <- paste(
  "Increments and ICERs are pairwise versus standard of care.",
  "'Dominated' in the ICER column: pairwise status 'Dominated by SoC' (more",
  "costly and no more effective than standard of care); a number: pairwise",
  "status 'Pairwise ICER vs SoC'; 'Cost-saving': 'Cost-saving vs SoC'.",
  "Frontier: dampack efficiency-frontier status",
  "across all three strategies.")
pairwise_caption <- function(strategy) paste0(strategy_label(strategy),
  ": increments and ICER pairwise versus standard of care (EUR, QALYs)")
tab(pairwise_table("crp"), pairwise_caption("crp"),
    align = c("l", "r", "r", "r", "l"), font_size = 9)
```

```{r pairwise-table-tmb-braf}
tab(pairwise_table("tmb_braf"), pairwise_caption("tmb_braf"),
    align = c("l", "r", "r", "r", "l"), font_size = 9) %>%
  tbl_footnote(general = pairwise_note, threeparttable = TRUE)
```

```{r range-summary}
scenario_rows <- function(strategy) {
  do.call(rbind, lapply(sens$scenarios$id, function(id) {
    pw <- sens$runs[[id]]$pairwise
    if (is.null(pw)) return(NULL)
    cbind(scenario = id, pw[pw$Strategy == strategy, ])
  }))
}
icer_range_text <- function(strategy) {
  rows <- scenario_rows(strategy)
  base_row <- base_pairwise[base_pairwise$Strategy == strategy, ]
  base_text <- switch(base_row$Status,
    "Pairwise ICER vs SoC" = paste("a pairwise ICER of", format_eur(base_row$ICER)),
    "Dominated by SoC" = "dominated by standard of care",
    "Cost-saving vs SoC" = "cost-saving versus standard of care",
    base_row$Status)
  finite <- rows[rows$Status == "Pairwise ICER vs SoC", ]
  dominated <- rows[rows$Status == "Dominated by SoC", ]
  parts <- character(0)
  if (nrow(finite) > 0) {
    lo <- finite[which.min(finite$ICER), ]
    hi <- finite[which.max(finite$ICER), ]
    parts <- c(parts, if (nrow(finite) == 1)
      sprintf("a pairwise ICER of %s in one scenario (%s)", format_eur(lo$ICER),
              cohort_labels[[lo$scenario]]) else
      sprintf("pairwise ICERs from %s (%s) to %s (%s) in %d scenarios",
              format_eur(lo$ICER), cohort_labels[[lo$scenario]],
              format_eur(hi$ICER), cohort_labels[[hi$scenario]], nrow(finite)))
  }
  if (nrow(dominated) > 0) {
    parts <- c(parts, sprintf("dominated by standard of care in %d (%s)",
      nrow(dominated), paste(cohort_labels[dominated$scenario], collapse = "; ")))
  }
  other <- rows[!rows$Status %in% c("Pairwise ICER vs SoC", "Dominated by SoC"), ]
  if (nrow(other) > 0) {
    parts <- c(parts, sprintf("%s in %d", paste(unique(other$Status), collapse = "/"),
                              nrow(other)))
  }
  sprintf("%s: %s (base case: %s)", strategy_label(strategy),
          paste(parts, collapse = "; "), base_text)
}
frontier_text <- function(strategy) {
  rows <- scenario_rows(strategy)
  sprintf("%s was on the efficiency frontier in %d of %d scenarios",
          strategy_label(strategy), sum(rows$Frontier_Status == "ND"), nrow(rows))
}
optimal_all <- vapply(sens$scenarios$id, function(id) {
  r <- sens$runs[[id]]$results
  if (is.null(r)) NA_character_ else r$Strategy[which.max(r$Effect * WTP - r$Cost)]
}, character(1))
base_optimal <- with(base$base_results, Strategy[which.max(Effect * WTP - Cost)])
```

**Range across the four scenarios.**

- `r icer_range_text("crp")`.
- `r icer_range_text("tmb_braf")`.
- `r frontier_text("crp")`; `r frontier_text("tmb_braf")`.
- `r if (all(optimal_all == base_optimal, na.rm = TRUE)) sprintf("%s had the highest net monetary benefit at WTP = %s in the base case and in every evaluated scenario, so the decision does not change.", strategy_label(base_optimal), format_eur(WTP)) else sprintf("The strategy with the highest net monetary benefit at WTP = %s changes from %s in the base case to %s in at least one scenario.", format_eur(WTP), strategy_label(base_optimal), paste(unique(strategy_label(optimal_all[optimal_all != base_optimal])), collapse = ", "))`

```{r scenario-drivers}
sc <- sens$scenarios
inc_effect <- function(id, strategy) value_of(sens$runs[[id]]$pairwise, strategy, "Inc_Effect")
# Mean absolute change in a strategy's incremental QALYs when one assignment is
# switched from negative to positive with the other assignment held fixed.
switch_change <- function(strategy, switched) {
  held <- setdiff(c("crp", "tmb_braf"), switched)
  mean(vapply(0:1, function(v) {
    lo <- sc$id[sc[[held]] == v & sc[[switched]] == 0]
    hi <- sc$id[sc[[held]] == v & sc[[switched]] == 1]
    abs(inc_effect(hi, strategy) - inc_effect(lo, strategy))
  }, numeric(1)))
}
changes <- outer(guided, c("crp", "tmb_braf"), Vectorize(switch_change))
dimnames(changes) <- list(guided, c("crp", "tmb_braf"))
control_qalys <- vapply(sens$scenarios$id, function(id)
  value_of(sens$runs[[id]]$results, control, "Effect"), numeric(1))
crp_rows <- scenario_rows("crp")
crp_base <- base_pairwise[base_pairwise$Strategy == "crp", ]
crp_ratio <- crp_rows$ICER[crp_rows$Status == "Pairwise ICER vs SoC"] / crp_base$ICER
```

Standard-of-care QALYs fall from
`r fmt_q(value_of(base$base_results, control, "Effect"))` in the base case to
between `r fmt_q(min(control_qalys, na.rm = TRUE))` and
`r fmt_q(max(control_qalys, na.rm = TRUE))`, because every restored patient
died within `r ceiling(max(restored$OSwk))` weeks and the population is
standardised to the enlarged cohort.
`r if (crp_base$Status == "Pairwise ICER vs SoC" && length(crp_ratio) > 0) sprintf("The CRP-guided pairwise ICER is lower than in the base case in %d of %d evaluated scenarios, at %s to %s of its base-case value.", sum(crp_ratio < 1), length(crp_ratio), fmt_pct(min(crp_ratio), 0), fmt_pct(max(crp_ratio), 0)) else ""`
Both assignments enter the joint model, so each one moves both guided
strategies. Switching the CRP assignment from negative to positive changes
the incremental QALYs of the CRP-guided strategy by
`r fmt_q(changes["crp", "crp"])` on average and those of the TMB/BRAF-guided
strategy by `r fmt_q(changes["tmb_braf", "crp"])`. Switching the TMB/BRAF
assignment changes them by `r fmt_q(changes["crp", "tmb_braf"])` and
`r fmt_q(changes["tmb_braf", "tmb_braf"])`. These changes are large relative
to the base-case increments of
`r fmt_q(value_of(base_pairwise, "crp", "Inc_Effect"))` (CRP-guided) and
`r fmt_q(value_of(base_pairwise, "tmb_braf", "Inc_Effect"))` (TMB/BRAF-guided).
The interaction estimates rest on few patients per arm and biomarker cell, so
`r n_restored` patients with early deaths are enough to move them.

# Costs and QALYs Accrued Before the First Nivolumab Dose

## Methods

All strategies receive the same treatment schedule until modeled week
`r decision_week`: no nivolumab dose is scheduled before week
`r decision_week`, and the FLOX schedules of the two arms are identical at
grid points 0 to `r decision_week - 1` (both checked when the report is
rendered). The first nivolumab
dose is at week `r pre$schedule$first_nivo_week`. Apart from the one-time
diagnostic test, any difference the model accrues between strategies before
week `r decision_week` therefore comes only from the fitted `Rx` and
biomarker-by-`Rx` effects acting from t = 0.

The deterministic base-case traces (`model_fun(..., return_traces = TRUE)`)
are passed through `calculate_outcomes()` subgroup by subgroup, and each
component is split at week `r decision_week` using the model's own
discounting and trapezoidal interval weights:

- **QALYs and ongoing progressed-state costs** (interval flows) are counted
  over the intervals from week 0 to week `r decision_week`. This is the full
  trapezoidal weight of grid points 0 to `r decision_week - 1` plus half the
  weight of grid point `r decision_week`.
- **Scheduled and one-time charges** are counted at grid points 0 to
  `r decision_week - 1`: drugs, CT scans, blood tests, visits, the baseline
  visit and the diagnostic test (CRP or NGS). Every charge at grid point
  `r decision_week`, including the first nivolumab dose, is excluded.
- **End-of-life costs** are counted for deaths in the intervals ending at
  weeks 1 to `r decision_week`, charged at those grid points.

The recomputed full-horizon totals equal `model_fun()` (largest absolute
difference `r fmt_diff(pre$check)`). The
diagnostic test is charged at t = 0 in every biomarker-guided strategy, so it
is shown separately from the survival-dependent part of the cost increment.

## Results

```{r pre-strategy-table}
week_idx <- decision_week + 1
traces <- model_fun(l_params_base, time_horizon = time_horizon, cl = cl,
                    return_traces = TRUE)$traces
occupancy_at <- function(strategy) {
  t <- traces[[strategy]]
  c(os = 1 - t$p_d[week_idx], pfs = t$p_pf[week_idx])
}
period <- sprintf("weeks 0-%d", decision_week)
x <- pre$strategy
occ <- sapply(x$Strategy, occupancy_at)
pre_table <- data.frame(
  Measure = c(paste("QALYs,", period), "QALYs, full horizon",
              paste("Cost,", period), "of which diagnostic test",
              "Cost, full horizon",
              sprintf("OS at week %d", decision_week),
              sprintf("PFS at week %d", decision_week)),
  rbind(fmt_q(x$qalys_pre, 5), fmt_q(x$qalys_full),
        format_eur(x$cost_pre), format_eur(x$diagnostic_pre),
        format_eur(x$cost_full),
        fmt_q(occ["os", ]), fmt_q(occ["pfs", ])),
  check.names = FALSE, stringsAsFactors = FALSE
)
names(pre_table) <- c("Measure", strategy_label(x$Strategy))
tab(pre_table, sprintf("Discounted QALYs and costs before week %d and over the full horizon (deterministic base case)", decision_week),
    align = c("l", rep("r", nrow(x)))) %>%
  tbl_footnote(general = sprintf(paste(
    "%s: accrued before the first nivolumab dose, as defined in the Methods.",
    "OS and PFS: population-averaged survival probabilities."), period),
    threeparttable = TRUE)
```

```{r pre-increment-table}
inc_table <- data.frame(
  Measure = c(paste("Inc. QALYs,", period), "Inc. QALYs, full horizon",
              "Share of full-horizon QALY increment",
              paste("Inc. cost,", period), "of which diagnostic test",
              "of which survival-dependent", "Inc. cost, full horizon",
              "Share of full-horizon cost increment",
              "Share, survival-dependent part only"),
  rbind(fmt_small(pre_inc$inc_qalys_pre), fmt_q(pre_inc$inc_qalys_full),
        fmt_pct(pre_inc$share_qalys, 3),
        format_eur(pre_inc$inc_cost_pre, 0.01),
        format_eur(pre_inc$inc_diagnostic_pre, 0.01),
        format_eur(pre_inc$inc_cost_pre_survival, 0.01),
        format_eur(pre_inc$inc_cost_full),
        fmt_pct(pre_inc$share_cost, 3), fmt_pct(pre_inc$share_cost_survival, 3)),
  check.names = FALSE, stringsAsFactors = FALSE
)
names(inc_table) <- c("Measure", strategy_label(pre_inc$Strategy))
tab(inc_table, sprintf("Increments versus standard of care: before week %d and full horizon", decision_week),
    align = c("l", rep("r", nrow(pre_inc)))) %>%
  tbl_footnote(general = paste(
    "Survival-dependent: the pre-decision cost increment without the diagnostic",
    "test, that is, the part driven by differences in state occupancy."),
    threeparttable = TRUE)
```

```{r pre-text}
crp_inc <- pre_inc[pre_inc$Strategy == "crp", ]
tmb_inc <- pre_inc[pre_inc$Strategy == "tmb_braf", ]
os_gap <- vapply(guided, function(s) occupancy_at(s)[["os"]] - occupancy_at(control)[["os"]], numeric(1))
pfs_gap <- vapply(guided, function(s) occupancy_at(s)[["pfs"]] - occupancy_at(control)[["pfs"]], numeric(1))
```

Before week `r decision_week`, the CRP-guided strategy accrues
`r fmt_small(crp_inc$inc_qalys_pre)` more QALYs than standard of care, which
is `r fmt_pct(crp_inc$share_qalys, 3)` of its full-horizon QALY increment of
`r fmt_q(crp_inc$inc_qalys_full)`. The survival-dependent part of its cost
increment before week `r decision_week` is
`r format_eur(crp_inc$inc_cost_pre_survival, 0.01)`
(`r fmt_pct(crp_inc$share_cost_survival, 3)` of the full-horizon cost
increment). The CRP test adds `r format_eur(crp_inc$inc_diagnostic_pre, 0.01)`.

For the TMB/BRAF-guided strategy the corresponding values are
`r fmt_small(tmb_inc$inc_qalys_pre)` QALYs
(`r fmt_pct(tmb_inc$share_qalys, 3)` of `r fmt_q(tmb_inc$inc_qalys_full)`) and
`r format_eur(tmb_inc$inc_cost_pre_survival, 0.01)`. Its larger pre-decision
cost increment is the NGS test
(`r format_eur(tmb_inc$inc_diagnostic_pre, 0.01)`), which the strategy
genuinely incurs.

The costs and QALYs accrued before the first nivolumab dose therefore
contribute almost nothing directly to either strategy's increments. The
curves have nevertheless separated by week `r decision_week`:
population-averaged OS differs from standard of care by
`r fmt_small(os_gap[["crp"]])` (CRP-guided) and
`r fmt_small(os_gap[["tmb_braf"]])` (TMB/BRAF-guided), and PFS by
`r fmt_small(pfs_gap[["crp"]])` and `r fmt_small(pfs_gap[["tmb_braf"]])`.
This separation carries into the rest of the horizon. The split above does
not attribute its later consequences; that would need the curves re-anchored
at the decision point (option (a)), which is not estimated here.

# Limitations

- **Corner scenarios only.** The four scenarios give every restored patient
  the same CRP value, and every patient with unknown TMB/BRAF the same
  TMB/BRAF value. With `r n_restored` unknown CRP values and
  `r n_tmb_unknown` unknown TMB/BRAF values there are `r n_combinations`
  combinations. The model is not linear in the assignments, so intermediate
  combinations need not fall between the corner results; the reported range
  covers the corner scenarios only. No imputation model or missing-data
  mechanism is assumed.
- **Distributions not re-selected.** Each scenario keeps the base-case
  distributions and checks only the OS >= PFS ordering. A new
  ordering-constrained selection on the enlarged cohort could choose a
  different pair.
- **Population and effects change together.** Restoring patients changes the
  target population (size, prevalences and age/sex mix) as well as the fitted
  effects, and the scenarios do not separate the two.
- **Deterministic only.** The scenarios quantify the sensitivity of the point
  estimates; parameter uncertainty is not propagated (no PSA).
- **Other exclusions.** The `r n_other_excluded` patients with a week-4 CRP
  but no TMB/BRAF result remain excluded in every scenario.
- **Pre-decision split.** The split before week `r decision_week` measures
  the costs and QALYs accrued in that period and the survival difference
  reached by its end. It is not an estimate of option (a), which would refit
  or re-anchor the curves so that the strategies are identical up to the
  decision point.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
