---
title: "Joint OS/PFS Coefficient Sampling"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    number-sections: true
    geometry: margin=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(sources = c("02", "03", "04", "05", "06"),
  funs = c("model_fun", "calculate_outcomes", "cea_helpers"),
  packages = c("here", "knitr", "dplyr", "survival", "flexsurv"))
component <- get_joint_sampling_models(sampling_models)
jc <- component$joint_covariance
if (is.null(jc)) stop("Regenerate joint sampling for issue #159")
ios <- seq_along(component$original_os$opt$par)
ipfs <- length(ios) + seq_along(component$original_pfs$opt$par)
psa_obj <- load_current_psa_cache()
base <- run_basecase(verbose = FALSE)$base_results
comparison <- create_psa_basecase_comparison(psa_obj, base)
incremental <- create_psa_incremental_comparison(psa_obj, base)
```

# Change and scope

Issue #159 implements the first proposed fix: estimate cross-endpoint coefficient dependence from paired patient bootstrap fits and draw OS and PFS coefficients together. The sampling method is `r component$method`. Every endpoint still has the multivariate-normal marginal distribution centred at its original maximum-likelihood estimate with its observed-information covariance. The deterministic model, parameter means, utility distributions and common population weighting are unchanged.

The bootstrap estimates dependence only. Its coefficient vectors are never used as PSA draws. This preserves the normal approximation introduced in issue #156 while restoring an estimated relationship between OS and PFS uncertainty. Coefficients use the unconstrained optimisation scale (log scale for positive baseline parameters), consistent with the [flexsurv covariance definition](https://chjackson.github.io/flexsurv/reference/flexsurvreg.html).

# Covariance construction

For each of `r jc$n_attempted` unstratified patient bootstrap resamples, both endpoints are fitted to the same sampled rows. A pair is excluded if either fit fails convergence, lacks a finite positive-definite covariance, or changes the estimable coefficient set. There is no rejection based on coefficient magnitude, outcome direction or survival crossings. More than 10% failed pairs, or insufficient rank to estimate the covariance, stops generation. Rejected pairs are never replaced with the original estimates.

Let $B$ be the empirical covariance of the retained paired bootstrap coefficients, with endpoint blocks $B_O$, $B_P$ and cross-block $B_{OP}$. Let $V_O$ and $V_P$ be the original fits' covariance matrices. Using symmetric positive-definite matrix square roots, define

$$
C_{OP} = V_O^{1/2} B_O^{-1/2} B_{OP} B_P^{-1/2} V_P^{1/2},
\qquad
V = \begin{pmatrix}V_O & C_{OP} \\ C_{OP}^{T} & V_P\end{pmatrix}.
$$

This is a block-diagonal congruence transformation of $B$. It preserves positive semidefiniteness and exactly retains both original marginal covariance blocks. The cross-block is a calibrated estimate of bootstrap dependence; it is not the unscaled empirical bootstrap cross-covariance. Directly combining that raw cross-block with different marginal covariance blocks need not produce a valid joint covariance matrix.

One normal vector is drawn with mean $(\hat\beta_O,\hat\beta_P)$ and covariance $V$, then split into OS and PFS coordinates. No coefficient or outcome centring correction is applied. Bootstrap and normal sampling each initialise their RNG with the recorded seed, so normal variates do not depend on the number of bootstrap attempts. All strategies share the same endpoint vectors within a draw; the joint biomarker population weights and economic parameters remain independent of survival coefficients.

# Diagnostics

```{r diagnostics}
diagnostics <- data.frame(
  Diagnostic = c("Bootstrap pairs attempted", "Successful pairs", "Failed pairs",
    "Normal PSA draws", "Minimum joint covariance eigenvalue",
    "Maximum OS marginal covariance difference", "Maximum PFS marginal covariance difference"),
  Value = c(jc$n_attempted, jc$n_successful, jc$n_failed, component$n_samples,
    min(eigen(jc$covariance, symmetric = TRUE)$values),
    max(abs(jc$covariance[ios, ios] - component$original_os$cov)),
    max(abs(jc$covariance[ipfs, ipfs] - component$original_pfs$cov))))
diagnostics$Value <- vapply(diagnostics$Value, function(x)
  format(x, scientific = x != 0 && abs(x) < 0.001, trim = TRUE, digits = 8), character(1))
knitr::kable(diagnostics, caption = "Covariance-generation diagnostics") %>% tbl_style()
if (length(jc$failure_reasons)) {
  failures <- data.frame(Reason = names(jc$failure_reasons), Pairs = as.integer(jc$failure_reasons))
  knitr::kable(failures, caption = "Excluded bootstrap pairs by reason") %>%
    tbl_style() %>% tbl_column_spec(1, width = "11cm")
}
```

```{r endpoint-correlations}
common <- intersect(colnames(jc$bootstrap_draws$os), colnames(jc$bootstrap_draws$pfs))
target <- cov2cor(jc$covariance)
realised <- cor(cbind(component$draws$os[, component$original_os$optpars],
                      component$draws$pfs[, component$original_pfs$optpars]))
correlations <- data.frame(Coefficient = common,
  Target = vapply(common, function(nm) target[paste0("os::", nm), paste0("pfs::", nm)], numeric(1)),
  Realised = vapply(common, function(nm) realised[match(nm, colnames(jc$bootstrap_draws$os)),
    length(ios) + match(nm, colnames(jc$bootstrap_draws$pfs))], numeric(1)))
knitr::kable(correlations, digits = 3, row.names = FALSE,
  caption = "OS/PFS correlations for corresponding coefficient coordinates") %>% tbl_style()
```

The bootstrap dependence estimate has finite-sample and Monte Carlo uncertainty that is not propagated as another PSA layer. The trial is small and sparse treatment/biomarker cells can make bootstrap fits unstable. Failed-pair exclusion can also affect the dependence estimate; the counts above disclose its extent. The covariance diagnostics and retained bootstrap coefficients are stored in the ignored sampling cache for audit.

# Deterministic versus probabilistic outcomes

The deterministic model evaluates nonlinear survival curves at the fitted coefficients. The PSA averages those curves over coefficient uncertainty. In general, $E[f(\beta)] \ne f(E[\beta])$. Before the ordering correction, discounted QALYs are a linear combination of OS and PFS areas with independent utilities. Changing only the OS/PFS dependence therefore cannot change their expected raw-curve QALYs while keeping both coefficient marginals fixed. It can change crossings, the resulting clamp correction, the distribution of net benefit and value of information. Finite Monte Carlo results can also change when drawing from the new covariance.

The zero-uncertainty regression sets the entire joint coefficient covariance to zero and fixes economic parameters and population weights. It reproduces every deterministic cost within EUR 1e-8 and QALY within 1e-12. This verifies agreement of the calculation paths, without recentering uncertain draws or relaxing the existing diagnostic.

```{r comparison}
compact <- function(x) {
  x <- x[, c(1, 2, match(c("Base_Case", "PSA_Mean", "PSA_SE", "Diff_SE"), names(x)))]
  names(x) <- c("Strategy", "Outcome", "Base", "PSA mean", "MC SE", "Difference (SE)")
  for (column in 3:5) x[[column]] <- ifelse(x$Outcome == "Cost",
    sprintf("%.0f", x[[column]]), sprintf("%.4f", x[[column]]))
  x[[6]] <- sprintf("%+.2f", x[[6]])
  x
}
knitr::kable(compact(comparison), caption = "PSA means versus fitted-parameter results") %>% tbl_style()
knitr::kable(compact(incremental), caption = "Incremental PSA means versus fitted-parameter increments") %>% tbl_style()
```

At the unchanged five-Monte-Carlo-SE threshold, `r sum(abs(comparison$Diff_SE) > 5)` of `r nrow(comparison)` level comparisons exceed the criterion. The criterion tests equality of outcome means; it is not a general consequence of correctly centred coefficient draws in a nonlinear model. Its numerical result remains visible in the test protocol. Expected-net-benefit decisions under uncertainty use the PSA; the deterministic results describe the fitted-parameter scenario.

Joint normal draws do not enforce OS >= PFS. The PSA retains its ordering clamp and [the ordering diagnostics](pfs_os_violations.md) quantify its effect separately. Neither nonzero correlation nor conditioning alone guarantees ordered survival curves.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
