---
title: "PFS > OS Ordering Violations in the PSA"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# ===============================================================================
# PFS > OS ordering violations in the PSA
#
# The PSA draws the OS and PFS coefficient vectors of the joint gamma models
# jointly (issue #159). A sampled pair can still put the predicted
# PFS curve above the predicted OS curve on part of the weekly grid, which a
# partitioned survival model cannot represent (progressed-state occupancy would
# be negative). model_fun() clamps PFS to OS (pmin) in PSA mode and emits a
# survival_ordering_warning; 10_PSA.R counts the warnings but keeps no curves.
#
# This report re-predicts the five subgroup curves of every draw in the
# sampling cache (R/pfs_os_violation_diagnostics.R, cached to
# data/tidy/pfs_os_violations_n{n}.rds) and reports
#   1. how many draws and PSA rows are affected, per curve;
#   2. where in the horizon and how far the curves cross;
#   3. the PFS-over-OS excess area before the clamp and the progressed-state
#      and progression-free areas before and after it;
#   4. the discounted-QALY consequence of the clamp per curve and strategy.
#
# Version history
#   1.0  2026-09-08  first version
#   1.1  2026-09-09  short curve labels and narrower tables (no scaled-down
#                    tables in the PDF); "area under the trough" renamed
#                    "PFS-over-OS excess area"; cache provenance table and
#                    consistency checks between the sampling, PSA and
#                    diagnostics caches (fingerprints and file dates)
# ===============================================================================
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05", "06"),
  funs = c("model_fun", "calculate_outcomes", "prediction_functions",
           "cea_helpers", "report_format", "psa_functions",
           "pfs_os_violation_diagnostics"),
  packages = c("here", "knitr", "ggplot2", "dplyr", "tidyr", "scales",
               "survival", "flexsurv"),
  set_theme = FALSE,
  quiet_sources = TRUE
)

theme_set(theme_minimal(base_size = 11) +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    plot.subtitle = element_text(size = 10, colour = "grey30"),
    plot.caption = element_text(size = 8.5, colour = "grey30", hjust = 0),
    legend.position = "bottom",
    legend.box = "vertical",
    legend.title = element_text(size = 9),
    legend.text = element_text(size = 9),
    strip.text = element_text(size = 10, face = "bold"),
    panel.grid.minor = element_blank(),
    panel.grid.major = element_line(colour = "grey90", linewidth = 0.3),
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 9)
  )
)

# ---- PSA cache (for the draw -> PSA row mapping) ---------------------------
expected_psa <- psa_cache_fingerprint(
  sampling_fingerprint = sampling_models$fingerprint,
  l_params_base = l_params_base,
  param_distributions = param_distributions,
  strategies = strategies,
  n_sim = n_sim,
  seed = analysis_seed,
  time_horizon = time_horizon,
  cl = cl
)
psa_obj <- load_psa_cache(
  verbose = FALSE, required = TRUE,
  expected_fingerprint = expected_psa,
  strategies = strategies, n_sim = n_sim,
  sampling_fingerprint = sampling_models$fingerprint
)

# ---- Per-draw diagnostics (cached; ~10 minutes on first run) ---------------
psa_params <- load_psa_params_cache(required = TRUE, seed = analysis_seed, n_sim = psa_obj$n_sim)
diag <- run_pfs_os_violation_diagnostics(
  sampling_models = sampling_models,
  data_complete = data_complete,
  data_original = data_complete,
  params = l_params_base,
  time_horizon = time_horizon,
  verbose = FALSE,
  psa_params = psa_params
)

# ---- Cache consistency: fingerprints first, file dates as a second guard ---
# The diagnostics fingerprint contains the sampling-cache fingerprint, so a
# regenerated sampling cache forces a regeneration above. The PSA cache stores
# the same sampling fingerprint; the three must agree, and the diagnostics must
# not predate the sampling-cache file they claim to describe.
prov <- list(
  sampling = cache_file_provenance(sampling_cache_path()),
  psa = cache_file_provenance(psa_obj_path()),
  diagnostics = cache_file_provenance(pfs_os_violation_cache_path())
)
if (!identical(psa_obj$fingerprint_inputs$sampling_fingerprint,
               diag$fingerprint_inputs$sampling_fingerprint)) {
  stop("The PSA cache and the violation diagnostics were built from different ",
       "sampling caches (", psa_obj$fingerprint_inputs$sampling_fingerprint,
       " vs ", diag$fingerprint_inputs$sampling_fingerprint, ")")
}
if (!identical(diag$fingerprint_inputs$sampling_fingerprint,
               sampling_models$fingerprint)) {
  stop("The violation diagnostics do not match the loaded sampling cache")
}
if (isTRUE(diag$creation_time < prov$sampling$mtime)) {
  stop("The violation diagnostics (", format(diag$creation_time),
       ") predate the sampling cache file (", format(prov$sampling$mtime), ")")
}
provenance_tbl <- data.frame(
  Cache = c("Sampling draws", "PSA results", "Violation diagnostics"),
  Modified = format(c(prov$sampling$mtime, prov$psa$mtime, prov$diagnostics$mtime),
                    "%Y-%m-%d %H:%M"),
  `Sampling fingerprint` = c(sampling_models$fingerprint,
                             psa_obj$fingerprint_inputs$sampling_fingerprint,
                             diag$fingerprint_inputs$sampling_fingerprint),
  check.names = FALSE, stringsAsFactors = FALSE
)
provenance_files <- paste(
  sprintf("%s: %s", provenance_tbl$Cache,
          basename(c(prov$sampling$path, prov$psa$path, prov$diagnostics$path))),
  collapse = "; ")

pc <- diag$per_curve
curves_meta <- diag$curves
curve_levels <- curves_meta$curve
curve_labels <- setNames(curves_meta$label, curves_meta$curve)
# Short labels for the tables (defined in the "Curves examined" table).
short_labels <- c(control = "SoC", crp_pos = "CRP+", crp_neg = "CRP-",
                  tmb_braf_pos = "TMB/BRAF+", tmb_braf_neg = "TMB/BRAF-")
short_labels <- short_labels[curve_levels]
if (anyNA(short_labels)) stop("No short label for curve(s): ",
                              paste(curve_levels[is.na(short_labels)], collapse = ", "))
pc$curve <- factor(pc$curve, levels = curve_levels)
pc$label <- curve_labels[as.character(pc$curve)]
pc$short <- factor(short_labels[as.character(pc$curve)], levels = short_labels)
n_draws <- diag$n_draws
n_curves <- length(curve_levels)

# Deterministic base case, for the incremental QALYs the clamp shift is
# compared with.
det_results <- model_fun(l_params_base, time_horizon = time_horizon, cl = cl,
                         determpsa = "det")
det_effect <- setNames(det_results$Effect, det_results$Strategy)

fmt_pct <- function(x, digits = 1) sprintf(paste0("%.", digits, "f%%"), 100 * x)
fmt_num <- function(x, digits = 3) formatC(x, format = "f", digits = digits, big.mark = ",")
mc_se <- function(p, n) sqrt(p * (1 - p) / n)
short_of <- function(curve) unname(short_labels[as.character(curve)])

# ---- Draw-level summary ----------------------------------------------------
by_draw <- pc %>%
  group_by(draw) %>%
  summarise(
    any_violation = any(violated),
    n_curves_violating = sum(violated),
    excess_area_total = sum(excess_area_years),
    .groups = "drop"
  )
share_any <- mean(by_draw$any_violation)
n_any <- sum(by_draw$any_violation)

# Draw -> PSA row mapping. psa_obj$model_idx is the sampling-cache draw behind
# each retained PSA row (issue #156); replaced draws point at the model that
# finally succeeded.
model_idx <- psa_obj$model_idx
psa_rows_affected <- by_draw$any_violation[match(psa_obj$sim, by_draw$draw)]
share_psa_rows <- mean(psa_rows_affected)
n_psa_rows <- length(model_idx)
n_replaced <- sum(model_idx != seq_along(model_idx))

# ---- Per-curve summary -----------------------------------------------------
per_curve_summary <- pc %>%
  group_by(curve) %>%
  summarise(
    n_violating = sum(violated),
    share = mean(violated),
    se = mc_se(mean(violated), n()),
    .groups = "drop"
  ) %>%
  mutate(label = curve_labels[as.character(curve)], short = short_of(curve))

# ---- Extent among violating draws ------------------------------------------
extent <- pc %>%
  filter(violated) %>%
  group_by(curve) %>%
  summarise(
    n = n(),
    med_n_pts = median(n_violations),
    q1_n_pts = quantile(n_violations, 0.25),
    q3_n_pts = quantile(n_violations, 0.75),
    max_n_pts = max(n_violations),
    med_first = median(first_week),
    min_first = min(first_week),
    med_last = median(last_week),
    max_last = max(last_week),
    med_max_excess = median(max_excess),
    p95_max_excess = quantile(max_excess, 0.95),
    max_max_excess = max(max_excess),
    .groups = "drop"
  ) %>%
  mutate(short = short_of(curve))

# ---- Excess area and state areas -------------------------------------------
area_all <- pc %>%
  group_by(curve) %>%
  summarise(
    mean_excess_all = mean(excess_area_years),
    mean_pp_raw = mean(pp_area_raw_years),
    mean_pp_clamped = mean(pp_area_clamped_years),
    mean_pf_raw = mean(pf_area_raw_years),
    mean_pf_clamped = mean(pf_area_clamped_years),
    mean_os = mean(os_area_years),
    .groups = "drop"
  ) %>%
  mutate(label = curve_labels[as.character(curve)], short = short_of(curve))

area_viol <- pc %>%
  filter(violated) %>%
  group_by(curve) %>%
  summarise(
    mean_excess = mean(excess_area_years),
    med_excess = median(excess_area_years),
    p95_excess = quantile(excess_area_years, 0.95),
    max_excess_area = max(excess_area_years),
    .groups = "drop"
  ) %>%
  mutate(label = curve_labels[as.character(curve)], short = short_of(curve))

# ---- QALY consequence -------------------------------------------------------
qaly_curve <- pc %>%
  group_by(curve) %>%
  summarise(
    mean_diff = mean(qaly_raw_minus_clamped),
    mean_diff_viol = mean(qaly_raw_minus_clamped[violated]),
    max_diff = max(qaly_raw_minus_clamped),
    mean_clamped = mean(qaly_clamped),
    .groups = "drop"
  ) %>%
  mutate(short = short_of(curve), rel = mean_diff / mean_clamped)

# Strategy-level QALY effect of the clamp: the guided strategies weight the
# positive and negative curves by each draw's common-population prevalence, and the QALY
# difference is linear in the curves.
control_strategy <- get_control_strategy()
prev <- setNames(
  vapply(get_biomarkers(), function(bm) l_params_base[[paste0("p_", bm)]], 1),
  get_biomarkers()
)
wide_diff <- pc %>%
  select(draw, curve, qaly_raw_minus_clamped) %>%
  pivot_wider(names_from = curve, values_from = qaly_raw_minus_clamped)
strategy_diff <- data.frame(draw = wide_diff$draw)
strategy_diff[[control_strategy]] <- wide_diff[[control_strategy]]
for (bm in get_biomarkers()) {
  draw_prevalence <- psa_params[[paste0("p_", bm)]][match(wide_diff$draw, psa_params$sim)]
  strategy_diff[[bm]] <- draw_prevalence * wide_diff[[paste0(bm, "_pos")]] +
    (1 - draw_prevalence) * wide_diff[[paste0(bm, "_neg")]]
}
strategy_qaly <- do.call(rbind, lapply(strategies, function(s) {
  d <- strategy_diff[[s]]
  inc <- if (s == control_strategy) rep(0, length(d)) else d - strategy_diff[[control_strategy]]
  data.frame(
    strategy = s,
    Strategy = unname(strategy_display_name(s)),
    mean_diff = mean(d), max_diff = max(d),
    mean_inc = mean(inc), min_inc = min(inc), max_inc = max(inc),
    mean_psa_effect = mean(psa_obj$effectiveness[[s]]),
    stringsAsFactors = FALSE
  )
}))
sq_crp <- strategy_qaly[strategy_qaly$strategy == "crp", ]
sq_tmb <- strategy_qaly[strategy_qaly$strategy == "tmb_braf", ]
sq_ctl <- strategy_qaly[strategy_qaly$strategy == control_strategy, ]

# Decomposition of the PSA-versus-base-case QALY gap: how much of it is the
# clamp. Raw PSA mean = clamped PSA mean + mean overstatement.
decomp <- do.call(rbind, lapply(strategies, function(s) {
  clamped <- mean(psa_obj$effectiveness[[s]])
  raw <- clamped + mean(strategy_diff[[s]])
  data.frame(strategy = s, base = det_effect[[s]], clamped = clamped, raw = raw,
             stringsAsFactors = FALSE)
}))
decomp$inc_base <- decomp$base - decomp$base[decomp$strategy == control_strategy]
decomp$inc_clamped <- decomp$clamped - decomp$clamped[decomp$strategy == control_strategy]
decomp$inc_raw <- decomp$raw - decomp$raw[decomp$strategy == control_strategy]
decomp_crp <- decomp[decomp$strategy == "crp", ]
clamp_share_of_gap <- (decomp_crp$inc_raw - decomp_crp$inc_clamped) /
  (decomp_crp$inc_base - decomp_crp$inc_clamped)

# ---- Timing curves ---------------------------------------------------------
timing <- diag$timing
timing$curve <- factor(timing$curve, levels = curve_levels)
timing$label <- curve_labels[as.character(timing$curve)]
peak_timing <- timing %>%
  group_by(curve, label) %>%
  summarise(peak_week = week[which.max(share_violating)],
            peak_share = max(share_violating), .groups = "drop") %>%
  mutate(short = short_of(curve))

# ---- Example curves (worst draw per curve) ---------------------------------
examples <- diag$examples
examples$curve <- factor(examples$curve, levels = curve_levels)
examples$label <- curve_labels[as.character(examples$curve)]
example_draws <- examples %>% distinct(curve, label, draw)

validation <- diag$validation
max_validation_diff <- max(validation$max_abs_diff)

# Figure captions built here because `!expr` needs a single YAML string.
timing_cap <- paste0(
  "Share of the ", format(n_draws, big.mark = ","),
  " draws in which PFS exceeds OS at each week of the horizon, by curve. ",
  "The share rises through the horizon and is highest at its end (week ",
  time_horizon, "): ",
  paste(sprintf("%s %s", peak_timing$short, fmt_pct(peak_timing$peak_share, 0)),
        collapse = "; "), "."
)
example_cap <- paste0(
  "The draw with the largest PFS-over-OS excess area for each curve (draws ",
  paste(example_draws$draw, collapse = ", "),
  "). Solid lines are the raw sampled OS and PFS; the shaded region is the ",
  "excess area, the trough where PFS lies above OS; the dashed line is the ",
  "clamped PFS = min(PFS, OS) that the model uses."
)
```

# Overview

The probabilistic sensitivity analysis (PSA) draws the coefficient vectors of the overall survival (OS) and progression-free survival (PFS) gamma models jointly (issue #159). Their cross-endpoint dependence is estimated by fitting both endpoints to the same patient bootstrap resamples, while preserving the fitted marginal covariance matrices. This replaces the independent draws of issue #156. Correlation does not enforce survival ordering: a sampled pair can still predict PFS above OS on part of the 10-year weekly grid. A partitioned survival model cannot represent a negative progressed-state occupancy OS - PFS.

The model handles the problem with a clamp. In PSA mode `model_fun()` replaces the PFS curve by min(PFS, OS) for any curve that crosses and emits a `survival_ordering_warning`; the PSA script counts those warnings per subgroup but does not retain the curves. In the deterministic base case the ordering is guaranteed by the ordering-constrained distribution selection and any crossing stops the model.

This report quantifies the crossings behind those warnings. For every one of the `r format(n_draws, big.mark = ",")` retained PSA rows it re-predicts the five population-averaged subgroup curves that the PSA uses and reports:

1. the number and share of draws, and of retained PSA rows, with at least one PFS > OS violation, overall and per curve;
2. where in the horizon the curves cross and by how much;
3. the **PFS-over-OS excess area**, the area between the two curves on the stretch where PFS lies above OS (the trough in the figures), before the clamp (after the clamp it is zero by construction), together with the progression-free and progressed-state areas before and after the clamp;
4. the discounted-QALY consequence of the clamp per curve and per strategy.

# Methods

## Two sources of variation in a PSA draw

Each PSA iteration draws one combined OS/PFS coefficient vector (log shapes, log baseline rates, and covariate effects on log rate) from a joint multivariate normal. Each endpoint retains the mean and marginal covariance of its own fit. Within the iteration the OS vector is shared by every patient and every curve, and so is the PFS vector. Patient heterogeneity is integrated out by averaging the patient curves with the shared weights from that row's joint biomarker distribution (issue #166). The paired-bootstrap cross-covariance links the two endpoints but does not impose OS >= PFS. The [joint sampling specification](joint_survival_sampling.md) reports bootstrap convergence and coefficient dependence.

## Curves examined

The PSA evaluates five curves per draw, each a population average over the complete-case patients of the subgroup with `Rx` set as the strategy dictates (issue #151). They are the curves that `model_fun()` checks and clamps one by one. The short labels in the first column are used in the tables that follow.

```{r curves-table}
curves_tbl <- curves_meta %>%
  transmute(
    Label = short_of(curve),
    Curve = label,
    Patients = n_patients,
    `Rx set to` = ifelse(subgroup == "positive", "Experimental", "Control"),
    Strategy = unname(strategy_display_name(strategy))
  )
knitr::kable(
  curves_tbl, booktabs = TRUE, align = c("l", "l", "r", "l", "l"),
  caption = "Subgroup curves evaluated per draw"
) %>%
  tbl_style(latex_options = "HOLD_position")
```

The curves are computed in closed form from the gamma accelerated-failure-time parameters of each draw (shape and covariate-specific rate) rather than through `flexsurv::predict()`, which makes the full pass about twenty times faster. The closed form was checked against the pipeline's own prediction helper (`generate_psa_population_averaged_predictions()`) on `r length(unique(validation$draw))` draws and all five curves for both outcomes: the largest absolute difference at any of the 521 weekly points is `r formatC(max_validation_diff, format = "e", digits = 1)`. The clamped QALYs computed here reproduce the strategy QALYs that `model_fun()` returns for the same draw.

## Metrics

For each draw and curve, with $t$ running over the weekly grid (0 to `r time_horizon` weeks) and $\Delta_t = \max(\mathrm{PFS}_t - \mathrm{OS}_t, 0)$ the excess of PFS over OS:

- **Violation**: $\Delta_t > 0$ at one or more time points. The number of violating time points, the first and last violating week, and the largest excess are recorded.
- **PFS-over-OS excess area (before the clamp)**: $\int \Delta_t \, dt$ by the trapezoidal rule on the weekly grid, in patient-years. It is the area between the PFS and OS curves on the stretch where PFS lies on top. After the clamp, PFS is replaced by min(PFS, OS) and the area is zero.
- **State areas**: the progression-free area $\int \mathrm{PFS}_t\,dt$ and the progressed-state area $\int (\mathrm{OS}_t - \mathrm{PFS}_t)\,dt$ before the clamp (the latter negative on the violating stretch), and $\int \min(\mathrm{PFS}_t, \mathrm{OS}_t)\,dt$ and $\int \max(\mathrm{OS}_t - \mathrm{PFS}_t, 0)\,dt$ after it, in patient-years. The clamp moves exactly the excess area from the progression-free state to the progressed state; OS is untouched.
- **QALY consequence**: discounted QALYs the raw curves would have produced minus the clamped QALYs. Because the model's cycle sum gives $p_{PF} = \mathrm{PFS}$ and $p_P = \mathrm{OS} - \mathrm{PFS}$, the difference is $\sum_t \Delta_t \,(u_{np} - u_p)\, cl\, w_t$ using each PSA row's sampled utilities, $cl = 1/52$ and effect discount weights $w_t$ at `r fmt_pct(l_params_base$dr_effects, 0)` per year. It is the amount by which the raw curves overstate QALYs by counting the excess as progression-free time at the higher utility.

Areas use the trapezoidal rule (the convention of `restricted_mean_survival()`); the QALY consequence uses the model's own cycle sum so that it matches `model_fun()` exactly.

## Mapping draws to PSA rows

The PSA object records, for every retained row (`sim`), the sampling-cache draw that produced it (`model_idx`; issue #156). Diagnostics retain the row's sampled joint-population weights and utilities and use its `model_idx` for the survival coefficients. Rows whose original draw failed therefore keep their economic parameters while using the replacement model. In the current cache `r n_replaced` of `r format(n_psa_rows, big.mark = ",")` rows were replaced. Counts below refer to these retained PSA rows.

## Cache provenance

The diagnostics are cached with a fingerprint of the sampling-cache fingerprint, the explicit prediction population, the PSA parameter table (including joint weights, utilities and model indices), the base parameters, the discount rate, the horizon and the cycle length. Changes to these inputs force regeneration. The PSA cache stores the same sampling fingerprint. Before rendering, this report stops unless all three caches carry the same sampling fingerprint and the diagnostics file is younger than the sampling-cache file.

```{r provenance-table}
knitr::kable(provenance_tbl, booktabs = TRUE, align = c("l", "l", "l"),
             caption = "Caches read by this report") %>%
  tbl_style(latex_options = c("HOLD_position")) %>%
  tbl_footnote(general = paste0("Files in data/tidy: ", provenance_files, "."))
```

# Results

## How many draws are affected

```{r headline}
headline <- data.frame(
  Quantity = c(
    "Sampling-cache draws evaluated",
    "Draws with PFS > OS on at least one curve",
    "Share of draws affected (Monte Carlo SE)",
    "Retained PSA rows",
    "PSA rows whose draw has at least one violation",
    "Share of PSA rows affected"
  ),
  Value = c(
    format(n_draws, big.mark = ","),
    format(n_any, big.mark = ","),
    sprintf("%s (%s)", fmt_pct(share_any), fmt_pct(mc_se(share_any, n_draws))),
    format(n_psa_rows, big.mark = ","),
    format(sum(psa_rows_affected), big.mark = ","),
    fmt_pct(share_psa_rows)
  ),
  stringsAsFactors = FALSE
)
knitr::kable(headline, booktabs = TRUE, align = c("l", "r"),
             caption = "Draws and PSA rows with a PFS > OS violation") %>%
  tbl_style(latex_options = "HOLD_position")
```

**`r fmt_pct(share_any)` of the `r format(n_draws, big.mark = ",")` coefficient draws** put PFS above OS on at least one of the five curves, and `r fmt_pct(share_psa_rows)` of the retained PSA rows come from such a draw. The clamp is therefore not a rare safety net but acts in roughly `r if (share_any > 0.4) "half" else if (share_any > 0.2) "a quarter to a half" else "a minority"` of the PSA.

```{r per-curve-table}
per_curve_tbl <- per_curve_summary %>%
  transmute(
    Curve = short,
    `Draws violating` = format(n_violating, big.mark = ","),
    `Share of draws` = fmt_pct(share),
    `MC SE` = fmt_pct(se, 2)
  )
knitr::kable(per_curve_tbl, booktabs = TRUE, align = c("l", "r", "r", "r"),
             caption = "Draws with PFS > OS, by curve") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Each draw contributes one OS and one PFS coefficient vector shared by all five ",
    "curves, so the same draw can violate on several curves. MC SE: binomial ",
    "Monte Carlo standard error of the share over ", format(n_draws, big.mark = ","),
    " draws."))
```

```{r n-curves-table}
n_curves_tbl <- by_draw %>%
  count(n_curves_violating, name = "draws") %>%
  mutate(share = draws / n_draws) %>%
  transmute(
    `Curves violating in the draw` = n_curves_violating,
    Draws = format(draws, big.mark = ","),
    Share = fmt_pct(share)
  )
knitr::kable(n_curves_tbl, booktabs = TRUE, align = c("r", "r", "r"),
             caption = "Number of curves (out of five) with PFS > OS per draw") %>%
  tbl_style(latex_options = "HOLD_position")
```

## Where and how far the curves cross

```{r extent-where-table}
extent_where_tbl <- extent %>%
  transmute(
    Curve = short,
    `Violating draws` = format(n, big.mark = ","),
    `Points, median [IQR]` = sprintf("%d [%d, %d]", as.integer(med_n_pts),
                                     as.integer(q1_n_pts), as.integer(q3_n_pts)),
    `Points, max` = as.integer(max_n_pts),
    `First week` = sprintf("%d (%d)", as.integer(med_first), as.integer(min_first)),
    `Last week` = sprintf("%d (%d)", as.integer(med_last), as.integer(max_last))
  )
knitr::kable(extent_where_tbl, booktabs = TRUE,
             align = c("l", "r", "r", "r", "r", "r"),
             caption = "Where the curves cross, among violating draws") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Points: number of the 521 weekly grid points (weeks 0 to ", time_horizon,
    ") at which PFS exceeds OS. First week: median (minimum) of the first ",
    "violating week; last week: median (maximum) of the last violating week."))
```

```{r extent-depth-table}
extent_depth_tbl <- extent %>%
  transmute(
    Curve = short,
    `Violating draws` = format(n, big.mark = ","),
    Median = sprintf("%.4f", med_max_excess),
    `95th percentile` = sprintf("%.4f", p95_max_excess),
    Maximum = sprintf("%.4f", max_max_excess)
  )
knitr::kable(extent_depth_tbl, booktabs = TRUE,
             align = c("l", "r", "r", "r", "r"),
             caption = "Largest PFS - OS within the draw (survival-probability units), among violating draws") %>%
  tbl_style(latex_options = "HOLD_position")
```

```{r timing-plot, fig.width=8, fig.height=5.5}
#| fig-cap: !expr timing_cap
ggplot(timing, aes(x = week, y = share_violating, colour = label)) +
  geom_line(linewidth = 0.8) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  scale_x_continuous(breaks = seq(0, time_horizon, by = 52),
                     labels = function(x) x / 52,
                     sec.axis = dup_axis(name = NULL, labels = NULL)) +
  labs(x = "Years from randomisation", y = "Share of draws with PFS > OS",
       colour = NULL, title = "When the sampled curves cross") +
  guides(colour = guide_legend(nrow = 2))
```

```{r mean-excess-plot, fig.width=8, fig.height=5.5}
#| fig-cap: "Mean excess of PFS over OS at each week, averaged over all draws (draws without a violation at that week contribute zero). The area under each line, in weeks, is 52 times the all-draw mean excess area of that curve in the state-areas table."
ggplot(timing, aes(x = week, y = mean_excess, colour = label)) +
  geom_line(linewidth = 0.8) +
  scale_x_continuous(breaks = seq(0, time_horizon, by = 52),
                     labels = function(x) x / 52) +
  labs(x = "Years from randomisation", y = "Mean PFS - OS (where positive)",
       colour = NULL, title = "Average depth of the excess over the horizon") +
  guides(colour = guide_legend(nrow = 2))
```

## PFS-over-OS excess area before and after the clamp

```{r area-viol-table}
area_viol_tbl <- area_viol %>%
  transmute(
    Curve = short,
    Mean = fmt_num(mean_excess, 4),
    Median = fmt_num(med_excess, 4),
    `95th percentile` = fmt_num(p95_excess, 4),
    Maximum = fmt_num(max_excess_area, 4),
    `After clamp` = "0"
  )
knitr::kable(area_viol_tbl, booktabs = TRUE,
             align = c("l", rep("r", 5)),
             caption = "PFS-over-OS excess area (patient-years) among violating draws, before and after the clamp") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Area = integral of max(PFS - OS, 0) over the ", time_horizon / 52,
    "-year horizon, trapezoidal rule on the weekly grid, in patient-years per ",
    "patient. After the clamp PFS = min(PFS, OS) and the area is zero for every draw."))
```

```{r area-all-table}
area_long <- bind_rows(
  area_all %>% transmute(short, State = "Progression-free",
                         raw = mean_pf_raw, clamped = mean_pf_clamped),
  area_all %>% transmute(short, State = "Progressed",
                         raw = mean_pp_raw, clamped = mean_pp_clamped)
) %>%
  mutate(State = factor(State, levels = c("Progression-free", "Progressed"))) %>%
  arrange(State, short) %>%
  transmute(
    State, Curve = short,
    `Before clamp` = fmt_num(raw, 4),
    `After clamp` = fmt_num(clamped, 4),
    Change = fmt_num(clamped - raw, 4)
  )
knitr::kable(area_long, booktabs = TRUE, align = c("l", "l", "r", "r", "r"),
             caption = "Mean state areas over all draws (patient-years), before and after the clamp") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Means over all ", format(n_draws, big.mark = ","), " draws (non-violating draws ",
    "are unchanged by the clamp). Progression-free area = integral of PFS ",
    "(min(PFS, OS) after the clamp); progressed area = integral of OS - PFS ",
    "(negative on the violating stretch before the clamp; max(OS - PFS, 0) after). ",
    "The change is the all-draw mean excess area, moved from the progression-free ",
    "to the progressed state; the OS area (",
    paste(sprintf("%s %s", area_all$short, fmt_num(area_all$mean_os, 3)), collapse = ", "),
    " patient-years) is unchanged."))
```

Averaged over all draws, the clamp moves `r fmt_num(area_all$mean_excess_all[area_all$curve == control_strategy], 4)` patient-years from the progression-free to the progressed state on the standard-of-care curve, against a mean progressed-state area after the clamp of `r fmt_num(area_all$mean_pp_clamped[area_all$curve == control_strategy], 3)` patient-years. The largest excess area on any curve is `r fmt_num(max(area_viol$max_excess_area), 3)` patient-years (`r area_viol$label[which.max(area_viol$max_excess_area)]`).

```{r area-distribution-plot, fig.width=8, fig.height=5}
#| fig-cap: "Distribution of the PFS-over-OS excess area among violating draws, by curve (log scale)."
ggplot(pc %>% filter(violated), aes(x = label, y = excess_area_years)) +
  geom_boxplot(outlier.size = 0.6, width = 0.5, fill = "grey90") +
  scale_y_log10(labels = label_number(accuracy = 0.0001)) +
  scale_x_discrete(labels = label_wrap(18)) +
  labs(x = NULL, y = "Excess area (patient-years, log scale)",
       title = "PFS-over-OS excess area among violating draws")
```

```{r example-plot, fig.width=8, fig.height=9}
#| fig-cap: !expr example_cap
ex_long <- examples %>%
  mutate(pfs_clamped = pmin(pfs, os), year = week / 52)
ggplot(ex_long, aes(x = year)) +
  geom_ribbon(aes(ymin = os, ymax = pmax(pfs, os)), fill = "firebrick", alpha = 0.25) +
  geom_line(aes(y = os, colour = "OS (raw)"), linewidth = 0.8) +
  geom_line(aes(y = pfs, colour = "PFS (raw)"), linewidth = 0.8) +
  geom_line(aes(y = pfs_clamped, colour = "PFS (clamped)"), linetype = "dashed",
            linewidth = 0.8) +
  facet_wrap(~ label, ncol = 2, labeller = label_wrap_gen(30)) +
  scale_colour_manual(values = c("OS (raw)" = "black", "PFS (raw)" = "firebrick",
                                 "PFS (clamped)" = "steelblue")) +
  scale_y_continuous(labels = percent_format(accuracy = 1)) +
  labs(x = "Years from randomisation", y = "Survival probability", colour = NULL,
       title = "Worst-case draw per curve")
```

## QALY consequence of the clamp

```{r qaly-curve-table}
qaly_curve_tbl <- qaly_curve %>%
  transmute(
    Curve = short,
    `All draws` = fmt_num(mean_diff, 4),
    `Violating draws` = fmt_num(mean_diff_viol, 4),
    Maximum = fmt_num(max_diff, 4),
    `Clamped QALYs` = fmt_num(mean_clamped, 3),
    Relative = fmt_pct(rel, 2)
  )
knitr::kable(qaly_curve_tbl, booktabs = TRUE,
             align = c("l", rep("r", 5)),
             caption = "Discounted QALYs the raw curves would add relative to the clamped curves, by curve") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Raw minus clamped discounted QALYs per patient = sum over cycles of ",
    "max(PFS - OS, 0) x (u_np - u_p) x cycle length x discount weight; mean over ",
    "all draws and over violating draws, and the maximum. Clamped QALYs: mean ",
    "over all draws. Relative: all-draw mean difference as a share of the mean ",
    "clamped QALYs of the curve."))
```

```{r qaly-strategy-table}
strategy_level_tbl <- strategy_qaly %>%
  transmute(
    Strategy,
    `Mean overstatement` = fmt_num(mean_diff, 4),
    Maximum = fmt_num(max_diff, 4),
    `Mean PSA QALYs` = fmt_num(mean_psa_effect, 3)
  )
knitr::kable(strategy_level_tbl, booktabs = TRUE, align = c("l", "r", "r", "r"),
             caption = "QALY overstatement of the raw curves by strategy (per patient, discounted)") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Strategy values use each PSA draw's joint-population weights, marginal ",
    "prevalences and utilities. Mean PSA QALYs are the cached PSA ",
    "means (clamped curves)."))
```

```{r qaly-increment-table}
strategy_inc_tbl <- strategy_qaly %>%
  filter(strategy != control_strategy) %>%
  transmute(
    Strategy,
    `Mean shift` = fmt_num(-mean_inc, 4),
    `Largest downward` = fmt_num(-max_inc, 4),
    `Largest upward` = fmt_num(-min_inc, 4)
  )
knitr::kable(strategy_inc_tbl, booktabs = TRUE, align = c("l", "r", "r", "r"),
             caption = "Shift of the incremental QALYs versus standard of care caused by the clamp (clamped minus raw, per patient)") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = paste0(
    "Per draw, the clamp's effect on the strategy's QALYs minus its effect on ",
    "standard of care. A negative value means the clamp makes the guided strategy ",
    "look worse relative to standard of care than the raw curves would."))
```

The clamp lowers the QALYs of every strategy, because the excess is progression-free time that becomes progressed time at the lower sampled utility. The mean overstatement the raw curves would have produced is `r fmt_num(sq_ctl$mean_diff, 4)` QALYs for standard of care, `r fmt_num(sq_crp$mean_diff, 4)` for the CRP-guided strategy and `r fmt_num(sq_tmb$mean_diff, 4)` for the TMB/BRAF-guided strategy. What matters for the decision is the effect on the increment: the clamp shifts the mean incremental QALYs of the CRP-guided strategy versus standard of care by `r fmt_num(-sq_crp$mean_inc, 4)` and of the TMB/BRAF-guided strategy by `r fmt_num(-sq_tmb$mean_inc, 4)`, with a per-draw range from `r fmt_num(-sq_crp$max_inc, 4)` to `r fmt_num(-sq_crp$min_inc, 4)` for CRP.

## Is the clamp why the PSA increments differ from the base case?

```{r decomp-level-table}
decomp_level_tbl <- decomp %>%
  transmute(
    Strategy = unname(strategy_display_name(strategy)),
    `Base case` = fmt_num(base, 4),
    `PSA, clamped` = fmt_num(clamped, 4),
    `PSA, raw` = fmt_num(raw, 4)
  )
knitr::kable(decomp_level_tbl, booktabs = TRUE, align = c("l", "r", "r", "r"),
             caption = "Discounted QALYs per patient: deterministic base case, PSA mean with the clamp (the cached PSA), and PSA mean the raw curves would have given") %>%
  tbl_style(latex_options = "HOLD_position") %>%
  tbl_footnote(general = "PSA, raw = cached PSA mean + mean overstatement of the raw curves for the strategy.")
```

```{r decomp-inc-table}
decomp_inc_tbl <- decomp %>%
  filter(strategy != control_strategy) %>%
  transmute(
    Strategy = unname(strategy_display_name(strategy)),
    `Base case` = fmt_num(inc_base, 4),
    `PSA, clamped` = fmt_num(inc_clamped, 4),
    `PSA, raw` = fmt_num(inc_raw, 4)
  )
knitr::kable(decomp_inc_tbl, booktabs = TRUE, align = c("l", "r", "r", "r"),
             caption = "Incremental discounted QALYs versus standard of care: base case, PSA mean with the clamp, and PSA mean without it") %>%
  tbl_style(latex_options = "HOLD_position")
```

The PSA incremental QALYs of the CRP-guided strategy are `r fmt_num(decomp_crp$inc_clamped, 4)`, compared with a deterministic increment of `r fmt_num(decomp_crp$inc_base, 4)`. Removing the clamp would give `r fmt_num(decomp_crp$inc_raw, 4)`: the clamp `r if (clamp_share_of_gap < 0) "narrows" else "widens"` the gap by an amount equal to `r fmt_pct(abs(clamp_share_of_gap), 1)` of the reported gap. The remaining difference reflects nonlinear averaging of survival curves over coefficient uncertainty and Monte Carlo error. Cross-endpoint dependence cannot change the expected raw-curve QALYs when the endpoint marginal distributions and independent utility/population distributions are held fixed. Earlier wording attributed the whole gap to endpoint independence; that causal attribution was too strong.

# Interpretation

- **The crossings are frequent but shallow.** About `r fmt_pct(share_any, 0)` of draws cross on at least one curve, yet the median violating draw crosses by at most `r sprintf("%.4f", median(pc$max_excess[pc$violated]))` in survival probability and carries an excess area of `r sprintf("%.4f", median(pc$excess_area_years[pc$violated]))` patient-years. The crossings sit in the extrapolated tail where both curves are close to their floor, so the area involved is small relative to the restricted OS area of about `r fmt_num(mean(area_all$mean_os), 2)` patient-years.
- **The clamp is a one-sided correction.** min(PFS, OS) accepts the OS draw as given and truncates PFS; it never raises OS. It lowers QALYs when the progression-free utility exceeds the progressed utility, without targeting the deterministic base case.
- **The consequence is differential but small.** The five curves cross at different rates (`r paste(sprintf("%s %s", per_curve_summary$short, fmt_pct(per_curve_summary$share, 0)), collapse = "; ")`), so the clamp moves the increments of the guided strategies versus standard of care, not only their levels. The mean shift on the CRP increment is `r fmt_num(-sq_crp$mean_inc, 4)` QALYs against a base-case incremental gain of `r fmt_num(decomp_crp$inc_base, 4)`. Individual draws can move by up to `r fmt_num(max(abs(c(strategy_qaly$min_inc, strategy_qaly$max_inc))), 3)` QALYs, substantially more than the mean shift.
- **Report both estimands.** The deterministic CRP increment is `r fmt_num(decomp_crp$inc_base, 4)` QALYs; the PSA mean is `r fmt_num(decomp_crp$inc_clamped, 4)` with the clamp and `r fmt_num(decomp_crp$inc_raw, 4)` without it. A nonlinear model can produce this difference under correctly centred coefficient uncertainty. The original five-SE diagnostic is retained; the separate zero-uncertainty regression verifies equality when all uncertainty is removed.
- **Joint covariance is implemented.** Issue #159 uses the first proposed fix: a paired patient bootstrap estimates dependence for joint normal coefficient draws. It does not guarantee ordered curves. A survival model parameterised to enforce ordering would be a separate structural change; correlation or conditioning alone is insufficient without that constraint.

# Notes

- The diagnostics are cached in `data/tidy/pfs_os_violations_n{n_samples}.rds`; `run_pfs_os_violation_diagnostics()` regenerates the cache on any fingerprint mismatch. The current cache was built from sampling cache `r sampling_models$fingerprint` (method `r get_joint_sampling_models(sampling_models)$method`) in `r sprintf("%.0f", diag$elapsed)` seconds on `r format(diag$creation_time, "%Y-%m-%d %H:%M")`.
- Curves are computed in closed form from the gamma parameters of each draw; `validate_direct_curves()` checks them against the pipeline's `predict()`-based helper before every regeneration and stops if they differ by more than 1e-8.
- All values are per patient over the 10-year horizon; areas are restricted means by the trapezoidal rule, QALY differences use the model's cycle sum.
- "PFS-over-OS excess area" is this report's term for the area between the two curves on the stretch where they are inverted; it is not a standard quantity. The figures call the same region the trough.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.0
