---
title: "PSA Extrapolation Plausibility"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    fig-width: 7
    fig-height: 7
    keep-tex: false
    geometry: [top=2.5cm, bottom=2.5cm, left=2.5cm, right=2.5cm]
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(sources = c("02", "03", "04", "05", "06"),
  funs = c("model_fun", "calculate_outcomes", "prediction_functions", "cea_helpers",
           "report_format", "psa_functions", "pfs_os_violation_diagnostics",
           "psa_extrapolation_diagnostics"),
  packages = c("here", "knitr", "ggplot2", "dplyr", "tidyr", "survival", "flexsurv"),
  set_theme = FALSE, quiet_sources = TRUE)
theme_set(theme_minimal(base_size = 10) + theme(legend.position = "bottom",
  panel.grid.minor = element_blank()))
psa <- load_current_psa_cache()
draws <- load_psa_params_cache(required = TRUE, seed = analysis_seed, n_sim = psa$n_sim)
population <- l_params_base$prediction_population
ordering <- read_extrapolation_ordering(pfs_os_violation_cache_path(),
  sampling_models, population, draws, l_params_base)
input_paths <- c(sampling_cache_path(), psa_obj_path(), psa_params_path(),
                 pfs_os_violation_cache_path())
hash_before <- tools::md5sum(input_paths)
life_path <- here::here("data/external/ssb_07902_2025.csv")
life <- read.csv(life_path)
times <- seq(0, time_horizon)
individual_ref <- population_reference_survival(population$Age,
  as.character(population$sex), life, times * cl)
reference <- rowMeans(individual_ref)
reconstructed <- reconstruct_extrapolation_curves(sampling_models, psa, draws,
  l_params_base, ordering)
labels <- c(control = "SoC", crp = "CRP", tmb_braf = "TMB/BRAF")
det <- model_fun(l_params_base, time_horizon = time_horizon, cl = cl)
det_q <- setNames(det$Effect, det$Strategy)
det_curve <- function(s, ep) {
  p <- if (ep == "os") l_params_base$p_os else l_params_base$p_pfs
  suffix <- toupper(ep)
  if (s == "control") return(p[[paste0(s, "_", suffix)]])
  prev <- l_params_base[[paste0("p_", s)]]
  prev * p[[paste0(s, "_pos_", suffix)]] +
    (1 - prev) * p[[paste0(s, "_neg_", suffix)]]
}
fmt <- function(x, digits = 4) formatC(x, format = "f", digits = digits)
pct <- function(x) paste0(fmt(100 * x, 2), "%")
tab <- function(x, digits = 3) knitr::kable(x, digits = digits,
  format = report_table_format(), row.names = FALSE) |> tbl_style(latex_options = "HOLD_position")
ribbon_rows <- spaghetti_rows <- metric_rows <- tail_rows <- list()
thinned <- unique(round(seq(1, psa$n_sim, length.out = 50)))
for (s in psa$strategies) {
  for (ep in c("os", "pfs")) {
    mat <- reconstructed$curves[[s]][[ep]]
    qs <- apply(mat, 2, quantile, probs = c(.025, .10, .25, .75, .90, .975))
    ribbon_rows[[paste(s, ep)]] <- data.frame(strategy = labels[[s]], endpoint = toupper(ep),
      year = times * cl, low95 = qs[1, ], low80 = qs[2, ], low50 = qs[3, ],
      high50 = qs[4, ], high80 = qs[5, ], high95 = qs[6, ],
      mean = colMeans(mat), deterministic = det_curve(s, ep), reference = reference)
    spaghetti_rows[[paste(s, ep)]] <- data.frame(strategy = labels[[s]], endpoint = toupper(ep),
      year = rep(times * cl, each = length(thinned)),
      draw = rep(thinned, length(times)), survival = as.vector(mat[thinned, ]))
    rmst <- apply(mat, 1, restricted_mean_survival, cycle_length = cl)
    metric_rows[[paste(s, ep)]] <- data.frame(strategy = labels[[s]], endpoint = toupper(ep),
      sim = psa$sim, model_idx = psa$model_idx, rmst = rmst)
    ts <- extrapolation_tail_summary(rmst, psa$effectiveness[, s])
    ts$strategy <- labels[[s]]; ts$endpoint <- toupper(ep)
    ts$deterministic <- det_q[[s]]
    tail_rows[[paste(s, ep)]] <- ts
  }
}
ribbons <- bind_rows(ribbon_rows)
spaghetti <- bind_rows(spaghetti_rows)
metrics <- bind_rows(metric_rows)
tails <- bind_rows(tail_rows)
exceedance <- bind_rows(lapply(psa$strategies, function(s) {
  mat <- reconstructed$curves[[s]]$os
  difference <- sweep(mat, 2, reference, "-")
  exceeds <- difference > 1e-10
  any_week <- which(colSums(exceeds) > 0)
  excess_rmst <- apply(pmax(difference, 0), 1, restricted_mean_survival, cycle_length = cl)
  data.frame(Strategy = labels[[s]], Any = sum(rowSums(exceeds) > 0),
    Week520 = sum(exceeds[, ncol(mat)]), Max520 = max(mat[, ncol(mat)]),
    AfterYear1 = sum(rowSums(exceeds[, times > 52, drop = FALSE]) > 0),
    FirstWeek = if (length(any_week)) min(times[any_week]) else NA_real_,
    LastWeek = if (length(any_week)) max(times[any_week]) else NA_real_,
    MaxExcess = max(pmax(difference, 0)), MeanExcessArea = mean(excess_rmst),
    DetExcess = any(det_curve(s, "os") - reference > 1e-10))
}))
alignment <- data.frame(Strategy = unname(labels[psa$strategies]),
  Deterministic = det_q[psa$strategies], PSA = colMeans(psa$effectiveness))
alignment$Gap <- alignment$PSA - alignment$Deterministic
alignment$MCSE <- apply(psa$effectiveness, 2, sd) / sqrt(psa$n_sim)
relation <- bind_rows(lapply(psa$strategies, function(s) {
  rmst <- metrics$rmst[metrics$strategy == labels[[s]] & metrics$endpoint == "OS"]
  cross <- reconstructed$crossing[, s]
  top <- rep(FALSE, length(rmst)); top[order(rmst, decreasing = TRUE)[seq_len(ceiling(.1 * length(rmst)))]] <- TRUE
  ft <- fisher.test(table(factor(top, levels = c(FALSE, TRUE)), factor(cross, levels = c(FALSE, TRUE))))
  data.frame(Strategy = labels[[s]], Cross = sum(cross), TopCross = sum(cross & top),
    TopN = sum(top), OtherCross = sum(cross & !top), OtherN = sum(!top),
    MedianCross = median(rmst[cross]), MedianOther = median(rmst[!cross]),
    OR = unname(ft$estimate), Lower = ft$conf.int[1], Upper = ft$conf.int[2], P = ft$p.value)
}))
stopifnot(identical(hash_before, tools::md5sum(input_paths)))
```

# Purpose and scope

This report investigates whether optimistic survival tails dominate the PSA mean
QALYs (issue #179). It uses all `r psa$n_sim` retained PSA rows and the existing joint
OS/PFS coefficient draws. SoC denotes standard of care; CRP denotes guidance by
week-4 CRP, before the first nivolumab dose; TMB/BRAF denotes baseline NGS guidance.
All strategies target the same `r nrow(population)` complete-case patients.

The sampling cache and paired PSA files pass their current input-fingerprint and
pair validations. The ordering cache passes its full fingerprint check, including
population, PSA parameters, utilities and horizon. No cache is generated or
rewritten. The reconstruction uses the saved `model_idx`, joint population weights
and utilities of each PSA row, and reproduces all cached strategy QALYs to a maximum
absolute error of `r format(reconstructed$max_qaly_error, scientific = TRUE)`.
The PFS curves shown are **after the subgroup-level OS clamp**, as used economically;
OS is unchanged. The ordering analysis uses the **raw, unclamped** subgroup curves.

```{r alignment}
tab(alignment, 5)
```

MCSE is the Monte Carlo standard error of the PSA mean. A nonlinear mean under
parameter uncertainty need not equal the deterministic result. The existing
five-MCSE alignment diagnostic remains a known failure; this report does not
recenter draws, relax that criterion, or replace reported economic results.

# Norwegian population reference

The public [Statistics Norway life table 07902](https://www.ssb.no/en/statbank/table/07902)
provides 2025 sex-specific annual death probabilities (updated 12 March 2026;
retrieved 23 September 2026 from the [official Deaths table](https://www.ssb.no/en/befolkning/fodte-og-dode/statistikk/dode)).
The versioned extract is `data/external/ssb_07902_2025.csv` (MD5
`r unname(tools::md5sum(life_path))`). Conditional survival from each patient's
baseline age uses constant hazards within each attained-age year,
$h_x=-\log(1-q_x)$, including fractional years. Trial sex 0 maps to female and 1 to
male. Individual reference curves are averaged equally over the observed cohort
(`r sum(as.character(population$sex) == "0")` female,
`r sum(as.character(population$sex) == "1")` male; mean age
`r fmt(mean(population$Age), 1)` years). The same fixed cohort reference is used for
every strategy and draw; PSA population-weight uncertainty remains in the cancer
curves. This is a 2025 **period** reference, with no future mortality improvement,
not a historical trial-year life table or an individual cancer-survival prediction.

The matched population survival at week 520 is `r pct(tail(reference, 1))`.
Exceedance means strategy-average OS exceeds that fixed reference by more than
$10^{-10}$ at any weekly point (or at week 520 specifically). The shared value of
one at week zero is not an exceedance. This aggregate check is a permissive
plausibility screen: it cannot establish plausible individual hazards, validate a
cancer-specific tail, or exclude implausibility below population survival.

```{r exceedance}
tab(data.frame(Strategy = exceedance$Strategy,
  `Any week: n (%)` = paste0(exceedance$Any, " (", pct(exceedance$Any / psa$n_sim), ")"),
  `Week 520: n (%)` = paste0(exceedance$Week520, " (", pct(exceedance$Week520 / psa$n_sim), ")"),
  `Maximum OS at 520` = pct(exceedance$Max520), check.names = FALSE))
```

```{r exceedance-timing}
tab(data.frame(Strategy = exceedance$Strategy,
  `First week` = exceedance$FirstWeek, `Last week` = exceedance$LastWeek,
  `After year 1: n` = exceedance$AfterYear1,
  `Max excess (pp)` = 100 * exceedance$MaxExcess, check.names = FALSE), 4)
```

The timing table pools all draws: it gives the earliest and latest weekly
exceedance, and the largest vertical excess in percentage points (pp).
The mean positive excess area is
`r paste(fmt(exceedance$MeanExcessArea, 7), collapse = ", ")` life-years for SoC,
CRP and TMB/BRAF, respectively. The deterministic OS curves also exceed the
reference for `r paste(exceedance$Strategy[exceedance$DetExcess], collapse = ", ")`.
Thus any-week counts must be interpreted alongside timing and magnitude, rather
than equated with the frequency of implausibly long tails. Gamma distributions
with shape greater than one start with zero hazard, whereas the population
reference has a positive hazard from time zero. A brief initial excess can arise
from this shape property; it is still a departure from the population reference.

# Sampled survival curves

Ribbons are pointwise central 95%, 80% and 50% intervals over **all 5,000** PSA
rows, drawn from light to dark. Fifty evenly spaced row indices supply the thin
spaghetti lines; they are not selected for their outcomes. Solid blue is the PSA
mean, dashed black the deterministic curve, and dotted red the Norwegian reference
(OS only). The lower plot makes the mean-minus-deterministic gap visible.

```{r survival-curves, fig.cap="All-strategy survival uncertainty and the matched Norwegian reference.", fig.height=8}
ggplot(ribbons, aes(year)) +
  geom_ribbon(aes(ymin = low95, ymax = high95), fill = "#bdd7e7") +
  geom_ribbon(aes(ymin = low80, ymax = high80), fill = "#9ecae1") +
  geom_ribbon(aes(ymin = low50, ymax = high50), fill = "#6baed6") +
  geom_line(data = spaghetti, aes(y = survival, group = draw), alpha = .10, linewidth = .2) +
  geom_line(aes(y = mean, colour = "PSA mean", linetype = "PSA mean"), linewidth = .7) +
  geom_line(aes(y = deterministic, colour = "Deterministic", linetype = "Deterministic"), linewidth = .7) +
  geom_line(data = filter(ribbons, endpoint == "OS"),
    aes(y = reference, colour = "Population", linetype = "Population"), linewidth = .7) +
  facet_grid(strategy ~ endpoint) +
  scale_colour_manual(values = c(Deterministic = "black", Population = "#b2182b", `PSA mean` = "#08519c")) +
  scale_linetype_manual(values = c(Deterministic = "dashed", Population = "dotted", `PSA mean` = "solid")) +
  labs(x = "Years from randomization", y = "Survival probability", colour = NULL, linetype = NULL)
```

```{r curve-gap, fig.cap="Pointwise PSA mean minus deterministic survival.", fig.height=4}
ggplot(ribbons, aes(year, mean - deterministic, colour = strategy)) +
  geom_hline(yintercept = 0, colour = "grey60") + geom_line() + facet_wrap(~ endpoint) +
  labs(x = "Years", y = "Survival difference", colour = "Strategy")
```

# Restricted means and tail contributions

Restricted mean survival time (RMST) is the undiscounted trapezoidal area from
week 0 to 520, in years, calculated with `restricted_mean_survival()`.
PFS RMST uses clamped curves. QALYs retain sampled utilities and 4% effect
discounting. Ranking is performed **separately within each strategy and endpoint**;
ties use PSA row order. Thus OS-ranked and PFS-ranked trims can remove different
draws. The top 1%, 5% and 10% contain 50, 250 and 500 rows, respectively.

```{r rmst-distribution, fig.cap="Distributions of ten-year restricted mean OS and PFS.", fig.height=6}
ggplot(metrics, aes(rmst)) + geom_histogram(bins = 45, fill = "#3182bd", colour = "white") +
  facet_grid(strategy ~ endpoint, scales = "free_x") +
  labs(x = "Restricted mean survival (years)", y = "PSA rows")
```

```{r rmst-summary}
summary_rmst <- metrics |> group_by(strategy, endpoint) |>
  summarise(Mean = mean(rmst), Median = median(rmst), P95 = quantile(rmst, .95),
    P99 = quantile(rmst, .99), Maximum = max(rmst), .groups = "drop")
tab(summary_rmst)
```

Contribution is the sum of QALYs in the selected upper tail divided by the sum
over all rows, equivalently its contribution to the untrimmed PSA mean. Trimmed
means renormalize over retained rows. These are **selection diagnostics only**:
trimming favorable outcomes necessarily lowers the mean even for a valid
distribution. It is not evidence by itself that any draw should be rejected.

```{r tail-contributions, results='asis'}
for (ep in c("OS", "PFS")) {
  cat("\n\n## Ranked by ", ep, " RMST\n\n", sep = "")
  tt <- filter(tails, endpoint == ep)
  print(tab(data.frame(Strategy = tt$strategy, Top = pct(tt$fraction),
    `RMST cutoff` = tt$cutoff, `QALY contribution` = pct(tt$contribution), check.names = FALSE)))
  cat("\n\n")
  print(tab(data.frame(Strategy = tt$strategy, Trim = pct(tt$fraction),
    `PSA mean` = tt$mean, `Trimmed mean` = tt$trimmed,
    `Trimmed - det.` = tt$trimmed - tt$deterministic, check.names = FALSE), 5))
  cat("\n\n")
}
```

# Relationship to PFS-above-OS violations

Each reconstructed row joins the ordering cache on **model_idx plus simulation
ID and curve**. The additional keys preserve the population and utility draws
if a replacement coefficient vector is reused. There are
`r sum(duplicated(psa$model_idx))` repeated model indices in this PSA. A guided
strategy is classified as crossing if either contributing subgroup crosses;
SoC uses its own curve. All reconstructed raw flags agree with the saved flags.
The long-tail indicator here is the **top 10% by strategy OS RMST**. Counts below
compare its crossing rate with the other 90%; medians describe OS RMST in crossing
and non-crossing draws.

```{r ordering-counts}
tab(data.frame(Strategy = relation$Strategy, Crossings = relation$Cross,
  `Top 10%: n (%)` = paste0(relation$TopCross, " (", pct(relation$TopCross / relation$TopN), ")"),
  `Other 90%: n (%)` = paste0(relation$OtherCross, " (", pct(relation$OtherCross / relation$OtherN), ")"),
  check.names = FALSE))
```

```{r ordering-association}
tab(data.frame(Strategy = relation$Strategy, `RMST: crossing` = relation$MedianCross,
  `RMST: other` = relation$MedianOther, `Odds ratio (95% CI)` =
    paste0(fmt(relation$OR, 2), " (", fmt(relation$Lower, 2), ", ", fmt(relation$Upper, 2), ")"),
  `Fisher p` = format.pval(relation$P, digits = 2, eps = .001), check.names = FALSE))
```

Fisher's exact test compares crossing odds in the upper decile versus the rest.
It describes association within simulated draws, not clinical hypothesis testing;
the three strategies share coefficient draws and these comparisons are dependent.

# Verdict

```{r verdict, results='asis'}
top1 <- filter(tails, endpoint == "OS", fraction == .01)
top10 <- filter(tails, endpoint == "OS", fraction == .10)
cat(sprintf(paste0(
  "The diagnostics support a broadly distributed nonlinear averaging effect rather than a mean dominated by a tiny, demonstrably implausible survival tail. ",
  "Across SoC, CRP and TMB/BRAF, the highest 1%% of OS-RMST draws contribute %s, %s and %s of total QALYs; ",
  "removing them changes the means by %.5f, %.5f and %.5f QALYs, leaving gaps of %.5f, %.5f and %.5f above the deterministic results. ",
  "The top 10%% contribute %s, %s and %s, showing meaningful upper-tail sensitivity without dominance. ",
  "%d of %d strategy-draw curves exceed matched population survival at any modeled week (%d at week 520). ",
  "Crossing rates in the top OS-RMST decile are %s, %s and %s versus %s, %s and %s in the remaining draws, distinguishing ordering violations from optimistic OS tails. ",
  "The exceedances occur between weeks %.0f and %.0f, with a maximum vertical excess of %.4f percentage points; ",
  "they therefore require interpretation as an early-curve limitation, not evidence that optimistic ten-year tails dominate the mean. ",
  "The evidence favors the broad-spread explanation for the mean shift, but does not establish that every extrapolation is plausible: ",
  "a general-population comparator is too permissive to establish cancer-specific extrapolation validity. ",
  "The unbounded extrapolation remains a stated limitation; no draw is excluded, no mean is corrected, and a population-mortality hazard floor remains outside this paper's scope.\n"),
  pct(top1$contribution[1]), pct(top1$contribution[2]), pct(top1$contribution[3]),
  top1$shift[1], top1$shift[2], top1$shift[3],
  (top1$trimmed - top1$deterministic)[1], (top1$trimmed - top1$deterministic)[2], (top1$trimmed - top1$deterministic)[3],
  pct(top10$contribution[1]), pct(top10$contribution[2]), pct(top10$contribution[3]),
  sum(exceedance$Any), psa$n_sim * length(psa$strategies), sum(exceedance$Week520),
  pct(relation$TopCross[1] / relation$TopN[1]), pct(relation$TopCross[2] / relation$TopN[2]), pct(relation$TopCross[3] / relation$TopN[3]),
  pct(relation$OtherCross[1] / relation$OtherN[1]), pct(relation$OtherCross[2] / relation$OtherN[2]), pct(relation$OtherCross[3] / relation$OtherN[3]),
  min(exceedance$FirstWeek, na.rm = TRUE), max(exceedance$LastWeek, na.rm = TRUE),
  100 * max(exceedance$MaxExcess)))
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
