---
title: "Survival Extrapolation Validation"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 2
    number-sections: true
    fig-width: 8
    fig-height: 5.5
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# ===============================================================================
# Survival extrapolation validation (issue #162, AdViSHE D4)
#
# 1. Dependent validation: model-predicted versus Kaplan-Meier OS and PFS at
#    1, 2, 3 and 5 years and the median, for the control arm and each economic
#    biomarker subgroup. The model is predicted for exactly the patients behind
#    each Kaplan-Meier curve, on their own arm (issue #157 convention).
# 2. Independent validation: the economic standard-of-care curves against
#    published first-line mCRC survival (data/external/survival_benchmarks.csv),
#    with the tolerance fixed in advance in R/survival_validation.R.
#
# Model intervals are 95% percentiles over joint coefficient draws from the
# sampling cache (script 06, read-only), with the patient population held fixed.
# ===============================================================================
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05", "06"),
  funs = c("prediction_functions", "report_format", "pfs_os_violation_diagnostics",
           "survival_validation"),
  packages = c("here", "knitr", "kableExtra", "ggplot2", "dplyr", "tidyr",
               "scales", "survival", "flexsurv"),
  set_theme = FALSE,
  quiet_sources = TRUE
)

theme_set(theme_minimal(base_size = 11) +
  theme(legend.position = "bottom", panel.grid.minor = element_blank(),
        plot.caption = element_text(size = 8.5, colour = "grey30", hjust = 0)))

years <- c(1, 2, 3, 5)
n_draws <- 1000
times <- 0:time_horizon
ctrl_rx <- levels(data_complete$Rx)[1]
exp_rx <- levels(data_complete$Rx)[2]
fit_os <- models$best_fit$os
fit_pfs <- models$best_fit$pfs
dist_os <- models$best_fit$os_distribution
dist_pfs <- models$best_fit$pfs_distribution

component <- get_joint_sampling_models(sampling_models)
set.seed(analysis_seed)
draw_idx <- sort(sample(seq_len(component$n_samples), min(n_draws, component$n_samples)))

# ---- Groups: the patients behind each Kaplan-Meier curve -----------------------
# Same subsets as subgroup_data() in survival_model_specification.qmd and
# biomarker_sets() in figure_pfs_os_curves.qmd: control arm; biomarker-positive
# patients on the experimental arm; biomarker-negative patients on the control arm.
group_meta <- data.frame(
  group = c("control", "crp_pos", "crp_neg", "tmb_braf_pos", "tmb_braf_neg"),
  label = c("SoC", "CRP+", "CRP-", "TMB/BRAF+", "TMB/BRAF-"),
  stringsAsFactors = FALSE
)
group_data <- function(group) {
  d <- data_complete
  if (group == "control") return(d[d$Rx == ctrl_rx, ])
  bm <- sub("_(pos|neg)$", "", group)
  status <- as.numeric(as.character(d[[bm]]))
  if (grepl("_pos$", group)) d[status == 1 & d$Rx == exp_rx, ]
  else d[status == 0 & d$Rx == ctrl_rx, ]
}

endpoint_cols <- list(OS = c(time = "OSwk", event = "Death"),
                      PFS = c(time = "PFSwk", event = "Progression"))
endpoint_fit <- function(ep) if (ep == "OS") fit_os else fit_pfs

predict_group <- function(fit, d) {
  curve <- predict_pop_avg(fit, d, times)
  if (is.null(curve) || length(curve) != length(times)) {
    stop("Population-averaged prediction failed for ", nrow(d), " patients")
  }
  curve
}

# ---- Economic standard-of-care curves and closed-form check --------------------
soc_data <- data_complete
soc_data$Rx <- factor(ctrl_rx, levels = levels(data_complete$Rx))
soc_curve <- list(OS = l_params_base$p_os$control_OS,
                  PFS = l_params_base$p_pfs$control_PFS)
for (ep in c("OS", "PFS")) {
  recomputed <- predict_group(endpoint_fit(ep), soc_data)
  if (max(abs(recomputed - soc_curve[[ep]])) > 1e-8) {
    stop("The economic SoC ", ep, " curve is not the joint model averaged over ",
         "the complete-case cohort with Rx = control.")
  }
  if (identical(endpoint_fit(ep)$dlist$name, "gamma")) {
    direct <- direct_gamma_pop_avg(endpoint_fit(ep), coef(endpoint_fit(ep)), soc_data, times)
    if (max(abs(direct - recomputed)) > 1e-8) {
      stop("Closed-form gamma curve differs from predict() for ", ep)
    }
  }
}
```

```{r dependent, include=FALSE}
fmt_pct <- function(x) ifelse(is.finite(x), sprintf("%.1f%%", 100 * x), "--")
fmt_ci_pct <- function(lo, hi) {
  ifelse(is.finite(lo) & is.finite(hi),
         sprintf("%.1f-%.1f%%", 100 * lo, 100 * hi), "--")
}
fmt_mo <- function(x) ifelse(is.finite(x), sprintf("%.1f", x), "NR")
fmt_ci_mo <- function(lo, hi) sprintf("%s-%s", fmt_mo(lo), fmt_mo(hi))

dependent_rows <- list()
for (ep in c("OS", "PFS")) {
  for (g in group_meta$group) {
    d <- group_data(g)
    t_col <- endpoint_cols[[ep]][["time"]]
    e_col <- endpoint_cols[[ep]][["event"]]
    km <- km_landmarks(d[[t_col]], d[[e_col]], years)
    km_med <- km_median_months(d[[t_col]], d[[e_col]])
    curve <- predict_group(endpoint_fit(ep), d)
    iv <- draw_landmark_intervals(
      draw_curves(component, tolower(ep), d, draw_idx, times), years)
    model_land <- curve_at_years(curve, years)
    model_med <- curve_median_months(curve)
    dependent_rows[[paste(ep, g)]] <- data.frame(
      endpoint = ep, group = g,
      label = sprintf("%s (n = %d)", group_meta$label[group_meta$group == g], nrow(d)),
      landmark = c(paste(years, ifelse(years == 1, "year", "years")), "Median (months)"),
      measure = c(rep("survival", length(years)), "median_months"),
      km = c(km$surv, km_med[["median"]]),
      km_lower = c(km$lower, km_med[["lower"]]),
      km_upper = c(km$upper, km_med[["upper"]]),
      n_risk = c(km$n_risk, NA),
      km_status = c(km$status, ifelse(is.finite(km_med[["median"]]), "Estimated",
                                      "Not reached")),
      model = c(model_land, model_med),
      model_lower = iv$lower, model_upper = iv$upper,
      last_follow_up_yr = max(d[[t_col]]) / 52,
      stringsAsFactors = FALSE
    )
  }
}
dependent <- bind_rows(dependent_rows)
dependent$in_km_ci <- ifelse(
  is.finite(dependent$km_lower) & is.finite(dependent$km_upper) & is.finite(dependent$model),
  ifelse(dependent$model >= dependent$km_lower & dependent$model <= dependent$km_upper,
         "Yes", "No"),
  "--")

dependent_table <- function(ep) {
  x <- dependent[dependent$endpoint == ep, ]
  is_med <- x$measure == "median_months"
  data.frame(
    Group = ifelse(x$landmark == x$landmark[1], x$label, ""),
    Landmark = x$landmark,
    `Kaplan-Meier` = ifelse(is_med, fmt_mo(x$km),
                            ifelse(grepl("^NE", x$km_status), "NE", fmt_pct(x$km))),
    `KM 95% CI` = ifelse(is_med, fmt_ci_mo(x$km_lower, x$km_upper),
                         fmt_ci_pct(x$km_lower, x$km_upper)),
    `At risk` = ifelse(is.na(x$n_risk), "", as.character(x$n_risk)),
    Model = ifelse(is_med, fmt_mo(x$model), fmt_pct(x$model)),
    `Model 95% interval` = ifelse(is_med, fmt_ci_mo(x$model_lower, x$model_upper),
                                  fmt_ci_pct(x$model_lower, x$model_upper)),
    `In KM CI` = x$in_km_ci,
    check.names = FALSE, stringsAsFactors = FALSE
  )
}

dep_eval <- dependent[dependent$in_km_ci != "--", ]
dep_out <- dep_eval[dep_eval$in_km_ci == "No", ]
n_ne <- sum(grepl("^NE", dependent$km_status))
n_few <- sum(grepl("^Fewer", dependent$km_status))
max_fu_yr <- max(c(data_complete$OSwk, data_complete$PFSwk)) / 52
```

```{r independent, include=FALSE}
benchmarks <- read_survival_benchmarks()
bench_path <- here::here(SURVIVAL_BENCHMARK_PATH)
bench_md5 <- unname(tools::md5sum(bench_path))
bench_commit <- tryCatch(
  system2("git", c("-C", shQuote(here::here()), "log", "--diff-filter=A",
                   "--format=%h %cs", "--", SURVIVAL_BENCHMARK_PATH), stdout = TRUE),
  error = function(e) character(0), warning = function(w) character(0))
bench_commit <- if (length(bench_commit) > 0) tail(bench_commit, 1) else "not available"

ctrl_data <- group_data("control")
model_curves <- list(
  soc = soc_curve,
  ctrl = list(OS = predict_group(fit_os, ctrl_data), PFS = predict_group(fit_pfs, ctrl_data))
)
model_draws <- list(
  soc = list(OS = draw_curves(component, "os", soc_data, draw_idx, times),
             PFS = draw_curves(component, "pfs", soc_data, draw_idx, times)),
  ctrl = list(OS = draw_curves(component, "os", ctrl_data, draw_idx, times),
              PFS = draw_curves(component, "pfs", ctrl_data, draw_idx, times))
)

model_value <- function(curve, row) {
  if (row$measure == "median_months") curve_median_months(curve)
  else curve_at_years(curve, row$time_years)
}
draw_interval <- function(mat, row) {
  v <- if (row$measure == "median_months") apply(mat, 1, curve_median_months)
       else apply(mat, 1, curve_at_years, years = row$time_years)
  stats::quantile(v, c(0.025, 0.975), na.rm = TRUE, names = FALSE)
}

comparison <- bind_rows(lapply(seq_len(nrow(benchmarks)), function(i) {
  row <- benchmarks[i, ]
  out <- row[, c("id", "source", "endpoint", "measure", "time_years", "estimate",
                 "lower", "upper", "role")]
  for (m in c("soc", "ctrl")) {
    val <- model_value(model_curves[[m]][[row$endpoint]], row)
    iv <- draw_interval(model_draws[[m]][[row$endpoint]], row)
    out[[paste0(m, "_value")]] <- val
    out[[paste0(m, "_lower")]] <- iv[1]
    out[[paste0(m, "_upper")]] <- iv[2]
    out[[paste0(m, "_verdict")]] <- evaluate_benchmark(val, row)
  }
  out
}))
comparison$soc_pass <- benchmark_passed(comparison$soc_verdict)
comparison$ctrl_pass <- benchmark_passed(comparison$ctrl_verdict)

short_source <- function(s) sub(" \\(.*\\)$", "", s)
# Short cohort tags so that rows from the same source can be told apart. Every
# benchmark id must match exactly one pattern, so a new row forces a new tag.
cohort_tags <- c(
  "^nordic7_a_" = "arm A",
  "^aasebo_mss_comb_" = "MSS, combination chemotherapy",
  "^aasebo_mss_chemo_" = "MSS, any chemotherapy",
  "^cnorway_sync_pall_" = "synchronous, palliative chemotherapy",
  "^cnorway_meta_pall_" = "metachronous, palliative chemotherapy",
  "^sorbye_no_all_" = "all ages",
  "^sorbye_no_lt60_" = "age <60"
)
cohort_tag <- function(id) {
  vapply(id, function(x) {
    hit <- vapply(names(cohort_tags), grepl, logical(1), x = x)
    if (sum(hit) != 1) stop("Benchmark id ", x, " needs exactly one cohort tag")
    cohort_tags[[which(hit)]]
  }, "", USE.NAMES = FALSE)
}
source_label <- function(r) paste0(short_source(r$source), ", ", cohort_tag(r$id))
measure_label <- function(r) {
  ifelse(r$measure == "median_months", paste(r$endpoint, "median (months)"),
         sprintf("%s at %s years", r$endpoint, formatC(r$time_years, format = "fg")))
}
fmt_value <- function(x, measure) {
  ifelse(measure == "median_months", fmt_mo(x), fmt_pct(x))
}
fmt_bench <- function(r) {
  est <- fmt_value(r$estimate, r$measure)
  ci <- ifelse(is.finite(r$lower) & is.finite(r$upper),
               ifelse(r$measure == "median_months",
                      sprintf(" (%s-%s)", fmt_mo(r$lower), fmt_mo(r$upper)),
                      sprintf(" (%s)", fmt_ci_pct(r$lower, r$upper))), "")
  paste0(est, ci)
}
fmt_model <- function(r, m) {
  v <- r[[paste0(m, "_value")]]; lo <- r[[paste0(m, "_lower")]]; hi <- r[[paste0(m, "_upper")]]
  ifelse(r$measure == "median_months",
         sprintf("%s (%s)", fmt_mo(v), fmt_ci_mo(lo, hi)),
         sprintf("%s (%s)", fmt_pct(v), fmt_ci_pct(lo, hi)))
}

n_soc_eval <- sum(!is.na(comparison$soc_pass))
n_soc_pass <- sum(comparison$soc_pass, na.rm = TRUE)
n_soc_fail <- sum(!comparison$soc_pass, na.rm = TRUE)
n_ctrl_pass <- sum(comparison$ctrl_pass, na.rm = TRUE)
n_ctrl_eval <- sum(!is.na(comparison$ctrl_pass))
fails <- comparison[!is.na(comparison$soc_pass) & !comparison$soc_pass, ]
comp_rows <- comparison[comparison$role == "comparable", ]
lb_rows <- comparison[comparison$role == "lower_bound", ]
tail_rows <- comparison[comparison$measure == "survival" & comparison$time_years >= 5, ]
tail_fail <- tail_rows[!tail_rows$soc_pass, ]

# Observed control-arm OS at its last follow-up time, for the tail discussion
ctrl_os_fit <- survfit(Surv(OSwk, Death) ~ 1, data = ctrl_data)
ctrl_last_wk <- max(ctrl_data$OSwk)
ctrl_km_last <- tail(ctrl_os_fit$surv, 1)
ctrl_last_event_wk <- max(ctrl_data$OSwk[ctrl_data$Death == 1])
soc_at_last <- curve_at_years(soc_curve$OS, ctrl_last_wk / 52)
ctrl_model_at_last <- curve_at_years(model_curves$ctrl$OS, ctrl_last_wk / 52)
ctrl_km_pfs_med <- km_median_months(ctrl_data$PFSwk, ctrl_data$Progression)
soc_pfs_med <- curve_median_months(soc_curve$PFS)
pfs_med_in_km <- is.finite(soc_pfs_med) &&
  soc_pfs_med >= ctrl_km_pfs_med[["lower"]] && soc_pfs_med <= ctrl_km_pfs_med[["upper"]]
pfs_fails <- fails[fails$endpoint == "PFS", ]
tail_text <- if (nrow(tail_rows) == 0) {
  "No benchmark reaches 5 years."
} else if (nrow(tail_fail) == 0) {
  sprintf("The model meets every benchmark at 5 years or later (%d checks).", nrow(tail_rows))
} else {
  sprintf(paste(
    "%d of the %d checks at 5 years or later fail (%s), all with model survival",
    "below a lower bound. The modelled standard-of-care OS is %s at 5 years and %s",
    "at 6.5 years. The extrapolated tail is therefore pessimistic relative to the",
    "external evidence, consistent with the fitted curve falling below the trial's",
    "own late Kaplan-Meier plateau (Section 2)."),
    nrow(tail_fail), nrow(tail_rows),
    paste(sprintf("%s, %s", source_label(tail_fail), measure_label(tail_fail)),
          collapse = "; "),
    fmt_pct(curve_at_years(soc_curve$OS, 5)), fmt_pct(curve_at_years(soc_curve$OS, 6.5)))
}
```

# Purpose and classification

This report answers validateHE finding TR-COMP-022 (AdViSHE item D4: model outcomes compared with empirical data) and GitHub issue #162. The economic model extrapolates the `r dist_os` (OS) and `r dist_pfs` (PFS) joint regression models, fitted to `r nrow(data_complete)` complete-case patients with at most `r sprintf("%.1f", max_fu_yr)` years of follow-up, to a `r round(time_horizon / 52)`-year horizon. Before this report, the fits had been compared only visually with the trial's own Kaplan-Meier curves (`para_models.qmd`, `survival_model_specification.qmd`).

The report contains two comparisons, classified as AdViSHE asks:

- **Dependent validation (Section 2).** Model versus Kaplan-Meier OS and PFS at 1, 2, 3 and 5 years and at the median, in the METIMMOX patients the curves were fitted to. Agreement here shows that the fit reproduces its own data. It says nothing about the extrapolated tail.
- **Independent validation (Section 3).** The economic standard-of-care curves against published survival of first-line mCRC patients outside METIMMOX. The benchmarks and the tolerance were committed (`r bench_commit`) before any comparison was computed.

The general-population plausibility check of the PSA draws (Norwegian life table) is in `psa_extrapolation_plausibility.qmd` (issue #179) and is not repeated here.

# Dependent validation: model versus trial Kaplan-Meier

Each Kaplan-Meier curve is compared with the model predicted for **exactly the same patients**, each with their own age, sex, biomarker values and actual arm, then averaged (the issue #157 convention). The groups are those that enter the economic model:

- control-arm patients (SoC);
- biomarker-positive patients on FLOX + nivolumab;
- biomarker-negative patients on FLOX.

Kaplan-Meier 95% confidence intervals use the log-log transformation. The model interval is the 2.5th-97.5th percentile over `r length(draw_idx)` joint coefficient draws from the PSA sampling cache, with the patients held fixed.

A Kaplan-Meier landmark after a group's last observed time is not estimable ("NE"). Where every patient had an event before the landmark, the estimate is 0 without a confidence interval. `r n_ne` of the `r nrow(dependent[dependent$measure == "survival", ])` landmark cells are NE, including every 5-year Kaplan-Meier cell. `r n_few` estimable cells rest on fewer than `r KM_FEW_AT_RISK` patients at risk.

```{r table-dep-os}
knitr::kable(dependent_table("OS"), format = report_table_format(), booktabs = TRUE,
             row.names = FALSE, align = "llrrrrrc",
             caption = "Overall survival: Kaplan-Meier versus model predicted for the same patients") |>
  tbl_style(latex_options = "HOLD_position", font_size = 9) |>
  tbl_footnote(general = paste(
    "NE: not estimable (after the group's last follow-up). NR: not reached.",
    "At risk: patients at risk at the landmark. In KM CI: model point estimate",
    "inside the Kaplan-Meier 95% CI; -- where the Kaplan-Meier CI is unavailable",
    "(not estimable, or no event yet so the estimate is 100% with a degenerate interval).",
    "Groups: SoC = control arm; + = biomarker-positive on FLOX + nivolumab;",
    "- = biomarker-negative on FLOX."), threeparttable = TRUE)
```

```{r table-dep-pfs}
knitr::kable(dependent_table("PFS"), format = report_table_format(), booktabs = TRUE,
             row.names = FALSE, align = "llrrrrrc",
             caption = "Progression-free survival: Kaplan-Meier versus model predicted for the same patients") |>
  tbl_style(latex_options = "HOLD_position", font_size = 9) |>
  tbl_footnote(general = paste(
    "As for the OS table. A Kaplan-Meier estimate of 0.0% without a CI means",
    "every patient in the group had progressed or died before the landmark."),
    threeparttable = TRUE)
```

Of the `r nrow(dep_eval)` cells with a Kaplan-Meier confidence interval, the model point estimate lies inside the interval in `r sum(dep_eval$in_km_ci == "Yes")`.
`r if (nrow(dep_out) > 0) paste0("It lies outside in ", nrow(dep_out), ": ", paste(sprintf("%s %s, %s (Kaplan-Meier %s, model %s)", dep_out$endpoint, sub(" \\(n = .*", "", dep_out$label), tolower(dep_out$landmark), ifelse(dep_out$measure == "median_months", paste(fmt_mo(dep_out$km), "months"), fmt_pct(dep_out$km)), ifelse(dep_out$measure == "median_months", paste(fmt_mo(dep_out$model), "months"), fmt_pct(dep_out$model))), collapse = "; "), ".") else "There is no cell where it lies outside."`
`r no_ev <- dependent[dependent$km_status == "No events before landmark", ]; if (nrow(no_ev) > 0) paste0("Cells without any event before the landmark have no informative interval and are not counted: ", paste(sprintf("%s %s, %s (model %s)", no_ev$endpoint, sub(" \\(n = .*", "", no_ev$label), no_ev$landmark, fmt_pct(no_ev$model)), collapse = "; "), ".") else ""`
With groups of `r min(sapply(group_meta$group, function(g) nrow(group_data(g))))` to `r max(sapply(group_meta$group, function(g) nrow(group_data(g))))` patients the Kaplan-Meier intervals are wide, so this is a weak test, and it cannot reach the 5-year landmark at all.

The control arm's observed OS is flat from its last death at week `r round(ctrl_last_event_wk)` (`r sprintf("%.1f", ctrl_last_event_wk / 52)` years) to its last follow-up at week `r round(ctrl_last_wk)`, at `r fmt_pct(ctrl_km_last)`. At that time the model predicts `r fmt_pct(ctrl_model_at_last)` for the same patients. The fitted curve keeps falling where the Kaplan-Meier curve has levelled off. That plateau rests on the few control patients still under follow-up and is not by itself evidence of a cured fraction.

# Independent validation: published first-line mCRC survival

## Benchmarks and tolerance

The benchmarks are in `data/external/survival_benchmarks.csv` (MD5 `r bench_md5`). Its provenance, including why each source is treated as comparable or as a lower bound, is in `data/external/README.md`. Every value is transcribed from a published table or text; nothing was digitised.

- **Comparable** sources are first-line oxaliplatin-based chemotherapy cohorts. They allow a two-sided check.
- **Lower-bound** sources are unselected or real-world populations: older patients, poorer performance status, monotherapy, and in the registries also untreated patients. A trial population receiving FLOX should not have shorter survival than these, so they allow a one-sided check only.

**Pre-specified tolerance.** `r survival_benchmark_tolerance()`

The primary model curve is the economic standard-of-care curve, the curve that enters the cost-effectiveness model: the joint model averaged over all `r nrow(data_complete)` complete-case patients with `Rx` set to control. The curve predicted for the `r nrow(ctrl_data)` control-arm patients is a secondary comparison (Section 3.4). The model interval is the 95% percentile range over the same `r length(draw_idx)` coefficient draws. It is reported for context but is not part of the tolerance.

```{r table-sources}
src <- benchmarks |>
  distinct(source, population, era, msi_selection, median_age, doi) |>
  transmute(Source = source, Population = population, Period = era,
            MSI = msi_selection,
            `Median age` = ifelse(is.na(median_age), "--", format(median_age)),
            DOI = doi)
knitr::kable(src, format = report_table_format(), booktabs = TRUE, row.names = FALSE,
             caption = "Benchmark sources") |>
  tbl_style(latex_options = "HOLD_position", font_size = 8) |>
  tbl_column_spec(1, width = "3.3cm") |>
  tbl_column_spec(2, width = "4.2cm") |>
  tbl_column_spec(6, width = "3.2cm")
```

## Comparison

```{r table-comparison}
cmp_tab <- data.frame(
  Source = source_label(comparison),
  Measure = measure_label(comparison),
  Benchmark = fmt_bench(comparison),
  Role = ifelse(comparison$role == "comparable", "Comparable", "Lower bound"),
  `Model SoC (95% interval)` = fmt_model(comparison, "soc"),
  Verdict = comparison$soc_verdict,
  check.names = FALSE, stringsAsFactors = FALSE
)
knitr::kable(cmp_tab, format = report_table_format(), booktabs = TRUE, row.names = FALSE,
             align = "llrlrl",
             caption = "Economic standard-of-care curve versus published benchmarks") |>
  tbl_style(latex_options = "HOLD_position", font_size = 8) |>
  tbl_footnote(general = paste(
    "Benchmark: estimate with reported 95% CI where available. Medians in months;",
    "survival as the proportion alive. Model SoC: the economic standard-of-care",
    "curve with the 2.5th-97.5th percentile over coefficient draws.",
    "Verdict: the pre-specified tolerance applied to the model point estimate."),
    threeparttable = TRUE)
```

**Result.** `r n_soc_pass` of the `r n_soc_eval` evaluable checks meet the pre-specified tolerance and `r n_soc_fail` do not. By role: `r sum(comp_rows$soc_pass, na.rm = TRUE)` of `r sum(!is.na(comp_rows$soc_pass))` comparable checks and `r sum(lb_rows$soc_pass, na.rm = TRUE)` of `r sum(!is.na(lb_rows$soc_pass))` lower-bound checks pass.

```{r fails, results="asis"}
if (nrow(fails) > 0) {
  cat("The failed checks:\n\n")
  for (i in seq_len(nrow(fails))) {
    r <- fails[i, ]
    direction <- if (r$role == "lower_bound") "below the lower bound" else
      if (r$soc_value > r$upper) "above the upper CI limit" else "below the lower CI limit"
    cat(sprintf("- %s, %s: model %s, benchmark %s (%s).\n",
                source_label(r), measure_label(r),
                fmt_value(r$soc_value, r$measure), fmt_bench(r), direction))
  }
  cat("\n")
}
```

## Interpretation

**Medians.** The model's standard-of-care median OS is `r fmt_mo(curve_median_months(soc_curve$OS))` months and its median PFS `r fmt_mo(soc_pfs_med)` months. The control-arm Kaplan-Meier median PFS is `r fmt_mo(ctrl_km_pfs_med[["median"]])` months (95% CI `r fmt_ci_mo(ctrl_km_pfs_med[["lower"]], ctrl_km_pfs_med[["upper"]])`), and METIMMOX's own publication reports 9.2 months for the control group (Ree et al. 2024, doi:10.1038/s41416-024-02696-6). `r if (nrow(pfs_fails) > 0 && pfs_med_in_km) "The model median PFS lies inside the trial's Kaplan-Meier interval, so the PFS failures reflect a difference between METIMMOX and the benchmark cohorts, not a fault of the fitted curve." else if (nrow(pfs_fails) > 0) "The model median PFS lies outside the trial's own Kaplan-Meier interval as well." else ""` Two differences can lengthen METIMMOX PFS relative to other trials:

- the analysis PFS endpoint counts deaths without recorded progression only within `r pfs_death_window_weeks` weeks of the last assessment (issue #181);
- the scan schedules differ between the trials.

**Tail.** `r tail_text`

`r if (any(grepl("^sorbye_no_lt60_", fails$id))) sprintf("*Post hoc remark, outside the pre-specified rule:* the registry rows for patients under 60 describe a younger population than METIMMOX (complete-case median age %s years), so they are a stricter bound than intended. The all-ages registry rows, which include patients over 75 and untreated patients, give: %s.", median(data_complete$Age), paste(sprintf("%s, %s", measure_label(comparison[grepl("^sorbye_no_all_", comparison$id), ]), tolower(comparison$soc_verdict[grepl("^sorbye_no_all_", comparison$id)])), collapse = "; ")) else ""`

**Consequence for the economic model.** This report checks the standard-of-care curve only. The guided strategies use the same joint model, so their tails are extrapolated with the same distribution. Whether a heavier tail would raise or lower the incremental QALYs depends on how the biomarker-by-treatment effects carry into it, and that is not assessed here. The survival-family structural sensitivity in `OWSA.qmd` is the existing bound on this uncertainty. No model input is changed by this report.

## Secondary comparison: control-arm patients

```{r table-ctrl}
ctrl_tab <- data.frame(
  Source = source_label(comparison),
  Measure = measure_label(comparison),
  Benchmark = fmt_bench(comparison),
  `Model, control-arm patients (95% interval)` = fmt_model(comparison, "ctrl"),
  Verdict = comparison$ctrl_verdict,
  check.names = FALSE, stringsAsFactors = FALSE
)
knitr::kable(ctrl_tab, format = report_table_format(), booktabs = TRUE, row.names = FALSE,
             align = "llrrl",
             caption = "Model predicted for the control-arm patients versus published benchmarks") |>
  tbl_style(latex_options = "HOLD_position", font_size = 8)
```

Predicted for the `r nrow(ctrl_data)` control-arm patients instead of the whole cohort, the model meets `r n_ctrl_pass` of `r n_ctrl_eval` checks. The two curves differ because the control arm has a different covariate mix (median age `r median(ctrl_data$Age)` versus `r median(data_complete$Age)` years, `r sum(as.numeric(as.character(ctrl_data$crp)) == 1)` of `r nrow(ctrl_data)` CRP-positive versus `r sum(as.numeric(as.character(data_complete$crp)) == 1)` of `r nrow(data_complete)`).

## Model-predicted control-arm OS at fixed landmarks

```{r table-landmarks}
land_bench <- function(y) {
  r <- benchmarks[benchmarks$endpoint == "OS" & benchmarks$measure == "survival" &
                    !is.na(benchmarks$time_years) & benchmarks$time_years == y, ]
  if (nrow(r) == 0) return("--")
  paste(sprintf("%s: %s", source_label(r), fmt_pct(r$estimate)), collapse = "; ")
}
km_ctrl <- dependent[dependent$endpoint == "OS" & dependent$group == "control" &
                       dependent$measure == "survival", ]
soc_iv <- draw_landmark_intervals(model_draws$soc$OS, years)
ctrl_iv <- draw_landmark_intervals(model_draws$ctrl$OS, years)
land_tab <- data.frame(
  Year = years,
  `Model SoC` = sprintf("%s (%s)", fmt_pct(curve_at_years(soc_curve$OS, years)),
                        fmt_ci_pct(soc_iv$lower[1:4], soc_iv$upper[1:4])),
  `Model, control-arm patients` = sprintf("%s (%s)",
    fmt_pct(curve_at_years(model_curves$ctrl$OS, years)),
    fmt_ci_pct(ctrl_iv$lower[1:4], ctrl_iv$upper[1:4])),
  `KM control arm` = ifelse(grepl("^NE", km_ctrl$km_status), "NE",
                            sprintf("%s (%s)", fmt_pct(km_ctrl$km),
                                    fmt_ci_pct(km_ctrl$km_lower, km_ctrl$km_upper))),
  `Published (lower bounds)` = vapply(years, land_bench, ""),
  check.names = FALSE, stringsAsFactors = FALSE
)
knitr::kable(land_tab, format = report_table_format(), booktabs = TRUE, row.names = FALSE,
             align = "rrrrl",
             caption = "Overall survival at 1, 2, 3 and 5 years: model, trial and published values") |>
  tbl_style(latex_options = "HOLD_position", font_size = 8) |>
  tbl_column_spec(5, width = "4.5cm")
```

None of the comparable sources reports landmark survival in its text or tables; they report medians only. The published landmark values above are all lower bounds.

```{r fig-tail, fig.height=5.5, fig.cap="Overall survival under standard of care. Solid line and band: the economic model curve (all complete-case patients with Rx = control) and its 95% coefficient-draw interval, compared with the published values (triangles; all are lower bounds). Dashed line: the model predicted for the control-arm patients, the same patients as the Kaplan-Meier step curve (issue #157 convention). Dotted line: end of trial follow-up."}
band <- data.frame(year = times / 52, model = soc_curve$OS,
                   ctrl = model_curves$ctrl$OS,
                   lower = apply(model_draws$soc$OS, 2, quantile, 0.025),
                   upper = apply(model_draws$soc$OS, 2, quantile, 0.975))
km_df <- data.frame(year = c(0, ctrl_os_fit$time) / 52, surv = c(1, ctrl_os_fit$surv))
pts <- comparison[comparison$endpoint == "OS" & comparison$measure == "survival", ]
pts$label <- source_label(pts)
line_cols <- c("Model, economic SoC" = "#2a78d6",
               "Model, control-arm patients" = "#2a78d6",
               "Kaplan-Meier, control arm" = "grey35")
line_types <- c("Model, economic SoC" = "solid",
                "Model, control-arm patients" = "dashed",
                "Kaplan-Meier, control arm" = "solid")
point_fills <- c("#eb6834", "#7b3294", "#1b9e77", "#e7298a", "#66a61e", "#a6761d")
ggplot() +
  geom_ribbon(data = band, aes(year, ymin = lower, ymax = upper), fill = "#2a78d6", alpha = 0.18) +
  geom_line(data = band, aes(year, model, colour = "Model, economic SoC",
                             linetype = "Model, economic SoC"), linewidth = 0.8) +
  geom_line(data = band, aes(year, ctrl, colour = "Model, control-arm patients",
                             linetype = "Model, control-arm patients"), linewidth = 0.6) +
  geom_step(data = km_df, aes(year, surv, colour = "Kaplan-Meier, control arm",
                              linetype = "Kaplan-Meier, control arm"), linewidth = 0.6) +
  geom_point(data = pts, aes(time_years, estimate, fill = label), shape = 24,
             size = 2.8, colour = "grey15") +
  geom_vline(xintercept = max_fu_yr, linetype = "dotted", colour = "grey50") +
  scale_colour_manual(values = line_cols, name = NULL) +
  scale_linetype_manual(values = line_types, name = NULL) +
  scale_fill_manual(values = point_fills[seq_along(unique(pts$label))], name = NULL) +
  scale_x_continuous(breaks = 0:10, limits = c(0, time_horizon / 52)) +
  scale_y_continuous(labels = percent_format(accuracy = 1), limits = c(0, 1)) +
  labs(x = "Years from randomisation", y = "Overall survival") +
  guides(colour = guide_legend(ncol = 1), linetype = guide_legend(ncol = 1),
         fill = guide_legend(ncol = 2))
```

# Applicability of the benchmarks

None of the benchmark cohorts matches METIMMOX exactly. The differences pull in both directions:

- **Era.** The benchmark cohorts were treated between 2001 and 2015; METIMMOX enrolled from 2018. Survival of metastatic colorectal cancer has improved over these decades (Sorbye et al. 2013; Storli et al. 2025). Older cohorts should therefore, if anything, show *shorter* survival, which supports their use as lower bounds.
- **MSI selection.** Only Aasebo et al. 2019 is restricted to MSS tumours. In that cohort 7% of unselected patients had MSI-high tumours, which had shorter survival with first-line chemotherapy than MSS tumours. Unselected cohorts are therefore slightly pessimistic for an MSS population.
- **Age and fitness.** The METIMMOX complete-case median age is `r median(data_complete$Age)` years, against 61 in NORDIC-VII arm A and about 70 in the population-based cohorts, which also include patients with performance status above 1.
- **Time origin.** The population-based studies measure OS from the diagnosis of metastatic disease, not from the start of first-line treatment, which lengthens their OS relative to METIMMOX.
- **Endpoint definitions.** PFS definitions and scan intervals differ between trials (see Section 3.3).

# Limitations

- The comparable sources report medians, not survival at 1, 2, 3 and 5 years. The only landmark benchmarks are lower bounds, so the tail is tested one-sidedly: an extrapolation that was too optimistic would not be detected.
- No benchmark is restricted to the METIMMOX eligibility criteria, and none reports survival by CRP or TMB/BRAF status. The biomarker-guided strategies are therefore validated only against the trial data (Section 2).
- The 5-year Kaplan-Meier landmark is not estimable in any group, because follow-up ends at `r sprintf("%.1f", max_fu_yr)` years.
- The full texts of Tveit et al. 2012 and Sorbye et al. 2013 were not accessible. NORDIC-VII confidence intervals come from a published tabulation of the trial, and the registry values from the abstract.
- The validateHE external-validation module was not run. This report is the external validation referred to in the manuscript methods (issue #160).

# References

- Tveit KM, Guren T, Glimelius B, et al. Phase III trial of cetuximab with continuous or intermittent fluorouracil, leucovorin, and oxaliplatin (Nordic FLOX) versus FLOX alone in first-line treatment of metastatic colorectal cancer: the NORDIC-VII study. J Clin Oncol 2012;30:1755-62. doi:10.1200/JCO.2011.38.0915
- Guren TK, Thomsen M, Kure EH, et al. Cetuximab in treatment of metastatic colorectal cancer: final survival analyses and extended RAS data from the NORDIC-VII study. Br J Cancer 2017;116:1271-8. doi:10.1038/bjc.2017.93
- Aasebo KO, Dragomir A, Sundstrom M, et al. Consequences of a high incidence of microsatellite instability and BRAF-mutated tumors: a population-based cohort of metastatic colorectal cancer patients. Cancer Med 2019;8:3623-35. doi:10.1002/cam4.2205
- Storli PE, Dille-Amdam RG, Skjerseth GH, et al. Synchronous metastases from colorectal cancer. Treatment and long-term survival compared to patients with metachronous metastases: a population-based study from Central Norway 2001-2015. Acta Oncol 2025;64:797-806. doi:10.2340/1651-226X.2025.42985 (labelled "Central Norway 2025" in the tables)
- Sorbye H, Cvancarova M, Qvortrup C, et al. Age-dependent improvement in median and long-term survival in unselected population-based Nordic registries of patients with synchronous metastatic colorectal cancer. Ann Oncol 2013;24:2354-60. doi:10.1093/annonc/mdt197
- Ree AH, Saltyte Benth J, Hamre HM, et al. First-line oxaliplatin-based chemotherapy and nivolumab for metastatic microsatellite-stable colorectal cancer: the randomised METIMMOX trial. Br J Cancer 2024;130:1921-8. doi:10.1038/s41416-024-02696-6

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
