---
title: "Cost-Effectiveness Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05", "06"),
  funs = c("model_fun", "calculate_outcomes", "cea_helpers", "report_format",
           "psa_functions")
)

basecase <- run_basecase(verbose = FALSE)
base_results <- basecase$base_results
icer_obj <- basecase$icer_obj
model_config <- basecase$model_config

# The PSA cache must have been generated from the inputs of this session. The
# expected fingerprint is the one 10_PSA.R stamps on the cache (sampling-cache
# fingerprint, l_params_base, PSA distributions, strategies, n_sim, seed,
# horizon and cycle length; issue #156); the loader stops on an absent or stale
# cache instead of rendering placeholders (issue #157). Script 06 is sourced
# for the sampling-cache fingerprint and the PSA distributions; it loads from
# cache in seconds.
expected_psa <- psa_cache_fingerprint(
  sampling_fingerprint = sampling_models$fingerprint,
  l_params_base = l_params_base,
  param_distributions = param_distributions,
  strategies = strategies,
  n_sim = n_sim,
  seed = analysis_seed,
  time_horizon = time_horizon,
  cl = cl
)
psa_obj <- load_psa_cache(
  verbose = FALSE, required = TRUE,
  expected_fingerprint = expected_psa,
  strategies = strategies, n_sim = n_sim,
  sampling_fingerprint = sampling_models$fingerprint
)

# PSA parameter draws, used to report the utility-ordering diagnostic below.
psa_params <- load_psa_params_cache(
  verbose = FALSE, required = TRUE,
  seed = analysis_seed, n_sim = psa_obj$n_sim
)
```

# Overview

This cost-effectiveness analysis evaluates standard of care against two pre-immunotherapy biomarker-guided immunotherapy strategies for metastatic MSS/pMMR colorectal cancer:

- CRP-guided treatment selection (CRP < 5 mg/L at week 4, before the first nivolumab dose)
- TMB/BRAF-guided treatment selection (baseline next-generation sequencing)

The economic survival model is a single joint model with CRP and TMB/BRAF treatment interactions. Economic strategies are restricted to biomarkers that are available before the decision to add immunotherapy is made.

**CRP timing.** CRP is not a baseline (pre-randomization) measurement. In the METIMMOX trial every patient received two cycles of FLOX before the first nivolumab dose, and the CRP used to define the CRP-guided strategy is the value measured at week 4 (cycle 3 day 1), i.e. at the point where the decision to add nivolumab is made. The model clock starts at randomization, but this has no economic consequence: up to week 4 both arms receive identical FLOX, monitoring and visits, and the week-4 blood test is already part of the monitoring schedule. Three patients without a week-4 CRP value died early (weeks 2.4, 15.7 and 20.9) and are excluded from the complete-case data on which the survival models are fitted, so the CRP subgroup curves are conditional on surviving to the week-4 measurement.

# Economic Survival Model

```{r model-table}
model_df <- data.frame(
  Component = c("OS", "PFS", "Control arm"),
  Formula = c(
    "Surv(OSwk, Death) ~ Age + sex + Rx + crp*Rx + tmb_braf*Rx",
    "Surv(PFSwk, Progression) ~ Age + sex + Rx + crp*Rx + tmb_braf*Rx",
    "Same joint OS and PFS models, predicted with Rx = control for every patient"
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  model_df,
  booktabs = TRUE,
  align = c("l", "l"),
  caption = "Single economic survival model"
) %>%
  tbl_style(latex_options = c("HOLD_position")) %>%
  tbl_column_spec(2, width = "10cm")
```

```{r strategy-table}
strategy_df <- data.frame(
  Strategy = strategy_label(get_strategies()),
  Definition = c(
    "All patients receive standard FLOX chemotherapy",
    "CRP-positive patients receive FLOX + nivolumab; CRP-negative patients receive FLOX",
    "TMB/BRAF-positive patients receive FLOX + nivolumab; TMB/BRAF-negative patients receive FLOX"
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  strategy_df,
  booktabs = TRUE,
  align = c("l", "l"),
  caption = "Economic strategies"
) %>%
  tbl_style(latex_options = c("HOLD_position")) %>%
  tbl_column_spec(2, width = "10cm")
```

# Base Case Results

```{r basecase-table}
base_display <- base_results %>%
  mutate(
    NMB = Effect * WTP - Cost,
    Strategy = strategy_label(Strategy),
    Cost = format_eur(Cost),
    Effect = sprintf("%.3f", Effect),
    NMB = format_eur(NMB)
  )

knitr::kable(
  base_display,
  booktabs = TRUE,
  align = c("l", "r", "r", "r"),
  col.names = c("Strategy", "Cost", "QALYs", "NMB"),
  caption = paste0("Base case results at WTP = EUR ", format(WTP, big.mark = ","))
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

```{r icer-table}
icer_display <- as.data.frame(icer_obj) %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Cost = format_eur(Cost),
    Effect = sprintf("%.3f", Effect),
    Inc_Cost = format_eur(Inc_Cost),
    Inc_Effect = ifelse(is.na(Inc_Effect), "--", sprintf("%.3f", Inc_Effect)),
    ICER = mapply(format_icer, ICER, Status)
  )

knitr::kable(
  icer_display,
  booktabs = TRUE,
  align = c("l", "r", "r", "r", "r", "r", "l"),
  col.names = c("Strategy", "Cost", "QALYs", "Incremental Cost",
                "Incremental QALYs", "ICER", "Status"),
  caption = "Incremental cost-effectiveness results"
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

```{r ce-plane, fig.cap="Cost-effectiveness plane for the single joint economic model"}
plot(
  icer_obj,
  txtsize = 11,
  currency = "EUR",
  effect_units = "QALYs",
  label = "all",
  alpha = 0.8
)
```

# Probabilistic Sensitivity Analysis

## Parameters sampled

The PSA samples the health-state utilities, the joint biomarker cell probabilities, and the resource-use costs (visit, baseline work-up, quarterly follow-up, end-of-life care), together with the survival models. Unit drug and test prices are **fixed** (issue #154): they are published tariffs or, for nivolumab, an assumed acquisition price, so treating them as uncertain would attribute decision uncertainty — and value of information — to quantities that no study could resolve. Their influence is reported in the one-way sensitivity analysis and in the biosimilar pricing scenario instead.

The two utilities are sampled jointly rather than independently. The PSA draws a non-negative decrement and sets the progressed utility to the progression-free utility minus that decrement, so no draw can place the progressed utility above the progression-free utility.

```{r utility-ordering}
reversal <- utility_reversal_fraction(psa_params)
cat(sprintf(
  paste0("Utility-ordering diagnostic: %d of %d PSA draws (%.1f%%) have u_p > u_np, ",
         "and %.1f%% exceed it by more than %.2f. The decrement parameterisation ",
         "makes these fractions zero by construction; independent beta draws ",
         "for the two utilities did not."),
  reversal$n_reversed, reversal$n, 100 * reversal$fraction,
  100 * reversal$fraction_material, reversal$margin
))
```

## Results

```{r psa-summary}
psa_summary <- create_psa_summary_table(psa_obj, wtp = WTP) %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Mean_Cost = format_eur(Mean_Cost),
    Mean_QALY = sprintf("%.3f", Mean_QALY),
    Prob_CE = scales::percent(Prob_CE, accuracy = 0.1)
  )

knitr::kable(
  psa_summary,
  booktabs = TRUE,
  align = c("l", "r", "r", "r"),
  col.names = c("Strategy", "Mean Cost", "Mean QALYs", "Probability Cost-Effective"),
  caption = paste0("PSA summary at WTP = EUR ", format(WTP, big.mark = ","))
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

The PSA and the base case use the same joint survival model: every PSA draw predicts the control, biomarker-positive, and biomarker-negative curves from one sampled coefficient vector of the joint fit (multivariate-normal draws, issue #156), with the control curve obtained by setting treatment to standard of care for every patient, exactly as in the base case. PSA means should therefore sit close to the base-case values, differing only through the nonlinearity of the partitioned survival model. The table below reports each difference in units of the PSA Monte Carlo standard error; the regression test `test_psa_basecase_alignment.R` flags any absolute difference above five standard errors. With 5,000 draws the standard errors are small, and the mean QALYs of every strategy sit a few hundredths of a QALY above the base case with the same sign: this is the mean bias of the extrapolated parametric curves under coefficient sampling, shared by all arms because they come from one fit, and it is documented as a known deviation in the test protocol.

```{r psa-basecase-table}
psa_vs_base <- create_psa_basecase_comparison(psa_obj, base_results) %>%
  mutate(
    Strategy = strategy_label(Strategy),
    Base_Case = ifelse(Outcome == "Cost", format_eur(Base_Case),
                       sprintf("%.4f", Base_Case)),
    PSA_Mean = ifelse(Outcome == "Cost", format_eur(PSA_Mean),
                      sprintf("%.4f", PSA_Mean)),
    PSA_SE = ifelse(Outcome == "Cost", format_eur(PSA_SE),
                    sprintf("%.4f", PSA_SE)),
    Diff = ifelse(Outcome == "Cost", format_eur(Diff),
                  sprintf("%+.4f", Diff)),
    Diff_SE = sprintf("%+.1f", Diff_SE)
  )

knitr::kable(
  psa_vs_base,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r", "r", "r"),
  col.names = c("Strategy", "Outcome", "Base Case", "PSA Mean",
                "PSA SE", "Difference", "Difference (SE)"),
  caption = "PSA means versus base-case values (difference in Monte Carlo standard errors)"
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

Because all strategies in a PSA draw share one sampled joint model, a shift that is common to every strategy (the mean bias of the extrapolated parametric curves under coefficient sampling) cancels in the increments, whereas a control-specific shift would not. The incremental comparison below therefore isolates what matters for the decision.

```{r psa-incremental-table}
psa_inc <- create_psa_incremental_comparison(psa_obj, base_results) %>%
  mutate(
    Comparator = paste(strategy_label(Comparator), "vs", strategy_label(get_control_strategy())),
    Base_Case = ifelse(Outcome == "Cost", format_eur(Base_Case),
                       sprintf("%+.4f", Base_Case)),
    PSA_Mean = ifelse(Outcome == "Cost", format_eur(PSA_Mean),
                      sprintf("%+.4f", PSA_Mean)),
    PSA_SE = ifelse(Outcome == "Cost", format_eur(PSA_SE),
                    sprintf("%.4f", PSA_SE)),
    Diff = ifelse(Outcome == "Cost", format_eur(Diff),
                  sprintf("%+.4f", Diff)),
    Diff_SE = sprintf("%+.1f", Diff_SE)
  )

knitr::kable(
  psa_inc,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r", "r", "r"),
  col.names = c("Comparison", "Outcome", "Base Case", "PSA Mean",
                "PSA SE", "Difference", "Difference (SE)"),
  caption = "Incremental PSA means versus base-case increments relative to standard of care"
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

```{r ceac, fig.cap="Cost-effectiveness acceptability curves"}
create_ceac_plot(psa_obj, wtp_line = WTP)
```

# Summary

The economic evaluation now uses one joint survival model and three economic strategies: standard of care, CRP-guided immunotherapy (week-4 CRP, before the first nivolumab dose), and TMB/BRAF-guided immunotherapy (baseline NGS).

# Common Target Population

Control and both guided strategies are evaluated in the same complete-case trial population (n = `r nrow(l_params_base$prediction_population)`). The base case uses its observed joint CRP and TMB/BRAF distribution. The PSA draws all four joint cell probabilities together using a Dirichlet distribution with the observed cell counts; marginal prevalences are derived from that draw. The age and sex distributions within each cell remain fixed. Every draw's common population weights apply to control and both guided strategies. This represents uncertainty in the trial population, not transport to an external population. The prevalence DSA changes one marginal while retaining the other marginal and joint odds ratio, and reweights every strategy consistently (issue #166).

# Scope Limitations

Three scope decisions bound the interpretation of these results (issue #154).

**No post-progression treatment costs.** After progression the model charges only the quarterly follow-up contact and the one-time end-of-life cost. Second-line systemic therapy, post-progression imaging and post-progression visits are not modeled. The strategies differ in time spent in the progressed state, so this omission is differential rather than a common offset. A structural scenario charging EUR 5,000 per quarter in the progressed state is reported in the one-way sensitivity analysis.

**Second treatment sequence given to all progression-free patients.** Both arms receive a second eight-cycle sequence at weeks 24-38, applied to every patient still progression-free at that point. METIMMOX re-treated on progression during the treatment break, so the model charges second-sequence drug and visit costs to patients who would not have been re-treated. A partitioned survival model has no on-treatment substate, so re-treatment cannot be conditioned on progression without restructuring the model; a structural scenario removing the second sequence, with survival held at the trial estimate, bounds the cost side of the assumption.

**Nivolumab price is an assumption.** The base-case price per administration is an assumed Norwegian hospital acquisition cost rather than a citable tariff, because Norwegian hospital prices are set by confidential LIS tender. It is the largest single cost driver; the biosimilar scenario and the one-way analysis show how the conclusions move with it.

Adverse-event costs and disutilities remain outside the modeled scope, as described in the project documentation.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.3
