---
title: "Clinical Effectiveness"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Load required libraries and shared Cox extraction helpers.
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("cox_extract", "tlr_landmark"),
  packages = c("here", "knitr", "kableExtra", "ggplot2", "dplyr", "tidyverse",
               "survival", "survminer", "coxphf", "glmnet", "vcd"),
  set_theme = FALSE
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r helper-functions, include=FALSE}
# =============================================================================
# HELPER FUNCTIONS
# =============================================================================

#' Extract results from standard Cox model (full table, interactions grouped at top)
extract_coxph_results <- function(model, reorder_interactions = TRUE) {
  if (is.null(model)) return(NULL)

  model_summary <- summary(model)
  coef_table <- model_summary$coefficients
  conf_table <- model_summary$conf.int

  results <- data.frame(
    Term = rownames(coef_table),
    HR = exp(coef(model)),
    CI_Lower = conf_table[, "lower .95"],
    CI_Upper = conf_table[, "upper .95"],
    P_Value = coef_table[, "Pr(>|z|)"],
    stringsAsFactors = FALSE
  )

  if (reorder_interactions) {
    # Put interaction terms at top
    is_interaction <- grepl(":", results$Term)
    results <- rbind(results[is_interaction, ], results[!is_interaction, ])
  }

  rownames(results) <- NULL
  results
}

#' Readable labels for model terms (issue #182)
#'
#' Maps coxph/coxphf term names (Age, sex1, RxExperimental arm, crp_num,
#' RxExperimental arm:crp_num, ...) and cox.zph term names (sex, Rx,
#' Rx:crp_num, GLOBAL) to display labels. `short = TRUE` drops the contrast
#' description. Unknown terms are returned unchanged.
term_label <- function(term, short = FALSE) {
  long_labels <- c(Age = "Age (per year)", sex = "Sex (male vs female)",
                   Rx = "Rx (experimental vs control)", crp_num = "CRP-positive",
                   tmb_braf_num = "TMB/BRAF-positive", tlr_num = "TLR-positive")
  short_labels <- c(Age = "Age", sex = "Sex", Rx = "Rx", crp_num = "CRP",
                    tmb_braf_num = "TMB/BRAF", tlr_num = "TLR")
  labels <- if (short) short_labels else long_labels
  vapply(term, function(t) {
    parts <- strsplit(t, ":", fixed = TRUE)[[1]]
    base <- sub("^Rx.*$", "Rx", sub("^sex.*$", "sex", parts))
    if (length(parts) == 2 && "Rx" %in% base) {
      bm <- setdiff(base, "Rx")
      if (length(bm) == 1 && bm %in% names(short_labels)) {
        return(paste(short_labels[[bm]], "x Rx"))
      }
    }
    if (length(parts) == 1 && base %in% names(labels)) return(labels[[base]])
    t
  }, character(1), USE.NAMES = FALSE)
}

#' Index of the single term matching a row pattern (issue #182)
#'
#' Every row of a comparison table must identify exactly one model term; a
#' pattern that matches two terms (for example `^Rx[A-Za-z]`, which also
#' matches `RxExperimental arm:tlr_num`) stops the render.
match_one_term <- function(pattern, terms, table_label = "") {
  idx <- grep(pattern, terms)
  if (length(idx) != 1) {
    stop(sprintf("Row pattern '%s' matches %d terms%s: %s", pattern, length(idx),
                 if (nzchar(table_label)) paste0(" in ", table_label) else "",
                 paste(terms[idx], collapse = ", ")))
  }
  idx
}

#' Format HR with CI for display (vectorized)
format_hr_ci <- function(hr, ci_lower, ci_upper, digits = 2) {
  mapply(function(h, l, u) {
    if (is.na(h)) return("--")
    sprintf(paste0("%.", digits, "f (%.", digits, "f-%.", digits, "f)"), h, l, u)
  }, hr, ci_lower, ci_upper, USE.NAMES = FALSE)
}

#' Build a side-by-side standard Cox vs Firth comparison table
build_std_firth_comparison <- function(std_results, firth_results, row_specs) {
  format_result_cell <- function(results_df, pattern) {
    if (is.null(results_df) || is.null(pattern)) return("--")
    idx <- match_one_term(pattern, results_df$Term, "standard Cox vs Firth table")
    format_hr_ci(
      results_df$HR[idx],
      results_df$CI_Lower[idx],
      results_df$CI_Upper[idx]
    )
  }

  do.call(rbind, lapply(row_specs, function(rs) {
    data.frame(
      Term = rs$label,
      Standard_Cox = format_result_cell(std_results, rs$std_pat),
      Firth = format_result_cell(firth_results, rs$firth_pat),
      stringsAsFactors = FALSE
    )
  }))
}

#' Render standard Cox vs Firth tables for both PDF and GFM outputs
render_std_firth_comparison_table <- function(comparison_df, caption,
                                             first_group_label, first_group_end,
                                             second_group_label) {
  table_format <- if (knitr::is_latex_output()) "latex" else "pipe"

  comparison_table <- comparison_df %>%
    kable(col.names = c("Term", "Standard Cox HR (95% CI)", "Firth HR (95% CI)"),
          caption = caption, booktabs = TRUE, format = table_format)

  if (knitr::is_latex_output()) {
    comparison_table %>%
      tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
      tbl_pack_rows(first_group_label, 1, first_group_end, bold = TRUE) %>%
      tbl_pack_rows(second_group_label, first_group_end + 1, nrow(comparison_df), bold = TRUE)
  } else {
    comparison_table
  }
}

#' Format p-value for display (vectorized)
format_pvalue <- function(p, digits = 3) {
  sapply(p, function(pval) {
    if (is.na(pval)) return("--")
    if (pval < 0.001) return("<0.001")
    sprintf(paste0("%.", digits, "f"), pval)
  }, USE.NAMES = FALSE)
}

#' Create log-log survival plot for PH diagnostics
create_loglog_plot <- function(data, time_var, event_var, strata_var, title) {
  formula <- as.formula(paste0("Surv(", time_var, ", ", event_var, ") ~ ", strata_var))
  km_fit <- survfit(formula, data = data)

  # Extract survival data
  surv_summary <- summary(km_fit)

  plot_data <- data.frame(
    time = surv_summary$time,
    surv = surv_summary$surv,
    strata = surv_summary$strata
  ) %>%
    filter(surv > 0 & surv < 1) %>%
    mutate(
      log_time = log(time),
      log_log_surv = log(-log(surv))
    )

  ggplot(plot_data, aes(x = log_time, y = log_log_surv, color = strata)) +
    geom_step(linewidth = 1) +
    labs(
      x = "log(Time in weeks)",
      y = "log(-log(S(t)))",
      title = title,
      subtitle = "Parallel lines support PH assumption",
      color = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

```{r data-preparation, include=FALSE}
# =============================================================================
# DATA PREPARATION
# =============================================================================

# Prepare data for Cox models.
# PRIMARY COHORT (issue #153): complete cases on the pre-immunotherapy
# biomarkers only (CRP, TMB/BRAF) plus covariates and endpoints. This is the
# same 68-patient cohort used by the economic survival models
# (04_parametric_survival_analysis.R) and the DAG association report. TLR
# completeness is NOT required here: the three patients without a TLR value
# left the study before the first on-treatment CT (exit reasons summarised in
# tlr_missing below; issue #182), and dropping them from the primary models
# would condition on remaining in the study until that scan.
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

# Ensure proper factor coding.
# `sex` is the renamed trial column "Sex 0female": level "0" = female,
# level "1" = male (see 01_data_prep.R, where Female <- 1 - `Sex 0female`).
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)
SEX_FEMALE_LEVEL <- "0"
SEX_MALE_LEVEL   <- "1"
stopifnot(all(levels(data_complete$sex) %in% c(SEX_FEMALE_LEVEL, SEX_MALE_LEVEL)))

# Biomarkers as numeric 0/1 for coxphf (interactions work better with numeric).
# tlr_num is NA for the three patients without a first on-treatment scan.
data_complete$crp_num <- as.numeric(as.character(data_complete$crp))
data_complete$tlr_num <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf_num <- as.numeric(as.character(data_complete$tmb_braf))

# Create numeric Rx for ridge regression
data_complete$Rx_num <- as.numeric(data_complete$Rx) - 1  # 0 = Control, 1 = Experimental

# TLR-COMPLETE COHORT: used only by the exploratory TLR responder and landmark
# analyses and by the TLR columns of the sample-characteristics table. It is
# the shared TLR landmark base cohort of tlr_landmark.R (issue #184), the
# TLR-classified patients within the complete-case cohort, the same base
# cohort as Figure 1 of the clinical paper and the DAG association tests.
# Applying the helper to data_complete keeps the report's derived columns
# (crp_num, tlr_num, tmb_braf_num, Rx_num, factor coding).
data_tlr <- tlr_landmark_base_cohort(data_complete, tlr_col = "tlr_num")
# Same patients (65) as the former rule and as the helper applied to `data`,
# in the same order.
stopifnot(
  identical(data_tlr$ID, data_complete$ID[!is.na(data_complete$tlr_num)]),
  identical(data_tlr$ID, tlr_landmark_base_cohort(data)$ID)
)
n_tlr_total   <- nrow(data_tlr)
n_tlr_missing <- n_total_missing_tlr <- nrow(data_complete) - n_tlr_total

# Study-exit reasons of the patients without a TLR value (issue #182): raw
# ProgressionExit from `data`, `AE exit` read from the tidy export and joined
# by ID inside tlr_missing_exit_summary(); `data` itself is not changed.
tlr_missing <- tlr_missing_exit_summary(data_complete, tlr_col = "tlr_num")
stopifnot(tlr_missing$n == n_tlr_missing)
tlr_missing_desc <- sprintf("left the study before the first on-treatment CT (%s)",
                            tlr_missing$reason_text)

# Sample characteristics (primary cohort)
n_total <- nrow(data_complete)
n_control <- sum(data_complete$Rx_num == 0)
n_experimental <- sum(data_complete$Rx_num == 1)

# Biomarker prevalence
prev_crp <- mean(data_complete$crp_num)
prev_tlr <- mean(data_tlr$tlr_num)
prev_tmb_braf <- mean(data_complete$tmb_braf_num)

# Event counts
n_deaths <- sum(data_complete$Death)
n_progressions <- sum(data_complete$Progression)
n_deaths_censored_pfs <- sum(data_complete$PFS_rule == "death_censored_at_assessment")
n_deaths_pfs_events <- sum(data_complete$PFS_rule == "death_within_window")
```

PFS counts recorded progression and deaths within `r pfs_death_window_weeks` weeks (inclusive) of the last assessment, using `r pfs_last_assessment` as the assessment-time proxy. In the primary cohort, `r n_deaths_censored_pfs` deaths without recorded progression are censored at that assessment and `r n_deaths_pfs_events` count as PFS death events.

```{r biomarker-correlation, include=FALSE}
# =============================================================================
# BIOMARKER CORRELATION ANALYSIS (Cramér's V)
# =============================================================================

# CRP vs TLR (TLR-complete subset)
crp_tlr_table <- table(data_tlr$crp_num, data_tlr$tlr_num)
crp_tlr_assoc <- assocstats(crp_tlr_table)
cramers_v_crp_tlr <- crp_tlr_assoc$cramer

# CRP vs TMB/BRAF (primary cohort)
crp_tmb_table <- table(data_complete$crp_num, data_complete$tmb_braf_num)
crp_tmb_assoc <- assocstats(crp_tmb_table)
cramers_v_crp_tmb <- crp_tmb_assoc$cramer

# TLR vs TMB/BRAF (TLR-complete subset)
tlr_tmb_table <- table(data_tlr$tlr_num, data_tlr$tmb_braf_num)
tlr_tmb_assoc <- assocstats(tlr_tmb_table)
cramers_v_tlr_tmb <- tlr_tmb_assoc$cramer

# Build correlation summary
correlation_df <- data.frame(
  Comparison = c("CRP vs TLR", "CRP vs TMB/BRAF", "TLR vs TMB/BRAF"),
  Cramers_V = round(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), 3),
  Interpretation = sapply(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), function(v) {
    if (v > 0.3) "Moderate/Strong"
    else if (v > 0.1) "Weak"
    else "Negligible"
  })
)
```

# Overview

This report presents clinical effectiveness results from the METIMMOX-1 trial, evaluating biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer.

The analysis uses **Firth-corrected Cox proportional hazards regression** with profile likelihood confidence intervals to assess treatment effect heterogeneity across two biomarkers that are available before the decision to add immunotherapy, identified by the causal DAG analysis:

- **CRP** (C-reactive protein): Low CRP (<5 mg/L) at week 4 (cycle 3 day 1), measured after the two FLOX cycles that both arms receive and before the first nivolumab dose — a prognostic and potentially predictive marker
- **TMB/BRAF**: High tumor mutational burden (≥9 mut/MB) or BRAF mutation — a baseline genomic marker

```{r crp-timing-counts, include=FALSE}
# Week-4 CRP by arm on the full trial data (before complete-case exclusion)
# and the follow-up of the patients with no week-4 value, quoted in the
# paragraph below so that the counts cannot drift from the data (issue #157).
# The baseline CRP comparison (CRP0cat, cycle 1 day 1) is derived in
# 01_data_prep.R and is not carried into the analysis data, so it is quoted
# from that script.
crp_arm_tab <- table(data$Rx, data$crp)
crp_arm_n <- rowSums(crp_arm_tab)
crp_arm_pos <- crp_arm_tab[, "1"]
crp_arm_fisher_p <- fisher.test(crp_arm_tab)$p.value
crp_missing <- data[is.na(data$crp), ]
crp_missing_weeks <- paste(sprintf("%.1f", sort(crp_missing$OSwk)), collapse = ", ")
# Describe the missing week-4 values by the death/follow-up time relative to
# week 4 (issue #182): a patient who died before week 4 could not have the
# measurement, the others were alive at week 4 without a value.
crp_missing_n_died_before4 <- sum(crp_missing$Death == 1 & crp_missing$OSwk < 4)
crp_missing_n_alive4 <- sum(crp_missing$OSwk >= 4)
stopifnot(crp_missing_n_died_before4 + crp_missing_n_alive4 == nrow(crp_missing))
crp_missing_arms <- table(droplevels(crp_missing$Rx))
crp_missing_arm_text <- paste(sprintf("%d %s", as.integer(crp_missing_arms),
                                      sub(" arm$", "-arm", tolower(names(crp_missing_arms)))),
                              collapse = " and ")
crp_missing_outcome <- sprintf(
  "%d died before week 4 and %d %s alive at week 4 without a week-4 value",
  crp_missing_n_died_before4, crp_missing_n_alive4,
  if (crp_missing_n_alive4 == 1) "was" else "were")
crp_missing_times <- if (all(crp_missing$Death == 1)) "deaths at weeks" else
  "death or last follow-up at weeks"
# Patients of the complete-case cohort who leave either risk set by week 4:
# a week-4 landmark would drop them.
n_cc_out_by_wk4 <- sum(data_complete$OSwk <= 4 | data_complete$PFSwk <= 4)
```

**CRP timing.** CRP is not a baseline (pre-randomization) measurement: the value used throughout is the week-4 CRP at the start of nivolumab, matching the post-hoc CRP analysis of the trial paper. Because nivolumab has not yet been given at week 4 and both arms receive identical FLOX until then, the DAG carries no `T -> CRP` edge. Two consequences follow. First, week-4 CRP-positivity differs by arm (experimental `r crp_arm_pos["Experimental arm"]`/`r crp_arm_n["Experimental arm"]`, control `r crp_arm_pos["Control arm"]`/`r crp_arm_n["Control arm"]`; Fisher p = `r format_pvalue(crp_arm_fisher_p)`) whereas baseline CRP was balanced (8/38 vs 7/35; p = 1; `CRP0cat` in `01_data_prep.R`, which is not part of the analysis data); this is treated as chance imbalance on a week-4 measurement in a small trial, not as a failure of randomization, and is what the `CRP:Rx` interaction is estimated against. Second, the `r nrow(crp_missing)` patients with no week-4 CRP (`r crp_missing_arm_text` patients) are excluded from the complete-case data: `r crp_missing_outcome` (`r crp_missing_times` `r crp_missing_weeks`). The exclusion is therefore not the same as conditioning on survival to week 4; the technical report `crp_week4_estimand.qmd` restores these patients under alternative CRP assignments. The clock remains randomization; a landmark analysis at week 4 would drop `r if (n_cc_out_by_wk4 == 0) "no further patients" else paste(n_cc_out_by_wk4, "further patient(s)")` from the complete-case cohort.

**Model specification is motivated by the causal DAG** (see `dag.qmd` and `dag_associations.qmd`). The DAG encodes treatment (T) as randomized with no parents, so no confounding adjustment is needed for causal identification; Age and Sex are included as precision covariates. Target lesion reduction (TLR) is positive when the sum of target-lesion diameters at the first on-treatment CT is at least 10% below its baseline value. TLR is encoded as a post-randomization intermediate variable (T → TLR → PFS): it is not a pre-treatment baseline characteristic and conditioning on it as a covariate would block part of the treatment effect pathway. TLR is therefore excluded from the primary survival models and examined separately as a descriptive endpoint.

The **unified DAG-informed model** is:

$$\text{Surv}(\text{time}, \text{event}) \sim \text{Age} + \text{sex} + \text{Rx} + \text{CRP} + \text{TMB/BRAF} + \text{CRP} \times \text{Rx} + \text{TMB/BRAF} \times \text{Rx}$$

Ridge regression (L2-penalized Cox) is applied as a sensitivity analysis to assess the stability of the interaction estimates under shrinkage. TLR is reported in a separate exploratory section.

# Methodological Notes

## Software Packages

This analysis uses the following R packages:

- `coxphf` version `r packageVersion("coxphf")`: Firth-corrected Cox regression with profile likelihood CIs
- `survival` version `r packageVersion("survival")`: Cox regression and Schoenfeld residual diagnostics
- `glmnet` version `r packageVersion("glmnet")`: Ridge regression sensitivity analysis
- `vcd` version `r packageVersion("vcd")`: Cramér's V for biomarker correlation assessment

## Firth-Corrected Cox Regression

We use Firth's penalized maximum likelihood method for Cox regression, which addresses:

1. **Monotone likelihood**: When a covariate perfectly separates events from non-events
2. **Small sample bias**: Reduces bias in coefficient estimates with sparse data
3. **Unstable confidence intervals**: Profile likelihood CIs are more reliable than Wald-based CIs in small samples

Statistical inference is based on **penalized likelihood ratio tests (PLRT)**, which are more appropriate than Wald tests for testing treatment-biomarker interactions in this setting.

Firth's penalty reduces the small-sample bias of the maximum-likelihood estimate; it does not make the estimate unbiased. Every Firth fit is run with an iteration limit of `r FIRTH_COX_MAXIT` (`coxphf`, step size 0.1), and the section "Firth Model Convergence" reports, for each fit, the estimation iterations, the largest number of profile-likelihood iterations for a confidence limit or PLRT, and whether the fit reached the limit.

## Ridge Regression Sensitivity Analysis

We use Ridge regression as a sensitivity analysis to assess the stability of our interaction estimates. Ridge regression (also called L2-penalized regression or Tikhonov regularization) belongs to the family of regularized or penalized regression methods. In survival analysis, this is implemented as a penalized Cox model.

**How Ridge regression works:**

- Ridge adds a penalty term that discourages large coefficients. The bigger a coefficient tries to get, the more the model resists, pulling estimates toward zero (HR toward 1.0).
- Unlike LASSO (alpha = 1), which sets some coefficients exactly to zero and performs variable selection, Ridge (alpha = 0) shrinks all coefficients but retains all predictors.
- The degree of shrinkage is controlled by the tuning parameter lambda, which is selected via **cross-validation (CV)**: the data are repeatedly split into training and validation sets, and the lambda that produces the best predictive performance is chosen. Here this is `glmnet::cv.glmnet(family = "cox", alpha = 0)` with 10-fold CV of the partial-likelihood deviance and `lambda.min`; fold assignment is seeded so the result is reproducible.
- **Implementation detail.** The model is fitted on an explicit design matrix (Age, sex, Rx, CRP, TMB/BRAF, CRP x Rx, TMB/BRAF x Rx) in which the product terms are constructed before fitting. This matters because `survival::ridge()` with a factor treatment variable and a formula interaction such as `crp:Rx` codes the interaction separately for each arm (the CRP slope within the control arm and within the experimental arm) rather than as the single treatment-by-biomarker contrast; the pre-built product term recovers the same contrast that the Firth model estimates. In the primary model only the CRP and TMB/BRAF main effects are penalized (penalty factor 1); Age, sex, Rx and the two interaction terms have penalty factor 0. glmnet does not provide standard errors, so ridge results are point estimates.

**Why not LASSO or Elastic Net?**

We determined that LASSO and elastic net are **not appropriate** for this analysis:

1. **Correlated biomarkers**: LASSO arbitrarily selects one of correlated predictors while setting others to zero, which does not reflect the clinical question of comparing ALL biomarker strategies.

2. **Hierarchy principle violation**: LASSO may select interaction terms (e.g., `crp:Rx`) while setting the main effect (`crp`) to zero, producing models that are difficult to interpret clinically.

3. **Clinical objective**: Our goal is to estimate treatment effect heterogeneity across ALL biomarkers simultaneously, not to select a "winning" biomarker.

Elastic net (alpha = 0.1–0.3) represents a compromise but does not fully address these concerns.

**Interpreting Ridge results:**

Ridge regression is not replacing the Firth estimates—it provides a reality check. When Ridge substantially shrinks an interaction coefficient toward zero while Firth estimates a large effect, this indicates the effect is too unstable to trust for practical use. The CV-selected lambda reflects how much regularization is needed for reasonable out-of-sample prediction given the sample size and collinearity structure.

# Data Preparation

## Sample Characteristics

```{r table-sample}
# Helper: format n (%) with subgroup denominator
fmt_n_pct <- function(n, total, digits = 1) {
  if (is.na(n) || total == 0) return("--")
  sprintf(paste0("%d (%.", digits, "f%%)"), n, 100 * n / total)
}

# Helper: format mean (SD)
fmt_mean_sd <- function(x, digits = 1) {
  if (length(x) == 0 || all(is.na(x))) return("--")
  sprintf(paste0("%.", digits, "f (%.", digits, "f)"),
          mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))
}

# Compute the column of statistics for a given subgroup
build_col <- function(df) {
  n <- nrow(df)
  rx_levels    <- levels(data_complete$Rx)
  # sex: level "0" = female, "1" = male ("Sex 0female" in the trial export).
  n_female     <- sum(df$sex == SEX_FEMALE_LEVEL)
  n_male       <- sum(df$sex == SEX_MALE_LEVEL)
  n_ctrl       <- sum(df$Rx == rx_levels[1])
  n_exp        <- sum(df$Rx == rx_levels[2])
  # TLR is missing for patients who left the study before the first
  # on-treatment scan, so the TLR-positive row uses the patients with a TLR
  # value as its denominator.
  n_tlr_known  <- sum(!is.na(df$tlr_num))
  c(
    as.character(n),
    fmt_mean_sd(df$Age),
    fmt_n_pct(n_male,   n),
    fmt_n_pct(n_female, n),
    fmt_n_pct(n_ctrl,   n),
    fmt_n_pct(n_exp,    n),
    fmt_n_pct(sum(df$Death),       n),
    fmt_n_pct(sum(df$Progression), n),
    fmt_n_pct(sum(df$crp_num),      n),
    fmt_n_pct(sum(df$tlr_num, na.rm = TRUE), n_tlr_known),
    fmt_n_pct(sum(df$tmb_braf_num), n)
  )
}

# Build subgroup data frames. CRP and TMB/BRAF columns use the primary
# 68-patient cohort; TLR columns use the TLR-complete subset.
sub_overall <- data_complete
sub_crp_pos <- data_complete[data_complete$crp_num      == 1, ]
sub_crp_neg <- data_complete[data_complete$crp_num      == 0, ]
sub_tlr_pos <- data_tlr[data_tlr$tlr_num == 1, ]
sub_tlr_neg <- data_tlr[data_tlr$tlr_num == 0, ]
sub_tmb_pos <- data_complete[data_complete$tmb_braf_num == 1, ]
sub_tmb_neg <- data_complete[data_complete$tmb_braf_num == 0, ]

table1_df <- data.frame(
  Characteristic = c(
    "Patients, n",
    "Age, mean (SD)",
    "Male",
    "Female",
    "Control (FLOX alone)",
    "Experimental (FLOX/nivolumab)",
    "Deaths (OS events)",
    "PFS events (progression or death)",
    "CRP-positive (low CRP)",
    "TLR-positive (early response)",
    "TMB/BRAF-positive"
  ),
  Overall = build_col(sub_overall),
  CRP_pos = build_col(sub_crp_pos),
  CRP_neg = build_col(sub_crp_neg),
  TLR_pos = build_col(sub_tlr_pos),
  TLR_neg = build_col(sub_tlr_neg),
  TMB_pos = build_col(sub_tmb_pos),
  TMB_neg = build_col(sub_tmb_neg),
  stringsAsFactors = FALSE
)

table1_df %>%
  kable(col.names = c("Characteristic", "Overall",
                      "Positive", "Negative",
                      "Positive", "Negative",
                      "Positive", "Negative"),
        caption = "Sample Characteristics by Biomarker Status",
        booktabs = TRUE, format = report_table_format(), align = c("l", rep("c", 7))) %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  tbl_header_above(c(" " = 2, "CRP" = 2, "TLR" = 2, "TMB/BRAF" = 2),
                   bold = TRUE) %>%
  tbl_pack_rows("Demographics",          2, 4,  bold = TRUE, italic = FALSE) %>%
  tbl_pack_rows("Treatment arm",         5, 6,  bold = TRUE, italic = FALSE) %>%
  tbl_pack_rows("Outcome events",        7, 8,  bold = TRUE, italic = FALSE) %>%
  tbl_pack_rows("Biomarker prevalence",  9, 11, bold = TRUE, italic = FALSE) %>%
  tbl_footnote(general = paste0(
             "Percentages within each column use the column subgroup as denominator. ",
             "CRP/TLR/TMB-BRAF rows in the corresponding subgroup column equal 100% by definition. ",
             "Overall, CRP and TMB/BRAF columns are the primary complete-case cohort (n = ", n_total,
             "); the TLR columns and the TLR-positive row use the ", n_tlr_total,
             " patients with a first on-treatment CT scan. The ", n_tlr_missing,
             " patients without a TLR value (", tlr_missing$arm_text, ") ",
             tlr_missing_desc, ". Sex: level 0 of the trial variable is female."),
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Biomarker Correlations

```{r table-correlation}
correlation_df %>%
  kable(col.names = c("Biomarker Pair", "Cramer's V", "Interpretation"),
        caption = "Biomarker Correlations (Cramer's V)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10)
```

**Note:** Cramér's V interpretation: <0.1 = Negligible, 0.1–0.3 = Weak, >0.3 = Moderate/Strong. The observed correlations are weak to negligible. While modest, any correlation among candidate biomarkers supports our decision not to use LASSO, which would arbitrarily select among correlated predictors.

\newpage

# Proportional Hazards Assumption

```{r ph-diagnostics, include=FALSE}
# =============================================================================
# PROPORTIONAL HAZARDS DIAGNOSTICS
# =============================================================================

# Fit standard coxph for Schoenfeld tests (not available in coxphf)
# Use the unified DAG-informed formula (CRP and TMB/BRAF only; TLR is a post-treatment mediator)
formula_diag_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                       crp_num:Rx + tmb_braf_num:Rx
formula_diag_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                               crp_num:Rx + tmb_braf_num:Rx

coxph_diag_os <- coxph(formula_diag_os, data = data_complete)
coxph_diag_pfs <- coxph(formula_diag_pfs, data = data_complete)

# Schoenfeld residual tests
zph_os <- cox.zph(coxph_diag_os)
zph_pfs <- cox.zph(coxph_diag_pfs)

# Extract results
zph_os_df <- as.data.frame(zph_os$table)
zph_pfs_df <- as.data.frame(zph_pfs$table)

# Covariate-level departures (issue #182): every term with Schoenfeld
# p < 0.05 is named in the text, with the consequence for its hazard ratio.
zph_flagged <- function(zph_df, alpha = 0.05) {
  rows <- setdiff(rownames(zph_df), "GLOBAL")
  rows[zph_df[rows, "p"] < alpha]
}
ph_flag_text <- function(zph_df, endpoint) {
  flagged <- zph_flagged(zph_df)
  if (length(flagged) == 0) {
    return(sprintf("No covariate-level test is below 0.05 in %s.", endpoint))
  }
  labels <- term_label(flagged, short = TRUE)
  items <- sprintf("%s (p = %s)", labels, format_pvalue(zph_df[flagged, "p"]))
  hr_names <- ifelse(flagged == "Rx", paste(endpoint, "treatment"),
                     paste(endpoint, labels))
  sprintf(paste0("In %s, the covariate-level test is below 0.05 for %s, so the %s ",
                 "hazard ratio%s a time-averaged summary of an effect that may ",
                 "change over follow-up."),
          endpoint, paste(items, collapse = " and "),
          paste(hr_names, collapse = " and "),
          if (length(flagged) == 1) " is" else "s are")
}
ph_flag_os_text  <- ph_flag_text(zph_os_df, "OS")
ph_flag_pfs_text <- ph_flag_text(zph_pfs_df, "PFS")
```

## Schoenfeld Residual Tests

The proportional hazards assumption was tested using scaled Schoenfeld residuals. A significant p-value indicates potential violation of the PH assumption for that covariate.

```{r table-schoenfeld}
# Combine OS and PFS results
stopifnot(identical(rownames(zph_os_df), rownames(zph_pfs_df)))
schoenfeld_df <- data.frame(
  Covariate = term_label(rownames(zph_os_df), short = TRUE),
  Chi_sq_OS = round(zph_os_df$chisq, 2),
  P_OS = format_pvalue(zph_os_df$p),
  Chi_sq_PFS = round(zph_pfs_df$chisq, 2),
  P_PFS = format_pvalue(zph_pfs_df$p)
)

schoenfeld_df %>%
  kable(col.names = c("Covariate", "Chi-square (OS)", "p-value", "Chi-square (PFS)", "p-value"),
        caption = "Schoenfeld Residual Test for Proportional Hazards Assumption",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_row_spec(nrow(schoenfeld_df), bold = TRUE)
```

**Note:** GLOBAL is the omnibus test for all covariates. Individual covariate tests help identify specific PH violations. `r ph_flag_os_text` `r ph_flag_pfs_text`

## Log-Log Survival Plots

```{r loglog-plots, fig.height=8, fig.width=10}
# Create log-log plots by treatment arm
p1 <- create_loglog_plot(data_complete, "OSwk", "Death", "Rx",
                         "Overall Survival by Treatment")
p2 <- create_loglog_plot(data_complete, "PFSwk", "Progression", "Rx",
                         "Progression-Free Survival by Treatment")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

**Interpretation:** Approximately parallel lines on the log-log plot support the proportional hazards assumption. Crossing or converging lines suggest time-varying effects.

\newpage

# Primary Analysis: Firth-Corrected Cox Models

```{r fit-unified-model, include=FALSE}
# =============================================================================
# FIT UNIFIED DAG-INFORMED FIRTH-CORRECTED COX MODELS
# Formula: Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx
# TLR excluded: post-randomization mediator (T -> TLR -> PFS in DAG)
# =============================================================================

formula_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                   crp_num:Rx + tmb_braf_num:Rx
formula_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                          crp_num:Rx + tmb_braf_num:Rx

std_os  <- coxph(formula_os,  data = data_complete)
std_pfs <- coxph(formula_pfs, data = data_complete)

model_os  <- fit_firth_cox(formula_os,  data_complete, "Unified OS")
model_pfs <- fit_firth_cox(formula_pfs, data_complete, "Unified PFS")

# Registry of every distinct Firth fit in the report, tabulated with its
# convergence diagnostics before the Discussion (issue #176). list(model)
# keeps failed (NULL) fits as entries.
firth_fits <- list()
register_firth <- function(label, model) {
  firth_fits[label] <<- list(model)
  invisible(model)
}
register_firth("Primary model, OS", model_os)
register_firth("Primary model, PFS", model_pfs)
```

```{r extract-results, include=FALSE}
# =============================================================================
# EXTRACT RESULTS FROM UNIFIED MODEL
# =============================================================================

results_os  <- extract_coxphf_results(model_os)
results_pfs <- extract_coxphf_results(model_pfs)

std_results_os  <- extract_coxph_results(std_os)
std_results_pfs <- extract_coxph_results(std_pfs)

primary_std_firth_row_specs <- list(
  list(label = "CRP x Rx",
       std_pat = "crp_num.*Rx|Rx.*crp_num",
       firth_pat = "crp_num.*Rx|Rx.*crp_num"),
  list(label = "TMB/BRAF x Rx",
       std_pat = "tmb_braf_num.*Rx|Rx.*tmb_braf_num",
       firth_pat = "tmb_braf_num.*Rx|Rx.*tmb_braf_num"),
  list(label = "Rx (experimental vs control)",
       std_pat = "^Rx[^:]+$",
       firth_pat = "^Rx[^:]+$"),
  list(label = "CRP",
       std_pat = "^crp_num$",
       firth_pat = "^crp_num$"),
  list(label = "TMB/BRAF",
       std_pat = "^tmb_braf_num$",
       firth_pat = "^tmb_braf_num$"),
  list(label = "Age (per year)",
       std_pat = "^Age$",
       firth_pat = "^Age$"),
  list(label = "Sex (male vs female)",
       std_pat = "^sex[^:]*$",
       firth_pat = "^sex[^:]*$")
)

std_firth_comparison_os <- build_std_firth_comparison(
  std_results_os, results_os, primary_std_firth_row_specs
)
std_firth_comparison_pfs <- build_std_firth_comparison(
  std_results_pfs, results_pfs, primary_std_firth_row_specs
)

# Convenience scalars for inline references in narrative.
# coxphf$prob (carried as P_Value) is the per-coefficient PLRT p-value.
get_pvalue_by_term <- function(results_df, pattern) {
  if (is.null(results_df)) return(NA_real_)
  idx <- grep(pattern, results_df$Term)
  if (length(idx) == 0) return(NA_real_)
  results_df$P_Value[idx[1]]
}

p_crp_os  <- get_pvalue_by_term(results_os,  "crp_num.*Rx|Rx.*crp_num")
p_tmb_os  <- get_pvalue_by_term(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
p_crp_pfs <- get_pvalue_by_term(results_pfs, "crp_num.*Rx|Rx.*crp_num")
p_tmb_pfs <- get_pvalue_by_term(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
```

## Standard Cox vs Firth

The standard Cox model is the unpenalized maximum-likelihood reference. Divergence between standard Cox and Firth estimates flags small-sample or near-separation instability that Firth corrects.

```{r table-std-firth-os}
render_std_firth_comparison_table(
  std_firth_comparison_os,
  caption = "Unified Model - Overall Survival: Standard Cox vs Firth",
  first_group_label = "Treatment x Biomarker Interactions",
  first_group_end = 2,
  second_group_label = "Main Effects and Covariates"
)
```

```{r table-std-firth-pfs}
render_std_firth_comparison_table(
  std_firth_comparison_pfs,
  caption = "Unified Model - Progression-Free Survival: Standard Cox vs Firth",
  first_group_label = "Treatment x Biomarker Interactions",
  first_group_end = 2,
  second_group_label = "Main Effects and Covariates"
)
```

## Unified Model Results

The unified DAG-informed model includes CRP (week 4, before the first nivolumab dose) and TMB/BRAF (baseline) as pre-immunotherapy biomarkers with their treatment interactions, adjusted for Age and Sex.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx`

### Overall Survival

```{r table-os}
if (!is.null(results_os)) {
  display_os <- results_os %>%
    mutate(
      Term   = term_label(Term),
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Unified Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interactions", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 3, nrow(display_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-pfs}
if (!is.null(results_pfs)) {
  display_pfs <- results_pfs %>%
    mutate(
      Term   = term_label(Term),
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Unified Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interactions", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 3, nrow(display_pfs), bold = TRUE)
}
```

\newpage

## Forest Plot

```{r forest-plot, fig.height=4, fig.width=8}
hr_crp_os  <- get_interaction_hr(results_os,  "crp_num.*Rx|Rx.*crp_num")
hr_tmb_os  <- get_interaction_hr(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
hr_crp_pfs <- get_interaction_hr(results_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_tmb_pfs <- get_interaction_hr(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

forest_data <- data.frame(
  Biomarker = rep(c("CRP", "TMB/BRAF"), 2),
  Outcome   = rep(c("Overall Survival", "Progression-Free Survival"), each = 2),
  HR        = c(hr_crp_os$HR,  hr_tmb_os$HR,  hr_crp_pfs$HR,  hr_tmb_pfs$HR),
  CI_Lower  = c(hr_crp_os$CI_Lower,  hr_tmb_os$CI_Lower,  hr_crp_pfs$CI_Lower,  hr_tmb_pfs$CI_Lower),
  CI_Upper  = c(hr_crp_os$CI_Upper,  hr_tmb_os$CI_Upper,  hr_crp_pfs$CI_Upper,  hr_tmb_pfs$CI_Upper)
)
forest_data <- forest_data[complete.cases(forest_data), ]

if (nrow(forest_data) > 0) {
  ggplot(forest_data, aes(x = HR, y = Biomarker)) +
    geom_point(size = 3, color = "#0072B2") +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.15, color = "#0072B2") +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4")) +
    facet_wrap(~ Outcome) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = "Treatment x Biomarker Interaction (Unified Model)",
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(panel.grid.minor = element_blank())
}
```

**Interpretation:** HR < 1 indicates that biomarker-positive patients derive greater benefit from experimental treatment (reduced hazard of death/progression). The dashed line at HR = 1 represents no differential treatment effect.

\newpage

# Sensitivity Analysis: Ridge Regression

Ridge regression (L2-penalized Cox, alpha = 0) shrinks coefficients toward zero but does not eliminate any, providing a sensitivity check for the stability of the interaction estimates. The same unified model terms are used, entered through an explicit design matrix in which the CRP x Rx and TMB/BRAF x Rx product terms are built before fitting, so each ridge interaction coefficient is the single treatment-by-biomarker contrast that the Firth model estimates (issue #153). Only the biomarker main effects (CRP and TMB/BRAF) are penalized; Age, sex, Rx and the two interaction terms carry a penalty factor of zero. The penalty lambda is chosen by 10-fold cross-validation of the partial-likelihood deviance (`glmnet::cv.glmnet`, `lambda.min`), with fold assignment seeded for reproducibility.

```{r ridge-regression, include=FALSE}
# =============================================================================
# RIDGE REGRESSION SENSITIVITY ANALYSIS (unified model), glmnet with CV lambda
#
# Why an explicit design matrix (issue #153): survival::ridge() with a factor Rx
# and `crp_num:Rx` in the formula codes the interaction for BOTH arm levels
# (RxControl:crp_num and RxExperimental:crp_num), i.e. the CRP slope within
# each arm rather than the CRP x Rx contrast. Building crp_x_rx = crp * Rx_num
# beforehand gives the same single interaction coefficient as the Firth model.
#
# Penalty design: L2 penalty on the biomarker main effects only (penalty
# factor 1 for crp and tmb_braf, 0 for Age, sex, Rx, and both interactions).
# Lambda: 10-fold CV of the Cox partial-likelihood deviance, lambda.min.
# glmnet reports no standard errors, so the ridge estimates are point estimates.
# =============================================================================

ridge_design <- function(df) {
  cbind(
    Age           = df$Age,
    sex_male      = as.numeric(df$sex == SEX_MALE_LEVEL),
    Rx            = df$Rx_num,
    crp           = df$crp_num,
    tmb_braf      = df$tmb_braf_num,
    crp_x_rx      = df$crp_num * df$Rx_num,
    tmb_braf_x_rx = df$tmb_braf_num * df$Rx_num
  )
}
ridge_penalty_factor <- c(Age = 0, sex_male = 0, Rx = 0, crp = 1, tmb_braf = 1,
                          crp_x_rx = 0, tmb_braf_x_rx = 0)
RIDGE_NFOLDS <- 10

fit_ridge_cv <- function(time, event, X, penalty_factor, seed = analysis_seed,
                         nfolds = RIDGE_NFOLDS) {
  stopifnot(identical(colnames(X), names(penalty_factor)))
  y <- survival::Surv(time, event)
  set.seed(seed)
  tryCatch({
    cvfit <- glmnet::cv.glmnet(
      x = X, y = y, family = "cox", alpha = 0,
      penalty.factor = unname(penalty_factor),
      nfolds = nfolds, standardize = TRUE
    )
    beta <- as.matrix(coef(cvfit, s = "lambda.min"))[, 1]
    list(
      cvfit = cvfit,
      lambda_min = cvfit$lambda.min,
      lambda_1se = cvfit$lambda.1se,
      coefs = data.frame(Term = names(beta), HR = exp(beta), SE = NA_real_,
                         stringsAsFactors = FALSE)
    )
  }, error = function(e) {
    warning("glmnet ridge fit failed: ", conditionMessage(e))
    NULL
  })
}

X_primary <- ridge_design(data_complete)
ridge_os_fit  <- fit_ridge_cv(data_complete$OSwk,  data_complete$Death,
                              X_primary, ridge_penalty_factor)
ridge_pfs_fit <- fit_ridge_cv(data_complete$PFSwk, data_complete$Progression,
                              X_primary, ridge_penalty_factor)
ridge_os_ok  <- !is.null(ridge_os_fit)
ridge_pfs_ok <- !is.null(ridge_pfs_fit)

get_ridge_term <- function(fit, term) {
  if (is.null(fit)) return(list(HR = NA_real_, SE = NA_real_))
  idx <- match(term, fit$coefs$Term)
  if (is.na(idx)) return(list(HR = NA_real_, SE = NA_real_))
  list(HR = fit$coefs$HR[idx], SE = NA_real_)
}

ridge_crp_os  <- get_ridge_term(ridge_os_fit,  "crp_x_rx")
ridge_tmb_os  <- get_ridge_term(ridge_os_fit,  "tmb_braf_x_rx")
ridge_crp_pfs <- get_ridge_term(ridge_pfs_fit, "crp_x_rx")
ridge_tmb_pfs <- get_ridge_term(ridge_pfs_fit, "tmb_braf_x_rx")

fmt_lambda <- function(fit) if (is.null(fit)) "--" else sprintf("%.3f", fit$lambda_min)
ridge_lambda_os  <- fmt_lambda(ridge_os_fit)
ridge_lambda_pfs <- fmt_lambda(ridge_pfs_fit)

# Qualitative label for the Firth -> ridge shift, used in the narrative so the
# wording follows the numbers (a >= 1.5-fold change in HR is called substantial).
shift_word <- function(firth_hr, ridge_hr, threshold = 1.5) {
  if (is.na(firth_hr) || is.na(ridge_hr)) return("cannot be assessed")
  ratio <- exp(abs(log(ridge_hr) - log(firth_hr)))
  if (ratio >= threshold) "changes substantially" else "changes little"
}
```

```{r table-ridge-os}
format_ridge_hr <- function(hr, se) {
  if (is.na(hr)) return("--")
  if (is.na(se)) sprintf("%.2f", hr) else sprintf("%.2f (SE: %.2f)", hr, se)
}

data.frame(
  Interaction = c("CRP x Rx", "TMB/BRAF x Rx"),
  Firth = c(
    format_hr_ci(hr_crp_os$HR, hr_crp_os$CI_Lower, hr_crp_os$CI_Upper),
    format_hr_ci(hr_tmb_os$HR, hr_tmb_os$CI_Lower, hr_tmb_os$CI_Upper)
  ),
  Ridge = c(
    format_ridge_hr(ridge_crp_os$HR, ridge_crp_os$SE),
    format_ridge_hr(ridge_tmb_os$HR, ridge_tmb_os$SE)
  )
) %>%
  kable(col.names = c("Interaction", "Firth (95% CI)", "Ridge (point est.)"),
        caption = "Overall Survival: Firth vs Ridge Regression",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = paste0("Ridge: glmnet L2 penalty (alpha = 0) on the CRP and TMB/BRAF main effects only; ",
                            "interaction product terms built before fitting; lambda by ", RIDGE_NFOLDS,
                            "-fold CV (lambda.min = ", ridge_lambda_os, "). glmnet gives no standard errors. ",
                            "A substantial shift vs Firth = estimate sensitive to regularization."),
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

```{r table-ridge-pfs}
data.frame(
  Interaction = c("CRP x Rx", "TMB/BRAF x Rx"),
  Firth = c(
    format_hr_ci(hr_crp_pfs$HR, hr_crp_pfs$CI_Lower, hr_crp_pfs$CI_Upper),
    format_hr_ci(hr_tmb_pfs$HR, hr_tmb_pfs$CI_Lower, hr_tmb_pfs$CI_Upper)
  ),
  Ridge = c(
    format_ridge_hr(ridge_crp_pfs$HR, ridge_crp_pfs$SE),
    format_ridge_hr(ridge_tmb_pfs$HR, ridge_tmb_pfs$SE)
  )
) %>%
  kable(col.names = c("Interaction", "Firth (95% CI)", "Ridge (point est.)"),
        caption = "Progression-Free Survival: Firth vs Ridge Regression",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = paste0("Ridge: glmnet L2 penalty (alpha = 0) on the CRP and TMB/BRAF main effects only; ",
                            "interaction product terms built before fitting; lambda by ", RIDGE_NFOLDS,
                            "-fold CV (lambda.min = ", ridge_lambda_pfs, "). glmnet gives no standard errors."),
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

**Interpretation:** Firth's method maximizes a penalized likelihood whose penalty reduces the small-sample bias of the maximum-likelihood estimate; the resulting estimate is bias-reduced, not unbiased. Ridge applies L2 shrinkage to the biomarker main effects (HR toward 1.0) with the penalty strength chosen by cross-validation; the interaction terms are unpenalized, so any movement in them reflects redistribution of the shrunken main-effect signal. Comparing the two methods reveals estimate stability: if Firth and Ridge agree closely, the estimate is robust; if the interaction moves substantially under ridge, the effect is sensitive to how the biomarker main effects are estimated in this sample.

\newpage

## PFS Endpoint Sensitivity: Death-Censoring Rule

```{r pfs-endpoint-sensitivity, include=FALSE}
pfs_specs <- list(
  primary = list(window = pfs_death_window_weeks, anchor = pfs_last_assessment),
  all_deaths = list(window = Inf, anchor = "TTPwk"),
  anchor_alt = list(window = 16, anchor = "LastEvalwk"),
  window8 = list(window = 8, anchor = "TTPwk"),
  window24 = list(window = 24, anchor = "TTPwk")
)
pfs_sens_rows <- lapply(names(pfs_specs), function(id) {
  spec <- pfs_specs[[id]]
  df <- derive_pfs_endpoint(data, spec$window, spec$anchor, verbose = FALSE)
  df <- df[complete.cases(df[, c("Age", "sex", "Rx", "crp", "tmb_braf",
                                "OSwk", "Death", "PFSwk", "Progression")]), ]
  stopifnot(setequal(df$ID, data_complete$ID))
  df$crp_num <- as.numeric(as.character(df$crp))
  df$tmb_braf_num <- as.numeric(as.character(df$tmb_braf))
  m <- fit_firth_cox(formula_pfs, df, paste("PFS endpoint", id))
  if (id == "primary") {
    stopifnot(isTRUE(all.equal(m$coefficients, model_pfs$coefficients, tolerance = 1e-10)),
              isTRUE(all.equal(m$ci.lower, model_pfs$ci.lower, tolerance = 1e-10)),
              isTRUE(all.equal(m$ci.upper, model_pfs$ci.upper, tolerance = 1e-10)),
              isTRUE(all.equal(m$prob, model_pfs$prob, tolerance = 1e-10)))
  } else {
    # The primary rule is the primary PFS fit (checked above); register the
    # alternative rules only.
    register_firth(sprintf("PFS rule: %s, %s",
                           if (is.infinite(spec$window)) "all deaths" else
                             sprintf("%g-wk window", spec$window),
                           spec$anchor), m)
  }
  res <- extract_coxphf_results(m)
  crp <- get_interaction_hr(res, "crp_num.*Rx|Rx.*crp_num")
  tmb <- get_interaction_hr(res, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
  km <- summary(survfit(Surv(PFSwk, Progression) ~ Rx, data = df))$table
  data.frame(Rule = id, Window = spec$window, Anchor = spec$anchor,
    Events = sum(df$Progression),
    Deaths_censored = sum(df$PFS_rule == "death_censored_at_assessment"),
    CRP_HR = format_hr_ci(crp$HR, crp$CI_Lower, crp$CI_Upper),
    CRP_p = format_pvalue(get_pvalue_by_term(res, "crp_num.*Rx|Rx.*crp_num")),
    TMB_HR = format_hr_ci(tmb$HR, tmb$CI_Lower, tmb$CI_Upper),
    TMB_p = format_pvalue(get_pvalue_by_term(res, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")),
    KM_control = unname(km[1, "median"]), KM_experimental = unname(km[2, "median"]))
})
pfs_sensitivity <- do.call(rbind, pfs_sens_rows)
pfs_sens_crp <- setNames(pfs_sensitivity$CRP_HR, pfs_sensitivity$Rule)
pfs_sens_events <- setNames(pfs_sensitivity$Events, pfs_sensitivity$Rule)
```

```{r table-pfs-endpoint-sensitivity}
pfs_sensitivity %>%
  kable(col.names = c("Rule", "Window (wk)", "Anchor", "PFS events", "Deaths censored",
                      "CRP x Rx HR (95% CI)", "PLRT p", "TMB/BRAF x Rx HR (95% CI)",
                      "PLRT p", "KM control (wk)", "KM experimental (wk)"),
        digits = 1, booktabs = TRUE, format = report_table_format(),
        caption = "PFS sensitivity to the death window and last-assessment proxy, on the same complete-case cohort") %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 8) %>%
  tbl_footnote(general = "A death without recorded progression is an event if the gap from the assessment is at most the window; otherwise censor at that assessment. Inf reproduces the pre-181 rule, an upper bound on observed PFS follow-up. Recorded progression times are unchanged. KM values are median PFS by randomized arm. TTPwk is Days until progression; LastEvalwk is Days until last evaluation. Assessment-date provenance remains subject to data-provider reconciliation.", threeparttable = TRUE)
```

The primary rule gives `r pfs_sens_events["primary"]` PFS events and CRP x Rx HR `r pfs_sens_crp["primary"]`; counting all deaths gives `r pfs_sens_events["all_deaths"]` events and HR `r pfs_sens_crp["all_deaths"]`. Using the alternative assessment date gives HR `r pfs_sens_crp["anchor_alt"]`. These analyses change endpoint ascertainment while holding the patient cohort and model formula fixed.

# Exploratory: TLR as a Predictive Biomarker (Responder Analysis)

This section presents an **exploratory responder analysis** that includes target lesion reduction (TLR) as an effect modifier in a Cox model with the same structural form as the primary analysis. Because TLR is measured post-randomization (at the first on-treatment CT scan), this is not a treatment-selection analysis: TLR status is itself influenced by treatment, and the resulting TLR x Rx interaction is informative only as a hypothesis-generating, responder-stratified contrast. It cannot be used to guide the decision to add immunotherapy, which is made before TLR is observed. The primary causal-DAG-informed analysis remains the inferential anchor for predictive biomarker claims.

The model adjusts for the pre-immunotherapy biomarkers **CRP** and **TMB/BRAF** as prognostic main effects (their treatment interactions belong to the primary analysis and are not re-estimated here). In the ridge sensitivity model, CRP and TMB/BRAF remain **unpenalized** (well-established prognostic adjustment covariates), while the **TLR main effect and TLR x Rx interaction are penalized**. These are the post-randomization terms whose stability we want to stress-test against the small effective sample size and the coupling of TLR and progression, which are read from the same first on-treatment scan.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx`

```{r tlr-descriptive, include=FALSE}
# Descriptive TLR statistics by treatment arm (TLR-complete subset)
tlr_by_arm <- data_tlr %>%
  group_by(Rx) %>%
  summarise(
    n = n(),
    n_tlr_pos = sum(tlr_num),
    pct_tlr_pos = round(100 * mean(tlr_num), 1)
  ) %>%
  mutate(Arm = ifelse(Rx == levels(Rx)[1], "Control (FLOX)", "Experimental (FLOX/nivo)"))
```

## Descriptive Context

### TLR Prevalence by Treatment Arm

```{r table-tlr-arm}
tlr_by_arm %>%
  select(Arm, n, n_tlr_pos, pct_tlr_pos) %>%
  kable(col.names = c("Treatment Arm", "N", "TLR-positive", "%"),
        caption = "TLR Prevalence by Treatment Arm (Descriptive)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = "TLR = target lesion reduction at the first on-treatment CT (post-treatment; definition in the Overview).",
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

### Kaplan-Meier Curves Stratified by TLR

```{r km-tlr, fig.height=5, fig.width=10}
km_os_tlr  <- survfit(Surv(OSwk, Death)       ~ tlr_num, data = data_tlr)
km_pfs_tlr <- survfit(Surv(PFSwk, Progression) ~ tlr_num, data = data_tlr)

p_os <- ggsurvplot(
  km_os_tlr, data = data_tlr,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Overall Survival by TLR status",
  xlab = "Time (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

p_pfs <- ggsurvplot(
  km_pfs_tlr, data = data_tlr,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Progression-Free Survival by TLR status",
  xlab = "Time (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

gridExtra::grid.arrange(p_os, p_pfs, ncol = 2)
```

**Note:** These curves are purely descriptive and stratify by a post-treatment response variable. The observed difference in survival by TLR status reflects treatment response, not a pre-treatment patient characteristic.

\newpage

```{r fit-tlr-firth, include=FALSE}
# =============================================================================
# TLR RESPONDER-ANALYSIS FIRTH-COX MODELS
# Formula: Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx
# CRP and TMB/BRAF enter as main-effect prognostic adjustments only.
# =============================================================================

formula_tlr_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                       tlr_num + tlr_num:Rx
formula_tlr_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                              tlr_num + tlr_num:Rx

# TLR-complete subset (n = n_tlr_total): TLR is undefined for the patients who
# left the study before the first on-treatment CT scan (see tlr_missing).
std_tlr_os  <- coxph(formula_tlr_os,  data = data_tlr)
std_tlr_pfs <- coxph(formula_tlr_pfs, data = data_tlr)

model_tlr_os  <- fit_firth_cox(formula_tlr_os,  data_tlr, "TLR OS")
model_tlr_pfs <- fit_firth_cox(formula_tlr_pfs, data_tlr, "TLR PFS")
register_firth("TLR responder, OS", model_tlr_os)
register_firth("TLR responder, PFS", model_tlr_pfs)

results_tlr_os  <- extract_coxphf_results(model_tlr_os)
results_tlr_pfs <- extract_coxphf_results(model_tlr_pfs)

std_results_tlr_os  <- extract_coxph_results(std_tlr_os)
std_results_tlr_pfs <- extract_coxph_results(std_tlr_pfs)

tlr_std_firth_row_specs <- list(
  list(label = "TLR x Rx",
       std_pat = "tlr_num.*Rx|Rx.*tlr_num",
       firth_pat = "tlr_num.*Rx|Rx.*tlr_num"),
  list(label = "TLR (main effect)",
       std_pat = "^tlr_num$",
       firth_pat = "^tlr_num$"),
  list(label = "Rx (experimental vs control)",
       std_pat = "^Rx[^:]+$",
       firth_pat = "^Rx[^:]+$"),
  list(label = "CRP",
       std_pat = "^crp_num$",
       firth_pat = "^crp_num$"),
  list(label = "TMB/BRAF",
       std_pat = "^tmb_braf_num$",
       firth_pat = "^tmb_braf_num$"),
  list(label = "Age (per year)",
       std_pat = "^Age$",
       firth_pat = "^Age$"),
  list(label = "Sex (male vs female)",
       std_pat = "^sex[^:]*$",
       firth_pat = "^sex[^:]*$")
)

std_firth_comparison_tlr_os <- build_std_firth_comparison(
  std_results_tlr_os, results_tlr_os, tlr_std_firth_row_specs
)
std_firth_comparison_tlr_pfs <- build_std_firth_comparison(
  std_results_tlr_pfs, results_tlr_pfs, tlr_std_firth_row_specs
)

# PLRT p-values for the TLR x Rx interaction (for narrative)
p_tlr_os  <- get_pvalue_by_term(results_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
p_tlr_pfs <- get_pvalue_by_term(results_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")
```

## Standard Cox vs Firth

The standard Cox model is the unpenalized maximum-likelihood reference. Divergence between standard Cox and Firth estimates flags small-sample or near-separation instability that Firth corrects.

```{r table-tlr-std-firth-os}
render_std_firth_comparison_table(
  std_firth_comparison_tlr_os,
  caption = "TLR Responder Model - Overall Survival: Standard Cox vs Firth",
  first_group_label = "TLR Terms",
  first_group_end = 2,
  second_group_label = "Adjustment Covariates"
)
```

```{r table-tlr-std-firth-pfs}
render_std_firth_comparison_table(
  std_firth_comparison_tlr_pfs,
  caption = "TLR Responder Model - Progression-Free Survival: Standard Cox vs Firth",
  first_group_label = "TLR Terms",
  first_group_end = 2,
  second_group_label = "Adjustment Covariates"
)
```

## Firth-Corrected Cox Model

### Overall Survival

```{r table-tlr-firth-os}
if (!is.null(results_tlr_os)) {
  display_tlr_os <- results_tlr_os %>%
    mutate(
      Term   = term_label(Term),
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "TLR Responder Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_tlr_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-tlr-firth-pfs}
if (!is.null(results_tlr_pfs)) {
  display_tlr_pfs <- results_tlr_pfs %>%
    mutate(
      Term   = term_label(Term),
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "TLR Responder Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_tlr_pfs), bold = TRUE)
}
```

\newpage

## Ridge Sensitivity Analysis (TLR Terms Penalized)

Ridge regression is applied here with a targeted penalty: only the TLR main effect and the TLR x Rx interaction are L2-shrunk. CRP, TMB/BRAF, Age, sex, and Rx are estimated without penalty, since they enter the model as adjustment covariates whose effects are not the inferential target.

```{r tlr-ridge, include=FALSE}
# =============================================================================
# RIDGE SENSITIVITY: penalize TLR main effect + TLR x Rx interaction
# CRP and TMB/BRAF main effects remain unpenalized (prognostic adjustment)
# Rx_num is defined earlier (0 = Control, 1 = Experimental).
# survival::ridge() takes raw variables, so pre-construct the interaction.
# =============================================================================

data_tlr$tlr_x_rx <- data_tlr$tlr_num * data_tlr$Rx_num

ridge_tlr_os_ok <- TRUE
tryCatch({
  ridge_tlr_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
      ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
    data = data_tlr
  )
}, error = function(e) { ridge_tlr_os_ok <<- FALSE; ridge_tlr_os <<- NULL })

ridge_tlr_pfs_ok <- TRUE
tryCatch({
  ridge_tlr_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
      ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
    data = data_tlr
  )
}, error = function(e) { ridge_tlr_pfs_ok <<- FALSE; ridge_tlr_pfs <<- NULL })

ridge_tlr_os_int  <- if (!is.null(ridge_tlr_os))  extract_ridge_interaction(ridge_tlr_os,  "tlr_x_rx\\)")  else list(HR = NA, SE = NA)
ridge_tlr_pfs_int <- if (!is.null(ridge_tlr_pfs)) extract_ridge_interaction(ridge_tlr_pfs, "tlr_x_rx\\)") else list(HR = NA, SE = NA)

# Firth TLR x Rx HRs for the in-text inline summary
tlr_firth_os  <- get_interaction_hr(results_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
tlr_firth_pfs <- get_interaction_hr(results_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")

# Extract all ridge coefficients into a tidy data frame
extract_all_ridge_coefs <- function(model) {
  if (is.null(model)) return(NULL)
  ct <- summary(model)$coefficients
  data.frame(
    Term = rownames(ct),
    HR = exp(ct[, "coef"]),
    SE = ct[, "se(coef)"],
    stringsAsFactors = FALSE
  )
}

ridge_tlr_os_coefs  <- extract_all_ridge_coefs(ridge_tlr_os)
ridge_tlr_pfs_coefs <- extract_all_ridge_coefs(ridge_tlr_pfs)

# Build the full-coefficient Firth vs Ridge comparison.
# Firth coefficient names: Age, sex<level>, Rx<level>, crp_num, tmb_braf_num,
#   tlr_num, Rx<level>:tlr_num
# Ridge coefficient names: Age, sex<level>, Rx<level>, crp_num, tmb_braf_num,
#   ridge(tlr_num), ridge(tlr_x_rx)
# Ridge patterns use the closing ")" to disambiguate the TLR main effect
# from the TLR x Rx interaction. The Rx pattern excludes interaction terms
# (issue #182: "^Rx[A-Za-z]" also matched "RxExperimental arm:tlr_num", which
# extract_coxphf_results() sorts first), and every pattern must match exactly
# one term (match_one_term()).
build_tlr_comparison <- function(firth_results, ridge_coefs) {
  row_specs <- list(
    list(label = "TLR x Rx",
         firth_pat = "tlr_num.*Rx|Rx.*tlr_num",
         ridge_pat = "tlr_x_rx\\)"),
    list(label = "TLR (main effect)",
         firth_pat = "^tlr_num$",
         ridge_pat = "tlr_num\\)"),
    list(label = "Age (per year)",
         firth_pat = "^Age$",
         ridge_pat = "^Age$"),
    list(label = "Sex (male vs female)",
         firth_pat = "^sex[^:]*$",
         ridge_pat = "^sex[^:]*$"),
    list(label = "Rx (experimental vs control)",
         firth_pat = "^Rx[^:]+$",
         ridge_pat = "^Rx[^:]+$"),
    list(label = "CRP",
         firth_pat = "^crp_num$",
         ridge_pat = "^crp_num$"),
    list(label = "TMB/BRAF",
         firth_pat = "^tmb_braf_num$",
         ridge_pat = "^tmb_braf_num$")
  )

  do.call(rbind, lapply(row_specs, function(rs) {
    firth_cell <- "--"
    ridge_cell <- "--"

    if (!is.null(firth_results)) {
      f_idx <- match_one_term(rs$firth_pat, firth_results$Term, "Firth vs ridge table (Firth)")
      firth_cell <- format_hr_ci(
        firth_results$HR[f_idx],
        firth_results$CI_Lower[f_idx],
        firth_results$CI_Upper[f_idx]
      )
    }

    if (!is.null(ridge_coefs)) {
      r_idx <- match_one_term(rs$ridge_pat, ridge_coefs$Term, "Firth vs ridge table (ridge)")
      ridge_cell <- format_ridge_hr(
        ridge_coefs$HR[r_idx],
        ridge_coefs$SE[r_idx]
      )
    }

    data.frame(Term = rs$label, Firth = firth_cell, Ridge = ridge_cell,
               stringsAsFactors = FALSE)
  }))
}

tlr_comparison_os  <- build_tlr_comparison(results_tlr_os,  ridge_tlr_os_coefs)
tlr_comparison_pfs <- build_tlr_comparison(results_tlr_pfs, ridge_tlr_pfs_coefs)
```

```{r table-tlr-ridge-os}
tlr_comparison_os %>%
  kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
        caption = "TLR Responder Model - Overall Survival: Firth vs Ridge, all coefficients",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
  tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(tlr_comparison_os), bold = TRUE) %>%
  tbl_footnote(general = "Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized. survival::ridge() does not produce confidence intervals; standard errors are shown for reference.",
           footnote_as_chunk = TRUE)
```

```{r table-tlr-ridge-pfs}
tlr_comparison_pfs %>%
  kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
        caption = "TLR Responder Model - Progression-Free Survival: Firth vs Ridge, all coefficients",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
  tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(tlr_comparison_pfs), bold = TRUE) %>%
  tbl_footnote(general = "Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized. survival::ridge() does not produce confidence intervals; standard errors are shown for reference.",
           footnote_as_chunk = TRUE)
```

**Interpretation:** The Firth HR is the penalized-likelihood estimate of the TLR x Rx interaction; Firth's penalty reduces its small-sample bias but does not make it unbiased. The ridge HR applies L2 shrinkage targeted at the TLR terms; if the ridge estimate is substantially closer to HR = 1.0 than the Firth estimate, the responder-stratified interaction is sensitive to regularization, consistent with a small-sample, partly tautological signal. Findings here are exploratory and should not be used for treatment selection, since TLR is not measurable before nivolumab starts. They may motivate landmark or formal causal-mediation analyses in future work.

\newpage

# Landmark Analysis: TLR at Week 9

```{r tlr-landmark-cohort, include=FALSE}
# =============================================================================
# LANDMARK COHORT CONSTRUCTION (issues #155, #184)
# The base cohort (tlr_landmark_base_cohort(), data_tlr above) and all three
# landmark definitions come from tlr_landmark.R and are shared with
# clin_effect_figure1.qmd and the DAG association tests, so the cohorts
# themselves, not only the landmark rule, are identical across the three.
# Endpoint-specific at-risk sets, strictly after the landmark; clock reset
# to the landmark:
#   OS  cohort: OSwk  > landmark; analysis time OSwk_lm  = OSwk  - landmark
#   PFS cohort: PFSwk > landmark; analysis time PFSwk_lm = PFSwk - landmark
# Primary: fixed week 9. Sensitivity: per-patient first-scan date (CT1wk) and
# fixed week 12. The helper also adds the ridge product term tlr_x_rx.
# The chunk runs before the section text, which quotes its counts.
# =============================================================================
LANDMARK_WK <- tlr_landmark_spec("week9")$week

# Landmark cohorts are built from the shared base cohort data_tlr (also the
# responder analysis cohort), so attrition is measured against n_tlr_total.
lm_all  <- build_all_tlr_landmark_cohorts(data_tlr)
lm_main <- lm_all$week9

data_lm_os  <- lm_main$os
data_lm_pfs <- lm_main$pfs

# Attrition / sample-size accounting
lm_attrition <- lm_main$attrition

# Characterize the PFS exclusions and the two departures of a fixed week-9
# landmark from the "reached the scan" ideal. Because progression and TLR are
# read from the SAME first on-treatment scan, patients who progress at that
# scan are TLR-negative by construction; a fixed week-9 cut removes only those
# whose scan fell before week 9 and keeps the rest with landmark times under
# one week, and it keeps patients whose TLR was read after week 9.
lm_diag             <- lm_main$diagnostics
n_pfs_excl          <- lm_diag$n_pfs_excluded
n_pfs_excl_prog     <- lm_diag$n_pfs_excl_progression_exit
n_pfs_excl_prog_tn  <- lm_diag$n_pfs_excl_progression_exit_tlr_neg
n_os_excl_death     <- lm_diag$n_os_excl_deaths
n_first_scan_prog   <- lm_diag$n_first_scan_progressors
n_first_scan_kept   <- lm_diag$n_first_scan_progressors_kept
n_scan_after_kept   <- lm_diag$n_scan_after_landmark_kept
n_scan_after_os     <- sum(data_lm_os$CT1wk > LANDMARK_WK)
scan_wk_range       <- range(data_tlr$CT1wk)

# The week-12 landmark is not after every first scan (issue #176): its
# retained first-scan progressors and after-landmark scans are computed, as
# for week 9, rather than asserted.
lm_wk12_diag <- lm_all$week12$diagnostics
n_word <- function(n, singular, plural = paste0(singular, "s")) {
  paste(n, if (n == 1) singular else plural)
}
wk12_fsp_part <- if (lm_wk12_diag$n_first_scan_progressors_kept == 0) {
  "excludes every first-scan progressor"
} else {
  sprintf("retains %s", n_word(lm_wk12_diag$n_first_scan_progressors_kept, "first-scan progressor"))
}
wk12_departure_text <- if (lm_wk12_diag$n_scan_after_landmark_kept == 0) {
  sprintf("which %s, and every retained patient's TLR was read by week 12", wk12_fsp_part)
} else {
  sprintf("which %s but still retains %s whose TLR was read after week 12, because the latest first scan was at week %.1f",
          wk12_fsp_part, n_word(lm_wk12_diag$n_scan_after_landmark_kept, "patient"),
          scan_wk_range[2])
}

# OS risk sets: the fixed landmarks leave the OS risk sets unchanged when no
# patient of the TLR-complete cohort dies or is censored by the landmark.
n_os_out_by_wk9  <- lm_all$week9$diagnostics$n_os_excluded
n_os_out_by_wk12 <- lm_all$week12$diagnostics$n_os_excluded
```

The responder analysis above treats TLR status as if it were known at baseline. It is not: TLR is measured at the first on-treatment CT scan, so a patient can only be classified TLR-positive or TLR-negative once alive at that scan. Remaining progression-free is not required: a patient whose progression is recorded at the scan is classified TLR-negative. Conditioning survival on a post-baseline response therefore induces **guarantee-time (immortal-time) bias** — TLR-classified patients are, by construction, a more favourable risk set than the full randomized population.

A **landmark analysis** addresses this bias by (i) fixing a landmark time, (ii) restricting each endpoint to the patients still at risk for it at the landmark, and (iii) measuring time **from the landmark onward**. The at-risk conditions differ by endpoint: the **OS** cohort requires only that the patient is alive and uncensored at the landmark, whereas the **PFS** cohort also requires that no progression and no PFS-counted death has occurred and that the patient was not censored at an earlier assessment. The primary landmark is **week 9**, the protocol time of the second CT (the first on-treatment response assessment): TLR compares this scan to the baseline CT, so a patient's TLR status does not exist until that scan. The actual first on-treatment scans, however, were not all at week 9: in the trial extract they fell between weeks `r sprintf("%.1f", scan_wk_range[1])` and `r sprintf("%.1f", scan_wk_range[2])` after inclusion (median `r sprintf("%.1f", median(data_tlr$CT1wk))`). A fixed week-9 landmark therefore does not guarantee that every retained patient had reached the scan, and it does not remove every patient whose progression was recorded at the first scan, so it reduces the bias rather than removing it. Both departures are counted below, and two sensitivity landmarks are reported (issue #155): a **per-patient landmark at each patient's own first-scan date**, which by construction retains no patient whose TLR is read after the landmark and, for PFS, no first-scan progressor, and a **fixed week-12 landmark**, `r wk12_departure_text`. This section **complements** the responder analysis above (which is retained for comparison); it does not replace it.

The base cohort and the three landmark definitions live in `R/tlr_landmark.R` and are shared with Figure 1 of the clinical effectiveness paper and the DAG association tests (issue #184). All three start from the same `r n_tlr_total` TLR-classified patients of the `r n_total`-patient complete-case cohort (`tlr_landmark_base_cohort()`) and apply the same rule: a patient enters an endpoint-specific cohort only if the endpoint time is strictly after the landmark. They therefore analyse the same landmark cohorts. Because the small trial loses patients with events or censoring before the landmark, the cohort sizes and event counts are reported explicitly, and all model fits are wrapped so a too-small cohort degrades gracefully rather than aborting the render.

## Landmark Cohort and Attrition

```{r table-lm-attrition}
lm_attrition %>%
  kable(col.names = c("Endpoint", "TLR-complete N",
                      "At risk after week 9", "Excluded by week 9",
                      "Events after week 9"),
        caption = "Week-9 landmark cohort: attrition and remaining events",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_footnote(general = "OS cohort: patients alive and uncensored after week 9. PFS cohort: patients who, by week 9, also had no recorded progression, no PFS-counted death and no censoring at an earlier assessment. Time is measured from week 9 onward.",
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Descriptive Context (Landmark Cohort)

### Characteristics of the Week-9 Landmark Cohorts by TLR Status

The two tables below describe the patients who enter the landmark analysis, overall and split by the TLR status that becomes defined at the week-9 scan. The at-risk set is endpoint-specific: the **overall-survival** cohort keeps everyone alive and uncensored at week 9, whereas the **progression-free-survival** cohort additionally drops patients who had progressed, died within the death window, or been censored by week 9. The PFS cohort is therefore smaller. Reporting both fixes the denominators for the OS and PFS models that follow and makes the composition of the two TLR groups directly comparable.

```{r lm-characteristics, include=FALSE}
# =============================================================================
# LANDMARK COHORT CHARACTERISTICS, split by TLR status.
# Two endpoint-specific at-risk sets:
#   OS  cohort (data_lm_os):  OSwk  > 9  (alive and uncensored at week 9)
#   PFS cohort (data_lm_pfs): PFSwk > 9  (also progression-free and not
#                                         censored at an earlier assessment)
# Note on sex: the source column is "Sex 0female", so sex == 0 is female.
# =============================================================================
format_n_pct <- function(count, n) {
  if (n == 0) return("--")
  sprintf("%d (%.1f%%)", count, 100 * count / n)
}

summarise_lm_cohort <- function(df) {
  n <- nrow(df)
  sex_num <- as.numeric(as.character(df$sex))
  c(
    sprintf("%d", n),
    sprintf("%.1f (%.1f)", mean(df$Age), sd(df$Age)),
    format_n_pct(sum(sex_num == 0), n),
    format_n_pct(sum(df$Rx == levels(df$Rx)[1]), n),
    format_n_pct(sum(df$Rx == levels(df$Rx)[2]), n),
    format_n_pct(sum(df$Death), n),
    format_n_pct(sum(df$Progression), n),
    format_n_pct(sum(df$crp_num), n),
    format_n_pct(sum(df$tmb_braf_num), n)
  )
}

build_lm_characteristics <- function(df) {
  data.frame(
    Characteristic = c("n", "Age, years, mean (SD)", "Female sex",
                       "Control arm (FLOX)", "Experimental arm (FLOX/nivolumab)",
                       "Deaths (OS events)", "PFS events (progression or death)",
                       "CRP-positive", "TMB/BRAF-positive"),
    All     = summarise_lm_cohort(df),
    TLR_pos = summarise_lm_cohort(df[df$tlr_num == 1, ]),
    TLR_neg = summarise_lm_cohort(df[df$tlr_num == 0, ]),
    stringsAsFactors = FALSE
  )
}

lm_characteristics_os  <- build_lm_characteristics(data_lm_os)
lm_characteristics_pfs <- build_lm_characteristics(data_lm_pfs)

render_lm_char_table <- function(char_df, caption) {
  tbl <- char_df %>%
    kable(col.names = c("Characteristic", "At-risk cohort", "TLR-positive", "TLR-negative"),
          caption = caption, booktabs = TRUE, align = c("l", "r", "r", "r"),
          format = if (knitr::is_latex_output()) "latex" else "pipe")
  if (knitr::is_latex_output()) {
    tbl %>% tbl_style(latex_options = c("hold_position"), font_size = 9)
  } else {
    tbl
  }
}
```

#### Overall-survival at-risk set (OSwk > 9)

```{r table-lm-characteristics-os}
render_lm_char_table(
  lm_characteristics_os,
  "Characteristics of the week-9 OS landmark cohort (alive at week 9), by TLR status"
)
```

`r if (n_os_out_by_wk9 == 0) sprintf("Because no patient of the TLR-complete cohort dies or is censored by week 9, the OS at-risk set coincides with that cohort (n = %d).", nrow(data_lm_os)) else sprintf("%s of the TLR-complete cohort died or were censored by week 9, leaving n = %d in the OS at-risk set.", n_word(n_os_out_by_wk9, "patient"), nrow(data_lm_os))` The `r n_tlr_missing` complete-case patients without a TLR value are outside this cohort: they `r tlr_missing_desc`.

#### Progression-free-survival at-risk set (PFSwk > 9)

```{r table-lm-characteristics-pfs}
render_lm_char_table(
  lm_characteristics_pfs,
  "Characteristics of the week-9 PFS landmark cohort (alive and progression-free at week 9), by TLR status"
)
```

The PFS at-risk set drops the `r nrow(data_lm_os) - nrow(data_lm_pfs)` patient(s) who had already progressed, died, or were censored by week 9, leaving n = `r nrow(data_lm_pfs)`.

*Definitions:* percentages are column percentages; the "Deaths" and "PFS events" rows count events over the whole follow-up, not only after the landmark. CRP-positive = CRP < 5 mg/L; TMB/BRAF-positive = TMB >= 9 mut/Mb or BRAF mutation; TLR-positive = target lesion reduction, as defined in the Overview.

**Note:** In both cohorts the two TLR groups are well matched on age, sex, and TMB/BRAF status, but differ sharply on treatment arm and CRP: the TLR-positive group is enriched for control-arm patients and for CRP-positivity, while every TLR-negative patient died during follow-up. These imbalances are the descriptive counterpart of the interaction estimates below and reinforce that TLR status is realised after randomization rather than being a baseline characteristic.

### TLR Prevalence by Treatment Arm at Week 9

```{r table-lm-tlr-arm}
tlr_by_arm_lm <- data_lm_os %>%
  group_by(Rx) %>%
  summarise(
    n = n(),
    n_tlr_pos = sum(tlr_num),
    pct_tlr_pos = round(100 * mean(tlr_num), 1),
    .groups = "drop"
  ) %>%
  mutate(Arm = ifelse(Rx == levels(Rx)[1], "Control (FLOX)", "Experimental (FLOX/nivo)"))

tlr_by_arm_lm %>%
  select(Arm, n, n_tlr_pos, pct_tlr_pos) %>%
  kable(col.names = c("Treatment Arm", "N", "TLR-positive", "%"),
        caption = "TLR Prevalence by Treatment Arm, Week-9 Landmark Cohort (OS at-risk set)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = "Restricted to patients alive and uncensored at week 9. TLR = target lesion reduction (definition in the Overview).",
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

### Landmark Kaplan-Meier Curves Stratified by TLR

```{r km-lm-tlr, fig.height=5, fig.width=10}
km_os_tlr_lm  <- survfit(Surv(OSwk_lm, Death)        ~ tlr_num, data = data_lm_os)
km_pfs_tlr_lm <- survfit(Surv(PFSwk_lm, Progression) ~ tlr_num, data = data_lm_pfs)

p_os_lm <- ggsurvplot(
  km_os_tlr_lm, data = data_lm_os,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Overall Survival by TLR status (from week 9)",
  xlab = "Time since landmark (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

p_pfs_lm <- ggsurvplot(
  km_pfs_tlr_lm, data = data_lm_pfs,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Progression-Free Survival by TLR status (from week 9)",
  xlab = "Time since landmark (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

gridExtra::grid.arrange(p_os_lm, p_pfs_lm, ncol = 2)
```

**Note:** Follow-up time is measured from the week-9 landmark. All patients shown were alive and uncensored (OS) or alive, progression-free and uncensored (PFS) at the landmark. The landmark reduces, but does not remove, the guarantee-time bias of the responder-analysis curves above: `r n_word(n_scan_after_os, "patient")` in the OS cohort and `r n_scan_after_kept` in the PFS cohort had their TLR read after week 9, and the PFS cohort retains `r n_word(n_first_scan_kept, "first-scan progressor")`.

\newpage

```{r fit-lm-tlr-firth, include=FALSE}
# =============================================================================
# LANDMARK FIRTH-COX MODELS (TLR responder form, conditioned on week-9 survival)
# Formula: Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx, time reset to landmark
# Reuses tlr_std_firth_row_specs defined in the responder section above.
# =============================================================================
formula_lm_tlr_os  <- Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                             tlr_num + tlr_num:Rx
formula_lm_tlr_pfs <- Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                                    tlr_num + tlr_num:Rx

std_lm_tlr_os  <- tryCatch(coxph(formula_lm_tlr_os,  data = data_lm_os),  error = function(e) NULL)
std_lm_tlr_pfs <- tryCatch(coxph(formula_lm_tlr_pfs, data = data_lm_pfs), error = function(e) NULL)

model_lm_tlr_os  <- tryCatch(fit_firth_cox(formula_lm_tlr_os,  data_lm_os,  "Landmark TLR OS"),  error = function(e) NULL)
model_lm_tlr_pfs <- tryCatch(fit_firth_cox(formula_lm_tlr_pfs, data_lm_pfs, "Landmark TLR PFS"), error = function(e) NULL)
register_firth("Landmark week 9, OS", model_lm_tlr_os)
register_firth("Landmark week 9, PFS", model_lm_tlr_pfs)

results_lm_tlr_os  <- if (!is.null(model_lm_tlr_os))  extract_coxphf_results(model_lm_tlr_os)  else NULL
results_lm_tlr_pfs <- if (!is.null(model_lm_tlr_pfs)) extract_coxphf_results(model_lm_tlr_pfs) else NULL

std_results_lm_tlr_os  <- if (!is.null(std_lm_tlr_os))  extract_coxph_results(std_lm_tlr_os)  else NULL
std_results_lm_tlr_pfs <- if (!is.null(std_lm_tlr_pfs)) extract_coxph_results(std_lm_tlr_pfs) else NULL

std_firth_comparison_lm_tlr_os <- if (!is.null(std_results_lm_tlr_os) && !is.null(results_lm_tlr_os))
  build_std_firth_comparison(std_results_lm_tlr_os, results_lm_tlr_os, tlr_std_firth_row_specs) else NULL
std_firth_comparison_lm_tlr_pfs <- if (!is.null(std_results_lm_tlr_pfs) && !is.null(results_lm_tlr_pfs))
  build_std_firth_comparison(std_results_lm_tlr_pfs, results_lm_tlr_pfs, tlr_std_firth_row_specs) else NULL

# PLRT p-values for the landmark TLR x Rx interaction (for narrative)
p_lm_tlr_os  <- if (!is.null(results_lm_tlr_os))  get_pvalue_by_term(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num") else NA
p_lm_tlr_pfs <- if (!is.null(results_lm_tlr_pfs)) get_pvalue_by_term(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num") else NA
```

## Standard Cox vs Firth (Landmark)

```{r table-lm-tlr-std-firth-os}
if (!is.null(std_firth_comparison_lm_tlr_os)) {
  render_std_firth_comparison_table(
    std_firth_comparison_lm_tlr_os,
    caption = "Landmark (Week 9) TLR Model - Overall Survival: Standard Cox vs Firth",
    first_group_label = "TLR Terms",
    first_group_end = 2,
    second_group_label = "Adjustment Covariates"
  )
}
```

```{r table-lm-tlr-std-firth-pfs}
if (!is.null(std_firth_comparison_lm_tlr_pfs)) {
  render_std_firth_comparison_table(
    std_firth_comparison_lm_tlr_pfs,
    caption = "Landmark (Week 9) TLR Model - Progression-Free Survival: Standard Cox vs Firth",
    first_group_label = "TLR Terms",
    first_group_end = 2,
    second_group_label = "Adjustment Covariates"
  )
}
```

## Firth-Corrected Cox Model (Landmark)

### Overall Survival

```{r table-lm-tlr-firth-os}
if (!is.null(results_lm_tlr_os)) {
  display_lm_tlr_os <- results_lm_tlr_os %>%
    mutate(
      Term   = term_label(Term),
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_lm_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Landmark TLR Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_lm_tlr_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-lm-tlr-firth-pfs}
if (!is.null(results_lm_tlr_pfs)) {
  display_lm_tlr_pfs <- results_lm_tlr_pfs %>%
    mutate(
      Term   = term_label(Term),
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_lm_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Landmark TLR Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_lm_tlr_pfs), bold = TRUE)
}
```

\newpage

## Ridge Sensitivity Analysis (Landmark, TLR Terms Penalized)

Ridge regression is applied to the landmark cohorts with the same targeted penalty as the responder analysis: only the TLR main effect and the TLR x Rx interaction are L2-shrunk, while Age, sex, Rx, CRP, and TMB/BRAF remain unpenalized.

```{r lm-tlr-ridge, include=FALSE}
# Reuses build_tlr_comparison() and extract_all_ridge_coefs() defined in the
# responder ridge chunk above. Models fitted on the week-9 landmark cohorts.
ridge_lm_tlr_os <- tryCatch(
  coxph(Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
        data = data_lm_os),
  error = function(e) NULL)

ridge_lm_tlr_pfs <- tryCatch(
  coxph(Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
        data = data_lm_pfs),
  error = function(e) NULL)

ridge_lm_tlr_os_int  <- if (!is.null(ridge_lm_tlr_os))  extract_ridge_interaction(ridge_lm_tlr_os,  "tlr_x_rx\\)")  else list(HR = NA, SE = NA)
ridge_lm_tlr_pfs_int <- if (!is.null(ridge_lm_tlr_pfs)) extract_ridge_interaction(ridge_lm_tlr_pfs, "tlr_x_rx\\)") else list(HR = NA, SE = NA)

# Firth landmark TLR x Rx HRs for the in-text inline summary
lm_tlr_firth_os  <- if (!is.null(results_lm_tlr_os))  get_interaction_hr(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num") else list(HR = NA, CI_Lower = NA, CI_Upper = NA)
lm_tlr_firth_pfs <- if (!is.null(results_lm_tlr_pfs)) get_interaction_hr(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num") else list(HR = NA, CI_Lower = NA, CI_Upper = NA)

ridge_lm_tlr_os_coefs  <- extract_all_ridge_coefs(ridge_lm_tlr_os)
ridge_lm_tlr_pfs_coefs <- extract_all_ridge_coefs(ridge_lm_tlr_pfs)

lm_tlr_comparison_os  <- if (!is.null(results_lm_tlr_os))  build_tlr_comparison(results_lm_tlr_os,  ridge_lm_tlr_os_coefs)  else NULL
lm_tlr_comparison_pfs <- if (!is.null(results_lm_tlr_pfs)) build_tlr_comparison(results_lm_tlr_pfs, ridge_lm_tlr_pfs_coefs) else NULL
```

```{r table-lm-tlr-ridge-os}
if (!is.null(lm_tlr_comparison_os)) {
  lm_tlr_comparison_os %>%
    kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
          caption = "Landmark TLR Model - Overall Survival: Firth vs Ridge, all coefficients",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(lm_tlr_comparison_os), bold = TRUE) %>%
    tbl_footnote(general = "Week-9 landmark cohort. Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized.",
             footnote_as_chunk = TRUE)
}
```

```{r table-lm-tlr-ridge-pfs}
if (!is.null(lm_tlr_comparison_pfs)) {
  lm_tlr_comparison_pfs %>%
    kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
          caption = "Landmark TLR Model - Progression-Free Survival: Firth vs Ridge, all coefficients",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(lm_tlr_comparison_pfs), bold = TRUE) %>%
    tbl_footnote(general = "Week-9 landmark cohort. Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized.",
             footnote_as_chunk = TRUE)
}
```

```{r lm-firth-comparison, include=FALSE}
# Responder versus week-9 landmark Firth estimates. The text describes the
# change from the numbers rather than asserting it (issue #182).
tlr_main_resp_pfs <- get_interaction_hr(results_tlr_pfs, "^tlr_num$")
tlr_main_lm_pfs   <- get_interaction_hr(results_lm_tlr_pfs, "^tlr_num$")
fold_change <- function(a, b) exp(abs(log(b) - log(a)))
hr_ci_txt <- function(x) format_hr_ci(x$HR, x$CI_Lower, x$CI_Upper)

# OS: with no patient leaving the risk set by week 9 the landmark is a common
# shift of the time origin, and the Cox (and Firth) estimate is unchanged.
os_lm_identical <- !is.null(model_lm_tlr_os) && !is.null(model_tlr_os) &&
  isTRUE(all.equal(unname(model_lm_tlr_os$coefficients),
                   unname(model_tlr_os$coefficients), tolerance = 1e-8))
os_landmark_text <- if (os_lm_identical && n_os_out_by_wk9 == 0) {
  sprintf(paste0(
    "*Overall survival*: no patient of the TLR-complete cohort dies or is censored by week 9, ",
    "so the landmark OS cohort is the whole TLR-complete cohort and every OS risk set is the ",
    "same as in the responder analysis. A Cox model is invariant to a common shift of the time ",
    "origin when no patient leaves the risk set, so the landmark Firth TLR x Rx HR (%s) is ",
    "identical to the responder estimate (%s). The identity is a consequence of the absence of ",
    "deaths and censoring before week 9 in this cohort; it is not evidence against a ",
    "guarantee-time artefact, because the %d complete-case patients who left the study before ",
    "the first on-treatment CT are outside both analyses."),
    hr_ci_txt(lm_tlr_firth_os), hr_ci_txt(tlr_firth_os), n_tlr_missing)
} else {
  sprintf(paste0(
    "*Overall survival*: %s of the TLR-complete cohort died or were censored by week 9; the ",
    "landmark Firth TLR x Rx HR is %s against %s in the responder analysis."),
    n_word(n_os_out_by_wk9, "patient"), hr_ci_txt(lm_tlr_firth_os), hr_ci_txt(tlr_firth_os))
}

# PFS: TLR main effect and TLR x Rx interaction, responder versus landmark.
tlr_main_fold <- fold_change(tlr_main_resp_pfs$HR, tlr_main_lm_pfs$HR)
tlr_main_change_word <- if (is.na(tlr_main_fold)) "not estimable" else
  if (tlr_main_fold < 1.25) "essentially unchanged" else "changed"
int_fold <- fold_change(tlr_firth_pfs$HR, lm_tlr_firth_pfs$HR)
int_toward_1 <- abs(log(lm_tlr_firth_pfs$HR)) < abs(log(tlr_firth_pfs$HR))
int_within_ci <- isTRUE(lm_tlr_firth_pfs$HR >= tlr_firth_pfs$CI_Lower &&
                          lm_tlr_firth_pfs$HR <= tlr_firth_pfs$CI_Upper)
pfs_int_move_text <- if (is.na(int_fold)) "cannot be compared" else sprintf(
  "moves %s %s, from %s (responder) to %s (week-9 landmark)%s",
  if (int_fold < 1.5) "slightly" else "substantially",
  if (isTRUE(int_toward_1)) "toward 1" else "away from 1",
  hr_ci_txt(tlr_firth_pfs), hr_ci_txt(lm_tlr_firth_pfs),
  if (int_within_ci) ", within the responder confidence interval" else "")
tlr_coupling_text <- if (tlr_main_change_word == "essentially unchanged") {
  paste0("Excluding these early events therefore does not weaken the TLR-PFS association, ",
         "and the landmark results do not indicate that the responder association is driven ",
         "by the coupling of TLR-negativity and progression at the same scan.")
} else {
  paste0("Excluding these early events changes the TLR main effect, so part of the ",
         "responder association may reflect the coupling of TLR-negativity and progression ",
         "at the same scan.")
}
sens_remove_all_fsp <- lm_all$scan$diagnostics$n_first_scan_progressors_kept == 0 &&
  lm_wk12_diag$n_first_scan_progressors_kept == 0

# Short OS statement for the Discussion and Summary (issue #182).
os_lm_summary_text <- if (os_lm_identical && n_os_out_by_wk9 == 0) {
  sprintf(paste0(
    "For **OS**, no patient of the TLR-complete cohort dies or is censored by week 9, so the ",
    "landmark TLR x Rx HR (%s) equals the responder estimate by construction; this identity ",
    "reflects the absence of early deaths and censoring in that cohort and does not test for a ",
    "guarantee-time artefact."), hr_ci_txt(lm_tlr_firth_os))
} else {
  sprintf("For **OS**, %s excluded by week 9 and the landmark TLR x Rx HR is %s against %s in the responder analysis.",
          n_word(n_os_out_by_wk9, "patient is", "patients are"),
          hr_ci_txt(lm_tlr_firth_os), hr_ci_txt(tlr_firth_os))
}
```

**Interpretation:** The two endpoints behave differently under the landmark.

`r os_landmark_text`

*Progression-free survival*: `r lm_attrition$N_excluded[2]` patients are excluded, of whom `r n_pfs_excl_prog` progressed (`r n_pfs_excl_prog_tn` of them **TLR-negative**); `r lm_diag$n_pfs_excl_death_pf` died progression-free within the death window and `r lm_diag$n_pfs_excl_censored` were censored at a last assessment on or before week 9. Progression and TLR are read from the *same* first on-treatment scan, so a patient whose tumour grows at that scan is classified both as a progression and as TLR-negative. In total `r n_first_scan_prog` patients progressed at their first scan, all TLR-negative. The fixed week-9 cut removes only the `r n_first_scan_prog - n_first_scan_kept` whose scan fell before week 9 and **keeps `r n_first_scan_kept`** whose scan fell after it, with landmark times of `r sprintf("%.1f", lm_diag$min_pfs_lm)` to `r sprintf("%.1f", max(data_lm_pfs$PFSwk_lm[data_lm_pfs$PFSwk == data_lm_pfs$CT1wk]))` weeks; it also keeps `r n_scan_after_kept` patients whose TLR was read after week 9, so for them the landmark covariate is measured after the landmark. Under the landmark the Firth TLR main effect is `r tlr_main_change_word` (HR `r hr_ci_txt(tlr_main_resp_pfs)` responder, `r hr_ci_txt(tlr_main_lm_pfs)` week-9 landmark), and the TLR x Rx HR `r pfs_int_move_text`. `r tlr_coupling_text` The sensitivity landmarks below `r if (sens_remove_all_fsp) paste("remove all", n_first_scan_prog, "first-scan progressors") else "remove further first-scan progressors"`.

### Landmark Sensitivity: Scan-Date and Week-12 Landmarks

```{r lm-sensitivity, include=FALSE}
# Repeat the landmark Firth TLR x Rx model under each landmark definition.
# The formulas are the week-9 ones; only the cohort and the time origin change.
lm_sens_fits <- lapply(lm_all, function(lm_obj) {
  dg <- lm_obj$diagnostics
  fit_lm <- function(formula, df, label) {
    m <- tryCatch(fit_firth_cox(formula, df, label), error = function(e) NULL)
    if (is.null(m)) {
      return(list(model = NULL, hr = list(HR = NA_real_, CI_Lower = NA_real_, CI_Upper = NA_real_),
                  p = NA_real_))
    }
    r <- extract_coxphf_results(m)
    list(model = m, hr = get_interaction_hr(r, "tlr_num.*Rx|Rx.*tlr_num"),
         p = get_pvalue_by_term(r, "tlr_num.*Rx|Rx.*tlr_num"))
  }
  os_fit  <- fit_lm(formula_lm_tlr_os,  lm_obj$os,  paste("Landmark", lm_obj$spec$id, "OS"))
  pfs_fit <- fit_lm(formula_lm_tlr_pfs, lm_obj$pfs, paste("Landmark", lm_obj$spec$id, "PFS"))
  row <- data.frame(
    Landmark = lm_obj$spec$label,
    N_os = dg$n_os,
    N_pfs = dg$n_pfs,
    PFS_events = sum(lm_obj$pfs$Progression),
    Censored_before = dg$n_pfs_excl_censored,
    First_scan_kept = dg$n_first_scan_progressors_kept,
    Scan_after = dg$n_scan_after_landmark_kept,
    OS_HR = format_hr_ci(os_fit$hr$HR, os_fit$hr$CI_Lower, os_fit$hr$CI_Upper),
    OS_p = format_pvalue(os_fit$p),
    PFS_HR = format_hr_ci(pfs_fit$hr$HR, pfs_fit$hr$CI_Lower, pfs_fit$hr$CI_Upper),
    PFS_p = format_pvalue(pfs_fit$p),
    stringsAsFactors = FALSE
  )
  list(row = row, os_model = os_fit$model, pfs_model = pfs_fit$model,
       os_hr = as.numeric(os_fit$hr$HR), pfs_hr = as.numeric(pfs_fit$hr$HR))
})
lm_sensitivity <- do.call(rbind, lapply(lm_sens_fits, `[[`, "row"))
rownames(lm_sensitivity) <- NULL

lm_sens_pfs_hr <- setNames(lm_sensitivity$PFS_HR, names(lm_all))
lm_sens_pfs_p  <- setNames(lm_sensitivity$PFS_p,  names(lm_all))
lm_sens_n_pfs  <- setNames(lm_sensitivity$N_pfs,  names(lm_all))
lm_sens_os_hr  <- setNames(lm_sensitivity$OS_HR,  names(lm_all))
lm_sens_os_hr_num  <- vapply(lm_sens_fits, `[[`, numeric(1), "os_hr")
lm_sens_pfs_hr_num <- vapply(lm_sens_fits, `[[`, numeric(1), "pfs_hr")

# The week-9 refit is the primary landmark fit; register only the other two
# definitions for the convergence table (issue #176).
stopifnot(isTRUE(all.equal(lm_sens_fits$week9$pfs_model$coefficients,
                           model_lm_tlr_pfs$coefficients, tolerance = 1e-10)),
          isTRUE(all.equal(lm_sens_fits$week9$os_model$coefficients,
                           model_lm_tlr_os$coefficients, tolerance = 1e-10)))
for (k in setdiff(names(lm_sens_fits), "week9")) {
  register_firth(sprintf("Landmark %s, OS", tolower(lm_all[[k]]$spec$short_label)),
                 lm_sens_fits[[k]]$os_model)
  register_firth(sprintf("Landmark %s, PFS", tolower(lm_all[[k]]$spec$short_label)),
                 lm_sens_fits[[k]]$pfs_model)
}

# PFS direction across landmark definitions.
pfs_same_direction <- !anyNA(lm_sens_pfs_hr_num) &&
  length(unique(sign(log(lm_sens_pfs_hr_num)))) == 1
pfs_direction_text <- if (pfs_same_direction) {
  sprintf(paste0("The direction of the PFS estimate is therefore not an artefact of the %s ",
                 "that the week-9 cut retains, but the confidence intervals are wide under ",
                 "every definition."),
          n_word(n_first_scan_kept, "first-scan progressor"))
} else {
  paste0("The direction of the PFS estimate differs between landmark definitions, and the ",
         "confidence intervals are wide under every definition.")
}

# OS across landmark definitions (issue #182): the fixed landmarks are common
# shifts of the time origin when nobody leaves the OS risk set by week 12; the
# per-patient landmark is not, so its estimate can differ.
os_fixed_identical <- n_os_out_by_wk12 == 0 &&
  isTRUE(all.equal(lm_sens_os_hr_num[["week9"]], lm_sens_os_hr_num[["week12"]], tolerance = 1e-8)) &&
  isTRUE(all.equal(lm_sens_os_hr_num[["week9"]], tlr_firth_os$HR, tolerance = 1e-8))
os_scan_fold <- fold_change(lm_sens_os_hr_num[["week9"]], lm_sens_os_hr_num[["scan"]])
os_sensitivity_text <- if (os_fixed_identical && !is.na(os_scan_fold)) {
  sprintf(paste0(
    "For OS, no patient of the TLR-complete cohort dies or is censored by week 12, so the ",
    "week-9 and week-12 landmarks are common shifts of the time origin and reproduce the ",
    "responder estimate exactly (TLR x Rx HR %s). The scan-date landmark gives %s: a ",
    "per-patient landmark is not a common shift of the time origin, so it changes the OS ",
    "risk sets. The OS estimate is therefore unchanged under the fixed landmarks and %s ",
    "under the scan-date landmark."),
    lm_sens_os_hr[["week9"]], lm_sens_os_hr[["scan"]],
    if (os_scan_fold < 1.1) "nearly unchanged" else "changed")
} else {
  sprintf("For OS, the TLR x Rx HR is %s at week 9, %s at the scan date and %s at week 12.",
          lm_sens_os_hr[["week9"]], lm_sens_os_hr[["scan"]], lm_sens_os_hr[["week12"]])
}
```

```{r table-lm-sensitivity}
lm_sensitivity %>%
  kable(col.names = c("Landmark", "N (OS)", "N (PFS)", "PFS events", "Censored before landmark",
                      "First-scan progressors retained", "TLR read after landmark",
                      "OS TLR x Rx HR (95% CI)", "PLRT p",
                      "PFS TLR x Rx HR (95% CI)", "PLRT p"),
        caption = "TLR x Rx interaction under three landmark definitions (Firth Cox, full adjustment set)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 8) %>%
  tbl_footnote(general = sprintf("Cohorts are patients with the endpoint time strictly after the landmark; time is measured from the landmark. First on-treatment scans fell between weeks %.1f and %.1f after inclusion. 'First-scan progressors retained' counts patients whose progression was recorded at the first scan (TLR-negative by construction) but who remain in the PFS cohort; 'TLR read after landmark' counts retained PFS patients whose first scan came after the landmark. The per-patient landmark sets both to zero by construction.", scan_wk_range[1], scan_wk_range[2]),
           threeparttable = TRUE)
```

The per-patient scan-date landmark and the week-12 landmark `r if (sens_remove_all_fsp) paste("both exclude all", n_first_scan_prog, "first-scan progressors") else "exclude more first-scan progressors than week 9"` (PFS cohort n = `r lm_sens_n_pfs["scan"]` and `r lm_sens_n_pfs["week12"]` versus `r lm_sens_n_pfs["week9"]` at week 9) and give a PFS TLR x Rx HR of `r lm_sens_pfs_hr["scan"]` (PLRT p `r lm_sens_pfs_p["scan"]`) and `r lm_sens_pfs_hr["week12"]` (p `r lm_sens_pfs_p["week12"]`), against `r lm_sens_pfs_hr["week9"]` (p `r lm_sens_pfs_p["week9"]`) at week 9. `r pfs_direction_text` The week-12 landmark still retains `r n_word(lm_wk12_diag$n_scan_after_landmark_kept, "patient")` whose TLR was read after week 12. `r os_sensitivity_text`

Neither analysis resolves the most fundamental issue: TLR lies on the causal path of treatment (Rx -> TLR -> outcome), so the TLR x Rx contrast is not a baseline patient-selection estimate under any time origin; disentangling it would require formal causal mediation, not a landmark. All estimates remain exploratory and imprecise (week-9 PLRT p `r format_pvalue(p_lm_tlr_os)` OS, `r format_pvalue(p_lm_tlr_pfs)` PFS) and must not guide treatment selection.

\newpage

```{r discussion-values, include=FALSE}
# Values quoted in the Discussion and Summary are pulled from the objects
# computed above so the prose cannot drift from the tables.
get_zph_p <- function(zph_df, pattern) {
  idx <- grep(pattern, rownames(zph_df))
  if (length(idx) == 0) NA_real_ else zph_df$p[idx[1]]
}
p_zph_os_global  <- get_zph_p(zph_os_df,  "^GLOBAL$")
p_zph_pfs_global <- get_zph_p(zph_pfs_df, "^GLOBAL$")
p_zph_pfs_crp    <- get_zph_p(zph_pfs_df, "^crp_num$")
p_zph_pfs_tmb    <- get_zph_p(zph_pfs_df, "^tmb_braf_num$")
p_zph_pfs_crp_rx <- get_zph_p(zph_pfs_df, "crp_num.*Rx|Rx.*crp_num")
p_zph_pfs_tmb_rx <- get_zph_p(zph_pfs_df, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# Firth HR (95% CI) and point-estimate shorthands
hr_txt <- function(x) format_hr_ci(x$HR, x$CI_Lower, x$CI_Upper)
hr_pt  <- function(x) if (is.na(x$HR)) "--" else sprintf("%.2f", x$HR)

# Marginal Firth Cox CRP -> PFS (CRP alone) on the complete-case cohort: the DAG
# association test quoted in the Discussion, with the specification of
# run_dag_edge_tests() in dag_association_tests.R (issue #157).
dag_crp_pfs_warnings <- character()
dag_crp_pfs_fit <- withCallingHandlers(
  coxphf::coxphf(
    Surv(PFSwk, Progression) ~ crp_num, data = data_complete,
    firth = TRUE, pl = TRUE, maxit = 100, maxstep = 0.1
  ),
  warning = function(w) dag_crp_pfs_warnings <<- c(dag_crp_pfs_warnings, conditionMessage(w))
)
attr(dag_crp_pfs_fit, "fit_warnings") <- dag_crp_pfs_warnings
register_firth("Marginal CRP -> PFS (DAG)", dag_crp_pfs_fit)
dag_crp_pfs_hr <- exp(unname(dag_crp_pfs_fit$coefficients["crp_num"]))
dag_crp_pfs_p <- unname(dag_crp_pfs_fit$prob["crp_num"])

# Convergence diagnostics of every distinct Firth fit (issue #176).
firth_convergence <- do.call(rbind, lapply(names(firth_fits), function(label) {
  cbind(Model = label, coxphf_convergence(firth_fits[[label]]), stringsAsFactors = FALSE)
}))
rownames(firth_convergence) <- NULL
firth_not_converged <- firth_convergence$Model[firth_convergence$Status != "Converged"]
firth_at_maxit <- firth_convergence$Model[firth_convergence$Status == "Reached maxit"]
```

# Firth Model Convergence

Each Firth fit reports the Newton-Raphson iterations of the penalized-likelihood estimation and, for every coefficient, the iterations used to find the two profile-likelihood confidence limits and the PLRT p-value. `coxphf` sets a limit or p-value to missing when its iteration count reaches the limit, so a fit that reaches it is flagged below; warnings raised during a fit (numerical problems) are also counted.

```{r table-firth-convergence}
firth_convergence %>%
  select(Model, N, Events, Iterations, Max_PL_iterations, Maxit, Status) %>%
  kable(col.names = c("Model", "N", "Events", "Iterations",
                      "PL iterations", "Limit", "Status"),
        caption = "Convergence of the Firth-corrected Cox fits",
        booktabs = TRUE, format = report_table_format(),
        align = c("l", rep("r", 5), "l")) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_footnote(general = paste0(
    "Iterations: Newton-Raphson iterations of the penalized-likelihood estimation. PL iterations: ",
    "the largest iteration count over all coefficients' lower and upper profile-likelihood limits ",
    "and PLRT p-values. Limit: the iteration limit (maxit). Status is 'Reached maxit' when any count ",
    "reaches the limit and 'Numerical warning' when coxphf reported a numerical problem. The primary ",
    "PFS rule and the week-9 refit of the landmark sensitivity table are the primary PFS and week-9 ",
    "landmark fits and are not repeated."),
    footnote_as_chunk = TRUE, threeparttable = TRUE)
```

`r if (length(firth_not_converged) == 0) sprintf("All %d Firth fits converged: estimation took at most %d iterations and the profile-likelihood limits and PLRT at most %d, against a limit of %s; no fit reached the limit or raised a numerical warning.", nrow(firth_convergence), max(firth_convergence$Iterations), max(firth_convergence$Max_PL_iterations), paste(unique(firth_convergence$Maxit), collapse = " or ")) else sprintf("%d of %d Firth fits did not converge cleanly (%s)%s; their affected confidence limits or p-values are missing or should be read with caution.", length(firth_not_converged), nrow(firth_convergence), paste(firth_not_converged, collapse = "; "), if (length(firth_at_maxit) > 0) sprintf(", of which %s reached the iteration limit", paste(firth_at_maxit, collapse = "; ")) else "")`

# Discussion

## Primary interaction results

The death-censoring sensitivity gives CRP x Rx PFS HR `r pfs_sens_crp["primary"]` under the primary window, `r pfs_sens_crp["all_deaths"]` when all deaths count, and `r pfs_sens_crp["anchor_alt"]` under the alternative last-assessment proxy; uncertainty about off-study ascertainment therefore affects this exploratory estimate.

Neither biomarker-treatment interaction reached conventional significance in the unified model (Firth HR with 95% CI in parentheses). For **overall survival**, CRP × Rx yielded HR `r hr_txt(hr_crp_os)` (PLRT p = `r format_pvalue(p_crp_os)`) and TMB/BRAF × Rx HR `r hr_txt(hr_tmb_os)` (p = `r format_pvalue(p_tmb_os)`) — point estimates close to null with very wide confidence intervals. For **progression-free survival**, the CRP × Rx interaction was directionally favourable but imprecise (HR `r hr_txt(hr_crp_pfs)`, p = `r format_pvalue(p_crp_pfs)`). The interaction HR is the ratio of the treatment hazard ratio in CRP-positive patients to that in CRP-negative patients (at the same TMB/BRAF status), so an estimate below 1 means a smaller estimated treatment hazard ratio in CRP-positive than in CRP-negative patients; the CI spans more than an order of magnitude and includes 1. The TMB/BRAF × Rx PFS interaction was HR `r hr_txt(hr_tmb_pfs)` (p = `r format_pvalue(p_tmb_pfs)`). These results are consistent with the trial being underpowered to detect treatment-effect heterogeneity (n = `r n_total`, `r sum(data_complete$Progression)` PFS events (progression or death), `r sum(data_complete$Death)` deaths): even a moderate subgroup effect (HR ~0.5) would require far larger samples for reliable estimation.

The PFS pattern is worth noting as a hypothesis-generating finding. The CRP direction (HR `r hr_pt(hr_crp_pfs)`) is consistent with the DAG association test showing CRP → PFS (marginal Firth HR `r sprintf("%.2f", dag_crp_pfs_hr)`, p = `r format_pvalue(dag_crp_pfs_p)`; see the DAG associations report) and the biological hypothesis that low CRP (reflecting lower systemic inflammation) identifies patients more likely to respond to immunotherapy. However, the OS CRP interaction estimate (HR `r hr_pt(hr_crp_os)`) is closer to null, suggesting that any PFS benefit does not clearly translate to an OS benefit in this dataset.

## Proportional hazards

The Schoenfeld global test gives p = `r format_pvalue(p_zph_os_global)` for OS and p = `r format_pvalue(p_zph_pfs_global)` for PFS. In PFS, the biomarker main-effect tests give p = `r format_pvalue(p_zph_pfs_crp)` for CRP and `r format_pvalue(p_zph_pfs_tmb)` for TMB/BRAF; the interaction tests give p = `r format_pvalue(p_zph_pfs_crp_rx)` and `r format_pvalue(p_zph_pfs_tmb_rx)`, respectively. These tests do not establish that the global PFS departure is confined to the main effects or that the interaction hazards are constant. `r ph_flag_os_text` `r ph_flag_pfs_text` The reported Cox hazard ratios are time-averaged summaries; time-varying effects would require further investigation in a larger cohort.

## Ridge regression sensitivity

The ridge model penalizes the CRP and TMB/BRAF main effects with a cross-validated lambda (OS lambda.min = `r ridge_lambda_os`, PFS lambda.min = `r ridge_lambda_pfs`) and estimates the interaction terms as pre-built product terms, so the ridge and Firth interaction coefficients are the same treatment-by-biomarker contrast. For OS, the CRP × Rx estimate `r shift_word(hr_crp_os$HR, ridge_crp_os$HR)` under this penalization (Firth HR `r hr_pt(hr_crp_os)` → Ridge HR `r hr_pt(ridge_crp_os)`), and the TMB/BRAF × Rx estimate `r shift_word(hr_tmb_os$HR, ridge_tmb_os$HR)` (`r hr_pt(hr_tmb_os)` → `r hr_pt(ridge_tmb_os)`). For PFS, the CRP × Rx estimate `r shift_word(hr_crp_pfs$HR, ridge_crp_pfs$HR)` (`r hr_pt(hr_crp_pfs)` → `r hr_pt(ridge_crp_pfs)`) and the TMB/BRAF × Rx estimate `r shift_word(hr_tmb_pfs$HR, ridge_tmb_pfs$HR)` (`r hr_pt(hr_tmb_pfs)` → `r hr_pt(ridge_tmb_pfs)`). A shift of at least 1.5-fold in the HR is labelled "substantial". Because only the main effects are penalized, any shift in an interaction term reflects redistribution of the shrunken main-effect signal rather than independent support for a particular effect size: an interaction that moves substantially is sensitive to how the biomarker main effects are estimated and should not be over-interpreted, while one that changes little is not driven by the main-effect estimates.

## TLR responder analysis (exploratory)

The exploratory responder model — `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx` — estimates the differential treatment effect between TLR-positive and TLR-negative subgroups while adjusting for the pre-immunotherapy biomarkers as prognostic main effects. The Firth-estimated TLR × Rx HR was `r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)` for overall survival and `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` for progression-free survival. The OS estimate sits **above 1.0**, which directionally implies the (TLR-positive vs TLR-negative) hazard contrast is *worse* on the experimental arm than on the control arm — the opposite of a "TLR-positive predicts immunotherapy benefit" pattern. PFS is closer to null. Ridge shrinkage of the TLR terms gives `r format_ridge_hr(ridge_tlr_os_int$HR, ridge_tlr_os_int$SE)` (OS) and `r format_ridge_hr(ridge_tlr_pfs_int$HR, ridge_tlr_pfs_int$SE)` (PFS): ridge moves the OS estimate modestly toward null but preserves the directional pattern, and barely changes the PFS estimate. PLRT p-values (`r format_pvalue(p_tlr_os)` OS, `r format_pvalue(p_tlr_pfs)` PFS) do not reach conventional significance, consistent with the wide profile-likelihood CIs in this small sample.

The directional pattern is consistent with the descriptive imbalance: TLR-positive prevalence is `r tlr_by_arm$pct_tlr_pos[1]`% in the control arm and `r tlr_by_arm$pct_tlr_pos[2]`% in the experimental arm. If TLR cleanly captured immunotherapy response one would expect higher TLR-positivity in the experimental arm, not lower. The observed prevalence pattern, together with the OS direction (HR > 1) of the TLR × Rx interaction, is more consistent with TLR acting as a **prognostic** marker (identifying chemotherapy-responsive disease, which is more prevalent in the control arm by chance or by timing) than as a predictive marker for immunotherapy benefit. Possible explanations for the imbalance include small-sample randomization imbalance, a timing artefact (TLR measured at a fixed CT that may occur during different treatment phases across arms), or genuine heterogeneity in the patient mix. Because TLR is itself influenced by treatment, the TLR × Rx interaction is a responder-stratified contrast — useful for hypothesis generation, but not a causal predictive-biomarker estimate.

## TLR landmark analysis (exploratory)

A **week-9 landmark analysis** measures survival from the protocol time of the second (first on-treatment) CT, close to the first on-treatment scan at which TLR is defined, to examine the guarantee-time bias of the responder analysis. Its at-risk conditions differ by endpoint: the OS cohort requires only that the patient is alive and uncensored at week 9, whereas the PFS cohort also requires no progression, no PFS-counted death and no censoring at an earlier assessment. `r os_lm_summary_text` For **PFS**, `r lm_attrition$N_excluded[2]` patients are excluded (including `r lm_diag$n_pfs_excl_censored` censored at their last assessment and `r lm_diag$n_pfs_excl_death_pf` death events within the window), with `r n_pfs_excl_prog_tn` of the `r n_pfs_excl_prog` excluded progressors being TLR-negative, because progression and TLR are ascertained at the same scan. The Firth TLR main effect is `r tlr_main_change_word` (HR `r hr_pt(tlr_main_resp_pfs)` responder, `r hr_pt(tlr_main_lm_pfs)` landmark) and the TLR × Rx HR `r pfs_int_move_text`. `r tlr_coupling_text` Because the actual first scans fell between weeks `r sprintf("%.1f", scan_wk_range[1])` and `r sprintf("%.1f", scan_wk_range[2])`, the fixed week-9 cut retains `r n_first_scan_kept` of the `r n_first_scan_prog` first-scan progressors and `r n_scan_after_kept` patients whose TLR was read after the landmark; a per-patient landmark at the scan date and a fixed week-12 landmark, which `r if (sens_remove_all_fsp) "exclude all first-scan progressors" else "exclude more first-scan progressors"`, give PFS TLR × Rx HRs of `r lm_sens_pfs_hr["scan"]` and `r lm_sens_pfs_hr["week12"]`, `r if (pfs_same_direction) "so the direction of the estimate does not depend on the landmark choice" else "and the direction of the estimate differs between definitions"`. Under any time origin TLR remains on the causal path of treatment, so a definitive predictive-biomarker estimate would require causal mediation rather than a landmark. Both analyses remain underpowered and exploratory, and neither supports baseline treatment selection on TLR.

\newpage

# Summary

**Study:** METIMMOX-1 biomarker subgroup analysis. N = `r n_total` complete cases, `r sum(data_complete$Death)` OS events, `r sum(data_complete$Progression)` PFS events (progression or death).

**Methods:** Two Firth-corrected Cox analyses are presented. **Primary (DAG-informed):** `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx` — pre-immunotherapy biomarkers (week-4 CRP before the first nivolumab dose; baseline TMB/BRAF) as effect modifiers; TLR omitted because it is measured on treatment. **Exploratory responder analysis:** `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx` — adds TLR and its treatment interaction, with CRP and TMB/BRAF retained as prognostic main-effect adjustments. Profile likelihood CIs, PLRT for interaction testing; `r if (length(firth_not_converged) == 0) sprintf("all %d Firth fits converged without reaching the iteration limit", nrow(firth_convergence)) else sprintf("%d of %d Firth fits did not converge cleanly (see Firth Model Convergence)", length(firth_not_converged), nrow(firth_convergence))`. Ridge sensitivity analysis penalizes the CRP/TMB main effects in the primary model and the TLR terms (main effect + TLR:Rx) in the exploratory model.

**Proportional hazards:** Global Schoenfeld p = `r format_pvalue(p_zph_os_global)` for OS and `r format_pvalue(p_zph_pfs_global)` for PFS. PFS biomarker main-effect p-values are `r format_pvalue(p_zph_pfs_crp)` (CRP) and `r format_pvalue(p_zph_pfs_tmb)` (TMB/BRAF), with interaction p-values `r format_pvalue(p_zph_pfs_crp_rx)` and `r format_pvalue(p_zph_pfs_tmb_rx)`. The global PFS result does not isolate a particular term. `r ph_flag_os_text` `r ph_flag_pfs_text` Interpret the Cox HRs as time-averaged summaries.

**Endpoint sensitivity:** The primary rule censors `r n_deaths_censored_pfs` late deaths without recorded progression; CRP x Rx PFS HR is `r pfs_sens_crp["primary"]`, compared with `r pfs_sens_crp["all_deaths"]` under the former all-deaths rule.

**Interaction estimates:**

| Interaction | OS HR (95% CI) | PLRT p | PFS HR (95% CI) | PLRT p |
|-------------|----------------|--------|-----------------|--------|
| CRP × Rx    | `r hr_txt(hr_crp_os)` | `r format_pvalue(p_crp_os)` | `r hr_txt(hr_crp_pfs)` | `r format_pvalue(p_crp_pfs)` |
| TMB/BRAF × Rx | `r hr_txt(hr_tmb_os)` | `r format_pvalue(p_tmb_os)` | `r hr_txt(hr_tmb_pfs)` | `r format_pvalue(p_tmb_pfs)` |

No interaction is statistically significant. CRP × Rx PFS (HR `r hr_pt(hr_crp_pfs)`) is the strongest directional signal; under ridge regularization of the biomarker main effects (glmnet, CV lambda) it `r shift_word(hr_crp_pfs$HR, ridge_crp_pfs$HR)` (Ridge HR `r hr_pt(ridge_crp_pfs)`). The TMB/BRAF × Rx OS interaction `r shift_word(hr_tmb_os$HR, ridge_tmb_os$HR)` (Ridge HR `r hr_pt(ridge_tmb_os)` vs Firth `r hr_pt(hr_tmb_os)`). The PFS PH diagnostic does not establish which term drives the global departure.

**TLR responder analysis (exploratory):** Firth TLR × Rx HR `r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)` for OS and `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` for PFS. Ridge-penalized TLR terms: `r format_ridge_hr(ridge_tlr_os_int$HR, ridge_tlr_os_int$SE)` (OS), `r format_ridge_hr(ridge_tlr_pfs_int$HR, ridge_tlr_pfs_int$SE)` (PFS). PLRT p-values (`r format_pvalue(p_tlr_os)` OS, `r format_pvalue(p_tlr_pfs)` PFS) do not reach conventional significance in this small sample. TLR-positive prevalence: control `r tlr_by_arm$pct_tlr_pos[1]`%, experimental `r tlr_by_arm$pct_tlr_pos[2]`% — markedly higher TLR-positivity in the control arm. The OS direction (HR > 1) of TLR × Rx, combined with the prevalence pattern, is more consistent with TLR acting as a prognostic marker for chemo-responsive disease than as a predictive marker for immunotherapy benefit. Because TLR is post-randomization, this is a responder-stratified, hypothesis-generating contrast rather than a causal predictive-biomarker estimate.

**TLR week-9 landmark analysis (exploratory):** A fixed week-9 landmark analysis — close to the first on-treatment scan at which TLR is defined — was added; its OS cohort requires patients alive and uncensored at week 9, and its PFS cohort also requires them to be progression-free and not censored at an earlier assessment. `r os_lm_summary_text` For **PFS**, `r lm_attrition$N_excluded[2]` patients are excluded (including `r lm_diag$n_pfs_excl_censored` censored at their last assessment and `r lm_diag$n_pfs_excl_death_pf` death events within the window), `r n_pfs_excl_prog_tn` of the `r n_pfs_excl_prog` excluded progressors being TLR-negative because progression and TLR are read from the same scan. The TLR main effect is `r tlr_main_change_word` (HR `r hr_pt(tlr_main_resp_pfs)` responder, `r hr_pt(tlr_main_lm_pfs)` landmark) and the TLR x Rx HR `r pfs_int_move_text`; the week-9 PLRT p-values are `r format_pvalue(p_lm_tlr_os)` (OS) and `r format_pvalue(p_lm_tlr_pfs)` (PFS). Because first scans fell between weeks `r sprintf("%.1f", scan_wk_range[1])` and `r sprintf("%.1f", scan_wk_range[2])`, the week-9 cut retains `r n_first_scan_kept` first-scan progressors and `r n_scan_after_kept` patients scanned after the landmark; sensitivity landmarks at each patient's scan date (PFS HR `r lm_sens_pfs_hr["scan"]`) and at week 12 (`r lm_sens_pfs_hr["week12"]`) `r if (sens_remove_all_fsp) "exclude all first-scan progressors" else "exclude more first-scan progressors"` and `r if (pfs_same_direction) "leave the direction unchanged" else "change the direction"`. Both analyses are retained for comparison; both are underpowered and exploratory, and the residual confounding from TLR being treatment-influenced needs causal mediation, not a landmark. Neither supports baseline treatment selection on TLR.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 3.10
