---
title: "Clinical Effectiveness"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Load required libraries and shared Cox extraction helpers.
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("cox_extract", "tlr_landmark"),
  packages = c("here", "knitr", "kableExtra", "ggplot2", "dplyr", "tidyverse",
               "survival", "survminer", "coxphf", "glmnet", "vcd"),
  set_theme = FALSE
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r helper-functions, include=FALSE}
# =============================================================================
# HELPER FUNCTIONS
# =============================================================================

#' Extract results from standard Cox model (full table, interactions grouped at top)
extract_coxph_results <- function(model, reorder_interactions = TRUE) {
  if (is.null(model)) return(NULL)

  model_summary <- summary(model)
  coef_table <- model_summary$coefficients
  conf_table <- model_summary$conf.int

  results <- data.frame(
    Term = rownames(coef_table),
    HR = exp(coef(model)),
    CI_Lower = conf_table[, "lower .95"],
    CI_Upper = conf_table[, "upper .95"],
    P_Value = coef_table[, "Pr(>|z|)"],
    stringsAsFactors = FALSE
  )

  if (reorder_interactions) {
    # Put interaction terms at top
    is_interaction <- grepl(":", results$Term)
    results <- rbind(results[is_interaction, ], results[!is_interaction, ])
  }

  rownames(results) <- NULL
  results
}

#' Apply Benjamini-Hochberg FDR correction
apply_bh_correction <- function(p_values) {
  p.adjust(p_values, method = "BH")
}

#' Format HR with CI for display (vectorized)
format_hr_ci <- function(hr, ci_lower, ci_upper, digits = 2) {
  mapply(function(h, l, u) {
    if (is.na(h)) return("--")
    sprintf(paste0("%.", digits, "f (%.", digits, "f-%.", digits, "f)"), h, l, u)
  }, hr, ci_lower, ci_upper, USE.NAMES = FALSE)
}

#' Build a side-by-side standard Cox vs Firth comparison table
build_std_firth_comparison <- function(std_results, firth_results, row_specs) {
  format_result_cell <- function(results_df, pattern) {
    if (is.null(results_df) || is.null(pattern)) return("--")
    idx <- grep(pattern, results_df$Term)
    if (length(idx) == 0) return("--")
    format_hr_ci(
      results_df$HR[idx[1]],
      results_df$CI_Lower[idx[1]],
      results_df$CI_Upper[idx[1]]
    )
  }

  do.call(rbind, lapply(row_specs, function(rs) {
    data.frame(
      Term = rs$label,
      Standard_Cox = format_result_cell(std_results, rs$std_pat),
      Firth = format_result_cell(firth_results, rs$firth_pat),
      stringsAsFactors = FALSE
    )
  }))
}

#' Render standard Cox vs Firth tables for both PDF and GFM outputs
render_std_firth_comparison_table <- function(comparison_df, caption,
                                             first_group_label, first_group_end,
                                             second_group_label) {
  table_format <- if (knitr::is_latex_output()) "latex" else "pipe"

  comparison_table <- comparison_df %>%
    kable(col.names = c("Term", "Standard Cox HR (95% CI)", "Firth HR (95% CI)"),
          caption = caption, booktabs = TRUE, format = table_format)

  if (knitr::is_latex_output()) {
    comparison_table %>%
      tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
      tbl_pack_rows(first_group_label, 1, first_group_end, bold = TRUE) %>%
      tbl_pack_rows(second_group_label, first_group_end + 1, nrow(comparison_df), bold = TRUE)
  } else {
    comparison_table
  }
}

#' Format p-value for display (vectorized)
format_pvalue <- function(p, digits = 3) {
  sapply(p, function(pval) {
    if (is.na(pval)) return("--")
    if (pval < 0.001) return("<0.001")
    sprintf(paste0("%.", digits, "f"), pval)
  }, USE.NAMES = FALSE)
}

#' Create forest plot for interaction HRs
create_interaction_forest_plot <- function(results_df, outcome = "OS") {
  ggplot(results_df,
         aes(x = HR, y = Biomarker, color = Model, shape = Model)) +
    geom_point(position = position_dodge(width = 0.5), size = 3) +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper),
                   position = position_dodge(width = 0.5), height = 0.2) +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4, 10),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4", "10")) +
    scale_color_manual(
      values = c("A: All-in-One" = "#E69F00",
                 "B: Focused" = "#56B4E9",
                 "C: Single" = "#009E73"),
      name = "Model Type"
    ) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = paste("Treatment × Biomarker Interaction:", outcome),
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(
      legend.position = "bottom",
      panel.grid.minor = element_blank()
    )
}

#' Create log-log survival plot for PH diagnostics
create_loglog_plot <- function(data, time_var, event_var, strata_var, title) {
  formula <- as.formula(paste0("Surv(", time_var, ", ", event_var, ") ~ ", strata_var))
  km_fit <- survfit(formula, data = data)

  # Extract survival data
  surv_summary <- summary(km_fit)

  plot_data <- data.frame(
    time = surv_summary$time,
    surv = surv_summary$surv,
    strata = surv_summary$strata
  ) %>%
    filter(surv > 0 & surv < 1) %>%
    mutate(
      log_time = log(time),
      log_log_surv = log(-log(surv))
    )

  ggplot(plot_data, aes(x = log_time, y = log_log_surv, color = strata)) +
    geom_step(linewidth = 1) +
    labs(
      x = "log(Time in weeks)",
      y = "-log(-log(S(t)))",
      title = title,
      subtitle = "Parallel lines support PH assumption",
      color = "Group"
    ) +
    theme_minimal() +
    theme(legend.position = "bottom")
}
```

```{r data-preparation, include=FALSE}
# =============================================================================
# DATA PREPARATION
# =============================================================================

# Prepare data for Cox models.
# PRIMARY COHORT (issue #153): complete cases on the pre-immunotherapy
# biomarkers only (CRP, TMB/BRAF) plus covariates and endpoints. This is the
# same 68-patient cohort used by the economic survival models
# (04_parametric_survival_analysis.R) and the DAG association report. TLR
# completeness is NOT required here: the three patients without a TLR value are
# early control-arm deaths who never reached the first on-treatment CT, and
# dropping them from the primary models would condition on surviving to that
# scan.
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

# Ensure proper factor coding.
# `sex` is the renamed trial column "Sex 0female": level "0" = female,
# level "1" = male (see 01_data_prep.R, where Female <- 1 - `Sex 0female`).
data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx <- as.factor(data_complete$Rx)
SEX_FEMALE_LEVEL <- "0"
SEX_MALE_LEVEL   <- "1"
stopifnot(all(levels(data_complete$sex) %in% c(SEX_FEMALE_LEVEL, SEX_MALE_LEVEL)))

# Biomarkers as numeric 0/1 for coxphf (interactions work better with numeric).
# tlr_num is NA for the three patients without a first on-treatment scan.
data_complete$crp_num <- as.numeric(as.character(data_complete$crp))
data_complete$tlr_num <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf_num <- as.numeric(as.character(data_complete$tmb_braf))

# Create numeric Rx for ridge regression
data_complete$Rx_num <- as.numeric(data_complete$Rx) - 1  # 0 = Control, 1 = Experimental

# TLR-COMPLETE COHORT: used only by the exploratory TLR responder and landmark
# analyses and by the TLR columns of the sample-characteristics table.
data_tlr <- data_complete[!is.na(data_complete$tlr_num), ]
n_tlr_total   <- nrow(data_tlr)
n_tlr_missing <- n_total_missing_tlr <- nrow(data_complete) - n_tlr_total

# Sample characteristics (primary cohort)
n_total <- nrow(data_complete)
n_control <- sum(data_complete$Rx_num == 0)
n_experimental <- sum(data_complete$Rx_num == 1)

# Biomarker prevalence
prev_crp <- mean(data_complete$crp_num)
prev_tlr <- mean(data_tlr$tlr_num)
prev_tmb_braf <- mean(data_complete$tmb_braf_num)

# Event counts
n_deaths <- sum(data_complete$Death)
n_progressions <- sum(data_complete$Progression)
```

```{r biomarker-correlation, include=FALSE}
# =============================================================================
# BIOMARKER CORRELATION ANALYSIS (Cramér's V)
# =============================================================================

# CRP vs TLR (TLR-complete subset)
crp_tlr_table <- table(data_tlr$crp_num, data_tlr$tlr_num)
crp_tlr_assoc <- assocstats(crp_tlr_table)
cramers_v_crp_tlr <- crp_tlr_assoc$cramer

# CRP vs TMB/BRAF (primary cohort)
crp_tmb_table <- table(data_complete$crp_num, data_complete$tmb_braf_num)
crp_tmb_assoc <- assocstats(crp_tmb_table)
cramers_v_crp_tmb <- crp_tmb_assoc$cramer

# TLR vs TMB/BRAF (TLR-complete subset)
tlr_tmb_table <- table(data_tlr$tlr_num, data_tlr$tmb_braf_num)
tlr_tmb_assoc <- assocstats(tlr_tmb_table)
cramers_v_tlr_tmb <- tlr_tmb_assoc$cramer

# Build correlation summary
correlation_df <- data.frame(
  Comparison = c("CRP vs TLR", "CRP vs TMB/BRAF", "TLR vs TMB/BRAF"),
  Cramers_V = round(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), 3),
  Interpretation = sapply(c(cramers_v_crp_tlr, cramers_v_crp_tmb, cramers_v_tlr_tmb), function(v) {
    if (v > 0.3) "Moderate/Strong"
    else if (v > 0.1) "Weak"
    else "Negligible"
  })
)
```

# Overview

This report presents clinical effectiveness results from the METIMMOX-1 trial, evaluating biomarker-guided treatment strategies for selecting immunotherapy candidates in metastatic MSS/pMMR colorectal cancer.

The analysis uses **Firth-corrected Cox proportional hazards regression** with profile likelihood confidence intervals to assess treatment effect heterogeneity across two biomarkers that are available before the decision to add immunotherapy, identified by the causal DAG analysis:

- **CRP** (C-reactive protein): Low CRP (<5 mg/L) at week 4 (cycle 3 day 1), measured after the two FLOX cycles that both arms receive and before the first nivolumab dose — a prognostic and potentially predictive marker
- **TMB/BRAF**: High tumor mutational burden (≥9 mut/MB) or BRAF mutation — a baseline genomic marker

```{r crp-timing-counts, include=FALSE}
# Week-4 CRP by arm on the full trial data (before complete-case exclusion)
# and the follow-up of the patients with no week-4 value, quoted in the
# paragraph below so that the counts cannot drift from the data (issue #157).
# The baseline CRP comparison (CRP0cat, cycle 1 day 1) is derived in
# 01_data_prep.R and is not carried into the analysis data, so it is quoted
# from that script.
crp_arm_tab <- table(data$Rx, data$crp)
crp_arm_n <- rowSums(crp_arm_tab)
crp_arm_pos <- crp_arm_tab[, "1"]
crp_arm_fisher_p <- fisher.test(crp_arm_tab)$p.value
crp_missing <- data[is.na(data$crp), ]
crp_missing_weeks <- paste(sprintf("%.1f", sort(crp_missing$OSwk)), collapse = ", ")
crp_missing_outcome <- if (nrow(crp_missing) > 0 && all(crp_missing$Death == 1)) {
  "early deaths"
} else {
  "lost early (death or censoring)"
}
```

**CRP timing.** CRP is not a baseline (pre-randomization) measurement: the value used throughout is the week-4 CRP at the start of nivolumab, matching the post-hoc CRP analysis of the trial paper. Because nivolumab has not yet been given at week 4 and both arms receive identical FLOX until then, the DAG carries no `T -> CRP` edge. Two consequences follow. First, week-4 CRP-positivity differs by arm (experimental `r crp_arm_pos["Experimental arm"]`/`r crp_arm_n["Experimental arm"]`, control `r crp_arm_pos["Control arm"]`/`r crp_arm_n["Control arm"]`; Fisher p = `r format_pvalue(crp_arm_fisher_p)`) whereas baseline CRP was balanced (8/38 vs 7/35; p = 1; `CRP0cat` in `01_data_prep.R`, which is not part of the analysis data); this is treated as chance imbalance on a week-4 measurement in a small trial, not as a failure of randomization, and is what the `CRP:Rx` interaction is estimated against. Second, the `r nrow(crp_missing)` patients with no week-4 CRP are `r crp_missing_outcome` (weeks `r crp_missing_weeks`) and are excluded from the complete-case data, so the CRP subgroups are conditional on surviving to the week-4 measurement. The clock remains randomization; a landmark analysis at week 4 would drop no further patients from the CRP subgroups.

**Model specification is motivated by the causal DAG** (see `dag.qmd` and `dag_associations.qmd`). The DAG encodes treatment (T) as randomized with no parents, so no confounding adjustment is needed for causal identification; Age and Sex are included as precision covariates. TLR (Tumor Lesion Reduction) is encoded as a post-randomization intermediate variable (T → TLR → PFS): it is not a pre-treatment baseline characteristic and conditioning on it as a covariate would block part of the treatment effect pathway. TLR is therefore excluded from the primary survival models and examined separately as a descriptive endpoint.

The **unified DAG-informed model** is:

$$\text{Surv}(\text{time}, \text{event}) \sim \text{Age} + \text{sex} + \text{Rx} + \text{CRP} + \text{TMB/BRAF} + \text{CRP} \times \text{Rx} + \text{TMB/BRAF} \times \text{Rx}$$

Ridge regression (L2-penalized Cox) is applied as a sensitivity analysis to assess the stability of the interaction estimates under shrinkage. TLR is reported in a separate exploratory section.

# Methodological Notes

## Software Packages

This analysis uses the following R packages:

- `coxphf` version `r packageVersion("coxphf")`: Firth-corrected Cox regression with profile likelihood CIs
- `survival` version `r packageVersion("survival")`: Cox regression and Schoenfeld residual diagnostics
- `glmnet` version `r packageVersion("glmnet")`: Ridge regression sensitivity analysis
- `vcd` version `r packageVersion("vcd")`: Cramér's V for biomarker correlation assessment

## Firth-Corrected Cox Regression

We use Firth's penalized maximum likelihood method for Cox regression, which addresses:

1. **Monotone likelihood**: When a covariate perfectly separates events from non-events
2. **Small sample bias**: Reduces bias in coefficient estimates with sparse data
3. **Unstable confidence intervals**: Profile likelihood CIs are more reliable than Wald-based CIs in small samples

Statistical inference is based on **penalized likelihood ratio tests (PLRT)**, which are more appropriate than Wald tests for testing treatment-biomarker interactions in this setting.

## Ridge Regression Sensitivity Analysis

We use Ridge regression as a sensitivity analysis to assess the stability of our interaction estimates. Ridge regression (also called L2-penalized regression or Tikhonov regularization) belongs to the family of regularized or penalized regression methods. In survival analysis, this is implemented as a penalized Cox model.

**How Ridge regression works:**

- Ridge adds a penalty term that discourages large coefficients. The bigger a coefficient tries to get, the more the model resists, pulling estimates toward zero (HR toward 1.0).
- Unlike LASSO (alpha = 1), which sets some coefficients exactly to zero and performs variable selection, Ridge (alpha = 0) shrinks all coefficients but retains all predictors.
- The degree of shrinkage is controlled by the tuning parameter lambda, which is selected via **cross-validation (CV)**: the data are repeatedly split into training and validation sets, and the lambda that produces the best predictive performance is chosen. Here this is `glmnet::cv.glmnet(family = "cox", alpha = 0)` with 10-fold CV of the partial-likelihood deviance and `lambda.min`; fold assignment is seeded so the result is reproducible.
- **Implementation detail.** The model is fitted on an explicit design matrix (Age, sex, Rx, CRP, TMB/BRAF, CRP x Rx, TMB/BRAF x Rx) in which the product terms are constructed before fitting. This matters because `survival::ridge()` with a factor treatment variable and a formula interaction such as `crp:Rx` codes the interaction separately for each arm (the CRP slope within the control arm and within the experimental arm) rather than as the single treatment-by-biomarker contrast; the pre-built product term recovers the same contrast that the Firth model estimates. In the primary model only the CRP and TMB/BRAF main effects are penalized (penalty factor 1); Age, sex, Rx and the two interaction terms have penalty factor 0. glmnet does not provide standard errors, so ridge results are point estimates.

**Why not LASSO or Elastic Net?**

We determined that LASSO and elastic net are **not appropriate** for this analysis:

1. **Correlated biomarkers**: LASSO arbitrarily selects one of correlated predictors while setting others to zero, which does not reflect the clinical question of comparing ALL biomarker strategies.

2. **Hierarchy principle violation**: LASSO may select interaction terms (e.g., `crp:Rx`) while setting the main effect (`crp`) to zero, producing models that are difficult to interpret clinically.

3. **Clinical objective**: Our goal is to estimate treatment effect heterogeneity across ALL biomarkers simultaneously, not to select a "winning" biomarker.

Elastic net (alpha = 0.1–0.3) represents a compromise but does not fully address these concerns.

**Interpreting Ridge results:**

Ridge regression is not replacing the Firth estimates—it provides a reality check. When Ridge substantially shrinks an interaction coefficient toward zero while Firth estimates a large effect, this indicates the effect is too unstable to trust for practical use. The CV-selected lambda reflects how much regularization is needed for reasonable out-of-sample prediction given the sample size and collinearity structure.

# Data Preparation

## Sample Characteristics

```{r table-sample}
# Helper: format n (%) with subgroup denominator
fmt_n_pct <- function(n, total, digits = 1) {
  if (is.na(n) || total == 0) return("--")
  sprintf(paste0("%d (%.", digits, "f%%)"), n, 100 * n / total)
}

# Helper: format mean (SD)
fmt_mean_sd <- function(x, digits = 1) {
  if (length(x) == 0 || all(is.na(x))) return("--")
  sprintf(paste0("%.", digits, "f (%.", digits, "f)"),
          mean(x, na.rm = TRUE), sd(x, na.rm = TRUE))
}

# Compute the column of statistics for a given subgroup
build_col <- function(df) {
  n <- nrow(df)
  rx_levels    <- levels(data_complete$Rx)
  # sex: level "0" = female, "1" = male ("Sex 0female" in the trial export).
  n_female     <- sum(df$sex == SEX_FEMALE_LEVEL)
  n_male       <- sum(df$sex == SEX_MALE_LEVEL)
  n_ctrl       <- sum(df$Rx == rx_levels[1])
  n_exp        <- sum(df$Rx == rx_levels[2])
  # TLR is missing for early deaths without a first on-treatment scan, so the
  # TLR-positive row uses the patients with a TLR value as its denominator.
  n_tlr_known  <- sum(!is.na(df$tlr_num))
  c(
    as.character(n),
    fmt_mean_sd(df$Age),
    fmt_n_pct(n_male,   n),
    fmt_n_pct(n_female, n),
    fmt_n_pct(n_ctrl,   n),
    fmt_n_pct(n_exp,    n),
    fmt_n_pct(sum(df$Death),       n),
    fmt_n_pct(sum(df$Progression), n),
    fmt_n_pct(sum(df$crp_num),      n),
    fmt_n_pct(sum(df$tlr_num, na.rm = TRUE), n_tlr_known),
    fmt_n_pct(sum(df$tmb_braf_num), n)
  )
}

# Build subgroup data frames. CRP and TMB/BRAF columns use the primary
# 68-patient cohort; TLR columns use the TLR-complete subset.
sub_overall <- data_complete
sub_crp_pos <- data_complete[data_complete$crp_num      == 1, ]
sub_crp_neg <- data_complete[data_complete$crp_num      == 0, ]
sub_tlr_pos <- data_tlr[data_tlr$tlr_num == 1, ]
sub_tlr_neg <- data_tlr[data_tlr$tlr_num == 0, ]
sub_tmb_pos <- data_complete[data_complete$tmb_braf_num == 1, ]
sub_tmb_neg <- data_complete[data_complete$tmb_braf_num == 0, ]

table1_df <- data.frame(
  Characteristic = c(
    "Patients, n",
    "Age, mean (SD)",
    "Male",
    "Female",
    "Control (FLOX alone)",
    "Experimental (FLOX/nivolumab)",
    "Deaths (OS events)",
    "PFS events (progression or death)",
    "CRP-positive (low CRP)",
    "TLR-positive (early response)",
    "TMB/BRAF-positive"
  ),
  Overall = build_col(sub_overall),
  CRP_pos = build_col(sub_crp_pos),
  CRP_neg = build_col(sub_crp_neg),
  TLR_pos = build_col(sub_tlr_pos),
  TLR_neg = build_col(sub_tlr_neg),
  TMB_pos = build_col(sub_tmb_pos),
  TMB_neg = build_col(sub_tmb_neg),
  stringsAsFactors = FALSE
)

table1_df %>%
  kable(col.names = c("Characteristic", "Overall",
                      "Positive", "Negative",
                      "Positive", "Negative",
                      "Positive", "Negative"),
        caption = "Sample Characteristics by Biomarker Status",
        booktabs = TRUE, format = report_table_format(), align = c("l", rep("c", 7))) %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  tbl_header_above(c(" " = 2, "CRP" = 2, "TLR" = 2, "TMB/BRAF" = 2),
                   bold = TRUE) %>%
  tbl_pack_rows("Demographics",          2, 4,  bold = TRUE, italic = FALSE) %>%
  tbl_pack_rows("Treatment arm",         5, 6,  bold = TRUE, italic = FALSE) %>%
  tbl_pack_rows("Outcome events",        7, 8,  bold = TRUE, italic = FALSE) %>%
  tbl_pack_rows("Biomarker prevalence",  9, 11, bold = TRUE, italic = FALSE) %>%
  tbl_footnote(general = paste0(
             "Percentages within each column use the column subgroup as denominator. ",
             "CRP/TLR/TMB-BRAF rows in the corresponding subgroup column equal 100% by definition. ",
             "Overall, CRP and TMB/BRAF columns are the primary complete-case cohort (n = ", n_total,
             "); the TLR columns and the TLR-positive row use the ", n_tlr_total,
             " patients with a first on-treatment CT scan (", n_tlr_missing,
             " early deaths have no TLR value). Sex: level 0 of the trial variable is female."),
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

## Biomarker Correlations

```{r table-correlation}
correlation_df %>%
  kable(col.names = c("Biomarker Pair", "Cramér's V", "Interpretation"),
        caption = "Biomarker Correlations (Cramér's V)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10)
```

**Note:** Cramér's V interpretation: <0.1 = Negligible, 0.1–0.3 = Weak, >0.3 = Moderate/Strong. The observed correlations are weak to negligible. While modest, any correlation among candidate biomarkers supports our decision not to use LASSO, which would arbitrarily select among correlated predictors.

\newpage

# Proportional Hazards Assumption

```{r ph-diagnostics, include=FALSE}
# =============================================================================
# PROPORTIONAL HAZARDS DIAGNOSTICS
# =============================================================================

# Fit standard coxph for Schoenfeld tests (not available in coxphf)
# Use the unified DAG-informed formula (CRP and TMB/BRAF only; TLR is a post-treatment mediator)
formula_diag_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                       crp_num:Rx + tmb_braf_num:Rx
formula_diag_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                               crp_num:Rx + tmb_braf_num:Rx

coxph_diag_os <- coxph(formula_diag_os, data = data_complete)
coxph_diag_pfs <- coxph(formula_diag_pfs, data = data_complete)

# Schoenfeld residual tests
zph_os <- cox.zph(coxph_diag_os)
zph_pfs <- cox.zph(coxph_diag_pfs)

# Extract results
zph_os_df <- as.data.frame(zph_os$table)
zph_pfs_df <- as.data.frame(zph_pfs$table)
```

## Schoenfeld Residual Tests

The proportional hazards assumption was tested using scaled Schoenfeld residuals. A significant p-value indicates potential violation of the PH assumption for that covariate.

```{r table-schoenfeld}
# Combine OS and PFS results
schoenfeld_df <- data.frame(
  Covariate = rownames(zph_os_df),
  Chi_sq_OS = round(zph_os_df$chisq, 2),
  P_OS = format_pvalue(zph_os_df$p),
  Chi_sq_PFS = round(zph_pfs_df$chisq, 2),
  P_PFS = format_pvalue(zph_pfs_df$p)
)

schoenfeld_df %>%
  kable(col.names = c("Covariate", "χ² (OS)", "p-value", "χ² (PFS)", "p-value"),
        caption = "Schoenfeld Residual Test for Proportional Hazards Assumption",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  tbl_row_spec(nrow(schoenfeld_df), bold = TRUE)
```

**Note:** GLOBAL is the omnibus test for all covariates. Individual covariate tests help identify specific PH violations.

## Log-Log Survival Plots

```{r loglog-plots, fig.height=8, fig.width=10}
# Create log-log plots by treatment arm
p1 <- create_loglog_plot(data_complete, "OSwk", "Death", "Rx",
                         "Overall Survival by Treatment")
p2 <- create_loglog_plot(data_complete, "PFSwk", "Progression", "Rx",
                         "Progression-Free Survival by Treatment")

gridExtra::grid.arrange(p1, p2, ncol = 2)
```

**Interpretation:** Approximately parallel lines on the log-log plot support the proportional hazards assumption. Crossing or converging lines suggest time-varying effects.

\newpage

# Primary Analysis: Firth-Corrected Cox Models

```{r fit-unified-model, include=FALSE}
# =============================================================================
# FIT UNIFIED DAG-INFORMED FIRTH-CORRECTED COX MODELS
# Formula: Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx
# TLR excluded: post-randomization mediator (T -> TLR -> PFS in DAG)
# =============================================================================

formula_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                   crp_num:Rx + tmb_braf_num:Rx
formula_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                          crp_num:Rx + tmb_braf_num:Rx

std_os  <- coxph(formula_os,  data = data_complete)
std_pfs <- coxph(formula_pfs, data = data_complete)

model_os  <- fit_firth_cox(formula_os,  data_complete, "Unified OS")
model_pfs <- fit_firth_cox(formula_pfs, data_complete, "Unified PFS")
```

```{r extract-results, include=FALSE}
# =============================================================================
# EXTRACT RESULTS FROM UNIFIED MODEL
# =============================================================================

results_os  <- extract_coxphf_results(model_os)
results_pfs <- extract_coxphf_results(model_pfs)

std_results_os  <- extract_coxph_results(std_os)
std_results_pfs <- extract_coxph_results(std_pfs)

primary_std_firth_row_specs <- list(
  list(label = "CRP x Rx",
       std_pat = "crp_num.*Rx|Rx.*crp_num",
       firth_pat = "crp_num.*Rx|Rx.*crp_num"),
  list(label = "TMB/BRAF x Rx",
       std_pat = "tmb_braf_num.*Rx|Rx.*tmb_braf_num",
       firth_pat = "tmb_braf_num.*Rx|Rx.*tmb_braf_num"),
  list(label = "Rx (Experimental)",
       std_pat = "^Rx[^:]+$",
       firth_pat = "^Rx[^:]+$"),
  list(label = "CRP",
       std_pat = "^crp_num$",
       firth_pat = "^crp_num$"),
  list(label = "TMB/BRAF",
       std_pat = "^tmb_braf_num$",
       firth_pat = "^tmb_braf_num$"),
  list(label = "Age",
       std_pat = "^Age$",
       firth_pat = "^Age$"),
  list(label = "Sex",
       std_pat = "^sex[^:]*$",
       firth_pat = "^sex[^:]*$")
)

std_firth_comparison_os <- build_std_firth_comparison(
  std_results_os, results_os, primary_std_firth_row_specs
)
std_firth_comparison_pfs <- build_std_firth_comparison(
  std_results_pfs, results_pfs, primary_std_firth_row_specs
)

# Convenience scalars for inline references in narrative.
# coxphf$prob (carried as P_Value) is the per-coefficient PLRT p-value.
get_pvalue_by_term <- function(results_df, pattern) {
  if (is.null(results_df)) return(NA_real_)
  idx <- grep(pattern, results_df$Term)
  if (length(idx) == 0) return(NA_real_)
  results_df$P_Value[idx[1]]
}

p_crp_os  <- get_pvalue_by_term(results_os,  "crp_num.*Rx|Rx.*crp_num")
p_tmb_os  <- get_pvalue_by_term(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
p_crp_pfs <- get_pvalue_by_term(results_pfs, "crp_num.*Rx|Rx.*crp_num")
p_tmb_pfs <- get_pvalue_by_term(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
```

## Standard Cox vs Firth

The standard Cox model is the unpenalized maximum-likelihood reference. Divergence between standard Cox and Firth estimates flags small-sample or near-separation instability that Firth corrects.

```{r table-std-firth-os}
render_std_firth_comparison_table(
  std_firth_comparison_os,
  caption = "Unified Model - Overall Survival: Standard Cox vs Firth",
  first_group_label = "Treatment x Biomarker Interactions",
  first_group_end = 2,
  second_group_label = "Main Effects and Covariates"
)
```

```{r table-std-firth-pfs}
render_std_firth_comparison_table(
  std_firth_comparison_pfs,
  caption = "Unified Model - Progression-Free Survival: Standard Cox vs Firth",
  first_group_label = "Treatment x Biomarker Interactions",
  first_group_end = 2,
  second_group_label = "Main Effects and Covariates"
)
```

## Unified Model Results

The unified DAG-informed model includes CRP (week 4, before the first nivolumab dose) and TMB/BRAF (baseline) as pre-immunotherapy biomarkers with their treatment interactions, adjusted for Age and Sex.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx`

### Overall Survival

```{r table-os}
if (!is.null(results_os)) {
  display_os <- results_os %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Unified Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interactions", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 3, nrow(display_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-pfs}
if (!is.null(results_pfs)) {
  display_pfs <- results_pfs %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Unified Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interactions", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 3, nrow(display_pfs), bold = TRUE)
}
```

\newpage

## Forest Plot

```{r forest-plot, fig.height=4, fig.width=8}
hr_crp_os  <- get_interaction_hr(results_os,  "crp_num.*Rx|Rx.*crp_num")
hr_tmb_os  <- get_interaction_hr(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
hr_crp_pfs <- get_interaction_hr(results_pfs, "crp_num.*Rx|Rx.*crp_num")
hr_tmb_pfs <- get_interaction_hr(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

forest_data <- data.frame(
  Biomarker = rep(c("CRP", "TMB/BRAF"), 2),
  Outcome   = rep(c("Overall Survival", "Progression-Free Survival"), each = 2),
  HR        = c(hr_crp_os$HR,  hr_tmb_os$HR,  hr_crp_pfs$HR,  hr_tmb_pfs$HR),
  CI_Lower  = c(hr_crp_os$CI_Lower,  hr_tmb_os$CI_Lower,  hr_crp_pfs$CI_Lower,  hr_tmb_pfs$CI_Lower),
  CI_Upper  = c(hr_crp_os$CI_Upper,  hr_tmb_os$CI_Upper,  hr_crp_pfs$CI_Upper,  hr_tmb_pfs$CI_Upper)
)
forest_data <- forest_data[complete.cases(forest_data), ]

if (nrow(forest_data) > 0) {
  ggplot(forest_data, aes(x = HR, y = Biomarker)) +
    geom_point(size = 3, color = "#0072B2") +
    geom_errorbarh(aes(xmin = CI_Lower, xmax = CI_Upper), height = 0.15, color = "#0072B2") +
    geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
    scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4),
                  labels = c("0.1", "0.25", "0.5", "1", "2", "4")) +
    facet_wrap(~ Outcome) +
    labs(
      x = "Hazard Ratio (log scale)",
      y = "",
      title = "Treatment x Biomarker Interaction (Unified Model)",
      subtitle = "Profile Likelihood 95% Confidence Intervals"
    ) +
    theme_minimal() +
    theme(panel.grid.minor = element_blank())
}
```

**Interpretation:** HR < 1 indicates that biomarker-positive patients derive greater benefit from experimental treatment (reduced hazard of death/progression). The dashed line at HR = 1 represents no differential treatment effect.

\newpage

# Sensitivity Analysis: Ridge Regression

Ridge regression (L2-penalized Cox, alpha = 0) shrinks coefficients toward zero but does not eliminate any, providing a sensitivity check for the stability of the interaction estimates. The same unified model terms are used, entered through an explicit design matrix in which the CRP x Rx and TMB/BRAF x Rx product terms are built before fitting, so each ridge interaction coefficient is the single treatment-by-biomarker contrast that the Firth model estimates (issue #153). Only the biomarker main effects (CRP and TMB/BRAF) are penalized; Age, sex, Rx and the two interaction terms carry a penalty factor of zero. The penalty lambda is chosen by 10-fold cross-validation of the partial-likelihood deviance (`glmnet::cv.glmnet`, `lambda.min`), with fold assignment seeded for reproducibility.

```{r ridge-regression, include=FALSE}
# =============================================================================
# RIDGE REGRESSION SENSITIVITY ANALYSIS (unified model), glmnet with CV lambda
#
# Why an explicit design matrix (issue #153): survival::ridge() with a factor Rx
# and `crp_num:Rx` in the formula codes the interaction for BOTH arm levels
# (RxControl:crp_num and RxExperimental:crp_num), i.e. the CRP slope within
# each arm rather than the CRP x Rx contrast. Building crp_x_rx = crp * Rx_num
# beforehand gives the same single interaction coefficient as the Firth model.
#
# Penalty design: L2 penalty on the biomarker main effects only (penalty
# factor 1 for crp and tmb_braf, 0 for Age, sex, Rx, and both interactions).
# Lambda: 10-fold CV of the Cox partial-likelihood deviance, lambda.min.
# glmnet reports no standard errors, so the ridge estimates are point estimates.
# =============================================================================

ridge_design <- function(df) {
  cbind(
    Age           = df$Age,
    sex_male      = as.numeric(df$sex == SEX_MALE_LEVEL),
    Rx            = df$Rx_num,
    crp           = df$crp_num,
    tmb_braf      = df$tmb_braf_num,
    crp_x_rx      = df$crp_num * df$Rx_num,
    tmb_braf_x_rx = df$tmb_braf_num * df$Rx_num
  )
}
ridge_penalty_factor <- c(Age = 0, sex_male = 0, Rx = 0, crp = 1, tmb_braf = 1,
                          crp_x_rx = 0, tmb_braf_x_rx = 0)
RIDGE_NFOLDS <- 10

fit_ridge_cv <- function(time, event, X, penalty_factor, seed = analysis_seed,
                         nfolds = RIDGE_NFOLDS) {
  stopifnot(identical(colnames(X), names(penalty_factor)))
  y <- survival::Surv(time, event)
  set.seed(seed)
  tryCatch({
    cvfit <- glmnet::cv.glmnet(
      x = X, y = y, family = "cox", alpha = 0,
      penalty.factor = unname(penalty_factor),
      nfolds = nfolds, standardize = TRUE
    )
    beta <- as.matrix(coef(cvfit, s = "lambda.min"))[, 1]
    list(
      cvfit = cvfit,
      lambda_min = cvfit$lambda.min,
      lambda_1se = cvfit$lambda.1se,
      coefs = data.frame(Term = names(beta), HR = exp(beta), SE = NA_real_,
                         stringsAsFactors = FALSE)
    )
  }, error = function(e) {
    warning("glmnet ridge fit failed: ", conditionMessage(e))
    NULL
  })
}

X_primary <- ridge_design(data_complete)
ridge_os_fit  <- fit_ridge_cv(data_complete$OSwk,  data_complete$Death,
                              X_primary, ridge_penalty_factor)
ridge_pfs_fit <- fit_ridge_cv(data_complete$PFSwk, data_complete$Progression,
                              X_primary, ridge_penalty_factor)
ridge_os_ok  <- !is.null(ridge_os_fit)
ridge_pfs_ok <- !is.null(ridge_pfs_fit)

get_ridge_term <- function(fit, term) {
  if (is.null(fit)) return(list(HR = NA_real_, SE = NA_real_))
  idx <- match(term, fit$coefs$Term)
  if (is.na(idx)) return(list(HR = NA_real_, SE = NA_real_))
  list(HR = fit$coefs$HR[idx], SE = NA_real_)
}

ridge_crp_os  <- get_ridge_term(ridge_os_fit,  "crp_x_rx")
ridge_tmb_os  <- get_ridge_term(ridge_os_fit,  "tmb_braf_x_rx")
ridge_crp_pfs <- get_ridge_term(ridge_pfs_fit, "crp_x_rx")
ridge_tmb_pfs <- get_ridge_term(ridge_pfs_fit, "tmb_braf_x_rx")

fmt_lambda <- function(fit) if (is.null(fit)) "--" else sprintf("%.3f", fit$lambda_min)
ridge_lambda_os  <- fmt_lambda(ridge_os_fit)
ridge_lambda_pfs <- fmt_lambda(ridge_pfs_fit)

# Qualitative label for the Firth -> ridge shift, used in the narrative so the
# wording follows the numbers (a >= 1.5-fold change in HR is called substantial).
shift_word <- function(firth_hr, ridge_hr, threshold = 1.5) {
  if (is.na(firth_hr) || is.na(ridge_hr)) return("cannot be assessed")
  ratio <- exp(abs(log(ridge_hr) - log(firth_hr)))
  if (ratio >= threshold) "changes substantially" else "changes little"
}
```

```{r table-ridge-os}
format_ridge_hr <- function(hr, se) {
  if (is.na(hr)) return("--")
  if (is.na(se)) sprintf("%.2f", hr) else sprintf("%.2f (SE: %.2f)", hr, se)
}

data.frame(
  Interaction = c("CRP x Rx", "TMB/BRAF x Rx"),
  Firth = c(
    format_hr_ci(hr_crp_os$HR, hr_crp_os$CI_Lower, hr_crp_os$CI_Upper),
    format_hr_ci(hr_tmb_os$HR, hr_tmb_os$CI_Lower, hr_tmb_os$CI_Upper)
  ),
  Ridge = c(
    format_ridge_hr(ridge_crp_os$HR, ridge_crp_os$SE),
    format_ridge_hr(ridge_tmb_os$HR, ridge_tmb_os$SE)
  )
) %>%
  kable(col.names = c("Interaction", "Firth (95% CI)", "Ridge (point est.)"),
        caption = "Overall Survival: Firth vs Ridge Regression",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = paste0("Ridge: glmnet L2 penalty (alpha = 0) on the CRP and TMB/BRAF main effects only; ",
                            "interaction product terms built before fitting; lambda by ", RIDGE_NFOLDS,
                            "-fold CV (lambda.min = ", ridge_lambda_os, "). glmnet gives no standard errors. ",
                            "A substantial shift vs Firth = estimate sensitive to regularization."),
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

```{r table-ridge-pfs}
data.frame(
  Interaction = c("CRP x Rx", "TMB/BRAF x Rx"),
  Firth = c(
    format_hr_ci(hr_crp_pfs$HR, hr_crp_pfs$CI_Lower, hr_crp_pfs$CI_Upper),
    format_hr_ci(hr_tmb_pfs$HR, hr_tmb_pfs$CI_Lower, hr_tmb_pfs$CI_Upper)
  ),
  Ridge = c(
    format_ridge_hr(ridge_crp_pfs$HR, ridge_crp_pfs$SE),
    format_ridge_hr(ridge_tmb_pfs$HR, ridge_tmb_pfs$SE)
  )
) %>%
  kable(col.names = c("Interaction", "Firth (95% CI)", "Ridge (point est.)"),
        caption = "Progression-Free Survival: Firth vs Ridge Regression",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = paste0("Ridge: glmnet L2 penalty (alpha = 0) on the CRP and TMB/BRAF main effects only; ",
                            "interaction product terms built before fitting; lambda by ", RIDGE_NFOLDS,
                            "-fold CV (lambda.min = ", ridge_lambda_pfs, "). glmnet gives no standard errors."),
           footnote_as_chunk = TRUE, threeparttable = TRUE)
```

**Interpretation:** Firth provides the best unbiased point estimate given the sample size and data structure. Ridge applies L2 shrinkage to the biomarker main effects (HR toward 1.0) with the penalty strength chosen by cross-validation; the interaction terms are unpenalized, so any movement in them reflects redistribution of the shrunken main-effect signal. Comparing the two methods reveals estimate stability: if Firth and Ridge agree closely, the estimate is robust; if the interaction moves substantially under ridge, the effect is sensitive to how the biomarker main effects are estimated in this sample.

\newpage

# Exploratory: TLR as a Predictive Biomarker (Responder Analysis)

This section presents an **exploratory responder analysis** that includes TLR (Tumor Lesion Reduction) as an effect modifier in a Cox model with the same structural form as the primary analysis. Because TLR is measured post-randomization (at the first on-treatment CT scan), this is not a treatment-selection analysis: TLR status is itself influenced by treatment, and the resulting TLR x Rx interaction is informative only as a hypothesis-generating, responder-stratified contrast. It cannot be used to guide the decision to add immunotherapy, which is made before TLR is observed. The primary causal-DAG-informed analysis remains the inferential anchor for predictive biomarker claims.

The model adjusts for the pre-immunotherapy biomarkers **CRP** and **TMB/BRAF** as prognostic main effects (their treatment interactions belong to the primary analysis and are not re-estimated here). In the ridge sensitivity model, CRP and TMB/BRAF remain **unpenalized** (well-established prognostic adjustment covariates), while the **TLR main effect and TLR x Rx interaction are penalized**. These are the post-randomization terms whose stability we want to stress-test against the small effective sample size and the partially tautological TLR-PFS association.

**Formula:** `Surv(time, event) ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx`

```{r tlr-descriptive, include=FALSE}
# Descriptive TLR statistics by treatment arm (TLR-complete subset)
tlr_by_arm <- data_tlr %>%
  group_by(Rx) %>%
  summarise(
    n = n(),
    n_tlr_pos = sum(tlr_num),
    pct_tlr_pos = round(100 * mean(tlr_num), 1)
  ) %>%
  mutate(Arm = ifelse(Rx == levels(Rx)[1], "Control (FLOX)", "Experimental (FLOX/nivo)"))
```

## Descriptive Context

### TLR Prevalence by Treatment Arm

```{r table-tlr-arm}
tlr_by_arm %>%
  select(Arm, n, n_tlr_pos, pct_tlr_pos) %>%
  kable(col.names = c("Treatment Arm", "N", "TLR-positive", "%"),
        caption = "TLR Prevalence by Treatment Arm (Descriptive)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = "TLR = Tumour Lesion Reduction >= 10% at first CT scan (post-treatment).",
           footnote_as_chunk = TRUE)
```

### Kaplan-Meier Curves Stratified by TLR

```{r km-tlr, fig.height=5, fig.width=10}
km_os_tlr  <- survfit(Surv(OSwk, Death)       ~ tlr_num, data = data_tlr)
km_pfs_tlr <- survfit(Surv(PFSwk, Progression) ~ tlr_num, data = data_tlr)

p_os <- ggsurvplot(
  km_os_tlr, data = data_tlr,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Overall Survival by TLR status",
  xlab = "Time (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

p_pfs <- ggsurvplot(
  km_pfs_tlr, data = data_tlr,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Progression-Free Survival by TLR status",
  xlab = "Time (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

gridExtra::grid.arrange(p_os, p_pfs, ncol = 2)
```

**Note:** These curves are purely descriptive and stratify by a post-treatment response variable. The observed difference in survival by TLR status reflects treatment response, not a pre-treatment patient characteristic.

\newpage

```{r fit-tlr-firth, include=FALSE}
# =============================================================================
# TLR RESPONDER-ANALYSIS FIRTH-COX MODELS
# Formula: Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx
# CRP and TMB/BRAF enter as main-effect prognostic adjustments only.
# =============================================================================

formula_tlr_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                       tlr_num + tlr_num:Rx
formula_tlr_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                              tlr_num + tlr_num:Rx

# TLR-complete subset (n = n_tlr_total): TLR is undefined for early deaths
# before the first on-treatment CT scan.
std_tlr_os  <- coxph(formula_tlr_os,  data = data_tlr)
std_tlr_pfs <- coxph(formula_tlr_pfs, data = data_tlr)

model_tlr_os  <- fit_firth_cox(formula_tlr_os,  data_tlr, "TLR OS")
model_tlr_pfs <- fit_firth_cox(formula_tlr_pfs, data_tlr, "TLR PFS")

results_tlr_os  <- extract_coxphf_results(model_tlr_os)
results_tlr_pfs <- extract_coxphf_results(model_tlr_pfs)

std_results_tlr_os  <- extract_coxph_results(std_tlr_os)
std_results_tlr_pfs <- extract_coxph_results(std_tlr_pfs)

tlr_std_firth_row_specs <- list(
  list(label = "TLR x Rx",
       std_pat = "tlr_num.*Rx|Rx.*tlr_num",
       firth_pat = "tlr_num.*Rx|Rx.*tlr_num"),
  list(label = "TLR (main effect)",
       std_pat = "^tlr_num$",
       firth_pat = "^tlr_num$"),
  list(label = "Rx (Experimental)",
       std_pat = "^Rx[^:]+$",
       firth_pat = "^Rx[^:]+$"),
  list(label = "CRP",
       std_pat = "^crp_num$",
       firth_pat = "^crp_num$"),
  list(label = "TMB/BRAF",
       std_pat = "^tmb_braf_num$",
       firth_pat = "^tmb_braf_num$"),
  list(label = "Age",
       std_pat = "^Age$",
       firth_pat = "^Age$"),
  list(label = "Sex",
       std_pat = "^sex[^:]*$",
       firth_pat = "^sex[^:]*$")
)

std_firth_comparison_tlr_os <- build_std_firth_comparison(
  std_results_tlr_os, results_tlr_os, tlr_std_firth_row_specs
)
std_firth_comparison_tlr_pfs <- build_std_firth_comparison(
  std_results_tlr_pfs, results_tlr_pfs, tlr_std_firth_row_specs
)

# PLRT p-values for the TLR x Rx interaction (for narrative)
p_tlr_os  <- get_pvalue_by_term(results_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
p_tlr_pfs <- get_pvalue_by_term(results_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")
```

## Standard Cox vs Firth

The standard Cox model is the unpenalized maximum-likelihood reference. Divergence between standard Cox and Firth estimates flags small-sample or near-separation instability that Firth corrects.

```{r table-tlr-std-firth-os}
render_std_firth_comparison_table(
  std_firth_comparison_tlr_os,
  caption = "TLR Responder Model - Overall Survival: Standard Cox vs Firth",
  first_group_label = "TLR Terms",
  first_group_end = 2,
  second_group_label = "Adjustment Covariates"
)
```

```{r table-tlr-std-firth-pfs}
render_std_firth_comparison_table(
  std_firth_comparison_tlr_pfs,
  caption = "TLR Responder Model - Progression-Free Survival: Standard Cox vs Firth",
  first_group_label = "TLR Terms",
  first_group_end = 2,
  second_group_label = "Adjustment Covariates"
)
```

## Firth-Corrected Cox Model

### Overall Survival

```{r table-tlr-firth-os}
if (!is.null(results_tlr_os)) {
  display_tlr_os <- results_tlr_os %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "TLR Responder Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_tlr_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-tlr-firth-pfs}
if (!is.null(results_tlr_pfs)) {
  display_tlr_pfs <- results_tlr_pfs %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "TLR Responder Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_tlr_pfs), bold = TRUE)
}
```

\newpage

## Ridge Sensitivity Analysis (TLR Terms Penalized)

Ridge regression is applied here with a targeted penalty: only the TLR main effect and the TLR x Rx interaction are L2-shrunk. CRP, TMB/BRAF, Age, sex, and Rx are estimated without penalty, since they enter the model as adjustment covariates whose effects are not the inferential target.

```{r tlr-ridge, include=FALSE}
# =============================================================================
# RIDGE SENSITIVITY: penalize TLR main effect + TLR x Rx interaction
# CRP and TMB/BRAF main effects remain unpenalized (prognostic adjustment)
# Rx_num is defined earlier (0 = Control, 1 = Experimental).
# survival::ridge() takes raw variables, so pre-construct the interaction.
# =============================================================================

data_tlr$tlr_x_rx <- data_tlr$tlr_num * data_tlr$Rx_num

ridge_tlr_os_ok <- TRUE
tryCatch({
  ridge_tlr_os <- coxph(
    Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
      ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
    data = data_tlr
  )
}, error = function(e) { ridge_tlr_os_ok <<- FALSE; ridge_tlr_os <<- NULL })

ridge_tlr_pfs_ok <- TRUE
tryCatch({
  ridge_tlr_pfs <- coxph(
    Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
      ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
    data = data_tlr
  )
}, error = function(e) { ridge_tlr_pfs_ok <<- FALSE; ridge_tlr_pfs <<- NULL })

ridge_tlr_os_int  <- if (!is.null(ridge_tlr_os))  extract_ridge_interaction(ridge_tlr_os,  "tlr_x_rx\\)")  else list(HR = NA, SE = NA)
ridge_tlr_pfs_int <- if (!is.null(ridge_tlr_pfs)) extract_ridge_interaction(ridge_tlr_pfs, "tlr_x_rx\\)") else list(HR = NA, SE = NA)

# Firth TLR x Rx HRs for the in-text inline summary
tlr_firth_os  <- get_interaction_hr(results_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
tlr_firth_pfs <- get_interaction_hr(results_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")

# Extract all ridge coefficients into a tidy data frame
extract_all_ridge_coefs <- function(model) {
  if (is.null(model)) return(NULL)
  ct <- summary(model)$coefficients
  data.frame(
    Term = rownames(ct),
    HR = exp(ct[, "coef"]),
    SE = ct[, "se(coef)"],
    stringsAsFactors = FALSE
  )
}

ridge_tlr_os_coefs  <- extract_all_ridge_coefs(ridge_tlr_os)
ridge_tlr_pfs_coefs <- extract_all_ridge_coefs(ridge_tlr_pfs)

# Build the full-coefficient Firth vs Ridge comparison.
# Firth coefficient names: Age, sex<level>, Rx<level>, crp_num, tmb_braf_num,
#   tlr_num, Rx<level>:tlr_num
# Ridge coefficient names: Age, sex<level>, Rx<level>, crp_num, tmb_braf_num,
#   ridge(tlr_num), ridge(tlr_x_rx)
# Ridge patterns use the closing ")" to disambiguate the TLR main effect
# from the TLR x Rx interaction.
build_tlr_comparison <- function(firth_results, ridge_coefs) {
  row_specs <- list(
    list(label = "TLR x Rx",
         firth_pat = "tlr_num.*Rx|Rx.*tlr_num",
         ridge_pat = "tlr_x_rx\\)"),
    list(label = "TLR (main effect)",
         firth_pat = "^tlr_num$",
         ridge_pat = "tlr_num\\)"),
    list(label = "Age",
         firth_pat = "^Age$",
         ridge_pat = "^Age$"),
    list(label = "Sex",
         firth_pat = "^sex",
         ridge_pat = "^sex"),
    list(label = "Rx (Experimental)",
         firth_pat = "^Rx[A-Za-z]",
         ridge_pat = "^Rx[A-Za-z]"),
    list(label = "CRP",
         firth_pat = "^crp_num$",
         ridge_pat = "^crp_num$"),
    list(label = "TMB/BRAF",
         firth_pat = "^tmb_braf_num$",
         ridge_pat = "^tmb_braf_num$")
  )

  do.call(rbind, lapply(row_specs, function(rs) {
    firth_cell <- "--"
    ridge_cell <- "--"

    if (!is.null(firth_results)) {
      f_idx <- grep(rs$firth_pat, firth_results$Term)
      if (length(f_idx) > 0) {
        firth_cell <- format_hr_ci(
          firth_results$HR[f_idx[1]],
          firth_results$CI_Lower[f_idx[1]],
          firth_results$CI_Upper[f_idx[1]]
        )
      }
    }

    if (!is.null(ridge_coefs)) {
      r_idx <- grep(rs$ridge_pat, ridge_coefs$Term)
      if (length(r_idx) > 0) {
        ridge_cell <- format_ridge_hr(
          ridge_coefs$HR[r_idx[1]],
          ridge_coefs$SE[r_idx[1]]
        )
      }
    }

    data.frame(Term = rs$label, Firth = firth_cell, Ridge = ridge_cell,
               stringsAsFactors = FALSE)
  }))
}

tlr_comparison_os  <- build_tlr_comparison(results_tlr_os,  ridge_tlr_os_coefs)
tlr_comparison_pfs <- build_tlr_comparison(results_tlr_pfs, ridge_tlr_pfs_coefs)
```

```{r table-tlr-ridge-os}
tlr_comparison_os %>%
  kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
        caption = "TLR Responder Model - Overall Survival: Firth vs Ridge, all coefficients",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
  tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(tlr_comparison_os), bold = TRUE) %>%
  tbl_footnote(general = "Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized. survival::ridge() does not produce confidence intervals; standard errors are shown for reference.",
           footnote_as_chunk = TRUE)
```

```{r table-tlr-ridge-pfs}
tlr_comparison_pfs %>%
  kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
        caption = "TLR Responder Model - Progression-Free Survival: Firth vs Ridge, all coefficients",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
  tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
  tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(tlr_comparison_pfs), bold = TRUE) %>%
  tbl_footnote(general = "Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized. survival::ridge() does not produce confidence intervals; standard errors are shown for reference.",
           footnote_as_chunk = TRUE)
```

**Interpretation:** The Firth HR is the best unbiased point estimate of the TLR x Rx interaction under penalized maximum likelihood. The ridge HR applies L2 shrinkage targeted at the TLR terms; if the ridge estimate is substantially closer to HR = 1.0 than the Firth estimate, the responder-stratified interaction is sensitive to regularization, consistent with a small-sample, partly tautological signal. Findings here are exploratory and should not be used for treatment selection, since TLR is not measurable before nivolumab starts. They may motivate landmark or formal causal-mediation analyses in future work.

\newpage

# Landmark Analysis: TLR at Week 9

The responder analysis above treats TLR status as if it were known at baseline. It is not: TLR is measured at the first on-treatment CT scan, so a patient can only be classified TLR-positive or TLR-negative *after* surviving (and remaining progression-free) long enough to reach that scan. Conditioning survival on a post-baseline response therefore induces **guarantee-time (immortal-time) bias** — TLR-classified patients are, by construction, a more favourable risk set than the full randomized population.

A **landmark analysis** removes this bias by (i) fixing a landmark time, (ii) restricting to patients still at risk after the landmark, and (iii) measuring survival **from the landmark onward**. The primary landmark is **week 9**, the protocol time of the second CT (the first on-treatment response assessment): TLR compares this scan to the baseline CT, so a patient's TLR status does not exist until that scan. The actual first on-treatment scans, however, were not all at week 9: in the trial extract they fell between weeks `r sprintf("%.1f", min(data_tlr$CT1wk))` and `r sprintf("%.1f", max(data_tlr$CT1wk))` after inclusion (median `r sprintf("%.1f", median(data_tlr$CT1wk))`). A fixed week-9 landmark therefore does not guarantee that every retained patient had reached the scan, and it does not remove every patient whose progression was recorded at the first scan. Both departures are counted below, and two sensitivity landmarks are reported: a **per-patient landmark at each patient's own first-scan date**, which by construction retains only patients progression-free after their TLR was read, and a **fixed week-12 landmark**, after the latest first scan (issue #155). This section **complements** the responder analysis above (which is retained for comparison); it does not replace it.

The three landmark definitions live in `R/tlr_landmark.R` and are shared with Figure 1 of the clinical effectiveness paper and the DAG association tests, so all three use one cohort rule: a patient enters an endpoint-specific cohort only if the endpoint time is strictly after the landmark. Because the small trial loses patients with events or censoring before the landmark, the cohort sizes and event counts are reported explicitly, and all model fits are wrapped so a too-small cohort degrades gracefully rather than aborting the render.

```{r tlr-landmark-cohort, include=FALSE}
# =============================================================================
# LANDMARK COHORT CONSTRUCTION (issue #155)
# All three landmark definitions come from tlr_landmark.R, shared with
# clin_effect_figure1.qmd and the DAG association tests. Endpoint-specific
# at-risk sets, strictly after the landmark; clock reset to the landmark:
#   OS  cohort: OSwk  > landmark; analysis time OSwk_lm  = OSwk  - landmark
#   PFS cohort: PFSwk > landmark; analysis time PFSwk_lm = PFSwk - landmark
# Primary: fixed week 9. Sensitivity: per-patient first-scan date (CT1wk) and
# fixed week 12. The helper also adds the ridge product term tlr_x_rx.
# =============================================================================
LANDMARK_WK <- tlr_landmark_spec("week9")$week

# Landmark cohorts are built from the TLR-complete subset (the responder
# analysis cohort), so attrition is measured against n_tlr_total.
lm_all  <- build_all_tlr_landmark_cohorts(data_tlr)
lm_main <- lm_all$week9

data_lm_os  <- lm_main$os
data_lm_pfs <- lm_main$pfs

# Attrition / sample-size accounting
lm_attrition <- lm_main$attrition

# Characterize the PFS exclusions and the two departures of a fixed week-9
# landmark from the "reached the scan" ideal. Because progression and TLR are
# read from the SAME first on-treatment scan, patients who progress at that
# scan are TLR-negative by construction; a fixed week-9 cut removes only those
# whose scan fell before week 9 and keeps the rest with landmark times under
# one week, and it keeps patients whose TLR was read after week 9.
lm_diag             <- lm_main$diagnostics
n_pfs_excl          <- lm_diag$n_pfs_excluded
n_pfs_excl_prog     <- lm_diag$n_pfs_excl_progressed
n_pfs_excl_prog_tn  <- lm_diag$n_pfs_excl_progressed_tlr_neg
n_os_excl_death     <- lm_diag$n_os_excl_deaths
n_first_scan_prog   <- lm_diag$n_first_scan_progressors
n_first_scan_kept   <- lm_diag$n_first_scan_progressors_kept
n_scan_after_kept   <- lm_diag$n_scan_after_landmark_kept
scan_wk_range       <- range(data_tlr$CT1wk)
```

## Landmark Cohort and Attrition

```{r table-lm-attrition}
lm_attrition %>%
  kable(col.names = c("Endpoint", "N in TLR-complete cohort",
                      "N at risk at week 9", "N excluded (event/censor < week 9)",
                      "Events from week 9"),
        caption = "Week-9 landmark cohort: attrition and remaining events",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  tbl_footnote(general = "Patients with death, progression, or censoring before week 9 are excluded from the corresponding endpoint. Survival is measured from week 9 onward.",
           footnote_as_chunk = TRUE)
```

## Descriptive Context (Landmark Cohort)

### Characteristics of the Week-9 Landmark Cohorts by TLR Status

The two tables below describe the patients who enter the landmark analysis, overall and split by the TLR status that becomes defined at the week-9 scan. The at-risk set is endpoint-specific: the **overall-survival** cohort keeps everyone alive at week 9, whereas the **progression-free-survival** cohort additionally drops patients who had already progressed by week 9. The PFS cohort is therefore smaller. Reporting both fixes the denominators for the OS and PFS models that follow and makes the composition of the two TLR groups directly comparable.

```{r lm-characteristics, include=FALSE}
# =============================================================================
# LANDMARK COHORT CHARACTERISTICS, split by TLR status.
# Two endpoint-specific at-risk sets:
#   OS  cohort (data_lm_os):  OSwk  >= 9  (alive at week 9)
#   PFS cohort (data_lm_pfs): PFSwk >= 9  (alive AND progression-free at week 9)
# Note on sex: the source column is "Sex 0female", so sex == 0 is female.
# =============================================================================
format_n_pct <- function(count, n) {
  if (n == 0) return("--")
  sprintf("%d (%.1f%%)", count, 100 * count / n)
}

summarise_lm_cohort <- function(df) {
  n <- nrow(df)
  sex_num <- as.numeric(as.character(df$sex))
  c(
    sprintf("%d", n),
    sprintf("%.1f (%.1f)", mean(df$Age), sd(df$Age)),
    format_n_pct(sum(sex_num == 0), n),
    format_n_pct(sum(df$Rx == levels(df$Rx)[1]), n),
    format_n_pct(sum(df$Rx == levels(df$Rx)[2]), n),
    format_n_pct(sum(df$Death), n),
    format_n_pct(sum(df$Progression), n),
    format_n_pct(sum(df$crp_num), n),
    format_n_pct(sum(df$tmb_braf_num), n)
  )
}

build_lm_characteristics <- function(df) {
  data.frame(
    Characteristic = c("n", "Age, years, mean (SD)", "Female sex",
                       "Control arm (FLOX)", "Experimental arm (FLOX/nivolumab)",
                       "Deaths (OS events)", "PFS events (progression or death)",
                       "CRP-positive", "TMB/BRAF-positive"),
    All     = summarise_lm_cohort(df),
    TLR_pos = summarise_lm_cohort(df[df$tlr_num == 1, ]),
    TLR_neg = summarise_lm_cohort(df[df$tlr_num == 0, ]),
    stringsAsFactors = FALSE
  )
}

lm_characteristics_os  <- build_lm_characteristics(data_lm_os)
lm_characteristics_pfs <- build_lm_characteristics(data_lm_pfs)

render_lm_char_table <- function(char_df, caption) {
  tbl <- char_df %>%
    kable(col.names = c("Characteristic", "At-risk cohort", "TLR-positive", "TLR-negative"),
          caption = caption, booktabs = TRUE, align = c("l", "r", "r", "r"),
          format = if (knitr::is_latex_output()) "latex" else "pipe")
  if (knitr::is_latex_output()) {
    tbl %>% tbl_style(latex_options = c("hold_position"), font_size = 9)
  } else {
    tbl
  }
}
```

#### Overall-survival at-risk set (OSwk > 9)

```{r table-lm-characteristics-os}
render_lm_char_table(
  lm_characteristics_os,
  "Characteristics of the week-9 OS landmark cohort (alive at week 9), by TLR status"
)
```

Because no patient dies or is censored before week 9, the OS at-risk set coincides with the full TLR-complete cohort (n = `r nrow(data_lm_os)`; the three early deaths without a TLR value are already outside this cohort).

#### Progression-free-survival at-risk set (PFSwk > 9)

```{r table-lm-characteristics-pfs}
render_lm_char_table(
  lm_characteristics_pfs,
  "Characteristics of the week-9 PFS landmark cohort (alive and progression-free at week 9), by TLR status"
)
```

The PFS at-risk set drops the `r nrow(data_lm_os) - nrow(data_lm_pfs)` patient(s) who had already progressed, died, or were censored by week 9, leaving n = `r nrow(data_lm_pfs)`.

*Definitions:* percentages are column percentages; the "Deaths" and "PFS events" rows count events over the whole follow-up, not only after the landmark. CRP-positive = CRP < 5 mg/L; TMB/BRAF-positive = TMB >= 9 mut/Mb or BRAF mutation; TLR-positive = tumour lesion reduction >= 10% at the first on-treatment CT.

**Note:** In both cohorts the two TLR groups are well matched on age, sex, and TMB/BRAF status, but differ sharply on treatment arm and CRP: the TLR-positive group is enriched for control-arm patients and for CRP-positivity, while every TLR-negative patient died during follow-up. These imbalances are the descriptive counterpart of the interaction estimates below and reinforce that TLR status is realised after randomization rather than being a baseline characteristic.

### TLR Prevalence by Treatment Arm at Week 9

```{r table-lm-tlr-arm}
tlr_by_arm_lm <- data_lm_os %>%
  group_by(Rx) %>%
  summarise(
    n = n(),
    n_tlr_pos = sum(tlr_num),
    pct_tlr_pos = round(100 * mean(tlr_num), 1),
    .groups = "drop"
  ) %>%
  mutate(Arm = ifelse(Rx == levels(Rx)[1], "Control (FLOX)", "Experimental (FLOX/nivo)"))

tlr_by_arm_lm %>%
  select(Arm, n, n_tlr_pos, pct_tlr_pos) %>%
  kable(col.names = c("Treatment Arm", "N", "TLR-positive", "%"),
        caption = "TLR Prevalence by Treatment Arm, Week-9 Landmark Cohort (OS at-risk set)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position"), font_size = 10) %>%
  tbl_footnote(general = "Restricted to patients alive at week 9. TLR = Tumour Lesion Reduction >= 10% at first CT scan.",
           footnote_as_chunk = TRUE)
```

### Landmark Kaplan-Meier Curves Stratified by TLR

```{r km-lm-tlr, fig.height=5, fig.width=10}
km_os_tlr_lm  <- survfit(Surv(OSwk_lm, Death)        ~ tlr_num, data = data_lm_os)
km_pfs_tlr_lm <- survfit(Surv(PFSwk_lm, Progression) ~ tlr_num, data = data_lm_pfs)

p_os_lm <- ggsurvplot(
  km_os_tlr_lm, data = data_lm_os,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Overall Survival by TLR status (from week 9)",
  xlab = "Time since landmark (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

p_pfs_lm <- ggsurvplot(
  km_pfs_tlr_lm, data = data_lm_pfs,
  pval = TRUE, conf.int = FALSE,
  legend.labs = c("TLR-negative", "TLR-positive"),
  title = "Progression-Free Survival by TLR status (from week 9)",
  xlab = "Time since landmark (weeks)", ylab = "Survival probability",
  ggtheme = theme_minimal()
)$plot

gridExtra::grid.arrange(p_os_lm, p_pfs_lm, ncol = 2)
```

**Note:** Follow-up time is measured from the week-9 landmark. All patients shown were alive (OS) or alive and progression-free (PFS) at the landmark, so the curves are free of the guarantee-time bias affecting the responder-analysis curves above.

\newpage

```{r fit-lm-tlr-firth, include=FALSE}
# =============================================================================
# LANDMARK FIRTH-COX MODELS (TLR responder form, conditioned on week-9 survival)
# Formula: Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx, time reset to landmark
# Reuses tlr_std_firth_row_specs defined in the responder section above.
# =============================================================================
formula_lm_tlr_os  <- Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                             tlr_num + tlr_num:Rx
formula_lm_tlr_pfs <- Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                                    tlr_num + tlr_num:Rx

std_lm_tlr_os  <- tryCatch(coxph(formula_lm_tlr_os,  data = data_lm_os),  error = function(e) NULL)
std_lm_tlr_pfs <- tryCatch(coxph(formula_lm_tlr_pfs, data = data_lm_pfs), error = function(e) NULL)

model_lm_tlr_os  <- tryCatch(fit_firth_cox(formula_lm_tlr_os,  data_lm_os,  "Landmark TLR OS"),  error = function(e) NULL)
model_lm_tlr_pfs <- tryCatch(fit_firth_cox(formula_lm_tlr_pfs, data_lm_pfs, "Landmark TLR PFS"), error = function(e) NULL)

results_lm_tlr_os  <- if (!is.null(model_lm_tlr_os))  extract_coxphf_results(model_lm_tlr_os)  else NULL
results_lm_tlr_pfs <- if (!is.null(model_lm_tlr_pfs)) extract_coxphf_results(model_lm_tlr_pfs) else NULL

std_results_lm_tlr_os  <- if (!is.null(std_lm_tlr_os))  extract_coxph_results(std_lm_tlr_os)  else NULL
std_results_lm_tlr_pfs <- if (!is.null(std_lm_tlr_pfs)) extract_coxph_results(std_lm_tlr_pfs) else NULL

std_firth_comparison_lm_tlr_os <- if (!is.null(std_results_lm_tlr_os) && !is.null(results_lm_tlr_os))
  build_std_firth_comparison(std_results_lm_tlr_os, results_lm_tlr_os, tlr_std_firth_row_specs) else NULL
std_firth_comparison_lm_tlr_pfs <- if (!is.null(std_results_lm_tlr_pfs) && !is.null(results_lm_tlr_pfs))
  build_std_firth_comparison(std_results_lm_tlr_pfs, results_lm_tlr_pfs, tlr_std_firth_row_specs) else NULL

# PLRT p-values for the landmark TLR x Rx interaction (for narrative)
p_lm_tlr_os  <- if (!is.null(results_lm_tlr_os))  get_pvalue_by_term(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num") else NA
p_lm_tlr_pfs <- if (!is.null(results_lm_tlr_pfs)) get_pvalue_by_term(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num") else NA
```

## Standard Cox vs Firth (Landmark)

```{r table-lm-tlr-std-firth-os}
if (!is.null(std_firth_comparison_lm_tlr_os)) {
  render_std_firth_comparison_table(
    std_firth_comparison_lm_tlr_os,
    caption = "Landmark (Week 9) TLR Model - Overall Survival: Standard Cox vs Firth",
    first_group_label = "TLR Terms",
    first_group_end = 2,
    second_group_label = "Adjustment Covariates"
  )
}
```

```{r table-lm-tlr-std-firth-pfs}
if (!is.null(std_firth_comparison_lm_tlr_pfs)) {
  render_std_firth_comparison_table(
    std_firth_comparison_lm_tlr_pfs,
    caption = "Landmark (Week 9) TLR Model - Progression-Free Survival: Standard Cox vs Firth",
    first_group_label = "TLR Terms",
    first_group_end = 2,
    second_group_label = "Adjustment Covariates"
  )
}
```

## Firth-Corrected Cox Model (Landmark)

### Overall Survival

```{r table-lm-tlr-firth-os}
if (!is.null(results_lm_tlr_os)) {
  display_lm_tlr_os <- results_lm_tlr_os %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_lm_tlr_os %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Landmark TLR Model: Overall Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_lm_tlr_os), bold = TRUE)
}
```

### Progression-Free Survival

```{r table-lm-tlr-firth-pfs}
if (!is.null(results_lm_tlr_pfs)) {
  display_lm_tlr_pfs <- results_lm_tlr_pfs %>%
    mutate(
      HR_CI  = format_hr_ci(HR, CI_Lower, CI_Upper),
      PLRT_p = format_pvalue(P_Value)
    ) %>%
    select(Term, HR_CI, PLRT_p)

  display_lm_tlr_pfs %>%
    kable(col.names = c("Term", "HR (95% CI)", "PLRT p-value"),
          caption = "Landmark TLR Model: Progression-Free Survival - Full Coefficient Table",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("Treatment x Biomarker Interaction", 1, 1, bold = TRUE) %>%
    tbl_pack_rows("Main Effects and Covariates", 2, nrow(display_lm_tlr_pfs), bold = TRUE)
}
```

\newpage

## Ridge Sensitivity Analysis (Landmark, TLR Terms Penalized)

Ridge regression is applied to the landmark cohorts with the same targeted penalty as the responder analysis: only the TLR main effect and the TLR x Rx interaction are L2-shrunk, while Age, sex, Rx, CRP, and TMB/BRAF remain unpenalized.

```{r lm-tlr-ridge, include=FALSE}
# Reuses build_tlr_comparison() and extract_all_ridge_coefs() defined in the
# responder ridge chunk above. Models fitted on the week-9 landmark cohorts.
ridge_lm_tlr_os <- tryCatch(
  coxph(Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
        data = data_lm_os),
  error = function(e) NULL)

ridge_lm_tlr_pfs <- tryCatch(
  coxph(Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE),
        data = data_lm_pfs),
  error = function(e) NULL)

ridge_lm_tlr_os_int  <- if (!is.null(ridge_lm_tlr_os))  extract_ridge_interaction(ridge_lm_tlr_os,  "tlr_x_rx\\)")  else list(HR = NA, SE = NA)
ridge_lm_tlr_pfs_int <- if (!is.null(ridge_lm_tlr_pfs)) extract_ridge_interaction(ridge_lm_tlr_pfs, "tlr_x_rx\\)") else list(HR = NA, SE = NA)

# Firth landmark TLR x Rx HRs for the in-text inline summary
lm_tlr_firth_os  <- if (!is.null(results_lm_tlr_os))  get_interaction_hr(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num") else list(HR = NA, CI_Lower = NA, CI_Upper = NA)
lm_tlr_firth_pfs <- if (!is.null(results_lm_tlr_pfs)) get_interaction_hr(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num") else list(HR = NA, CI_Lower = NA, CI_Upper = NA)

ridge_lm_tlr_os_coefs  <- extract_all_ridge_coefs(ridge_lm_tlr_os)
ridge_lm_tlr_pfs_coefs <- extract_all_ridge_coefs(ridge_lm_tlr_pfs)

lm_tlr_comparison_os  <- if (!is.null(results_lm_tlr_os))  build_tlr_comparison(results_lm_tlr_os,  ridge_lm_tlr_os_coefs)  else NULL
lm_tlr_comparison_pfs <- if (!is.null(results_lm_tlr_pfs)) build_tlr_comparison(results_lm_tlr_pfs, ridge_lm_tlr_pfs_coefs) else NULL
```

```{r table-lm-tlr-ridge-os}
if (!is.null(lm_tlr_comparison_os)) {
  lm_tlr_comparison_os %>%
    kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
          caption = "Landmark TLR Model - Overall Survival: Firth vs Ridge, all coefficients",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(lm_tlr_comparison_os), bold = TRUE) %>%
    tbl_footnote(general = "Week-9 landmark cohort. Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized.",
             footnote_as_chunk = TRUE)
}
```

```{r table-lm-tlr-ridge-pfs}
if (!is.null(lm_tlr_comparison_pfs)) {
  lm_tlr_comparison_pfs %>%
    kable(col.names = c("Term", "Firth (95% CI)", "Ridge HR (SE)"),
          caption = "Landmark TLR Model - Progression-Free Survival: Firth vs Ridge, all coefficients",
          booktabs = TRUE, format = report_table_format()) %>%
    tbl_style(latex_options = c("hold_position"), font_size = 9) %>%
    tbl_pack_rows("TLR Terms (Ridge-penalized)", 1, 2, bold = TRUE) %>%
    tbl_pack_rows("Adjustment Covariates (Ridge-unpenalized)", 3, nrow(lm_tlr_comparison_pfs), bold = TRUE) %>%
    tbl_footnote(general = "Week-9 landmark cohort. Ridge applies L2 shrinkage to the TLR main effect and the TLR x Rx interaction only; Age, sex, Rx, CRP, and TMB/BRAF are unpenalized.",
             footnote_as_chunk = TRUE)
}
```

**Interpretation:** The two endpoints behave very differently under the landmark, and the contrast is itself informative.

*Overall survival* is clean: `r lm_attrition$N_excluded[1]` patient(s) are excluded (no deaths occur before week 9), so the landmark OS cohort is the full TLR-complete population and the landmark Firth TLR x Rx HR (`r format_hr_ci(lm_tlr_firth_os$HR, lm_tlr_firth_os$CI_Lower, lm_tlr_firth_os$CI_Upper)`) is **identical** to the responder estimate (`r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)`) — a Cox model is invariant to a common shift of the time origin when no one leaves the risk set. The OS responder signal is therefore not an early-death guarantee-time artefact.

*Progression-free survival* exposes a deeper problem. `r lm_attrition$N_excluded[2]` patients are excluded, of whom `r n_pfs_excl_prog` progressed, `r n_pfs_excl_prog_tn` of them **TLR-negative**. This is not a coincidence: progression and TLR are read from the *same* first on-treatment scan, so a patient whose tumour grows at that scan is simultaneously classified as a progression and as TLR-negative. In total `r n_first_scan_prog` patients progressed at their first scan, all TLR-negative. The fixed week-9 cut removes only the `r n_first_scan_prog - n_first_scan_kept` whose scan fell before week 9 and **keeps `r n_first_scan_kept`** whose scan fell after it, with landmark times of `r sprintf("%.1f", lm_diag$min_pfs_lm)` to `r sprintf("%.1f", max(data_lm_pfs$PFSwk_lm[data_lm_pfs$PFSwk == data_lm_pfs$CT1wk]))` weeks; it also keeps `r n_scan_after_kept` patients whose TLR was read after week 9, so for them the landmark covariate is measured after the landmark. Even so, the landmark shifts the Firth TLR x Rx HR from `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` (responder) to `r format_hr_ci(lm_tlr_firth_pfs$HR, lm_tlr_firth_pfs$CI_Lower, lm_tlr_firth_pfs$CI_Upper)` (week-9 landmark). The responder PFS association is thus **partly tautological** — TLR-negativity and early progression are the same measurement — which the landmark makes explicit by excluding the coupled events. The sensitivity landmarks below remove all `r n_first_scan_prog` first-scan progressors.

### Landmark Sensitivity: Scan-Date and Week-12 Landmarks

```{r lm-sensitivity, include=FALSE}
# Repeat the landmark Firth TLR x Rx model under each landmark definition.
# The formulas are the week-9 ones; only the cohort and the time origin change.
lm_sens_rows <- lapply(lm_all, function(lm_obj) {
  dg <- lm_obj$diagnostics
  fit_lm <- function(formula, df, label) {
    m <- tryCatch(fit_firth_cox(formula, df, label), error = function(e) NULL)
    if (is.null(m)) return(list(hr = list(HR = NA, CI_Lower = NA, CI_Upper = NA), p = NA))
    r <- extract_coxphf_results(m)
    list(hr = get_interaction_hr(r, "tlr_num.*Rx|Rx.*tlr_num"),
         p = get_pvalue_by_term(r, "tlr_num.*Rx|Rx.*tlr_num"))
  }
  os_fit  <- fit_lm(formula_lm_tlr_os,  lm_obj$os,  paste("Landmark", lm_obj$spec$id, "OS"))
  pfs_fit <- fit_lm(formula_lm_tlr_pfs, lm_obj$pfs, paste("Landmark", lm_obj$spec$id, "PFS"))
  data.frame(
    Landmark = lm_obj$spec$label,
    N_os = dg$n_os,
    N_pfs = dg$n_pfs,
    PFS_events = sum(lm_obj$pfs$Progression),
    First_scan_kept = dg$n_first_scan_progressors_kept,
    Scan_after = dg$n_scan_after_landmark_kept,
    OS_HR = format_hr_ci(os_fit$hr$HR, os_fit$hr$CI_Lower, os_fit$hr$CI_Upper),
    OS_p = format_pvalue(os_fit$p),
    PFS_HR = format_hr_ci(pfs_fit$hr$HR, pfs_fit$hr$CI_Lower, pfs_fit$hr$CI_Upper),
    PFS_p = format_pvalue(pfs_fit$p),
    stringsAsFactors = FALSE
  )
})
lm_sensitivity <- do.call(rbind, lm_sens_rows)
rownames(lm_sensitivity) <- NULL

lm_sens_pfs_hr <- setNames(lm_sensitivity$PFS_HR, names(lm_all))
lm_sens_pfs_p  <- setNames(lm_sensitivity$PFS_p,  names(lm_all))
lm_sens_n_pfs  <- setNames(lm_sensitivity$N_pfs,  names(lm_all))
```

```{r table-lm-sensitivity}
lm_sensitivity %>%
  kable(col.names = c("Landmark", "N (OS)", "N (PFS)", "PFS events",
                      "First-scan progressors retained", "TLR read after landmark",
                      "OS TLR x Rx HR (95% CI)", "PLRT p",
                      "PFS TLR x Rx HR (95% CI)", "PLRT p"),
        caption = "TLR x Rx interaction under three landmark definitions (Firth Cox, full adjustment set)",
        booktabs = TRUE, format = report_table_format()) %>%
  tbl_style(latex_options = c("hold_position", "scale_down"), font_size = 8) %>%
  tbl_footnote(general = sprintf("Cohorts are patients with the endpoint time strictly after the landmark; time is measured from the landmark. First on-treatment scans fell between weeks %.1f and %.1f after inclusion. 'First-scan progressors retained' counts patients whose progression was recorded at the first scan (TLR-negative by construction) but who remain in the PFS cohort; 'TLR read after landmark' counts retained PFS patients whose first scan came after the landmark. The per-patient landmark sets both to zero by construction.", scan_wk_range[1], scan_wk_range[2]),
           threeparttable = TRUE)
```

The per-patient scan-date landmark and the week-12 landmark both exclude all `r n_first_scan_prog` first-scan progressors (PFS cohort n = `r lm_sens_n_pfs["scan"]` and `r lm_sens_n_pfs["week12"]` versus `r lm_sens_n_pfs["week9"]` at week 9) and give a PFS TLR x Rx HR of `r lm_sens_pfs_hr["scan"]` (PLRT p `r lm_sens_pfs_p["scan"]`) and `r lm_sens_pfs_hr["week12"]` (p `r lm_sens_pfs_p["week12"]`), against `r lm_sens_pfs_hr["week9"]` (p `r lm_sens_pfs_p["week9"]`) at week 9. No patient dies before week 12, so the OS estimate is unchanged under every landmark. The direction of the PFS estimate is therefore not an artefact of the three first-scan progressors that the week-9 cut retains, but the confidence intervals are wide under every definition.

Neither analysis resolves the most fundamental issue: TLR lies on the causal path of treatment (Rx -> TLR -> outcome), so the TLR x Rx contrast is not a baseline patient-selection estimate under any time origin; disentangling it would require formal causal mediation, not a landmark. All estimates remain exploratory and imprecise (week-9 PLRT p `r format_pvalue(p_lm_tlr_os)` OS, `r format_pvalue(p_lm_tlr_pfs)` PFS) and must not guide treatment selection.

\newpage

```{r discussion-values, include=FALSE}
# Values quoted in the Discussion and Summary are pulled from the objects
# computed above so the prose cannot drift from the tables.
get_zph_p <- function(zph_df, pattern) {
  idx <- grep(pattern, rownames(zph_df))
  if (length(idx) == 0) NA_real_ else zph_df$p[idx[1]]
}
p_zph_os_global  <- get_zph_p(zph_os_df,  "^GLOBAL$")
p_zph_pfs_global <- get_zph_p(zph_pfs_df, "^GLOBAL$")
p_zph_pfs_crp    <- get_zph_p(zph_pfs_df, "^crp_num$")
p_zph_pfs_tmb    <- get_zph_p(zph_pfs_df, "^tmb_braf_num$")
p_zph_pfs_crp_rx <- get_zph_p(zph_pfs_df, "crp_num.*Rx|Rx.*crp_num")
p_zph_pfs_tmb_rx <- get_zph_p(zph_pfs_df, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# Firth HR (95% CI) and point-estimate shorthands
hr_txt <- function(x) format_hr_ci(x$HR, x$CI_Lower, x$CI_Upper)
hr_pt  <- function(x) if (is.na(x$HR)) "--" else sprintf("%.2f", x$HR)

# Unadjusted Firth Cox CRP -> PFS on the complete-case cohort: the DAG
# association test quoted in the Discussion, with the specification of
# run_dag_edge_tests() in dag_association_tests.R (issue #157).
dag_crp_pfs_fit <- coxphf::coxphf(
  Surv(PFSwk, Progression) ~ crp_num, data = data_complete,
  firth = TRUE, pl = TRUE, maxit = 100, maxstep = 0.1
)
dag_crp_pfs_hr <- exp(unname(dag_crp_pfs_fit$coefficients["crp_num"]))
dag_crp_pfs_p <- unname(dag_crp_pfs_fit$prob["crp_num"])
```

# Discussion

## Primary interaction results

Neither biomarker-treatment interaction reached conventional significance in the unified model (Firth HR with 95% CI in parentheses). For **overall survival**, CRP × Rx yielded HR `r hr_txt(hr_crp_os)` (PLRT p = `r format_pvalue(p_crp_os)`) and TMB/BRAF × Rx HR `r hr_txt(hr_tmb_os)` (p = `r format_pvalue(p_tmb_os)`) — point estimates close to null with very wide confidence intervals. For **progression-free survival**, the CRP × Rx interaction was directionally favourable but imprecise (HR `r hr_txt(hr_crp_pfs)`, p = `r format_pvalue(p_crp_pfs)`): CRP-positive patients in the experimental arm had a lower estimated hazard of progression or death than CRP-positive controls, though the CI spans more than an order of magnitude and includes 1. The TMB/BRAF × Rx PFS interaction was HR `r hr_txt(hr_tmb_pfs)` (p = `r format_pvalue(p_tmb_pfs)`). These results are consistent with the trial being underpowered to detect treatment-effect heterogeneity (n = `r n_total`, `r sum(data_complete$Progression)` PFS events (progression or death), `r sum(data_complete$Death)` deaths): even a moderate subgroup effect (HR ~0.5) would require far larger samples for reliable estimation.

The PFS pattern is worth noting as a hypothesis-generating finding. The CRP direction (HR `r hr_pt(hr_crp_pfs)`) is consistent with the DAG association test showing CRP → PFS (unadjusted Firth HR `r sprintf("%.2f", dag_crp_pfs_hr)`, p = `r format_pvalue(dag_crp_pfs_p)`; see the DAG associations report) and the biological hypothesis that low CRP (reflecting lower systemic inflammation) identifies patients more likely to respond to immunotherapy. However, the OS CRP interaction estimate (HR `r hr_pt(hr_crp_os)`) is closer to null, suggesting that any PFS benefit does not clearly translate to an OS benefit in this dataset.

## Proportional hazards

The PH assumption was well supported in overall survival (Schoenfeld global p = `r format_pvalue(p_zph_os_global)`). In progression-free survival the global test indicated some departure from proportionality (p = `r format_pvalue(p_zph_pfs_global)`), and this is carried by the biomarker main effects rather than the interaction terms: CRP main effect p = `r format_pvalue(p_zph_pfs_crp)`, TMB/BRAF main effect p = `r format_pvalue(p_zph_pfs_tmb)`, versus CRP × Rx p = `r format_pvalue(p_zph_pfs_crp_rx)` and TMB/BRAF × Rx p = `r format_pvalue(p_zph_pfs_tmb_rx)`. This suggests that the prognostic hazard ratios for CRP and TMB/BRAF are not constant over time in PFS, which may reflect different kinetics of early vs late events (now including deaths) across biomarker-defined subgroups. The PFS main-effect estimates for CRP and TMB/BRAF should therefore be read as time-averaged effects; a time-varying Cox model or landmark analysis would be more appropriate for characterizing them. The interaction estimates themselves are not flagged by this diagnostic.

## Ridge regression sensitivity

The ridge model penalizes the CRP and TMB/BRAF main effects with a cross-validated lambda (OS lambda.min = `r ridge_lambda_os`, PFS lambda.min = `r ridge_lambda_pfs`) and estimates the interaction terms as pre-built product terms, so the ridge and Firth interaction coefficients are the same treatment-by-biomarker contrast. For OS, the CRP × Rx estimate `r shift_word(hr_crp_os$HR, ridge_crp_os$HR)` under this penalization (Firth HR `r hr_pt(hr_crp_os)` → Ridge HR `r hr_pt(ridge_crp_os)`), and the TMB/BRAF × Rx estimate `r shift_word(hr_tmb_os$HR, ridge_tmb_os$HR)` (`r hr_pt(hr_tmb_os)` → `r hr_pt(ridge_tmb_os)`). For PFS, the CRP × Rx estimate `r shift_word(hr_crp_pfs$HR, ridge_crp_pfs$HR)` (`r hr_pt(hr_crp_pfs)` → `r hr_pt(ridge_crp_pfs)`) and the TMB/BRAF × Rx estimate `r shift_word(hr_tmb_pfs$HR, ridge_tmb_pfs$HR)` (`r hr_pt(hr_tmb_pfs)` → `r hr_pt(ridge_tmb_pfs)`). A shift of at least 1.5-fold in the HR is labelled "substantial". Because only the main effects are penalized, any shift in an interaction term reflects redistribution of the shrunken main-effect signal rather than independent support for a particular effect size: an interaction that moves substantially is sensitive to how the biomarker main effects are estimated and should not be over-interpreted, while one that changes little is not driven by the main-effect estimates.

## TLR responder analysis (exploratory)

The exploratory responder model — `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx` — estimates the differential treatment effect between TLR-positive and TLR-negative subgroups while adjusting for the pre-immunotherapy biomarkers as prognostic main effects. The Firth-estimated TLR × Rx HR was `r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)` for overall survival and `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` for progression-free survival. The OS estimate sits **above 1.0**, which directionally implies the (TLR-positive vs TLR-negative) hazard contrast is *worse* on the experimental arm than on the control arm — the opposite of a "TLR-positive predicts immunotherapy benefit" pattern. PFS is closer to null. Ridge shrinkage of the TLR terms gives `r format_ridge_hr(ridge_tlr_os_int$HR, ridge_tlr_os_int$SE)` (OS) and `r format_ridge_hr(ridge_tlr_pfs_int$HR, ridge_tlr_pfs_int$SE)` (PFS): ridge moves the OS estimate modestly toward null but preserves the directional pattern, and barely changes the PFS estimate. PLRT p-values (`r format_pvalue(p_tlr_os)` OS, `r format_pvalue(p_tlr_pfs)` PFS) do not reach conventional significance, consistent with the wide profile-likelihood CIs in this small sample.

The directional pattern is consistent with the descriptive imbalance: TLR-positive prevalence is `r tlr_by_arm$pct_tlr_pos[1]`% in the control arm and `r tlr_by_arm$pct_tlr_pos[2]`% in the experimental arm. If TLR cleanly captured immunotherapy response one would expect higher TLR-positivity in the experimental arm, not lower. The observed prevalence pattern, together with the OS direction (HR > 1) of the TLR × Rx interaction, is more consistent with TLR acting as a **prognostic** marker (identifying chemotherapy-responsive disease, which is more prevalent in the control arm by chance or by timing) than as a predictive marker for immunotherapy benefit. Possible explanations for the imbalance include small-sample randomization imbalance, a timing artefact (TLR measured at a fixed CT that may occur during different treatment phases across arms), or genuine heterogeneity in the patient mix. Because TLR is itself influenced by treatment, the TLR × Rx interaction is a responder-stratified contrast — useful for hypothesis generation, but not a causal predictive-biomarker estimate.

## TLR landmark analysis (exploratory)

A **week-9 landmark analysis** conditions on survival to the protocol time of the second (first on-treatment) CT — the scan at which TLR is defined — and measures survival from that point, to test whether the responder signal is a guarantee-time artefact. The two endpoints diverge instructively. For **OS**, `r lm_attrition$N_excluded[1]` patients are excluded (no early deaths), so the landmark estimate is identical to the responder estimate (`r format_hr_ci(lm_tlr_firth_os$HR, lm_tlr_firth_os$CI_Lower, lm_tlr_firth_os$CI_Upper)`): the OS signal is not driven by early-death immortal time. For **PFS**, `r lm_attrition$N_excluded[2]` patients are excluded, with `r n_pfs_excl_prog_tn` of the `r n_pfs_excl_prog` excluded progressors being TLR-negative, because progression and TLR are ascertained at the same scan; removing these coupled events moves the Firth TLR × Rx HR from `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` to `r format_hr_ci(lm_tlr_firth_pfs$HR, lm_tlr_firth_pfs$CI_Lower, lm_tlr_firth_pfs$CI_Upper)`. The PFS responder association is therefore partly tautological. Because the actual first scans fell between weeks `r sprintf("%.1f", scan_wk_range[1])` and `r sprintf("%.1f", scan_wk_range[2])`, the fixed week-9 cut retains `r n_first_scan_kept` of the `r n_first_scan_prog` first-scan progressors and `r n_scan_after_kept` patients whose TLR was read after the landmark; a per-patient landmark at the scan date and a fixed week-12 landmark, which exclude all first-scan progressors, give PFS TLR × Rx HRs of `r lm_sens_pfs_hr["scan"]` and `r lm_sens_pfs_hr["week12"]`, so the direction of the estimate does not depend on the landmark choice. Under any time origin TLR remains on the causal path of treatment, so a definitive predictive-biomarker estimate would require causal mediation rather than a landmark. Both analyses remain underpowered and exploratory, and neither supports baseline treatment selection on TLR.

\newpage

# Summary

**Study:** METIMMOX-1 biomarker subgroup analysis. N = `r n_total` complete cases, `r sum(data_complete$Death)` OS events, `r sum(data_complete$Progression)` PFS events (progression or death).

**Methods:** Two Firth-corrected Cox analyses are presented. **Primary (DAG-informed):** `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + CRP:Rx + TMB/BRAF:Rx` — pre-immunotherapy biomarkers (week-4 CRP before the first nivolumab dose; baseline TMB/BRAF) as effect modifiers; TLR omitted because it is measured on treatment. **Exploratory responder analysis:** `Surv ~ Age + sex + Rx + CRP + TMB/BRAF + TLR + TLR:Rx` — adds TLR and its treatment interaction, with CRP and TMB/BRAF retained as prognostic main-effect adjustments. Profile likelihood CIs, PLRT for interaction testing. Ridge sensitivity analysis penalizes the CRP/TMB main effects in the primary model and the TLR terms (main effect + TLR:Rx) in the exploratory model.

**Proportional hazards:** No violations in OS (global p = `r format_pvalue(p_zph_os_global)`). In PFS the global test gives p = `r format_pvalue(p_zph_pfs_global)`, carried by the biomarker main effects (CRP p = `r format_pvalue(p_zph_pfs_crp)`; TMB/BRAF p = `r format_pvalue(p_zph_pfs_tmb)`) rather than the interaction terms (CRP × Rx p = `r format_pvalue(p_zph_pfs_crp_rx)`; TMB/BRAF × Rx p = `r format_pvalue(p_zph_pfs_tmb_rx)`); PFS biomarker main-effect estimates should be read as time-averaged.

**Interaction estimates:**

| Interaction | OS HR (95% CI) | PLRT p | PFS HR (95% CI) | PLRT p |
|-------------|----------------|--------|-----------------|--------|
| CRP × Rx    | `r hr_txt(hr_crp_os)` | `r format_pvalue(p_crp_os)` | `r hr_txt(hr_crp_pfs)` | `r format_pvalue(p_crp_pfs)` |
| TMB/BRAF × Rx | `r hr_txt(hr_tmb_os)` | `r format_pvalue(p_tmb_os)` | `r hr_txt(hr_tmb_pfs)` | `r format_pvalue(p_tmb_pfs)` |

No interaction is statistically significant. CRP × Rx PFS (HR `r hr_pt(hr_crp_pfs)`) is the strongest directional signal; under ridge regularization of the biomarker main effects (glmnet, CV lambda) it `r shift_word(hr_crp_pfs$HR, ridge_crp_pfs$HR)` (Ridge HR `r hr_pt(ridge_crp_pfs)`). The TMB/BRAF × Rx OS interaction `r shift_word(hr_tmb_os$HR, ridge_tmb_os$HR)` (Ridge HR `r hr_pt(ridge_tmb_os)` vs Firth `r hr_pt(hr_tmb_os)`). The PFS PH departure concerns the biomarker main effects, not the interaction terms.

**TLR responder analysis (exploratory):** Firth TLR × Rx HR `r format_hr_ci(tlr_firth_os$HR, tlr_firth_os$CI_Lower, tlr_firth_os$CI_Upper)` for OS and `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` for PFS. Ridge-penalized TLR terms: `r format_ridge_hr(ridge_tlr_os_int$HR, ridge_tlr_os_int$SE)` (OS), `r format_ridge_hr(ridge_tlr_pfs_int$HR, ridge_tlr_pfs_int$SE)` (PFS). PLRT p-values (`r format_pvalue(p_tlr_os)` OS, `r format_pvalue(p_tlr_pfs)` PFS) do not reach conventional significance in this small sample. TLR-positive prevalence: control `r tlr_by_arm$pct_tlr_pos[1]`%, experimental `r tlr_by_arm$pct_tlr_pos[2]`% — markedly higher TLR-positivity in the control arm. The OS direction (HR > 1) of TLR × Rx, combined with the prevalence pattern, is more consistent with TLR acting as a prognostic marker for chemo-responsive disease than as a predictive marker for immunotherapy benefit. Because TLR is post-randomization, this is a responder-stratified, hypothesis-generating contrast rather than a causal predictive-biomarker estimate.

**TLR week-9 landmark analysis (exploratory):** A landmark analysis conditioning on survival to the second (first on-treatment) CT in week 9 — the scan at which TLR is defined — was added. For OS, `r lm_attrition$N_excluded[1]` patients are excluded (no early deaths), so the landmark HR `r format_hr_ci(lm_tlr_firth_os$HR, lm_tlr_firth_os$CI_Lower, lm_tlr_firth_os$CI_Upper)` is identical to the responder value: the OS signal is not an early-death immortal-time artefact. For PFS, `r lm_attrition$N_excluded[2]` patients are excluded, `r n_pfs_excl_prog_tn` of the `r n_pfs_excl_prog` excluded progressors being TLR-negative because progression and TLR are read from the same scan; this shifts the HR from `r format_hr_ci(tlr_firth_pfs$HR, tlr_firth_pfs$CI_Lower, tlr_firth_pfs$CI_Upper)` (responder) to `r format_hr_ci(lm_tlr_firth_pfs$HR, lm_tlr_firth_pfs$CI_Lower, lm_tlr_firth_pfs$CI_Upper)` (landmark), exposing the PFS association as partly tautological (PLRT p `r format_pvalue(p_lm_tlr_os)` OS, `r format_pvalue(p_lm_tlr_pfs)` PFS). Because first scans fell between weeks `r sprintf("%.1f", scan_wk_range[1])` and `r sprintf("%.1f", scan_wk_range[2])`, the week-9 cut retains `r n_first_scan_kept` first-scan progressors and `r n_scan_after_kept` patients scanned after the landmark; sensitivity landmarks at each patient's scan date (PFS HR `r lm_sens_pfs_hr["scan"]`) and at week 12 (`r lm_sens_pfs_hr["week12"]`) exclude all first-scan progressors and leave the direction unchanged. Both analyses are retained for comparison; both are underpowered and exploratory, and the residual confounding from TLR being treatment-influenced needs causal mediation, not a landmark. Neither supports baseline treatment selection on TLR.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 3.7
