---
title: "Causal DAG"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  gfm:
    toc: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 9
    fig-height: 7
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup}
#| include: false
source(here::here("R/report_setup.R"))
setup_report(
  funs = c("dag_helpers", "dag_association_tests"),
  packages = c("here", "knitr", "kableExtra", "dagitty", "ggdag", "ggplot2",
               "dplyr", "ggtext"),
  set_theme = FALSE
)
```

# Introduction

This report presents the directed acyclic graph (DAG) for the METIMMOX-1 cost-effectiveness analysis. The DAG encodes the assumed causal structure between patient characteristics, biomarkers, treatment, intermediate outcomes, and survival endpoints. It was specified in DAGitty format and visualised using the **ggdag** package in R.

Three node types are distinguished:

- **Exposure** (T): the randomised treatment (alternating FLOX + nivolumab vs FLOX alone)
- **Outcomes** (PFS, OS): the clinical endpoints of interest
- **Latent** (U): unmeasured patient characteristics that act as common causes of biomarkers and/or survival

# Node Definitions

```{r node-table}
node_defs <- data.frame(
  Node = c("Age", "Sex", "U", "TMB_BRAF", "CRP", "T",
           "TxTMB", "TxCRP", "TLR", "PFS", "OS"),
  Label = c("Age", "Sex", "U", "TMB/BRAF", "CRP", "T",
            "T x TMB", "T x CRP", "TLR", "PFS", "OS"),
  Type = c("Covariate", "Covariate", "Latent",
           "Biomarker", "Biomarker", "Exposure",
           "Effect modifier", "Effect modifier", "Mediator", "Outcome", "Outcome"),
  Description = c(
    "Patient age at baseline",
    "Patient sex",
    "Unmeasured prognostic factors (latent)",
    "Combined biomarker: TMB >= 9 mut/MB or BRAF mutation",
    "C-reactive protein at week 4, before the first nivolumab dose (positive: CRP < 5 mg/L)",
    "Treatment: alternating FLOX + nivolumab vs FLOX alone",
    "Interaction between treatment and TMB/BRAF status",
    "Interaction between treatment and CRP status",
    "Target lesion reduction: at least 10% reduction in the sum of target-lesion diameters at the first on-treatment CT",
    "Progression-free survival",
    "Overall survival"
  )
)

tbl <- kable(node_defs,
             col.names = c("Node", "Display", "Type", "Description"),
             caption = "DAG node definitions",
             booktabs = TRUE)
if (knitr::is_latex_output()) {
  tbl |>
    tbl_style(latex_options = c("HOLD_position"), font_size = 10) |>
    tbl_column_spec(4, width = "7.5cm")
} else {
  tbl
}
```

**CRP timing.** The CRP node is the week-4 value (cycle 3 day 1), measured after the two FLOX cycles that both arms receive and before the first nivolumab dose, not the baseline (pre-randomization) value. It is nevertheless drawn without a `T -> CRP` edge: at week 4 no nivolumab has been given and the two arms have received identical treatment, so treatment assignment cannot yet have affected CRP. CRP is therefore a pre-immunotherapy covariate in the DAG, unlike TLR, which is read from the first on-treatment CT after nivolumab has started and is modelled as a mediator (`T -> TLR`).

# Causal Structure

```{r dag-define}
#| include: false

# `dag` is provided by dag_helpers.R.
```

```{r dag-plot}
#| fig-cap: "Causal DAG for the METIMMOX-1 analysis. Node colour indicates role: blue = exposure (T), red = outcomes (PFS, OS), green = latent variable (U), grey = covariates and intermediate variables. Solid arrows denote assumed causal effects; dashed arrows indicate the hypothesised interaction effects of T x TMB/BRAF and T x CRP on PFS and OS. Node abbreviations: T = Treatment; TxTMB = Treatment x TMB/BRAF interaction; TxCRP = Treatment x CRP interaction; TLR = target lesion reduction; U = Unmeasured confounders."
#| fig-width: 9
#| fig-height: 7

tidy_dag <- tidy_dagitty(dag)

# DAGitty uses y-down coordinates; flip to ggplot2 y-up convention
tidy_dag$data <- tidy_dag$data |>
  mutate(
    y    = 1 - y,
    yend = if_else(is.na(yend), NA_real_, 1 - yend),
    hyp  = !is.na(to) & name %in% c("TxTMB", "TxCRP") & to %in% c("PFS", "OS")
  )

# Colour palette
plot_dag(tidy_dag, dag_palette)
```

# Causal Analysis

Because T is a randomised exposure with no parents in the DAG, there are no backdoor paths from T to PFS or OS. The sections below confirm this using dagitty's formal algorithms and list the implied conditional independencies encoded by the DAG.

## Adjustment Sets

```{r adjustment-sets}
#| results: asis

report_adj <- function(dag_obj, exposure, outcome) {
  adj <- adjustmentSets(dag_obj, exposure = exposure, outcome = outcome,
                        type = "minimal")
  if (length(adj) == 0) {
    cat(sprintf(
      "**%s -> %s:** No adjustment required (randomised exposure; no open backdoor paths).\n\n",
      exposure, outcome
    ))
  } else {
    sets <- sapply(adj, function(s) {
      if (length(s) == 0) "{}" else paste0("{", paste(s, collapse = ", "), "}")
    })
    cat(sprintf("**%s -> %s:** Minimal adjustment sets: %s\n\n",
                exposure, outcome, paste(sets, collapse = "; ")))
  }
}

report_adj(dag, "T", "PFS")
report_adj(dag, "T", "OS")
```

## Implied Conditional Independencies

```{r ci-classification}
#| include: false

# Classification shared with the DAG association tests (issue #170): a
# statement holds by construction when one of its two variables is an
# interaction node whose parents (T and the biomarker) are both conditioned on.
ci_table <- function(dag_obj) {
  cov <- dag_ci_coverage(dag_obj)
  data.frame(
    Statement = cov$statement,
    Construction = ifelse(cov$definitional,
                          paste0("Yes (", cov$determined, " fixed by {Z})"), "No"),
    stringsAsFactors = FALSE
  )
}
ci_main <- ci_table(dag)
n_ci_main <- nrow(ci_main)
n_ci_main_def <- sum(ci_main$Construction != "No")
```

The DAG implies `r n_ci_main` conditional independencies. `r n_ci_main_def` of them hold by construction: the interaction nodes are deterministic (`TxTMB = T x TMB_BRAF`, `TxCRP = T x CRP`), so a statement that conditions on both parents of an interaction node and involves that node is true whatever the data. The remaining `r n_ci_main - n_ci_main_def` statements are the testable implications examined in the DAG association report.

```{r independencies}
if (n_ci_main == 0) {
  cat("The DAG implies no testable conditional independencies (saturated structure).\n")
} else {
  tbl2 <- kable(ci_main,
               col.names = c("Implied conditional independence  (X _||_ Y | {Z})",
                             "Holds by construction"),
               caption   = "Conditional independencies implied by the causal DAG",
               booktabs  = TRUE)
  if (knitr::is_latex_output()) {
    tbl2 |> tbl_style(latex_options = c("HOLD_position"), font_size = 10)
  } else {
    tbl2
  }
}
```

# Sensitivity Analysis: Excluding Age/Sex → TMB/BRAF

This sensitivity DAG removes the `Age -> TMB_BRAF` and `Sex -> TMB_BRAF` edges while keeping the remainder of the structure identical to the primary specification. The primary DAG retains these arrows on biological grounds; this sensitivity analysis shows the downstream implications of omitting them.

```{r dag-sens-define}
#| include: false

# `dag_sens` is provided by dag_helpers.R.
```

## Sensitivity DAG

```{r dag-sens-plot}
#| fig-cap: "Sensitivity DAG for the METIMMOX-1 analysis, excluding the Age -> TMB_BRAF and Sex -> TMB_BRAF edges while retaining all other assumed causal relationships. Solid arrows denote assumed causal effects; dashed arrows indicate the hypothesised interaction effects of T x TMB/BRAF and T x CRP on PFS and OS."
#| fig-width: 9
#| fig-height: 7

tidy_dag_sens <- tidy_dagitty(dag_sens)

# DAGitty uses y-down coordinates; flip to ggplot2 y-up convention
tidy_dag_sens$data <- tidy_dag_sens$data |>
  mutate(
    y    = 1 - y,
    yend = if_else(is.na(yend), NA_real_, 1 - yend),
    hyp  = !is.na(to) & name %in% c("TxTMB", "TxCRP") & to %in% c("PFS", "OS")
  )

plot_dag(tidy_dag_sens, dag_palette)
```

## Sensitivity Causal Analysis

The treatment node remains randomised in the sensitivity DAG, so the formal adjustment recommendations for `T -> PFS` and `T -> OS` are unchanged. The main difference is in the implied conditional independencies, which now reflect the omission of direct Age/Sex effects on TMB/BRAF status.

### Adjustment Sets

```{r adjustment-sets-sens}
#| results: asis

report_adj(dag_sens, "T", "PFS")
report_adj(dag_sens, "T", "OS")
```

### Implied Conditional Independencies

```{r independencies-sens}
indep_sens_df <- ci_table(dag_sens)

if (nrow(indep_sens_df) == 0) {
  cat("The sensitivity DAG implies no testable conditional independencies (saturated structure).\n")
} else {
  tbl3 <- kable(
    indep_sens_df,
    col.names = c("Implied conditional independence  (X _||_ Y | {Z})",
                  "Holds by construction"),
    caption   = "Conditional independencies implied by the sensitivity DAG",
    booktabs  = TRUE
  )
  if (knitr::is_latex_output()) {
    tbl3 |> tbl_style(latex_options = c("HOLD_position"), font_size = 10)
  } else {
    tbl3
  }
}
```

# Simplified DAG

The following DAG presents the same causal assumptions in a condensed form intended for a clinical audience. The interaction terms (T x TMB/BRAF and T x CRP), the latent common-cause node (U) and the TLR mediator have been omitted, and PFS and OS are merged into one survival node; their roles are described in the text. Age and sex are separate nodes, so that the simplified graph keeps the full DAG's covariate structure: both point to TMB/BRAF, and only age points to survival (the full DAG's `Age -> OS`; there is no edge from sex to an outcome). The dashed arrow from T to survival indicates that the magnitude of the treatment effect on survival outcomes is hypothesised to be modified by TMB/BRAF and CRP status, the central question addressed by the biomarker analysis.

```{r dag-simple-define}
#| include: false

# `dag_simple` is provided by dag_helpers.R.
```

```{r dag-simple-plot}
#| fig-cap: "Figure 3. Simplified causal DAG for METIMMOX-1. Solid arrows denote assumed causal effects. Age and sex both point to TMB/BRAF; only age points to survival, because the full DAG has an Age -> OS edge and no edge from sex to either outcome (PFS and OS are merged into one survival node, so the age arrow stands for Age -> OS). The dashed arrow indicates that the treatment effect on survival is hypothesised to be modified by TMB/BRAF and CRP status. Interaction, latent-variable and TLR nodes are shown in the full DAG. Abbreviations: CRP = C-reactive protein, OS = overall survival, PFS = progression-free survival, T = treatment, TMB = tumour mutational burden."
#| fig-width: 9
#| fig-height: 6

# Shared with clin_effect_figure_simplified_dag.qmd (plot_simple_dag() in
# dag_helpers.R), so the report and the clinical paper draw the same graph.
plot_simple_dag(dag_simple)
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.3
