---
title: "DAG Association Tests"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  gfm:
    toc: true
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup}
#| include: false
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("dag_helpers", "assoc_tests", "tlr_landmark", "dag_association_tests"),
  packages = c("here", "knitr", "kableExtra", "dplyr", "dagitty", "survival",
               "coxphf", "logistf", "coin"),
  set_theme = FALSE
)

# The canonical DAG (`dag`) comes from dag_helpers.R; this report no longer
# defines its own graph (issue #155). All datasets, including the week-9
# landmark PFS cohort for TLR -> PFS and the counting-process data for the
# time-dependent PFS -> OS test, are built by prepare_dag_data().
dd <- prepare_dag_data(data, landmark = "week9")

n_source <- nrow(dd$data)
n_main <- nrow(dd$data_main)
n_tlr <- nrow(dd$data_tlr)
n_lm_pfs <- nrow(dd$data_lm_pfs)
lm_diag <- dd$landmark$diagnostics
lm_label <- dd$landmark$spec$short_label

event_summary <- data.frame(
  Dataset = c("Source dataset after scripts 02 and 03",
              "Main complete-case dataset for survival and interaction models",
              "TLR subset with observed tlr",
              paste0("TLR landmark PFS cohort (progression-free after ",
                     tolower(lm_label), ")")),
  N = c(n_source, n_main, n_tlr, n_lm_pfs),
  Deaths = c(sum(dd$data$Death, na.rm = TRUE),
             sum(dd$data_main$Death, na.rm = TRUE),
             sum(dd$data_tlr$Death, na.rm = TRUE),
             sum(dd$data_lm_pfs$Death, na.rm = TRUE)),
  PFS_events = c(sum(dd$data$Progression, na.rm = TRUE),
                 sum(dd$data_main$Progression, na.rm = TRUE),
                 sum(dd$data_tlr$Progression, na.rm = TRUE),
                 sum(dd$data_lm_pfs$Progression, na.rm = TRUE))
)
```

```{r helpers}
#| include: false
render_table <- function(df, caption, font_size = 9,
                         landscape_pdf = FALSE, scale_down = TRUE) {
  align_string <- paste(rep("l", ncol(df)), collapse = "")
  tbl <- kable(df, caption = caption, booktabs = knitr::is_latex_output(),
               align = align_string)
  if (knitr::is_latex_output()) {
    latex_options <- c("hold_position")
    if (scale_down) {
      latex_options <- c(latex_options, "scale_down")
    }
    tbl <- tbl |>
      kable_styling(latex_options = latex_options, font_size = font_size)
    if (landscape_pdf) {
      tbl <- tbl |>
        landscape()
    }
  }
  tbl
}

edge_coverage <- dag_edge_coverage(dag)
ci_coverage <- dag_ci_coverage(dag)
n_edges_all <- length(edge_coverage$all)
n_edges_testable <- length(edge_coverage$testable)
n_edges_latent <- length(edge_coverage$latent)
n_edges_definitional <- length(edge_coverage$definitional)
n_ci_all <- nrow(ci_coverage)
n_ci_definitional <- sum(ci_coverage$definitional)
n_ci_testable <- n_ci_all - n_ci_definitional
n_ci_balance <- sum(ci_coverage$arm_balance)
```

```{r run-tests}
#| include: false
edge_results <- run_dag_edge_tests(dag, dd)
ci_results <- run_dag_ci_tests(dag, dd, seed = analysis_seed)

edge_summary_table <- edge_results |>
  mutate(`p-value` = fmt_p(p_value)) |>
  select(Edge = Item, Test, N, Effect, `p-value`, Conclusion)

ci_summary_table <- ci_results |>
  mutate(
    `p-value` = fmt_p(p_value),
    `Arm balance check` = ifelse(Randomization_Check, "Yes", "No")
  ) |>
  select(`CI statement` = Item, Test, N, Effect, `p-value`,
         `Arm balance check`, Conclusion)

consolidated_summary_table <- bind_rows(
  edge_results |>
    transmute(Domain = "Direct edge", Item, Effect,
              `p-value` = fmt_p(p_value), Conclusion),
  ci_results |>
    transmute(Domain = "Conditional independence", Item, Effect,
              `p-value` = fmt_p(p_value), Conclusion)
)

untested_edges <- data.frame(
  Edge = c(edge_coverage$latent, edge_coverage$definitional),
  Reason = c(rep("Latent parent (U is unobserved)", n_edges_latent),
             rep("Definitional (interaction node is T x biomarker)",
                 n_edges_definitional)),
  stringsAsFactors = FALSE
)

supported_edges <- edge_results |>
  filter(p_value < 0.05) |>
  pull(Item)

ci_tested <- ci_results |> filter(!Definitional)
ci_violations <- ci_tested |>
  filter(p_value < 0.05) |>
  pull(Item)

randomization_checks <- ci_results |>
  filter(Randomization_Check) |>
  mutate(`p-value` = fmt_p(p_value)) |>
  select(Item, `p-value`, Conclusion)

p_of <- function(df, item) fmt_p(df$p_value[df$Item == item])
effect_of <- function(df, item) df$Effect[df$Item == item]
```

# Introduction

This report provides the empirical companion to `dag.qmd`. The DAG encodes the assumed causal structure for METIMMOX-1; this document asks whether the observable parts of that structure are broadly compatible with the data available in the repository.

The emphasis is deliberately modest. These tests do not prove causal direction, and failure to reject a conditional independence does not verify the DAG. Instead, the report checks whether the observable arrows imply associations in the expected places and whether the DAG-implied conditional independencies look plausible in the observed sample.

# Methods

## Data and Variables

Only scripts `02_setup_and_global_variables.R` and `03_biomarker_strategies.R` were sourced. No survival-model fitting scripts were run.

The available repository extract contains `r n_source` patients after scripts 02 and 03. The main complete-case dataset used for survival and interaction models contains `r n_main` patients. TLR in the DAG corresponds to `tlr` in the data, and the TLR subset with observed `tlr` contains `r n_tlr` patients. The TLR landmark PFS cohort (patients progression-free after the `r tolower(lm_label)` landmark, see below) contains `r n_lm_pfs` patients.

Patients without follow-up CT assessment have `tlr = NA` and were excluded from TLR analyses. Those analyses therefore rely on a missing-at-random assumption conditional on the observed covariates included in each model.

```{r data-summary}
render_table(
  event_summary,
  caption = "Analysis datasets used in the DAG association report"
)
```

For the interaction nodes, `T` was coded as `T_num = 1` for the experimental arm and `0` for control, `TxTMB` was defined as `T_num * tmb_braf` and `TxCRP` as `T_num * crp`.

## Graph-derived test lists

The graph tested here is the canonical `dag` object from `dag_helpers.R`, the same object rendered in `dag.qmd`. Both the edge list and the list of implied conditional independencies are derived from that object at render time (`dagitty::edges()` and `dagitty::impliedConditionalIndependencies()`), and the report stops if the DAG implies a statement that has no prespecified test or a test targets a statement the DAG no longer implies. An earlier version typed both lists by hand from a graph without the `TxCRP` node and therefore tested 13 of the 19 implied independencies and neither `TxCRP` edge.

The DAG has `r n_edges_all` edges. `r n_edges_latent` originate from the latent node `U` and are not testable. `r n_edges_definitional` point into the constructed interaction nodes (`T -> TxTMB`, `TMB_BRAF -> TxTMB`, `T -> TxCRP`, `CRP -> TxCRP`) and hold by definition. The remaining `r n_edges_testable` edges are tested. The DAG implies `r n_ci_all` conditional independencies; `r n_ci_definitional` of them relate the two interaction nodes given `T` and hold by construction (given `T = 0` both nodes are zero, and given `T = 1` and the conditioned biomarker one of them is constant), leaving `r n_ci_testable` testable statements, of which `r n_ci_balance` are marginal statements involving `T` that double as arm-balance checks.

## Statistical Tests

Each testable edge or independence was tested using a prespecified method:

- Wilcoxon rank-sum for continuous-versus-binary comparisons
- Fisher's exact test for 2 x 2 tables
- Mantel-Haenszel tests for binary associations conditional on one binary stratifier
- Firth-corrected Cox regression (`coxphf`) for time-to-event endpoints
- Firth-corrected logistic regression (`logistf`) for TLR models
- A conditional permutation test (`coin::independence_test`) for `Age _||_ TxTMB | {TMB_BRAF}`

Two edge tests need a time origin other than randomisation (issue #155):

- **`PFS -> OS`**: progression is entered as a time-dependent indicator in a counting-process Firth Cox model for death (`survival::tmerge` on the progression-only trial event, `ProgressionExit` / `TTPwk`). Entering PFS time as a fixed covariate, as an earlier version did, is tautological because `PFSwk <= OSwk` by construction and PFS time is unknown at baseline (immortal-time bias).
- **`TLR -> PFS`**: TLR is read at the first on-treatment CT, so a test from randomisation conditions on surviving progression-free to that scan (guarantee-time bias). The edge is therefore tested on the `r tolower(lm_label)` landmark PFS cohort from `tlr_landmark.R`, the same cohort and time origin used by `clinical_effectiveness.qmd` and Figure 1 of the clinical effectiveness paper: patients progression-free after the landmark, with time measured from the landmark. Of the `r lm_diag$n_first_scan_progressors` patients whose progression is recorded at the first scan itself (all TLR-negative because progression and TLR are read from the same scan), `r lm_diag$n_first_scan_progressors_kept` remain in the week-9 cohort because their scan fell after week 9, and `r lm_diag$n_scan_after_landmark_kept` retained patients had their TLR read after the landmark. The clinical effectiveness report repeats the landmark analysis at each patient's own scan date and at week 12 as sensitivity analyses.

## Multiple Testing

No multiplicity correction was applied in this version of the report. All statistical summaries therefore use raw p-values only, and the findings should be interpreted as exploratory rather than confirmatory.

# Direct Edge Tests

## Covariate edges (Age/Sex -> TMB_BRAF)

Age and sex are the only baseline covariates with direct arrows into `TMB_BRAF`. The age association was tested with a Wilcoxon rank-sum test and the sex association with Fisher's exact test.

## Untested edges (latent and definitional)

```{r untested-edges}
render_table(
  untested_edges,
  caption = "DAG edges without an empirical test"
)
```

## Biomarker edges (TMB_BRAF, CRP -> PFS, OS, TLR)

Direct biomarker effects on `PFS` and `OS` were tested with univariable Firth Cox models in the main dataset. Direct effects on `TLR` were tested in the `tlr` subset using Firth logistic regression.

## Treatment edges (T -> PFS, OS, TLR)

Treatment effects were evaluated with `T_num` as a binary predictor, preserving the randomised-arm coding from the trial extract.

## Interaction edges (TxTMB, TxCRP -> PFS, OS)

Each interaction node was tested using the interaction coefficient from `Surv(...) ~ T_num + biomarker + T_num:biomarker` for both `PFS` and `OS`. These are the same interaction-scale questions emphasised in `clinical_effectiveness.qmd`, but used here as DAG edge checks rather than biomarker-model comparisons. The `TxCRP` edges are the ones that drive the CRP-guided strategy in the economic model.

## Mediator edge (TLR -> PFS)

The `TLR -> PFS` edge was estimated in the `r tolower(lm_label)` landmark PFS cohort (n = `r n_lm_pfs`) with time measured from the landmark, as described in Methods.

## Outcome chain (PFS -> OS)

The `PFS -> OS` edge was represented by a Firth Cox model for death with a time-dependent progression indicator (n = `r n_main` patients, `r nrow(dd$data_td)` counting-process intervals). The hazard ratio compares the death hazard after a recorded progression with the hazard before it.

## Edge summary table

```{r edge-summary}
render_table(
  edge_summary_table,
  caption = "Direct edge tests",
  font_size = 8,
  landscape_pdf = TRUE,
  scale_down = FALSE
)
```

# Conditional Independence Tests

## Arm balance (marginal CIs involving T)

The `r n_ci_balance` CI statements involving `T` without a conditioning set double as arm-balance checks. If any of them were significant, that would suggest imbalance between arms in this realised sample rather than a structural failure of the DAG. Age, Sex and TMB/BRAF are baseline characteristics, so their checks are randomisation checks in the strict sense. CRP is the week-4 value (before the first nivolumab dose, after two FLOX cycles common to both arms), so its check asks whether the arms were balanced on CRP at the point where the immunotherapy decision is made.

```{r randomization-checks}
render_table(
  randomization_checks,
  caption = "Arm balance checks implied by the DAG"
)
```

One arm-balance check, `CRP _||_ T`, was significant on the raw scale (p = `r p_of(ci_results, "CRP _||_ T")`): week-4 CRP-positivity was 17/36 in the experimental arm and 7/35 in the control arm. The baseline (cycle 1 day 1) CRP, which is not used in the analysis, was balanced (8/38 vs 7/35; Fisher p = 1), so randomisation itself was not at fault. Because both arms receive identical FLOX up to week 4 and nivolumab has not yet been given, the week-4 difference cannot be a treatment effect either; it is read as chance imbalance on a week-4 measurement in a small trial. The other checks, all on baseline characteristics, remained non-significant.

## Structural CIs (conditional)

The DAG implies `r n_ci_all` observable conditional independencies after excluding the latent node `U`. `r n_ci_definitional` hold by construction (see Methods) and are listed without a test; the remaining `r n_ci_testable` were tested using the prespecified conditional models or stratified tests. Statements that condition on `T` and a biomarker and involve the matching interaction node (for example `TLR _||_ TxTMB | {T, TMB_BRAF}`) are tested parametrically as the interaction coefficient of a Firth logistic model, because within strata of `T` and the biomarker the interaction node is constant.

## CI summary table

```{r ci-summary}
render_table(
  ci_summary_table,
  caption = "Conditional-independence tests",
  font_size = 8,
  landscape_pdf = TRUE,
  scale_down = FALSE
)
```

# Consolidated Summary Table

```{r consolidated-summary}
render_table(
  consolidated_summary_table,
  caption = "Consolidated summary of direct edge and conditional-independence tests",
  font_size = 8,
  landscape_pdf = TRUE,
  scale_down = FALSE
)
```

# Discussion

```{r discussion-text, results='asis'}
edge_n_sig <- sum(edge_results$p_value < 0.05, na.rm = TRUE)
ci_n_fail <- sum(ci_tested$p_value < 0.05, na.rm = TRUE)
ci_n_ok <- sum(ci_tested$p_value >= 0.05, na.rm = TRUE)

sig_items <- function(items) {
  items[items %in% supported_edges]
}
prognostic_sig <- sig_items(c("CRP -> PFS", "CRP -> OS", "TMB_BRAF -> PFS", "TMB_BRAF -> OS"))
tlr_in_sig <- sig_items(c("CRP -> TLR", "TMB_BRAF -> TLR", "T -> TLR"))
treatment_sig <- sig_items(c("T -> PFS", "T -> OS"))
interaction_sig <- sig_items(c("TxTMB -> PFS", "TxTMB -> OS", "TxCRP -> PFS", "TxCRP -> OS"))
covariate_sig <- sig_items(c("Age -> TMB_BRAF", "Sex -> TMB_BRAF", "Age -> OS"))

list_or_none <- function(x) if (length(x) == 0) "none" else paste(x, collapse = "; ")

# Sentences for the Conclusion, computed here so that the counts and the named
# edges cannot drift from the tables (issue #157).
interaction_sig_text <- if (length(interaction_sig) == 0) {
  "none is below p = 0.05 in this small sample"
} else {
  paste0(paste0("`", interaction_sig, "`", collapse = " and "),
         if (length(interaction_sig) == 1) " is the only one" else " are the ones",
         " below p = 0.05 in this small sample, and ",
         if (length(interaction_sig) == 1) "it" else "they",
         " should be read together with the adjusted interaction estimates in the clinical effectiveness report")
}
ci_violation_summary <- if (length(ci_violations) == 0) {
  "no conditional-independence violation"
} else {
  paste0(length(ci_violations), " conditional-independence violation",
         if (length(ci_violations) > 1) "s" else "",
         " (", paste(ci_violations, collapse = "; "), ")")
}

if (length(supported_edges) == 0) {
  supported_edge_text <- "No direct edge reached p < 0.05."
} else {
  supported_edge_text <- paste0(
    "Direct edges with p < 0.05: ",
    paste(supported_edges, collapse = "; "),
    "."
  )
}

if (length(ci_violations) == 0) {
  ci_violation_text <- "No DAG-implied conditional independence was contradicted at p < 0.05."
} else {
  ci_violation_text <- paste0(
    "Conditional independencies contradicted by the data at p < 0.05: ",
    paste(ci_violations, collapse = "; "),
    "."
  )
}

cat(paste0(
  "The direct-edge analysis found ", edge_n_sig, " of ", n_edges_testable,
  " tested edges with p < 0.05. ", supported_edge_text,
  " Among the prognostic biomarker edges, those with p < 0.05 were: ",
  list_or_none(prognostic_sig), ". Among the edges into TLR: ",
  list_or_none(tlr_in_sig), ". Among the covariate edges: ",
  list_or_none(covariate_sig), ".", "\n\n",
  "The two disease-course edges are no longer tautological. PFS -> OS, now estimated with a time-dependent progression indicator, gives HR ",
  effect_of(edge_results, "PFS -> OS"), " (p = ", p_of(edge_results, "PFS -> OS"),
  ") for death after versus before a recorded progression; this is an estimate of how much a progression raises the subsequent death hazard, not a restatement of PFS <= OS. TLR -> PFS on the ",
  tolower(lm_label), " landmark cohort gives HR ", effect_of(edge_results, "TLR -> PFS"),
  " (p = ", p_of(edge_results, "TLR -> PFS"), ", n = ", n_lm_pfs,
  "). Because progression and TLR are read from the same scan, TLR-negativity and first-scan progression are partly the same measurement; the week-9 landmark removes ",
  lm_diag$n_first_scan_progressors - lm_diag$n_first_scan_progressors_kept, " of the ", lm_diag$n_first_scan_progressors,
  " first-scan progressors and keeps ", lm_diag$n_first_scan_progressors_kept,
  ", so the estimate should be read alongside the scan-date and week-12 landmark sensitivity analyses in the clinical effectiveness report.", "\n\n",
  "Treatment-related edges: those with p < 0.05 were ", list_or_none(treatment_sig),
  " for the direct treatment edges and ", list_or_none(interaction_sig),
  " for the interaction edges. TxCRP -> PFS gives HR ", effect_of(edge_results, "TxCRP -> PFS"),
  " (p = ", p_of(edge_results, "TxCRP -> PFS"), ") and TxCRP -> OS HR ",
  effect_of(edge_results, "TxCRP -> OS"), " (p = ", p_of(edge_results, "TxCRP -> OS"),
  "); TxTMB -> PFS gives HR ", effect_of(edge_results, "TxTMB -> PFS"), " (p = ",
  p_of(edge_results, "TxTMB -> PFS"), ") and TxTMB -> OS HR ",
  effect_of(edge_results, "TxTMB -> OS"), " (p = ", p_of(edge_results, "TxTMB -> OS"),
  "). These are the same treatment-by-biomarker contrasts as the interaction terms of the economic survival model, estimated here without covariate adjustment, and the intervals are wide.", "\n\n",
  "Among the ", n_ci_testable, " tested conditional-independence statements, ", ci_n_ok,
  " were compatible with the DAG at p >= 0.05 and ", ci_n_fail,
  " were contradicted by the data. ", ci_violation_text,
  " CRP _||_ T had p = ", p_of(ci_results, "CRP _||_ T"),
  ", reflecting a chance arm imbalance in week-4 CRP (baseline CRP was balanced, and no nivolumab has been given by week 4, so this is neither a randomisation failure nor a treatment effect), and CRP _||_ TxTMB | {TMB_BRAF} had p = ",
  p_of(ci_results, "CRP _||_ TxTMB | {TMB_BRAF}"),
  ", which follows from the same arm imbalance because TxTMB is a function of T. The new statements involving TxCRP (Age _||_ TxCRP, Sex _||_ TxCRP, TMB_BRAF _||_ TxCRP | {CRP}, TLR _||_ TxCRP | {CRP, T}) had p = ",
  p_of(ci_results, "Age _||_ TxCRP"), ", ", p_of(ci_results, "Sex _||_ TxCRP"), ", ",
  p_of(ci_results, "TMB_BRAF _||_ TxCRP | {CRP}"), " and ",
  p_of(ci_results, "TLR _||_ TxCRP | {CRP, T}"),
  ". The week-4 CRP arm imbalance therefore remains the main place where the current DAG looks least secure in this dataset.", "\n\n",
  "Interpretation should remain cautious. The latent node U is unobserved, TLR analyses depend on non-missing follow-up imaging and on the landmark definition, the available repository extract is modest in size, and several tests are necessarily low-power. These checks therefore speak to empirical compatibility, not causal proof."
))
```

# Conclusion

This report adds a data-facing complement to the causal DAG by testing, from the same `dag` object that `dag.qmd` renders, every observable edge and every implied conditional independence of the graph. The prognostic biomarker edges and the two disease-course edges, now estimated with a time-dependent progression indicator and a landmark cohort rather than tautological baseline covariates, are where the empirical signal is clearest. The direct treatment edges are uncertain; of the interaction edges, `r interaction_sig_text`.

The data also surface `r ci_violation_summary` against the assumed graph, traceable to the chance arm imbalance in week-4 CRP. The most defensible takeaway is therefore that the DAG captures much of the prognostic structure in the data, while the CRP-related balance and interaction structure may need refinement or stronger justification in future versions.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.2
