---
title: "Enriched Population Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "08b"),
  funs = c("cea_helpers", "report_format"),
  set_theme = FALSE,
  quiet_sources = TRUE
)

enriched_display <- enriched_comparison %>%
  transmute(
    Biomarker,
    Prevalence = sprintf("%.1f%%", Prevalence * 100),
    Base_Cost = format_eur(Base_Cost),
    Base_Effect = sprintf("%.3f", Base_Effect),
    Base_ICER = format_icer(Base_ICER, Base_Status),
    Base_Frontier = frontier_label(Base_Frontier_Status),
    Enr_Cost = format_eur(Enr_Cost),
    Enr_Effect = sprintf("%.3f", Enr_Effect),
    Enr_Ctrl_Cost = format_eur(Enr_Ctrl_Cost),
    Enr_Ctrl_Effect = sprintf("%.3f", Enr_Ctrl_Effect),
    Enr_Screening = format_eur(Enr_Screening_Cost),
    Enr_ICER = format_icer(Enr_ICER, Enr_Status),
    Pct_Change = ifelse(is.na(Pct_Change), "--", sprintf("%+.1f%%", Pct_Change))
  )
```

# Overview

This report presents a ceiling scenario for the economic biomarkers included in the single joint model. The analysis compares biomarker-positive patients receiving FLOX + nivolumab with biomarker-positive patients receiving FLOX only.

Economic biomarkers are CRP and TMB/BRAF.

**Screening cost.** To treat one biomarker-positive patient the guided strategy must first identify one. On average 1 / prevalence patients are tested per positive found, so the experimental arm carries the expected screening cost per identified positive, the biomarker test cost divided by the canonical full-cohort prevalence, in place of a single test (issue #157). The control arm carries no test cost, because every patient receives FLOX under standard of care whether or not the biomarker is known. The screening cost is reported as its own column in the detailed table; it is `r paste(sprintf("%s for %s", format_eur(enriched_comparison$Enr_Screening_Cost), enriched_comparison$Biomarker), collapse = " and ")` per identified positive.

# Biomarker Prevalence

```{r prevalence-table}
prev_df <- strategies_df %>%
  filter(id %in% get_biomarkers()) %>%
  transmute(
    Biomarker = biomarker_label(id),
    Prevalence = sprintf("%.1f%%", prevalence * 100),
    `N Positive` = sapply(id, function(bm) sum(data[[bm]] == 1, na.rm = TRUE))
  )

knitr::kable(
  prev_df,
  booktabs = TRUE,
  align = c("l", "r", "r"),
  caption = "Economic biomarker-positive prevalences"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

# Base Case vs Enriched Population

```{r enriched-summary}
summary_cols <- c("Biomarker", "Prevalence", "Base_ICER", "Base_Frontier",
                  "Enr_ICER", "Pct_Change")

knitr::kable(
  enriched_display[, summary_cols],
  booktabs = TRUE,
  align = c("l", "r", "r", "l", "r", "r"),
  col.names = c("Biomarker", "Prevalence", "Base ICER (vs SoC)",
                "Base frontier", "Enriched ICER (vs SoC)", "Change"),
  caption = "Base case and enriched-population ICERs (pairwise versus standard of care)"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"), font_size = 9) %>%
  kableExtra::footnote(
    general = paste(
      "Both ICER columns are pairwise comparisons against standard of care.",
      "'Base Case Frontier' is the dampack efficiency-frontier status of the",
      "guided strategy among the three base-case strategies: a strategy that is",
      "dominated on the frontier (more costly and less effective than the other",
      "guided strategy) still has a finite pairwise ICER, but the percentage",
      "change between such ICERs is not meaningful and is shown as '--'."
    ),
    threeparttable = TRUE
  )
```

```{r enriched-detail}
detail_cols <- c("Biomarker", "Enr_Cost", "Enr_Effect",
                 "Enr_Ctrl_Cost", "Enr_Ctrl_Effect", "Enr_Screening", "Enr_ICER")

knitr::kable(
  enriched_display[, detail_cols],
  booktabs = TRUE,
  align = c("l", "r", "r", "r", "r", "r", "r"),
  col.names = c("Biomarker", "Experimental Cost", "Experimental QALYs",
                "Control Cost", "Control QALYs",
                "Screening cost per identified positive", "Enriched ICER"),
  caption = "Detailed enriched-population results (pairwise versus standard of care)"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::footnote(
    general = paste(
      "The experimental cost includes the screening cost per identified positive",
      "(biomarker test cost divided by the canonical prevalence) in place of a",
      "single test; the control cost includes no test. The enriched ICER is the",
      "pairwise comparison of the two arms."
    ),
    threeparttable = TRUE
  )
```

```{r enriched-plot, fig.cap="Base case and enriched-population ICERs"}
plot_df <- enriched_comparison %>%
  select(Biomarker, Base_ICER, Enr_ICER, Base_Status, Enr_Status) %>%
  tidyr::pivot_longer(
    cols = c(Base_ICER, Enr_ICER),
    names_to = "Analysis",
    values_to = "ICER"
  ) %>%
  mutate(
    Analysis = recode(Analysis,
                      Base_ICER = "Base case",
                      Enr_ICER = "Enriched population"),
    Biomarker = biomarker_label(tolower(gsub("/", "_", Biomarker)))
  )

ggplot(plot_df, aes(x = Biomarker, y = ICER, fill = Analysis)) +
  geom_col(position = position_dodge(width = 0.75), width = 0.65) +
  geom_hline(yintercept = WTP, linetype = "dashed", color = "gray40") +
  scale_y_continuous(labels = scales::dollar_format(prefix = "EUR ", scale = 0.001,
                                                    suffix = "K")) +
  labs(x = NULL, y = "ICER", fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Interpretation

The enriched analysis isolates expected value among biomarker-positive patients and removes dilution from biomarker-negative patients who would receive standard care under a guided strategy. The enriched control arm is counterfactual and is generated from the fitted single joint survival model. The comparison is not free of the biomarker-negative patients altogether: finding each positive requires testing 1 / prevalence patients, and that screening cost is charged to the experimental arm.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.2
