---
title: "Input Parameters"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05"),
  funs = c("report_format", "model_fun", "calculate_outcomes", "cea_helpers",
           "crp_week4_estimand"),
  set_theme = FALSE
)

fmt_pct <- function(x) scales::percent(x, accuracy = 0.1)
```

# Model Configuration

State utilities and ongoing progressed-state costs are integrated over the
intervals between weekly grid points using the trapezoidal rule (half weight at
weeks 0 and 520). Thus 521 points span exactly 520 weeks: with no mortality,
unit utilities and no discounting, the model returns 10 QALYs. Quarterly
follow-up and post-progression cost rates accrue as four times the quarterly
rate per year of progressed-state occupancy. Discount weights are applied at
each grid point before integration. Drug administrations, scheduled tests and
visits, baseline screening and end-of-life events retain their full costs at
their modeled time points; they are not half-cycle corrected (issue #163).

Diagnostic prices are read directly from `c_test_CRP` and `c_test_NGS` on every
calculation, including direct model and enriched-population calls. A legacy
`c_test_biomarker` lookup is ignored; editing a scalar price needs no separate
synchronization step (issue #173).

```{r model-config}
config <- get_current_model_config()

config_table <- data.frame(
  Item = c("Economic strategies", "Economic biomarkers", "OS formula",
           "PFS formula", "Control arm"),
  Value = c(
    paste(get_strategies(), collapse = ", "),
    paste(get_biomarkers(), collapse = ", "),
    paste(deparse(config$formulas$shared$os), collapse = " "),
    paste(deparse(config$formulas$shared$pfs), collapse = " "),
    "The joint OS and PFS models predicted with Rx = control for every patient (no separate control formula; issue #151)"
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  config_table,
  booktabs = TRUE,
  align = c("l", "l"),
  caption = "Single economic model configuration"
) %>%
  tbl_style(latex_options = c("HOLD_position")) %>%
  tbl_column_spec(2, width = "11cm")
```

# Biomarker Prevalence

```{r biomarker-prevalence}
prevalence_table <- strategies_df %>%
  filter(id %in% get_biomarkers()) %>%
  transmute(
    Biomarker = recode(id, crp = "CRP-positive", tmb_braf = "TMB/BRAF-positive"),
    Prevalence = fmt_pct(prevalence),
    Source = "METIMMOX-1 trial data"
  )

knitr::kable(
  prevalence_table,
  booktabs = TRUE,
  align = c("l", "r", "l"),
  caption = "Economic biomarker prevalences"
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

Every economic strategy uses the same complete-case population (n = `r nrow(l_params_base$prediction_population)`). Its observed joint CRP and TMB/BRAF distribution defines the base case. In the PSA, the four joint cell probabilities are drawn together from a Dirichlet distribution with the observed cell counts, and the two marginal prevalences are derived. This represents uncertainty in the trial population's joint biomarker proportions, with age and sex distributions within each cell held fixed. The population weights change control and both guided strategies together. The one-way prevalence analysis rakes this same joint distribution to the changed marginal, retaining the other marginal and the joint odds ratio (issue #166).

# Estimand of the CRP-Guided Strategy

```{r crp-estimand}
# Deterministic sensitivity results of reports/technical/crp_week4_estimand.qmd,
# recomputed with the same functions (R/crp_week4_estimand.R; issue #175).
estimand_base <- calculate_pairwise_icers(model_fun(l_params_base))
estimand_sens <- run_crp_missingness_sensitivity(data, l_params_base, models, time_points)
estimand_summary <- summarise_crp_missingness(estimand_sens, estimand_base, WTP)
estimand_optimal <- attr(estimand_summary, "optimal")
decision_week <- which(l_params_base$l_nivo == 1)[1] - 1
estimand_pre <- pre_decision_increments(pre_decision_outcomes(
  l_params_base, decision_week = decision_week, time_horizon = time_horizon, cl = cl))
n_no_week4_crp <- length(estimand_sens$restored_rows)
n_scenarios <- nrow(estimand_sens$scenarios)
crp_range <- estimand_summary[estimand_summary$Strategy == "crp", ]
tmb_range <- estimand_summary[estimand_summary$Strategy == "tmb_braf", ]
crp_pre <- estimand_pre[estimand_pre$Strategy == "crp", ]
range_text <- function(x) {
  parts <- character(0)
  if (x$n_finite > 1) parts <- c(parts, sprintf("pairwise ICERs from %s to %s in %d scenarios",
    fmt_eur(x$icer_min), fmt_eur(x$icer_max), x$n_finite))
  if (x$n_finite == 1) parts <- c(parts, sprintf("a pairwise ICER of %s in one scenario",
    fmt_eur(x$icer_min)))
  if (x$n_dominated > 0) parts <- c(parts, sprintf("dominated by standard of care in %d",
    x$n_dominated))
  if (x$n_cost_saving > 0) parts <- c(parts, sprintf("cost-saving versus standard of care in %d",
    x$n_cost_saving))
  base <- switch(x$base_status,
    "Pairwise ICER vs SoC" = fmt_eur(x$base_icer),
    "Dominated by SoC" = "dominated by standard of care",
    "Cost-saving vs SoC" = "cost-saving versus standard of care",
    x$base_status)
  sprintf("%s (base case: %s)", paste(parts, collapse = "; "), base)
}
optimal_text <- if (length(unique(estimand_optimal)) == 1) {
  sprintf("%s has the highest net monetary benefit at WTP = %s in the base case and in every scenario.",
          strategy_label(estimand_optimal[[1]]), fmt_eur(WTP))
} else {
  sprintf("The strategy with the highest net monetary benefit at WTP = %s differs between the base case (%s) and at least one scenario.",
          fmt_eur(WTP), strategy_label(estimand_optimal[["base"]]))
}
```

The economic model estimates a **randomisation-time policy**. Every strategy
is assigned at randomisation (t = 0), and costs and QALYs are counted from
then. The CRP-guided strategy is assigned using the week-4 CRP value (cycle 3
day 1), which is available before the first nivolumab dose at modeled week
`r decision_week`. The fitted treatment and biomarker-by-treatment effects act
from t = 0, although all strategies receive identical treatment until that
dose. The `r n_no_week4_crp` patients without a week-4 CRP are excluded from
the complete-case cohort of `r nrow(data_complete)` patients (issue #175).

The technical report `reports/technical/crp_week4_estimand.qmd` quantifies
both choices deterministically. It restores the patients without a week-4 CRP
under `r n_scenarios` combinations of assigned CRP status and assigned
TMB/BRAF status (for the patients whose TMB/BRAF status is unknown):

- **CRP-guided:** `r range_text(crp_range)`.
- **TMB/BRAF-guided:** `r range_text(tmb_range)`.
- `r optimal_text`

Before the first nivolumab dose, the CRP-guided strategy accrues
`r format(signif(crp_pre$inc_qalys_pre, 3), scientific = FALSE)` more QALYs
than standard of care. This is `r scales::percent(crp_pre$share_qalys, accuracy = 0.001)`
of its full-horizon QALY increment.

# Utilities

The two health-state utilities are not sampled independently in the PSA. Independent beta draws placed the progressed utility above the progression-free utility in a substantial minority of draws (about 16% under the CORRECT utilities and about 49% under the IPD utilities), which widened the PSA with orderings that cannot occur. The PSA instead draws a non-negative decrement `u_decrement` (gamma, CV 0.15, mean equal to the base-case difference `u_np - u_p`) and sets `u_p = u_np - u_decrement`, so `u_p <= u_np` holds in every draw and the marginal mean of `u_p` is unchanged (issue #154). The realised reversal fraction is reported in the cost-effectiveness report.

```{r utility-table}
utility_table <- data.frame(
  Parameter = c("Progression-free utility", "Post-progression utility"),
  Symbol = c("u_np", "u_p"),
  Base_Case = c(l_params_base$u_np, l_params_base$u_p),
  DSA_Low = c(l_params_base$u_np, l_params_base$u_p) * (1 - DSA_mult),
  DSA_High = pmin(c(l_params_base$u_np, l_params_base$u_p) * (1 + DSA_mult), 1),
  stringsAsFactors = FALSE
) %>%
  mutate(across(c(Base_Case, DSA_Low, DSA_High), ~ sprintf("%.3f", .x)))

knitr::kable(
  utility_table,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r"),
  col.names = c("Parameter", "Symbol", "Base Case", "DSA Low", "DSA High"),
  caption = "Health-state utilities"
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

# Costs

Unit drug and test costs are **fixed in the PSA** and varied deterministically only (issue #154). They are published tariffs, laboratory prices, or — for nivolumab — an assumed acquisition price; none of them is a quantity that further research could resolve, so sampling them attributed decision uncertainty — and, under the earlier nearest-neighbour value-of-information estimator, research value — to prices that are known. Fixing them roughly halved total EVPI (from EUR 45.2 to EUR 22.1 per patient) without changing any base-case result. Visit, baseline, follow-up and end-of-life costs remain probabilistic because they bundle genuine resource-use uncertainty, and the deterministic influence of the prices is undiminished: the nivolumab price is still the second-largest one-way driver for both guided strategies.

The nivolumab price of `r sprintf("EUR %s", format(l_params_base$c_drug_nivo, big.mark = ","))` per administration is an **assumption, not a citable tariff**: it represents an assumed Norwegian hospital acquisition price (about 40% below list). Norwegian hospital prices are set by confidential LIS tender and cannot be published; international list prices are higher. Eight administrations give about `r sprintf("EUR %s", format(8 * l_params_base$c_drug_nivo, big.mark = ","))` per treated patient, making this the largest single cost driver in the model. It is varied by +/-20% in the one-way analysis and by a factor of three in the biosimilar scenario.

```{r cost-table}
cost_spec <- parameter_distribution_spec()
cost_psa_status <- function(symbol) {
  row <- cost_spec[cost_spec$parameter == symbol, , drop = FALSE]
  if (nrow(row) != 1) return("Fixed")
  if (row$psa) "Sampled (gamma)" else "Fixed"
}

cost_table <- data.frame(
  Parameter = c(
    "Nivolumab per administration",
    "FLOX per administration",
    "CT scan",
    "Routine blood monitoring",
    "CRP biomarker test",
    "NGS test",
    "Visit",
    "Baseline other cost",
    "Follow-up other cost",
    "Post-progression treatment (per quarter)",
    "End-of-life cost"
  ),
  Symbol = c(
    "c_drug_nivo", "c_drug_FLOX", "c_test_CT", "c_test_blood",
    "c_test_CRP", "c_test_NGS", "c_other_visit", "c_other_baseline",
    "c_other_follow", "c_other_pp", "c_other_last"
  ),
  Base_Case = c(
    l_params_base$c_drug_nivo, l_params_base$c_drug_FLOX,
    l_params_base$c_test_CT, l_params_base$c_test_blood,
    l_params_base$c_test_CRP, l_params_base$c_test_NGS, l_params_base$c_other_visit,
    l_params_base$c_other_baseline, l_params_base$c_other_follow,
    l_params_base$c_other_pp, l_params_base$c_other_last
  ),
  stringsAsFactors = FALSE
) %>%
  mutate(
    PSA = vapply(Symbol, cost_psa_status, character(1)),
    DSA_Low = pmax(Base_Case * (1 - DSA_mult), 0),
    DSA_High = Base_Case * (1 + DSA_mult),
    across(c(Base_Case, DSA_Low, DSA_High), fmt_eur)
  ) %>%
  select(Parameter, Symbol, Base_Case, DSA_Low, DSA_High, PSA)

knitr::kable(
  cost_table,
  booktabs = TRUE,
  align = c("l", "l", "r", "r", "r", "l"),
  col.names = c("Parameter", "Symbol", "Base Case", "DSA Low", "DSA High", "PSA"),
  caption = "Cost inputs"
) %>%
  tbl_style(latex_options = c("HOLD_position", "scale_down")) %>%
  tbl_footnote(
    general = c(
      "Fixed parameters are not sampled in the PSA and therefore carry no value-of-information; they are varied in the one-way analysis.",
      "c_other_pp is zero in the base case: post-progression treatment is outside the modeled scope (see below). Its deterministic range is degenerate, so it is tested as a structural scenario rather than in the one-way analysis."
    ),
    general_title = "Notes: "
  )
```

## Post-progression treatment costs

The base case applies **no post-progression treatment cost**. Once a patient has progressed, the model charges only the quarterly follow-up contact (`c_other_follow`) and the one-time end-of-life cost (`c_other_last`); second-line systemic therapy, post-progression imaging and post-progression outpatient visits are not modeled. Because the strategies differ in the time patients spend in the progressed state, this omission is **differential** rather than a common offset, and its direction depends on which strategy accrues more progressed time. The parameter `c_other_pp` makes the omission explicit and is varied in a structural scenario (EUR 5,000 per quarter in the progressed state) reported in the one-way sensitivity analysis.

## Second treatment sequence

The treatment schedules give a second eight-cycle sequence at weeks 24-38 to **every patient still progression-free** at that point, in both arms. In METIMMOX the second sequence was started on progression during the treatment break, so the model charges second-sequence drug and visit costs to progression-free patients who would not have been re-treated. A partitioned survival model has no on-treatment substate, so re-treatment cannot be triggered on progression without restructuring the model; the assumption is instead bounded by a structural scenario that removes the second sequence entirely while holding survival at the trial estimate, giving a cost-side bound.

# Structural Parameters

```{r structural-table}
structural_table <- data.frame(
  Parameter = c("Cycle length", "Time horizon", "Cost discount rate",
                "Effect discount rate", "Willingness-to-pay threshold",
                "PSA sample size"),
  Value = c(
    paste0(cl * 52, " week (1/52 year = ", format(cl, digits = 3), " years)"),
    paste0(time_horizon, " weeks (", time_horizon * cl, " years)"),
    fmt_pct(dr),
    fmt_pct(dr),
    fmt_eur(WTP),
    format(n_samples, big.mark = ",")
  ),
  stringsAsFactors = FALSE
)

knitr::kable(
  structural_table,
  booktabs = TRUE,
  align = c("l", "r"),
  caption = "Structural model parameters"
) %>%
  tbl_style(latex_options = c("HOLD_position"))
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.5
