---
title: "Parametric Survival Models"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
  gfm:
    toc: true
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("R/report_setup.R"))
setup_report(
  sources = c("02", "03", "04", "05"),
  funs = c("report_format"),
  packages = c(REPORT_PACKAGES, "survminer"),
  set_theme = FALSE
)

coef_table <- function(fit, outcome, distribution) {
  if (is.null(fit)) return(NULL)
  tab <- as.data.frame(fit$res)
  tab$Parameter <- rownames(tab)
  rownames(tab) <- NULL
  # flexsurvreg: baseline distribution parameters are reported on their natural
  # scale; covariate effects are on the log of the location parameter
  # (issue #153: state the scale explicitly instead of leaving it implicit).
  baseline_pars <- fit$dlist$pars
  location <- fit$dlist$location
  tab %>%
    transmute(
      Outcome = outcome,
      Distribution = distribution,
      Parameter,
      Scale = ifelse(Parameter %in% baseline_pars,
                     "baseline parameter (natural scale)",
                     paste0("covariate effect on log(", location, ")")),
      Estimate = est,
      SE = se,
      L95 = `L95%`,
      U95 = `U95%`
    )
}

surv_curve_df <- function(strategy, endpoint = c("os", "pfs")) {
  endpoint <- match.arg(endpoint)
  source_list <- if (endpoint == "os") l_params_base$p_os else l_params_base$p_pfs
  suffix <- if (endpoint == "os") "OS" else "PFS"

  data.frame(
    Week = time_points,
    Control = source_list[[paste0("control_", suffix)]],
    Positive = source_list[[paste0(strategy, "_pos_", suffix)]],
    Negative = source_list[[paste0(strategy, "_neg_", suffix)]],
    Weighted = source_list[[paste0(strategy, "_weighted_", suffix)]],
    Biomarker = biomarker_label(strategy),
    Endpoint = ifelse(endpoint == "os", "Overall survival", "Progression-free survival"),
    stringsAsFactors = FALSE
  ) %>%
    pivot_longer(cols = c(Control, Positive, Negative, Weighted),
                 names_to = "Curve", values_to = "Survival")
}
```

# Overview

This report documents the parametric survival models used in the economic evaluation. A single joint model is fitted for both endpoints:

```{r formula-table}
formula_df <- data.frame(
  Endpoint = c("Overall survival", "Progression-free survival"),
  Formula = c(
    paste(deparse(get_strategy_formula("crp", "os")), collapse = " "),
    paste(deparse(get_strategy_formula("crp", "pfs")), collapse = " ")
  ),
  stringsAsFactors = FALSE
)

knitr::kable(formula_df, booktabs = TRUE, align = c("l", "l"),
             caption = "Economic survival formulas") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "11cm")
```

# Distribution Selection

```{r selection-summary, include=FALSE}
selected_os  <- models$best_fit$os_distribution
selected_pfs <- models$best_fit$pfs_distribution
ordered_selection <- models$ordered_selection
```

The OS and PFS distributions are selected **jointly** from the nine candidate families: the selected pair is the one with the lowest combined AIC among all pairs whose population-averaged curves satisfy OS >= PFS for control and every economic biomarker subgroup at every weekly time point of the `r time_horizon / 52`-year horizon. Under this rule the selected pair is **OS `r selected_os` / PFS `r selected_pfs`** (combined AIC `r sprintf("%.2f", models$best_fit$combined_aic)`), which is `r sprintf("%.2f", ordered_selection$ic_penalty)` AIC above the unconstrained minimum-AIC pair. The lowest marginal-AIC distribution of an endpoint taken on its own is therefore not necessarily the selected one; the "Selected" column marks the distributions in use.

```{r os-ic}
os_ic <- models$full$os_ic %>%
  filter(!is.na(AIC)) %>%
  arrange(AIC) %>%
  mutate(
    delta_AIC = AIC - min(AIC),
    delta_BIC = BIC - min(BIC),
    Selected = ifelse(Distribution == selected_os, "Yes", "")
  )

knitr::kable(
  os_ic,
  booktabs = TRUE,
  digits = 2,
  align = c("l", rep("r", 4), "c"),
  caption = "Overall survival distribution comparison (ordered by marginal AIC)"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::row_spec(which(os_ic$Selected == "Yes"), bold = TRUE)
```

```{r pfs-ic}
pfs_ic <- models$full$pfs_ic %>%
  filter(!is.na(AIC)) %>%
  arrange(AIC) %>%
  mutate(
    delta_AIC = AIC - min(AIC),
    delta_BIC = BIC - min(BIC),
    Selected = ifelse(Distribution == selected_pfs, "Yes", "")
  )

knitr::kable(
  pfs_ic,
  booktabs = TRUE,
  digits = 2,
  align = c("l", rep("r", 4), "c"),
  caption = "Progression-free survival distribution comparison (ordered by marginal AIC)"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::row_spec(which(pfs_ic$Selected == "Yes"), bold = TRUE)
```

```{r pair-audit}
pairs <- ordered_selection$pairs
n_show <- min(12, nrow(pairs))
sel_idx <- which(pairs$os_distribution == selected_os & pairs$pfs_distribution == selected_pfs)
show_idx <- sort(unique(c(seq_len(n_show), sel_idx)))

pairs_display <- pairs[show_idx, ] %>%
  transmute(
    Rank = show_idx,
    `OS distribution` = os_distribution,
    `PFS distribution` = pfs_distribution,
    `Combined AIC` = sprintf("%.2f", combined_ic),
    `OS >= PFS` = ifelse(ordered, "Yes", "No"),
    `Violating points` = ifelse(is.na(n_violations), "--", as.character(n_violations)),
    Selected = ifelse(os_distribution == selected_os & pfs_distribution == selected_pfs, "Yes", "")
  )

knitr::kable(
  pairs_display,
  booktabs = TRUE,
  row.names = FALSE,
  align = c("r", "l", "l", "r", "c", "r", "c"),
  caption = sprintf("Joint (OS, PFS) pair audit: top %d of %d pairs by combined AIC plus the selected pair",
                    n_show, nrow(pairs))
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::row_spec(which(pairs_display$Selected == "Yes"), bold = TRUE) %>%
  kableExtra::footnote(
    general = "Violating points: number of (subgroup, week) points at which the population-averaged PFS curve exceeds the OS curve over the model horizon. The selected pair is the lowest combined-AIC pair with no violation.",
    threeparttable = TRUE
  )
```

# Coefficients

Coefficient scales differ by row type. Rows named after a distribution parameter (for example `shape` and `rate` for the gamma family, `shape` and `scale` for Weibull PH) are the baseline parameters on their natural scale. All covariate rows (Age, sex, Rx, biomarkers and their interactions) are additive effects on the log of the distribution's location parameter (`log(rate)` for gamma, `log(scale)` for Weibull PH, so that exp(coefficient) is a rate ratio for gamma and a hazard ratio for Weibull PH). The `Scale` column states this for every row.

```{r coefficients}
coef_rows <- list(
  coef_table(models$full$os[[models$best_fit$os_distribution]], "OS", models$best_fit$os_distribution),
  coef_table(models$full$pfs[[models$best_fit$pfs_distribution]], "PFS", models$best_fit$pfs_distribution),
  coef_table(models$full$os$weibullph, "OS", "weibullph"),
  coef_table(models$full$pfs$weibullph, "PFS", "weibullph")
)

coef_display <- bind_rows(coef_rows) %>%
  mutate(
    Estimate = sprintf("%.4f", Estimate),
    SE = sprintf("%.4f", SE),
    `95% CI` = sprintf("[%.4f, %.4f]", L95, U95)
  ) %>%
  select(Outcome, Distribution, Parameter, Scale, Estimate, SE, `95% CI`)

knitr::kable(
  coef_display,
  booktabs = TRUE,
  align = c("l", "l", "l", "l", "r", "r", "r"),
  caption = sprintf("Selected (OS %s, PFS %s) and Weibull PH coefficient estimates",
                    selected_os, selected_pfs)
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down")) %>%
  kableExtra::footnote(
    general = "Baseline parameters are on their natural scale; covariate rows are additive effects on the log location parameter (gamma: log(rate), exp(coef) = rate ratio; Weibull PH: log(scale), exp(coef) = hazard ratio).",
    threeparttable = TRUE
  )
```

# Strategy Survival Curves

```{r survival-curves, fig.cap="Predicted survival curves for economic biomarker strategies", fig.height=8, fig.width=10}
plot_data <- bind_rows(
  lapply(get_biomarkers(), surv_curve_df, endpoint = "os"),
  lapply(get_biomarkers(), surv_curve_df, endpoint = "pfs")
)

ggplot(plot_data, aes(x = Week, y = Survival, color = Curve, linetype = Curve)) +
  geom_line(linewidth = 0.8) +
  facet_grid(Biomarker ~ Endpoint) +
  scale_y_continuous(labels = scales::percent_format()) +
  labs(x = "Weeks", y = "Survival probability", color = NULL, linetype = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom")
```

# Summary

The economic model uses one joint formula for both CRP-guided and TMB/BRAF-guided strategies. The OS and PFS distributions are selected jointly as the minimum combined-AIC pair that keeps OS >= PFS for every subgroup over the model horizon (currently OS `r selected_os`, PFS `r selected_pfs`), not by marginal AIC per endpoint; Weibull PH is retained as a familiar reference fit.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.1
