---
title: "Forest Plot: Treatment x Biomarker Interaction Hazard Ratios"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  html:
    embed-resources: true
execute:
  echo: false
  warning: false
  message: false
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("cox_extract"),
  packages = c("here", "ggplot2", "dplyr", "scales", "survival", "coxphf"),
  set_theme = FALSE
)

theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 12, face = "bold"),
    legend.position = "bottom",
    axis.title = element_text(size = 10),
    axis.text = element_text(size = 9)
  )
)

```

This vignette consolidates the treatment-by-biomarker interaction hazard ratios from
the clinical effectiveness analysis into a single forest plot. It reports the
`CRP x Tx` and `TMB/BRAF x Tx` interactions from the **unified pre-treatment-biomarker
model** and the `TLR x Tx` interaction from the **week-9 landmark** TLR model, each
estimated by both **Firth-corrected Cox** regression and **ridge Cox** regression.
Model formulas and extraction logic mirror `scripts/QMD/report/clinical_effectiveness.qmd`.

```{r helpers, include=FALSE}
#' Convert a ridge {HR, SE} list into {HR, CI_Lower, CI_Upper} using a Wald
#' 95% interval on the log scale: exp(log(HR) +/- 1.96 * SE).
ridge_to_hr_ci <- function(ridge_res) {
  if (is.null(ridge_res) || is.na(ridge_res$HR) || is.na(ridge_res$SE))
    return(list(HR = ifelse(is.null(ridge_res), NA, ridge_res$HR),
                CI_Lower = NA, CI_Upper = NA))
  loghr <- log(ridge_res$HR)
  list(HR       = ridge_res$HR,
       CI_Lower = exp(loghr - 1.96 * ridge_res$SE),
       CI_Upper = exp(loghr + 1.96 * ridge_res$SE))
}
```

```{r data-prep, include=FALSE}
# =============================================================================
# DATA PREPARATION (mirrors clinical_effectiveness.qmd)
# =============================================================================
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

data_complete$sex <- as.factor(data_complete$sex)
data_complete$Rx  <- as.factor(data_complete$Rx)

data_complete$crp_num      <- as.numeric(as.character(data_complete$crp))
data_complete$tlr_num      <- as.numeric(as.character(data_complete$tlr))
data_complete$tmb_braf_num <- as.numeric(as.character(data_complete$tmb_braf))
data_complete$Rx_num       <- as.numeric(data_complete$Rx) - 1  # 0 = Control, 1 = Experimental

# Week-9 landmark cohorts (clock reset to landmark; endpoint-specific at-risk sets)
LANDMARK_WK <- 9

data_lm_os  <- data_complete[data_complete$OSwk  >= LANDMARK_WK, ]
data_lm_os$OSwk_lm   <- data_lm_os$OSwk  - LANDMARK_WK

data_lm_pfs <- data_complete[data_complete$PFSwk >= LANDMARK_WK, ]
data_lm_pfs$PFSwk_lm <- data_lm_pfs$PFSwk - LANDMARK_WK

# Pre-built ridge interaction term (survival::ridge() takes raw variables)
data_lm_os$tlr_x_rx  <- data_lm_os$tlr_num  * data_lm_os$Rx_num
data_lm_pfs$tlr_x_rx <- data_lm_pfs$tlr_num * data_lm_pfs$Rx_num
```

```{r fit-unified, include=FALSE}
# =============================================================================
# UNIFIED MODEL: CRP x Tx and TMB/BRAF x Tx (TLR excluded as post-rand. mediator)
# =============================================================================
formula_os  <- Surv(OSwk, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                   crp_num:Rx + tmb_braf_num:Rx
formula_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                          crp_num:Rx + tmb_braf_num:Rx

# --- Firth ---
model_os  <- fit_firth_cox(formula_os,  data_complete, "Unified OS")
model_pfs <- fit_firth_cox(formula_pfs, data_complete, "Unified PFS")
results_os  <- extract_coxphf_results(model_os)
results_pfs <- extract_coxphf_results(model_pfs)

firth_crp_os  <- get_interaction_hr(results_os,  "crp_num.*Rx|Rx.*crp_num")
firth_tmb_os  <- get_interaction_hr(results_os,  "tmb_braf_num.*Rx|Rx.*tmb_braf_num")
firth_crp_pfs <- get_interaction_hr(results_pfs, "crp_num.*Rx|Rx.*crp_num")
firth_tmb_pfs <- get_interaction_hr(results_pfs, "tmb_braf_num.*Rx|Rx.*tmb_braf_num")

# --- Ridge (penalize main effects only; interactions unpenalized) ---
ridge_os <- tryCatch(
  coxph(Surv(OSwk, Death) ~ Age + sex + Rx +
          ridge(crp_num, tmb_braf_num, theta = 1, scale = TRUE) +
          crp_num:Rx + tmb_braf_num:Rx, data = data_complete),
  error = function(e) NULL)
ridge_pfs <- tryCatch(
  coxph(Surv(PFSwk, Progression) ~ Age + sex + Rx +
          ridge(crp_num, tmb_braf_num, theta = 1, scale = TRUE) +
          crp_num:Rx + tmb_braf_num:Rx, data = data_complete),
  error = function(e) NULL)

ridge_crp_os  <- ridge_to_hr_ci(extract_ridge_interaction(ridge_os,  "Experimental.*crp|crp.*Experimental"))
ridge_tmb_os  <- ridge_to_hr_ci(extract_ridge_interaction(ridge_os,  "Experimental.*tmb|tmb.*Experimental"))
ridge_crp_pfs <- ridge_to_hr_ci(extract_ridge_interaction(ridge_pfs, "Experimental.*crp|crp.*Experimental"))
ridge_tmb_pfs <- ridge_to_hr_ci(extract_ridge_interaction(ridge_pfs, "Experimental.*tmb|tmb.*Experimental"))
```

```{r fit-landmark-tlr, include=FALSE}
# =============================================================================
# WEEK-9 LANDMARK TLR MODEL: TLR x Tx (CRP, TMB/BRAF as main-effect adjustments)
# =============================================================================
formula_lm_tlr_os  <- Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                             tlr_num + tlr_num:Rx
formula_lm_tlr_pfs <- Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
                                                    tlr_num + tlr_num:Rx

# --- Firth ---
model_lm_tlr_os  <- tryCatch(fit_firth_cox(formula_lm_tlr_os,  data_lm_os,  "Landmark TLR OS"),  error = function(e) NULL)
model_lm_tlr_pfs <- tryCatch(fit_firth_cox(formula_lm_tlr_pfs, data_lm_pfs, "Landmark TLR PFS"), error = function(e) NULL)
results_lm_tlr_os  <- if (!is.null(model_lm_tlr_os))  extract_coxphf_results(model_lm_tlr_os)  else NULL
results_lm_tlr_pfs <- if (!is.null(model_lm_tlr_pfs)) extract_coxphf_results(model_lm_tlr_pfs) else NULL

firth_tlr_os  <- get_interaction_hr(results_lm_tlr_os,  "tlr_num.*Rx|Rx.*tlr_num")
firth_tlr_pfs <- get_interaction_hr(results_lm_tlr_pfs, "tlr_num.*Rx|Rx.*tlr_num")

# --- Ridge (penalize TLR main effect + TLR x Rx; adjustments unpenalized) ---
ridge_lm_tlr_os <- tryCatch(
  coxph(Surv(OSwk_lm, Death) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE), data = data_lm_os),
  error = function(e) NULL)
ridge_lm_tlr_pfs <- tryCatch(
  coxph(Surv(PFSwk_lm, Progression) ~ Age + sex + Rx + crp_num + tmb_braf_num +
          ridge(tlr_num, tlr_x_rx, theta = 1, scale = TRUE), data = data_lm_pfs),
  error = function(e) NULL)

ridge_tlr_os  <- ridge_to_hr_ci(extract_ridge_interaction(ridge_lm_tlr_os,  "tlr_x_rx\\)"))
ridge_tlr_pfs <- ridge_to_hr_ci(extract_ridge_interaction(ridge_lm_tlr_pfs, "tlr_x_rx\\)"))
```

```{r build-forest-data, include=FALSE}
# =============================================================================
# COMBINE: 3 interactions x 2 outcomes x 2 methods = 12 rows
# =============================================================================
make_row <- function(interaction, outcome, method, est) {
  data.frame(
    Interaction = interaction, Outcome = outcome, Method = method,
    HR = est$HR, CI_Lower = est$CI_Lower, CI_Upper = est$CI_Upper,
    stringsAsFactors = FALSE
  )
}

forest_data <- rbind(
  # Unified model -- Firth
  make_row("CRP x Tx",      "Overall Survival",          "Firth", firth_crp_os),
  make_row("TMB/BRAF x Tx", "Overall Survival",          "Firth", firth_tmb_os),
  make_row("CRP x Tx",      "Progression-Free Survival", "Firth", firth_crp_pfs),
  make_row("TMB/BRAF x Tx", "Progression-Free Survival", "Firth", firth_tmb_pfs),
  # Unified model -- Ridge
  make_row("CRP x Tx",      "Overall Survival",          "Ridge", ridge_crp_os),
  make_row("TMB/BRAF x Tx", "Overall Survival",          "Ridge", ridge_tmb_os),
  make_row("CRP x Tx",      "Progression-Free Survival", "Ridge", ridge_crp_pfs),
  make_row("TMB/BRAF x Tx", "Progression-Free Survival", "Ridge", ridge_tmb_pfs),
  # Landmark TLR model -- Firth
  make_row("TLR x Tx",      "Overall Survival",          "Firth", firth_tlr_os),
  make_row("TLR x Tx",      "Progression-Free Survival", "Firth", firth_tlr_pfs),
  # Landmark TLR model -- Ridge
  make_row("TLR x Tx",      "Overall Survival",          "Ridge", ridge_tlr_os),
  make_row("TLR x Tx",      "Progression-Free Survival", "Ridge", ridge_tlr_pfs)
)

forest_data <- forest_data[!is.na(forest_data$HR), ]

# Order interactions top-to-bottom; reverse so CRP appears at the top of the axis
forest_data$Interaction <- factor(forest_data$Interaction,
  levels = rev(c("CRP x Tx", "TMB/BRAF x Tx", "TLR x Tx")))
forest_data$Outcome <- factor(forest_data$Outcome,
  levels = c("Overall Survival", "Progression-Free Survival"))
forest_data$Method <- factor(forest_data$Method, levels = c("Firth", "Ridge"))
```

## Forest Plot

```{r forest-plot, fig.width=10, fig.height=5}
p <- ggplot(forest_data, aes(x = HR, y = Interaction, color = Method)) +
  geom_vline(xintercept = 1, linetype = "dashed", color = "gray50") +
  geom_pointrange(aes(xmin = CI_Lower, xmax = CI_Upper),
                  position = position_dodge(width = 0.5), size = 0.5) +
  scale_x_log10(breaks = c(0.1, 0.25, 0.5, 1, 2, 4),
                labels = c("0.1", "0.25", "0.5", "1", "2", "4")) +
  scale_color_manual(values = c(Firth = "#0072B2", Ridge = "#D55E00")) +
  facet_wrap(~ Outcome) +
  labs(
    x = "Hazard Ratio (log scale)",
    y = "",
    title = "Treatment x Biomarker Interaction Hazard Ratios",
    subtitle = "Unified model (CRP, TMB/BRAF) and week-9 landmark TLR model",
    color = "Method"
  ) +
  theme_minimal() +
  theme(panel.grid.minor = element_blank(), legend.position = "bottom")

p
```

**Interpretation:** HR < 1 indicates that biomarker-positive patients derive greater
benefit from experimental treatment (reduced hazard of death/progression). The dashed
line at HR = 1 represents no differential treatment effect.

**Methods note:** Firth confidence intervals are profile-likelihood intervals (from
`coxphf`); ridge confidence intervals are Wald intervals computed on the log scale as
`exp(log(HR) +/- 1.96 x SE)`, since the ridge fit does not return profile-likelihood
intervals. The unified model penalizes (ridge) the CRP and TMB/BRAF main effects, leaving
the interaction terms unpenalized; the landmark TLR model penalizes the TLR main effect
and the TLR x Tx interaction, leaving the adjustment covariates unpenalized.

```{r save-figure, include=FALSE}
figs_dir <- here("figs")
if (!dir.exists(figs_dir)) dir.create(figs_dir, recursive = TRUE)

ggsave(
  filename = here("figs", "forrest-plot.png"),
  plot = p,
  width = 10, height = 5, dpi = 300, bg = "white"
)
cat("Figure saved to:", here("figs", "forrest-plot.png"), "\n")
```
