---
title: "baseline characteristics"
author: "Ben Geisler"
date: "2025-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#libraries
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(tableone, dplyr, ggplot2, readr)
```

# METIMMOX baseline chracteristics

#load full dataset
```{r}
setwd("..") 
METIMMOX <- readRDS(file="data/tidy/METIMMOX.rds")
```

## Replicating Table 1 from Metlzer et al. Br J Ca 2022 paper

```{r}
tab1vars <- c("Age", "BMI", "Female", "ECOG0", "RAS/RAF", "RightLeft", "InSitu", "Liver", "nMets", "sMet")

factor_vars1 <- c("Female", "ECOG0", "RAS/RAF",  "RightLeft", "InSitu", "Liver", "sMet", "Rx")

non_normal1 <- c("Age", "BMI", "nMets")

label_list1 <- c(
  Age = "Age (years)",
  Female = "Female",
  ECOG0 = "ECOG performance status 0",
    BMI = "Body Mass Index (kg/m²)",
  'RAS/RAF' = "RAS/BRAF-mutant tumor",
  InSitu = "Primary tumor in situ",
  Liver = "Liver involvement",
  nMets = "Number of metastatic sites",
  sMet = "Synchronous metastasis"
)



tab1 <- CreateTableOne(vars = tab1vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       factorVars = factor_vars1,
                       addOverall = FALSE,
                       test = FALSE)

print(tab1, nonnormal = non_normal1, exact = tab1vars, mapLabels = label_list,
      explain = TRUE)
rm(tab1, factor_vars1, label_list1, non_normal1, tab1vars)
```

## Table 2: modified baseline characteristics

```{r}

tab2vars <- c("Age", "Female", "RAS/RAF", "RightLeft", "TMB", "TLR", "CRP0", "ECOG0", "InSitu", "Liver", "nMets", "sMet", "BMI")

factor_vars2 <- c("Female", "RAS/RAF", "Rx", "RightLeft", "Liver", "ECOG0", "InSitu", "sMet")

non_normal2 <- c("Age", "BMI", "nMets", "TMB", "CRP0", "TLR")

label_list2 <- c(
  Age = "Age (years)",
  Female = "Female",
  ECOG0 = "ECOG performance status 0",
    'RAS/RAF' = "RAS/BRAF-mutant tumor",
  InSitu = "Primary tumor in situ",
    Liver = "Liver involvement",
  TMB = "tumor mutation burden",
  CRP0 = "C-reactive protein at baseline",
  TLR = "Target-lesion reduction after first cycle",
  nMets = "Number of metastatic sites",
  sMet = "Synchronous metastasis",
  BMI = "Body Mass Index (kg/m²)"
)



tab2 <- CreateTableOne(vars = tab2vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       factorVars = factor_vars2,
                       addOverall = TRUE)

print(tab2, nonnormal = non_normal2, exact = tab2vars, mapLabels = label_list,
      explain = TRUE)

rm(tab2, factor_vars2, label_list2, non_normal2, tab2vars)
```

##Table 3: labs at baseline (S1V1)

```{r}

tab3vars <- c("Hb...469",                         
  "Hematocrit...470",                  "WBC...471",                         "Neutrophils...472",                 "Lymphocytes...473",
  "Monocytes...474",                   "Basophils...475",                   "Eosinophils...476",                 "Thrombocytes...477",               
  "CRP...478",                              "Creatinine...479",                  "Sodium...480",                      "Potassium...481",                  
  "Calcium...482",                     "Magnesium...483",                   "Phosphate...484",                   "Glucose...485",                    
  "ALT...486",                         "AST...487",                         "ALP...488",                         "GT...489",                         
  "Bilirubin...490",                   "Albumin...491",                     "INR...492",                         "LDH...493",                        
  "TSH...494",                         "T4...495",                          "CEA...496",                         "CA19.9...497",                     
  "CA125...498")


tab3 <- CreateTableOne(vars = tab3vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       addOverall = TRUE)

print(tab3, nonnormal = tab3vars, exact = tab3vars, explain = TRUE)
print(tab3, exact = tab3vars, explain = TRUE)

rm(tab3, tab3vars)
```

##Table 4: Labs after two FLOX cycles (S1V3)

```{r}

tab4vars <- c("Hb...531",                          "Hematocrit...532",                  "WBC...533",
 "Neutrophils...534",                 "Lymphocytes...535",                 "Monocytes...536",                   "Basophils...537",                  
 "Eosinophils...538",                 "Thrombocytes...539",                "CRP...540",                         "Creatinine...541",                 
 "Sodium...542",                      "Potassium...543",                   "Calcium...544",                     "Magnesium...545",                  
 "Phosphate...546",                   "Glucose...547",                     "ALT...548",                         "AST...549",                        
 "ALP...550",                         "GT...551",                          "Bilirubin...552",                   "Albumin...553",                    
 "INR...554",                         "LDH...555",                         "TSH...556",                         "T4...557",                         
 "CEA...558",                         "CA19.9...559",                      "CA125...560"                       )

tab4 <- CreateTableOne(vars = tab4vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       addOverall = TRUE)

print(tab4, nonnormal = tab4vars, exact = tab3vars, explain = TRUE, cont.stats = c("mean.sd", "median.iqr"))
print(tab4, exact = tab4vars, explain = TRUE)

rm(tab4, tab4vars)
```

##Figure 1: Histogram of TLR Stratified by Rx

```{r}
# Create the histogram stratified by Rx
ggplot(data = METIMMOX, aes(x = TLR, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "TLR",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()
```

##Figure 2: Histogram of baseline and follow-up CRP, stratified by Rx

```{r}

# Create the histogram stratified by Rx
ggplot(data = METIMMOX, aes(x = CRP0, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "Baseline CRP",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()

ggplot(data = METIMMOX, aes(x = CRP1, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "CRP after two FLOX cycles",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()
```

##Figure 3: Histogram of Tumor-mutation Burden, Stratified by Rx

```{r}

# Create the histogram stratified by Rx
ggplot(data = METIMMOX, aes(x = TMB, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "TMB",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()
```

##Table 5: Possible covariates to stratify by

```{r}

tab5vars <- c("TLR", "CRP1", "TMB")

non_normal5 <- c("TLR", "CRP1", "TMB")

tab5 <- CreateTableOne(vars = tab5vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       addOverall = TRUE)

print(tab5, exact = tab5vars, nonnormal = non_normal5, explain = TRUE)

rm(tab5, non_normal5, tab5vars)
```

##Table 6: Possible covariates to stratify by - experimental arm

```{r}
# Create separate tables for each categorical variable
tlr_table <- CreateTableOne(vars = c("TLR"),
                            strata = c("TLRcat"),
                            data = METIMMOX,
                            factorVars = c("TLRcat"),
                            addOverall = TRUE)

crp1_table <- CreateTableOne(vars = c("CRP1"),
                             strata = c("CRP1cat"),
                             data = METIMMOX,
                             factorVars = c("CRP1cat"),
                             addOverall = TRUE)

tmb_table <- CreateTableOne(vars = c("TMB"),
                            strata = c("TMBcat"),
                            data = METIMMOX,
                            factorVars = c("TMBcat"),
                            addOverall = TRUE)

non_normal6 <- c("TLR", "CRP1", "TMB")

# Print the tables
cat("Table stratified by TLR ≥10% after two FLOX cycles:\n")
print(tlr_table, exact = c("TLR"), nonnormal = non_normal6, explain = TRUE)

cat("\nTable stratified by CRP <5 after two FLOX cycles:\n")
print(crp1_table, exact = c("CRP1"), nonnormal = non_normal6, explain = TRUE)

cat("\nTable stratified by tumor mutation burden >8 Mut/Mb:\n")
print(tmb_table, exact = c("TMB"), nonnormal = non_normal6, explain = TRUE)

rm(crp1_table, tlr_table, tmb_table, non_normal6)
```

##Table 7: RAS/RAF status

```{r}

# Create separate logical vectors for each condition
left_sided <- METIMMOX$RightLeft == 1
wildtype <- METIMMOX$Mutation == "wt"

# Combine the logical vectors
left_wildtype <- left_sided & wildtype

# Calculate the proportion of left-sided and wildtype patients
prop_left_wildtype <- mean(left_wildtype)

# Calculate the proportion of everyone else
prop_everyone_else <- 1 - prop_left_wildtype

# Create a contingency table of RightLeft and Mutation
contingency_table <- table(METIMMOX$RightLeft, METIMMOX$Mutation)

# Calculate the row proportions
row_proportions <- prop.table(contingency_table, margin = 1)

# Print the results
cat("Proportion of left-sided and wildtype patients:\n")
print(prop_left_wildtype)

cat("\nProportion of everyone else:\n")
print(prop_everyone_else)

cat("\nContingency table of RightLeft and Mutation:\n")
print(contingency_table)

cat("\nRow proportions:\n")
print(row_proportions)

rm(contingency_table, left_sided, left_wildtype, prop_everyone_else, prop_left_wildtype, row_proportions, wildtype)
```
