---
title: "Survival Analysis"
author: "Ben Geisler"
date: "2025-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## load faster binary format
```{r}
rm(list = ls())
setwd("..") 
METIMMOX <- readRDS(file="data/tidy/METIMMOX.rds")
```

# Survival Analysis 1: PFS

```{r}
rm(list = ls())
METIMMOX <- readRDS(file="METIMMOX.rds")

METIMMOX_control <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])
METIMMOX_experimental <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])
```

## Overall

```{r}
surv_object_pfs <- Surv(time = METIMMOX$PFSmo, event = METIMMOX$`Progression exit`)
fit.km <- survfit(surv_object_pfs ~ 1, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Progression-free Survival")
legend("topright", legend = c("Kaplan-Meier Estimate w/ 95% CI"), lty = 1, col = "black")

rm(fit.km)
```

###Compare this to Weibull

```{r}
fit.weibull <- flexsurvreg(surv_object_pfs ~ 1, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Progression-free Survival")
legend("topright", legend = c("Weibull Estimate w/ 95% CI"), lty = 1, col = "red")

rm(fit.weibull)
```

## Control vs. Experimental arm

```{r}
fit.km <- survfit(surv_object_pfs ~ Rx, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))

median_pfs <- summary(fit.km)$table[, "median"]
group_levels <- levels(METIMMOX$Rx)

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX$PFSmo)

# Add median PFS annotations to the plot for each treatment group
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}

```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}

#  median PFS for each treatment group
cat("Median PFS by Treatment Group:\n")
for (i in 1:length(group_levels)) {
  cat(group_levels[i], ": ", round(median_pfs[i], 2), " months\n", sep = "")
}

log_rank_test <- survdiff(surv_object_pfs ~ Rx, data = METIMMOX)
print(log_rank_test)

# Cox PH regression model with Rx as the predictor variable
cox_model <- coxph(surv_object_pfs ~ Rx, data = METIMMOX)
summary(cox_model)

# HR and CI 
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (Rx):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")

rm(fit.km,group_levels,i,median_pfs,n_groups,x_offset,y_values)
```

```{r}
fit.weibull <- flexsurvreg(surv_object_pfs ~ Rx, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Progression-free Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))
```

```{r}
km_control <- survfit(surv_object_pfs ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[1]))

# KM for  control arm only
ggsurvplot(km_control, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "blue", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$PFSmo)), title = "Control Arm", surv.scale="percent")
```

```{r}

km_experimental <- survfit(surv_object_pfs ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[2]))
ggsurvplot(km_experimental, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "pink", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$PFSmo)), title = "Experimental Arm", surv.scale="percent")
```

##by TL reduction ≥10% (experimental arm)

```{r}

surv_control <- Surv(time = METIMMOX_control$PFSmo, event = METIMMOX_control$`Progression exit`)
surv_experimental <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)

km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tlr1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 1))
km_tlr0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 0))

plot(km_control, xlab = "Months", ylab = "Progression-free Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# TLRcat=1 curve from the experimental group in pink
lines(km_tlr1, col = "pink", lwd = 2, conf.int = FALSE)

# TLRcat=0 curve from the experimental group as a dashed black line
lines(km_tlr0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control Group", "≥10% TL reduction", "<10% TL reduction"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}

medians <- tapply(METIMMOX_experimental$PFSmo, METIMMOX_experimental$TLRcat, median, na.rm = TRUE)
cat("Medians of PFSmo stratified by TLRcat (experimental arm):\n")
print(medians)

log_rank_test <- survdiff(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in PFS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in PFS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by TL reduction <10% (experimental arm)
cox_model <- coxph(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for TL reduction <10% (experimental arm)
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (TLRcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(medians,log_rank_test,cox_model,hr,ci)
```

### PH assumption 
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("<10% TL reduction", "≥10% TL reduction"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by CRP \<5 after two FLOX cycles (experimental arm)

```{r}

km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_crp1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 1))
km_crp0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 0))

# KM for the control group in blue
plot(km_control, xlab = "Months", ylab = "Progression-free Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# CRP1cat=1 curve from the experimental group in pink
lines(km_crp1, col = "pink", lwd = 2, conf.int = FALSE)

# CRP1cat=0 curve from the experimental group as a dashed black line
lines(km_crp0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control Group", "CRP < 5.0", "CRP ≥ 5.0"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

## same without control arm

```{r}
# Create the survival object using the METIMMOX_experimental dataset
surv_object_pfs_exp <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)

# Fit the Kaplan-Meier model using the METIMMOX_experimental dataset and survival object
fit.km <- survfit(surv_object_pfs_exp ~ CRP1cat, data = METIMMOX_experimental)

plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("black", "pink"), lty = c("dashed", "solid"))

legend("topright", legend = c("CRP ≥5.0", "CRP <5.0"), lty = c("dashed", "solid"), col = c("black", "pink"))

median_pfs <- summary(fit.km)$table[, "median"]

group_levels <- c("CRP ≥5.0", "CRP <5.0")

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX_experimental$PFSmo)

# Add median PFS annotations to the plot for each CRP1cat group
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}
```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}
medians <- tapply(METIMMOX_experimental$PFSmo, METIMMOX_experimental$CRP1cat, median, na.rm = TRUE)
cat("Medians of PFSmo stratified by CRP1cat (experimental arm):\n")
print(medians)

log_rank_test <- survdiff(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in PFS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in PFS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by CRP ≥5 after two FLOX cycles (experimental arm)
cox_model <- coxph(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for CRP ≥5 after two FLOX cycles (experimental arm)
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (CRP1cat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(medians,log_rank_test,cox_model,hr,ci)
```

## same analysis, but similar to poster

```{r}
km_control_crp1 <- survfit(surv_control ~ 1, data = METIMMOX_control, subset = (CRP1cat == 1))
km_control_crp0 <- survfit(surv_control ~ 1, data = METIMMOX_control, subset = (CRP1cat == 0))
km_experimental_crp1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 1))
km_experimental_crp0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 0))

# KM for the control group with CRP < 5.0 as a solid darker blue line
plot(km_control_crp1, xlab = "Months", ylab = "Progression-free Survival", col = "cadetblue", lwd = 2,
     conf.int = FALSE, xlim = c(0, 44), xaxt = "n")
axis(1, at = seq(0, 44, by = 2), labels = seq(0, 44, by = 2))

# KM for the control group with CRP ≥ 5.0 as a dotted darker blue line
lines(km_control_crp0, col = "cadetblue", lty = 2, lwd = 2, conf.int = FALSE)

# KM for the experimental group with CRP < 5.0 as a solid magenta line
lines(km_experimental_crp1, col = "deeppink3", lwd = 2, conf.int = FALSE)

# KM for the experimental group with CRP ≥ 5.0 as a dotted magenta line
lines(km_experimental_crp0, col = "deeppink3", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control, CRP < 5.0", "Control, CRP ≥ 5.0",
                              "Experimental, CRP < 5.0", "Experimental, CRP ≥ 5.0"),
       col = c("cadetblue", "cadetblue", "deeppink3", "deeppink3"), lty = c(1, 2, 1, 2), lwd = 2)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("CRP ≥5", "CRP <5"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by TMB >8 Mut/Mb

```{r}

km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tmb1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 1))
km_tmb0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 0))

# KM for the control group in blue
plot(km_control, xlab = "Months", ylab = "Progression-free Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# TMBcat=1 curve from the experimental group in pink
lines(km_tmb1, col = "pink", lwd = 2, conf.int = FALSE)

# TMBcat=0 curve from the experimental group as a dashed black line
lines(km_tmb0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control Group", "TMB >8 Mut/Mb", "TMB ≤8 Mut/Mb"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

## same without control arm

```{r}
# Create the survival object using the METIMMOX_experimental dataset
surv_object_pfs_exp <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)

# Fit the Kaplan-Meier model using the METIMMOX_experimental dataset and survival object
fit.km <- survfit(surv_object_pfs_exp ~ TMBcat, data = METIMMOX_experimental)

plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("black", "pink"), lty = c("dashed", "solid"))

legend("topright", legend = c("TMB ≤8", "TMB >8"), lty = c("dashed", "solid"), col = c("black", "pink"))

median_pfs <- summary(fit.km)$table[, "median"]

group_levels <- c("TMB ≤8", "TMB >8")

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX_experimental$PFSmo)

# Add median PFS annotations to the plot for each CRP1cat group
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}
```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}
log_rank_test <- survdiff(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in PFS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in PFS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by TMB ≥10 Mut/Mb (experimental arm)
cox_model <- coxph(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for TMB ≥10 Mut/Mb (experimental arm)
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (TMBcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(medians,log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("TMB <=8", "TMB >8"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

## same analysis, but similar to poster

```{r}
surv_object_pfs_exp <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)
fit.km <- survfit(surv_object_pfs_exp ~ TMBcat, data = METIMMOX_experimental)
plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("cadetblue", "deeppink3"), lty = c("solid", "solid"), xlim = c(0, 48), axes = FALSE)
axis(1, at = seq(0, 48, by = 12), labels = seq(0, 48, by = 12))
axis(2)
legend("topright", legend = c("TMB ≤8", "TMB >8"), lty = c("solid", "solid"), col = c("cadetblue", "deeppink3"))
median_pfs <- summary(fit.km)$table[, "median"]
group_levels <- c("TMB ≤8", "TMB >8")
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)
x_offset <- 0.05 * 48
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}
```

# Survival Analysis 2: OS

```{r}
rm(list = setdiff(ls(), "METIMMOX"))

METIMMOX <- readRDS("METIMMOX.rds")
METIMMOX_control <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])
METIMMOX_experimental <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])

```

## Overall

```{r}
surv_object_os <- Surv(time = METIMMOX$OSmo, event = METIMMOX$Death)
fit.km <- survfit(surv_object_os ~ 1, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Overall Survival")
legend("topright", legend = c("Kaplan-Meier Estimate w/ 95% CI"), lty = 1, col = "black")
```

###compare to a quick Weibull

```{r}
fit.weibull <- flexsurvreg(surv_object_os ~ 1, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Overall Survival")
legend("topright", legend = c("Weibull Estimate w/ 95% CI"), lty = 1, col = "red")
```

##Control vs. Experimental arm

```{r}
fit.km <- survfit(surv_object_os ~ Rx, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Overall Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))

# median PFS for each treatment group
median_os <- summary(fit.km)$table[, "median"]
group_levels <- levels(METIMMOX$Rx)

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX$OSmo)

# Add median PFS annotations to the plot for each treatment group
for (i in 1:n_groups) {
  text(x = median_os[i] + x_offset, y = y_values[i],
       labels = paste("Median OS (", group_levels[i], "):", round(median_os[i], 1)),
       pos = 4)
}
```

```{r}
fit.weibull <- flexsurvreg(surv_object_os ~ Rx, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Overall Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))
```

```{r}
km_control <- survfit(surv_object_os ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[1]))

ggsurvplot(km_control, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "blue", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$OSmo)), title = "Control Arm", surv.scale="percent")
```

```{r}
km_experimental <- survfit(surv_object_os ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[2]))

ggsurvplot(km_experimental, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "pink", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$OSmo)), title = "Experimental Arm", surv.scale="percent")
```

##by TL reduction ≥10% (experimental arm)

```{r}

surv_control <- Surv(time = METIMMOX_control$OSmo, event = METIMMOX_control$Death)
surv_experimental <- Surv(time = METIMMOX_experimental$OSmo, event = METIMMOX_experimental$Death)

# Fit the Kaplan-Meier curves
km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tlr1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 1))
km_tlr0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 0))

# Plot the Kaplan-Meier curve for the control group in blue
plot(km_control, xlab = "Months", ylab = "Overall Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# Add the TLRcat=1 curve from the experimental group in pink
lines(km_tlr1, col = "pink", lwd = 2, conf.int = FALSE)

# Add the TLRcat=0 curve from the experimental group as a dashed black line
lines(km_tlr0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

# Add a legend
legend("topright", legend = c("Control Group", "≥10% TL reduction", "<10% TL reduction"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

##by CRP ≤5 after two FLOX cycles (experimental arm)

```{r}

# Fit the Kaplan-Meier curves
km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_crp1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 1))
km_crp0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 0))

# Plot the Kaplan-Meier curve for the control group in blue
plot(km_control, xlab = "Months", ylab = "Overall Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# Add the CRP1cat=1 curve from the experimental group in pink
lines(km_crp1, col = "pink", lwd = 2, conf.int = FALSE)

# Add the CRP1cat=0 curve from the experimental group as a dashed black line
lines(km_crp0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

# Add a legend
legend("topright", legend = c("Control Group", "CRP ≤ 5.0", "CRP > 5.0"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

##by TMB >8 Mut/Mb (experimental arm)

```{r}

# Fit the Kaplan-Meier curves
km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tmb1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 1))
km_tmb0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 0))

# Plot the Kaplan-Meier curve for the control group in blue
plot(km_control, xlab = "Months", ylab = "Overall Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# Add the TMBcat=1 curve from the experimental group in pink
lines(km_tmb1, col = "pink", lwd = 2, conf.int = FALSE)

# Add the CRP1cat=0 curve from the experimental group as a dashed black line
lines(km_tmb0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

# Add a legend
legend("topright", legend = c("Control Group", "TMB >8 Mut/Mb", "TMB ≤8 Mut/Mb"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

## log rank tests and hazarad ratios from Cox PH regression models for OS

### Control vs. experimental

```{r}

median_os <- summary(fit.km)$table[, "median"]
group_levels <- levels(METIMMOX$Rx)
cat("Median OS by Treatment Group:\n")
for (i in 1:length(group_levels)) {
  cat(group_levels[i], ": ", round(median_os[i], 2), " months\n", sep = "")
}

log_rank_test <- survdiff(surv_object_os ~ Rx, data = METIMMOX)
print(log_rank_test)

# Cox PH regression model with Rx as the predictor variable
cox_model <- coxph(surv_object_os ~ Rx, data = METIMMOX)
summary(cox_model)

# HR and CI for Rx
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))

# Print the hazard ratio and confidence interval
cat("Hazard Ratio (Rx):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(median_os,group_levels,log_rank_test,cox_model,hr,ci)
```

##by TL reduction ≥10% (experimental arm)

```{r}

log_rank_test <- survdiff(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in OS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in OS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression  model stratified by TLRcat in the experimental group
cox_model <- coxph(surv_experimental ~ TLRcat, data = METIMMOX_experimental)

# Print the summary of the Cox model
summary(cox_model)

# Extract the hazard ratio and confidence interval for TLRcat
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))

# Print the hazard ratio and confidence interval
cat("Hazard Ratio (TLRcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("TLR <=10%", "TLR >10%"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by CRP <5 after two FLOX cycles (experimental arm)

```{r}

log_rank_test <- survdiff(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in OS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in OS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model stratified by CRP1cat in the experimental group
cox_model <- coxph(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for CRP1cat
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (CRP1cat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("CRP >=5", "CRP <5"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by TMB >8 Mut/Mb (experimental arm)

```{r}

log_rank_test <- survdiff(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in OS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in OS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by TMBcat in the experimental group
cox_model <- coxph(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for TMBcat
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (TMBcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("TMB <=8", "TMB >8"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

# Survival Analyis 3: compare biomarkers

## PFS
```{r}
library(survival)
library(survminer)

surv_obj <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)
```

```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat + TMBcat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)", "TMBcat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```

```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```
## OS

```{r}
rm(surv_obj)
surv_obj <- Surv(time = METIMMOX_experimental$OSmo, event = METIMMOX_experimental$`Death`)
```



```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat + TMBcat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)", "TMBcat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```

```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```