---
title: "METIMMOX-prep only"
output: html_document
date: "2025-04-29"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load more libraries
```{r}
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(devtools, readxl, dplyr, tableone, ggplot2, flexsurv, survival, survminer, gems, mstate, tidyverse, xtable, darthtools, dampack, mvtnorm, Matrix)
#if (!requireNamespace("darthtools", quietly = TRUE)) {  install.packages("dampack", repos = c(
#  DARTH = 'https://raw.githubusercontent.com/DARTH-git/dampack/master/repos',
#  CRAN = 'https://cloud.r-project.org'))}
```

# Load dataset

Important: We will not import patients who are not assigned to either the experimental or the control arm; also removing pts 1-030 and 1-037 (de-randomized by Anne to receive experimental treatment after 30 days)

```{r, eval=FALSE}
rm(list = ls())
METIMMOXraw <- read_excel("clinical data/METIMMOX w TMB 241101.xlsx", skip = 1) %>%
  filter(!is.na(`Study1/control0`) & `Study1/control0` != "" & 
         !ID %in% c("1-030", "1-037"))
```

## rename some covariates and create categorical variables/factors

```{r, eval=FALSE}

rm(list = setdiff(ls(), "METIMMOXraw"))

METIMMOX <- METIMMOXraw
rm(METIMMOXraw)

METIMMOX$Rx <- factor(METIMMOX$`Study1/control0`, levels = c(0, 1), labels = c("Control arm", "Experimental arm"))

METIMMOX$Female <- 1 - METIMMOX$"Sex 0female"
METIMMOX$Female <- factor(METIMMOX$Female, levels = c(0, 1), labels = c("Male", "Female"))

METIMMOX$ECOG0 <- 1- METIMMOX$S1V0
METIMMOX$ECOG0 <- factor(METIMMOX$ECOG0, levels = c(0, 1), labels = c("ECOG>1", "ECOG=0"))

METIMMOX$`RAS/RAF` <- factor(METIMMOX$`RAS/RAF`, levels = c(0, 1), labels = c("wildtype", "RAS/BRAF-mutant tumor"))

METIMMOX$RightLeft <- factor(METIMMOX$`Right0/Left`, levels = c(0, 1), labels = c("Right-sided primary tumor", "Left-sided primary tumor"))

METIMMOX$Liver <- as.factor(ifelse(grepl("^Liver", METIMMOX$`Metastatic organ`), 1, 0))

METIMMOX$InSitu <- factor (METIMMOX$`Primary tumor in situ`, levels = c(0, 1), labels = c("Primary tumor not in situ", "Primary tumour in situ"))

METIMMOX$nMets <- METIMMOX$`Number of metastatic sites`

METIMMOX$sMet <- 1- METIMMOX$`New0/Metachronous`
METIMMOX$sMet <- factor(METIMMOX$sMet, levels = c(0, 1), labels = c("Metachronous", "Synchronous"))

METIMMOX$CT1tl <- as.numeric(METIMMOX$`TL LD...130`)
METIMMOX$TLR <- METIMMOX$CT1tl / METIMMOX$`TL LD...121`
METIMMOX$TLRcat <- as.factor(ifelse(METIMMOX$TLR <= 0.9, 1, 0))

METIMMOX$CRP0 <- METIMMOX$`CRP...478`
METIMMOX$CRP0cat <- as.factor(ifelse(METIMMOX$CRP0 < 5, 1, 0))

METIMMOX$CRP1 <- METIMMOX$`CRP...540`
METIMMOX$CRP1cat <- as.factor(ifelse(METIMMOX$CRP1 < 5, 1, 0))

METIMMOX$TMB <- as.numeric(METIMMOX$TMB)
METIMMOX$TMBcat <- as.factor(ifelse(METIMMOX$TMB >= 9, 1, 0))

METIMMOX$PFSmo <- METIMMOX$`Days until progression`*12/365

METIMMOX$OSmo <-METIMMOX$`Days until death/last follow up`*12/365

METIMMOX$PFSwk <- METIMMOX$`Days until progression`/7

METIMMOX$OSwk <-METIMMOX$`Days until death/last follow up`/7


saveRDS(METIMMOX, file="METIMMOX.rds")
```

## load faster binary format
```{r}
rm(list = ls())
METIMMOX <- readRDS(file="METIMMOX.rds")
```

# METIMMOX baseline chracteristics

## Replicating Table 1 from Metlzer et al. Br J Ca 2022 paper

```{r}
tab1vars <- c("Age", "BMI", "Female", "ECOG0", "RAS/RAF", "RightLeft", "InSitu", "Liver", "nMets", "sMet")

factor_vars1 <- c("Female", "ECOG0", "RAS/RAF",  "RightLeft", "InSitu", "Liver", "sMet", "Rx")

non_normal1 <- c("Age", "BMI", "nMets")

label_list1 <- c(
  Age = "Age (years)",
  Female = "Female",
  ECOG0 = "ECOG performance status 0",
    BMI = "Body Mass Index (kg/m²)",
  'RAS/RAF' = "RAS/BRAF-mutant tumor",
  InSitu = "Primary tumor in situ",
  Liver = "Liver involvement",
  nMets = "Number of metastatic sites",
  sMet = "Synchronous metastasis"
)



tab1 <- CreateTableOne(vars = tab1vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       factorVars = factor_vars1,
                       addOverall = FALSE,
                       test = FALSE)

print(tab1, nonnormal = non_normal1, exact = tab1vars, mapLabels = label_list,
      explain = TRUE)
rm(tab1, factor_vars1, label_list1, non_normal1, tab1vars)
```

## Table 2: modified baseline characteristics

```{r}

tab2vars <- c("Age", "Female", "RAS/RAF", "RightLeft", "TMB", "TLR", "CRP0", "ECOG0", "InSitu", "Liver", "nMets", "sMet", "BMI")

factor_vars2 <- c("Female", "RAS/RAF", "Rx", "RightLeft", "Liver", "ECOG0", "InSitu", "sMet")

non_normal2 <- c("Age", "BMI", "nMets", "TMB", "CRP0", "TLR")

label_list2 <- c(
  Age = "Age (years)",
  Female = "Female",
  ECOG0 = "ECOG performance status 0",
    'RAS/RAF' = "RAS/BRAF-mutant tumor",
  InSitu = "Primary tumor in situ",
    Liver = "Liver involvement",
  TMB = "tumor mutation burden",
  CRP0 = "C-reactive protein at baseline",
  TLR = "Target-lesion reduction after first cycle",
  nMets = "Number of metastatic sites",
  sMet = "Synchronous metastasis",
  BMI = "Body Mass Index (kg/m²)"
)



tab2 <- CreateTableOne(vars = tab2vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       factorVars = factor_vars2,
                       addOverall = TRUE)

print(tab2, nonnormal = non_normal2, exact = tab2vars, mapLabels = label_list,
      explain = TRUE)

rm(tab2, factor_vars2, label_list2, non_normal2, tab2vars)
```

##Table 3: labs at baseline (S1V1)

```{r}

tab3vars <- c("Hb...469",                         
  "Hematocrit...470",                  "WBC...471",                         "Neutrophils...472",                 "Lymphocytes...473",
  "Monocytes...474",                   "Basophils...475",                   "Eosinophils...476",                 "Thrombocytes...477",               
  "CRP...478",                              "Creatinine...479",                  "Sodium...480",                      "Potassium...481",                  
  "Calcium...482",                     "Magnesium...483",                   "Phosphate...484",                   "Glucose...485",                    
  "ALT...486",                         "AST...487",                         "ALP...488",                         "GT...489",                         
  "Bilirubin...490",                   "Albumin...491",                     "INR...492",                         "LDH...493",                        
  "TSH...494",                         "T4...495",                          "CEA...496",                         "CA19.9...497",                     
  "CA125...498")


tab3 <- CreateTableOne(vars = tab3vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       addOverall = TRUE)

print(tab3, nonnormal = tab3vars, exact = tab3vars, explain = TRUE)
print(tab3, exact = tab3vars, explain = TRUE)

rm(tab3, tab3vars)
```

##Table 4: Labs after two FLOX cycles (S1V3)

```{r}

tab4vars <- c("Hb...531",                          "Hematocrit...532",                  "WBC...533",
 "Neutrophils...534",                 "Lymphocytes...535",                 "Monocytes...536",                   "Basophils...537",                  
 "Eosinophils...538",                 "Thrombocytes...539",                "CRP...540",                         "Creatinine...541",                 
 "Sodium...542",                      "Potassium...543",                   "Calcium...544",                     "Magnesium...545",                  
 "Phosphate...546",                   "Glucose...547",                     "ALT...548",                         "AST...549",                        
 "ALP...550",                         "GT...551",                          "Bilirubin...552",                   "Albumin...553",                    
 "INR...554",                         "LDH...555",                         "TSH...556",                         "T4...557",                         
 "CEA...558",                         "CA19.9...559",                      "CA125...560"                       )

tab4 <- CreateTableOne(vars = tab4vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       addOverall = TRUE)

print(tab4, nonnormal = tab4vars, exact = tab3vars, explain = TRUE, cont.stats = c("mean.sd", "median.iqr"))
print(tab4, exact = tab4vars, explain = TRUE)

rm(tab4, tab4vars)
```

##Figure 1: Histogram of TLR Stratified by Rx

```{r}
# Create the histogram stratified by Rx
ggplot(data = METIMMOX, aes(x = TLR, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "TLR",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()
```

##Figure 2: Histogram of baseline and follow-up CRP, stratified by Rx

```{r}

# Create the histogram stratified by Rx
ggplot(data = METIMMOX, aes(x = CRP0, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "Baseline CRP",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()

ggplot(data = METIMMOX, aes(x = CRP1, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "CRP after two FLOX cycles",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()
```

##Figure 3: Histogram of Tumor-mutation Burden, Stratified by Rx

```{r}

# Create the histogram stratified by Rx
ggplot(data = METIMMOX, aes(x = TMB, fill = Rx)) +
  geom_histogram(bins = 20, alpha = 0.7, position = "identity", na.rm = TRUE) +
  labs(x = "TMB",
       y = "Frequency",
       fill = "Rx") +
  theme_minimal()
```

##Table 5: Possible covariates to stratify by

```{r}

tab5vars <- c("TLR", "CRP1", "TMB")

non_normal5 <- c("TLR", "CRP1", "TMB")

tab5 <- CreateTableOne(vars = tab5vars,
                       strata = c("Rx"),
                       data = METIMMOX,
                       addOverall = TRUE)

print(tab5, exact = tab5vars, nonnormal = non_normal5, explain = TRUE)

rm(tab5, non_normal5, tab5vars)
```

##Table 6: Possible covariates to stratify by - experimental arm

```{r}
# Create separate tables for each categorical variable
tlr_table <- CreateTableOne(vars = c("TLR"),
                            strata = c("TLRcat"),
                            data = METIMMOX,
                            factorVars = c("TLRcat"),
                            addOverall = TRUE)

crp1_table <- CreateTableOne(vars = c("CRP1"),
                             strata = c("CRP1cat"),
                             data = METIMMOX,
                             factorVars = c("CRP1cat"),
                             addOverall = TRUE)

tmb_table <- CreateTableOne(vars = c("TMB"),
                            strata = c("TMBcat"),
                            data = METIMMOX,
                            factorVars = c("TMBcat"),
                            addOverall = TRUE)

non_normal6 <- c("TLR", "CRP1", "TMB")

# Print the tables
cat("Table stratified by TLR ≥10% after two FLOX cycles:\n")
print(tlr_table, exact = c("TLR"), nonnormal = non_normal6, explain = TRUE)

cat("\nTable stratified by CRP <5 after two FLOX cycles:\n")
print(crp1_table, exact = c("CRP1"), nonnormal = non_normal6, explain = TRUE)

cat("\nTable stratified by tumor mutation burden >8 Mut/Mb:\n")
print(tmb_table, exact = c("TMB"), nonnormal = non_normal6, explain = TRUE)

rm(crp1_table, tlr_table, tmb_table, non_normal6)
```

##Table 7: RAS/RAF status

```{r}

# Create separate logical vectors for each condition
left_sided <- METIMMOX$RightLeft == 1
wildtype <- METIMMOX$Mutation == "wt"

# Combine the logical vectors
left_wildtype <- left_sided & wildtype

# Calculate the proportion of left-sided and wildtype patients
prop_left_wildtype <- mean(left_wildtype)

# Calculate the proportion of everyone else
prop_everyone_else <- 1 - prop_left_wildtype

# Create a contingency table of RightLeft and Mutation
contingency_table <- table(METIMMOX$RightLeft, METIMMOX$Mutation)

# Calculate the row proportions
row_proportions <- prop.table(contingency_table, margin = 1)

# Print the results
cat("Proportion of left-sided and wildtype patients:\n")
print(prop_left_wildtype)

cat("\nProportion of everyone else:\n")
print(prop_everyone_else)

cat("\nContingency table of RightLeft and Mutation:\n")
print(contingency_table)

cat("\nRow proportions:\n")
print(row_proportions)

rm(contingency_table, left_sided, left_wildtype, prop_everyone_else, prop_left_wildtype, row_proportions, wildtype)
```

# Survival Analysis 1: PFS

```{r}
rm(list = ls())
METIMMOX <- readRDS(file="METIMMOX.rds")

METIMMOX_control <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])
METIMMOX_experimental <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])
```

## Overall

```{r}
surv_object_pfs <- Surv(time = METIMMOX$PFSmo, event = METIMMOX$`Progression exit`)
fit.km <- survfit(surv_object_pfs ~ 1, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Progression-free Survival")
legend("topright", legend = c("Kaplan-Meier Estimate w/ 95% CI"), lty = 1, col = "black")

rm(fit.km)
```

###Compare this to Weibull

```{r}
fit.weibull <- flexsurvreg(surv_object_pfs ~ 1, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Progression-free Survival")
legend("topright", legend = c("Weibull Estimate w/ 95% CI"), lty = 1, col = "red")

rm(fit.weibull)
```

## Control vs. Experimental arm

```{r}
fit.km <- survfit(surv_object_pfs ~ Rx, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))

median_pfs <- summary(fit.km)$table[, "median"]
group_levels <- levels(METIMMOX$Rx)

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX$PFSmo)

# Add median PFS annotations to the plot for each treatment group
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}

```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}

#  median PFS for each treatment group
cat("Median PFS by Treatment Group:\n")
for (i in 1:length(group_levels)) {
  cat(group_levels[i], ": ", round(median_pfs[i], 2), " months\n", sep = "")
}

log_rank_test <- survdiff(surv_object_pfs ~ Rx, data = METIMMOX)
print(log_rank_test)

# Cox PH regression model with Rx as the predictor variable
cox_model <- coxph(surv_object_pfs ~ Rx, data = METIMMOX)
summary(cox_model)

# HR and CI 
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (Rx):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")

rm(fit.km,group_levels,i,median_pfs,n_groups,x_offset,y_values)
```

```{r}
fit.weibull <- flexsurvreg(surv_object_pfs ~ Rx, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Progression-free Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))
```

```{r}
km_control <- survfit(surv_object_pfs ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[1]))

# KM for  control arm only
ggsurvplot(km_control, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "blue", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$PFSmo)), title = "Control Arm", surv.scale="percent")
```

```{r}

km_experimental <- survfit(surv_object_pfs ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[2]))
ggsurvplot(km_experimental, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "pink", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$PFSmo)), title = "Experimental Arm", surv.scale="percent")
```

##by TL reduction ≥10% (experimental arm)

```{r}

surv_control <- Surv(time = METIMMOX_control$PFSmo, event = METIMMOX_control$`Progression exit`)
surv_experimental <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)

km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tlr1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 1))
km_tlr0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 0))

plot(km_control, xlab = "Months", ylab = "Progression-free Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# TLRcat=1 curve from the experimental group in pink
lines(km_tlr1, col = "pink", lwd = 2, conf.int = FALSE)

# TLRcat=0 curve from the experimental group as a dashed black line
lines(km_tlr0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control Group", "≥10% TL reduction", "<10% TL reduction"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}

medians <- tapply(METIMMOX_experimental$PFSmo, METIMMOX_experimental$TLRcat, median, na.rm = TRUE)
cat("Medians of PFSmo stratified by TLRcat (experimental arm):\n")
print(medians)

log_rank_test <- survdiff(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in PFS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in PFS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by TL reduction <10% (experimental arm)
cox_model <- coxph(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for TL reduction <10% (experimental arm)
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (TLRcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(medians,log_rank_test,cox_model,hr,ci)
```

### PH assumption 
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("<10% TL reduction", "≥10% TL reduction"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by CRP \<5 after two FLOX cycles (experimental arm)

```{r}

km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_crp1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 1))
km_crp0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 0))

# KM for the control group in blue
plot(km_control, xlab = "Months", ylab = "Progression-free Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# CRP1cat=1 curve from the experimental group in pink
lines(km_crp1, col = "pink", lwd = 2, conf.int = FALSE)

# CRP1cat=0 curve from the experimental group as a dashed black line
lines(km_crp0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control Group", "CRP < 5.0", "CRP ≥ 5.0"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

## same without control arm

```{r}
# Create the survival object using the METIMMOX_experimental dataset
surv_object_pfs_exp <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)

# Fit the Kaplan-Meier model using the METIMMOX_experimental dataset and survival object
fit.km <- survfit(surv_object_pfs_exp ~ CRP1cat, data = METIMMOX_experimental)

plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("black", "pink"), lty = c("dashed", "solid"))

legend("topright", legend = c("CRP ≥5.0", "CRP <5.0"), lty = c("dashed", "solid"), col = c("black", "pink"))

median_pfs <- summary(fit.km)$table[, "median"]

group_levels <- c("CRP ≥5.0", "CRP <5.0")

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX_experimental$PFSmo)

# Add median PFS annotations to the plot for each CRP1cat group
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}
```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}
medians <- tapply(METIMMOX_experimental$PFSmo, METIMMOX_experimental$CRP1cat, median, na.rm = TRUE)
cat("Medians of PFSmo stratified by CRP1cat (experimental arm):\n")
print(medians)

log_rank_test <- survdiff(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in PFS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in PFS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by CRP ≥5 after two FLOX cycles (experimental arm)
cox_model <- coxph(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for CRP ≥5 after two FLOX cycles (experimental arm)
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (CRP1cat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(medians,log_rank_test,cox_model,hr,ci)
```

## same analysis, but similar to poster

```{r}
km_control_crp1 <- survfit(surv_control ~ 1, data = METIMMOX_control, subset = (CRP1cat == 1))
km_control_crp0 <- survfit(surv_control ~ 1, data = METIMMOX_control, subset = (CRP1cat == 0))
km_experimental_crp1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 1))
km_experimental_crp0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 0))

# KM for the control group with CRP < 5.0 as a solid darker blue line
plot(km_control_crp1, xlab = "Months", ylab = "Progression-free Survival", col = "cadetblue", lwd = 2,
     conf.int = FALSE, xlim = c(0, 44), xaxt = "n")
axis(1, at = seq(0, 44, by = 2), labels = seq(0, 44, by = 2))

# KM for the control group with CRP ≥ 5.0 as a dotted darker blue line
lines(km_control_crp0, col = "cadetblue", lty = 2, lwd = 2, conf.int = FALSE)

# KM for the experimental group with CRP < 5.0 as a solid magenta line
lines(km_experimental_crp1, col = "deeppink3", lwd = 2, conf.int = FALSE)

# KM for the experimental group with CRP ≥ 5.0 as a dotted magenta line
lines(km_experimental_crp0, col = "deeppink3", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control, CRP < 5.0", "Control, CRP ≥ 5.0",
                              "Experimental, CRP < 5.0", "Experimental, CRP ≥ 5.0"),
       col = c("cadetblue", "cadetblue", "deeppink3", "deeppink3"), lty = c(1, 2, 1, 2), lwd = 2)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("CRP ≥5", "CRP <5"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by TMB >8 Mut/Mb

```{r}

km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tmb1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 1))
km_tmb0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 0))

# KM for the control group in blue
plot(km_control, xlab = "Months", ylab = "Progression-free Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# TMBcat=1 curve from the experimental group in pink
lines(km_tmb1, col = "pink", lwd = 2, conf.int = FALSE)

# TMBcat=0 curve from the experimental group as a dashed black line
lines(km_tmb0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

legend("topright", legend = c("Control Group", "TMB >8 Mut/Mb", "TMB ≤8 Mut/Mb"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

## same without control arm

```{r}
# Create the survival object using the METIMMOX_experimental dataset
surv_object_pfs_exp <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)

# Fit the Kaplan-Meier model using the METIMMOX_experimental dataset and survival object
fit.km <- survfit(surv_object_pfs_exp ~ TMBcat, data = METIMMOX_experimental)

plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("black", "pink"), lty = c("dashed", "solid"))

legend("topright", legend = c("TMB ≤8", "TMB >8"), lty = c("dashed", "solid"), col = c("black", "pink"))

median_pfs <- summary(fit.km)$table[, "median"]

group_levels <- c("TMB ≤8", "TMB >8")

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX_experimental$PFSmo)

# Add median PFS annotations to the plot for each CRP1cat group
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}
```

### log rank tests and hazarad ratios from Cox PH regression models for PFS

```{r}
log_rank_test <- survdiff(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in PFS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in PFS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by TMB ≥10 Mut/Mb (experimental arm)
cox_model <- coxph(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for TMB ≥10 Mut/Mb (experimental arm)
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (TMBcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(medians,log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("TMB <=8", "TMB >8"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

## same analysis, but similar to poster

```{r}
surv_object_pfs_exp <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)
fit.km <- survfit(surv_object_pfs_exp ~ TMBcat, data = METIMMOX_experimental)
plot(fit.km, xlab = "Months", ylab = "Progression-free Survival", col = c("cadetblue", "deeppink3"), lty = c("solid", "solid"), xlim = c(0, 48), axes = FALSE)
axis(1, at = seq(0, 48, by = 12), labels = seq(0, 48, by = 12))
axis(2)
legend("topright", legend = c("TMB ≤8", "TMB >8"), lty = c("solid", "solid"), col = c("cadetblue", "deeppink3"))
median_pfs <- summary(fit.km)$table[, "median"]
group_levels <- c("TMB ≤8", "TMB >8")
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)
x_offset <- 0.05 * 48
for (i in 1:n_groups) {
  text(x = median_pfs[i] + x_offset, y = y_values[i],
       labels = paste("Median PFS (", group_levels[i], "):", round(median_pfs[i], 1)),
       pos = 4)
}
```

# Survival Analysis 2: OS

```{r}
rm(list = setdiff(ls(), "METIMMOX"))

METIMMOX <- readRDS("METIMMOX.rds")
METIMMOX_control <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])
METIMMOX_experimental <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])

```

## Overall

```{r}
surv_object_os <- Surv(time = METIMMOX$OSmo, event = METIMMOX$Death)
fit.km <- survfit(surv_object_os ~ 1, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Overall Survival")
legend("topright", legend = c("Kaplan-Meier Estimate w/ 95% CI"), lty = 1, col = "black")
```

###compare to a quick Weibull

```{r}
fit.weibull <- flexsurvreg(surv_object_os ~ 1, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Overall Survival")
legend("topright", legend = c("Weibull Estimate w/ 95% CI"), lty = 1, col = "red")
```

##Control vs. Experimental arm

```{r}
fit.km <- survfit(surv_object_os ~ Rx, data = METIMMOX)
plot(fit.km, xlab = "Months", ylab = "Overall Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))

# median PFS for each treatment group
median_os <- summary(fit.km)$table[, "median"]
group_levels <- levels(METIMMOX$Rx)

# evenly spaced y-values for text annotations
n_groups <- length(group_levels)
y_values <- seq(from = 0.8, to = 0.8 - (n_groups - 1) * 0.1, length.out = n_groups)

# Define x-axis offset for text annotations
x_offset <- 0.05 * max(METIMMOX$OSmo)

# Add median PFS annotations to the plot for each treatment group
for (i in 1:n_groups) {
  text(x = median_os[i] + x_offset, y = y_values[i],
       labels = paste("Median OS (", group_levels[i], "):", round(median_os[i], 1)),
       pos = 4)
}
```

```{r}
fit.weibull <- flexsurvreg(surv_object_os ~ Rx, data = METIMMOX, dist="weibull")
plot(fit.weibull, xlab = "Months", ylab = "Overall Survival", col = c("blue", "pink"))
legend("topright", legend = levels(METIMMOX$Rx), lty = 1, col = c("blue", "pink"))
```

```{r}
km_control <- survfit(surv_object_os ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[1]))

ggsurvplot(km_control, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "blue", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$OSmo)), title = "Control Arm", surv.scale="percent")
```

```{r}
km_experimental <- survfit(surv_object_os ~ 1, data = METIMMOX, subset = (Rx == levels(Rx)[2]))

ggsurvplot(km_experimental, data = METIMMOX, conf.int = TRUE,
           conf.int.style = "ribbon", surv.median.line = "hv", ggtheme = theme_bw(),
           palette = "pink", risk.table = TRUE, legend = "none",
           xlim = c(0, max(METIMMOX$OSmo)), title = "Experimental Arm", surv.scale="percent")
```

##by TL reduction ≥10% (experimental arm)

```{r}

surv_control <- Surv(time = METIMMOX_control$OSmo, event = METIMMOX_control$Death)
surv_experimental <- Surv(time = METIMMOX_experimental$OSmo, event = METIMMOX_experimental$Death)

# Fit the Kaplan-Meier curves
km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tlr1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 1))
km_tlr0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TLRcat == 0))

# Plot the Kaplan-Meier curve for the control group in blue
plot(km_control, xlab = "Months", ylab = "Overall Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# Add the TLRcat=1 curve from the experimental group in pink
lines(km_tlr1, col = "pink", lwd = 2, conf.int = FALSE)

# Add the TLRcat=0 curve from the experimental group as a dashed black line
lines(km_tlr0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

# Add a legend
legend("topright", legend = c("Control Group", "≥10% TL reduction", "<10% TL reduction"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

##by CRP ≤5 after two FLOX cycles (experimental arm)

```{r}

# Fit the Kaplan-Meier curves
km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_crp1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 1))
km_crp0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (CRP1cat == 0))

# Plot the Kaplan-Meier curve for the control group in blue
plot(km_control, xlab = "Months", ylab = "Overall Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# Add the CRP1cat=1 curve from the experimental group in pink
lines(km_crp1, col = "pink", lwd = 2, conf.int = FALSE)

# Add the CRP1cat=0 curve from the experimental group as a dashed black line
lines(km_crp0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

# Add a legend
legend("topright", legend = c("Control Group", "CRP ≤ 5.0", "CRP > 5.0"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

##by TMB >8 Mut/Mb (experimental arm)

```{r}

# Fit the Kaplan-Meier curves
km_control <- survfit(surv_control ~ 1, data = METIMMOX_control)
km_tmb1 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 1))
km_tmb0 <- survfit(surv_experimental ~ 1, data = METIMMOX_experimental, subset = (TMBcat == 0))

# Plot the Kaplan-Meier curve for the control group in blue
plot(km_control, xlab = "Months", ylab = "Overall Survival", col = "blue", lwd = 2, 
     conf.int = FALSE)

# Add the TMBcat=1 curve from the experimental group in pink
lines(km_tmb1, col = "pink", lwd = 2, conf.int = FALSE)

# Add the CRP1cat=0 curve from the experimental group as a dashed black line
lines(km_tmb0, col = "black", lty = 2, lwd = 2, conf.int = FALSE)

# Add a legend
legend("topright", legend = c("Control Group", "TMB >8 Mut/Mb", "TMB ≤8 Mut/Mb"),
       col = c("blue", "pink", "black"), lty = c(1, 1, 2), lwd = 2)
```

## log rank tests and hazarad ratios from Cox PH regression models for OS

### Control vs. experimental

```{r}

median_os <- summary(fit.km)$table[, "median"]
group_levels <- levels(METIMMOX$Rx)
cat("Median OS by Treatment Group:\n")
for (i in 1:length(group_levels)) {
  cat(group_levels[i], ": ", round(median_os[i], 2), " months\n", sep = "")
}

log_rank_test <- survdiff(surv_object_os ~ Rx, data = METIMMOX)
print(log_rank_test)

# Cox PH regression model with Rx as the predictor variable
cox_model <- coxph(surv_object_os ~ Rx, data = METIMMOX)
summary(cox_model)

# HR and CI for Rx
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))

# Print the hazard ratio and confidence interval
cat("Hazard Ratio (Rx):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(median_os,group_levels,log_rank_test,cox_model,hr,ci)
```

##by TL reduction ≥10% (experimental arm)

```{r}

log_rank_test <- survdiff(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in OS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in OS between the TLRcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression  model stratified by TLRcat in the experimental group
cox_model <- coxph(surv_experimental ~ TLRcat, data = METIMMOX_experimental)

# Print the summary of the Cox model
summary(cox_model)

# Extract the hazard ratio and confidence interval for TLRcat
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))

# Print the hazard ratio and confidence interval
cat("Hazard Ratio (TLRcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TLRcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("TLR <=10%", "TLR >10%"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by CRP <5 after two FLOX cycles (experimental arm)

```{r}

log_rank_test <- survdiff(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in OS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in OS between the CRP1cat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model stratified by CRP1cat in the experimental group
cox_model <- coxph(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for CRP1cat
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (CRP1cat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ CRP1cat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("CRP >=5", "CRP <5"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

##by TMB >8 Mut/Mb (experimental arm)

```{r}

log_rank_test <- survdiff(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
print(log_rank_test)
if (log_rank_test$pvalue < 0.05) {
  cat("There is a significant difference in OS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
} else {
  cat("There is no significant difference in OS between the TMBcat groups in the experimental arm (p =", log_rank_test$pvalue, ")\n")
}

# Cox PH regression model, stratified by TMBcat in the experimental group
cox_model <- coxph(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
summary(cox_model)

# HR and CI for TMBcat
hr <- exp(coef(cox_model))
ci <- exp(confint(cox_model))
cat("Hazard Ratio (TMBcat):", round(hr, 2), "\n")
cat("95% Confidence Interval:", round(ci[, 1], 2), "-", round(ci[, 2], 2), "\n")
rm(log_rank_test,cox_model,hr,ci)
```

### PH assumption
```{r}
# 1. Log-log plots
km_fit_exp <- survfit(surv_experimental ~ TMBcat, data = METIMMOX_experimental)
par(mfrow = c(1, 2))
plot(km_fit_exp, fun = "cloglog", xlab = "Log(Time)", ylab = "Log(-Log(Survival))",
     col = c("black", "pink"), lty = c(2, 1), lwd = 2,
     main = "Log-Log Survival Curves")
legend("bottomright", legend = c("TMB <=8", "TMB >8"),
       col = c("black", "pink"), lty = c(2, 1), lwd = 2)

# 2. Schoenfeld residuals test and plot
cox_zph_result <- cox.zph(cox_model)
plot(cox_zph_result)

# 3. Output test results
print(cox_zph_result)

# 4. Interpretation
cat("\n--- Interpretation of Proportional Hazards Assumption ---\n")
if (cox_zph_result$table[1, "p"] < 0.05) {
  cat("The proportional hazards assumption appears to be violated (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("Consider using an extended Cox model with time-dependent coefficients\n")
  cat("or stratification for the TMBcat variable.\n")
} else {
  cat("The proportional hazards assumption appears to be met (p =", 
      round(cox_zph_result$table[1, "p"], 4), ").\n")
  cat("The Cox proportional hazards model is appropriate for your data.\n")
}
```

# Survival Analyis 3: compare biomarkers

## PFS
```{r}
library(survival)
library(survminer)

surv_obj <- Surv(time = METIMMOX_experimental$PFSmo, event = METIMMOX_experimental$`Progression exit`)
```

```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat + TMBcat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)", "TMBcat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```

```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```
## OS

```{r}
rm(surv_obj)
surv_obj <- Surv(time = METIMMOX_experimental$OSmo, event = METIMMOX_experimental$`Death`)
```



```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat + TMBcat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)", "TMBcat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```

```{r}
multivariate_cox <- coxph(surv_obj ~ TLRcat + CRP1cat, 
                          data = METIMMOX_experimental)

summary_result <- summary(multivariate_cox)
print(summary_result)

hr <- exp(coef(multivariate_cox))
ci <- exp(confint(multivariate_cox))

results_table <- data.frame(
  Variable = c("TLRcat (positive)", "CRP1cat (positive)"),
  HR = sprintf("%.2f", hr),
  CI_95 = sprintf("%.2f-%.2f", ci[,1], ci[,2]),
  P_value = sprintf("%.3f", summary_result$coefficients[,5])
)
print(results_table)

ph_test <- cox.zph(multivariate_cox)
print(ph_test)

par(mfrow = c(2, 2))
plot(ph_test)
par(mfrow = c(1, 1))

# concordance index (C-index)
c_index <- summary_result$concordance
cat("\nModel Performance:\n")
cat("Concordance Index (C-index):", round(c_index[1], 3), 
    "\nStandard Error:", round(c_index[2], 3), "\n")
rm(multivariate_cox,summary_result,results_table,ph_test,c_index)
```

# Create partitioned survival models & export to Excel

```{r}
rm(list = setdiff(ls(), "METIMMOX"))
```


## load survival functions from DARTH

Source: <https://github.com/DARTH-git/Survival-analysis-and-decision-modeling/> Note: I have modified this code to only fit Weibul models given that not all the other models converge

```{r}
source("DARTH_surv_func.R")
```

## if necessary, can create custom function to create individual partitioned survival models

```{r}
#PSM.fun <- function()  
#{
#}
```

##setup

```{r}
# number of states in the model
v_n       <- c("non-progressed", "progressed", "dead") # state names
n_s       <- length(v_n)           # No of states 
n_i       <- 5000                  # number of simulations 
c_l       <- 1 / 52.1429                # cycle length (a week)
n_t       <- 10                    # number of years (10 years)
times     <- seq(0, n_t, c_l)  # the cycles in years
set.seed(1234)                 # set the seed


# Create a transition probability matrix  with all transitions indicated and numbered
tmat <- matrix(NA, n_s, n_s, dimnames = list(v_n,v_n))
tmat["non-progressed", "progressed"]  <- 1
tmat["non-progressed", "dead"]  <- 2
tmat["progressed"   , "dead"]  <- 3

```

##individual parametric models
### control group

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_control.csv")
#rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)

########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

###select Weibull model for now Source: <https://github.com/DARTH-git/Survival-analysis-and-decision-modeling/> Note: I have modified this code to only fit Weibul models given that not all the other models converge

```{r}
#source("DARTH_surv_func.R")
source("DARTH_surv_func weib only.R")
```

###compare Weibull models with KM curve: PFS

```{r}
METIMMOX_lim <- METIMMOX %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)

KM.pfs <- survfit(Surv(time = PFSmo, event = `Progression exit`) ~ 1, data = METIMMOX_lim)
KM.os <- survfit(Surv(time = OSmo, event = Death) ~ 1, data = METIMMOX_lim)

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

plot(KM.pfs, ylab = "Survival Probability", xlab = "Time",  main = paste ("True vs Fitted PFS")) 
lines(best.pfs,  col = 2, t = times, lty = 2)   

plot(KM.os, ylab = "Survival Probability", xlab = "Time",  main = c("True vs Fitted OS"))
lines(best.os,  col = 2, t = times, lty = 2)  

rm("METIMMOX_lim", "KM.pfs", "KM.os", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TLR reduction <10% - include

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TLRcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)
#write.csv(METIMMOX_lim, "test.csv")

########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times, extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tlr0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TLR reduction ≥10% - exclude

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TLRcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tlr1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TLR reduction <10% - exclude

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TLRcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)
#write.csv(METIMMOX_lim, "test.csv")

########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times, extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tlr0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TLR reduction ≥10% - include

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TLRcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tlr1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - CRP <5

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & CRP1cat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#rite.csv(PSM, "PSM_con_crp1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - CRP >=5

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & CRP1cat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_crp0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - CRP <5

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & CRP1cat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_crp1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - CRP >=5.0

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & CRP1cat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_crp0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TMB <=8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TMBcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tmb0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TMB >8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TMBcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tmb1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TMB <=8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TMBcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tmb0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TMB >8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TMBcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tmb1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

# QALys

```{r}
rm(list = setdiff(ls(), "METIMMOX"))

METIMMOX <- readRDS("METIMMOX.rds")
METIMMOX_control <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])
METIMMOX_experimental <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])
```

##VAS

```{r}
METIMMOX_rx <- METIMMOX %>%
  select(ID, Rx) 
QALYsraw <- read_excel("clinical data/231208 METIMMOX EQ_5D_5L.xlsx", sheet = 2, skip = 1) %>%
  rename(ID = SubjectId)
colnames(QALYsraw)

QALYsVAS <- QALYsraw %>%
  select(ID, ends_with("_VAS"))
QALYsVAS <- merge(METIMMOX_rx, QALYsVAS, by = "ID", all = FALSE)
colnames(QALYsVAS)
str(QALYsVAS)

# Get the column names excluding "ID" and "Rx"
cols_to_convert <- setdiff(colnames(QALYsVAS), c("ID", "Rx"))

# Convert character columns to numeric
QALYsVAS_numeric <- QALYsVAS %>%
  mutate(across(all_of(cols_to_convert), as.numeric))

# Get the column names of numeric columns excluding "ID" and "Rx"
numeric_cols <- QALYsVAS_numeric %>%
  select(-ID, -Rx) %>%
  select_if(is.numeric) %>%
  colnames()

#create table with the number of observations and median scores for numeric columns
if (length(numeric_cols) > 0) {
  obs_median_table <- QALYsVAS_numeric %>%
    reframe(across(all_of(numeric_cols), ~list(Observations = sum(!is.na(.)), Median = median(., na.rm = TRUE)))) %>%
    pivot_longer(everything(), names_to = "Variable", values_to = "Value") %>%
    unnest(cols = c(Value)) %>%
    mutate(Measure = rep(c("Observations", "Median"), length.out = n())) %>%
    pivot_wider(names_from = Measure, values_from = Value) %>%
    group_by(Variable) %>%
    summarise(Observations = sum(Observations),
              Median = median(Median)) %>%
    ungroup()
  
  print(obs_median_table)
} else {
  print("No numeric columns found in the dataset.")
}
print(obs_median_table)
```

##EQ5D conversion

```{r}
METIMMOX_rx <- METIMMOX %>%
  select(ID, Rx, "First progression") 
QALYsmanual <- read_excel("clinical data/EQ5Dmanual.xlsx", sheet = 1, skip = 0)

eq5d5l_data <- merge(METIMMOX_rx, QALYsmanual, by = "ID")

# new variable 'progressed' 
eq5d5l_data$progressed <- ifelse(eq5d5l_data$`First progression` < eq5d5l_data$Date, 1, 0)

eq5d5l_utility_dk <- function(mo, sc, ua, pd, ad) {
  utility <- 1 - (
    0.041 * (mo == 2) + 0.054 * (mo == 3) + 0.157 * (mo == 4) + 0.220 * (mo == 5) +
    0.035 * (sc == 2) + 0.050 * (sc == 3) + 0.144 * (sc == 4) + 0.209 * (sc == 5) +
    0.033 * (ua == 2) + 0.040 * (ua == 3) + 0.139 * (ua == 4) + 0.174 * (ua == 5) +
    0.048 * (pd == 2) + 0.094 * (pd == 3) + 0.381 * (pd == 4) + 0.537 * (pd == 5) +
    0.072 * (ad == 2) + 0.191 * (ad == 3) + 0.430 * (ad == 4) + 0.618 * (ad == 5)
  )
  
  return(utility)
}

eq5d5l_utility_uk <- function(mo, sc, ua, pd, ad) {
  utility <- 1 - (
    0.058 * (mo == 2) + 0.076 * (mo == 3) + 0.207 * (mo == 4) + 0.274 * (mo == 5) +
    0.050 * (sc == 2) + 0.080 * (sc == 3) + 0.164 * (sc == 4) + 0.203 * (sc == 5) +
    0.050 * (ua == 2) + 0.063 * (ua == 3) + 0.162 * (ua == 4) + 0.184 * (ua == 5) +
    0.063 * (pd == 2) + 0.084 * (pd == 3) + 0.276 * (pd == 4) + 0.335 * (pd == 5) +
    0.078 * (ad == 2) + 0.104 * (ad == 3) + 0.285 * (ad == 4) + 0.289 * (ad == 5)
  )
  
  return(utility)
}

#utility_dk <- eq5d5l_utility_dk(eq5d5ldata["mo"], eq5d5ldata["sc"], eq5d5ldata["ua"], eq5d5ldata["pd"], eq5d5ldata["ad"])
#utility_uk <- eq5d5l_utility_uk(eq5d5ldata["mo"], eq5d5ldata["sc"], eq5d5ldata["ua"], eq5d5ldata["pd"], eq5d5ldata["ad"])
#print(utility_dk)
#print(utility_uk)


eq5d5l_data$utility_dk <- eq5d5l_utility_dk(eq5d5l_data$mo, eq5d5l_data$sc, eq5d5l_data$ua, eq5d5l_data$pd, eq5d5l_data$ad)
eq5d5l_data$utility_uk <- eq5d5l_utility_uk(eq5d5l_data$mo, eq5d5l_data$sc, eq5d5l_data$ua, eq5d5l_data$pd, eq5d5l_data$ad)

# summarize
cat("Summary of utility_dk stratified by progressed:\n")
summary_dk <- aggregate(utility_dk ~ progressed, data = eq5d5l_data, FUN = function(x) c(Mean = mean(x), 
                                                                                           Median = median(x),
                                                                                           SD = sd(x),
                                                                                           Min = min(x),
                                                                                           Max = max(x)))
summary_dk <- do.call(data.frame, summary_dk)
print(summary_dk)
cat("\n")

cat("Summary of utility_uk stratified by progressed:\n")
summary_uk <- aggregate(utility_uk ~ progressed, data = eq5d5l_data, FUN = function(x) c(Mean = mean(x),
                                                                                           Median = median(x),
                                                                                           SD = sd(x),
                                                                                           Min = min(x),
                                                                                           Max = max(x)))
summary_uk <- do.call(data.frame, summary_uk)
print(summary_uk)

# box-and-whisker plots
plot_dk <- ggplot(eq5d5l_data, aes(x = factor(progressed), y = utility_dk, fill = factor(progressed))) +
  geom_boxplot() +
  labs(x = "Progressed", y = "Utility (Danish Value Set)", fill = "Progressed") +
  scale_fill_discrete(labels = c("No", "Yes")) +
  theme_minimal()

print(plot_dk)

plot_uk <- ggplot(eq5d5l_data, aes(x = factor(progressed), y = utility_uk, fill = factor(progressed))) +
  geom_boxplot() +
  labs(x = "Progressed", y = "Utility (U.K. Value Set)", fill = "Progressed") +
  scale_fill_discrete(labels = c("No", "Yes")) +
  theme_minimal()

print(plot_uk)
```


#this was were we ended with the Excel model.
# -------------------------------------------------------------