---
title: "survival models"
author: "Ben Geisler"
date: "2025-08-29"
output: pdf_document
---

# load required libries
```{r}
require(pacman)
pacman::p_load(
  survival,
  flexsurv,
  dplyr,
  ggplot2,
  emmeans
)
```

# fit_all_direct function by Frederick
```{r}
fit_all_direct <- function(fit_data,
                    fit_formula, # the survival formula
                    fit_dists = c("exponential",
                                  "gamma",
                                  "genf",
                                  "gengamma",
                                  "gompertz",
                                  "weibull",
                                  "weibullph",
                                  "llogis",
                                  "lognormal"),
                    strip_bkgr_dat = TRUE # to delete data from fitted objects
                    ){
 
  # Load packages
  require(survival)
  require(flexsurv)
 
  # Define names to automatically create named list of fits
  names(fit_dists) <- fit_dists
 
  # Extract data object name
  data_name <- deparse(substitute(fit_data))
 
  # Fit KM ignoring any subgroups
  km_all <- eval(as.call(list(quote(survival::survfit),
                              formula = update(fit_formula, ~ 1),
                              data = quote(fit_data))))
 
  # Fit KM with strata - but remove interaction terms first
  # Extract main effects only for survfit
  formula_terms <- terms(fit_formula)
  main_effects <- attr(formula_terms, "term.labels")
  # Remove interaction terms (those containing ":")
  main_effects <- main_effects[!grepl(":", main_effects)]
  
  if(length(main_effects) > 0) {
    # Create formula with main effects only
    km_formula <- as.formula(paste(deparse(fit_formula[[2]]), "~", paste(main_effects, collapse = " + ")))
    km_std <- eval(as.call(list(quote(survival::survfit),
                                formula = km_formula,
                                data = quote(fit_data))))
  } else {
    # If no main effects, use the intercept-only model
    km_std <- km_all
  }
 
  # Fit all standard models (these can handle interactions)
  fits <- lapply(fit_dists,
                 function(x){
                   tryCatch(expr = eval(as.call(list(quote(flexsurvreg),
                                                     formula = fit_formula,
                                                     data = quote(fit_data),
                                                     dist = x))),
                            error = function(e) paste("Error message:", e$message))
                 })
 
  # Strip background data from fitted models
  if(strip_bkgr_dat) {
    for (i in 1:length(fit_dists)) {
      tryCatch(fits[[i]][["data"]] <- NULL,
               error = function(e) NULL)
    }
  }
 
  # Create result list
  res <- list(data_name = data_name,
              km_all = km_all,
              km_std = km_std,
              fitted_models = fits)
}
```

# helper function to extract both AIC and BIC
```{r}
extract_ic_table <- function(results) {
  # Simple data frame to collect results
  ic_data <- data.frame(
    Model = character(),
    Distribution = character(),
    AIC = numeric(),
    BIC = numeric(),
    stringsAsFactors = FALSE
  )
  
  # Loop through each model
  for (model_name in names(results)) {
    fitted_models <- results[[model_name]]$fitted_models
    
    # Loop through each distribution
    for (dist_name in names(fitted_models)) {
      fit_obj <- fitted_models[[dist_name]]
      
      # Initialize values
      aic_val <- NA
      bic_val <- NA
      
      # Check if it's a successful fit
      if (inherits(fit_obj, "flexsurvreg")) {
        # Try AIC 
        aic_result <- try(AIC(fit_obj), silent = TRUE)
        if (!inherits(aic_result, "try-error")) {
          aic_val <- aic_result
        }
        
        # Calculate BIC manually: BIC = -2*loglik + k*log(n)
        tryCatch({
          loglik <- fit_obj$loglik
          k <- length(fit_obj$coefficients)
          n <- fit_obj$N
          
          if (!is.null(loglik) && !is.null(k) && !is.null(n)) {
            bic_val <- -2 * loglik + k * log(n)
          }
        }, error = function(e) NULL)
      }
      
      # Add row
      ic_data <- rbind(ic_data, data.frame(
        Model = model_name,
        Distribution = dist_name,
        AIC = aic_val,
        BIC = bic_val,
        stringsAsFactors = FALSE
      ))
    }
  }
  
  return(ic_data)
}
```

# main code - check dataset
```{r}
# Define the right-hand side formulas once
formula_rhs <- list(
  "0" = ~ 1,
  "1" = ~ crp:Rx,
  "2" = ~ tlr:Rx,
  "3" = ~ tmb_braf:Rx,
  "4" = ~ Age + sex + crp:Rx,
  "5" = ~ Age + sex + tlr:Rx,
  "6" = ~ Age + sex + tmb_braf:Rx,
  "7" = ~ crp:Rx + tlr:Rx + tmb_braf:Rx,
  "8" = ~ Age + sex + crp:Rx + tlr:Rx + tmb_braf:Rx
  )

# Initialize empty lists
formulas_os <- list()
formulas_pfs <- list()

# Populate both lists via loop
for (i in names(formula_rhs)) {
  # Create OS formula
  formulas_os[[paste0("os", i)]] <- as.formula(paste("Surv(OSwk, Death)", deparse(formula_rhs[[i]])))
  
  # Create PFS formula  
  formulas_pfs[[paste0("pfs", i)]] <- as.formula(paste("Surv(PFSwk, Progression)", deparse(formula_rhs[[i]])))
}

os_results <- list()
pfs_results <- list()

for (nm in names(formulas_os)) {
  os_results[[nm]] <- fit_all_direct(data_control, formulas_os[[nm]])
}

for (nm in names(formulas_pfs)) {
  pfs_results[[nm]] <- fit_all_direct(data_control, formulas_pfs[[nm]])
}

# Extract IC tables
ic_table_os <- extract_ic_table(os_results)
ic_table_pfs <- extract_ic_table(pfs_results)

# Function to rearrange IC table - models as rows, distributions as columns
rearrange_ic_table <- function(ic_table) {
  # Split into AIC and BIC tables
  aic_wide <- reshape(ic_table[, c("Model", "Distribution", "AIC")], 
                      idvar = "Model", 
                      timevar = "Distribution", 
                      direction = "wide")
  
  bic_wide <- reshape(ic_table[, c("Model", "Distribution", "BIC")], 
                      idvar = "Model", 
                      timevar = "Distribution", 
                      direction = "wide")
  
  # Clean column names
  names(aic_wide) <- gsub("AIC\\.", "", names(aic_wide))
  names(bic_wide) <- gsub("BIC\\.", "", names(bic_wide))
  
  # Add prefix to distinguish AIC from BIC
  names(aic_wide)[-1] <- paste0("AIC_", names(aic_wide)[-1])
  names(bic_wide)[-1] <- paste0("BIC_", names(bic_wide)[-1])
  
  # Merge AIC and BIC tables
  combined <- merge(aic_wide, bic_wide, by = "Model")
  
  # Reorder columns: Model, then all AIC columns, then all BIC columns
  aic_cols <- grep("^AIC_", names(combined), value = TRUE)
  bic_cols <- grep("^BIC_", names(combined), value = TRUE)
  
  combined <- combined[, c("Model", aic_cols, bic_cols)]
  
  return(combined)
}

# Rearrange tables
ic_table_os_wide <- rearrange_ic_table(ic_table_os)
ic_table_pfs_wide <- rearrange_ic_table(ic_table_pfs)

# Print rearranged tables
print("OS Models - Wide Format:")
print(ic_table_os_wide)

print("PFS Models - Wide Format:")
print(ic_table_pfs_wide)
```

# output all model parameters
```{r}
check_model_parameters <- function(results, model_name) {
  model_results <- results[[model_name]]
  
  cat("=== Parameter Summary for", model_name, "===\n")
  
  for (dist in names(model_results$fitted_models)) {
    fit_obj <- model_results$fitted_models[[dist]]
    if (inherits(fit_obj, "flexsurvreg")) {
      cat("\n", dist, ":\n")
      print(fit_obj$res.t)
      cat("Parameter names:", paste(rownames(fit_obj$res.t), collapse = ", "), "\n")
    } else {
      cat("\n", dist, ": FAILED FIT\n")
    }
  }
}

# First, let's check the parameters
cat("Checking OS0 parameters:\n")
check_model_parameters(os_results, "os0")

cat("\n\nChecking PFS0 parameters:\n")
check_model_parameters(pfs_results, "pfs0")
```

# plotting function
```{r}
plot_single_survival <- function(results, 
                                outcome_type = "OS", 
                                model_name = "os0") {
  
  # Extract the specific model results
  model_results <- results[[model_name]]
  
  # Get KM estimates
  km_fit <- model_results$km_all
  
  # Determine time range
  time_max <- max(km_fit$time, na.rm = TRUE)
  
  # Create time sequence for predictions
  time_seq <- seq(0.01, time_max, length.out = 200)
  
  # Extract KM data for plotting
  km_data <- data.frame(
    time = km_fit$time,
    surv = km_fit$surv,
    lower = km_fit$lower,
    upper = km_fit$upper
  ) %>%
    filter(!is.na(surv) & time >= 0)
  
  # Colors for different distributions
  dist_colors <- c(
    "exponential" = "#E31A1C",
    "weibull" = "#1F78B4", 
    "llogis" = "#33A02C",
    "lognormal" = "#FF7F00",
    "gamma" = "#6A3D9A",
    "gompertz" = "#FB9A99",
    "gengamma" = "#A6CEE3",
    "genf" = "#B2DF8A",
    "weibullph" = "#FDBF6F"
  )
  
  # Initialize plot
  p <- ggplot() +
    geom_step(data = km_data, 
              aes(x = time, y = surv), 
              color = "black", 
              linewidth = 1.5) +
    geom_ribbon(data = km_data,
                aes(x = time, ymin = lower, ymax = upper),
                alpha = 0.2,
                fill = "grey50") +
    theme_minimal() +
    labs(
      title = paste(outcome_type, "- Model:", model_name),
      x = "Time (weeks)",
      y = "Survival Probability",
      color = "Distribution"
    ) +
    theme(
      plot.title = element_text(size = 14, hjust = 0.5),
      legend.position = "bottom"
    ) +
    scale_y_continuous(limits = c(0, 1))
  
  # Get all available distributions
  available_dists <- names(model_results$fitted_models)
  
  # Add parametric fits with correct parameterizations
  parametric_data <- data.frame()
  
  for (dist in available_dists) {
    fit_obj <- model_results$fitted_models[[dist]]
    
    if (inherits(fit_obj, "flexsurvreg")) {
      tryCatch({
        
        # Extract parameters from the fit object
        params <- fit_obj$res.t[, "est"]
        
        surv_pred <- switch(dist,
          
          "exponential" = {
            rate <- exp(params["rate"])
            exp(-rate * time_seq)
          },
          
          "weibull" = {
            shape <- exp(params["shape"])
            scale <- exp(params["scale"])
            exp(-(time_seq/scale)^shape)
          },
          
          "weibullph" = {
            # CORRECTED: WeibullPH uses S(t) = exp(-exp(scale) * t^exp(shape))
            shape <- exp(params["shape"])
            log_scale <- params["scale"]  # This is log(baseline hazard)
            exp(-exp(log_scale) * time_seq^shape)
          },
          
          "llogis" = {
            shape <- exp(params["shape"])
            scale <- exp(params["scale"])
            1 / (1 + (time_seq/scale)^shape)
          },
          
          "lognormal" = {
            meanlog <- params["meanlog"]
            sdlog <- exp(params["sdlog"])
            1 - plnorm(time_seq, meanlog = meanlog, sdlog = sdlog)
          },
          
          "gamma" = {
            shape <- exp(params["shape"])
            rate <- exp(params["rate"])
            1 - pgamma(time_seq, shape = shape, rate = rate)
          },
          
          "gompertz" = {
            shape <- params["shape"]
            rate <- exp(params["rate"])
            if (abs(shape) < 1e-6) {
              exp(-rate * time_seq)
            } else {
              exp(-rate/shape * (exp(shape * time_seq) - 1))
            }
          },
          
          "gengamma" = {
            mu <- params["mu"]
            sigma <- exp(params["sigma"])
            Q <- params["Q"]
            1 - flexsurv::pgengamma(time_seq, mu = mu, sigma = sigma, Q = Q)
          },
          
          "genf" = {
            mu <- params["mu"]
            sigma <- exp(params["sigma"])
            Q <- params["Q"]
            P <- params["P"]
            1 - flexsurv::pgenf(time_seq, mu = mu, sigma = sigma, Q = Q, P = P)
          },
          
          NA
        )
        
        if (!all(is.na(surv_pred))) {
          valid_idx <- !is.na(surv_pred) & surv_pred >= 0 & surv_pred <= 1 & is.finite(surv_pred)
          if (sum(valid_idx) > 10) {
            temp_data <- data.frame(
              time = time_seq[valid_idx],
              surv = surv_pred[valid_idx],
              distribution = dist
            )
            parametric_data <- rbind(parametric_data, temp_data)
          }
        }
        
      }, error = function(e) {
        # Silent error handling
      })
    }
  }
  
  # Add parametric curves
  if (nrow(parametric_data) > 0) {
    p <- p + geom_line(data = parametric_data,
                      aes(x = time, y = surv, color = distribution),
                      linewidth = 0.8) +
          scale_color_manual(values = dist_colors)
  }
  
  return(p)
}
```

#survival plots for PFS0 and OS0 only
```{r}
# Create individual OS plot
os0_plot <- plot_single_survival(os_results, "Overall Survival", "os0")

# Create individual PFS plot
pfs0_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs0")

# Display plots one by one
print("OS Model 0 (Intercept only):")
print(os0_plot)

print("PFS Model 0 (Intercept only):")
print(pfs0_plot)
```

# ---
# Function to calculate estimated marginal means
```{r}
calculate_emmeans <- function(data) {
  
  # Calculate means for continuous variables
  age_mean <- mean(data$Age, na.rm = TRUE)
  
  # Calculate mode/most frequent category for categorical variables
  sex_mode <- as.numeric(names(sort(table(data$sex), decreasing = TRUE))[1])
  rx_mode <- names(sort(table(data$Rx), decreasing = TRUE))[1]
  
  # For binary biomarkers, calculate the proportion
  crp_mean <- mean(data$crp, na.rm = TRUE)
  tlr_mean <- mean(data$tlr, na.rm = TRUE)
  tmb_braf_mean <- mean(data$tmb_braf, na.rm = TRUE)
  
  emmeans_data <- list(
    Age = age_mean,
    sex = sex_mode,
    Rx = rx_mode,
    crp = crp_mean,
    tlr = tlr_mean,
    tmb_braf = tmb_braf_mean
  )
  
  cat("Estimated Marginal Means:\n")
  cat("Age:", round(age_mean, 2), "\n")
  cat("sex:", sex_mode, "\n")
  cat("Rx:", rx_mode, "\n")
  cat("crp:", round(crp_mean, 3), "\n")
  cat("tlr:", round(tlr_mean, 3), "\n")
  cat("tmb_braf:", round(tmb_braf_mean, 3), "\n\n")
  
  return(emmeans_data)
}
```

# Main function to create scenario plots
```{r}
create_scenario_plots_from_existing <- function(data, os_results, pfs_results, 
                                               models_to_plot = paste0("os", 1:8),
                                               dist_to_use = "weibull") {
  
  # Calculate estimated marginal means
  emmeans_data <- calculate_emmeans(data)
  
  # Define scenarios
  scenarios <- list(
    "crp_1" = list(var = "crp", value = 1, label = "CRP = 1"),
    "crp_0" = list(var = "crp", value = 0, label = "CRP = 0"),
    "tlr_1" = list(var = "tlr", value = 1, label = "TLR = 1"),
    "tlr_0" = list(var = "tlr", value = 0, label = "TLR = 0"),
    "tmb_braf_1" = list(var = "tmb_braf", value = 1, label = "TMB_BRAF = 1"),
    "tmb_braf_0" = list(var = "tmb_braf", value = 0, label = "TMB_BRAF = 0")
  )
  
  # Time sequence for predictions
  time_max <- max(c(data$OSwk, data$PFSwk), na.rm = TRUE)
  time_seq <- seq(0.01, time_max, length.out = 200)
  
  # Colors for scenarios
  scenario_colors <- c(
    "crp_1" = "#E31A1C", "crp_0" = "#FB9A99",
    "tlr_1" = "#1F78B4", "tlr_0" = "#A6CEE3", 
    "tmb_braf_1" = "#33A02C", "tmb_braf_0" = "#B2DF8A"
  )
  
  # Store results
  plot_results <- list()
  
  for (model_name in models_to_plot) {
    
    cat("Processing model:", model_name, "\n")
    
    # Get fitted models from your existing results
    os_fit <- os_results[[model_name]]$fitted_models[[dist_to_use]]
    pfs_model_name <- gsub("os", "pfs", model_name)
    pfs_fit <- pfs_results[[pfs_model_name]]$fitted_models[[dist_to_use]]
    
    # Check if fits exist and are valid
    if (!inherits(os_fit, "flexsurvreg") || !inherits(pfs_fit, "flexsurvreg")) {
      cat("Skipping", model_name, "- invalid fit objects\n")
      next
    }
    
    # Temporarily restore data to fit objects
    os_fit$data <- data
    pfs_fit$data <- data
    
    # Create prediction data for each scenario
    scenario_data <- data.frame()
    
    for (scenario_name in names(scenarios)) {
      scenario_info <- scenarios[[scenario_name]]
      
      # Create newdata for this scenario
      newdata <- create_scenario_newdata(data, emmeans_data, scenario_info$var, scenario_info$value)
      
      # Predict OS
      tryCatch({
        os_pred <- summary(os_fit, t = time_seq, type = "survival", newdata = newdata)
        
        if (is.data.frame(os_pred) && "est" %in% names(os_pred)) {
          temp_os <- data.frame(
            time = time_seq,
            surv = os_pred$est,
            outcome = "OS",
            scenario = scenario_name,
            scenario_label = scenario_info$label
          )
          scenario_data <- rbind(scenario_data, temp_os)
          cat("✓ OS prediction successful for", scenario_name, "\n")
        }
      }, error = function(e) {
        cat("✗ OS prediction failed for", scenario_name, ":", e$message, "\n")
      })
      
      # Predict PFS
      tryCatch({
        pfs_pred <- summary(pfs_fit, t = time_seq, type = "survival", newdata = newdata)
        
        if (is.data.frame(pfs_pred) && "est" %in% names(pfs_pred)) {
          temp_pfs <- data.frame(
            time = time_seq,
            surv = pfs_pred$est,
            outcome = "PFS", 
            scenario = scenario_name,
            scenario_label = scenario_info$label
          )
          scenario_data <- rbind(scenario_data, temp_pfs)
          cat("✓ PFS prediction successful for", scenario_name, "\n")
        }
      }, error = function(e) {
        cat("✗ PFS prediction failed for", scenario_name, ":", e$message, "\n")
      })
    }
    
    # Remove data from fit objects again
    os_fit$data <- NULL
    pfs_fit$data <- NULL
    
    # Create plots if we have data
    if (nrow(scenario_data) > 0) {
      
      # OS plot
      os_data <- scenario_data[scenario_data$outcome == "OS", ]
      if (nrow(os_data) > 0) {
        os_plot <- ggplot(os_data, aes(x = time, y = surv, color = scenario)) +
          geom_line(linewidth = 1.2) +
          scale_color_manual(values = scenario_colors, 
                           labels = setNames(sapply(scenarios, function(x) x$label), names(scenarios))) +
          theme_minimal() +
          labs(
            title = paste("Overall Survival -", model_name, "(", dist_to_use, ")"),
            x = "Time (weeks)",
            y = "Survival Probability",
            color = "Scenario"
          ) +
          theme(legend.position = "bottom") +
          scale_y_continuous(limits = c(0, 1)) +
          guides(color = guide_legend(ncol = 3))
        
        plot_results[[paste0(model_name, "_os")]] <- os_plot
      }
      
      # PFS plot
      pfs_data <- scenario_data[scenario_data$outcome == "PFS", ]
      if (nrow(pfs_data) > 0) {
        pfs_plot <- ggplot(pfs_data, aes(x = time, y = surv, color = scenario)) +
          geom_line(linewidth = 1.2) +
          scale_color_manual(values = scenario_colors,
                           labels = setNames(sapply(scenarios, function(x) x$label), names(scenarios))) +
          theme_minimal() +
          labs(
            title = paste("Progression-Free Survival -", pfs_model_name, "(", dist_to_use, ")"),
            x = "Time (weeks)",
            y = "Survival Probability", 
            color = "Scenario"
          ) +
          theme(legend.position = "bottom") +
          scale_y_continuous(limits = c(0, 1)) +
          guides(color = guide_legend(ncol = 3))
        
        plot_results[[paste0(pfs_model_name, "_pfs")]] <- pfs_plot
      }
    } else {
      cat("No valid predictions for", model_name, "\n")
    }
  }
  
  return(plot_results)
}
```

# Execute the analysis
```{r}
cat("=== Creating Scenario-Based Survival Plots (Using Existing Models) ===\n")

# Create scenario plots using your existing fitted models
scenario_plots <- create_scenario_plots_from_existing(
  data = data,
  os_results = os_results,
  pfs_results = pfs_results,
  models_to_plot = paste0("os", 1:8),
  dist_to_use = "weibull"  # Change this to your preferred distribution
)

# Display results
if (length(scenario_plots) > 0) {
  cat("\nCreated", length(scenario_plots), "scenario plots\n")
  
  # Show first few plots
  if ("os1_os" %in% names(scenario_plots)) {
    print("OS1 scenario plot:")
    print(scenario_plots$os1_os)
  }
  
  if ("pfs1_pfs" %in% names(scenario_plots)) {
    print("PFS1 scenario plot:")
    print(scenario_plots$pfs1_pfs)
  }
  
  # Save all plots
  if (!dir.exists("scenario_plots")) {
    dir.create("scenario_plots")
  }
  
  for (plot_name in names(scenario_plots)) {
    ggsave(
      filename = paste0("scenario_plots/", plot_name, "_scenarios.png"),
      plot = scenario_plots[[plot_name]],
      width = 12, height = 6, dpi = 300
    )
  }
  
  cat("All scenario plots saved in 'scenario_plots' directory\n")
} else {
  cat("No plots were created. Check the error messages above.\n")
}

# Print summary
cat("\nScenario Analysis Summary:\n")
cat("- Models analyzed: 1 through 8 (OS and PFS)\n") 
cat("- Scenarios per model: 6 (crp 0/1, tlr 0/1, tmb_braf 0/1)\n")
cat("- Distribution used:", "weibull", "\n")
cat("- Total plots created:", length(scenario_plots), "\n")

# List which models were successful
if (length(scenario_plots) > 0) {
  successful_models <- unique(gsub("_(os|pfs)$", "", names(scenario_plots)))
  cat("- Successful models:", paste(successful_models, collapse = ", "), "\n")
}
```

#survival plots for all other models
```{r}

# Create individual OS plots
os1_plot <- plot_single_survival(os_results, "Overall Survival", "os1")
os2_plot <- plot_single_survival(os_results, "Overall Survival", "os2")
os3_plot <- plot_single_survival(os_results, "Overall Survival", "os3")
os4_plot <- plot_single_survival(os_results, "Overall Survival", "os4")
os5_plot <- plot_single_survival(os_results, "Overall Survival", "os5")
os6_plot <- plot_single_survival(os_results, "Overall Survival", "os6")
os7_plot <- plot_single_survival(os_results, "Overall Survival", "os7")
os8_plot <- plot_single_survival(os_results, "Overall Survival", "os8")

# Create individual PFS plots
pfs1_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs1")
pfs2_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs2")
pfs3_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs3")
pfs4_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs4")
pfs5_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs5")
pfs6_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs6")
pfs7_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs7")
pfs8_plot <- plot_single_survival(pfs_results, "Progression-Free Survival", "pfs8")

# Display plots one by one
print("OS Model 1 (crp:Rx):")
print(os1_plot)

print("OS Model 2 (tlr:Rx):")
print(os2_plot)

print("OS Model 3 (tmb_braf:Rx):")
print(os3_plot)

print("OS Model 4 (Age + sex + crp:Rx):")
print(os4_plot)

print("OS Model 5 (Age + sex + tlr:Rx):")
print(os5_plot)

print("OS Model 6 (Age + sex + tmb_braf:Rx):")
print(os6_plot)

print("OS Model 7 (crp:Rx + tlr:Rx + tmb_braf:Rx):")
print(os7_plot)

print("OS Model 8 (Age + sex + crp:Rx + tlr:Rx + tmb_braf:Rx):")
print(os8_plot)

print("PFS Model 1 (crp:Rx):")
print(pfs1_plot)

print("PFS Model 2 (tlr:Rx):")
print(pfs2_plot)

print("PFS Model 3 (tmb_braf:Rx):")
print(pfs3_plot)

print("PFS Model 4 (Age + sex + crp:Rx):")
print(pfs4_plot)

print("PFS Model 5 (Age + sex + tlr:Rx):")
print(pfs5_plot)

print("PFS Model 6 (Age + sex + tmb_braf:Rx):")
print(pfs6_plot)

print("PFS Model 7 (crp:Rx + tlr:Rx + tmb_braf:Rx):")
print(pfs7_plot)

print("PFS Model 8 (Age + sex + crp:Rx + tlr:Rx + tmb_braf:Rx):")
print(pfs8_plot)

```


#debug
```{r}
debug_results <- function(results, result_name) {
  cat("=== Debugging", result_name, "===\n")
  
  for (model_name in names(results)) {
    cat("\nModel:", model_name, "\n")
    fitted_models <- results[[model_name]]$fitted_models
    
    for (dist_name in names(fitted_models)) {
      fit_obj <- fitted_models[[dist_name]]
      if (inherits(fit_obj, "flexsurvreg")) {
        cat("  ✓", dist_name, "- Valid flexsurvreg object\n")
      } else if (is.character(fit_obj)) {
        cat("  ✗", dist_name, "- Error:", fit_obj, "\n")
      } else {
        cat("  ✗", dist_name, "- Invalid object type:", class(fit_obj), "\n")
      }
    }
  }
  cat("\n")
}

# Debug your results
debug_results(os_results, "OS Results")
debug_results(pfs_results, "PFS Results")
```

