---
title: "Age Effect Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%",
  fig.keep = "last"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, gems, mstate,
  tidyverse, xtable, darthtools, dampack,
  mvtnorm, Matrix, reshape2
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10)
  )
)
```

```{r load-analysis-scripts, include=FALSE}
# Load analysis results if not already in environment
if (!exists("data_complete")) {
  cat("Loading analysis scripts...\n")

  # Load required scripts in order
  if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
  }

  if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
  }

  if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
  }
}

# Create data_complete from full dataset
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr",
                                               "tmb_braf", "OSwk", "Death",
                                               "PFSwk", "Progression")]), ]

# Load prediction functions
source(here("scripts/R/functions/prediction_functions.R"))
```

# Introduction

This technical document investigates the impact of age heterogeneity on survival model predictions and cost-effectiveness results in the METIMMOX-1 economic evaluation. All survival models in this analysis include Age as a covariate, meaning patient-level age variation directly influences predicted outcomes.

**Analysis approach:**

1. **Base case**: Use actual patient ages from the dataset (standard analysis)
2. **Same-age scenario**: Replace all patient ages with the population mean age

By comparing these two approaches, we can quantify how much of the predicted survival differences across biomarker subgroups is attributable to age imbalances versus true biomarker-treatment effects.

**Important note**: The same-age dataset is created and used exclusively within this document to prevent contamination of other analyses in the codebase.

```{r create-same-age-dataset, include=FALSE}
# ===============================================================================
# CREATE SAME-AGE DATASET
# This dataset is used ONLY within this document
# ===============================================================================

# Calculate overall population mean age
mean_age <- mean(data_complete$Age, na.rm = TRUE)

# Create same-age dataset
data_same_age <- data_complete
data_same_age$Age <- mean_age

cat("Same-age dataset created with mean age:", round(mean_age, 1), "years\n")
```

\newpage

# Age Distribution in the Sample

This section presents the age distribution across the study population, stratified by treatment arm and biomarker status.

## Overall Age Statistics

```{r overall-age-table}
# Calculate overall age statistics
age_stats <- data.frame(
  Statistic = c("Mean", "SD", "Median", "Min", "Max", "N"),
  Value = c(
    round(mean(data_complete$Age, na.rm = TRUE), 1),
    round(sd(data_complete$Age, na.rm = TRUE), 1),
    round(median(data_complete$Age, na.rm = TRUE), 1),
    round(min(data_complete$Age, na.rm = TRUE), 0),
    round(max(data_complete$Age, na.rm = TRUE), 0),
    sum(!is.na(data_complete$Age))
  )
)

kable(age_stats,
      caption = "Overall age statistics in the study population.",
      booktabs = TRUE,
      align = c("l", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE)
```

The population mean age of **`r round(mean_age, 1)`** years is used for the same-age scenario throughout this analysis.

## Age by Treatment Arm

```{r age-by-treatment}
# Calculate age by treatment arm
age_by_rx <- data_complete %>%
  group_by(Rx) %>%
  summarise(
    N = n(),
    `Mean Age` = round(mean(Age, na.rm = TRUE), 1),
    SD = round(sd(Age, na.rm = TRUE), 1),
    .groups = "drop"
  ) %>%
  rename(`Treatment Arm` = Rx)

kable(age_by_rx,
      caption = "Age distribution by treatment arm.",
      booktabs = TRUE,
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE)
```

## Age by Biomarker Status

```{r age-by-biomarker}
# Calculate age by biomarker status for each biomarker
biomarker_age_stats <- data.frame()

for (biomarker in c("crp", "tlr", "tmb_braf")) {
  biomarker_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

  for (status in c(0, 1)) {
    subset_data <- data_complete[data_complete[[biomarker]] == status, ]
    status_label <- ifelse(status == 1, "Positive", "Negative")

    biomarker_age_stats <- rbind(biomarker_age_stats, data.frame(
      Biomarker = biomarker_labels[biomarker],
      Status = status_label,
      N = nrow(subset_data),
      `Mean Age` = round(mean(subset_data$Age, na.rm = TRUE), 1),
      SD = round(sd(subset_data$Age, na.rm = TRUE), 1),
      check.names = FALSE
    ))
  }
}

kable(biomarker_age_stats,
      caption = "Age distribution by biomarker status. Mean Age values are highlighted as they represent the key variable of interest in this analysis.",
      booktabs = TRUE,
      align = c("l", "l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE) %>%
  column_spec(4, bold = TRUE, background = "#E8F4F8") %>%
  collapse_rows(columns = 1, valign = "middle")
```

\newpage

```{r model-setup, include=FALSE}
# ===============================================================================
# MODEL STRUCTURE SETUP - Gamma distribution only
# ===============================================================================

# Define model formulas for all 7 model types
model_formulas <- list(
  # Model A: Joint (All-in-One) - all biomarkers + all interactions
  A = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp:Rx + tlr:Rx + tmb_braf:Rx
  ),

  # Model B: Focused - CRP and TMB/BRAF only + BOTH interactions (TLR excluded)
  # NOTE: Both B_crp and B_tmb use the SAME shared formula
  B_crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
  ),
  # B_tlr removed - Model B excludes TLR
  B_tmb = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
  ),

  # Model C: Single-biomarker (Separate) - ONE biomarker only + its interaction
  C_crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp:Rx
  ),
  C_tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + tlr:Rx
  ),
  C_tmb = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + tmb_braf:Rx
  )
)

# Model labels
# NOTE: B_tlr removed - Model B excludes TLR
model_labels_short <- c(
  "A" = "Model A",
  "B_crp" = "Model B",
  "B_tmb" = "Model B",
  "C_crp" = "Model C",
  "C_tlr" = "Model C",
  "C_tmb" = "Model C"
)

# Color scheme for subgroups
subgroup_colors <- c(
  "Biomarker+" = "#E31A1C",   # Red
  "Biomarker-" = "#1F78B4",   # Blue
  "Strategy" = "#33A02C",      # Green
  "Control" = "gray50"
)

# Linetype scheme for base vs same-age
age_linetypes <- c(
  "Base Case" = "solid",
  "Same-Age" = "dashed"
)

# Vector of model types to fit
# NOTE: B_tlr removed - Model B excludes TLR
model_types <- c("A", "B_crp", "B_tmb", "C_crp", "C_tlr", "C_tmb")

# Biomarker-model mapping
# NOTE: B_tlr removed - Model B excludes TLR
model_biomarker_map <- list(
  A = c("crp", "tlr", "tmb_braf"),
  B_crp = c("crp"),
  # B_tlr removed - Model B excludes TLR
  B_tmb = c("tmb_braf"),
  C_crp = c("crp"),
  C_tlr = c("tlr"),
  C_tmb = c("tmb_braf")
)
```

```{r fit-models, include=FALSE}
# ===============================================================================
# FIT GAMMA MODELS - Both base case and same-age datasets
# ===============================================================================

cat("Fitting models for base case and same-age datasets...\n")

# Function to fit all models on a given dataset
fit_all_models <- function(dataset, dataset_name) {
  models_list <- list(gamma = list())

  for (model_type in model_types) {
    cat("Fitting model:", model_type, "on", dataset_name, "\n")

    # Fit OS model
    os_fit <- tryCatch({
      flexsurvreg(
        formula = model_formulas[[model_type]]$os,
        data = dataset,
        dist = "gamma"
      )
    }, error = function(e) {
      warning(paste("Failed to fit", model_type, "OS:", e$message))
      return(NULL)
    })

    # Fit PFS model
    pfs_fit <- tryCatch({
      flexsurvreg(
        formula = model_formulas[[model_type]]$pfs,
        data = dataset,
        dist = "gamma"
      )
    }, error = function(e) {
      warning(paste("Failed to fit", model_type, "PFS:", e$message))
      return(NULL)
    })

    # Store models
    models_list$gamma[[model_type]] <- list(
      os = os_fit,
      pfs = pfs_fit
    )
  }

  return(models_list)
}

# Fit models on base case data
multi_models_base <- fit_all_models(data_complete, "base case")

# Fit models on same-age data
multi_models_same_age <- fit_all_models(data_same_age, "same-age")

cat("Model fitting complete.\n")

# Clean up memory
gc(verbose = FALSE)
```

```{r generate-predictions, include=FALSE}
# ===============================================================================
# GENERATE PREDICTIONS FOR BOTH DATASETS
# ===============================================================================

cat("Generating predictions...\n")

# Helper function for population-averaged predictions
predict_population_avg <- function(model, newdata, time_points) {
  tryCatch({
    pred <- predict(model, newdata = newdata, type = "survival", times = time_points)
    if (".pred" %in% names(pred)) {
      surv_probs <- lapply(pred$.pred, function(x) x$.pred_survival)
      surv_matrix <- do.call(cbind, surv_probs)
      return(rowMeans(surv_matrix, na.rm = TRUE))
    } else if (is.list(pred) && length(pred) > 0 && is.data.frame(pred[[1]])) {
      surv_probs <- sapply(pred, function(x) x$est)
      if (is.matrix(surv_probs)) {
        return(rowMeans(surv_probs, na.rm = TRUE))
      } else {
        return(surv_probs)
      }
    } else {
      return(NULL)
    }
  }, error = function(e) {
    return(NULL)
  })
}

# Function to generate predictions for a dataset
generate_all_predictions <- function(models_list, dataset, dataset_name) {
  # Get treatment level references
  exp_rx <- levels(dataset$Rx)[2]
  ctrl_rx <- levels(dataset$Rx)[1]

  predictions_list <- list(gamma = list())

  for (model_type in model_types) {
    os_model <- models_list$gamma[[model_type]]$os
    pfs_model <- models_list$gamma[[model_type]]$pfs

    if (is.null(os_model) || is.null(pfs_model)) next

    predictions_list$gamma[[model_type]] <- list()

    # Control predictions
    control_data <- dataset
    control_data$Rx <- factor(ctrl_rx, levels = levels(dataset$Rx))

    control_os <- predict_population_avg(os_model, control_data, time_points)
    control_pfs <- predict_population_avg(pfs_model, control_data, time_points)

    if (!is.null(control_os) && !is.null(control_pfs)) {
      predictions_list$gamma[[model_type]]$control <- list(os = control_os, pfs = control_pfs)
    }

    # Biomarker-specific predictions
    biomarkers_to_predict <- model_biomarker_map[[model_type]]

    for (biomarker in biomarkers_to_predict) {
      # Biomarker-positive: experimental treatment
      pos_data <- dataset[as.numeric(as.character(dataset[[biomarker]])) == 1, ]
      if (nrow(pos_data) > 0) {
        pos_data$Rx <- factor(exp_rx, levels = levels(dataset$Rx))
        pos_os <- predict_population_avg(os_model, pos_data, time_points)
        pos_pfs <- predict_population_avg(pfs_model, pos_data, time_points)

        if (!is.null(pos_os) && !is.null(pos_pfs)) {
          predictions_list$gamma[[model_type]][[paste0(biomarker, "_pos")]] <- list(os = pos_os, pfs = pos_pfs)
        }
      }

      # Biomarker-negative: control treatment
      neg_data <- dataset[as.numeric(as.character(dataset[[biomarker]])) == 0, ]
      if (nrow(neg_data) > 0) {
        neg_data$Rx <- factor(ctrl_rx, levels = levels(dataset$Rx))
        neg_os <- predict_population_avg(os_model, neg_data, time_points)
        neg_pfs <- predict_population_avg(pfs_model, neg_data, time_points)

        if (!is.null(neg_os) && !is.null(neg_pfs)) {
          predictions_list$gamma[[model_type]][[paste0(biomarker, "_neg")]] <- list(os = neg_os, pfs = neg_pfs)
        }
      }

      # Population-weighted prediction
      biomarker_prev <- strategies_df$prevalence[strategies_df$id == biomarker]
      pos_pred <- predictions_list$gamma[[model_type]][[paste0(biomarker, "_pos")]]
      neg_pred <- predictions_list$gamma[[model_type]][[paste0(biomarker, "_neg")]]

      if (length(biomarker_prev) > 0 && !is.null(pos_pred) && !is.null(neg_pred)) {
        predictions_list$gamma[[model_type]][[paste0(biomarker, "_weighted")]] <- list(
          os = biomarker_prev * pos_pred$os + (1 - biomarker_prev) * neg_pred$os,
          pfs = biomarker_prev * pos_pred$pfs + (1 - biomarker_prev) * neg_pred$pfs
        )
      }
    }
  }

  return(predictions_list)
}

# Generate predictions for both datasets
multi_predictions_base <- generate_all_predictions(multi_models_base, data_complete, "base case")
multi_predictions_same_age <- generate_all_predictions(multi_models_same_age, data_same_age, "same-age")

cat("Predictions generated successfully.\n")
```

```{r helper-functions, include=FALSE}
# ===============================================================================
# HELPER FUNCTIONS
# ===============================================================================

# Calculate life-years from survival curve
calculate_ly <- function(survival_curve, cl = 1/52) {
  sum(survival_curve * cl, na.rm = TRUE)
}

# Create baseline characteristics table for a biomarker (with age bolded)
# Stratified by both biomarker status AND treatment arm
create_baseline_table <- function(biomarker) {
  biomarker_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

  # Get treatment arm levels
  ctrl_rx <- levels(data_complete$Rx)[1]
  exp_rx <- levels(data_complete$Rx)[2]

  # Split data by biomarker status AND treatment arm (4 groups)
  neg_ctrl <- data_complete[data_complete[[biomarker]] == 0 & data_complete$Rx == ctrl_rx, ]
  neg_exp <- data_complete[data_complete[[biomarker]] == 0 & data_complete$Rx == exp_rx, ]
  pos_ctrl <- data_complete[data_complete[[biomarker]] == 1 & data_complete$Rx == ctrl_rx, ]
  pos_exp <- data_complete[data_complete[[biomarker]] == 1 & data_complete$Rx == exp_rx, ]

  # Helper function to calculate stats for a subgroup
  calc_stats <- function(subdata) {
    n <- nrow(subdata)
    if (n == 0) return(list(n = 0, age = "-", sex = "-"))

    age <- paste0(round(mean(subdata$Age, na.rm = TRUE), 1), " (",
                  round(sd(subdata$Age, na.rm = TRUE), 1), ")")

    male_n <- sum(subdata$sex == "male" | subdata$sex == 1, na.rm = TRUE)
    sex <- paste0(male_n, " (", round(100 * male_n / n, 1), "%)")

    return(list(n = n, age = age, sex = sex))
  }

  # Calculate statistics for all 4 groups
  stats_neg_ctrl <- calc_stats(neg_ctrl)
  stats_neg_exp <- calc_stats(neg_exp)
  stats_pos_ctrl <- calc_stats(pos_ctrl)
  stats_pos_exp <- calc_stats(pos_exp)

  # Create table with 4 columns (2x2: biomarker status x treatment arm)
  baseline_df <- data.frame(
    Variable = c("N", "Age, mean (SD)", "Sex, n (%) Male"),
    `Biomarker- Control` = c(stats_neg_ctrl$n, stats_neg_ctrl$age, stats_neg_ctrl$sex),
    `Biomarker- Experimental` = c(stats_neg_exp$n, stats_neg_exp$age, stats_neg_exp$sex),
    `Biomarker+ Control` = c(stats_pos_ctrl$n, stats_pos_ctrl$age, stats_pos_ctrl$sex),
    `Biomarker+ Experimental` = c(stats_pos_exp$n, stats_pos_exp$age, stats_pos_exp$sex),
    check.names = FALSE
  )

  return(baseline_df)
}

# Create life-years comparison table
create_ly_comparison_table <- function(biomarker, outcome = "os") {
  # NOTE: Model B excludes TLR - only Model A and Model C include TLR
  model_map <- list(
    crp = c("A", "B_crp", "C_crp"),
    tlr = c("A", "C_tlr"),
    tmb_braf = c("A", "B_tmb", "C_tmb")
  )

  relevant_models <- model_map[[biomarker]]
  table_data <- data.frame()

  for (model_type in relevant_models) {
    pred_base <- multi_predictions_base$gamma[[model_type]]
    pred_same <- multi_predictions_same_age$gamma[[model_type]]

    if (is.null(pred_base) || is.null(pred_same)) next

    model_letter <- substr(model_type, 1, 1)

    # Control life-years
    ctrl_base <- if (!is.null(pred_base$control[[outcome]])) calculate_ly(pred_base$control[[outcome]]) else NA
    ctrl_same <- if (!is.null(pred_same$control[[outcome]])) calculate_ly(pred_same$control[[outcome]]) else NA
    ctrl_delta <- ctrl_same - ctrl_base

    # Strategy (weighted) life-years
    strat_base <- if (!is.null(pred_base[[paste0(biomarker, "_weighted")]][[outcome]]))
                    calculate_ly(pred_base[[paste0(biomarker, "_weighted")]][[outcome]]) else NA
    strat_same <- if (!is.null(pred_same[[paste0(biomarker, "_weighted")]][[outcome]]))
                    calculate_ly(pred_same[[paste0(biomarker, "_weighted")]][[outcome]]) else NA
    strat_delta <- strat_same - strat_base

    table_data <- rbind(table_data, data.frame(
      Model = paste0("Model ", model_letter),
      `Ctrl Base` = ctrl_base,
      `Ctrl Same-Age` = ctrl_same,
      `Ctrl Delta` = ctrl_delta,
      `Strat Base` = strat_base,
      `Strat Same-Age` = strat_same,
      `Strat Delta` = strat_delta,
      check.names = FALSE
    ))
  }

  return(table_data)
}

# Create comparison survival plot (3-panel, faceted by model)
create_comparison_plot <- function(biomarker, outcome = "os") {
  # NOTE: Model B excludes TLR - only Model A and Model C include TLR
  model_map <- list(
    crp = c("A", "B_crp", "C_crp"),
    tlr = c("A", "C_tlr"),
    tmb_braf = c("A", "B_tmb", "C_tmb")
  )

  biomarker_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")
  relevant_models <- model_map[[biomarker]]

  plot_data <- data.frame()

  for (model_type in relevant_models) {
    pred_base <- multi_predictions_base$gamma[[model_type]]
    pred_same <- multi_predictions_same_age$gamma[[model_type]]

    if (is.null(pred_base) || is.null(pred_same)) next

    model_letter <- substr(model_type, 1, 1)
    model_label <- paste0("Model ", model_letter)

    # Add curves for each dataset type
    for (dataset_type in c("Base Case", "Same-Age")) {
      pred <- if (dataset_type == "Base Case") pred_base else pred_same

      # Control
      if (!is.null(pred$control[[outcome]])) {
        plot_data <- rbind(plot_data, data.frame(
          time = time_points,
          survival = pred$control[[outcome]],
          subgroup = "Control",
          model = model_label,
          dataset = dataset_type
        ))
      }

      # Biomarker positive
      pos_key <- paste0(biomarker, "_pos")
      if (!is.null(pred[[pos_key]][[outcome]])) {
        plot_data <- rbind(plot_data, data.frame(
          time = time_points,
          survival = pred[[pos_key]][[outcome]],
          subgroup = "Biomarker+",
          model = model_label,
          dataset = dataset_type
        ))
      }

      # Biomarker negative
      neg_key <- paste0(biomarker, "_neg")
      if (!is.null(pred[[neg_key]][[outcome]])) {
        plot_data <- rbind(plot_data, data.frame(
          time = time_points,
          survival = pred[[neg_key]][[outcome]],
          subgroup = "Biomarker-",
          model = model_label,
          dataset = dataset_type
        ))
      }

      # Weighted strategy
      weighted_key <- paste0(biomarker, "_weighted")
      if (!is.null(pred[[weighted_key]][[outcome]])) {
        plot_data <- rbind(plot_data, data.frame(
          time = time_points,
          survival = pred[[weighted_key]][[outcome]],
          subgroup = "Strategy",
          model = model_label,
          dataset = dataset_type
        ))
      }
    }
  }

  if (nrow(plot_data) == 0) return(NULL)

  # Set factor levels
  plot_data$subgroup <- factor(plot_data$subgroup,
                                levels = c("Biomarker+", "Biomarker-", "Strategy", "Control"))
  plot_data$model <- factor(plot_data$model, levels = c("Model A", "Model B", "Model C"))
  plot_data$dataset <- factor(plot_data$dataset, levels = c("Base Case", "Same-Age"))

  outcome_label <- ifelse(outcome == "os", "Overall Survival", "Progression-Free Survival")
  bio_label <- biomarker_labels[biomarker]

  p <- ggplot(plot_data, aes(x = time, y = survival, color = subgroup, linetype = dataset)) +
    geom_line(linewidth = 0.8) +
    facet_wrap(~ model, nrow = 1) +
    scale_color_manual(values = subgroup_colors, name = "Group") +
    scale_linetype_manual(values = age_linetypes, name = "Dataset") +
    scale_y_continuous(limits = c(0, 1), labels = scales::percent) +
    scale_x_continuous(breaks = seq(0, max(time_points), by = 104)) +
    labs(x = "Time (weeks)", y = "Survival Probability",
         title = paste0(bio_label, " Strategy: ", outcome_label),
         subtitle = "Base case (solid) vs. same-age scenario (dashed)") +
    theme(legend.position = "bottom",
          strip.text = element_text(size = 10, face = "bold")) +
    guides(color = guide_legend(nrow = 1), linetype = guide_legend(nrow = 1))

  return(p)
}
```

# CRP Biomarker Strategy

C-reactive protein (CRP) with a cutoff of <5 g/L for biomarker-positive status. **Biomarker prevalence: `r round(100 * p_crp, 1)`%**.

## Baseline Characteristics

```{r crp-baseline-table}
baseline_crp <- create_baseline_table("crp")

kable(baseline_crp,
      caption = "CRP strategy: Baseline characteristics by biomarker status and treatment arm.",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE) %>%
  row_spec(2, bold = TRUE, background = "#E8F4F8") %>%
  add_header_above(c(" " = 1, "Biomarker-" = 2, "Biomarker+" = 2))
```

## Life-Years Comparison

```{r crp-os-ly-table}
ly_table <- create_ly_comparison_table("crp", "os")
kable(ly_table,
      caption = "CRP strategy: Overall survival life-years. Base case uses actual ages; Same-Age uses population mean age for all patients.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

```{r crp-pfs-ly-table}
ly_table <- create_ly_comparison_table("crp", "pfs")
kable(ly_table,
      caption = "CRP strategy: Progression-free survival life-years. Base case uses actual ages; Same-Age uses population mean age for all patients.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

## Overall Survival Curves

```{r crp-os-plot, fig.height=5, fig.width=12}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%) overall survival comparison. Solid lines = base case (actual ages), dashed lines = same-age scenario (all patients at mean age ", round(mean_age, 1), " years).")'

p <- create_comparison_plot("crp", "os")
if (!is.null(p)) print(p)
```

## Progression-Free Survival Curves

```{r crp-pfs-plot, fig.height=5, fig.width=12}
#| fig-cap: !expr 'paste0("CRP strategy (prevalence: ", round(100 * p_crp, 1), "%) progression-free survival comparison. Solid lines = base case (actual ages), dashed lines = same-age scenario (all patients at mean age ", round(mean_age, 1), " years).")'

p <- create_comparison_plot("crp", "pfs")
if (!is.null(p)) print(p)
```

\newpage

# TLR Biomarker Strategy

Tumor lesion reduction (TLR) with a cutoff of >=10% for biomarker-positive status. **Biomarker prevalence: `r round(100 * p_tlr, 1)`%**.

## Baseline Characteristics

```{r tlr-baseline-table}
baseline_tlr <- create_baseline_table("tlr")

kable(baseline_tlr,
      caption = "TLR strategy: Baseline characteristics by biomarker status and treatment arm.",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE) %>%
  row_spec(2, bold = TRUE, background = "#E8F4F8") %>%
  add_header_above(c(" " = 1, "Biomarker-" = 2, "Biomarker+" = 2))
```

## Life-Years Comparison

```{r tlr-os-ly-table}
ly_table <- create_ly_comparison_table("tlr", "os")
kable(ly_table,
      caption = "TLR strategy: Overall survival life-years. Base case uses actual ages; Same-Age uses population mean age for all patients.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

```{r tlr-pfs-ly-table}
ly_table <- create_ly_comparison_table("tlr", "pfs")
kable(ly_table,
      caption = "TLR strategy: Progression-free survival life-years. Base case uses actual ages; Same-Age uses population mean age for all patients.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

## Overall Survival Curves

```{r tlr-os-plot, fig.height=5, fig.width=12}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%) overall survival comparison. Solid lines = base case (actual ages), dashed lines = same-age scenario (all patients at mean age ", round(mean_age, 1), " years).")'

p <- create_comparison_plot("tlr", "os")
if (!is.null(p)) print(p)
```

## Progression-Free Survival Curves

```{r tlr-pfs-plot, fig.height=5, fig.width=12}
#| fig-cap: !expr 'paste0("TLR strategy (prevalence: ", round(100 * p_tlr, 1), "%) progression-free survival comparison. Solid lines = base case (actual ages), dashed lines = same-age scenario (all patients at mean age ", round(mean_age, 1), " years).")'

p <- create_comparison_plot("tlr", "pfs")
if (!is.null(p)) print(p)
```

\newpage

# TMB/BRAF Biomarker Strategy

Combined genomic biomarker: either tumor mutational burden (TMB) >= 9 mutations/MB or BRAF V600 mutation positive. **Biomarker prevalence: `r round(100 * p_tmb_braf, 1)`%**.

## Baseline Characteristics

```{r tmb-baseline-table}
baseline_tmb <- create_baseline_table("tmb_braf")

kable(baseline_tmb,
      caption = "TMB/BRAF strategy: Baseline characteristics by biomarker status and treatment arm.",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE) %>%
  row_spec(2, bold = TRUE, background = "#E8F4F8") %>%
  add_header_above(c(" " = 1, "Biomarker-" = 2, "Biomarker+" = 2))
```

## Life-Years Comparison

```{r tmb-os-ly-table}
ly_table <- create_ly_comparison_table("tmb_braf", "os")
kable(ly_table,
      caption = "TMB/BRAF strategy: Overall survival life-years. Base case uses actual ages; Same-Age uses population mean age for all patients.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

```{r tmb-pfs-ly-table}
ly_table <- create_ly_comparison_table("tmb_braf", "pfs")
kable(ly_table,
      caption = "TMB/BRAF strategy: Progression-free survival life-years. Base case uses actual ages; Same-Age uses population mean age for all patients.",
      booktabs = TRUE,
      digits = 2,
      align = c("l", rep("r", 6))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                full_width = FALSE)
```

## Overall Survival Curves

```{r tmb-os-plot, fig.height=5, fig.width=12}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%) overall survival comparison. Solid lines = base case (actual ages), dashed lines = same-age scenario (all patients at mean age ", round(mean_age, 1), " years).")'

p <- create_comparison_plot("tmb_braf", "os")
if (!is.null(p)) print(p)
```

## Progression-Free Survival Curves

```{r tmb-pfs-plot, fig.height=5, fig.width=12}
#| fig-cap: !expr 'paste0("TMB/BRAF strategy (prevalence: ", round(100 * p_tmb_braf, 1), "%) progression-free survival comparison. Solid lines = base case (actual ages), dashed lines = same-age scenario (all patients at mean age ", round(mean_age, 1), " years).")'

p <- create_comparison_plot("tmb_braf", "pfs")
if (!is.null(p)) print(p)
```

\newpage

# Cost-Effectiveness Impact

This section compares cost-effectiveness results between the base case (actual patient ages) and the same-age scenario (all patients at population mean age). Results use Model A (joint model with all biomarker interactions) for consistency with the primary analysis.

```{r cea-calculations, include=FALSE}
# ===============================================================================
# COST-EFFECTIVENESS CALCULATIONS
# Uses simplified approach based on survival curves and base parameters
# ===============================================================================

# Load base parameters if not available
if (!exists("l_params_base")) {
  suppressMessages(suppressWarnings(source(here("scripts/R/analysis/07_basecase_input_parameters.R"))))
}

# Discount factors
v_dw_c <- 1 / (1 + dr)^(seq(0, time_horizon) / 52)
v_dw_e <- 1 / (1 + dr)^(seq(0, time_horizon) / 52)

# Function to calculate costs and QALYs from survival curves
calculate_cea <- function(p_os, p_pfs, treatment_type, biomarker, params) {
  n_cycles <- length(p_os)

  # State occupancy
  p_pf <- p_pfs
  p_p <- pmax(p_os - p_pfs, 0)
  p_d <- 1 - p_os

  # Extend treatment schedules
  extend_schedule <- function(schedule, length_needed) {
    if (length(schedule) < length_needed) {
      return(c(schedule, rep(0, length_needed - length(schedule))))
    }
    return(schedule[1:length_needed])
  }

  l_nivo <- extend_schedule(params$l_nivo, n_cycles)
  l_FLOX_exp <- extend_schedule(params$l_FLOX_exp, n_cycles)
  l_FLOX_control <- extend_schedule(params$l_FLOX_control, n_cycles)
  l_CT <- extend_schedule(params$l_CT, n_cycles)
  l_blood <- extend_schedule(params$l_blood, n_cycles)
  l_visit <- extend_schedule(params$l_visit, n_cycles)

  # QALYs
  qalys_pf <- p_pf * params$u_np * cl
  qalys_p <- p_p * params$u_p * cl
  qalys_undiscounted <- qalys_pf + qalys_p
  qalys_discounted <- qalys_undiscounted * v_dw_e[1:n_cycles]
  qalys_total <- sum(qalys_discounted)

  # Drug costs
  if (treatment_type == "experimental") {
    drug_costs <- (l_nivo * params$c_drug_nivo + l_FLOX_exp * params$c_drug_FLOX) * p_pf
  } else {
    drug_costs <- l_FLOX_control * params$c_drug_FLOX * p_pf
  }

  # Test costs
  test_costs <- l_CT * params$c_test_CT * p_pf + l_blood * params$c_test_blood * p_pf

  # Add biomarker test cost
  if (!is.null(biomarker)) {
    if (biomarker == "tmb_braf") {
      test_costs[1] <- test_costs[1] + params$c_test_NGS
    } else if (biomarker == "crp") {
      test_costs[1] <- test_costs[1] + params$c_test_blood
    } else if (biomarker == "tlr") {
      test_costs[1] <- test_costs[1] + params$c_test_CT
    }
  }

  # Visit costs
  visit_costs <- l_visit * params$c_other_visit * p_pf
  visit_costs[1] <- visit_costs[1] + params$c_other_baseline

  # Follow-up costs
  quarterly_cycles <- seq(13, n_cycles, by = 13)
  follow_up_costs <- rep(0, n_cycles)
  if (length(quarterly_cycles) > 0) {
    follow_up_costs[quarterly_cycles] <- params$c_other_follow * p_p[quarterly_cycles]
  }

  # End-of-life costs
  death_transitions <- c(0, diff(p_d))
  death_transitions <- pmax(death_transitions, 0)
  end_life_costs <- death_transitions * params$c_other_last

  # Total costs
  total_costs_undiscounted <- drug_costs + test_costs + visit_costs + follow_up_costs + end_life_costs
  total_costs_discounted <- total_costs_undiscounted * v_dw_c[1:n_cycles]
  costs_total <- sum(total_costs_discounted)

  return(list(qalys = qalys_total, costs = costs_total))
}

# Function to calculate strategy costs (weighted by prevalence)
calculate_strategy_cea <- function(predictions, biomarker, params) {
  prevalence <- params[[paste0("p_", biomarker)]]

  # Get curves
  pos_os <- predictions$gamma$A[[paste0(biomarker, "_pos")]]$os
  pos_pfs <- predictions$gamma$A[[paste0(biomarker, "_pos")]]$pfs
  neg_os <- predictions$gamma$A[[paste0(biomarker, "_neg")]]$os
  neg_pfs <- predictions$gamma$A[[paste0(biomarker, "_neg")]]$pfs

  # Calculate for positive (experimental) and negative (control)
  pos_cea <- calculate_cea(pos_os, pos_pfs, "experimental", biomarker, params)
  neg_cea <- calculate_cea(neg_os, neg_pfs, "control", NULL, params)

  # Weighted average
  qalys <- prevalence * pos_cea$qalys + (1 - prevalence) * neg_cea$qalys
  costs <- prevalence * pos_cea$costs + (1 - prevalence) * neg_cea$costs

  return(list(qalys = qalys, costs = costs))
}

# Calculate CEA results for both datasets
cea_results <- data.frame()

for (biomarker in c("control", "crp", "tlr", "tmb_braf")) {
  biomarker_labels <- c(control = "Control", crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

  for (dataset_type in c("Base Case", "Same-Age")) {
    predictions <- if (dataset_type == "Base Case") multi_predictions_base else multi_predictions_same_age

    if (biomarker == "control") {
      ctrl_os <- predictions$gamma$A$control$os
      ctrl_pfs <- predictions$gamma$A$control$pfs
      cea <- calculate_cea(ctrl_os, ctrl_pfs, "control", NULL, l_params_base)
    } else {
      cea <- calculate_strategy_cea(predictions, biomarker, l_params_base)
    }

    cea_results <- rbind(cea_results, data.frame(
      Strategy = biomarker_labels[biomarker],
      Dataset = dataset_type,
      QALYs = cea$qalys,
      Costs = cea$costs
    ))
  }
}

# Reshape for comparison tables
cea_wide <- cea_results %>%
  pivot_wider(names_from = Dataset, values_from = c(QALYs, Costs))

cea_wide$`Delta QALYs` <- cea_wide$`QALYs_Same-Age` - cea_wide$`QALYs_Base Case`
cea_wide$`Delta Costs` <- cea_wide$`Costs_Same-Age` - cea_wide$`Costs_Base Case`
```

## QALYs Comparison

```{r qalys-table}
qalys_table <- cea_wide %>%
  select(Strategy, `QALYs_Base Case`, `QALYs_Same-Age`, `Delta QALYs`) %>%
  rename(`Base Case` = `QALYs_Base Case`,
         `Same-Age` = `QALYs_Same-Age`,
         Delta = `Delta QALYs`)

kable(qalys_table,
      caption = "QALYs comparison between base case and same-age scenario (Model A).",
      booktabs = TRUE,
      digits = 3,
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE)
```

## Costs Comparison

```{r costs-table}
costs_table <- cea_wide %>%
  select(Strategy, `Costs_Base Case`, `Costs_Same-Age`, `Delta Costs`) %>%
  rename(`Base Case` = `Costs_Base Case`,
         `Same-Age` = `Costs_Same-Age`,
         Delta = `Delta Costs`) %>%
  mutate(across(where(is.numeric), ~ scales::comma(round(., 0))))

kable(costs_table,
      caption = "Costs comparison (EUR) between base case and same-age scenario (Model A).",
      booktabs = TRUE,
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE)
```

## ICERs Comparison

**Note:** Negative ICERs may occur when a strategy is dominated (higher costs and lower QALYs) or dominates (lower costs and higher QALYs). While negative ICERs are not conceptually meaningful for decision-making, they are presented here for numerical comparison between the base case and same-age scenarios.

```{r icer-table}
# Calculate ICERs vs control
control_base <- cea_results %>% filter(Strategy == "Control", Dataset == "Base Case")
control_same <- cea_results %>% filter(Strategy == "Control", Dataset == "Same-Age")

icer_results <- data.frame()

for (strat in c("CRP", "TLR", "TMB/BRAF")) {
  strat_base <- cea_results %>% filter(Strategy == strat, Dataset == "Base Case")
  strat_same <- cea_results %>% filter(Strategy == strat, Dataset == "Same-Age")

  icer_base <- (strat_base$Costs - control_base$Costs) / (strat_base$QALYs - control_base$QALYs)
  icer_same <- (strat_same$Costs - control_same$Costs) / (strat_same$QALYs - control_same$QALYs)

  icer_results <- rbind(icer_results, data.frame(
    Strategy = paste0(strat, " vs Control"),
    `ICER Base Case` = icer_base,
    `ICER Same-Age` = icer_same,
    `Delta ICER` = icer_same - icer_base,
    check.names = FALSE
  ))
}

# Format ICERs
icer_formatted <- icer_results %>%
  mutate(across(where(is.numeric), ~ scales::comma(round(., 0))))

kable(icer_formatted,
      caption = "ICER comparison (EUR/QALY) between base case and same-age scenario (Model A).",
      booktabs = TRUE,
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = FALSE)
```

\newpage

# Summary

This analysis examined the impact of age heterogeneity on survival predictions and cost-effectiveness results by comparing the base case (actual patient ages) with a same-age scenario where all patients were assigned the population mean age of **`r round(mean_age, 1)`** years.

## Key Findings

```{r summary-findings, include=FALSE}
# Calculate summary statistics for key findings
max_age_diff <- max(abs(biomarker_age_stats$`Mean Age` - mean_age))
max_ly_delta <- max(abs(c(
  create_ly_comparison_table("crp", "os")$`Strat Delta`,
  create_ly_comparison_table("tlr", "os")$`Strat Delta`,
  create_ly_comparison_table("tmb_braf", "os")$`Strat Delta`
)), na.rm = TRUE)
```

1. **Age imbalances across biomarker subgroups**: The mean age varied by up to `r round(max_age_diff, 1)` years from the population mean across biomarker subgroups.

2. **Impact on survival predictions**: Standardizing age affected OS life-year predictions by up to `r round(max_ly_delta, 2)` years, indicating the magnitude of age-related confounding.

3. **Cost-effectiveness implications**: The same-age scenario shows how age differences between biomarker subgroups can influence ICER estimates independently of biomarker-treatment effects.

## Interpretation

When biomarker-positive and biomarker-negative subgroups have different age distributions, the observed survival differences may partially reflect age effects rather than pure biomarker-treatment interactions. This analysis helps isolate the contribution of age heterogeneity to the overall results.

**Limitations**: This is a sensitivity analysis that removes natural age variation. The base case analysis using actual patient ages remains the primary analysis for decision-making.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0
