---
title: "All Parametric Survival Models"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "center",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  devtools, readxl, tableone, flexsurv,
  survival, survminer, tidyverse
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    legend.position = "bottom",
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10)
  ))
```

```{r load-analysis, include=FALSE}
# Load analysis results if not already in environment
if (!exists("models")) {
  cat("Loading parametric survival analysis results...\n")

  # Load required scripts in order
  if (file.exists(here("scripts/R/analysis/02_setup_and_global_variables.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/02_setup_and_global_variables.R"))))
  }

  if (file.exists(here("scripts/R/analysis/03_biomarker_strategies.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/03_biomarker_strategies.R"))))
  }

  if (file.exists(here("scripts/R/analysis/06_parametric_survival_analysis.R"))) {
    suppressMessages(suppressWarnings(source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))))
  }
}

# Define helper function to extract coefficients from a flexsurvreg model
extract_coefficients <- function(model_obj, dist_name) {
  if (!inherits(model_obj, "flexsurvreg")) {
    return(NULL)
  }

  coef_data <- as.data.frame(model_obj$res.t)

  coef_table <- data.frame(
    Parameter = rownames(coef_data),
    Estimate = round(coef_data$est, 4),
    SE = round(coef_data$se, 4),
    `exp(Est)` = round(exp(coef_data$est), 4),
    stringsAsFactors = FALSE,
    check.names = FALSE
  )

  # Clean up parameter names
  coef_table$Parameter <- gsub("^Age$", "Age (per year)", coef_table$Parameter)
  coef_table$Parameter <- gsub("^sex1$", "Sex (male vs female)", coef_table$Parameter)

  rownames(coef_table) <- NULL
  return(coef_table)
}

# Define distribution display names
dist_display_names <- c(
  "exponential" = "Exponential",
  "weibull" = "Weibull (AFT)",
  "weibullph" = "Weibull (PH)",
  "llogis" = "Log-logistic",
  "lognormal" = "Log-normal",
  "gamma" = "Gamma",
  "gompertz" = "Gompertz",
  "gengamma" = "Generalized Gamma",
  "genf" = "Generalized F"
)
```

# Overview

This technical document presents the regression coefficients for **all parametric survival models** fitted in the METIMMOX-1 economic evaluation. While the primary analysis uses the best-fitting model (selected by AIC), this document provides full transparency by showing coefficients for all distributions tested.

## Model Specification

All models use the following covariate structure (full model with age and sex adjustment):

**Overall Survival (OS):**
```
Surv(OSwk, Death) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx
```

**Progression-Free Survival (PFS):**
```
Surv(PFSwk, Progression) ~ Age + sex + Rx + crp*Rx + tlr*Rx + tmb_braf*Rx
```

## Distributions Tested

Nine parametric distributions were fitted to each outcome:

1. **Exponential** - Constant hazard rate
2. **Weibull (AFT)** - Accelerated failure time parameterization
3. **Weibull (PH)** - Proportional hazards parameterization
4. **Log-logistic** - Allows for non-monotonic hazard
5. **Log-normal** - Log-transformed normal distribution for survival times
6. **Gamma** - Two-parameter distribution, flexible shape
7. **Gompertz** - Hazard increases exponentially with time
8. **Generalized Gamma** - Three-parameter family including Weibull, gamma, and log-normal as special cases
9. **Generalized F** - Four-parameter family, most flexible

\newpage

# Model Selection Summary

## Overall Survival (OS) Models

```{r os-aic-table}
#| tbl-cap: "Overall Survival model fit comparison (sorted by AIC)"

if (exists("models") && !is.null(models$full$os_ic)) {

  os_ic <- models$full$os_ic %>%
    arrange(AIC) %>%
    mutate(
      AIC = round(AIC, 2),
      BIC = round(BIC, 2),
      `Delta AIC` = round(AIC - min(AIC, na.rm = TRUE), 2),
      Rank = rank(AIC, na.last = "keep")
    )

  # Mark best model
  os_ic$Selected <- ""
  os_ic$Selected[1] <- "***"

  # Add display names
  os_ic$Distribution <- sapply(os_ic$Distribution, function(d) {
    if (d %in% names(dist_display_names)) dist_display_names[d] else d
  })

  if (knitr::is_latex_output()) {
    kable(os_ic, format = "latex", booktabs = TRUE, escape = FALSE) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(os_ic, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("OS model comparison not available.\n")
}
```

## Progression-Free Survival (PFS) Models

```{r pfs-aic-table}
#| tbl-cap: "Progression-Free Survival model fit comparison (sorted by AIC)"

if (exists("models") && !is.null(models$full$pfs_ic)) {

  pfs_ic <- models$full$pfs_ic %>%
    arrange(AIC) %>%
    mutate(
      AIC = round(AIC, 2),
      BIC = round(BIC, 2),
      `Delta AIC` = round(AIC - min(AIC, na.rm = TRUE), 2),
      Rank = rank(AIC, na.last = "keep")
    )

  # Mark best model
  pfs_ic$Selected <- ""
  pfs_ic$Selected[1] <- "***"

  # Add display names
  pfs_ic$Distribution <- sapply(pfs_ic$Distribution, function(d) {
    if (d %in% names(dist_display_names)) dist_display_names[d] else d
  })

  if (knitr::is_latex_output()) {
    kable(pfs_ic, format = "latex", booktabs = TRUE, escape = FALSE) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(pfs_ic, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }

} else {
  cat("PFS model comparison not available.\n")
}
```

\newpage

# Overall Survival (OS) Model Coefficients

```{r os-best-model, results='asis'}
if (exists("models") && !is.null(models$best_fit$os_distribution)) {
  cat("**Best-fitting distribution:**", models$best_fit$os_distribution,
      "(AIC:", round(models$best_fit$os_aic, 2), ")\n\n")
}
```

The following tables present the regression coefficients for each fitted OS model. Parameters include:

- **Distribution-specific parameters** (e.g., shape, scale, rate)
- **Age** - Effect per year of age
- **Sex** - Effect of male vs female
- **Rx** - Main treatment effect (experimental vs control)
- **Biomarker:Rx interactions** - Treatment effect modification by biomarker status

```{r os-coefficients, results='asis'}
if (exists("models") && !is.null(models$full$os)) {

  # Get list of fitted OS models
  os_models <- models$full$os

  # Get best distribution for highlighting
  best_os_dist <- if (!is.null(models$best_fit$os_distribution)) {
    models$best_fit$os_distribution
  } else {
    ""
  }

  # Order distributions: best first, then alphabetically
  dist_names <- names(os_models)
  dist_names <- dist_names[sapply(os_models[dist_names], function(x) inherits(x, "flexsurvreg"))]

  if (length(dist_names) > 0 && best_os_dist %in% dist_names) {
    other_dists <- sort(setdiff(dist_names, best_os_dist))
    dist_names <- c(best_os_dist, other_dists)
  }

  for (dist in dist_names) {
    model_obj <- os_models[[dist]]

    if (inherits(model_obj, "flexsurvreg")) {

      # Section header
      display_name <- if (dist %in% names(dist_display_names)) {
        dist_display_names[dist]
      } else {
        dist
      }

      if (dist == best_os_dist) {
        cat("\n## ", display_name, " (Best Fit)\n\n", sep = "")
      } else {
        cat("\n## ", display_name, "\n\n", sep = "")
      }

      # Extract and display coefficients
      coef_table <- extract_coefficients(model_obj, dist)

      if (!is.null(coef_table) && nrow(coef_table) > 0) {

        if (knitr::is_latex_output()) {
          print(kable(coef_table, format = "latex", booktabs = TRUE,
                col.names = c("Parameter", "Estimate", "SE", "exp(Est)"),
                align = c("l", "r", "r", "r")) %>%
            kableExtra::kable_styling(font_size = 9,
                                     latex_options = c("striped", "HOLD_position")))
        } else {
          print(kable(coef_table, format = "html",
                col.names = c("Parameter", "Estimate", "SE", "exp(Est)")) %>%
            kableExtra::kable_styling(bootstrap_options = c("striped", "hover")))
        }

        cat("\n\n")
      } else {
        cat("Coefficients not available for this model.\n\n")
      }
    }
  }

} else {
  cat("OS models not available.\n")
}
```

\newpage

# Progression-Free Survival (PFS) Model Coefficients

```{r pfs-best-model, results='asis'}
if (exists("models") && !is.null(models$best_fit$pfs_distribution)) {
  cat("**Best-fitting distribution:**", models$best_fit$pfs_distribution,
      "(AIC:", round(models$best_fit$pfs_aic, 2), ")\n\n")
}
```

The following tables present the regression coefficients for each fitted PFS model.

```{r pfs-coefficients, results='asis'}
if (exists("models") && !is.null(models$full$pfs)) {

  # Get list of fitted PFS models
  pfs_models <- models$full$pfs

  # Get best distribution for highlighting
  best_pfs_dist <- if (!is.null(models$best_fit$pfs_distribution)) {
    models$best_fit$pfs_distribution
  } else {
    ""
  }

  # Order distributions: best first, then alphabetically
  dist_names <- names(pfs_models)
  dist_names <- dist_names[sapply(pfs_models[dist_names], function(x) inherits(x, "flexsurvreg"))]

  if (length(dist_names) > 0 && best_pfs_dist %in% dist_names) {
    other_dists <- sort(setdiff(dist_names, best_pfs_dist))
    dist_names <- c(best_pfs_dist, other_dists)
  }

  for (dist in dist_names) {
    model_obj <- pfs_models[[dist]]

    if (inherits(model_obj, "flexsurvreg")) {

      # Section header
      display_name <- if (dist %in% names(dist_display_names)) {
        dist_display_names[dist]
      } else {
        dist
      }

      if (dist == best_pfs_dist) {
        cat("\n## ", display_name, " (Best Fit)\n\n", sep = "")
      } else {
        cat("\n## ", display_name, "\n\n", sep = "")
      }

      # Extract and display coefficients
      coef_table <- extract_coefficients(model_obj, dist)

      if (!is.null(coef_table) && nrow(coef_table) > 0) {

        if (knitr::is_latex_output()) {
          print(kable(coef_table, format = "latex", booktabs = TRUE,
                col.names = c("Parameter", "Estimate", "SE", "exp(Est)"),
                align = c("l", "r", "r", "r")) %>%
            kableExtra::kable_styling(font_size = 9,
                                     latex_options = c("striped", "HOLD_position")))
        } else {
          print(kable(coef_table, format = "html",
                col.names = c("Parameter", "Estimate", "SE", "exp(Est)")) %>%
            kableExtra::kable_styling(bootstrap_options = c("striped", "hover")))
        }

        cat("\n\n")
      } else {
        cat("Coefficients not available for this model.\n\n")
      }
    }
  }

} else {
  cat("PFS models not available.\n")
}
```

\newpage

# Interpretation Guide

## Distribution-Specific Parameters

Different parametric distributions have different ancillary parameters:

| Distribution | Ancillary Parameters |
|--------------|---------------------|
| Exponential | rate |
| Weibull (AFT) | shape, scale |
| Weibull (PH) | shape, scale |
| Log-logistic | shape, scale |
| Log-normal | meanlog, sdlog |
| Gamma | shape, rate |
| Gompertz | shape, rate |
| Generalized Gamma | mu, sigma, Q |
| Generalized F | mu, sigma, Q, P |

## Coefficient Interpretation

- **Estimate**: The coefficient on the log scale (for AFT models) or log-hazard scale (for PH models)
- **SE**: Standard error of the coefficient estimate
- **exp(Est)**: Exponentiated coefficient
  - For AFT models: time ratio (values >1 indicate longer survival)
  - For PH models: hazard ratio (values <1 indicate lower hazard/better survival)

## Biomarker Interaction Terms

The biomarker:Rx interaction terms indicate treatment effect modification:

- **crp1:RxExperimental** - Effect of experimental treatment in CRP-positive patients (relative to CRP-negative)
- **tlr1:RxExperimental** - Effect of experimental treatment in TLR-positive patients
- **tmb_braf1:RxExperimental** - Effect of experimental treatment in TMB_BRAF-positive patients

A significant interaction suggests the biomarker predicts differential treatment benefit.

# Summary

This document presents the full set of parametric survival model coefficients for the METIMMOX-1 economic evaluation. The best-fitting models (selected by AIC) are:

```{r summary-table}
if (exists("models") && !is.null(models$best_fit)) {

  summary_df <- data.frame(
    Outcome = c("Overall Survival (OS)", "Progression-Free Survival (PFS)"),
    `Best Distribution` = c(
      if (!is.null(models$best_fit$os_distribution)) {
        dist_display_names[models$best_fit$os_distribution]
      } else "Not available",
      if (!is.null(models$best_fit$pfs_distribution)) {
        dist_display_names[models$best_fit$pfs_distribution]
      } else "Not available"
    ),
    AIC = c(
      if (!is.null(models$best_fit$os_aic)) round(models$best_fit$os_aic, 2) else NA,
      if (!is.null(models$best_fit$pfs_aic)) round(models$best_fit$pfs_aic, 2) else NA
    ),
    check.names = FALSE
  )

  if (knitr::is_latex_output()) {
    kable(summary_df, format = "latex", booktabs = TRUE) %>%
      kableExtra::kable_styling(font_size = 10, latex_options = c("striped", "HOLD_position"))
  } else {
    kable(summary_df, format = "html") %>%
      kableExtra::kable_styling(bootstrap_options = c("striped", "hover"))
  }
}
```

All model coefficients are provided for transparency and to support sensitivity analyses exploring alternative distributional assumptions.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.0