---
title: "All Parametric Survival Models"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03", "04"),
  packages = c("here", "knitr", "kableExtra", "dplyr", "tidyr", "survival", "flexsurv"),
  set_theme = FALSE
)

extract_model_coefs <- function(fit, endpoint, distribution) {
  if (is.null(fit)) return(NULL)
  tab <- as.data.frame(fit$res)
  tab$Parameter <- rownames(tab)
  rownames(tab) <- NULL
  tab %>%
    transmute(
      Endpoint = endpoint,
      Distribution = distribution,
      Parameter,
      Estimate = est,
      SE = se,
      L95 = `L95%`,
      U95 = `U95%`
    )
}
```

# Overview

This technical appendix lists every fitted parametric distribution for the single joint economic survival model. Overall survival (OS) and progression-free survival (PFS) are not selected independently. The base-case pair is the pair with the lowest combined AIC among candidates that preserve OS $\geq$ PFS for control and every economic biomarker subgroup at every weekly time point over the modeled horizon.

With the current data and 10-year horizon, this ordering-constrained procedure selects **gamma for OS and gamma for PFS**. The manuscript's gamma and Model-A/B/C statements are retained only as historical descriptions; they do not define the executable selection procedure or the current single-model structure.

```{r formula-table}
formula_df <- data.frame(
  Endpoint = c("Overall survival", "Progression-free survival"),
  Formula = c(
    paste(deparse(get_strategy_formula("crp", "os")), collapse = " "),
    paste(deparse(get_strategy_formula("crp", "pfs")), collapse = " ")
  ),
  stringsAsFactors = FALSE
)

knitr::kable(formula_df, booktabs = TRUE, align = c("l", "l"),
             caption = "Fitted economic survival formulas") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position")) %>%
  kableExtra::column_spec(2, width = "11cm")
```

# Information Criteria

```{r ic-table}
ic_table <- bind_rows(
  models$full$os_ic %>% mutate(Endpoint = "Overall survival"),
  models$full$pfs_ic %>% mutate(Endpoint = "Progression-free survival")
) %>%
  filter(!is.na(AIC)) %>%
  group_by(Endpoint) %>%
  arrange(AIC, .by_group = TRUE) %>%
  mutate(
    Delta_AIC = AIC - min(AIC),
    Delta_BIC = BIC - min(BIC)
  ) %>%
  ungroup()

knitr::kable(
  ic_table,
  booktabs = TRUE,
  digits = 2,
  align = "r",
  caption = "Information criteria for all fitted distributions"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
```

# Coefficient Tables

```{r all-coefficients}
coef_rows <- list()
for (dist in names(models$full$os)) {
  coef_rows[[paste0("os_", dist)]] <- extract_model_coefs(models$full$os[[dist]], "OS", dist)
}
for (dist in names(models$full$pfs)) {
  coef_rows[[paste0("pfs_", dist)]] <- extract_model_coefs(models$full$pfs[[dist]], "PFS", dist)
}

coef_df <- bind_rows(coef_rows) %>%
  mutate(
    Estimate = sprintf("%.4f", Estimate),
    SE = sprintf("%.4f", SE),
    `95% CI` = sprintf("[%.4f, %.4f]", L95, U95)
  ) %>%
  select(Endpoint, Distribution, Parameter, Estimate, SE, `95% CI`)

knitr::kable(
  coef_df,
  booktabs = TRUE,
  align = c("l", "l", "l", "r", "r", "r"),
  caption = "Coefficient estimates for all fitted parametric models"
) %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"), font_size = 8)
```

# Ordering-Constrained Selection Summary

```{r best-fit}
best_fit <- data.frame(
  Endpoint = c("Overall survival", "Progression-free survival"),
  Distribution = c(models$best_fit$os_distribution, models$best_fit$pfs_distribution),
  AIC = c(models$best_fit$os_aic, models$best_fit$pfs_aic),
  stringsAsFactors = FALSE
)

knitr::kable(best_fit, booktabs = TRUE, digits = 2,
             caption = "Selected minimum-combined-AIC pair satisfying OS >= PFS") %>%
  kableExtra::kable_styling(latex_options = c("HOLD_position"))
```

The pair is selected jointly. Consequently, an endpoint's selected family need not be its independently lowest-AIC family. The full candidate-pair audit and the combined-AIC penalty relative to independent endpoint selection are stored in `models$ordered_selection` and `models$best_fit$ordering_aic_penalty`, respectively.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 5.0
