---
title: "Bug Fix Impact Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

<!--
SNAPSHOT SYSTEM OVERVIEW:

PURPOSE:
  Track the impact of bug fixes on cost-effectiveness analysis results by
  comparing baseline (before fix) and fixed (after fix) snapshots.
  Supports multi-model snapshots (A=joint, B=focused, C=separate).

WORKFLOW:
  1. Before fixing bug: Rscript 15_save_snapshot.R <issue> baseline
  2. Fix the bug and commit changes
  3. After fixing bug:  Rscript 15_save_snapshot.R <issue> fixed
  4. Generate this report: quarto render bug_fix_impact.qmd

FILE NAMING:
  - snapshot_<issue>_baseline_<commit>.rds  (before fix)
  - snapshot_<issue>_fixed_<commit>.rds     (after fix)
  - psa_<issue>_baseline_<commit>.rds       (PSA before)
  - psa_<issue>_fixed_<commit>.rds          (PSA after)

SNAPSHOT FORMAT:
  Legacy (v2.0): top-level base_results, icer_obj, nmb_at_wtp, psa_summary
  Multi-model (v3.0+): same top-level fields PLUS models = list(joint=..., focused=..., separate=...)

REPORT BEHAVIOR:
  - Automatically finds the most recent baseline/fixed snapshot pair
  - Detects multi-model vs legacy snapshots and adapts display
  - Multi-model: shows per-model sections (A, B, C) + cross-model summary
  - Legacy: shows single model section
-->

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "left",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  png, grid, dampack
)

# Load snapshot utilities for multi-model detection
source(here::here("scripts/R/functions/snapshot_utils.R"))

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r load-snapshots}
# Find all snapshot files
snapshots_dir <- here::here("data", "output", "snapshots")
all_files <- list.files(snapshots_dir, pattern = "^snapshot_.*\\.rds$", full.names = TRUE)

if (length(all_files) == 0) {
  stop("No snapshot files found in data/output/snapshots/. Please run 15_save_snapshot.R first.")
}

# Extract issue numbers and status from filenames
file_info <- data.frame(
  path = all_files,
  filename = basename(all_files),
  stringsAsFactors = FALSE
)

# Parse filenames: snapshot_<issue>_<status>_<commit>.rds
file_info$issue <- gsub("snapshot_(\\d+)_.*", "\\1", file_info$filename)
file_info$status <- gsub("snapshot_\\d+_(baseline|fixed)_.*", "\\1", file_info$filename)
file_info$commit <- gsub("snapshot_\\d+_(baseline|fixed)_(.*)\\.rds", "\\2", file_info$filename)

# Identify all complete snapshot pairs (issues with both baseline and fixed)
all_issues <- unique(file_info$issue)
complete_pairs <- data.frame(
  Issue = character(),
  Baseline_Commit = character(),
  Fixed_Commit = character(),
  Baseline_File = character(),
  Fixed_File = character(),
  stringsAsFactors = FALSE
)

for (issue in all_issues) {
  baseline_exists <- any(file_info$issue == issue & file_info$status == "baseline")
  fixed_exists <- any(file_info$issue == issue & file_info$status == "fixed")

  if (baseline_exists && fixed_exists) {
    baseline_commit <- file_info$commit[file_info$issue == issue & file_info$status == "baseline"][1]
    fixed_commit <- file_info$commit[file_info$issue == issue & file_info$status == "fixed"][1]
    baseline_file <- file_info$path[file_info$issue == issue & file_info$status == "baseline"][1]
    fixed_file <- file_info$path[file_info$issue == issue & file_info$status == "fixed"][1]

    # Get timestamp from fixed snapshot file
    fixed_snap_temp <- readRDS(fixed_file)
    timestamp <- fixed_snap_temp$metadata$timestamp

    complete_pairs <- rbind(complete_pairs, data.frame(
      Issue = issue,
      Baseline_Commit = baseline_commit,
      Fixed_Commit = fixed_commit,
      Baseline_File = baseline_file,
      Fixed_File = fixed_file,
      Timestamp = timestamp,
      stringsAsFactors = FALSE
    ))
  }
}

# Sort by timestamp (most recent first)
complete_pairs <- complete_pairs[order(complete_pairs$Timestamp, decreasing = TRUE), ]

# Fetch issue titles from GitHub
complete_pairs$Issue_Title <- sapply(complete_pairs$Issue, function(issue_num) {
  tryCatch({
    result <- system(paste0("gh issue view ", issue_num, " --json title --jq .title"),
                     intern = TRUE, ignore.stderr = TRUE)
    if (length(result) > 0 && result != "") {
      return(result[1])
    } else {
      return("")
    }
  }, error = function(e) {
    return("")
  })
})

if (nrow(complete_pairs) == 0) {
  stop("No complete snapshot pairs found. Each issue needs both baseline and fixed snapshots.")
}

# Get the most recent snapshot pair
latest_pair <- complete_pairs[1, ]
latest_issue <- latest_pair$Issue

# Load snapshots for the most recent issue
baseline_snapshot <- readRDS(latest_pair$Baseline_File)
fixed_snapshot <- readRDS(latest_pair$Fixed_File)

# Load PSA objects (handle both legacy single-object and new list format)
baseline_psa_file <- gsub("snapshot_", "psa_", latest_pair$Baseline_File)
fixed_psa_file <- gsub("snapshot_", "psa_", latest_pair$Fixed_File)

baseline_psa_raw <- readRDS(baseline_psa_file)
fixed_psa_raw <- readRDS(fixed_psa_file)

# Detect format: legacy = single psa object, new = named list
if (inherits(baseline_psa_raw, "psa")) {
  baseline_psa_all <- list(legacy = baseline_psa_raw)
} else {
  baseline_psa_all <- baseline_psa_raw
}
if (inherits(fixed_psa_raw, "psa")) {
  fixed_psa_all <- list(legacy = fixed_psa_raw)
} else {
  fixed_psa_all <- fixed_psa_raw
}

# Extract metadata
issue_num <- latest_issue
before_meta <- baseline_snapshot$metadata
after_meta <- fixed_snapshot$metadata

# Detect multi-model snapshots
baseline_multimodel <- is_multimodel_snapshot(baseline_snapshot)
fixed_multimodel <- is_multimodel_snapshot(fixed_snapshot)
both_multimodel <- baseline_multimodel && fixed_multimodel

model_display_names <- c(
  joint = "Model A: Joint",
  focused = "Model B: Focused",
  separate = "Model C: Separate",
  legacy = "Single Model"
)

if (both_multimodel) {
  model_names <- intersect(
    names(baseline_snapshot$models),
    names(fixed_snapshot$models)
  )
} else {
  model_names <- "legacy"
}
```

```{r compute-comparisons}
# Reusable function: compute all comparisons for one model
compute_model_comparison <- function(bl_data, fx_data, bl_psa = NULL, fx_psa = NULL) {
  base_before <- bl_data$icer_obj
  base_after <- fx_data$icer_obj

  base_comp <- merge(
    base_before[, c("Strategy", "Cost", "Effect", "Inc_Cost", "Inc_Effect", "ICER")],
    base_after[, c("Strategy", "Cost", "Effect", "Inc_Cost", "Inc_Effect", "ICER")],
    by = "Strategy",
    suffixes = c("_before", "_after")
  )
  base_comp$Cost_diff <- base_comp$Cost_after - base_comp$Cost_before
  base_comp$Effect_diff <- base_comp$Effect_after - base_comp$Effect_before
  base_comp$ICER_diff <- ifelse(
    is.na(base_comp$ICER_before) | is.na(base_comp$ICER_after),
    NA, base_comp$ICER_after - base_comp$ICER_before
  )

  # NMB comparison
  nmb_before <- bl_data$nmb_at_wtp
  nmb_after <- fx_data$nmb_at_wtp
  nmb_comp <- merge(
    nmb_before[, c("Strategy", "NMB")],
    nmb_after[, c("Strategy", "NMB")],
    by = "Strategy", suffixes = c("_before", "_after")
  )
  nmb_comp$NMB_diff <- nmb_comp$NMB_after - nmb_comp$NMB_before
  nmb_comp <- nmb_comp[order(-nmb_comp$NMB_after), ]

  optimal_before <- nmb_before$Strategy[which.max(nmb_before$NMB)]
  optimal_after <- nmb_after$Strategy[which.max(nmb_after$NMB)]

  # PSA comparison
  psa_comp <- NULL
  if (!is.null(bl_data$psa_summary) && !is.null(fx_data$psa_summary)) {
    psa_comp <- merge(
      bl_data$psa_summary, fx_data$psa_summary,
      by = "Strategy", suffixes = c("_before", "_after")
    )
    psa_comp$meanCost_diff <- psa_comp$meanCost_after - psa_comp$meanCost_before
    psa_comp$meanEffect_diff <- psa_comp$meanEffect_after - psa_comp$meanEffect_before
  }

  # Significance metrics
  max_cost_change <- max(abs(base_comp$Cost_diff), na.rm = TRUE)
  max_effect_change <- max(abs(base_comp$Effect_diff), na.rm = TRUE)
  max_icer_change <- max(abs(base_comp$ICER_diff), na.rm = TRUE)

  list(
    base_comp = base_comp,
    base_before = base_before,
    base_after = base_after,
    nmb_comp = nmb_comp,
    psa_comp = psa_comp,
    bl_psa = bl_psa,
    fx_psa = fx_psa,
    optimal_before = optimal_before,
    optimal_after = optimal_after,
    optimal_changed = optimal_before != optimal_after,
    max_cost_change = max_cost_change,
    max_effect_change = max_effect_change,
    max_icer_change = max_icer_change
  )
}

# Compute comparisons for each model
all_comparisons <- list()
for (model_name in model_names) {
  if (model_name == "legacy") {
    bl_data <- list(
      icer_obj = baseline_snapshot$icer_obj,
      nmb_at_wtp = baseline_snapshot$nmb_at_wtp,
      psa_summary = baseline_snapshot$psa_summary
    )
    fx_data <- list(
      icer_obj = fixed_snapshot$icer_obj,
      nmb_at_wtp = fixed_snapshot$nmb_at_wtp,
      psa_summary = fixed_snapshot$psa_summary
    )
  } else {
    bl_data <- baseline_snapshot$models[[model_name]]
    fx_data <- fixed_snapshot$models[[model_name]]
  }

  # Get PSA objects for this model
  bl_psa <- if (model_name %in% names(baseline_psa_all)) baseline_psa_all[[model_name]] else NULL
  fx_psa <- if (model_name %in% names(fixed_psa_all)) fixed_psa_all[[model_name]] else NULL

  all_comparisons[[model_name]] <- compute_model_comparison(
    bl_data, fx_data, bl_psa, fx_psa
  )
}

# Check for parameter changes (uses metadata, model-independent)
param_names <- names(before_meta$parameters)
param_changes <- c()
for (param in param_names) {
  before_val <- before_meta$parameters[[param]]
  after_val <- after_meta$parameters[[param]]
  if (!identical(before_val, after_val)) {
    param_changes <- c(param_changes, param)
  }
}
```

# Summary

This report compares cost-effectiveness analysis results before and after addressing GitHub issue #`r issue_num`. The comparison assesses whether bug fixes or model changes affected results.

**Current Comparison:**

- **Issue:** #`r issue_num` - `r if(latest_pair$Issue_Title != "") latest_pair$Issue_Title else "No title available"`
- **Baseline:** Commit `r before_meta$git_commit` (`r before_meta$timestamp`)
- **Fixed:** Commit `r after_meta$git_commit` (`r after_meta$timestamp`)
- **Models included:** `r if(both_multimodel) paste(sapply(model_names, function(m) model_display_names[m]), collapse = ", ") else "Single model (legacy snapshot)"`

\newpage

# Metadata Comparison

```{r metadata-table}
# Get model structure display
get_ms_display <- function(meta) {
  ms <- meta$parameters$MODEL_STRUCTURE
  if (is.null(ms) || is.na(ms)) return("0 (joint)")
  paste0(ms, " (", c("joint", "focused", "separate")[ms + 1], ")")
}

metadata_comp <- data.frame(
  Item = c("Git Commit", "Timestamp", "R Version", "Issue Number",
           "Model Structure", "Multi-Model Snapshot"),
  Baseline = c(
    before_meta$git_commit,
    before_meta$timestamp,
    before_meta$r_version,
    before_meta$issue_number,
    get_ms_display(before_meta),
    ifelse(baseline_multimodel, "Yes", "No")
  ),
  Fixed = c(
    after_meta$git_commit,
    after_meta$timestamp,
    after_meta$r_version,
    after_meta$issue_number,
    get_ms_display(after_meta),
    ifelse(fixed_multimodel, "Yes", "No")
  )
)

kable(metadata_comp,
      caption = "Metadata Comparison",
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

## Global Parameters

```{r parameters-table}
param_comp <- data.frame(
  Parameter = param_names,
  Baseline = sapply(param_names, function(p) {
    val <- before_meta$parameters[[p]]
    if (is.na(val)) return("NA")
    if (is.numeric(val)) return(format(val, scientific = FALSE, big.mark = ","))
    return(as.character(val))
  }),
  Fixed = sapply(param_names, function(p) {
    val <- after_meta$parameters[[p]]
    if (is.na(val)) return("NA")
    if (is.numeric(val)) return(format(val, scientific = FALSE, big.mark = ","))
    return(as.character(val))
  }),
  stringsAsFactors = FALSE
)

param_comp$Changed <- ifelse(param_comp$Baseline != param_comp$Fixed, "Yes", "No")

kable(param_comp,
      caption = "Global Parameter Comparison",
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down")) %>%
  row_spec(which(param_comp$Changed == "Yes"), bold = TRUE, color = "red")
```

\newpage

# Per-Model Comparisons

```{r per-model-comparisons, results='asis', fig.width=8, fig.height=5}
for (model_name in model_names) {
  comp <- all_comparisons[[model_name]]
  display_name <- model_display_names[model_name]

  cat("\n\n## ", display_name, "\n\n")

  # ---- Base Case Incremental Cost ----
  cat("### Base Case Results\n\n")

  base_comp <- comp$base_comp
  control_cost_before <- base_comp$Cost_before[base_comp$Strategy == "control"]
  control_cost_after <- base_comp$Cost_after[base_comp$Strategy == "control"]
  control_effect_before <- base_comp$Effect_before[base_comp$Strategy == "control"]
  control_effect_after <- base_comp$Effect_after[base_comp$Strategy == "control"]

  base_inc <- base_comp %>%
    mutate(
      Inc_Cost_bl = Cost_before - control_cost_before,
      Inc_Cost_fx = Cost_after - control_cost_after,
      Inc_Effect_bl = Effect_before - control_effect_before,
      Inc_Effect_fx = Effect_after - control_effect_after
    )

  # Incremental Cost table
  cost_d <- base_inc %>%
    mutate(
      Cost_diff = Inc_Cost_fx - Inc_Cost_bl,
      Inc_Cost_bl = format(round(Inc_Cost_bl, 2), big.mark = ",", nsmall = 2),
      Inc_Cost_fx = format(round(Inc_Cost_fx, 2), big.mark = ",", nsmall = 2),
      Cost_diff = format(round(Cost_diff, 2), big.mark = ",", nsmall = 2)
    ) %>%
    select(Strategy, Inc_Cost_bl, Inc_Cost_fx, Cost_diff)

  print(kable(cost_d,
        caption = paste0(display_name, " - Incremental Cost Comparison"),
        col.names = c("Strategy", "Baseline (EUR)", "Fixed (EUR)", "Difference (EUR)"),
        booktabs = TRUE, format = "latex", align = c("l", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position")))

  cat("\n\\vspace{0.5em}\n\n")

  # Incremental Effect table
  effect_d <- base_inc %>%
    mutate(
      Effect_diff = Inc_Effect_fx - Inc_Effect_bl,
      Inc_Effect_bl = format(round(Inc_Effect_bl, 4), nsmall = 4),
      Inc_Effect_fx = format(round(Inc_Effect_fx, 4), nsmall = 4),
      Effect_diff = format(round(Effect_diff, 4), nsmall = 4)
    ) %>%
    select(Strategy, Inc_Effect_bl, Inc_Effect_fx, Effect_diff)

  print(kable(effect_d,
        caption = paste0(display_name, " - Incremental Effect Comparison"),
        col.names = c("Strategy", "Baseline (QALYs)", "Fixed (QALYs)", "Difference (QALYs)"),
        booktabs = TRUE, format = "latex", align = c("l", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position")))

  cat("\n\\vspace{0.5em}\n\n")

  # ICER table
  icer_d <- base_comp %>%
    select(Strategy, ICER_before, ICER_after) %>%
    mutate(
      ICER_diff = ICER_after - ICER_before,
      ICER_before = ifelse(is.na(ICER_before), "---",
                           format(round(ICER_before, 0), big.mark = ",")),
      ICER_after = ifelse(is.na(ICER_after), "---",
                          format(round(ICER_after, 0), big.mark = ",")),
      ICER_diff = ifelse(is.na(ICER_diff), "---",
                         format(round(ICER_diff, 0), big.mark = ","))
    )

  print(kable(icer_d,
        caption = paste0(display_name, " - ICER Comparison"),
        col.names = c("Strategy", "Baseline (EUR/QALY)", "Fixed (EUR/QALY)", "Difference (EUR/QALY)"),
        booktabs = TRUE, format = "latex", align = c("l", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position")))

  # ---- Efficiency Frontier ----
  cat("\n\n### Efficiency Frontier\n\n")

  baseline_icer <- dampack::calculate_icers(
    cost = comp$base_before$Cost,
    effect = comp$base_before$Effect,
    strategies = comp$base_before$Strategy
  )
  fixed_icer <- dampack::calculate_icers(
    cost = comp$base_after$Cost,
    effect = comp$base_after$Effect,
    strategies = comp$base_after$Strategy
  )

  p_bl <- plot(baseline_icer, txtsize = 10, currency = "EUR",
               effect_units = "QALYs", label = "all") +
    labs(title = "Baseline") +
    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5))

  p_fx <- plot(fixed_icer, txtsize = 10, currency = "EUR",
               effect_units = "QALYs", label = "all") +
    labs(title = "Fixed") +
    theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5))

  print(gridExtra::grid.arrange(p_bl, p_fx, nrow = 2))

  # ---- NMB ----
  cat("\n\n### Net Monetary Benefit\n\n")

  nmb_d <- comp$nmb_comp %>%
    mutate(
      NMB_before = format(round(NMB_before, 2), big.mark = ",", nsmall = 2),
      NMB_after = format(round(NMB_after, 2), big.mark = ",", nsmall = 2),
      NMB_diff = format(round(NMB_diff, 2), big.mark = ",", nsmall = 2)
    )

  print(kable(nmb_d,
        caption = paste0(display_name, " - NMB at WTP = EUR ",
                        format(before_meta$parameters$WTP, big.mark = ",")),
        col.names = c("Strategy", "Baseline (EUR)", "Fixed (EUR)", "Difference (EUR)"),
        booktabs = TRUE, format = "latex") %>%
    kable_styling(latex_options = c("striped", "hold_position")) %>%
    row_spec(1, bold = TRUE, background = "#E8F4F8"))

  cat("\n\n**Optimal Strategy:** ",
      if (comp$optimal_changed) {
        paste0("**Changed** from ", comp$optimal_before, " to ", comp$optimal_after)
      } else {
        paste0("Unchanged (", comp$optimal_after, ")")
      }, "\n\n", sep = "")

  # ---- PSA Results ----
  if (!is.null(comp$psa_comp)) {
    cat("### PSA Results\n\n")
    psa_comp <- comp$psa_comp

    # PSA Cost table
    psa_cost_d <- psa_comp %>%
      mutate(
        BL = sprintf("EUR %s (EUR %s; EUR %s)",
                     format(round(meanCost_before, 2), big.mark = ",", nsmall = 2),
                     format(round(Cost_2.5_percent_before, 2), big.mark = ",", nsmall = 2),
                     format(round(Cost_97.5_percent_before, 2), big.mark = ",", nsmall = 2)),
        FX = sprintf("EUR %s (EUR %s; EUR %s)",
                     format(round(meanCost_after, 2), big.mark = ",", nsmall = 2),
                     format(round(Cost_2.5_percent_after, 2), big.mark = ",", nsmall = 2),
                     format(round(Cost_97.5_percent_after, 2), big.mark = ",", nsmall = 2)),
        Diff = format(round(meanCost_diff, 2), big.mark = ",", nsmall = 2)
      ) %>%
      select(Strategy, BL, FX, Diff)

    print(kable(psa_cost_d,
          caption = paste0(display_name, " - PSA Cost Results"),
          col.names = c("Strategy", "Baseline Mean (2.5%; 97.5%)",
                        "Fixed Mean (2.5%; 97.5%)", "Difference (EUR)"),
          booktabs = TRUE, format = "latex", align = c("l", "r", "r", "r")) %>%
      kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                    font_size = 9))

    cat("\n\\vspace{0.5em}\n\n")

    # PSA Effect table
    psa_eff_d <- psa_comp %>%
      mutate(
        BL = sprintf("%.4f (%.4f; %.4f)",
                     meanEffect_before, Effect_2.5_percent_before,
                     Effect_97.5_percent_before),
        FX = sprintf("%.4f (%.4f; %.4f)",
                     meanEffect_after, Effect_2.5_percent_after,
                     Effect_97.5_percent_after),
        Diff = sprintf("%.4f", meanEffect_diff)
      ) %>%
      select(Strategy, BL, FX, Diff)

    print(kable(psa_eff_d,
          caption = paste0(display_name, " - PSA Effect Results"),
          col.names = c("Strategy", "Baseline Mean (2.5%; 97.5%)",
                        "Fixed Mean (2.5%; 97.5%)", "Difference (QALYs)"),
          booktabs = TRUE, format = "latex", align = c("l", "r", "r", "r")) %>%
      kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                    font_size = 9))

    cat("\n\\vspace{0.5em}\n\n")

    # PSA ICER table
    psa_icer_d <- psa_comp %>%
      select(Strategy, meanCost_before, meanEffect_before,
             meanCost_after, meanEffect_after) %>%
      mutate(
        inc_cost_bl = meanCost_before - meanCost_before[1],
        inc_eff_bl = meanEffect_before - meanEffect_before[1],
        icer_bl = ifelse(inc_eff_bl > 0.0001, inc_cost_bl / inc_eff_bl, NA),
        inc_cost_fx = meanCost_after - meanCost_after[1],
        inc_eff_fx = meanEffect_after - meanEffect_after[1],
        icer_fx = ifelse(inc_eff_fx > 0.0001, inc_cost_fx / inc_eff_fx, NA)
      ) %>%
      mutate(
        BL_ICER = ifelse(is.na(icer_bl), "---",
                         sprintf("EUR %s/QALY",
                                 format(round(icer_bl, 0), big.mark = ","))),
        FX_ICER = ifelse(is.na(icer_fx), "---",
                         sprintf("EUR %s/QALY",
                                 format(round(icer_fx, 0), big.mark = ",")))
      ) %>%
      select(Strategy, BL_ICER, FX_ICER)

    print(kable(psa_icer_d,
          caption = paste0(display_name, " - PSA ICER Results"),
          col.names = c("Strategy", "Baseline Mean ICER", "Fixed Mean ICER"),
          booktabs = TRUE, format = "latex", align = c("l", "r", "r")) %>%
      kable_styling(latex_options = c("striped", "hold_position"), font_size = 10))
  }

  # ---- PSA Scatter Plots ----
  bl_psa <- comp$bl_psa
  fx_psa <- comp$fx_psa

  if (!is.null(bl_psa) && !is.null(fx_psa)) {
    cat("\n\n### PSA Scatter Plots\n\n")

    bl_psa_data <- data.frame(
      Strategy = rep(bl_psa$strategies, each = bl_psa$n_sim),
      Cost = as.vector(as.matrix(bl_psa$cost)),
      Effect = as.vector(as.matrix(bl_psa$effectiveness)),
      Snapshot = "Baseline"
    )
    fx_psa_data <- data.frame(
      Strategy = rep(fx_psa$strategies, each = fx_psa$n_sim),
      Cost = as.vector(as.matrix(fx_psa$cost)),
      Effect = as.vector(as.matrix(fx_psa$effectiveness)),
      Snapshot = "Fixed"
    )

    p_bl_scatter <- ggplot(bl_psa_data,
                           aes(x = Effect, y = Cost, color = Strategy)) +
      geom_point(alpha = 0.4, size = 2) +
      labs(title = "Baseline", x = "Effect (QALYs)", y = "Cost (EUR)") +
      theme_minimal() +
      theme(legend.position = "bottom",
            legend.text = element_text(size = 8),
            axis.title = element_text(size = 10))

    p_fx_scatter <- ggplot(fx_psa_data,
                           aes(x = Effect, y = Cost, color = Strategy)) +
      geom_point(alpha = 0.4, size = 2) +
      labs(title = "Fixed", x = "Effect (QALYs)", y = "Cost (EUR)") +
      theme_minimal() +
      theme(legend.position = "bottom",
            legend.text = element_text(size = 8),
            axis.title = element_text(size = 10))

    print(gridExtra::grid.arrange(p_bl_scatter, p_fx_scatter, ncol = 2))
  }

  cat("\n\n\\newpage\n\n")
}
```

# Cross-Model Summary

```{r cross-model-summary}
if (length(model_names) > 1) {
  cross_summary <- data.frame(
    Model = character(),
    Optimal_Before = character(),
    Optimal_After = character(),
    Changed = character(),
    Max_Cost = numeric(),
    Max_Effect = numeric(),
    Max_ICER = numeric(),
    stringsAsFactors = FALSE
  )

  for (mn in model_names) {
    comp <- all_comparisons[[mn]]
    cross_summary <- rbind(cross_summary, data.frame(
      Model = model_display_names[mn],
      Optimal_Before = comp$optimal_before,
      Optimal_After = comp$optimal_after,
      Changed = ifelse(comp$optimal_changed, "Yes", "No"),
      Max_Cost = comp$max_cost_change,
      Max_Effect = comp$max_effect_change,
      Max_ICER = comp$max_icer_change,
      stringsAsFactors = FALSE
    ))
  }

  cross_display <- cross_summary %>%
    mutate(
      Max_Cost = format(round(Max_Cost, 2), big.mark = ",", nsmall = 2),
      Max_Effect = format(round(Max_Effect, 4), nsmall = 4),
      Max_ICER = format(round(Max_ICER, 0), big.mark = ",")
    )

  kable(cross_display,
        caption = "Cross-Model Impact Summary",
        col.names = c("Model", "Opt. (BL)", "Opt. (Fix)", "Changed?",
                      "Max Cost Delta (EUR)", "Max Effect Delta (QALYs)",
                      "Max ICER Delta (EUR/QALY)"),
        booktabs = TRUE, format = "latex",
        align = c("l", "l", "l", "c", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"),
                  font_size = 9)
} else {
  # Single model - show simple summary
  comp <- all_comparisons[[model_names[1]]]
  cat("Single-model snapshot. See the detailed comparison above.\n")
}
```

\newpage

# Comparison Across Recent Issues

## Available Snapshot Pairs

```{r available-snapshots-table}
if (nrow(complete_pairs) > 0) {
  pairs_display <- complete_pairs %>%
    select(Issue, Issue_Title, Baseline_Commit, Fixed_Commit) %>%
    mutate(
      Issue_Title = ifelse(Issue_Title == "", "---", Issue_Title)
    )

  # Find which row is the current issue (before any formatting)
  current_row <- which(pairs_display$Issue == issue_num)

  kable(pairs_display,
        caption = "All Available Snapshot Pairs",
        col.names = c("Issue", "Title", "Baseline Commit", "Fixed Commit"),
        booktabs = TRUE,
        format = "latex",
        align = c("l", "l", "l", "l")) %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10) %>%
    column_spec(1, width = "1cm") %>%
    column_spec(2, width = "6cm") %>%
    column_spec(c(3, 4), width = "2.5cm") %>%
    row_spec(current_row, bold = TRUE, background = "#E8F4F8")
} else {
  cat("No snapshot pairs available.\n")
}
```

## Multi-Issue Impact Summary

```{r multi-issue-comparison, results='asis'}
# Compare across multiple recent issues if available
n_issues_available <- nrow(complete_pairs)

if (n_issues_available >= 2) {
  cat("This table summarizes the impact of bug fixes across the most recent issues:\n\n")

  # Get up to 5 most recent issues (already sorted by timestamp descending)
  n_to_compare <- min(5, n_issues_available)
  recent_issues <- head(complete_pairs, n_to_compare)

  # Build comparison table (uses legacy top-level fields for consistency)
  multi_comp <- data.frame(
    Issue = character(),
    Issue_Title = character(),
    Optimal_Baseline = character(),
    Optimal_Fixed = character(),
    Changed = character(),
    Max_Cost_Change = numeric(),
    Max_Effect_Change = numeric(),
    Max_ICER_Change = numeric(),
    stringsAsFactors = FALSE
  )

  for (i in seq_len(nrow(recent_issues))) {
    issue_row <- recent_issues[i, ]

    # Load snapshots (use top-level fields for cross-issue comparison)
    snap_base <- readRDS(issue_row$Baseline_File)
    snap_fixed <- readRDS(issue_row$Fixed_File)

    base_comp_temp <- merge(
      snap_base$icer_obj[, c("Strategy", "Cost", "Effect", "ICER")],
      snap_fixed$icer_obj[, c("Strategy", "Cost", "Effect", "ICER")],
      by = "Strategy",
      suffixes = c("_before", "_after")
    )

    base_comp_temp$Cost_diff <- base_comp_temp$Cost_after - base_comp_temp$Cost_before
    base_comp_temp$Effect_diff <- base_comp_temp$Effect_after - base_comp_temp$Effect_before
    base_comp_temp$ICER_diff <- ifelse(
      is.na(base_comp_temp$ICER_before) | is.na(base_comp_temp$ICER_after),
      NA, base_comp_temp$ICER_after - base_comp_temp$ICER_before
    )

    nmb_base <- snap_base$nmb_at_wtp
    nmb_fixed <- snap_fixed$nmb_at_wtp
    opt_base <- nmb_base$Strategy[which.max(nmb_base$NMB)]
    opt_fixed <- nmb_fixed$Strategy[which.max(nmb_fixed$NMB)]

    multi_comp <- rbind(multi_comp, data.frame(
      Issue = issue_row$Issue,
      Issue_Title = ifelse(issue_row$Issue_Title == "", "---",
                           issue_row$Issue_Title),
      Optimal_Baseline = opt_base,
      Optimal_Fixed = opt_fixed,
      Changed = ifelse(opt_base != opt_fixed, "Yes", "No"),
      Max_Cost_Change = max(abs(base_comp_temp$Cost_diff), na.rm = TRUE),
      Max_Effect_Change = max(abs(base_comp_temp$Effect_diff), na.rm = TRUE),
      Max_ICER_Change = max(abs(base_comp_temp$ICER_diff), na.rm = TRUE),
      stringsAsFactors = FALSE
    ))
  }

  # Find which row is the current issue
  current_row <- which(multi_comp$Issue == issue_num)

  # Format for display
  multi_comp_display <- multi_comp %>%
    mutate(
      Max_Cost_Change = format(round(Max_Cost_Change, 2), big.mark = ",", nsmall = 2),
      Max_Effect_Change = format(round(Max_Effect_Change, 4), nsmall = 4),
      Max_ICER_Change = format(round(Max_ICER_Change, 0), big.mark = ",")
    )

  print(kable(multi_comp_display,
        caption = paste0("Summary of Bug Fix Impacts (", n_to_compare,
                        " Most Recent Issues)"),
        col.names = c("Issue", "Title", "Opt. (BL)", "Opt. (Fix)", "Chg?",
                      "Max Cost Delta (EUR)", "Max Effect Delta (QALYs)",
                      "Max ICER Delta (EUR/QALY)"),
        booktabs = TRUE, format = "latex",
        align = c("l", "l", "l", "l", "c", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"),
                  font_size = 8) %>%
    column_spec(2, width = "4cm") %>%
    column_spec(c(1, 5), width = "0.8cm") %>%
    column_spec(c(3, 4), width = "2cm") %>%
    column_spec(c(6, 7, 8), width = "1.8cm") %>%
    row_spec(current_row, bold = TRUE, background = "#E8F4F8"))
}
```

\newpage

# Summary

```{r summary-text, results='asis'}
# Use the first model for the top-level summary stats
primary <- all_comparisons[[model_names[1]]]

cat("The comparison for issue #", issue_num, " shows:\n\n", sep = "")

cat("- **Models compared:** ",
    if (both_multimodel) paste(model_display_names[model_names], collapse = ", ")
    else "Single model (legacy snapshot)", "\n", sep = "")

cat("- **Optimal Strategy (",
    model_display_names[model_names[1]], "):** ",
    if (primary$optimal_changed)
      paste0("Changed from ", primary$optimal_before,
             " to ", primary$optimal_after)
    else paste0("Unchanged (", primary$optimal_after, ")"),
    "\n", sep = "")

cat("- **Maximum Cost Change:** EUR ",
    format(round(primary$max_cost_change, 2), big.mark = ",", nsmall = 2),
    " (", if (primary$max_cost_change > 100) "substantial" else "minor",
    ")\n", sep = "")

cat("- **Maximum Effect Change:** ",
    format(round(primary$max_effect_change, 3), nsmall = 3), " QALYs (",
    if (primary$max_effect_change > 0.01) "substantial" else "minor",
    ")\n", sep = "")

cat("- **Maximum ICER Change:** EUR ",
    format(round(primary$max_icer_change, 0), big.mark = ","), "/QALY (",
    if (primary$max_icer_change > 1000) "substantial" else "minor",
    ")\n", sep = "")

cat("- **Parameter Changes:** ",
    if (length(param_changes) > 0) paste(param_changes, collapse = ", ")
    else "None detected", "\n", sep = "")

any_significant <- primary$optimal_changed ||
  primary$max_cost_change > 100 ||
  primary$max_effect_change > 0.01 ||
  primary$max_icer_change > 1000

cat("\n", if (any_significant) {
  "**Interpretation:** Changes exceed typical thresholds and should be carefully reviewed to ensure they align with the intended bug fix."
} else {
  "**Interpretation:** Changes are within expected bounds for bug fixes that improve numerical stability or code quality."
}, "\n", sep = "")
```

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 3.0
