---
title: "Bug Fix Impact Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
                      fig.align = "center", fig.width = 8, fig.height = 6,
                      dpi = 300, out.width = "100%")
knitr::opts_knit$set(root.dir = here::here())

source(here::here("scripts/R/functions/report_setup.R"))
setup_report(
  sources = c("02", "03"),
  funs = c("snapshot_utils", "report_format"),
  packages = c("here", "knitr", "kableExtra", "dplyr", "ggplot2", "scales"),
  set_knitr = FALSE,
  set_theme = FALSE
)

snapshots_dir <- here::here("data", "output", "snapshots")
snapshot_files <- if (dir.exists(snapshots_dir)) {
  list.files(snapshots_dir, pattern = "^snapshot_.*\\.rds$", full.names = FALSE)
} else {
  character()
}

snapshot_info <- if (length(snapshot_files) > 0) {
  do.call(rbind, lapply(snapshot_files, parse_snapshot_filename)) %>%
    mutate(mtime = file.info(file.path(snapshots_dir, filename))$mtime) %>%
    arrange(issue, mtime)
} else {
  data.frame()
}

selected_issue <- if (nrow(snapshot_info) > 0) {
  tail(unique(snapshot_info$issue), 1)
} else {
  NA_character_
}

comparison_pair <- if (!is.na(selected_issue)) {
  tryCatch(select_snapshots_for_comparison(selected_issue, snapshots_dir),
           error = function(e) NULL)
} else {
  NULL
}

before_snapshot <- after_snapshot <- NULL
if (!is.null(comparison_pair)) {
  before_snapshot <- load_snapshot(comparison_pair$before$snapshot, snapshots_dir)
  after_snapshot <- load_snapshot(comparison_pair$after$snapshot, snapshots_dir)
}

```

# Snapshot Inventory

```{r inventory}
if (nrow(snapshot_info) == 0) {
  cat("No snapshot files were found in data/output/snapshots.")
} else {
  inventory <- snapshot_info %>%
    select(filename, issue, status, commit, mtime)

  knitr::kable(
    inventory,
    booktabs = TRUE,
    align = "l",
    caption = "Available single-model snapshots"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
}
```

# Selected Comparison

```{r selected}
if (is.null(comparison_pair)) {
  cat("No baseline/fixed or earliest/latest snapshot pair was available for comparison.")
} else {
  pair_df <- data.frame(
    Role = c("Before", "After"),
    Snapshot = c(comparison_pair$before$snapshot, comparison_pair$after$snapshot),
    PSA = c(comparison_pair$before$psa, comparison_pair$after$psa),
    stringsAsFactors = FALSE
  )

  knitr::kable(
    pair_df,
    booktabs = TRUE,
    align = c("l", "l", "l"),
    caption = paste0("Selected snapshot pair for issue \\#", selected_issue)
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
}
```

# Base Case Impact

```{r base-impact}
if (!is.null(before_snapshot) && !is.null(after_snapshot)) {
  before <- before_snapshot$base_results
  after <- after_snapshot$base_results

  impact <- before %>%
    select(Strategy, Cost_Before = Cost, Effect_Before = Effect) %>%
    inner_join(
      after %>% select(Strategy, Cost_After = Cost, Effect_After = Effect),
      by = "Strategy"
    ) %>%
    mutate(
      Cost_Change = Cost_After - Cost_Before,
      Effect_Change = Effect_After - Effect_Before,
      Strategy = strategy_label(Strategy),
      across(c(Cost_Before, Cost_After, Cost_Change), format_eur),
      across(c(Effect_Before, Effect_After, Effect_Change), ~ sprintf("%.4f", .x))
    )

  knitr::kable(
    impact,
    booktabs = TRUE,
    align = c("l", "r", "r", "r", "r", "r", "r"),
    col.names = c("Strategy", "Cost Before", "QALYs Before",
                  "Cost After", "QALYs After", "Cost Change", "QALY Change"),
    caption = "Base case impact by strategy"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position", "scale_down"))
}
```

```{r nmb-impact}
if (!is.null(before_snapshot) && !is.null(after_snapshot)) {
  before_nmb <- before_snapshot$nmb_at_wtp %>%
    select(Strategy, NMB_Before = NMB)
  after_nmb <- after_snapshot$nmb_at_wtp %>%
    select(Strategy, NMB_After = NMB)

  nmb_impact <- inner_join(before_nmb, after_nmb, by = "Strategy") %>%
    mutate(
      NMB_Change = NMB_After - NMB_Before,
      Strategy = strategy_label(Strategy),
      across(c(NMB_Before, NMB_After, NMB_Change), format_eur)
    )

  knitr::kable(
    nmb_impact,
    booktabs = TRUE,
    align = c("l", "r", "r", "r"),
    col.names = c("Strategy", "NMB Before", "NMB After", "NMB Change"),
    caption = "Net monetary benefit impact"
  ) %>%
    kableExtra::kable_styling(latex_options = c("HOLD_position"))
}
```

# Interpretation

This report expects the current single-model snapshot format produced by `scripts/R/analysis/13_save_snapshot.R`. If older snapshots contain obsolete multi-model components, `load_snapshot()` warns during render and the comparison table uses the top-level single-model results.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 4.0
