---
title: "Bug Fix Impact Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

<!--
SNAPSHOT SYSTEM OVERVIEW:

PURPOSE:
  Track the impact of bug fixes on cost-effectiveness analysis results by
  comparing baseline (before fix) and fixed (after fix) snapshots.

WORKFLOW:
  1. Before fixing bug: Rscript 15_save_snapshot.R <issue> baseline
  2. Fix the bug and commit changes
  3. After fixing bug:  Rscript 15_save_snapshot.R <issue> fixed
  4. Generate this report: quarto render bug_fix_impact.qmd

FILE NAMING:
  - snapshot_<issue>_baseline_<commit>.rds  (before fix)
  - snapshot_<issue>_fixed_<commit>.rds     (after fix)
  - psa_<issue>_baseline_<commit>.rds       (PSA before)
  - psa_<issue>_fixed_<commit>.rds          (PSA after)

REPORT BEHAVIOR:
  - Automatically finds the most recent baseline/fixed snapshot pair
  - Loads snapshots directly from data/output/snapshots/
  - Computes all comparisons on-the-fly (no intermediate files)
  - Shows detailed results including PSA scatter plots
-->

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "left",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  png, grid, dampack
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r load-snapshots}
# Find all snapshot files
snapshots_dir <- here::here("data", "output", "snapshots")
all_files <- list.files(snapshots_dir, pattern = "^snapshot_.*\\.rds$", full.names = TRUE)

if (length(all_files) == 0) {
  stop("No snapshot files found in data/output/snapshots/. Please run 15_save_snapshot.R first.")
}

# Extract issue numbers and status from filenames
file_info <- data.frame(
  path = all_files,
  filename = basename(all_files),
  stringsAsFactors = FALSE
)

# Parse filenames: snapshot_<issue>_<status>_<commit>.rds
file_info$issue <- gsub("snapshot_(\\d+)_.*", "\\1", file_info$filename)
file_info$status <- gsub("snapshot_\\d+_(baseline|fixed)_.*", "\\1", file_info$filename)
file_info$commit <- gsub("snapshot_\\d+_(baseline|fixed)_(.*)\\.rds", "\\2", file_info$filename)

# Identify all complete snapshot pairs (issues with both baseline and fixed)
all_issues <- unique(file_info$issue)
complete_pairs <- data.frame(
  Issue = character(),
  Baseline_Commit = character(),
  Fixed_Commit = character(),
  Baseline_File = character(),
  Fixed_File = character(),
  stringsAsFactors = FALSE
)

for (issue in all_issues) {
  baseline_exists <- any(file_info$issue == issue & file_info$status == "baseline")
  fixed_exists <- any(file_info$issue == issue & file_info$status == "fixed")

  if (baseline_exists && fixed_exists) {
    baseline_commit <- file_info$commit[file_info$issue == issue & file_info$status == "baseline"][1]
    fixed_commit <- file_info$commit[file_info$issue == issue & file_info$status == "fixed"][1]
    baseline_file <- file_info$path[file_info$issue == issue & file_info$status == "baseline"][1]
    fixed_file <- file_info$path[file_info$issue == issue & file_info$status == "fixed"][1]

    # Get timestamp from fixed snapshot file
    fixed_snap_temp <- readRDS(fixed_file)
    timestamp <- fixed_snap_temp$metadata$timestamp

    complete_pairs <- rbind(complete_pairs, data.frame(
      Issue = issue,
      Baseline_Commit = baseline_commit,
      Fixed_Commit = fixed_commit,
      Baseline_File = baseline_file,
      Fixed_File = fixed_file,
      Timestamp = timestamp,
      stringsAsFactors = FALSE
    ))
  }
}

# Sort by timestamp (most recent first)
complete_pairs <- complete_pairs[order(complete_pairs$Timestamp, decreasing = TRUE), ]

# Fetch issue titles from GitHub
complete_pairs$Issue_Title <- sapply(complete_pairs$Issue, function(issue_num) {
  tryCatch({
    # Use gh CLI to fetch issue title
    result <- system(paste0("gh issue view ", issue_num, " --json title --jq .title"),
                     intern = TRUE, ignore.stderr = TRUE)
    if (length(result) > 0 && result != "") {
      return(result[1])
    } else {
      return("")
    }
  }, error = function(e) {
    return("")
  })
})

if (nrow(complete_pairs) == 0) {
  stop("No complete snapshot pairs found. Each issue needs both baseline and fixed snapshots.")
}

# Get the most recent snapshot pair (first row, since sorted by timestamp descending)
latest_pair <- complete_pairs[1, ]
latest_issue <- latest_pair$Issue

# Load snapshots for the most recent issue
baseline_snapshot <- readRDS(latest_pair$Baseline_File)
fixed_snapshot <- readRDS(latest_pair$Fixed_File)

# Load PSA objects
baseline_psa_file <- gsub("snapshot_", "psa_", latest_pair$Baseline_File)
fixed_psa_file <- gsub("snapshot_", "psa_", latest_pair$Fixed_File)

baseline_psa <- readRDS(baseline_psa_file)
fixed_psa <- readRDS(fixed_psa_file)

# Extract metadata
issue_num <- latest_issue
before_meta <- baseline_snapshot$metadata
after_meta <- fixed_snapshot$metadata
```

# Summary

This report compares cost-effectiveness analysis results before and after addressing GitHub issue #`r issue_num`. The comparison assesses whether bug fixes or model changes affected results.

**Current Comparison:**

- **Issue:** #`r issue_num` - `r if(latest_pair$Issue_Title != "") latest_pair$Issue_Title else "No title available"`
- **Baseline:** Commit `r before_meta$git_commit` (`r before_meta$timestamp`)
- **Fixed:** Commit `r after_meta$git_commit` (`r after_meta$timestamp`)

\newpage

```{r compute-comparisons}
# Compare base case results
base_before <- baseline_snapshot$icer_obj
base_after <- fixed_snapshot$icer_obj

base_comp <- merge(
  base_before[, c("Strategy", "Cost", "Effect", "Inc_Cost", "Inc_Effect", "ICER")],
  base_after[, c("Strategy", "Cost", "Effect", "Inc_Cost", "Inc_Effect", "ICER")],
  by = "Strategy",
  suffixes = c("_before", "_after")
)

base_comp$Cost_diff <- base_comp$Cost_after - base_comp$Cost_before
base_comp$Effect_diff <- base_comp$Effect_after - base_comp$Effect_before
base_comp$Cost_pct_change <- (base_comp$Cost_diff / base_comp$Cost_before) * 100
base_comp$Effect_pct_change <- (base_comp$Effect_diff / base_comp$Effect_before) * 100
base_comp$ICER_diff <- ifelse(
  is.na(base_comp$ICER_before) | is.na(base_comp$ICER_after),
  NA,
  base_comp$ICER_after - base_comp$ICER_before
)

# Compare NMB
nmb_before <- baseline_snapshot$nmb_at_wtp
nmb_after <- fixed_snapshot$nmb_at_wtp

nmb_comp <- merge(
  nmb_before[, c("Strategy", "NMB")],
  nmb_after[, c("Strategy", "NMB")],
  by = "Strategy",
  suffixes = c("_before", "_after")
)
nmb_comp$NMB_diff <- nmb_comp$NMB_after - nmb_comp$NMB_before
nmb_comp <- nmb_comp[order(-nmb_comp$NMB_after), ]

optimal_before <- nmb_before$Strategy[which.max(nmb_before$NMB)]
optimal_after <- nmb_after$Strategy[which.max(nmb_after$NMB)]

# Compare PSA
psa_before <- baseline_snapshot$psa_summary
psa_after <- fixed_snapshot$psa_summary

psa_comp <- merge(
  psa_before,
  psa_after,
  by = "Strategy",
  suffixes = c("_before", "_after")
)
psa_comp$meanCost_diff <- psa_comp$meanCost_after - psa_comp$meanCost_before
psa_comp$meanEffect_diff <- psa_comp$meanEffect_after - psa_comp$meanEffect_before

# Check for parameter changes
param_names <- names(before_meta$parameters)
param_changes <- c()
for (param in param_names) {
  before_val <- before_meta$parameters[[param]]
  after_val <- after_meta$parameters[[param]]
  if (!identical(before_val, after_val)) {
    param_changes <- c(param_changes, param)
  }
}

# Calculate significance thresholds
max_cost_change <- max(abs(base_comp$Cost_diff), na.rm = TRUE)
max_effect_change <- max(abs(base_comp$Effect_diff), na.rm = TRUE)
max_icer_change <- max(abs(base_comp$ICER_diff), na.rm = TRUE)

optimal_changed <- optimal_before != optimal_after
cost_significant <- max_cost_change > 100
effect_significant <- max_effect_change > 0.01
icer_significant <- max_icer_change > 1000
```

\newpage

# Metadata Comparison

```{r metadata-table}
metadata_comp <- data.frame(
  Item = c("Git Commit", "Timestamp", "R Version", "Issue Number"),
  Baseline = c(
    before_meta$git_commit,
    before_meta$timestamp,
    before_meta$r_version,
    before_meta$issue_number
  ),
  Fixed = c(
    after_meta$git_commit,
    after_meta$timestamp,
    after_meta$r_version,
    after_meta$issue_number
  )
)

kable(metadata_comp,
      caption = "Metadata Comparison",
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

## Global Parameters

```{r parameters-table}
param_comp <- data.frame(
  Parameter = param_names,
  Baseline = sapply(param_names, function(p) {
    val <- before_meta$parameters[[p]]
    if (is.na(val)) return("NA")
    if (is.numeric(val)) return(format(val, scientific = FALSE, big.mark = ","))
    return(as.character(val))
  }),
  Fixed = sapply(param_names, function(p) {
    val <- after_meta$parameters[[p]]
    if (is.na(val)) return("NA")
    if (is.numeric(val)) return(format(val, scientific = FALSE, big.mark = ","))
    return(as.character(val))
  }),
  stringsAsFactors = FALSE
)

param_comp$Changed <- ifelse(param_comp$Baseline != param_comp$Fixed, "Yes", "No")

kable(param_comp,
      caption = "Global Parameter Comparison",
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down")) %>%
  row_spec(which(param_comp$Changed == "Yes"), bold = TRUE, color = "red")
```

\newpage

# Base Case Results Comparison

```{r base-case-incremental-setup}
# Calculate incremental values relative to control for ALL strategies
# (dampack's Inc_Cost/Inc_Effect are NA for reference and dominated strategies)
control_cost_before <- base_comp$Cost_before[base_comp$Strategy == "control"]
control_cost_after <- base_comp$Cost_after[base_comp$Strategy == "control"]
control_effect_before <- base_comp$Effect_before[base_comp$Strategy == "control"]
control_effect_after <- base_comp$Effect_after[base_comp$Strategy == "control"]

base_incremental <- base_comp %>%
  mutate(
    # Calculate incremental values vs control for all strategies
    Calc_Inc_Cost_before = Cost_before - control_cost_before,
    Calc_Inc_Cost_after = Cost_after - control_cost_after,
    Calc_Inc_Effect_before = Effect_before - control_effect_before,
    Calc_Inc_Effect_after = Effect_after - control_effect_after
  )
```

```{r base-case-incremental-cost-table}
# Table 3a: Incremental Cost Comparison
cost_display <- base_incremental %>%
  mutate(
    Cost_diff = Calc_Inc_Cost_after - Calc_Inc_Cost_before
  ) %>%
  select(Strategy, Calc_Inc_Cost_before, Calc_Inc_Cost_after, Cost_diff) %>%
  mutate(
    Calc_Inc_Cost_before = format(round(Calc_Inc_Cost_before, 2), big.mark = ",", nsmall = 2),
    Calc_Inc_Cost_after = format(round(Calc_Inc_Cost_after, 2), big.mark = ",", nsmall = 2),
    Cost_diff = format(round(Cost_diff, 2), big.mark = ",", nsmall = 2)
  )

kable(cost_display,
      caption = "Base Case Incremental Cost Comparison",
      col.names = c("Strategy", "Baseline (€)", "Fixed (€)", "Difference (€)"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

\vspace{0.5em}

```{r base-case-incremental-effect-table}
# Table 3b: Incremental Effect Comparison
effect_display <- base_incremental %>%
  mutate(
    Effect_diff = Calc_Inc_Effect_after - Calc_Inc_Effect_before
  ) %>%
  select(Strategy, Calc_Inc_Effect_before, Calc_Inc_Effect_after, Effect_diff) %>%
  mutate(
    Calc_Inc_Effect_before = format(round(Calc_Inc_Effect_before, 4), nsmall = 4),
    Calc_Inc_Effect_after = format(round(Calc_Inc_Effect_after, 4), nsmall = 4),
    Effect_diff = format(round(Effect_diff, 4), nsmall = 4)
  )

kable(effect_display,
      caption = "Base Case Incremental Effect Comparison",
      col.names = c("Strategy", "Baseline (QALYs)", "Fixed (QALYs)", "Difference (QALYs)"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

\vspace{0.5em}

```{r base-case-icer-table}
# Table 3c: ICER Comparison
icer_display <- base_incremental %>%
  select(Strategy, ICER_before, ICER_after) %>%
  mutate(
    ICER_diff = ICER_after - ICER_before,
    ICER_before = ifelse(is.na(ICER_before), "—", format(round(ICER_before, 0), big.mark = ",")),
    ICER_after = ifelse(is.na(ICER_after), "—", format(round(ICER_after, 0), big.mark = ",")),
    ICER_diff = ifelse(is.na(ICER_diff), "—", format(round(ICER_diff, 0), big.mark = ","))
  )

kable(icer_display,
      caption = "Base Case ICER Comparison",
      col.names = c("Strategy", "Baseline (€/QALY)", "Fixed (€/QALY)", "Difference (€/QALY)"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

## Efficiency Frontier Comparison

```{r efficiency-frontier, fig.cap="Cost-effectiveness efficiency frontier comparison using dampack. Baseline (top) and fixed (bottom) strategies are shown with the efficiency frontier connecting non-dominated strategies. Dominated strategies appear off the frontier line.", out.width="100%", fig.height=9}
# Create ICER objects for baseline and fixed using dampack
baseline_icer <- dampack::calculate_icers(
  cost = base_before$Cost,
  effect = base_before$Effect,
  strategies = base_before$Strategy
)

fixed_icer <- dampack::calculate_icers(
  cost = base_after$Cost,
  effect = base_after$Effect,
  strategies = base_after$Strategy
)

# Create plots using dampack's plot method
plot_baseline_frontier <- plot(baseline_icer,
                                txtsize = 10,
                                currency = "€",
                                effect_units = "QALYs",
                                label = "all") +
  labs(title = "Baseline") +
  theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5))

plot_fixed_frontier <- plot(fixed_icer,
                              txtsize = 10,
                              currency = "€",
                              effect_units = "QALYs",
                              label = "all") +
  labs(title = "Fixed") +
  theme(plot.title = element_text(size = 12, face = "bold", hjust = 0.5))

# Arrange vertically (one below the other)
gridExtra::grid.arrange(plot_baseline_frontier, plot_fixed_frontier, nrow = 2)
```

## Net Monetary Benefit Comparison

```{r nmb-table}
nmb_display <- nmb_comp %>%
  mutate(
    NMB_before = format(round(NMB_before, 2), big.mark = ",", nsmall = 2),
    NMB_after = format(round(NMB_after, 2), big.mark = ",", nsmall = 2),
    NMB_diff = format(round(NMB_diff, 2), big.mark = ",", nsmall = 2)
  )

kable(nmb_display,
      caption = paste0("Net Monetary Benefit Comparison at WTP = €",
                      format(before_meta$parameters$WTP, big.mark = ",")),
      col.names = c("Strategy", "Baseline (€)", "Fixed (€)", "Difference (€)"),
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  row_spec(1, bold = TRUE, background = "#E8F4F8")
```

**Optimal Strategy:** `r if(optimal_changed) paste0("**Changed** from ", optimal_before, " to ", optimal_after) else paste0("Unchanged (", optimal_after, ")")`

\newpage

# PSA Results Comparison

```{r psa-cost-table}
psa_cost_display <- psa_comp %>%
  select(Strategy,
         meanCost_before, Cost_2.5_percent_before, Cost_97.5_percent_before,
         meanCost_after, Cost_2.5_percent_after, Cost_97.5_percent_after,
         meanCost_diff) %>%
  mutate(
    Baseline_Cost = sprintf("€%s (€%s; €%s)",
                           format(round(meanCost_before, 2), big.mark = ",", nsmall = 2),
                           format(round(Cost_2.5_percent_before, 2), big.mark = ",", nsmall = 2),
                           format(round(Cost_97.5_percent_before, 2), big.mark = ",", nsmall = 2)),
    Fixed_Cost = sprintf("€%s (€%s; €%s)",
                        format(round(meanCost_after, 2), big.mark = ",", nsmall = 2),
                        format(round(Cost_2.5_percent_after, 2), big.mark = ",", nsmall = 2),
                        format(round(Cost_97.5_percent_after, 2), big.mark = ",", nsmall = 2)),
    Difference = format(round(meanCost_diff, 2), big.mark = ",", nsmall = 2)
  ) %>%
  select(Strategy, Baseline_Cost, Fixed_Cost, Difference)

kable(psa_cost_display,
      caption = paste0("PSA Cost Results (n = ",
                      format(before_meta$parameters$n_sim, big.mark = ","), " simulations)"),
      col.names = c("Strategy", "Baseline Mean (2.5%; 97.5%)", "Fixed Mean (2.5%; 97.5%)", "Difference (€)"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

\vspace{0.5em}

```{r psa-effect-table}
psa_effect_display <- psa_comp %>%
  select(Strategy,
         meanEffect_before, Effect_2.5_percent_before, Effect_97.5_percent_before,
         meanEffect_after, Effect_2.5_percent_after, Effect_97.5_percent_after,
         meanEffect_diff) %>%
  mutate(
    Baseline_Effect = sprintf("%.4f (%.4f; %.4f)",
                             meanEffect_before,
                             Effect_2.5_percent_before,
                             Effect_97.5_percent_before),
    Fixed_Effect = sprintf("%.4f (%.4f; %.4f)",
                          meanEffect_after,
                          Effect_2.5_percent_after,
                          Effect_97.5_percent_after),
    Difference = sprintf("%.4f", meanEffect_diff)
  ) %>%
  select(Strategy, Baseline_Effect, Fixed_Effect, Difference)

kable(psa_effect_display,
      caption = paste0("PSA Effects Results (n = ",
                      format(before_meta$parameters$n_sim, big.mark = ","), " simulations)"),
      col.names = c("Strategy", "Baseline Mean (2.5%; 97.5%)", "Fixed Mean (2.5%; 97.5%)", "Difference (QALYs)"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

\vspace{0.5em}

```{r psa-icer-table}
# Calculate ICERs from PSA means as point estimates
# Note: This is an approximation; ideally would calculate from iteration-level data
psa_icer_display <- psa_comp %>%
  select(Strategy, meanCost_before, meanEffect_before, meanCost_after, meanEffect_after) %>%
  # Assume first strategy is reference (control)
  mutate(
    # For baseline
    inc_cost_bl = meanCost_before - meanCost_before[1],
    inc_effect_bl = meanEffect_before - meanEffect_before[1],
    icer_bl = ifelse(inc_effect_bl > 0.0001, inc_cost_bl / inc_effect_bl, NA),
    # For fixed
    inc_cost_fx = meanCost_after - meanCost_after[1],
    inc_effect_fx = meanEffect_after - meanEffect_after[1],
    icer_fx = ifelse(inc_effect_fx > 0.0001, inc_cost_fx / inc_effect_fx, NA)
  ) %>%
  mutate(
    Baseline_ICER = ifelse(is.na(icer_bl), "—",
                           sprintf("€%s/QALY", format(round(icer_bl, 0), big.mark = ","))),
    Fixed_ICER = ifelse(is.na(icer_fx), "—",
                       sprintf("€%s/QALY", format(round(icer_fx, 0), big.mark = ",")))
  ) %>%
  select(Strategy, Baseline_ICER, Fixed_ICER)

kable(psa_icer_display,
      caption = paste0("PSA ICER Results (n = ",
                      format(before_meta$parameters$n_sim, big.mark = ","), " simulations)"),
      col.names = c("Strategy", "Baseline Mean ICER", "Fixed Mean ICER"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", "r", "r")) %>%
  kable_styling(latex_options = c("striped", "hold_position"), font_size = 10)
```

*Note: ICERs calculated from PSA mean costs and effects as point estimates.*

## PSA Visual Analysis

### PSA Scatter Plots (Side-by-Side)

```{r psa-sidebyside, fig.cap="Cost-effectiveness plane showing PSA simulations baseline (left) and fixed (right)", out.width="100%", fig.height=5}
# Extract PSA data
baseline_psa_data <- data.frame(
  Strategy = rep(baseline_psa$strategies, each = baseline_psa$n_sim),
  Cost = as.vector(as.matrix(baseline_psa$cost)),
  Effect = as.vector(as.matrix(baseline_psa$effectiveness)),
  Snapshot = "Baseline"
)

fixed_psa_data <- data.frame(
  Strategy = rep(fixed_psa$strategies, each = fixed_psa$n_sim),
  Cost = as.vector(as.matrix(fixed_psa$cost)),
  Effect = as.vector(as.matrix(fixed_psa$effectiveness)),
  Snapshot = "Fixed"
)

# Create side-by-side plots
plot_baseline <- ggplot(baseline_psa_data, aes(x = Effect, y = Cost, color = Strategy)) +
  geom_point(alpha = 0.4, size = 2.5) +
  labs(title = "Baseline", x = "Effect (QALYs)", y = "Cost (€)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 9),
        axis.title = element_text(size = 10))

plot_fixed <- ggplot(fixed_psa_data, aes(x = Effect, y = Cost, color = Strategy)) +
  geom_point(alpha = 0.4, size = 2.5) +
  labs(title = "Fixed", x = "Effect (QALYs)", y = "Cost (€)") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.text = element_text(size = 9),
        axis.title = element_text(size = 10))

gridExtra::grid.arrange(plot_baseline, plot_fixed, ncol = 2)
```

### PSA Scatter Plots (Overlaid)

```{r psa-overlaid, fig.cap="Overlaid cost-effectiveness plane comparing baseline and fixed PSA simulations. This plot overlays all PSA simulation results from both snapshots on a single plane, where each point represents one PSA iteration for a given strategy. Hollow circles indicate baseline simulations, while filled circles indicate fixed simulations. Colors distinguish strategies, while shapes distinguish snapshots. The overlay allows direct visual comparison of how the probabilistic distributions changed after the bug fix: if the fix was purely methodological with no impact on central estimates, baseline and fixed points would overlap completely, whereas systematic shifts in the point clouds indicate changes in underlying model behavior.", out.width="85%", fig.height=6}
# Combine data
combined_psa_data <- rbind(baseline_psa_data, fixed_psa_data)

ggplot(combined_psa_data, aes(x = Effect, y = Cost, color = Strategy, shape = Snapshot)) +
  geom_point(alpha = 0.3, size = 3) +
  scale_shape_manual(values = c("Baseline" = 21, "Fixed" = 16),
                     name = "Snapshot",
                     labels = c("Baseline (hollow)", "Fixed (filled)")) +
  labs(title = "Baseline vs Fixed Comparison",
       x = "Effect (QALYs)",
       y = "Cost (€)",
       color = "Strategy") +
  theme_minimal() +
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.text = element_text(size = 9),
        axis.title = element_text(size = 10))
```

\newpage

# Comparison Across Recent Issues

## Available Snapshot Pairs

```{r available-snapshots-table}
if (nrow(complete_pairs) > 0) {
  pairs_display <- complete_pairs %>%
    select(Issue, Issue_Title, Baseline_Commit, Fixed_Commit) %>%
    mutate(
      Issue_Title = ifelse(Issue_Title == "", "—", Issue_Title)
    )

  # Find which row is the current issue (before any formatting)
  current_row <- which(pairs_display$Issue == issue_num)

  kable(pairs_display,
        caption = "All Available Snapshot Pairs",
        col.names = c("Issue", "Title", "Baseline Commit", "Fixed Commit"),
        booktabs = TRUE,
        format = "latex",
        align = c("l", "l", "l", "l")) %>%
    kable_styling(latex_options = c("striped", "HOLD_position"), font_size = 10) %>%
    column_spec(1, width = "1cm") %>%
    column_spec(2, width = "6cm") %>%
    column_spec(c(3, 4), width = "2.5cm") %>%
    row_spec(current_row, bold = TRUE, background = "#E8F4F8")
} else {
  cat("No snapshot pairs available.\n")
}
```

## Multi-Issue Impact Summary

```{r multi-issue-comparison, results='asis'}
# Compare across multiple recent issues if available
n_issues_available <- nrow(complete_pairs)

if (n_issues_available >= 2) {
  cat("This table summarizes the impact of bug fixes across the most recent issues:\n\n")

  # Get up to 5 most recent issues (already sorted by timestamp descending)
  n_to_compare <- min(5, n_issues_available)
  recent_issues <- head(complete_pairs, n_to_compare)

  # Build comparison table
  multi_comp <- data.frame(
    Issue = character(),
    Issue_Title = character(),
    Optimal_Baseline = character(),
    Optimal_Fixed = character(),
    Changed = character(),
    Max_Cost_Change = numeric(),
    Max_Effect_Change = numeric(),
    Max_ICER_Change = numeric(),
    stringsAsFactors = FALSE
  )

  for (i in 1:nrow(recent_issues)) {
    issue_row <- recent_issues[i, ]

    # Load snapshots
    snap_base <- readRDS(issue_row$Baseline_File)
    snap_fixed <- readRDS(issue_row$Fixed_File)

    # Compare
    base_comp_temp <- merge(
      snap_base$icer_obj[, c("Strategy", "Cost", "Effect", "ICER")],
      snap_fixed$icer_obj[, c("Strategy", "Cost", "Effect", "ICER")],
      by = "Strategy",
      suffixes = c("_before", "_after")
    )

    base_comp_temp$Cost_diff <- base_comp_temp$Cost_after - base_comp_temp$Cost_before
    base_comp_temp$Effect_diff <- base_comp_temp$Effect_after - base_comp_temp$Effect_before
    base_comp_temp$ICER_diff <- ifelse(
      is.na(base_comp_temp$ICER_before) | is.na(base_comp_temp$ICER_after),
      NA,
      base_comp_temp$ICER_after - base_comp_temp$ICER_before
    )

    nmb_base <- snap_base$nmb_at_wtp
    nmb_fixed <- snap_fixed$nmb_at_wtp
    opt_base <- nmb_base$Strategy[which.max(nmb_base$NMB)]
    opt_fixed <- nmb_fixed$Strategy[which.max(nmb_fixed$NMB)]

    multi_comp <- rbind(multi_comp, data.frame(
      Issue = issue_row$Issue,
      Issue_Title = ifelse(issue_row$Issue_Title == "", "—", issue_row$Issue_Title),
      Optimal_Baseline = opt_base,
      Optimal_Fixed = opt_fixed,
      Changed = ifelse(opt_base != opt_fixed, "Yes", "No"),
      Max_Cost_Change = max(abs(base_comp_temp$Cost_diff), na.rm = TRUE),
      Max_Effect_Change = max(abs(base_comp_temp$Effect_diff), na.rm = TRUE),
      Max_ICER_Change = max(abs(base_comp_temp$ICER_diff), na.rm = TRUE),
      stringsAsFactors = FALSE
    ))
  }

  # Find which row is the current issue
  current_row <- which(multi_comp$Issue == issue_num)

  # Format for display
  multi_comp_display <- multi_comp %>%
    mutate(
      Max_Cost_Change = format(round(Max_Cost_Change, 2), big.mark = ",", nsmall = 2),
      Max_Effect_Change = format(round(Max_Effect_Change, 4), nsmall = 4),
      Max_ICER_Change = format(round(Max_ICER_Change, 0), big.mark = ",")
    )

  print(kable(multi_comp_display,
        caption = paste0("Summary of Bug Fix Impacts (", n_to_compare, " Most Recent Issues)"),
        col.names = c("Issue", "Title", "Opt. (BL)", "Opt. (Fix)", "Chg?",
                      "Max Cost Δ (€)", "Max Effect Δ (QALYs)", "Max ICER Δ (€/QALY)"),
        booktabs = TRUE,
        format = "latex",
        align = c("l", "l", "l", "l", "c", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"), font_size = 8) %>%
    column_spec(2, width = "4cm") %>%
    column_spec(c(1, 5), width = "0.8cm") %>%
    column_spec(c(3, 4), width = "2cm") %>%
    column_spec(c(6, 7, 8), width = "1.8cm") %>%
    row_spec(current_row, bold = TRUE, background = "#E8F4F8"))
}
```

\newpage

# Summary

The comparison for issue #`r issue_num` shows:

- **Optimal Strategy:** `r if(optimal_changed) paste0("Changed from ", optimal_before, " to ", optimal_after) else paste0("Unchanged (", optimal_after, ")")`
- **Maximum Cost Change:** €`r format(round(max_cost_change, 2), big.mark = ",", nsmall = 2)` (`r if(cost_significant) "substantial" else "minor"`)
- **Maximum Effect Change:** `r format(round(max_effect_change, 3), nsmall = 3)` QALYs (`r if(effect_significant) "substantial" else "minor"`)
- **Maximum ICER Change:** €`r format(round(max_icer_change, 0), big.mark = ",")`/QALY (`r if(icer_significant) "substantial" else "minor"`)
- **Parameter Changes:** `r if(length(param_changes) > 0) paste(param_changes, collapse = ", ") else "None detected"`

`r if(optimal_changed || cost_significant || effect_significant || icer_significant) "**Interpretation:** Changes exceed typical thresholds and should be carefully reviewed to ensure they align with the intended bug fix." else "**Interpretation:** Changes are within expected bounds for bug fixes that improve numerical stability or code quality."`

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 2.0