---
title: "Bug Fix Impact Analysis"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

<!--
SNAPSHOT SYSTEM OVERVIEW:

PURPOSE:
  Track the impact of bug fixes on cost-effectiveness analysis results by
  comparing baseline (before fix) and fixed (after fix) snapshots.

WORKFLOW:
  1. Before fixing bug: Rscript 15_save_snapshot.R <issue> baseline
  2. Fix the bug and commit changes
  3. After fixing bug:  Rscript 15_save_snapshot.R <issue> fixed
  4. Generate this report: quarto render bug_fix_impact.qmd

FILE NAMING:
  - snapshot_<issue>_baseline_<commit>.rds  (before fix)
  - snapshot_<issue>_fixed_<commit>.rds     (after fix)
  - psa_<issue>_baseline_<commit>.rds       (PSA before)
  - psa_<issue>_fixed_<commit>.rds          (PSA after)

REPORT BEHAVIOR:
  - Automatically finds the most recent baseline/fixed snapshot pair
  - Loads snapshots directly from data/output/snapshots/
  - Computes all comparisons on-the-fly (no intermediate files)
  - Shows detailed results including PSA scatter plots
-->

```{r setup, include=FALSE}
# Set global knitr options
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  fig.align = "left",
  fig.width = 8,
  fig.height = 6,
  dpi = 300,
  out.width = "100%"
)

# Set working directory to project root
knitr::opts_knit$set(root.dir = here::here())

# Load required libraries
if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  here, knitr, kableExtra, ggplot2, dplyr,
  flextable, officer, scales, gridExtra,
  png, grid
)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    plot.title = element_text(size = 14, face = "bold"),
    plot.subtitle = element_text(size = 12),
    axis.title = element_text(size = 11),
    axis.text = element_text(size = 10),
    legend.title = element_text(size = 11),
    legend.text = element_text(size = 10),
    strip.text = element_text(size = 11, face = "bold")
  ))
```

```{r load-snapshots}
# Find all snapshot files
snapshots_dir <- here::here("data", "output", "snapshots")
all_files <- list.files(snapshots_dir, pattern = "^snapshot_.*\\.rds$", full.names = TRUE)

if (length(all_files) == 0) {
  stop("No snapshot files found in data/output/snapshots/. Please run 15_save_snapshot.R first.")
}

# Extract issue numbers and status from filenames
file_info <- data.frame(
  path = all_files,
  filename = basename(all_files),
  stringsAsFactors = FALSE
)

# Parse filenames: snapshot_<issue>_<status>_<commit>.rds
file_info$issue <- gsub("snapshot_(\\d+)_.*", "\\1", file_info$filename)
file_info$status <- gsub("snapshot_\\d+_(baseline|fixed)_.*", "\\1", file_info$filename)
file_info$commit <- gsub("snapshot_\\d+_(baseline|fixed)_(.*)\\.rds", "\\2", file_info$filename)

# Identify all complete snapshot pairs (issues with both baseline and fixed)
all_issues <- unique(file_info$issue)
complete_pairs <- data.frame(
  Issue = character(),
  Baseline_Commit = character(),
  Fixed_Commit = character(),
  Baseline_File = character(),
  Fixed_File = character(),
  stringsAsFactors = FALSE
)

for (issue in all_issues) {
  baseline_exists <- any(file_info$issue == issue & file_info$status == "baseline")
  fixed_exists <- any(file_info$issue == issue & file_info$status == "fixed")

  if (baseline_exists && fixed_exists) {
    baseline_commit <- file_info$commit[file_info$issue == issue & file_info$status == "baseline"][1]
    fixed_commit <- file_info$commit[file_info$issue == issue & file_info$status == "fixed"][1]
    baseline_file <- file_info$path[file_info$issue == issue & file_info$status == "baseline"][1]
    fixed_file <- file_info$path[file_info$issue == issue & file_info$status == "fixed"][1]

    # Get timestamp from fixed snapshot file
    fixed_snap_temp <- readRDS(fixed_file)
    timestamp <- fixed_snap_temp$metadata$timestamp

    complete_pairs <- rbind(complete_pairs, data.frame(
      Issue = issue,
      Baseline_Commit = baseline_commit,
      Fixed_Commit = fixed_commit,
      Baseline_File = baseline_file,
      Fixed_File = fixed_file,
      Timestamp = timestamp,
      stringsAsFactors = FALSE
    ))
  }
}

# Sort by timestamp (most recent first)
complete_pairs <- complete_pairs[order(complete_pairs$Timestamp, decreasing = TRUE), ]

# Fetch issue titles from GitHub
complete_pairs$Issue_Title <- sapply(complete_pairs$Issue, function(issue_num) {
  tryCatch({
    # Use gh CLI to fetch issue title
    result <- system(paste0("gh issue view ", issue_num, " --json title --jq .title"),
                     intern = TRUE, ignore.stderr = TRUE)
    if (length(result) > 0 && result != "") {
      return(result[1])
    } else {
      return("")
    }
  }, error = function(e) {
    return("")
  })
})

if (nrow(complete_pairs) == 0) {
  stop("No complete snapshot pairs found. Each issue needs both baseline and fixed snapshots.")
}

# Get the most recent snapshot pair (first row, since sorted by timestamp descending)
latest_pair <- complete_pairs[1, ]
latest_issue <- latest_pair$Issue

# Load snapshots for the most recent issue
baseline_snapshot <- readRDS(latest_pair$Baseline_File)
fixed_snapshot <- readRDS(latest_pair$Fixed_File)

# Load PSA objects
baseline_psa_file <- gsub("snapshot_", "psa_", latest_pair$Baseline_File)
fixed_psa_file <- gsub("snapshot_", "psa_", latest_pair$Fixed_File)

baseline_psa <- readRDS(baseline_psa_file)
fixed_psa <- readRDS(fixed_psa_file)

# Extract metadata
issue_num <- latest_issue
before_meta <- baseline_snapshot$metadata
after_meta <- fixed_snapshot$metadata
```

# Summary

This report compares cost-effectiveness analysis results before and after addressing GitHub issue #`r issue_num`. The comparison assesses whether bug fixes or model changes affected results.

**Current Comparison:**

- **Issue:** #`r issue_num`
- **Baseline:** Commit `r before_meta$git_commit` (`r before_meta$timestamp`)
- **Fixed:** Commit `r after_meta$git_commit` (`r after_meta$timestamp`)

## Available Snapshot Pairs

```{r available-snapshots-table}
if (nrow(complete_pairs) > 0) {
  pairs_display <- complete_pairs %>%
    select(Issue, Issue_Title, Baseline_Commit, Fixed_Commit) %>%
    mutate(
      Issue = paste0("#", Issue),
      Issue_Title = ifelse(Issue_Title == "", "—", Issue_Title),
      Status = ifelse(Issue == paste0("#", issue_num), "Current", "")
    )

  kable(pairs_display,
        caption = "All Available Snapshot Pairs",
        col.names = c("Issue", "Title", "Baseline Commit", "Fixed Commit", "Status"),
        booktabs = TRUE,
        format = "latex",
        align = c("l", "l", "l", "l", "c")) %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"), font_size = 9) %>%
    row_spec(which(pairs_display$Status == "Current"), bold = TRUE, background = "#E8F4F8")
} else {
  cat("No snapshot pairs available.\n")
}
```

\newpage

```{r compute-comparisons}
# Compare base case results
base_before <- baseline_snapshot$icer_obj
base_after <- fixed_snapshot$icer_obj

base_comp <- merge(
  base_before[, c("Strategy", "Cost", "Effect", "Inc_Cost", "Inc_Effect", "ICER")],
  base_after[, c("Strategy", "Cost", "Effect", "Inc_Cost", "Inc_Effect", "ICER")],
  by = "Strategy",
  suffixes = c("_before", "_after")
)

base_comp$Cost_diff <- base_comp$Cost_after - base_comp$Cost_before
base_comp$Effect_diff <- base_comp$Effect_after - base_comp$Effect_before
base_comp$Cost_pct_change <- (base_comp$Cost_diff / base_comp$Cost_before) * 100
base_comp$Effect_pct_change <- (base_comp$Effect_diff / base_comp$Effect_before) * 100
base_comp$ICER_diff <- ifelse(
  is.na(base_comp$ICER_before) | is.na(base_comp$ICER_after),
  NA,
  base_comp$ICER_after - base_comp$ICER_before
)

# Compare NMB
nmb_before <- baseline_snapshot$nmb_at_wtp
nmb_after <- fixed_snapshot$nmb_at_wtp

nmb_comp <- merge(
  nmb_before[, c("Strategy", "NMB")],
  nmb_after[, c("Strategy", "NMB")],
  by = "Strategy",
  suffixes = c("_before", "_after")
)
nmb_comp$NMB_diff <- nmb_comp$NMB_after - nmb_comp$NMB_before
nmb_comp <- nmb_comp[order(-nmb_comp$NMB_after), ]

optimal_before <- nmb_before$Strategy[which.max(nmb_before$NMB)]
optimal_after <- nmb_after$Strategy[which.max(nmb_after$NMB)]

# Compare PSA
psa_before <- baseline_snapshot$psa_summary
psa_after <- fixed_snapshot$psa_summary

psa_comp <- merge(
  psa_before,
  psa_after,
  by = "Strategy",
  suffixes = c("_before", "_after")
)
psa_comp$meanCost_diff <- psa_comp$meanCost_after - psa_comp$meanCost_before
psa_comp$meanEffect_diff <- psa_comp$meanEffect_after - psa_comp$meanEffect_before

# Check for parameter changes
param_names <- names(before_meta$parameters)
param_changes <- c()
for (param in param_names) {
  before_val <- before_meta$parameters[[param]]
  after_val <- after_meta$parameters[[param]]
  if (!identical(before_val, after_val)) {
    param_changes <- c(param_changes, param)
  }
}

# Calculate significance thresholds
max_cost_change <- max(abs(base_comp$Cost_diff), na.rm = TRUE)
max_effect_change <- max(abs(base_comp$Effect_diff), na.rm = TRUE)
max_icer_change <- max(abs(base_comp$ICER_diff), na.rm = TRUE)

optimal_changed <- optimal_before != optimal_after
cost_significant <- max_cost_change > 100
effect_significant <- max_effect_change > 0.01
icer_significant <- max_icer_change > 1000
```

\newpage

# Metadata Comparison

```{r metadata-table}
metadata_comp <- data.frame(
  Item = c("Git Commit", "Timestamp", "R Version", "Issue Number"),
  Baseline = c(
    before_meta$git_commit,
    before_meta$timestamp,
    before_meta$r_version,
    before_meta$issue_number
  ),
  Fixed = c(
    after_meta$git_commit,
    after_meta$timestamp,
    after_meta$r_version,
    after_meta$issue_number
  )
)

kable(metadata_comp,
      caption = "Metadata Comparison",
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position"))
```

## Global Parameters

```{r parameters-table}
param_comp <- data.frame(
  Parameter = param_names,
  Baseline = sapply(param_names, function(p) {
    val <- before_meta$parameters[[p]]
    if (is.na(val)) return("NA")
    if (is.numeric(val)) return(format(val, scientific = FALSE, big.mark = ","))
    return(as.character(val))
  }),
  Fixed = sapply(param_names, function(p) {
    val <- after_meta$parameters[[p]]
    if (is.na(val)) return("NA")
    if (is.numeric(val)) return(format(val, scientific = FALSE, big.mark = ","))
    return(as.character(val))
  }),
  stringsAsFactors = FALSE
)

param_comp$Changed <- ifelse(param_comp$Baseline != param_comp$Fixed, "Yes", "No")

kable(param_comp,
      caption = "Global Parameter Comparison",
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down")) %>%
  row_spec(which(param_comp$Changed == "Yes"), bold = TRUE, color = "red")
```

\newpage

# Base Case Results Comparison

```{r base-case-table}
base_display <- base_comp %>%
  select(Strategy,
         Cost_before, Cost_after, Cost_diff, Cost_pct_change,
         Effect_before, Effect_after, Effect_diff, Effect_pct_change,
         ICER_before, ICER_after, ICER_diff) %>%
  mutate(
    Cost_before = format(round(Cost_before, 2), big.mark = ",", nsmall = 2),
    Cost_after = format(round(Cost_after, 2), big.mark = ",", nsmall = 2),
    Cost_diff = format(round(Cost_diff, 2), big.mark = ",", nsmall = 2),
    Cost_pct_change = format(round(Cost_pct_change, 2), nsmall = 2),
    Effect_before = format(round(Effect_before, 4), nsmall = 4),
    Effect_after = format(round(Effect_after, 4), nsmall = 4),
    Effect_diff = format(round(Effect_diff, 4), nsmall = 4),
    Effect_pct_change = format(round(Effect_pct_change, 2), nsmall = 2),
    ICER_before = ifelse(is.na(ICER_before), "—", format(round(ICER_before, 0), big.mark = ",")),
    ICER_after = ifelse(is.na(ICER_after), "—", format(round(ICER_after, 0), big.mark = ",")),
    ICER_diff = ifelse(is.na(ICER_diff), "—", format(round(ICER_diff, 0), big.mark = ","))
  )

kable(base_display,
      caption = "Base Case Cost-Effectiveness Results Comparison",
      col.names = c("Strategy",
                    "Baseline", "Fixed", "Difference", "% Change",
                    "Baseline", "Fixed", "Difference", "% Change",
                    "Baseline", "Fixed", "Difference"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", rep("r", 11))) %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, "Cost (€)" = 4, "Effect (QALYs)" = 4, "ICER (€/QALY)" = 3))
```

## Net Monetary Benefit Comparison

```{r nmb-table}
nmb_display <- nmb_comp %>%
  mutate(
    NMB_before = format(round(NMB_before, 2), big.mark = ",", nsmall = 2),
    NMB_after = format(round(NMB_after, 2), big.mark = ",", nsmall = 2),
    NMB_diff = format(round(NMB_diff, 2), big.mark = ",", nsmall = 2)
  )

kable(nmb_display,
      caption = paste0("Net Monetary Benefit Comparison at WTP = €",
                      format(before_meta$parameters$WTP, big.mark = ",")),
      col.names = c("Strategy", "Baseline (€)", "Fixed (€)", "Difference (€)"),
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position")) %>%
  row_spec(1, bold = TRUE, background = "#E8F4F8")
```

**Optimal Strategy:** `r if(optimal_changed) paste0("**Changed** from ", optimal_before, " to ", optimal_after) else paste0("Unchanged (", optimal_after, ")")`

\newpage

# PSA Results Comparison

## Summary Statistics

```{r psa-summary-table}
psa_display <- psa_comp %>%
  select(Strategy,
         meanCost_before, meanCost_after, meanCost_diff,
         meanEffect_before, meanEffect_after, meanEffect_diff) %>%
  mutate(
    meanCost_before = format(round(meanCost_before, 2), big.mark = ",", nsmall = 2),
    meanCost_after = format(round(meanCost_after, 2), big.mark = ",", nsmall = 2),
    meanCost_diff = format(round(meanCost_diff, 2), big.mark = ",", nsmall = 2),
    meanEffect_before = format(round(meanEffect_before, 4), nsmall = 4),
    meanEffect_after = format(round(meanEffect_after, 4), nsmall = 4),
    meanEffect_diff = format(round(meanEffect_diff, 4), nsmall = 4)
  )

kable(psa_display,
      caption = paste0("PSA Mean Costs and Effects (n = ",
                      format(before_meta$parameters$n_sim, big.mark = ","), " simulations)"),
      col.names = c("Strategy",
                    "Baseline", "Fixed", "Difference",
                    "Baseline", "Fixed", "Difference"),
      booktabs = TRUE,
      format = "latex") %>%
  kable_styling(latex_options = c("striped", "hold_position", "scale_down"), font_size = 10) %>%
  add_header_above(c(" " = 1, "Mean Cost (€)" = 3, "Mean Effect (QALYs)" = 3))
```

## 95% Credible Intervals

```{r psa-ci-table}
#| tbl-cap: "PSA 95% Credible Intervals"

psa_ci_display <- psa_comp %>%
  select(Strategy,
         Cost_2.5_percent_before, Cost_97.5_percent_before,
         Cost_2.5_percent_after, Cost_97.5_percent_after,
         Effect_2.5_percent_before, Effect_97.5_percent_before,
         Effect_2.5_percent_after, Effect_97.5_percent_after) %>%
  mutate(
    Cost_2.5_percent_before = format(round(Cost_2.5_percent_before, 2), big.mark = ",", nsmall = 2),
    Cost_97.5_percent_before = format(round(Cost_97.5_percent_before, 2), big.mark = ",", nsmall = 2),
    Cost_2.5_percent_after = format(round(Cost_2.5_percent_after, 2), big.mark = ",", nsmall = 2),
    Cost_97.5_percent_after = format(round(Cost_97.5_percent_after, 2), big.mark = ",", nsmall = 2),
    Effect_2.5_percent_before = format(round(Effect_2.5_percent_before, 4), nsmall = 4),
    Effect_97.5_percent_before = format(round(Effect_97.5_percent_before, 4), nsmall = 4),
    Effect_2.5_percent_after = format(round(Effect_2.5_percent_after, 4), nsmall = 4),
    Effect_97.5_percent_after = format(round(Effect_97.5_percent_after, 4), nsmall = 4)
  )

kable(psa_ci_display,
      col.names = c("Strategy",
                    "2.5%", "97.5%", "2.5%", "97.5%",
                    "2.5%", "97.5%", "2.5%", "97.5%"),
      booktabs = TRUE,
      format = "latex",
      align = c("l", rep("r", 8)),
      linesep = "") %>%
  kable_styling(latex_options = c("striped", "HOLD_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, "Cost Baseline" = 2, "Cost Fixed" = 2, "Effect Baseline" = 2, "Effect Fixed" = 2))
```

\newpage

# Visual Comparison

## PSA Scatter Plots (Side-by-Side)

```{r psa-sidebyside, fig.cap="Cost-effectiveness plane showing PSA simulations baseline (left) and fixed (right)", out.width="100%", fig.height=5}
# Extract PSA data
baseline_psa_data <- data.frame(
  Strategy = rep(baseline_psa$strategies, each = baseline_psa$n_sim),
  Cost = as.vector(as.matrix(baseline_psa$cost)),
  Effect = as.vector(as.matrix(baseline_psa$effectiveness)),
  Snapshot = "Baseline"
)

fixed_psa_data <- data.frame(
  Strategy = rep(fixed_psa$strategies, each = fixed_psa$n_sim),
  Cost = as.vector(as.matrix(fixed_psa$cost)),
  Effect = as.vector(as.matrix(fixed_psa$effectiveness)),
  Snapshot = "Fixed"
)

# Create side-by-side plots
plot_baseline <- ggplot(baseline_psa_data, aes(x = Effect, y = Cost, color = Strategy)) +
  geom_point(alpha = 0.3, size = 1) +
  labs(title = "Baseline", x = "Effect (QALYs)", y = "Cost (€)") +
  theme_minimal() +
  theme(legend.position = "bottom")

plot_fixed <- ggplot(fixed_psa_data, aes(x = Effect, y = Cost, color = Strategy)) +
  geom_point(alpha = 0.3, size = 1) +
  labs(title = "Fixed", x = "Effect (QALYs)", y = "Cost (€)") +
  theme_minimal() +
  theme(legend.position = "bottom")

gridExtra::grid.arrange(plot_baseline, plot_fixed, ncol = 2)
```

## PSA Scatter Plots (Overlaid)

```{r psa-overlaid, fig.cap="Cost-effectiveness plane with overlaid baseline and fixed PSA simulations", out.width="80%", fig.height=6}
# Combine data
combined_psa_data <- rbind(baseline_psa_data, fixed_psa_data)

ggplot(combined_psa_data, aes(x = Effect, y = Cost, color = Strategy, shape = Snapshot)) +
  geom_point(alpha = 0.3, size = 1.5) +
  scale_shape_manual(values = c("Baseline" = 1, "Fixed" = 16)) +
  labs(title = "Baseline vs Fixed Comparison",
       x = "Effect (QALYs)",
       y = "Cost (€)") +
  theme_minimal() +
  theme(legend.position = "bottom")
```

\newpage

```{r multi-issue-comparison, results='asis'}
# Compare across multiple recent issues if available
n_issues_available <- nrow(complete_pairs)

if (n_issues_available >= 2) {
  cat("# Comparison Across Recent Issues\n\n")

  # Get up to 5 most recent issues (already sorted by timestamp descending)
  n_to_compare <- min(5, n_issues_available)
  recent_issues <- head(complete_pairs, n_to_compare)

  # Build comparison table
  multi_comp <- data.frame(
    Issue = character(),
    Issue_Title = character(),
    Optimal_Baseline = character(),
    Optimal_Fixed = character(),
    Changed = character(),
    Max_Cost_Change = numeric(),
    Max_Effect_Change = numeric(),
    Max_ICER_Change = numeric(),
    stringsAsFactors = FALSE
  )

  for (i in 1:nrow(recent_issues)) {
    issue_row <- recent_issues[i, ]

    # Load snapshots
    snap_base <- readRDS(issue_row$Baseline_File)
    snap_fixed <- readRDS(issue_row$Fixed_File)

    # Compare
    base_comp_temp <- merge(
      snap_base$icer_obj[, c("Strategy", "Cost", "Effect", "ICER")],
      snap_fixed$icer_obj[, c("Strategy", "Cost", "Effect", "ICER")],
      by = "Strategy",
      suffixes = c("_before", "_after")
    )

    base_comp_temp$Cost_diff <- base_comp_temp$Cost_after - base_comp_temp$Cost_before
    base_comp_temp$Effect_diff <- base_comp_temp$Effect_after - base_comp_temp$Effect_before
    base_comp_temp$ICER_diff <- ifelse(
      is.na(base_comp_temp$ICER_before) | is.na(base_comp_temp$ICER_after),
      NA,
      base_comp_temp$ICER_after - base_comp_temp$ICER_before
    )

    nmb_base <- snap_base$nmb_at_wtp
    nmb_fixed <- snap_fixed$nmb_at_wtp
    opt_base <- nmb_base$Strategy[which.max(nmb_base$NMB)]
    opt_fixed <- nmb_fixed$Strategy[which.max(nmb_fixed$NMB)]

    multi_comp <- rbind(multi_comp, data.frame(
      Issue = paste0("#", issue_row$Issue),
      Issue_Title = ifelse(issue_row$Issue_Title == "", "—", issue_row$Issue_Title),
      Optimal_Baseline = opt_base,
      Optimal_Fixed = opt_fixed,
      Changed = ifelse(opt_base != opt_fixed, "Yes", "No"),
      Max_Cost_Change = max(abs(base_comp_temp$Cost_diff), na.rm = TRUE),
      Max_Effect_Change = max(abs(base_comp_temp$Effect_diff), na.rm = TRUE),
      Max_ICER_Change = max(abs(base_comp_temp$ICER_diff), na.rm = TRUE),
      stringsAsFactors = FALSE
    ))
  }

  # Format for display
  multi_comp_display <- multi_comp %>%
    mutate(
      Max_Cost_Change = format(round(Max_Cost_Change, 2), big.mark = ",", nsmall = 2),
      Max_Effect_Change = format(round(Max_Effect_Change, 4), nsmall = 4),
      Max_ICER_Change = format(round(Max_ICER_Change, 0), big.mark = ",")
    )

  cat("This table summarizes the impact of bug fixes across the", n_to_compare, "most recent issues:\n\n")

  print(kable(multi_comp_display,
        caption = paste0("Summary of Bug Fix Impacts (", n_to_compare, " Most Recent Issues)"),
        col.names = c("Issue", "Title", "Optimal (Baseline)", "Optimal (Fixed)", "Changed?",
                      "Max Cost Change (€)", "Max Effect Change (QALYs)", "Max ICER Change (€/QALY)"),
        booktabs = TRUE,
        format = "latex",
        align = c("l", "l", "l", "l", "c", "r", "r", "r")) %>%
    kable_styling(latex_options = c("striped", "hold_position", "scale_down"), font_size = 8) %>%
    row_spec(which(multi_comp$Issue == paste0("#", issue_num)), bold = TRUE, background = "#E8F4F8"))

  cat("\n\n\\newpage\n\n")
}
```

# Summary

The comparison for issue #`r issue_num` shows:

- **Optimal Strategy:** `r if(optimal_changed) paste0("Changed from ", optimal_before, " to ", optimal_after) else paste0("Unchanged (", optimal_after, ")")`
- **Maximum Cost Change:** €`r format(round(max_cost_change, 2), big.mark = ",", nsmall = 2)` (`r if(cost_significant) "substantial" else "minor"`)
- **Maximum Effect Change:** `r format(round(max_effect_change, 3), nsmall = 3)` QALYs (`r if(effect_significant) "substantial" else "minor"`)
- **Maximum ICER Change:** €`r format(round(max_icer_change, 0), big.mark = ",")`/QALY (`r if(icer_significant) "substantial" else "minor"`)
- **Parameter Changes:** `r if(length(param_changes) > 0) paste(param_changes, collapse = ", ") else "None detected"`

`r if(optimal_changed || cost_significant || effect_significant || icer_significant) "**Interpretation:** Changes exceed typical thresholds and should be carefully reviewed to ensure they align with the intended bug fix." else "**Interpretation:** Changes are within expected bounds for bug fixes that improve numerical stability or code quality."`

---

**Report completed on:** `r Sys.Date()`  
**Repository:** ben-geisler/METIMMOX-1  
**Report version:** 1.0
