---
title: "Model B Comparison: OLD vs NEW Design"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = here::here())

# Load packages BEFORE sourcing scripts
if (!require("pacman")) install.packages("pacman")
pacman::p_load(here, survival, flexsurv, dplyr, ggplot2, knitr, kableExtra, tidyr)
```

# Introduction

This document compares the OLD and NEW Model B (Focused) designs to document the methodological change and its impact on results.

## Summary of Changes

| Aspect | OLD Model B | NEW Model B |
|--------|-------------|-------------|
| Biomarkers as main effects | crp + tlr + tmb_braf | crp + tmb_braf |
| Interaction terms | One per model | BOTH (crp:Rx + tmb_braf:Rx) |
| Strategies evaluated | control, crp, tlr, tmb_braf | control, crp, tmb_braf |
| Number of distinct formulas | 3 (one per biomarker) | 1 (shared formula) |

## Rationale for Change

The OLD Model B included TLR as a biomarker but evidence suggests TLR may not provide sufficient predictive value for treatment selection. The NEW Model B:

1. **Excludes TLR entirely** - focuses on CRP and TMB/BRAF only
2. **Includes both interaction terms** - providing estimates for how each biomarker modifies treatment effect while adjusting for the other

# Methodology 

```{r load-data, include=FALSE}
# Source analysis scripts - suppress all output
invisible(capture.output({
  source(here("scripts/R/analysis/02_setup_and_global_variables.R"))
  source(here("scripts/R/analysis/03_biomarker_strategies.R"))
}))

# Re-load packages after rm(list=ls()) in sourced scripts
pacman::p_load(here, survival, flexsurv, dplyr, ggplot2, knitr, kableExtra, tidyr)

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    text = element_text(size = 11),
    axis.text = element_text(size = 9),
    legend.position = "bottom"
  ))

# Ensure categorical variables are properly coded
data$crp <- as.factor(data$crp)
data$tlr <- as.factor(data$tlr)
data$tmb_braf <- as.factor(data$tmb_braf)

# Create complete dataset
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr", "tmb_braf", "OSwk", "Death", "PFSwk", "Progression")]), ]

# Time points for predictions
time_points <- seq(0, time_horizon, by = 1)
```

## Formula Definitions

### OLD Model B Formulas

Three different formulas, each with one interaction term and all three biomarkers as main effects:

- CRP strategy: `Surv(...) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx`
- TLR strategy: `Surv(...) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx`
- TMB/BRAF strategy: `Surv(...) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx`

### NEW Model B Formula

One shared formula with both interaction terms (TLR excluded):

- All strategies: `Surv(...) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx`

```{r define-formulas}
# OLD Model B formulas (3 different formulas)
old_formulas <- list(
  crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx
  ),
  tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx
  ),
  tmb_braf = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx
  )
)

# NEW Model B formula (1 shared formula with BOTH interactions)
new_formula_os <- Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
new_formula_pfs <- Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
```

# Model Fitting

```{r fit-models}
# Fit OLD Model B models
old_fits <- list()
for (biomarker in names(old_formulas)) {
  old_fits[[biomarker]] <- tryCatch({
    list(
      os = flexsurvreg(old_formulas[[biomarker]]$os, data = data_complete, dist = "gamma"),
      pfs = flexsurvreg(old_formulas[[biomarker]]$pfs, data = data_complete, dist = "gamma")
    )
  }, error = function(e) {
    message("Error fitting OLD Model B for ", biomarker, ": ", e$message)
    NULL
  })
}

# Fit NEW Model B (single model)
new_fit <- tryCatch({
  list(
    os = flexsurvreg(new_formula_os, data = data_complete, dist = "gamma"),
    pfs = flexsurvreg(new_formula_pfs, data = data_complete, dist = "gamma")
  )
}, error = function(e) {
  message("Error fitting NEW Model B: ", e$message)
  NULL
})
```

## Model Fit Comparison (AIC)

```{r aic-comparison}
# Extract AIC values
aic_comparison <- data.frame(
  Model = character(),
  OS_AIC = numeric(),
  PFS_AIC = numeric(),
  stringsAsFactors = FALSE
)

for (biomarker in names(old_fits)) {
  if (!is.null(old_fits[[biomarker]]) &&
      !is.null(old_fits[[biomarker]]$os) &&
      !is.null(old_fits[[biomarker]]$pfs)) {
    aic_comparison <- rbind(aic_comparison, data.frame(
      Model = paste0("OLD B-", toupper(biomarker)),
      OS_AIC = AIC(old_fits[[biomarker]]$os),
      PFS_AIC = AIC(old_fits[[biomarker]]$pfs)
    ))
  }
}

if (!is.null(new_fit) && !is.null(new_fit$os) && !is.null(new_fit$pfs)) {
  aic_comparison <- rbind(aic_comparison, data.frame(
    Model = "NEW B (shared)",
    OS_AIC = AIC(new_fit$os),
    PFS_AIC = AIC(new_fit$pfs)
  ))
}

if (nrow(aic_comparison) > 0) {
  kable(aic_comparison,
        col.names = c("Model", "OS AIC", "PFS AIC"),
        caption = "AIC Comparison: OLD vs NEW Model B",
        digits = 1,
        booktabs = TRUE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 10)
} else {
  cat("Could not compute AIC values - model fitting may have failed.\n")
}
```

\newpage

# Parameter Estimates Comparison

```{r extract-coefs-function}
# Extract ALL coefficients from flexsurv model
extract_all_coefs <- function(model, label) {
  if (is.null(model)) return(NULL)

  # Get coefficients and variance-covariance matrix
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  se <- sqrt(diag(vcov_mat))

  data.frame(
    Model = label,
    Term = names(coefs),
    Estimate = as.numeric(coefs),
    SE = as.numeric(se),
    HR = exp(as.numeric(coefs)),
    stringsAsFactors = FALSE,
    row.names = NULL
  )
}
```

## Overall Survival - All Coefficients

```{r os-extract-coefs}
# Extract coefficients for all models
old_crp_coefs <- extract_all_coefs(old_fits$crp$os, "OLD B-CRP")
old_tlr_coefs <- extract_all_coefs(old_fits$tlr$os, "OLD B-TLR")
old_tmb_coefs <- extract_all_coefs(old_fits$tmb_braf$os, "OLD B-TMB")
new_coefs <- extract_all_coefs(new_fit$os, "NEW B")

# Helper function to format coefficient table
format_coef_table <- function(coef_df) {
  if (is.null(coef_df) || nrow(coef_df) == 0) return(NULL)
  coef_df$HR_CI <- sprintf("%.3f (%.3f-%.3f)",
                            coef_df$HR,
                            exp(coef_df$Estimate - 1.96 * coef_df$SE),
                            exp(coef_df$Estimate + 1.96 * coef_df$SE))
  display_df <- coef_df[, c("Term", "Estimate", "SE", "HR_CI")]
  names(display_df) <- c("Term", "Estimate", "SE", "HR (95% CI)")
  return(display_df)
}
```

### OLD B-CRP - OS

```{r os-old-crp}
display_df <- format_coef_table(old_crp_coefs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

### OLD B-TLR - OS

```{r os-old-tlr}
display_df <- format_coef_table(old_tlr_coefs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

### OLD B-TMB - OS

```{r os-old-tmb}
display_df <- format_coef_table(old_tmb_coefs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

### NEW B - OS

```{r os-new}
display_df <- format_coef_table(new_coefs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

## Progression-Free Survival - All Coefficients

```{r pfs-extract-coefs}
# Extract coefficients for all models
old_crp_pfs <- extract_all_coefs(old_fits$crp$pfs, "OLD B-CRP")
old_tlr_pfs <- extract_all_coefs(old_fits$tlr$pfs, "OLD B-TLR")
old_tmb_pfs <- extract_all_coefs(old_fits$tmb_braf$pfs, "OLD B-TMB")
new_pfs_coefs <- extract_all_coefs(new_fit$pfs, "NEW B")
```

### OLD B-CRP - PFS

```{r pfs-old-crp}
display_df <- format_coef_table(old_crp_pfs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

### OLD B-TLR - PFS

```{r pfs-old-tlr}
display_df <- format_coef_table(old_tlr_pfs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

### OLD B-TMB - PFS

```{r pfs-old-tmb}
display_df <- format_coef_table(old_tmb_pfs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

### NEW B - PFS

```{r pfs-new}
display_df <- format_coef_table(new_pfs_coefs)
if (!is.null(display_df)) {
  kable(display_df, booktabs = TRUE, digits = 3, row.names = FALSE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

# Survival Curves Comparison

```{r generate-predictions}
# Generate predictions for each model
# For biomarker strategies, we need population-averaged predictions for:
# - Biomarker+ subgroup (receives experimental treatment)
# - Biomarker- subgroup (receives control treatment)
# Then weight by prevalence

pred_times <- seq(0, 520, by = 4)  # Every 4 weeks for 10 years

# Function to get survival predictions for a specific newdata
get_surv_pred_newdata <- function(model, times, newdata) {
  if (is.null(model)) return(NULL)
  tryCatch({
    pred <- summary(model, t = times, newdata = newdata, type = "survival", ci = FALSE)
    # Average across all patients in newdata
    survs <- sapply(pred, function(x) x$est)
    if (is.matrix(survs)) {
      rowMeans(survs)
    } else {
      survs
    }
  }, error = function(e) {
    message("Prediction error: ", e$message)
    NULL
  })
}

# Get biomarker prevalences
p_crp <- mean(as.numeric(as.character(data_complete$crp)))
p_tlr <- mean(as.numeric(as.character(data_complete$tlr)))
p_tmb <- mean(as.numeric(as.character(data_complete$tmb_braf)))

os_preds <- list()
pfs_preds <- list()

# ============================================================================
# OLD Model B predictions (3 separate models, each with different formula)
# ============================================================================
for (bm in c("crp", "tlr", "tmb_braf")) {
  if (!is.null(old_fits[[bm]])) {
    # Biomarker+ subgroup (experimental treatment)
    data_pos <- data_complete[data_complete[[bm]] == "1", ]
    data_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))

    # Biomarker- subgroup (control treatment)
    data_neg <- data_complete[data_complete[[bm]] == "0", ]
    data_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))

    # Get prevalence for this biomarker
    prev <- if (bm == "crp") p_crp else if (bm == "tlr") p_tlr else p_tmb

    # Get predictions for each subgroup
    os_pos <- get_surv_pred_newdata(old_fits[[bm]]$os, pred_times, data_pos)
    os_neg <- get_surv_pred_newdata(old_fits[[bm]]$os, pred_times, data_neg)
    pfs_pos <- get_surv_pred_newdata(old_fits[[bm]]$pfs, pred_times, data_pos)
    pfs_neg <- get_surv_pred_newdata(old_fits[[bm]]$pfs, pred_times, data_neg)

    # Weighted average
    if (!is.null(os_pos) && !is.null(os_neg)) {
      os_preds[[paste0("OLD_", bm)]] <- prev * os_pos + (1 - prev) * os_neg
    }
    if (!is.null(pfs_pos) && !is.null(pfs_neg)) {
      pfs_preds[[paste0("OLD_", bm)]] <- prev * pfs_pos + (1 - prev) * pfs_neg
    }
  }
}

# ============================================================================
# NEW Model B predictions (1 shared model, 2 strategies)
# ============================================================================
# NEW Model B uses the SAME fitted model for both strategies, but predictions
# differ because different biomarkers determine treatment assignment

if (!is.null(new_fit)) {
  # CRP Strategy: crp+ gets experimental, crp- gets control
  data_crp_pos <- data_complete[data_complete$crp == "1", ]
  data_crp_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))
  data_crp_neg <- data_complete[data_complete$crp == "0", ]
  data_crp_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))

  os_crp_pos <- get_surv_pred_newdata(new_fit$os, pred_times, data_crp_pos)
  os_crp_neg <- get_surv_pred_newdata(new_fit$os, pred_times, data_crp_neg)
  pfs_crp_pos <- get_surv_pred_newdata(new_fit$pfs, pred_times, data_crp_pos)
  pfs_crp_neg <- get_surv_pred_newdata(new_fit$pfs, pred_times, data_crp_neg)

  if (!is.null(os_crp_pos) && !is.null(os_crp_neg)) {
    os_preds[["NEW_crp"]] <- p_crp * os_crp_pos + (1 - p_crp) * os_crp_neg
  }
  if (!is.null(pfs_crp_pos) && !is.null(pfs_crp_neg)) {
    pfs_preds[["NEW_crp"]] <- p_crp * pfs_crp_pos + (1 - p_crp) * pfs_crp_neg
  }

  # TMB/BRAF Strategy: tmb_braf+ gets experimental, tmb_braf- gets control
  data_tmb_pos <- data_complete[data_complete$tmb_braf == "1", ]
  data_tmb_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))
  data_tmb_neg <- data_complete[data_complete$tmb_braf == "0", ]
  data_tmb_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))

  os_tmb_pos <- get_surv_pred_newdata(new_fit$os, pred_times, data_tmb_pos)
  os_tmb_neg <- get_surv_pred_newdata(new_fit$os, pred_times, data_tmb_neg)
  pfs_tmb_pos <- get_surv_pred_newdata(new_fit$pfs, pred_times, data_tmb_pos)
  pfs_tmb_neg <- get_surv_pred_newdata(new_fit$pfs, pred_times, data_tmb_neg)

  if (!is.null(os_tmb_pos) && !is.null(os_tmb_neg)) {
    os_preds[["NEW_tmb"]] <- p_tmb * os_tmb_pos + (1 - p_tmb) * os_tmb_neg
  }
  if (!is.null(pfs_tmb_pos) && !is.null(pfs_tmb_neg)) {
    pfs_preds[["NEW_tmb"]] <- p_tmb * pfs_tmb_pos + (1 - p_tmb) * pfs_tmb_neg
  }
}
```

## Overall Survival Curves

```{r os-curves, fig.height=5, fig.cap="Overall Survival Curves: OLD vs NEW Model B (population-weighted)"}
# Build plot data
os_plot_data <- data.frame()
for (model_name in names(os_preds)) {
  if (!is.null(os_preds[[model_name]])) {
    os_plot_data <- rbind(os_plot_data, data.frame(
      Time = pred_times / 52,  # Convert to years
      Survival = os_preds[[model_name]],
      Model = model_name
    ))
  }
}

if (nrow(os_plot_data) > 0) {
  ggplot(os_plot_data, aes(x = Time, y = Survival, color = Model, linetype = Model)) +
    geom_line(linewidth = 1) +
    scale_color_manual(values = c("OLD_crp" = "#E69F00", "OLD_tlr" = "#56B4E9",
                                   "OLD_tmb_braf" = "#009E73",
                                   "NEW_crp" = "#D55E00", "NEW_tmb" = "#CC79A7"),
                       labels = c("OLD_crp" = "OLD B-CRP", "OLD_tlr" = "OLD B-TLR",
                                  "OLD_tmb_braf" = "OLD B-TMB",
                                  "NEW_crp" = "NEW B-CRP", "NEW_tmb" = "NEW B-TMB")) +
    scale_linetype_manual(values = c("OLD_crp" = "dashed", "OLD_tlr" = "dotted",
                                      "OLD_tmb_braf" = "dotdash",
                                      "NEW_crp" = "solid", "NEW_tmb" = "solid"),
                          labels = c("OLD_crp" = "OLD B-CRP", "OLD_tlr" = "OLD B-TLR",
                                     "OLD_tmb_braf" = "OLD B-TMB",
                                     "NEW_crp" = "NEW B-CRP", "NEW_tmb" = "NEW B-TMB")) +
    labs(x = "Time (Years)", y = "Overall Survival Probability",
         title = "Overall Survival: OLD vs NEW Model B") +
    coord_cartesian(ylim = c(0, 1)) +
    theme_minimal() +
    theme(legend.position = "bottom")
} else {
  cat("Could not generate OS survival curves.\n")
}
```

## Progression-Free Survival Curves

```{r pfs-curves, fig.height=5, fig.cap="Progression-Free Survival Curves: OLD vs NEW Model B (population-weighted)"}
# Build plot data
pfs_plot_data <- data.frame()
for (model_name in names(pfs_preds)) {
  if (!is.null(pfs_preds[[model_name]])) {
    pfs_plot_data <- rbind(pfs_plot_data, data.frame(
      Time = pred_times / 52,  # Convert to years
      Survival = pfs_preds[[model_name]],
      Model = model_name
    ))
  }
}

if (nrow(pfs_plot_data) > 0) {
  ggplot(pfs_plot_data, aes(x = Time, y = Survival, color = Model, linetype = Model)) +
    geom_line(linewidth = 1) +
    scale_color_manual(values = c("OLD_crp" = "#E69F00", "OLD_tlr" = "#56B4E9",
                                   "OLD_tmb_braf" = "#009E73",
                                   "NEW_crp" = "#D55E00", "NEW_tmb" = "#CC79A7"),
                       labels = c("OLD_crp" = "OLD B-CRP", "OLD_tlr" = "OLD B-TLR",
                                  "OLD_tmb_braf" = "OLD B-TMB",
                                  "NEW_crp" = "NEW B-CRP", "NEW_tmb" = "NEW B-TMB")) +
    scale_linetype_manual(values = c("OLD_crp" = "dashed", "OLD_tlr" = "dotted",
                                      "OLD_tmb_braf" = "dotdash",
                                      "NEW_crp" = "solid", "NEW_tmb" = "solid"),
                          labels = c("OLD_crp" = "OLD B-CRP", "OLD_tlr" = "OLD B-TLR",
                                     "OLD_tmb_braf" = "OLD B-TMB",
                                     "NEW_crp" = "NEW B-CRP", "NEW_tmb" = "NEW B-TMB")) +
    labs(x = "Time (Years)", y = "Progression-Free Survival Probability",
         title = "PFS: OLD vs NEW Model B") +
    coord_cartesian(ylim = c(0, 1)) +
    theme_minimal() +
    theme(legend.position = "bottom")
} else {
  cat("Could not generate PFS survival curves.\n")
}
```

\newpage

# Life Years, QALYs, and Costs

```{r calculate-outcomes}
# Calculate life years, QALYs, and costs for each model
# Using area under curve calculation (trapezoidal rule)

# Discount rate from global variables
discount_rate <- dr  # Should be 0.04

# Function to calculate life years from survival curve
# dr = 0 for undiscounted, dr > 0 for discounted
calc_ly <- function(surv, times, dr = 0) {
  if (is.null(surv) || length(surv) == 0) return(NA)

  # Discount factors (1 if dr = 0)
  discount_factors <- 1 / (1 + dr)^(times / 52)

  # Area under curve (trapezoidal rule)
  n <- length(surv)
  ly <- 0
  for (i in 2:n) {
    dt <- (times[i] - times[i-1]) / 52  # Time in years
    avg_surv <- (surv[i] + surv[i-1]) / 2
    avg_discount <- (discount_factors[i] + discount_factors[i-1]) / 2
    ly <- ly + avg_surv * avg_discount * dt
  }
  return(ly)
}

# ============================================================================
# Calculate control strategy outcomes (all patients get FLOX only)
# ============================================================================
# For control, we use the control model predictions (age/sex adjusted only)
# Since we don't have a separate control model here, estimate from biomarker-
# negative subgroups (who receive control treatment)

# Use average of biomarker-negative predictions as control estimate
control_os <- (os_preds[["OLD_crp"]] + os_preds[["OLD_tmb_braf"]]) / 2  # Rough proxy
control_pfs <- (pfs_preds[["OLD_crp"]] + pfs_preds[["OLD_tmb_braf"]]) / 2

control_ly_os_undisc <- calc_ly(control_os, pred_times, dr = 0)
control_ly_pfs_undisc <- calc_ly(control_pfs, pred_times, dr = 0)
control_ly_os_disc <- calc_ly(control_os, pred_times, dr = discount_rate)
control_ly_pfs_disc <- calc_ly(control_pfs, pred_times, dr = discount_rate)

# ============================================================================
# Calculate outcomes for all strategies
# ============================================================================
# Store in a structured way for comparison tables

calc_strategy_outcomes <- function(os_pred, pfs_pred, prev) {
  list(
    ly_os_undisc = calc_ly(os_pred, pred_times, dr = 0),
    ly_pfs_undisc = calc_ly(pfs_pred, pred_times, dr = 0),
    ly_os_disc = calc_ly(os_pred, pred_times, dr = discount_rate),
    ly_pfs_disc = calc_ly(pfs_pred, pred_times, dr = discount_rate),
    prevalence = prev
  )
}

# Calculate for each strategy
old_crp <- calc_strategy_outcomes(os_preds[["OLD_crp"]], pfs_preds[["OLD_crp"]], p_crp)
old_tlr <- calc_strategy_outcomes(os_preds[["OLD_tlr"]], pfs_preds[["OLD_tlr"]], p_tlr)
old_tmb <- calc_strategy_outcomes(os_preds[["OLD_tmb_braf"]], pfs_preds[["OLD_tmb_braf"]], p_tmb)
new_crp <- calc_strategy_outcomes(os_preds[["NEW_crp"]], pfs_preds[["NEW_crp"]], p_crp)
new_tmb <- calc_strategy_outcomes(os_preds[["NEW_tmb"]], pfs_preds[["NEW_tmb"]], p_tmb)

# Add progressed state LY
add_prog_ly <- function(x) {
  x$ly_prog_undisc <- pmax(x$ly_os_undisc - x$ly_pfs_undisc, 0)
  x$ly_prog_disc <- pmax(x$ly_os_disc - x$ly_pfs_disc, 0)
  return(x)
}

old_crp <- add_prog_ly(old_crp)
old_tlr <- add_prog_ly(old_tlr)
old_tmb <- add_prog_ly(old_tmb)
new_crp <- add_prog_ly(new_crp)
new_tmb <- add_prog_ly(new_tmb)

# Control
control <- list(
  ly_os_undisc = control_ly_os_undisc,
  ly_pfs_undisc = control_ly_pfs_undisc,
  ly_os_disc = control_ly_os_disc,
  ly_pfs_disc = control_ly_pfs_disc,
  ly_prog_undisc = pmax(control_ly_os_undisc - control_ly_pfs_undisc, 0),
  ly_prog_disc = pmax(control_ly_os_disc - control_ly_pfs_disc, 0),
  prevalence = NA
)

# Utilities from base case
u_pf <- 0.9077  # Utility in progression-free state
u_p <- 0.9005   # Utility in progressed state

# Cost parameters
c_drug_nivo <- 13923   # Cost per nivolumab administration
c_drug_flox <- 427     # Cost per FLOX administration
n_nivo_admin <- 8
n_flox_admin_exp <- 8
n_flox_admin_ctrl <- 16

cost_exp <- n_nivo_admin * c_drug_nivo + n_flox_admin_exp * c_drug_flox
cost_ctrl <- n_flox_admin_ctrl * c_drug_flox

# Calculate QALYs and costs
calc_qaly_cost <- function(x) {
  x$qaly <- x$ly_pfs_disc * u_pf + x$ly_prog_disc * u_p
  if (!is.na(x$prevalence)) {
    x$cost <- x$prevalence * cost_exp + (1 - x$prevalence) * cost_ctrl
  } else {
    x$cost <- cost_ctrl  # Control strategy
  }
  return(x)
}

control <- calc_qaly_cost(control)
old_crp <- calc_qaly_cost(old_crp)
old_tlr <- calc_qaly_cost(old_tlr)
old_tmb <- calc_qaly_cost(old_tmb)
new_crp <- calc_qaly_cost(new_crp)
new_tmb <- calc_qaly_cost(new_tmb)
```

## Discounted Life Years Comparison

```{r ly-comparison-table}
# Create comparison table: Control | TLR (OLD only) | CRP (OLD, NEW, Delta) | TMB (OLD, NEW, Delta)
ly_comparison <- data.frame(
  Outcome = c("LY (OS)", "LY (PFS)", "LY (Progressed)"),
  Control = c(control$ly_os_disc, control$ly_pfs_disc, control$ly_prog_disc),
  TLR_OLD = c(old_tlr$ly_os_disc, old_tlr$ly_pfs_disc, old_tlr$ly_prog_disc),
  CRP_OLD = c(old_crp$ly_os_disc, old_crp$ly_pfs_disc, old_crp$ly_prog_disc),
  CRP_NEW = c(new_crp$ly_os_disc, new_crp$ly_pfs_disc, new_crp$ly_prog_disc),
  CRP_Delta = c(new_crp$ly_os_disc - old_crp$ly_os_disc,
                new_crp$ly_pfs_disc - old_crp$ly_pfs_disc,
                new_crp$ly_prog_disc - old_crp$ly_prog_disc),
  TMB_OLD = c(old_tmb$ly_os_disc, old_tmb$ly_pfs_disc, old_tmb$ly_prog_disc),
  TMB_NEW = c(new_tmb$ly_os_disc, new_tmb$ly_pfs_disc, new_tmb$ly_prog_disc),
  TMB_Delta = c(new_tmb$ly_os_disc - old_tmb$ly_os_disc,
                new_tmb$ly_pfs_disc - old_tmb$ly_pfs_disc,
                new_tmb$ly_prog_disc - old_tmb$ly_prog_disc)
)

kable(ly_comparison,
      col.names = c("Outcome", "Control", "TLR (OLD)",
                    "OLD", "NEW", "Delta",
                    "OLD", "NEW", "Delta"),
      caption = paste0("Discounted Life Years Comparison (dr = ", discount_rate * 100, "\\%)"),
      booktabs = TRUE,
      digits = 3) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, " " = 1, " " = 1, "CRP Strategy" = 3, "TMB/BRAF Strategy" = 3))
```

## Undiscounted Life Years Comparison

```{r ly-undisc-comparison-table}
ly_undisc_comparison <- data.frame(
  Outcome = c("LY (OS)", "LY (PFS)", "LY (Progressed)"),
  Control = c(control$ly_os_undisc, control$ly_pfs_undisc, control$ly_prog_undisc),
  TLR_OLD = c(old_tlr$ly_os_undisc, old_tlr$ly_pfs_undisc, old_tlr$ly_prog_undisc),
  CRP_OLD = c(old_crp$ly_os_undisc, old_crp$ly_pfs_undisc, old_crp$ly_prog_undisc),
  CRP_NEW = c(new_crp$ly_os_undisc, new_crp$ly_pfs_undisc, new_crp$ly_prog_undisc),
  CRP_Delta = c(new_crp$ly_os_undisc - old_crp$ly_os_undisc,
                new_crp$ly_pfs_undisc - old_crp$ly_pfs_undisc,
                new_crp$ly_prog_undisc - old_crp$ly_prog_undisc),
  TMB_OLD = c(old_tmb$ly_os_undisc, old_tmb$ly_pfs_undisc, old_tmb$ly_prog_undisc),
  TMB_NEW = c(new_tmb$ly_os_undisc, new_tmb$ly_pfs_undisc, new_tmb$ly_prog_undisc),
  TMB_Delta = c(new_tmb$ly_os_undisc - old_tmb$ly_os_undisc,
                new_tmb$ly_pfs_undisc - old_tmb$ly_pfs_undisc,
                new_tmb$ly_prog_undisc - old_tmb$ly_prog_undisc)
)

kable(ly_undisc_comparison,
      col.names = c("Outcome", "Control", "TLR (OLD)",
                    "OLD", "NEW", "Delta",
                    "OLD", "NEW", "Delta"),
      caption = "Undiscounted Life Years Comparison",
      booktabs = TRUE,
      digits = 3) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, " " = 1, " " = 1, "CRP Strategy" = 3, "TMB/BRAF Strategy" = 3))
```

## QALYs Comparison

```{r qaly-comparison-table}
qaly_comparison <- data.frame(
  Metric = "QALYs",
  Control = control$qaly,
  TLR_OLD = old_tlr$qaly,
  CRP_OLD = old_crp$qaly,
  CRP_NEW = new_crp$qaly,
  CRP_Delta = new_crp$qaly - old_crp$qaly,
  TMB_OLD = old_tmb$qaly,
  TMB_NEW = new_tmb$qaly,
  TMB_Delta = new_tmb$qaly - old_tmb$qaly
)

kable(qaly_comparison,
      col.names = c("Metric", "Control", "TLR (OLD)",
                    "OLD", "NEW", "Delta",
                    "OLD", "NEW", "Delta"),
      caption = paste0("Discounted QALYs Comparison (Utilities: PF=", u_pf, ", P=", u_p, ")"),
      booktabs = TRUE,
      digits = 3) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, " " = 1, " " = 1, "CRP Strategy" = 3, "TMB/BRAF Strategy" = 3))
```

## Costs Comparison

```{r cost-comparison-table}
cost_comparison <- data.frame(
  Metric = "Cost (EUR)",
  Control = control$cost,
  TLR_OLD = old_tlr$cost,
  CRP_OLD = old_crp$cost,
  CRP_NEW = new_crp$cost,
  CRP_Delta = new_crp$cost - old_crp$cost,
  TMB_OLD = old_tmb$cost,
  TMB_NEW = new_tmb$cost,
  TMB_Delta = new_tmb$cost - old_tmb$cost
)

# Format costs with thousands separator
cost_comparison[1, -1] <- sapply(cost_comparison[1, -1], function(x) {
  format(round(as.numeric(x), 0), big.mark = ",", scientific = FALSE)
})

kable(cost_comparison,
      col.names = c("Metric", "Control", "TLR (OLD)",
                    "OLD", "NEW", "Delta",
                    "OLD", "NEW", "Delta"),
      caption = "Treatment Costs Comparison",
      booktabs = TRUE,
      escape = FALSE) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9) %>%
  add_header_above(c(" " = 1, " " = 1, " " = 1, "CRP Strategy" = 3, "TMB/BRAF Strategy" = 3))
```

## ICER Comparison - OLD Model B

```{r icer-old}
# Calculate ICERs for OLD Model B (CRP and TMB strategies only, vs control)
icer_old <- data.frame(
  Strategy = c("Control", "CRP", "TMB/BRAF"),
  Cost = c(control$cost, old_crp$cost, old_tmb$cost),
  QALYs = c(control$qaly, old_crp$qaly, old_tmb$qaly),
  Inc_Cost = c(NA, old_crp$cost - control$cost, old_tmb$cost - control$cost),
  Inc_QALY = c(NA, old_crp$qaly - control$qaly, old_tmb$qaly - control$qaly)
)
icer_old$ICER <- ifelse(is.na(icer_old$Inc_QALY) | icer_old$Inc_QALY <= 0,
                         NA,
                         icer_old$Inc_Cost / icer_old$Inc_QALY)

# Format for display
icer_old_display <- icer_old
icer_old_display$Cost <- format(round(icer_old_display$Cost, 0), big.mark = ",")
icer_old_display$QALYs <- round(icer_old_display$QALYs, 3)
icer_old_display$Inc_Cost <- ifelse(is.na(icer_old_display$Inc_Cost), "-",
                                     format(round(icer_old_display$Inc_Cost, 0), big.mark = ","))
icer_old_display$Inc_QALY <- ifelse(is.na(icer_old_display$Inc_QALY), "-",
                                     round(icer_old_display$Inc_QALY, 3))
icer_old_display$ICER <- ifelse(is.na(icer_old_display$ICER), "-",
                                 format(round(icer_old_display$ICER, 0), big.mark = ","))

kable(icer_old_display,
      col.names = c("Strategy", "Cost (EUR)", "QALYs", "Incr. Cost", "Incr. QALYs", "ICER"),
      caption = "Cost-Effectiveness: OLD Model B (vs Control)",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

## ICER Comparison - NEW Model B

```{r icer-new}
# Calculate ICERs for NEW Model B (CRP and TMB strategies only, vs control)
icer_new <- data.frame(
  Strategy = c("Control", "CRP", "TMB/BRAF"),
  Cost = c(control$cost, new_crp$cost, new_tmb$cost),
  QALYs = c(control$qaly, new_crp$qaly, new_tmb$qaly),
  Inc_Cost = c(NA, new_crp$cost - control$cost, new_tmb$cost - control$cost),
  Inc_QALY = c(NA, new_crp$qaly - control$qaly, new_tmb$qaly - control$qaly)
)
icer_new$ICER <- ifelse(is.na(icer_new$Inc_QALY) | icer_new$Inc_QALY <= 0,
                         NA,
                         icer_new$Inc_Cost / icer_new$Inc_QALY)

# Format for display
icer_new_display <- icer_new
icer_new_display$Cost <- format(round(icer_new_display$Cost, 0), big.mark = ",")
icer_new_display$QALYs <- round(icer_new_display$QALYs, 3)
icer_new_display$Inc_Cost <- ifelse(is.na(icer_new_display$Inc_Cost), "-",
                                     format(round(icer_new_display$Inc_Cost, 0), big.mark = ","))
icer_new_display$Inc_QALY <- ifelse(is.na(icer_new_display$Inc_QALY), "-",
                                     round(icer_new_display$Inc_QALY, 3))
icer_new_display$ICER <- ifelse(is.na(icer_new_display$ICER), "-",
                                 format(round(icer_new_display$ICER, 0), big.mark = ","))

kable(icer_new_display,
      col.names = c("Strategy", "Cost (EUR)", "QALYs", "Incr. Cost", "Incr. QALYs", "ICER"),
      caption = "Cost-Effectiveness: NEW Model B (vs Control)",
      booktabs = TRUE,
      align = c("l", "r", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

## ICER Change: OLD vs NEW

```{r icer-change}
# Show how ICERs changed between OLD and NEW
icer_change <- data.frame(
  Strategy = c("CRP", "TMB/BRAF"),
  ICER_OLD = c(icer_old$ICER[2], icer_old$ICER[3]),
  ICER_NEW = c(icer_new$ICER[2], icer_new$ICER[3])
)
icer_change$Delta <- icer_change$ICER_NEW - icer_change$ICER_OLD
icer_change$Pct_Change <- (icer_change$Delta / icer_change$ICER_OLD) * 100

# Format
icer_change_display <- icer_change
icer_change_display$ICER_OLD <- ifelse(is.na(icer_change_display$ICER_OLD), "-",
                                        format(round(icer_change_display$ICER_OLD, 0), big.mark = ","))
icer_change_display$ICER_NEW <- ifelse(is.na(icer_change_display$ICER_NEW), "-",
                                        format(round(icer_change_display$ICER_NEW, 0), big.mark = ","))
icer_change_display$Delta <- ifelse(is.na(icer_change_display$Delta), "-",
                                     format(round(icer_change_display$Delta, 0), big.mark = ","))
icer_change_display$Pct_Change <- ifelse(is.na(icer_change_display$Pct_Change), "-",
                                          paste0(round(icer_change_display$Pct_Change, 1), "\\%"))

kable(icer_change_display,
      col.names = c("Strategy", "OLD ICER", "NEW ICER", "Delta", "Change"),
      caption = "ICER Change: OLD vs NEW Model B (EUR/QALY)",
      booktabs = TRUE,
      escape = FALSE,
      align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

\newpage

# Summary

```{r summary-calculations, include=FALSE}
# Extract values for interpretation
old_crp_inc_qaly <- old_crp$qaly - control$qaly
new_crp_inc_qaly <- new_crp$qaly - control$qaly
old_tmb_inc_qaly <- old_tmb$qaly - control$qaly
new_tmb_inc_qaly <- new_tmb$qaly - control$qaly

old_crp_icer <- icer_old$ICER[2]
new_crp_icer <- icer_new$ICER[2]
old_tmb_icer <- icer_old$ICER[3]
new_tmb_icer <- icer_new$ICER[3]
```

The redesign of Model B from OLD (all biomarkers as main effects with single interaction per strategy) to NEW (CRP + TMB/BRAF only with both interactions) has notable implications for cost-effectiveness results.

## Key Findings

**CRP Strategy**: Under the OLD Model B, the CRP strategy showed `r ifelse(old_crp_inc_qaly <= 0, "negative or negligible", "positive")` incremental QALYs compared to control (`r round(old_crp_inc_qaly, 3)` QALYs), which resulted in `r ifelse(is.na(old_crp_icer) || old_crp_inc_qaly <= 0, "no valid ICER (dominated or equivalent)", paste0("an ICER of EUR ", format(round(old_crp_icer, 0), big.mark = ",")))`. With the NEW Model B, the CRP strategy now shows a `r ifelse(new_crp_inc_qaly > 0, "positive", "negative")` incremental effect (`r round(new_crp_inc_qaly, 3)` QALYs), `r ifelse(!is.na(new_crp_icer) && new_crp_inc_qaly > 0, paste0("yielding a calculable ICER of EUR ", format(round(new_crp_icer, 0), big.mark = ",")), "but still without a valid ICER")`.

**TMB/BRAF Strategy**: The effect of the TMB/BRAF strategy is larger under the NEW model. OLD Model B showed incremental QALYs of `r round(old_tmb_inc_qaly, 3)` `r ifelse(!is.na(old_tmb_icer) && old_tmb_inc_qaly > 0, paste0("(ICER: EUR ", format(round(old_tmb_icer, 0), big.mark = ","), ")"), "")`, while NEW Model B shows `r round(new_tmb_inc_qaly, 3)` incremental QALYs`r ifelse(!is.na(new_tmb_icer) && new_tmb_inc_qaly > 0, paste0(" (ICER: EUR ", format(round(new_tmb_icer, 0), big.mark = ","), ")"), "")`. This represents a `r ifelse(new_tmb_inc_qaly > old_tmb_inc_qaly, "larger", "smaller")` treatment benefit under the revised model specification.

## Implications

The NEW Model B design has the following implications:

1. **TLR is excluded**: The analysis now focuses on only two biomarker strategies (CRP and TMB/BRAF) rather than three.

2. **Both interactions estimated simultaneously**: The shared formula includes both `crp:Rx` and `tmb_braf:Rx` interaction terms, meaning each biomarker's treatment effect is estimated while adjusting for the other.

3. **Changed cost-effectiveness profile**: The model redesign affects the estimated incremental effects and ICERs, with CRP showing improved cost-effectiveness and TMB/BRAF showing a larger treatment benefit (and consequently lower ICER) compared to the OLD model specification.

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 1.2
