---
title: "Model B Comparison: Original vs Current Design"
subtitle: "METIMMOX-1 Economic Evaluation"
author: "Ben Geisler"
date: "`r Sys.Date()`"
format:
  pdf:
    toc: true
    toc-depth: 3
    number-sections: true
    fig-width: 8
    fig-height: 6
    keep-tex: false
    geometry:
      - top=2.5cm
      - bottom=2.5cm
      - left=2.5cm
      - right=2.5cm
    fontsize: 11pt
    documentclass: article
    classoption: [a4paper]
execute:
  echo: false
  warning: false
  message: false
  cache: false
  fig-cap-location: bottom
  tbl-cap-location: top
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
knitr::opts_knit$set(root.dir = here::here())

# Load packages BEFORE sourcing scripts
if (!require("pacman")) install.packages("pacman")
pacman::p_load(here, survival, flexsurv, dplyr, ggplot2, knitr, kableExtra, tidyr)
```

# Introduction

This document compares the **Original** and **Current** Model B (Focused) designs to document the methodological change and its impact on survival predictions.

## Summary of Changes

| Aspect | Original Model B | Current Model B |
|--------|-----------------|-----------------|
| Biomarkers as main effects | crp + tlr + tmb_braf (all three) | crp + tmb_braf (tlr dropped as main effect) |
| Interaction terms | One per strategy (crp:Rx, tlr:Rx, or tmb_braf:Rx) | CRP/TMB: both (crp:Rx + tmb_braf:Rx); TLR: tlr:Rx only |
| Strategies evaluated | control, crp, tlr, tmb_braf | control, crp, tlr, tmb_braf |
| Number of distinct formulas | 3 (one per strategy, all unique) | 2 (CRP/TMB shared + TLR separate) |

## Rationale for Change

The Original Model B included all three biomarkers (crp, tlr, tmb_braf) as main effects in every strategy formula, with only the strategy-specific biomarker having a treatment interaction. The Current Model B was redesigned to:

1. **Drop `tlr` as a main effect** - TLR is not included as a prognostic main effect in other strategies' formulas
2. **Add both CRP and TMB/BRAF interactions** for the CRP and TMB/BRAF strategies - these two biomarkers share a formula with both interaction terms (`crp:Rx + tmb_braf:Rx`)
3. **Keep TLR interaction only** for the TLR strategy - TLR's treatment effect is estimated with only `tlr:Rx`, adjusting for CRP and TMB/BRAF as main effects
4. **Use centralized configuration** via `model_configs.R` as the single source of truth

```{r pagebreak-1, results='asis'}
cat("\\newpage\n")
```

# Methodology

```{r load-data, include=FALSE}
# Source analysis scripts - suppress all output
invisible(capture.output({
  source(here("scripts/R/analysis/02_setup_and_global_variables.R"))
  source(here("scripts/R/analysis/03_biomarker_strategies.R"))
  source(here("scripts/R/analysis/06_parametric_survival_analysis.R"))
  source(here("scripts/R/analysis/07_basecase_input_parameters.R"))
}))

# Re-load packages after rm(list=ls()) in sourced scripts
pacman::p_load(here, survival, flexsurv, dplyr, ggplot2, knitr, kableExtra, tidyr)

# Source calculate_outcomes for cost/QALY computation in economic sections
source(here("scripts/R/functions/calculate_outcomes.R"))

# Set ggplot theme
theme_set(theme_minimal() +
  theme(
    text = element_text(size = 11),
    axis.text = element_text(size = 9),
    legend.position = "bottom"
  ))

# Ensure categorical variables are properly coded
data$crp <- as.factor(data$crp)
data$tlr <- as.factor(data$tlr)
data$tmb_braf <- as.factor(data$tmb_braf)

# Create complete dataset
data_complete <- data[complete.cases(data[, c("Age", "sex", "Rx", "crp", "tlr", "tmb_braf", "OSwk", "Death", "PFSwk", "Progression")]), ]

# Time points for predictions
pred_times <- seq(0, 520, by = 4)  # Every 4 weeks for 10 years
```

## Formula Definitions

### Original Model B (per-strategy, all 3 biomarkers as main effects)

Each strategy has its own formula with all three biomarkers as main effects plus only the strategy-specific interaction:

- CRP: `Surv(...) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx`
- TLR: `Surv(...) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx`
- TMB/BRAF: `Surv(...) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx`

### Current Model B (per-strategy, CRP/TMB shared + TLR separate)

CRP and TMB/BRAF share a formula with both interactions; TLR has its own formula:

- CRP: `Surv(...) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx`
- TLR: `Surv(...) ~ Age + sex + Rx + crp + tmb_braf + tlr:Rx`
- TMB/BRAF: `Surv(...) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx`

```{r define-formulas}
# Original Model B formulas (per-strategy, all 3 biomarkers as main effects)
orig_formulas <- list(
  crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + crp:Rx
  ),
  tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + tlr:Rx
  ),
  tmb_braf = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tlr + tmb_braf + tmb_braf:Rx
  )
)

# Current Model B formulas (per-strategy, CRP/TMB shared + TLR separate)
current_formulas <- list(
  crp = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
  ),
  tlr = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + tlr:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + tlr:Rx
  ),
  tmb_braf = list(
    os = Surv(OSwk, Death) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx,
    pfs = Surv(PFSwk, Progression) ~ Age + sex + Rx + crp + tmb_braf + crp:Rx + tmb_braf:Rx
  )
)

# Control formula (age- and sex-adjusted only, fitted on control-arm patients)
control_formula_os <- Surv(OSwk, Death) ~ Age + sex
control_formula_pfs <- Surv(PFSwk, Progression) ~ Age + sex
```

## Formula Comparison Table

```{r formula-table}
# Build a compact formula comparison table showing only distinguishing terms
# All formulas share "Age + sex + Rx + ..." prefix; OS and PFS use same RHS
formula_table <- data.frame(
  Strategy = c("CRP", "TLR", "TMB/BRAF"),
  Orig_Main = c("crp + tlr + tmb/braf", "crp + tlr + tmb/braf", "crp + tlr + tmb/braf"),
  Orig_Interaction = c("crp:Rx", "tlr:Rx", "tmb/braf:Rx"),
  Curr_Main = c("crp + tmb/braf", "crp + tlr + tmb/braf", "crp + tmb/braf"),
  Curr_Interaction = c("crp:Rx + tmb/braf:Rx", "tlr:Rx", "crp:Rx + tmb/braf:Rx"),
  stringsAsFactors = FALSE
)

kable(formula_table,
      col.names = c("Strategy", "Main Effects", "Interactions",
                     "Main Effects", "Interactions"),
      caption = "Formula Comparison: Original vs Current Model B. All formulas share the common prefix Age + sex + Rx. OS and PFS use the same right-hand side.",
      booktabs = TRUE,
      escape = FALSE) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 9) %>%
  add_header_above(c(" " = 1, "Original Model B" = 2, "Current Model B" = 2))
```

**Key differences:**

- **Main effects**: Original includes `tlr` as a main effect in all formulas; Current drops `tlr`
- **Interactions**: Original has one interaction per strategy; Current CRP/TMB have *both* `crp:Rx + tmb_braf:Rx`
- **TLR formula**: Original adjusts for all 3 biomarkers (crp + tlr + tmb_braf); Current adjusts for crp + tmb_braf only

\newpage

# Model Fitting

```{r fit-models}
# Fit Original Model B (per-strategy)
orig_fits <- list()
for (biomarker in names(orig_formulas)) {
  orig_fits[[biomarker]] <- tryCatch({
    list(
      os = flexsurvreg(orig_formulas[[biomarker]]$os, data = data_complete, dist = "gamma"),
      pfs = flexsurvreg(orig_formulas[[biomarker]]$pfs, data = data_complete, dist = "gamma")
    )
  }, error = function(e) {
    message("Error fitting Original Model B for ", biomarker, ": ", e$message)
    NULL
  })
}

# Fit Current Model B (per-strategy)
current_fits <- list()
for (biomarker in names(current_formulas)) {
  current_fits[[biomarker]] <- tryCatch({
    list(
      os = flexsurvreg(current_formulas[[biomarker]]$os, data = data_complete, dist = "gamma"),
      pfs = flexsurvreg(current_formulas[[biomarker]]$pfs, data = data_complete, dist = "gamma")
    )
  }, error = function(e) {
    message("Error fitting Current Model B for ", biomarker, ": ", e$message)
    NULL
  })
}

# Fit control model (age+sex adjusted, control arm only)
data_control <- data_complete[data_complete$Rx == levels(data_complete$Rx)[1], ]
control_fit <- tryCatch({
  list(
    os = flexsurvreg(control_formula_os, data = data_control, dist = "gamma"),
    pfs = flexsurvreg(control_formula_pfs, data = data_control, dist = "gamma")
  )
}, error = function(e) {
  message("Error fitting control model: ", e$message)
  NULL
})
```

## Model Fit Comparison (AIC)

```{r aic-comparison}
aic_comparison <- data.frame(
  Model = character(),
  OS_AIC = numeric(),
  PFS_AIC = numeric(),
  stringsAsFactors = FALSE
)

for (biomarker in names(orig_fits)) {
  if (!is.null(orig_fits[[biomarker]])) {
    aic_comparison <- rbind(aic_comparison, data.frame(
      Model = paste0("Original B-", toupper(biomarker)),
      OS_AIC = AIC(orig_fits[[biomarker]]$os),
      PFS_AIC = AIC(orig_fits[[biomarker]]$pfs)
    ))
  }
}

for (biomarker in names(current_fits)) {
  if (!is.null(current_fits[[biomarker]])) {
    aic_comparison <- rbind(aic_comparison, data.frame(
      Model = paste0("Current B-", toupper(biomarker)),
      OS_AIC = AIC(current_fits[[biomarker]]$os),
      PFS_AIC = AIC(current_fits[[biomarker]]$pfs)
    ))
  }
}

if (nrow(aic_comparison) > 0) {
  kable(aic_comparison,
        col.names = c("Model", "OS AIC", "PFS AIC"),
        caption = "AIC Comparison: Original vs Current Model B",
        digits = 1,
        booktabs = TRUE) %>%
    kable_styling(latex_options = c("hold_position"), font_size = 10)
} else {
  cat("Could not compute AIC values - model fitting may have failed.\n")
}
```

\newpage

# Parameter Estimates Comparison

```{r extract-coefs-function}
extract_all_coefs <- function(model, label) {
  if (is.null(model)) return(NULL)
  coefs <- coef(model)
  vcov_mat <- vcov(model)
  se <- sqrt(diag(vcov_mat))

  data.frame(
    Model = label,
    Term = names(coefs),
    Estimate = as.numeric(coefs),
    SE = as.numeric(se),
    HR = exp(as.numeric(coefs)),
    stringsAsFactors = FALSE,
    row.names = NULL
  )
}

format_coef_table <- function(coef_df) {
  if (is.null(coef_df) || nrow(coef_df) == 0) return(NULL)
  coef_df$HR_CI <- sprintf("%.3f (%.3f-%.3f)",
                            coef_df$HR,
                            exp(coef_df$Estimate - 1.96 * coef_df$SE),
                            exp(coef_df$Estimate + 1.96 * coef_df$SE))
  display_df <- coef_df[, c("Term", "Estimate", "SE", "HR_CI")]
  names(display_df) <- c("Term", "Estimate", "SE", "HR (95% CI)")
  return(display_df)
}
```

## CRP Strategy - OS Coefficients

```{r os-crp-coefs}
orig_crp <- extract_all_coefs(orig_fits$crp$os, "Original B-CRP")
curr_crp <- extract_all_coefs(current_fits$crp$os, "Current B-CRP")

if (!is.null(orig_crp)) {
  kable(format_coef_table(orig_crp), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Original Model B-CRP - OS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

if (!is.null(curr_crp)) {
  kable(format_coef_table(curr_crp), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Current Model B-CRP - OS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

## TLR Strategy - OS Coefficients

```{r os-tlr-coefs}
orig_tlr <- extract_all_coefs(orig_fits$tlr$os, "Original B-TLR")
curr_tlr <- extract_all_coefs(current_fits$tlr$os, "Current B-TLR")

if (!is.null(orig_tlr)) {
  kable(format_coef_table(orig_tlr), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Original Model B-TLR - OS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

if (!is.null(curr_tlr)) {
  kable(format_coef_table(curr_tlr), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Current Model B-TLR - OS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

## TMB/BRAF Strategy - OS Coefficients

```{r os-tmb-coefs}
orig_tmb <- extract_all_coefs(orig_fits$tmb_braf$os, "Original B-TMB")
curr_tmb <- extract_all_coefs(current_fits$tmb_braf$os, "Current B-TMB")

if (!is.null(orig_tmb)) {
  kable(format_coef_table(orig_tmb), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Original Model B-TMB/BRAF - OS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

if (!is.null(curr_tmb)) {
  kable(format_coef_table(curr_tmb), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Current Model B-TMB/BRAF - OS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

## CRP Strategy - PFS Coefficients

```{r pfs-crp-coefs}
orig_crp_pfs <- extract_all_coefs(orig_fits$crp$pfs, "Original B-CRP")
curr_crp_pfs <- extract_all_coefs(current_fits$crp$pfs, "Current B-CRP")

if (!is.null(orig_crp_pfs)) {
  kable(format_coef_table(orig_crp_pfs), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Original Model B-CRP - PFS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

if (!is.null(curr_crp_pfs)) {
  kable(format_coef_table(curr_crp_pfs), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Current Model B-CRP - PFS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

## TLR Strategy - PFS Coefficients

```{r pfs-tlr-coefs}
orig_tlr_pfs <- extract_all_coefs(orig_fits$tlr$pfs, "Original B-TLR")
curr_tlr_pfs <- extract_all_coefs(current_fits$tlr$pfs, "Current B-TLR")

if (!is.null(orig_tlr_pfs)) {
  kable(format_coef_table(orig_tlr_pfs), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Original Model B-TLR - PFS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

if (!is.null(curr_tlr_pfs)) {
  kable(format_coef_table(curr_tlr_pfs), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Current Model B-TLR - PFS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

## TMB/BRAF Strategy - PFS Coefficients

```{r pfs-tmb-coefs}
orig_tmb_pfs <- extract_all_coefs(orig_fits$tmb_braf$pfs, "Original B-TMB")
curr_tmb_pfs <- extract_all_coefs(current_fits$tmb_braf$pfs, "Current B-TMB")

if (!is.null(orig_tmb_pfs)) {
  kable(format_coef_table(orig_tmb_pfs), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Original Model B-TMB/BRAF - PFS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}

if (!is.null(curr_tmb_pfs)) {
  kable(format_coef_table(curr_tmb_pfs), booktabs = TRUE, digits = 3, row.names = FALSE,
        caption = "Current Model B-TMB/BRAF - PFS Coefficients") %>%
    kable_styling(latex_options = c("hold_position"), font_size = 9)
}
```

\newpage

# Survival Curves Comparison

```{r generate-predictions}
# Function to get population-averaged survival predictions
get_surv_pred_newdata <- function(model, times, newdata) {
  if (is.null(model)) return(NULL)
  tryCatch({
    pred <- summary(model, t = times, newdata = newdata, type = "survival", ci = FALSE)
    survs <- sapply(pred, function(x) x$est)
    if (is.matrix(survs)) rowMeans(survs) else survs
  }, error = function(e) {
    message("Prediction error: ", e$message)
    NULL
  })
}

# Get biomarker prevalences
p_crp <- mean(as.numeric(as.character(data_complete$crp)))
p_tlr <- mean(as.numeric(as.character(data_complete$tlr)))
p_tmb <- mean(as.numeric(as.character(data_complete$tmb_braf)))

os_preds <- list()
pfs_preds <- list()

# ============================================================================
# Control predictions (age+sex adjusted, all control patients)
# ============================================================================
if (!is.null(control_fit)) {
  os_preds[["CTRL"]] <- get_surv_pred_newdata(control_fit$os, pred_times, data_control)
  pfs_preds[["CTRL"]] <- get_surv_pred_newdata(control_fit$pfs, pred_times, data_control)
}

# ============================================================================
# Original Model B predictions (per-strategy, all 3 biomarkers as main effects)
# ============================================================================
for (bm in names(orig_fits)) {
  if (!is.null(orig_fits[[bm]])) {
    data_pos <- data_complete[data_complete[[bm]] == "1", ]
    data_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))
    data_neg <- data_complete[data_complete[[bm]] == "0", ]
    data_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))

    prev <- switch(bm, crp = p_crp, tlr = p_tlr, tmb_braf = p_tmb)

    os_pos <- get_surv_pred_newdata(orig_fits[[bm]]$os, pred_times, data_pos)
    os_neg <- get_surv_pred_newdata(orig_fits[[bm]]$os, pred_times, data_neg)
    pfs_pos <- get_surv_pred_newdata(orig_fits[[bm]]$pfs, pred_times, data_pos)
    pfs_neg <- get_surv_pred_newdata(orig_fits[[bm]]$pfs, pred_times, data_neg)

    if (!is.null(os_pos) && !is.null(os_neg)) {
      os_preds[[paste0("ORIG_", bm)]] <- prev * os_pos + (1 - prev) * os_neg
    }
    if (!is.null(pfs_pos) && !is.null(pfs_neg)) {
      pfs_preds[[paste0("ORIG_", bm)]] <- prev * pfs_pos + (1 - prev) * pfs_neg
    }
  }
}

# ============================================================================
# Current Model B predictions (per-strategy formulas)
# ============================================================================
for (bm in names(current_fits)) {
  if (!is.null(current_fits[[bm]])) {
    data_pos <- data_complete[data_complete[[bm]] == "1", ]
    data_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))
    data_neg <- data_complete[data_complete[[bm]] == "0", ]
    data_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))

    prev <- switch(bm, crp = p_crp, tlr = p_tlr, tmb_braf = p_tmb)

    os_pos <- get_surv_pred_newdata(current_fits[[bm]]$os, pred_times, data_pos)
    os_neg <- get_surv_pred_newdata(current_fits[[bm]]$os, pred_times, data_neg)
    pfs_pos <- get_surv_pred_newdata(current_fits[[bm]]$pfs, pred_times, data_pos)
    pfs_neg <- get_surv_pred_newdata(current_fits[[bm]]$pfs, pred_times, data_neg)

    if (!is.null(os_pos) && !is.null(os_neg)) {
      os_preds[[paste0("CURR_", bm)]] <- prev * os_pos + (1 - prev) * os_neg
    }
    if (!is.null(pfs_pos) && !is.null(pfs_neg)) {
      pfs_preds[[paste0("CURR_", bm)]] <- prev * pfs_pos + (1 - prev) * pfs_neg
    }
  }
}
```

```{r generate-weekly-predictions}
# ============================================================================
# WEEKLY PREDICTIONS for economic calculations
# Treatment schedules in l_params_base are weekly vectors (length 521).
# We also store subgroup-specific (pos/neg) predictions for cost computation.
# ============================================================================

weekly_times <- seq(0, 520, by = 1)  # 521 weekly time points

# Storage: nested lists keyed by "CTRL", "ORIG_crp", "CURR_crp", etc.
econ_preds <- list()

# Control predictions (weekly)
if (!is.null(control_fit)) {
  econ_preds[["CTRL"]] <- list(
    os = get_surv_pred_newdata(control_fit$os, weekly_times, data_control),
    pfs = get_surv_pred_newdata(control_fit$pfs, weekly_times, data_control)
  )
}

# Original Model B (weekly, with subgroups)
for (bm in names(orig_fits)) {
  if (!is.null(orig_fits[[bm]])) {
    data_pos <- data_complete[data_complete[[bm]] == "1", ]
    data_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))
    data_neg <- data_complete[data_complete[[bm]] == "0", ]
    data_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))
    prev <- switch(bm, crp = p_crp, tlr = p_tlr, tmb_braf = p_tmb)

    os_pos_w <- get_surv_pred_newdata(orig_fits[[bm]]$os, weekly_times, data_pos)
    os_neg_w <- get_surv_pred_newdata(orig_fits[[bm]]$os, weekly_times, data_neg)
    pfs_pos_w <- get_surv_pred_newdata(orig_fits[[bm]]$pfs, weekly_times, data_pos)
    pfs_neg_w <- get_surv_pred_newdata(orig_fits[[bm]]$pfs, weekly_times, data_neg)

    key <- paste0("ORIG_", bm)
    econ_preds[[key]] <- list(
      os = prev * os_pos_w + (1 - prev) * os_neg_w,
      pfs = prev * pfs_pos_w + (1 - prev) * pfs_neg_w,
      os_pos = os_pos_w, os_neg = os_neg_w,
      pfs_pos = pfs_pos_w, pfs_neg = pfs_neg_w,
      prev = prev, biomarker = bm
    )
  }
}

# Current Model B (weekly, with subgroups)
for (bm in names(current_fits)) {
  if (!is.null(current_fits[[bm]])) {
    data_pos <- data_complete[data_complete[[bm]] == "1", ]
    data_pos$Rx <- factor(levels(data_complete$Rx)[2], levels = levels(data_complete$Rx))
    data_neg <- data_complete[data_complete[[bm]] == "0", ]
    data_neg$Rx <- factor(levels(data_complete$Rx)[1], levels = levels(data_complete$Rx))
    prev <- switch(bm, crp = p_crp, tlr = p_tlr, tmb_braf = p_tmb)

    os_pos_w <- get_surv_pred_newdata(current_fits[[bm]]$os, weekly_times, data_pos)
    os_neg_w <- get_surv_pred_newdata(current_fits[[bm]]$os, weekly_times, data_neg)
    pfs_pos_w <- get_surv_pred_newdata(current_fits[[bm]]$pfs, weekly_times, data_pos)
    pfs_neg_w <- get_surv_pred_newdata(current_fits[[bm]]$pfs, weekly_times, data_neg)

    key <- paste0("CURR_", bm)
    econ_preds[[key]] <- list(
      os = prev * os_pos_w + (1 - prev) * os_neg_w,
      pfs = prev * pfs_pos_w + (1 - prev) * pfs_neg_w,
      os_pos = os_pos_w, os_neg = os_neg_w,
      pfs_pos = pfs_pos_w, pfs_neg = pfs_neg_w,
      prev = prev, biomarker = bm
    )
  }
}
```

## Overall Survival Curves

```{r os-curves, fig.height=6, fig.cap="Overall Survival Curves: Original vs Current Model B (population-weighted strategies + control reference)"}
# Define colors and linetypes for all models
model_colors <- c(
  "CTRL" = "black",
  "ORIG_crp" = "#E69F00", "ORIG_tlr" = "#0072B2", "ORIG_tmb_braf" = "#009E73",
  "CURR_crp" = "#D55E00", "CURR_tlr" = "#56B4E9", "CURR_tmb_braf" = "#CC79A7"
)
model_labels <- c(
  "CTRL" = "Control (Age+Sex)",
  "ORIG_crp" = "Orig B-CRP", "ORIG_tlr" = "Orig B-TLR", "ORIG_tmb_braf" = "Orig B-TMB",
  "CURR_crp" = "Curr B-CRP", "CURR_tlr" = "Curr B-TLR", "CURR_tmb_braf" = "Curr B-TMB"
)
model_linetypes <- c(
  "CTRL" = "dotted",
  "ORIG_crp" = "dashed", "ORIG_tlr" = "dashed", "ORIG_tmb_braf" = "dashed",
  "CURR_crp" = "solid", "CURR_tlr" = "solid", "CURR_tmb_braf" = "solid"
)

os_plot_data <- data.frame()
for (model_name in names(os_preds)) {
  if (!is.null(os_preds[[model_name]])) {
    os_plot_data <- rbind(os_plot_data, data.frame(
      Time = pred_times / 52,
      Survival = os_preds[[model_name]],
      Model = model_name
    ))
  }
}

if (nrow(os_plot_data) > 0) {
  ggplot(os_plot_data, aes(x = Time, y = Survival, color = Model, linetype = Model)) +
    geom_line(linewidth = 1) +
    scale_color_manual(values = model_colors, labels = model_labels) +
    scale_linetype_manual(values = model_linetypes, labels = model_labels) +
    labs(x = "Time (Years)", y = "Overall Survival Probability",
         title = "Overall Survival: Original vs Current Model B") +
    coord_cartesian(ylim = c(0, 1)) +
    theme(legend.position = "bottom") +
    guides(color = guide_legend(nrow = 2), linetype = guide_legend(nrow = 2))
} else {
  cat("Could not generate OS survival curves.\n")
}
```

## Progression-Free Survival Curves

```{r pfs-curves, fig.height=6, fig.cap="Progression-Free Survival Curves: Original vs Current Model B (population-weighted strategies + control reference)"}
pfs_plot_data <- data.frame()
for (model_name in names(pfs_preds)) {
  if (!is.null(pfs_preds[[model_name]])) {
    pfs_plot_data <- rbind(pfs_plot_data, data.frame(
      Time = pred_times / 52,
      Survival = pfs_preds[[model_name]],
      Model = model_name
    ))
  }
}

if (nrow(pfs_plot_data) > 0) {
  ggplot(pfs_plot_data, aes(x = Time, y = Survival, color = Model, linetype = Model)) +
    geom_line(linewidth = 1) +
    scale_color_manual(values = model_colors, labels = model_labels) +
    scale_linetype_manual(values = model_linetypes, labels = model_labels) +
    labs(x = "Time (Years)", y = "Progression-Free Survival Probability",
         title = "PFS: Original vs Current Model B") +
    coord_cartesian(ylim = c(0, 1)) +
    theme(legend.position = "bottom") +
    guides(color = guide_legend(nrow = 2), linetype = guide_legend(nrow = 2))
} else {
  cat("Could not generate PFS survival curves.\n")
}
```

\newpage

# Life Years, QALYs, and Costs

This section compares discounted and undiscounted life-years, QALYs, costs, and ICERs between Original and Current Model B specifications.

```{r econ-helpers}
# ============================================================================
# SHARED HELPER FUNCTIONS for economic calculations
# ============================================================================

# Discount weights (weekly, length 521)
dr_c_val <- l_params_base$dr_costs
dr_e_val <- l_params_base$dr_effects
v_dw_c <- 1 / (1 + dr_c_val)^(seq(0, 520) / 52)
v_dw_e <- 1 / (1 + dr_e_val)^(seq(0, 520) / 52)
cl_val <- l_params_base$cl  # 1/52

# Calculate undiscounted life-years from 4-weekly predictions
calculate_ly <- function(survival_curve, step_weeks = 4) {
  if (is.null(survival_curve)) return(NA)
  sum(survival_curve, na.rm = TRUE) * step_weeks / 52
}

# Calculate discounted life-years from weekly survival curve
calculate_discounted_ly <- function(os_curve, dw = v_dw_e, cl = cl_val) {
  if (is.null(os_curve)) return(NA)
  sum(os_curve * dw * cl, na.rm = TRUE)
}

# Compute state occupancy from OS and PFS curves
compute_states <- function(os, pfs) {
  pfs <- pmin(pfs, os)  # PFS cannot exceed OS
  p_pf <- pfs
  p_p <- pmax(os - pfs, 0)
  p_d <- 1 - os
  p_pf[1] <- 1.0; p_p[1] <- 0.0; p_d[1] <- 0.0
  list(p_pf = p_pf, p_p = p_p, p_d = p_d)
}

# Calculate QALYs from weekly OS + PFS curves
calculate_qalys <- function(os, pfs, u_np, u_p, dw = v_dw_e, cl = cl_val) {
  if (is.null(os) || is.null(pfs)) return(NA)
  states <- compute_states(os, pfs)
  sum((states$p_pf * u_np + states$p_p * u_p) * dw * cl, na.rm = TRUE)
}

# Compute strategy-level cost and QALY using calculate_outcomes()
compute_strategy_economics <- function(pred_entry, params) {
  if (is.null(pred_entry)) return(list(cost = NA, qaly = NA))

  # For control strategy (no subgroup split)
  if (is.null(pred_entry$os_pos)) {
    states <- compute_states(pred_entry$os, pred_entry$pfs)
    res <- calculate_outcomes(
      params = params, p_pf = states$p_pf, p_p = states$p_p, p_d = states$p_d,
      treatment_type = "standard", biomarker = NULL,
      v_dw_c = v_dw_c, v_dw_e = v_dw_e, cl = cl_val
    )
    return(list(cost = res$costs_total, qaly = res$qalys_total))
  }

  # For biomarker strategy: compute subgroup outcomes separately, then weight
  prev <- pred_entry$prev
  bm <- pred_entry$biomarker

  # Positive subgroup (experimental treatment)
  states_pos <- compute_states(pred_entry$os_pos, pred_entry$pfs_pos)
  res_pos <- calculate_outcomes(
    params = params, p_pf = states_pos$p_pf, p_p = states_pos$p_p, p_d = states_pos$p_d,
    treatment_type = "experimental", biomarker = bm,
    v_dw_c = v_dw_c, v_dw_e = v_dw_e, cl = cl_val
  )

  # Negative subgroup (standard treatment)
  states_neg <- compute_states(pred_entry$os_neg, pred_entry$pfs_neg)
  res_neg <- calculate_outcomes(
    params = params, p_pf = states_neg$p_pf, p_p = states_neg$p_p, p_d = states_neg$p_d,
    treatment_type = "standard", biomarker = bm,
    v_dw_c = v_dw_c, v_dw_e = v_dw_e, cl = cl_val
  )

  # Prevalence-weighted total
  total_cost <- prev * res_pos$costs_total + (1 - prev) * res_neg$costs_total
  total_qaly <- prev * res_pos$qalys_total + (1 - prev) * res_neg$qalys_total

  return(list(cost = total_cost, qaly = total_qaly))
}
```

## Life-Years Comparison

Life-years are calculated as the area under the survival curve (restricted mean survival time) over the 10-year time horizon. Population-weighted estimates for each biomarker strategy. Discounting at `r sprintf("%.0f%%", dr_e_val * 100)` per year.

```{r life-years-comparison}
# Compute all LY values: discounted and undiscounted, OS and PFS
# Using weekly predictions (econ_preds) for all calculations
biomarkers <- c("crp", "tlr", "tmb_braf")
bm_labels <- c(crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

# Control values
ctrl_disc_os  <- calculate_discounted_ly(econ_preds[["CTRL"]]$os)
ctrl_disc_pfs <- calculate_discounted_ly(econ_preds[["CTRL"]]$pfs)
ctrl_undisc_os  <- sum(econ_preds[["CTRL"]]$os, na.rm = TRUE) * cl_val
ctrl_undisc_pfs <- sum(econ_preds[["CTRL"]]$pfs, na.rm = TRUE) * cl_val

# Build wide table: rows = outcome, columns = Control + Old/New/Delta per biomarker
outcomes <- c("Discounted LY (OS)", "Discounted LY (PFS)",
              "Undiscounted LY (OS)", "Undiscounted LY (PFS)")
ctrl_vals <- c(ctrl_disc_os, ctrl_disc_pfs, ctrl_undisc_os, ctrl_undisc_pfs)

ly_wide <- data.frame(Outcome = outcomes, Control = ctrl_vals, stringsAsFactors = FALSE)

for (bm in biomarkers) {
  orig_key <- paste0("ORIG_", bm)
  curr_key <- paste0("CURR_", bm)

  orig_disc_os  <- calculate_discounted_ly(econ_preds[[orig_key]]$os)
  orig_disc_pfs <- calculate_discounted_ly(econ_preds[[orig_key]]$pfs)
  orig_undisc_os  <- sum(econ_preds[[orig_key]]$os, na.rm = TRUE) * cl_val
  orig_undisc_pfs <- sum(econ_preds[[orig_key]]$pfs, na.rm = TRUE) * cl_val

  curr_disc_os  <- calculate_discounted_ly(econ_preds[[curr_key]]$os)
  curr_disc_pfs <- calculate_discounted_ly(econ_preds[[curr_key]]$pfs)
  curr_undisc_os  <- sum(econ_preds[[curr_key]]$os, na.rm = TRUE) * cl_val
  curr_undisc_pfs <- sum(econ_preds[[curr_key]]$pfs, na.rm = TRUE) * cl_val

  orig_vals <- c(orig_disc_os, orig_disc_pfs, orig_undisc_os, orig_undisc_pfs)
  curr_vals <- c(curr_disc_os, curr_disc_pfs, curr_undisc_os, curr_undisc_pfs)
  delta_vals <- curr_vals - orig_vals

  ly_wide[[paste0(bm, "_old")]] <- orig_vals
  ly_wide[[paste0(bm, "_new")]] <- curr_vals
  ly_wide[[paste0(bm, "_delta")]] <- delta_vals
}

# Format for display
ly_display <- ly_wide
ly_display$Control <- sprintf("%.3f", ly_display$Control)
for (bm in biomarkers) {
  ly_display[[paste0(bm, "_old")]]   <- sprintf("%.3f", ly_wide[[paste0(bm, "_old")]])
  ly_display[[paste0(bm, "_new")]]   <- sprintf("%.3f", ly_wide[[paste0(bm, "_new")]])
  ly_display[[paste0(bm, "_delta")]] <- sprintf("%+.3f", ly_wide[[paste0(bm, "_delta")]])
}

kable(ly_display,
      col.names = c("Outcome", "Control",
                     "Old", "New", "Delta",
                     "Old", "New", "Delta",
                     "Old", "New", "Delta"),
      caption = "Life-Years Comparison: Original vs Current Model B (population-weighted)",
      booktabs = TRUE,
      align = c("l", "r", rep("r", 9))) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) %>%
  add_header_above(c(" " = 2, "CRP" = 3, "TLR" = 3, "TMB/BRAF" = 3))
```

## QALYs Comparison

QALYs are computed using weekly-resolution OS and PFS predictions, with utility weights of `r sprintf("%.4f", l_params_base$u_np)` (progression-free) and `r sprintf("%.4f", l_params_base$u_p)` (progressed), discounted at `r sprintf("%.0f%%", dr_e_val * 100)` per year.

```{r qaly-comparison}
u_np <- l_params_base$u_np
u_p <- l_params_base$u_p

# Control QALY
ctrl_qaly <- calculate_qalys(econ_preds[["CTRL"]]$os, econ_preds[["CTRL"]]$pfs, u_np, u_p)

# Build wide table: single row, columns = Control + Old/New/Delta per biomarker
qaly_wide <- data.frame(Outcome = "QALYs", Control = ctrl_qaly, stringsAsFactors = FALSE)

for (bm in biomarkers) {
  orig_key <- paste0("ORIG_", bm)
  curr_key <- paste0("CURR_", bm)

  orig_qaly <- calculate_qalys(econ_preds[[orig_key]]$os, econ_preds[[orig_key]]$pfs, u_np, u_p)
  curr_qaly_bm <- calculate_qalys(econ_preds[[curr_key]]$os, econ_preds[[curr_key]]$pfs, u_np, u_p)

  qaly_wide[[paste0(bm, "_old")]] <- orig_qaly
  qaly_wide[[paste0(bm, "_new")]] <- curr_qaly_bm
  qaly_wide[[paste0(bm, "_delta")]] <- curr_qaly_bm - orig_qaly
}

# Format
qaly_display <- qaly_wide
qaly_display$Control <- sprintf("%.4f", qaly_display$Control)
for (bm in biomarkers) {
  qaly_display[[paste0(bm, "_old")]]   <- sprintf("%.4f", qaly_wide[[paste0(bm, "_old")]])
  qaly_display[[paste0(bm, "_new")]]   <- sprintf("%.4f", qaly_wide[[paste0(bm, "_new")]])
  qaly_display[[paste0(bm, "_delta")]] <- sprintf("%+.4f", qaly_wide[[paste0(bm, "_delta")]])
}

kable(qaly_display,
      col.names = c("Outcome", "Control",
                     "Old", "New", "Delta",
                     "Old", "New", "Delta",
                     "Old", "New", "Delta"),
      caption = "QALYs Comparison: Original vs Current Model B (population-weighted, discounted)",
      booktabs = TRUE,
      align = c("l", "r", rep("r", 9))) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 8) %>%
  add_header_above(c(" " = 2, "CRP" = 3, "TLR" = 3, "TMB/BRAF" = 3))
```

\newpage

## Cost Comparison

Costs include drug costs (nivolumab, FLOX), test costs (CT, blood, NGS), visit costs, follow-up costs, and end-of-life costs. Biomarker-positive patients receive experimental treatment; biomarker-negative patients receive standard treatment. Costs are prevalence-weighted and discounted.

```{r cost-comparison}
cost_table <- data.frame(
  Strategy = character(), Original_Cost = numeric(), Current_Cost = numeric(),
  stringsAsFactors = FALSE
)

# Control costs
ctrl_econ <- compute_strategy_economics(econ_preds[["CTRL"]], l_params_base)
cost_table <- rbind(cost_table, data.frame(
  Strategy = "Control", Original_Cost = ctrl_econ$cost, Current_Cost = ctrl_econ$cost
))

# Biomarker strategies
for (bm in c("crp", "tlr", "tmb_braf")) {
  bm_label <- switch(bm, crp = "CRP", tlr = "TLR", tmb_braf = "TMB/BRAF")

  orig_econ <- compute_strategy_economics(econ_preds[[paste0("ORIG_", bm)]], l_params_base)
  curr_econ <- compute_strategy_economics(econ_preds[[paste0("CURR_", bm)]], l_params_base)

  cost_table <- rbind(cost_table, data.frame(
    Strategy = bm_label,
    Original_Cost = orig_econ$cost,
    Current_Cost = curr_econ$cost
  ))
}

cost_table$Diff <- cost_table$Current_Cost - cost_table$Original_Cost

cost_display <- cost_table
cost_display$Original_Cost <- sprintf("EUR %s", format(round(cost_display$Original_Cost), big.mark = ","))
cost_display$Current_Cost <- sprintf("EUR %s", format(round(cost_display$Current_Cost), big.mark = ","))
cost_display$Diff <- ifelse(cost_table$Strategy == "Control", "-",
                             sprintf("%+.0f", cost_table$Diff))

kable(cost_display,
      col.names = c("Strategy", "Original B (Cost)", "Current B (Cost)", "Difference (EUR)"),
      caption = "Discounted Costs: Original vs Current Model B",
      booktabs = TRUE, align = c("l", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

## ICER Comparison - Original Model B

Incremental cost-effectiveness ratios (ICERs) for the Original Model B specification, comparing each biomarker strategy to the control (standard of care).

```{r icer-original}
orig_results <- data.frame(
  Strategy = c("Control", "CRP", "TLR", "TMB/BRAF"),
  Cost = numeric(4), QALY = numeric(4),
  stringsAsFactors = FALSE
)

# Control
orig_results$Cost[1] <- ctrl_econ$cost
orig_results$QALY[1] <- ctrl_qaly

# Biomarker strategies
for (i in seq_along(c("crp", "tlr", "tmb_braf"))) {
  bm <- c("crp", "tlr", "tmb_braf")[i]
  key <- paste0("ORIG_", bm)
  econ <- compute_strategy_economics(econ_preds[[key]], l_params_base)
  orig_results$Cost[i + 1] <- econ$cost
  orig_results$QALY[i + 1] <- calculate_qalys(econ_preds[[key]]$os, econ_preds[[key]]$pfs, u_np, u_p)
}

orig_results$Inc_Cost <- orig_results$Cost - orig_results$Cost[1]
orig_results$Inc_QALY <- orig_results$QALY - orig_results$QALY[1]
orig_results$ICER <- ifelse(orig_results$Strategy == "Control", NA,
                             orig_results$Inc_Cost / orig_results$Inc_QALY)

# Helper to format ICER with dominated/dominant labels
format_icer <- function(icer, inc_cost, inc_qaly, is_control) {
  if (is_control) return("Reference")
  if (inc_qaly < 0 & inc_cost > 0) return("Dominated")
  if (inc_qaly > 0 & inc_cost < 0) return("Dominant")
  if (inc_qaly < 0 & inc_cost < 0) return("Dominated")
  sprintf("EUR %s", format(round(icer), big.mark = ","))
}

orig_icer_display <- orig_results
orig_icer_display$Cost <- sprintf("EUR %s", format(round(orig_icer_display$Cost), big.mark = ","))
orig_icer_display$QALY <- sprintf("%.4f", orig_icer_display$QALY)
orig_icer_display$Inc_Cost <- ifelse(orig_results$Strategy == "Control", "-",
                                      sprintf("EUR %s", format(round(orig_results$Inc_Cost), big.mark = ",")))
orig_icer_display$Inc_QALY <- ifelse(orig_results$Strategy == "Control", "-",
                                      sprintf("%.4f", orig_results$Inc_QALY))
orig_icer_display$ICER <- mapply(format_icer,
                                  orig_results$ICER, orig_results$Inc_Cost, orig_results$Inc_QALY,
                                  orig_results$Strategy == "Control")

kable(orig_icer_display,
      col.names = c("Strategy", "Cost", "QALY", "Inc. Cost", "Inc. QALY", "ICER"),
      caption = "Cost-Effectiveness: Original Model B (vs Control)",
      booktabs = TRUE, align = c("l", "r", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9)
```

## ICER Comparison - Current Model B

```{r icer-current}
curr_results <- data.frame(
  Strategy = c("Control", "CRP", "TLR", "TMB/BRAF"),
  Cost = numeric(4), QALY = numeric(4),
  stringsAsFactors = FALSE
)

# Control (same as Original)
curr_results$Cost[1] <- ctrl_econ$cost
curr_results$QALY[1] <- ctrl_qaly

# Biomarker strategies
for (i in seq_along(c("crp", "tlr", "tmb_braf"))) {
  bm <- c("crp", "tlr", "tmb_braf")[i]
  key <- paste0("CURR_", bm)
  econ <- compute_strategy_economics(econ_preds[[key]], l_params_base)
  curr_results$Cost[i + 1] <- econ$cost
  curr_results$QALY[i + 1] <- calculate_qalys(econ_preds[[key]]$os, econ_preds[[key]]$pfs, u_np, u_p)
}

curr_results$Inc_Cost <- curr_results$Cost - curr_results$Cost[1]
curr_results$Inc_QALY <- curr_results$QALY - curr_results$QALY[1]
curr_results$ICER <- ifelse(curr_results$Strategy == "Control", NA,
                             curr_results$Inc_Cost / curr_results$Inc_QALY)

curr_icer_display <- curr_results
curr_icer_display$Cost <- sprintf("EUR %s", format(round(curr_icer_display$Cost), big.mark = ","))
curr_icer_display$QALY <- sprintf("%.4f", curr_icer_display$QALY)
curr_icer_display$Inc_Cost <- ifelse(curr_results$Strategy == "Control", "-",
                                      sprintf("EUR %s", format(round(curr_results$Inc_Cost), big.mark = ",")))
curr_icer_display$Inc_QALY <- ifelse(curr_results$Strategy == "Control", "-",
                                      sprintf("%.4f", curr_results$Inc_QALY))
curr_icer_display$ICER <- mapply(format_icer,
                                  curr_results$ICER, curr_results$Inc_Cost, curr_results$Inc_QALY,
                                  curr_results$Strategy == "Control")

kable(curr_icer_display,
      col.names = c("Strategy", "Cost", "QALY", "Inc. Cost", "Inc. QALY", "ICER"),
      caption = "Cost-Effectiveness: Current Model B (vs Control)",
      booktabs = TRUE, align = c("l", "r", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position", "scale_down"), font_size = 9)
```

\newpage

## ICER Change: Original vs Current Model B

```{r icer-change}
change_table <- data.frame(
  Strategy = c("CRP", "TLR", "TMB/BRAF"),
  Orig_Inc_Cost = orig_results$Inc_Cost[2:4],
  Orig_Inc_QALY = orig_results$Inc_QALY[2:4],
  Orig_ICER = orig_results$ICER[2:4],
  Curr_Inc_Cost = curr_results$Inc_Cost[2:4],
  Curr_Inc_QALY = curr_results$Inc_QALY[2:4],
  Curr_ICER = curr_results$ICER[2:4],
  stringsAsFactors = FALSE
)

# Determine if strategy is dominated/dominant
is_dominated <- function(inc_cost, inc_qaly) {
  (inc_qaly < 0 & inc_cost > 0) | (inc_qaly < 0 & inc_cost < 0)
}
is_dominant <- function(inc_cost, inc_qaly) {
  inc_qaly > 0 & inc_cost < 0
}

orig_dom <- is_dominated(change_table$Orig_Inc_Cost, change_table$Orig_Inc_QALY) |
            is_dominant(change_table$Orig_Inc_Cost, change_table$Orig_Inc_QALY)
curr_dom <- is_dominated(change_table$Curr_Inc_Cost, change_table$Curr_Inc_QALY) |
            is_dominant(change_table$Curr_Inc_Cost, change_table$Curr_Inc_QALY)

# Format ICER columns
format_icer_val <- function(icer, inc_cost, inc_qaly) {
  mapply(function(ic, iq, v) {
    if (iq < 0 & ic > 0) "Dominated"
    else if (iq > 0 & ic < 0) "Dominant"
    else if (iq < 0 & ic < 0) "Dominated"
    else sprintf("EUR %s", format(round(v), big.mark = ","))
  }, inc_cost, inc_qaly, icer)
}

change_display <- data.frame(
  Strategy = change_table$Strategy,
  Orig_ICER = format_icer_val(change_table$Orig_ICER, change_table$Orig_Inc_Cost, change_table$Orig_Inc_QALY),
  Curr_ICER = format_icer_val(change_table$Curr_ICER, change_table$Curr_Inc_Cost, change_table$Curr_Inc_QALY),
  stringsAsFactors = FALSE
)

# Change columns: only meaningful when both ICERs are numeric (not dominated/dominant)
both_numeric <- !orig_dom & !curr_dom
change_display$ICER_Change <- ifelse(both_numeric,
                                      sprintf("%+.0f", change_table$Curr_ICER - change_table$Orig_ICER),
                                      "-")
change_display$Pct_Change <- ifelse(both_numeric,
                                     sprintf("%+.1f%%", (change_table$Curr_ICER - change_table$Orig_ICER) / abs(change_table$Orig_ICER) * 100),
                                     "-")

kable(change_display,
      col.names = c("Strategy", "Original ICER", "Current ICER", "Change (EUR)", "Change (%)"),
      caption = "ICER Change from Original to Current Model B Specification",
      booktabs = TRUE, align = c("l", "r", "r", "r", "r")) %>%
  kable_styling(latex_options = c("hold_position"), font_size = 10)
```

# Summary

The redesign of Model B from the Original specification to the Current specification involves two key structural changes:

## Key Differences

1. **`tlr` dropped as a main effect**: The Original Model B included all three biomarkers (crp, tlr, tmb_braf) as main effects in every strategy formula, adjusting for each biomarker's prognostic effect. The Current Model B only includes crp and tmb_braf as main effects, dropping tlr.

2. **Interaction structure changed**: The Original Model B had exactly one treatment interaction per strategy (the strategy's own biomarker). The Current Model B uses both `crp:Rx + tmb_braf:Rx` for the CRP and TMB/BRAF strategies, while TLR uses only `tlr:Rx`.

3. **Both versions include all three strategies**: Both Original and Current Model B evaluate all four strategies (control, CRP, TLR, TMB/BRAF) with per-strategy formulas.

## Rationale

The Current Model B reflects the analytical judgment that:

- CRP and TMB/BRAF treatment effects are best estimated jointly (shared formula with both interactions)
- TLR's treatment effect should be estimated with its own interaction term only
- TLR's prognostic effect (as a main effect) is not needed for adjustment in other formulas

## Impact on Results

The comprehensive economic comparison above quantifies the impact of these formula changes across multiple dimensions:

- **Parameter estimates**: OS and PFS coefficients for all three biomarker strategies, showing how coefficient values change between specifications
- **Survival**: Population-weighted OS and PFS curves comparing predicted survival trajectories
- **Life-years**: Both discounted and undiscounted restricted mean survival times
- **QALYs**: Quality-adjusted outcomes incorporating utilities for progression-free and progressed states
- **Costs**: Full strategy-level costs including drug, test, visit, follow-up, and end-of-life costs
- **ICERs**: Incremental cost-effectiveness ratios versus control, and the change in ICERs between specifications

---

**Report completed on:** `r Sys.Date()`\
**Repository:** ben-geisler/METIMMOX-1\
**Report version:** 2.2
