---
title: "Export PSM to Excel"
author: "Ben Geisler"
date: "2025-09-18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Load more libraries
```{r}
if (!require("pacman")) install.packages("pacman")
library(pacman)
p_load(devtools, readxl, dplyr, tableone, ggplot2, flexsurv, survival, survminer, gems, mstate, tidyverse, xtable, darthtools, dampack, mvtnorm, Matrix)
#if (!requireNamespace("darthtools", quietly = TRUE)) {  install.packages("dampack", repos = c(
#  DARTH = 'https://raw.githubusercontent.com/DARTH-git/dampack/master/repos',
#  CRAN = 'https://cloud.r-project.org'))}
```

## load faster binary format
```{r}
rm(list = ls())
setwd("../../..") 
METIMMOX <- readRDS(file="data/tidy/METIMMOX.rds")
```


# Create partitioned survival models & export to Excel

```{r}
rm(list = setdiff(ls(), "METIMMOX"))
```


## load survival functions from DARTH

Source: <https://github.com/DARTH-git/Survival-analysis-and-decision-modeling/> Note: I have modified this code to only fit Weibul models given that not all the other models converge

```{r}
source("DARTH_surv_func.R")
```

## if necessary, can create custom function to create individual partitioned survival models

```{r}
#PSM.fun <- function()  
#{
#}
```

##setup

```{r}
# number of states in the model
v_n       <- c("non-progressed", "progressed", "dead") # state names
n_s       <- length(v_n)           # No of states 
n_i       <- 5000                  # number of simulations 
c_l       <- 1 / 52.1429                # cycle length (a week)
n_t       <- 10                    # number of years (10 years)
times     <- seq(0, n_t, c_l)  # the cycles in years
set.seed(1234)                 # set the seed


# Create a transition probability matrix  with all transitions indicated and numbered
tmat <- matrix(NA, n_s, n_s, dimnames = list(v_n,v_n))
tmat["non-progressed", "progressed"]  <- 1
tmat["non-progressed", "dead"]  <- 2
tmat["progressed"   , "dead"]  <- 3

```

##individual parametric models
### control group

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1])

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_control.csv")
#rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2])

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)

########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

###select Weibull model for now Source: <https://github.com/DARTH-git/Survival-analysis-and-decision-modeling/> Note: I have modified this code to only fit Weibul models given that not all the other models converge

```{r}
#source("DARTH_surv_func.R")
source("DARTH_surv_func weib only.R")
```

###compare Weibull models with KM curve: PFS

```{r}
METIMMOX_lim <- METIMMOX %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)

KM.pfs <- survfit(Surv(time = PFSmo, event = `Progression exit`) ~ 1, data = METIMMOX_lim)
KM.os <- survfit(Surv(time = OSmo, event = Death) ~ 1, data = METIMMOX_lim)

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

plot(KM.pfs, ylab = "Survival Probability", xlab = "Time",  main = paste ("True vs Fitted PFS")) 
lines(best.pfs,  col = 2, t = times, lty = 2)   

plot(KM.os, ylab = "Survival Probability", xlab = "Time",  main = c("True vs Fitted OS"))
lines(best.os,  col = 2, t = times, lty = 2)  

rm("METIMMOX_lim", "KM.pfs", "KM.os", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TLR reduction <10% - include

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TLRcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)
#write.csv(METIMMOX_lim, "test.csv")

########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times, extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tlr0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TLR reduction ≥10% - exclude

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TLRcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tlr1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TLR reduction <10% - exclude

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TLRcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)
#write.csv(METIMMOX_lim, "test.csv")

########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times, extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tlr0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TLR reduction ≥10% - include

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TLRcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tlr1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - CRP <5

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & CRP1cat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#rite.csv(PSM, "PSM_con_crp1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - CRP >=5

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & CRP1cat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_crp0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - CRP <5

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & CRP1cat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_crp1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - CRP >=5.0

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & CRP1cat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_crp0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TMB <=8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TMBcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tmb0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### control group - TMB >8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[1] & TMBcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_con_tmb1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TMB <=8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TMBcat == 0)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tmb0.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```

### experimental group - TMB >8

```{r}
METIMMOX_lim <- subset(METIMMOX, Rx == levels(METIMMOX$Rx)[2] & TMBcat == 1)

METIMMOX_lim <- METIMMOX_lim %>%
  select(ID, PFSmo, `Progression exit`, OSmo, Death) %>%
  mutate(PFSmo = PFSmo / 12, OSmo = OSmo / 12)


########################Partitioned Survival model ################

# fit all parametric models to the data and extract the AIC/BIC. 
# Select the one with the most appropriate fit
# Repeat for PFS and OS

fit.pfs  <- fit.fun(time ="PFSmo", status = "Progression exit", data = METIMMOX_lim, times = times, extrapolate = T) 
fit.os   <- fit.fun(time = "OSmo", status = "Death" , data = METIMMOX_lim, times = times,
                                        extrapolate = T) 

best.pfs <- fit.pfs[["Weibull"]]  
best.os  <- fit.os [["Weibull"]]

# construct a partitioned survival model out of the fitted models
PSM <- partsurv(best.pfs,best.os, time = times)$trace

#write.csv(PSM, "PSM_exp_tmb1.csv")
rm("METIMMOX_lim", "PSM", "fit.pfs", "fit.os", "best.pfs", "best.os")
```